### 2012-05-28 2011-sgr/AJ-version/referee-response-1.txt
Initial commit.

Firstly, the authors wish to thank the referee for their constructive comments. Apologies for the delay in responding to feedback.

Introduction:

1) Some references to the substructures alluded to in the first sentence should be provided.

Added reference to the Helmi 2008 review paper (2008A&ARv..15..145H), and references therein.

2) The term "admits" would more appropriately be replaced with "emphasizes".

Corrected in the revised manuscript.

Section 2. Target Selection

1) Some explicit statement should be included to the effect that, while the selection box favors a metal poor population at 40 kpc, it will also contain (and not be significantly biased against) similar metal poor stars at half that distance (e.g. the VSS).

Added "This selection box favors a metal-poor population at Sgr stream-like distances ($\sim40$ kpc) but will also contain similarly metal-poor stars at VOD/VSS distances ($\sim20$ kpc) without being significantly biased."

2) Some reference should be made to Table 1, and reasons given for choosing the particular fields observed. Are these fields part of a larger survey, or were they optimized for the VOD/VSS?

Edited to include this reference, and noted that fields were chosen to be within the VOD/Sgr region.

Section 3. Observations

1) The spectral resolution in the red arm (where the Ca lines of interest are) should be provided.

Added (R = 4400) in the revised manuscript.

2) Note that the reddening maps of Schlegel et al. (1998) have been significantly recalibrated by Schafly et al. (2010, 2011). These corrections (~14%) should be taken into account.

Corrections made using Schlafly (2010, 2011) corrections and assuming a Fitzpatrick (1999) profile where $R_V$ = 3.1 - these changes are also reflected in the manuscript.

Section 4. Dwarf/Giant separation

1) The colors in Figure 2 are somewhat difficult to sort out. Colors distinguishable by 99% of the population include black, white, and the primary colors (blue, red, and yellow) and, when it is necessary to resort to colors,  these should always be used first.

Primary colors have been used to identify metallicity, and the size of these points has been increased for clarity.

Section 6. Metallicities

1) "ascertained" is better replaced with "measured".

Corrected in the revised manuscript.

Section 7.1 Substructure Identification

1) The Gaussian halo distribution in Figure 3 doesn't look properly normalized. I.e. the area under the curve appears to be less than that under the histogram of observational velocities.  If corrected, then features B and C would then appear to be considerably less significant, though the simulation results will be unchanged.

The referee is correct in that the area under the curve is less than the area under the histogram of observational velocities. This is because the Gaussian distribution is meant to represent the underlying halo population present. Originally we have started with a Gaussian sample of 178 giants and we have removed significant (> 2.5 sigma) kinematic deviations (substructure) from the population, resulting in the Gaussian shown. This is noted in the figure caption, however it has been made more explicit;

"The Gaussian represents the halo contribution; it is normalised such that the integral equals the number of observed stars excluding those outside a 2.5-$\sigma$ excess."

2) The term "bandwidth" for the width or sigma of a normal distribution is not really appropriate. This should simply be called "width" or "sigma", both here and in Section 7.2.1

Corrected in Sections 7.1 and 7.2.1.

3) The simulation plot (Figure 4) is interesting, but somewhat difficult to interpret. For one thing, it is difficult to see individual data points superposed on the differently colored grid blocks. This figure should include a separate panel showing just the data points by themselves. Having done that, it is probably not necessary to show them superimposed on the simulations. Here again color is an issue. From context, I infer that the black (or very dark) blocks show regions in [Fe/H] vs V_GSR where the simulations rarely or never produced any stars. But this isn't clear from the color-bar, both ends of which are very dark. Moreover, the red through white through blue scaling is, to my eye, somewhat non-monotonic. In this instance, a grey scale plot would be much more readily interpreted, with very light indicating numerous simulation counts, and very dark indicating infrequent occurrences.

This plot has been separated into two panels as described, and is now in greyscale (and is noticeably easier to interpret).

Section 7.2.1

1) B_odot and Lambda_odot should be defined here (in words), rather than forcing the reader to consult LM10.

Added; "The $10^5$ Sgr debris particles are represented along the best-fit great-circle ($\Lambda_\odot$, $B_\odot$) where the longitudinal coordinate $\Lambda_\odot$ is zero in the direction of the Sgr core and increases along the trailing debris."

2) The scaling of the LM10 models should be described.  Should the particles correspond to the Sgr stream star for star? Or does each particle represent some number of stars, presumably scattered around each particle's position?  The upshot is that, while one can make arguments about relative likelihood, I don't think one can make definitive statements based on the fact that only 2 particles (stars) are found in the observed region using a prolate model. If each particle represents hundreds or thousands of stars, then Sgr stars could still outnumber all other halo stars in this region, and the population found here might well be consistent with the model. It might be interesting to examine the distribution of Sgr giants among the four observed fields. Are they distributed more or less uniformly, or is there a significant gradient? If not, this may be an additional reason to discount the prolate model, though not a conclusive one.

This has been addressed in the revised manuscript; "These $10^5$ particles are proportional to the stream density, implying a negligible stream concentration in this observable region. When the number of field configurations is accounted for, our observed Sgr K-giants are uniformly distributed across the fields."

3) Once again, Figure 6 is a bit difficult to interpret due to the colors used. Black, blue, red, and yellow would be much easier for virtually all readers.

Altered.

4) "forecast" is better replaced with "predict".

Corrected in the revised manuscript.

5) I am unclear as to why the K giants with highly negative velocities in the spherical and oblate models are "early". This should be explained or deleted.

The term was implying earlier (younger) K-giants, however the sentence did not contribute significant weight to the reasoning for why extremely negative velocity stars are not found. The sentence has been deleted.

6) I am puzzled by the "kinematic disruption may result from bifurcation". Should this have been the other way around? And in the following sentence, I don't think the authors can reasonably say that an unmodeled disruption scenario would yield "precisely" the broadening they see in their data.

Corrected, and removed the assumption about the unmodeled disruption scenario.

Section 7.2.2

1) The metallicity histogram in Figure 8 shows all stars with V_GSR < 0. However, in the text the authors refine their mean metallicity estimate using "only stars attributed to Feature A". How is this attribution made? By velocity? What limits? Is it the gray region in Figure 3? The limits should be explicitly indicated.

The region has been explicitly stated; "... the stars attributed to Feature A (as defined by the shaded region in Figure \ref{fig:velocity-histogram}, between $-140 < V_{gsr} < -30$ km s$^{-1}$) this ..."

2) One thing that isn't clear from Figure 4 (for the reasons given above) is what happens if one plots a velocity histogram for the stars in Figure 8 with [Fe/H] < -1.8.  Do they still show a bias towards highly negative velocities, or could they largely be halo contaminants?

The velocity histogram of our Figure 8 members with [Fe/H] < -1.8 peaks at $V_{gsr}$ = -115 km/s, and are generally biased towards highly negative velocities. This has been addressed in the revised manuscript: "Although there may be some halo contamination in our sample, in general our more metal-poor Feature A members have higher negative velocities, indicative of Sgr stream membership."

3) I think the last paragraph of this section is too understated. The target selection criteria certainly would have excluded the highest metallicity members of the stream. At a minimum, "slightly biased" should be "somewhat biased".

Corrected in the revised manuscript. It is also acknowledged in Sections 2 and 9 that our selection methodology is likely biased.

4) Section 7.3 - "calculated" should be "measured".

Corrected in the revised manuscript.

5) Concerning the spread in metallicity in the VSS indicating a dwarf galaxy rather than an isolated cluster, this is no longer such a convincing argument. We now know of several globular clusters with multiple populations.

Mentioned in the revised manuscript; "This led \citet{Duffau;et-al_2006} to infer the progenitor of the VSS was likely a dSph galaxy, as a large dispersion in $\mbox{[m/H]}$ indicates self-enrichment and implies the structure is a galaxy and not an isolated stellar cluster \--- although some globular clusters are also now known to contain sizeable dispersions in $\mbox{[m/H]}$."

6) The last sentence in the first paragraph should be expanded. How many stars are identified with the VSS, and what fraction of all stars with similar velocities does this represent?

Corrected in the revised manuscript.

Section 8

1) Some mention should be made in the abstract of the discovery of the carbon stars, if only to enable other researchers to search for and find this work.

Added 'carbon' to the star keywords and added "We also present data on five carbon stars which were discovered in our sample." as the final sentence in the abstract.

Section 9

1) The statement "a prolate dark halo predicts no debris" should be amended to something like "relatively little debris". Similarly, unless some argument can be made concerning the scaling of the models or the distribution of Sgr stars among the observed fields, it is presumptuous to conclude that "we would not expect Sgr debris to dominate our sample".

Amended:
"A prolate dark halo predicts relatively little debris in our observed fields. If the spheroid is prolate and LJM05 presents an accurate representation, Sgr debris may not dominate our sample (as it does so) even if we were $\Delta{}B_\odot\sim10^\circ$ closer to the great circle best-fit."

2) I think the last half of the last sentence is true, but perhaps not the first half. As noted above, looking at the velocity distribution of the most metal poor stars is required before one can conclude that they're not just halo contaminants.

Addressed in Section 7.2.2 of the revised manuscript and edited the final sentence: "These observations also demonstrate that the Sagittarius stream likely hosts a substantially larger abundance range than previously undiscovered, including a previously uncovered metal-poor population of K-giants."

### 2012-05-28 2011-sgr/AJ-version/sgr_vod_2011.tex
Initial commit.

\documentclass[preprint2]{aastex}

\shorttitle{Kinematics \& Chemistry of Halo Substructures: The Vicinity of the VOD}
\shortauthors{Casey, Keller \& Da Costa}

\begin{document}

\title{Kinematics \& Chemistry of Halo Substructures: The Vicinity of the Virgo Over-Density}

\author{Andrew R. Casey, Stefan Keller and Gary Da Costa}
\affil{Research School of Astronomy \& Astrophysics,
	Australian National University, Mt Stromlo Observatory, via Cotter Rd, Weston, ACT 2611, Australia}

\begin{abstract}
We present observations obtained with the AAT's 2dF wide field spectrograph AAOmega of K-type stars located within a region of the sky which contains the Virgo Over-Density and the leading arm of the Sagittarius Stream.  On the basis of the resulting velocity histogram we isolate populations in these overlapping regions, including Sagittarius and previously discovered Virgo groups. Through comparisons with \textit{N}-body models of the Galaxy-Sagittarius interaction, we find a tri-axial dark matter halo is favoured and we exclude a prolate shape. This result is contradictory with other observations along the Sagittarius leading arm, which typically favour prolate models.  We have also uncovered K-giant members of Sagittarius that are notably more metal poor ($\langle[$Fe/H$]\rangle = -1.7\,\pm\,0.3$) than previous studies. This suggests a significantly wider metallicity distribution exists in the Sagittarius Stream than formerly considered. We also present data on five serendipitous carbon stars which were uncovered in our sample.
\end{abstract}

\keywords{Galaxy: halo, structure --- Individual: Sagittarius, Virgo Stellar Stream --- Stars: K-giants}

\section{Introduction}
\label{sec:introduction}

The proportion of substructure recently uncovered in the Galaxy has highlighted the crucial involvement accretion has played in the formation of the Milky Way \citep{Bell;et-al_2008}. Properties of these stellar structures allow us to probe the formation mechanisms and history of the Galaxy. Recent studies \citep{Carollo;et-al_2007, Carollo;et-al_2010} have suggested multiple evolution methods are required for galaxy formation to reconcile observational evidence, although this is a subject of ongoing debate \citep{Schoenrich;et-al_2010}. Regardless, the dissipation-less merging paradigm is widely accepted, and consistent with favoured Cold Dark Matter ($\Lambda$CDM) cosmology models. Through the examination of ongoing accretion events in the Milky Way and fossils from previous mergers, we can trace the evolution of the outer most regions of the Galaxy \citep[e.g.,][]{Helmi;White_2001}.

 Accretion is at least partly \citep[e.g.,][]{Starkenburg;et-al_2009}, if not entirely responsible for the formation of the stellar halo. \citet{Bell;et-al_2008} compared Sloan Digital Sky Survey \citep[hereafter SDSS]{York;et-al_2000} data to galaxy formation simulations using different dark halos and found that observations are consistent with the stellar halo being entirely formed by hierarchical merging of accreted satellites (see also \citet{Xue;et-al_2011}).

Unquestionably the most prominent ongoing accretion event within the Milky Way is that of the Sagittarius (Sgr) dwarf Spheroidal (dSph) galaxy. Originally uncovered by \citet{Ibata;et-al_1994} as a co-moving group of K- and M-type giants, the tidal tails of Sgr circle our Galaxy. As such they have been extensively traced with red-clump stars \citep{Majewski;et-al_1999}, carbon stars \citep{Totten;Irwin_1998, Ibata;et-al_2001}, RR Lyrae stars \citep{Ivezic;et-al_2000, Vivas;et-al_2005, Keller;et-al_2008, Watkins;et-al_2009, Prior;et-al_2009b}, A-type stars \citep{Newberg;et-al_2003}, BHB stars \citep{Ruhland;et-al_2011} and K/M-giants \citep{Majewski;et-al_2003,  Yanny;et-al_2009, Keller;Yong;Da_Costa_2010}. With spatial and kinematical information, tracers originating from the host system can be unequivocally identified. This is because they remain dynamically cold, and are identifiable as kinematic substructures long after they are stripped from their progenitor \citep[for example][]{Ibata;Lewis_1998, Helmi;White_1999}.

Stellar tracers within these tails are kinematically sensitive to the galactic potential. This has led various groups to model the Sgr interaction with different dark matter profiles. \citet{Martinez-Delgado;et-al_2004} traced the Northern leading arm and found a near spherical or oblate ($q \approx 0.85$) dark matter halo best represented the observed debris, which coincided with the findings of \citet{Ibata;et-al_2001}. In contrast, \citet{Helmi_2004} found evidence in the Sgr leading debris that most favoured a prolate ($q = 1.25$) halo. \citet{Vivas;et-al_2005} found that either a prolate or spherical model of  \citet{Helmi_2004} would fit their observed RR Lyrae data, rather than those of an oblate model. \citet{Johnston;et-al_2005} later pointed out that no prolate model can reproduce the orbital pole precession of the Sgr debris, but an oblate potential could. \citet[hereafter LJM05]{Law;et-al_2005} performed simulations using data of the Sgr debris from the 2-Micron All Sky Survey (2MASS) catalogue and found that the kinematics of leading debris was best fit by prolate halos, whereas the trailing debris typically favoured oblate halos.

\citet{Belokurov;et-al_2006} found an apparent bifurcation within the Sgr debris, which \citet{Fellhauer;et-al_2006} argued can only result from a dark halo having a near spherical shape. \citet{Law;et-al_2009} introduced a tri-axial model with a varying flattening profile $q$, which replicates the orbital precession seen and matched kinematic observations of the Sgr debris. However \citet{Law;Majewski_2010} (hereafter LM10) conceded this may be a purely numerical solution as tri-axial halos are dynamically unstable, and emphasizes more kinematic measurements in other regions of the Sgr stream are required.

After the Sgr stellar stream, the Virgo Over-Density (VOD) is arguably the next most significant substructure within our Galaxy. The first over-density in the vicinity of the VOD was observed as a group of RR Lyrae stars by the QUEST survey \citep{Vivas;et-al_2001}. The collaboration later named this the ``$12\fh4$ clump'' \citep{Zinn;et-al_2004}. The broad nature of the VOD was later uncovered from the SDSS catalogue as a diffuse over-density of main-sequence turnoff stars centered at $r_\odot \sim18$ kpc \citep[which ][dubbed as S297+63-20.5]{Newberg;et-al_2002}. The nomenclature on the substructure names within this region is varied, however when referring to the VOD we are discussing the spatial over-density of stars within the region, separate from any co-moving groups.

The difficulty arises in accurately distinguishing the VOD. There are multiple substructures along this line of sight. \citet{Duffau;et-al_2006} took observations of BHB and RR Lyrae within the ``$12\fh4$ clump'' and found a common velocity of $V_{GSR} = 99.8$ km s$^{-1}$ with $\sigma_{v} = 17.3$ km s$^{-1}$. It should be noted that the dispersion in kinematics measured by \citet{Duffau;et-al_2006} is essentially their velocity precision, so the substructure may possess a much smaller $\sigma_v$. This co-moving group was coined the Virgo Stellar Stream (VSS) and thus differentiated it from the broad spatial over-density. This distinction from the VOD was somewhat strengthened with new distance measurements which placed the VOD centroid at $r_\odot = 16$ kpc \citep{Juric;et-al_2008, Keller_2010}, and the VSS 3 kpc further away \citep{Duffau;et-al_2006}. Although when considered in the light of systematic and observational uncertainties, this is of marginal significance. Moreover \citet{Juric;et-al_2008} suggests the VOD may extend between $r_\odot = 6$ to 20 kpc, which further complicates the matter of distance separation.

The relationship between the VSS and the S297+63-20.5 over-density is still unclear. \citet{Newberg;et-al_2007} found a kinematic signature of $V_{GSR} = 130 \pm 10$ km s$^{-1}$ for members of the VOD/S297+63-20.5, which is extremely close to the VSS peak. The VSS and S297+63-20.5 are co-incident in space, but their velocity difference has not yet been reconciled. The distance measurements between S297+63-20.5 and the VSS are similar enough (to within $\sim1$ kpc) within probable distance uncertainties for \citet{Newberg;et-al_2007} and \citet{Prior;et-al_2009a} to infer they are part of the same structure. \citet{Newberg;et-al_2007} estimate a distance to S297+63-20.5 of $r_\odot = 18$ kpc from $g_0 = 20.5$ turnoff stars, but they concede the structure is likely dispersed along the line of sight as the Color-Magnitude Diagram (CMD) for this region does not demonstrate a tight sequence.  Certainly this region of sky, aptly coined the 'Field of Streams' by \citet{Belokurov;et-al_2006}, is complex territory.

Photometric studies are inadequate to fully untangle this region. Kinematics are essential to identify co-moving groups that are distinct from the general halo field. Chemical information is vital to accurately distinguish these substructures and understand their origins. However, very few studies have directly investigated metallicities for these stars. In this paper we present spectroscopic observations of K-giants in this region.  Substructure kinematics are used to probe the shape of dark matter in the Galaxy. We report both the velocities and metallicities of these giants in an effort to help untangle this accretion-dominated region.

Target selection methodology is outlined in the next section, which is followed with details regarding the observations. Techniques used to separate K-giants from dwarfs are discussed in \S\ref{sec:dwarf-giant-separation}, and our analysis procedure for kinematics (\S\ref{sec:kinematics}) and metallicities (\S\ref{sec:metallicities}) follows. A discussion of substructures is outlined in \S\ref{sec:discussion} and in \S\ref{sec:conclusions} we conclude with some final remarks and critical interpretations.

\section{Target Selection}
\label{sec:target-selection}

When the presence of a stellar substructure is uncovered, K-giants provide excellent candidates for spectroscopic follow-up. They allow for precise radial velocities and chemical abundances. In order to specifically target K-giants, we have chosen candidates within the color selection box shown in Figure \ref{fig:cmd-target-selection}, taken from the SDSS DR7 catalogue. Field dwarfs are expected to contaminate the sample due to their similarity in colors. Although K-dwarfs are difficult to distinguish photometrically, we can spectroscopically separate these through the equivalent width (EW) of the  gravity-sensitive triplet Mg I lines at 5167.3, 5172.7, and 5183.6 \AA\ (see \S\ref{sec:dwarf-giant-separation}).

\begin{figure}[h]
	\includegraphics[width=\columnwidth]{./cmd_selection.eps}
	\caption{CMD of our observed regions from SDSS DR7, overlaid with the color selection criterion used to target K-giants. Appropriate Dartmouth isochrones \citep{Dotter;et-al_2008} are shown for Sgr debris at a distance of $r_\odot =40$ kpc \citep{Belokurov;et-al_2006}}
	\label{fig:cmd-target-selection}
\end{figure}

\section{Observations}
\label{sec:observations}

Our targets were observed over two runs using AAOmega on the 3.9-m Anglo-Australian Telescope at Siding Springs Observatory in New South Wales, Australia. AAOmega is a double-beam, multi-object (392) fibre-fed spectrograph covering a two degree field of view. The targets were observed in normal visitor mode in April 2009. Throughout all observations, sufficient sky and guide fibres ($\sim30$ and 7-8 respectively) were allocated to ensure optimal sky subtraction and astrometry. In total 3,453 science targets were observed within 4 fields throughout the VOD/VSS region, as outlined in Table \ref{tab:observations}. Multiple configurations were observed for most fields to permit measurements of bright ($i < 16$) and faint ($i > 16$) stars, as well as repeat observations on a subset of stars.

% NOTE TO THE EDITOR - This table ought to be in a single column.

\begin{deluxetable}{cccc}
\tablecolumns{1}
\tablewidth{0pt}
\tabletypesize{\scriptsize}
\tablecaption{Observed fields\label{tab:observations}}
\tablehead{
	\colhead{Field} &
	\colhead{$\alpha$-center} &
	\colhead{$\delta$-center} &
	\colhead{Field} \\ 
	& (J2000.0) & (J2000.0) & Configurations
}
\startdata
A & 12 00 00 & $+00$ 00 00 & 1 \\ 
B & 12 20 00 & $-01$ 00 00 & 2 \\ 
C & 12 40 00 & $-02$ 00 00 & 3 \\ 
D & 12 56 00 & $-02$ 42 00 & 6 \\ 
\enddata
\end{deluxetable}

The beam was split into the red and blue arms using the 5700 \AA{} dichroic. The 580V grating in the blue arm yields spectra between 370-580 nm, with a resolution of $R = 1300$. In the red arm we used the 1000I grating ($R = 4400$) which spans the spectral range from 800-950 nm. This coverage includes the Ca II NIR Triplet (CaT), which is used for radial velocities and metallicities. To minimise scattered-light cross talk between fibres, science targets on each configuration were limited to 1.5 magnitudes in range. Globular clusters NGC 5024, 5053 and 5904 were observed as radial velocity and metallicity standards.

The data was reduced using the 2\textsc{DFDR}\footnote{http://www.aao.gov.au/AAO/2df/aaomega} pipeline. After being flat-fielded, the fibres were throughput calibrated and the sky spectrum was subtracted using the median of the dedicated sky fibres. Wavelength calibration was achieved from arc lamp exposures taken between each set of science fields. Multiple object frames were successively taken to assist with cosmic ray removal.

\section{Dwarf / Giant separation}
\label{sec:dwarf-giant-separation}

	When discussing our data with respect to stellar streams and substructures within the halo, we are referring only to K-type giants.  Dwarfs that fall within our apparent magnitude limit are not sufficiently distant to probe halo substructures. Our resolution is adequate such that the Mg I triplet lines can be individually measured and used to discriminate dwarfs.

A grid of synthetic spectra has been generated to quantitively establish a giant/dwarf star separation criterion. The grid was generated using \citet{Castelli;Kurucz_2004} model atmospheres with MOOG\footnote{http://www.as.utexas.edu/$\sim$chris/moog.html} and the line list of \citet{Kurucz;Bell_1995}. Spectra was also generated using stellar parameters for the Sun and Arcturus. The strength of the Mg I lines were tuned to match both the Solar and Arcturus atlases of \citet{Hinkle;et-al_2003}. \citet{Girardi;et-al_2004} isochrones have been used to translate our de-reddened $g - i$ color range to effective temperature. Reddening is accounted for using the maps of \citet{Schlegel;Finkbeiner;Davis_1998}. The corresponding effective temperature region ranges from 3900 to 5200 K, and is stepped at 25 K intervals. We have assumed typical K-type surface gravities of $\log{g} = 2$ for giants and $\log{g} = 4.5$ for dwarfs. Metallicities of [Fe/H] $= -0.5$, $-1.5$, and $-2.5$ were considered for both surface gravities.

All synthetic spectra was mapped onto the same wavelength space as our observations. Intensity was convolved with a Gaussian kernel of 3.03 \AA{} to match our observed resolution with the 580V grating. Mg I line strengths for our observations and synthetic spectra is shown against $g - i$ in Figure \ref{fig:dwarf-giant-separation}. As expected, there is an overlap of Mg I strengths between metal-rich ``giants'' ($\log{g} = 2$) and metal-poor ``dwarfs'' ($\log{g} = 4.5$). However, we do not expect metal-poor dwarfs to be a principle contaminant due to their intrinsically low luminosities and paucity.

\begin{figure}[h]
	\includegraphics[width=\columnwidth]{./dwarf_giant_separation.eps}
	\caption{The sum of the Mg I triplet EWs for observations and synthetic spectra shown against the Sloan $g\,-\,i$ color. Synthetic spectra is shown for $\log{g} = 2$ ($\bigtriangleup$) and $\log{g} = 4.5$ ($\bigtriangledown$), and points are colored by metallicity. Our dwarf/giant separation line is shown (solid). }
	\label{fig:dwarf-giant-separation}
\end{figure}

 Using our synthetic grid, we have varied the slope and offset of our separation line to assess the effectiveness in differentiating giants from dwarfs.  A linear rule has been adopted to differentiate the populations, which maximises giant recoverability with minimal contamination. Using the rule,
\begin{equation}
	EW_{Mg\,I} < 3(g-i) + 0.5
\end{equation}
\noindent we identify 185 giants in our observed fields. An analysis of our 185 giant candidates revealed three stars with high proper motions, all of which lay close to our dwarf/giant separation line. This suggests they are dwarfs, and have been excluded. Some possible giant targets were discarded due to insufficient S/N, or because the Mg I triplet fell on bad columns of the detector. All efforts were made to minimise these losses. The distilled giant sample size is 178.

\section{Radial Velocities}
\label{sec:kinematics}

The Ca II triplet absorption lines at 8498.0, 8542.1 and 8662.1 \AA{}  have been used to measure radial velocities. These lines are strong, and easily identifiable in Red Giant Branch (RGB) stars even at low resolution.  Observed spectra have been cross-correlated with typical synthetic spectra of a K-giant ($T_{eff} = 4500$ K, $\log{g} = 2$, [Fe/H] $= -1.5$), and heliocentric corrections were made. Radial velocity measurements made on the standard stars in our globular clusters agree (within 3 km s$^{-1}$) with the catalogue of \citet{Harris_1996} (2011 edition). A number of our targets were observed on multiple fields, which allows us to calculate the internal measurement error. The differences between multiple measurements of the same target was calculated, and they form a half-normal distribution with a HWHM $= 3.58$ km s$^{-1}$.

In order to compare our kinematic results in a homogenous manner, we have translated our heliocentric velocities to a galactocentric frame. We have adopted the circular velocity of the Local Standard of Rest (LSR) at the Sun as 220 km s$^{-1}$ \citep{Kerr;Lynden-Bell_1986} and accounted for the Sun's peculiar velocity to the LSR by using 16.5 km s$^{-1}$ towards $l = 53^\circ, b = 25^\circ$ \citep{Mihalas;Binney_1981}. The corrected line of sight velocity is then given by,
\begin{eqnarray}
	&V_{GSR} = & V_{OBS} + 220\sin{l}\cos{b} + 16.5  \\
	& 		 &\times[\sin{b}\sin{25} + \cos{b}\cos{25}\cos{(l - 53)}] \nonumber
\end{eqnarray}
\noindent where $V_{OBS}$ is the heliocentric corrected observed line of sight velocity. A caveat to this reference transformation is that other authors in the literature have used slightly different formulae to transpose their kinematics to a galactocentric frame. This will result in a systematic shift in velocities between authors of up to $\sim11$ km s$^{-1}$.

\section{Metallicities}
\label{sec:metallicities}

We have measured metallicities for our giants using the strength of the Ca triplet lines. This technique was originally empirically described for individual stars in globular  clusters \citep{Armandroff;Da-Costa_1991}. A spectroscopic analysis using VLT/FLAMES observations of RGB stars from composite populations led \citet{Battaglia;et-al_2008} to conclude that a calibrated CaT-[Fe/H] relationship can be confidently used in composite stellar populations \citep[see also][]{Rutledge;Hesser;Stetson_1997, Starkenburg;et-al_2010}. The caveat to this technique is that a luminosity (specifically $V - V_{HB}$) is required for calibration, and we have to assume a $V_{HB}$ luminosity here. Johnson V-band magnitudes were calculated from SDSS \textit{ugriz} photometry using \citet{Jester;et-al_2005} transformations. The weaker third Ca triplet line is more susceptible to noise and residual sky-line contamination \citep{Tolstoy;et-al_2001,Battaglia;et-al_2008}. Consequently, the strongest two CaT lines (8542 and 8662\AA) have been used to form a reduced EW (W') such that,

\begin{eqnarray}
	\textstyle\sum{W}\, &=& EW_{8542} + EW_{8662} \\
	W' &=&\textstyle\sum{W} + 0.64\left(\pm 0.02\right)\left(V-V_{HB}\right)
\end{eqnarray}
\noindent and the metallicity linearly varies with W' where,
\begin{equation}
	\mbox{[Fe/H]}_{\mbox{\small{CaT}}} = (-2.81\pm0.16) + (0.44\pm0.04) W'
	\label{eq:feh-cat}
\end{equation}

Using this calibration, our globular cluster standard stars (with known $V_{HB}$ magnitudes) have metallicities that match well with the \citet{Harris_1996} catalogue (2011 edition). Only K-giants within the valid calibration range ($0 > V-V_{HB} > -3$) were considered for metallicities. We assume that we have two dominant substructures present in our observations; the leading arm of Sagittarius and the Virgo Over-Density (see \S\ref{sec:substructure-identification}). The Sagittarius stream dominates our negative $V_{GSR}$ population, and our positive kinematic space is primarily comprised of VOD members. As such we have separated our population at $V_{GSR} = 0$ km s${-1}$ into two samples with assumed $V_{HB}$ magnitudes. Although this introduces a (known) systemic effect, it is a required assumption to estimate the metallicity distribution of each population.

The horizontal branch magnitude assumed for the VSS/VOD has been ascertained from previous RR Lyrae studies. As RR Lyraes sit on the horizontal branch, the $V_{HB}$ is taken as the V-band median of four \citet{Prior;et-al_2009a} and three  \citet{Duffau;et-al_2006} VSS members to yield $\langle{}V\rangle{} = 17.09$. This combined value precisely matches the mean solely reported by \citet{Duffau;et-al_2006}. In our K-giant sample with positive galactocentric velocities, we assume $V_{HB} = 17.09$ which implies these stars are at a distance of $\sim20$ kpc.

As the distance to the Sgr debris varies greatly throughout the halo, the horizontal branch magnitude varies with the position along the stream. 
Through CMD comparisons with the Sgr core \citep{Bellazzini;et-al_2006}, \citet{Belokurov;et-al_2006} determined distances along the two branches of the Sgr bifurcation.  Revised distance measurements by \citet{Siegel;et-al_2007} (as tabulated in Table 1 of LM10) have been crucial in constraining dark halo models. Our observations lay on the edge of Branch A (Figure \ref{fig:sgr-field-of-streams}).

We have assumed distances to these stars by interpolating their position along a cubic spline fitted to published distances \citep{Siegel;et-al_2007}. Recent distance measurements of the stream by \citet{Ruhland;et-al_2011} match the stream distances used here within the uncertainties. The horizontal branch magnitude $V_{HB}$ is calculated using this assumed distance and the known luminosity of RR Lyrae stars \citep[$M_V = +0.69;$][]{Tsujimoto;et-al_1998}. Typical $V_{HB}$ magnitude derived for the Sgr members is $18.7$, at a distance of $\sim{}41$ kpc. Reddening is accounted for using the \citet{Schlegel;Finkbeiner;Davis_1998} maps. Uncertainties in distance are not interpolated; they are taken as the largest published uncertainty of the closest neighbouring data points, and this is propagated through to our reported metallicity uncertainties.

\section{Discussion}
\label{sec:discussion}

	\subsection{Substructure Identification}
	\label{sec:substructure-identification}

A significant kinematic deviation from a canonical halo population signifies a co-moving group. There are multiple substructures along our line-of-sight. These features are identified first and discussed separately. We have represented our galactocentric velocities with a generalised histogram (Figure \ref{fig:velocity-histogram}) to quantitatively compare the observed stellar kinematics against the hypothesis that the parent distribution ca be described by a canonical halo ($\mu = 0$ km s$^{-1}$, $\sigma = 101.6$ km s$^{-1}$ \citep{Sirko;et-al_2004}).

	\begin{figure}[h!]
		\includegraphics[width=\columnwidth]{./velocity_halo.eps}
		\caption{Generalised histogram of $V_{GSR}$ for our 178 K-type giants, highlighting their significance against a canonical halo population. The Gaussian is normalised such that the integral equals the number of observed stars excluding those outside a 2.5-$\sigma$ excess. Significant ($>3\sigma$) kinematic deviations from the smooth distribution are appropriately grouped and labelled.}
		\label{fig:velocity-histogram}
	\end{figure}

The generalised histogram represents each data point with a Gaussian kernel of an equal width (deviation). As our internal kinematic errors between multiple measurements summate to a half-normal distribution with a FWHM of 7.16 km s$^{-1}$, we have opted for a sigma value of 10 km s$^{-1}$ the generalised histogram in Figure \ref{fig:velocity-histogram} to avoid under-smoothing.

	\begin{figure}[h!]
		\includegraphics[width=\columnwidth]{./monte_carlo.eps}
		\caption{Monte-Carlo simulation results illustrating the number of times simulations could reproduce our observed data in the equivalent multi-dimensional bin. Significant features discussed in the text are labelled.}
		\label{fig:monte-carlo}
	\end{figure}

	\begin{figure*}[t!]
		\includegraphics[width=\textwidth]{./adapted_belokurov_2006.eps}
		\caption{Observed fields are outlined upon a panoramic view of the Sgr stream, to demonstrate our field locations in context with the Sagittarius stream. This plot is an adaptation of Figure 2 in \citet{Belokurov;et-al_2006}, which uses the 2MASS M-giant sample of \citet{Majewski;et-al_2003}.}
		\label{fig:sgr-field-of-streams}
	\end{figure*}

	The most significant ($>3\sigma$) kinematic peaks have been labeled Features A, B, and C. Features A and C are our most significant structures, and the importance of Feature B becomes more evident through Monte-Carlo simulations. Velocities and metallicities of our K-giants have been binned into grid blocks of 15 km s$^{-1}$ and 0.3 dex \--- roughly twice the error in each dimension. A population of 178 stars were randomly drawn from a simulated halo with canonical kinematics. Metallicities were randomly assigned using the observed halo Metallicity Distribution Function (MDF) of \citet{Ryan;Norris_1991}. Each simulated population was binned identically to our observed sample. Simulation grid blocks with counts equal to or exceeding stars in our equivalent observed grid block were noted, and summed after 10,000 simulations. Results from our Monte-Carlo simulations are illustrated in Figure \ref{fig:monte-carlo}. These were consistently significant when the grid was midpoint offset in both dimensions, except for the grid-block centered at $\sim185$ km s$^{-1}$ and $\sim-1.4$ dex, which has consequently been left unlabelled.

	 Substructure becomes statistically significant when the observed grid blocks are rarely replicated in Monte-Carlo simulations. Specifically, the number of members in Feature A of Figure \ref{fig:velocity-histogram} was never reproduced in some grid bins. This feature is well in excess of the halo and has a wide spread in kinematics. \citet{Chou;et-al_2007} mapped the Sgr debris across the sky using K/M-giants and found galactocentric velocity signatures between $-205$ km s$^{-1}$ to $-31$ km s$^{-1}$ in this region. As such we attribute this wide, significant kinematic peak as the leading arm of the Sagittarius tidal tail. Feature A is discussed in the next section. Another feature where grid blocks were never reproduced in our simulations was Feature C. This feature may also be attributed to Sgr debris and is discussed further in \S\ref{sec:feature-c}.

	 The clump of stars in the velocity bin centered on $V_{GSR} \approx 130$ km s$^{-1}$ and [Fe/H] $\approx -2$ was replicated only $\sim1$\% in 10,000 simulations. We attribute these members to the Virgo Stellar Stream. These members are coincident in spatial position, velocity, and metallicity with previously reported values of the VSS obtained by F turnoff/BHB stars \citep{Newberg;et-al_2007} and RR Lyrae stars \citep{Prior;et-al_2009a}. Feature B is discussed in \S\ref{sec:the-vss}.

	\subsection{Feature A \--- Sagittarius Debris}
	\label{sec:sgr-debris}

	The bounds of our observed region are overlaid upon a panoramic projection of the Sagittarius stream, and the  ``Field of Streams''  \citep{Belokurov;et-al_2006} in Figure \ref{fig:sgr-field-of-streams}. This is a crowded region of globular clusters, substructures and overlapping stellar streams, primarily populated by the Sagittarius Northern leading arm. Simply from a spatial perspective, we expect the Sgr debris to dominate our data. Although the VOD is present, it is much more diffuse.

	\subsubsection{Comparing Sagittarius Debris to Dark Matter Halo Models}

	In order to investigate the spatial coverage and kinematics of our Sagittarius members, we have compared our giants with the constant flattening spheroidal models of LJM05 and the more recent tri-axial model of LM10. The simulated data output from these is readily available online\footnote{http://www.astro.virginia.edu/$\sim$srm4n/Sgr/}, and their released models have the best-fitting parameters for each dark halo shape (prolate, spherical, oblate and tri-axial).  These are the only simulations available which make use of an all-sky data set; the 2MASS M-giant sample. We have not considered particles farther than 60 kpc to match realistic observation limitations. For comprehensive details of the simulations the reader is referred to the papers of \citet{Law;et-al_2005} and \citet{Law;Majewski_2010}.

	\begin{figure}[t!]
		\includegraphics[width=\columnwidth]{./sgr_spatial.eps}
		\caption{Our fields and observed bounds are shown with the simulated particles from multiple \textit{N}-body simulations by LJM05 and LM10. These particles are distance restricted (up to 60 kpc), and color-coded by their peri-centric passage following the same convention by \citet{Law;Majewski_2010} (orange;most recent passage, magenta; previous passage, cyan; oldest observable passage).}
		\label{fig:law-spatial}
	\end{figure}

	The Northern leading arm of Sgr is particularly sensitive both kinematically and spatially to the shape of the Milky Way dark halo (Figure \ref{fig:law-spatial}). Most models predict the Sgr stream to pass directly through our fields, whereas the prolate model predicts the edge of the stream near this region and no particles directly in our fields. Spatially, the prolate model predicts the Sgr stream to pass much lower in $B_\odot$ than our observed fields. When we extend a rectangle bounded by the edges of our fields (as per the zoomed insets in Figure \ref{fig:law-spatial}) a mere two particles are predicted. If this prolate halo model is a true representation of the Sgr debris, this does not exclude the potential of finding some Sgr debris in our fields. However, it does imply that if the LJM05 prolate model is an accurate representation of the dark halo then Sgr would not be the dominant population, contrary to our preferred interpretation of the observations.

	In comparison the tri-axial, spherical and oblate models predict varying debris from previous peri-centric passages in our fields. A kinematic comparison against our observations is necessary to evaluate model predictions. As the prolate model has only two simulated particles within our extended bounds there is no qualitative kinematic comparison to be made for this model, and as such the prolate model is excluded from further kinematic analysis.

	\begin{figure*}[t!]
		\includegraphics[width=\textwidth]{./sgr_velocities.eps}
		\caption{A generalised histogram (left) of the galactocentric rest frame velocities in our sample (dotted line) compared to the velocities (solid line) from the \textit{N}-body models of LJM05, LM10 of particles within the same spatial coverage and distance range (up to $r_\odot \sim 60$ kpc) of our observed sample. Heliocentric distances for particles used to generate each velocity histogram are shown on the right. Particles are marked by their recency of passage. A plus ($+$) denotes debris from the current peri-centric passage by Sgr, circles ($\circ$) mark the previous passage, and squares ($\square$) represent debris from two previous passages. The prolate model from LJM05 is not considered in this plot (see text).}
		\label{fig:law-vel-compare}
	\end{figure*}

	The number of predicted particles observable differs between models. Consequently the kinematics for each model have been represented as a generalised histogram (Figure \ref{fig:law-vel-compare}). For consistency all simulation output and observed data has been convolved with a Gaussian kernel of 10 km s$^{-1}$; the sigma used for the previous generalised histogram in Figure \ref{fig:velocity-histogram}. Predicted distances and peri-centric ages are shown, demonstrating that debris from multiple passages are predicted along the line of sight. A much tighter velocity sequence is predicted here by the tri-axial model than the constant flattening models. This is because the tri-axial model predicts a pericenter almost precisely in our observable region, whereas the spherical and oblate models predicts a large wrap along the line of sight, resulting in a wide spread of distances and velocities.

	Predicted distances are consistent with what we would expect from our observations. The median luminosities of our giants is $g\sim17.5$, so for the tri-axial model particles at $45$ kpc this corresponds to an absolute magnitude of $M_g\sim-0.8$; quite reasonable for a K-giant. Similarly for the spherical and oblate models, typical distances of $\sim25$ kpc will yield luminosities of $M_g\sim+0.5$ which is also reasonable.

	The spherical and oblate models also predict close-by debris with extremely negative galactocentric velocities. This signature is not represented in our data. Much closer K-giants are less likely to be identified given our luminosity range, although these early K-giants are much more numerous, so this is unlikely to explain our lack of highly negative kinematics.  The lowest observed velocity is $\sim{}-250$ km s$^{-1}$ and we have only two observations less than $V_{GSR} < -200$ km s$^{-1}$. In contrast, the spherical/oblate models predict velocities well below $V_{GSR} < -300$ km s$^{-1}$. These predicted highly negative  velocities were also not found in Sgr RR Lyrae observations taken by \citet{Prior;et-al_2009b}. If the dark matter potential is well-represented by either an oblate or spherical halo, then this discrepancy must be reconciled.

	The oblate and spherical model also illustrate a similar signature at $r_\odot \sim$12 kpc, with particle velocities ranging between $-100 < V_{GSR} < 0$ km s$^{-1}$. This is the edge of a predicted crossing-point between different wraps of the stream, which occurs at $\sim12$ kpc. These particles (and the positive kinematic signature around $\sim$20 kpc in the oblate model), are relatively minor signatures when compared to the Northern arm feature. If these signatures are present in our observed fields, their relatively low density compared to the northern arm feature would prevent them from appearing as significant.

	Although the predicted velocity distribution is narrower than what we observe, the LM10 tri-axial dark halo model best fits our observations. The observed sample broadens most prominently towards more negative galactocentric velocities at $\sim-200$ km s$^{-1}$, still well higher than oblate/spherical predictions. Halo contamination at highly negative velocities is likely to be small. One reconciliation for this tri-axial model/observed kinematic discrepancy may lie in the workings of the tri-axial model itself. Unlike other models considered, the tri-axial model does not reproduce the observed bifurcation in the Sgr stream \citep{Belokurov;et-al_2006}. Although observationally untested, it is reasonable to suggest a bifurcation may result from a significant kinematic disruption. Such an effect could result in a broader kinematic distribution \--- similar to what we observed \--- which is most notable at the stream edges.

	There is further work required through observations and simulations to reconcile kinematic discrepancies. Typical examinations of the leading arm debris usually favour prolate halos and evidence along the trailing arm typically favours oblate halos \citep{Helmi_2004, Martinez-Delgado;et-al_2004, Law;et-al_2005}. Kinematic predictions of the LM10 tri-axial model reasonably match our observations, whereas the prolate model has been excluded as significant debris is not predicted in this edge of the stream. These observations along the Northern leading arm are the first which are not reproducible with the current prolate model of LJM05, contrary to previous groups who have surveyed closer to the leading arm debris.

	\subsubsection{A Metal-Poor Population Uncovered in Sagittarius Debris}
	\label{sec:sgr-metal-poor}

	Many groups have found the population of the Sgr core to possess a mean [Fe/H] $\sim -0.5$ dex \citep{Cacciari;et-al_2002, Bonifacio;et-al_2004, Monaco;et-al_2005}. As the host circles the Milky Way the older, more metal-poor stars are preferentially stripped from the progenitor, creating a metallicity gradient along the stream \citep{Chou;et-al_2007, Keller;Yong;Da_Costa_2010}. In this region of the stream, very few Sgr member metallicies have been reported. \citet{Vivas;et-al_2005} found a mean metallicity of $\langle$[Fe/H]$\rangle = -1.77$ from spectra of 16 RR Lyraes along a nearby region of the Sgr leading arm. Similarly, \citet{Prior;et-al_2009b} found $\langle$[Fe/H]$\rangle = -1.79 \pm 0.08$ for 21 type \textit{ab} RR Lyrae stars in the region. This is somewhat expected since only the oldest, most metal-poor stars can form RR Lyraes.

	Investigating the MDF of the Sgr debris requires an unbiased sample. Generally K-giants are excellent stellar candidates for such investigations as all stars go through this evolutionary phase whereas M-giants are consistently metal-rich. If we apply the metallicity gradient found by \citet[][from M-giants]{Keller;Yong;Da_Costa_2010} to these observed K-giants, we would expect an abundance mean near $\sim{}-1.2$ dex in this observed region. The metallicity distribution for our negative $V_{GSR}$ sample is shown in Figure \ref{fig:sgr-metallicity-hist}, and illustrates a metal-poor population. The mean of our distribution is $\langle$[Fe/H]$\rangle = -1.7\,\pm\,0.3$ dex. If we include only the stars attributed to Feature A (Sgr debris) this value increases by only 0.04 dex, well within observational uncertainties. As a comparison, in a sample of metal-rich biased M-giants from the 2MASS data \citet{Chou;et-al_2007} found a mean metallicity of $\langle$[Fe/H]$\rangle = -0.72$ dex for their best subsample in the Northern leading arm of Sgr.

	\begin{figure}[h]
		\includegraphics[width=\columnwidth]{./sgr_feh_hist.eps}
		\caption{Metallicity histograms for K-giant members in our negative galactocentric velocity sample, which is largely populated by Sgr debris from the Northern leading arm.}
		\label{fig:sgr-metallicity-hist}
	\end{figure}

	It is likely that our observed K-giant sample is biased towards more metal-poor members. Given a typical distance of $r_\odot\sim 40$ kpc for the Sgr debris in this region \citep{Belokurov;et-al_2006}, a 12 Gyr old Dartmouth \citep{Dotter;et-al_2008} isochrone with a metallicity of [Fe/H] $= -1.5$ falls directly within our target selection window. The more metal-rich isochrone with [Fe/H] $= -0.5$ does not pass through our selection range. This is consistent with our observed metallicities. Although this does not prohibit the possibility of more metal-rich members within our sample, it implies that our distribution is somewhat biased towards the metal-poor end of the MDF. The tail of our Sgr distribution extends from $-0.71$ to $-2.35$ dex.

	\subsection{Feature B \--- The Virgo Stellar Stream}
	\label{sec:the-vss}

	Another substructure which was distinguished from the general over-density of the VOD is the Virgo Stellar Stream \citep{Duffau;et-al_2006}. Several RR Lyrae stars were noted with a common velocity of $V_{GSR} = 130$ km s$^{-1}$ \citep{Newberg;et-al_2007, Prior;et-al_2009a}. \citet{Prior;et-al_2009a} also measured metallicities of stars with this kinematic signature and found a mean [Fe/H] $= -1.95\,\pm\,0.1$ for the VSS, although this is based on RR Lyraes and is therefore potentially biased to the metallicity of the oldest populations. The RR Lyrae sample from \citet{Duffau;et-al_2006} found a $\langle$[Fe/H]$\rangle = -1.86$ with a much larger abundance spread of $\sigma = 0.40$, which was several times the relative uncertainty in individual values ($\sigma_{\mbox{[Fe/H]}} = 0.08$ dex). This led \citet{Duffau;et-al_2006} to infer the progenitor of the VSS was likely a dSph galaxy, as a large dispersion in $\mbox{[m/H]}$ indicates self-enrichment and implies the structure is a galaxy and not an isolated stellar cluster \--- although there are numerous globular clusters with multiple populations. Similar to \citet{Duffau;et-al_2006}, we  also observe an abundance spread within this kinematic bin including some giants with kinematics and metallicities ($V_{GSR} = 130 \pm 9$ km s$^{-1}$, [Fe/H] =$ -2.0 \pm 0.16$) matching those found by \citet{Prior;et-al_2009a}. Monte-Carlo simulations reproduced these few targets a mere $\sim1$\% in 10,000 simulations \--- demonstrating their significance.

	High resolution follow-up spectroscopy on these targets and other VSS candidates at higher metallicities in this kinematic range will provide crucial information about the origin of the VSS.  Investigating [$\alpha$/Fe] ratios in these candidates can constrain the mass of the VSS progenitor and discern whether the host was a dSph \citep{Venn;et-al_2004, Casetti-Dinescu;et-al_2009}.  Future observations are planned.

	\subsection{Feature C \--- Sagittarius debris?}
	\label{sec:feature-c}

	The last significant kinematic substructure we identify in our data is Feature C. There are two peaks identified here at $V_{GSR} = 200$ and $240$ km s$^{-1}$. These features cannot be explained by a smooth halo distribution. \citet{Newberg;et-al_2007} identified a 4-$\sigma$ peak at $V_{GSR} = 200$ km s$^{-1}$ in their sample of F turnoff stars centered on $(l, b) = (288^\circ, 62^\circ)$. Our nearest field to their plate (Field B) hosts only one star associated with this peak; most of our these stars are located within our most populated Field D. \citet{Prior;et-al_2009b} also noted stars in this kinematic range and compiled a list of authors who have also observed such peaks (see \citet{Sirko;et-al_2004, Duffau;et-al_2006, Starkenburg;et-al_2009}). \citet{Prior;et-al_2009b} argue these stars may be associated with trailing debris of Sagittarius, as suggested by models (LJM05, LM10).  Although this trailing debris would be much closer than the nearby visible leading arm, these observations support the interpretation by \citet{Prior;et-al_2009b} as the metallicities are quite similar to the nearby Sgr debris.

	This substructure has a range of metallicities on our scale. These metallicities were derived with the distance modulus to the VOD/VSS, and may not be exact representations. As such the abundance dispersion we observe is either representative, or these stars have a common metallicity and are dispersed along the line of sight. Unfortunately neither can be positively excluded without further observations. If these peaks are associated with the trailing debris of Sagittarius debris, they are likely to be further away than the VOD. On our scale that would make these stars more metal-rich than shown in Figure \ref{fig:monte-carlo}. However the nearest trailing debris particles predicted from any best-fitting dark halo potential that could explain this kinematic peak occurs at $\sim\Lambda_\odot = 310^\circ$; our observations range in $\Lambda_\odot$ between $256-273^\circ$. Whether this substructure is separate from Sagittarius debris or not remains equivocal. Nevertheless the apparent metallicities of the Feature C stars are not inconsistent with those of a Sgr population given our results for Feature A and those of \citet{Keller;Yong;Da_Costa_2010}.

\section{Carbon Stars}

	In our sample we have identified five carbon stars. With the color selections to target K-giants, this region also overlaps with where we would expect to find carbon stars (Figure \ref{fig:carbon-sdss}). Although these stars were not specifically targeted, their surface densities are so low \citep[$\approx$ 1 per 50 deg$^2$;][]{Green;et-al_1994} that we would not expect them as a substantial contaminant.  Although our sky coverage is small ($\sim$12.5 deg$^2$), the observed carbon star spatial density is $\sim20$x higher than expected. All five carbon stars are recognisable by the presence of distinctive 4737- and 5165 \AA\, Swan C$_2$ bands.

\begin{figure}[h!]
	\includegraphics[width=\columnwidth]{./carbon_stars.eps}
	\caption{Sloan \textit{u \--- g} and \textit{g \--- r} colors for our carbon stars, and the identified carbon stars and classifications by \citet{Downes;et-al_2004}. Carbon stars identified in this work have been shaded for clarity.}
	\label{fig:carbon-sdss}
\end{figure}

	 Dwarf carbon stars exhibit a spectral signature which mimics that of a typical CH-type giant carbon star, however they have anomalous JHK colors \citep{Green;et-al_1992} and high proper motions. The existence of the 4300 \AA{} CH G-band is representative of a CH-type carbon star, and is found in all five of our carbon stars. SDSS photometry for our stars match well with the F/G-type CH carbon stars identified by \citet{Downes;et-al_2004}, as seen in Figure \ref{fig:carbon-sdss}. However these targets were not spectroscopically observed in the SDSS follow-up survey SEGUE. Additionally, through comparisons with previous carbon-type star catalogues \citep{Totten;Irwin_1998, Downes;et-al_2004, Goswami;et-al_2010}, the stars tabulated in Table \ref{tb:carbon-stars} are previously unclassified carbon stars. This is largely because our objects are too faint to have been observed by previous spectroscopic carbon star surveys.

\begin{deluxetable}{cccccccccccc}
\tablewidth{0pt}
\tabletypesize{\scriptsize}
\tablecaption{Properties of carbon stars found in our sample \label{tb:carbon-stars}}
\tablehead{
	\colhead{SDSS Name J+\tablenotemark{a}} & 
	\colhead{$M_g$} &
	\colhead{\it{u-g}} &
	\colhead{\it{g-r}} &
	\colhead{\it{r-i}} &
	\colhead{\it{i-z}} &
	\colhead{\it{H-K}} &
	\colhead{\it{J-H}} &
	\colhead{$\mu_{\alpha\cos{\delta}}\tablenotemark{c}$} &
	\colhead{$\mu_\delta\tablenotemark{c}$} &
	\colhead{$V_{GSR}$} & 
	\colhead{Likely} \\
	& & & & & & & & (mas yr$^{-1}$) & (mas yr$^{-1}$) & (km s$^{-1}$) & dwarf?
}

\startdata
121740.94-001839.5 & 18.66 & 1.10 & 0.54 & 0.16 & 0.05 & ...\tablenotemark{b}& ...\tablenotemark{b} & \phn$-3.0 \pm 5.4$  & $-18.0 \pm 5.4$\phn & $\phn-71 \pm 34$ & Yes\\
121853.18-004628.4 & 17.71 & 1.67 & 0.73 & 0.22 & 0.11 & \phd0.24 & 0.36 &  \phn$-3.7 \pm 4.5$ & $-0.5 \pm 4.5$ & $+176 \pm 9$ & - \\
122053.71-011709.5 & 17.65 & 1.79 & 0.80 & 0.26 & 0.13 & \phd0.16 & 0.56 &  \phn$-7.3 \pm 4.3$ & $-3.9 \pm 4.3$ & $\phn+31 \pm 11$ & - \\
125410.80-032744.0 & 18.59 & 1.43 & 0.64 & 0.22 & 0.05 & \phd0.56 & 0.32 &$-21.1 \pm 5.0 $ & $-7.7 \pm 5.0$ & $\phn-41 \pm 9\phn$ & Yes \\ 
125416.52-031437.6 & 16.85 & 1.72 & 0.73 & 0.25 & 0.11 & -0.11 & 0.50 & $-19.8 \pm 4.2$ & \phd\phn$8.7 \pm 4.2$& $\phn+15 \pm 4\phn$ & Yes \\
\enddata
\tablenotetext{a}{To keep with convention, positional information has been truncated. Full information available through the SDSS archive.}
\tablenotetext{b}{No \textit{JHK} photometry is available for this object as it is fainter than the 2MASS survey limit.}
\tablenotetext{c}{Proper motions taken from the PPMXL Catalog \citep{Roser;et-al_2010}.}
\end{deluxetable}

	There is 2MASS photometry available for four of these stars. Of those, two stars (SDSS J125410.80-032744.0 and J125416.52-031437.6) exhibit anomalous JHK colors and significant ($> 3\sigma$) proper motions; characteristics of a dwarf carbon star. A third star also exhibits significant proper motion (SDSS J121740.94-001839.5), however JHK photometry is unavailable. The two remaining stars in our sample have JHK photometry characteristic of the F/G type CH carbon stars found by \citet{Downes;et-al_2004} in their Faint High-Latitude Carbon (FHLC) star survey (Figure \ref{fig:carbon-sdss}), and do not exhibit significant proper motion - which strongly suggests they are not dwarfs \citep{Green;et-al_1994, Deutsch_1994}. All identified K-giant stars in our distilled sample had no proper motion detectable above measurement errors.  These carbon star kinematics are representative of a typical halo population.

\section{Conclusions}
\label{sec:conclusions}

	We present spectroscopic observations of K-type stars in a crowded region of the 'Field of Streams', where significant substructure is present. We utilise the gravity-sensitive Mg I triplet to separate giants and dwarfs. Radial velocities and metallicities of 178 K-giants have been determined. We have recovered kinematic substructure found by other authors, which cannot be explained by a smooth halo distribution. Highly negative velocity signatures match those expected by the Sagittarius stream debris, and we identify a clump of K-giants with metallicities and kinematics which make them highly probable members of the Virgo Stellar Stream.

	Stars in this region of the Sagittarius stream are kinematically sensitive to the shape of the Galactic dark halo. As such, we have compared our velocity distribution to the Sgr-Milky Way dark matter models of \citet{Law;et-al_2005, Law;Majewski_2010}. Typically, leading arm debris favour prolate models and trailing arm debris favour oblate models. A prolate dark halo predicts relatively little debris in our observed fields. If the spheroid is prolate and LJM05 presents an accurate representation, we would not expect Sgr debris to dominate our sample (as it does so) even if we were $\Delta{}B_\odot\sim10^\circ$ closer to the great circle best-fit. However, Sgr debris is our most significant kinematic structure observed. No single model perfectly represents our data, although we find the more recent tri-axial model (LM10) best represents our observed kinematics. Future tri-axial models of Sgr with bifurcation treatment are likely to more closely represent our observations.

	Observed metallicities for K-giants in this region of the Sgr stream are notably lower than expected based on other Sgr samples, demonstrating the presence of a metal-poor population in the  Sagittarius debris. Although isochrones indicate we may be biased towards metal-poor members at these distances, these stars are unequivocally Sagittarius in origin. Metallicity gradients reported suggest a mean of $\langle[$Fe/H$]\rangle\sim{}-1.2$, whereas our population has $\langle[$Fe/H$]\rangle = -1.7 \pm 0.3$ dex. Previously reported metal-poor abundances in this region have been from old RR Lyraes where we would expect $\langle[$Fe/H$]\rangle\sim{}-1.7$ dex or young M-giants where $\langle[$Fe/H$]\rangle\sim{}-0.7$ dex is reasonable. Thus the sample presented here is more representative of the complete MDF. These observations also demonstrate that the Sagittarius stream hosts a substantially larger abundance range than previously found, including a previously uncovered metal-poor population of K-giants.

\section{Acknowledgements}
ARC acknowledges the financial support through the Australian Research Council Laureate Fellowship 0992131. SK and GDaC acknowledge the financial support from the Australian Research Council through Discovery Program DP0878137.

This publication makes use of data products from the Two Micron All Sky Survey, which is a joint project of the University of Massachusetts and the Infrared Processing and Analysis Center/California Institute of Technology, funded by the National Aeronautics and Space Administration and the National Science Foundation.

Funding for the SDSS and SDSS-II has been provided by the Alfred P. Sloan Foundation, the Participating Institutions, the National Science Foundation, the U.S. Department of Energy, the National Aeronautics and Space Administration, the Japanese Monbukagakusho, the Max Planck Society, and the Higher Education Funding Council for England. The SDSS Web Site is http://www.sdss.org/.

The SDSS is managed by the Astrophysical Research Consortium for the Participating Institutions. The Participating Institutions are the American Museum of Natural History, Astrophysical Institute Potsdam, University of Basel, University of Cambridge, Case Western Reserve University, University of Chicago, Drexel University, Fermilab, the Institute for Advanced Study, the Japan Participation Group, Johns Hopkins University, the Joint Institute for Nuclear Astrophysics, the Kavli Institute for Particle Astrophysics and Cosmology, the Korean Scientist Group, the Chinese Academy of Sciences (LAMOST), Los Alamos National Laboratory, the Max-Planck-Institute for Astronomy (MPIA), the Max-Planck-Institute for Astrophysics (MPA), New Mexico State University, Ohio State University, University of Pittsburgh, University of Portsmouth, Princeton University, the United States Naval Observatory, and the University of Washington.
\bibliographystyle{apj}
\bibliography{bibliography}

\end{document}

### 2012-05-28 2011-sgr/AJ-version/sgr_vod_revised_2011.tex
Initial commit.

--- 2012-05-28 2011-sgr/AJ-version/sgr_vod_2011.tex
@@
 
-\author{Andrew R. Casey, Stefan Keller and Gary Da Costa}
+\author{Andrew R. Casey, Stefan C. Keller and Gary Da Costa}
 \affil{Research School of Astronomy \& Astrophysics,
-	Australian National University, Mt Stromlo Observatory, via Cotter Rd, Weston, ACT 2611, Australia}
+	Australian National University, Mount Stromlo Observatory, via Cotter Rd, Weston, ACT 2611, Australia}
 
@@
 We present observations obtained with the AAT's 2dF wide field spectrograph AAOmega of K-type stars located within a region of the sky which contains the Virgo Over-Density and the leading arm of the Sagittarius Stream.
-On the basis of the resulting velocity histogram we isolate populations in these overlapping regions, including Sagittarius and previously discovered Virgo groups.
+On the basis of the resulting velocity histogram we isolate halo substructures in these overlapping regions including Sagittarius and previously discovered Virgo groups.
 Through comparisons with \textit{N}-body models of the Galaxy-Sagittarius interaction, we find a tri-axial dark matter halo is favoured and we exclude a prolate shape.
 This result is contradictory with other observations along the Sagittarius leading arm, which typically favour prolate models.
-We have also uncovered K-giant members of Sagittarius that are notably more metal poor ($\langle[$Fe/H$]\rangle = -1.7\,\pm\,0.3$) than previous studies.
+We have also uncovered K-giant members of Sagittarius that are notably more metal poor ($\langle[$Fe/H$]\rangle = -1.7\,\pm\,0.3$ dex) than previous studies.
 This suggests a significantly wider metallicity distribution exists in the Sagittarius Stream than formerly considered.
-We also present data on five serendipitous carbon stars which were uncovered in our sample.
+We also present data on five carbon stars which were discovered in our sample.
 \end{abstract}
 
-\keywords{Galaxy: halo, structure --- Individual: Sagittarius, Virgo Stellar Stream --- Stars: K-giants}
+\keywords{Galaxy: halo, structure --- Individual: Sagittarius, Virgo Stellar Stream --- Stars: carbon, K-giants}
 
@@
 
-The proportion of substructure recently uncovered in the Galaxy has highlighted the crucial involvement accretion has played in the formation of the Milky Way \citep{Bell;et-al_2008}.
+The proportion of substructure recently uncovered in the Galaxy has highlighted the crucial involvement accretion has played in the formation of the Milky Way \citep[see][and references therein]{Helmi_2008}.
 Properties of these stellar structures allow us to probe the formation mechanisms and history of the Galaxy.
-Recent studies \citep{Carollo;et-al_2007, Carollo;et-al_2010} have suggested multiple evolution methods are required for galaxy formation to reconcile observational evidence, although this is a subject of ongoing debate \citep{Schoenrich;et-al_2010}.
-Regardless, the dissipation-less merging paradigm is widely accepted, and consistent with favoured Cold Dark Matter ($\Lambda$CDM) cosmology models.
-Through the examination of ongoing accretion events in the Milky Way and fossils from previous mergers, we can trace the evolution of the outer most regions of the Galaxy \citep[e.g.,][]{Helmi;White_2001}.
+Recent studies \citep{Carollo;et-al_2007, Carollo;et-al_2010} have suggested multiple evolutionary paths are required for galaxy formation to reconcile observational evidence, although this is a subject of ongoing debate \citep{Schoenrich;et-al_2011}.
+Regardless, the dissipation-less merging paradigm is widely accepted and consistent with favoured Cold Dark Matter ($\Lambda$CDM) cosmology models.
+Through the examination of ongoing accretion events in the Milky Way and fossils from previous mergers we can trace the evolution of the outer most regions of the Galaxy \citep[e.g.,][]{Helmi;White_2001}.
 
@@
 Unquestionably the most prominent ongoing accretion event within the Milky Way is that of the Sagittarius (Sgr) dwarf Spheroidal (dSph) galaxy.
-Originally uncovered by \citet{Ibata;et-al_1994} as a co-moving group of K- and M-type giants, the tidal tails of Sgr circle our Galaxy.
+Originally discovered by \citet{Ibata;et-al_1994} as a co-moving group of K- and M-type giants, the tidal tails of Sgr circle our Galaxy.
 As such they have been extensively traced with red-clump stars \citep{Majewski;et-al_1999}, carbon stars \citep{Totten;Irwin_1998, Ibata;et-al_2001}, RR Lyrae stars \citep{Ivezic;et-al_2000, Vivas;et-al_2005, Keller;et-al_2008, Watkins;et-al_2009, Prior;et-al_2009b}, A-type stars \citep{Newberg;et-al_2003}, BHB stars \citep{Ruhland;et-al_2011} and K/M-giants \citep{Majewski;et-al_2003,  Yanny;et-al_2009, Keller;Yong;Da_Costa_2010}.
-With spatial and kinematical information, tracers originating from the host system can be unequivocally identified.
-This is because they remain dynamically cold, and are identifiable as kinematic substructures long after they are stripped from their progenitor \citep[for example][]{Ibata;Lewis_1998, Helmi;White_1999}.
+Tracers originating from the host system can be unequivocally identified with spatial and kinematical information because they remain dynamically cold, and are identifiable as kinematic substructures long after they are stripped from their progenitor \citep[for example][]{Ibata;Lewis_1998, Helmi;White_1999}.
 
-Stellar tracers within these tails are kinematically sensitive to the galactic potential.
+Stellar tracers within these tidal tails are kinematically sensitive to the galactic potential.
 This has led various groups to model the Sgr interaction with different dark matter profiles.
-\citet{Martinez-Delgado;et-al_2004} traced the Northern leading arm and found a near spherical or oblate ($q \approx 0.85$) dark matter halo best represented the observed debris, which coincided with the findings of \citet{Ibata;et-al_2001}.
+\citet{Martinez-Delgado;et-al_2004} traced the Northern leading arm and found a near spherical or oblate ($q \approx 0.85$) dark matter halo best represented the observed debris, coinciding with the findings of \citet{Ibata;et-al_2001}.
 In contrast, \citet{Helmi_2004} found evidence in the Sgr leading debris that most favoured a prolate ($q = 1.25$) halo.
-\citet{Vivas;et-al_2005} found that either a prolate or spherical model of  \citet{Helmi_2004} would fit their observed RR Lyrae data, rather than those of an oblate model.
-\citet{Johnston;et-al_2005} later pointed out that no prolate model can reproduce the orbital pole precession of the Sgr debris, but an oblate potential could.
+\citet{Vivas;et-al_2005} found that either a prolate or spherical model of  \citet{Helmi_2004} would fit their RR Lyrae observations, rather than those of an oblate model.
+\citet{Johnston;et-al_2005} later pointed out that no prolate model can reproduce the orbital pole precession of the Sgr debris but an oblate potential could.
 \citet[hereafter LJM05]{Law;et-al_2005} performed simulations using data of the Sgr debris from the 2-Micron All Sky Survey (2MASS) catalogue and found that the kinematics of leading debris was best fit by prolate halos, whereas the trailing debris typically favoured oblate halos.
+\citet{Prior;et-al_2009a} reached a similar conclusion.
 
-\citet{Belokurov;et-al_2006} found an apparent bifurcation within the Sgr debris, which \citet{Fellhauer;et-al_2006} argued can only result from a dark halo having a near spherical shape.
-\citet{Law;et-al_2009} introduced a tri-axial model with a varying flattening profile $q$, which replicates the orbital precession seen and matched kinematic observations of the Sgr debris.
-However \citet{Law;Majewski_2010} (hereafter LM10) conceded this may be a purely numerical solution as tri-axial halos are dynamically unstable, and emphasizes more kinematic measurements in other regions of the Sgr stream are required.
+\citet{Belokurov;et-al_2006} found an apparent bifurcation within the Sgr debris which \citet{Fellhauer;et-al_2006} argued can only result from a dark halo having a near spherical shape.
+\citet{Law;et-al_2009} introduced a tri-axial model with a varying flattening profile $q$, which replicates the orbital precession seen and matches kinematic observations of the Sgr debris.
+However \citet{Law;Majewski_2010} (hereafter LM10) concede this may be a purely numerical solution as tri-axial halos are dynamically unstable.
+They emphasize that  more kinematic measurements in other regions of the Sgr stream are required.
 
@@
 The broad nature of the VOD was later uncovered from the SDSS catalogue as a diffuse over-density of main-sequence turnoff stars centered at $r_\odot \sim18$ kpc \citep[which ][dubbed as S297+63-20.5]{Newberg;et-al_2002}.
-The nomenclature on the substructure names within this region is varied, however when referring to the VOD we are discussing the spatial over-density of stars within the region, separate from any co-moving groups.
+The nomenclature on the substructure names within this region is varied, however in this paper when referring to the VOD we are discussing the spatial over-density of stars within the region, separate from any detected co-moving groups.
 
-The difficulty arises in accurately distinguishing the VOD.
-There are multiple substructures along this line of sight.
+The difficulty arises in accurately distinguishing the VOD as there are multiple substructures along this line-of-sight.
 \citet{Duffau;et-al_2006} took observations of BHB and RR Lyrae within the ``$12\fh4$ clump'' and found a common velocity of $V_{GSR} = 99.8$ km s$^{-1}$ with $\sigma_{v} = 17.3$ km s$^{-1}$.
-It should be noted that the dispersion in kinematics measured by \citet{Duffau;et-al_2006} is essentially their velocity precision, so the substructure may possess a much smaller $\sigma_v$.
-This co-moving group was coined the Virgo Stellar Stream (VSS) and thus differentiated it from the broad spatial over-density.
+It should be noted that the dispersion in kinematics measured by \citet{Duffau;et-al_2006} is essentially their velocity precision, so the substructure may possess a much smaller kinematic dispersion.
+This co-moving group was coined the Virgo Stellar Stream (VSS) to differentiate it from the broad spatial over-density.
 This distinction from the VOD was somewhat strengthened with new distance measurements which placed the VOD centroid at $r_\odot = 16$ kpc \citep{Juric;et-al_2008, Keller_2010}, and the VSS 3 kpc further away \citep{Duffau;et-al_2006}.
-Although when considered in the light of systematic and observational uncertainties, this is of marginal significance.
-Moreover \citet{Juric;et-al_2008} suggests the VOD may extend between $r_\odot = 6$ to 20 kpc, which further complicates the matter of distance separation.
+Although, when considered in the light of systematic and observational uncertainties, this is of marginal significance.
+Additionally, \citet{Juric;et-al_2008} suggests the VOD may extend between $r_\odot = 6$ to 20 kpc, which further complicates the matter of distance separation.
 
 The relationship between the VSS and the S297+63-20.5 over-density is still unclear.
-\citet{Newberg;et-al_2007} found a kinematic signature of $V_{GSR} = 130 \pm 10$ km s$^{-1}$ for members of the VOD/S297+63-20.5, which is extremely close to the VSS peak.
+\citet{Newberg;et-al_2007} found a kinematic signature at $V_{GSR} = 130 \pm 10$ km s$^{-1}$ for members of the VOD/S297+63-20.5, which is extremely close to the VSS peak.
 The VSS and S297+63-20.5 are co-incident in space, but their velocity difference has not yet been reconciled.
-The distance measurements between S297+63-20.5 and the VSS are similar enough (to within $\sim1$ kpc) within probable distance uncertainties for \citet{Newberg;et-al_2007} and \citet{Prior;et-al_2009a} to infer they are part of the same structure.
-\citet{Newberg;et-al_2007} estimate a distance to S297+63-20.5 of $r_\odot = 18$ kpc from $g_0 = 20.5$ turnoff stars, but they concede the structure is likely dispersed along the line of sight as the Color-Magnitude Diagram (CMD) for this region does not demonstrate a tight sequence.
+The distance measurements between S297+63-20.5 and the VSS are similar enough ($\sim1$ kpc) within probable distance uncertainties for \citet{Newberg;et-al_2007} and \citet{Prior;et-al_2009a} to infer they are part of the same structure.
+\citet{Newberg;et-al_2007} estimate a distance to S297+63-20.5 of $r_\odot = 18$ kpc from $g_0 = 20.5$ turnoff stars, but they concede the structure is likely dispersed along the line-of-sight as the Color-Magnitude Diagram (CMD) for this region does not demonstrate a tight sequence.
 Certainly this region of sky, aptly coined the 'Field of Streams' by \citet{Belokurov;et-al_2006}, is complex territory.
@@
 In this paper we present spectroscopic observations of K-giants in this region.
-Substructure kinematics are used to probe the shape of dark matter in the Galaxy.
+Sgr stream kinematics are used to probe the shape of the dark matter halo in the Galaxy.
 We report both the velocities and metallicities of these giants in an effort to help untangle this accretion-dominated region.
 
-Target selection methodology is outlined in the next section, which is followed with details regarding the observations.
+Target selection methodology is outlined in the next section which is followed with details regarding the observations.
 Techniques used to separate K-giants from dwarfs are discussed in \S\ref{sec:dwarf-giant-separation}, and our analysis procedure for kinematics (\S\ref{sec:kinematics}) and metallicities (\S\ref{sec:metallicities}) follows.
-A discussion of substructures is outlined in \S\ref{sec:discussion} and in \S\ref{sec:conclusions} we conclude with some final remarks and critical interpretations.
+A discussion of substructures is outlined in \S\ref{sec:discussion}, and in \S\ref{sec:carbon-stars} we report the carbon stars discovered in our sample.
+In \S\ref{sec:conclusions} we conclude with some final remarks and critical interpretations.
 
@@
 They allow for precise radial velocities and chemical abundances.
-In order to specifically target K-giants, we have chosen candidates within the color selection box shown in Figure \ref{fig:cmd-target-selection}, taken from the SDSS DR7 catalogue.
+In order to specifically target K-giants we have chosen candidates within the color selection box shown in Figure \ref{fig:cmd-target-selection}, taken from the SDSS DR7 catalogue.
+This selection box favors a metal-poor population at Sgr stream-like distances ($\sim40$ kpc) but will also contain similarly metal-poor stars at VOD/VSS distances ($\sim20$ kpc) without being significantly biased.
 Field dwarfs are expected to contaminate the sample due to their similarity in colors.
-Although K-dwarfs are difficult to distinguish photometrically, we can spectroscopically separate these through the equivalent width (EW) of the  gravity-sensitive triplet Mg I lines at 5167.3, 5172.7, and 5183.6 \AA\ (see \S\ref{sec:dwarf-giant-separation}).
+Although K-dwarfs are difficult to distinguish photometrically we can spectroscopically separate these through the equivalent width (EW) of the  gravity-sensitive Mg I triplet lines at 5167.3, 5172.7, and 5183.6 \AA\ (see \S\ref{sec:dwarf-giant-separation}).
 
 \begin{figure}[h]
-	\includegraphics[width=\columnwidth]{./cmd_selection.eps}
+	\includegraphics[width=\columnwidth]{./cmd.eps}
 	\caption{CMD of our observed regions from SDSS DR7, overlaid with the color selection criterion used to target K-giants.
@@
 The targets were observed in normal visitor mode in April 2009.
-Throughout all observations, sufficient sky and guide fibres ($\sim30$ and 7-8 respectively) were allocated to ensure optimal sky subtraction and astrometry.
-In total 3,453 science targets were observed within 4 fields throughout the VOD/VSS region, as outlined in Table \ref{tab:observations}.
+Throughout all observations, sufficient sky fibres ($\sim30$) were allocated to ensure optimal sky subtraction.
+In total 3,453 science targets were observed across 4 fields within the VOD/Sgr region, as outlined in Table \ref{tab:observations}.
 Multiple configurations were observed for most fields to permit measurements of bright ($i < 16$) and faint ($i > 16$) stars, as well as repeat observations on a subset of stars.
@@
 This coverage includes the Ca II NIR Triplet (CaT), which is used for radial velocities and metallicities.
-To minimise scattered-light cross talk between fibres, science targets on each configuration were limited to 1.5 magnitudes in range.
+Science targets on each configuration were limited to 1.5 magnitudes in range to minimise scattered-light cross talk between fibres.
 Globular clusters NGC 5024, 5053 and 5904 were observed as radial velocity and metallicity standards.
@@
 The data was reduced using the 2\textsc{DFDR}\footnote{http://www.aao.gov.au/AAO/2df/aaomega} pipeline.
-After being flat-fielded, the fibres were throughput calibrated and the sky spectrum was subtracted using the median of the dedicated sky fibres.
+After being flat-fielded, the fibres were throughput calibrated and the sky spectrum was subtracted using the median flux of the dedicated sky fibres.
 Wavelength calibration was achieved from arc lamp exposures taken between each set of science fields.
-Multiple object frames were successively taken to assist with cosmic ray removal.
+Multiple object frames were combined to assist with cosmic ray removal.
 
@@
 Dwarfs that fall within our apparent magnitude limit are not sufficiently distant to probe halo substructures.
-Our resolution is adequate such that the Mg I triplet lines can be individually measured and used to discriminate dwarfs.
+Our resolution is adequate such that the Mg I triplet lines can be individually measured and used to discriminate against dwarfs.
 
-A grid of synthetic spectra has been generated to quantitively establish a giant/dwarf star separation criterion.
+A grid of synthetic spectra has been generated to quantitively establish a suitable giant/dwarf separation criterion.
 The grid was generated using \citet{Castelli;Kurucz_2004} model atmospheres with MOOG\footnote{http://www.as.utexas.edu/$\sim$chris/moog.html} and the line list of \citet{Kurucz;Bell_1995}.
-Spectra was also generated using stellar parameters for the Sun and Arcturus.
+Spectra were also generated using stellar parameters for the Sun and Arcturus.
 The strength of the Mg I lines were tuned to match both the Solar and Arcturus atlases of \citet{Hinkle;et-al_2003}.
 \citet{Girardi;et-al_2004} isochrones have been used to translate our de-reddened $g - i$ color range to effective temperature.
-Reddening is accounted for using the maps of \citet{Schlegel;Finkbeiner;Davis_1998}.
+Reddening is accounted for using the \citet{Schlafly;Finkbeiner_2011} corrected dust maps of \citet{Schlegel;Finkbeiner;Davis_1998} assuming a \citet{Fitzpatrick_1999} dust profile where $R_V = 3.1$.
 The corresponding effective temperature region ranges from 3900 to 5200 K, and is stepped at 25 K intervals.
@@
 
-All synthetic spectra was mapped onto the same wavelength space as our observations.
-Intensity was convolved with a Gaussian kernel of 3.03 \AA{} to match our observed resolution with the 580V grating.
-Mg I line strengths for our observations and synthetic spectra is shown against $g - i$ in Figure \ref{fig:dwarf-giant-separation}.
+All synthetic spectra was mapped onto the same wavelength intervals before the flux was convolved with a Gaussian kernel of 3.03 \AA{} to match our 580V observations.
+Mg I line strengths for our observations and synthetic spectra are shown against $g - i$ in Figure \ref{fig:dwarf-giant-separation}.
 As expected, there is an overlap of Mg I strengths between metal-rich ``giants'' ($\log{g} = 2$) and metal-poor ``dwarfs'' ($\log{g} = 4.5$).
-However, we do not expect metal-poor dwarfs to be a principle contaminant due to their intrinsically low luminosities and paucity.
+However we do not expect metal-poor dwarfs to be a principle contaminant due to their intrinsically low luminosities and comparative rarity.
 
 \begin{figure}[h]
-	\includegraphics[width=\columnwidth]{./dwarf_giant_separation.eps}
+	\includegraphics[width=\columnwidth]{./dwarfgiant.eps}
 	\caption{The sum of the Mg I triplet EWs for observations and synthetic spectra shown against the Sloan $g\,-\,i$ color.
-Synthetic spectra is shown for $\log{g} = 2$ ($\bigtriangleup$) and $\log{g} = 4.5$ ($\bigtriangledown$), and points are colored by metallicity.
+Synthetic spectra are shown for $\log{g} = 2$ ($\bigtriangledown$) and $\log{g} = 4.5$ ($\bigtriangleup$), and points are colored by metallicity.
 Our dwarf/giant separation line is shown (solid).
@@
  Using our synthetic grid, we have varied the slope and offset of our separation line to assess the effectiveness in differentiating giants from dwarfs.
-A linear rule has been adopted to differentiate the populations, which maximises giant recoverability with minimal contamination.
+A linear rule has been adopted to differentiate the populations and maximise giant recoverability with minimal contamination.
 Using the rule,
 \begin{equation}
-	EW_{Mg\,I} < 3(g-i) + 0.5
+	EW_{Mg\,I} < 3(g-i)_o + 0.5
 \end{equation}
 \noindent we identify 185 giants in our observed fields.
-An analysis of our 185 giant candidates revealed three stars with high proper motions, all of which lay close to our dwarf/giant separation line.
-This suggests they are dwarfs, and have been excluded.
-Some possible giant targets were discarded due to insufficient S/N, or because the Mg I triplet fell on bad columns of the detector.
+An analysis of our 185 giant candidates revealed three stars with high proper motions \citep[PPMXL Catalog][]{Roser;et-al_2010}, all of which lay close to our dwarf/giant separation line.
+This suggests they are dwarfs, and they have been excluded.
+Some possible giant targets were also discarded due to insufficient S/N, or because the Mg I triplet fell on bad columns of the detector.
 All efforts were made to minimise these losses.
-The distilled giant sample size is 178.
+The distilled giant sample size is 178 stars.
+All identified K-giant stars in our distilled sample had no proper motion detectable above measurement errors.
 
@@
 These lines are strong, and easily identifiable in Red Giant Branch (RGB) stars even at low resolution.
-Observed spectra have been cross-correlated with typical synthetic spectra of a K-giant ($T_{eff} = 4500$ K, $\log{g} = 2$, [Fe/H] $= -1.5$), and heliocentric corrections were made.
-Radial velocity measurements made on the standard stars in our globular clusters agree (within 3 km s$^{-1}$) with the catalogue of \citet{Harris_1996} (2011 edition).
-A number of our targets were observed on multiple fields, which allows us to calculate the internal measurement error.
-The differences between multiple measurements of the same target was calculated, and they form a half-normal distribution with a HWHM $= 3.58$ km s$^{-1}$.
+Observed spectra have been cross-correlated with a synthetic spectrum of a typical K-giant ($T_{eff} = 4500$ K, $\log{g} = 2$, [Fe/H] $= -1.5$) to measure radial velocities.
+Heliocentric corrections were also applied.
+Radial velocity measurements made of the standard stars in our globular clusters agree (within 3 km s$^{-1}$) with the catalogue of \citet{Harris_1996} (2011 edition).
+Further, a number of our targets were observed on multiple fields, which allows us to calculate the internal measurement error.
+The differences between multiple measurements of the same target were calculated and they form a half-normal distribution with a HWHM $= 3.58$ km s$^{-1}$.
 
@@
 We have adopted the circular velocity of the Local Standard of Rest (LSR) at the Sun as 220 km s$^{-1}$ \citep{Kerr;Lynden-Bell_1986} and accounted for the Sun's peculiar velocity to the LSR by using 16.5 km s$^{-1}$ towards $l = 53^\circ, b = 25^\circ$ \citep{Mihalas;Binney_1981}.
-The corrected line of sight velocity is then given by,
+The corrected line-of-sight velocity is then given by,
 \begin{eqnarray}
@@
 \end{eqnarray}
-\noindent where $V_{OBS}$ is the heliocentric corrected observed line of sight velocity.
+\noindent where $V_{OBS}$ is the heliocentric-corrected observed line-of-sight velocity.
 A caveat to this reference transformation is that other authors in the literature have used slightly different formulae to transpose their kinematics to a galactocentric frame.
-This will result in a systematic shift in velocities between authors of up to $\sim11$ km s$^{-1}$.
+This will result in possible systematic shifts in velocities between authors of up to $\sim11$ km s$^{-1}$.
 
@@
 The caveat to this technique is that a luminosity (specifically $V - V_{HB}$) is required for calibration, and we have to assume a $V_{HB}$ luminosity here.
-Johnson V-band magnitudes were calculated from SDSS \textit{ugriz} photometry using \citet{Jester;et-al_2005} transformations.
+Johnson V-band magnitudes for our giants were calculated from SDSS \textit{ugriz} photometry using \citet{Jester;et-al_2005} transformations.
 The weaker third Ca triplet line is more susceptible to noise and residual sky-line contamination \citep{Tolstoy;et-al_2001,Battaglia;et-al_2008}.
-Consequently, the strongest two CaT lines (8542 and 8662\AA) have been used to form a reduced EW (W') such that,
+Consequently, only the strongest two CaT lines (8542 and 8662\AA) have been used to form a reduced EW (W') such that,
 
@@
 
-Using this calibration, our globular cluster standard stars (with known $V_{HB}$ magnitudes) have metallicities that match well with the \citet{Harris_1996} catalogue (2011 edition).
+Using this calibration our globular cluster standard stars (with known $V_{HB}$ magnitudes) have metallicities that match well with the \citet{Harris_1996} catalogue (2011 edition).
 Only K-giants within the valid calibration range ($0 > V-V_{HB} > -3$) were considered for metallicities.
-We assume that we have two dominant substructures present in our observations; the leading arm of Sagittarius and the Virgo Over-Density (see \S\ref{sec:substructure-identification}).
-The Sagittarius stream dominates our negative $V_{GSR}$ population, and our positive kinematic space is primarily comprised of VOD members.
-As such we have separated our population at $V_{GSR} = 0$ km s${-1}$ into two samples with assumed $V_{HB}$ magnitudes.
+We assume that we have two dominant substructures present in our observations; the leading arm of Sgr and the Virgo Over-Density (see \S\ref{sec:substructure-identification}).
+The Sgr stream dominates our negative $V_{GSR}$ population, and our positive kinematic space primarily comprises VOD and VSS members.
+As such we have separated our population at $V_{GSR} = 0$ km s$^{-1}$ into two samples with assumed $V_{HB}$ magnitudes.
 Although this introduces a (known) systemic effect, it is a required assumption to estimate the metallicity distribution of each population.
@@
 The horizontal branch magnitude assumed for the VSS/VOD has been ascertained from previous RR Lyrae studies.
-As RR Lyraes sit on the horizontal branch, the $V_{HB}$ is taken as the V-band median of four \citet{Prior;et-al_2009a} and three  \citet{Duffau;et-al_2006} VSS members to yield $\langle{}V\rangle{} = 17.09$.
-This combined value precisely matches the mean solely reported by \citet{Duffau;et-al_2006}.
+As RR Lyrae stars sit on the horizontal branch, the $V_{HB}$ is taken as the V-band median of four \citet{Prior;et-al_2009a} and three  \citet{Duffau;et-al_2006} VSS members to yield $\langle{}V\rangle{} = 17.09$.
+This combined value precisely matches the mean reported by \citet{Duffau;et-al_2006}.
 In our K-giant sample with positive galactocentric velocities, we assume $V_{HB} = 17.09$ which implies these stars are at a distance of $\sim20$ kpc.
@@
 The horizontal branch magnitude $V_{HB}$ is calculated using this assumed distance and the known luminosity of RR Lyrae stars \citep[$M_V = +0.69;$][]{Tsujimoto;et-al_1998}.
-Typical $V_{HB}$ magnitude derived for the Sgr members is $18.7$, at a distance of $\sim{}41$ kpc.
-Reddening is accounted for using the \citet{Schlegel;Finkbeiner;Davis_1998} maps.
+Typical $V_{HB}$ magnitude derived for the Sgr members is $18.7$, corresponding to a distance of $\sim{}41$ kpc.
+Reddening is accounted for using the \citet{Schlegel;Finkbeiner;Davis_1998} maps with \citet{Schlafly;Finkbeiner_2011} corrections as described in \S\ref{sec:dwarf-giant-separation}.
 Uncertainties in distance are not interpolated; they are taken as the largest published uncertainty of the closest neighbouring data points, and this is propagated through to our reported metallicity uncertainties.
+The kinematics and metallicities derived for our giant sample are discussed in the following section.
 
@@
 These features are identified first and discussed separately.
-We have represented our galactocentric velocities with a generalised histogram (Figure \ref{fig:velocity-histogram}) to quantitatively compare the observed stellar kinematics against the hypothesis that the parent distribution ca be described by a canonical halo ($\mu = 0$ km s$^{-1}$, $\sigma = 101.6$ km s$^{-1}$ \citep{Sirko;et-al_2004}).
+We have represented our galactocentric velocities with a generalised histogram (Figure \ref{fig:velocity-histogram}) to quantitatively compare the observed stellar kinematics against the hypothesis that the parent distribution can be described by a canonical halo where $\mu = 0$ km s$^{-1}$, and $\sigma = 101.6$ km s$^{-1}$ \citep{Sirko;et-al_2004}.
 
@@
 		\includegraphics[width=\columnwidth]{./velocity_halo.eps}
-		\caption{Generalised histogram of $V_{GSR}$ for our 178 K-type giants, highlighting their significance against a canonical halo population.
-The Gaussian is normalised such that the integral equals the number of observed stars excluding those outside a 2.5-$\sigma$ excess.
+		\caption{Generalised histogram of $V_{GSR}$ for our 178 K-type giants, highlighting the substructure present.
+The Gaussian represents the halo contribution; it is normalised such that the integral equals the number of observed stars excluding those outside a 2.5-$\sigma$ excess.
 Significant ($>3\sigma$) kinematic deviations from the smooth distribution are appropriately grouped and labelled.}
@@
 
-The generalised histogram represents each data point with a Gaussian kernel of an equal width (deviation).
-As our internal kinematic errors between multiple measurements summate to a half-normal distribution with a FWHM of 7.16 km s$^{-1}$, we have opted for a sigma value of 10 km s$^{-1}$ the generalised histogram in Figure \ref{fig:velocity-histogram} to avoid under-smoothing.
-
-	\begin{figure}[h!]
-		\includegraphics[width=\columnwidth]{./monte_carlo.eps}
-		\caption{Monte-Carlo simulation results illustrating the number of times simulations could reproduce our observed data in the equivalent multi-dimensional bin.
+		\begin{figure*}[t!]
+		\includegraphics[width=\textwidth]{./monte_carlo.eps}
+		\caption{The observed data for the 178 giant star sample (left panel).
+Monte-Carlo simulation results illustrating the number of times simulations could reproduce our observed data in the equivalent multi-dimensional bin (right panel).
 Significant features discussed in the text are labelled.}
 		\label{fig:monte-carlo}
-	\end{figure}
-
-	\begin{figure*}[t!]
-		\includegraphics[width=\textwidth]{./adapted_belokurov_2006.eps}
-		\caption{Observed fields are outlined upon a panoramic view of the Sgr stream, to demonstrate our field locations in context with the Sagittarius stream.
-This plot is an adaptation of Figure 2 in \citet{Belokurov;et-al_2006}, which uses the 2MASS M-giant sample of \citet{Majewski;et-al_2003}.}
-		\label{fig:sgr-field-of-streams}
 	\end{figure*}
 
+The generalised histogram represents each data point with a Gaussian kernel of an equal deviation.
+As our internal kinematic errors between multiple measurements summate to a half-normal distribution with a FWHM of 7.16 km s$^{-1}$, we have opted for a sigma value of 10 km s$^{-1}$ for the generalised histogram in Figure \ref{fig:velocity-histogram} to avoid under-smoothing.
 The most significant ($>3\sigma$) kinematic peaks have been labeled Features A, B, and C.
 Features A and C are our most significant structures, and the importance of Feature B becomes more evident through Monte-Carlo simulations.
-Velocities and metallicities of our K-giants have been binned into grid blocks of 15 km s$^{-1}$ and 0.3 dex \--- roughly twice the error in each dimension.
-A population of 178 stars were randomly drawn from a simulated halo with canonical kinematics.
+
+	Velocities and metallicities of our K-giants, shown in the left panel of Figure \ref{fig:monte-carlo}, were binned into grid blocks of 15 km s$^{-1}$ and 0.3 dex \--- roughly twice the error in each dimension.
+To interpret these data a population of 178 stars was randomly drawn from a simulated halo with canonical kinematics.
 Metallicities were randomly assigned using the observed halo Metallicity Distribution Function (MDF) of \citet{Ryan;Norris_1991}.
 Each simulated population was binned identically to our observed sample.
-Simulation grid blocks with counts equal to or exceeding stars in our equivalent observed grid block were noted, and summed after 10,000 simulations.
-Results from our Monte-Carlo simulations are illustrated in Figure \ref{fig:monte-carlo}.
-These were consistently significant when the grid was midpoint offset in both dimensions, except for the grid-block centered at $\sim185$ km s$^{-1}$ and $\sim-1.4$ dex, which has consequently been left unlabelled.
+Simulation grid blocks with counts equal to or exceeding stars in the equivalent observed grid block were noted, and summed after 10,000 simulations.
+Results from our Monte-Carlo simulations are illustrated in Figure \ref{fig:monte-carlo} (right).
+The identified Features A, B, and C in our results were consistently significant when the grid was midpoint offset in both dimensions, except for the grid-block centered at $\sim185$ km s$^{-1}$ and $\sim-1.4$ dex, which has consequently been left unlabelled.
 
 	 Substructure becomes statistically significant when the observed grid blocks are rarely replicated in Monte-Carlo simulations.
-Specifically, the number of members in Feature A of Figure \ref{fig:velocity-histogram} was never reproduced in some grid bins.
+Specifically, the number of members in Feature A was never reproduced in some grid bins.
 This feature is well in excess of the halo and has a wide spread in kinematics.
 \citet{Chou;et-al_2007} mapped the Sgr debris across the sky using K/M-giants and found galactocentric velocity signatures between $-205$ km s$^{-1}$ to $-31$ km s$^{-1}$ in this region.
-As such we attribute this wide, significant kinematic peak as the leading arm of the Sagittarius tidal tail.
+As such we attribute this wide, significant kinematic peak as the leading arm of the Sgr tidal tail.
 Feature A is discussed in the next section.
@@
 	 The clump of stars in the velocity bin centered on $V_{GSR} \approx 130$ km s$^{-1}$ and [Fe/H] $\approx -2$ was replicated only $\sim1$\% in 10,000 simulations.
-We attribute these members to the Virgo Stellar Stream.
-These members are coincident in spatial position, velocity, and metallicity with previously reported values of the VSS obtained by F turnoff/BHB stars \citep{Newberg;et-al_2007} and RR Lyrae stars \citep{Prior;et-al_2009a}.
+We attribute these stars to the Virgo Stellar Stream, as they are coincident in spatial position, velocity, and metallicity with previously reported values of the VSS obtained by F turnoff/BHB stars \citep{Newberg;et-al_2007} and RR Lyrae stars \citep{Prior;et-al_2009a}.
 Feature B is discussed in \S\ref{sec:the-vss}.
+
+	\begin{figure*}[t!]
+		\includegraphics[width=\textwidth]{./adapted_belokurov_2006.eps}
+		\caption{Observed fields are outlined upon a panoramic view of the Sgr stream, to demonstrate our field locations in context with the Sgr stream.
+This plot is an adaptation of Figure 2 in \citet{Belokurov;et-al_2006}, which uses the 2MASS M-giant sample of \citet{Majewski;et-al_2003}.}
+		\label{fig:sgr-field-of-streams}
+	\end{figure*}
 
@@
 
-	The bounds of our observed region are overlaid upon a panoramic projection of the Sagittarius stream, and the  ``Field of Streams''  \citep{Belokurov;et-al_2006} in Figure \ref{fig:sgr-field-of-streams}.
-This is a crowded region of globular clusters, substructures and overlapping stellar streams, primarily populated by the Sagittarius Northern leading arm.
+	  Our observed fields are overlaid upon a panoramic projection of the Sgr stream and the  ``Field of Streams''  \citep{Belokurov;et-al_2006} in Figure \ref{fig:sgr-field-of-streams}.
+This is a crowded region of globular clusters, substructures and overlapping stellar streams, primarily populated by the Sgr Northern leading arm.
 Simply from a spatial perspective, we expect the Sgr debris to dominate our data.
@@
 
-	In order to investigate the spatial coverage and kinematics of our Sagittarius members, we have compared our giants with the constant flattening spheroidal models of LJM05 and the more recent tri-axial model of LM10.
-The simulated data output from these is readily available online\footnote{http://www.astro.virginia.edu/$\sim$srm4n/Sgr/}, and their released models have the best-fitting parameters for each dark halo shape (prolate, spherical, oblate and tri-axial).
+	In order to investigate the spatial coverage and kinematics of our Sgr members we have compared our data with the constant flattening spheroidal models of LJM05, and the more recent tri-axial model of LM10.
+The simulated data output from these models is readily available online\footnote{http://www.astro.virginia.edu/$\sim$srm4n/Sgr/}, and the released models have the best-fitting parameters for each dark halo shape (prolate, spherical, oblate and tri-axial).
 These are the only simulations available which make use of an all-sky data set; the 2MASS M-giant sample.
 We have not considered particles farther than 60 kpc to match realistic observation limitations.
+The $10^5$ model Sgr debris particles from their simulations are represented along the best-fit great-circle ($\Lambda_\odot$, $B_\odot$) where the longitudinal coordinate $\Lambda_\odot$ is zero in the direction of the Sgr core and increases along the trailing debris.
 For comprehensive details of the simulations the reader is referred to the papers of \citet{Law;et-al_2005} and \citet{Law;Majewski_2010}.
@@
 	\begin{figure}[t!]
-		\includegraphics[width=\columnwidth]{./sgr_spatial.eps}
+		\includegraphics[width=\columnwidth]{./law_spatial.eps}
 		\caption{Our fields and observed bounds are shown with the simulated particles from multiple \textit{N}-body simulations by LJM05 and LM10.
-These particles are distance restricted (up to 60 kpc), and color-coded by their peri-centric passage following the same convention by \citet{Law;Majewski_2010} (orange;most recent passage, magenta; previous passage, cyan; oldest observable passage).}
+These particles are distance restricted (up to 60 kpc), and color-coded by their peri-centric passage (yellow; most recent passage, red; previous passage, blue; oldest observable passage).}
 		\label{fig:law-spatial}
@@
 	The Northern leading arm of Sgr is particularly sensitive both kinematically and spatially to the shape of the Milky Way dark halo (Figure \ref{fig:law-spatial}).
-Most models predict the Sgr stream to pass directly through our fields, whereas the prolate model predicts the edge of the stream near this region and no particles directly in our fields.
-Spatially, the prolate model predicts the Sgr stream to pass much lower in $B_\odot$ than our observed fields.
-When we extend a rectangle bounded by the edges of our fields (as per the zoomed insets in Figure \ref{fig:law-spatial}) a mere two particles are predicted.
+The spherical, oblate and tri-axial models predict the Sgr stream to pass directly through our fields, whereas the prolate model predicts only the edge of the stream near this region and no particles directly in our fields.
+Spatially, the prolate model predicts the Sgr stream to pass much lower in latitude ($B_\odot$) than our observed fields.
+When we extend a rectangle bounded by the edges of our fields (as per the zoomed insets in Figure \ref{fig:law-spatial}) a mere two model particles are found.
+The $10^5$ model particles are proportional to the stream density so the lack of model particles implies a negligible stream concentration in our observed region.
+Observationally, when the number of field configurations is accounted for our observed Sgr K-giants are uniformly distributed across the fields.
 If this prolate halo model is a true representation of the Sgr debris, this does not exclude the potential of finding some Sgr debris in our fields.
-However, it does imply that if the LJM05 prolate model is an accurate representation of the dark halo then Sgr would not be the dominant population, contrary to our preferred interpretation of the observations.
+However, it does imply that if the LJM05 prolate model is an accurate representation of the dark halo then Sgr would not be the dominant population \--- contrary to our preferred interpretation of the observations.
 
-	In comparison the tri-axial, spherical and oblate models predict varying debris from previous peri-centric passages in our fields.
+	In comparison, the tri-axial, spherical and oblate models predict varying amounts of debris from previous peri-centric passages in our fields.
 A kinematic comparison against our observations is necessary to evaluate model predictions.
-As the prolate model has only two simulated particles within our extended bounds there is no qualitative kinematic comparison to be made for this model, and as such the prolate model is excluded from further kinematic analysis.
+As the prolate model has only two simulated particles within our extended bounds there is no qualitative kinematic comparison to be made for this model, therefore the prolate model is excluded from further kinematic analysis.
 
@@
 Heliocentric distances for particles used to generate each velocity histogram are shown on the right.
-Particles are marked by their recency of passage.
+Particles are marked by their peri-centric passage.
 A plus ($+$) denotes debris from the current peri-centric passage by Sgr, circles ($\circ$) mark the previous passage, and squares ($\square$) represent debris from two previous passages.
@@
 	The number of predicted particles observable differs between models.
-Consequently the kinematics for each model have been represented as a generalised histogram (Figure \ref{fig:law-vel-compare}).
+Consequently, the kinematics for each model have been represented as a generalised histogram (Figure \ref{fig:law-vel-compare}).
 For consistency all simulation output and observed data has been convolved with a Gaussian kernel of 10 km s$^{-1}$; the sigma used for the previous generalised histogram in Figure \ref{fig:velocity-histogram}.
-Predicted distances and peri-centric ages are shown, demonstrating that debris from multiple passages are predicted along the line of sight.
-A much tighter velocity sequence is predicted here by the tri-axial model than the constant flattening models.
-This is because the tri-axial model predicts a pericenter almost precisely in our observable region, whereas the spherical and oblate models predicts a large wrap along the line of sight, resulting in a wide spread of distances and velocities.
+Predicted distances and peri-centric ages are shown, demonstrating that debris from multiple passages are predicted along the line-of-sight.
+A much tighter velocity sequence is predicted by the tri-axial model than the constant flattening models.
+This is because the tri-axial model predicts a peri-center almost precisely in our observable region, whereas the spherical and oblate models predict a large wrap along the line-of-sight, resulting in a wide spread of distances and velocities.
 
@@
 This signature is not represented in our data.
-Much closer K-giants are less likely to be identified given our luminosity range, although these early K-giants are much more numerous, so this is unlikely to explain our lack of highly negative kinematics.
 The lowest observed velocity is $\sim{}-250$ km s$^{-1}$ and we have only two observations less than $V_{GSR} < -200$ km s$^{-1}$.
@@
 These particles (and the positive kinematic signature around $\sim$20 kpc in the oblate model), are relatively minor signatures when compared to the Northern arm feature.
-If these signatures are present in our observed fields, their relatively low density compared to the northern arm feature would prevent them from appearing as significant.
+If these signatures are present in our observed fields, their relatively low density compared to the Northern arm feature would prevent them from appearing as significant.
 
 	Although the predicted velocity distribution is narrower than what we observe, the LM10 tri-axial dark halo model best fits our observations.
-The observed sample broadens most prominently towards more negative galactocentric velocities at $\sim-200$ km s$^{-1}$, still well higher than oblate/spherical predictions.
+The observed sample broadens most prominently towards more negative galactocentric velocities at $\sim-200$ km s$^{-1}$, considerably higher than oblate/spherical model predictions.
 Halo contamination at highly negative velocities is likely to be small.
-One reconciliation for this tri-axial model/observed kinematic discrepancy may lie in the workings of the tri-axial model itself.
+One reconciliation for this discrepancy between our observations and the tri-axial model may lie in the workings of the tri-axial model itself.
 Unlike other models considered, the tri-axial model does not reproduce the observed bifurcation in the Sgr stream \citep{Belokurov;et-al_2006}.
 Although observationally untested, it is reasonable to suggest a bifurcation may result from a significant kinematic disruption.
-Such an effect could result in a broader kinematic distribution \--- similar to what we observed \--- which is most notable at the stream edges.
+Such an effect could result in a broader kinematic distribution \--- similar to what we have observed \--- which is most notable at the stream edges.
 
@@
 	Many groups have found the population of the Sgr core to possess a mean [Fe/H] $\sim -0.5$ dex \citep{Cacciari;et-al_2002, Bonifacio;et-al_2004, Monaco;et-al_2005}.
-As the host circles the Milky Way the older, more metal-poor stars are preferentially stripped from the progenitor, creating a metallicity gradient along the stream \citep{Chou;et-al_2007, Keller;Yong;Da_Costa_2010}.
-In this region of the stream, very few Sgr member metallicies have been reported.
-\citet{Vivas;et-al_2005} found a mean metallicity of $\langle$[Fe/H]$\rangle = -1.77$ from spectra of 16 RR Lyraes along a nearby region of the Sgr leading arm.
+The observed metallicity gradient along the stream suggests that as the host circles the Milky Way the older, more metal-poor stars are preferentially stripped from the progenitor \citep{Chou;et-al_2007, Keller;Yong;Da_Costa_2010}.
+In this region of the stream very few Sgr member metallicies have been reported.
+\citet{Vivas;et-al_2005} found a mean metallicity of $\langle$[Fe/H]$\rangle = -1.77$ from spectra of 16 RR Lyrae stars along a nearby region of the Sgr leading arm.
 Similarly, \citet{Prior;et-al_2009b} found $\langle$[Fe/H]$\rangle = -1.79 \pm 0.08$ for 21 type \textit{ab} RR Lyrae stars in the region.
@@
 If we apply the metallicity gradient found by \citet[][from M-giants]{Keller;Yong;Da_Costa_2010} to these observed K-giants, we would expect an abundance mean near $\sim{}-1.2$ dex in this observed region.
-The metallicity distribution for our negative $V_{GSR}$ sample is shown in Figure \ref{fig:sgr-metallicity-hist}, and illustrates a metal-poor population.
+The metallicity distribution for our entire negative $V_{GSR}$ sample is shown in Figure \ref{fig:sgr-metallicity-hist}, and illustrates a metal-poor population.
 The mean of our distribution is $\langle$[Fe/H]$\rangle = -1.7\,\pm\,0.3$ dex.
-If we include only the stars attributed to Feature A (Sgr debris) this value increases by only 0.04 dex, well within observational uncertainties.
+If we include only the stars attributed to Feature A (as defined by the shaded region in Figure \ref{fig:velocity-histogram}, between $-140 < V_{gsr} < -30$ km s$^{-1}$) this value increases by only 0.04 dex; well within observational uncertainties.
 As a comparison, in a sample of metal-rich biased M-giants from the 2MASS data \citet{Chou;et-al_2007} found a mean metallicity of $\langle$[Fe/H]$\rangle = -0.72$ dex for their best subsample in the Northern leading arm of Sgr.
+Although there may be some halo contamination in our sample, in general our more metal-poor Feature A members have higher negative velocities, which is expected for Sgr stream members in this region.
 
@@
 The more metal-rich isochrone with [Fe/H] $= -0.5$ does not pass through our selection range.
-This is consistent with our observed metallicities.
-Although this does not prohibit the possibility of more metal-rich members within our sample, it implies that our distribution is somewhat biased towards the metal-poor end of the MDF.
+This is consistent with our observed metallicities for Sgr.
+Although this does not prohibit the possibility of more metal-rich members within our sample, it implies that our distribution is biased towards the metal-poor end of the MDF.
 The tail of our Sgr distribution extends from $-0.71$ to $-2.35$ dex.
@@
 Several RR Lyrae stars were noted with a common velocity of $V_{GSR} = 130$ km s$^{-1}$ \citep{Newberg;et-al_2007, Prior;et-al_2009a}.
-\citet{Prior;et-al_2009a} also measured metallicities of stars with this kinematic signature and found a mean [Fe/H] $= -1.95\,\pm\,0.1$ for the VSS, although this is based on RR Lyraes and is therefore potentially biased to the metallicity of the oldest populations.
+\citet{Prior;et-al_2009a} also measured metallicities of stars with this kinematic signature and found a mean [Fe/H] $= -1.95\,\pm\,0.1$ for the VSS, although this is based on RR Lyrae stars and  therefore is potentially biased to the oldest, most metal-poor populations.
 The RR Lyrae sample from \citet{Duffau;et-al_2006} found a $\langle$[Fe/H]$\rangle = -1.86$ with a much larger abundance spread of $\sigma = 0.40$, which was several times the relative uncertainty in individual values ($\sigma_{\mbox{[Fe/H]}} = 0.08$ dex).
-This led \citet{Duffau;et-al_2006} to infer the progenitor of the VSS was likely a dSph galaxy, as a large dispersion in $\mbox{[m/H]}$ indicates self-enrichment and implies the structure is a galaxy and not an isolated stellar cluster \--- although there are numerous globular clusters with multiple populations.
-Similar to \citet{Duffau;et-al_2006}, we  also observe an abundance spread within this kinematic bin including some giants with kinematics and metallicities ($V_{GSR} = 130 \pm 9$ km s$^{-1}$, [Fe/H] =$ -2.0 \pm 0.16$) matching those found by \citet{Prior;et-al_2009a}.
-Monte-Carlo simulations reproduced these few targets a mere $\sim1$\% in 10,000 simulations \--- demonstrating their significance.
+This led \citet{Duffau;et-al_2006} to infer the progenitor of the VSS was likely a dSph galaxy, as a large dispersion in $\mbox{[m/H]}$ indicates self-enrichment and implies the structure is a galaxy and not an isolated stellar cluster.
+Although some globular clusters are also now known to contain multiple populations and sizeable $\mbox{[m/H]}$ dispersions, globular clusters in general  have a much smaller dispersion than that observed here.
+Similar to \citet{Duffau;et-al_2006}, we  also observe an abundance spread within this kinematic bin including two K-giants with mean kinematics and metallicities ($\langle{}V_{GSR}\rangle{} = 130 \pm 9$ km s$^{-1}, \langle\mbox{[Fe/H]}\rangle = -2.0 \pm 0.16$) matching those found by \citet{Prior;et-al_2009a}.
+Monte-Carlo simulations reproduced these targets a mere $\sim1$\% in 10,000 simulations \--- highlighting their significance.
 
 	High resolution follow-up spectroscopy on these targets and other VSS candidates at higher metallicities in this kinematic range will provide crucial information about the origin of the VSS.
-Investigating [$\alpha$/Fe] ratios in these candidates can constrain the mass of the VSS progenitor and discern whether the host was a dSph \citep{Venn;et-al_2004, Casetti-Dinescu;et-al_2009}.
+Investigating [$\alpha$/Fe] ratios in these candidates can constrain the mass of the VSS progenitor and discern whether the host was indeed a dSph \citep{Venn;et-al_2004, Casetti-Dinescu;et-al_2009}.
 Future observations are planned.
@@
 \citet{Newberg;et-al_2007} identified a 4-$\sigma$ peak at $V_{GSR} = 200$ km s$^{-1}$ in their sample of F turnoff stars centered on $(l, b) = (288^\circ, 62^\circ)$.
-Our nearest field to their plate (Field B) hosts only one star associated with this peak; most of our these stars are located within our most populated Field D.
-\citet{Prior;et-al_2009b} also noted stars in this kinematic range and compiled a list of authors who have also observed such peaks (see \citet{Sirko;et-al_2004, Duffau;et-al_2006, Starkenburg;et-al_2009}).
-\citet{Prior;et-al_2009b} argue these stars may be associated with trailing debris of Sagittarius, as suggested by models (LJM05, LM10).
-Although this trailing debris would be much closer than the nearby visible leading arm, these observations support the interpretation by \citet{Prior;et-al_2009b} as the metallicities are quite similar to the nearby Sgr debris.
+Our nearest field to their plate (Field B) hosts only one star associated with this peak; most of our stars are located within our most populated Field D.
+\citet{Prior;et-al_2009b} also noted stars in this kinematic range and compiled a list of authors who have similarly observed such peaks (see \citet{Sirko;et-al_2004, Duffau;et-al_2006, Starkenburg;et-al_2009}).
+\citet{Prior;et-al_2009b} argue these stars may be associated with trailing debris of Sgr, as suggested by models (LJM05, LM10).
+Although this trailing debris would be much closer than the nearby visible leading arm, our observations support the interpretation by \citet{Prior;et-al_2009b} as the metallicities are quite similar to the nearby Sgr debris.
 
-	This substructure has a range of metallicities on our scale.
-These metallicities were derived with the distance modulus to the VOD/VSS, and may not be exact representations.
-As such the abundance dispersion we observe is either representative, or these stars have a common metallicity and are dispersed along the line of sight.
+	This substructure has a range of metallicities.
+These metallicities were derived assuming a single distance modulus to the VOD/VSS.
+The abundance dispersion we observe is either representative, or these stars have a common metallicity and are dispersed along the line-of-sight.
 Unfortunately neither can be positively excluded without further observations.
-If these peaks are associated with the trailing debris of Sagittarius debris, they are likely to be further away than the VOD.
+If these peaks are associated with the trailing debris of Sgr debris, they are likely to be further away than the VOD.
 On our scale that would make these stars more metal-rich than shown in Figure \ref{fig:monte-carlo}.
-However the nearest trailing debris particles predicted from any best-fitting dark halo potential that could explain this kinematic peak occurs at $\sim\Lambda_\odot = 310^\circ$; our observations range in $\Lambda_\odot$ between $256-273^\circ$.
-Whether this substructure is separate from Sagittarius debris or not remains equivocal.
-Nevertheless the apparent metallicities of the Feature C stars are not inconsistent with those of a Sgr population given our results for Feature A and those of \citet{Keller;Yong;Da_Costa_2010}.
+However, the nearest trailing debris particles predicted from any best-fitting dark halo potential that could explain this kinematic peak occur at $\sim\Lambda_\odot = 310^\circ$; our observations range in longitude  between $\Lambda_\odot = 256-273^\circ$.
+Whether this substructure is separate from Sgr debris or not remains equivocal.
+Nevertheless, the apparent metallicities of the Feature C stars are not inconsistent with those of a Sgr population given our results for Feature A and those of \citet{Keller;Yong;Da_Costa_2010}.
 
 \section{Carbon Stars}
+\label{sec:carbon-stars}
 
 	In our sample we have identified five carbon stars.
-With the color selections to target K-giants, this region also overlaps with where we would expect to find carbon stars (Figure \ref{fig:carbon-sdss}).
+Our colour selection to select K-giants overlaps with where we would expect to find carbon stars.
 Although these stars were not specifically targeted, their surface densities are so low \citep[$\approx$ 1 per 50 deg$^2$;][]{Green;et-al_1994} that we would not expect them as a substantial contaminant.
@@
 However these targets were not spectroscopically observed in the SDSS follow-up survey SEGUE.
-Additionally, through comparisons with previous carbon-type star catalogues \citep{Totten;Irwin_1998, Downes;et-al_2004, Goswami;et-al_2010}, the stars tabulated in Table \ref{tb:carbon-stars} are previously unclassified carbon stars.
+Through comparisons with previous carbon-type star catalogues \citep{Totten;Irwin_1998, Downes;et-al_2004, Goswami;et-al_2010}, the stars tabulated in Table \ref{tb:carbon-stars} are previously unclassified carbon stars.
 This is largely because our objects are too faint to have been observed by previous spectroscopic carbon star surveys.
@@
 	There is 2MASS photometry available for four of these stars.
-Of those, two stars (SDSS J125410.80-032744.0 and J125416.52-031437.6) exhibit anomalous JHK colors and significant ($> 3\sigma$) proper motions; characteristics of a dwarf carbon star.
+Of those, two stars (SDSS J125410.80-032744.0 and J125416.52-031437.6) exhibit anomalous JHK colors and significant ($> 3\sigma$) proper motions \citep[PPMXL][]{Roser;et-al_2010}; characteristics of a dwarf carbon star.
 A third star also exhibits significant proper motion (SDSS J121740.94-001839.5), however JHK photometry is unavailable.
 The two remaining stars in our sample have JHK photometry characteristic of the F/G type CH carbon stars found by \citet{Downes;et-al_2004} in their Faint High-Latitude Carbon (FHLC) star survey (Figure \ref{fig:carbon-sdss}), and do not exhibit significant proper motion - which strongly suggests they are not dwarfs \citep{Green;et-al_1994, Deutsch_1994}.
-All identified K-giant stars in our distilled sample had no proper motion detectable above measurement errors.
-These carbon star kinematics are representative of a typical halo population.
 
@@
 
-	We present spectroscopic observations of K-type stars in a crowded region of the 'Field of Streams', where significant substructure is present.
+	We present spectroscopic observations of K-type stars in a region of the 'Field of Streams', where significant substructure is present.
 We utilise the gravity-sensitive Mg I triplet to separate giants and dwarfs.
@@
 We have recovered kinematic substructure found by other authors, which cannot be explained by a smooth halo distribution.
-Highly negative velocity signatures match those expected by the Sagittarius stream debris, and we identify a clump of K-giants with metallicities and kinematics which make them highly probable members of the Virgo Stellar Stream.
+Highly negative velocity signatures match those expected by the Sgr stream debris, and we also identify a group of K-giants with metallicities and kinematics which make them highly probable members of the Virgo Stellar Stream.
 
-	Stars in this region of the Sagittarius stream are kinematically sensitive to the shape of the Galactic dark halo.
+	Stars in this region of the Sgr stream are kinematically sensitive to the shape of the Galactic dark halo.
 As such, we have compared our velocity distribution to the Sgr-Milky Way dark matter models of \citet{Law;et-al_2005, Law;Majewski_2010}.
@@
 A prolate dark halo predicts relatively little debris in our observed fields.
-If the spheroid is prolate and LJM05 presents an accurate representation, we would not expect Sgr debris to dominate our sample (as it does so) even if we were $\Delta{}B_\odot\sim10^\circ$ closer to the great circle best-fit.
+If the spheroid is prolate and LJM05 presents an accurate representation, Sgr debris would not be expected to dominate our sample even if we were $\Delta{}B_\odot\sim10^\circ$ closer to the great circle best-fit.
 However, Sgr debris is our most significant kinematic structure observed.
 No single model perfectly represents our data, although we find the more recent tri-axial model (LM10) best represents our observed kinematics.
-Future tri-axial models of Sgr with bifurcation treatment are likely to more closely represent our observations.
 
-	Observed metallicities for K-giants in this region of the Sgr stream are notably lower than expected based on other Sgr samples, demonstrating the presence of a metal-poor population in the  Sagittarius debris.
-Although isochrones indicate we may be biased towards metal-poor members at these distances, these stars are unequivocally Sagittarius in origin.
-Metallicity gradients reported suggest a mean of $\langle[$Fe/H$]\rangle\sim{}-1.2$, whereas our population has $\langle[$Fe/H$]\rangle = -1.7 \pm 0.3$ dex.
-Previously reported metal-poor abundances in this region have been from old RR Lyraes where we would expect $\langle[$Fe/H$]\rangle\sim{}-1.7$ dex or young M-giants where $\langle[$Fe/H$]\rangle\sim{}-0.7$ dex is reasonable.
-Thus the sample presented here is more representative of the complete MDF.
-These observations also demonstrate that the Sagittarius stream hosts a substantially larger abundance range than previously found, including a previously uncovered metal-poor population of K-giants.
+	Observed metallicities for K-giants in this region of the Sgr stream are notably lower than expected based on other Sgr samples, demonstrating the presence of a metal-poor population in the  Sgr debris.
+Although isochrones indicate we are biased towards metal-poor members at these distances, these stars are unequivocally Sgr in origin.
+Metallicity gradients reported, suggest a mean of $\langle[$Fe/H$]\rangle\sim{}-1.2$, whereas our population has $\langle[$Fe/H$]\rangle = -1.7 \pm 0.3$ dex.
+Previously reported abundances in this region have been ascertained from observing RR Lyrae stars (where the mean metallicity found was $\langle\mbox{[Fe/H]}\rangle\sim{}-1.7$ dex) or from observing M-giants (where $\langle\mbox{[Fe/H]}\rangle\sim{}-0.7$ dex was reported).
+In both scenarios the measurements are reasonable with what we would expect from each particular stellar population.
+Thus the sample presented here is more representative of the complete MDF, and less susceptible  to age or metallicity biases.
+These observations also demonstrate that the Sgr stream likely hosts a substantially larger abundance range than previously found, including a previously un-detected metal-poor population of K-giants.
 

### 2012-05-28 2011-sgr/aastex.tex
Initial commit.

--- 2012-05-28 2011-sgr/AJ-version/sgr_vod_2011.tex
@@
 
-\shorttitle{Kinematics \& Chemistry of Halo Substructures: The Vicinity of the VOD}
+\shorttitle{}
 \shortauthors{Casey, Keller \& Da Costa}
@@
 \affil{Research School of Astronomy \& Astrophysics,
-	Australian National University, Mt Stromlo Observatory, via Cotter Rd, Weston, ACT 2611, Australia}
+	Australian National University,
+	Canberra, Australia}
 
@@
 This suggests a significantly wider metallicity distribution exists in the Sagittarius Stream than formerly considered.
-We also present data on five serendipitous carbon stars which were uncovered in our sample.
 \end{abstract}
@@
 
-The proportion of substructure recently uncovered in the Galaxy has highlighted the crucial involvement accretion has played in the formation of the Milky Way \citep{Bell;et-al_2008}.
+The proportion of substructure recently uncovered in the Galaxy has highlighted the crucial involvement accretion has played in the formation of the Milky Way.
 Properties of these stellar structures allow us to probe the formation mechanisms and history of the Galaxy.
@@
 Regardless, the dissipation-less merging paradigm is widely accepted, and consistent with favoured Cold Dark Matter ($\Lambda$CDM) cosmology models.
-Through the examination of ongoing accretion events in the Milky Way and fossils from previous mergers, we can trace the evolution of the outer most regions of the Galaxy \citep[e.g.,][]{Helmi;White_2001}.
+Through the examination of ongoing accretion events in the Milky Way and fossils from previous mergers, we can trace the evolution of the outer most regions of the Galaxy \citep[][e.g.
+]{Helmi;White_2001}.
 
- Accretion is at least partly \citep[e.g.,][]{Starkenburg;et-al_2009}, if not entirely responsible for the formation of the stellar halo.
+%ultimately trace the formation history of the Galaxy. 
+%This technique of studying stellar populations as surrogates of galactic archaeology was first proposed in the seminal paper of \citet{Eggen;Lynden-Bell;Sandage_1962}, who observed a metallicity abundance declivity in stars from the disk to the halo.
+From these measurements they inferred that  the Galaxy formed by a rapid collapse of a relatively homogenous protogalactic cloud.
+In contrast of this inference, \citet{Searle;Zinn_1978} observed a wide scope of metallicities in globular clusters irrespective of their galactocentric distance.
+This implied a formation paradigm based on the hierarchical accretion of protogalactic fragments.
+
+ Accretion is at least partly \citep[][e.g.]{Starkenburg;et-al_2009}, if not entirely responsible for the formation of the stellar halo.
 \citet{Bell;et-al_2008} compared Sloan Digital Sky Survey \citep[hereafter SDSS]{York;et-al_2000} data to galaxy formation simulations using different dark halos and found that observations are consistent with the stellar halo being entirely formed by hierarchical merging of accreted satellites (see also \citet{Xue;et-al_2011}).
@@
 Originally uncovered by \citet{Ibata;et-al_1994} as a co-moving group of K- and M-type giants, the tidal tails of Sgr circle our Galaxy.
-As such they have been extensively traced with red-clump stars \citep{Majewski;et-al_1999}, carbon stars \citep{Totten;Irwin_1998, Ibata;et-al_2001}, RR Lyrae stars \citep{Ivezic;et-al_2000, Vivas;et-al_2005, Keller;et-al_2008, Watkins;et-al_2009, Prior;et-al_2009b}, A-type stars \citep{Newberg;et-al_2003}, BHB stars \citep{Ruhland;et-al_2011} and K/M-giants \citep{Majewski;et-al_2003,  Yanny;et-al_2009, Keller;Yong;Da_Costa_2010}.
+As such they have been extensively traced with red-clump stars \citep{Majewski;et-al_1999}, carbon stars \citep{Totten;Irwin_1998, Ibata;et-al_2001}, RR Lyrae stars \citep{Ivezic;et-al_2000, Vivas;et-al_2005, Keller;et-al_2008, Watkins;et-al_2009, Prior;et-al_2009b}, A-type stars \citep{Newberg;et-al_2003} and K/M-giants \citep{Majewski;et-al_2003,  Yanny;et-al_2009, Keller;Yong;Da_Costa_2010}.
 With spatial and kinematical information, tracers originating from the host system can be unequivocally identified.
@@
 \citet{Law;et-al_2009} introduced a tri-axial model with a varying flattening profile $q$, which replicates the orbital precession seen and matched kinematic observations of the Sgr debris.
-However \citet{Law;Majewski_2010} (hereafter LM10) conceded this may be a purely numerical solution as tri-axial halos are dynamically unstable, and emphasizes more kinematic measurements in other regions of the Sgr stream are required.
+However \citet{Law;Majewski_2010} (hereafter LM10) conceded this may be a purely numerical solution as tri-axial halos are dynamically unstable, and admits more kinematic measurements in other regions of the Sgr stream are required.
 
@@
 The nomenclature on the substructure names within this region is varied, however when referring to the VOD we are discussing the spatial over-density of stars within the region, separate from any co-moving groups.
+
+% At the core of the VOD, multiple studies find a peak density of RR Lyrae \citep{Vivas;et-al_2001, Ivezic;et-al_2005} and F-type main sequence stars \citep{Newberg;et-al_2002} at ($\alpha, \delta$) = (190$^\circ$, 0$^\circ$).
+Close by, \citet{Juric;et-al_2008} find the F-type main sequence peak at ($\alpha, \delta$) = (192$^\circ$, +2$^\circ$) and \citet{Keller_2010} finds the sub-giant peak density at ($\alpha, \delta$) = (194.6$^\circ$, +1.8$^\circ$).
+The exact spatial centroid of the VOD remains equivocal.
+
+%Furthermore, the spatial bounds of the VOD remains unclear.
+There is some agreement that the boundaries of the structure extend outside the SDSS catalogue \citep{Newberg;et-al_2007,Prior;et-al_2009a,Keller;et-al_2009}.
+Observations to date represent lower limits on the VOD bounds.
+\citet{Juric;et-al_2008} used photometric parallaxes to ascertain a spatial limit, and found the diffuse structure spanned $\sim1000$ deg$^{2}$.
+\citet{Prior;et-al_2009a} estimated a lower coverage of $\sim760$ deg$^2$ from the luminosity function excess in the region.
+\citet{Duffau;et-al_2006} had previously used a similar technique to \citet{Prior;et-al_2009a} and yielded a minimum sky coverage of 106 deg$^2$.
 
@@
 They allow for precise radial velocities and chemical abundances.
-In order to specifically target K-giants, we have chosen candidates within the color selection box shown in Figure \ref{fig:cmd-target-selection}, taken from the SDSS DR7 catalogue.
-Field dwarfs are expected to contaminate the sample due to their similarity in colors.
+In order to specifically target K-giants, we have chosen candidates within the colour selection box shown in Figure \ref{fig:cmd-target-selection}, taken from the SDSS DR7 catalogue.
+Field dwarfs are expected to contaminate the sample due to their similarity in colours.
 Although K-dwarfs are difficult to distinguish photometrically, we can spectroscopically separate these through the equivalent width (EW) of the  gravity-sensitive triplet Mg I lines at 5167.3, 5172.7, and 5183.6 \AA\ (see \S\ref{sec:dwarf-giant-separation}).
 
+%\begin{eqnarray}
+%		0.6 <& (g-i)_o &< 1.7 \nonumber \\
+%		15 <& i_o &< 18 \\
+%-15(g-i)_o + 27 <& g_o &< -3.75(g-i)_o \nonumber
+%\end{eqnarray}
+%These criteria are marked in the CMD for this region in Figure \ref{fig:cmd-target-selection}. 
 \begin{figure}[h]
-	\includegraphics[width=\columnwidth]{./cmd_selection.eps}
-	\caption{CMD of our observed regions from SDSS DR7, overlaid with the color selection criterion used to target K-giants.
+	\includegraphics[width=\columnwidth]{./figures/cmd.eps}
+	\caption{CMD of our observed regions from SDSS DR7, overlaid with the colour selection criterion used to target K-giants.
 Appropriate Dartmouth isochrones \citep{Dotter;et-al_2008} are shown for Sgr debris at a distance of $r_\odot =40$ kpc \citep{Belokurov;et-al_2006}}
@@
 Throughout all observations, sufficient sky and guide fibres ($\sim30$ and 7-8 respectively) were allocated to ensure optimal sky subtraction and astrometry.
-In total 3,453 science targets were observed within 4 fields throughout the VOD/VSS region, as outlined in Table \ref{tab:observations}.
+In total 3,453 science targets were observed across 4 fields (Table \ref{tab:observations}).
 Multiple configurations were observed for most fields to permit measurements of bright ($i < 16$) and faint ($i > 16$) stars, as well as repeat observations on a subset of stars.
-
-% NOTE TO THE EDITOR - This table ought to be in a single column.
 
@@
 \startdata
-A & 12 00 00 & $+00$ 00 00 & 1 \\ 
-B & 12 20 00 & $-01$ 00 00 & 2 \\ 
-C & 12 40 00 & $-02$ 00 00 & 3 \\ 
-D & 12 56 00 & $-02$ 42 00 & 6 \\ 
+A & 12 00 00 & $+00$ 00 00 & 1 \\ % & 188 \\ %180
+B & 12 20 00 & $-01$ 00 00 & 2 \\ %& 673 \\ %185
+C & 12 40 00 & $-02$ 00 00 & 3 \\ %& 870 \\ %190
+D & 12 56 00 & $-02$ 42 00 & 6 \\ %& 1,722 %194
 \enddata
@@
 The 580V grating in the blue arm yields spectra between 370-580 nm, with a resolution of $R = 1300$.
-In the red arm we used the 1000I grating ($R = 4400$) which spans the spectral range from 800-950 nm.
+In the red arm we used the 1000I grating which spans the spectral range from 800-950 nm.
 This coverage includes the Ca II NIR Triplet (CaT), which is used for radial velocities and metallicities.
@@
 Multiple object frames were successively taken to assist with cosmic ray removal.
+%Three thirty-minute science exposures were taken for each faint field, and three twenty-five minute exposures for bright fields.
 
@@
 
+%\begin{figure*}[t]
+%	\includegraphics[width=\textwidth]{./figures/spectra.eps}
+%	\caption{Blue arm spectra for a K-type giant (top) and dwarf (bottom) star, highlighting the difference in the gravity-sensitive Mg I triplet profiles at 5167.3, 5172.7 and 5183.6 \AA{}, and the typical fitting achieved.}
+%	\label{fig:dwarf-giant-comparison}
+%\end{figure*}
+
 A grid of synthetic spectra has been generated to quantitively establish a giant/dwarf star separation criterion.
@@
 The strength of the Mg I lines were tuned to match both the Solar and Arcturus atlases of \citet{Hinkle;et-al_2003}.
-\citet{Girardi;et-al_2004} isochrones have been used to translate our de-reddened $g - i$ color range to effective temperature.
+\citet{Girardi;et-al_2004} isochrones have been used to translate our de-reddened $g - i$ colour range to effective temperature.
 Reddening is accounted for using the maps of \citet{Schlegel;Finkbeiner;Davis_1998}.
@@
 However, we do not expect metal-poor dwarfs to be a principle contaminant due to their intrinsically low luminosities and paucity.
-
 \begin{figure}[h]
-	\includegraphics[width=\columnwidth]{./dwarf_giant_separation.eps}
-	\caption{The sum of the Mg I triplet EWs for observations and synthetic spectra shown against the Sloan $g\,-\,i$ color.
-Synthetic spectra is shown for $\log{g} = 2$ ($\bigtriangleup$) and $\log{g} = 4.5$ ($\bigtriangledown$), and points are colored by metallicity.
+	\includegraphics[width=\columnwidth]{./figures/dwarfgiants.eps}
+	\caption{The sum of the Mg I triplet EWs for observations and synthetic spectra shown against the Sloan $g\,-\,i$ colour.
+Synthetic spectra is shown for $\log{g} = 2$ ($\bigtriangleup$) and $\log{g} = 4.5$ ($\bigtriangledown$), and points are coloured by metallicity.
 Our dwarf/giant separation line is shown (solid).
@@
 \end{figure}
-
+ %The choice of separation criterion affects our dwarf contamination, and our giant recoverability. 
  Using our synthetic grid, we have varied the slope and offset of our separation line to assess the effectiveness in differentiating giants from dwarfs.
@@
 \label{sec:kinematics}
+%Their prominence allows us to determine accurate radial velocities even in noisy data.
 
@@
 The differences between multiple measurements of the same target was calculated, and they form a half-normal distribution with a HWHM $= 3.58$ km s$^{-1}$.
+%This measurement includes velocity measurements of identified dwarfs, as we are focussed here on determining the systematic accuracy of our velocity measurements and not identifying substructures.
+
+%\begin{figure}[h]
+%	\includegraphics[width=\columnwidth]{./figures/vel_error.eps}
+%	\caption{Internal radial velocity errors between multiple measurements. This sample includes all targets (dwarfs and giants) with sufficient S/N that were observed more than once.}
+%	\label{fig:multiple-kinematics}
+%\end{figure}
 
@@
 
-We have measured metallicities for our giants using the strength of the Ca triplet lines.
+We have ascertained metallicities for our giants using the strength of the Ca triplet lines.
 This technique was originally empirically described for individual stars in globular  clusters \citep{Armandroff;Da-Costa_1991}.
@@
 Consequently, the strongest two CaT lines (8542 and 8662\AA) have been used to form a reduced EW (W') such that,
+\begin{comment}
+%Nevertheless the CaT-[Fe/H] relationship is strong for RGB stars in composite populations within the range $-2.5 < \mbox{[Fe/H]} < -0.5$.
 
+%However, a systematic trend in this high resolution spectra was found where metallicity is overestimated by $\sim0.1$ dex at low metallicities ($\mbox{[Fe/H]} < -2.2$) and underestimated by $\sim0.1-0.2$ dex at higher metallicities ($\mbox{[Fe/H]} > -1.2$) using this calibration.
+\citet{Battaglia;et-al_2008} indicate higher Ca abundances may affect the CaT equivalent width sufficiently to cause this trend, although [Fe/H] is the certain dominant factor contributing to the CaT line strength.
+
+%The [Ca/H] - [Fe/H] association is linear, although this technique is only applicable for stars brighter than the horizontal branch ($V - V_{HB} > 0$).
+Transformations from SDSS $ugriz$ photometry to $UBVR_{C}I_{C}$ has been performed using the transformation equations in \citet{Jester;et-al_2005}.
+Photometric errors (including those from transformations) are propagated to our reported metallicity errors.
+
+%The sum of the CaT EW is scaled to form a 'reduced EW' (W').
+There is some discussion in which combination of the three CaT lines should be used.
+In this work we have taken the total equivalent width as the sum of the two stronger Ca lines ($\lambda_{8542}$, $\lambda_{8662}$).
+The weakest Ca line is usually the most unreliable when calculating equivalent widths due to noise and the possibility of residual sky-line contamination.
+Moreover, following a comparison of scaling relations between CaT and [Fe/H], \citet{Battaglia;et-al_2008} found using only the two strongest lines (as \citet{Tolstoy;et-al_2001} had done) was the most robust.
+As such, we have adopted the best-fitting relationship found by \citet{Battaglia;et-al_2008} for this work.
+The reduced EW is calculable by
+\end{comment}
 \begin{eqnarray}
@@
 
+\begin{comment}
+%When applying this technique to our K-giants, the difficulty is that $V_{HB}$ is not easily defined.
+The horizontal branch magnitude varies between stellar systems, and is dependent on the heliocentric distance to, and morphology of, the stellar environment.
+
+%Observations here include a composite population.
+Some stars are members of the Sgr leading arm, others are members of the VOD/VSS (see \S\ref{sec:substructure-identification}), all superimposed upon a background of halo stars.
+We can identify some substructures kinematically, but we cannot differentiate halo stars within those velocity bins.
+However in our observed region there are known dominant structures.
+The Sagittarius stream dominates our negative $V_{GSR}$ population, and our positive kinematic space is largely comprised of members from the VOD (see \S\ref{sec:substructure-identification}).
+As such we have separated our population at $V_{GSR} = 0$ into two samples to ascertain $V_{HB}$ for the two most dominant populations; Sgr and the VOD.
+Although this technique introduces a (known) systemic effect, it is the most useful way to estimate the metallicity distribution of each population.
+\end{comment}
+
 As the distance to the Sgr debris varies greatly throughout the halo, the horizontal branch magnitude varies with the position along the stream. 
@@
 
+\begin{comment}
+The horizontal branch magnitude for the Sgr debris varies with age and distance.
+\citet{Belokurov;et-al_2006} determined distances along the two branches of the Sgr bifurcation using a colour-magnitude comparison with the Sgr main body \citep{Bellazzini;et-al_2006}.
+After being scaled for a revised distance modulus to the Sgr core \citep[$(m-M)_{0} = 17.27;$][]{Siegel;et-al_2007}, these distance measurements were used to constrain the more recent tri-axial halo simulation by LM10.
+We can use these observed distances (as tabulated in Table 1 of LM10) and the known absolute magnitude of RR Lyrae stars \citep[$M_V = +0.69;$][]{Tsujimoto;et-al_1998} to calculate the horizontal branch magnitude for each position of the Sgr stream.
+Reddening is accounted for each star using the maps of \citet{Schlegel;Finkbeiner;Davis_1998} and is scaled to the V-band with $A/E(B-V) = 3.240$.
+A spline is fitted to the tabulated right ascension and distance measurements, and the distance to each star is found by evaluating the right ascension of each star along the spline.
+Distance to the branch does not vary significantly with declination.
+The distance error is taken as the largest error from the two neighbouring distance measurements.
+%Distance errors are also propagated through to our reported metallicity error, which is at most $\sim 0.16$ dex. 
+\end{comment}
+
 \section{Discussion}
 \label{sec:discussion}
+
+		%Along our line of sight, the spatial region examined in this paper incorporates the superposition of multiple substructures, some of which may be inter-related.
+To facilitate a logical flow of discussion, these substructures are identified first and discussed separately.
 
@@
 	\begin{figure}[h!]
-		\includegraphics[width=\columnwidth]{./velocity_halo.eps}
+		\includegraphics[width=\columnwidth]{./figures/velocity-halo.eps}
 		\caption{Generalised histogram of $V_{GSR}$ for our 178 K-type giants, highlighting their significance against a canonical halo population.
@@
 
-The generalised histogram represents each data point with a Gaussian kernel of an equal width (deviation).
-As our internal kinematic errors between multiple measurements summate to a half-normal distribution with a FWHM of 7.16 km s$^{-1}$, we have opted for a sigma value of 10 km s$^{-1}$ the generalised histogram in Figure \ref{fig:velocity-histogram} to avoid under-smoothing.
+The generalised histogram represents each data point with a Gaussian kernel of an equal bandwidth (deviation).
+As our internal kinematic errors between multiple measurements summate to a half-normal distribution with a FWHM of 7.16 km s$^{-1}$, we have opted for a bandwidth value of 10 km s$^{-1}$ the generalised histogram in Figure \ref{fig:velocity-histogram} to avoid under-smoothing.
 
 	\begin{figure}[h!]
-		\includegraphics[width=\columnwidth]{./monte_carlo.eps}
+		\includegraphics[width=\columnwidth]{./figures/montecarlo.eps}
 		\caption{Monte-Carlo simulation results illustrating the number of times simulations could reproduce our observed data in the equivalent multi-dimensional bin.
 Significant features discussed in the text are labelled.}
+		%\caption{Results from our 10,000 binned kinematic and chemical Monte-Carlo simulations, overlaid with our observed K-giant sample properties.
+Each bin is coloured by the number of times Monte-Carlo simulations reproduced at least the same number of observed stars in that bin.
+Red bins indicate particularly rare clumps, and blue bins demonstrate common samples.}
 		\label{fig:monte-carlo}
 	\end{figure}
+%We have looked at stars in our dataset with repeated observations to gain an approximation for the bandwidth selection.
+% Their statistical significance is determined by a comparison to a canonical halo population \citep[$\mu = 0$ km s$^{-1}, \sigma = 101.6$ km s$^{-1}$][]{Sirko;et-al_2004}.
 
 	\begin{figure*}[t!]
-		\includegraphics[width=\textwidth]{./adapted_belokurov_2006.eps}
+		%\plottwo{./figures/belokurov2006.eps}{./figures/belokurov2006.eps} %#todo - bw/color + newline for caption
+		\includegraphics[width=\textwidth]{./figures/belokurov2006.eps}
 		\caption{Observed fields are outlined upon a panoramic view of the Sgr stream, to demonstrate our field locations in context with the Sagittarius stream.
@@
 Although the VOD is present, it is much more diffuse.
+\begin{comment}
+%It is useful to see how our fields spatially overlap with the Sgr stream. 
+	%\textit{N}-body models of the Sgr stream suggest highly negative velocities in this region (LJM05, LM10).
+This has led several authors who have observed negative kinematic peaks in nearby fields \citep{Yanny;et-al_2009, Prior;et-al_2009b}, to attribute these as members of Sagittarius as we have here.
+
+	%The bifurcation in Sagittarius \citep{Belokurov;et-al_2006} is evident here, and our observed fields overlap with the the lower declination Branch A.
+	%The consequential tidal tails from the Sgr-Milky Way interaction has been modelled by many groups \citep[e.g. ][]{Helmi_2004, Law;et-al_2005, Law;Majewski_2010}. 
+\end{comment}
 
@@
 For comprehensive details of the simulations the reader is referred to the papers of \citet{Law;et-al_2005} and \citet{Law;Majewski_2010}.
+%Simulations are matched to the 2MASS M-giant sample, which provides an all-sky view of the Sgr stream.
+%\citet{Law;et-al_2005} describe the Milky Way as a smooth, rigid potential and represent Sgr with $10^5$ self-gravitating particles.
+The Galactic potential is represented with three primary components; a \citet{Miyamoto;Nagai_1975} disk, a Hernquist spheroid and a logarithmic halo.
+The models of LJM05 have a constant degree of flattening, $q$, whereas the more recent LM10 tri-axial model has a minor/major axis ratio $(c/a)_\Phi = 0.72$ and an intermediate axis ratio $(b/a)_\Phi = 0.99$ at radii $20 < r < 60$ kpc.
+Their simulations adopt a spherical heliocentric coordinate system ($\Lambda_\odot, B_\odot$) where the longitudinal axis $\Lambda_\odot = 0^\circ$ at the Sgr core, and $B_\odot$ represents the best fitting great circle of the Sgr debris.
+For comprehensive details of the simulations the reader is referred to the papers of \citet{Law;et-al_2005} and \citet{Law;Majewski_2010}.
+The spatial distribution of the simulated Sgr tidal tails are illustrated in Figure \ref{fig:law-spatial}, which shows the simulated particles from the LJM05 and LM10 models, and our observed fields.
+To match realistic observation limitations we have not considered particles farther than 60 kpc.
 
 	\begin{figure}[t!]
-		\includegraphics[width=\columnwidth]{./sgr_spatial.eps}
+		\includegraphics[width=\columnwidth]{./figures/lawspatial.eps}
+		%\plottwo{./figures/law_spatial_copy.eps}{./figures/law_spatial_copy.eps} %#todo - b/w version
 		\caption{Our fields and observed bounds are shown with the simulated particles from multiple \textit{N}-body simulations by LJM05 and LM10.
-These particles are distance restricted (up to 60 kpc), and color-coded by their peri-centric passage following the same convention by \citet{Law;Majewski_2010} (orange;most recent passage, magenta; previous passage, cyan; oldest observable passage).}
+These particles are distance restricted (up to 60 kpc), and colour-coded by their peri-centric passage following the same convention by \citet{Law;Majewski_2010} (orange;most recent passage, magenta; previous passage, cyan; oldest observable passage).}
 		\label{fig:law-spatial}
 	\end{figure}
+%To evaluate how well models predict the position and kinematics of the Sgr debris, we require either a large set of accurate stellar kinematics and distances, or targeted regions of the stream where a change in the shape of the dark halo results in significantly different simulated positions and kinematics.
+The latter is particularly the case for our fields .
 
@@
 	\begin{figure*}[t!]
-		\includegraphics[width=\textwidth]{./sgr_velocities.eps}
+		\includegraphics[width=\textwidth]{./figures/lawvelcompare-bw.eps}
 		\caption{A generalised histogram (left) of the galactocentric rest frame velocities in our sample (dotted line) compared to the velocities (solid line) from the \textit{N}-body models of LJM05, LM10 of particles within the same spatial coverage and distance range (up to $r_\odot \sim 60$ kpc) of our observed sample.
@@
 Consequently the kinematics for each model have been represented as a generalised histogram (Figure \ref{fig:law-vel-compare}).
-For consistency all simulation output and observed data has been convolved with a Gaussian kernel of 10 km s$^{-1}$; the sigma used for the previous generalised histogram in Figure \ref{fig:velocity-histogram}.
+For consistency all simulation output and observed data has been convolved with a Gaussian kernel of 10 km s$^{-1}$; the bandwidth used for the previous generalised histogram in Figure \ref{fig:velocity-histogram}.
 Predicted distances and peri-centric ages are shown, demonstrating that debris from multiple passages are predicted along the line of sight.
 A much tighter velocity sequence is predicted here by the tri-axial model than the constant flattening models.
-This is because the tri-axial model predicts a pericenter almost precisely in our observable region, whereas the spherical and oblate models predicts a large wrap along the line of sight, resulting in a wide spread of distances and velocities.
+This is because the tri-axial model predicts a pericenter almost precisely in our observable region, whereas the spherical and oblate models forecast a large wrap along the line of sight, resulting in a wide spread of distances and velocities.
+
+	 %A generalised histogram is an effective method to evaluate the model predictions, because the size the overall distribution is scaled such that the integral of each distribution is unity.
+Therefore populations of different sizes (i.e.
+our observed sample and the varying size of each simulation output) are scaled appropriately so we can compare the kinematic signatures.
+One caveat of this technique is that the relative size of each sample must be acknowledged when evaluating the predictions made by a model.
+A narrow distribution \--- which may perfectly match the observed data \--- may simply be a consequence of an extremely small sample size, yielding an ineffective comparison.
+Indeed if we included a comparison with the prolate model the entire distribution may appear to represent the observed data closely in a qualitative sense, however that distribution would be composed from a mere two simulated particles.
+%One caveat for generalised histograms is that a narrow distribution (which may perfectly match observations) may simply be a consequence of a small number of predicted particles, yielding an ineffective comparison.
+With this caveat in mind we have shown the simulated particle distances in Figure \ref{fig:law-vel-compare}.
+In this region there is debris from multiple passages predicted along the line of sight.
+Particles have been marked by their recency of peri-centric passage.
+Distinguishing particles by their peri-centric age allows us to qualitatively differentiate relative kinematic contributions of the stream.
+In all three models, the Northern arm is clearly distinguishable, albeit the tri-axial model has a much tighter sequence in velocity.
+This is attributed to the position of the predicted pericenter.
+The tri-axial model predicts a pericenter almost precisely where our fields were observed, whereas the spherical and oblate model predict a large wrap of the stream along the line of sight, resulting in a large spread in kinematics and heliocentric distances.
 
@@
 If these signatures are present in our observed fields, their relatively low density compared to the northern arm feature would prevent them from appearing as significant.
+%Therefore, we cannot use the edge particles of these nearby simulated wraps to discern substantial information regarding the dark halo of the Milky Way.
 
@@
 Unlike other models considered, the tri-axial model does not reproduce the observed bifurcation in the Sgr stream \citep{Belokurov;et-al_2006}.
-Although observationally untested, it is reasonable to suggest a bifurcation may result from a significant kinematic disruption.
-Such an effect could result in a broader kinematic distribution \--- similar to what we observed \--- which is most notable at the stream edges.
+Although observationally untested, it is reasonable to suggest a kinematic disruption may result from the bifurcation.
+Such an effect would result in a broader kinematic distribution especially at the stream edges, precisely as seen in our data.
+\begin{comment}		
+	Although the debris kinematics may plausibly match our data, the tri-axial particles are predicted to be farther away than other model predictions.
+The tri-axial distribution is much narrower than our observed sample.
+Halo contamination in this distribution is likely to be small.
+The profile broadening in our sample extends most prominently at highly negative galactocentric velocities ($\sim-200$ km s$^{-1}$).
+Given any Gaussian-like population with a mean near zero, we would expect less halo members at high galactocentric velocities \--- positive or negative.
+One reconciliation for this profile discrepancy may lie in the workings of the tri-axial model itself.
+Unlike the other models compared here from LJM05, the tri-axial model does not reproduce the bifurcation observed in the Sgr stream \citep{Belokurov;et-al_2006}.
+Studies prior to the model development suggested the bifurcation may result from the progenitor internal dynamics, and not primarily consequential from the shape of the Milky Way dark halo \citep{Fellhauer;et-al_2006, Penarrubia;et-al_2010}.
+However a later study by \citet{Penarrubia;et-al_2011} found no evidence for internal rotation in the remnant core sufficient to produce the bifurcation.
+
+	A comparative targeted study along each branch is necessary to discern a kinematic disruption.
+Our observed region lies on the lower declination Branch A.
+Given that, the spread in velocity associated with a bifurcation would be observed.
+
+	The lack of bifurcation treatment in the LM10 model may explain the particularly narrow distribution predicted.
+Other groups have observed the spatial disruption caused by the bifurcation, however whether a kinematic variation exists between branches is observationally untested.
+Given the kinematic interactions within the progenitor, and the gravitational influence of the halo, it is reasonable to suggest a kinematic disruption may consequent from the bifurcation.
+Such an effect may result in a wider kinematic distribution, precisely as seen in our data.
+	% If these distance predictions are accurate they would likely be outside our observable range. Clearly more detailed investigation is required.
+\end{comment}
 
@@
 	\label{sec:sgr-metal-poor}
+
+	%The Sgr progenitor is a composite stellar population with a radial abundance declivity.
+As the host circles the Milky Way the older, more metal-poor stars are preferentially stripped from the progenitor \citep{Piatek;Pryor_1995}.
+	%While the core hosts the more metal-rich members \citep{Bonifacio;et-al_2004, Monaco;et-al_2005}, the most ancient wraps of the stream comprises the more metal-poor members \citep{Chou;et-al_2007}.
 
@@
 	\begin{figure}[h]
-		\includegraphics[width=\columnwidth]{./sgr_feh_hist.eps}
+		\includegraphics[width=\columnwidth]{./figures/fehhist.eps}
 		\caption{Metallicity histograms for K-giant members in our negative galactocentric velocity sample, which is largely populated by Sgr debris from the Northern leading arm.}
@@
 This is consistent with our observed metallicities.
-Although this does not prohibit the possibility of more metal-rich members within our sample, it implies that our distribution is somewhat biased towards the metal-poor end of the MDF.
+Although this does not prohibit the possibility of more metal-rich members within our sample, it implies that our distribution may be slightly biased towards the metal-poor end of the MDF.
 The tail of our Sgr distribution extends from $-0.71$ to $-2.35$ dex.
+\begin{comment}
+	%However since only the oldest, and most metal-poor stars can form RR Lyrae stars, this is a biased sample.
+Investigating the age-metallicity relationship and the MDF for the Sgr debris requires an unbiased sample of metallicities.
+K-giants are an excellent stellar candidate for such measurements as all stars go through this evolutionary phase.
+Thus, their metallicities are more representative of the true MDF.
+	% It does not fully represent the Sgr stream population, and we cannot infer information about the MDF of the stream from this sample. 
+	%The metallicity distribution for our negative galactocentric sample is shown in Figure \ref{fig:sgr-metallicity-hist}.
+This illustrates a metal-poor population in Sagittarius, with a mean of $\langle$[Fe/H]$\rangle = -1.73\,\pm\,0.33$ dex.
+If we include only the stars attributed to Feature A (Sgr debris), this value is $\langle$[Fe/H]$\rangle = -1.69\,\pm\,0.36$.
+This value didn't change significantly (to $-0.68$ dex) when their less certain subsample was included, and the difference within samples is less than their intrinsic dispersion ($\sim 0.3$ dex).
+Although our sample size of K-giants is larger (47 in this bin) than the sample used by \citet{Chou;et-al_2007} (31 M-giants), their members were sparsely positioned, and covered larger spatial range of the Sgr debris.
+The tail of our distribution extends from $-0.71$ to $-2.35$ dex.
+%Admittedly even though we have a larger sample, it is insufficient to accurately represent the entire MDF for this region of the stream.
+	% In this Sgr sample, we cannot unequivocally state that \textit{every} star is a member of Sgr debris.
+It is likely we have some fraction of halo members present in our sample.
+When we consider the Sgr debris members (Feature A), the clump in velocities and metallicity space is significant.
+This clump was never reproduced in 10,000 Monte-Carlo simulations.
+Although we cannot exclude contamination in our sample by halo members, it is clear Sgr is the most influential population in our negative velocity sample \--- dominant in both kinematic and chemical space.
+As such, this sample demonstrates an unbiased representation of Sgr debris metallicities along the leading arm; one which shows a much greater metal deficiency than previously reported.
 
+	This work illustrates the presence of a RGB metal-poor population in the Sgr debris, despite our target selection being biased towards this conclusion. 
+	It is unlikely that the reported abundance gradients
+
+	either: 1 we're biased the other way and m-giants biased towards metal-rich and there is more work to be done, demonstrating the Sgr debris has an extremely large range of metallicities
+
+		2. there is a larger abundance gradient larger than reported.
+
+	As members of metal-rich members of Sgr
+
+	Since members of Sgr are identified in this region with muc
+
+	\subsubsection{Are the peaks at $-44$ and $-81$ km s$^{-1}$ in Feature A related?}
+	\label{sec:sgr-peak-analysis}
+
+	Two of our strongest observed features occur at $V_{GSR} = - 44$ and $-81$ km s$^{-1}$ (Figure \ref{fig:velocity-histogram}).
+This section examines whether these two peaks are observations of unique structures within the Sgr stream, or a sampling artefact of a single feature.
+\citet{Vivas;et-al_2008} noted that the most populated group in their sample of BHB and RR Lyrae stars had a mean velocity of $V_{GSR} = -49$ km s$^{-1}$ with a standard deviation of 22 km s$^{-1}$, some of which were from the  \citet{Sirko;et-al_2004} sample.
+Metallicity measurements of their variables returned a mean metallicity of $\langle$[Fe/H]$\rangle$ = $-1.72$ dex with a standard deviation of 0.28 dex.
+Our K-giant metallicities agree with these findings.
+In the equivalent bin ($-80 < V_{GSR} < -10$ km s$^{-1}$) we find a mean of $\langle$[Fe/H]$\rangle = -1.7$ dex and a standard deviation of 0.3 dex.
+
+%This sample comprised of nine RR Lyrae stars and five BHB stars from the $-80 < V_{GSR} < -10$ km s$^{-1}$
+%In this region of high negative velocity, \citet{Vivas;et-al_2008} expect relatively high contamination from unrelated halo stars and suggest this may skew their kinematics.
+However they state this does not account for the diffuse metallicity distribution.
+The spread is likely representative of the true population, and not caused by the contamination of non-members into an otherwise narrow distribution.
+
+	\begin{figure*}[t!]
+		\includegraphics[width=\textwidth]{./figures/vivas-newberg-duffau.eps}
+		\caption{The sky coverage examined in this data set which contains K-giants within our velocity bin ranges $-54 < V_{GSR} < -34$ km s$^{-1}$ (green squares) and $-91 < V_{GSR} < -71$ km s$^{-1}$ (blue circles), and the spatial coverage examined by \citet{Newberg;et-al_2007} who separately noted an identical peak at $V_{GSR} = -76$ km s$^{-1}$.
+The exact positions of stars found within this bin were unavailable.
+Sky covered by \citet{Vivas;et-al_2008} extends outside this plot, although all stars assigned to their peak at $V_{GSR} = -49$ km s$^{-1}$ are shown.}
+		\label{fig:newberg-duffau-vivas-spatial}
+	\end{figure*}
+
+% However, contrary to \citet{Vivas;et-al_2008}, we find a narrow peak in this distribution whereas \citet{Vivas;et-al_2008} found a sparse distribution at [Fe/H] $\sim-1.7$ and no indications of contamination by non-members.
+Multiple groups have noted the peak near $V_{GSR} = -81$ km s$^{-1}$.
+
+\citet{Vivas;et-al_2008} did not identify an additional peak at $-81$ km s$^{-1}$, whereas \citet{Duffau;et-al_2006} noted slight peaks at $-49$ and $-76$ km s$^{-1}$ in their sample which included 10 BHBs from the \citet{Sirko;et-al_2004} sample as well.
+The peak at $V_{gsr} = -76$ km s$^{-1}$ was also noted by \citet{Brink;et-al_2010} in their narrow spatial area (within our Field 2).
+Due to different galactocentric transformations, \citet{Brink;et-al_2010} measurements are offset from ours by up to $\sim{}+12$ km s$^{-1}$.
+
+\citet{Newberg;et-al_2007} found a 3-$\sigma$ excess of F-type stars in the $-80 < V_{GSR} < -48$ km s$^{-1}$ bin, centered on $-76$ km s$^{-1}$.
+Using the same galactocentric transformations as \citet{Newberg;et-al_2007}, our velocities would be consistently more positive with a mean offset of $+7.8\pm3.2$ km s$^{-1}$, implying our K-giants and these F-types are members of the same structure.
+
+%Distance estimates suggest this structure and the $-44/-49$ km s$^{-1}$ feature are distinct, although there are large uncertainties.
+RR Lyrae measurements place the \citet{Vivas;et-al_2008} feature at $7.5 < D < 9.5$ kpc and conservative estimates ($M_{g_0}=+4.2$) place the F-type sample at $11 \lesssim D \lesssim 14$ kpc
+
+%\citet{Vivas;et-al_2008} argues that given the observational uncertainties, the \citet{Newberg;et-al_2007} stars may be members of their $-49$ km s$^{-1}$ structure, however the distances have not been reconciled yet.
+RR Lyraes in the \citet{Vivas;et-al_2008} $-49$ km s$^{-1}$ sample have a distance of $7.5 < D < 9.5$ kpc, whereas conservative estimates place the \citet{Newberg;et-al_2007} F-type sample at $11 \lesssim D \lesssim 14$ kpc.
+
+%This variation is spatially dependent, and as such the discrepancy between our peaks cannot be accounted for without tabulated spatial and kinematic information for each star.
+Mismatching the offsets could incur an incorrect variation of up to 11 km s$^{-1}$, simply because of the sky covered.
+%The discrepancy between our $-81$ km s$^{-1}$ peak and the $-76$ km s$^{-1}$ signature found by \citet{Newberg;et-al_2007} may be reconcilable.
+Using the same kinematic transformation as \citet{Newberg;et-al_2007}, our reported velocities would be consistently more positive with a mean offset of $+7.8\pm3.2$ km s$^{-1}$.
+\citet{Newberg;et-al_2007} notes that their $-76$ km s$^{-1}$ feature is more pronounced in the fainter $(l, b) = (300^\circ, 55^\circ)$ field, although upon recognising the feature they note it is also seen in their more northerly plate at $(288^\circ, 62^\circ)$.
+The more spatially prominent region covered by \citet{Newberg;et-al_2007} was not observed by \citet{Vivas;et-al_2008}, so the spatial overlap between these authors could not be fully investigated.
+
+%The sky covered by \citet{Duffau;et-al_2006} (which included the $-49$ and $-76$ km s$^{-1}$ features) ranged from ($\alpha, \delta$) $\approx$ (175 to 200$^\circ$, $-2$ to 0$^\circ$), which overlaps with this work and the \citet{Newberg;et-al_2007} fields (Figure \ref{fig:newberg-duffau-vivas-spatial}).
+Our $-81$ km s$^{-1}$ group is most spatially concentrated within ($\alpha, \delta$) = (189 to 195$^\circ$, $-3.5$ to $-1.5^\circ$), which overlaps where \citet{Duffau;et-al_2006} observed a similar peak and extremely close to the centroid where \citet{Newberg;et-al_2007} found their $-76$ km s$^{-1}$ peak of F-type stars.
+
+	\begin{figure}[h]
+		\includegraphics[width=\columnwidth]{./figures/feh-peak-bins.eps}
+		\caption{Metallicity distribution for K-giants within the two nearby peaks at $V_{GSR} = -44$ km s$^{-1}$ (top) and $-81$ km s$^{-1}$ (bottom).}
+		\label{fig:feh-peak-bins}
+	\end{figure}
+
+	The kinematic peaks near $V_{GSR} = -44$ and $-81$ km s$^{-1}$ overlap spatially (Figure \ref{fig:newberg-duffau-vivas-spatial}) and have been reported separately by multiple authors.
+Metallicities for these kinematic bins (Figure \ref{fig:feh-peak-bins}) do not demonstrate a substantial difference in mean abundance.
+If these two kinematic peaks are indeed separate
+
+	\citet{Vivas;et-al_2008} argue that given the observational uncertainties the \citet{Newberg;et-al_2007} sample at $-76$ km s$^{-1}$ may be members of their $-49$ km s$^{-1}$ sample.
+However the kinematic dispersions for these groups are quite low; 22 km s$^{-1}$ for the \citet{Vivas;et-al_2008} $-49$ km s$^{-1}$ sample and a mere 10 km s$^{-1}$ for the \citet{Newberg;et-al_2007} $-76$ km s$^{-1}$ sample.
+Moreover, the two peaks (within galactocentric transformation discrepancies) have been identified by many groups \citep[and this work]{Sirko;et-al_2004,Duffau;et-al_2006, Newberg;et-al_2007, Vivas;et-al_2008}.
+Separate repeat kinematic observations suggests these two features are distinct, although metallicity estimates from these observations do not demonstrate a mean abundance difference.
+Further abundance analysis may reveal a discernible difference between the two kinematic bins.
+
+	%The two samples may have identifiable abundance discrepancies which could differentiate them.
+
+	 %illustrates the metallicities for these two peaks.
+Although the sample size here is small, the $-81$ km s$^{-1}$ signature seems to peak in metallicity at the same point as our Sgr debris, whereas the $-44$ km s$^{-1}$ apex shows a sparse distribution.
+
+	%A larger sample is favourable as it is problematic to distinguish or otherwise assign common membership to these moving groups.
+
+	 %However due to larger spectroscopic sample obtained here, and previously repeated measurements by multiple authors, it is suggested these may be separate kinematic structures superimposed on one another.
+This claim is further strengthened given the kinematic dispersions from previous groups; 22 km s$^{-1}$ for the $-49$ km s$^{-1}$ by  \citet{Vivas;et-al_2008} and 10 km s$^{-1}$ for the $-76$ km s$^{-1}$ group by \citet{Newberg;et-al_2007}.
+If these structures are distinct, whether they are all associated to Sgr debris is a secondary question.
+Further investigation in this region is required.
+
+\end{comment}
 	\subsection{Feature B \--- The Virgo Stellar Stream}
@@
 Several RR Lyrae stars were noted with a common velocity of $V_{GSR} = 130$ km s$^{-1}$ \citep{Newberg;et-al_2007, Prior;et-al_2009a}.
-\citet{Prior;et-al_2009a} also measured metallicities of stars with this kinematic signature and found a mean [Fe/H] $= -1.95\,\pm\,0.1$ for the VSS, although this is based on RR Lyraes and is therefore potentially biased to the metallicity of the oldest populations.
+\citet{Prior;et-al_2009a} also calculated metallicities of stars with this kinematic signature and found a mean [Fe/H] $= -1.95\,\pm\,0.1$ for the VSS, although this is based on RR Lyraes and is therefore potentially biased to the metallicity of the oldest populations.
 The RR Lyrae sample from \citet{Duffau;et-al_2006} found a $\langle$[Fe/H]$\rangle = -1.86$ with a much larger abundance spread of $\sigma = 0.40$, which was several times the relative uncertainty in individual values ($\sigma_{\mbox{[Fe/H]}} = 0.08$ dex).
-This led \citet{Duffau;et-al_2006} to infer the progenitor of the VSS was likely a dSph galaxy, as a large dispersion in $\mbox{[m/H]}$ indicates self-enrichment and implies the structure is a galaxy and not an isolated stellar cluster \--- although there are numerous globular clusters with multiple populations.
-Similar to \citet{Duffau;et-al_2006}, we  also observe an abundance spread within this kinematic bin including some giants with kinematics and metallicities ($V_{GSR} = 130 \pm 9$ km s$^{-1}$, [Fe/H] =$ -2.0 \pm 0.16$) matching those found by \citet{Prior;et-al_2009a}.
+This led \citet{Duffau;et-al_2006} to infer the progenitor of the VSS was likely a dSph galaxy, as a large dispersion in $\mbox{[m/H]}$ indicates self-enrichment and implies the structure is a galaxy and not an isolated stellar cluster.
+We  also see an abundance spread within this kinematic bin, including some giants with kinematics and metallicities ($V_{GSR} = 130 \pm 9$ km s$^{-1}$, [Fe/H] =$ -2.0 \pm 0.16$) matching those found by \citet{Prior;et-al_2009a}.
 Monte-Carlo simulations reproduced these few targets a mere $\sim1$\% in 10,000 simulations \--- demonstrating their significance.
+
+	%Based on measurements of seven type ab RRLs that have values of Vgsr that are consistent with membership, the VSS has <[FE/H]> = -1.86 and sigma= 0.40.
+Because this dispersion is several times the average of the sigma feh values (0.08) we conclude that the VSS has a significant range in [Fe/H].
+A range of this magnitude is characteristic of all the dSph satellite galaxies of the Milky Way but not of the vast majority of globular clusters
+
+	%We cannot unequivocally state whether members of the VSS are present in our K-giant sample \textit{only} from looking at kinematic signatures alone.
+In Figure \ref{fig:velocity-histogram} there is a peak at $V_{GSR} = +130$ km s$^{-1}$, however this is not as dominant as found by other authors.
+
+	% The most likely VSS K-giant members are visibly separated from the bulk sample in velocity-metallicity space (Figure \ref{fig:velocity-metallicity}.
+Galactocentric velocities of these candidates ranges from $V_{GSR} = 127$ to $132$ km s$^{-1}$; which matches the kinematic signature seen by others studying the VSS.
+Furthermore the metallicities of our most probable candidates range from [Fe/H] = -1.89 to -2.03, identical to metallicity measurements of the VSS found by \citet{Prior;et-al_2009a} using RR Lyraes.
+Although RR Lyraes are typically representative of an older, more metal-poor population, it is interesting that these candidates match the VSS characteristics in spatial position, velocity, and metallicity.
+Monte-Carlo simulations replicated this clump at $V_{GSR} = +130$ km s$^{-1}$ and [Fe/H]$ = -1.95$ a mere 11 times in 10,000 \--- demonstrating their significance.
+
+	%\begin{figure}[h]
+	%	\includegraphics[width=\columnwidth]{./figures/vss-candidates_copy.eps}
+	%	\caption{Galactocentric velocities and metallicity measurements for K-giants in our sample.
+Members contributing to the VSS peak are shaded, and our most probable VSS K-giant candidates are identified.}
+	%	\label{fig:velocity-metallicity}
+	%\end{figure}
 
@@
 Future observations are planned.
+
+%K-Giants are the perfect candidate for high resolution spectroscopy, as they are cool enough to provide detailed elemental abundances, from which the formation history of the parent origin can be inferred.
 
@@
 
+%In any case we can be sure that the CaT-[Fe/H] calibration yields realistic metallicities.
+
 	This substructure has a range of metallicities on our scale.
@@
 On our scale that would make these stars more metal-rich than shown in Figure \ref{fig:monte-carlo}.
-However the nearest trailing debris particles predicted from any best-fitting dark halo potential that could explain this kinematic peak occurs at $\sim\Lambda_\odot = 310^\circ$; our observations range in $\Lambda_\odot$ between $256-273^\circ$.
+However the nearest trailing debris particles predicted from any best-fitting dark halo potential that could explain this kinematic peak occurs at $\sim\Lambda_\odot = 310^\circ$; our observations range in $\Lambda_\odot$ between $256^\circ-273^\circ$.
 Whether this substructure is separate from Sagittarius debris or not remains equivocal.
-Nevertheless the apparent metallicities of the Feature C stars are not inconsistent with those of a Sgr population given our results for Feature A and those of \citet{Keller;Yong;Da_Costa_2010}.
 
@@
 	In our sample we have identified five carbon stars.
-With the color selections to target K-giants, this region also overlaps with where we would expect to find carbon stars (Figure \ref{fig:carbon-sdss}).
+With the colour selections to target K-giants, this region also overlaps with where we would expect to find carbon stars (Figure \ref{fig:carbon-sdss}).
 Although these stars were not specifically targeted, their surface densities are so low \citep[$\approx$ 1 per 50 deg$^2$;][]{Green;et-al_1994} that we would not expect them as a substantial contaminant.
@@
 
+\begin{comment}
+	\begin{figure}[h]
+		\includegraphics[width=\columnwidth]{./figures/carbon_copy.eps}
+		\caption{J-H and H-K colours for carbon stars recovered by \citet{Totten;et-al_2000}, and those found in this sample.
+Four of our five carbon stars are represented with plus symbols (+); 2MASS photometry for our faintest carbon star was not available.
+Carbon stars identified in this work have been shaded for clarity.
+This plot is an adaptation of Figure 3 in \citet{Totten;et-al_2000}.}
+		\label{fig:carbon-colours}
+	\end{figure}
+\end{comment}
+
 \begin{figure}[h!]
-	\includegraphics[width=\columnwidth]{./carbon_stars.eps}
-	\caption{Sloan \textit{u \--- g} and \textit{g \--- r} colors for our carbon stars, and the identified carbon stars and classifications by \citet{Downes;et-al_2004}.
+	\includegraphics[width=\columnwidth]{./figures/carbonstarcolor.eps}
+	\caption{Sloan \textit{u \--- g} and \textit{g \--- r} colours for our carbon stars, and the identified carbon stars and classifications by \citet{Downes;et-al_2004}.
 Carbon stars identified in this work have been shaded for clarity.}
@@
 
-	 Dwarf carbon stars exhibit a spectral signature which mimics that of a typical CH-type giant carbon star, however they have anomalous JHK colors \citep{Green;et-al_1992} and high proper motions.
+	%There are at least three kinds of carbon stars present in the halo; (i) N-type carbon stars, (ii) giant CH-type carbon stars and (iii) and dwarf CH-type carbon stars \citep{Totten;Irwin_1998}.
+N-type carbon stars are formed by carbon-enriched dredge-up during the post-main-sequence phase of a normal asymptotic giant branch (AGB) star.
+First generation carbon stars (CH-type) are not considered to have undergone carbon-enriched dredge-up, and their carbon abundance is attributable to mass transfer within a binary system.
+
+%These dwarf carbon stars are believed to form in binary systems where material has accreted from a now-invisible companion during its ascent up to the AGB \citep{Dahn;et-al_1977}.
+Giant CH-type carbon stars are similar to metal-poor carbon stars found in globular clusters \citep{Harding_1962} and in some dSph galaxies \citep{Demers;Battinelli_2002}.
+
+	 Dwarf carbon stars exhibit a spectral signature which mimics that of a typical CH-type giant carbon star, however they have anomalous JHK colours \citep{Green;et-al_1992} and high proper motions.
 The existence of the 4300 \AA{} CH G-band is representative of a CH-type carbon star, and is found in all five of our carbon stars.
@@
 	There is 2MASS photometry available for four of these stars.
-Of those, two stars (SDSS J125410.80-032744.0 and J125416.52-031437.6) exhibit anomalous JHK colors and significant ($> 3\sigma$) proper motions; characteristics of a dwarf carbon star.
+Of those, two stars (SDSS J125410.80-032744.0 and J125416.52-031437.6) exhibit anomalous JHK colours and significant ($> 3\sigma$) proper motions; characteristics of a dwarf carbon star.
 A third star also exhibits significant proper motion (SDSS J121740.94-001839.5), however JHK photometry is unavailable.
@@
 
+%Measuring the gravity sensitive Mg I triplet lines in both synthetic and observed spectra, we have demonstrated an excellent dwarf/giant separation criterion.
 	We present spectroscopic observations of K-type stars in a crowded region of the 'Field of Streams', where significant substructure is present.
@@
 
+	%Through investigating Sgr debris we have identified multiple kinematic peaks as found by other authors.
+These peaks have a small kinematic separation compared to the observational uncertainties.
+Although our sample size is small, the first hint of these structures as being separate entities has been identified through apparent discrepancies in their metallicity distribution functions.
 	Stars in this region of the Sagittarius stream are kinematically sensitive to the shape of the Galactic dark halo.
@@
 Typically, leading arm debris favour prolate models and trailing arm debris favour oblate models.
-A prolate dark halo predicts relatively little debris in our observed fields.
+A prolate dark halo predicts no debris in our observed fields.
 If the spheroid is prolate and LJM05 presents an accurate representation, we would not expect Sgr debris to dominate our sample (as it does so) even if we were $\Delta{}B_\odot\sim10^\circ$ closer to the great circle best-fit.
@@
 These observations also demonstrate that the Sagittarius stream hosts a substantially larger abundance range than previously found, including a previously uncovered metal-poor population of K-giants.
+
+	%This suggests either higher abundance gradients along the stream than previously reported, or the Sgr debris has an extremely wide metallically spread.
+Although biased towards metal-rich members, \citet{Chou;et-al_2007} find a mean metallicity of $\langle[$Fe/H$]\rangle = -0.72 \pm 0.30$ dex along the leading arm from M-giants.
+These contrasting observations imply the metallicity distribution function of the debris remains largely unknown.
+\begin{comment}
+
+	at one point Sagittarius hosted a substantial spread in abundances, and that the metallicity distribution function for the debris remains a mystery.
+
+	including the metal-poor population found here.
+
+	This suggests that thereAlthough this K-giant sample 	
+	M-giant studies in this region by
+
+	These observations host a sample of K-giant metallicities for Sagittarius debris along the leading arm.
+
+	In contrast to   who found a mean metallicity of  stream in their metal-rich biased M-giant sample, we find a mean metallicity of  Although we have large uncertainties in our metallicity distribution, this is indicative of a more metal-poor population present within this region of the stream.%This is representative of the generally more metal-poor, older population along this region of the stream.
+
+	This work illustrates the presence of a RGB metal-poor population in the Sgr debris, despite our target selection being biased towards this conclusion. 
+	It is unlikely that the reported abundance gradients
+
+	either: 1 we're biased the other way and m-giants biased towards metal-rich and there is more work to be done, demonstrating the Sgr debris has an extremely large range of metallicities
+
+		2. there is a larger abundance gradient larger than reported.
+
+	As members of metal-rich members of Sgr
+
+	Since members of Sgr are identified in this region with muc 
+\end{comment}
 
@@
 \bibliographystyle{apj}
-\bibliography{bibliography}
+\bibliography{draft}
 

### 2012-05-28 2011-sgr/ads_defns.tex
Initial commit.

\newcommand{\aj}{AJ}                   % Astronomical Journal
\newcommand{\araa}{ARA\&A}             % Annual Review of Astron and Astrophys
\newcommand{\apj}{ApJ}                 % Astrophysical Journal
\newcommand{\apjl}{ApJ}                % Astrophysical Journal, Letters
\newcommand{\apjlett}{ApJ}
\newcommand{\apjs}{ApJS}               % Astrophysical Journal, Supplement
\newcommand{\apjsupp}{ApJS}     
\newcommand{\ao}{Appl.~Opt.}           % Applied Optics
\newcommand{\applopt}{Appl.~Opt.} 
\newcommand{\apss}{Ap\&SS}             % Astrophysics and Space Science
\newcommand{\aap}{A\&A}                % Astronomy and Astrophysics
\newcommand{\astap}{A\&A}  
\newcommand{\aapr}{A\&A~Rev.}          % Astronomy and Astrophysics Reviews
\newcommand{\aaps}{A\&AS}              % Astronomy and Astrophysics, Supplement
\newcommand{\azh}{AZh}                 % Astronomicheskii Zhurnal
\newcommand{\baas}{BAAS}               % Bulletin of the AAS
\newcommand{\jrasc}{JRASC}             % Journal of the RAS of Canada
\newcommand{\memras}{MmRAS}            % Memoirs of the RAS
\newcommand{\mnras}{MNRAS}             % Monthly Notices of the RAS
\newcommand{\pra}{Phys.~Rev.~A}        % Physical Review A: General Physics
\newcommand{\prb}{Phys.~Rev.~B}        % Physical Review B: Solid State
\newcommand{\prc}{Phys.~Rev.~C}        % Physical Review C
\newcommand{\prd}{Phys.~Rev.~D}        % Physical Review D
\newcommand{\pre}{Phys.~Rev.~E}        % Physical Review E
\newcommand{\prl}{Phys.~Rev.~Lett.}    % Physical Review Letters
\newcommand{\pasp}{PASP}               % Publications of the ASP
\newcommand{\pasj}{PASJ}               % Publications of the ASJ
\newcommand{\qjras}{QJRAS}             % Quarterly Journal of the RAS
\newcommand{\skytel}{S\&T}             % Sky and Telescope
\newcommand{\solphys}{Sol.~Phys.}      % Solar Physics
\newcommand{\sovast}{Soviet~Ast.}      % Soviet Astronomy
\newcommand{\ssr}{Space~Sci.~Rev.}     % Space Science Reviews
\newcommand{\zap}{ZAp}                 % Zeitschrift fuer Astrophysik
\newcommand{\nat}{Nature}              % Nature
\newcommand{\iaucirc}{IAU~Circ.}       % IAU Cirulars
\newcommand{\aplett}{Astrophys.~Lett.} % Astrophysics Letters
\newcommand{\apspr}{Astrophys.~Space~Phys.~Res.}
                % Astrophysics Space Physics Research
\newcommand{\bain}{Bull.~Astron.~Inst.~Netherlands} 
                % Bulletin Astronomical Institute of the Netherlands
\newcommand{\fcp}{Fund.~Cosmic~Phys.}  % Fundamental Cosmic Physics
\newcommand{\gca}{Geochim.~Cosmochim.~Acta}   % Geochimica Cosmochimica Acta
\newcommand{\grl}{Geophys.~Res.~Lett.} % Geophysics Research Letters
\newcommand{\jcp}{J.~Chem.~Phys.}      % Journal of Chemical Physics
\newcommand{\jgr}{J.~Geophys.~Res.}    % Journal of Geophysics Research
\newcommand{\jqsrt}{J.~Quant.~Spec.~Radiat.~Transf.}
                % Journal of Quantitiative Spectroscopy and Radiative Transfer
\newcommand{\memsai}{Mem.~Soc.~Astron.~Italiana}
                % Mem. Societa Astronomica Italiana
\newcommand{\nphysa}{Nucl.~Phys.~A}   % Nuclear Physics A
\newcommand{\physrep}{Phys.~Rep.}   % Physics Reports
\newcommand{\physscr}{Phys.~Scr}   % Physica Scripta
\newcommand{\planss}{Planet.~Space~Sci.}   % Planetary Space Science
\newcommand{\procspie}{Proc.~SPIE}   % Proceedings of the SPIE
%
%\let\astap=\aap
%\let\apjlett=\apjl
%\let\apjsupp=\apjs
%\let\applopt=\ao

### 2012-05-28 2011-sgr/draft.tex
Initial commit.

%% \documentclass{aastex}
\documentclass{emulateapj}

\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{booktabs} % For toprule and bottomrule in tables
\usepackage{multirow}
\usepackage{amsmath}

\newcommand{\pasa}{PASA}               % PASA

\shorttitle{To be decided by committee after the Summer Solstice}
\shortauthors{Casey, Keller and Da Costa}

\begin{document}

	\title{To be decided by committee after the Solstice}
	\author{Andy Casey, Stefan Keller, Gary Da Costa}
	\affil{	Research School of Astronomy \& Astrophysics,
		Australian National University,
		Canberra, Australia}

	\begin{abstract}

	\end{abstract}

	\keywords{Galaxy: halo, structure --- Stars: abundances}

	\section{Introduction}

	The proportion of substructure uncovered in the Galactic stellar halo over the last few decades has highlighted the crucial involvement accretion has played in the formation of the Milky Way. Properties of these stellar structures allow us to probe both the formation mechanisms and history of the Galaxy. This technique of studying stellar populations as surrogates of galactic archeology was first proposed in the seminal paper of \citet{Eggen;Lynden-Bell;Sandage_1962} who observed a metallicity abundance declivity in stars from the disk to the halo. From these measurements they inferred that  the Galaxy formed by a rapid collapse of a relatively homogenous protogalactic cloud. In contrast of this inference, \citet{Searle;Zinn_1978} observed a wide scope of metallicities within globular clusters irrespective of their galactocentric distance, which implied a formation paradigm based on the hierarchical accretion of protogalactic fragments. Recent studies \citep{Carollo;et-al_2007, Carollo;et-al_2010} have suggested multiple evolution mechanisms are required for galaxy formation to reconcile observational evidence, although this is a subject for ongoing debate. Regardless, the quiescent dissipation-less merging paradigm is widely accepted, and consistent with favoured Cold Dark Matter ($\Lambda$CDM) cosmology models. Through the examination of ongoing accretion events in the Milky Way and fossils from previous mergers, we can ultimately trace the formation history of the Galaxy.

	The stellar halo has formed at least partly \citep{Starkenburg;et-al_2009}, if not entirely by accretion. \citet{Bell;et-al_2008} compared observations from the Sloan Digital Sky Survey \citep[hereafter SDSS]{York;et-al_2000} to simulations and found that observations are consistent with the stellar halo being entirely formed by the hierarchical merging of accreted satellites.

	Unquestionably the most prominent accretion event within the Milky Way is that of the Sagittarius (Sgr) dwarf Spheroidal (dSph) galaxy. Originally uncovered by \citet{Ibata;et-al_1994} as a co-moving group of K- and M-type giants, the tidal tails of Sgr circle our Galaxy, and as such they have been extensively traced with red-clump stars \citep{Majewski;et-al_1999}, carbon stars \citep{Totten;Irwin_1998, Ibata;et-al_2001}, RR Lyrae stars \citep{Ivezic;et-al_2000, Vivas;et-al_2005, Watkins;et-al_2009, Prior;et-al_2009a}, A-type stars \citep{Newberg;et-al_2003} and K/M-giants \citep{Majewski;et-al_2003}. With spatial and kinematical information, tracers originating from the dwarf progenitor can be unequivocally identified. This is because they remain dynamically cold and identifiable as kinematic substructure long after they are stripped from their progenitor \citep{Ibata;Lewis_1998, Helmi;White_1999}.

	Stellar tracers within these tails are kinematically sensitive to the galactic potential. Their bulk kinematic signature is reflective of the shape and quantity of dark matter in the Milky Way. This has led various groups to model the Sgr tidal tails in different galactic potentials. \citet{Martinez-Delgado;et-al_2004} traced the northern arm and found a near spherical or oblate ($q \approx 0.85$) dark matter halo best represented the observed debris, which coincides with the findings of \citet{Ibata;et-al_2001}. In contrast, \citet{Helmi_2004} found evidence in the Sgr leading debris kinematics that most favoured a prolate ($q = 1.25$) halo. \citet{Vivas;et-al_2005} found that either the prolate or spherical models of  \citet{Helmi_2004} best fit their observed RR Lyrae data than those of an oblate model. \citet{Johnston;et-al_2005} later pointed out that no prolate model can reproduce the orbital pole procession of the Sgr debris, but an oblate potential excellently replicated the procession. \citet[hereafter LJM05]{Law;et-al_2005} performed simulations using data of the Sgr debris from the 2-Micron All Sky Survey (2MASS) catalogue and found that the kinematics of leading debris was best fit by prolate halos, whereas the trailing debris favoured oblate halos.

	\citet{Belokurov;et-al_2006} found an apparent bifurcation within the Sgr debris, which \citet{Fellhauer;et-al_2006} argued can only result with by a dark halo having close to a spherical shape. \citet{Law;et-al_2009} introduced a tri-axial model with a varying flattenning profile $q$ which replicates the orbital procession seen, and kinematically matches observations of the Sgr debris. However, \citet{Law;Majewski_2010} (hereafter LM10) concedes this may be a purely numerical solution as tri-axial halos are dynamically unstable, and admits more kinematic observations in other regions of the Sgr stream are required.

	After the Sgr stellar stream, the Virgo Over-Density (VOD) is arguably the next most significant substructure within our Galaxy. The first over-density in the vicinity of the VOD was observed as a group of RR Lyrae stars ~13 kpc away by the QUEST survey \citep{Vivas;et-al_2001}. The collaboration later named this the ``$12\fh4$ clump'' \citep{Zinn;et-al_2004}. The broad nature of the VOD as a diffuse over-density of main-sequence turnoff stars centered at $r_\odot \sim18 \text{kpc}$ \citep[which ][dubbed as S297+63-20.5]{Newberg;et-al_2002} was uncovered within the SDSS catalogue. The nomenclature on the substructure names within this region is varied, however when referring to the VOD we are discussing the spatial over-density of stars within the region which includes numerous distinct superimposed moving groups. Within the VOD itself, multiple studies find a peak density of RR Lyrae \citep{Vivas;et-al_2001, Ivezic;et-al_2005} and F-type main sequence stars \citep{Newberg;et-al_2002} at (R.A., Dec) = (190$^\circ$, 0$^\circ$). Close by, \citet{Juric;et-al_2008} find the F-type main sequence peak at (R.A., Dec) = (192$^\circ$, +2$^\circ$) and \citet{Keller_2010} finds the sub-giant peak density at (R.A., Dec) = (194.6$^\circ$, +1.8$^\circ$). The exact spatial centroid of the VOD remains equivocal, and appears to be influenced by the selection effects of stellar type.

	%, which was  found to be a co-moving group and was titled the Virgo Stellar Stream \citep[VSS;]{Duffau;et-al_2006} to distinguish it from the VOD.%

	Furthermore, the spatial bounds of the VOD remains unclear. There is some agreement that the boundaries of the structure extend outside the SDSS catalogue \citep{Newberg;et-al_2007,Prior;et-al_2009a,Keller;et-al_2009}. Observations to date represent lower limits on the VOD extent.\citet{Juric;et-al_2008} used photometric parallaxes to describe a diffuse over-density spanning $\sim$1000 deg$^2$, whereas \citet{Prior;et-al_2009a} estimated a coverage of $\sim$760 deg$^2$ from the luminosity function excess in the region. \citet{Duffau;et-al_2006} previously used a similar technique to \citet{Prior;et-al_2009a} and yielded a minimum sky coverage of 106 deg$^2$. A spatial boundary of 144 deg$^2$ was derived by \citet{Keller_2010} for the VOD from the luminosity function excess of sub-giants, which is more in-line with \citet{Duffau;et-al_2006} as a lower limit than other studies, which \citet{Keller_2010} attributes to low resolution data.

	Within this region of sky there are multiple substructures along the line of sight. \citet{Duffau;et-al_2006} took observations of BHB and RR Lyrae within the ``$12\fh4$ clump'' and found a common velocity of $V_{GSR} = 99.8$ km s$^{-1}$ with $\sigma = 17.3$ km s$^{-1}$. This kinematic distinction from the VOD was strengthened by distance estimations which placed the VOD centroid at $r_{\odot} = 16 \text{kpc}$ \citep{Juric;et-al_2008, Keller_2010}, and the VSS 3 kpc further away \citep{Duffau;et-al_2006}. However, \citet{Juric;et-al_2008} suggests the VOD may extend from heliocentric distances between 6 to 20 kpc, complicating the matter of distance separation.

	The relationship between the VSS and the S297+63-20.5 over-density is still unclear. \citet{Newberg;et-al_2007} found a kinematic signature of $V_{GSR} = 130 \pm 10$ km s$^{-1}$ for S297+63-20.5, which is remarkably close to the VSS. The VSS and S297+63-20.5 are co-incident in space, but the relationship between the two is not certain as the velocity difference has not yet been reconciled. \citet{Newberg;et-al_2007} estimate a distance to S297+63-20.5 of $r_{\odot} = 18 \text{kpc}$ from $g_0 = 20.5$ turnoff stars, but they concede the structure is likely dispersed along the line of sight as the color-magnitude diagram of this region does not demonstrate a tight sequence. The distance measurements between S297+63-20.5 and the VSS are remarkably similar enough ($\sim1 \text{kpc}$) for \citet{Newberg;et-al_2007,Prior;et-al_2009a} to infer they are part of the same structure.

	Whether these signatures are indeed separate entities or a consequence of combined measurement error between groups remains unclear. However it is certain that this region of sky, aptly coined as the 'Field of Streams' by \citet{Belokurov;et-al_2006}, is complex territory.

	In this paper we present spectroscopic observations of K-giants in this region. We use the kinematics of these relics to probe the dark halo of the Galaxy, and use the spatial, kinematic and metallicity signatures to distinguish, and strengthen substructure relationships in this accretion-dominated region.

	Target selection methodology is outlined in the next section, which is followed by detailed information regarding the observations. Our technique to separate K-giants from dwarfs are discussed in \S\ref{sec:dwarf-giant-separation}, and our analysis procedure for kinematics (\S\ref{sec:kinematics}) and metallicites (\S\ref{sec:metallicities}) follows. A discussion of substructures is outlined in \S\ref{sec:discussion} and in \S\ref{sec:conclusions} we conclude with some final remarks and critical interpretations.

	\section{Target Selection}
	\label{sec:target-selection}

	Our tracer selection for these observations were K-type giants. When the presence of a substructure  is uncovered, K-giants provide an excellent stellar type for spectroscopic follow-up as they provide precise radial velocities and allow for detailed chemical abundance analysis.

\begin{figure}[h!]
	\centering
	\includegraphics[width=9.2cm,height=6.8cm]{./figures/cmd.eps}
	\caption{Colour-magnitude diagram of the observed regions, illustrating the colour selection box.}
	\label{fig:cmd-target-selection}
\end{figure}

\noindent In order to specifically target K-giants, we have chosen candidates within the colour selection box

	\begin{eqnarray}
				0.6 <& (g-i)_o &< 1.7 \nonumber \\
				15 <& i_o &< 18 \\
		-15(g-i)_o + 27 <& g_o &< -3.75(g-i)_o \nonumber
	\end{eqnarray}

This selection region is illustrated in the colour magnitude diagram in Figure \ref{fig:cmd-target-selection}. Within this colour selection window, halo field dwarfs are expected to contaminate the sample due to their similarity in colours. Although K-dwarfs are difficult to distinguish photometrically, we can spectroscopically separate these through the absorption strength of the Mg 5180 \AA\, gravity-sensitive triplet (see \S\ref{sec:dwarf-giant-separation}).

	\section{Observations}
	\label{sec:observations}

	Our targets were observed in multiple runs using AAOmega on the 3.9-m Anglo-Australian Telescope (now the Australian Astronomical Telescope) at Siding Springs Observatory in New South Wales, Australia. AAOmega is a double-beam, multi-object fibre-fed spectrograph covering a two degree field of view. The targets were observed in normal visitor mode during two runs in April 2009. Throughout all observations, sufficient sky and guide fibres ($\sim 30$ and $7-8$ respectively) were allocated to ensure optimal sky subtraction and astrometry.

	The beam was split into the red and blue arms using the 5700 \AA\,dichroic. The 580V grating in the blue arm was used to provide giant/dwarf separation by measuring the absorption strength of the 5180 \AA\,Mg feature. The 580V grating yields spectra between 370-580 nm, with a resolution of $R = 1300 \AA$/px. In the red arm we used the slightly higher resolution (R$\sim$4400) 1000I grating which covers the spectral range between 800-950 nm. This coverage includes the Ca II infrared triplet, which is used for radial velocity measurements and metallicity estimations. To minimise scattered-light cross talk between fibres, the objects of each each configuration were limited to 1.5 magnitudes in range. Globular clusters NGC 5024, 5053 and 5904 were observed as radial velocity and metallicity standards, and no telluric standards were observed as telluric features do not affect the spectral features we are interested in.

	The data was reduced using the 2\textsc{DFDR} pipeline. After being flat-fielded the sky spectrum was subtracted using the median of the sky fibres and a carefully examined sky line list. The fibres were throughput calibrated, and wavelength calibration was achieved from arc lamp exposures between each set of science fields. Three thirty minute object exposures for each faint ($g > 16$) science field, and twenty-five minute exposures for bright ($g < 16$) field were taken to assist with cosmic ray removal.

	\section{Dwarf / Giant separation}
	\label{sec:dwarf-giant-separation}

	Photometric similarities in K-type giants and dwarfs will result in substantial contamination in our sample by dwarfs. In order to discriminate between these samples we have used the gravity-sensitive Mg feature at  5180 \AA. Our resolution is sufficient that this triplet is not blended and can be fitted with the sum of three Gaussian profiles. The Mg feature equivalent width is taken as the sum of the widths of each profile. One would expect a broader profile, in dwarf stars where the surface gravity is higher than that of giants. A blue spectra comparison between a giant and dwarf star is illustrated above in Figure \ref{fig:dwarf-giant-comparison}. The distinction in profile width is evident in Figure \ref{fig:dwarf-giant-separation}, which also demonstrates our separation line between giants and dwarfs. Contaminating dwarfs populate the dominant branch with a broader Mg profile, and K-giants populate the less-distinguishable lower branch. We identify 185 giants in this sample, and calculate the contamination of our input sample as 91\% dwarfs.

	\begin{figure*}[t!]
	\centering
	\includegraphics[width=18.4cm]{./figures/spectra.eps}
	\caption{Blue arm spectra for a K-type giant (top) and dwarf (bottom) star, highlighting the difference in the gravity-sensitive Mg 5180 \AA\, absorption profile.}
	\label{fig:dwarf-giant-comparison}
\end{figure*}

	%91 % is everything else. dwarfs is probably ~90% because some are identifiable carbon stars.

	\begin{figure}[h!]
		\centering
		\includegraphics[width=9.2cm]{./figures/dwarfgiant_copy.eps}
		\caption{Equivalent width of the Mg 5180 \AA\ feature shown against the $g\,-\,i$ colour. The thick line is used to separate our dwarfs from giants. Field dwarf contaminants are largely illustrated in the dominant upper branch, and giant stars populate the lower horizontal branch.}
		\label{fig:dwarf-giant-separation}
	\end{figure}

	\section{Radial Velocities}
	\label{sec:kinematics}

	We have used the Ca triplet absorption lines at 8498, 8542 and 8662 \AA\, to measure radial velocities. These lines are strong, easily identifiable  (Figure \ref{fig:spectra}a) in RGB stars even at low resolution, and their prominence allows us to determine accurate radial velocities even with low signal-to-noise data. Our data has been cross-correlated with typical synthetic spectra of a K-giant ($T_{eff} = 4500$ K, $\log{g} = 0$, [Fe/H] $= -1.5$), and heliocentric corrections were made. Radial velocity measurements made on the standard stars in our globular clusters match up well (within 3 km s$^{-1}$) with the catalogue of \citet{Harris_1996} (2010 edition). Many of our targets were observed on multiple fields, which allows us to calculate the internal measurement error. The differences between multiple measurements of the same target were tabulated, and as expected form a half-normal distribution (Figure \ref{fig:multiple-kinematics}). The FWHM of this curve is +7.16 km s$^{-1}$. Kinematically 'cold' structures are typically identifiable if their peak signature has a FWHM of $< 8 $km s$^{-1}$, thus our intrinsic measurement error is small enough to identify cold substructures.

	\begin{figure*}[t!]
		\centering
		\includegraphics[width=18.4cm]{./figures/vel_error.eps}
		\caption{Internal radial velocity errors between multiple measurements of the same star. This sample includes all targets (dwarfs and giants) that were observed more than once.}
		\label{fig:multiple-kinematics}
	\end{figure*}

	In order to compare our kinematic results in a homogenous manner, we have translated our observed line of sight velocity to a galactocentric frame. We have adopted the circular velocity of the Local Standard of Rest (LSR) at the Sun as 220 km s$^{-1}$ \citep{Kerr;Lynden-Bell_1986} and accounted for the Sun's peculiar velocity to the LSR by using 16.5 km s$^{-1}$ towards $l = 53^{\circ}, b= 25^{\circ}$ \citep{Mihalas;Binney_1981}. The corrected line of sight velocity is then given by,
	\begin{align}
		V_{GSR} =  \,&\,V_{OBS} + 220\sin{l}\cos{b} + 16.5  \\
		 			&\,\, \times[\sin{b}\sin{25} + \cos{b}\cos{25}\cos{(l - 53)}] \nonumber
	\end{align}

\noindent where $V_{OBS}$ is the heliocentric corrected observed line of sight velocity.

	A caveat to this reference transformation is that previous authors in the literature have used slightly different formulae to transpose their kinematics to a galactocentric rest frame. This will result in a systematic shift in all corrected velocities between two authors using varied equations, and the level of the shift is purely dependent on the Galactic location of the observations taken. Impacts from this variation are discussed later in the text.

\section{Metallicities}
	\label{sec:metallicities}
	We have further used the Ca II triplet (CaT) lines to obtain approximate metallicity abundances  for our giant stars. Through measuring the profile width (W') of the CaT absorption lines, we can ascertain a metallicity determination using their magnitude above the horizontal branch as a calibrator. This technique was originally empirically described for individual stars \citep{Armandroff;Da-Costa_1991}, and has been extended to globular cluster members \citep{Rutledge;Hesser;Stetson_1997}, RGB stars and dSph members \citep{Battaglia;et-al_2008}. A spectroscopic analysis using VLT/FLAMES observations of RGB stars from composite populations led\citet{Battaglia;et-al_2008} to conclude, that a calibrated CaT-[Fe/H] relationship can be confidently used in composite stellar populations. However, a systematic trend is present where metallicity is overestimated by $\sim0.1$ dex at low metallicities ([Fe/H] < -2.2) and underestimated by $\sim0.1-0.2$ dex at higher metallicities ([Fe/H] > -1.2). \citet{Battaglia;et-al_2008} indicate higher Ca abundances may affect the CaT W' sufficiently to cause this trend, although [Fe/H] is the certain dominant factor contributing to the CaT W'. Nevertheless the CaT-[Fe/H] relationship is strong for RGB stars in composite populations (as observed here) above the horizontal branch within the range $-2.5 < $[Fe/H]$ < -0.5$.

The calcium-metallicity association is linear. The sum of equivalent widths of the CaT lines is scaled to form a 'reduced EW' (W'), which is calibrated by the stars magnitude above the horizontal branch ($V - V_{HB}$). This technique is only applicable for stars brighter than the horizontal branch ($V - V_{HB} > 0$). There is some discussion in which combination of the three CaT lines should be used. In this work we have taken the total equivalent width as the sum of the two stronger Ca lines ($\lambda_{8542}$, $\lambda_{8662}$). The weakest Ca line is usually the most unreliable when calculating equivalent width due to limited S/N and the possibility of residual sky-line contamination. Moreover, following a comparison of scaling relations between CaT and [Fe/H], \citet{Battaglia;et-al_2008} found using only the two strongest lines (as \citet{Tolstoy;et-al_2001} had done) was the most robust. As such, we have adopted the best-fitting relationship found by \citet{Battaglia;et-al_2008} for this work. The reduced EW is calculable by

\begin{eqnarray}
	\textstyle\sum{W}\, &=& EW_{8542} + EW_{8662} \\
	W' &=&\textstyle\sum{W} + 0.64\left(\pm 0.02\right)\left(V-V_{HB}\right)
\end{eqnarray}

\noindent and the metallicity linearly varies with the reduced EW such that,

\begin{equation}
	\text{[Fe/H]}_{\text{CaT}} = (-2.81 \pm 0.16) + (0.44 \pm 0.04) W'
	\label{eq:feh-cat}
\end{equation}

Using this calibration, our globular cluster standard stars have metallicities that match well with the \citet{Harris_1996} catalogue (2010 edition). When applying this technique to our K-giants, the difficulty is that the magnitude of the horizontal branch ($V_{HB}$) is not easily distinguished. $V_{HB}$ varies between stellar systems, and is dependent on the heliocentric distance and morphology of the stellar environment. This is a composite population; some stars are members of the Sgr stellar stream, others are members of the VOD/VSS, all superimposed upon field stars. Ideally we would want to uniquely identify each star to a stellar system and ascertain the horizontal branch magnitude. We can identify substructures kinematically, but we cannot differentiate halo stars. However, in our observed region there are known, dominant structures. The Sagittarius stream dominates our negative $V_{GSR}$ population, and our positive kinematic space is largely comprised of members from the VOD. As such we have kinematically separated our population at $V_{GSR} = 0$ into two samples to ascertain $V_{HB}$ for the two most dominant populations; Sgr and the VOD. Although this technique introduces a (known) systemic effect, it is the most useful way to accurately deduce the metallicity distribution. Statistically the most dominant [Fe/H] bin in each sample will be evident, and field halo stars or members from different substructures, will only add noise to the distribution.

\# rr lyrae table for

The horizontal branch magnitude for the VSS has been ascertained from RR Lyrae observations by \citet{Prior;et-al_2009a}. Four of their RR Lyrae observations are proposed VSS members based on their galactocentric velocities, and the properties of these observations are listed in Table \ref{tab:prior-rrls}. The horizontal branch magnitude for all our K-giants with positive galactocentric velocities is taken as the median V-band magnitude of these four RR Lyraes, and calculated as $V_{HB} = 17.13$.

In order to determine the horizontal branch magnitude for the Sgr members a different technique has been used. The $V_{HB}$ of the dwarf progenitor is known, but it cannot be used for members along the stream, as the branch apparent magnitude is age- and distance-dependent. (\#citation needed) measured distances for

%	Classical calibrations between CaT-[Fe/H] have used the magnitude above the horizontal branch as the dependent variable (cite me). The magnitude of the horizontal branch varies between stellar systems, and is dependent on heliocentric distance and the morphology of the system \citep{Harris_1996}. To reduce systematic errors between measurements, the same calibration ought to be used on all stars within our sample. However the stars examined here presumably originate from multiple, complex stellar environments and one cannot expect their horizontal branch morphologies to be the same. As our structures are identifiable through their kinematics, we could use known distances to many of these substructures in order to derive a $V_{HB}$ for each system. Although our substructures are recognisable, there is significant overlap between features which makes the kinematic selection windows of features ambiguous to chose at best. In contrast the absolute magnitudes $M_I$ and $M_V$ introduce a much smaller systematic effect. Although \citet{Cole;et-al_2004} showed the effect of different ages of RGB stars is a negligible source of error for metallicities derived from the CaT calibration, \citet{Carrera;et-al_2007} shows it is advantageous to use $M_I$ (instead of $M_V$) for the calibration because it is much less sensitive to age effects. With these caveats in mind, we have decided to use the $M_I$-[Fe/H] calibration. As such, Equation \ref{eq:starkenburg-metallicity} becomes

% A caveat to the Ca II line strength-[Fe/H] relationship is that it is empirically defined and not entirely well understood.

% Globular cluster stars used for the calibration are typically drawn from a single population, however the stars examined here are drawn from multiple, sometimes unknown, origins. Moreover, differing [Ca/Fe] ratios between multiple globular clusters is expected to affect the strength of the Ca lines.

	%A comparison between multiple calibrations between groups yields close correlations between the techniques \citep{Battaglia;et-al_2008}.
%	Although the origins of the VOD and many of the nearby spatial substructures is unknown, many of the targets examined may have origins in the Sagittarius dSph galaxy. It is appropriate to use calibrations made on RGB stars, and as such the technique described within \citet{Starkenburg;et-al_2010} is implemented here. Using their relationship, the equivalent width sum  to determine an abundance for either [Fe/H] or [Ca/H]. Calibrations have been provided between three different absolute magnitudes; $\left(V-V_{HB}\right)$, $M_V$ or $M_{I}$ (Johnson-Cousins). Coefficients for the functional form of the equation (Eq. \ref{eq:starkenburg-metallicity}) depend on the absolute magnitude-abundance calibration used. The term $V_{HB}$ specifies the $V$ magnitude of the horizontal branch, and as these calibrations are only valid for RGB stars, \citet{Starkenburg;et-al_2010} stresses they should not be applied to stars outside $-3 < \left(V-V_{HB}\right) < 0$, $-3 < M_V < 0.8$, or $-4 < M_I < 0$.

%	\begin{eqnarray}
%		\label{eq:starkenburg-metallicity}
%		\text{[Fe/H]} &=& a + b \times M_X + c \times EW_{(2+3)} \\
%				      &\,   &\,\,\,\,\,     + d \times EW_{(2+3)}^{-1.5} + e \times EW_{(2+3)} \times M_X \nonumber
%	\end{eqnarray}

	\section{Discussion}
	\label{sec:discussion}

	Along our line of sight, the spatial region examined in this paper incorporates the superposition of multiple substructures, some which may be inter-related. To facilitate a logical flow of discussion, these substructures ought to be separated and identified first.

		\subsection{Substructure Identification}
		\label{sec:substructure-identification}

		When discussing our data with respect to stellar streams and substructures within the halo from here, we are referring only to K-type giants.  Dwarfs are too faint to be found at a sufficiently large distance where we are exploring substructures. Given a randomly selected distribution of stars, we ought to expect their galactocentric velocities to be representative of the halo if the sample is sufficiently large. A significant kinematic deviation from a canonical halo population is the classic signature of a co-moving group. In order to quantitatively compare the kinematics of stars in our sample to a halo distribution, we have represented our galactocentric velocities with a generalised histogram (Figure \ref{fig:velocity-histogram}). The generalised histogram represents each data point with a Gaussian kernel of an equal bandwidth (deviation). The selection of bandwidth is important and can over- or under-smooth data and misrepresent results if chosen incorrectly.

		In order to gain an approximation for the bandwidth selection we have looked at stars in our dataset with repeated observations. Since we are investigating the systematic accuracy of our velocity measurements, and not focussed on substructure identification, we can include K-type dwarfs in our multiple measurement sample in order to gain a more accurate representation of the systemic measurement error. A histogram showing the number of repeated observations, as well as the errors in repeat velocity measurements between stars is shown in Figure \ref{fig:multiple-kinematics}. The kinematic errors between multiple measurements summate to a half-normal distribution with a FWHM of 7.16 km s$^{-1}$. This represents the minimum bandwidth we can feasibly use to represent our data. We have opted for a bandwidth value of 10 km s$^{-1}$ for the generalised histogram in Figure \ref{fig:velocity-histogram}.

\begin{figure}[h]
	\centering
	\includegraphics[width=9.2cm]{./figures/besancon_copy.eps}
	\caption{Generalised histogram of $V_{GSR}$ for the sample K-type giants, highlighting their significance against the predicted observations by the  Besan\c{c}on model for this spatial region.}
	\label{fig:velocity-histogram}
\end{figure}

	As evident in Figure \ref{fig:velocity-histogram}, there are significant ($> 3\sigma$) tight kinematic signature peaks. As previously noted, the fields observed here have numerous identified overlapping substructures, and potentially many more which have not been disentangled. The most dominant of these features (Feature A) is that within the bin of $-200 < V_{GSR} < -10$, where we would expect some halo contaminants, especially at the more positive velocity end of the bin. This wide spread in kinematics has a bulk overall dominant signature well in excess of the halo. We attribute this wide, yet significant kinematic peak to a single membership; the leading arm of the Sagittarius tidal tail.

	One could argue that the generalised histogram presented in Figure \ref{fig:velocity-histogram} is over-smoothed, and perhaps three independent kinematic signatures are present within this bin. This is indeed possible, however using the minimum bandwidth possible (6.76 km s$^{-1}$) without over-interpreting the data, the shape of the peaks remains consistently narrow, although no firm conclusions can be drawn about possible sub-populations. It is also possible that these peaks are artefacts of the sampled population, and would not appear in the same positions given a different (or larger) sample size. Representing the data as a generalised histogram with an appropriate bandwidth is a methodical way to eliminate such projected artefacts, and they ought not to be statistically significant in Figure \ref{fig:velocity-histogram}. Alternatively we present evidence (see \S\ref{sec:sgr-peak-analysis}) suggesting these features are indeed real, and not consequences of the sampled distribution. Albeit they have a wide kinematic distribution, may still be members of a single population.

	Feature B is our next most evident substructure at $V_{GSR} = +130$ km s$^{-1}$, which we attribute to the Virgo Stellar Stream, as other authors have \citep{Newberg;et-al_2007, Prior;et-al_2009a}. These members in our 130 km s$^{-1}$ bin ($120 < V_{GSR} < 140$ km s$^{-1}$) are coincident in spatial position, velocity, and metallicity (see \S\ref{sec:the-vss}) with previously reported values of the VSS obtained by F turnoff and BHB stars \citep{Newberg;et-al_2007} and RR Lyrae stars \citep{Prior;et-al_2009a}.

	\subsection{Feature A \--- Sagittarius Debris}

	The tidal debris of Sagittarius wraps around the entire Galaxy, and these tails have been extensively traced \citep{Belokurov;et-al_2006,Newberg;et-al_2007,Yanny;et-al_2009}. It is useful to see how the bounds of our observed fields spatially overlap with the Sagittarius stream (and other substructures), so we can provide a useful analysis. Figure \ref{fig:sgr-field-of-streams} shows the bounds of our observed region overlayed upon a panoramic projection of the Sagittarius stream and the 'Field of Streams' from \citet{Belokurov;et-al_2006}. This is a crowded region of globular clusters, substructures and overlapping stellar streams, primarily populated by the Sagittarius Northern arm. The bifurcation in Sagittarius \citep{Belokurov;et-al_2006} is evident here, and our observed fields overlap with the the more southern Branch A.

	\begin{figure*}[t]
		\centering
		\includegraphics[width=18.4cm]{./figures/belokurov2006.eps}
		\caption{Spatial bounds of our observed fields outlined upon a panoramic view of the Sgr stream, using the 2MASS M giants of \citet{Majewski;et-al_2003} with SDSS stars. This plot is an adaptation of Figure 2 in \citet{Belokurov;et-al_2006}.}
		\label{fig:sgr-field-of-streams}
	\end{figure*}

	Simply from a spatial perspective, we expect Sagittarius debris to dominate our data. \textit{N}-body models of the Sagittarius stream suggest highly negative velocities in this region \citep{Law;et-al_2005,Law;Majewski_2010}, which has led several authors \citep{Yanny;et-al_2009, Prior;et-al_2009b}, who have observed co-moving groups with highly negative kinematic signatures in nearby fields, to attribute these as members of Sagittarius.  Our generalised histogram in Figure \ref{fig:velocity-histogram} demonstrates a bulk kinematic signature, well in excess of the halo. Smaller kinematic signatures are difficult to distinguish, and determining their membership can be arduous. The extent of the kinematic signature here can only result from a dominant population, such as Sagittarius.

	\subsection{Sagittarius Debris: Comparison to Models}

	The consequential tidal tails from the Sgr-Milky Way interaction has been modelled by many groups \citep[e.g. ][]{Helmi_2004, Law;et-al_2005, Law;Majewski_2010}. In order to further investigate the spatial coverage and kinematics from our sample of stars attributed to Sagittarius, we have compared our sample of K-giants with the constant flattening spheroidal models of LJM05 and the more recent tri-axial model of LM10. The simulated data output from these is readily available online\footnote{http://www.astro.virginia.edu/$\sim$srm4n/Sgr/}, and their released models have the best-fitting parameters for each model classification (prolate, spherical, oblate and tri-axial). Simulations are matched to the 2MASS M-giant sample, which provides an all-sky view of the Sgr stream. These are the only simulations available which make use of an all-sky data set, and comparisons between each model will be more consistent than comparing models between different authors.

		\citet{Law;et-al_2005} describe the Milky Way as a smooth, rigid potential and represent Sgr with $10^5$ self-gravitating particles. The Galactic potential is represented with three primary components; a \citet{Miyamoto;Nagai_1975} disk, a Hernquist spheroid and a logarithmic halo. The models of LJM05 have a constant degree of flattening, $q$, whereas the more recent LM10 tri-axial model has a minor/major axis ratio $(c/a)_\Phi = 0.72$ and an intermediate axis ratio $(b/a)_\Phi = 0.99$ at radii $20 < r < 60 $kpc. In models with constant flattening, three classification types were considered and the value $q$ was chosen from the best-fitting simulation type; prolate (constrained $q > 1; q = 1.25$ set), spherical ($q = 1.0$ set), and oblate (constrained $q < 1; q = 0.80$ set). Their models integrate over 3 Gyrs (around four orbits) and predict heliocentric distances and galactocentric velocities, and adopt a heliocentric Sgr coordinate system with longitude $\Lambda_\odot$ and latitude $B_\odot$, as defined by \citet{Majewski;et-al_2003}. The Sgr core is centered at $\Lambda_\odot = 0^\circ$, and latitude plane is defined by the best-fitting great circle of the Sgr debris. For comprehensive details of the simulations the reader is referred to the papers of \citet{Law;et-al_2005, Law;Majewski_2010}. To illustrate the spatial distribution simulated by the Sgr tidal tails, Figure \ref{fig:law-spatial} shows the simulated particles from the LJM05 and LM10 models, and our observed fields are outlined in black.

		\begin{figure}[h]
			\centering
			\includegraphics[width=9.2cm]{./figures/law_spatial_copy.eps} 
			\caption{The bounds of our observed area is outlined in black against the simulated particles from multiple \textit{N}-body simulations by LJM05, LM10. The particles are colour-coded by their peri-centric passage following the same convention by \citet{Law;Majewski_2010} (magenta; previous passage, cyan; oldest observable passage). \\ A colour version of this plot available in the online journal.}
			\label{fig:law-spatial}
		\end{figure}

	The Northern leading arm of Sgr is particularly sensitive to both kinematic and spatial changes in the shape of the Milky Way dark halo. To evaluate how well models predict the position and kinematics of the Sgr debris, we require either a large set of accurate stellar kinematics and distances, or targeted regions of the stream where a change in the shape of the dark halo results in significantly different simulated positions and kinematics. The latter is particularly the case for our fields when compared to the spatial positions predicted by the prolate model (Figure \ref{fig:law-spatial}).  All other models predict the Sgr stream to pass directly through our fields, however the prolate model predicts no particles directly in our fields, and when we extend a rectangle bounded by the edges of our fields only two particles are found. Spatially the prolate model predicts the Sgr stream to pass more southward (in $B_\odot$) than our observed fields. If this prolate halo model is a true representation of the Sgr debris, this does not exclude the potential of finding some Sgr debris in our fields. However it strongly suggests that if the dark halo is indeed prolate, and the LJM05 prolate model is a good representation of the halo, Sgr would not be the dominant observed population as we see in our fields.

	In comparison, the tri-axial, spherical and oblate models predict varying amounts of particles from previous peri-centric passages to pass through our observable region. To adequately evaluate the model predictions of Sgr debris, a kinematic comparison between the predicted and observed values is necessary. As the prolate model has only two simulated particles within our observable bounds there is no qualitative kinematic comparison to be made for this model.

	The number of predicted particles in our observed region is different for each model, and as the amount will not necessarily reflect the size of our observed sample. Consequently the kinematics for each model have been represented as a generalised histogram (Figure \ref{fig:law-vel-compare}). For consistency all simulation output and observed data has been convolved with a Gaussian kernel of 10 km s$^{-1}$; the bandwidth used for the generalised histograms with observed data. A generalised histogram is an effective method to evaluate the model predictions, because the size the overall distribution is scaled such that the integral of each distribution is unity. Therefore populations of different sizes (i.e. our observed sample and the varying size of each simulation output) are scaled appropriately so we can evaluate the kinematic signatures. One caveat of this technique is that the relative size of each sample must be acknowledged when evaluating the predictions made by a model. A narrow distribution \--- which may perfectly match the observed data \--- may simply be a consequence of an extremely small sample size, yielding an ineffective comparison. Indeed if we included a comparison with the prolate model the entire distribution may appear to represent the observed data closely in a qualitative sense, however that distribution would be composed from a mere two simulated particles.

\begin{figure*}[t!]
	\centering
	\includegraphics[width=18.4cm]{./figures/lawvelcompare-bw.eps}
	\caption{A generalised histogram (left) of the galactocentric rest frame velocities in our sample (dotted line) compared to the velocities from the \textit{N}-body models of LJM 05, LM 10 of particles within the same spatial coverage and age of our observed sample (solid lines). The model particles used to generate each velocity histogram are shown on the right in velocity-heliocentric distance space, and they are labelled by their recency of passage. A plus ($+$) denotes debris from the current peri-centric passage by Sgr, circles ($\circ$) mark the previous passage, and squares ($\square$) represent debris from two previous passages.}
	\label{fig:law-vel-compare}
\end{figure*}

	With this caveat in mind we have also shown the simulated particles predicted within our observable bounds on a kinematic-distance scale in Figure \ref{fig:law-vel-compare}. Clearly, in this small region there is debris from multiple passages predicted along the line of sight, and as such particles have been marked by their recency of peri-centric passage. Distinguishing particles by their peri-centric age allows us to qualitatively differentiate relative kinematic contributions of the stream by their recency of passage.  In all three models, the Northern arm is clearly distinguishable, albeit the tri-axial model has a much tighter sequence in velocities. This is attributed to the position of the predicted pericenter. The tri-axial model predicts a pericenter almost precisely where our fields were observed, whereas the spherical and oblate model predict a large wrap of the stream along the line of sight, resulting in a large spread in kinematics and heliocentric distances.

	In our observed fields, the spherical and oblate models predict close-by debris with extremely highly negative galactocentric velocities. This signature is not representated in our data. The lowest observed velocity is $\sim -250$ km s$^{-1}$ and we have only two observations less than $V_{GSR} < -200$ km s$^{-1}$. In contrast, in these two simulations the bulk predicted kinematic signature extends well below $V_{GSR} < -300$ km s$^{-1}$. If the dark matter potential is well-represented by either of these LJM05 simulations then this discrepancy must be reconciled.

	K-giants have a large range in absolute magnitudes, nevertheless nearby stars will appear brighter and may be brighter than the magnitude range of our observed targets. A colour-magnitude diagram for the Besan\c{c}on model data in this area is shown in Figure \ref{fig:besancon-cmd}a, which highlights the giant branch and includes an outline of our target selection criteria. The predicted distances to each of these stars along the giant branch is represented in Figure \ref{fig:besancon-cmd}b, which shows a predicted observable distance range for K-giants between X to Y kpc - as we would expect. Using this distance cut to exclude unobservable stars, we would lose some of our simulated particles in the most negative velocity region for each model in Figure \ref{fig:law-vel-compare}. However this constraint is insufficient to adequately explain the substantial velocity discrepancy between our observed data, and the LJM05 spherical/oblate models.

\begin{figure}[h!]
	\centering
	\includegraphics[width=9.2cm,height=7cm]{./figures/besancon-cmd_copy.eps}
	\caption{Colour-magnitude diagram using $M_V$ against $B-V$ from the Besan\c{c}on model in this area (left), illustrating the giant branch. The distances to those giant-branch stars are shown in the histogram on the right, representing the range of potential K-giant observable distances. }
	\label{fig:besancon-cmd}
\end{figure}

	These two models also illustrate a similarity signature at $\sim$12 kpc, with simulated particle velocities ranging between $-100 < V_{GSR} < 0$ km s$^{-1}$. This is the edge of a simulated crossing-point between different wraps of the stream, which occurs at $\sim12$ kpc and yields a wide range of kinematics focussed at a common distance. These particles (and the positive kinematic signature around $\sim$20 kpc in the oblate model), are relatively minor signatures when compared to the overall bulk signature of the Northern arm. If these signatures are present in our observed fields, their banality would prevent them from appearing as significant relative to either a normal halo population, or a halo population in addition to expected substructure material (e.g. the VSS, 12\fh4 clump, S297+63-20.5). As such we cannot use the edge particles of these nearby simulated wraps to discern substantial information regarding the dark halo of the Milky Way.

	In this region, the kinematic predictions of the tri-axial dark halo model best fit our observed data. However, the tri-axial model kinematics favour our data set, the predicted kinematic distribution from a tri-axial halo is much narrower than our observed sample. Our broad observed sample is unlikely to be a consequence from considerable halo members. The profile broadening in our sample extends most prominently at highly negative galactocentric velocities ($\sim -200$ km s$^{-1}$). Given any Gaussian-like population with a mean near zero, we would expect less halo members at high galactocentric velocities \--- positive or negative. One reconciliation for this profile discrepency may lie in the workings of the tri-axial model itself. Unlike the other models compared here from LJM 05, the tri-axial model does not reproduce the bifurcation observed in the Sgr stream \citep{Belokurov;et-al_2006} as recent studies prior to the model development suggested this may be an outcome from the internal dynamics within the progenitor, and not primarily resultant from the shape of the Milky Way dark halo\citep{Fellhauer;et-al_2006}. However, \citet{Penarrubia;et-al_2010} recently found no evidence for internal rotation in the remnant core of the Sgr dwarf sufficient enough to produce a bifurcation.

	The lack of bifurcation treatment in this model may explain the particularly narrow distribution predicted in this region. Other groups have observed the spatial disruption caused by the bifurcation, however whether a kinematic variation exists between branches is unclear. Given the kinematic interactions within the progenitor, and the gravitational influence of the halo, it is reasonable to suggest a kinematic disruption may consequent from the bifurcation. A comparative targeted study along each branch would be necessary to discern a kinematic disruption. The region observed here is on the southern edge of Branch A. Despite that, some overlap between the two branches is plausible, and we postulate that such a kinematic variation may explain the discrepancy between the predicted narrow distribution which peaks in concert with our data, and the broader observed profile.

%The astute reader will notice in Figure \ref{fig:law-vel-compare} that the tri-axial model also predicts two wraps from different peri-centric passages in this region. The two are predicted to be close in distance, and if present they would be spatially indistinguishable in our fields. However there is a known metallicity gradient along the Sgr field \citep{cite-me}, and multiple metallicity sub-populations which vary in density along the wraps. One might expect then that if the tri-axial model by LM 10 is a good representation of the Sgr streams in this region, that we might see a bi-modal metallicity distribution in the Sgr-attributed members. Exploring this idea, Figure \ref{fig:sgr-metallicity-hist} demonstrates the metallicity distribution for all K-giant members with negative galactocentric velocities. Although this sample will contain halo members and contaminants, the dominant population is Sagittarius. No bi-modal distribution is observed, however this does not exclude the possibility; our metallicity accuracy ($\pm 0.3$ dex) would not be sufficient to discern stars from an immediately previous wrap ($\pm $N dex; cite-me). Moreover, members of the previous wrap would be sparsely populated in comparison to its younger counterpart.

\subsection{Sagittarius Debris: A Metal-Poor Population Uncovered?}
\label{sec:sgr-metal-poor}

\# To do.	
	\begin{figure}[h!]
		\centering
		\includegraphics[width=9.2cm]{./figures/fehhist_copy.eps}
		\caption{Metallicity determinations for K-giants with negative galactocentric velocities; which are largely attributed to the Sagittarius Northern arm.}
		\label{fig:sgr-metallicity-hist}
	\end{figure}

\subsection{Sagittarius debris: Are the features at $-49$ and $-76$ km s$^{-1}$ related?}
\label{sec:sgr-peak-analysis}

	Our most dominant kinematic groups peaks at $V_{GSR} = - 49$ and $-76$ km s$^{-1}$. Intuitively one may wonder whether these two objects are observations of unique structures or a systemic artefact of a single structure. \citet{Vivas;et-al_2008} noted that the most populated group in their sample of BHB and RR Lyrae stars occurred within the bounds $-80 < V_{GSR} < -10$ km s$^{-1}$, and had a mean velocity of $V_{GSR} = -49$ km s$^{-1}$ with a standard deviation of 22 km s$^{-1}$. This sample comprised of nine RR Lyrae stars and five BHB stars. Metallicity measurements of the variables within the group yielded a mean metallicity of $\langle$[Fe/H]$\rangle$ = -1.72 dex with a standard deviation of 0.28 dex. In this region of high negative velocity\citet{Vivas;et-al_2008} expect relatively high contamination from unrelated halo stars and suggest this may skew their kinematics. However they state this does not account for the diffuse metallicity distribution. The spread is likely representative of the true population, and not caused by the contamination of non-members into an otherwise narrow distribution.

\# As a comparison, our K-giants in the same galactocentric velocity range demonstrate a metallicity of X and a standard deviation of Y dex. \\
\# Is ours higher or lower? \\
\# Is there some selection metallicity effect when comparing K-giant derived metallicities to RR Lyraes? \\
\# ie would you expect RR Lyraes to be more metal poor because they are an older generation, etc \\

	The peak velocity signature at $V_{GSR} = -76$ km s$^{-1}$ has also been noted by others. \citet{Duffau;et-al_2006} observed BHB stars in this region and illustrated a slight peak in the bin $-80 \lesssim V_{GSR} \lesssim -50$ km s$^{-1}$. \citet{Newberg;et-al_2007} found a significant peak in the velocities of F-type stars at $-76$ km s$^{-1}$, which \citet{Vivas;et-al_2008} notes may be members of the $-49$ km s$^{-1}$ structure, given the errors. The RR Lyraes in the \citet{Vivas;et-al_2008} sample at $V_{GSR} = -49$ km s$^{-1}$ have a distance of $7.5 < D < 9.5$ kpc and using a conservatively faint absolute magnitude $M_g = +4.2$ for the \citet{Newberg;et-al_2007} sample, \citet{Vivas;et-al_2008} estimate the distance to the F-type stars would be around $11 \lesssim D \lesssim 14$ kpc. If these two features are related then their distance and kinematic discrepancies must be reconciled, and their spatial coverage is worthy of interrogation.

	\begin{figure}[h!]
		\centering
		\includegraphics[width=9.2cm,height=7cm]{./figures/blank.eps}
		\caption{The sky coverage examined in this data set which contains K-giants within our velocity bin ranges $-59 < V_{GSR} < -39 $km s$^{-1}$ (green squares) and $-86 < V_{GSR} < -66 $km s$^{-1}$ (blue circles), and the spatial coverage examined by other authors \citep{Duffau;et-al_2006, Newberg;et-al_2007} who separately noted the same peaks; illustrating the spatial overlap.}
		\label{fig:newberg-duffau-vivas-spatial}
	\end{figure}

	\citet{Newberg;et-al_2007} notes that their $-76$ km s$^{-1}$ feature is more pronounced in the fainter $(l, b) = (300^\circ, 55^\circ)$ field, although upon recognising the feature they note it is also seen in their more northerly plate at $(288^\circ, 62^\circ)$. The more spatially prominent region covered by \citet{Newberg;et-al_2007} was not observed by \citet{Vivas;et-al_2008}, so the spatial overlap between these authors could not be fully investigated. The spatial region covered by \citet{Duffau;et-al_2006} (which included the $-49$ and $-76$ km s$^{-1}$ features) ranged from (R.A., Dec.) $\approx$ (175 to 200$^\circ$, -2 to 0$^\circ$), which overlaps with this work and the fields by \citet{Newberg;et-al_2007} (Figure \ref{fig:newberg-duffau-vivas-spatial}). Our $-76$ km s$^{-1}$ group is most spatially concentrated within (R.A., Dec.) = (189 to 195$^\circ$, $-3.5$ to $-1.5^\circ$), which overlaps with the region where \citet{Duffau;et-al_2006} observed a similar peak and extremely close to the centroid where \citet{Newberg;et-al_2007} found their $-76$ km s$^{-1}$ peak of F-type stars.

		Although we uncover more stars from the $-49$ km s$^{-1}$ peak in this spatial region we also expect a higher contamination of halo stars in this sample. With that caveat in mind we can see the sample extending towards (R.A., Dec.) = ($180^\circ$, $0.5^\circ$), although there are only N stars here. Similarly we might expect that perhaps one of in the $-76$ km s$^{-1}$ group that are separated from the clump is a contaminant, or that the group is simply not as diffuse as the $-49$ km s$^{-1}$. A larger sample is favourable as it is problematic to distinguish or otherwise assign common membership to these moving groups based on their spatial coverage. However due to repeated measurements by multiple authors and given their kinematic dispersions, X km s$^{-1}$ for the $-49$ km s$^{-1}$ group and Y km s$^{-1}$ for the $-76$ km s$^{-1}$ group, this suggests these may be separate kinematic structures superimposed on one another. Further investigation in this region to explore this idea would be interesting.

	\subsection{Feature B \--- The Virgo Stellar Stream}
	\label{sec:the-vss}

	As previously mentioned, our observable region falls within the 'Field of Streams' where multiple stellar substructures and co-moving groups have been noted by several groups. The largest, most diffuse structure in this region is the VOD, stretching up to $\sim$1000 deg$^2$ across the sky \citep{Juric;et-al_2008}. One such smaller substructure which was distinguished from the general over-density of the VOD is the Virgo Stellar Stream \citep{Duffau;et-al_2006}. Several RR Lyrae stars were noted by \citet{Prior;et-al_2009a} with a common velocity of $V_{GSR} = 130$ km s$^{-1}$. This kinematic signature has been repeatedly observed in this region by other groups \citep{Newberg;et-al_2007, Prior;et-al_2009a}, and \citet{Prior;et-al_2009a} used measurements of RR Lyrae stars with the same kinematic signature to obtain a metallicity of [Fe/H] = -1.95 for the VSS.

	% Discuss the VGSR = 100 discrepancy? %

	We cannot unequivocally state whether members of the VSS are present in our K-giant sample \textit{only} from looking at kinematic signatures alone. In Figure \ref{fig:velocity-histogram} there is a slight peak at $V_{GSR} = +130$ km s$^{-1}$, however this peak is not statistically significant. It is impossible to discern which, if any, members within the bin $120 < V_{GSR} < 140$ km s$^{-1}$ are potential VSS candidates. Kinematics of members in the bin are perfectly representative of randomly selected stars within the halo. The discrimination between halo and potential VSS candidates becomes more discernible when we explore metallicity measurements. Figure \ref{fig:velocity-metallicity} shows the velocities and metallicities for all of our K-giant candidates. % Discuss the sharp jump at VGSR = 0 and what implications that has. %

	\begin{figure}
		\centering
		\includegraphics[width=9.2cm]{./figures/vss-candidates_copy.eps}
		\caption{Galactocentric velocities and metallicity measurements for K-giants in our sample. Highly likely VSS K-giant candidates are identified.}
		\label{fig:velocity-metallicity}
	\end{figure}

	The most likely VSS K-giant members are visibly separated from the bulk sample in velocity-metallicity space. Of the four candidates highlighted, three are highly probable VSS members, and another giant could be a member of VSS \--- given the error in metallicity. Galactocentric velocities of these candidates ranges from $V_{GSR} = 127$ to $132$ km s$^{-1}$; which matches the kinematic signature seen by others studying the VSS. Furthermore the metallicities of our most probable candidates range from [Fe/H] = -1.89 to -2.03, identical to metallicity measurements of the VSS found by \citet{Prior;et-al_2009a} using RR Lyraes. Although RR Lyraes are typically representative of an older, more metal-poor population, it is interesting that these candidates match the VSS characteristics in spatial position, velocity, and metallicity.

	High resolution follow-up spectroscopy on these targets will provide crucial information about the origin of the VSS. K-Giants are the perfect candidate for high resolution spectroscopy, as they are cool enough to provide detailed elemental abundances, from which the formation history of the parent origin can be inferred. Investigating [$\alpha$/Fe] ratios in these candidates can discern whether the origin of the VSS was a dSph \citep{Venn;et-al_2004, Casetti-Dinescu;et-al_2009}. Furthermore, high resolution spectroscopy will also help untangle (or perhaps strengthen) the relationship between the VSS and the VOD. Future observations are planned.

	\subsection{Carbon Stars}

		In our sample we have identified five carbon stars as contaminants. With the colour selections made to target K-giants, this region also overlaps with where we would expect to find carbon stars. Although these stars were not specifically targeted, their surface densities are so low \citep[$\approx$ 1 per 50 deg$^2$;][]{Green;et-al_1994} and our sky coverage is small ($\sim$ 8 deg$^2$), such that we would not expect them to be a large contaminant. All five carbon stars in are data are recognisable by the presence of distinctive 4737- and 5165 \AA\, Swan C$_2$ bands.

	\begin{figure}[h]
		\centering
		\includegraphics[width=9.1cm]{./figures/carbon.eps}
		\caption{J-H and H-K colours for carbon stars recovered by \citet{Totten;et-al_2000}, and those found in this sample. Four of our five carbon stars are represented with plus symbols (+); \textit{JHK} photometry for our faintest carbon star was not available. \\ This plot is an adaptation of Figure 3 in \citet{Totten;et-al_2000}}
		\label{fig:carbon-colours}
	\end{figure}

	There are at least three kinds of carbon stars present in the halo; (i) N-type carbon stars, (ii) giant CH-type carbon stars and (iii) and dwarf CH-type carbon stars \citep{Totten;Irwin_1998}. N-type carbon stars are formed by carbon-enriched dredge-up during the post-main-sequence phase of a normal asymptotic giant branch (AGB) star. First generation carbon stars (CH-type) are not considered to have undergone carbon-enriched dredge-up, and their carbon abundance is attributable to mass transfer within a binary system. Dwarf carbon stars emit a spectral signature which mimics that of a typical CH-type giant carbon star, however they have anomalous JHK colours \citep{Green;et-al_1992} and unusually high proper motions. These dwarf carbon stars are believed to form in binary systems where material has accreted from a now-invisible companion during its ascent up to the AGB \citep{Dahn;et-al_1977}.

	Giant CH-type carbon stars are similar to metal-poor carbon stars found in globular clusters \citep{Harding_1962} and in some dSph galaxies (\#citation needed) . The existence of the 4300 \AA\,CH g-band is representative of a CH-type carbon star, and is found in all five of our carbon stars. SDSS photometry for our stars match well with the F/G-type CH carbon stars identified by \citet{Downes;et-al_2004}.The JHK colours of our entire carbon sample are characteristic of the F/G-type CH carbon stars found by \citet{Totten;Irwin_1998} in their cool carbon star survey (Figure \ref{fig:carbon-colours}). None of our stars exhibit significant proper motion, which strongly suggests they are not dwarfs \citep{Green;et-al_1994, Deutsch_1994}.

\begin{figure}[h]
	\includegraphics[width=9.2cm]{./figures/carbonstarcolor.eps}
	\caption{Sloan \textit{u \-- g} and \textit{g \--- r} colours for our carbon stars, and the identified carbon star populations from SDSS.}
	\label{fig:carbon-sdss}
\end{figure}

	\begin{table*}[t]
	\centering
	{\hfill{}
		\begin{tabular}{c c c c c c c c c c}
		\toprule
		\multirow{2}{*}{SDSS Name J+\tablenotemark{a}}	&\multirow{2}{*}{\textit{u-g}}	& \multirow{2}{*}{\textit{g-r}}	& \multirow{2}{*}{\textit{r-i}} & \multirow{2}{*}{\textit{i-z}} & \multirow{2}{*}{\textit{J-H}} & \multirow{2}{*}{\textit{H-K}} & $\mu$ & $V_{GSR}$		& [Fe/H]	\\
									&		 	&		  	&			&			&			& &	(mas yr$^{-1}$)       	&(km s$^{-1}$)		& (dex)	\\ 
		\toprule
		121740.94-001839.5				& 1.10		& 0.54		& 0.16 		& 0.05		& ...\tablenotemark{b}& ...\tablenotemark{b}	& $15.0 \pm 4.2$ & $\:-59 \pm 33\;$	& $-1.78 \pm 0.16$ \\
		121853.18-004628.4				& 1.67		& 0.73 		& 0.22		& 0.11		& 0.36		& 0.24		& $\:\:3.2 \pm 4.2$ & $\:-31 \pm 8.5$	& $-0.87 \pm 0.16$ \\
		122053.71-011709.5  				& 1.79		& 0.80		& 0.26		& 0.13		& 0.56		& 0.16		& $\:\:2.8 \pm 4.2$ & $\:+25 \pm 3.9$	& $-1.23 \pm 0.16$ \\
		125410.80-032744.0				& 1.43		& 0.64		& 0.22		& 0.05		& 0.32		& 0.56		& $18.8 \pm 4.2$ & $\:+40 \pm 9.9$	& $-1.24 \pm 0.16$ \\	
		125416.52-031437.6				& 1.72		& 0.73		& 0.25		& 0.11		& 0.50		& -0.11\:	 	& $15.5 \pm 4.2$ & $+182 \pm 8.2\;$	& $-1.60 \pm 0.16$ \\

		\bottomrule
		\end{tabular}

	}
	\hfill{}
	\caption{Object names and measurements for the five F/G-type CH carbon stars found within our sample.}
	\label{tb:carbon-stars}
	%\tablenotetext{a}{In keeping with convention, positional information has been truncated. Full information is available through the SDSS archive.}
	%\tablenotetext{b}{No \textit{JHK} photometry is available for this object as it is fainter than the 2MASS limit.}

	\end{table*}

	As these stars were selected from the SDSS catalogue, \textit{ugriz} photometry is available. However they were not spectroscopically observed in the follow-up SEGUE survey. Through comparisons with previous carbon-type star catalogues \citep{Totten;Irwin_1998, Downes;et-al_2004, Goswami;et-al_2010}, the stars tabulated in Table \ref{tb:carbon-stars} are previously unclassified. This is largely because our stars are too faint to have been classified by previous carbon surveys. The kinematics of our carbon stars are representative of a typical halo population.

	\section{Conclusions}
	\label{sec:conclusions}

	Lorem ipsum dolor sit amet, consectetur adipiscing elit. Vestibulum malesuada placerat tellus et hendrerit. Praesent eu velit vel velit suscipit scelerisque. Vestibulum pellentesque suscipit felis. Proin et ligula euismod lectus convallis ornare vitae ut diam. Aliquam scelerisque vehicula porta. Integer vulputate vulputate tempor. Mauris tincidunt nunc ac magna tincidunt dapibus. Nam auctor suscipit sapien, sed vestibulum enim lacinia vel. Fusce ullamcorper volutpat vehicula. Phasellus ornare rutrum facilisis. In tristique scelerisque nisl vitae ornare. Etiam varius consectetur sapien, sed lobortis mauris interdum ac. Integer leo urna, sodales in venenatis eu, ultrices ut nunc. Donec vestibulum dui et sem ultricies vel posuere ligula iaculis. Etiam gravida gravida augue non congue. Quisque lorem eros, faucibus non lacinia sit amet, imperdiet id metus.

	Lorem ipsum dolor sit amet, cosectetur adipiscing elit. Vestibulum malesuada placerat tellus et hendrerit. Praesent eu velit vel velit suscipit scelerisque. Vestibulum pellentesque suscipit felis. Proin et ligula euismod lectus convallis ornare vitae ut diam. Aliquam scelerisque vehicula porta. Integer vulputate vulputate tempor. Mauris tincidunt nunc ac magna tincidunt dapibus. Nam auctor suscipit sapien, sed vestibulum enim lacinia vel. Fusce ullamcorper volutpat vehicula. Phasellus ornare rutrum facilisis. In tristique scelerisque nisl vitae ornare. Etiam varius consectetur sapien, sed lobortis mauris interdum ac. Integer leo urna, sodales in venenatis eu, ultrices ut nunc. Donec vestibulum dui et sem ultricies vel posuere ligula iaculis. Etiam gravida gravida augue non congue.

\bibliographystyle{hapj}
\bibliography{draft}

\end{document}

### 2012-05-28 2012-scope/scope-draft.tex
Initial commit.

%!TEX TS-program = pdflatex
\documentclass{emulateapj}

\shorttitle{The SCOPE package}
\shortauthors{Casey}

\begin{document}

\title{The SCOPE package for automatic analysis of spectroscopic observations}

\author{Andrew R. Casey\altaffilmark{1}}
\altaffiltext{1}{Research School of Astronomy \& Astrophysics, Australian National University, Mount Stromlo Observatory, via Cotter Rd, Weston, ACT 2611, Australia; acasey@mso.anu.edu.au}

\begin{abstract}
\end{abstract}

% introducion to big data, surveys
% has caused a need to evolve the data techniques in use
% it is important to maintain tangibility to the data when shifting to automatic methods

% ccds helped lead the first photometric surveys
% now we have all-sky surveys across all parts of the electromgnetic spectrum
% spectroscopic surveys have particularly taken off, in both the stellar and galactic regime

\keywords{Galaxy: halo, structure --- Individual: Virgo Overdensity --- Stars: K-giants}

\section{Introduction}
Astronomy is an exceptionally data-rich science. In recent decades the number of large scale surveys has only highlighted this fact. Astronomers are increasingly trying to automate traditional measurement techniques simply to keep up with the data acquisition rates. However, as the astronomical community transitions from traditional analysis techniques to automated methods, it is of critical importance that we retain tangibility with the data.

% Introduction (and motivation)
% Overview
% - introduction of chi^2 and general overview
% - rough description of steps involved and their associated subsections where they are explained
% -

% Methodology
% - normalisation
% - doppler correction
% - Re-sampling the reference spectra
% - photometric priors
% - solution steps
%   - decoupled and coupled methods

% Usage

%

% initially was just photometry, then low res spec, now high res spec + radio +

% large scale surveys
% number of spectral grids + atmospheres available is growing so that it makes this sort of analysis easier
% even in smaller-scale data sets, the learning curve is high (code) and the information is effectively lost
% combinations of synthetic spectra + packages can be used in tandem, but there is some tangibility to the data lost. SCOPE is designed not to be a black-box
% we outline the details of the scope package and provide extensive examples and tutorials on setting up recipes and then applying them to massive data sets
% intention to largely dampen the learning curve such that more information can be extracted from existing spectra at little extra cost
% repeatedly shown that extra information can be extracted from large surveys when atmospheric parameters are available (hubble telescope data archives, FEROS data set)

\section{Overview}
SCOPE determines the parameters of observed spectra by comparing them against a set of spectra with well-defined parameters. Normally the reference spectra are synthetic, but SCOPE does not enforce such constraints \--- a well-sampled observed library with trusted, homogeneously derived parameters will suffice. Parameters are determined by minimising the $\chi^2$ value,

\begin{equation}
\chi^2 = \frac{1}{N-M}\sum\limits_{i=0}^{N}\frac{(F_i - f_i)^2}{\sigma_i}
\end{equation}

\noindent{}between the observed ($f_i$) and the reference ($F_i$) flux, where $M$ is the number of degrees of freedom, $N$ is the number of flux points and $\sigma_i$ is the uncertainty in the observed flux. A $\chi^2$ value is determined against every reference spectra in order to avoid local minima.

The normalisation of both observations and reference spectra is critically important, simply by definition of the $\chi^2$ parameter. Observations (and reference spectra) are normalised (Section \ref{sec:normalisation}), and doppler corrected (Section \ref{sec:doppler-corrected) before any $\chi^2$ comparison is made. Reference spectra are assumed to be at rest frame.

Prior to comparison, the standards

SCOPE is completely configurable. Parameters can be measured using the entire spectral regions, or only pre-selected regions which you know will be astrophysically sensitive to that parameter (e.g. Fe lines for stellar metallicity). Solution steps are provided which completely control how a parameter should be measured, and what constraints should be placed on this measurement.

\subsection{Dimensions and Parameters}

An important distinction must be made early on regarding the vernacular employed within this paper, and SCOPE itself. Dimensions are defined as the orthogonal axes of the reference grid, and parameters are values which we wish to measure on the observed spectrum. Usually, these two terms are largely interchangeable: we want to measure effective temperature of our observed spectrum, so the effective temperature of the minimum $\chi^2$ point is our observed temperature. The distinction becomes clear when we wish to measure multiple parameters on the same dimension.

An example of such a scenario is when we may want to measure the effective temperature using multiple spectral regions. The H$\beta$ Balmer line at $\Lambda$ is an excellent discriminant of effective temperature \citep{Barklem}, and one may want to compare the H-$\beta$ temperature derived and the temperature when using a global spectrum fit. SCOPE easily allows for such tests. The techniques of setting up such tests within SCOPE are described in Section \ref{sec:solution-steps}, but it is important to clearly distinguish between parameters and dimensions.

\subsection{De-coupled, Pseudo-Coupled and Coupled methods}

% SCOPE basics: x^2
% comparison against a set of spectra with "expected" values
% introduce dimensions/parameters, be explicit that scope doesn't care what they are
\subsection{Normalisation}
\subsection{Doppler corrections}
\subsection{Grid sampling}
\subsection{Multidimensional interpolation}

\section{Defining a recipe}
% scope is very much GIGO
% intention is to test a recipe until it is robust against your calibrators
% existing recipes in the literature and online (including the model atmospheres, line lists, etc)

\subsection{Introducing photometric priors}
\label{sec:photometric-priors}

\subsection{Optimisation algorithms}

\bibliographystyle{apj}
\bibliography{bibliography}

\end{document}

### 2012-05-28 2012-vod/draft.tex
Initial commit.

%!TEX TS-program = pdflatex
\documentclass{emulateapj}

\shorttitle{The Origin of the VOD}
\shortauthors{Casey et al}

\begin{document}

\title{The Origin of the Virgo Overdensity}

% Authors on original proposal: Stefan Keller, Andy Casey, Gary Da Costa, Daniel Zucker, Elaina Hyde, Kenji Bekki

\author{Andrew R. Casey\altaffilmark{1}, Stefan C. Keller\altaffilmark{1}, Gary Da Costa\altaffilmark{1}, Daniel Zucker\altaffilmark{2}, Elaina Hyde\altaffilmark{2}, \and Kenji Bekki\altaffilmark{3}}
\altaffiltext{1}{Research School of Astronomy \& Astrophysics, Australian National University, Mount Stromlo Observatory, via Cotter Rd, Weston, ACT 2611, Australia; acasey@mso.anu.edu.au}
\altaffiltext{2}{Department of Physics \& Astronomy, Macquarie University, Sydney 2109, Australia}
\altaffiltext{3}{ICRAR M468, The University of Western Australia, 35 Stirling Highway, Crawley, Western Australia 6009, Perth, Australia}

\begin{abstract}
\end{abstract}

\keywords{Galaxy: halo, structure --- Individual: Virgo Overdensity --- Stars: K-giants}

\section{Introduction}
%Accretion has played a vital role in the formation of the Galaxy. Consistent with the hierarchical framework of \citet{Searle;Zinn_1978}, star clusters conglomerate together to form large-scale structures like the Milky Way.

%During later mergers, dwarf spheroidals and globular clusters experience tidal stresses during their infall. These stresses cause the perimeter stars to become unbounded from their parent cluster, and a stream of stars lie in its wake.

%The number of recent and ongoing mergers detected has increased dramatically in the wake of large sky surveys. We are only starting to realise the rich level of substructure within the galactic halo.

One of the most prominent of these substructures is the Virgo Overdensity (VOD). The VOD is a diffuse overdensity of stars, which is greatly dispersed along the line of sight. The VOD represents the most complex, accretion-dominated volume in the Milky Way. It is a junction for overlapping stellar streams of distinct origins \citet{Belokurov;et-al_2006}, which further complicates the task of assigning membership to stars in this region. This has also made the nature of the VOD particularly difficult to interpret: Are we witnessing the remnant of an early minor merger in the formation history of the Galaxy? Is the spatial overdensity simply an observational consequence of overlapping stellar streams? Or, is the VOD distribution smooth, and an inevitable consequence of a triaxial dark matter halo? We seek to untangle this region and address these questions.

The QUEST survey \citet{Vivas;et-al_2001} first observed an overdensity of RR Lyrae stars in this region (see also \citet{Zinn;etal_2004}). \citet{Newberg;et-al_2002} independently identified a diffuse overdensity of turnoff stars $r_\odot \sim18$ kpc away in the same direction. At the time, no relationship between these clumps could be examined. In fact, the sheer size of the VOD could not be appreciated until \citet{Juric;et-al_2008} examined the halo stellar density in the Sloan Digital Sky Survey \citep[hereafter SDSS]{York;et-al_2000} data release. \citet{Juric;et-al_2008} described the VOD as spanning well over $1,000$ deg$^{2}$ on the sky. Angular size measurements of the VOD have remained lower limits even as more data becomes available \citep{Duffau;et-al_2006, Juric;et-al_2008, Bonaco;et-al_2012}, as the substructure extends further south past the SDSS boundary. It is likely the full perimeter of the VOD will not be explored until the SkyMapper telescope \citep{Keller;et-al_2007} images this region.

The nature of the VOD is particularly important. There have been multiple kinematically cold stellar streams detected within the VOD. This strongly suggests the VOD is associated with at least one of these accreted substructures. Although the spatial overdensity is rich with substructure, it does not preclude the possibility that the overdensity is galactic in origin. Such a result which would be strong evidence for a triaxial dark matter halo \citep{Newberg;et-al_2007}. Substructures like the VOD and the Sgr tidal tails are excellent tracers of the galactic potential \citep{Law;et-al_2005, Casey;et-al_2012a}.

%The most prominent of these interacting stellar streams is the Sagittarius (Sgr) stream, which \citet{} argue is responsible for the spatial overdensity in Virgo. Who disagreed?

%As this region overlaps with several co-moving groups, it is difficult to distinguish stellar streams and halo contaminants from true VOD members. Stellar streams are somewhat easier to identify because they demonstrate a tight kinematic signature which persists for long timescales.  Table \ref{tab:vod-streams} compiles all of the published  indicators of substructure in this region.

% what streams are running through this region

% kinematics of streams; is the VOD distinct from

% metallicity of streams;

% origin remains debateable
There is no conclusive literature regarding the origin of the VOD, or the relationship between the spatial overdensity and the multiple kinematic signatures. Unfortunately, distances are not precise enough to help untangle the region. The uncertainty in distance for the VSS and the line-of-sight distance dispersion for the VOD has led some authors to infer they are part of the same substructure\citet{Duffau;et-al_2006, Newberg;et-al_2007, Prior;et-al_2009a}. With this hypothesis, given the low metallicities of the VSS \citep{Duffau;et-al_2006, Prior;et-al_2009a} and the wide range of metallicities present in the VOD \citep{Juric;et-al_2008}, many groups \citep{Duffau;et-al_2006, Martinez-Delgado;et-al_2007, Juric;et-al_2008} to conclude we are witnessing the tidal debris of a disrupted dwarf spheroidal (dSph) galaxy of low metallicity.

\citet{Martinez-Delgado;et-al_2007} suggest this invading dwarf is the prominent Sagittarius (Sgr) dSph galaxy. If this hypothesis is correct, the tidal debris would pass through the solar neighbourhood, providing an excellent test for the presence of weakly interacting massive dark matter particles. \citet{Martinez-Delgado;et-al_2007} predicted highly negative velocities for VOD members in this region. This signature was not observed by \citet{Newberg;et-al_2007}, implying that the VOD is distinct from the tidal debris of Sgr. However, this does not exclude the possibility of the VOD originating from a different dSph.

We present spectroscopic observations of MANY K-type stars across nineteen discretely sampled fields in the known VOD DR7 footprint \--- which was the most recent at the time of the proposal. In \S{sec:candidate-selection} we describe the candidate selection employed to minimise contamination of foreground dwarfs. Section \ref{observations} provides details of the observations taken and the data reduction method. We provide an extensive description of our spectral analysis in \S\ref{sec:spectral-analysis}, including the model atmospheres, line lists and code employed to perform these analyses. Our adopted analysis technique is verified against a plethora of spectroscopic standards in \S\ref{sec:calibration}. The data is outlined in \S\ref{sec:data} and we discuss our findings in \S\ref{sec:discussion}. We conclude in Section \ref{sec:conclusion} with critical interpretations, and outline future work necessary for this region.

\section{Candidate Selection}
We have targeted K-type giants throughout the known footprint of the VOD. These stars allow for accurate radial velocity measurements and a metallicity determination which is unbiased by their spectral type. However, colour selections employed for K giants are generally contaminated by faint, nearby dwarfs. We have taken every step to reduce this contamination, beginning with our initial colour selection.

% talk about colour selection
% 2mass and sdss, isochrone, probability, ppmxl

Some K-type dwarfs will inevitably reach into our sample. We can largely discard these contaminants with accurate surface gravity determination (see \S\ref{sec:calibration}). With our candidate selection described above, we estimate a dwarf contamination rate of approximately twenty percent.

\section{Observations and Data Reduction}
\subsection{Observations}
We present nineteen fields covering the confirmed extent of the VOD within the SDSS DR7 footprint, as illustrated in Figure \ref{fig:target-fields}. Table \ref{tab:target-fields} lists the positions, seeing, median airmass and number of stars targeted for all of our fields.

\begin{figure}[h!]
	\includegraphics[width=\columnwidth]{./figures/fields.pdf}
	\caption{A northern Galactic cap polar plot showing the density of F turnoff stars (where $0.2 < (g - r)_0 < 0.3, (u - g)_0 > 0.4$ and $20.0 < g_0 < 21.0$) as selected by \citet{Newberg;et-al_2007}. Darker regions indicate a higher density of turnoff stars. The Sgr leading stream is evident, as is the broad extent of the VOD. The positions of our nineteen fields are shown.
	}
	\label{fig:target-fields}
\end{figure}

Observations were undertaken in normal visitor mode using the AAOmega instrument on the 3.9 m Australian Astronomical Telescope (AAT) in Coonabarabran, NSW during April 2011. The AAOmega 2dF system is a fibre-fed, dual-beam multiplexing spectrograph with interchangeable VPH gratings. AAOmega is capable of simultaneously observing 400 targets over a two degree field. The VPH gratings used were the 1500V and 1700D in the blue and red arm respectively. The 1500V grating provides a spectral coverage from $425-600$ nm at a resolution of $R \simeq 3,700$. The central wavelength for the blue arm was set to $475$ nm to prevent the gravity-sensitive Mg I b triplet lines at $\sim517$ nm falling on defective regions of the detector. The 1700D grating in the red arm provides moderate resolution ($R \simeq 10,000$) over the wavelength range $830-900$ nm, which includes the strong Ca II NIR triplet lines.

Thirty sky fibres were allocated in each field to allow for optimal sky subtraction, and a minimum of six fibres were allocated to bright stars for guiding.

\begin{deluxetable}{cccccc}
\tablecolumns{1}
\tablewidth{\columnwidth}
\tabletypesize{\scriptsize}
\tablecaption{Field centroids and observational data\label{tab:target-fields}}
\tablehead{
	\colhead{Field} &
	\colhead{$\alpha$} &
	\colhead{$\delta$} &
	\colhead{Science} &
	\colhead{Median} &
	\colhead{Seeing} \\ 
 & (J2000) & (J2000) & Targets & Airmass & (")
}
\startdata
1 & 12 45 34  & $-$02 50 15 & 353 & 1.14 & 1.5 \\
2 & 12 46 18  & +01 09 30 & 350 & 1.24 & 1.5 \\
3 & 12 47 01  & +05 09 14 & 350 & 1.31 & 1.5 \\
4 & 12 47 46  & +09 09 01 & 324 & 1.34 & 1.5 \\
5 & 12 44 50  & $-$06 49 58 & 351 & 1.10 & 1.5 \\
6 & 12 44 06  & $-$10 49 44 & 353 & 1.49 & 1.5 \\
7 & 12 43 20  & $-$14 49 31 & 350 & 1.07 & 1.5 \\
8 & 13 09 42  & +00 29 09 & 351 & 1.30 & 1.5 \\
9 & 13 08 32  & +04 30 01 & 349 & 1.27 & 1.5 \\
10 & 13 09 35 & $-$02 33 04 & 352 & 1.39 & 1.5 \\
11 & ? & ? & ? & ? & ? \\
12 & ? & ? & ? & ? & ? \\
13 & 12 57 35 & $-$02 50 02 & 353 & 1.87 & 1.5 \\
14 & 12 33 36 & $-$02 33 41 & 350 & 1.20 & 1.5 \\
15 & 12 34 57 & +01 25 54 & 352 & 1.25 & 1.5 \\
16 & 12 36 33 & +05 24 58 & 349 & 1.31 & 1.5 \\
17 & 12 25 12 & +04 59 45 & 351 & 1.64 & 1.5 \\
18 & 12 22 48 & +01 01 10 & 352 & 1.30 & 1.5 \\
19 & 12 20 54 & $-$02 43 55 & 349 & 1.72 & 1.5 
\enddata
\end{deluxetable}

% http://www.briancasey.org/artifacts/astro/airmass.cgi

\subsection{Data Reduction}
The data was reduced using the supplied 2\textsc{DFDR} package (April 2009 version). Each frame was flat-fielded and wavelength calibrated from flat and arc frames taken between each exposure. Throughput calibration for each fibre was achieved using the night sky lines, and the sky spectrum was removed using the median flux of the dedicated sky fibres. Three twenty minute object frames were median combined to remove cosmic rays.

% speak about SNR

\section{Spectral Analysis}
\label{sec:spectral-analysis}

Stellar parameters for all of our observations were determined using the Spectral COmparison and Parameter Evaluation (SCOPE) package, which will be fully described in a later contribution \citep{Casey;et-al_2012d}. SCOPE normalises all our observations, performs doppler corrections and determines stellar parameters in an iterative manner.

\subsection{Normalisation}
Correct determination of the continuum is crucial to estimating the stellar parameters. The normalisation technique used must be sufficiently robust in noisy signals or in the presence of molecular bands, where the continuum determination can be non-trivial. A synthetic template of a typical halo giant ($T_{eff} = 4500$ K, $\log{g} = 2.5$ dex, $[\mbox{M}/\mbox{H}] = -1.5$ dex) has been used in order to estimate continuum regions of our observed spectra.

We have defined continuum regions in the synthetic spectrum where the flux level resides between $F_i: [0.96, 1.00]$. To avoid individual pixels being described as regions of continuum, we impose a minimum width of $0.5$ \AA{} for any continuum region. No maximum continuum width is imposed.

A third order cubic spline with defined knot spacing ($15$ nm in the blue arm, $20$ nm in the red arm) is fit to all observed flux points within our determined continuum regions. The knots are placed such that the distance between outer knots and the edge of the spectrum are equal. The number of knots employed is maximised until this outer distance becomes less than half the knot spacing.

The spline is weighted by the observed flux level. The difference between the determined continuum and the observed flux is calculated, and 5-$\sigma$ deviations are clipped to avoid CCD defects or persistent cosmic rays being used to incorrectly describe the continuum. This spline-fitting process is iteratively repeated until no such deviations exist.

If the observation spectrum is particularly noisy or sufficiently more metal-rich than our initial template, then our iterative spline technique discards the edge continuum regions in the sigma clipping process. When this occurs the spline may become unbounded from the outer edge knot. To correct for this effect we divide our resultant spectrum with the perfect synthetic spectrum, and fit a low order polynomial to this shape. Only the edge effects discussed above contribute to the shape of this polynomial. This technique provides a negligible correction in high SNR observations, and ensures our normalisation is robust for even the noisiest spectrum.

Although this normalisation process is robust, experience has shown that it systematically underestimates the level of continuum by $\sim{1-2}\%$. As a final step, we demand the median flux level in continuum regions of our normalised spectra is unity.

\subsection{Radial Velocities}
Radial velocities are measured iteratively for each observation. The reduced spectrum is initially cross-correlated between $845$ nm $< \lambda <$ $870$ nm with the same synthetic spectrum employed for normalisation. The red and blue observed orders are shifted to rest frame before any further analysis.

After the stellar parameters have been determined, we interpolate to a synthetic template with these parameters and re-measure the radial velocity. These additional radial velocity measurements provide more realistic uncertainties, and are always consistent with our initial velocity measurements.

Heliocentric velocities have been translated to a galactocentric frame. We have adopted the circular velocity of the Local Standard of Rest (LSR) at the Sun as $220 \mbox{km s}^{-1}$ \citep{Kerr;Lynden-Bell_1986} and accounted for the Sun's peculiar motion to the LSR by using $16.5 \mbox{km s}^{-1}$ towards $l = 53^\circ$, $b = 25^\circ$ \citep{Mihalas;Binney_1981}. The corrected line-of-sight velocity is then given by,
\begin{eqnarray}
	&V_{GSR} = & V_{OBS} + 220\sin{l}\cos{b} + 16.5  \\
	& 		 &\times[\sin{b}\sin{25} + \cos{b}\cos{25}\cos{(l - 53)}], \nonumber
\label{eq:vgsr}
\end{eqnarray}
\noindent{}where $V_{OBS}$ is the heliocentric-corrected observed line-of-sight velocity. We note that published velocity peaks for this region have employed slightly different formulae to transpose their kinematics to a galactocentric frame. This will result in a systematic shift in velocities between authors \--- greater than the individual uncertainties. We will address relevant discrepancies individually later in the text.

\subsection{Grid of Synthetic Spectra}

The observed stellar parameters are determined by comparing our observations to a grid of synthetic spectra with defined values. Our grid has four dimensions: effective temperature ($T_{eff}$), surface gravity ($\log{g}$), metallicity ($[\mbox{Fe}/\mbox{H}]$) and alpha enhancement ($[\alpha/\mbox{Fe}]$). The bounds of this grid are illustrated in Figure \ref{fig:grid-boundaries}. These boundaries sufficiently extend past the expected values from our observations.

\begin{figure}[h!]
	\includegraphics[width=\columnwidth]{./figures/grid-points.pdf}
	\caption{A 2D representation of our synthetic grid points. Each illustrated point has a number of metallicities: the pluses (+) indicate metallicity points between -2.5 and +0.5 dex with 0.5 dex steps and an additional point at [Fe/H] = $+0.2$ dex, and the encircled pluses (++) illustrate where we have extended our metallicity grid down to [Fe/H] = -5.5 at 0.5 dex steps. Every point has a solar-level [$\alpha$/Fe] and an alpha enhancement [$\alpha$/Fe] = +0.4 dex.}
	\label{fig:grid-boundaries}
\end{figure}

Throughout this article we refer to the metallicity ($[\mbox{Fe}/\mbox{H}]$) as the bulk metal content of heavy elements. Standard spectroscopic abundance notation is adopted such that the ratio of two elements in a star relative to their ratio in the Sun is
\begin{equation}
[\mbox{A}/\mbox{B}] \equiv \log{[n(\mbox{A})/n(\mbox{B})]} - \log{[n(\mbox{A})/n(\mbox{B})]}_\odot,
\end{equation}
\noindent{}where $n$ represents the number density. The level of alpha enhancement ($[\alpha/\mbox{Fe}]$) is quantified by the abundance of the $\alpha$-elements Mg, Si, S, Ar, Ca and Ti. These elements all vary together.

\subsubsection{Model Atmospheres}
A model stellar atmosphere is required before a synthetic spectrum can be computed. Stellar atmosphere models tabulate pressure, temperature, electron fraction and opacity as a function of optical depth within the stellar atmosphere. We have chosen to use the \citet{Castelli;Kurucz_2004} grid of plane-parallel model atmospheres with no convective overshoot \citep{Castelli;Kurucz_1997} and updated opacity distribution functions \citep{Castelli;Kurucz_2003}. Microturbulent velocity ($v_t$) for our synthetic spectra was fixed as $2$ km s$^{-1}$.

\subsubsection{Line List}
We have compiled a line list of wavelengths, excitation potentials (EPs), and oscillator strengths ($\log{gf}$) for atomic, hyperfine and molecular transitions spanning our observed spectral range. Generally the wavelength transition locations are well known, however oscillator strengths are notoriously difficult to measure. High resolution spectroscopic analysis will typically only compare line strengths for well established transitions within the linear regime of the curve of growth. In this analysis we are considering a wide spectral range at a lower resolution, where most lines will be blended. Consequently we must use an extensive library of transitions, which will all contribute to the derived parameters with varying degree.

We began by querying the Vienna Atomic Line Database \citep[VALD][]{Kupka;et-al_1999} in March 2012 and retrieved all neutral and singular atomic transitions within the spectral ranges $380-605$ nm and $830-890$ nm with $0 < \mbox{EP} < 10.2$ eV and $\log{gf} > -5$. The list was supplemented with molecular transitions from \citet{Kurucz_1992} for the $A^2\Pi-X^{2}\Sigma$ CN and MgH transitions, and all C$_2$ transitions. Hyperfine transitions for Li, Sc, V, Mn, Co, Cu, and Eu from \citet{Kurucz_1993} were included in our list.

SCOPE's line list calibration routine was employed to match our generated synthetic spectrum with the Solar \citep{Wallace;et-al_2011} and Arcturus \citep{Hinkle;et-al_2003} atlases. We generated spectra in MOOG \citep[see \S\ref{sec:synth-generation}]{Sneden_1973}, using a Solar atmosphere model where $T_{eff}= 5577$ K, $\log{g} = 4.437$, $[\mbox{M}/\mbox{H}] = 0.00$ and $v_{t} = 1.0$ km s$^{-1}$. The synthetic spectrum was matched to the atlas dispersion and convolved with a $0.05$ dex wide Gaussian kernel.

We chose to perform our line calibration interactively on selected line discrepancies instead of using a completely automatic approach. Beginning with the strong line transitions, the oscillator strength of each line is varied and the $\chi^2$ statistic (variant of Eq. \ref{eq:chi}) between the synthetic spectrum and the observed atlas is calculated. The Nelder-Mead optimisation algorithm \citep{Nelder;Mead_1965} was employed to determine the oscillator strength and minimise the $\chi^2$ value. We iterated until a $10^{-4}$ relative change in $\log{gf}$ was achieved. When the transition in question belongs to a multiplet, we alter the relative oscillator strength for all transitions in the multiplet simultaneously. It is worth noting that although we found a much better statistical fit when altering each transition individually, this is forbidden by quantum mechanics.

We repeated this process for the discrepant weaker transitions. Our revised strong line list was employed and the relative oscillator strength was varied for lines in the weaker multiplets. When we observed an absorption feature not present in our line list, we invented a Fe transition with the required excitation potential and oscillator strength to replicate the observed profile. Using this calibration technique the median absolute RMS between our synthetic spectrum and the Sun has decreased from $1.3 \times 10^{-3}$ to Y, and the deviation from $9.3 \times 10^{-2}$ to B.

This calibration process was repeated on the Arcturus atlas of \citet{Hinkle;et-al_2003}. We used a depth-varying atmospheric model for Arcturus \citep{Kurucz}, where $T_{eff} = X, \log{g} = X, [\mbox{Fe}/\mbox{H}] = 0.00$. Taking the Solar atlas to be more precise and the Solar atmosphere to be better modelled, we only used Arcturus-calibrated oscillator strengths if they did not increase the $\chi^2$ value in the equivalent Solar spectrum. The mean absolute RMS of our fit lowered from $X \pm Y$ (using the Solar-calibrated line list) to $Z \pm A$ through this technique. The entirety of our line list is published in Table \ref{tab:line-list}.

\begin{deluxetable}{cccc}
\tablecolumns{1}
\tablewidth{\columnwidth}
\tablecaption{List of transition lines\label{tab:line-list}}
\tablehead{
	\colhead{Wavelength} &
	\colhead{Species} &
	\colhead{EP} &
	\colhead{$\log{gf}$} \\ 
	(\AA) & & (eV) & (dex)
}
\startdata
8300.229 & 25.0 & 6.752 & -2.602 \\
8300.229\tablenotemark{a} & 25.0 & 6.752 & -2.602 \\
8300.229 & 25.0 & 6.752 & -2.602 \\
8300.229\tablenotemark{b} & 25.0 & 6.752 & -2.602 \\
\enddata
\tablenotetext{a}{Invented transition to match atlas.}
\tablenotetext{b}{Strong transition.}
\end{deluxetable}

\subsubsection{Synthetic Spectrum Generation}
\label{sec:synth-generation}
The synthetic spectrum for each grid point has been generated using MOOG. We have employed \citet{Anders;Grevesse_1989} solar abundances, with the exception of Fe, where we have used the revised value from \citet{Asplund;et-al_2005}. The absorption caused by stronger transitions was considered at every wavelength step. In the blue arm, the strong lines include the Ca H, Ca K, and Mg I b triplet lines at $\lambda517$nm. For the red arm these lines include the Ca II NIR triplet lines, and Na I at $\lambda8807$. The absorption contribution for all weaker transitions was considered within $2$ \AA{} of their core depth.

The spectra was generated at a resolution of $0.10$ \AA{} px$^{-1}$, and is later re-sampled to match the observed wavelength-pixel dispersion and convolved to match our resolving power.

\subsection{Stellar Parameter Determination}

SCOPE determines stellar parameters by minimising the $\chi^2$ value,
\begin{equation}
\chi^2 = \frac{1}{N-M}\sum\limits_{i=0}^{N}\frac{(F_i - f_i)^2}{\sigma_i}
\end{equation}
\noindent{}where the synthetic and observed flux is represented by $F_i$ and $f_i$ respectively, $M$ is the number of degrees of freedom (e.g. $T_{eff}$, $\log{g}$, $[\mbox{Fe}/\mbox{H}]$, $[\alpha/\mbox{Fe}]$), and the uncertainty $\sigma_i$ is measured from $(\mbox{S}/\mbox{N})^{-2}$.

Observations are compared against the grid of synthetic spectra and a $\chi^2$ value is determined at every grid point. This sampling technique is a relatively expensive computational step, but it is necessary to confidently prevent false positive determinations of atmospheric parameters. There are techniques available within SCOPE to minimise the level of sampling required (see \S\ref{sec:effective-temperature}).

When the grid sampling is completed a subset of points surrounding the minimum $\chi_{min}^2$ point are used for flux interpolation. Because our observed parameters do not reside on evenly spaced grid points, interpolation within the synthetic grid of fluxes is necessary. We linearly interpolate in flux space \--- not $\chi^2$ space \--- such that our synthetic flux becomes a continuous function within the grid boundaries. One-dimensional splines are fit to the minimum along each axis, and an estimate of the inter-grid $\chi^2$ minima is provided as an initial guess to a Nelder-Mead optimising algorithm (see Figure \ref{fig:chi-estimate}). Points within the entire subset are sampled until the minima is found and a $10^{-8}$ tolerance in $\chi^2$ is achieved.

% Figure showing chi^2 sampling and a spline estimate, then the optimisation.

\subsubsection{Photometric temperature estimates}
\label{sec:photometric-estimates}

All of our observations were cross-matched against the 2MASS catalogue prior to analysis and a photometric temperature is calculated. Photometric estimates of stellar parameters can be used to restrict the level of synthetic grid sampling required. We have adopted the empirical $T_{eff}$-colour relationship for F0-K5 giant stars from \citet{Alonso;et-al},
\begin{equation}
\theta_{eff} = 0.5816 + 0.9134(J-K)_0 - 0.1443(J-K)_{0}^2
\end{equation}

\noindent{}where $T_{eff} = 5040/\theta_{eff}$. The dust maps of \citet{Schlegel;et-al_1998} with revised bandpasses from \citet{Schonrich;et-al_2011} were used to correct for interstellar extinction. Because we are constraining the range of temperature points sampled in our synthetic grid, it is of critical importance not to underestimate the uncertainty in this relationship. \citet{Alonso;et-al} report an uncertainty of $125$ K using this relationship. We have pessimistically included the photometric uncertainties ($\sigma_J$, $\sigma_K$) to estimate a photometric contribution to the total error budget as,
\begin{equation}
\sigma_{phot} = T_{eff}(J_0+\sigma_J - K_0 +\sigma_K) - T_{eff}(J_0 - K_0)
\end{equation}

\noindent{}and added these two error sources in quadrature. The synthetic grid is restricted by 3-$\sigma_{total}$ either side of the photometric temperature (typically this equates to $\sim\pm1,200$ K). In extremely rare cases when the grid has been photometrically constrained and the spectroscopically determined temperature was close to the edge of the restricted grid, the photometric constraint was removed and the analysis was repeated.

\subsubsection{Solution steps}
\label{sec:solution-steps}

SCOPE allows us to set up any number of solution steps, where we can solve for atmospheric parameters either individually or any number of them simultaneously. After extensive testing, we have adopted a recipe which solves for $T_{eff}$, $[\mbox{Fe}/\mbox{H}]$, and $[\alpha/\mbox{Fe}]$ first simultaneously, and then solves for $\log{g}$. Different wavelength regions are used for the $\chi^2$ evaluation in each solution step. These comparison regions are tabulated in Table \ref{tab:solution-setup}.

% table here showing entire comparison regions
% Dimension(s) | Regions

\begin{deluxetable}{ccccc}
\tablecolumns{1}
\tablewidth{\columnwidth}
\tablecaption{SCOPE solution setup.\label{tab:solution-setup}.}
\tablehead{
& Measured & Fixed & \multicolumn{2}{c}{Regions} \\
	\colhead{Step} &
	\colhead{Parameters} &
	\colhead{Parameters} &
	\colhead{$\lambda_a$} &
	\colhead{$\lambda_b$} \\
	& & & (\AA{}) & (\AA{})
}
\startdata
1 & $T_{eff}, [\mbox{Fe}/\mbox{H}], [\alpha/\mbox{H}]$ & None & 8400.0 & 8850.0 \\
&&& 8400.0 & 8850.0 \\
 2 & $\log{g}$ & $T_{eff}, [\mbox{Fe}/\mbox{H}]$ & 8400.0 & 8850.0
\enddata
\end{deluxetable}

\subsubsection{Metallicity, $[\mbox{Fe}/\mbox{H}]$}
We solve for metallicity and temperature simultaneously. After extensive testing we determined that the known degeneracies between $T_{eff}-[\mbox{Fe}/\mbox{H}]$ are simply too prominent in our data to allow for solving $T_{eff}$ and [Fe/H] separately.

\subsubsection{Alpha Abundance, $[\alpha/\mbox{Fe}]$}

\begin{equation}
[\alpha/\mbox{Fe}] = [\alpha/\mbox{H}] - [\mbox{Fe}/\mbox{H}]
\end{equation}

\subsubsection{Surface Gravity, $\log{g}$}
We solve for surface gravity in our second solution step. During this step we only use the $516-519$ nm region surrounding the Mg I b triplet lines for comparison. The $\chi^2$ statistic has a tendency to be influenced by regions of the spectrum which are not sensitive to atmospheric parameters. This is typically nor a problem for $T_{eff}$ and [Fe/H] because large regions of the spectrum are sensitive to these parameters. Given the difficulty in measuring surface gravity, we have chosen only to use a region which we know is particularly gravity sensitive.

Tests performed with SCOPE have indicated that if $T_{eff}$ is not fixed when measuring $\log{g}$ then the $\chi^2$ space is not sufficiently well-described in order to find the true surface gravity. Multiple local minima are present; an incorrect initial guess is often provided to our optimisation algorithm. We also noticed a strong degeneracy present between [Fe/H] and $\log{g}$: if [Fe/H] is fixed to the value we have determined in the previous solution step, then then our surface gravity measurements incur significant scatter. Hence, when measuring surface gravity we fix the temperature to the value we have previously determined, and allow [Fe/H] to be free.

\section{Verification of analysis technique}
\label{sec:calibration}

We have validated our analysis technique with three different data sets: two high resolution spectroscopic libraries with exquisite S/N, and RGB stars in ten globular clusters observed on the AAT.

\subsection{Spectroscopic Libraries}
There is a growing number of high resolution spectroscopic libraries available for comparison, however few of them cover the spectral range covered by AAOmega's 1500V/1700D filter set.

\label{sec:S4N}
\subsubsection{The S$^4$N Library}
The S${^4}$N library contains high resolution, high S/N spectroscopic observations of 118 stars within the Solar neighbourhood \citep{Allende-Prieto;et-al_2004}. These observations cover a wide wavelength range from $\sim362$ nm to $921$ nm with a resolving power of $R\simeq50,000$. Published spectra are already normalised and placed at rest frame. Thus, we chose not to re-normalise the spectra or apply doppler corrections.

The S$^4$N observations were interpolated to the same pixel-dispersion map as our observations, and convolved to match our resolving power. The S/N for the S$^4$N spectra varies between $150-600$. Resampling these observations adds correlated noise, albeit negligible in this case. Hence we are now effectively working with medium resolution observations with exceptional S/N. We have chosen not to add additional shot noise for this initial comparison \--- the effects of Poisson noise are examined later in \S\ref{sec:shot-noise}.

\begin{figure*}[t!]
	\includegraphics[width=\textwidth]{./figures/s4n-comparison.pdf}
	\caption{Comparison between the determined atmospheric parameters for the S$^{4}$N stellar catalogue at high resolution \citep{S4N}, and the values determined after resampling and convolving the spectra to our observed dispersion and resolution. The dashed lines indicate 1\---$\sigma$ deviations between the expected and determined parameters.}
	\label{fig:s4n-comparison}
\end{figure*}

Discrepancies between the expected atmospheric parameters of \citet{Barklem;et-al_2004} and derived values are illustrated in Figure \ref{fig:s4n-differences}. We recover atmospheric parameters with excellent precision. The 1\---$\sigma$ dispersions in $T_{eff}$, $\log{g}$ and $[\mbox{Fe}/\mbox{H}]$ correspond to $205$ K, $0.40$ dex and $0.15$ dex respectively. These values are tabulated with our CFLIB discrepancies in Table \ref{tab:grid-boundaries}, and are typical uncertainties for spectra at this dispersion and resolution.

% see allende-prieto re IRFM -- Blackwell

\subsubsection{CFLIB}
\label{sec:CFLIB}
Although our S$^4$N comparative results are encouraging, the S$^4$N stars are all solar neighbourhood dwarfs and do not represent our target selection. In fact, they more closely represent our contaminants. We have performed the same analysis on the CFLIB library \citep{Valdes;et-al_2007}, which includes both giants and dwarfs. The atmospheric parameters reported for CFLIB come from a variety of literature sources; the analysis technique was not homogenous. Compared to S$^4$N, we can expect a larger dispersion in these results.

Most CFLIB spectra extends from $346$ nm to $964$ nm. Multiple exposures with different grating configurations are required to cover this full spectral range and consequently some observations have only partial wavelength coverage. We excluded observations which did not have coverage across our $\chi^2$ comparison regions. Observations with expected parameters outside of our synthetic grid boundaries were also discarded.

% Instead of using the single measurements compiled by \citet{Valdes;et-al_2004} as our expected parameters, we queried the PASTEL database \citep{Soubiran;et-al_2010} for all the CFLIB stars with multiple measurements of the stellar parameters. We excluded observations where only one determination of the stellar parameters was available, or if the published parameters were wildly inconsistent. Our distilled sample size of CFLIB spectra is 361 stars \--- including 188 giants and 173 dwarfs (separated by $\log{g} = 3.5$).

% num covering spectral regions: 800 (spectra)

% JUST ON PASTEL
% num with 2+ measurements in all dimensions: 646 (multi)
% num within grid: 671 (inbounds)
% num with [fe/h] < -1 (mp): 90
% intersection of (inbounds) & (multi | mp): 611 (total)

% WITH SPECTRAL RANGE INCL.
% intersection of (total) & (spectra): 438
% multiple measurements: 386 (multi)18
% in bounds: 392 (in_bounds)
% mp: 24 (mp)
% usable (in_bounds) & | ((multi_measured) | (mp)): 361
% giants (logg < 3.5) in (usable): 188
% dwarfs (logg >= 3.5) in (usable): 173

% Include figure for CFLIB results

\begin{deluxetable}{lccc}
\tablecolumns{1}
\tablewidth{\columnwidth}
\tablecaption{Biases and dispersions for derived parameters in existing high resolution libraries.\label{tab:hrs-comparison}}
\tablehead{
	 &
	\colhead{$T_{eff}$} &
	\colhead{$[\mbox{Fe}/\mbox{H}]$} &
	\colhead{$\log{g}$} \\ 
	 & (K) & (dex) & (cm s$^{-1}$)
}
\startdata
S$^{4}$N (all stars) & $33 \pm 190$ & $0.02 \pm 0.15$ & $-0.04 \pm 0.35$ \\
CFLIB (dwarfs)\tablenotemark{a} & & & \\
CFLIB (giants)\tablenotemark{a} & & & \\
CFLIB (all stars) & & &
\enddata
\tablenotetext{a}{For this comparison, we separate giants and dwarfs at $\log{g} = 3.5$ dex.}
\end{deluxetable}

% Discuss CFLIB comparison values and any systematic offsets between dwarfs/giants and perhaps MPG/MPD/MRG/MRD

\subsection{Globular Clusters}
\label{sec:globular-clusters}
The CFLIB and S$^4$N spectral libraries provide an excellent way to verify our analysis technique against atmospheric parameters determined by excitation and equilibrium balances. Although they were resampled and convolved to match our observed conditions, ultimately they were not observed on the AAT. As a final verification of our technique we observed red giant stars in multiple globular clusters to compare kinematics and stellar parameters.

Observed globular clusters are tabulated in Table \ref{tab:globular-clusters} with their relevant properties \citep{Harris}.

% median metallicities

% tabulated values of stuff employed (age, feh, etc)
% name (alt name), Age, v_helio, harris v_helio, feh, harris feh, No. stars

\begin{deluxetable}{lcccccc}
\tablecolumns{1}
\tablewidth{\columnwidth}
\tablecaption{Observed cluster median metallicities and kinematics.\label{tab:globular-clusters}}
\tablehead{
	\colhead{Cluster} &
	\colhead{Age} &
	\colhead{$V_{helio,ARC}$} &
	\colhead{$V_{helio,HARRIS}$} &
	\colhead{feh} &
	\colhead{feh} &
	\colhead{vmvhb} 
}
\startdata
\enddata
\tablenotetext{a}{For this comparison, we separate giants and dwarfs at $\log{g} = 3.5$ dex.}
\end{deluxetable}

% isochrones and points for every cluster

\subsection{The effects of shot noise}
\label{sec:shot-noise}
We have employed the S$^4$N library to examine the affect of Poisson shot noise on our derived stellar parameters. All S$^4$N spectra were analysed with four levels of S/N: 15, 30, 50 and 100 px$^{-1}$. The $1\--\sigma$ dispersions in derived stellar parameters are illustrated in Figure \ref{fig:shot-noise} and tabulated in Table \ref{tab:shot-noise}. No significant biases in derived stellar parameters were found with increased Poisson noise.

\begin{deluxetable}{cccc}
\tablecolumns{1}
\tablewidth{0pt}
\tabletypesize{\scriptsize}
\tablecaption{Dispersion in derived stellar parameters for S$^4$N stars with artificial shot noise.\label{tab:shot-noise}}
\tablehead{
	\colhead{S/N} &
	\colhead{$T_{eff}$} &
	\colhead{$\log{g}$} &
	\colhead{$[\mbox{M}/\mbox{H}]$} \\ 
	(px$^{-1}$) & (K) & (dex) & (dex)
}
\startdata
100 & 0 & 0 & 0 \\
50 & 0 & 0 & 0 \\
30 & 0 & 0 & 0 \\
15 & 0 & 0 & 0 
\enddata
\end{deluxetable}

% confident that our analysis is valid
% confident down to a certain SNR, at which point below this value we will not use derived parameters?

The analysis procedure described in S\ref{sec:calibration} was applied to all 10,232 spectroscopic observations.

\section{Data Quality}

We carefully inspected both beam of every normalised observation and its best-fitting synthetic fit prior to interpreting our results. During this process we uncovered 2 typical carbon stars and identified sub-optimal normalisation for 35 objects. There were 35 spectroscopic binaries were discarded from further analysis, as well as 832 other observations with indecipherable signal. Observations with incorrect continuum determination were  interactively re-normalised using the same process described in \S\ref{sec:normalisation} with slightly varied constraints on sigma clipping and spline knot placement.

Stellar parameters derived from observations with a S/N below 20 are uncertain and have not been published. An upper limit on $\chi^2$ has not been placed. However, we visually inspected every observation with a $\chi^2$ value greater than FOUR?. These unusually high $\chi^2$ values are ubiquitously attributable to bad columns in our comparison regions. After inspecting our data for quality assurance, our distilled sample of results is 9,820 K-type stars \--- roughly X\% were excluded.

% SNR vs V_err? 
% SNR vs chi^2
% fibre number and chi^2 to illustrate effect of bad columns?

\section{Results}
\label{sec:results}

\section{Discussion}
\label{sec:discussion}

\section{Conclusions}
\label{sec:conclusions}

\section{Acknowledgements}
\label{sec:acknowledgements}

ARC is pleased to acknowledge the financial support through the Australian Research Council Laureate Fellowship 0992131.  SK and GDaC acknowledge the financial support from the Australian Research Council through Discovery Program DP0878137.

This publication makes use of data products from the Two Micron All Sky Survey, which is a joint project of the University of Massachusetts and the Infrared Processing and Analysis Center/California Institute of Technology, funded by the National Aeronautics and Space Administration and the National Science Foundation.

Funding for the SDSS and SDSS-II has been provided by the Alfred P. Sloan Foundation, the Participating Institutions, the National Science Foundation, the U.S. Department of Energy, the National Aeronautics and Space Administration, the Japanese Monbukagakusho, the Max Planck Society, and the Higher Education Funding Council for England. The SDSS Web Site is http://www.sdss.org/.

The SDSS is managed by the Astrophysical Research Consortium for the Participating Institutions. The Participating Institutions are the American Museum of Natural History, Astrophysical Institute Potsdam, University of Basel, University of Cambridge, Case Western Reserve University, University of Chicago, Drexel University, Fermilab, the Institute for Advanced Study, the Japan Participation Group, Johns Hopkins University, the Joint Institute for Nuclear Astrophysics, the Kavli Institute for Particle Astrophysics and Cosmology, the Korean Scientist Group, the Chinese Academy of Sciences (LAMOST), Los Alamos National Laboratory, the Max-Planck-Institute for Astronomy (MPIA), the Max-Planck-Institute for Astrophysics (MPA), New Mexico State University, Ohio State University, University of Pittsburgh, University of Portsmouth, Princeton University, the United States Naval Observatory, and the University of Washington.

\bibliographystyle{apj}
\bibliography{bibliography}

\end{document}

### 2012-05-28 2011-sgr/figures/besancon.py

@@ -1,0 +1,131 @@
+import matplotlib.pyplot as plt
+import glob
+import atpy
+from numpy import *
+import re
+import ephem
+
+filenames = glob.glob('*.resu')
+
+bandwidth = 10.0
+x = arange(-400., 400., 1.)
+
+
+besanconVgsr = []
+color = []
+mag = []
+VgsrCorrection = 0.0
+for filename in filenames:
+    
+    datafile = open(filename, 'r')
+    content = datafile.readlines()
+    
+    for line in content:
+        if re.search('a\(2000\.0\)\s+:\s+', line):
+            
+            # could be done better, but fuck it
+            a, b, c = line.split(':')
+            b, a = b.split('Step')
+            
+            ra1, ra2 = b.split('-')
+            ra1 = ra1.replace('h', ':').replace('m', ':').strip(' s').replace(' ', '')
+            ra2 = ra2.replace('h', ':').replace('m', ':').strip(' s').replace(' ', '')
+            ra1 = ephem.Equatorial(ra1, 0., epoch=ephem.J2000)
+            ra2 = ephem.Equatorial(ra2, 0., epoch=ephem.J2000)
+            
+            ra = 0.5*(ra2.ra - ra1.ra) + ra1.ra
+            
+            c, d = c.split('Step')
+            dec1, dec2 = c.split(' - ')
+            
+            dec1 = dec1.replace('d', ':').replace('m', ':').strip(' s').replace(' ', '')
+            dec2 = dec2.replace('d', ':').replace('m', ':').strip(' s').replace(' ', '')
+            dec1 = ephem.Equatorial(0., dec1, epoch=ephem.J2000)
+            dec2 = ephem.Equatorial(0., dec2, epoch=ephem.J2000)
+            
+            dec = 0.5*(dec2.dec - dec1.dec) + dec1.dec
+            
+            coords = ephem.Equatorial(ra, dec, epoch=ephem.J2000)
+            galactic = ephem.Galactic(coords, epoch=1958)
+            l, b = [degrees(_) for _ in [galactic.long, galactic.lat]]
+
+            # Get heliocentric and galactocentric corrections (Website stefan gave me)
[…]

### 2012-05-28 2011-sgr/figures/carbonstarcolor.py

@@ -1,0 +1,85 @@
+
+
+import matplotlib.pyplot as plt
+from matplotlib.patches import Circle
+import Image
+from numpy import linspace, array
+plt.rcParams['text.usetex'] = True
+plot = Image.open('carbonstars.jpg')
+dpi = plt.rcParams['figure.dpi']
+figsize = plot.size[0]/float(dpi), plot.size[1]/float(dpi)
+
+
+textsize = 16
+labelsize = 15
+
+xnum, ynum = 6, 4 #original bounds of the image
+# flipping it around
+xnum, ynum = 4, 6
+
+plt.close('all')
+fig = plt.figure(figsize=figsize)
+fig.subplots_adjust(left=0.1, bottom=0.05, right=0.95, top=0.95)
+
+subplot = fig.add_subplot(111)
+#subplot.set_frame_on(False)
+#subplot.set_axis_off()
+subplot.imshow(plot, origin='lower', aspect='auto')
+
+
+xbound, ybound = subplot.get_xbound(), subplot.get_ybound()
+xscale, yscale = (xbound[1]-xbound[0])/float(xnum), (ybound[1]-ybound[0])/float(ynum)
+
+subplot.set_xticks(linspace(xbound[0], xbound[1], xnum + 1))
+labels = ['']
+labels.extend(range(1, xnum+1))
+
+subplot.set_xticklabels(map(str, labels))
+
+subplot.xaxis.set_tick_params(labelsize=labelsize)
+
+
+subplot.set_yticks(linspace(ybound[0], ybound[1], ynum+1))
+labels = ['']
+labels.extend(range(1, ynum+1))
+subplot.set_yticklabels(map(str, labels))
+subplot.yaxis.set_tick_params(labelsize=labelsize)
+#subplot.set_xlabel(r'\textit{u} $-$ \textit{g}', fontsize=textsize)
+#subplot.set_ylabel(r'\textit{g} $-$ \textit{r}', fontsize=textsize)
+# flipping it around
+subplot.set_xlabel(r'$(g - r)_o$', fontsize=textsize)
+subplot.set_ylabel(r'$(u - g)_o$', fontsize=textsize)
+
+
+#Add our carbon stars
+
+stars = [
+            [1.096, 0.538],
+            [1.668, 0.725],
+            [1.789, 0.799],
+            [1.428, 0.641],
+            [1.719, 0.728]
+        ]
+
+# flipping it around
+stars = [[b,a] for a, b in stars]
+
[…]

### 2012-05-28 2011-sgr/figures/cmd.py

@@ -1,0 +1,93 @@
+#!/usr/bin/python
+
+
+from matplotlib import pyplot as plt
+from matplotlib import rc as rc
+from matplotlib.patches import Polygon
+import atpy, glob
+from numpy import loadtxt, log10
+
+g_o = []
+gmi_o = []
+
+
+data = []
+
+SDSS_files = glob.glob('SDSS_*.xml')
+
+for SDSS_file in SDSS_files:
+    table = atpy.Table(SDSS_file, verbose=False)
+    
+    # g_o
+    [g_o.append(item) for item in table.data['g']]
+    
+    # (g - i)_o
+    colour = table.data['g'] - table.data['i']
+    [gmi_o.append(item) for item in colour]
+    
+
+# Plot it up
+fig = plt.figure()
+fig.subplots_adjust(left=0.1, right=0.95, top=0.95, bottom=0.1)
+ax = fig.add_subplot(111)
+
+fontsize = 14
+labelsize = 14.5
+ax.scatter(gmi_o, g_o, color='k', s=1, alpha=0.10)
+
+# load up the isochrone data
+isochrone_m1p5 = loadtxt('dartmouth_12gr_fehm15_alpha0.isochrone', usecols=(6,8))
+isochrone_m0p5 = loadtxt('dartmouth_12gr_fehm05_alpha0.isochrone', usecols=(6,8))
+
+d = 40 # kpc
+gmi = isochrone_m0p5[:, 0] - isochrone_m0p5[:, 1]
+g = -5 + 5*log10(d*10**3) + isochrone_m0p5[:,0]
+
+ax.scatter(gmi, g, marker='o', edgecolor='#CE040F', facecolor='None', s=20, zorder=5, label='Dartmouth isochrone (12 Gyr, $r_\odot = 40$ kpc, [Fe/H] = -0.5)')
+#ax.text(1.5, 16, '12 Gyr Isochrone at $r_\odot = 45$ kpc with [Fe/H] $= -1.5$', color='g', horizontalalignment='left', fontsize=labelsize)
+
+gmi = isochrone_m1p5[:, 0] - isochrone_m1p5[:, 1]
+g = - 5 + 5*log10(d*10**3) + isochrone_m1p5[:,0]
+
+ax.scatter(gmi, g, marker='o', edgecolor='#2165BF', facecolor='None', s=20, zorder=5, label='Dartmouth isochrone (12 Gyr, $r_\odot = 40$ kpc, [Fe/H] = -1.5)')
[…]

### 2012-05-28 2011-sgr/figures/correct_vhb.py

@@ -1,0 +1,34 @@
+import atpy, os
+
+table = atpy.Table('combined.xml', verbose=False)
+
+vgsr_index = table.columns.keys.index('V_{gsr} (fxcor)')
+
+
+update_data = table.data
+Vhb = 17.135
+Vhberr = 0.165
+RRLMv = +0.69
+
+for row in update_data:
+    if row[vgsr_index] > 0.:
+        
+        
+        row[table.columns.keys.index('V_{hb}')] = Vhb
+        
+        row[table.columns.keys.index('V_{hb,err}')] = Vhberr
+        row[table.columns.keys.index('D')] = 10**((Vhb - RRLMv  + 5 - row[table.columns.keys.index('E(B-V)')]*2.682)/5.) * 10**(-3)
+
+        row[table.columns.keys.index('D_{err}')] = 10**((Vhb + Vhberr - RRLMv + 5 - row[table.columns.keys.index('E(B-V)')]*2.682)/5.) * 10**(-3)
+        row[table.columns.keys.index('V-V_{HB}')] = row['V (Jester 2005)'] - Vhb
+        row[table.columns.keys.index('[Fe/H] (Battaglia)')] = -2.81 + 0.44*(row['EW_{CaT2}'] + row['EW_{CaT3}'] + 0.64*(row['V (Jester 2005)'] - Vhb))
+        row[table.columns.keys.index('[Fe/H]_{err} (Battaglia)')] = 0.16 + 0.04*(0.02*(row['V (Jester 2005)'] - (Vhb + Vhberr)))
+        
+        
+        
+        
+
+        
+        
+os.system('rm -f combined.xml') 
+table.write('combined.xml', verbose=False)

### 2012-05-28 2011-sgr/figures/dwarfgiant.py

@@ -1,0 +1,159 @@
+import atpy
+import pylab as plt
+from numpy import *
+import os
+from scipy import interpolate
+import matplotlib
+plt.rcParams['text.usetex'] = True
+
+def cmap_discretize(cmap, N):
+    """Return a discrete colormap from the continuous colormap cmap.
+    
+        cmap: colormap instance, eg. cm.jet. 
+        N: Number of colors.
+    
+    Example
+        x = resize(arange(100), (5,100))
+        djet = cmap_discretize(cm.jet, 5)
+        imshow(x, cmap=djet)
+    """
+
+    cdict = cmap._segmentdata.copy()
+    # N colors
+    colors_i = linspace(0,1.,N)
+    # N+1 indices
+    indices = linspace(0,1.,N+1)
+    for key in ('red','green','blue'):
+        # Find the N colors
+        D = array(cdict[key])
+        I = interpolate.interp1d(D[:,0], D[:,1])
+        colors = I(colors_i)
+        # Place these colors at the correct indices.
+        A = zeros((N+1,3), float)
+        A[:,0] = indices
+        A[1:,1] = colors
+        A[:-1,2] = colors
+        # Create a tuple for the dictionary.
+        L = []
+        for l in A:
+            L.append(tuple(l))
+        cdict[key] = tuple(L)
+    # Return colormap object.
+    return matplotlib.colors.LinearSegmentedColormap('colormap',cdict,1024)
+  
+
+def cmap_map(function,cmap):
+    """ Applies function (which should operate on vectors of shape 3:
+    [r, g, b], on colormap cmap. This routine will break any discontinuous     points in a colormap.
+    """
+    cdict = cmap._segmentdata
+    step_dict = {}
+    # Firt get the list of points where the segments start or end
+    for key in ('red','green','blue'):         step_dict[key] = map(lambda x: x[0], cdict[key])
+    step_list = sum(step_dict.values(), [])
+    step_list = array(list(set(step_list)))
[…]

### 2012-05-28 2011-sgr/figures/dwarfgiants_true.py

@@ -1,0 +1,171 @@
+
+import atpy
+import matplotlib
+import matplotlib.pyplot as plt
+from numpy import *
+from scipy import interpolate
+
+fontsize=15.
+from matplotlib import rc
+#rc('font',**{'family':'sans-serif','sans-serif':['Helvetica']})
+plt.rcParams['font.size'] = fontsize
+
+plt.rcParams['text.usetex'] = True
+#plt.rcParams['text.dvipnghack'] = True
+plt.close('all')
+
+
+def cmap_discretize(cmap, N):
+    """Return a discrete colormap from the continuous colormap cmap.
+    
+        cmap: colormap instance, eg. cm.jet. 
+        N: Number of colors.
+    
+    Example
+        x = resize(arange(100), (5,100))
+        djet = cmap_discretize(cm.jet, 5)
+        imshow(x, cmap=djet)
+    """
+
+    cdict = cmap._segmentdata.copy()
+    # N colors
+    colors_i = linspace(0,1.,N)
+    # N+1 indices
+    indices = linspace(0,1.,N+1)
+    for key in ('red','green','blue'):
+        # Find the N colors
+        D = array(cdict[key])
+        I = interpolate.interp1d(D[:,0], D[:,1])
+        colors = I(colors_i)
+        # Place these colors at the correct indices.
+        A = zeros((N+1,3), float)
+        A[:,0] = indices
+        A[1:,1] = colors
+        A[:-1,2] = colors
+        # Create a tuple for the dictionary.
+        L = []
+        for l in A:
+            L.append(tuple(l))
+        cdict[key] = tuple(L)
+    # Return colormap object.
+    return matplotlib.colors.LinearSegmentedColormap('colormap',cdict,1024)
+  
+  
+
+table = atpy.Table('combined.xml', verbose=False)
+
+subset = '(table.Candidates == True) & (-350. < table.Vgsr) & (table.Vgsr < 350.)'
+
+table = table.where(eval(subset))
+
+
+logg, feh, ewmg, gmi = loadtxt('synthetic.out', usecols=(2,3,4,6), unpack=True)
+
+giants_gmi = []
[…]

### 2012-05-28 2011-sgr/figures/ewmg_justification/analyse.py

@@ -1,0 +1,132 @@
+import glob, re
+from  numpy import *
+from scipy import interpolate, ndimage
+import matplotlib.pyplot as plt
+from pyraf import iraf
+import os
+
+
+def GKItoEPS(GKIfilename):
+    '''
+    Converts an outputted IRAF GKI file to an EPS file with the same base name and location
+    '''
+
+    # Remove all existing first
+    if glob.glob('sgi*.eps'): os.system('rm -f sgi*.eps')
+    
+    EPSfilename = GKIfilename[0:-3] + 'eps'
+    
+    # Generate the mosaic
+    iraf.gflush()
+    iraf.gkimosaic(input=GKIfilename, device='eps', nx=1, ny=1, interactive='no', fill='yes', output='', Stdout=1)
+    iraf.gflush()
+    EPSfiles = glob.glob('sgi*.eps')
+    
+    i = 0
+    while not len(EPSfiles):
+
+        if (i > 15):
+            iraf.gkimosaic(input=GKIfilename, device='eps', nx=1, ny=1, interactive='no', fill='yes', output='', Stdout=1)
+            iraf.gflush()
+            
+        EPSfiles = glob.glob('sgi*.eps')
+        i += 1
+
+    # File movements
+    os.system('mv ' + EPSfiles[0] + ' ' + EPSfilename)
+    os.system('rm -f ' + GKIfilename)
+    
+    return EPSfilename
+
+
+
+
+iraf.noao()
+iraf.onedspec()
+
+gauss_val = 2.938/2. # A/pix
+
+synWavelength = loadtxt('LAMBDA_R20.DAT')
+
+
+obsWavelength = loadtxt('../blue_giant.txt').transpose()[0]
+
+plt.close('all')
+spectrumFiles = glob.glob('*.ASC')
+
+data = []
+for spectrumFile in spectrumFiles:
+    
+    string = re.sub('[T|G|V]', ' ', spectrumFile).split()
+    Teff = float(string[0])
+    
+    if 'P' in string[1]:
+        logg, feh = string[1].replace('P', ' ').split()
+        
+        logg = float(logg)/10.
+        feh = float(feh)/10.
+    
+    elif 'M' in string[1]:
+        logg, feh = string[1].replace('M', ' ').split()
+        
+        logg = float(logg)/10.
+        feh = float(feh)/-10.
+        
+    
+    # load in the spectra
+    
+    flux = loadtxt(spectrumFile)
+    
[…]

### 2012-05-28 2011-sgr/figures/ewmg_justification/formatlist.py

@@ -1,0 +1,21 @@
+from numpy import loadtxt
+
+import os
+
+olddata = open('linelist.original', 'r')
+
+
+os.system('rm -f linelist.formatted')
+newdata = open('linelist.formatted', 'w')
+
+data = olddata.readlines()
+
+for line in data:
+    if not line.startswith('-'):
+
+        line = line.split()
+        newdata.write("  %4.3f    %s     %1.3f    %1.3f\n" % (float(line[0])*10., line[2][0:5]+'0', float(line[5]), float(line[1]),))
+
+newdata.close()
+olddata.close()
+

### 2012-05-28 2011-sgr/figures/ewmg_justification/gengrid.py

@@ -1,0 +1,6 @@
+
+from numpy import *
+
+teff_range = list(arange(3900, 5200, 100))
+logg_range = list(arange(0, 5, 1))
+feh_range = list(arange(-2.5, -0.5, 0.5))

### 2012-05-28 2011-sgr/figures/fehhist.py

@@ -1,0 +1,133 @@
+
+import matplotlib.pyplot as plt
+plt.rcParams['text.usetex'] = True
+from numpy import *
+import atpy
+
+
+filename = 'combined.xml'
+column = '[Fe/H] (Battaglia)'
+
+table = atpy.Table(filename, verbose=False)
+
+histData1 = []
+histData2 = []
+histData3 = []
+histData4 = []
+histData5 = []
+
+for item in table.data:
+    #if(item[column] > -3.0) and (item[column] < -0.5) and item['K-Giants'] and (-350. < item['V_{gsr} (fxcor)']) and (item['V_{gsr} (fxcor)'] < 0.):
+    if (item[column] > -3.0) and (item[column] < -0.5) and item['K-Giants'] and (-140. < item['V_{gsr} (fxcor)']) and (item['V_{gsr} (fxcor)'] < -30.):
+    #if (item[column] > -3.0) and (item[column] < -0.5) and item['K-Giants'] and (item['V_{gsr} (fxcor)'] > -300.):# (item['V_{gsr} (fxcor)'] < 0.0):
+    #iif (item['K-Giants']):
+        if (-120. < item['V_{gsr} (fxcor)']) and (item['V_{gsr} (fxcor)'] < -30.):
+            histData1.append(item[column])
+        else:
+            histData5.append(item[column])
+            
+        if (-54. < item['V_{gsr} (fxcor)']) and (item['V_{gsr} (fxcor)'] < -34.):
+            histData2.append(item[column])
+            
+        if (-91. < item['V_{gsr} (fxcor)']) and (item['V_{gsr} (fxcor)'] < -71.):
+            histData3.append(item[column])
+            
+        
+        histData4.append(item[column])
+            
+            
+rwidth = 0.90
+edgecolor = '#000000'
+facecolor = 'none'
+bins = arange(-2.6, -0.8, 0.20)
+
+
+plt.close('all')
+
+fig = plt.figure()
+
+ax1 = fig.add_subplot(211)
+
[…]

### 2012-05-28 2011-sgr/figures/gist-copy.py

@@ -1,0 +1,807 @@
+#!/usr/bin/python
+# *-* coding:utf-8 -*-
+# vim: set fileencoding=utf-8 :
+"""
+Generalized histogram python code
+
+Andy Casey - June 2010
+
+Create a generalized histogram given a TOPCAT ASCII file
+
+	
+Inputs:
+
+	None.
+	
+	Simply run 'python gen-histogram.py' or your python executable weapon of choice
+	then it will ask you what's needed.
+	
+	Tab completion will intuitively show you the expressions you can use.
+
+Outputs:
+
+	kernel.png
+	cdf.png
+	
+
+Notes:
+
+	Use typical python-like (engrish) expression for the logic expression.
+	
+	Examples of logic expression:
+	
+	1. 	(( EWMgH > 0 and sensible ) or ( EWMgH > 0 and HGHT1fx >= 0.7)) and interpMgH != 0
+	
+	2. 	my-giant-subset or my-giant-subset-2
+	
+	3. 	5 > EWMgH >= 4
+	
+	If your expression is invalid, it will tell you - it cannot be broken. If you give
+	it an expression that returns zero data items, it will completely ignore your
+	expression and use all rows in the file.
+	
+	Using logic expressions like this WON'T work:
+	
+	1. 	EWMgH>0 and l>32
+	
+	2. 	VGSR1 > 0 && EWCaT > 0
+	
+	Because the header items need to be words (separated by spaces), so 'EWMgH>0' won't
+	be recognized but 'EWMgH >0' is okay. And the ||, && logic isn't python-like, so
+	you'll have to use and/or instead.
+
+"""
+
+
+import os, glob, readline, atexit
+import random as rand
+from itertools import count, izip
+from numpy import *
+from matplotlib.pyplot import *
+from pylab import *
+#from matplotlib import rcParams
+#matplotlib.rcParams['text.usetex'] = True
+
+options = []
+
+# Tab completion
+def complete(text, state):
+	for option in options:
+		if option.startswith(text):
+			if not state:
+				return option
+			else:
+				state -= 1
+
+readline.parse_and_bind('tab: complete')
+readline.set_completer(complete)
+#' \t\n`~!@#$%^&*()-=+[{]}\\|;:\'",<>/?'
+readline.set_completer_delims(' \t\n`~!@#$%^&*=+[{]}\\|;:\'"<>/?')
+histfile = os.path.join(os.environ['HOME'], '.pyhist')
+try:
+	readline.read_history_file(histfile)
+except IOError:
[…]

### 2012-05-28 2011-sgr/figures/gistogram.py

@@ -1,0 +1,810 @@
+#!/usr/bin/python
+# *-* coding:utf-8 -*-
+# vim: set fileencoding=utf-8 :
+"""
+Generalized histogram python code
+
+Andy Casey - June 2010
+
+Create a generalized histogram given a TOPCAT ASCII file
+
+	
+Inputs:
+
+	None.
+	
+	Simply run 'python gen-histogram.py' or your python executable weapon of choice
+	then it will ask you what's needed.
+	
+	Tab completion will intuitively show you the expressions you can use.
+
+Outputs:
+
+	kernel.png
+	cdf.png
+	
+
+Notes:
+
+	Use typical python-like (engrish) expression for the logic expression.
+	
+	Examples of logic expression:
+	
+	1. 	(( EWMgH > 0 and sensible ) or ( EWMgH > 0 and HGHT1fx >= 0.7)) and interpMgH != 0
+	
+	2. 	my-giant-subset or my-giant-subset-2
+	
+	3. 	5 > EWMgH >= 4
+	
+	If your expression is invalid, it will tell you - it cannot be broken. If you give
+	it an expression that returns zero data items, it will completely ignore your
+	expression and use all rows in the file.
+	
+	Using logic expressions like this WON'T work:
+	
+	1. 	EWMgH>0 and l>32
+	
+	2. 	VGSR1 > 0 && EWCaT > 0
+	
+	Because the header items need to be words (separated by spaces), so 'EWMgH>0' won't
+	be recognized but 'EWMgH >0' is okay. And the ||, && logic isn't python-like, so
+	you'll have to use and/or instead.
+
+"""
+
+#import pdb
+import os, glob, readline, atexit
+import random as rand
+from itertools import count, izip
+from numpy import *
+from matplotlib.pyplot import *
+from pylab import *
+#from matplotlib import rcParams
+#matplotlib.rcParams['text.usetex'] = True
+
+options = []
+close('all')
+# Tab completion
+def complete(text, state):
+	for option in options:
+		if option.startswith(text):
+			if not state:
+				return option
+			else:
+				state -= 1
+
+readline.parse_and_bind('tab: complete')
+readline.set_completer(complete)
+#' \t\n`~!@#$%^&*()-=+[{]}\\|;:\'",<>/?'
+readline.set_completer_delims(' \t\n`~!@#$%^&*=+[{]}\\|;:\'"<>/?')
+histfile = os.path.join(os.environ['HOME'], '.pyhist')
+try:
[…]

### 2012-05-28 2011-sgr/figures/lawspatial.py

@@ -1,0 +1,364 @@
+#!/usr/bin/python
+
+import matplotlib.pyplot as plt
+import numpy as np
+import atpy
+import pdb
+from numpy import *
+
+from mpl_toolkits.axes_grid1.inset_locator import zoomed_inset_axes
+from mpl_toolkits.axes_grid1.inset_locator import mark_inset
+import matplotlib.patches as mpatches
+plt.rcParams['text.usetex'] = True
+
+modelFiles = ['prolate.dat', 'oblate.dat', 'spherical.dat', 'SgrTriax_DYN.dat']
+#modelFiles = ['SgrTriax_DYN.dat']
+textsize = 15
+labelsize = 14
+observations = atpy.Table('combined.xml', verbose=False)
+
+observedSpatialLimits = ['Sgr_lambda', 'Sgr_b']
+modelSpatialLimits = ['lambda', 'beta']
+spatialTolerances = [0.0, 0.0]
+xbounds = [250, 345]
+ybounds = [-30, 30]
+distbounds = [0, 60]
+inc = 15
+
+observedDataParameter = 'Vgsr'
+observedErrorParameter = 'Verr'
+modelParameter = 'vgsr'
+modelDistanceParameter = 'dist'
+modelMarkerParameter = 'Pcol'
+
+subsetLogic = '(observations.kgiants == True) & (-250. < observations.Vgsr) & (observations.Vgsr < 250.)'
+
+# Number of data points in x-dimension
+resolution = 5000
+
+
+# Generate the subset
+
+observationsSubset = observations.where(eval(subsetLogic)).data
+observedData = observationsSubset[observedDataParameter]
+observedError = observationsSubset[observedErrorParameter]
+
+# Calculate bandwidth and ranges
+
+# Bandwidth estimated using a Epanechnikov kernel
+epanechnikov = ((40*(np.pi)**0.5)/len(observationsSubset[observedDataParameter]))**(0.2)
+
+bandwidth = 10.0
+
+offset = 100.0
+x = np.linspace(min(observedData) - offset, offset + max(observedData), resolution)
+#x = np.linspace(min(xBound), max(xBound), resolution)
+#print "min, max", min(observedData), max(observedData)
+#pdb.set_trace()
+
+observedHistogram = np.zeros(len(x))
+
+spatialLimits = []
+for observedSpatialLimit in observedSpatialLimits:
[…]

### 2012-05-28 2011-sgr/figures/lawvelcompare.py

@@ -1,0 +1,512 @@
+#!/usr/bin/python
+
+import matplotlib.pyplot as plt
+import numpy as np
+import atpy
+from numpy import *
+from matplotlib.patches import Rectangle
+
+useColor = False
+
+modelFiles = ['prolate.dat', 'oblate.dat', 'spherical.dat', 'SgrTriax_DYN.dat']
+
+labelsize=10
+fontsize=11
+
+observations = atpy.Table('combined.xml', verbose=False)
+
+observedSpatialLimits = ['Sgr_lambda', 'Sgr_b']
+modelSpatialLimits = ['lambda', 'beta']
+spatialTolerances = [0.0, 0.0]
+
+observedDataParameter = 'Vgsr'
+observedErrorParameter = 'Verr'
+modelParameter = 'vgsr'
+modelDistanceParameter = 'dist'
+modelMarkerParameter = 'Pcol'
+
+subsetLogic = '(observations.kgiants == True) & (-250. < observations.Vgsr) & (observations.Vgsr < 250.)'
+
+# Number of data points in x-dimension
+resolution = 500
+
+xBound = [-400, 400]
+distBound = [0, 60]
+
+# Generate the subset
+
+observationsSubset = observations.where(eval(subsetLogic)).data
+observedData = observationsSubset[observedDataParameter]
+observedError = observationsSubset[observedErrorParameter]
+
+# Calculate bandwidth and ranges
+
+# Bandwidth estimated using a Epanechnikov kernel
+epanechnikov = ((40*(np.pi)**0.5)/len(observationsSubset[observedDataParameter]))**(0.2)
+
+bandwidth = 10.0
+#bandwidth = np.mean(observationsSubset[observedErrorParameter]) * epanechnikov
+
+offset = 100.0
+x = np.linspace(min(observedData) - offset, offset + max(observedData), resolution)
+x = np.linspace(min(xBound), max(xBound), resolution)
+
+
+#pdb.set_trace()
+
+observedHistogram = zeros(len(x))
+
+spatialLimits = []
+for observedSpatialLimit in observedSpatialLimits:
+    spatialLimits.append([min(observationsSubset[observedSpatialLimit]), max(observationsSubset[observedSpatialLimit])])
+
[…]

### 2012-05-28 2011-sgr/figures/spectra.py

@@ -1,0 +1,53 @@
+
+import matplotlib.pyplot as plt
+from numpy import loadtxt
+from mpl_toolkits.axes_grid1.inset_locator import inset_axes
+from matplotlib.offsetbox import OffsetImage, AnnotationBbox
+
+
+plt.close('all')
+
+fig = plt.figure()
+
+# Giant
+giantAxe = fig.add_subplot(211)
+wavelength, flux = loadtxt('blue_giant.txt', unpack=True)
+
+giantAxe.plot(wavelength, flux, 'k-')
+
+"""
+# FOR TESTING IMAGE ONLY - WE WANT imagebox TO RETURN our .EPS file from IRAF
+from matplotlib._png import read_png
+fn = get_sample_data("lena.png", asfileobj=False)
+arr_lena = read_png(fn)
+
+imagebox = OffsetImage(arr_lena, zoom=0.4)
+
+# END TEST
+#xys = (5150., 0.70)
+
+#giantAxeInset = AnnotationBbox(imagebox, xys, xybox=(5300., 0.9), xycoords='data', \
+#                  boxcoords='data', pad=0.)
+                  
+#giantAxe.add_artist(giantAxeInset)
+
+#giantAxeInset = inset_axes(giantAxe, width=1.0, height=3.0, loc=5, bbox_to_anchor=(0.8, 0.5), bbox_transform=giantAxe.transAxes)
+#giantAxeInset.set
+#giantAxeInset.imshow(arr_lena)
+"""
+
+dwarfAxe = fig.add_subplot(212)
+wavelength, flux = loadtxt('blue_dwarf.txt', unpack=True)
+dwarfAxe.plot(wavelength, flux, 'k-')
+dwarfAxe.set_xlabel(r'Wavelength (\AA{})', fontsize=14)
+dwarfAxe.set_ylabel('Counts')
+giantAxe.set_ylabel('Counts', fontsize=14)
+plt.setp(giantAxe.get_xticklabels(), visible=False)
+
+giantAxe.set_xlim(3630., 5650.)
+dwarfAxe.set_xlim(3630., 5650.)
+plt.draw()
+plt.savefig('spectra.eps')
+
+#giantAxeInset = inset_axes(giantAxe, width=5, height=1, loc=5) # Location 5 = on the right, 7 = center right
+

### 2012-05-28 2011-sgr/figures/velhist.py

@@ -1,0 +1,70 @@
+
+
+import matplotlib.pyplot as plt
+
+import atpy
+from numpy import *
+
+
+column = 'V_{gsr} (fxcor)'
+table = atpy.Table('multiple_observations.xml', verbose=False)
+
+
+
+column = 'Derived error ' + column
+
+plt.close('all')
+fig = plt.figure()
+"""
+ax1 = fig.add_subplot(121)
+
+binsize = 1
+groupSizes = table.data['GroupSize']
+for i, groupSize in enumerate(table.data['GroupSize']):
+    if groupSize < 0:
+        groupSizes[i] = 1
+    else: groupSizes[i] = int(groupSize)
+        
+ax1.hist(groupSizes, bins=max(groupSizes), range=[1, max(groupSizes) + 1], align='mid', rwidth=0.90, color='#666666')
+ax1.set_xlabel(r'Number of repeated observations')
+ax1.set_ylabel(r'Number of stars')
+    
+ax1.set_xticklabels(['', '1', '', '2', '', '3', '', '4', ''])
+
+"""
+
+ax = fig.add_subplot(111)
+binsize = 2.5 # km s
+range = [0, 20]
+
+bins = range[1]/binsize
+bins = ax.hist(table.data[column], bins=bins, range=range, align='mid', rwidth=0.90, color='#666666')
+ax.set_xlabel(r'Internal velocity error (km s$^{-1}$)')
+ax.set_ylabel('Number of observations')
+
+x = arange(0, 20, 0.01)
+variance = std(table.data[column])
+
+y = 1/sqrt(2*pi*variance**2) * exp((-x**2) / (2*variance**2))
+ 
+y = bins[0][0] * y / max(y)
+ax.plot(x, y, 'k--')
+
+
+from matplotlib.patches import FancyArrowPatch
+
+for i, _ in enumerate(y):
+    if bins[0][0]/2. > _:
+        break
+
+i = i - 1
+
+    
+arrow = FancyArrowPatch([0, bins[0][0]/2.], [x[i], bins[0][0]/2.], arrowstyle='<|-|>', mutation_scale=15., facecolor='k', edgecolor='k')
+ax.add_patch(arrow)
+
+plt.figtext((x[i]*2.)/ax.get_xbound()[1] - 0.07, (bins[0][0]/2.)/ax.get_ybound()[1], r'HWHM = %3.2f km s$^{-1}$' % x[i], color='k', horizontalalignment='left')
+
+plt.draw()
+
+fig.savefig('vel_error.eps')

### 2012-05-28 2011-sgr/figures/vivas-newberg-duffau.py

@@ -1,0 +1,148 @@
+
+
+import atpy
+import ephem
+import matplotlib.pyplot as plt
+fontsize=13
+vivas = atpy.Table('Vivas2008.xml', verbose=False)
+sirko = atpy.Table('Sirko2004a.vot', verbose=False)
+
+
+RRLs = vivas.where((6.5 < vivas.Dis) & (vivas.Dis < 9.5) & (-80 < vivas.Vgsr) & (vivas.Vgsr < -10))
+BHBs = sirko.where((6.5 < sirko.Dist) & (sirko.Dist < 10.5) & (-80 < sirko.Vgal) & (sirko.Vgal < -10) & (170 < sirko.RAJ2000) & (sirko.RAJ2000 < 215) & (-4 < sirko.DEJ2000) & (sirko.DEJ2000 < 4))
+
+plt.close('all')
+fig = plt.figure(figsize=(15.0, 4.8))
+ax = fig.add_subplot(111)
+plt.subplots_adjust(left=0.05, bottom=0.05, right=0.97, top=0.97, wspace=0.20, hspace=0.20)
+plt.rcParams['text.usetex'] = True
+#'font.size' : 10,
+#          'axes.labelsize' : 10,
+#          'font.size' : 10,
+#          'text.fontsize' : 10,
+#          'legend.fontsize': 10,
+#          'xtick.labelsize' : 8,
+#          'ytick.labelsize' : 8,
+plt.rcParams['font.size'] = 11
+plt.rcParams['axes.labelsize'] = 16
+plt.rcParams['text.fontsize'] = 12
+plt.rcParams['legend.fontsize'] = 11
+plt.rcParams['xtick.labelsize'] = 16
+plt.rcParams['ytick.labelsize'] = 16
+#fig.set_figheight(6.8125)
+#fig.set_figwidth(16.712499999999999)
+
+
+# Newberg 2007 SEGUE plates
+
+
+newbergPlates = [[300, 55], [288, 62]]
+area = 7.0 # SEGUE overview document on ADS
+radius = (area/pi)**0.5
+
+for newbergPlate in newbergPlates:
+
+    l, b = map(radians, newbergPlate)
+     
+    coords = ephem.Galactic(l, b, epoch='1958')
+    ra, dec = map(degrees, coords.to_radec())
+    
+    circle = plt.Circle((ra, dec), radius=radius, ec='#000000', fc='none', linestyle='dashed')
+
[…]

### 2012-05-28 2011-sgr/figures/vss-candidates.py

@@ -1,0 +1,284 @@
+import matplotlib.pyplot as plt
+import matplotlib.patches as patches
+import atpy
+from numpy import *
+import matplotlib
+import matplotlib.text as text
+from pylab import *
+from matplotlib.image import NonUniformImage, AxesImage
+from scipy import interpolate
+plt.rcParams['text.usetex'] = True
+plt.rcParams['text.fontsize'] = 13.
+plt.rcParams['font.size'] = 13.
+def cmap_discretize(cmap, N):
+    """Return a discrete colormap from the continuous colormap cmap.
+    
+        cmap: colormap instance, eg. cm.jet. 
+        N: Number of colors.
+    
+    Example
+        x = resize(arange(100), (5,100))
+        djet = cmap_discretize(cm.jet, 5)
+        imshow(x, cmap=djet)
+    """
+
+    cdict = cmap._segmentdata.copy()
+    # N colors
+    colors_i = linspace(0,1.,N)
+    # N+1 indices
+    indices = linspace(0,1.,N+1)
+    for key in ('red','green','blue'):
+        # Find the N colors
+        D = array(cdict[key])
+        I = interpolate.interp1d(D[:,0], D[:,1])
+        colors = I(colors_i)
+        # Place these colors at the correct indices.
+        A = zeros((N+1,3), float)
+        A[:,0] = indices
+        A[1:,1] = colors
+        A[:-1,2] = colors
+        # Create a tuple for the dictionary.
+        L = []
+        for l in A:
+            L.append(tuple(l))
+        cdict[key] = tuple(L)
+    # Return colormap object.
+    return matplotlib.colors.LinearSegmentedColormap('colormap',cdict,1024)
+  
+
+
+table = atpy.Table('combined.xml', verbose=False)
+
+# standard binning
+xbound = [-300., 300]
+xerr = 15.
+yerr = 0.28
+ybound = [-2.46, -0.3]
+
+# offset by half
+#xbound = [-307.5, 300]
+#xerr = 15.
+#yerr = 0.30
[…]

### 2012-05-29 2012-oss/draft-oss.tex
initial commit of OSS paper which includes V_helios, SNR, airmass in obs table

%!TEX TS-program = pdflatex
\documentclass{emulateapj}

\shorttitle{OSS on MIKE}
\shortauthors{Casey et al}

\begin{document}

\title{High Resolution Spectroscopic Analysis of Orphan Stream Giants}

\author{Andrew R. Casey\altaffilmark{1,2}, Stefan C. Keller\altaffilmark{1}, Frebel, Anna\altaffilmark{2}, Gary Da Costa\altaffilmark{1}, Elizabeth Maunder\altaffilmark{1}}
\altaffiltext{1}{Research School of Astronomy \& Astrophysics, Australian National University, Mount Stromlo Observatory, via Cotter Rd, Weston, ACT 2611, Australia}
\altaffiltext{2}{Massachusetts Institute of Technology, Kavli Institute for Astrophysics and Space Research,
77 Massachusetts Avenue, Cambridge, MA 02139, USA}

\begin{abstract}
\end{abstract}

\keywords{Galaxy: halo, structure --- Individual: Orphan Stream --- Stars: K-giants}

\section{Introduction}

\section{Observations and Data Analysis}

\begin{deluxetable*}{lcccccc}
\tablecolumns{2}
\tabletypesize{\scriptsize}
\tablecaption{Observed Targets\label{tab:observed-targets}}
\tablehead{
	\colhead{Star} &
	\colhead{$\alpha$} &
	\colhead{$\delta$} &
	\colhead{Air mass} &
	\colhead{S/N\tablenotemark{a}} &
	\colhead{$V_{\mbox{helio}}$} &
	\colhead{Comment} \\
 & (J2000) & (J2000) & & (px$^{-1}$) & (km s$^{-1}$) &
}
\startdata
HD 136316 & 15 22 17.2 & $-$53 14 13.9 & 1.118 & 335 & $-38.21 \pm 1.09$ & \\
HD 141531 & 15 49 16.9 & 09 36 42.5 & 1.309 & 280 & $2.63 \pm 1.02$ & \\
HD 142948 & 16 00 01.6 & $-$53 51 04.1 & 1.107 & 271 & $30.26 \pm 0.87$ & \\
HD 41667 & 06 05 03.7 & $-$32 59 36.8 & 1.005 & 272 & $297.79 \pm 1.72$ & \\
HD 44007 & 06 18 48.6 & $-$14 50 44.2 & 1.033 & 239 & $163.41 \pm 1.25$ & \\
HD 47536 & 06 37 47.7 & $-$32 20 20.1 & 1.002 & 257 & $78.87 \pm 1.21$ & \\
HD 76932 & 08 58 44.2 & $-$16 07 54.2 & 1.158 & 289 & $119.18 \pm 1.18$ & \\
HD 84903 & 09 47 19.3 & $-$41 27 04.9 & 1.260 & 294 & $77.65 \pm 1.41$ & \\
HD 59984 & 07 32 05.7 & $-$08 52 56.1 & 1.111 & 402 & $55.74 \pm 0.53$ & \\
HD 60060 & 07 29 59.6 & $-$52 39 04.3 & 1.127 & 414 & $25.60 \pm 1.08$ & \\
HD 60228 & 07 30 30.8 & $-$54 23 58.6 & 1.139 & 338 & $48.58 \pm 1.67$ & \\
OSS TGT 1    & 10 46 50.6 & $-$00 13 17.9 & 1.363 & 48 & $218.15 \pm 1.72$ & \\
OSS TGT 2    & 10 47 17.8 &    00 25 06.9 & 1.995 & 59 & $222.16 \pm 1.28$ & \\
OSS TGT 3    & 10 47 30.3 & $-$00 01 22.6 & 1.156 & 49 & $226.35 \pm 1.27$ & \\
OSS TGT 4    & 10 49 08.3 &    00 01 59.3 & 1.881 & 48 & $227.50 \pm 2.05$ & Poor seeing.\\
OSS TGT 5    & 10 50 33.7 &    00 12 18.3 & 1.295 & 31 & $249.01 \pm 2.58$ & Poor seeing. \\
HR 6141  & 16 30 12.3 & $-$25 06 52.0 & 1.003 & 406 & - & Telluric std.

\enddata
\tablenotetext{a}{S/N measured at 600 nm for each target.}
\end{deluxetable*}

% HDs 59984, 76932, 136316, 84903, 44007, 142948
% OS 2,4,5,6,8 (file name convention) here is OS 1,2,3,4,5

\subsection{Target Selection and Observations}

\subsection{Telluric Absorption Correction}

We observed the spectroscopic white dwarf HR6141 on March 15th, 2011 with the same slit configuration. The airmass during during this observation was 1.003. We assume all detected absorption lines in this spectrum are atmospheric, except for H$\alpha$. Continuum and absorption features in each echelle order were identified by eye and the spectrum was normalised using cubic splines with defined knot spacings. Overlapping echelle orders were stitched together and the normalised telluric template was interpolated onto the wavelength array for our observed stars. Each stellar spectrum was corrected by the normalised template adjusted by the ratio of the air masses, following the Beer-Lambert law:

\begin{equation}
d = \frac{s}{t^{X_{(obs)}/X_{(tel)}}}
\end{equation}

\subsection{Radial Velocities}
We measured radial velocities for every target by cross-correlating each telluric-divided observed spectrum with a synthetic template of $T_{eff} = 4500$ K, $\log{g} = 2.5$, [Fe/H] = -1.5, and [$\alpha$/Fe] = 0.0 over the wavelength region $845$ nm $< \Lambda < 870$ nm. Observed spectra were shifted to rest frame for line measurements. A number of radial velocity and halo standards were observed during this program, and our heliocentric velocities agree excellently with literature values.

\subsection{Line Measurements}

\subsection{Stellar Parameters}

\subsubsection{Effective Temperature}

\subsubsection{Surface Gravity}

\subsection{Uncertainty Analysis}

\section{Abundances}

\section{Discussion}

\section{Results}

\section{Conclusions}

\end{document}

### 2012-07-24 2012-oss/draft-oss.tex
updated

@@
 
+\subsection{Observations}
+
 \begin{deluxetable*}{lcccccc}
@@
 	\colhead{Air mass} &
+	\colhead{Seeing} &
 	\colhead{S/N\tablenotemark{a}} &
@@
 	\colhead{Comment} \\
- & (J2000) & (J2000) & & (px$^{-1}$) & (km s$^{-1}$) &
+ & (J2000) & (J2000) & & (") & (px$^{-1}$) & (km s$^{-1}$) &
 }
 \startdata
-HD 136316 & 15 22 17.2 & $-$53 14 13.9 & 1.118 & 335 & $-38.21 \pm 1.09$ & \\
-HD 141531 & 15 49 16.9 & 09 36 42.5 & 1.309 & 280 & $2.63 \pm 1.02$ & \\
-HD 142948 & 16 00 01.6 & $-$53 51 04.1 & 1.107 & 271 & $30.26 \pm 0.87$ & \\
-HD 41667 & 06 05 03.7 & $-$32 59 36.8 & 1.005 & 272 & $297.79 \pm 1.72$ & \\
-HD 44007 & 06 18 48.6 & $-$14 50 44.2 & 1.033 & 239 & $163.41 \pm 1.25$ & \\
-HD 47536 & 06 37 47.7 & $-$32 20 20.1 & 1.002 & 257 & $78.87 \pm 1.21$ & \\
-HD 76932 & 08 58 44.2 & $-$16 07 54.2 & 1.158 & 289 & $119.18 \pm 1.18$ & \\
-HD 84903 & 09 47 19.3 & $-$41 27 04.9 & 1.260 & 294 & $77.65 \pm 1.41$ & \\
-HD 59984 & 07 32 05.7 & $-$08 52 56.1 & 1.111 & 402 & $55.74 \pm 0.53$ & \\
-HD 60060 & 07 29 59.6 & $-$52 39 04.3 & 1.127 & 414 & $25.60 \pm 1.08$ & \\
-HD 60228 & 07 30 30.8 & $-$54 23 58.6 & 1.139 & 338 & $48.58 \pm 1.67$ & \\
-OSS TGT 1    & 10 46 50.6 & $-$00 13 17.9 & 1.363 & 48 & $218.15 \pm 1.72$ & \\
-OSS TGT 2    & 10 47 17.8 &    00 25 06.9 & 1.995 & 59 & $222.16 \pm 1.28$ & \\
-OSS TGT 3    & 10 47 30.3 & $-$00 01 22.6 & 1.156 & 49 & $226.35 \pm 1.27$ & \\
-OSS TGT 4    & 10 49 08.3 &    00 01 59.3 & 1.881 & 48 & $227.50 \pm 2.05$ & Poor seeing.\\
-OSS TGT 5    & 10 50 33.7 &    00 12 18.3 & 1.295 & 31 & $249.01 \pm 2.58$ & Poor seeing. \\
-HR 6141  & 16 30 12.3 & $-$25 06 52.0 & 1.003 & 406 & - & Telluric std.
+HD 136316 & 15 22 17.2 & $-$53 14 13.9 & ? & 1.118 & 335 & $-38.21 \pm 1.09$ & \\
+HD 141531 & 15 49 16.9 & 09 36 42.5 & ? & 1.309 & 280 & $2.63 \pm 1.02$ & \\
+HD 142948 & 16 00 01.6 & $-$53 51 04.1 & ? & 1.107 & 271 & $30.26 \pm 0.87$ & \\
+HD 41667 & 06 05 03.7 & $-$32 59 36.8 & ? & 1.005 & 272 & $297.79 \pm 1.72$ & \\
+HD 44007 & 06 18 48.6 & $-$14 50 44.2 & ? & 1.033 & 239 & $163.41 \pm 1.25$ & \\
+HD 47536 & 06 37 47.7 & $-$32 20 20.1 & ? & 1.002 & 257 & $78.87 \pm 1.21$ & \\
+HD 76932 & 08 58 44.2 & $-$16 07 54.2 & ? & 1.158 & 289 & $119.18 \pm 1.18$ & \\
+HD 84903 & 09 47 19.3 & $-$41 27 04.9 & ? & 1.260 & 294 & $77.65 \pm 1.41$ & \\
+HD 59984 & 07 32 05.7 & $-$08 52 56.1 & ? & 1.111 & 402 & $55.74 \pm 0.53$ & \\
+HD 60060 & 07 29 59.6 & $-$52 39 04.3 & ? & 1.127 & 414 & $25.60 \pm 1.08$ & \\
+HD 60228 & 07 30 30.8 & $-$54 23 58.6 & ? & 1.139 & 338 & $48.58 \pm 1.67$ & \\
+OSS 1    & 10 46 50.6 & $-$00 13 17.9 & 0.8 & 1.363 & 48 & $218.15 \pm 1.72$ & \\
+OSS 2    & 10 47 17.8 &    00 25 06.9 & ? & 1.995 & 59 & $222.16 \pm 1.28$ & \\
+OSS 3    & 10 47 30.3 & $-$00 01 22.6 & 0.71 & 1.156 & 49 & $226.35 \pm 1.27$ & \\
+OSS 4    & 10 49 08.3 &    00 01 59.3 & ? & 1.881 & 48 & $227.50 \pm 2.05$ & Poor seeing.\\
+OSS 5    & 10 50 33.7 &    00 12 18.3 & ? & 1.295 & 31 & $249.01 \pm 2.58$ & Poor seeing. \\
+HR 6141  & 16 30 12.3 & $-$25 06 52.0 & ? & 1.003 & 406 & - & Telluric std.
 
@@
 
-\subsection{Telluric Absorption Correction}
-
-We observed the spectroscopic white dwarf HR6141 on March 15th, 2011 with the same slit configuration.
-The airmass during during this observation was 1.003.
-We assume all detected absorption lines in this spectrum are atmospheric, except for H$\alpha$.
-Continuum and absorption features in each echelle order were identified by eye and the spectrum was normalised using cubic splines with defined knot spacings.
-Overlapping echelle orders were stitched together and the normalised telluric template was interpolated onto the wavelength array for our observed stars.
-Each stellar spectrum was corrected by the normalised template adjusted by the ratio of the air masses, following the Beer-Lambert law:
-
-\begin{equation}
-d = \frac{s}{t^{X_{(obs)}/X_{(tel)}}}
-\end{equation}
+\subsection{Data Reduction}
+The data were reduced using the latest version of the MIKE pipeline outlined in \citet{Kelson;2003}.
+For comparison we also reduced our HD 59984 spectra using standard methods in \textsc{IRAF} and found no noteworthy difference between the reduced products.
+Individual frames for each object were co-added before analysis.
+We carefully normalised every echelle order using cubic splines.
+Overlapping normalised orders on each CCD were stitched together, such that a continuous normalised spectra from each CCD remains.
+We do not include line measurements that are susceptible to telluric absorption, so no telluric corrections were made.
 
 \subsection{Radial Velocities}
-We measured radial velocities for every target by cross-correlating each telluric-divided observed spectrum with a synthetic template of $T_{eff} = 4500$ K, $\log{g} = 2.5$, [Fe/H] = -1.5, and [$\alpha$/Fe] = 0.0 over the wavelength region $845$ nm $< \Lambda < 870$ nm.
-Observed spectra were shifted to rest frame for line measurements.
-A number of radial velocity and halo standards were observed during this program, and our heliocentric velocities agree excellently with literature values.
+We measured radial velocities for every target by cross-correlating each normalised red  spectrum with a synthetic template.
+Our synthetic template was generated in \textsc{MOOG}\footnotemark{a}\footnotetext{Sneden's website} using a \citet{Castelli-Kurucz;2004} model atmospheres with $T_{eff} = 4500$ K, $\log{g} = 2.5$, [Fe/H] = -1.5, [$\alpha$/Fe] = 0.0 and no convective overshoot.
+The line list of \citet{Kirby;et-al_2008} was employed to generate spectra between $845$ nm $< \Lambda < 870$ nm.
+Both the blue and red co-added, normalised frames were shifted to rest before equivalent width measurements.
+A number of radial velocity and halo standards were observed during this program, and our heliocentric velocities agree excellently with literature values (Table \ref{tab:observed-targets}).
 
@@
 \subsection{Stellar Parameters}
+
+HD59984 5750 K, 1.55 vt, 3.55 logg -0.95,+0.40,
+================================================
+Fe I EPS 6.52 +/- 0.16 (210 lines)
+Slope, Offset, Corr: 0.01, 6.53, 0.05
+
+Fe I REW
+Slope, Offset, Corr: 0.0, 6.55, 0.00
+
+Fe I lambda
+Slope, Offset, Corr: 3.84e-05, 6.35, 0.17
+
+Fe II EPS 6.53 +/- 0.18 (22 lines)
+
+Fe II REW
+Slope, Offset, Corr: 0.07, 6.94, 0.09
+
+Fe II lambda
+Slope, Offset, Corr: 1.41e-04, 5.91, 0.36
+
+OSS 2: JMK = 0.633
+4571.9947676752899 K using Alonso 1999 paper
+inspected all profiles + saved only Fe ones that were good in red + blue
+================================================
+4600 K, 1.85, 0.80, -1.77, 0.40
+
+Fe I: 5.73 +/- 0.14 (139 lines)
+
+Fe I EPS
+S, O, C: 0.00, 5.72, 0.01
+
+Fe I REW
+S, O, C: -0.03, 5.58, -0.04
+
+Fe I Lambda:
+S, O, C: 3.98e-05, 5.51, 0.21
+
+Fe II: 5.72 +/- 0.16 (21 lines)
+
+Fe II EPS: None
+
+Fe II REW S, O, C: 0.03, 5.84, 0.05
+
+Fe II Lambda: 2.1e-05, 5.58, 0.09
 

### 2012-07-24 2012-vod/draft.tex
updated vod

@@
 Substructures like the VOD and the Sgr tidal tails are excellent tracers of the galactic potential \citep{Law;et-al_2005, Casey;et-al_2012a}.
+
+%Carlin et al ha a table of previously detected substructures (velocities, distances, fehs)
 
@@
 
-We have validated our analysis technique with three different data sets: two high resolution spectroscopic libraries with exquisite S/N, and RGB stars in ten globular clusters observed on the AAT.
+We have validated our analysis technique with three different data sets.
+This includes two high resolution spectroscopic stellar libraries: the Indo-US library of Coude feed stellar spectra \citep[][hereafter CFLIB]{Valdes;et-al_2004}, and the Spectroscopic Survey of Stars in the Solar Neighbourhood \citep[][hereafter S$^{4}$N]{Allende_Prieto;et-al_2004}.
+These libraries sufficiently cover the spectral region covered by our observed configuration.
+As a further reference calibration, we observed AGB and RGB stars in ten globular clusters in our programme.
 
 \subsection{Spectroscopic Libraries}
-There is a growing number of high resolution spectroscopic libraries available for comparison, however few of them cover the spectral range covered by AAOmega's 1500V/1700D filter set.
 

### 2012-07-28 2012-oss/draft-oss.tex
stellar parameters for oss + alphas added

@@
 HR 6141  & 16 30 12.3 & $-$25 06 52.0 & ? & 1.003 & 406 & - & Telluric std.
-
 \enddata
@@
 We measured radial velocities for every target by cross-correlating each normalised red  spectrum with a synthetic template.
-Our synthetic template was generated in \textsc{MOOG}\footnotemark{a}\footnotetext{Sneden's website} using a \citet{Castelli-Kurucz;2004} model atmospheres with $T_{eff} = 4500$ K, $\log{g} = 2.5$, [Fe/H] = -1.5, [$\alpha$/Fe] = 0.0 and no convective overshoot.
+Our synthetic template was generated in \textsc{MOOG} using a \citet{Castelli-Kurucz;2004} model atmospheres with $T_{eff} = 4500$ K, $\log{g} = 2.5$, [Fe/H] = -1.5, [$\alpha$/Fe] = 0.0 and no convective overshoot.
 The line list of \citet{Kirby;et-al_2008} was employed to generate spectra between $845$ nm $< \Lambda < 870$ nm.
@@
 
-OSS 2: JMK = 0.633
+OSS 1:
+161.71091670000001 -0.2216389
+SDSS DR 8 closest source is 3.793" away, and 17.47 mag in g
+ugriz: 18.823 17.467 16.934 16.712 16.597
+No reddenning corrected for, Jester 2005 transformations
+UBVRI = 18.06255 17.88487 17.14253 16.68055 16.24855
+B -V = 0.74
+Estimating a [Fe/H] = -1.9 and using Alonso et al 1999 eq 4 yields 4986 K
+
+With the red arm only:
+5110 / 1.20 / 3.10 / -1.14 / 0.40
+(with [Fe/H] = -1.14, the estimated temp from photometry is 5014 K)
+
+Fe I Abundance 6.42 +/- 0.19 (106 lines)
+S, O, C: 0.00, 6.41, 0.01
+
+Reduced EW S, O, C: 0.10, 6.87, 0.08
+
+Lambda S, O, C: 9.41e-05, 5.89, 0.28
+
+Fe II Abundance: 6.44 +/- 0.17 (8 lines)
+
+Reduced EW S, O, C: -0.09, 6.01, -0.09
+
+Lamba S, O, C: 1.64e-04, 5.53, 0.53
+
+Wiith the red and blue, starting at 5000K, -1.9
+
+5070 / 1.6 / 2.9 / -1.4 / 0.40
+
+Fe I Abundance: 6.15 +/- 0.25 (117 lines)
+SOC: 0.01, 6.12, 0.03
+
+Reduced EW SOC: 0.00, 6.12, 0.00
+Lambda SOC: 1.41e-04, 5.42, 0.42
+
+Fe II Abundance: 6.14 +/- 0.19 (19 lines)
+
+Reduced EW SOC: -0.04, 5.95, -0.05
+Lambda SOC: 1.09e-04, 5.61, 0.41
+
+Followed from this (USING RED AND BLUE data) and excluded outliers.
+
+4040 / 1.4 / 2.8 / -1.2 / 0.40 ("FINAL" files) <-- doesn't quite fit on isochrone, but close-ish
+Fe I abundance: 6.24 +/- 0.16 (149 lines)
+SOC: 0.02, 6.18, 0.13
+REW SOC: 0.03, 6.39, 0.04
+Lambda SOC: 0.81e-05, 5.78, 0.38
+
+Fe II abundance: 6.19 +/- 0.16 (15 lines)
+REW SOC: 0.03, 6.33, 0.04
+Lambda SOC: 1.08e-04, 5.65, 0.46
+
+ALPHA ELEMENTS Mg, Si, Ca, Ti
+==============
+
+OSS 2: JMK = 0.633 (no reddenning correction)
 4571.9947676752899 K using Alonso 1999 paper
+SDSS (DR8) u g r i z -- searched at 161.8240417 0.4185833, found source 2.05" away
+18.063 16.252 15.479, 15.146, 14.950
+
 inspected all profiles + saved only Fe ones that were good in red + blue
@@
 
+=================================
+Incorporating isochrones in:
+4550 K / 1.85 / 0.8 / -1.80 / 0.40
+
+Fe I Abundance: 5.71 +/- 0.16 (112 lines)
+Fe I EPS S, O, C: 0.01, 5.66, 0.10
+
+Fe I REW S, O, C: -0.03, 5.54, -0.04
+
+Fe I Lambda: 8.01e-06, 5.66, 0.03
+
+Fe II Abundance: 5.75 +/- 0.10 (8 lines)
+
+Fe II REW S, O, C: 0.35, 7.52, 0.68
+
+Fe II Lambda = -1.29e-04, 6.48, -0.70
+
+Loaded in all local line list from OSS2/os_4_all_global_auto.moogew
+
+ALPHA ELEMENTS
+Ne, Mg, Si, S, Ar, Ca, Ti
+
+Ne I, II -- no lines present in line list
+
+Mg I: 5.90 +/- 0.10 (6 lines), Solar 7.60 +/- 0.04
+Inspected all six line profiles; they look perfect.
+SOC: 0.05, 5.74, 0.35 // 0.00, 5.93, 0.00 // 3.03e-05, 5.77, 0.15
+[Mg I/Fe] = 0.10 +/- 0.10
+
+Si
+5565 very small but clean (6 mA)
+4102 is great
+3095 is a bit blended
+Si I: 5.66 +/- 0.26 (3 lines), Solar 7.51 +/- 0.03
+Inspected the three lines we have, they don't look fantastic...  3095 could go..
+SOC -0.14, 6.14, -0.78 // 0.29, 7.12, 0.92
+[Si I/Fe] = -0.05 +/- 0.26
+
+S I, II -- no lines present in line list: they are mainly in the infrared
+
+Ar I, II -- no lines present in line list
+
+Ca I: 4.79 +/- 0.12 (17 lines), Solar 6.34 +/- 0.04
+Inspected all the lines I have; they all look reasonable. Outliers could be confidently excluded.
+SOC: // 0.48, 7.08, 0.77 // -9.21e-05, 5.30, -0.51
+[Ca I/Fe] = 0.25 +/- 0.12
+
+Ti I: 3.00 +/- 0.16 (20 lines), Solar 4.95 +/- 0.05
+Inspected all the lines, excluded some dodgey measurements and duplicates, then clipped outliers.
+SOC: // -0.04, 2.83, -0.04 // 6.68e-05, 2.69, 0.18
+[Ti I/Fe] = -0.15 +/- 0.16
+
+Ti II: 3.19 +/- 0.14 (23 lines), Solar 4.95 +/- 0.05
+Inspected all the lines, excluded some dodgey measurements & duplicates then clipped outliers.
+SOC: 0.00, 3.23, 0.01 // 0.22, 4.27, 0.28 // -4.71e-05, 3.44, -0.13
+[Te II/Fe] = 0.04 +/- 0.14
+
+Na I: 4.21 +/- 0.05 (3 lines), Solar 6.24 +/- 0.04
+Inspected all three line profiles; they look perfect.
+SOC: -0.06, 4.23, -0.96 // 0.11, 4.71, 0.95
+[Na I/Fe] = -0.23 +/- 0.05
+
+OSS 3: 161.8761667 -0.0229444
+Not in 2mass (3 arcsecond cone)
+SDSS  Closest point is 2.85 arcseconds away at 17.4 mag in g
+u g r i z (SDSS DR 8)
+18.881 17.400 16.748 16.497 16.316
+Using Alonso et al 1999 eq 4 relation, and Jester 2005 transformations:
+UBVRI = 18.13946 17.86428 17.00532 16.51173 16.05073
+BMV = 0.85895999999999972
+Tried inital guess of [Fe/H] as = -1.9 gives 4719 K, giving -1.7 gives 4735 K
+using -1.9 guess and starting at 4719 K
+
+Best so far (before excluding outliers)
+4800 K, 1.90, 1.70, -1.87, 0.40
+
+after outliers
+4810, 1.85, 1.70, -1.87, 0.40
+
+Fe I 5.68 +/- 0.18 (181 lines)
+Abundances
+S, O, C: 0.00, 5.67, 0.03
+
+Reduced EW
+S, O, C: -0.06, 5.38, -0.08
+
+Lambda S, O, C: 8.33e-05, 5.25, 0.34
+
+Fe II 5.67 +/- 0.23 (26 lines)
+
+Reduced EW S, O, C: 0.07, 6.00, 0.09
+
+Lambda S, O, C: 1.44e-04, 4.95, 0.40
+
+===============
+with isochrones
+4780 / 1.7 / 1.55 / -1.80 / +0.40
+
+Fe I abundance 5.74 +/- 0.13 (112 lines)
+S, O, C: 0.00 5.73 0.03
+Reduced EW SOC: 0.03 5.86 0.04
+Lambda SOC: 3.11e-05, 5.57, 0.13
+
+Fe II abundances 5.69 +/- 0.19 (8 lines)
+Reduced EW SOC: -0.14, 5.03, -0.16
+Lambda SOC: 1.73e-04, 4.75, 0.49
+
+OSS 4
+162.2845417 0.0331389
+In SDSS DR8 found closest 16.4 gmag star at 1.113 arcseconds away
+u g r i z
+17.935 16.440 15.770 15.465 15.299
+no redenning, jester transform, assume -1.9 feh and using B-V ~ 0.88
+Alonso et al 1999 eq 4
+initial start teff = 4693 K
+
+an emp???
+
+4550 /  1.9 / 0.8 / -2.7 / 0.4
+
+Fe I Abundance 4.75 +/- 0.19 (150 lines)
+S, O, C: 0.00, 4.76, 0.01
+
+REW S, O, C: 0.04, 4.95, 0.07
+
+Lambda S, O, C: 4.11e-06, 4.74, 0.01
+
+Fe II Abundance 4.78 +/- 0.16 (18 lines)
+
+REW S, O, C: -0.06, 4.51, -0.09
+
+Lambda S, O, C: 9.90e-05, 4.32, 0.33
+
+Using isochrones:
+
+4670 / 1.95 / 1.10 / -2.70 / +0.40
+Fe I Abundance 4.84 +/- 0.24 (168)
+-0.01, 4.88, -0.03
+0.01, 4.93, 0.02
+5e-5, 4.61, 0.15
+
+Fe II Abundance 4.87 +/- 0.21 (21)
+-0.01, 4.84, -0.01
+1.09e-04 4.37 0.27
+
+=============
+4580 K / 2.05 / 0.80 / -2.79 / +0.40
+( doesn't quite sit on the expected isochrone)
+
+Fe I abundance: 4.75 +/- 0.17 (128 lines)
+-0.01 / 4.77 / -0.05
+0.03 / 4.88 / 0.04
+9.62e-06 / 4.70 / 0.40
+
+Fe II abundance: 4.77 +/- 0.15 (15 lines)
+-0.01 / 4.69 / -0.02
+
+6.49e-05 / 4.44 / 0.15
+
+OSS 5
+162.6405417 0.2050833
+SDSS DR8 nearest target is 1.196" away at 18th magnitude in g
+ugriz = 19.628 17.997 17.338 17.065 16.908
+No reddenning correction and using Jester 2005:
+UBVRI = 18.85619 18.46401 17.59819 17.08062 16.59762
+bmv = 0.87
+
+Guessing [Fe/H] = -1.9 yields Teff = 4709 K
+Arbitrarily chosing lines only redward of 4400 A
+
+5200 / 2.0 / 2.9 / -0.95 / 0.40
+
+Fe I 6.60 +/- 0.22 (90 lines)
+0.00, 6.62, 0.01
+0.00, 6.65, 0.00
+9.2e-5, 6.12, 0.27
+
+Fe II 6.60 +/- 0.35 (17 lines)
+0.12, 7.14, 0.07
+9.81e-05, 6.09, 0.20
+
 \subsubsection{Effective Temperature}

### 2012-07-28 2011-sgr/figures/ewmg_justification/analyse.py
removed ew mg justification for 2011 Sgr paper

@@ -1,132 +1,0 @@
-import glob, re
-from  numpy import *
-from scipy import interpolate, ndimage
-import matplotlib.pyplot as plt
-from pyraf import iraf
-import os
-
-
-def GKItoEPS(GKIfilename):
-    '''
-    Converts an outputted IRAF GKI file to an EPS file with the same base name and location
-    '''
-
-    # Remove all existing first
-    if glob.glob('sgi*.eps'): os.system('rm -f sgi*.eps')
-    
-    EPSfilename = GKIfilename[0:-3] + 'eps'
-    
-    # Generate the mosaic
-    iraf.gflush()
-    iraf.gkimosaic(input=GKIfilename, device='eps', nx=1, ny=1, interactive='no', fill='yes', output='', Stdout=1)
-    iraf.gflush()
-    EPSfiles = glob.glob('sgi*.eps')
-    
-    i = 0
-    while not len(EPSfiles):
-
-        if (i > 15):
-            iraf.gkimosaic(input=GKIfilename, device='eps', nx=1, ny=1, interactive='no', fill='yes', output='', Stdout=1)
-            iraf.gflush()
-            
-        EPSfiles = glob.glob('sgi*.eps')
-        i += 1
-
-    # File movements
-    os.system('mv ' + EPSfiles[0] + ' ' + EPSfilename)
-    os.system('rm -f ' + GKIfilename)
-    
-    return EPSfilename
-
-
-
-
-iraf.noao()
-iraf.onedspec()
-
-gauss_val = 2.938/2. # A/pix
-
-synWavelength = loadtxt('LAMBDA_R20.DAT')
-
-
-obsWavelength = loadtxt('../blue_giant.txt').transpose()[0]
-
-plt.close('all')
-spectrumFiles = glob.glob('*.ASC')
-
-data = []
-for spectrumFile in spectrumFiles:
-    
-    string = re.sub('[T|G|V]', ' ', spectrumFile).split()
-    Teff = float(string[0])
-    
-    if 'P' in string[1]:
-        logg, feh = string[1].replace('P', ' ').split()
-        
-        logg = float(logg)/10.
-        feh = float(feh)/10.
-    
-    elif 'M' in string[1]:
-        logg, feh = string[1].replace('M', ' ').split()
-        
-        logg = float(logg)/10.
-        feh = float(feh)/-10.
-        
-    
-    # load in the spectra
-    
-    flux = loadtxt(spectrumFile)
-    
[…]

### 2012-07-28 2011-sgr/figures/ewmg_justification/formatlist.py

@@ -1,21 +1,0 @@
-from numpy import loadtxt
-
-import os
-
-olddata = open('linelist.original', 'r')
-
-
-os.system('rm -f linelist.formatted')
-newdata = open('linelist.formatted', 'w')
-
-data = olddata.readlines()
-
-for line in data:
-    if not line.startswith('-'):
-
-        line = line.split()
-        newdata.write("  %4.3f    %s     %1.3f    %1.3f\n" % (float(line[0])*10., line[2][0:5]+'0', float(line[5]), float(line[1]),))
-
-newdata.close()
-olddata.close()
-

### 2012-07-28 2011-sgr/figures/ewmg_justification/gengrid.py

@@ -1,6 +1,0 @@
-
-from numpy import *
-
-teff_range = list(arange(3900, 5200, 100))
-logg_range = list(arange(0, 5, 1))
-feh_range = list(arange(-2.5, -0.5, 0.5))

### 2012-07-28 2012-oss/draft-oss.tex
alpha elements for OSS1

@@
 
-4040 / 1.4 / 2.8 / -1.2 / 0.40 ("FINAL" files) <-- doesn't quite fit on isochrone, but close-ish
+5040 / 1.4 / 2.8 / -1.2 / 0.40 ("FINAL" files) <-- doesn't quite fit on isochrone, but close-ish
 Fe I abundance: 6.24 +/- 0.16 (149 lines)
@@
 
-ALPHA ELEMENTS Mg, Si, Ca, Ti
+ALPHA ELEMENTS Mg, Si, Ca, Ti <-> (12, 
 ==============
+
+Mg I: 6.56 +/- 0.10 (4 lines), Solar 7.60 +/- 0.04
+Inspected all four line profiles; they look perfect.
+SOC: // // 4.51e-05, 6.29, 0.29
+[Mg I/Fe] = 0.16 +/- 0.10
+
+Si I: 6.57 +/- 0.23 (4 lines), Solar 7.51 +/- 0.03
+Inspected all four line profiles; they all look great (one is 'reasonable')
+SOC: 0.04, 6.36, 0.22 // 0.17, 7.37, 0.28 // 7.75e-05, 6.11, 0.23
+[Si I/Fe] = 0.26 +/- 0.23
+
+Ca I: 5.48 +/- 0.14 (14 lines), Solar 6.34 +/- 0.04
+Inspected all lines; they all look good.
+SOC: // // 1.44e-04, 4.60, 0.70
+[Ca I/Fe] = 0.34 +/- 0.14
+
+Ti I: 3.73 +/- 0.15 (21 lines) Solar 4.95 +/- 0.05
+Inspected all lines; they all look good.
+SOC: // 0.36, 5.49, 0.42 // 2.94e-05, 3.59, 0.08
+[Ti I/Fe] = -0.02 +/- 0.15
+
+Ti II: 3.91 +/- 0.10 (25 lines) Solar 4.95 +/- 0.05
+SOC: -0.02, 3.91, -0.09 // 0.22, 4.93, 0.43 // -2.70e-05, 4.01, -0.10
+[Ti II/Fe] = 0.16 +/- 0.10
 

### 2012-07-29 2012-oss/draft-oss.tex
alpha elements in for all OSS TGTS

@@
 
-ALPHA ELEMENTS Mg, Si, Ca, Ti <-> (12, 
+ALPHA ELEMENTS Mg, Si, Ca, Ti
 ==============
@@
 
+FINAL (this was done blindly too because I actually thought I was analysing OSS4)
+=====
+4780 / 1.7 / 1.55 / -1.79 / +0.40 <--> fits well on isochrone, saved as "FINAL"
+
+Fe I abundance: 5.71 +/- 0.12 (154 lines)
+SOC: 0.00, 5.70, 0.04 // -0.03, 5.57, -0.05 // 3.21e-05, 5.55, 0.20
+
+Fe II abundance: 5.71 +/- 0.16 (20 lines)
+SOC: // 0.03, 5.84, 0.04 // 6.42e-05, 5.39, 0.25
+
+ALPHA ABUNDANCES Mg, Si, Ca, Ti
+================
+
+Mg I: 5.95 +/- 0.05 (5 lines), Solar 7.60 +/- 0.04
+I inspected all the lines and clipped outliers.
+SOC: -0.01, 5.95, -.18 // 0.11, 6.44, 0.84 // -9.34e-05, 6.40, -0.72
+[Mg I/Fe] = 0.14 +/- 0.05
+
+Si I: 6.25 +/- 0.05 (2 lines), Solar 7.51 +/- 0.03
+excluded no lines:
+5565 line is not present
+5701 line is present, blended and not measured by code -- I measured it by hand
+5772 line is not present
+The two lines we have look really good.
+After I measured the line at 5701 and put them in:
+Si I: 6.20 +/- 0.16 (3 lines), Solar 7.51 +/- 0.03
+SOC: -0.03, 6.25, -0.27 // 0.22, 7.25, 0.65 // -5.47e-05, 6.42, -0.26
+[Si I/Fe] = 0.48 +/- 0.16
+
+Ca I: 4.87 +/- 0.09 (18 lines), Solar 6.34 +/- 0.04
+I inspected all the lines and clipped outliers.
+SOC: // 0.15, 5.61, 0.30 // 3.62e-05, 4.66, 0.30
+[Ca I/Fe] = 0.32 +/- 0.09
+
+Ti I: 3.13 +/- 0.09 (23 lines), Solar 4.95 +/- 0.05
+I inspected all the lines + clipped outliers
+SOC: // -0.01, 3.10, -0.02 // -5.4e-06, 3.18, -0.02
+[Ti I/Fe] = -0.03 +/- 0.09
+
+Ti II: 3.36 +/- 0.09 (24 lines), Solar 4.95 +/- 0.05
+I inspected all the lines + clipped outliers
+SOC: -0.04, 3.42, -0.16 // 0.08, 3.74, 0.18 //-1.35e-05, 3.43, -0.06
+[Ti II/Fe] = 0.20 +/- 0.09
+
+Na: 4.42 +/- 0.07 (3 lines), Solar 6.24 +/- 0.04
+SOC: -0.07, 4.43, -1.00 // 0.15, 5.09, 0.99
+[Na I/Fe] = -0.03 +/- 0.07
+
 OSS 4
@@
 
+FINAL
 =============
@@
 
+FINAL WITH EXCLUSIONS
+=====================
+4580 K / 2.05 / 0.80 / -2.75 / +0.40
+
+Fe I abundance: 4.74 +/- 0.11 (89 lines)
+SOC: 0.00, 4.75, -0.05 // -0.01, 4.70, -0.02 // 9.19e-06, 4.70, 0.06
+
+Fe II abundance: 4.77 +/- 0.12 (13 lines)
+SOC: // 0.00, 4.74, -0.01 // 1.16e-04, 4.21, 0.34
+
+Saved as "FINAL" <-> adopting these values
+
+ALPHA ELEMENTS
+==============
+
+Mg I: 5.11 +/- 0.13 (7 lines), Solar 7.60 +/- 0.04
+Inspected all lines, kept good ones then removed two spurious outliers.
+SOC: -0.02, 5.14, -0.19 // -0.14, 4.44, -0.31 // 1.54e-04, 4.39, 0.74
+[Mg I/Fe] = 0.26 +/- 0.13
+
+Si I: 5.38 +/- 0.03 (3 lines), Solar 7.51 +/- 0.03
+Inspected all lines and removed one outlier.
+SOC: -0.01, 5.43, -0.72 // 0.02, 5.50, 0.54 // -2.42e-05, 5.50,-0.65
+[Si I/Fe] = 0.62 +/- 0.03
+
+Ca I: 3.75 +/- 0.09 (9 lines), Solar 6.34 +/- 0.04
+Inspected all lines as usual
+SOC: // // 2.84e-05, 3.60, 0.26
+[Ca I/Fe] = 0.16 +/- 0.10
+
+Na I: 3.69 +/- 0.04 (2 lines), Solar 6.24 +/- 0.04
+Inspected both lines (they were all that was measured) & they are very clean.
+SOC: // // //
+[Na I/Fe] = 0.20 +/- 0.04
+
+Ti I: 2.28 +/- 0.15 (13 lines), Solar 4.95 +/- 0.05
+Inspected lines as always; these lines were more difficult to measure than usual.
+SOC: // 0.09, 2.70, 0.14 // -1.08e-04, 2.75, -0.24
+[Ti I/Fe] = 0.08 +/- 0.15
+
+Ti II: 2.31 +/- 0.09 (24 lines), Solar 4.95 +/- 0.05
+SOC: 0.00, 2.31, -0.02 // 0.00, 2.32, 0.01 // 2.39e-05, 2.19, 0.12
+[Ti II/Fe] = 0.11 +/- 0.15
+
+Alphas saved as "ALPHA"
+
 OSS 5
@@
 Guessing [Fe/H] = -1.9 yields Teff = 4709 K
-Arbitrarily chosing lines only redward of 4400 A
+Arbitrarily chosing lines only redward of 4400 A because S/N shit.
 
-5200 / 2.0 / 2.9 / -0.95 / 0.40
+5200 / 2.0 / 2.9 / -0.95 / 0.40 (fits perfectly on the isochrone)
 
@@
 9.81e-05, 6.09, 0.20
+
+FINAL
+5250 / 1.85 / 3.00 / -0.80 / 0.40 (first perfectly on isochrone)
+
+Fe I: 6.68 +/- 0.18 (99 lines)
+-0.01, 6.72, -0.06
+0.00, 6.68, 0.00
+5.61e-05, 6.38, 0.19
+
+Fe II: 6.71 +/- 0.25 (14 lines)
+0.28, 8.07, 0.24
+5.55e-05, 6.42, 0.16
+
+USING THESE VALUES (saved as "results")
+
+NOTE: so because this spectra is so shitty i ignored all lines (Fe, alpha elements) blue ward of 4000 Angstroms EXCEPT for Silicon only because there are so few lines.
+
+ALPHA ELEMENTS
+==============
+
+Mg I: 6.70 +/- 0.15 (5 lines), Solar 7.60 +/- 0.04
+All inspected
+SOC: -0.05, 6.94, -0.61 // -1.48e-04, 7.49, -0.58
+[Mg I/Fe] = -0.10 +/- 0.15
+
+Na I: 5.17 +/- 0.13 (4 lines), Solar 6.24 +/- 0.04
+All inspected and look good.
+SOC: 0.11, 5.08, 0.96 // -0.36, 3.53, -0.97 // //
+[Na I/Fe] = -0.27 +/- 0.13
+
+Si I: 6.78 +/- 0.31 (4 lines), Solar 7.51 +/- 0.03
+Lines look okay, but spectrum is crappy.
+SOC: 0.12, 6.35, 0.59 // -0.07, 6.41, -0.14 // 1.92e-04, 5.82, 0.54
+[Si I/Fe] = 0.07 +/- 0.31
+
+Ca I: 5.77 +/- 0.12 (10 lines), Solar 6.34 +/- 0.04
+All lines inspected and look good.
+SOC: // // -1.49e-04, 6.68, -0.45
+[Ca I/Fe] = 0.23 +/- 0.12
+
+Ti I: 4.26 +/- 0.36 (15 lines), Solar 4.95 +/- 0.05
+Lines look good, excluded all outliers and it's still a bit crap. Lot of scatter!
+SOC: // 0.95, 8.88, 0.54 // 2.20e-04, 3.25, 0.24
+[Ti I/Fe] = 0.11 +/- 0.36
+
+Ti II: 4.28 +/- 0.19 (13 lines), Solar 4.95 +/- 0.05
+Lines are good; could have gotten rid of a few more outliers but chose not to.
+SOC: 0.04, 4.16, 0.13 // // 7.89e-05, 3.86, 0.16
+[Ti II/Fe] = 0.13 +/- 0.19
 

### 2012-08-04 2012-oss/draft-oss.tex
added a lot to the intro

--- 2012-07-28 2012-oss/draft-oss.tex
@@
 
-\shorttitle{OSS on MIKE}
+\usepackage{verbatim} % for comment blocks
+\usepackage{pdflscape} % landscape tables
+
+\shorttitle{First HRS Analysis on the Orphan Stream}
 \shortauthors{Casey et al}
@@
 
-\title{High Resolution Spectroscopic Analysis of Orphan Stream Giants}
+\title{The First High-Resolution Spectroscopic Analysis on the Orphan Stream}
 
 \author{Andrew R. Casey\altaffilmark{1,2}, Stefan C. Keller\altaffilmark{1}, Frebel, Anna\altaffilmark{2}, Gary Da Costa\altaffilmark{1}, Elizabeth Maunder\altaffilmark{1}}
-\altaffiltext{1}{Research School of Astronomy \& Astrophysics, Australian National University, Mount Stromlo Observatory, via Cotter Rd, Weston, ACT 2611, Australia}
+\altaffiltext{1}{Research School of Astronomy \& Astrophysics, Australian National University, Mount Stromlo Observatory, via Cotter Rd, Weston, ACT 2611, Australia; \email{arcasey@mso.anu.edu.au}}
 \altaffiltext{2}{Massachusetts Institute of Technology, Kavli Institute for Astrophysics and Space Research,
@@
 \begin{abstract}
+test
 \end{abstract}
@@
 
-\section{Observations and Data Analysis}
+% galactic structure, accretion, build up of galaxies
+In the last decade the importance of hierarchical merging for the formation of galaxies has become unambiguously clear.
+In $\Lambda$CDM cosmology, small clusters conglomerate together to form dwarf galaxies.
+If these dwarf galaxies become sufficiently close to larger galaxies, they begin infalling and tidal forces cause a stream of stars to be left in their wake.
+These disrupted stars accrete onto the Milky Way, contributing to a significant fraction of the halo \citet{Bell;et-al_2008}.
 
-\subsection{Observations}
+% how streams form
+% streams agree with lambda cdm
+% streams contribute a significant part to the halo
 
-\begin{deluxetable*}{lcccccc}
+% dominant streams have been identified by their kinematic signatures 
+  The Milky Way is the best laboratory to investigate the extent accretion plays in galaxy formation and evolution.
+Historically, the signatures of accretion events have been identified either through prominent stellar over-densities [citations needed] or by co-moving groups; numerous spatially coincident stars moving with the same velocity [citations needed].
+The kinematics of stars in streams allow us to reconstruct the orbital history of the host and place constraints on the Milky Way potential, including the shape and extent of dark matter in the Galaxy [citation needed].
+
+% wealth of data provided by SDSS, allowed orphan stream to be discovered independently
+With increasing all-sky survey data being made openly available, searching for stellar over-densities has become extremely efficient [cite koposov].
+Using simple color cuts in the SDSS DR5 [citation needed] data set, both \citet{Grillmair_2006} and \citet{Belokurov;et-al_2007} independently discovered the Orphan Stream as a coherent structure spanning over $60^\circ$ in the sky.
+The Orphan Stream is uniquely distinct from  other stellar streams uncovered in the halo.
+It has an extremely low surface brightness and is only $\approx2^\circ$ wide \--- which is significantly narrower than other structures found in the Field of Streams \citep{Belokurov;et-al_2006} like Sagittarius ($15^\circ$ wide; [citation needed]).
+Moreover, the Orphan Stream was aptly named by \citet{Belokurov;et-al_2007} because unlike most other streams, no associated host was found in the SDSS data set, and no existing known system has been reliably associated.
+The Orphan stream extends well past the celestial equator, outside of the SDSS footprint.
+Unfortunately the stream has a sufficiently low surface density \citet{Newberg;et-al_2010} found prevents it from being detected within the existing SuperCOSMOS survey \citep{Hambly;et-al_2001}.
+It is unlikely that this region will be adequately imaged until the SkyMapper telescope commences the Southern Sky Survey \citep{Keller;et-al_2007}.
+At least until then, it remains a orphaned stream without a parent system.
+
+  % Should I discuss the observational bias, e.g. that we need the smaller ones to really start to pinpoint down the MW potential?
+
+% orphan stream is aptly named and is unique to all other streams. the parent remains lost, although a lot of work has been put in to associating the stream
+In the absence of observational data to identify an undiscovered parent host, there has been much effort on associating the Orphan Stream with an existing Milky Way satellite [citations needed].
+Given the XX and XX, it is likely the parent host is a dwarf spheroidal galaxy [citations needed], although \citet{Grillmair_2006} predicts the host to be completely disrupted.
+In the search for an associated system, \citet{Belokurov;et-al_2007} first demonstrated that the Complex A, Ruprecht 106, and Palomar 1 all lie on the same great circle path of the Orphan stream, speculating some association between the four.
+
+% Let's deal with the Complex A controversy first
+A detailed analysis on the Orphan Stream orbit is required to examine any potential associations. Kinematics and/or proper motions are required to adequately determine an orbit.
+\citet{Belokurov;et-al_2007} listed admittedly two tenuous kinematic observations along the stream, one of which it later appears was erroneous.
+
+% talk about fellhauer
+
+Using these measurements \--- the best, and only at the time \--- and assuming Complex A and the Orphan Stream shared the same orbit, \citet{Jin;Lynden-Bell_2007} found a representative orbit to match observations.
+Unfortunately their predicted heliocentric velocities that were inconsistent with \citet{Fellhaur;et-al_2007} and later observations by \citet{Newberg;et-al_2010}.
+Moreover, distances estimated by \citet{Jin;Lynden-Bell_2007} were under-predicted by a factor of three.
+
+In contrast to these simulations, \citet{Sales;et-al_2007} using a X found an orbit which reproduced the velocities, positions and characteristics of the stream, but found no evidence of association with Complex A, or UMaII.
+Their findings indicate that the parent system is likely to be dark matter dominated, and have similar characteristics to some of the Milky Way dwarfs already known (XX, XX and XX).
+Only self-gravitating systems dominated by dark matter can survive sufficiently long enough to form a stream stretching $\approx55^\circ$ across the sky.
+
+% talk more about Sales
+
+As the SEGUE [acronym needed] data became available, \citet{Newberg;et-al_2010} employed a detailed selection method in order to identify BHB stars in the SDSS data sample.
+% blah blah blah
+
+% perhaps mention Sales et al explaining how low surface brightness streams cant be found without spectroscopic surveys
+
+More recently, \citet{Keller;et-al_2012} targeted FGK giants on the Southern end of the SDSS footprint.
+As the stream crosses the celestial equator it is closest to us and the surface brightness peaks, making it an ideal place to identify stream members.
+Using inclusive SDSS cuts they targeted hundreds of stars with medium resolution spectroscopy.
+By identifying likely stream giants based on kinematics and surface gravity estimates, they identified X likely Orphan Stream giants.
+In this paper we present a detailed chemical analysis on five of those members using high resolution spectroscopic data from the Magellan Clay telescope.
+Details regarding the observations are outlined in Section \ref{sec:observations}, followed by X.
+
+\section{Observations}
+We present high resolution follow-up observations using the Magellan Inamori Kyocera Echelle (MIKE) spectrograph.
+
+% details of the resolution that MIKE provides, etc
+
+\subsection{Target Selection}
+% this is double-up
+The Orphan Stream has an extremely low surface brightness [citations needed] of XX, and there is a well-described distance gradient along the Orphan stream \citep{Belokurov;et-al_2007,Newberg;et-al_2010}.
+Therefore the best place to identify stream members within the SDSS sky coverage is near the celestial equator where the stream is closest to us, right at the edge of the SDSS footprint.
+
+\subsection{High Resolution Observations}
+
+\begin{deluxetable*}{lccccccc}
 \tablecolumns{2}
@@
 	\colhead{Air mass} &
-	\colhead{Seeing} &
 	\colhead{S/N\tablenotemark{a}} &
@@
 	\colhead{Comment} \\
- & (J2000) & (J2000) & & (") & (px$^{-1}$) & (km s$^{-1}$) &
+ & (J2000) & (J2000) & & (px$^{-1}$) & (km s$^{-1}$) &
 }
 \startdata
-HD 136316 & 15 22 17.2 & $-$53 14 13.9 & ? & 1.118 & 335 & $-38.21 \pm 1.09$ & \\
-HD 141531 & 15 49 16.9 & 09 36 42.5 & ? & 1.309 & 280 & $2.63 \pm 1.02$ & \\
-HD 142948 & 16 00 01.6 & $-$53 51 04.1 & ? & 1.107 & 271 & $30.26 \pm 0.87$ & \\
-HD 41667 & 06 05 03.7 & $-$32 59 36.8 & ? & 1.005 & 272 & $297.79 \pm 1.72$ & \\
-HD 44007 & 06 18 48.6 & $-$14 50 44.2 & ? & 1.033 & 239 & $163.41 \pm 1.25$ & \\
-HD 47536 & 06 37 47.7 & $-$32 20 20.1 & ? & 1.002 & 257 & $78.87 \pm 1.21$ & \\
-HD 76932 & 08 58 44.2 & $-$16 07 54.2 & ? & 1.158 & 289 & $119.18 \pm 1.18$ & \\
-HD 84903 & 09 47 19.3 & $-$41 27 04.9 & ? & 1.260 & 294 & $77.65 \pm 1.41$ & \\
-HD 59984 & 07 32 05.7 & $-$08 52 56.1 & ? & 1.111 & 402 & $55.74 \pm 0.53$ & \\
-HD 60060 & 07 29 59.6 & $-$52 39 04.3 & ? & 1.127 & 414 & $25.60 \pm 1.08$ & \\
-HD 60228 & 07 30 30.8 & $-$54 23 58.6 & ? & 1.139 & 338 & $48.58 \pm 1.67$ & \\
-OSS 1    & 10 46 50.6 & $-$00 13 17.9 & 0.8 & 1.363 & 48 & $218.15 \pm 1.72$ & \\
-OSS 2    & 10 47 17.8 &    00 25 06.9 & ? & 1.995 & 59 & $222.16 \pm 1.28$ & \\
-OSS 3    & 10 47 30.3 & $-$00 01 22.6 & 0.71 & 1.156 & 49 & $226.35 \pm 1.27$ & \\
-OSS 4    & 10 49 08.3 &    00 01 59.3 & ? & 1.881 & 48 & $227.50 \pm 2.05$ & Poor seeing.\\
-OSS 5    & 10 50 33.7 &    00 12 18.3 & ? & 1.295 & 31 & $249.01 \pm 2.58$ & Poor seeing. \\
-HR 6141  & 16 30 12.3 & $-$25 06 52.0 & ? & 1.003 & 406 & - & Telluric std.
+HD 136316 & 15 22 17.2 & $-$53 14 13.9 & 1.118 & 335 & $-38.2 \pm 1.1$       & \\
+HD 141531 & 15 49 16.9 &\phs09 36 42.5 & 1.309 & 280 & $\phn\phn2.6 \pm 1.0$ & \\
+HD 142948 & 16 00 01.6 & $-$53 51 04.1 & 1.107 & 271 & $\phn30.3 \pm 0.9$    & \\
+HD 41667  & 06 05 03.7 & $-$32 59 36.8 & 1.005 & 272 & $297.8 \pm 1.7$       & \\
+HD 44007  & 06 18 48.6 & $-$14 50 44.2 & 1.033 & 239 & $163.4 \pm 1.3$       & \\
+HD 47536  & 06 37 47.7 & $-$32 20 20.1 & 1.002 & 257 & $\phn78.9 \pm 1.2$    & \\
+HD 76932  & 08 58 44.2 & $-$16 07 54.2 & 1.158 & 289 & $119.2 \pm 1.2$       & \\
+HD 84903  & 09 47 19.3 & $-$41 27 04.9 & 1.260 & 294 & $\phn77.7 \pm 1.4$    & \\
+HD 59984  & 07 32 05.7 & $-$08 52 56.1 & 1.111 & 402 & $\phn55.7 \pm 0.5$    & \\
+HD 60060  & 07 29 59.6 & $-$52 39 04.3 & 1.127 & 414 & $\phn25.6 \pm 1.1$    & \\
+HD 60228  & 07 30 30.8 & $-$54 23 58.6 & 1.139 & 338 & $\phn48.6 \pm 1.7$    & \\
+OSS 1     & 10 46 50.6 & $-$00 13 17.9 & 1.363 &  48 & $218.2 \pm 1.7$       & \\
+OSS 2     & 10 47 17.8 &\phs00 25 06.9 & 1.995 &  59 & $222.2 \pm 1.3$       & \\
+OSS 3     & 10 47 30.3 & $-$00 01 22.6 & 1.156 &  49 & $226.4 \pm 1.3$       & \\
+OSS 4     & 10 49 08.3 &\phs00 01 59.3 & 1.881 &  48 & $227.5 \pm 2.1$       & Poor seeing\\
+OSS 5     & 10 50 33.7 &\phs00 12 18.3 & 1.295 &  31 & $249.0 \pm 2.6$       & Poor seeing \\
+HR 6141   & 16 30 12.3 & $-$25 06 52.0 & 1.003 & 406 & \nodata               & Telluric
 \enddata
-\tablenotetext{a}{S/N measured at 600 nm for each target.}
+\tablenotetext{a}{S/N measured at 6000 \AA{} for each target.}
 \end{deluxetable*}
@@
 
-\subsection{Target Selection and Observations}
+\subsection{Data Reduction}
 
-\subsection{Data Reduction}
 The data were reduced using the latest version of the MIKE pipeline outlined in \citet{Kelson;2003}.
@@
 We carefully normalised every echelle order using cubic splines.
-Overlapping normalised orders on each CCD were stitched together, such that a continuous normalised spectra from each CCD remains.
-We do not include line measurements that are susceptible to telluric absorption, so no telluric corrections were made.
+Overlapping normalised orders on each CCD were stitched together, such that a continuous normalised spectra from each CCD results.
+No telluric corrections were made, as they do not affect the spectral regions we are interested in.
 
 \subsection{Radial Velocities}
+
 We measured radial velocities for every target by cross-correlating each normalised red  spectrum with a synthetic template.
-Our synthetic template was generated in \textsc{MOOG} using a \citet{Castelli-Kurucz;2004} model atmospheres with $T_{eff} = 4500$ K, $\log{g} = 2.5$, [Fe/H] = -1.5, [$\alpha$/Fe] = 0.0 and no convective overshoot.
+Our synthetic template was generated in \textsc{MOOG} using an $\alpha$ element enhanced \citet{Castelli-Kurucz;2004} model atmospheres with $T_{eff} = 4500$ K, $\log{g} = 2.5$, [Fe/H] = -1.5 and no convective overshoot.
 The line list of \citet{Kirby;et-al_2008} was employed to generate spectra between $845$ nm $< \Lambda < 870$ nm.
-Both the blue and red co-added, normalised frames were shifted to rest before equivalent width measurements.
+Both the blue and red normalised frames were shifted to rest before measuring equivalent widths.
 A number of radial velocity and halo standards were observed during this program, and our heliocentric velocities agree excellently with literature values (Table \ref{tab:observed-targets}).
 
+\subsection{Line List}
+\label{sec:line-list}
+
+% table
+
 \subsection{Line Measurements}
+An automatic routine has been developed to determine the local continuum and robustly measure the equivalent width of an absorption line.
+First, we estimate the local continuum surrounding the rest wavelength (Table \ref{tab:line-list}) by iteratively fitting a low order polynomial to $10$ \AA{} either side of the rest wavelength, and clipping only extreme outliers.
+This process does not determine the final local continuum; all we need is an initial estimate.
+
+Given a rest wavelength and our local continuum estimate, a Gaussian absorption profile is fitted in an iterative process.
+During this process we have three free parameters: the rest wavelength, the FWHM of the Gaussian profile, and the flux level at the profile trough.
+The initial value for the minimum flux is taken as the flux level at rest wavelength, and 0.1 \AA{} is used as the initial FWHM for the Gaussian profile.
+The actual FWHM of our final profile and the subsequent equivalent width measured is largely independent of the initial FWHM provided; only an initial guess is required to decrease computational cost.
+The difference between our calculated profile and the actual flux is calculated at each iteration, and we use least-squares minimisation to arrive at the best fitting line profile.
+
+Once this process is complete, we use the measured line FWHM in order to decide where the true continuum surrounding the line should start.
+Again, we iteratively fit a low order polynomial to the surrounding $10$ \AA{} \--- excluding $3\sigma$ of our measured profile\footnote{Recall that FWHM $\approx 2.355\sigma$} \--- but in this step the outlier clipping is more involved: after each iteration we identify flux points as outliers if $>2.5-\sigma$, and we identify sequentially occurring outlier points as probable minima of an absorption line.
+At each group of outlier points we attempt to fit a Gaussian absorption profile in the same process described above.
+If a profile is successfully fitted, then we exclude all points within $3-\sigma$ of the detected line from any more continuum determination.
+In this process, absorption lines are automatically detected and excluded, leaving only the continuum.
+
+When multiple lines are measured from our line list there are stringent quality constraints put in place to eliminate false positive measurements: the final rest wavelength must be within <$10$ \AA{} to the initial guess, the FWHM of each line should be reasonable with respect to all other lines, and the $\chi^2$ difference between the final profile and the spectrum must be reasonable.
+The $\chi^2$ constraint helps identify measurements where nearby lines are blended.
+
+For spectra which has been perfectly normalised and has high S/N, the method described here will always find the continuum to be unity.
+For low S/N objects, or where the normalisation is sub-par, our technique robustly determines the true local continuum.
+We must stress that this process is not 'blind'; the profile and local continuum determination for every measured line has been carefully inspected by the authors.
+All false positive measurements were discarded during the inspection process, and no lines required manual re-measurement.
+
+%We have verified the accuracy of our automatically determined equivalent widths in two ways:
+We have verified the accuracy of our automatically determined equivalent widths both internally and externally.
+For an internal comparison we have compared careful hand measurements of the equivalent widths against those determined automatically for two stars: the bright metal-rich dwarf HD 59984, and our metal-poor giant target OSS 4.
+The results of this comparison are shown in Figures \ref{fig:hd59984-ew-comparison} and \ref{fig:oss4-ew-comparison}, and demonstrate our measurement code at varying S/N.
+HD59984 has a S/N $\approx XX$ px$^{-1}$ at 600 nm, and the difference between equivalent width measurement methods is negligible.
+Our target star OSS 4 has a much more modest S/N of $\approx50$ px$^{-1}$ at 600 nm, and the two techniques still agree excellently.
+
+These internal comparisons validate the effectiveness of the local continuum fitting within a wide bracket of S/N ratios.
+To verify our equivalent width accuracy to an external source, we have automatically measured equivalent widths for the metal-poor sub-giant HD140283 and compared our measurements to those of \citet{Norris;et-al_1996}.
+
+The comparison is shown in Figure \ref{fig:norris-ew-comparison}, and the two techniques agree excellently.
+There is a systematic offset of XX m\AA{} and random scatter of YY m\AA{} between the two techniques.
+We are confident that our automatic measurement technique can reliably determine equivalent width measurements that are consistent with the literature, over a wide range of evolutionary phases, metallicities and signal quality.
 
 \subsection{Stellar Parameters}
-
-HD59984 5750 K, 1.55 vt, 3.55 logg -0.95,+0.40,
-================================================
-Fe I EPS 6.52 +/- 0.16 (210 lines)
-Slope, Offset, Corr: 0.01, 6.53, 0.05
-
-Fe I REW
-Slope, Offset, Corr: 0.0, 6.55, 0.00
-
-Fe I lambda
-Slope, Offset, Corr: 3.84e-05, 6.35, 0.17
-
-Fe II EPS 6.53 +/- 0.18 (22 lines)
-
-Fe II REW
-Slope, Offset, Corr: 0.07, 6.94, 0.09
-
-Fe II lambda
-Slope, Offset, Corr: 1.41e-04, 5.91, 0.36
-
-OSS 1:
-161.71091670000001 -0.2216389
-SDSS DR 8 closest source is 3.793" away, and 17.47 mag in g
-ugriz: 18.823 17.467 16.934 16.712 16.597
-No reddenning corrected for, Jester 2005 transformations
-UBVRI = 18.06255 17.88487 17.14253 16.68055 16.24855
-B -V = 0.74
-Estimating a [Fe/H] = -1.9 and using Alonso et al 1999 eq 4 yields 4986 K
-
-With the red arm only:
-5110 / 1.20 / 3.10 / -1.14 / 0.40
-(with [Fe/H] = -1.14, the estimated temp from photometry is 5014 K)
-
-Fe I Abundance 6.42 +/- 0.19 (106 lines)
-S, O, C: 0.00, 6.41, 0.01
-
-Reduced EW S, O, C: 0.10, 6.87, 0.08
-
-Lambda S, O, C: 9.41e-05, 5.89, 0.28
-
-Fe II Abundance: 6.44 +/- 0.17 (8 lines)
-
-Reduced EW S, O, C: -0.09, 6.01, -0.09
-
-Lamba S, O, C: 1.64e-04, 5.53, 0.53
-
-Wiith the red and blue, starting at 5000K, -1.9
-
-5070 / 1.6 / 2.9 / -1.4 / 0.40
-
-Fe I Abundance: 6.15 +/- 0.25 (117 lines)
-SOC: 0.01, 6.12, 0.03
-
-Reduced EW SOC: 0.00, 6.12, 0.00
-Lambda SOC: 1.41e-04, 5.42, 0.42
-
-Fe II Abundance: 6.14 +/- 0.19 (19 lines)
-
-Reduced EW SOC: -0.04, 5.95, -0.05
-Lambda SOC: 1.09e-04, 5.61, 0.41
-
-Followed from this (USING RED AND BLUE data) and excluded outliers.
-
-4040 / 1.4 / 2.8 / -1.2 / 0.40 ("FINAL" files) <-- doesn't quite fit on isochrone, but close-ish
-Fe I abundance: 6.24 +/- 0.16 (149 lines)
-SOC: 0.02, 6.18, 0.13
-REW SOC: 0.03, 6.39, 0.04
-Lambda SOC: 0.81e-05, 5.78, 0.38
-
-Fe II abundance: 6.19 +/- 0.16 (15 lines)
-REW SOC: 0.03, 6.33, 0.04
-Lambda SOC: 1.08e-04, 5.65, 0.46
-
-ALPHA ELEMENTS Mg, Si, Ca, Ti
-==============
-
-OSS 2: JMK = 0.633 (no reddenning correction)
-4571.9947676752899 K using Alonso 1999 paper
-SDSS (DR8) u g r i z -- searched at 161.8240417 0.4185833, found source 2.05" away
-18.063 16.252 15.479, 15.146, 14.950
-
-inspected all profiles + saved only Fe ones that were good in red + blue
-================================================
-4600 K, 1.85, 0.80, -1.77, 0.40
-
-Fe I: 5.73 +/- 0.14 (139 lines)
-
-Fe I EPS
-S, O, C: 0.00, 5.72, 0.01
-
-Fe I REW
-S, O, C: -0.03, 5.58, -0.04
-
-Fe I Lambda:
-S, O, C: 3.98e-05, 5.51, 0.21
-
-Fe II: 5.72 +/- 0.16 (21 lines)
-
-Fe II EPS: None
-
-Fe II REW S, O, C: 0.03, 5.84, 0.05
-
-Fe II Lambda: 2.1e-05, 5.58, 0.09
-
-=================================
-Incorporating isochrones in:
-4550 K / 1.85 / 0.8 / -1.80 / 0.40
-
-Fe I Abundance: 5.71 +/- 0.16 (112 lines)
-Fe I EPS S, O, C: 0.01, 5.66, 0.10
-
-Fe I REW S, O, C: -0.03, 5.54, -0.04
-
-Fe I Lambda: 8.01e-06, 5.66, 0.03
-
-Fe II Abundance: 5.75 +/- 0.10 (8 lines)
-
-Fe II REW S, O, C: 0.35, 7.52, 0.68
-
-Fe II Lambda = -1.29e-04, 6.48, -0.70
-
-Loaded in all local line list from OSS2/os_4_all_global_auto.moogew
-
-ALPHA ELEMENTS
-Ne, Mg, Si, S, Ar, Ca, Ti
-
-Ne I, II -- no lines present in line list
-
-Mg I: 5.90 +/- 0.10 (6 lines), Solar 7.60 +/- 0.04
-Inspected all six line profiles; they look perfect.
-SOC: 0.05, 5.74, 0.35 // 0.00, 5.93, 0.00 // 3.03e-05, 5.77, 0.15
-[Mg I/Fe] = 0.10 +/- 0.10
-
-Si
-5565 very small but clean (6 mA)
-4102 is great
-3095 is a bit blended
-Si I: 5.66 +/- 0.26 (3 lines), Solar 7.51 +/- 0.03
-Inspected the three lines we have, they don't look fantastic...  3095 could go..
-SOC -0.14, 6.14, -0.78 // 0.29, 7.12, 0.92
-[Si I/Fe] = -0.05 +/- 0.26
-
-S I, II -- no lines present in line list: they are mainly in the infrared
-
-Ar I, II -- no lines present in line list
-
-Ca I: 4.79 +/- 0.12 (17 lines), Solar 6.34 +/- 0.04
-Inspected all the lines I have; they all look reasonable. Outliers could be confidently excluded.
-SOC: // 0.48, 7.08, 0.77 // -9.21e-05, 5.30, -0.51
-[Ca I/Fe] = 0.25 +/- 0.12
-
-Ti I: 3.00 +/- 0.16 (20 lines), Solar 4.95 +/- 0.05
-Inspected all the lines, excluded some dodgey measurements and duplicates, then clipped outliers.
-SOC: // -0.04, 2.83, -0.04 // 6.68e-05, 2.69, 0.18
-[Ti I/Fe] = -0.15 +/- 0.16
-
-Ti II: 3.19 +/- 0.14 (23 lines), Solar 4.95 +/- 0.05
-Inspected all the lines, excluded some dodgey measurements & duplicates then clipped outliers.
-SOC: 0.00, 3.23, 0.01 // 0.22, 4.27, 0.28 // -4.71e-05, 3.44, -0.13
-[Te II/Fe] = 0.04 +/- 0.14
-
-Na I: 4.21 +/- 0.05 (3 lines), Solar 6.24 +/- 0.04
-Inspected all three line profiles; they look perfect.
-SOC: -0.06, 4.23, -0.96 // 0.11, 4.71, 0.95
-[Na I/Fe] = -0.23 +/- 0.05
-
-OSS 3: 161.8761667 -0.0229444
-Not in 2mass (3 arcsecond cone)
-SDSS  Closest point is 2.85 arcseconds away at 17.4 mag in g
-u g r i z (SDSS DR 8)
-18.881 17.400 16.748 16.497 16.316
-Using Alonso et al 1999 eq 4 relation, and Jester 2005 transformations:
-UBVRI = 18.13946 17.86428 17.00532 16.51173 16.05073
-BMV = 0.85895999999999972
-Tried inital guess of [Fe/H] as = -1.9 gives 4719 K, giving -1.7 gives 4735 K
-using -1.9 guess and starting at 4719 K
-
-Best so far (before excluding outliers)
-4800 K, 1.90, 1.70, -1.87, 0.40
-
-after outliers
-4810, 1.85, 1.70, -1.87, 0.40
-
-Fe I 5.68 +/- 0.18 (181 lines)
-Abundances
-S, O, C: 0.00, 5.67, 0.03
-
-Reduced EW
-S, O, C: -0.06, 5.38, -0.08
-
-Lambda S, O, C: 8.33e-05, 5.25, 0.34
-
-Fe II 5.67 +/- 0.23 (26 lines)
-
-Reduced EW S, O, C: 0.07, 6.00, 0.09
-
-Lambda S, O, C: 1.44e-04, 4.95, 0.40
-
-===============
-with isochrones
-4780 / 1.7 / 1.55 / -1.80 / +0.40
-
-Fe I abundance 5.74 +/- 0.13 (112 lines)
-S, O, C: 0.00 5.73 0.03
-Reduced EW SOC: 0.03 5.86 0.04
-Lambda SOC: 3.11e-05, 5.57, 0.13
-
-Fe II abundances 5.69 +/- 0.19 (8 lines)
-Reduced EW SOC: -0.14, 5.03, -0.16
-Lambda SOC: 1.73e-04, 4.75, 0.49
-
-OSS 4
-162.2845417 0.0331389
-In SDSS DR8 found closest 16.4 gmag star at 1.113 arcseconds away
-u g r i z
-17.935 16.440 15.770 15.465 15.299
-no redenning, jester transform, assume -1.9 feh and using B-V ~ 0.88
-Alonso et al 1999 eq 4
-initial start teff = 4693 K
-
-an emp???
-
-4550 /  1.9 / 0.8 / -2.7 / 0.4
-
-Fe I Abundance 4.75 +/- 0.19 (150 lines)
-S, O, C: 0.00, 4.76, 0.01
-
-REW S, O, C: 0.04, 4.95, 0.07
-
-Lambda S, O, C: 4.11e-06, 4.74, 0.01
-
-Fe II Abundance 4.78 +/- 0.16 (18 lines)
-
-REW S, O, C: -0.06, 4.51, -0.09
-
-Lambda S, O, C: 9.90e-05, 4.32, 0.33
-
-Using isochrones:
-
-4670 / 1.95 / 1.10 / -2.70 / +0.40
-Fe I Abundance 4.84 +/- 0.24 (168)
--0.01, 4.88, -0.03
-0.01, 4.93, 0.02
-5e-5, 4.61, 0.15
-
-Fe II Abundance 4.87 +/- 0.21 (21)
--0.01, 4.84, -0.01
-1.09e-04 4.37 0.27
-
-=============
-4580 K / 2.05 / 0.80 / -2.79 / +0.40
-( doesn't quite sit on the expected isochrone)
-
-Fe I abundance: 4.75 +/- 0.17 (128 lines)
--0.01 / 4.77 / -0.05
-0.03 / 4.88 / 0.04
-9.62e-06 / 4.70 / 0.40
-
-Fe II abundance: 4.77 +/- 0.15 (15 lines)
--0.01 / 4.69 / -0.02
-
-6.49e-05 / 4.44 / 0.15
-
-OSS 5
-162.6405417 0.2050833
-SDSS DR8 nearest target is 1.196" away at 18th magnitude in g
-ugriz = 19.628 17.997 17.338 17.065 16.908
-No reddenning correction and using Jester 2005:
-UBVRI = 18.85619 18.46401 17.59819 17.08062 16.59762
-bmv = 0.87
-
-Guessing [Fe/H] = -1.9 yields Teff = 4709 K
-Arbitrarily chosing lines only redward of 4400 A
-
-5200 / 2.0 / 2.9 / -0.95 / 0.40
-
-Fe I 6.60 +/- 0.22 (90 lines)
-0.00, 6.62, 0.01
-0.00, 6.65, 0.00
-9.2e-5, 6.12, 0.27
-
-Fe II 6.60 +/- 0.35 (17 lines)
-0.12, 7.14, 0.07
-9.81e-05, 6.09, 0.20
 
@@
 \subsection{Uncertainty Analysis}
+
+\begin{deluxetable}{lcccccccccl}
+\tablecolumns{1}
+\tabletypesize{\scriptsize}
+\tablecaption{Stellar Parameters\label{tab:stellar-parameters}}
+\tablehead{
+& \multicolumn{4}{c}{This work}  &
+& \multicolumn{4}{c}{Literature} & \\
+  \cline{2-5} \cline{7-10} \\
+  \colhead{Star} &
+  \colhead{$T_{\mbox{eff}}$} &
+ \colhead{$\log{(g)}$} &
+	\colhead{[Fe/H]} &
+	\colhead{$v_t$} 
+	&&
+	\colhead{$T_{\mbox{eff}}$} &
+	\colhead{$\log{(g)}$} &
+	\colhead{[Fe/H]} &
+	\colhead{$v_t$} &
+	\colhead{Reference} \\
+ & [K] & [dex] & [dex] & [km s$^{-1}$] 
+&& [K] & [dex] & [dex] & [km s$^{-1}$] & 
+}
+\startdata
+HD 136316 & $4370$ & $1.00$ & $-1.99$ & $1.95$ 
+         && $4469$ & $1.29$ & $-1.74$ & $1.90$ & \citet{Gratton;et-al_2000} \\
+HD 141531 & $4330$ & $0.90$ & $-1.74$ & $1.80$ 
+         && $4335$ & $1.11$ & $-1.62$ & $1.50$ & \citet{Gratton;et-al_2000} \\
+HD 142948 & $4870$ & $2.20$ & $-0.78$ & $1.45$ 
+         && $4713$ & $2.17$ & $-0.77$ & $1.38$ & \citet{Gratton;et-al_2000} \\
+HD 41667  & $4600$ & $1.70$ & $-1.23$ & $1.50$  
+         && $4605$ & $1.88$ & $-1.16$ & $1.44$ & \citet{Gratton;et-al_2000} \\
+HD 44007  & $4800$ & $1.80$ & $-1.77$ & $1.55$ 
+         && $4850$ & $2.00$ & $-1.71$ & $2.20$ & \citet{Fulbright_2000} \\
+HD 47536  & & & & 
+         &&\nodata &\nodata & \nodata &\nodata & \\
+HD 76932  & & & & 
+         && $5900$ & $4.20$ & $-0.70$ & $1.25$ & \citet{Fulbright_2000} \\
+HD 84903  & & & & 
+         && $4500$ & $0.80$ & $-2.60$ & $2.00$ & \citet{Francois_1996} \\
+HD 59984  & & & & 
+         && & & & & Binary system.\\
+HD 60060  & & & & 
+         &&\nodata &\nodata & \nodata &\nodata & \\
+HD 60228  & & & & 
+         &&\nodata &\nodata & \nodata &\nodata & \\
+OSS 1     & 5040 & 2.80 & -1.22 & 1.40 && & & & & \\
+OSS 2     & 4550 & 0.80 & -1.78 & 1.85 && & & & & \\
+OSS 3     & 4780 & 1.55 & -1.79 & 1.70 && & & & & \\
+OSS 4     & 4580 & 0.80 & -2.75 & 2.05 && & & & & \\
+OSS 5     & 5250 & 3.00 & -0.80 & 1.85 && & & & & 
+\enddata
+\end{deluxetable}
+
+\begin{deluxetable}{lccccccccccccccccc}
+\tablecolumns{18}
+\tablewidth{\textwidth}
+\tabletypesize{\scriptsize}
+\tablecaption{Chemical Abundances\label{tab:stellar-parameters}}
+\tablehead{
+&  \multicolumn{5}{c}{OSS 1} & \colhead{} &
+	\multicolumn{5}{c}{OSS 2} & \colhead{} &
+	\multicolumn{5}{c}{OSS 3} \\
+	\cline{2-6} \cline{8-12} \cline{14-18} \\
+\colhead{Species} 
+ & $\log\epsilon$(X) & [X/H] & [X/Fe] & $N$ & $\sigma$ &
+ & $\log\epsilon$(X) & [X/H] & [X/Fe] & $N$ & $\sigma$ &
+ & $\log\epsilon$(X) & [X/H] & [X/Fe] & $N$ & $\sigma$
+}
+\startdata
+Na \textsc{I} & ? & ? & ? & ? & ?
+             && $4.21$ & $-2.03$ &    $-0.23$ &   $3$ & $0.05$
+             && $4.42$ & $-1.82$ &    $-0.03$ &   $3$ & $0.07$  \\
+Mg \textsc{I} & $6.56$ & $-1.04$ & \phs$0.16$ &   $4$ & $0.10$  
+             && $5.90$ & $-1.70$ & \phs$0.10$ &   $6$ & $0.10$   
+             && $5.95$ & $-1.65$ & \phs$0.15$ &   $5$ & $0.05$  \\
+Si \textsc{I} & $6.57$ & $-0.94$ & \phs$0.26$ &   $4$ & $0.23$
+             && $5.66$ & $-1.85$ &    $-0.05$ &   $3$ & $0.26$   
+             && $6.20$ & $-1.31$ & \phs$0.43$ &   $3$ & $0.16$  \\
+Ca \textsc{I} & $5.48$ & $-0.86$ & \phs$0.34$ &  $14$ & $0.14$
+             && $4.79$ & $-1.55$ & \phs$0.25$ &  $17$ & $0.12$   
+             && $4.87$ & $-1.47$ & \phs$0.32$ &  $18$ & $0.09$  \\
+Ti \textsc{I} & $3.73$ & $-1.22$ &    $-0.02$ &  $21$ & $0.15$  
+             && $3.00$ & $-1.95$ &    $-0.15$ &  $20$ & $0.16$   
+             && $3.13$ & $-1.82$ &    $-0.03$ &  $23$ & $0.09$  \\
+Ti \textsc{II}& $3.91$ & $-1.04$ & \phs$0.16$ &  $25$ & $0.10$  
+             && $3.19$ & $-1.76$ & \phs$0.04$ &  $23$ & $0.14$   
+             && $3.36$ & $-1.59$ & \phs$0.20$ &  $24$ & $0.09$  \\
+Fe \textsc{I} & $6.24$ & $-1.26$ &    \nodata & $149$ & $0.16$  
+             && $5.71$ & $-1.79$ &    \nodata & $112$ & $0.16$  
+             && $5.71$ & $-1.79$ &    \nodata & $154$ & $0.12$  \\
+Fe \textsc{II}& $6.19$ & $-1.21$ & \phs$0.05$ &  $15$ & $0.16$
+             && $5.75$ & $-1.75$ &    $-0.04$ &   $8$ & $0.10$   
+             && $5.71$ & $-1.79$ & \phs$0.00$ &  $20$ & $0.16$  \\
+
+\\ & \multicolumn{5}{c}{OSS 4} && \multicolumn{5}{c}{OSS 5} \\
+     \cline{2-6} \cline{8-12} \\
+Na \textsc{I} & $3.69$ & $-2.55$ & \phs$0.20$ &  $2$ & $0.04$
+             && $5.17$ & $-1.07$ &    $-0.27$ &  $4$ & $0.13$ \\ 
+Mg \textsc{I} & $5.11$ & $-2.49$ & \phs$0.26$ &  $7$ & $0.13$
+             && $6.70$ & $-0.90$ &    $-0.10$ &  $5$ & $0.15$ \\
+Si \textsc{I} & $5.38$ & $-2.13$ & \phs$0.62$ &  $3$ & $0.03$
+             && $6.78$ & $-0.73$ & \phs$0.07$ &  $4$ & $0.07$ \\
+Ca \textsc{I} & $3.75$ & $-2.59$ & \phs$0.16$ &  $9$ & $0.10$
+             && $5.77$ & $-0.57$ & \phs$0.23$ & $10$ & $0.12$ \\
+Ti \textsc{I} & $2.28$ & $-2.67$ & \phs$0.08$ & $13$ & $0.15$
+             && $4.26$ & $-0.69$ & \phs$0.11$ & $15$ & $0.36$ \\
+Ti \textsc{II}& $2.31$ & $-2.64$ & \phs$0.11$ & $24$ & $0.15$
+             && $4.28$ & $-0.67$ & \phs$0.13$ & $13$ & $0.19$ \\
+Fe \textsc{I} & $4.74$ & $-2.76$ &    \nodata & $89$ & $0.11$
+             && $6.68$ & $-0.82$ &    \nodata & $99$ & $0.18$ \\
+Fe \textsc{II}& $4.77$ & $-2.73$ & \phs$0.03$ & $13$ & $0.12$
+             && $6.71$ & $-0.79$ &    $-0.03$ & $14$ & $0.16$ \\
+\enddata
+\end{deluxetable}
 
@@
 
+\bibliographystyle{apj}
+\bibliography{bibliography}
 \end{document}

### 2012-08-04 2012-oss/medium-res-paper.tex
included some medium res writing + selection

We present two sets of spectroscopic observations: medium resolution spectroscopy with AAOmega on the Australian Astronomical Telescope, and the follow-up of Orphan stream candidates with high resolution echelle spectroscopy using MIKE on the Magellan Clay telescope.

\subsection{Medium Resolution Observations}

\subsubsection{Target Selection}
Given the well-described distance gradient along the Orphan stream \citep{Belokurov;et-al_2007,Newberg;et-al_2010}, we have chosen to target stars closest to us, near the celestial equator and on the edge of the SDSS footprint.

% sdss cuts employed

\subsubsection{Observations}
AAOmega is a dual beam multi-object spectrograph which is capable of simultaneously observing spectra of 400 targets across a $2^\circ$ field of view. We employed the 1000I grating in the red arm which provides spectral coverage between $X \leq \lambda \leq Y$ nm at $R$ = XXXX, and the 580V grating in the blue arm that covers $X \leq \lambda \leq Y$ nm with a lower resolving power of $R \approx 1300$. The data were taken in visitor mode during Y 2009.

The data were reduced using the supplied \textsc{2DFDR} reduction pipeline, which includes flat fielding, sky subtraction, and wavelength calibration. The median S/N obtained in the red arm for our fields is modest at 35 px$^{-1}$. However, with the presence of strong Ca \textsc{II} triplet lines we are able to ascertain reliable radial velocity measurements and reasonable estimates on metallicity \citep[][and references therein]{Starkenburg;et-al_2010}.

\subsubsection{Data Analysis}

Radial velocities were measured by cross-correlating our normalised reduced spectra with a synthetic template of K-giant with a temperature of $4500$ K, $\log{g}$ = 2 and [Fe/H] = $-1.5$ across the range $845 \leq \lambda \leq 870$ nm. The equivalent widths for the Ca \textsc{II} lines were measured by E. M. and used to estimate metallicities using the \citet{Battaglia;et-al_2008} relationship and an assumed distance of $X$ kpc [citation needed]. In order to eliminate K dwarves from our sample we have measured the equivalent widths of the gravity-sensitive Mg \textsc{I}b lines at $518$ nm and employed the dwarf discriminant described in \citet{Casey;et-al_2012}.

% using a combination of cuts we have identified X likely K-giant candidates for high resolution spectroscopic follow-up. these candidates are highlighted in Figure X?

### 2012-08-16 2012-oss-mrs/draft-oss-mrs.tex
OSS MRS paper draft 1 as submitted to GDC and SK

%!TEX TS-program = pdflatex
\documentclass{emulateapj}

\usepackage{amssymb} % for resolution symbol

\shorttitle{Chemistry of the Orphan Stream I}
\shortauthors{Casey et al}

\begin{document}

\title{Chemistry of the Orphan Stream I: Identifying Stream Candidates with Low Resolution Spectroscopy}

\author{Andrew R. Casey\altaffilmark{1,2}, Stefan C. Keller\altaffilmark{1}, Gary Da Costa\altaffilmark{1}, Elizabeth Maunder\altaffilmark{1}}
\altaffiltext{1}{Research School of Astronomy \& Astrophysics, Australian National University, Mount Stromlo Observatory, via Cotter Rd, Weston, ACT 2611, Australia; \email{arcasey@mso.anu.edu.au}}
\altaffiltext{2}{Massachusetts Institute of Technology, Kavli Institute for Astrophysics and Space Research,
77 Massachusetts Avenue, Cambridge, MA 02139, USA}

\begin{abstract}
We present coordinates and properties of K giant members in the Orphan Stream, which have been identified from low resolution spectroscopic data taken with AAOmega on the Australian Astronomical Telescope. With modest S/N and independent cuts in photometry, kinematics, gravity and metallicity we yield self-consistent, highly probable stream members. Our data indicates an overall stream metallicity of [Fe/H] $= -1.74 \pm 0.05$ which is more metal-rich than previously found and unbiased by spectral type. We find a revised stream distance of 24 kpc near the celestial equator, and our kinematic signature peaks at $V_{helio} \sim 218$\,km s$^{-1}$. We highlight members for high resolution spectroscopic follow-up.
\end{abstract}

\keywords{Galaxy: halo, structure --- Individual: Orphan Stream --- Stars: K-giants}

\section{Introduction}
\label{sec:introduction}

The Milky Way stellar halo has been partly formed through the accretion of smaller satellites. As smaller satellites infall onto the Milky Way, tidal forces disrupt the satellite. Stars which were once gravitationally bound to the satellite are left behind in a stream of stars. Stream members have kinematics which are sensitive to the shape of the galactic potential, allowing us to constrain the Milky Way potential, and reconstruct the formation history of the Milky Way. The level of accreted substructure in the Milky Way has only recently become apparent through multi-band photometric surveys like the Sloan Digital Sky Survey (SDSS). The more prominent of the detectable substructures, like Sagittarius, have been well-studied. One of the more prominent \-- yet less studied \-- substructures is that of the Orphan Stream.

The Orphan Stream was independently detected by both \citet{Grillmair;Dionatos_2006} and \citet{Belokurov;et-al_2006}, and is unique from other substructures in the halo. The stream stretches over $60\,^\circ$ in the sky, has a low surface brightness and a narrow stream width of only $\sim2^\circ$ and as the name suggests, the parent largely remains a mystery. The stream extends past the celestial equator \-- outside the SDSS footprint \-- and is not detectable through bright southern surveys like SuperCOSMOS [citation needed]. Whilst the parent system remains elusive, significant effort has been placed on associating the stream with known Milky Way satellites \citep{Zucker;et-al_2006, Fellhaur;et-al_2007,Jin;Lynden_Bell_2007,Sales;et-al_2008}. In contrast, there has been relatively limited observational work on the Orphan Stream other than the original discovery papers \citep{Grillmair;Dionatos_2006, Belokurov;et-al_2006, Belokurov;et-al_2007} and the work of \citet{Newberg;et-al_2010}. This is largely to be expected given the absence of multi-band photometry in the southern sky, the difficulty in reliably separating Orphan Stream members from halo stars and the low luminosity of stream members. It is unlikely the full extent of the Orphan Stream will be detected until the SkyMapper telescope surveys this region \citep{Keller;et-al_2007}.

As \citet{Sales;et-al_2008} points out, there is a natural observational bias towards more massive and recent mergers like Sagittarius. The fainter end of this substructure distribution has yet to be fully recovered, or thoroughly examined. Interestingly, there are indications that  some fainter substructures like the Orphan Stream \citep{Newberg;et-al_2010} and the Palomar 5 tidal tails \citep{Odenkirchen;et-al_2009} have orbits which seem to be best-fit by Milky Way models with nearly 60\% less mass \citep{Newberg;et-al_2010} than generally reported by \citet{Xue;et-al_2008, Koposov;et-al_2010}. Such a discrepancy in the mass of the Milky Way is worrying. A more complete photometric and kinematic map of the stream may provide the best test as to whether this mass discrepancy for faint substructure orbits is real or an artefact of incomplete observations. Whilst the full spatial extent of the stream remains incomplete, we can examine the detailed chemistry of the stream and investigate the stream history, as well as make predictions about the nature of the progenitor.

In this letter we present a detailed, self-consistent analysis to identify K giant members of the Orphan Stream. Using our selection method we have published the locations of seven highly probable Orphan Stream candidates, all worthy of high resolution spectroscopic follow up. In the following section of this letter we outline our initial photometric target selection. In section \S\ref{sec:target-selection} we outline our target selection and section \S\ref{sec:observations} describes the low resolution observations. The data analysis, including stream identification, is described in \S\ref{sec:analysis}. In \S\ref{sec:conclusions} we discuss our conclusions, predictions, and necessary future work necessary on this topic.

\section{Target Selection}
\label{sec:target-selection}

We have targeted K giant members of the Orphan Stream in order to investigate their detailed chemistry. Because K-giants are difficult to unambiguously detect from photometry alone, low resolution spectroscopy is required to estimate stellar parameters and determine radial velocities. The Orphan Stream has a low spatial over-density on the order of $\sim10\%$ [citation needed], which also makes it difficult to separate stream members from halo stars. However, there is a well described distance gradient along the stream \citep{Belokurov;et-al_2007, Newberg;et-al_2010} which provides an indication on where we should focus our spectroscopic efforts.

The Orphan Stream is closest to us in two locations on the edge of the SDSS footprint: at the celestial equator \citep{Belokurov;et-al_2007}, and along outrigger SEGUE Stripe 1540 \citep{Newberg;et-al_2010}. These two locations are unequivocally the best place to recover bright stream members. We have targeted two fields centered on ($\alpha$, $\delta$) = (10:48:15, 00:00:00) and (10:48:15, -02:30:00), and employed a combination of colour cuts with the SDSS DR 7 \citep{Abazajian;et-al_2009} data set in order to identify likely K giants:

\begin{eqnarray}
(g - i)_0 &>& 0.6 \\
0.86i_0 + 3.30 >& g_0 &> 0.95i_0 + 1.35 \\
19.00 >& g &> 15.75
\end{eqnarray}

\textbf{Stefan can you see if you can find your original selection SQL \-- I deduced these relationships from cross-matching against SDSS and fitting boundary lines.}

Given our colour selection we expect to recover giants and dwarf contaminants. At a given temperature, K dwarfs exhibit a infrared excess relative to giants which allows a clean selection of giants \citep{Bessell;Brett_1988}. However, given the apparent magnitude of the Orphan Stream in this region ($g \sim 18$), no 2MASS infrared photometry is available. Thus we expect our sample to be contaminated by foreground dwarfs to some extent.

\section{Observations}
\label{sec:observations}

Observations took place on the Australian Astronomical Telescope using the AAOmega spectrograph in April 2009. AAOmega is a fibre-fed, dual beam multi-object spectrograph which is capable of simultaneously observing spectra of 400 (science and sky) targets across a $2^\circ$ field of view. We used the 5700\,{\AA} dichroic in combination with the 1000I grating in the red arm, and the 580V grating in the blue arm. This provides a spectral coverage between $800 \leq \lambda \leq 950$\,nm in the red at $\mathcal{R} \approx 4400$, and between $370 \leq \lambda \leq 580$\,nm with a lower resolving power of $\mathcal{R} \approx 1300$.

The data were reduced using the supplied \textsc{2DFDR} reduction pipeline \footnote{http://www.aao.gov.au/2df/aaomega/aaomega\_2dfdr.html}. After flat-fielding, throughput calibration for each fibre was achieved using the intensity of skylines in each fibre. The median flux of dedicated sky fibres was taken for sky subtraction, and wavelength calibration was performed using arc lamp exposures between science frames. Three thirty minute science exposures were median combined to assist with cosmic ray removal. The median S/N obtained in the red arm for our fields is modest at 35\,px$^{-1}$. With the presence of strong Ca \textsc{II} triplet lines in the red arm we are able to ascertain reliable radial velocities and reasonable estimates on overall metallicity \citep[][and references therein]{Starkenburg;et-al_2010}. Our spectral region also includes gravity-sensitive magnesium lines: Mg I at 8807\,{\AA}, and the Mg Ib 3$p$-4$s$ triplet lines. As we demonstrate in the next section, these lines are sufficient to discriminate dwarfs and giants even with weak signal.

The blue and red arm were normalised using a third order cubic spline after multiple iterations of outlier clipping. We used defined knot spacings of 20 nm in the red arm, and 5 nm in the blue arm in order to accommodate often poor S/N, and varying strengths of molecular band-heads.

\section{Analysis}
\label{sec:analysis}

We have employed a combination of separate criterion to identify likely Orphan Stream members: kinematics, a giant/dwarf indication from Mg I lines, and metallicity from Ca II triplet lines. Each criterion is discussed here separately.

\subsection{Kinematics}
Radial velocities were measured by cross-correlating our normalised spectra against a K-giant synthetic template with a temperature of $4500$\,K, $\log{g}$ = 2 and [Fe/H] = $-1.5$ across the range $845 \leq \lambda \leq 870$\,nm. Heliocentric velocities were translated to the galactic rest frame by adopting the local standard of rest velocity as 220\,km s$^{-1}$ towards $(l, b) = (53^\circ, 25^\circ)$ \citep{Kerr;Lynden-Bell_1986, Mihalas;Binney_1981}\footnote{Where $V_{\textsc{gsr}} = V_{\textsc{helio}} + 220\sin{l}\cos{b} + 16.5\times[\sin{b}\sin{25} + \cos{b}\cos{25}\cos{(l - 53)}]$}. \citet{Newberg;et-al_2010} presented a comprehensive kinematic dataset on the Orphan Stream using BHB stars and employed a slightly different galactocentric transformation. This systematic difference equates to our galactocentric rest frame velocities being on average $\sim5$\,km s$^{-1}$ lower than those of \citet{Newberg;et-al_2010}.

% Besan\c{c}on heliocentric velocities have been translated to a galactocentric frame in the same way as our targets.
Figure \ref{fig:velocities} shows a histogram of our galactocentric velocities, compared to the predicted smooth halo velocity distribution for this region from the Besan\c{c}on model \citep{Robin;et-al_2003}. It is clear that our target selection has yielded mostly nearby thick disk dwarf stars with $V_{\textsc{gsr}} \approx -120$\,km s$^{-1}$. The expected kinematic signature for the Orphan Stream, as \citet{Newberg;et-al_2010} reported, is labelled in Figure \ref{fig:velocities}. No statistically significant peak representative of the Orphan Stream exists in our sample. From kinematics alone, our targets appears largely indistinguishable from a smooth halo distribution.

\begin{figure}[h]
	\includegraphics[width=\columnwidth]{./figures/vgsr-histogram.pdf}
	\caption{Galactocentric rest frame velocities for our observed sampled (grey), and predicted  Besan\c{c}on velocities (white) which have been scaled to match our observed sample size. The expected kinematic signature from \citet{Newberg;et-al_2010} for the Orphan Stream is highlighted, as is our kinematic selection window (green).}
	\label{fig:velocities}
\end{figure}

In this region \citet{Newberg;et-al_2010} found the Orphan Stream to have $V_{\textsc{gsr}} = 110$ km s$^{-1}$ from BHB stars, approximately $105$\,km s$^{-1}$ on our scale. We have nominated a relatively wide kinematic selection region between $75 \leq V_{\textsc{gsr}} \leq 135$ km s$^{-1}$, which yields 25 Orphan Stream candidates. The typical uncertainty in our kinematics is $\pm{}3.5$\,km s$^{-1}$, although for our fainter targets this quickly increases to $\sim10$ km s$^{-1}$.

\subsection{Dwarf/Giant Discrimination}
\label{sec:dwarf-giant}

We have measured the equivalent widths of the gravity-sensitive Mg I line at 8807 \AA{} to distinguish dwarfs from giants. At a given temperature (or $g \-- r$) and metallicity, giant stars present narrow Mg I absorption lines than their dwarf contaminants. Given our target selection, our sample is likely to contain many more dwarfs than giants. In four cases no Mg I 8807 \AA{} line was apparent, so an upper limit was estimated based on the S/N. In these cases the candidate was considered a ``non-dwarf" because we cannot exclusively rule out a metal-poor sub-giant with this criterion alone. For these purposes we are only looking for a simple indication as to whether a star is likely a dwarf or not. Figure \ref{fig:ew-mg} illustrates the trend with EW$_{\lambda8807}$ against SDSS $g \-- r$ de-reddened\footnote{All magnitudes presented in this paper are de-reddened}, illustrating the dominant upper dwarf branch we wish to exclude. The adopted dwarf/giant separation line is shown. Admittedly this selection criterion appears extremely inclusive of dwarfs, but we are allowing multiple inclusive cuts and taking the union of these selections to identify Orphan Stream giants.

\begin{figure}[h]
	\includegraphics[width=\columnwidth]{./figures/ew-mg.pdf}
	\caption{De-reddened $g \-- r$ against the measured equivalent width of the Mg I transition at 8807 \AA{}. Dwarf contaminants occupy the more populous upper branch. Our separation line between dwarfs and giants is shown in green.}
	\label{fig:ew-mg}
\end{figure}

It is worth noting that we initially performed this analysis using the total equivalent width of the Mg\,\textsc{I}b triplet near 5175\,{\AA}. As expected, this region has a consistently lower S/N than the Mg\,\textsc{I} line at 8807\,{\AA}. However, the separation between giants and dwarfs was arguably more distinguished when using the Mg I b triplet equivalent width instead of using the $\lambda{}8807$ line. In either case, both analyses were entirely consistent with each other: the same candidate selection was found using both techniques. However, given the poorer signal at the Mg\,\textsc{I}b triplet, we were forced to adopt many more upper limits than when using the 8807{\AA} line. Because we classify all upper limits as being ``non-dwarfs" (i.e. potential OSS giants), we deduced a slightly larger candidate sample for the Mg\,\textsc{I}b analysis, which was primarily populated by upper limits. In conclusion, we found the Mg\,\textsc{I} line at 8807 appeared to be a more consistent dwarf discriminant given our weak S/N \--- particularly for our fainter stars \--- and thus we have used the 8807{\AA} Mg \textsc{I} selection throughout the rest of our analysis.

Our dwarf/giant separation line in Figure \ref{fig:ew-mg} yields 425 potential giants. This fraction of giants ($\sim{}44\%$) is much larger than what would be expected given our selection criterion (e.g. see \citet{Casey;et-al_2012a}). Hence, our gravity criterion is extremely inclusive and susceptible to dwarf contamination. Upon taking the union of our kinematic and gravity selections, we deduce eighteen stars that appear likely Orphan Stream K giants.

\subsection{Metallicities}
\label{sec:metallicities}

We have measured the equivalent widths of the Ca\,\textsc{II} near-infrared triplet lines for stars which meet our kinematic and surface gravity criteria. After correcting for luminosity, the equivalent width of the Ca\,\textsc{II} triplet lines provide a good indication for the metallicity of a RGB star \citep{Amandroff;Da_Costa_1991}. We have employed the \citet{Starkenburg;et-al_2010} relationship and corrected for luminosity in $g$ against the horizontal branch magnitude at $g_0$ = 17.1 \citep{Newberg;et-al_2010}. Strictly speaking, the Ca\,\textsc{II}-[Fe/H] relationship is only valid for stars brighter than the horizontal branch, although the situation only becomes dire at $g \-- g_{HB} \sim +1$ [citation needed]. Many of our candidates are fainter than this valid luminosity range, and therefore they should not be excluded solely because of their derived metallicities. Stars fainted than $g_0$ will have slightly lower metallicities than predicted by our Ca\,\textsc{II}-[Fe/H] relationship, and for these stars we will only use metallicities to assign a relative qualitative likelihood for stream membership.

\begin{figure}[h]
	\includegraphics[width=\columnwidth]{./figures/cmd.pdf}
	\caption{Color magnitude diagram showing our observed candidates (grey) and highlighting candidates which meet our kinematic and gravity cuts. Candidates are colored by their metallicity, and those with upper limiting gravities are marked as triangles. Highly probable stream members are marked. Relevant 10 Gyr \citet{Girardi;et-al_2008} isochrones at $[\mbox{Fe/H}] = -1.5$ (dotted), $-2.0$ (dashed) at 21.4\,kpc \citep{Newberg;et-al_2010} are shown, as well as our best-fitting 10 Gyr isochrone of $[\mbox{Fe/H}] = -1.74$ at 24\,kpc (solid).}
	\label{fig:cmd}
\end{figure}

Figure \ref{fig:cmd} illustrates all eighteen candidates which meet both our kinematic and surface gravity criterion. Candidates are coloured by their metallicity deduced from the Ca\,\textsc{II} triplet. There are four candidates above $g_0 \sim 17.1$ which are within our valid luminosity range. Two of these objects at $g \-- r \sim 0.57$ are slightly metal-rich than expected for the stream, and are excluded from membership. There appears to be an extremely metal-poor star in this sample with an estimated $[\mbox{Fe/H}] = -2.70$ which may be associated with the Orphan Stream. The likely parent system of the Orphan Stream is a Milky Way dwarf spheroidal \citep{Belokurov;et-al_2007, Sales;et-al_2008}, which are known to have a wide metallicity distribution function [citation needed?], including an over-represented population of extremely metal poor stars \citep{Frebel;et-al_2010, Kirby;et-al_2010}. Thus, we keep this extremely metal-poor star as a potential stream member for follow-up chemical analysis. 
% speak about OSS 1?

\citet{Newberg;et-al_2010} found the median Orphan Stream metallicity to be [Fe/H] $= -2.1$ from BHB stars, and a distance of $21.4 \pm 1.0$\,kpc in this region. In Figure \ref{fig:cmd} we have overlaid 10 Gyr old isochrones from \citet{Girardi;et-al_2008} with metallicities of [Fe/H] $= -2.0$ and $-1.5$ at a distance of $21.4$ kpc \citep{Newberg;et-al_2010}. Four of our most probable Orphan Stream members fall between these isochrones. Assuming the three highly probable members outside our valid luminosity range are over-predicted by $\sim+0.1$ dex [citation needed], when combining our four Orphan Stream members we yield a stream metallicity of $[\mbox{Fe/H}] = -1.74 \pm 0.05$. This is slightly more metal-rich than the $[\mbox{Fe/H}] =-2.1$ found by \citet{Newberg;et-al_2010} from BHB stars. This is to be expected as BHB stars are intrinsically representative of an older, more metal-poor population.

Given that our four Orphan Stream stars cover range along the giant branch, we are in a good position to revise the distance estimate to the stream. Given a 10 Gyr \citet{Girardi;et-al_2008} isochrone at $[\mbox{Fe/H}] = -1.74$, we find a best-fitting distance to the stream of 24 kpc at ($l, $b) = ($250^\circ$, $50^\circ$). This isochrone is also shown in Figure \ref{fig:cmd}, and it is clear that the four most probable member stars lie almost precisely on this isochrone. Our derived distance is slightly farther than the $21.4 \pm 1.0$ kpc found by \citet{Newberg;et-al_2010}, but given the inherent uncertainties in determining distance we argue these distances are largely in agreement.

\begin{deluxetable*}{lcccccccccl}
\tabletypesize{\scriptsize}
\tablecaption{Identified Orphan Stream Members\label{tab:oss-members}}
\tablehead{
	\colhead{Star} &
	\colhead{$\alpha$} &
	\colhead{$\delta$} &
	\colhead{$g$} &
	\colhead{$g \-- r$} &
	\colhead{$V_{helio}$} &
	\colhead{$V_{\textsc{gsr}}$} &
	\colhead{$V_{err}$} &
	\colhead{$EW_{\lambda8807}$} &
	\colhead{[Fe/H]} &
	\colhead{Comment} \\
Name & (J2000) & (J2000) & & & (kms $^{-1}$) & (km s$^{-1}$) & (km s$^{-1}$) & (\AA) & (dex)
}
\startdata
OSS 1 & 10 46 50.6 & $-$00 13 17.9 & 17.33 & 0.50  &  215.5  & \phn77.0 & 4.0 & 0.416 & -1.31 & Unlikely member! \\
OSS 2 & 10 47 17.6 & $+$00 25 07.7 & 16.09 &  0.73 &  215.7  & \phn79.2 & 3.3 & 0.212 & -1.84 & Highly probable member \\
OSS 3 & 10 47 30.1 & $-$00 01 24.6 & 17.25 &  0.61 &  221.4  & \phn83.6 & 3.4 & 0.123 & -1.62 & Highly probable member \\
OSS 4 & 10 49 08.3 & $+$00 02 00.2 & 16.27 &  0.62 &  218.5  & \phn81.5 & 4.6 & 0.034 & -2.70 & Possible EMP member \\
OSS 6 & 10 48 20.9 & $+$00 26 34.4 & 17.88 &  0.55 &  254.9  & 118.8 & 11.7 & 0.469 & -1.65 & Highly probable member \\
OSS 7 & 10 46 29.3 & $-$00 19 38.5 & 17.77 &  0.56 &  217.3  & \phn78.4 & 5.2 & 0.126 & -1.63 & Highly probable member 
\enddata
\end{deluxetable*}

\section{Conclusion}
\label{sec:conclusions}

We have presented a detailed analysis to isolate individual Orphan Stream K giants from low resolution spectroscopy using a combination of photometric, kinematic, gravity, and metallicity information. Although each individual criterion is likely to induce some level contamination, the resulting union of these selections reveal highly probable, self-consistent, Orphan Stream K giants.  We deduce a stream metallicity of $[\mbox{Fe/H}] = -1.74 \pm 0.05$ which is not biased by spectral type. Recall that the metallicity determination was performed after kinematic and gravity cuts, and our most probable members lay perfectly on a 10 Gyr isochrone of $[\mbox{Fe/H}] = -1.74$. Our stream members indicate a revised distance to the stream of $24$\,kpc at $(l, b) = (250^\circ$, $50^\circ)$, slightly farther than that deduced by \citet{Newberg;et-al_2010}.

If the Orphan Stream continues through SEGUE stripe 1540 at $(l, b) = (271^\circ$, $38^\circ)$ as \citet{Newberg;et-al_2010} found, then the stream is even closer there than in the region analysed here. Thus, if our observations and analyses are repeated at $(271^\circ$, $38^\circ)$, we predict brighter (and subsequently more numerous) K giant stream members will be recovered.

The K giants presented here can provide great insight into the chemistry, and history of the Orphan Stream. High resolution spectroscopic observations have been taken for our most highly probable members and a detailed chemical analysis will be presented in an accompanying paper (Casey et al. 2012c, in preparation). Detailed chemical abundances can help determine both the nature of the host system, and allow us to compare peculiar chemical signatures with those of the known Milky Way satellites in order to associate likely parents. However at least for the moment, the Orphan Stream remains appropriately named.

\section{Acknowledgements}
ARC acknowledges the financial support through the Australian Research Council Laureate Fellowship 0992131, and from the Australian Prime Minister's Endeavour Award Research Fellowship, which has facilitated his research at MIT. SK and GDaC acknowledge the financial support from the Australian Research Council through Discovery Program DP0878137.

Funding for the SDSS and SDSS-II has been provided by the Alfred P. Sloan Foundation, the Participating Institutions, the National Science Foundation, the U.S. Department of Energy, the National Aeronautics and Space Administration, the Japanese Monbukagakusho, the Max Planck Society, and the Higher Education Funding Council for England. The SDSS Web Site is http://www.sdss.org/.

The SDSS is managed by the Astrophysical Research Consortium for the Participating Institutions. The Participating Institutions are the American Museum of Natural History, Astrophysical Institute Potsdam, University of Basel, University of Cambridge, Case Western Reserve University, University of Chicago, Drexel University, Fermilab, the Institute for Advanced Study, the Japan Participation Group, Johns Hopkins University, the Joint Institute for Nuclear Astrophysics, the Kavli Institute for Particle Astrophysics and Cosmology, the Korean Scientist Group, the Chinese Academy of Sciences (LAMOST), Los Alamos National Laboratory, the Max-Planck-Institute for Astronomy (MPIA), the Max-Planck-Institute for Astrophysics (MPA), New Mexico State University, Ohio State University, University of Pittsburgh, University of Portsmouth, Princeton University, the United States Naval Observatory, and the University of Washington.

\bibliographystyle{apj}
\bibliography{bibliography}
\end{document}

### 2012-08-16 2012-oss-mrs/figures/cmd.py

@@ -1,0 +1,134 @@
+
+good_candidate_oids = [570, 169, 143, 604, 337, ]#571, 76, 264]
+#upperlimit_candidate_oids = [798, 570, 932, 604, 424, 672, 685]
+upperlimit_candidate_oids = []
+dodgy_candidate_oid = False
+
+distance = 23.7 #kpc (my measurement)
+my_distance_modulus = 5 * np.log10(distance * 1000) - 5
+newberg_distance_modulus = 5 * np.log10(21.4 * 1000) - 5 # Newberg et al 2010 estimate distance at (l, b) = (250, 50) of 21.4 +/- 1.0 kpc
+
+labelsize = 13
+fontsize = 13
+
+xlims = (0.1, 1.1)
+ylims = (15.5, 20.5)
+
+
+my_cmap = matplotlib.colors.LinearSegmentedColormap.from_list('mycm', ['#000080','#44BB44', '#AA0000'])
+
+
+fig = plt.figure()
+ax = fig.add_subplot(111)
+
+# Load in all colour data
+oid, g0, g, r0 = np.loadtxt('ew-mg-all.data', usecols=(0, 19, 9, 20, ), unpack=True)
+ax.scatter(g0 - r0, g0, c='#cccccc', facecolor='none', alpha=0.2)
+
+
+if dodgy_candidate_oid:
+    idx = np.where(oid == dodgy_candidate_oid)[0]
+    if len(idx) == 0:
+        
+        print "Couldn't find the dodgy candidate ID info!"
+        #raise a
+    
+    elif len(idx) > 1:
+        print "OKAY we have too many,.."
+        raise a
+    
+    print idx, oid[idx], g0[idx] - r0[idx], g0[idx]
+    ax.scatter(g0[idx] - r0[idx], g0[idx], facecolor='white', edgecolor='k', s=50)
+    ax.scatter(g0[idx] - r0[idx], g0[idx], facecolor='none', edgecolor='k', s=130, zorder=-1)
+
+# Load in isochrone information
+
+g, r = np.loadtxt('giardi-10gyr-1.5.data', unpack=True)
+ax.plot(g - r, g + newberg_distance_modulus, 'k:', zorder=-10, label='[Fe/H] $=-1.5$ at $21.4$ kpc')
+
+g, r = np.loadtxt('giardi-10gyr-1.74.data', unpack=True)
[…]

### 2012-08-16 2012-oss-mrs/figures/ew-mg.py

@@ -1,0 +1,82 @@
+from scipy.interpolate import splrep, splev
+
+from matplotlib import rc
+rc('font',**{'family':'sans-serif','sans-serif':['Helvetica']})
+## for Palatino and other serif fonts use:
+#rc('font',**{'family':'serif','serif':['Palatino']})
+#rc('text', usetex=True)
+
+fontsize = 13
+labelsize = 13
+
+xlims = (0.4, 1.2)
+ylims = (0, 1.5)
+
+fig = plt.figure()
+ax = fig.add_subplot(111)
+
+ax.set_xlim(xlims)
+ax.set_ylim(ylims)
+
+# Plot our data
+g, r, ew = np.loadtxt('ew-mg-all.data', usecols=(19, 20, 5, ), unpack=True)
+
+# Distinguish upper limits and normal measurements
+idx = np.where(ew < 0)
+g_upperlims, r_upperlims, ew_upperlims = (item.copy() for item in (g[idx], r[idx], ew[idx]))
+
+idx = np.where(ew > 0)
+g, r, ew = g[idx], r[idx], ew[idx]
+
+# Plot everything
+
+# Now plot the upper limits
+ax.errorbar(g_upperlims - r_upperlims, -ew_upperlims, fmt='ko', yerr=0.05, lolims=True, zorder=0)
+ax.scatter(g_upperlims - r_upperlims, -ew_upperlims, edgecolor='none', marker='o', facecolor='w', zorder=1)
+
+ax.scatter(g - r, ew, marker='o', facecolor='none')
+
+
+# Now plot the dividing spline
+
+match_points = np.array([
+    [0.40, 0.35],
+    [0.50, 0.45],
+    [0.70, 0.72],
+    [0.80, 0.80],
+    [0.85, 0.83],
+    [0.90, 0.84],
+    [1.00, 0.81],
+    [1.10, 0.75],
+    [1.20, 0.70]
+])
+# convert to mA
+
+tck = splrep(match_points[:, 0], match_points[:, 1], k=3)
+
+x = np.arange(ax.get_xlim()[0], ax.get_xlim()[1], 0.01)
+y = splev(x, tck)
+
+giants = 0
+for gi, ri, ewi in zip(g, r, ew):
+    idx = np.searchsorted(x, gi - ri) - 1
+    if idx >= len(y):
+        continue
+    
+    if y[idx] >= ewi:
+        giants += 1
+        
[…]

### 2012-08-16 2012-oss-mrs/figures/vgsr-histogram.py

@@ -1,0 +1,55 @@
+ # -*- coding: utf-8 -*-
+
+
+fontsize = 11
+labelsize = 11
+binx = 20.
+
+oss_vgsrs = [75, 135]
+oss_member_count = 10
+oss_vgsr_centroid = oss_vgsrs[0] + 0.5 * (oss_vgsrs[1] - oss_vgsrs[0])
+
+
+
+
+matplotlib.rc('font', **{'sans-serif' : 'Arial',
+                         'family' : 'sans-serif'})
+
+obs_vgsr = np.loadtxt('velocities.data', delimiter=',', usecols=(-1,))
+besancon_vgsr = np.loadtxt('besancon.data', usecols=(-1,))
+
+
+bins = np.arange(-250, 250, binx)
+
+fig = plt.figure()
+obs_ax = fig.add_subplot(111)
+
+hist_obs, bins = np.histogram(obs_vgsr, bins=bins)
+
+
+
+# Normalise the besancon results
+hist_besancon, bins = np.histogram(besancon_vgsr, bins=bins, normed=True)
+hist_besancon *= len(besancon_vgsr) * binx/10.
+
+#obs_ax.hist([obs_vgsr, besancon_vgsr], bins=bins, histtype='bar', color=['grey', 'none'], label=['Observed', u'Besançon'])
+#obs_ax.bar([bins[:-1], bins[:-1]], [hist_obs, hist_besancon], [np.diff(bins), np.diff(bins)], color=['r', 'g'])
+obs_ax.bar(bins[:-1], hist_obs, np.diff(bins)/2, color='#dddddd', label='Observed')
+obs_ax.bar(bins[:-1] + np.diff(bins)[0]/2, hist_besancon, np.diff(bins)/2, color='white', label=u'Besançon (Robin et al. 2003)')
+
+obs_ax.set_xlim(-250, 250)
+obs_ax.set_xlabel('$V_{GSR}$ [km s$^{-1}$]', fontsize=labelsize)
+obs_ax.set_ylabel('$N$', fontsize=labelsize)
+
+patch = Rectangle((oss_vgsrs[0], 0), oss_vgsrs[1] - oss_vgsrs[0], obs_ax.get_ylim()[1], color='g', alpha=0.5, zorder=-1)
+obs_ax.add_patch(patch)
+
+idx = np.searchsorted(bins, oss_vgsr_centroid) - 1
[…]

### 2012-08-16 2012-aqs/draft-aqs.tex
added 2012 aquarius stream paper folder

--- 2012-07-28 2012-oss/draft-oss.tex
@@
 
-\shorttitle{OSS on MIKE}
+\shorttitle{AQS on MIKE}
 \shortauthors{Casey et al}
@@
 
-\title{High Resolution Spectroscopic Analysis of Orphan Stream Giants}
+\title{The First High Resolution Spectroscopic Analysis on the Aquarius Stream}
 
-\author{Andrew R. Casey\altaffilmark{1,2}, Stefan C. Keller\altaffilmark{1}, Frebel, Anna\altaffilmark{2}, Gary Da Costa\altaffilmark{1}, Elizabeth Maunder\altaffilmark{1}}
+\author{Andrew R. Casey\altaffilmark{1,2}, Stefan C. Keller\altaffilmark{1}, Frebel, Anna\altaffilmark{2}, Gary Da Costa\altaffilmark{1}}
 \altaffiltext{1}{Research School of Astronomy \& Astrophysics, Australian National University, Mount Stromlo Observatory, via Cotter Rd, Weston, ACT 2611, Australia}
@@
 
-\keywords{Galaxy: halo, structure --- Individual: Orphan Stream --- Stars: K-giants}
+\keywords{Galaxy: halo, structure --- Individual: Aquarius Stream --- Stars: FGK-giants}
 
@@
 
-\begin{deluxetable*}{lcccccc}
+\begin{deluxetable*}{lcccccccc}
 \tablecolumns{2}
@@
 	\colhead{$\delta$} &
+	\colhead{Observed} &
 	\colhead{Air mass} &
@@
 	\colhead{Comment} \\
- & (J2000) & (J2000) & & (") & (px$^{-1}$) & (km s$^{-1}$) &
+ & (J2000) & (J2000) & & & (") & (px$^{-1}$) & (km s$^{-1}$) & \\
 }
 \startdata
-HD 136316 & 15 22 17.2 & $-$53 14 13.9 & ? & 1.118 & 335 & $-38.21 \pm 1.09$ & \\
-HD 141531 & 15 49 16.9 & 09 36 42.5 & ? & 1.309 & 280 & $2.63 \pm 1.02$ & \\
-HD 142948 & 16 00 01.6 & $-$53 51 04.1 & ? & 1.107 & 271 & $30.26 \pm 0.87$ & \\
-HD 41667 & 06 05 03.7 & $-$32 59 36.8 & ? & 1.005 & 272 & $297.79 \pm 1.72$ & \\
-HD 44007 & 06 18 48.6 & $-$14 50 44.2 & ? & 1.033 & 239 & $163.41 \pm 1.25$ & \\
-HD 47536 & 06 37 47.7 & $-$32 20 20.1 & ? & 1.002 & 257 & $78.87 \pm 1.21$ & \\
-HD 76932 & 08 58 44.2 & $-$16 07 54.2 & ? & 1.158 & 289 & $119.18 \pm 1.18$ & \\
-HD 84903 & 09 47 19.3 & $-$41 27 04.9 & ? & 1.260 & 294 & $77.65 \pm 1.41$ & \\
-HD 59984 & 07 32 05.7 & $-$08 52 56.1 & ? & 1.111 & 402 & $55.74 \pm 0.53$ & \\
-HD 60060 & 07 29 59.6 & $-$52 39 04.3 & ? & 1.127 & 414 & $25.60 \pm 1.08$ & \\
-HD 60228 & 07 30 30.8 & $-$54 23 58.6 & ? & 1.139 & 338 & $48.58 \pm 1.67$ & \\
-OSS 1    & 10 46 50.6 & $-$00 13 17.9 & 0.8 & 1.363 & 48 & $218.15 \pm 1.72$ & \\
-OSS 2    & 10 47 17.8 &    00 25 06.9 & ? & 1.995 & 59 & $222.16 \pm 1.28$ & \\
-OSS 3    & 10 47 30.3 & $-$00 01 22.6 & 0.71 & 1.156 & 49 & $226.35 \pm 1.27$ & \\
-OSS 4    & 10 49 08.3 &    00 01 59.3 & ? & 1.881 & 48 & $227.50 \pm 2.05$ & Poor seeing.\\
-OSS 5    & 10 50 33.7 &    00 12 18.3 & ? & 1.295 & 31 & $249.01 \pm 2.58$ & Poor seeing. \\
-HR 6141  & 16 30 12.3 & $-$25 06 52.0 & ? & 1.003 & 406 & - & Telluric std.
+
+AQS 1 & 12 43 42.9 & -44 40 35.8 & April 2011 & ? & ? & 260 & ? & ? \\
+AQS 2 & 12 51 24.8 & -13 29 31.3 & April 2011 & ? & ? & 232 & ? & ? \\
+
 \enddata
@@
 
-% HDs 59984, 76932, 136316, 84903, 44007, 142948
-% OS 2,4,5,6,8 (file name convention) here is OS 1,2,3,4,5
-
-\subsection{Target Selection and Observations}
-
-\subsection{Data Reduction}
-The data were reduced using the latest version of the MIKE pipeline outlined in \citet{Kelson;2003}.
-For comparison we also reduced our HD 59984 spectra using standard methods in \textsc{IRAF} and found no noteworthy difference between the reduced products.
-Individual frames for each object were co-added before analysis.
-We carefully normalised every echelle order using cubic splines.
-Overlapping normalised orders on each CCD were stitched together, such that a continuous normalised spectra from each CCD remains.
-We do not include line measurements that are susceptible to telluric absorption, so no telluric corrections were made.
-
-\subsection{Radial Velocities}
-We measured radial velocities for every target by cross-correlating each normalised red  spectrum with a synthetic template.
-Our synthetic template was generated in \textsc{MOOG} using a \citet{Castelli-Kurucz;2004} model atmospheres with $T_{eff} = 4500$ K, $\log{g} = 2.5$, [Fe/H] = -1.5, [$\alpha$/Fe] = 0.0 and no convective overshoot.
-The line list of \citet{Kirby;et-al_2008} was employed to generate spectra between $845$ nm $< \Lambda < 870$ nm.
-Both the blue and red co-added, normalised frames were shifted to rest before equivalent width measurements.
-A number of radial velocity and halo standards were observed during this program, and our heliocentric velocities agree excellently with literature values (Table \ref{tab:observed-targets}).
-
-\subsection{Line Measurements}
-
-\subsection{Stellar Parameters}
-
-HD59984 5750 K, 1.55 vt, 3.55 logg -0.95,+0.40,
-================================================
-Fe I EPS 6.52 +/- 0.16 (210 lines)
-Slope, Offset, Corr: 0.01, 6.53, 0.05
-
-Fe I REW
-Slope, Offset, Corr: 0.0, 6.55, 0.00
-
-Fe I lambda
-Slope, Offset, Corr: 3.84e-05, 6.35, 0.17
-
-Fe II EPS 6.53 +/- 0.18 (22 lines)
-
-Fe II REW
-Slope, Offset, Corr: 0.07, 6.94, 0.09
-
-Fe II lambda
-Slope, Offset, Corr: 1.41e-04, 5.91, 0.36
-
-OSS 1:
-161.71091670000001 -0.2216389
-SDSS DR 8 closest source is 3.793" away, and 17.47 mag in g
-ugriz: 18.823 17.467 16.934 16.712 16.597
-No reddenning corrected for, Jester 2005 transformations
-UBVRI = 18.06255 17.88487 17.14253 16.68055 16.24855
-B -V = 0.74
-Estimating a [Fe/H] = -1.9 and using Alonso et al 1999 eq 4 yields 4986 K
-
-With the red arm only:
-5110 / 1.20 / 3.10 / -1.14 / 0.40
-(with [Fe/H] = -1.14, the estimated temp from photometry is 5014 K)
-
-Fe I Abundance 6.42 +/- 0.19 (106 lines)
-S, O, C: 0.00, 6.41, 0.01
-
-Reduced EW S, O, C: 0.10, 6.87, 0.08
-
-Lambda S, O, C: 9.41e-05, 5.89, 0.28
-
-Fe II Abundance: 6.44 +/- 0.17 (8 lines)
-
-Reduced EW S, O, C: -0.09, 6.01, -0.09
-
-Lamba S, O, C: 1.64e-04, 5.53, 0.53
-
-Wiith the red and blue, starting at 5000K, -1.9
-
-5070 / 1.6 / 2.9 / -1.4 / 0.40
-
-Fe I Abundance: 6.15 +/- 0.25 (117 lines)
-SOC: 0.01, 6.12, 0.03
-
-Reduced EW SOC: 0.00, 6.12, 0.00
-Lambda SOC: 1.41e-04, 5.42, 0.42
-
-Fe II Abundance: 6.14 +/- 0.19 (19 lines)
-
-Reduced EW SOC: -0.04, 5.95, -0.05
-Lambda SOC: 1.09e-04, 5.61, 0.41
-
-Followed from this (USING RED AND BLUE data) and excluded outliers.
-
-5040 / 1.4 / 2.8 / -1.2 / 0.40 ("FINAL" files) <-- doesn't quite fit on isochrone, but close-ish
-Fe I abundance: 6.24 +/- 0.16 (149 lines)
-SOC: 0.02, 6.18, 0.13
-REW SOC: 0.03, 6.39, 0.04
-Lambda SOC: 0.81e-05, 5.78, 0.38
-
-Fe II abundance: 6.19 +/- 0.16 (15 lines)
-REW SOC: 0.03, 6.33, 0.04
-Lambda SOC: 1.08e-04, 5.65, 0.46
-
-ALPHA ELEMENTS Mg, Si, Ca, Ti <-> (12, 
-==============
-
-Mg I: 6.56 +/- 0.10 (4 lines), Solar 7.60 +/- 0.04
-Inspected all four line profiles; they look perfect.
-SOC: // // 4.51e-05, 6.29, 0.29
-[Mg I/Fe] = 0.16 +/- 0.10
-
-Si I: 6.57 +/- 0.23 (4 lines), Solar 7.51 +/- 0.03
-Inspected all four line profiles; they all look great (one is 'reasonable')
-SOC: 0.04, 6.36, 0.22 // 0.17, 7.37, 0.28 // 7.75e-05, 6.11, 0.23
-[Si I/Fe] = 0.26 +/- 0.23
-
-Ca I: 5.48 +/- 0.14 (14 lines), Solar 6.34 +/- 0.04
-Inspected all lines; they all look good.
-SOC: // // 1.44e-04, 4.60, 0.70
-[Ca I/Fe] = 0.34 +/- 0.14
-
-Ti I: 3.73 +/- 0.15 (21 lines) Solar 4.95 +/- 0.05
-Inspected all lines; they all look good.
-SOC: // 0.36, 5.49, 0.42 // 2.94e-05, 3.59, 0.08
-[Ti I/Fe] = -0.02 +/- 0.15
-
-Ti II: 3.91 +/- 0.10 (25 lines) Solar 4.95 +/- 0.05
-SOC: -0.02, 3.91, -0.09 // 0.22, 4.93, 0.43 // -2.70e-05, 4.01, -0.10
-[Ti II/Fe] = 0.16 +/- 0.10
-
-OSS 2: JMK = 0.633 (no reddenning correction)
-4571.9947676752899 K using Alonso 1999 paper
-SDSS (DR8) u g r i z -- searched at 161.8240417 0.4185833, found source 2.05" away
-18.063 16.252 15.479, 15.146, 14.950
-
-inspected all profiles + saved only Fe ones that were good in red + blue
-================================================
-4600 K, 1.85, 0.80, -1.77, 0.40
-
-Fe I: 5.73 +/- 0.14 (139 lines)
-
-Fe I EPS
-S, O, C: 0.00, 5.72, 0.01
-
-Fe I REW
-S, O, C: -0.03, 5.58, -0.04
-
-Fe I Lambda:
-S, O, C: 3.98e-05, 5.51, 0.21
-
-Fe II: 5.72 +/- 0.16 (21 lines)
-
-Fe II EPS: None
-
-Fe II REW S, O, C: 0.03, 5.84, 0.05
-
-Fe II Lambda: 2.1e-05, 5.58, 0.09
-
-=================================
-Incorporating isochrones in:
-4550 K / 1.85 / 0.8 / -1.80 / 0.40
-
-Fe I Abundance: 5.71 +/- 0.16 (112 lines)
-Fe I EPS S, O, C: 0.01, 5.66, 0.10
-
-Fe I REW S, O, C: -0.03, 5.54, -0.04
-
-Fe I Lambda: 8.01e-06, 5.66, 0.03
-
-Fe II Abundance: 5.75 +/- 0.10 (8 lines)
-
-Fe II REW S, O, C: 0.35, 7.52, 0.68
-
-Fe II Lambda = -1.29e-04, 6.48, -0.70
-
-Loaded in all local line list from OSS2/os_4_all_global_auto.moogew
-
-ALPHA ELEMENTS
-Ne, Mg, Si, S, Ar, Ca, Ti
-
-Ne I, II -- no lines present in line list
-
-Mg I: 5.90 +/- 0.10 (6 lines), Solar 7.60 +/- 0.04
-Inspected all six line profiles; they look perfect.
-SOC: 0.05, 5.74, 0.35 // 0.00, 5.93, 0.00 // 3.03e-05, 5.77, 0.15
-[Mg I/Fe] = 0.10 +/- 0.10
-
-Si
-5565 very small but clean (6 mA)
-4102 is great
-3095 is a bit blended
-Si I: 5.66 +/- 0.26 (3 lines), Solar 7.51 +/- 0.03
-Inspected the three lines we have, they don't look fantastic...  3095 could go..
-SOC -0.14, 6.14, -0.78 // 0.29, 7.12, 0.92
-[Si I/Fe] = -0.05 +/- 0.26
-
-S I, II -- no lines present in line list: they are mainly in the infrared
-
-Ar I, II -- no lines present in line list
-
-Ca I: 4.79 +/- 0.12 (17 lines), Solar 6.34 +/- 0.04
-Inspected all the lines I have; they all look reasonable. Outliers could be confidently excluded.
-SOC: // 0.48, 7.08, 0.77 // -9.21e-05, 5.30, -0.51
-[Ca I/Fe] = 0.25 +/- 0.12
-
-Ti I: 3.00 +/- 0.16 (20 lines), Solar 4.95 +/- 0.05
-Inspected all the lines, excluded some dodgey measurements and duplicates, then clipped outliers.
-SOC: // -0.04, 2.83, -0.04 // 6.68e-05, 2.69, 0.18
-[Ti I/Fe] = -0.15 +/- 0.16
-
-Ti II: 3.19 +/- 0.14 (23 lines), Solar 4.95 +/- 0.05
-Inspected all the lines, excluded some dodgey measurements & duplicates then clipped outliers.
-SOC: 0.00, 3.23, 0.01 // 0.22, 4.27, 0.28 // -4.71e-05, 3.44, -0.13
-[Te II/Fe] = 0.04 +/- 0.14
-
-Na I: 4.21 +/- 0.05 (3 lines), Solar 6.24 +/- 0.04
-Inspected all three line profiles; they look perfect.
-SOC: -0.06, 4.23, -0.96 // 0.11, 4.71, 0.95
-[Na I/Fe] = -0.23 +/- 0.05
-
-OSS 3: 161.8761667 -0.0229444
-Not in 2mass (3 arcsecond cone)
-SDSS  Closest point is 2.85 arcseconds away at 17.4 mag in g
-u g r i z (SDSS DR 8)
-18.881 17.400 16.748 16.497 16.316
-Using Alonso et al 1999 eq 4 relation, and Jester 2005 transformations:
-UBVRI = 18.13946 17.86428 17.00532 16.51173 16.05073
-BMV = 0.85895999999999972
-Tried inital guess of [Fe/H] as = -1.9 gives 4719 K, giving -1.7 gives 4735 K
-using -1.9 guess and starting at 4719 K
-
-Best so far (before excluding outliers)
-4800 K, 1.90, 1.70, -1.87, 0.40
-
-after outliers
-4810, 1.85, 1.70, -1.87, 0.40
-
-Fe I 5.68 +/- 0.18 (181 lines)
-Abundances
-S, O, C: 0.00, 5.67, 0.03
-
-Reduced EW
-S, O, C: -0.06, 5.38, -0.08
-
-Lambda S, O, C: 8.33e-05, 5.25, 0.34
-
-Fe II 5.67 +/- 0.23 (26 lines)
-
-Reduced EW S, O, C: 0.07, 6.00, 0.09
-
-Lambda S, O, C: 1.44e-04, 4.95, 0.40
-
-===============
-with isochrones
-4780 / 1.7 / 1.55 / -1.80 / +0.40
-
-Fe I abundance 5.74 +/- 0.13 (112 lines)
-S, O, C: 0.00 5.73 0.03
-Reduced EW SOC: 0.03 5.86 0.04
-Lambda SOC: 3.11e-05, 5.57, 0.13
-
-Fe II abundances 5.69 +/- 0.19 (8 lines)
-Reduced EW SOC: -0.14, 5.03, -0.16
-Lambda SOC: 1.73e-04, 4.75, 0.49
-
-OSS 4
-162.2845417 0.0331389
-In SDSS DR8 found closest 16.4 gmag star at 1.113 arcseconds away
-u g r i z
-17.935 16.440 15.770 15.465 15.299
-no redenning, jester transform, assume -1.9 feh and using B-V ~ 0.88
-Alonso et al 1999 eq 4
-initial start teff = 4693 K
-
-an emp???
-
-4550 /  1.9 / 0.8 / -2.7 / 0.4
-
-Fe I Abundance 4.75 +/- 0.19 (150 lines)
-S, O, C: 0.00, 4.76, 0.01
-
-REW S, O, C: 0.04, 4.95, 0.07
-
-Lambda S, O, C: 4.11e-06, 4.74, 0.01
-
-Fe II Abundance 4.78 +/- 0.16 (18 lines)
-
-REW S, O, C: -0.06, 4.51, -0.09
-
-Lambda S, O, C: 9.90e-05, 4.32, 0.33
-
-Using isochrones:
-
-4670 / 1.95 / 1.10 / -2.70 / +0.40
-Fe I Abundance 4.84 +/- 0.24 (168)
--0.01, 4.88, -0.03
-0.01, 4.93, 0.02
-5e-5, 4.61, 0.15
-
-Fe II Abundance 4.87 +/- 0.21 (21)
--0.01, 4.84, -0.01
-1.09e-04 4.37 0.27
-
-=============
-4580 K / 2.05 / 0.80 / -2.79 / +0.40
-( doesn't quite sit on the expected isochrone)
-
-Fe I abundance: 4.75 +/- 0.17 (128 lines)
--0.01 / 4.77 / -0.05
-0.03 / 4.88 / 0.04
-9.62e-06 / 4.70 / 0.40
-
-Fe II abundance: 4.77 +/- 0.15 (15 lines)
--0.01 / 4.69 / -0.02
-
-6.49e-05 / 4.44 / 0.15
-
-OSS 5
-162.6405417 0.2050833
-SDSS DR8 nearest target is 1.196" away at 18th magnitude in g
-ugriz = 19.628 17.997 17.338 17.065 16.908
-No reddenning correction and using Jester 2005:
-UBVRI = 18.85619 18.46401 17.59819 17.08062 16.59762
-bmv = 0.87
-
-Guessing [Fe/H] = -1.9 yields Teff = 4709 K
-Arbitrarily chosing lines only redward of 4400 A
-
-5200 / 2.0 / 2.9 / -0.95 / 0.40
-
-Fe I 6.60 +/- 0.22 (90 lines)
-0.00, 6.62, 0.01
-0.00, 6.65, 0.00
-9.2e-5, 6.12, 0.27
-
-Fe II 6.60 +/- 0.35 (17 lines)
-0.12, 7.14, 0.07
-9.81e-05, 6.09, 0.20
-
-\subsubsection{Effective Temperature}
-
-\subsubsection{Surface Gravity}
-
-\subsection{Uncertainty Analysis}
-
-\section{Abundances}
-
-\section{Discussion}
-
-\section{Results}
-
-\section{Conclusions}
-
 \end{document}

### 2012-08-16 2012-oss-hrs/draft-oss.tex
added 2012 oss HRS paper folder

--- 2012-08-04 2012-oss/draft-oss.tex
@@
 
-\shorttitle{First HRS Analysis on the Orphan Stream}
+\shorttitle{Chemistry of the Orphan Stream II}
 \shortauthors{Casey et al}
@@
 
-\title{The First High-Resolution Spectroscopic Analysis on the Orphan Stream}
+\title{Chemistry of the Orphan Stream II: The First High-Resolution Spectroscopic Analysis on the Orphan Stream}
 
@@
 
-\subsection{Stellar Parameters}
+\newpage
 
-\subsubsection{Effective Temperature}
-
-\subsubsection{Surface Gravity}
-
-\subsection{Uncertainty Analysis}
-
-\begin{deluxetable}{lcccccccccl}
+\begin{deluxetable*}{lcccccccccl}
 \tablecolumns{1}
@@
 \enddata
-\end{deluxetable}
+\end{deluxetable*}
 
-\begin{deluxetable}{lccccccccccccccccc}
+\newpage
+\newpage
+
+\newpage
+\newpage
+
+\begin{deluxetable*}{lccccccccccccccccc}
 \tablecolumns{18}
@@
 \tabletypesize{\scriptsize}
-\tablecaption{Chemical Abundances\label{tab:stellar-parameters}}
+\tablecaption{Standard Star Chemistries\label{tab:stellar-parameters}}
+\tablehead{
+&  \multicolumn{5}{c}{HD 142948} & \colhead{} &
+	\multicolumn{5}{c}{HD 141531} & \colhead{} &
+	\multicolumn{5}{c}{HD 44007} \\
+	\cline{2-6} \cline{8-12} \cline{14-18} \\
+\colhead{Species} 
+ & $\log\epsilon$(X) & [X/H] & [X/Fe] & $N$ & $\sigma$ &
+ & $\log\epsilon$(X) & [X/H] & [X/Fe] & $N$ & $\sigma$ &
+ & $\log\epsilon$(X) & [X/H] & [X/Fe] & $N$ & $\sigma$
+}
+\startdata
+
+Na \textsc{I} & 5.99 & $-$0.25 & \phn0.53 &  1 & \nodata\tablenotemark{a} % HD 142948
+             && 4.56 & $-$1.68 & \phn0.04 &  2 & 0.07    % HD 141531
+             && 4.53 & $-$1.71 & \phn0.06 &  3 & 0.05 \\ % HD 44007
+Mg \textsc{I} & 7.21 & $-$0.39 & \phn0.39 &  4 & 0.06
+             && 6.26 & $-$1.34 & \phn0.38 &  4 & 0.12
+             && 6.16 & $-$1.44 & \phn0.33 &  3 & 0.04 \\
+O \textsc{I}  & 8.54 & $-$0.15 & \phn0.63 &  2 & 0.05
+             && 7.51 & $-$1.18 & \phn0.54 &  2 & \phn0.00\tablenotemark{a}
+             && 7.50 & $-$1.19 & \phn0.58 &  1 & \nodata\tablenotemark{a} \\
+Si \textsc{I} & 6.67 & $-$0.84 &  $-$0.06 &  2 & 0.07
+             && 5.86 & $-$1.65 & \phn0.07 &  3 & 0.20
+             && 6.19 & $-$1.32 & \phn0.45 &  3 & \phn0.02\tablenotemark{a} \\
+Ca \textsc{I} & 5.83 & $-$0.51 & \phn0.27 &  8 & 0.07
+             && 4.91 & $-$1.43 & \phn0.29 & 12 & 0.09
+             && 5.02 & $-$1.32 & \phn0.45 & 16 & 0.08 \\
+Ti \textsc{I} & 4.26 & $-$0.69 & \phn0.09 & 15 & 0.11
+             && 3.09 & $-$1.86 &  $-$0.14 & 19 & 0.11
+             && 3.32 & $-$1.63 & \phn0.14 & 19 & 0.08 \\
+Ti \textsc{II}& 4.53 & $-$0.42 & \phn0.36 & 18 & 0.11
+             && 3.53 & $-$1.42 & \phn0.30 & 22 & 0.11
+             && 3.50 & $-$1.45 & \phn0.32 & 32 & 0.12 \\        
+Sc \textsc{II}& ?    &   ?     &    ?     &  ? &  ?
+             && 1.60 & $-$1.55 & \phn0.17 &  7 & \phn0.04\tablenotemark{a}
+             && 1.46 & $-$1.69 & \phn0.08 &  9 & 0.06 \\
+Fe \textsc{I} & 6.72 & $-$0.78 & \phn0.00 & 104& 0.14
+             && 5.78 & $-$1.72 & \phn0.00 & 100& 0.11
+             && 5.72 & $-$1.78 & \phn0.00 & 135& 0.10 \\
+Fe \textsc{II}& 6.73 & $-$0.77 & \phn0.01 & 13 & 0.18
+             && 5.86 & $-$1.64 & \phn0.08 & 11 & 0.10
+             && 5.70 & $-$1.80 &  $-$0.02 & 14 & 0.11 \\
+V \textsc{I}  & 6.27 &\phn2.34 & \phn3.12 &  2 & \phn0.02\tablenotemark{a}
+             && 4.69 &\phn0.76 & \phn2.50 &  2 & 0.22
+             && 4.63 &\phn0.70 & \phn2.47 &  3 & \phn0.04\tablenotemark{a} \\
+Cr \textsc{I} & 4.66 & $-$0.98 &  $-$0.20 &  6 & 0.07
+             && 3.61 & $-$2.03 &  $-$0.29 & 10 & 0.08
+             && 3.67 & $-$1.97 &  $-$0.20 & 13 & 0.06 \\
+Cr \textsc{II}& 4.83 & $-$0.81 &  $-$0.03 &  3 & \phn0.04\tablenotemark{a}
+             && 4.06 & $-$1.58 & \phn0.16 &  2 & 0.07
+             && 4.00 & $-$1.64 & \phn0.13 &  5 & 0.05 \\
+Mn \textsc{I} & 4.98 & $-$0.45 & \phn0.33 &  4 & 0.12
+             && 3.72 & $-$1.71 & \phn0.03 &  5 & 0.18
+             && 3.44 & $-$1.99 &  $-$0.22 &  6 & 0.22 \\
+Co \textsc{I} & 4.06 & $-$0.93 &  $-$0.15 &  3 & \phn0.01\tablenotemark{a}
+             && 2.97 & $-$2.02 &  $-$0.28 &  3 & 0.15
+             && 3.13 & $-$1.86 &  $-$0.09 &  4 & 0.10 \\
+Ni \textsc{I} & 5.52 & $-$0.70 & \phn0.08 &  8 & 0.08
+             && 4.33 & $-$1.89 &  $-$0.15 & 13 & 0.09
+             && 4.34 & $-$1.88 &  $-$0.11 & 13 & 0.09 \\
+\enddata
+\tablenotetext{a}{Minimum uncertainty of $\pm$0.05 dex adopted for this measurement.}
+\end{deluxetable*}
+
+\newpage
+\newpage
+
+\begin{deluxetable*}{lccccccccccccccccc}
+\tablecolumns{18}
+\tablewidth{\textwidth}
+\tabletypesize{\scriptsize}
+\tablecaption{Orphan Stream Chemistry\label{tab:stellar-parameters}}
 \tablehead{
@@
 \startdata
-Na \textsc{I} & ? & ? & ? & ? & ?
-             && $4.21$ & $-2.03$ &    $-0.23$ &   $3$ & $0.05$
-             && $4.42$ & $-1.82$ &    $-0.03$ &   $3$ & $0.07$  \\
+Na \textsc{I} & ? & ? & ? & ? & ?                              % OSS 1
+             && $4.21$ & $-2.03$ &    $-0.23$ &   $3$ & $0.05$ % OSS 2
+             && $4.42$ & $-1.82$ &    $-0.03$ &   $3$ & $0.07$ % OSS 3
+             \\
 Mg \textsc{I} & $6.56$ & $-1.04$ & \phs$0.16$ &   $4$ & $0.10$  
@@
              && $5.71$ & $-1.79$ & \phs$0.00$ &  $20$ & $0.16$  \\
+Sc \textsc{II}&&&&&  % OSS 1
+             && $1.10$ & $-2.05$ &    $-0.27$ &   $7$ & $0.07$ 
+             && $1.25$ & $-1.90$ &    $-0.11$ &  $10$ & $0.10$ \\
+V \textsc{I}  &&&&&  % OSS 1
+             && $4.50$ & \phs$0.57$ & $-1.21$ &   $4$ & $0.17$ 
+             && $4.57$ & \phs$0.64$ & $-1.15$ &   $3$ & $0.03$ \\
+Cr \textsc{I} &&&&&  % OSS 1
+             && $3.63$ & $-2.01$ &    $-0.23$ &  $12$ & $0.08$ 
+             && $3.63$ & $-2.01$ &    $-0.22$ &  $15$ & $0.11$ \\
+Cr \textsc{II}&&&&&  % OSS 1
+             && $3.81$ & $-1.83$ &    $-0.05$ &   $3$ & $0.11$ 
+             && $3.99$ & $-1.65$ & \phs$0.14$ &   $3$ & $0.04$ \\
+Mn \textsc{I} &&&&&  % OSS 1
+             && $3.42$ & $-2.01$ &    $-0.23$ &   $4$ & $0.04$ 
+             && $3.41$ & $-2.02$ &    $-0.23$ &   $6$ & $0.14$ \\
+Co \textsc{I} &&&&&  % OSS 1
+             && $3.14$ & $-1.85$ &    $-0.07$ &   $3$ & $0.19$ 
+             && $3.00$ & $-1.99$ &    $-0.20$ &   $5$ & $0.17$ \\
+Ni \textsc{I} &&&&&  % OSS 1
+             && $4.24$ & $-1.98$ &    $-0.20$ &   $7$ & $0.07$ 
+             && $4.32$ & $-1.90$ &    $-0.11$ &  $13$ & $0.12$ \\
 
@@
 \enddata
-\end{deluxetable}
+\end{deluxetable*}
 
-\section{Abundances}
+\newpage
+\newpage
 
-\section{Discussion}
-
-\section{Results}
-
-\section{Conclusions}
+\newpage
+\newpage
 

### 2012-08-16 2012-segue-1/rlunnan_v1.tex
added 2012 segue 1 paper + data. This is the pre-draft before it was re-sent out to the co-authors

\documentclass[manuscript]{aastex}
%\documentclass[11pt,preprint]{aastex}
%% preprint2 produces a double-column, single-spaced document:
%\documentclass{emulateapj}
%\documentclass[preprint2]{aastex}

\bibliographystyle{apj}
\usepackage{epsfig,graphicx}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage{lscape}
\usepackage{comment}
\usepackage{threeparttable}

\begin{document}

\title{The 300 km~s$^{-1}$ stellar stream near Segue\,1: Insights From High-Resolution Spectroscopy of its brightest star}
\author{Ragnhild Lunnan$^1$,  Anna Frebel$^1$, John E. Norris$^2$, Rosemary F. G. Wyse$^3$ and Gerard Gilmore$^4$}
\affil{$^1$ Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138, USA}
\affil{$^2$ Research School of Astronomy \& Astrophysics, The Australian National University, Mount Stromlo Observatory, Cotter Road, Weston, ACT 2611, Australia}
\affil{$^3$ The Johns Hopkins University, Department of Physics \& Astronomy, 300 N. Charles Street, Baltimore, MD 21218, USA}
\affil{$^4$ Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK}
\email{rlunnan@cfa.harvard.edu}

\begin{abstract}
In kinematic surveys of the faint satellite galaxy Segue\,1, an overdensity of stars with velocities around 300~km~s$^{-1}$ has been seen, first seen in \citet{Geha2009} and interpreted as a possible stellar stream. We present a high-resolution spectrum and abundance analysis of Segue1-11, the brightest likely stream member star from the kinematic sample of \citet{Norris2010a}. We determine a metallicity of [Fe/H] $ = -1.44$ for Segue1-11, and find abundance patterns similar to typical halo stars at this metallicity. Comparing our stellar parameter solution to theoretical isochrones, we estimate a distance of $18 \pm 7$ kpc. Both the metallicity and distance estimates are in good agreement with what can be inferred from comparing the SDSS photometric data of the stream stars to globular cluster sequences. While several other structures overlap with the stream in this part of the sky, the combination of kinematic, chemical and distance information makes it unlikely that these stars are associated with either the Segue\,1 galaxy, the Sagittarius stream or the Orphan stream.

\end{abstract}

\keywords{Galaxy: halo -- Galaxy: kinematics and dynamics -- stars: abundances}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}
\label{sec:intro}

In the $\Lambda$CDM model, structure builds up hierarchically, with smaller objects merging to build larger ones. One consequence of this is stellar streams in the galactic halo, produced as accreted objects are tidally disrupted (see e.g. \citealt{Lynden-Bell1995} and references therein). A well-known example is the stream extending from the Sagittarius dwarf spheroidal, which has been traced more than one full wrap around the Milky Way \citep[e.g.][]{Ibata1994, Majewski2003}. In a particularly busy piece of sky dubbed the ``Field of Streams'' \citep{Belokurov2006b}, at least two wraps of the Sagittarius stream as well as several other structures are visible.

A new velocity structure in this field has recently been discovered overlapping with the ultra-faint object Segue\,1 \citep{Belokurov2007}: Radial velocity data to determine Segue\,1's velocity dispersion by \citet{Geha2009} revealed a group of stars moving near 300~km~s$^{-1}$. The same overdensity of stars at this velocity was seen by Norris et al. (2010; hereafter N10)\nocite{Norris2010a}, who targeted Segue\,1 stars in the RGB locus, and in the larger spectroscopic sample of Segue\,1 stars of Simon et al. (2011; hereafter S11)\nocite{Simon2011}. The stars have so far been interpreted as part of a stellar stream, and we shall refer to it as the ``300~km~s$^{-1}$ stream'' throughout this paper. Since the full extent of this structure has not been mapped out, however, we note that it is also possible these stars belong to a bound object.

From SDSS photometry, one can get an estimate of the distance and metallicity of the stream by comparing the color-magnitude diagram to globular cluster sequences and isochrones. To further characterize the stream chemically, however, high-resolution spectroscopy is necessary. Here, we present the first high-resolution spectrum and detailed abundance analysis of a star in the 300~km~s$^{-1}$ stream.

This paper is organized as follows. We briefly discuss the sample from which the main target for high-resolution spectroscopy was selected in Section~\ref{sec:medres}. The observations and basic data analysis of our target star is presented in Section~\ref{sec:obs}, and the abundance analysis in Section~\ref{sec:abund}. We interpret the results and discuss the nature and potential origin of the stream in Section~\ref{sec:char}. Our conclusions are summarized in Section~\ref{sec:conc}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Stream sample and target selection}
\label{sec:medres}

There are two existing medium-resolution spectroscopic studies of the region around Segue\,1, N10 and S11. N10's data was obtained with the Anglo-Australian Telescope's AAOmega spectrograph, which can take simultaneous spectra of 400 targets over a field 2$^{\circ}$ in diameter. They were targeting stars in the RGB locus. S11, on the other hand, were using the {\small DEIMOS} spectrograph on the KeckII telescope, focusing on an area within $\sim 15$\arcmin of the center of Segue\,1, and going deeper than N10. Table~\ref{tab:members} lists all stars (52 total) in the two samples with heliocentric radial velocities higher than 240~km~s$^{-1}$, i.e. stars with higher velocities than consistent with Segue\,1 membership and so potential stream candidates. This includes four targets from the AAOmega sample not published in N10 due to slightly lower confidence in the radial velocity measurement.

Figure~\ref{fig:col_mag} summarizes the properties of the two samples. The top left panel shows a histogram of the heliocentric radial velocities measured. The central peak ($\sim$ 270-330~km~s$^{-1}$) has a mean velocity of 300~km~s$^{-1}$ and a dispersion of 10.3~km~s$^{-1}$. Considering the independent N10 and S11 samples separately we still arrive at a dispersion of 10~km~s$^{-1}$ for the central peak, and similar means (303~km~s$^{-1}$ for N10 versus 298~km~s$^{-1}$ for S11). It is not clear whether the intermediate ``bridge'' candidates with 240~km~s$^{-1}$ $< v_{helio} < $270~km~s~$^{-1}$ or the three extreme-velocity stars with $v_{helio} > $ 340~km~s$^{-1}$ should be considered part of the same structure, but follow-up observations tracing the stream over a larger field of view could resolve this. Either way, the mean velocity of this structure is extreme, and the dispersion is resolved and high -- it is not a cold stream.

The top right panel of Fig.~\ref{fig:col_mag} shows the color-magnitude diagram of all the stream candidate stars from Table~\ref{tab:members}. Here, stream candidates are shown as black circles. (Three stars redder than $(g-i) = 1.2 $ are not shown.) For comparison, the green triangles show radial velocity members of the Segue\,1 dwarf galaxy, which was the target of the N10 and S11 studies. Open symbols show stars from the N10/AAO sample, while filled symbols are from the S11 sample. Note that the N10 sample covers a much larger field of view but does not go as deep -- as a result, most of the bright stream stars, including our target (star symbol), show up in this sample. In order to illustrate the photometric criteria used in the samples, the blue and red dots show the stars observed by N10 and S11, respectively, that meet their photometric selection cut but are radial velocity non-members of Segue\,1 and the stream.

The solid line shows the M5 cluster sequence \citep{An2008}, which gives a good fit to the stream main sequence and subgiant branch when shifted to a distance of 18~kpc. The metallicity of M5 is [Fe/H] $= -1.3$, and so the SDSS photometry suggests that the stream is slightly more metal-rich than Segue\,1. The red giant branch of the stream is bluer than this sequence, however, and is better fit by e.g. the RGB of the more metal-poor cluster M92.

There are six stream candidate stars brighter than $r = 19$, and thus possible candidates for high-resolution spectroscopy. Our chosen target (SDSSJ100914.95+155948.4; the first star in Table~\ref{tab:members}) is marked with an open star symbol. It is identified as ``Segue1-11'' in N10, and we shall refer to it by this designation throughout the paper. Its location in the color-magnitude diagram indicates that it is most likely a red giant, though it could also be consistent with a horizontal branch at this distance. Both its colors, and the radial velocity of 301~km~s$^{-1}$ measured by N10 are consistent with stream membership. The medium-resolution spectrum indicated a metallicity of [Fe/H]$\simeq -0.7$. Accordingly, we deemed it the best candidate for high-resolution spectroscopy follow-up.

The nature of the other five bright stars is less clear. As noted in \citet{Geha2009}, random halo stars at these extreme velocities are very rare. If they indeed were turnoff stars, the stream would have a coherent velocity over four magnitudes in distance modulus, which also seems unlikely given orbits. The three stars around $r\sim 17.5$ could be RHB stars, but if so raises the question of why we do not see the expected, more numerous red giants. The nature of the very bright star at $r = 15.8$ is also not understood. To resolve these questions, getting spectra of these brighter stars could provide more insight.

Finally, the spatial coverage of the two samples is shown in the two bottom panels. The brighter stream stars in the N10 sample (left) extend at least over 1$^{\circ}$ on the sky; the deeper sample of S11 (right) only covers a 15\arcmin radius around the center of Segue\,1. The box size here represents the full field of view observed in the N10 sample, and so for the lower left panels, again, all stars observed by N10 are shown to better illustrate the distribution. Follow-up observations to determine the full extent of this stream on the sky, as well as deeper observations in a larger region than that covered by S11, would be very important for better understanding and characterizing this structure.

\begin{table}
 \begin{threeparttable}
  \begin{center}
    \caption{Stream Member Candidate Stars}
    \label{tab:members}
    {\tiny
    \begin{tabular}{c c c c c c}
     \hline \hline

       Identifier                    & $g$     &  $r$    &    $i$    & $v_{hel}$ & Ref.       \\ \hline  
     SDSSJ100914.95+155948.4\tnote{a}     & 17.997   & 17.495   & 17.262     &  307  & N10     \\
     SDSSJ100740.13+160309.7\tnote{b}    & 19.965   & 19.551   & 19.448     &  298	& N10     \\
     SDSSJ100659.01+154418.8         & 19.721   & 19.333   & 19.144     &  307	& N10     \\ 
     SDSSJ100651.80+154941.5         & 20.365   & 20.049   & 19.911     &  300 	& AAO     \\
     SDSSJ100619.95+154612.7         & 20.094   & 19.786   & 19.679     &  315 	& AAO     \\
     SDSSJ100612.02+154548.4         & 20.080   & 19.626   & 19.616     &  327	& N10     \\
     SDSSJ100530.59+155418.1         & 19.831   & 19.493   & 19.314     &  305	& N10     \\
     SDSSJ100627.73+155408.6         & 20.155   & 19.880   & 19.711     &  300	& AAO     \\
     SDSSJ100647.74+161330.1         & 20.011   & 19.704   & 19.516     &  300  & AAO     \\
     SDSSJ100658.49+162045.6         & 19.840   & 19.379   & 19.187     &  295	& N10     \\
     SDSSJ100839.66+162826.7         & 19.169   & 18.739   & 18.608     &  288	& N10     \\   
     SDSSJ100600.16+160518.6         & 20.220	& 19.688   & 19.518	&  242  & N10     \\
     SDSSJ100618.74+160339.0         & 21.678   & 21.147   & 20.906     &  268  & S11     \\
     SDSSJ100619.99+160042.1         & 21.705   & 21.417   & 21.180     &  305	& S11     \\
     SDSSJ100630.89+161512.1         & 21.479   & 21.131   & 20.952     &  321	& S11     \\
     SDSSJ100642.76+155709.3         & 21.562   & 21.233   & 21.029     &  291	& S11     \\
     SDSSJ100646.78+160608.3         & 20.534   & 20.221   & 20.076     &  294	& S11     \\
     SDSSJ100648.52+160958.1         & 20.279   & 19.980   & 19.798     &  306	& S11     \\
     SDSSJ100650.83+160351.2         & 22.137   & 21.952   & 21.838     &  312	& S11     \\
     SDSSJ100654.23+155520.7         & 22.127   & 21.533   & 21.290     &  268	& S11     \\
     SDSSJ100656.13+160660.0         & 21.347   & 21.099   & 20.994     &  302	& S11     \\
     SDSSJ100658.54+155748.9         & 21.562   & 21.096   & 20.840     &  290	& S11     \\
     SDSSJ100704.58+160130.8         & 21.229   & 20.814   & 20.762     &  295	& S11     \\
     SDSSJ100704.63+160812.6         & 21.088   & 20.851   & 20.743     &  296	& S11     \\
     SDSSJ100708.37+155646.3         & 22.039   & 21.562   & 21.458     &  286	& S11     \\
     SDSSJ100709.07+160436.6         & 22.292   & 21.889   & 21.576     &  312	& S11     \\
     SDSSJ100709.74+155312.3         & 16.113   & 15.833   & 15.721     &  303	& S11     \\
     SDSSJ100712.96+155734.8         & 18.287   & 18.009   & 17.872     &  307	& S11     \\
     SDSSJ100713.69+160444.8         & 22.139   & 21.765   & 21.476     &  293	& S11     \\
     SDSSJ100715.51+160552.1         & 20.360   & 20.076   & 19.974     &  282	& S11     \\
     SDSSJ100715.53+161519.1         & 20.741   & 20.439   & 20.427     &  266	& S11     \\
     SDSSJ100717.15+160511.9         & 22.104   & 21.781   & 21.385     &  266	& S11     \\
     SDSSJ100717.36+160355.6         & 20.116   & 19.778   & 19.646     &  295	& S11     \\
     SDSSJ100720.00+160137.5         & 17.626   & 17.274   & 17.127     &  312	& S11     \\
     SDSSJ100721.16+161118.2         & 20.990   & 19.732   & 19.203     &  281	& S11     \\
     SDSSJ100721.77+155424.5         & 20.619   & 20.223   & 20.220     &  307	& S11     \\
     SDSSJ100729.58+161107.1         & 20.358   & 19.347   & 19.026     &  309  & S11     \\     
     SDSSJ100732.47+160500.5         & 22.588   & 22.043   & 21.911     &  281	& S11     \\
     SDSSJ100734.97+155431.5         & 20.788   & 20.542   & 20.391     &  303	& S11     \\
     SDSSJ100737.37+160746.2         & 21.253   & 20.992   & 20.812     &  296	& S11     \\
     SDSSJ100740.15+155855.6         & 21.323   & 20.969   & 20.809     &  295	& S11     \\
     SDSSJ100742.51+160006.8         & 22.476   & 22.024   & 21.463     &  296	& S11     \\
     SDSSJ100743.78+154932.9         & 22.472   & 20.985   & 20.369     &  299	& S11     \\
     SDSSJ100747.19+160545.5         & 20.135   & 19.770   & 19.677     &  294	& S11     \\ 
     SDSSJ100735.92+161125.7         & 23.791   & 22.084   & 22.003    &  242  & S11     \\
     SDSSJ100625.70+155422.1         & 21.587   & 21.135   & 20.950    &  244	& S11     \\
     SDSSJ100711.80+160630.4         & 22.802   & 22.160   & 21.952    &  247	& S11     \\
     SDSSJ100707.80+160721.5         & 20.643   & 20.342   & 20.239    &  248	& S11     \\
     SDSSJ100735.24+155715.3         & 22.535   & 21.135   & 20.411    &  255	& S11     \\
     SDSSJ100628.41+155628.8         & 17.852   & 17.560   & 17.431    &  347	& S11     \\
     SDSSJ100736.92+155958.9         & 21.994   & 21.871   & 21.609    &  373	& S11     \\
     SDSSJ100651.74+161759.2         & 21.407   & 20.923   & 20.953    &  394	& S11     \\ \hline

     \end{tabular} }
     \begin{tablenotes}
       \item[a]{{\tiny Segue1-11, target star.}}
%       \item[b]{{\tiny From high-resolution measurement (this paper).}}
       \item[b]{{\tiny Observed by both N10 and S11.}}
      \end{tablenotes}
     \end{center}
   \end{threeparttable}
\end{table}

\begin{figure*}
 \begin{center}
  \begin{tabular}{cc}
    \includegraphics[width=8.5cm]{velhist.ps} & \includegraphics[width=8.5cm]{cm_2.ps} \\
    \includegraphics[width=8.5cm]{coord1.ps}  & \includegraphics[width=8.5cm]{coord2.ps}  \\
  \end{tabular}
  \caption{ {\scriptsize Summarizing the properties of the stream star candidates found in N10 and S11. Top left: Heliocentric radial velocity histogram of all stars in the combined N10 and S11 samples with a measured velocity greater than 240~km~s$^{-1}$. The black dashed line shows stars in the N10 sample, the blue dotted lines show stars in the S11 sample, and the solid red line shows the total. Top right: Color-magnitude diagram of the 300~km~s$^{-1}$ stream candidate stars found in S11 (filled circles) and N10 (open circles). The open star symbol denotes our target for high-resolution spectroscopy follow-up. The green triangles show radial velocity members of the ultra-faint dwarf galaxy Segue\,1, which was the target for the spectroscopic studies in which the stream stars were found. Blue (N10) and red (S11) dots show the remainding stars that still meet the photometric cuts in either sample, but are not radial velocity members of Segue\,1 or the stream. Photometry is from the Sloan Digital Sky Survey, DR7 \citep{Abazajian2009}. The black line shows the globular cluster sequence of M5 \citep{An2008}, shifted according to the appropriate reddening for the stream stars, and to a best-fit distance of 18 kpc. Note that this is slightly closer than the $23 \pm 2$ kpc distance of Segue\,1 \citep{Belokurov2007}.    Bottom: coordinate plots of stream candidate stars, showing the N10 sample (left) and S11 sample (right). The box size represents the 2$^{\circ}$ field of view covered by N10 centered on Segue\,1; S11 on the other hand only  observed stars within 15\arcmin of Segue\,1's center. Symbols as in the color-magnitude diagram.} }
  \label{fig:col_mag}
 \end{center}
\end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Observations and Data Analysis}
\label{sec:obs}

\subsection{Observations}

A spectrum of Segue1-11 was obtained with the MIKE spectrograph \citep{mike}
on the Magellan Clay telescope in March 2010. The total exposure time for
this V = 17.6 mag star was 4.5 hours, distributed over six exposures to
 allow for removal of cosmic rays. MIKE spectra have
nearly full optical wavelength coverage from $\sim3500$-9000\,{\AA}. Using
a 1.0\arcsec\, slit and $2\times2$ on-chip binning, a resolution of
$\sim30,000$ is achieved in the red, and $\sim28,000$ in the blue
wavelength regime.

The data were reduced using an echelle data reduction pipeline made for
MIKE\footnote{Available at http://obs.carnegiescience.edu/Code/python}.
The reduced individual orders were normalized and merged to produce
final one-dimensional blue and red spectra ready for the analysis. The
$S/N$ of the data are 17 at $\sim4500$\,{\AA} and 20 at $\sim5200$\,{\AA}.

In addition to our main target, we also took MIKE spectra of three bright comparison stars chosen from the Fulbright (2000; hereafter F00)\nocite{Fulbright2000} sample in March 2011. These comparison stars were chosen based on having stellar parameters and metallicities that bracketed our first estimate for Segue1-11. Table~\ref{tab:targets} shows the targets, and Table~\ref{tab:segobs} summarizes the observations.  Spectra were taken with a 1.0\arcsec\, slit and short exposures, in order to get a similar data quality and S/N to that of the Segue1-11 spectrum. Fig.~\ref{fig:mglines} shows the spectrum of Segue1-11 and the short-exposure spectra of the comparison stars in the region around the Mg b-lines at 5170\AA. By comparing stellar parameters and abundances derived from these short-exposure spectra to the published values, we obtain another check on our calculated uncertainties.

\begin{table}
 \begin{threeparttable}
 \begin{center}
   \caption{Targets: Segue1-11 and comparison stars}
   \label{tab:targets}
   \begin{tabular}{l c c c c}
     \hline \hline
       Name       &  RA            & Dec             & V$_{\mbox{mag}}$ & B-V       \\ \hline  
       Segue 1-11 &  $10:09:14.95$ &  $+15:59:48.4$  & 17.70\tnote{a}   &  0.68\tnote{a}       \\
       HIP37335   &  $07:39:50.11$ &  $-01:31:20.37$ & 9.25             &  0.82       \\
       HIP47139   &  $09:36:19.95$ &  $-20:53:14.75$ & 8.34             &  1.01       \\
       HIP68807   &  $14:05:13.02$ &  $-14:51:25.45$ & 7.25             &  0.93       \\ \hline    
  \end{tabular}
  \begin{tablenotes}
   \item[a]{Transformed from the SDSS photometry following \citet{Jordi2006}}
  \end{tablenotes}
 \end{center}
\end{threeparttable}
\end{table}

\begin{table}
 \begin{center}
   \caption{Summary of Observations}
   \label{tab:segobs}
   \begin{tabular}{c c c c }
     \hline \hline
       Object    &  UT date    & UT start time & t$_{\mbox{exp}}$ (s)   \\ \hline  
       Segue1-11 &  03/08/2010 & 02:35         & 3000            \\
       Segue1-11 &  03/08/2010 & 05:30         & 3600            \\
       Segue1-11 &  03/19/2010 & 05:06         & 3000            \\
       Segue1-11 &  03/22/2010 & 00:37         & 3100            \\
       Segue1-11 &  03/22/2010 & 05:22         & 2800            \\
       Segue1-11 &  03/23/2010 & 05:08         & 700             \\
       HIP37335  &  03/13/2011 & 23:41         &  7              \\
       HIP68807  &  03/12/2011 & 10:08         &  1              \\
       HIP47139  &  03/13/2011 & 23:53         &  5              \\
      \hline
  \end{tabular}
 \end{center}
\end{table}

\begin{figure}
 \begin{center}
  \includegraphics[width=9cm]{Mgspecs.ps}
  \caption{High-resolution spectrum of our target star, Segue1-11, and the three comparison stars from the F00 sample, in the region around the Mg b-lines. Shown here are the short exposures of the comparison stars, taken to obtain a similar resolution and S/N as the Segue1-11 spectrum.}
  \label{fig:mglines}
 \end{center}
\end{figure}

\subsection{Line Strength Measurements}
\label{sec:linemes}
We obtained a first estimate for the radial velocity from the two strong Mg b lines in the green region of the spectrum, and two additional Mg lines in the blue. Equivalent widths were then measured by fitting Gaussian profiles, and our estimate corrected based on the mean radial velocity from all the lines measured. Using these 366 lines, we find a heliocentric radial velocity of $307.62$~km~s$^{-1}$, with a standard error of the mean of 0.09~km~s$^{-1}$. This is slightly higher than the estimate of $301$~km~s$^{-1}$ from N10 based on the medium resolution spectrum, but consistent within their estimated velocity uncertainty of 10~km~s$^{-1}$. We note that our measurement is well within the estimated range for the 300~km~s$^{-1}$ stream.

The linelist used for the abundance analysis is based on lines presented in \citet{Roederer2010}, \citet{Aoki2007b}, and \citet{Cayrel2004}. In the instances where the same
line was included in more than one (original) linelist, the most up to
date oscillator strength was used, following Roederer et al. (2010).
This linelist was initally compiled for work on stars more metal-poor than
the target, but besides the strongest lines, we found it to
work well for this metallicity range also.

For atomic lines, equivalent widths were measured by fitting Gaussian profiles. Lines with reduced equivalent widths $\log$(EW/$\lambda$) $> -4.5$ were not used for abundance determination, since they fall near the flat part of the curve-of-growth. Given the noise in the spectra, most lines with EW $\lesssim 20$ m\AA\,  were cautiously excluded for abundance determinations.

For molecular features and elements with hyperfine splitting, we used a spectrum synthesis approach. The abundance was then determined by matching synthesized spectra of different abundances to the observed data. See Section~\ref{sec:abund} for details.

\subsection{Stellar Parameters}
\label{sec:stpar}
The stellar parameters were determined by using the iron lines in each spectrum, by an iterative process. First, the microturbulence is fixed by demanding that the line abundances show no trend with reduced equivalent width ($\log \mbox{EW}/\lambda$). Similarly, effective temperature is set by requiring no trend of abundance with excitation potential of the lines. Finally, the gravity is fixed by requiring that the abundance derived from Fe II lines agree with that obtained from Fe I to within 0.05 dex. By varying the temperature and microturbulence, and comparing the slope to the scatter in the data, we adopt an uncertainty of $\pm$ 150 K in temperature, and $\pm$ 0.3~km~s$^{-1}$ in microturbulence. Similarly, we obtain an uncertainty in the gravity of about $\pm$ 0.4 dex by seeing how much gravity can be changed with Fe I and Fe II still being consistent within the scatter.

Table~\ref{tab:comp_para} shows the resulting stellar parameters for Segue1-11 and the three comparison stars obtained with this method, with the values obtained by F00 in parenthesis for comparison. For HIP68807 and HIP47139, our solutions agree well with the parameters published in F00. For HIP37335, we arrive at a slightly higher temperature and gravity, and thus metallicity, than F00.

Figure~\ref{fig:isochr} shows the adopted stellar parameters overplotted with theoretical 10 Gyr isochrones \citep{Kim2002}. Our solution agrees reasonably well with the tracks within their uncertainties. As its position on the color-magnitude diagram suggested, spectroscopically derived stellar parameters confirm that our star is located on the red giant branch.

For comparison, we also use the SDSS colors to determine the temperature photometrically by interpolating the SDSS {\it ugriz} colors to the isochrones from \citet{Kim2002}, using the color tables of Castelli (http://wwwuser.oat.ts.astro.it/castelli/).  This results in a slightly warmer solution (depending on which colors we use), with T$_{\mbox{\small{eff}}} \sim 5400$ K and $\log g \sim 3.5$. If we instead use this set of stellar parameters, we would arrive at [Fe/H] of $-1.3$. This is, however, well within our estimate of uncertainty for the metallicity (see Section~\ref{sec:unc}). For the rest of the analysis, we use the parameters derived from spectroscopy, however, to facilitate comparison with the Fulbright/Hipparcos stars.

\begin{table}
\begin{threeparttable}
 \begin{center}
   \caption{Stellar parameters: Segue1-11 and comparison stars}
   \label{tab:comp_para}
   \begin{tabular}{l c c c c  }
     \hline \hline
       Name       &  T$_{\mbox{\tiny{eff}}}$ (K) & $\log$ g  & [Fe/H]            & $v_{\mu}$ (km~s$^{-1}$)   \\ \hline  
       Segue 1-11 &  5200          &  2.6      & $-1.4$            & 1.5                \\
       HIP37335\tnote{a}   &  5100 (4850)   &  2.9 (2.7)& $-1.0$ ($-1.2$)   & 1.5 (1.5)           \\
       HIP47139   &  4550 (4600)   &  0.9 (1.3)& $-1.6$ ($-1.4$)   & 2.3 (1.8)          \\
       HIP68807   &  4600 (4575)   &  1.0 (1.1)& $-1.8$ ($-1.8$)   & 2.0 (1.9)          \\ \hline
  \end{tabular}
  \begin{tablenotes}
  \item[a]{While our solution for HIP37335 is warmer than what was found in F00, we note that our solution agrees with other literature sources for this star \citep[e.g.,][]{Soubiran2008, Cenarro2007, Peterson1981}.}
  \end{tablenotes}
 \end{center}
 \end{threeparttable}
\end{table}

\begin{figure}
 \begin{center}
  \includegraphics[width=9cm]{isochrones_10Gyr.ps}
  \caption{Adopted stellar parameters for Segue1-11 (filled star), as well as for the three comparison stars (filled triangles). The open triangles show the values for the comparison stars from Fulbright (2000). Error bars are $\pm$ 150 K and 0.4 dex in $\log g$. Also shown are theoretical 10-Gyr isochrones at [Fe/H] = $-2.5$, $-1.5$ and $-0.5$ respectively \citep{Kim2002}.}
  \label{fig:isochr}
 \end{center}
\end{figure}

\subsection{Model Atmospheres}
Our abundance analysis utilizes one-dimensional plane-parallel Kurucz
model atmospheres with no overshooting \citep{kurucz}. They are computed
under the assumption of local thermodynamic equilibrium (LTE). We use the
2010 version of the MOOG synthesis code (first described in Sneden 1973)\nocite{moog}
for this analysis.  In this version, scattering is currently treated as
true absorption, which may have consequences for abundances derived from
lines in the blue region of the spectrum (see \citet{Frebel2010a} for test on
the matter). Since we have no lines bluer than 4000\,{\AA}, this is, however,
not a serious concern for this analysis.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Abundance Analysis of Segue1-11}
\label{sec:abund}

The derived stellar abundances of Segue1-11 are summarized in Table~\ref{tab:seg11_abund}. The uncertainties quoted are the standard error of the mean, but we adopt a minimum uncertainty of 0.05 dex. Solar abundances are taken from \citet{Asplund2009}.

 This section discusses the measurement and uncertainties of the different elements in more detail.

\begin{table}
  \begin{center}
 \caption{Segue1-11 Abundances Measured}
 \label{tab:seg11_abund}
    \begin{tabular}{l c c c c c c}
     \hline \hline
Elem. & $\log\epsilon (\mbox{X}_{\odot})$ & $\log\epsilon (\mbox{X})$ & $\sigma$ & $N$ & [X/H] & [X/Fe] \\ \hline
C (CH) & 8.43 & 7.24     & 0.21 & 2   & $-1.19$ & $+0.25 $ \\
Na\,I  & 6.24 & 4.93     & 0.08 & 3   & $-1.31$ & $+0.15 $ \\
Mg\,I  & 7.60 & 6.30     & 0.07 & 6   & $-1.30$ & $+0.14 $ \\
Ca\,I  & 6.34 & 5.30     & 0.06 & 16  & $-1.04$ & $+0.40 $ \\
Sc\,II & 3.15 & 1.46     & 0.05 & 3	  & $-1.69$ & $-0.25 $ \\ 
Ti\,I  & 4.95 & 3.69     & 0.07 & 18  & $-1.26$ & $+0.18 $ \\
Ti\,II & 4.95 & 3.77     & 0.06 & 17  & $-1.18$ & $+0.26 $ \\
Cr\,I  & 5.64 & 3.96     & 0.05 & 8   & $-1.68$ & $-0.24 $ \\
Mn\,I  & 5.43 & 3.41     & 0.07 & 3	  & $-2.02$ & $-0.58 $ \\ 
Fe\,I  & 7.50 & 6.04     & 0.05 & 103 & $-1.46$ & ...      \\
Fe\,II & 7.50 & 6.08     & 0.05 & 10  & $-1.42$ & ...      \\
Co\,I  & 4.99 & 3.29     & 0.12 & 3   & $-1.70$ & $-0.26 $ \\ 
Ni\,I  & 6.22 & 4.73     & 0.06 & 14  & $-1.49$ & $-0.05 $ \\
Zn\,I  & 4.56 & 3.18     & 0.25 & 2   & $-1.38$ & $+0.06 $ \\ 
Sr\,II & 2.87 & 0.50:    & 0.40 & 1  & $-3.07$: & $-0.93$: \\ 
Ba\,II & 2.18 & 0.83     & 0.21 & 2	  & $-1.35$ & $+0.09 $ \\
La\,II & 1.10 & $-0.38$  & 0.30 & 1 & $-1.48$ & $-0.04$ \\
Eu\,II & 0.52 & $-0.39$: & 0.40 & 1	  & $-0.91$: & $+0.53 $: \\ \hline

 \end{tabular}				      
 \end{center}
\end{table}

\subsection{Carbon}
The carbon abundance was determined by synthesis of the carbon G-band head at 4313\,\AA\, and the CH feature at 4325\,\AA. An example of this, comparing the observed spectrum to four synthesized spectra, is shown in Fig.~\ref{fig:gband}. Here, the thick red line shows the carbon abundance adopted for this region,while the blue and green show the synthesis with $\Delta$[C/Fe] $\pm$ 0.3 dex. Synthesis of the feature at 4325\,\AA\, was done independently; the carbon abundance quoted in Table~\ref{tab:seg11_abund} is the mean of the two. Given the noise in the data, we adopt a fit uncertainty of $\pm$ 0.3 dex.

\begin{figure}
 \begin{center}
  \includegraphics[width=9cm]{CH_synth.ps}
  \caption{Example of determining carbon abundance by synthesis: The black dotted line shows the actual spectrum of Segue1-11 at the carbon g-band, while the colored lines show synthesized spectra at different carbon abundances. }
  \label{fig:gband}
 \end{center}
\end{figure}

\subsection{Light elements}
Abundances of elements without hyperfine structure were determined from the equivalent width measurements, as described in Section~\ref{sec:linemes}. In that case, the uncertainties listed in Table~\ref{tab:seg11_abund} are the standard error of the mean of the abundances determined from the individual lines for each element. Abundances of elements with hyperfine structure (Mn, Co) were determined by synthesis of individual lines.

In general, the abundance patterns derived from the high-resolution spectrum are similar to those of outer halo stars at this metallicity (also see Section~\ref{sec:ab_rat} and  Fig.~\ref{fig:light_el}). The possible exception is Mg, which at [Mg/Fe]$=0.14$ is low compared to the other $\alpha$-elements. We note, however, that the derived Mg abundance is very sensitive to the assumed surface gravity in the model, and that our Mg measurements for the three comparison stars are lower than that measured in F00 (also see Section~\ref{sec:unc} and Table~\ref{tab:hipabund}), so this could be a systematic effect. Taking the $\alpha$-element abundance as (Ca + Mg + Ti)/3, we find [$\alpha$/Fe]$= +0.26 $. Segue1-11 is at the low end of $\alpha$-enhancement compared to most halo stars at this metallicity, but still higher than $\alpha$-abundances seen in classical dwarf spheroidal galaxies \citep[e.g.][]{Tolstoy2009}.

\subsection{Neutron-capture elements}

Strontium abundance was determined by synthesis of the line at 4215\,\AA, illustrated in Fig.~\ref{fig:nc_syn}. The line at 4077\,\AA\, is also visible in the spectrum but too noisy to use for abundance determination; the data are however not inconsistent with what is determined from the line at 4215\,\AA\, within the uncertainties. Given the noise level even at 4215\,\AA\, compared to the difference between the synthesized spectra, this value should be regarded as uncertain. In particular, even though the Sr abundance appears abnormally low compared to other stellar populations in Fig.~\ref{fig:nc_el}, this is likely not significant given the uncertainty.

Barium abundance was determined by synthesis of the lines at 4554 and 6496\,\AA, with the abundance quoted in Table~\ref{tab:seg11_abund} being the average of the two. The synthesis of the 6496\,\AA\,  line is shown in Fig.~\ref{fig:nc_syn}. We adopt an uncertainty of $\pm$ 0.3 dex. Europium was determined by synthesis of the line at 4129\,\AA. Like strontium, there is considerable uncertainty due to the noisy spectrum. Lanthanum was determined by synthesis of the line at 4333\,\AA. Other lines are visible but too noisy for more precise abundance determination; the upper limits derived are however consistent with the result derived from the line at 4333\,\AA. Synthesis of the 4333\,\AA\, line is shown in Fig.~\ref{fig:nc_syn}.

\begin{figure*}
 \begin{center}
  \begin{tabular}{cc}
  \includegraphics[width=8.5cm]{sr4215_synth.ps} & \includegraphics[width=8.5cm]{ba6496_synth.ps} \\
  \includegraphics[width=8.5cm]{eu4129_synth.ps} &  \includegraphics[width=8.5cm]{la4333_synth.ps} \\
  \end{tabular}
  \caption{Determining the abundances of Sr, Ba, Eu and La by comparing the observed lines to synthesized spectra at different abundances. }
  \label{fig:nc_syn}
 \end{center}
\end{figure*}

\subsection{Uncertainties}
\label{sec:unc}
Random errors come from uncertainties in placing the continuum level; we estimate the random uncertainty in the abundance of an element as the standard error of the mean abundance determined from individual lines. For elements that were determined from fitting a single line to a synthetic spectrum (Sr, Eu and La), the error quoted in the second column is the fit uncertainty.

Systematic errors arise from uncertainties in the stellar parameters, as described in Section~\ref{sec:stpar}. To quantify this effect, we redo the analysis with the stellar parameters for Segue1-11 changed by $+150$ K, $+0.4$ dex, and $+0.3$~km~s$^{-1}$ in temperature, log g and microturbulence respectively, and record the corresponding change in abundance. Table~\ref{tab:seg11_sigma} shows the result. The total uncertainty is obtained by summing the individual components in quadrature.

Another check of the uncertainties, given the data quality, comes from comparing the F00 abundances for our comparison stars to what we obtain from our low S/N spectra. Table~\ref{tab:hipabund} shows the derived abundances for the comparison stars, and lists the published values from F00 also. Our abundances are in good agreement within the uncertainties, especially when taking into account the different stellar parameter solution for HIP37335. We note that we systematically arrive at lower Mg abundances for the comparison stars than F00, but not for the other $\alpha$-elements Ca and Ti. This could indicate that our Mg abundance for Segue1-11 is also too low.

\begin{table}
 \begin{center}
 \caption{Abundance Uncertainties for Segue1-11}
 \label{tab:seg11_sigma}
  \begin{tabular}{l c c c c c}
  \hline \hline
  Elem.    & Random      & $\Delta T_{eff}$ & $\Delta \log g$ & $\Delta v_{micr}$ & Total       \\
           & Uncer.      & +150 K           &  +0.4 dex       & +0.3~km~s$^{-1}$  & Uncer.      \\ \hline
  C (CH)   &  0.21       &  0.30            & $-0.05$         & $-0.02$           & 0.37        \\
  Na\,I    &  0.08 	 &  0.16            & $-0.10$	      &	$-0.04$		  & 0.21	\\
  Mg\,I    &  0.07 	 &  0.16            & $-0.11$	      &	$-0.05$           & 0.21	\\
  Ca\,I    &  0.06 	 &  0.13	    & $-0.05$	      &	$-0.10$		  & 0.18	\\
  Sc\,II   &  0.05 	 &  0.02	    & $+0.16$	      &	$-0.02$		  & 0.17	\\
  Ti\,I    &  0.07 	 &  0.20	    & $-0.02$	      &	$-0.09$		  & 0.23	\\
  Ti\,II   &  0.06 	 &  0.03	    & $+0.15$	      &	$-0.09$		  & 0.19	\\
  Cr\,I    &  0.05 	 &  0.19	    & $-0.01$	      &	$-0.08$		  & 0.21	\\
  Mn\,I    &  0.07 	 &  0.15	    & $-0.03$	      &	$-0.10$		  & 0.20	\\ 
  Fe\,I    &  0.05 	 &  0.18	    & $-0.04$	      &	$-0.13$		  & 0.23	\\
  Fe\,II   &  0.05 	 &$-0.02$	    & $+0.16$	      &	$-0.09$		  & 0.19	\\
  Co\,I    &  0.12 	 &  0.25	    & $+0.00$	      &	$-0.20$		  & 0.34	\\ 
  Ni\,I    &  0.06 	 &  0.14	    & $+0.00$	      &	$-0.06$		  & 0.16	\\
  Zn\,I    &  0.25 	 &  0.04	    & $+0.10$	      &	$-0.05$		  & 0.28	\\
  Sr\,II   &  0.40 	 &  0.10	    & $+0.02$	      &	$-0.10$		  & 0.42	\\ 
  Ba\,II   &  0.21 	 &  0.09	    & $+0.08$	      &	$-0.18$		  & 0.30	\\
  La\,II   &  0.30       &  0.05            & $+0.15$         & $-0.05$           & 0.34        \\
  Eu\,II   &  0.40 	 &  0.05	    & $+0.15$	      &	$-0.05$		  & 0.43	\\ \hline

  \end{tabular}
 \end{center}
\end{table}

\begin{table}
  \begin{center}
 \caption{Abundances measured for HIP37335, HIP68807 and HIP47139}
 \label{tab:hipabund}
    {\tiny
    \begin{tabular}{l c c c c c c }
     \hline \hline
Elem.  & $\log\epsilon (\mbox{X})$ & $\sigma$ & $N$ & [X/H] & [X/Fe] & [X/Fe]fb \\ \hline
       &          &       & HIP37335 &              &             &            \\ \hline
C (CH) &   7.71   & 0.21    &  2    &    $ -0.72 $  &  $ +0.29 $  &             \\
Na\,I  &   5.46   & 0.07    &  4    &    $ -0.78 $  &  $ +0.23 $  &   $+0.32 $  \\       
Mg\,I  &   7.05   & 0.12    &  4    &    $ -0.55 $  &  $ +0.46 $  &   $+0.63 $  \\       
Ca\,I  &   5.86   & 0.05    &  16   &    $ -0.48 $  &  $ +0.53 $  &   $+0.44 $  \\       
Sc\,II &   2.40   & 0.05    &  9    &    $ -0.75 $  &  $ +0.26 $  &   $      $  \\       
Ti\,I  &   4.20   & 0.05    &  28   &    $ -0.75 $  &  $ +0.26 $  &   $+0.26 $  \\       
Ti\,II &   4.20   & 0.05    &  16   &    $ -0.75 $  &  $ +0.26 $  &   $      $  \\       
Cr\,I  &   4.65   & 0.05    &  14   &    $ -0.99 $  &  $ +0.02 $  &   $-0.05 $  \\       
Mn\,I  &   4.61   & 0.05    &  3    &    $ -0.82 $  &  $ +0.19 $  &   $      $  \\       
Fe\,I  &   6.50   & 0.05    &  124  &    $ -1.00 $  &  $ ...   $  &  $(-1.26)$  \\       
Fe\,II &   6.48   & 0.05    &  15   &    $ -1.02 $  &  $ ...   $  &   $      $  \\  
Co\,I  &   3.55   & 0.05    &  3    &    $ -1.44 $  &  $ -0.43 $  &             \\
Ni\,I  &   5.30   & 0.05    &  24   &    $ -0.92 $  &  $ +0.09 $  &   $+0.10 $  \\   
Zn\,I  &   3.78   & 0.08    &   2   &    $ -0.78 $  &  $ +0.23 $  &   $      $  \\       
Ba\,II &   1.43   & 0.21    &  2    &    $ -0.75 $  &  $ +0.26 $  &   $-0.02 $  \\
La\,II &   0.42   & 0.30    &  1    &    $ -0.68 $  &  $ +0.33 $  &             \\
Eu\,II & $-0.19$  & 0.30    &  1    &    $ -0.71 $  &  $ +0.30	$  &   $+0.38 $  \\  \hline      
       &          &       & HIP68807 &              &             &            \\ \hline

C (CH) &     6.76 &  0.21     &    2   &      $ -1.67 $  &   $ +0.17 $  &               \\
Na\,I  &     4.36 &  0.05     &    3   &      $ -1.88 $  &   $ -0.04 $  &  $  -0.13  $  \\       
Mg\,I  &     6.17 &  0.05     &    6   &      $ -1.43 $  &   $ +0.41 $  &  $  +0.49  $  \\       
Ca\,I  &     4.89 &  0.05     &    17  &      $ -1.45 $  &   $ +0.39 $  &  $  +0.37  $  \\       
Sc\,II &     1.45 &  0.06     &    6   &      $ -1.70 $  &   $ +0.14 $  &  $         $  \\       
Ti\,I  &     3.25 &  0.05     &    23  &      $ -1.70 $  &   $ +0.14 $  &  $  +0.20  $  \\       
Ti\,II &     3.45 &  0.05     &    18  &      $ -1.50 $  &   $ +0.34 $  &  $         $  \\       
Cr\,I  &     3.61 &  0.05     &    14  &      $ -2.03 $  &   $ -0.19 $  &  $  -0.12  $  \\       
Mn\,I  &     3.40 &  0.07     &    3   &      $ -2.03 $  &   $ -0.19 $  &  $         $  \\       
Fe\,I  &     5.64 &  0.05     &    127 &      $ -1.86 $  &   $ ...   $  &  $ (-1.83) $  \\       
Fe\,II &     5.68 &  0.05     &    14  &      $ -1.82 $  &   $ ...   $  &  $         $  \\       
Ni\,I  &     4.48 &  0.05     &    12  &      $ -1.74 $  &   $ +0.10 $  &  $  -0.03  $  \\    
Zn\,I  &     2.84 &               &    1   &      $ -1.72 $  &   $ +0.12 $  &  $         $  \\      
Ba\,II &     0.69 &  0.14     &    3   &      $ -1.49 $  &   $ +0.35 $  &  $  +0.27  $  \\
La\,II &  $-0.68$ &  0.30     &    1   &      $-1.78$    &   $ +0.06 $  &               \\
Eu\,II &  $-0.99$ &  0.40     &    1   &      $ -1.51 $	 &   $ +0.33 $	&  $  +0.40  $  \\ \hline
       &          &       & HIP47139 &              &             &            \\ \hline

C (CH) &   6.61     &  0.21   &   2    &    $ -1.82 $  &  $ -0.24 $  &                \\
O\,I   &   8.14     &  ...        &   1    &    $ -0.55 $  &  $+ 1.03 $  &                \\
Na\,I  &   4.65     &  0.05   &   4    &    $ -1.59 $  &  $ -0.01 $  &  $ -0.18   $   \\       
Mg\,I  &   6.42     &  0.08   &   4    &    $ -1.18 $  &  $ +0.40 $  &  $ +0.54   $   \\       
Ca\,I  &   5.05     &  0.05   &   16   &    $ -1.29 $  &  $ +0.29 $  &  $ +0.27   $   \\       
Sc\,II &   1.64     &  0.05   &   12   &    $ -1.51 $  &  $ +0.07 $  &  $         $   \\       
Ti\,I  &   3.52     &  0.05   &   26   &    $ -1.43 $  &  $ +0.15 $  &  $ +0.29   $   \\       
Ti\,II &   3.67     &  0.05   &   18   &    $ -1.28 $  &  $ +0.30 $  &  $         $   \\       
Cr\,I  &   3.94     &  0.07   &   16   &    $ -1.70 $  &  $ -0.12 $  &  $ -0.17   $   \\       
Mn\,I  &   3.58     &  0.07   &   3    &    $ -1.85 $  &  $ -0.27 $  &  $         $   \\       
Fe\,I  &   5.91     &  0.05   &   109  &    $ -1.59 $  &  $ ...   $  &  $ (-1.46) $   \\       
Fe\,II &   5.94     &  0.05   &   11   &    $ -1.56 $  &  $ ...   $  &  $         $   \\       
Ni\,I  &   4.65     &  0.05   &   18   &    $ -1.57 $  &  $ +0.01 $  &  $ +0.00   $   \\  
Zn\,I  &   2.97     &  0.11   &   2    &    $ -1.59 $  &  $ -0.01 $  &  $         $   \\     
Ba\,II &   0.92     &  0.10   &   3    &    $ -1.26 $  &  $ +0.32 $  &  $ +0.16   $   \\
La\,II &   $-0.48$  &  0.30   &   1    &    $ -1.58 $  &  $ +0.00 $  &                \\
Eu\,II & $ -0.4 9$  &  0.40   &   1    &    $ -1.01 $  &  $ +0.57 $  &                \\  \hline

  \end{tabular}}
 \end{center}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Characterizing the 300~km~s$^{-1}$ Stream}
\label{sec:char}

\begin{figure*}
 \begin{center}
  \includegraphics{light_el.ps}
  \caption{Abundance ratios for light elements in Segue1-11 (filled star symbol), as measured from our high-resolution spectrum. For comparison, red and cyan points show thin and thick disk stars respectively, blue points show halo stars, and the crosses show stars in the classical dwarf galaxies Draco, Sextans, Ursa Minor, Carina, Fornax, Sculptor and Leo I. A typical error bar for our measurements is shown in the lower-left panel; also see Table~\ref{tab:seg11_sigma}. }
  \label{fig:light_el}
 \end{center}
\end{figure*}

\begin{figure*}
 \begin{center}
  \includegraphics{nc_el.ps}
  \caption{Abundance ratios for the neutron-capture elements Sr, Ba, La and Eu in Segue1-11. Symbols as in Fig.~\ref{fig:light_el}.}
  \label{fig:nc_el}
 \end{center}
\end{figure*}

\subsection{Metallicity of Stream}
We determine a metallicity of [Fe/H] $= -1.44 $ for Segue1-11 based on the high-resolution spectrum. This is consistent with what we estimate from fitting globular cluster sequences to the photometry. It adds support to the result that the stream stars have higher metallicity than Segue\,1 system, as noted in S11 based on Ca triplet equivalents widths. The AAOmega sample of N10 contains some metallicity estimates based on CaII K line strengths; in addition to Segue1-11, the spectrum of the stream star Segue1-101 (SDSSJ100659.01+154418.8) has enough counts to yield [Fe/H] $\simeq -1.7$. Beyond this, we do not have data to determine the metallicity spread of the stream.

\subsection{Abundance Ratios}
\label{sec:ab_rat}
Figures~\ref{fig:light_el} and \ref{fig:nc_el} show the abundance patterns of Segue1-11, based on our high-resolution spectrum. The blue, cyan and red points show stars in the halo, thick disk and thin disk respectively, from the sample of \citet{Fulbright2000, Fulbright2002} (as classified by \citealt{Venn2004}). Since the Fulbright sample does not include Cr, Sr and La measurements, comparison points  (halo stars) for these elements are taken from \citet{Lai2007} and \citet{Barklem2005}. In addition, the crosses show abundance patterns of stars in the classical dwarf galaxies Draco, Sextans, Ursa Minor, Carina, Fornax, Sculptor and Leo I \citep{Shetrone2001, Shetrone2003, Geisler2005, Aoki2009, Cohen2009}.

The abundance ratios of Segue1-11 overlap well with the general halo population at that metallicity, though as noted in Section~\ref{sec:abund} the $\alpha$- and particularly Mg abundances are on the low end. (The Sr abundance also appears low, but as discussed in Section~\ref{sec:abund}, this is likely not significant due to the noisy spectrum in this region.) On the other hand, the general abundance pattern is still closer to a typical halo star than to a classical dwarf spheroidal galaxy star.

We note that these abundance patterns are important for interpreting the nature of the stream and its potential progenitor. Judging from this one star, it may be that this is the first stream with halo-like abundances. This predicament illustrates that a careful mapping of the region around Segue\,1 and the 300~km~s$^{-1}$ stream is of great importance. Only then can the nature of the 300~km~s$^{-1}$ stars be determined in more detail, and especially whether there are two different poulations at this high velocity: the halo, and the stream. Initial work on SDSS data to address this question hints that this region is more complex than assumed thus far. An attempt to decompose the many populations in the Segue\,1 region will be presented in a forthcoming paper (A. Jayaraman et al., in preparation).

\subsection{Distance to stream}

We use two different methods of estimating the distance to the stream. First, we interpolate the stellar parameters derived from the absorption lines onto the [Fe/H] $= -1.5$ isochrone shown in Fig.~\ref{fig:isochr}, extracting an inferred absolute magnitude $M_V \simeq +1.37$ for Segue1-11. Transforming from the Sloan photometry following \citet{Jordi2006}, and correcting for extinction according to \citet{Schlegel1998}, we find Segue1-11 has $V = 17.60$. This yields a distance modulus of $16.23$, resulting in a best distance estimate of $\simeq 18$ kpc. Given their uncertainty, however, a distance within $\pm 7$ kpc of this estimate would still be consistent with the stellar parameters derived from spectroscopy.

A second distance estimate comes from using the photometric data and comparing the color-magnitude diagram to various globular cluster sequences from \citet{An2008}, shifted according to the distance moduli and reddenings compiled in \citet{Harris1996}. As seen in Fig.~\ref{fig:col_mag}, the M5 sequence is a good fit to the stream data when shifted to a distance of 18 kpc. This is in good agreement with the estimate based on spectroscopically determined stellar parameters.

Both the isochrone fit based on the single spectroscopic measurement and the photometric data indicate that the stream stars are at a distance of $\simeq 18$ kpc, slightly closer than the assumed distance of $23 \pm 2$ kpc \citep{Belokurov2007} for Segue\,1 itself. However, the uncertainties on both values are substantial enough that we cannot rule out that they are at the same distance. We also caution that since the stream stars were picked out in color-magnitude filters targeting stars at the distance of Segue1, the stream stars in our sample by design cannot be at a very different distance.

We note that with galactic coordinates $l, b \simeq 220^{\circ}, 50^{\circ}$ and a heliocentric distance of 18 kpc, the stream stars are located in the outer galaxy. A heliocentric radial velocity of 300~km~s$^{-1}$ translates to Galactic Standard of Rest velocity of about 230~km~s$^{-1}$ in this direction, so the stream stars appear to be on a low angular momentum orbit that would eventually bring them far into the inner Galaxy.

\subsection{Origin of Stream}
We discuss here some possible scenarios regarding the origin of the stream.

\begin{itemize}
\item Since these high-velocity stars were discovered in a survey targeting Segue 1 members, a natural question to ask is whether the stream is related to the Segue\,1 dwarf galaxy. We find this an unlikely scenario for several reasons. First, the study of S11 finds no evidence that the Segue\,1 system is being tidally disrupted. Our distance estimate, based both on the high-resolution spectroscopy data and the photometry indicate that the stream stars are at a slightly closer distance than Segue\,1, though the data are not good enough to rule out that they are at the same distance. In addition, the color-magnitude diagrams suggest that the stream members are in general at a higher metallicity than Segue\,1, which our high-resolution measurement of one stream star also confirms.

\item Another possibility, suggested by \citet{Geha2009}, is that these stars could be associated with the Sagittarius stream. Indeed at least two wraps of Sagittarius overlap with Segue 1 in this direction, and \citet{Niederste-Ostholt2009} argues that Segue 1 itself is a star cluster from the Sagittarius galaxy. But as for the stream stars, our metallicity measurement indicates that the 300~km~s$^{-1}$ stream is more metal-poor than Sgr debris \citep{Chou2007}. In addition, no model of Sagittarius that we are aware of predicts a wrap at this velocity, however; the part of the Sagittarius stream proposed to be contaminating Segue 1 samples has $v_{GSR} \sim 130$~km~s$^{-1}$ \citep{Niederste-Ostholt2009}, while the stream stars have $v_{GSR} \sim 230$~km~s$^{-1}$.

\item The Orphan Stream \citep{Belokurov2007b} crosses the Sagittarius stream on the sky near Segue1, and at a similar distance modulus . Again, however, the velocities do not agree -- the reported velocities of the Orphan Stream are around $v_{GSR} \sim 110$~km~s$^{-1}$ \citep{Newberg2010}. In addition, the Orphan stream is metal-poor, with a reported mean metallicity of BHB stars [Fe/H] $ = -2.1$. Although both the Orphan Stream and Sagittarius Stream overlap with the 300~km~s$^{-1}$ stars, then, the combined metallicity and velocity information suggest that they are unrelated.

\item We have assumed throughout this paper that the 300~km~s$^{-1}$ feature is a stellar stream, but as pointed out in S11, until we can determine the full spatial extent of these stars, we cannot rule out that the stars belong to a bound object. If so, given the 1$^{\circ}$ extent seen in N10, its physical diameter would be at least 300 ($d / 18$ kpc) pc. This highlights the need for follow-up observations to map out the full extent of the 300~km~s$^{-1}$ stars.

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Conclusions}
\label{sec:conc}
We have presented a high-resolution spectrum and abundance analysis of Segue1-11, a bright star in the 300~km~s$^{-1}$ stream near the ultra-faint dwarf galaxy Segue1. We determine a metallicity [Fe/H] $= -1.44$ for this star, with abundance ratios similar to typical halo stars at this metallicity. Fitting the stellar parameter solution onto theoretical isochrones, we estimate a distance of $18 \pm 7$ kpc. Both the metallicity and distance are in good agreement with estimates obtained from comparing the SDSS photometry to globular cluster sequences.

Although the 300~km~s$^{-1}$ stars are found in a region of sky with many known structures, the combination of velocity, chemistry and distance information makes it unlikely that these stars are associated with any of the Sagittarius stream, the Orphan stream, or the Segue\,1 dwarf galaxy. We therefore conclude that these stars belong to a new structure in the crowded ``Field of Streams''. Its features include an extreme mean velocity of 300~km~s$^{-1}$, a resolved and high velocity dispersion of 10~km~s$^{-1}$, a broad spatial distribution, and halo-like chemical abundances. The abundance patterns in particular make this stream very interesting to study in the context of halo formation.

\section{Acknowledgements}
A.F. acknowledges support of a Clay Fellowship administered by the Smithsonian Astrophysical Observatory. J.E.N. acknowledges support from the Australian Research Council (grants DP0663562, and DP0984924) for studies of the Galaxy's most metal-poor stars and ultra-faint satellite systems. R.F.G.W. acknowledges support from NSF grant AST-0908326.

%\bibliography{/home/rlunnan/myReferences}
\begin{thebibliography}{40}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi

\bibitem[{{Abazajian} {et~al.}(2009){Abazajian}, {Adelman-McCarthy},
  {Ag{\"u}eros}, {Allam}, {Allende Prieto}, {An}, {Anderson}, {Anderson},
  {Annis}, {Bahcall}, \& et~al.}]{Abazajian2009}
{Abazajian}, K.~N., {et~al.} 2009, \apjs, 182, 543

\bibitem[{{An} {et~al.}(2008){An}, {Johnson}, {Clem}, {Yanny}, {Rockosi},
  {Morrison}, {Harding}, {Gunn}, {Allende Prieto}, {Beers}, {Cudworth},
  {Ivans}, {Ivezi{\'c}}, {Lee}, {Lupton}, {Bizyaev}, {Brewington},
  {Malanushenko}, {Malanushenko}, {Oravetz}, {Pan}, {Simmons}, {Snedden},
  {Watters}, \& {York}}]{An2008}
{An}, D., {et~al.} 2008, \apjs, 179, 326

\bibitem[{{Aoki} {et~al.}(2007){Aoki}, {Honda}, {Beers}, {Takada-Hidai},
  {Iwamoto}, {Tominaga}, {Umeda}, {Nomoto}, {Norris}, \& {Ryan}}]{Aoki2007b}
{Aoki}, W., {et~al.} 2007, \apj, 660, 747

\bibitem[{{Aoki} {et~al.}(2009){Aoki}, {Arimoto}, {Sadakane}, {Tolstoy},
  {Battaglia}, {Jablonka}, {Shetrone}, {Letarte}, {Irwin}, {Hill}, {Francois},
  {Venn}, {Primas}, {Helmi}, {Kaufer}, {Tafelmeyer}, {Szeifert}, \&
  {Babusiaux}}]{Aoki2009}
---. 2009, \aap, 502, 569

\bibitem[{{Asplund} {et~al.}(2009){Asplund}, {Grevesse}, {Sauval}, \&
  {Scott}}]{Asplund2009}
{Asplund}, M., {Grevesse}, N., {Sauval}, A.~J., \& {Scott}, P. 2009, \araa, 47,
  481

\bibitem[{{Barklem} {et~al.}(2005){Barklem}, {Christlieb}, {Beers}, {Hill},
  {Bessell}, {Holmberg}, {Marsteller}, {Rossi}, {Zickgraf}, \&
  {Reimers}}]{Barklem2005}
{Barklem}, P.~S., {et~al.} 2005, \aap, 439, 129

\bibitem[{{Belokurov} {et~al.}(2006){Belokurov}, {Zucker}, {Evans}, {Gilmore},
  {Vidrih}, {Bramich}, {Newberg}, {Wyse}, {Irwin}, {Fellhauer}, {Hewett},
  {Walton}, {Wilkinson}, {Cole}, {Yanny}, {Rockosi}, {Beers}, {Bell},
  {Brinkmann}, {Ivezi{\'c}}, \& {Lupton}}]{Belokurov2006b}
{Belokurov}, V., {et~al.} 2006, \apjl, 642, L137

\bibitem[{{Belokurov} {et~al.}(2007{\natexlab{a}}){Belokurov}, {Evans},
  {Irwin}, {Lynden-Bell}, {Yanny}, {Vidrih}, {Gilmore}, {Seabroke}, {Zucker},
  {Wilkinson}, {Hewett}, {Bramich}, {Fellhauer}, {Newberg}, {Wyse}, {Beers},
  {Bell}, {Barentine}, {Brinkmann}, {Cole}, {Pan}, \& {York}}]{Belokurov2007b}
---. 2007{\natexlab{a}}, \apj, 658, 337

\bibitem[{{Belokurov} {et~al.}(2007{\natexlab{b}}){Belokurov}, {Zucker},
  {Evans}, {Kleyna}, {Koposov}, {Hodgkin}, {Irwin}, {Gilmore}, {Wilkinson},
  {Fellhauer}, {Bramich}, {Hewett}, {Vidrih}, {De Jong}, {Smith}, {Rix},
  {Bell}, {Wyse}, {Newberg}, {Mayeur}, {Yanny}, {Rockosi}, {Gnedin},
  {Schneider}, {Beers}, {Barentine}, {Brewington}, {Brinkmann}, {Harvanek},
  {Kleinman}, {Krzesinski}, {Long}, {Nitta}, \& {Snedden}}]{Belokurov2007}
---. 2007{\natexlab{b}}, \apj, 654, 897

\bibitem[{{Bernstein} {et~al.}(2003){Bernstein}, {Shectman}, {Gunnels},
  {Mochnacki}, \& {Athey}}]{mike}
{Bernstein}, R., {Shectman}, S.~A., {Gunnels}, S.~M., {Mochnacki}, S., \&
  {Athey}, A.~E. 2003, in Society of Photo-Optical Instrumentation Engineers
  (SPIE) Conference Series, Vol. 4841, Society of Photo-Optical Instrumentation
  Engineers (SPIE) Conference Series, ed. {M.~Iye \& A.~F.~M.~Moorwood}, 1694

\bibitem[{{Cayrel} {et~al.}(2004){Cayrel}, {Depagne}, {Spite}, {Hill}, {Spite},
  {Fran{\c c}ois}, {Plez}, {Beers}, {Primas}, {Andersen}, {Barbuy},
  {Bonifacio}, {Molaro}, \& {Nordstr{\"o}m}}]{Cayrel2004}
{Cayrel}, R., {et~al.} 2004, \aap, 416, 1117

\bibitem[{{Cenarro} {et~al.}(2007){Cenarro}, {Peletier},
  {S{\'a}nchez-Bl{\'a}zquez}, {Selam}, {Toloba}, {Cardiel},
  {Falc{\'o}n-Barroso}, {Gorgas}, {Jim{\'e}nez-Vicente}, \&
  {Vazdekis}}]{Cenarro2007}
{Cenarro}, A.~J., {et~al.} 2007, \mnras, 374, 664

\bibitem[{{Chou} {et~al.}(2007){Chou}, {Majewski}, {Cunha}, {Smith},
  {Patterson}, {Mart{\'{\i}}nez-Delgado}, {Law}, {Crane}, {Mu{\~n}oz}, {Garcia
  L{\'o}pez}, {Geisler}, \& {Skrutskie}}]{Chou2007}
{Chou}, M.-Y., {et~al.} 2007, \apj, 670, 346

\bibitem[{{Cohen} \& {Huang}(2009)}]{Cohen2009}
{Cohen}, J.~G., \& {Huang}, W. 2009, \apj, 701, 1053

\bibitem[{{Frebel} {et~al.}(2010){Frebel}, {Simon}, {Geha}, \&
  {Willman}}]{Frebel2010a}
{Frebel}, A., {Simon}, J.~D., {Geha}, M., \& {Willman}, B. 2010, ApJ, 708, 560

\bibitem[{{Fulbright}(2000)}]{Fulbright2000}
{Fulbright}, J.~P. 2000, \aj, 120, 1841

\bibitem[{{Fulbright}(2002)}]{Fulbright2002}
---. 2002, \aj, 123, 404

\bibitem[{{Geha} {et~al.}(2009){Geha}, {Willman}, {Simon}, {Strigari}, {Kirby},
  {Law}, \& {Strader}}]{Geha2009}
{Geha}, M., {Willman}, B., {Simon}, J.~D., {Strigari}, L.~E., {Kirby}, E.~N.,
  {Law}, D.~R., \& {Strader}, J. 2009, \apj, 692, 1464

\bibitem[{{Geisler} {et~al.}(2005){Geisler}, {Smith}, {Wallerstein},
  {Gonzalez}, \& {Charbonnel}}]{Geisler2005}
{Geisler}, D., {Smith}, V.~V., {Wallerstein}, G., {Gonzalez}, G., \&
  {Charbonnel}, C. 2005, \aj, 129, 1428

\bibitem[{{Harris}(1996)}]{Harris1996}
{Harris}, W.~E. 1996, \aj, 112, 1487

\bibitem[{{Ibata} {et~al.}(1994){Ibata}, {Gilmore}, \& {Irwin}}]{Ibata1994}
{Ibata}, R.~A., {Gilmore}, G., \& {Irwin}, M.~J. 1994, \nat, 370, 194

\bibitem[{{Jordi} {et~al.}(2006){Jordi}, {Grebel}, \& {Ammon}}]{Jordi2006}
{Jordi}, K., {Grebel}, E.~K., \& {Ammon}, K. 2006, \aap, 460, 339

\bibitem[{{Kim} {et~al.}(2002){Kim}, {Demarque}, {Yi}, \&
  {Alexander}}]{Kim2002}
{Kim}, Y.-C., {Demarque}, P., {Yi}, S.~K., \& {Alexander}, D.~R. 2002, \apjs,
  143, 499

\bibitem[{{Kurucz}(1993)}]{kurucz}
{Kurucz}, R.~L. 1993, {Kurucz CD-ROM 13, ATLAS9 Stellar Atmosphere Programs and
  2 km/s Grid}, Cambridge: SAO

\bibitem[{{Lai} {et~al.}(2007){Lai}, {Johnson}, {Bolte}, \&
  {Lucatello}}]{Lai2007}
{Lai}, D.~K., {Johnson}, J.~A., {Bolte}, M., \& {Lucatello}, S. 2007, \apj,
  667, 1185

\bibitem[{{Lynden-Bell} \& {Lynden-Bell}(1995)}]{Lynden-Bell1995}
{Lynden-Bell}, D., \& {Lynden-Bell}, R.~M. 1995, \mnras, 275, 429

\bibitem[{{Majewski} {et~al.}(2003){Majewski}, {Skrutskie}, {Weinberg}, \&
  {Ostheimer}}]{Majewski2003}
{Majewski}, S.~R., {Skrutskie}, M.~F., {Weinberg}, M.~D., \& {Ostheimer}, J.~C.
  2003, \apj, 599, 1082

\bibitem[{{Newberg} {et~al.}(2010){Newberg}, {Willett}, {Yanny}, \&
  {Xu}}]{Newberg2010}
{Newberg}, H.~J., {Willett}, B.~A., {Yanny}, B., \& {Xu}, Y. 2010, \apj, 711,
  32

\bibitem[{{Niederste-Ostholt} {et~al.}(2009){Niederste-Ostholt}, {Belokurov},
  {Evans}, {Gilmore}, {Wyse}, \& {Norris}}]{Niederste-Ostholt2009}
{Niederste-Ostholt}, M., {Belokurov}, V., {Evans}, N.~W., {Gilmore}, G.,
  {Wyse}, R.~F.~G., \& {Norris}, J.~E. 2009, \mnras, 398, 1771

\bibitem[{{Norris} {et~al.}(2010){Norris}, {Wyse}, {Gilmore}, {Yong}, {Frebel},
  {Wilkinson}, {Belokurov}, \& {Zucker}}]{Norris2010a}
{Norris}, J.~E., {Wyse}, R.~F.~G., {Gilmore}, G., {Yong}, D., {Frebel}, A.,
  {Wilkinson}, M.~I., {Belokurov}, V., \& {Zucker}, D.~B. 2010, \apj, 723, 1632

\bibitem[{{Peterson}(1981)}]{Peterson1981}
{Peterson}, R.~C. 1981, \apj, 244, 989

\bibitem[{{Roederer} {et~al.}(2010){Roederer}, {Sneden}, {Thompson}, {Preston},
  \& {Shectman}}]{Roederer2010}
{Roederer}, I.~U., {Sneden}, C., {Thompson}, I.~B., {Preston}, G.~W., \&
  {Shectman}, S.~A. 2010, \apj, 711, 573

\bibitem[{{Schlegel} {et~al.}(1998){Schlegel}, {Finkbeiner}, \&
  {Davis}}]{Schlegel1998}
{Schlegel}, D.~J., {Finkbeiner}, D.~P., \& {Davis}, M. 1998, \apj, 500, 525

\bibitem[{{Shetrone} {et~al.}(2003){Shetrone}, {Venn}, {Tolstoy}, {Primas},
  {Hill}, \& {Kaufer}}]{Shetrone2003}
{Shetrone}, M., {Venn}, K.~A., {Tolstoy}, E., {Primas}, F., {Hill}, V., \&
  {Kaufer}, A. 2003, \aj, 125, 684

\bibitem[{{Shetrone} {et~al.}(2001){Shetrone}, {C{\^o}t{\'e}}, \&
  {Sargent}}]{Shetrone2001}
{Shetrone}, M.~D., {C{\^o}t{\'e}}, P., \& {Sargent}, W.~L.~W. 2001, \apj, 548,
  592

\bibitem[{{Simon} {et~al.}(2011){Simon}, {Geha}, {Minor}, {Martinez}, {Kirby},
  {Bullock}, {Kaplinghat}, {Strigari}, {Willman}, {Choi}, {Tollerud}, \&
  {Wolf}}]{Simon2011}
{Simon}, J.~D., {et~al.} 2011, \apj, 733, 46

\bibitem[{{Sneden}(1973)}]{moog}
{Sneden}, C.~A. 1973, PhD thesis, The University of Texas at Austin

\bibitem[{{Soubiran} {et~al.}(2008){Soubiran}, {Bienaym{\'e}}, {Mishenina}, \&
  {Kovtyukh}}]{Soubiran2008}
{Soubiran}, C., {Bienaym{\'e}}, O., {Mishenina}, T.~V., \& {Kovtyukh}, V.~V.
  2008, \aap, 480, 91

\bibitem[{{Tolstoy} {et~al.}(2009){Tolstoy}, {Hill}, \& {Tosi}}]{Tolstoy2009}
{Tolstoy}, E., {Hill}, V., \& {Tosi}, M. 2009, ARA\&A, 47, 371

\bibitem[{{Venn} {et~al.}(2004){Venn}, {Irwin}, {Shetrone}, {Tout}, {Hill}, \&
  {Tolstoy}}]{Venn2004}
{Venn}, K.~A., {Irwin}, M., {Shetrone}, M.~D., {Tout}, C.~A., {Hill}, V., \&
  {Tolstoy}, E. 2004, \aj, 128, 1177

\end{thebibliography}

\end{document}

### 2012-08-16 2012-segue-1/segue_draft2.tex
added 2012 segue 1 paper + data. This is the pre-draft before it was re-sent out to the co-authors

--- 2012-08-16 2012-segue-1/rlunnan_v1.tex
@@
-\documentclass[manuscript]{aastex}
+\documentclass{emulateapj}
 %\documentclass[11pt,preprint]{aastex}
@@
 We present a high-resolution spectrum and abundance analysis of Segue1-11, the brightest likely stream member star from the kinematic sample of \citet{Norris2010a}.
-We determine a metallicity of [Fe/H] $ = -1.44$ for Segue1-11, and find abundance patterns similar to typical halo stars at this metallicity.
+We determine a metallicity of [Fe/H] $ = -1.44 \pm XX$ for Segue1-11, and find abundance patterns similar to typical halo stars at this metallicity.
 Comparing our stellar parameter solution to theoretical isochrones, we estimate a distance of $18 \pm 7$ kpc.
@@
 A well-known example is the stream extending from the Sagittarius dwarf spheroidal, which has been traced more than one full wrap around the Milky Way \citep[e.g.][]{Ibata1994, Majewski2003}.
-In a particularly busy piece of sky dubbed the ``Field of Streams'' \citep{Belokurov2006b}, at least two wraps of the Sagittarius stream as well as several other structures are visible.
+In a part of the sky dubbed the ``Field of Streams'' \citep{Belokurov2006b}, at least two wraps of the Sagittarius stream as well as several other structures are visible.
 
@@
 This includes four targets from the AAOmega sample not published in N10 due to slightly lower confidence in the radial velocity measurement.
+All photometry is from the Sloan Digital Sky Survey, DR7 \citep{Abazajian2009}.
+The estimated velocity uncertainty for the N10 stars is 10~km~s$^{-1}$; the individual velocity uncertainties for S11 stars are shown in the table.
 
@@
 The top left panel shows a histogram of the heliocentric radial velocities measured.
-The central peak ($\sim$ 270-330~km~s$^{-1}$) has a mean velocity of 300~km~s$^{-1}$ and a dispersion of 10.3~km~s$^{-1}$.
-Considering the independent N10 and S11 samples separately we still arrive at a dispersion of 10~km~s$^{-1}$ for the central peak, and similar means (303~km~s$^{-1}$ for N10 versus 298~km~s$^{-1}$ for S11).
+The central peak ($\sim$ 270-330~km~s$^{-1}$) has a mean velocity of $300.4 \pm 1.1 \mbox{km s}^{-1}$ and a dispersion of $10.3 \pm 1.2 \mbox{km s}^{-1}$.
+Considering the independent N10 and S11 samples separately we still arrive at a dispersion of 10~km~s$^{-1}$ for the central peak, and similar means ($303.3 \pm 3$~km~s$^{-1}$ for N10 versus $299.1 \pm 1$~km~s$^{-1}$ for S11).
 It is not clear whether the intermediate ``bridge'' candidates with 240~km~s$^{-1}$ $< v_{helio} < $270~km~s~$^{-1}$ or the three extreme-velocity stars with $v_{helio} > $ 340~km~s$^{-1}$ should be considered part of the same structure, but follow-up observations tracing the stream over a larger field of view could resolve this.
@@
 Note that the N10 sample covers a much larger field of view but does not go as deep -- as a result, most of the bright stream stars, including our target (star symbol), show up in this sample.
-In order to illustrate the photometric criteria used in the samples, the blue and red dots show the stars observed by N10 and S11, respectively, that meet their photometric selection cut but are radial velocity non-members of Segue\,1 and the stream.
+In order to illustrate the photometric criteria used in the samples, the blue and red dots show the stars observed by N10 and S11, respectively, that met their photometric selection cut for follow-up spectroscopy, but are radial velocity non-members of Segue\,1 and the stream.
 
 The solid line shows the M5 cluster sequence \citep{An2008}, which gives a good fit to the stream main sequence and subgiant branch when shifted to a distance of 18~kpc.
-The metallicity of M5 is [Fe/H] $= -1.3$, and so the SDSS photometry suggests that the stream is slightly more metal-rich than Segue\,1.
+The metallicity of M5 is [Fe/H] $= -1.3$, and the SDSS photometry suggests that the stream is slightly more metal-rich than Segue\,1 \citep{Simon2011}.
 The red giant branch of the stream is bluer than this sequence, however, and is better fit by e.g.
@@
 
-\begin{table}
- \begin{threeparttable}
-  \begin{center}
-    \caption{Stream Member Candidate Stars}
-    \label{tab:members}
-    {\tiny
-    \begin{tabular}{c c c c c c}
-     \hline \hline
-
-       Identifier                    & $g$     &  $r$    &    $i$    & $v_{hel}$ & Ref.       \\ \hline  
-     SDSSJ100914.95+155948.4\tnote{a}     & 17.997   & 17.495   & 17.262     &  307  & N10     \\
-     SDSSJ100740.13+160309.7\tnote{b}    & 19.965   & 19.551   & 19.448     &  298	& N10     \\
-     SDSSJ100659.01+154418.8         & 19.721   & 19.333   & 19.144     &  307	& N10     \\ 
-     SDSSJ100651.80+154941.5         & 20.365   & 20.049   & 19.911     &  300 	& AAO     \\
-     SDSSJ100619.95+154612.7         & 20.094   & 19.786   & 19.679     &  315 	& AAO     \\
-     SDSSJ100612.02+154548.4         & 20.080   & 19.626   & 19.616     &  327	& N10     \\
-     SDSSJ100530.59+155418.1         & 19.831   & 19.493   & 19.314     &  305	& N10     \\
-     SDSSJ100627.73+155408.6         & 20.155   & 19.880   & 19.711     &  300	& AAO     \\
-     SDSSJ100647.74+161330.1         & 20.011   & 19.704   & 19.516     &  300  & AAO     \\
-     SDSSJ100658.49+162045.6         & 19.840   & 19.379   & 19.187     &  295	& N10     \\
-     SDSSJ100839.66+162826.7         & 19.169   & 18.739   & 18.608     &  288	& N10     \\   
-     SDSSJ100600.16+160518.6         & 20.220	& 19.688   & 19.518	&  242  & N10     \\
-     SDSSJ100618.74+160339.0         & 21.678   & 21.147   & 20.906     &  268  & S11     \\
-     SDSSJ100619.99+160042.1         & 21.705   & 21.417   & 21.180     &  305	& S11     \\
-     SDSSJ100630.89+161512.1         & 21.479   & 21.131   & 20.952     &  321	& S11     \\
-     SDSSJ100642.76+155709.3         & 21.562   & 21.233   & 21.029     &  291	& S11     \\
-     SDSSJ100646.78+160608.3         & 20.534   & 20.221   & 20.076     &  294	& S11     \\
-     SDSSJ100648.52+160958.1         & 20.279   & 19.980   & 19.798     &  306	& S11     \\
-     SDSSJ100650.83+160351.2         & 22.137   & 21.952   & 21.838     &  312	& S11     \\
-     SDSSJ100654.23+155520.7         & 22.127   & 21.533   & 21.290     &  268	& S11     \\
-     SDSSJ100656.13+160660.0         & 21.347   & 21.099   & 20.994     &  302	& S11     \\
-     SDSSJ100658.54+155748.9         & 21.562   & 21.096   & 20.840     &  290	& S11     \\
-     SDSSJ100704.58+160130.8         & 21.229   & 20.814   & 20.762     &  295	& S11     \\
-     SDSSJ100704.63+160812.6         & 21.088   & 20.851   & 20.743     &  296	& S11     \\
-     SDSSJ100708.37+155646.3         & 22.039   & 21.562   & 21.458     &  286	& S11     \\
-     SDSSJ100709.07+160436.6         & 22.292   & 21.889   & 21.576     &  312	& S11     \\
-     SDSSJ100709.74+155312.3         & 16.113   & 15.833   & 15.721     &  303	& S11     \\
-     SDSSJ100712.96+155734.8         & 18.287   & 18.009   & 17.872     &  307	& S11     \\
-     SDSSJ100713.69+160444.8         & 22.139   & 21.765   & 21.476     &  293	& S11     \\
-     SDSSJ100715.51+160552.1         & 20.360   & 20.076   & 19.974     &  282	& S11     \\
-     SDSSJ100715.53+161519.1         & 20.741   & 20.439   & 20.427     &  266	& S11     \\
-     SDSSJ100717.15+160511.9         & 22.104   & 21.781   & 21.385     &  266	& S11     \\
-     SDSSJ100717.36+160355.6         & 20.116   & 19.778   & 19.646     &  295	& S11     \\
-     SDSSJ100720.00+160137.5         & 17.626   & 17.274   & 17.127     &  312	& S11     \\
-     SDSSJ100721.16+161118.2         & 20.990   & 19.732   & 19.203     &  281	& S11     \\
-     SDSSJ100721.77+155424.5         & 20.619   & 20.223   & 20.220     &  307	& S11     \\
-     SDSSJ100729.58+161107.1         & 20.358   & 19.347   & 19.026     &  309  & S11     \\     
-     SDSSJ100732.47+160500.5         & 22.588   & 22.043   & 21.911     &  281	& S11     \\
-     SDSSJ100734.97+155431.5         & 20.788   & 20.542   & 20.391     &  303	& S11     \\
-     SDSSJ100737.37+160746.2         & 21.253   & 20.992   & 20.812     &  296	& S11     \\
-     SDSSJ100740.15+155855.6         & 21.323   & 20.969   & 20.809     &  295	& S11     \\
-     SDSSJ100742.51+160006.8         & 22.476   & 22.024   & 21.463     &  296	& S11     \\
-     SDSSJ100743.78+154932.9         & 22.472   & 20.985   & 20.369     &  299	& S11     \\
-     SDSSJ100747.19+160545.5         & 20.135   & 19.770   & 19.677     &  294	& S11     \\ 
-     SDSSJ100735.92+161125.7         & 23.791   & 22.084   & 22.003    &  242  & S11     \\
-     SDSSJ100625.70+155422.1         & 21.587   & 21.135   & 20.950    &  244	& S11     \\
-     SDSSJ100711.80+160630.4         & 22.802   & 22.160   & 21.952    &  247	& S11     \\
-     SDSSJ100707.80+160721.5         & 20.643   & 20.342   & 20.239    &  248	& S11     \\
-     SDSSJ100735.24+155715.3         & 22.535   & 21.135   & 20.411    &  255	& S11     \\
-     SDSSJ100628.41+155628.8         & 17.852   & 17.560   & 17.431    &  347	& S11     \\
-     SDSSJ100736.92+155958.9         & 21.994   & 21.871   & 21.609    &  373	& S11     \\
-     SDSSJ100651.74+161759.2         & 21.407   & 20.923   & 20.953    &  394	& S11     \\ \hline
-
-     \end{tabular} }
-     \begin{tablenotes}
-       \item[a]{{\tiny Segue1-11, target star.}}
-%       \item[b]{{\tiny From high-resolution measurement (this paper).}}
-       \item[b]{{\tiny Observed by both N10 and S11.}}
-      \end{tablenotes}
-     \end{center}
-   \end{threeparttable}
-\end{table}
+\begin{deluxetable*}{lcccccccc}
+\tabletypesize{\scriptsize}
+\tablecaption{Stream Member Candidate Stars\label{tab:members}}
+\tablehead{
+	\colhead{Identifier} &
+	\colhead{R. A.} &
+	\colhead{Dec.} &
+	\colhead{$g$} &
+	\colhead{$r$} &
+	\colhead{$i$} &
+	\colhead{$g \-- r$} &
+	\colhead{$V_{hel}$} &
+	\colhead{Ref} \\
+  & (J2000) & (J2000) & & & & & (km s$^{-1}$) &  
+}
+\startdata
+300S-1\tablenotemark{a} & 10\phn09\phn15.0 & $+$15\phn59\phn48.4 &  17.99 & 17.49 & 17.26 & 0.73 & 307 & N10 \\
+300S-2 & 10\phn07\phn40.1 & $+$16\phn03\phn09.7 &  19.96 & 19.55 & 19.44 & 0.52 & 298 & N10, S11    \\
+300S-3 & 10\phn06\phn59.0 & $+$15\phn44\phn18.8 &  19.72 & 19.33 & 19.14 & 0.58 & 307 & N10     \\
+300S-4 & 10\phn06\phn51.8 & $+$15\phn49\phn41.5 &  20.36 & 20.04 & 19.91 & 0.45 & 300 & AAO     \\
+300S-5 & 10\phn06\phn20.0 & $+$15\phn46\phn12.7 &  20.09 & 19.78 & 19.67 & 0.42 & 315 & AAO     \\
+300S-6 & 10\phn06\phn12.0 & $+$15\phn45\phn48.4 &  20.08 & 19.62 & 19.61 & 0.47 & 327 & N10     \\
+300S-7 & 10\phn05\phn30.6 & $+$15\phn54\phn18.1 &  19.83 & 19.49 & 19.31 & 0.52 & 305 & N10     \\
+300S-8 & 10\phn06\phn27.7 & $+$15\phn54\phn08.6 &  20.15 & 19.88 & 19.71 & 0.44 & 300 & AAO     \\
+300S-9 & 10\phn06\phn47.7 & $+$16\phn13\phn30.1 &  20.01 & 19.70 & 19.51 & 0.50 & 300 & AAO     \\
+300S-10 & 10\phn06\phn58.5 & $+$16\phn20\phn45.6 &  19.84 & 19.37 & 19.18 & 0.66 & 295 & N10     \\
+300S-11 & 10\phn08\phn39.7 & $+$16\phn28\phn26.7 &  19.16 & 18.73 & 18.60 & 0.56 & 288 & N10     \\
+300S-12 & 10\phn06\phn00.2 & $+$16\phn05\phn18.6 &  20.22 & 19.68 & 19.51 & 0.71 & 242 & N10      \\
+300S-13 & 10\phn06\phn18.7 & $+$16\phn03\phn39.0 &  21.67 & 21.14 & 20.90 & 0.77 & 268.6  $\pm$\phn3.1 & S11     \\
+300S-14 & 10\phn06\phn20.0 & $+$16\phn00\phn42.1 &  21.70 & 21.41 & 21.18 & 0.52 & 305.5  $\pm$\phn4.3 & S11     \\
+300S-15 & 10\phn06\phn30.9 & $+$16\phn15\phn12.1 &  21.47 & 21.13 & 20.95 & 0.52 & 321.0  $\pm$\phn8.8 & S11     \\
+300S-16 & 10\phn06\phn42.8 & $+$15\phn57\phn09.3 &  21.56 & 21.23 & 21.02 & 0.54 & 291.9  $\pm$\phn6.4 & S11     \\
+300S-17 & 10\phn06\phn46.8 & $+$16\phn06\phn08.3 &  20.53 & 20.22 & 20.07 & 0.46 & 294.5  $\pm$\phn2.9 & S11     \\
+300S-18 & 10\phn06\phn48.5 & $+$16\phn09\phn58.1 &  20.27 & 19.98 & 19.79 & 0.48 & 306.0  $\pm$\phn2.6 & S11     \\
+300S-19 & 10\phn06\phn50.8 & $+$16\phn03\phn51.2 &  22.13 & 21.95 & 21.83 & 0.30 & 312.6  $\pm$11.9 & G09, S11     \\
+300S-20 & 10\phn06\phn54.2 & $+$15\phn55\phn20.7 &  22.12 & 21.53 & 21.29 & 0.83 & 268.5  $\pm$\phn6.2 & S11     \\
+300S-21 & 10\phn06\phn56.1 & $+$16\phn06\phn60.0 &  21.34 & 21.09 & 20.99 & 0.35 & 302.0  $\pm$\phn2.6 & S11     \\
+300S-22 & 10\phn06\phn58.5 & $+$15\phn57\phn48.9 &  21.56 & 21.09 & 20.84 & 0.72 & 290.5  $\pm$\phn3.6 & S11     \\
+300S-23 & 10\phn07\phn04.6 & $+$16\phn01\phn30.8 &  21.22 & 20.81 & 20.76 & 0.46 & 295.8  $\pm$\phn3.9 & S11     \\
+300S-24 & 10\phn07\phn04.6 & $+$16\phn08\phn12.6 &  21.08 & 20.85 & 20.74 & 0.34 & 296.9  $\pm$\phn3.4 & S11     \\
+300S-25 & 10\phn07\phn08.4 & $+$15\phn56\phn46.3 &  22.03 & 21.56 & 21.45 & 0.58 & 286.3  $\pm$\phn5.4 & S11     \\
+300S-26 & 10\phn07\phn09.1 & $+$16\phn04\phn36.6 &  22.29 & 21.88 & 21.57 & 0.72 & 312.7  $\pm$\phn6.4 & S11     \\
+300S-27 & 10\phn07\phn09.7 & $+$15\phn53\phn12.3 &  16.11 & 15.83 & 15.72 & 0.39 & 303.4  $\pm$\phn2.2 & S11     \\
+300S-28 & 10\phn07\phn13.0 & $+$15\phn57\phn34.8 &  18.28 & 18.00 & 17.87 & 0.41 & 307.9  $\pm$\phn2.4 & S11     \\
+300S-29 & 10\phn07\phn13.7 & $+$16\phn04\phn44.8 &  22.13 & 21.76 & 21.47 & 0.66 & 293.4  $\pm$\phn4.8 & G09, S11     \\
+300S-30 & 10\phn07\phn15.5 & $+$16\phn05\phn52.1 &  20.36 & 20.07 & 19.97 & 0.39 & 282.0  $\pm$\phn2.8 & S11     \\
+300S-31 & 10\phn07\phn15.5 & $+$16\phn15\phn19.1 &  20.74 & 20.43 & 20.42 & 0.32 & 266.8  $\pm$\phn3.1 & S11     \\
+300S-32 & 10\phn07\phn17.2 & $+$16\phn05\phn11.9 &  22.10 & 21.78 & 21.38 & 0.72 & 266.3  $\pm$\phn4.4 & S11     \\
+300S-33 & 10\phn07\phn17.4 & $+$16\phn03\phn55.6 &  20.11 & 19.77 & 19.64 & 0.47 & 295.9  $\pm$\phn2.4 & G09, S11    \\
+300S-34 & 10\phn07\phn20.0 & $+$16\phn01\phn37.5 &  17.62 & 17.27 & 17.12 & 0.50 & 312.7  $\pm$\phn2.2 & S11     \\
+300S-35 & 10\phn07\phn21.2 & $+$16\phn11\phn18.2 &  20.99 & 19.73 & 19.20 & 1.79 & 281.6  $\pm$\phn2.4 & S11     \\
+300S-36 & 10\phn07\phn21.8 & $+$15\phn54\phn24.5 &  20.61 & 20.22 & 20.22 & 0.39 & 307.2  $\pm$\phn5.5 & S11     \\
+300S-37 & 10\phn07\phn29.6 & $+$16\phn11\phn07.1 &  20.35 & 19.34 & 19.02 & 1.33 & 309.6  $\pm$\phn2.2 & S11     \\
+300S-38 & 10\phn07\phn32.5 & $+$16\phn05\phn00.5 &  22.58 & 22.04 & 21.91 & 0.67 & 281.1  $\pm$\phn6.9 & G09, S11     \\
+300S-39 & 10\phn07\phn35.0 & $+$15\phn54\phn31.5 &  20.78 & 20.54 & 20.39 & 0.39 & 303.2  $\pm$\phn2.8 & S11     \\
+300S-40 & 10\phn07\phn37.3 & $+$16\phn07\phn46.2 &  21.25 & 20.99 & 20.81 & 0.44 & 296.0  $\pm$\phn3.9 & S11     \\
+300S-41 & 10\phn07\phn40.2 & $+$15\phn58\phn55.6 &  21.32 & 20.96 & 20.80 & 0.52 & 295.8  $\pm$\phn3.8 & S11     \\
+300S-42 & 10\phn07\phn42.5 & $+$16\phn00\phn06.8 &  22.47 & 22.02 & 21.46 & 1.01 & 296.6  $\pm$10.3 & S11     \\
+300S-43 & 10\phn07\phn43.8 & $+$15\phn49\phn32.9 &  22.47 & 20.98 & 20.36 & 2.11 & 299.2  $\pm$\phn2.5 & S11     \\
+300S-44 & 10\phn07\phn47.2 & $+$16\phn05\phn45.5 &  20.13 & 19.77 & 19.67 & 0.46 & 294.3  $\pm$\phn2.4 & S11     \\
+300S-45 & 10\phn07\phn35.9 & $+$16\phn11\phn25.7 &  23.79 & 22.08 & 22.00 & 1.79 & 242.2  $\pm$\phn7.8 & S11     \\
+300S-46 & 10\phn06\phn25.7 & $+$15\phn54\phn22.1 &  21.58 & 21.13 & 20.95 & 0.63 & 244.3  $\pm$\phn5.6 & S11     \\
+300S-47 & 10\phn07\phn11.8 & $+$16\phn06\phn30.4 &  22.80 & 22.16 & 21.95 & 0.85 & 247.1  $\pm$15.9 & S11     \\
+300S-48 & 10\phn07\phn07.8 & $+$16\phn07\phn21.5 &  20.64 & 20.34 & 20.23 & 0.41 & 247.7  $\pm$\phn2.8 & S11     \\
+300S-49 & 10\phn07\phn35.2 & $+$15\phn57\phn15.3 &  22.53 & 21.13 & 20.41 & 2.12 & 255.1  $\pm$\phn3.0 & S11     \\
+300S-50 & 10\phn06\phn28.4 & $+$15\phn56\phn28.8 &  17.85 & 17.56 & 17.43 & 0.42 & 347.1  $\pm$\phn2.9 & S11     \\
+300S-51 & 10\phn07\phn36.9 & $+$15\phn59\phn58.9 &  21.99 & 21.87 & 21.60 & 0.39 & 373.0  $\pm$\phn6.0 & S11     \\
+300S-52 & 10\phn06\phn51.7 & $+$16\phn17\phn59.2 &  21.40 & 20.92 & 20.95 & 0.45 & 394.9  $\pm$\phn8.9 & S11 
+\enddata
+\tablenotetext{a}{Target star, referenced as Segue1-11 in N10}
+\end{deluxetable*}
 
@@
 
-\begin{table}
- \begin{threeparttable}
- \begin{center}
-   \caption{Targets: Segue1-11 and comparison stars}
-   \label{tab:targets}
-   \begin{tabular}{l c c c c}
-     \hline \hline
-       Name       &  RA            & Dec             & V$_{\mbox{mag}}$ & B-V       \\ \hline  
-       Segue 1-11 &  $10:09:14.95$ &  $+15:59:48.4$  & 17.70\tnote{a}   &  0.68\tnote{a}       \\
-       HIP37335   &  $07:39:50.11$ &  $-01:31:20.37$ & 9.25             &  0.82       \\
-       HIP47139   &  $09:36:19.95$ &  $-20:53:14.75$ & 8.34             &  1.01       \\
-       HIP68807   &  $14:05:13.02$ &  $-14:51:25.45$ & 7.25             &  0.93       \\ \hline    
-  \end{tabular}
-  \begin{tablenotes}
-   \item[a]{Transformed from the SDSS photometry following \citet{Jordi2006}}
-  \end{tablenotes}
- \end{center}
-\end{threeparttable}
-\end{table}
-
-\begin{table}
- \begin{center}
-   \caption{Summary of Observations}
-   \label{tab:segobs}
-   \begin{tabular}{c c c c }
-     \hline \hline
-       Object    &  UT date    & UT start time & t$_{\mbox{exp}}$ (s)   \\ \hline  
-       Segue1-11 &  03/08/2010 & 02:35         & 3000            \\
-       Segue1-11 &  03/08/2010 & 05:30         & 3600            \\
-       Segue1-11 &  03/19/2010 & 05:06         & 3000            \\
-       Segue1-11 &  03/22/2010 & 00:37         & 3100            \\
-       Segue1-11 &  03/22/2010 & 05:22         & 2800            \\
-       Segue1-11 &  03/23/2010 & 05:08         & 700             \\
-       HIP37335  &  03/13/2011 & 23:41         &  7              \\
-       HIP68807  &  03/12/2011 & 10:08         &  1              \\
-       HIP47139  &  03/13/2011 & 23:53         &  5              \\
-      \hline
-  \end{tabular}
- \end{center}
-\end{table}
+\begin{deluxetable*}{lcccccccc}
+\tabletypesize{\scriptsize}
+\tablecaption{Observed Targets \label{tab:targets}}
+\tablehead{
+	\colhead{Name} &
+	\colhead{R. A.} &
+	\colhead{Dec.} &
+	\colhead{$V$} &
+	\colhead{$B \-- V$} & 
+	\colhead{UT Date} &
+	\colhead{UT Start} &
+	\colhead{$t_{exp}$} \\
+  & (J2000) & (J2000) & & & & & ($s$)   
+}
+\startdata  
+300S-1     &  10\phn09\phn15.0 &  $+$15\phn59\phn48.4 & 17.70\tablenotemark{a} &  0.68\tablenotemark{a} & 03/08/2010 & 02:35 & 3000 \\
+ & & & & & 03/08/2010 & 05:30 & 3600 \\
+ & & & & & 03/19/2010 & 05:06 & 3000 \\
+ & & & & & 03/22/2010 & 00:37 & 3100 \\
+ & & & & & 03/22/2010 & 05:22 & 2800 \\
+ & & & & & 03/23/2010 & 05:08 & 700 \\
+HIP37335   &  07\phn39\phn50.1 &  $-$01\phn31\phn20.4 & 9.25 &  0.82 & 03/13/2011 & 23:41 & 7      \\
+HIP47139   &  09\phn36\phn20.0 &  $-$20\phn53\phn14.8 & 8.34 &  1.01 & 03/12/2011 & 10:08 & 1      \\
+HIP68807   &  14\phn05\phn13.0 &  $-$14\phn51\phn25.5 & 7.25 &  0.93 & 03/13/2011 & 23:53 & 5      
+\enddata
+\tablenotetext{a}{Transformed from SDSS photometry following \citet{Jordi2006}}
+\end{deluxetable*}
 
@@
  \begin{center}
-  \includegraphics[width=9cm]{Mgspecs.ps}
+  \includegraphics[width=9cm]{Mgspecs_fixed.eps}
   \caption{High-resolution spectrum of our target star, Segue1-11, and the three comparison stars from the F00 sample, in the region around the Mg b-lines.
@@
 Equivalent widths were then measured by fitting Gaussian profiles, and our estimate corrected based on the mean radial velocity from all the lines measured.
-Using these 366 lines, we find a heliocentric radial velocity of $307.62$~km~s$^{-1}$, with a standard error of the mean of 0.09~km~s$^{-1}$.
+Using these 366 lines, we find a heliocentric radial velocity of $307.6$~km~s$^{-1}$, with a standard error of the mean of 0.1~km~s$^{-1}$.
 This is slightly higher than the estimate of $301$~km~s$^{-1}$ from N10 based on the medium resolution spectrum, but consistent within their estimated velocity uncertainty of 10~km~s$^{-1}$.
@@
 This is, however, well within our estimate of uncertainty for the metallicity (see Section~\ref{sec:unc}).
-For the rest of the analysis, we use the parameters derived from spectroscopy, however, to facilitate comparison with the Fulbright/Hipparcos stars.
-
-\begin{table}
-\begin{threeparttable}
- \begin{center}
-   \caption{Stellar parameters: Segue1-11 and comparison stars}
-   \label{tab:comp_para}
-   \begin{tabular}{l c c c c  }
-     \hline \hline
-       Name       &  T$_{\mbox{\tiny{eff}}}$ (K) & $\log$ g  & [Fe/H]            & $v_{\mu}$ (km~s$^{-1}$)   \\ \hline  
-       Segue 1-11 &  5200          &  2.6      & $-1.4$            & 1.5                \\
-       HIP37335\tnote{a}   &  5100 (4850)   &  2.9 (2.7)& $-1.0$ ($-1.2$)   & 1.5 (1.5)           \\
-       HIP47139   &  4550 (4600)   &  0.9 (1.3)& $-1.6$ ($-1.4$)   & 2.3 (1.8)          \\
-       HIP68807   &  4600 (4575)   &  1.0 (1.1)& $-1.8$ ($-1.8$)   & 2.0 (1.9)          \\ \hline
-  \end{tabular}
-  \begin{tablenotes}
-  \item[a]{While our solution for HIP37335 is warmer than what was found in F00, we note that our solution agrees with other literature sources for this star \citep[e.g.,][]{Soubiran2008, Cenarro2007, Peterson1981}.}
-  \end{tablenotes}
- \end{center}
- \end{threeparttable}
-\end{table}
+For the rest of the analysis, we use the parameters derived from spectroscopy to facilitate the relative analysis with the \citet{Fulbright2000} stars.
 
@@
 
-\begin{table}
-  \begin{center}
- \caption{Segue1-11 Abundances Measured}
- \label{tab:seg11_abund}
-    \begin{tabular}{l c c c c c c}
-     \hline \hline
-Elem. & $\log\epsilon (\mbox{X}_{\odot})$ & $\log\epsilon (\mbox{X})$ & $\sigma$ & $N$ & [X/H] & [X/Fe] \\ \hline
-C (CH) & 8.43 & 7.24     & 0.21 & 2   & $-1.19$ & $+0.25 $ \\
-Na\,I  & 6.24 & 4.93     & 0.08 & 3   & $-1.31$ & $+0.15 $ \\
-Mg\,I  & 7.60 & 6.30     & 0.07 & 6   & $-1.30$ & $+0.14 $ \\
-Ca\,I  & 6.34 & 5.30     & 0.06 & 16  & $-1.04$ & $+0.40 $ \\
-Sc\,II & 3.15 & 1.46     & 0.05 & 3	  & $-1.69$ & $-0.25 $ \\ 
-Ti\,I  & 4.95 & 3.69     & 0.07 & 18  & $-1.26$ & $+0.18 $ \\
-Ti\,II & 4.95 & 3.77     & 0.06 & 17  & $-1.18$ & $+0.26 $ \\
-Cr\,I  & 5.64 & 3.96     & 0.05 & 8   & $-1.68$ & $-0.24 $ \\
-Mn\,I  & 5.43 & 3.41     & 0.07 & 3	  & $-2.02$ & $-0.58 $ \\ 
-Fe\,I  & 7.50 & 6.04     & 0.05 & 103 & $-1.46$ & ...      \\
-Fe\,II & 7.50 & 6.08     & 0.05 & 10  & $-1.42$ & ...      \\
-Co\,I  & 4.99 & 3.29     & 0.12 & 3   & $-1.70$ & $-0.26 $ \\ 
-Ni\,I  & 6.22 & 4.73     & 0.06 & 14  & $-1.49$ & $-0.05 $ \\
-Zn\,I  & 4.56 & 3.18     & 0.25 & 2   & $-1.38$ & $+0.06 $ \\ 
-Sr\,II & 2.87 & 0.50:    & 0.40 & 1  & $-3.07$: & $-0.93$: \\ 
-Ba\,II & 2.18 & 0.83     & 0.21 & 2	  & $-1.35$ & $+0.09 $ \\
+\begin{deluxetable}{lcccccccc}
+\tabletypesize{\scriptsize}
+\tablecaption{300S-1 Abundances \label{tab:seg11_abund}}
+\tablehead{
+	\colhead{Element} &
+	\colhead{$\log\epsilon (\mbox{X}_{\odot})$} &
+	\colhead{$\log\epsilon (\mbox{X})$} &
+	\colhead{$\sigma$} &
+	\colhead{$N$} & 
+	[X/H] &
+	[X/Fe] \\
+	& (dex) & (dex) & (dex) & & (dex) & (dex)
+}
+\startdata  
+C (CH) & 8.43 & \phn7.24 & 0.21 & 2   & $-1.19$ & $+0.25 $ \\
+Na\,I  & 6.24 & \phn4.93 & 0.08 & 3   & $-1.31$ & $+0.15 $ \\
+Mg\,I  & 7.60 & \phn6.30 & 0.07 & 6   & $-1.30$ & $+0.14 $ \\
+Ca\,I  & 6.34 & \phn5.30 & 0.06 & 16  & $-1.04$ & $+0.40 $ \\
+Sc\,II & 3.15 & \phn1.46 & 0.05 & 3   & $-1.69$ & $-0.25 $ \\ 
+Ti\,I  & 4.95 & \phn3.69 & 0.07 & 18  & $-1.26$ & $+0.18 $ \\
+Ti\,II & 4.95 & \phn3.77 & 0.06 & 17  & $-1.18$ & $+0.26 $ \\
+Cr\,I  & 5.64 & \phn3.96 & 0.05 & 8   & $-1.68$ & $-0.24 $ \\
+Mn\,I  & 5.43 & \phn3.41 & 0.07 & 3   & $-2.02$ & $-0.58 $ \\ 
+Fe\,I  & 7.50 & \phn6.04 & 0.05 & 103 & $-1.46$ & \nodata  \\
+Fe\,II & 7.50 & \phn6.08 & 0.05 & 10  & $-1.42$ & \nodata  \\
+Co\,I  & 4.99 & \phn3.29 & 0.12 & 3   & $-1.70$ & $-0.26$ \\ 
+Ni\,I  & 6.22 & \phn4.73 & 0.06 & 14  & $-1.49$ & $-0.05$ \\
+Zn\,I  & 4.56 & \phn3.18 & 0.25 & 2   & $-1.38$ & $+0.06$ \\ 
+Sr\,II & 2.87 & \phn0.50:& 0.40 & 1   & $-3.07$:& $-0.93$: \\ 
+Ba\,II & 2.18 & \phn0.83 & 0.21 & 2   & $-1.35$ & $+0.09$ \\
 La\,II & 1.10 & $-0.38$  & 0.30 & 1   & $-1.48$ & $-0.04$ \\
-Eu\,II & 0.52 & $-0.39$: & 0.40 & 1	  & $-0.91$: & $+0.53 $: \\ \hline
-
- \end{tabular}				      
- \end{center}
-\end{table}
+Eu\,II & 0.52 & $-0.39$: & 0.40 & 1   & $-0.91$: & $+0.53 $:
+\enddata
+\end{deluxetable}
 
@@
 Random errors come from uncertainties in placing the continuum level; we estimate the random uncertainty in the abundance of an element as the standard error of the mean abundance determined from individual lines.
-For elements that were determined from fitting a single line to a synthetic spectrum (Sr, Eu and La), the error quoted in the second column is the fit uncertainty.
+For elements that were determined from fitting a single line to a synthetic spectrum (Sr, Eu and La), the error quoted in the second colu
+ is the fit uncertainty.
 
@@
 Our abundances are in good agreement within the uncertainties, especially when taking into account the different stellar parameter solution for HIP37335.
-We note that we systematically arrive at lower Mg abundances for the comparison stars than F00, but not for the other $\alpha$-elements Ca and Ti.
+
+%We note that we systematically arrive at lower Mg abundances for the comparison stars than F00, but not for the other $\alpha$-elements Ca and Ti.
 This could indicate that our Mg abundance for Segue1-11 is also too low.
 
-\begin{table}
- \begin{center}
- \caption{Abundance Uncertainties for Segue1-11}
- \label{tab:seg11_sigma}
-  \begin{tabular}{l c c c c c}
-  \hline \hline
-  Elem.    & Random      & $\Delta T_{eff}$ & $\Delta \log g$ & $\Delta v_{micr}$ & Total       \\
-           & Uncer.      & +150 K           &  +0.4 dex       & +0.3~km~s$^{-1}$  & Uncer.      \\ \hline
-  C (CH)   &  0.21       &  0.30            & $-0.05$         & $-0.02$           & 0.37        \\
-  Na\,I    &  0.08 	 &  0.16            & $-0.10$	      &	$-0.04$		  & 0.21	\\
-  Mg\,I    &  0.07 	 &  0.16            & $-0.11$	      &	$-0.05$           & 0.21	\\
-  Ca\,I    &  0.06 	 &  0.13	    & $-0.05$	      &	$-0.10$		  & 0.18	\\
-  Sc\,II   &  0.05 	 &  0.02	    & $+0.16$	      &	$-0.02$		  & 0.17	\\
-  Ti\,I    &  0.07 	 &  0.20	    & $-0.02$	      &	$-0.09$		  & 0.23	\\
-  Ti\,II   &  0.06 	 &  0.03	    & $+0.15$	      &	$-0.09$		  & 0.19	\\
-  Cr\,I    &  0.05 	 &  0.19	    & $-0.01$	      &	$-0.08$		  & 0.21	\\
-  Mn\,I    &  0.07 	 &  0.15	    & $-0.03$	      &	$-0.10$		  & 0.20	\\ 
-  Fe\,I    &  0.05 	 &  0.18	    & $-0.04$	      &	$-0.13$		  & 0.23	\\
-  Fe\,II   &  0.05 	 &$-0.02$	    & $+0.16$	      &	$-0.09$		  & 0.19	\\
-  Co\,I    &  0.12 	 &  0.25	    & $+0.00$	      &	$-0.20$		  & 0.34	\\ 
-  Ni\,I    &  0.06 	 &  0.14	    & $+0.00$	      &	$-0.06$		  & 0.16	\\
-  Zn\,I    &  0.25 	 &  0.04	    & $+0.10$	      &	$-0.05$		  & 0.28	\\
-  Sr\,II   &  0.40 	 &  0.10	    & $+0.02$	      &	$-0.10$		  & 0.42	\\ 
-  Ba\,II   &  0.21 	 &  0.09	    & $+0.08$	      &	$-0.18$		  & 0.30	\\
-  La\,II   &  0.30       &  0.05            & $+0.15$         & $-0.05$           & 0.34        \\
-  Eu\,II   &  0.40 	 &  0.05	    & $+0.15$	      &	$-0.05$		  & 0.43	\\ \hline
-
-  \end{tabular}
- \end{center}
-\end{table}
-
-\begin{table}
-  \begin{center}
- \caption{Abundances measured for HIP37335, HIP68807 and HIP47139}
- \label{tab:hipabund}
-    {\tiny
-    \begin{tabular}{l c c c c c c }
-     \hline \hline
-Elem.  & $\log\epsilon (\mbox{X})$ & $\sigma$ & $N$ & [X/H] & [X/Fe] & [X/Fe]fb \\ \hline
-       &          &       & HIP37335 &              &             &            \\ \hline
-C (CH) &   7.71   & 0.21    &  2    &    $ -0.72 $  &  $ +0.29 $  &             \\
-Na\,I  &   5.46   & 0.07    &  4    &    $ -0.78 $  &  $ +0.23 $  &   $+0.32 $  \\       
-Mg\,I  &   7.05   & 0.12    &  4    &    $ -0.55 $  &  $ +0.46 $  &   $+0.63 $  \\       
-Ca\,I  &   5.86   & 0.05    &  16   &    $ -0.48 $  &  $ +0.53 $  &   $+0.44 $  \\       
-Sc\,II &   2.40   & 0.05    &  9    &    $ -0.75 $  &  $ +0.26 $  &   $      $  \\       
-Ti\,I  &   4.20   & 0.05    &  28   &    $ -0.75 $  &  $ +0.26 $  &   $+0.26 $  \\       
-Ti\,II &   4.20   & 0.05    &  16   &    $ -0.75 $  &  $ +0.26 $  &   $      $  \\       
-Cr\,I  &   4.65   & 0.05    &  14   &    $ -0.99 $  &  $ +0.02 $  &   $-0.05 $  \\       
-Mn\,I  &   4.61   & 0.05    &  3    &    $ -0.82 $  &  $ +0.19 $  &   $      $  \\       
-Fe\,I  &   6.50   & 0.05    &  124  &    $ -1.00 $  &  $ ...   $  &  $(-1.26)$  \\       
-Fe\,II &   6.48   & 0.05    &  15   &    $ -1.02 $  &  $ ...   $  &   $      $  \\  
-Co\,I  &   3.55   & 0.05    &  3    &    $ -1.44 $  &  $ -0.43 $  &             \\
-Ni\,I  &   5.30   & 0.05    &  24   &    $ -0.92 $  &  $ +0.09 $  &   $+0.10 $  \\   
-Zn\,I  &   3.78   & 0.08    &   2   &    $ -0.78 $  &  $ +0.23 $  &   $      $  \\       
-Ba\,II &   1.43   & 0.21    &  2    &    $ -0.75 $  &  $ +0.26 $  &   $-0.02 $  \\
-La\,II &   0.42   & 0.30    &  1    &    $ -0.68 $  &  $ +0.33 $  &             \\
-Eu\,II & $-0.19$  & 0.30    &  1    &    $ -0.71 $  &  $ +0.30	$  &   $+0.38 $  \\  \hline      
-       &          &       & HIP68807 &              &             &            \\ \hline
-
-C (CH) &     6.76 &  0.21     &    2   &      $ -1.67 $  &   $ +0.17 $  &               \\
-Na\,I  &     4.36 &  0.05     &    3   &      $ -1.88 $  &   $ -0.04 $  &  $  -0.13  $  \\       
-Mg\,I  &     6.17 &  0.05     &    6   &      $ -1.43 $  &   $ +0.41 $  &  $  +0.49  $  \\       
-Ca\,I  &     4.89 &  0.05     &    17  &      $ -1.45 $  &   $ +0.39 $  &  $  +0.37  $  \\       
-Sc\,II &     1.45 &  0.06     &    6   &      $ -1.70 $  &   $ +0.14 $  &  $         $  \\       
-Ti\,I  &     3.25 &  0.05     &    23  &      $ -1.70 $  &   $ +0.14 $  &  $  +0.20  $  \\       
-Ti\,II &     3.45 &  0.05     &    18  &      $ -1.50 $  &   $ +0.34 $  &  $         $  \\       
-Cr\,I  &     3.61 &  0.05     &    14  &      $ -2.03 $  &   $ -0.19 $  &  $  -0.12  $  \\       
-Mn\,I  &     3.40 &  0.07     &    3   &      $ -2.03 $  &   $ -0.19 $  &  $         $  \\       
-Fe\,I  &     5.64 &  0.05     &    127 &      $ -1.86 $  &   $ ...   $  &  $ (-1.83) $  \\       
-Fe\,II &     5.68 &  0.05     &    14  &      $ -1.82 $  &   $ ...   $  &  $         $  \\       
-Ni\,I  &     4.48 &  0.05     &    12  &      $ -1.74 $  &   $ +0.10 $  &  $  -0.03  $  \\    
-Zn\,I  &     2.84 &               &    1   &      $ -1.72 $  &   $ +0.12 $  &  $         $  \\      
-Ba\,II &     0.69 &  0.14     &    3   &      $ -1.49 $  &   $ +0.35 $  &  $  +0.27  $  \\
-La\,II &  $-0.68$ &  0.30     &    1   &      $-1.78$    &   $ +0.06 $  &               \\
-Eu\,II &  $-0.99$ &  0.40     &    1   &      $ -1.51 $	 &   $ +0.33 $	&  $  +0.40  $  \\ \hline
-       &          &       & HIP47139 &              &             &            \\ \hline
-
-C (CH) &   6.61     &  0.21   &   2    &    $ -1.82 $  &  $ -0.24 $  &                \\
-O\,I   &   8.14     &  ...        &   1    &    $ -0.55 $  &  $+ 1.03 $  &                \\
-Na\,I  &   4.65     &  0.05   &   4    &    $ -1.59 $  &  $ -0.01 $  &  $ -0.18   $   \\       
-Mg\,I  &   6.42     &  0.08   &   4    &    $ -1.18 $  &  $ +0.40 $  &  $ +0.54   $   \\       
-Ca\,I  &   5.05     &  0.05   &   16   &    $ -1.29 $  &  $ +0.29 $  &  $ +0.27   $   \\       
-Sc\,II &   1.64     &  0.05   &   12   &    $ -1.51 $  &  $ +0.07 $  &  $         $   \\       
-Ti\,I  &   3.52     &  0.05   &   26   &    $ -1.43 $  &  $ +0.15 $  &  $ +0.29   $   \\       
-Ti\,II &   3.67     &  0.05   &   18   &    $ -1.28 $  &  $ +0.30 $  &  $         $   \\       
-Cr\,I  &   3.94     &  0.07   &   16   &    $ -1.70 $  &  $ -0.12 $  &  $ -0.17   $   \\       
-Mn\,I  &   3.58     &  0.07   &   3    &    $ -1.85 $  &  $ -0.27 $  &  $         $   \\       
-Fe\,I  &   5.91     &  0.05   &   109  &    $ -1.59 $  &  $ ...   $  &  $ (-1.46) $   \\       
-Fe\,II &   5.94     &  0.05   &   11   &    $ -1.56 $  &  $ ...   $  &  $         $   \\       
-Ni\,I  &   4.65     &  0.05   &   18   &    $ -1.57 $  &  $ +0.01 $  &  $ +0.00   $   \\  
-Zn\,I  &   2.97     &  0.11   &   2    &    $ -1.59 $  &  $ -0.01 $  &  $         $   \\     
-Ba\,II &   0.92     &  0.10   &   3    &    $ -1.26 $  &  $ +0.32 $  &  $ +0.16   $   \\
-La\,II &   $-0.48$  &  0.30   &   1    &    $ -1.58 $  &  $ +0.00 $  &                \\
-Eu\,II & $ -0.4 9$  &  0.40   &   1    &    $ -1.01 $  &  $ +0.57 $  &                \\  \hline
-
-  \end{tabular}}
- \end{center}
-\end{table}
+\begin{deluxetable}{lcccccccc}
+\tabletypesize{\scriptsize}
+\tablecaption{Derived Stellar Parameters \label{tab:comp_para}}
+\tablehead{
+	\colhead{Element} &
+	\colhead{Random} &
+	\colhead{$\Delta{}T_{eff}$} &
+	\colhead{$\Delta\log{g}$} &
+	\colhead{$\Delta{}v_t$} &
+	\colhead{Total} \\
+ & Uncert. & $+150 K$ & $+0.4$ dex & $+0.3$ km s$^{-1}$ & Uncert.
+}
+\startdata
+  C (CH)   &  0.21  & \phn\;0.30     & $-0.05$         & $-0.02$           & 0.37        \\
+  Na\,I    &  0.08 	 & \phn\;0.16     & $-0.10$	      &	$-0.04$		  & 0.21	\\
+  Mg\,I    &  0.07 	 & \phn\;0.16     & $-0.11$	      &	$-0.05$           & 0.21	\\
+  Ca\,I    &  0.06 	 & \phn\;0.13	    & $-0.05$	      &	$-0.10$		  & 0.18	\\
+  Sc\,II   &  0.05 	 & \phn\;0.02	    & $+0.16$	      &	$-0.02$		  & 0.17	\\
+  Ti\,I    &  0.07 	 & \phn\;0.20	    & $-0.02$	      &	$-0.09$		  & 0.23	\\
+  Ti\,II   &  0.06 	 & \phn\;0.03	    & $+0.15$	      &	$-0.09$		  & 0.19	\\
+  Cr\,I    &  0.05 	 & \phn\;0.19	    & $-0.01$	      &	$-0.08$		  & 0.21	\\
+  Mn\,I    &  0.07 	 & \phn\;0.15	    & $-0.03$	      &	$-0.10$		  & 0.20	\\ 
+  Fe\,I    &  0.05 	 & \phn\;0.18	    & $-0.04$	  &	$-0.13$		  & 0.23	\\
+  Fe\,II   &  0.05 	 & $-$0.02     & $+0.16$	  &	$-0.09$		  & 0.19	\\
+  Co\,I    &  0.12 	 & \phn\;0.25	    & $+0.00$	  &	$-0.20$		  & 0.34	\\ 
+  Ni\,I    &  0.06 	 & \phn\;0.14	    & $+0.00$	  &	$-0.06$		  & 0.16	\\
+  Zn\,I    &  0.25 	 & \phn\;0.04	    & $+0.10$	  &	$-0.05$		  & 0.28	\\
+  Sr\,II   &  0.40 	 & \phn\;0.10	    & $+0.02$	  &	$-0.10$		  & 0.42	\\ 
+  Ba\,II   &  0.21 	 & \phn\;0.09	    & $+0.08$	  &	$-0.18$		  & 0.30	\\
+  La\,II   &  0.30  & \phn\;0.05    & $+0.15$     & $-0.05$       & 0.34        \\
+  Eu\,II   &  0.40 	 & \phn\;0.05	  & $+0.15$	      &	$-0.05$		  & 0.43
+\enddata
+\end{deluxetable}
 
@@
 \label{sec:char}
+
+\subsection{Stream Membership}
+As demonstrated by other authors, there is unequivocally a coherent stream present here with a kinematic peak $v_{helio} = 300$ km s$^{-1}$ \citep{Geha2009, Norris2010, Simon2011}.
+At more extreme velocities, halo contaminants become less likely.
+Given that a stream is present here with high velocities, it is worth quantifying the likelihood whether the star analysed here is a contaminant or not.
+As a comparison we have queried a the Besan\c{c}on model \citep{Robin2003} with a $1^\circ$ cone for representative halo metallicities and kinematics in this region.
+A two-sample Kolmogorov–Smirnov test with kinematics yields a $p = 0.097$, or an $\sim10$\% chance that the star analysed here is a halo contaminant.
+When coupled with metallicity, it is clear that this star sits separate from the main halo population (Figure \ref{fig:besancon}).
+We note that the same probability cutoff was employed by \citet{Simon2011} in order to examine stream members.
+
+\begin{figure*}
+  \includegraphics[width=\columnwidth]{besancon.eps}
+  \caption{Kinematics and metallicities for representative halo stars from the Besan\c{c}on model \citep{Robin2003}. The star analysed here, Segue1-11, is marked as a filled star.}
+  \label{fig:besancon}
+\end{figure*}
 
@@
 \subsection{Metallicity of Stream}
-We determine a metallicity of [Fe/H] $= -1.44 $ for Segue1-11 based on the high-resolution spectrum.
-This is consistent with what we estimate from fitting globular cluster sequences to the photometry.
+We determine a metallicity of [Fe/H] $= -1.44 \pm XX $ for Segue1-11 based on the high-resolution spectrum.
+This is consistent with what we estimate from fitting globular cluster sequences to the photometry, and generally in agreement with the prediction of [Fe/H] $= -1.3$ from \citet{Simon2011}.
 It adds support to the result that the stream stars have higher metallicity than Segue\,1 system, as noted in S11 based on Ca triplet equivalents widths.
@@
 Given their uncertainty, however, a distance within $\pm 7$ kpc of this estimate would still be consistent with the stellar parameters derived from spectroscopy.
+Furthermore, our distance estimate of 18 kpc is in good agreement with \citet{Simon2011} who find a distance of 22 kpc to the stream.
 
@@
 Indeed at least two wraps of Sagittarius overlap with Segue 1 in this direction, and \citet{Niederste-Ostholt2009} argues that Segue 1 itself is a star cluster from the Sagittarius galaxy.
-But as for the stream stars, our metallicity measurement indicates that the 300~km~s$^{-1}$ stream is more metal-poor than Sgr debris \citep{Chou2007}.
-In addition, no model of Sagittarius that we are aware of predicts a wrap at this velocity, however; the part of the Sagittarius stream proposed to be contaminating Segue 1 samples has $v_{GSR} \sim 130$~km~s$^{-1}$ \citep{Niederste-Ostholt2009}, while the stream stars have $v_{GSR} \sim 230$~km~s$^{-1}$.
+But as for the stream stars, our metallicity measurement indicates that the 300~km~s$^{-1}$ stream does not have metallicities representative of Sgr debris, \citep{Chou2007, Casey2012}, and no Sgr debris model that we are aware of predicts a wrap at this velocity.
+Moreover, the part of the Sagittarius stream proposed to be contaminating Segue 1 samples has $v_{GSR} \sim 130$~km~s$^{-1}$ \citep{Niederste-Ostholt2009}, while the stream stars have $v_{GSR} \sim 230$~km~s$^{-1}$.
 
@@
 We have presented a high-resolution spectrum and abundance analysis of Segue1-11, a bright star in the 300~km~s$^{-1}$ stream near the ultra-faint dwarf galaxy Segue1.
-We determine a metallicity [Fe/H] $= -1.44$ for this star, with abundance ratios similar to typical halo stars at this metallicity.
+We determine a metallicity [Fe/H] $= -1.44 \pm XX$ for this star, with abundance ratios similar to typical halo stars at this metallicity.
 Fitting the stellar parameter solution onto theoretical isochrones, we estimate a distance of $18 \pm 7$ kpc.
 Both the metallicity and distance are in good agreement with estimates obtained from comparing the SDSS photometry to globular cluster sequences.
+
+The fact that this stream may be largely chemically indifferent from the halo is particularly interesting.
+This is relevant to chemical tagging \citep{Freeman;Bland-Hawthorn2003}, which infers that stars originating from a common origin can be unambiguously identified solely by their chemistry and without the need for kinematics.
+This stream is most noticable only with its kinematics, and not by any particular chemical signature identified in this work.
+Although the luminosity, number of abundances analysed or abundance uncertainties presented here do not match the strict requirements for the complete chemical tagging planned in future galactic archaeology surveys \citep{Ting2012}, we identify this 300 km s$^{-1}$ stream as a candidate for testing and validating the chemical tagging concept.
+It would be particularly interesting to determine whether chemical tagging alone could identify members belonging to this 300 km s$^{-1}$ stream without the need for kinematics, as the chemical elements analysed here are only marginally distinguishable from the halo.
 
@@
 acknowledges support of a Clay Fellowship administered by the Smithsonian Astrophysical Observatory.
+A.R.C.
+acknowledges the financial support through the Australian Research Council Laureate Fellowship 0992131, and from the Australian Prime Minister's Endeavour Award Research Fellowship, which has facilitated his research at MIT.
 J.E.N.
@@
   Engineers (SPIE) Conference Series, ed. {M.~Iye \& A.~F.~M.~Moorwood}, 1694
+
+\bibitem[{{Casey} {et~al.}(2012){Casey}, {Keller}, {Da Costa}}]{Casey2012}
+{Casey}, A. R., {et~al.} 2012, \aj, 143, 88
 
@@
 
+\bibitem[{Robin} {et~al.}(2003){Robin}, {Reyl{\'e}}, {Derri{\`e}re}, \& {Picaud}]{Robin2003}
+{Robin}, A.~C., 2003, \aap, 409, 523
+
 \bibitem[{{Roederer} {et~al.}(2010){Roederer}, {Sneden}, {Thompson}, {Preston},
@@
 
+\bibitem[{{Ting} {et~al.}(2012){Ting}, {Freeman}, {Kobayashi}, {de Silva}, \& {Bland-Hawthorn}}]{Ting2012}
+{Ting}, Y.~S., {Freeman}, K.~C., {Kobayashi}, C., {de Silva}, G.~M., \& {Bland-Hawthorn}, J.
+ 2012, \mnras, 421, 1231
+
 \bibitem[{{Tolstoy} {et~al.}(2009){Tolstoy}, {Hill}, \& {Tosi}}]{Tolstoy2009}

### 2012-08-16 2012-segue-1/andy/norm.py

@@ -1,0 +1,24 @@
+import os
+from pyraf import iraf
+
+iraf.noao()
+iraf.noao.onedspec()
+iraf.obsutil()
+iraf.imred()
+iraf.ccdr()
+iraf.ech()
+
+def normalise_mike_spectra(filename):
+    
+    os.system('rm -f red.fits red_multic.fits red_multicim.fits red_multicom.fits red_multicimcom.fits endred.fits a.fits b.fits c.fits d.fits e.fits f.fits *.par')
+    iraf.noao.onedspec.scopy(input=filename, output="red.fits", aperture="", bands=2, beams="1", format="multispec")
+    iraf.noao.onedspec.cont(input="red.fits", output="red_multic.fits", order=6, overrid="yes", markrej="no")
+    iraf.images.imutil.imarith(operand1="red.fits", op="/", operand2="red_multic.fits", result="red_multicim.fits")
+    iraf.noao.onedspec.scombine("red.fits", "red_multicom.fits", combine="sum", group="images")
+    iraf.noao.onedspec.scombine("red_multicim.fits", "red_multicimcom.fits", combine="sum", group="images")
+    iraf.images.imutil.imarith(operand1="red_multicom.fits", op="/", operand2="red_multicimcom.fits", result="endred.fits")
+    os.system("cp endred.fits %s_norm.fits" % (filename.replace('.fits', ''), ))
+    iraf.noao.onedspec.wspectext(input="%s_norm.fits" % (filename.replace('.fits', ''), ), output="%s_norm.txt" % (filename.replace('.fits', ''), ), header="no")
+    os.system('rm -f red.fits red_multic.fits red_multicim.fits red_multicom.fits red_multicimcom.fits endred.fits a.fits b.fits c.fits d.fits e.fits f.fits')
+    
+    return True

### 2012-08-16 2012-segue-1/andy/profiles.py

@@ -1,0 +1,1 @@
+/Users/andycasey/thesis/observing/magellan-mike/analysis/mew/profiles.py

### 2012-08-16 2012-segue-1/ks2.c

@@ -1,0 +1,115 @@
+/*
+
+Muac - A fast algorithm for the 2d KS test (v1.1, 13 June 1999).
+
+Copyright (C) 1998 Andrew Cooke  (Jara Software)
+
+Comments to jara@andrewcooke.free-online.co.uk
+
+This program is free software; you can redistribute it and/or modify
+it under the terms of the GNU General Public License as published by
+the Free Software Foundation; either version 2 of the License, or (at
+your option) any later version.
+
+This program is distributed in the hope that it will be useful, but
+WITHOUT ANY WARRANTY; without even the implied warranty of
+MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the GNU
+General Public License for more details.
+
+You should have received a copy of the GNU General Public License
+along with this program; if not, write to the Free Software
+Foundation, Inc., 59 Temple Place, Suite 330, Boston, MA 02111-1307
+USA
+
+These conditions also apply to any other files distributed with this
+program.
+
+*/
+
+#include "stdlib.h"
+#include "stdio.h"
+
+/* --- global structs and routines -------------------- */
+
+#include "muac.h"
+
+
+/* --- local structs and routines --------------------- */
+
+void readFile( float **x, float **y, int *n, char *name ) ;
+
+
+/* --- test muac routine ------------------------------ */
+
+void main( int argc, char **argv ) {
+
+  float *x1 ; /* pointer to data for first set */
+  float *y1 ;
+  float *x2 ; /* pointer to data for second set */
+  float *y2 ;
+  int n1 ;    /* number of points in each set */
+  int n2 ; 
+  
+  if ( argc != 3 ) {
+    fprintf( stderr, "\nUsage: ks2 file1 file2\n" ) ;
+    fprintf( stderr, "Diagnostic messages to stderr; result to stdout.\n" ) ;
+    fprintf( stderr, "Result is maximum fractional difference, NOT a transformed statistic.\n" ) ;
+    fprintf( stderr, "2D KS test using fast muac algorithm (v1.1) (c) Andrew Cooke 1999\n" ) ;
[…]

### 2012-08-16 2012-segue-1/muac.c

@@ -1,0 +1,408 @@
+/*
+
+Muac - A fast algorithm for the 2d KS test (v1.1, 13 June 1999).
+
+Copyright (C) 1998 Andrew Cooke  (Jara Software)
+
+Comments to jara@andrewcooke.free-online.co.uk
+
+This program is free software; you can redistribute it and/or modify
+it under the terms of the GNU General Public License as published by
+the Free Software Foundation; either version 2 of the License, or (at
+your option) any later version.
+
+This program is distributed in the hope that it will be useful, but
+WITHOUT ANY WARRANTY; without even the implied warranty of
+MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the GNU
+General Public License for more details.
+
+You should have received a copy of the GNU General Public License
+along with this program; if not, write to the Free Software
+Foundation, Inc., 59 Temple Place, Suite 330, Boston, MA 02111-1307
+USA
+
+These conditions also apply to any other files distributed with this
+program.
+
+*/
+
+/* --- the main routines for a fast 2d ks test -------- */
+
+#include "stdlib.h"
+#include "stdio.h"
+
+/* --- global structs and routines -------------------- */
+
+#include "muac.h"
+#undef DEBUG
+
+/* --- local structs and routines --------------------- */
+
+typedef struct node {
+  struct node *parent ;
+  struct node *left ;
+  struct node *right ;
+  MuacRecord *data ;
+  float score ;
+  float min ;
+  float max ;
+  float delta ;
+} Node ;
+
+float sweep( MuacRecord *in, int nPoints, int reverse, float *score ) ;
+void reCalc( Node *node ) ;
+Node *addNode( MuacRecord *data, Node *root, Node *treeData, int *treeIndex,
+               float *score ) ;
+Node *newNode( Node *parent, Node **side, MuacRecord *data, Node *treeData, 
+               int *treeIndex, float *score ) ;
+Node *allocTree( int nPoints, int *treeIndex ) ;
+Node *allocNode( Node *treeData, int *treeIndex ) ;
+void freeTree( Node *treeData, int *treeIndex ) ;
+void quickSort( MuacRecord *in, int nPoints ) ;
+void ranSort( MuacRecord *in, int start, int end ) ;
[…]

### 2012-08-16 2012-segue-1/muac.h

@@ -1,0 +1,44 @@
+/*
+
+Muac - A fast algorithm for the 2d KS test (v1.1, 13 June 1999).
+
+Copyright (C) 1998 Andrew Cooke  (Jara Software)
+
+Comments to jara@andrewcooke.free-online.co.uk
+
+This program is free software; you can redistribute it and/or modify
+it under the terms of the GNU General Public License as published by
+the Free Software Foundation; either version 2 of the License, or (at
+your option) any later version.
+
+This program is distributed in the hope that it will be useful, but
+WITHOUT ANY WARRANTY; without even the implied warranty of
+MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the GNU
+General Public License for more details.
+
+You should have received a copy of the GNU General Public License
+along with this program; if not, write to the Free Software
+Foundation, Inc., 59 Temple Place, Suite 330, Boston, MA 02111-1307
+USA
+
+These conditions also apply to any other files distributed with this
+program.
+
+*/
+
+
+typedef struct {
+  float x ;
+  float y ;
+  char type ;
+} MuacRecord ;
+
+/* this routine expects an array of data which has already been sorted
+   by y */
+float muac( MuacRecord* in, int n1, int n2 ) ;
+
+/* this routine expects unsorted data - the sorting is randomized, so
+   using with sorted data will not cause problems */
+float unsortedMuac( float* x1, float* y1, int n1, 
+                    float* x2, float* y2, int n2 ) ;
+

### 2012-08-16 2012-segue-1/plot-besancon.py

@@ -1,0 +1,113 @@
+
+# definitions for the axes
+left, width = 0.1, 0.65
+bottom, height = 0.1, 0.65
+bottom_h = left_h = left+width+0.02
+rect_scatter = [left, bottom, width, height]
+rect_histx = [left, bottom_h, width, 0.2]
+rect_histy = [left_h, bottom, 0.2, height]
+# start with a rectangular Figure
+plt.figure(1, figsize=(8,8))
+axScatter = plt.axes(rect_scatter)
+axHistx = plt.axes(rect_histx)
+axHisty = plt.axes(rect_histy)
+halo_v, halo_feh = np.loadtxt('1344124484.054352.resu', usecols=(15, 19))
+halo_v = np.loadtxt('1344124484.054352.resu', usecols=(15, 19))
+halo
+halo_v
+halo_feh = halo_v[:,1]
+halo_v = halo_v[:, 0]
+halo_v
+axScatter.scatter(halo_v, halo_feh, facecolor='k')
+xHist = axHistx.hist(halo_v)
+yHist = axHisty.hist(halo_feh, orientation='horizontal')
+plt.draw()
+axScatter.set_xlim(-400, 400)
+axScatter.set_xlim(-350, 350)
+axHistx.set_xlim(-350, 350)
+xHist.set_facecolor('k')
+xHist
+axHistx.hist(x, facecolor='#666666')
+axHistx.hist(halo_v, facecolor='#666666')
+axHisty.hist(halo_feh, facecolor='#666666')
+plt.draw()
+axHistx.clear()
+axHisty.clear()
+axHistx.hist(halo_v, facecolor='none')
+axHisty.hist(halo_feh, facecolor='none', orientation='horizontal')
+plt.draw()
+axHistx.set_xlabel('')
+axHisty.set_ylabel('')
+axHistx.get_xticks()
+axHistx.set_xticklabels(['']*7)
+axHisty.get_yticks()
+axHisty.set_yticklabels(['']*9)
+plt.draw()
+axScatter.set_xlabel('$V_{helio}$ (km/s)')
+axScatter.set_ylabel('[Fe/H]')
+plt.draw()
+star = axScatter.scatter([307], [-1.44], facecolor='k', marker='*', size=50)
+star = axScatter.scatter([307], [-1.44], facecolor='k', marker='*', s=50)
+plt.draw()
+star.set_visible(False)
[…]

### 2012-09-03 2012-oss-mrs/draft-oss-mrs.tex
Made most corrections to GDC comments and suggestions

@@
 \begin{abstract}
-We present coordinates and properties of K giant members in the Orphan Stream, which have been identified from low resolution spectroscopic data taken with AAOmega on the Australian Astronomical Telescope.
+We present coordinates and properties of candidate K giant members in the Orphan Stream, which have been identified from low resolution spectroscopic data taken with AAOmega on the Australian Astronomical Telescope.
 With modest S/N and independent cuts in photometry, kinematics, gravity and metallicity we yield self-consistent, highly probable stream members.
@@
 We find a revised stream distance of 24 kpc near the celestial equator, and our kinematic signature peaks at $V_{helio} \sim 218$\,km s$^{-1}$.
-We highlight members for high resolution spectroscopic follow-up.
+We highlight likely members for high resolution spectroscopic follow-up.
 \end{abstract}
@@
 
-The Milky Way stellar halo has been partly formed through the accretion of smaller satellites.
-As smaller satellites infall onto the Milky Way, tidal forces disrupt the satellite.
+The Milky Way stellar halo has partly formed through the accretion of satellites which are disrupted by tidal forces as they fall into the Milky Way's potential.
 Stars which were once gravitationally bound to the satellite are left behind in a stream of stars.
-Stream members have kinematics which are sensitive to the shape of the galactic potential, allowing us to constrain the Milky Way potential, and reconstruct the formation history of the Milky Way.
+Stream kinematics are sensitive to the shape of the galactic potential, allowing us to constrain the Milky Way potential, and reconstruct the formation history of the Milky Way.
 The level of accreted substructure in the Milky Way has only recently become apparent through multi-band photometric surveys like the Sloan Digital Sky Survey (SDSS).
@@
 
-The Orphan Stream was independently detected by both \citet{Grillmair;Dionatos_2006} and \citet{Belokurov;et-al_2006}, and is unique from other substructures in the halo.
-The stream stretches over $60\,^\circ$ in the sky, has a low surface brightness and a narrow stream width of only $\sim2^\circ$ and as the name suggests, the parent largely remains a mystery.
-The stream extends past the celestial equator \-- outside the SDSS footprint \-- and is not detectable through bright southern surveys like SuperCOSMOS [citation needed].
+The Orphan Stream was independently detected by both \citet{Grillmair;Dionatos_2006} and \citet{Belokurov;et-al_2006}, and is distinct from other substructures in the halo.
+The stream stretches over $60\,^\circ$ in the sky, has a low surface brightness and a narrow stream width of only $\sim2^\circ$ and as the name suggests, the parent object largely remains a mystery.
+The stream extends past the celestial equator \-- outside the SDSS footprint \-- but is not detected in existing southern surveys \citep{Newberg;et-al_2010}.
 Whilst the parent system remains elusive, significant effort has been placed on associating the stream with known Milky Way satellites \citep{Zucker;et-al_2006, Fellhaur;et-al_2007,Jin;Lynden_Bell_2007,Sales;et-al_2008}.
-In contrast, there has been relatively limited observational work on the Orphan Stream other than the original discovery papers \citep{Grillmair;Dionatos_2006, Belokurov;et-al_2006, Belokurov;et-al_2007} and the work of \citet{Newberg;et-al_2010}.
+In contrast, there has been relatively limited observational work on the Orphan Stream itself other than the original discovery papers \citep{Grillmair;Dionatos_2006, Belokurov;et-al_2006, Belokurov;et-al_2007} and the work of \citet{Newberg;et-al_2010}.
 This is largely to be expected given the absence of multi-band photometry in the southern sky, the difficulty in reliably separating Orphan Stream members from halo stars and the low luminosity of stream members.
@@
 In this letter we present a detailed, self-consistent analysis to identify K giant members of the Orphan Stream.
-Using our selection method we have published the locations of seven highly probable Orphan Stream candidates, all worthy of high resolution spectroscopic follow up.
-In the following section of this letter we outline our initial photometric target selection.
-In section \S\ref{sec:target-selection} we outline our target selection and section \S\ref{sec:observations} describes the low resolution observations.
-The data analysis, including stream identification, is described in \S\ref{sec:analysis}.
-In \S\ref{sec:conclusions} we discuss our conclusions, predictions, and necessary future work necessary on this topic.
+Using our selection method we have catalogued the locations of seven highly probable Orphan Stream candidates, all worthy of high resolution spectroscopic follow up.
+In the following section we outline our photometric target selection.
+In Section \S\ref{sec:observations} we describe the low resolution spectroscopic observations.
+The data analysis, including stream identification, is discussed in \S\ref{sec:analysis} and in \S\ref{conclusions} the conclusions, predictions and future work are presented.
 
@@
 Because K-giants are difficult to unambiguously detect from photometry alone, low resolution spectroscopy is required to estimate stellar parameters and determine radial velocities.
-The Orphan Stream has a low spatial over-density on the order of $\sim10\%$ [citation needed], which also makes it difficult to separate stream members from halo stars.
+The Orphan Stream has a low spatial over-density on the order of $\sim10\%$ [citation needed], which makes it difficult to separate stream members from halo stars.
 However, there is a well described distance gradient along the stream \citep{Belokurov;et-al_2007, Newberg;et-al_2010} which provides an indication on where we should focus our spectroscopic efforts.
@@
 Given our colour selection we expect to recover giants and dwarf contaminants.
-At a given temperature, K dwarfs exhibit a infrared excess relative to giants which allows a clean selection of giants \citep{Bessell;Brett_1988}.
-However, given the apparent magnitude of the Orphan Stream in this region ($g \sim 18$), no 2MASS infrared photometry is available.
-Thus we expect our sample to be contaminated by foreground dwarfs to some extent.
+The lack of 2MASS photometry for the selected stars means we cannot use the $(J-H, H-K)$ diagram to aid the separation of candidate giants from contaminating dwarfs.
 
@@
 We used the 5700\,{\AA} dichroic in combination with the 1000I grating in the red arm, and the 580V grating in the blue arm.
-This provides a spectral coverage between $800 \leq \lambda \leq 950$\,nm in the red at $\mathcal{R} \approx 4400$, and between $370 \leq \lambda \leq 580$\,nm with a lower resolving power of $\mathcal{R} \approx 1300$.
+This provides a spectral coverage between $800 \leq \lambda \leq 950$\,nm in the red at $\mathcal{R} \approx 4400$, and between $370 \leq \lambda \leq 580$\,nm with a lower resolving power of $\mathcal{R} \approx 1300$ in the blue.
 
-The data were reduced using the supplied \textsc{2DFDR} reduction pipeline \footnote{http://www.aao.gov.au/2df/aaomega/aaomega\_2dfdr.html}.
+The data were reduced using the standard \textsc{2DFDR} reduction pipeline \footnote{http://www.aao.gov.au/2df/aaomega/aaomega\_2dfdr.html}.
 After flat-fielding, throughput calibration for each fibre was achieved using the intensity of skylines in each fibre.
@@
 With the presence of strong Ca \textsc{II} triplet lines in the red arm we are able to ascertain reliable radial velocities and reasonable estimates on overall metallicity \citep[][and references therein]{Starkenburg;et-al_2010}.
-Our spectral region also includes gravity-sensitive magnesium lines: Mg I at 8807\,{\AA}, and the Mg Ib 3$p$-4$s$ triplet lines.
+Our spectral region also includes gravity-sensitive magnesium lines: Mg I at 8807\,{\AA}, and the Mg I\,b 3$p$-4$s$ triplet lines at $\sim$5178\,{\AA}.
 As we demonstrate in the next section, these lines are sufficient to discriminate dwarfs and giants even with weak signal.
@@
 In this region \citet{Newberg;et-al_2010} found the Orphan Stream to have $V_{\textsc{gsr}} = 110$ km s$^{-1}$ from BHB stars, approximately $105$\,km s$^{-1}$ on our scale.
-We have nominated a relatively wide kinematic selection region between $75 \leq V_{\textsc{gsr}} \leq 135$ km s$^{-1}$, which yields 25 Orphan Stream candidates.
+To isolate potential Orphan Stream members we have nominated a relatively wide kinematic selection region between $75 \leq V_{\textsc{gsr}} \leq 135$ km s$^{-1}$, which yields 25 Orphan Stream candidates.
 The typical uncertainty in our kinematics is $\pm{}3.5$\,km s$^{-1}$, although for our fainter targets this quickly increases to $\sim10$ km s$^{-1}$.
@@
 
-We have measured the equivalent widths of the gravity-sensitive Mg I line at 8807 \AA{} to distinguish dwarfs from giants.
+We have measured the equivalent widths of the gravity-sensitive Mg I line at 8807 \AA{} to distinguish dwarfs from giants \citep{Battaglia;Starkenburg_2012}.
 At a given temperature (or $g \-- r$) and metallicity, giant stars present narrow Mg I absorption lines than their dwarf contaminants.
@@
 The adopted dwarf/giant separation line is shown.
-Admittedly this selection criterion appears extremely inclusive of dwarfs, but we are allowing multiple inclusive cuts and taking the union of these selections to identify Orphan Stream giants.
+Admittedly this selection criterion is not particularly strict, but we are allowing multiple inclusive cuts and taking the intersection of these criteria to identify Orphan Stream giants.
 
@@
 
-It is worth noting that we initially performed this analysis using the total equivalent width of the Mg\,\textsc{I}b triplet near 5175\,{\AA}.
-As expected, this region has a consistently lower S/N than the Mg\,\textsc{I} line at 8807\,{\AA}.
-However, the separation between giants and dwarfs was arguably more distinguished when using the Mg I b triplet equivalent width instead of using the $\lambda{}8807$ line.
-In either case, both analyses were entirely consistent with each other: the same candidate selection was found using both techniques.
-However, given the poorer signal at the Mg\,\textsc{I}b triplet, we were forced to adopt many more upper limits than when using the 8807{\AA} line.
+This analysis was also performed using the total equivalent width of the Mg\,\textsc{I}\,b triplet lines.
+Both analyses were entirely consistent with each other: essentially the same candidate selection was found using both techniques.
+However, given slightly poorer signal at the Mg\,\textsc{I}\,b triplet, we were forced to adopt many more upper limits than when using the 8807{\AA} line.
 Because we classify all upper limits as being ``non-dwarfs" (i.e.
-potential OSS giants), we deduced a slightly larger candidate sample for the Mg\,\textsc{I}b analysis, which was primarily populated by upper limits.
+potential OSS giants), we deduced a slightly larger candidate sample for the Mg\,\textsc{I}\,b analysis, which was primarily populated by upper limits.
 In conclusion, we found the Mg\,\textsc{I} line at 8807 appeared to be a more consistent dwarf discriminant given our weak S/N \--- particularly for our fainter stars \--- and thus we have used the 8807{\AA} Mg \textsc{I} selection throughout the rest of our analysis.
@@
 Hence, our gravity criterion is extremely inclusive and susceptible to dwarf contamination.
-Upon taking the union of our kinematic and gravity selections, we deduce eighteen stars that appear likely Orphan Stream K giants.
+Upon taking the intersection of our kinematic and gravity selections, we deduce eighteen stars that appear likely Orphan Stream K giants.
 
@@
 We have employed the \citet{Starkenburg;et-al_2010} relationship and corrected for luminosity in $g$ against the horizontal branch magnitude at $g_0$ = 17.1 \citep{Newberg;et-al_2010}.
-Strictly speaking, the Ca\,\textsc{II}-[Fe/H] relationship is only valid for stars brighter than the horizontal branch, although the situation only becomes dire at $g \-- g_{HB} \sim +1$ [citation needed].
+Strictly speaking, the Ca\,\textsc{II}-[Fe/H] calibation is only valid for stars brighter than the horizontal branch, although the relationship only becomes significantly inappropriate near $g \-- g_{HB} \sim +1$ \citep{Savine;et-al_2012}.
 Many of our candidates are fainter than this valid luminosity range, and therefore they should not be excluded solely because of their derived metallicities.
@@
 There are four candidates above $g_0 \sim 17.1$ which are within our valid luminosity range.
-Two of these objects at $g \-- r \sim 0.57$ are slightly metal-rich than expected for the stream, and are excluded from membership.
+One of these objects at $(g \-- r, g) \sim (0.57, 17)$ is +0.64\,dex more metal-rich than expected for the stream, and is excluded from membership.
+Another is only +0.21\,dex more metal-rich and sits at (0.57, 16.1), but it's position relative to the isochrone is inconsistent with our inferred metallicity.
 There appears to be an extremely metal-poor star in this sample with an estimated $[\mbox{Fe/H}] = -2.70$ which may be associated with the Orphan Stream.
-The likely parent system of the Orphan Stream is a Milky Way dwarf spheroidal \citep{Belokurov;et-al_2007, Sales;et-al_2008}, which are known to have a wide metallicity distribution function [citation needed?], including an over-represented population of extremely metal poor stars \citep{Frebel;et-al_2010, Kirby;et-al_2010}.
+The likely parent system of the Orphan Stream is a Milky Way dwarf spheroidal \citep{Belokurov;et-al_2007, Sales;et-al_2008}, which are known to have a wide metallicity distribution function \citep{Tafelmayer;et-al_2010, Tolstoy;et-al_2009}, including an over-represented population of extremely metal poor stars \citep{Frebel;et-al_2010, Kirby;et-al_2010}.
 Thus, we keep this extremely metal-poor star as a potential stream member for follow-up chemical analysis.
@@
 This is slightly more metal-rich than the $[\mbox{Fe/H}] =-2.1$ found by \citet{Newberg;et-al_2010} from BHB stars.
-This is to be expected as BHB stars are intrinsically representative of an older, more metal-poor population.
 
@@
 The K giants presented here can provide great insight into the chemistry, and history of the Orphan Stream.
-High resolution spectroscopic observations have been taken for our most highly probable members and a detailed chemical analysis will be presented in an accompanying paper (Casey et al.
+High resolution spectroscopic observations have been taken for our most highly probable members and a detailed chemical analysis will be presented in a forthcoming paper (Casey et al.
 2012c, in preparation).
@@
 
-\section{Acknowledgements}
+\acknowledgements
 ARC acknowledges the financial support through the Australian Research Council Laureate Fellowship 0992131, and from the Australian Prime Minister's Endeavour Award Research Fellowship, which has facilitated his research at MIT.
-SK and GDaC acknowledge the financial support from the Australian Research Council through Discovery Program DP0878137.
+SK and GDaC acknowledge the financial support from the Australian Research Council through Discovery Programs DP0878137 and DP120101237.
 

### 2012-09-04 2012-oss-mrs/draft-oss-mrs.tex
Incorporated comments and suggestions by GDC

@@
 
-\author{Andrew R. Casey\altaffilmark{1,2}, Stefan C. Keller\altaffilmark{1}, Gary Da Costa\altaffilmark{1}, Elizabeth Maunder\altaffilmark{1}}
+\author{Andrew R. Casey\altaffilmark{1,2}, Stefan C. Keller\altaffilmark{1}, Gary Da Costa\altaffilmark{1}, Elizabeth Maunder\altaffilmark{1}, Anna Frebel\altaffilmark{2}}
 \altaffiltext{1}{Research School of Astronomy \& Astrophysics, Australian National University, Mount Stromlo Observatory, via Cotter Rd, Weston, ACT 2611, Australia; \email{arcasey@mso.anu.edu.au}}
@@
 With modest S/N and independent cuts in photometry, kinematics, gravity and metallicity we yield self-consistent, highly probable stream members.
-Our data indicates an overall stream metallicity of [Fe/H] $= -1.74 \pm 0.05$ which is more metal-rich than previously found and unbiased by spectral type.
+Our data indicates an overall stream metallicity of [Fe/H] $= -1.78 \pm 0.08$ which is more metal-rich than previously found and unbiased by spectral type.
 We find a revised stream distance of 24 kpc near the celestial equator, and our kinematic signature peaks at $V_{helio} \sim 218$\,km s$^{-1}$.
+The Orphan Stream appears extremely cold, with an intrinsic dispersion of less than $0.3 \pm 3.3$ km s$^{-1}$.
 We highlight likely members for high resolution spectroscopic follow-up.
@@
 In contrast, there has been relatively limited observational work on the Orphan Stream itself other than the original discovery papers \citep{Grillmair;Dionatos_2006, Belokurov;et-al_2006, Belokurov;et-al_2007} and the work of \citet{Newberg;et-al_2010}.
-This is largely to be expected given the absence of multi-band photometry in the southern sky, the difficulty in reliably separating Orphan Stream members from halo stars and the low luminosity of stream members.
+This is largely to be expected given the absence of multi-band photometry in the southern sky and the total low luminosity of the stream, making it difficult in reliably identifying Orphan Stream members from halo stars.
 It is unlikely the full extent of the Orphan Stream will be detected until the SkyMapper telescope surveys this region \citep{Keller;et-al_2007}.
@@
 In Section \S\ref{sec:observations} we describe the low resolution spectroscopic observations.
-The data analysis, including stream identification, is discussed in \S\ref{sec:analysis} and in \S\ref{conclusions} the conclusions, predictions and future work are presented.
+The data analysis, including stream identification, is discussed in \S\ref{sec:analysis} and in \S\ref{sec:conclusions} the conclusions, predictions and future work are presented.
 
@@
 These two locations are unequivocally the best place to recover bright stream members.
-We have targeted two fields centered on ($\alpha$, $\delta$) = (10:48:15, 00:00:00) and (10:48:15, -02:30:00), and employed a combination of colour cuts with the SDSS DR 7 \citep{Abazajian;et-al_2009} data set in order to identify likely K giants:
+We have targeted two fields centered on ($\alpha$, $\delta$) = (10 48 15, 00 00 00) and (10 48 15, $-02$ 30 00), and employed a combination of colour cuts with the SDSS DR 7 \citep{Abazajian;et-al_2009} data set in order to identify likely K giants:
 
 \begin{eqnarray}
-(g - i)_0 &>& 0.6 \\
-0.86i_0 + 3.30 >& g_0 &> 0.95i_0 + 1.35 \\
-19.00 >& g &> 15.75
+0.6 <& (g-i)_0 &< 1.7 \\
+-15(g-i)_0 + 27 <& g_0 &< -3.75(g-i)_0 + 22.5 \\
+15  <& i_0  &< 18 
 \end{eqnarray}
-
-\textbf{Stefan can you see if you can find your original selection SQL \-- I deduced these relationships from cross-matching against SDSS and fitting boundary lines.}
 
@@
 	\includegraphics[width=\columnwidth]{./figures/vgsr-histogram.pdf}
-	\caption{Galactocentric rest frame velocities for our observed sampled (grey), and predicted  Besan\c{c}on velocities (white) which have been scaled to match our observed sample size.
+	\caption{Galactocentric rest frame velocities for stars in both our observed fields (grey), and predicted Besan\c{c}on velocities which have been scaled to match our observed sample size.
 The expected kinematic signature from \citet{Newberg;et-al_2010} for the Orphan Stream is highlighted, as is our kinematic selection window (green).}
@@
 We have employed the \citet{Starkenburg;et-al_2010} relationship and corrected for luminosity in $g$ against the horizontal branch magnitude at $g_0$ = 17.1 \citep{Newberg;et-al_2010}.
-Strictly speaking, the Ca\,\textsc{II}-[Fe/H] calibation is only valid for stars brighter than the horizontal branch, although the relationship only becomes significantly inappropriate near $g \-- g_{HB} \sim +1$ \citep{Savine;et-al_2012}.
+Strictly speaking, the Ca\,\textsc{II}\---[Fe/H] calibation is only valid for stars brighter than the horizontal branch, although the relationship only becomes significantly inappropriate near $g \-- g_{HB} \sim +1$ \citep{Saviane;et-al_2012}.
 Many of our candidates are fainter than this valid luminosity range, and therefore they should not be excluded solely because of their derived metallicities.
-Stars fainted than $g_0$ will have slightly lower metallicities than predicted by our Ca\,\textsc{II}-[Fe/H] relationship, and for these stars we will only use metallicities to assign a relative qualitative likelihood for stream membership.
+Stars fainted than $g_0$ will have slightly lower metallicities than predicted by our Ca\,\textsc{II}\---[Fe/H] relationship, and for these stars we will only use metallicities to assign a relative qualitative likelihood for stream membership.
 
@@
 Highly probable stream members are marked.
-Relevant 10 Gyr \citet{Girardi;et-al_2008} isochrones at $[\mbox{Fe/H}] = -1.5$ (dotted), $-2.0$ (dashed) at 21.4\,kpc \citep{Newberg;et-al_2010} are shown, as well as our best-fitting 10 Gyr isochrone of $[\mbox{Fe/H}] = -1.74$ at 24\,kpc (solid).}
+Relevant 10 Gyr \citet{Girardi;et-al_2008} isochrones at $[\mbox{Fe/H}] = -1.5$ (dotted), $-2.0$ (dashed) at 21.4\,kpc \citep{Newberg;et-al_2010} are shown, as well as our best-fitting 10 Gyr isochrone of $[\mbox{Fe/H}] = -1.78$ at 24\,kpc (solid).}
 	\label{fig:cmd}
@@
 There appears to be an extremely metal-poor star in this sample with an estimated $[\mbox{Fe/H}] = -2.70$ which may be associated with the Orphan Stream.
-The likely parent system of the Orphan Stream is a Milky Way dwarf spheroidal \citep{Belokurov;et-al_2007, Sales;et-al_2008}, which are known to have a wide metallicity distribution function \citep{Tafelmayer;et-al_2010, Tolstoy;et-al_2009}, including an over-represented population of extremely metal poor stars \citep{Frebel;et-al_2010, Kirby;et-al_2010}.
+The likely parent system of the Orphan Stream is a Milky Way dwarf spheroidal \citep{Belokurov;et-al_2007, Sales;et-al_2008}, which are known to have a wide metallicity distribution function \citep{Tolstoy;et-al_2009}, including populations of extremely metal-poor stars \citep{Kirby;et-al_2010,Frebel;et-al_2010,Tafelmeyer;et-al_2010}.
 Thus, we keep this extremely metal-poor star as a potential stream member for follow-up chemical analysis.
@@
 Four of our most probable Orphan Stream members fall between these isochrones.
-Assuming the three highly probable members outside our valid luminosity range are over-predicted by $\sim+0.1$ dex [citation needed], when combining our four Orphan Stream members we yield a stream metallicity of $[\mbox{Fe/H}] = -1.74 \pm 0.05$.
-This is slightly more metal-rich than the $[\mbox{Fe/H}] =-2.1$ found by \citet{Newberg;et-al_2010} from BHB stars.
+The brightest of these green points has an abundance which is in good agreement with the isochrone value.
+The line strength abundances for the other three stars (OSS 3, 6 and 7 \--- see Table \ref{tab:oss-members}) are less certain, as these stars are fainter than the horizontal branch.
+
+We can ascertain abundance corrections for our stars fainter than the horizontal branch by comparing our $V-V_{HB}$ and $EW_{\lambda8452} + EW_{\lambda8662}$ with those measured by \citet{Saviane;et-al_2012} for globular clusters.
+Only two clusters had measured Ca \textsc{II} equivalent widths for stars fainter than the horizontal branch: NGC 6397 with $[\mbox{Fe/H}] = -1.99$ and NGC 6254 with $[\mbox{Fe/H}] = -1.57$ \citep[both abundances from][]{Carretta;et-al_2009}.
+OSS 6 and OSS 7 lie at the mid-point between these cluster stars, implying an abundance of $[\mbox{Fe/H}] \sim -1.78$, or a mean correction of $-0.14$ dex for OSS 6 and 7.
+Although OSS 3 is 0.15 magnitudes fainter than the horizontal branch, it has equivalent widths consistent with our inferred metallicity of $[\mbox{Fe/H}] = -1.62$, so no correction was made.
+With corrections included for OSS 6 and 7 we find a median stream metallicity from our four most probable stars of $[\mbox{Fe/H}] = -1.78 \pm 0.08$, which is slightly more metal-rich than the $[\mbox{Fe/H}] =-2.1$ found by \citet{Newberg;et-al_2010} from BHB stars.
+If we include our EMP candidate, the median decreases by 0.01 dex and the spread increases to 0.39\,dex.
 
@@
 \startdata
-OSS 1 & 10 46 50.6 & $-$00 13 17.9 & 17.33 & 0.50  &  215.5  & \phn77.0 & 4.0 & 0.416 & -1.31 & Unlikely member! \\
-OSS 2 & 10 47 17.6 & $+$00 25 07.7 & 16.09 &  0.73 &  215.7  & \phn79.2 & 3.3 & 0.212 & -1.84 & Highly probable member \\
-OSS 3 & 10 47 30.1 & $-$00 01 24.6 & 17.25 &  0.61 &  221.4  & \phn83.6 & 3.4 & 0.123 & -1.62 & Highly probable member \\
-OSS 4 & 10 49 08.3 & $+$00 02 00.2 & 16.27 &  0.62 &  218.5  & \phn81.5 & 4.6 & 0.034 & -2.70 & Possible EMP member \\
-OSS 6 & 10 48 20.9 & $+$00 26 34.4 & 17.88 &  0.55 &  254.9  & 118.8 & 11.7 & 0.469 & -1.65 & Highly probable member \\
-OSS 7 & 10 46 29.3 & $-$00 19 38.5 & 17.77 &  0.56 &  217.3  & \phn78.4 & 5.2 & 0.126 & -1.63 & Highly probable member 
+OSS 1 & 10 46 50.6 & $-$00 13 17.9 & 17.33 & 0.50  &  215.5  & 77.0 & 4.0 & 0.416 & $-1.31$ & Unlikely member! \\
+OSS 2 & 10 47 17.6 & $+$00 25 07.7 & 16.09 &  0.73 &  215.7  & 79.2 & 3.3 & 0.212 & $-1.84$ & Highly probable member \\
+OSS 3 & 10 47 30.1 & $-$00 01 24.6 & 17.25 &  0.61 &  221.4  & 83.6 & 3.4 & 0.123 & $-1.62$ & Highly probable member \\
+OSS 4 & 10 49 08.3 & $+$00 02 00.2 & 16.27 &  0.62 &  218.5  & 81.5 & 4.6 & 0.034 & $-2.70$ & Possible EMP member \\
+OSS 6 & 10 48 20.9 & $+$00 26 34.4 & 17.88 &  0.55 &  254.9  & 118.8 & 11.7 & 0.469 & $-1.79$\tablenotemark{a} & Highly probable member \\
+OSS 7 & 10 46 29.3 & $-$00 19 38.5 & 17.77 &  0.56 &  217.3  & 78.4 & 5.2 & 0.126 & $-1.77$\tablenotemark{a} & Highly probable member 
 \enddata
+\tablenotetext{a}{Abundance correction of $-0.14$\,dex included (see \S\ref{sec:metallicities}).}
 \end{deluxetable*}
@@
 We have presented a detailed analysis to isolate individual Orphan Stream K giants from low resolution spectroscopy using a combination of photometric, kinematic, gravity, and metallicity information.
-Although each individual criterion is likely to induce some level contamination, the resulting union of these selections reveal highly probable, self-consistent, Orphan Stream K giants.
-We deduce a stream metallicity of $[\mbox{Fe/H}] = -1.74 \pm 0.05$ which is not biased by spectral type.
-Recall that the metallicity determination was performed after kinematic and gravity cuts, and our most probable members lay perfectly on a 10 Gyr isochrone of $[\mbox{Fe/H}] = -1.74$.
-Our stream members indicate a revised distance to the stream of $24$\,kpc at $(l, b) = (250^\circ$, $50^\circ)$, slightly farther than that deduced by \citet{Newberg;et-al_2010}.
+Although each individual criterion is likely to induce some level contamination, their intersection reveals highly probable, self-consistent, Orphan Stream K giants.
+We deduce a stream metallicity of $[\mbox{Fe/H}] = -1.78 \pm 0.08$ which is not biased by spectral type.
+Recall that the metallicity determination was performed after kinematic and gravity cuts, and our most probable members lay perfectly on a 10 Gyr isochrone of $[\mbox{Fe/H}] = -1.78$.
+Our stream members indicate a revised distance to the stream of $24$\,kpc at $(l, b) = (250\,^\circ$, $50\,^\circ)$, slightly farther than that deduced by \citet{Newberg;et-al_2010}.
 
-If the Orphan Stream continues through SEGUE stripe 1540 at $(l, b) = (271^\circ$, $38^\circ)$ as \citet{Newberg;et-al_2010} found, then the stream is even closer there than in the region analysed here.
-Thus, if our observations and analyses are repeated at $(271^\circ$, $38^\circ)$, we predict brighter (and subsequently more numerous) K giant stream members will be recovered.
+If the Orphan Stream continues through SEGUE stripe 1540 at $(l, b) = (271\,^\circ$, $38\,^\circ)$ as \citet{Newberg;et-al_2010} found, then the stream is even closer there than in the region analysed here.
+Thus, if our observations and analyses are repeated at $(271\,^\circ$, $38\,^\circ)$, we predict K giant stream members of brighter apparent magnitude will be recovered.
+If the stream density is similar to or higher than what we observe at $(l, b) = (250\,^\circ, 50\,^\circ)$ then more K giant Orphan Stream members are likely to be recovered in the stripe 1540 field.
+
+Although OSS 6 has an uncertain radial velocity, using a maximum-likelihood estimation we find the mean stream galactocentric velocity at $(l, b) = (250\,^\circ, 50\,^\circ)$ from five stars to be $V_{GSR} = 82 \pm 1.6$ km s$^{-1}$ and the intrinsic dispersion to be $0.3 \pm 3.3$ km s$^{-1}$.
+For our four stars with low radial velocity errors this dispersion is found to be $0.00 \pm 2.4$ km s$^{-1}$.
+These velocities indicate that the Orphan Stream is a very cold stream, and implies their motion is largely perpendicular to the line of sight.
 

### 2012-09-04 2012-oss-mrs/figures/cmd.py

@@ -1,5 +1,6 @@
 
-good_candidate_oids = [570, 169, 143, 604, 337, ]#571, 76, 264]
+good_candidate_oids = [570, 169, 143, 604, 337]# 571, 76, 264]
+
 #upperlimit_candidate_oids = [798, 570, 932, 604, 424, 672, 685]
 upperlimit_candidate_oids = []
 dodgy_candidate_oid = False
@@ -46,7 +47,7 @@ if dodgy_candidate_oid:
 g, r = np.loadtxt('giardi-10gyr-1.5.data', unpack=True)
 ax.plot(g - r, g + newberg_distance_modulus, 'k:', zorder=-10, label='[Fe/H] $=-1.5$ at $21.4$ kpc')
 
-g, r = np.loadtxt('giardi-10gyr-1.74.data', unpack=True)
+g, r = np.loadtxt('giardi-10gyr-1.79.data', unpack=True)
 ax.plot(g - r, g + my_distance_modulus, 'k-', lw=2, zorder=-1, label='[Fe/H] $=-1.74$ at $24$ kpc')
 
 g, r = np.loadtxt('giardi-10gyr-2.0.data', unpack=True)
@@ -67,6 +68,10 @@ scat_upperlims = ax.scatter(g0[idx] - r0[idx], g0[idx], c=feh[idx], marker='v', 
 # Plot normal measurements
 idx = np.where(ew > 0)
 scat = ax.scatter(g0[idx] - r0[idx], g0[idx], c=feh[idx], edgecolor='k', vmin=-2.8, vmax=-0.8, s=50, cmap=my_cmap)
+
+
+for g__, gmr__, feh__ in zip(g0[idx], g0[idx] - r0[idx], feh[idx]):
+    print g__, gmr__, feh__
 
 
 

### 2012-09-04 2012-oss-mrs/figures/vgsr-histogram.py

@@ -34,10 +34,17 @@ hist_besancon *= len(besancon_vgsr) * binx/10.
 
 #obs_ax.hist([obs_vgsr, besancon_vgsr], bins=bins, histtype='bar', color=['grey', 'none'], label=['Observed', u'Besançon'])
 #obs_ax.bar([bins[:-1], bins[:-1]], [hist_obs, hist_besancon], [np.diff(bins), np.diff(bins)], color=['r', 'g'])
-obs_ax.bar(bins[:-1], hist_obs, np.diff(bins)/2, color='#dddddd', label='Observed')
-obs_ax.bar(bins[:-1] + np.diff(bins)[0]/2, hist_besancon, np.diff(bins)/2, color='white', label=u'Besançon (Robin et al. 2003)')
+
+
+
+#obs_ax.bar(bins[:-1] + np.diff(bins)[0]/2, hist_besancon, np.diff(bins)/2, color='white', label=u'Besançon (Robin et al. 2003)')
+#obs_ax.scatter(bins[:-1] + np.diff(bins)[0]/2, hist_besancon, facecolor='k', zorder=3)
+obs_bar = obs_ax.bar(bins[:-1], hist_obs, np.diff(bins), color='#cccccc', label='Observed')
+obs_plot = obs_ax.plot(bins[:-1] + np.diff(bins)[0]/2, hist_besancon, '--ok', zorder=2, label=u'Besançon model (Robin et al. 2003)')
+
 
 obs_ax.set_xlim(-250, 250)
+obs_ax.set_ylim(0, obs_ax.get_ylim()[1])
 obs_ax.set_xlabel('$V_{GSR}$ [km s$^{-1}$]', fontsize=labelsize)
 obs_ax.set_ylabel('$N$', fontsize=labelsize)
 
@@ -45,10 +52,11 @@ patch = Rectangle((oss_vgsrs[0], 0), oss_vgsrs[1] - oss_vgsrs[0], obs_ax.get_yli
 obs_ax.add_patch(patch)
 
 idx = np.searchsorted(bins, oss_vgsr_centroid) - 1
-obs_ax.annotate('Orphan Stream', (oss_vgsr_centroid, hist_obs[idx] + 5), (oss_vgsr_centroid, obs_ax.get_ylim()[1]/4), horizontalalignment='center', arrowprops={'arrowstyle': '->'})
[…]

### 2012-09-12 2012-oss-mrs/draft-oss-mrs.tex
Current status of paper prior to applying GDC comments

@@
 \author{Andrew R. Casey\altaffilmark{1,2}, Stefan C. Keller\altaffilmark{1}, Gary Da Costa\altaffilmark{1}, Elizabeth Maunder\altaffilmark{1}, Anna Frebel\altaffilmark{2}}
-\altaffiltext{1}{Research School of Astronomy \& Astrophysics, Australian National University, Mount Stromlo Observatory, via Cotter Rd, Weston, ACT 2611, Australia; \email{arcasey@mso.anu.edu.au}}
+\altaffiltext{1}{Research School of Astronomy \& Astrophysics, Australian National University, Mount Stromlo Observatory, via Cotter Rd, Weston, ACT 2611, Australia; \email{acasey@mso.anu.edu.au}}
 \altaffiltext{2}{Massachusetts Institute of Technology, Kavli Institute for Astrophysics and Space Research,
@@
 The stream stretches over $60\,^\circ$ in the sky, has a low surface brightness and a narrow stream width of only $\sim2^\circ$ and as the name suggests, the parent object largely remains a mystery.
-The stream extends past the celestial equator \-- outside the SDSS footprint \-- but is not detected in existing southern surveys \citep{Newberg;et-al_2010}.
+The stream extends past the celestial equator \--- outside the SDSS footprint \--- but is not detected in existing southern surveys \citep{Newberg;et-al_2010}.
 Whilst the parent system remains elusive, significant effort has been placed on associating the stream with known Milky Way satellites \citep{Zucker;et-al_2006, Fellhaur;et-al_2007,Jin;Lynden_Bell_2007,Sales;et-al_2008}.
@@
 % Besan\c{c}on heliocentric velocities have been translated to a galactocentric frame in the same way as our targets.
-Figure \ref{fig:velocities} shows a histogram of our galactocentric velocities, compared to the predicted smooth halo velocity distribution for this region from the Besan\c{c}on model \citep{Robin;et-al_2003}.
+Figure \ref{fig:velocities} shows a histogram of our galactocentric velocities, compared to the predicted smooth line-of-sight velocity distribution for this region from the Besan\c{c}on model \citep{Robin;et-al_2003}.
 It is clear that our target selection has yielded mostly nearby thick disk dwarf stars with $V_{\textsc{gsr}} \approx -120$\,km s$^{-1}$.
@@
 Both analyses were entirely consistent with each other: essentially the same candidate selection was found using both techniques.
-However, given slightly poorer signal at the Mg\,\textsc{I}\,b triplet, we were forced to adopt many more upper limits than when using the 8807{\AA} line.
+However, given slightly poorer signal at the Mg\,\textsc{I}\,b triplet, we were forced to adopt many more upper limits than when using the 8807 {\AA} line.
 Because we classify all upper limits as being ``non-dwarfs" (i.e.
@@
 
-We can ascertain abundance corrections for our stars fainter than the horizontal branch by comparing our $V-V_{HB}$ and $EW_{\lambda8452} + EW_{\lambda8662}$ with those measured by \citet{Saviane;et-al_2012} for globular clusters.
-Only two clusters had measured Ca \textsc{II} equivalent widths for stars fainter than the horizontal branch: NGC 6397 with $[\mbox{Fe/H}] = -1.99$ and NGC 6254 with $[\mbox{Fe/H}] = -1.57$ \citep[both abundances from][]{Carretta;et-al_2009}.
+We can ascertain abundance corrections for our stars fainter than the horizontal branch by comparing our $g - g_{HB}$ (or $V-V_{HB}$) and $EW_{\lambda8452} + EW_{\lambda8662}$ with those measured by \citet{Saviane;et-al_2012} for globular clusters.
+Only two clusters from \citet{Saviane;et-al_2012} had measured Ca \textsc{II} equivalent widths for stars fainter than the horizontal branch: NGC 6397 with $[\mbox{Fe/H}] = -1.99$ and NGC 6254 with $[\mbox{Fe/H}] = -1.57$ \citep[both abundances from][]{Carretta;et-al_2009}.
 OSS 6 and OSS 7 lie at the mid-point between these cluster stars, implying an abundance of $[\mbox{Fe/H}] \sim -1.78$, or a mean correction of $-0.14$ dex for OSS 6 and 7.

### 2012-09-12 2012-oss-mrs/Response_GDC_20120912_II.txt
Incorporated all comments from Comments_GDC_20120912_II.txt

Ok, now the draft.  Given my previous message I think 4.3 is likely to get revised a bit along the lines:
- discuss Ca II metallicities (with the calibration issues, etc)
- discuss isochrone metallicities given Newburg distance.
- correlate these estimates
==> sample of most probable members  (and less likely, and probably not, members)
Then given the probable members, likely first revise distance estimate - will give minor adjustment to isochrone abundances.
Show isochrone fit.  Then in probably new section discuss:
a) metallicity spread of probable members - noting if significant, then expect progenitor likely dSph.  If small, then progenitor more likely a GC - as in Wylie de Boer et al 2012 ApJ 755 35 for Aquarius.  Probably can't say too much because will depend on confirmation of membership, e.g. the metal-poor star.  But we can speculate.
b) the line of site velocity dispersion - seemingly very small.

More specific comments.  (Happy with responses to my earlier comments).

Abstract.  I think technically the AAT is still the Anglo-Australian Telescope despite the name change of the AAO.  May be stick with AAT?

>> You're right. I knew that one of them (AAO/AAT) had changed names and the other had not. I got them mixed up. Corrected in text.

Second last sentence of Abstract.  I'd prefer something like "The observed velocity dispersion of our highest probability members is consistent with arising from the velocity errors alone, indicating that, at least as regards the
line-of-sight, the Orphan Stream is kinematically quite cold.

>> That's better: Changed.

top of right hand column page 1, first 4 lines:
"total low luminosity" ==> "low total luminosity"
>> Changed.

"in reliably identifying" ==> "to separate reliably"
>> Altered to "to reliably separate Orphan Stream members from halo stars": "to separate reliably" didn't quite make sense in context.

"will be detected" ==> "will be established"
>> Changed.

and I think the Keller et al reference should go after "SkyMapper" rather than at the end of the sentence, although not a big issue.
>> Placed after "SkyMapper telescope".

Next para - maybe "Consequently, the fainter…"
>> Changed

maybe an "and" between Xue et al and Koposov et al rather than a semi-colon.
>> Added

maybe "kinematic maps of these streams"  - we're not talking specifically of the OS here.
>> Changed to "More complete photometric and kinematic maps of these low total luminosity streams may provide the best test as to whether this mass discrepancy is an artefact of incomplete observations."

Last para:
"seven highly probable Orphan Stream candidates"  - the 'seven' might need changing.  It is after all 5 stars in section 5.
>> #TODO

page 2, left column 3rd line.  Surely one of the discovery papers can fill "[citation needed]".
>> I checked them all just now, and none of them make this claim. I can't remember where I first got this number from, but it's about right. I don't think it's too big of a claim to leave there without a citation. I've removed the [citation needed], and I'm happy to see what the referee says.

3 lines from the bottom: "discriminate dwarfs from giants"  (i.e. and ==> from)
>> Changed

2 lines from the bottom "spectra" is missing after "arm".
>> Added

2nd paragraph of 4.1.  Think we need to say that "stars" in the Besancon models were selected in the same way as the observed sample, i.e. same colour and magnitude cuts.  (New Fig 1 is fine).
>> Whoops! I had forgotten to do this after Stefan gave me the true selection criteria. I've done it now though and re-plotted the histogram. The kinematic distribution did not change significantly. I've also added the following as the second sentence in 2nd paragraph of 4.1: " We have selected predicted stars from Besan\c{c}on using the same criterion outlined in \S\ref{sec:target-selection} after using the \citet{Jordi;et-al_2006} colour transformations."

5th line of 4.2 on page 3 "narrow" ==> "narrower"
>> Changed

(Haven't made any specific comments on current 4.3 - not appropriate if it's going to be revised as I suggested).

2nd para of Section 5.  I think the words "brighter than our current limit of g ~ 18" need to go in after "members" as it doesn't quite make sense otherwise.  
>> Sorry: I can't find this anywhere in the text.

3rd para - probably put "i.e., consistent with zero" after "0.3 +/- 3.3 kms-1".  Again the numbers might change if the sample of members changes.  And this actual paragraph will probably now come before the conclusions section.

OK, enough!

Cheers,
Gary

### 2012-09-12 2012-oss-mrs/draft-oss-mrs.tex
Incorporated all comments from Comments_GDC_20120912_II.txt

@@
 \begin{abstract}
-We present coordinates and properties of candidate K giant members in the Orphan Stream, which have been identified from low resolution spectroscopic data taken with AAOmega on the Australian Astronomical Telescope.
+We present coordinates and properties of candidate K giant members in the Orphan Stream, which have been identified from low resolution spectroscopic data taken with AAOmega on the Anglo-Astronomical Telescope.
 With modest S/N and independent cuts in photometry, kinematics, gravity and metallicity we yield self-consistent, highly probable stream members.
@@
 We find a revised stream distance of 24 kpc near the celestial equator, and our kinematic signature peaks at $V_{helio} \sim 218$\,km s$^{-1}$.
-The Orphan Stream appears extremely cold, with an intrinsic dispersion of less than $0.3 \pm 3.3$ km s$^{-1}$.
-We highlight likely members for high resolution spectroscopic follow-up.
+The observed velocity dispersion of our highest probability members is consistent with arising from the velocity errors alone, indicating that, at least as regards the
+line-of-sight, the Orphan Stream is kinematically quite cold. We highlight likely members for high resolution spectroscopic follow-up.
 \end{abstract}
@@
 In contrast, there has been relatively limited observational work on the Orphan Stream itself other than the original discovery papers \citep{Grillmair;Dionatos_2006, Belokurov;et-al_2006, Belokurov;et-al_2007} and the work of \citet{Newberg;et-al_2010}.
-This is largely to be expected given the absence of multi-band photometry in the southern sky and the total low luminosity of the stream, making it difficult in reliably identifying Orphan Stream members from halo stars.
-It is unlikely the full extent of the Orphan Stream will be detected until the SkyMapper telescope surveys this region \citep{Keller;et-al_2007}.
+This is largely to be expected given the absence of multi-band photometry in the southern sky and the low total luminosity of the stream, making it difficult to reliably seperate Orphan Stream members from halo stars.
+It is unlikely the full extent of the Orphan Stream will be established until the SkyMapper telescope \citep{Keller;et-al_2007} surveys this region.
 
 As \citet{Sales;et-al_2008} points out, there is a natural observational bias towards more massive and recent mergers like Sagittarius.
-The fainter end of this substructure distribution has yet to be fully recovered, or thoroughly examined.
-Interestingly, there are indications that  some fainter substructures like the Orphan Stream \citep{Newberg;et-al_2010} and the Palomar 5 tidal tails \citep{Odenkirchen;et-al_2009} have orbits which seem to be best-fit by Milky Way models with nearly 60\% less mass \citep{Newberg;et-al_2010} than generally reported by \citet{Xue;et-al_2008, Koposov;et-al_2010}.
+Consequently, the fainter end of this substructure distribution has yet to be fully recovered, or thoroughly examined.
+Interestingly, there are indications that  some fainter substructures like the Orphan Stream \citep{Newberg;et-al_2010} and the Palomar 5 tidal tails \citep{Odenkirchen;et-al_2009} have orbits which seem to be best-fit by Milky Way models with nearly 60\% less mass \citep{Newberg;et-al_2010} than generally reported by \citet{Xue;et-al_2008} and \citet{Koposov;et-al_2010}.
 Such a discrepancy in the mass of the Milky Way is worrying.
-A more complete photometric and kinematic map of the stream may provide the best test as to whether this mass discrepancy for faint substructure orbits is real or an artefact of incomplete observations.
+More complete photometric and kinematic maps of these low total luminosity streams may provide the best test as to whether this mass discrepancy is an artefact of incomplete observations.
 Whilst the full spatial extent of the stream remains incomplete, we can examine the detailed chemistry of the stream and investigate the stream history, as well as make predictions about the nature of the progenitor.
@@
 Because K-giants are difficult to unambiguously detect from photometry alone, low resolution spectroscopy is required to estimate stellar parameters and determine radial velocities.
-The Orphan Stream has a low spatial over-density on the order of $\sim10\%$ [citation needed], which makes it difficult to separate stream members from halo stars.
+The Orphan Stream has a low spatial over-density on the order of $\sim10\%$, which makes it difficult to separate stream members from halo stars.
 However, there is a well described distance gradient along the stream \citep{Belokurov;et-al_2007, Newberg;et-al_2010} which provides an indication on where we should focus our spectroscopic efforts.
@@
 
-Observations took place on the Australian Astronomical Telescope using the AAOmega spectrograph in April 2009.
+Observations took place on the Anglo-Astronomical Telescope using the AAOmega spectrograph in April 2009.
 AAOmega is a fibre-fed, dual beam multi-object spectrograph which is capable of simultaneously observing spectra of 400 (science and sky) targets across a $2^\circ$ field of view.
@@
 Our spectral region also includes gravity-sensitive magnesium lines: Mg I at 8807\,{\AA}, and the Mg I\,b 3$p$-4$s$ triplet lines at $\sim$5178\,{\AA}.
-As we demonstrate in the next section, these lines are sufficient to discriminate dwarfs and giants even with weak signal.
+As we demonstrate in the next section, these lines are sufficient to discriminate dwarfs from giants even with weak signal.
 
-The blue and red arm were normalised using a third order cubic spline after multiple iterations of outlier clipping.
+The blue and red arm spectra were normalised using a third order cubic spline after multiple iterations of outlier clipping.
 We used defined knot spacings of 20 nm in the red arm, and 5 nm in the blue arm in order to accommodate often poor S/N, and varying strengths of molecular band-heads.
@@
 Figure \ref{fig:velocities} shows a histogram of our galactocentric velocities, compared to the predicted smooth line-of-sight velocity distribution for this region from the Besan\c{c}on model \citep{Robin;et-al_2003}.
+We have selected predicted stars from Besan\c{c}on using the same criterion outlined in \S\ref{sec:target-selection} after using the \citet{Jordi;et-al_2006} colour transformations.
 It is clear that our target selection has yielded mostly nearby thick disk dwarf stars with $V_{\textsc{gsr}} \approx -120$\,km s$^{-1}$.
@@
 We have measured the equivalent widths of the gravity-sensitive Mg I line at 8807 \AA{} to distinguish dwarfs from giants \citep{Battaglia;Starkenburg_2012}.
-At a given temperature (or $g \-- r$) and metallicity, giant stars present narrow Mg I absorption lines than their dwarf contaminants.
+At a given temperature (or $g \-- r$) and metallicity, giant stars present narrower Mg I absorption lines than their dwarf contaminants.
 Given our target selection, our sample is likely to contain many more dwarfs than giants.
@@
 
-Although OSS 6 has an uncertain radial velocity, using a maximum-likelihood estimation we find the mean stream galactocentric velocity at $(l, b) = (250\,^\circ, 50\,^\circ)$ from five stars to be $V_{GSR} = 82 \pm 1.6$ km s$^{-1}$ and the intrinsic dispersion to be $0.3 \pm 3.3$ km s$^{-1}$.
+Although OSS 6 has an uncertain radial velocity, using a maximum-likelihood estimation we find the mean stream galactocentric velocity at $(l, b) = (250\,^\circ, 50\,^\circ)$ from five stars to be $V_{GSR} = 82 \pm 1.6$ km s$^{-1}$ and the intrinsic dispersion to be $0.3 \pm 3.3$ km s$^{-1}$, i.e., consistent with zero.
 For our four stars with low radial velocity errors this dispersion is found to be $0.00 \pm 2.4$ km s$^{-1}$.

### 2012-09-12 2012-oss-mrs/figures/vgsr-histogram.py

@@ -16,7 +16,7 @@ matplotlib.rc('font', **{'sans-serif' : 'Arial',
                          'family' : 'sans-serif'})
 
 obs_vgsr = np.loadtxt('velocities.data', delimiter=',', usecols=(-1,))
-besancon_vgsr = np.loadtxt('besancon.data', usecols=(-1,))
+besancon_vgsr = np.loadtxt('besancon_sel.txt', usecols=(-2,))
 
 
 bins = np.arange(-250, 250, binx)
@@ -30,7 +30,7 @@ hist_obs, bins = np.histogram(obs_vgsr, bins=bins)
 
 # Normalise the besancon results
 hist_besancon, bins = np.histogram(besancon_vgsr, bins=bins, normed=True)
-hist_besancon *= len(besancon_vgsr) * binx/10.
+hist_besancon *= len(besancon_vgsr) * binx/10. *4.
 
 #obs_ax.hist([obs_vgsr, besancon_vgsr], bins=bins, histtype='bar', color=['grey', 'none'], label=['Observed', u'Besançon'])
 #obs_ax.bar([bins[:-1], bins[:-1]], [hist_obs, hist_besancon], [np.diff(bins), np.diff(bins)], color=['r', 'g'])

### 2012-09-12 2012-oss-mrs/Response_GDC_20120912_II.txt
Fixed text to match for new Vgsr histogram plot

@@
 
+>> In light of the new Besancon histogram, there is a hint of Orphan Stream there in kinematics alone, so I have altered the text:
+>> "No statistically significant peak representative of the Orphan Stream exists in our sample"
+>> to
+>> "There is no sharp kinematic peak representative of the Orphan Stream exists in our sample."
+>> The statistical significance is probably questionable, i.e.
+it could be argued either way, so rather than make a bold statement I've erred on the side of caution -- since we recover OSS members quite reliably using a combination of cuts anyways.
+
 5th line of 4.2 on page 3 "narrow" ==> "narrower"
@@
 
+>> Added.
+
 OK, enough!

### 2012-09-12 2012-oss-mrs/draft-oss-mrs.tex
Fixed text to match for new Vgsr histogram plot
Minor changes after a readthrough

@@
 
-\author{Andrew R. Casey\altaffilmark{1,2}, Stefan C. Keller\altaffilmark{1}, Gary Da Costa\altaffilmark{1}, Elizabeth Maunder\altaffilmark{1}, Anna Frebel\altaffilmark{2}}
+\author{Andrew R. Casey\altaffilmark{1,2}, Stefan C. Keller\altaffilmark{1}, Gary Da Costa\altaffilmark{1}, Elizabeth Maunder\altaffilmark{1}}
 \altaffiltext{1}{Research School of Astronomy \& Astrophysics, Australian National University, Mount Stromlo Observatory, via Cotter Rd, Weston, ACT 2611, Australia; \email{acasey@mso.anu.edu.au}}
@@
 The more prominent of the detectable substructures, like Sagittarius, have been well-studied.
-One of the more prominent \-- yet less studied \-- substructures is that of the Orphan Stream.
+One of the more prominent \--- yet less studied \--- substructures is that of the Orphan Stream.
 
@@
 In this letter we present a detailed, self-consistent analysis to identify K giant members of the Orphan Stream.
-Using our selection method we have catalogued the locations of seven highly probable Orphan Stream candidates, all worthy of high resolution spectroscopic follow up.
+Using our selection method we have catalogued the locations of X highly probable Orphan Stream candidates, all worthy of high resolution spectroscopic follow up.
 In the following section we outline our photometric target selection.
-In Section \S\ref{sec:observations} we describe the low resolution spectroscopic observations.
+In section \ref{sec:observations} we describe the low resolution spectroscopic observations.
 The data analysis, including stream identification, is discussed in \S\ref{sec:analysis} and in \S\ref{sec:conclusions} the conclusions, predictions and future work are presented.
@@
 
-Given our colour selection we expect to recover giants and dwarf contaminants.
+Given our colour selection we expect to recover giants, and dwarf contaminants.
 The lack of 2MASS photometry for the selected stars means we cannot use the $(J-H, H-K)$ diagram to aid the separation of candidate giants from contaminating dwarfs.
@@
 
-The data were reduced using the standard \textsc{2DFDR} reduction pipeline \footnote{http://www.aao.gov.au/2df/aaomega/aaomega\_2dfdr.html}.
+The data were reduced using the standard \textsc{2DFDR} reduction pipeline\footnote{http://www.aao.gov.au/2df/aaomega/aaomega\_2dfdr.html}.
 After flat-fielding, throughput calibration for each fibre was achieved using the intensity of skylines in each fibre.
@@
 The expected kinematic signature for the Orphan Stream, as \citet{Newberg;et-al_2010} reported, is labelled in Figure \ref{fig:velocities}.
-No statistically significant peak representative of the Orphan Stream exists in our sample.
+There is no sharp kinematic peak representative of the Orphan Stream exists in our sample.
 From kinematics alone, our targets appears largely indistinguishable from a smooth halo distribution.
@@
 Given our target selection, our sample is likely to contain many more dwarfs than giants.
-In four cases no Mg I 8807 \AA{} line was apparent, so an upper limit was estimated based on the S/N.
+In some cases no Mg I 8807 \AA{} line was apparent, so an upper limit was estimated based on the S/N.
 In these cases the candidate was considered a ``non-dwarf" because we cannot exclusively rule out a metal-poor sub-giant with this criterion alone.
 For these purposes we are only looking for a simple indication as to whether a star is likely a dwarf or not.
-Figure \ref{fig:ew-mg} illustrates the trend with EW$_{\lambda8807}$ against SDSS $g \-- r$ de-reddened\footnote{All magnitudes presented in this paper are de-reddened}, illustrating the dominant upper dwarf branch we wish to exclude.
+Figure \ref{fig:ew-mg} illustrates the trend with EW$_{\lambda8807}$ against SDSS $g \-- r$ de-reddened\footnote{All magnitudes presented in this letter are de-reddened}, illustrating the dominant upper dwarf branch we wish to exclude.
 The adopted dwarf/giant separation line is shown.
@@
 Given that our four Orphan Stream stars cover range along the giant branch, we are in a good position to revise the distance estimate to the stream.
-Given a 10 Gyr \citet{Girardi;et-al_2008} isochrone at $[\mbox{Fe/H}] = -1.74$, we find a best-fitting distance to the stream of 24 kpc at ($l, $b) = ($250^\circ$, $50^\circ$).
+Given a 10 Gyr \citet{Girardi;et-al_2008} isochrone at $[\mbox{Fe/H}] = -1.78$, we find a best-fitting distance to the stream of 24 kpc at ($l, $b) = ($250^\circ$, $50^\circ$).
 This isochrone is also shown in Figure \ref{fig:cmd}, and it is clear that the four most probable member stars lie almost precisely on this isochrone.
-Our derived distance is slightly farther than the $21.4 \pm 1.0$ kpc found by \citet{Newberg;et-al_2010}, but given the inherent uncertainties in determining distance we argue these distances are largely in agreement.
+Our derived distance is slightly farther than the $21.4 \pm 1.0$ kpc found by \citet{Newberg;et-al_2010}, but given the inherent uncertainties in determining distances we argue these measurements are largely in agreement.
 
@@
 
-If the Orphan Stream continues through SEGUE stripe 1540 at $(l, b) = (271\,^\circ$, $38\,^\circ)$ as \citet{Newberg;et-al_2010} found, then the stream is even closer there than in the region analysed here.
+If the Orphan Stream continues through SEGUE Stripe 1540 at $(l, b) = (271\,^\circ$, $38\,^\circ)$ as \citet{Newberg;et-al_2010} found, then the stream is even closer there than in the region analysed here.
 Thus, if our observations and analyses are repeated at $(271\,^\circ$, $38\,^\circ)$, we predict K giant stream members of brighter apparent magnitude will be recovered.
-If the stream density is similar to or higher than what we observe at $(l, b) = (250\,^\circ, 50\,^\circ)$ then more K giant Orphan Stream members are likely to be recovered in the stripe 1540 field.
+If the stream density is similar to or higher than what we observe at $(l, b) = (250\,^\circ, 50\,^\circ)$ then more K giant Orphan Stream members are likely to be recovered in the Stripe 1540 field.
 

### 2012-09-14 2012-oss-mrs/figures/cmd.py
Updated data tables after using isochrone- and line strength-derived metallicities and a consistency criterion

@@ -1,6 +1,15 @@
 
 good_candidate_oids = [570, 169, 143, 604, 337]# 571, 76, 264]
 
+# Using isochrone consistency check
+good_candidate_oids.extend([917, 768, 76, 685, 932])
+
+# OSS 1
+#good_candidate_oids.append(492)
+
+# OSS 5
+#good_candidate_oids.append(672)
+
 #upperlimit_candidate_oids = [798, 570, 932, 604, 424, 672, 685]
 upperlimit_candidate_oids = []
 dodgy_candidate_oid = False
@@ -56,28 +65,28 @@ ax.plot(g - r, g + newberg_distance_modulus, 'k--', zorder=-10, label='[Fe/H] $=
 
 
 # Load in our candidates
-oid, g0, g, r0, ew, feh = np.loadtxt('all-candidates.data', usecols=(0, 19, 9, 20, 5, 25), unpack=True)
+oid, g0, g, r0, ew, feh_cat, feh_iso, feh_iso_upperlimit = np.loadtxt('all-candidates.data', usecols=(0, 19, 9, 20, 5, 25, 26, 27), unpack=True)
 
-table_data = np.loadtxt('all-candidates.data', usecols=(0, 1, 2, -7, -6, 4, 3, 5, -1, ))
+table_data = np.loadtxt('all-candidates.data', usecols=(0, 1, 2, 19, 20, 4, 3, 5, 25, 26 ))
 
 # Plot upper measurements
 idx = np.where(ew < 0)
-scat_upperlims = ax.scatter(g0[idx] - r0[idx], g0[idx], c=feh[idx], marker='v', edgecolor='k', vmin=-2.8, vmax=-0.8, s=50, cmap=my_cmap)
+scat_upperlims = ax.scatter(g0[idx] - r0[idx], g0[idx], c=feh_cat[idx], marker='v', edgecolor='k', vmin=-2.8, vmax=-0.8, s=50, cmap=my_cmap)
 
 
 # Plot normal measurements
 idx = np.where(ew > 0)
-scat = ax.scatter(g0[idx] - r0[idx], g0[idx], c=feh[idx], edgecolor='k', vmin=-2.8, vmax=-0.8, s=50, cmap=my_cmap)
+scat = ax.scatter(g0[idx] - r0[idx], g0[idx], c=feh_cat[idx], edgecolor='k', vmin=-2.8, vmax=-0.8, s=50, cmap=my_cmap)
 
 
[…]

### 2012-09-14 2012-oss-mrs/draft-oss-mrs.tex
Updated stream membership table, figures and text after performing metallicity consistency criterion. Improved many small grammatical mistakes after a thorough readthrough

@@
 
-\title{Chemistry of the Orphan Stream I: Identifying Stream Candidates with Low Resolution Spectroscopy}
+\title{Chemistry of the Orphan Stream I: Identifying Stream Members from Low Resolution Spectroscopy}
 
@@
 Our data indicates an overall stream metallicity of [Fe/H] $= -1.78 \pm 0.08$ which is more metal-rich than previously found and unbiased by spectral type.
+The metallicity dispersion in our stream sample is indicative that the Orphan Stream has a dSph origin.
 We find a revised stream distance of 24 kpc near the celestial equator, and our kinematic signature peaks at $V_{helio} \sim 218$\,km s$^{-1}$.
@@
 The stream stretches over $60\,^\circ$ in the sky, has a low surface brightness and a narrow stream width of only $\sim2^\circ$ and as the name suggests, the parent object largely remains a mystery.
-The stream extends past the celestial equator \--- outside the SDSS footprint \--- but is not detected in existing southern surveys \citep{Newberg;et-al_2010}.
+The stream extends past the celestial equator \--- outside the SDSS footprint \--- but has not been detected in existing southern surveys \citep{Newberg;et-al_2010}.
 Whilst the parent system remains elusive, significant effort has been placed on associating the stream with known Milky Way satellites \citep{Zucker;et-al_2006, Fellhaur;et-al_2007,Jin;Lynden_Bell_2007,Sales;et-al_2008}.
@@
 Consequently, the fainter end of this substructure distribution has yet to be fully recovered, or thoroughly examined.
-Interestingly, there are indications that  some fainter substructures like the Orphan Stream \citep{Newberg;et-al_2010} and the Palomar 5 tidal tails \citep{Odenkirchen;et-al_2009} have orbits which seem to be best-fit by Milky Way models with nearly 60\% less mass \citep{Newberg;et-al_2010} than generally reported by \citet{Xue;et-al_2008} and \citet{Koposov;et-al_2010}.
+Interestingly, there are indications that  some fainter substructures like the Orphan Stream and the Palomar 5 tidal tails \citep{Odenkirchen;et-al_2009} have orbits which seem to be best-fit by Milky Way models with nearly 60\% less mass \citep{Newberg;et-al_2010} than generally reported by \citet{Xue;et-al_2008} and \citet{Koposov;et-al_2010}.
 Such a discrepancy in the mass of the Milky Way is worrying.
-More complete photometric and kinematic maps of these low total luminosity streams may provide the best test as to whether this mass discrepancy is an artefact of incomplete observations.
-Whilst the full spatial extent of the stream remains incomplete, we can examine the detailed chemistry of the stream and investigate the stream history, as well as make predictions about the nature of the progenitor.
+More complete photometric and kinematic maps of these low total luminosity streams may provide the best test as to whether this mass discrepancy is real, or an artefact of incomplete observations.
+Whilst the full spatial extent of the stream remains incomplete, we can examine the detailed chemistry of its members and investigate the stream history, as well as make predictions about the nature of the host system.
 
@@
 In the following section we outline our photometric target selection.
-In section \ref{sec:observations} we describe the low resolution spectroscopic observations.
+In \S\ref{sec:observations} we describe the low resolution spectroscopic observations.
 The data analysis, including stream identification, is discussed in \S\ref{sec:analysis} and in \S\ref{sec:conclusions} the conclusions, predictions and future work are presented.
@@
 We have targeted two fields centered on ($\alpha$, $\delta$) = (10 48 15, 00 00 00) and (10 48 15, $-02$ 30 00), and employed a combination of colour cuts with the SDSS DR 7 \citep{Abazajian;et-al_2009} data set in order to identify likely K giants:
-
 \begin{eqnarray}
@@
 Three thirty minute science exposures were median combined to assist with cosmic ray removal.
-The median S/N obtained in the red arm for our fields is modest at 35\,px$^{-1}$.
+The median S/N obtained in the red arm for our fields is modest at 35 per pixel.
 With the presence of strong Ca \textsc{II} triplet lines in the red arm we are able to ascertain reliable radial velocities and reasonable estimates on overall metallicity \citep[][and references therein]{Starkenburg;et-al_2010}.
@@
 
-We have employed a combination of separate criterion to identify likely Orphan Stream members: kinematics, a giant/dwarf indication from Mg I lines, and metallicity from Ca II triplet lines.
+We have employed a combination of separate criterion to identify likely Orphan Stream members: kinematics, a giant/dwarf indication from Mg I lines, and consistent metallicities from isochrone fitting and the Ca\,\textsc{II} triplet lines.
 Each criterion is discussed here separately.
@@
 \subsection{Kinematics}
-Radial velocities were measured by cross-correlating our normalised spectra against a K-giant synthetic template with a temperature of $4500$\,K, $\log{g}$ = 2 and [Fe/H] = $-1.5$ across the range $845 \leq \lambda \leq 870$\,nm.
+Radial velocities were measured by cross-correlating our normalised spectra against a K-giant synthetic template with a temperature of $4500$\,K, $\log{g}$ = 1 and [Fe/H] = $-1.5$ across the range $845 \leq \lambda \leq 870$\,nm.
 Heliocentric velocities were translated to the galactic rest frame by adopting the local standard of rest velocity as 220\,km s$^{-1}$ towards $(l, b) = (53^\circ, 25^\circ)$ \citep{Kerr;Lynden-Bell_1986, Mihalas;Binney_1981}\footnote{Where $V_{\textsc{gsr}} = V_{\textsc{helio}} + 220\sin{l}\cos{b} + 16.5\times[\sin{b}\sin{25} + \cos{b}\cos{25}\cos{(l - 53)}]$}.
@@
 Figure \ref{fig:velocities} shows a histogram of our galactocentric velocities, compared to the predicted smooth line-of-sight velocity distribution for this region from the Besan\c{c}on model \citep{Robin;et-al_2003}.
-We have selected predicted stars from Besan\c{c}on using the same criterion outlined in \S\ref{sec:target-selection} after using the \citet{Jordi;et-al_2006} colour transformations.
+We have selected predicted stars from the Besan\c{c}on model using the same criterion outlined in \S\ref{sec:target-selection} after using the \citet{Jordi;et-al_2006} colour transformations.
 It is clear that our target selection has yielded mostly nearby thick disk dwarf stars with $V_{\textsc{gsr}} \approx -120$\,km s$^{-1}$.
@@
 To isolate potential Orphan Stream members we have nominated a relatively wide kinematic selection region between $75 \leq V_{\textsc{gsr}} \leq 135$ km s$^{-1}$, which yields 25 Orphan Stream candidates.
-The typical uncertainty in our kinematics is $\pm{}3.5$\,km s$^{-1}$, although for our fainter targets this quickly increases to $\sim10$ km s$^{-1}$.
+The typical uncertainty in our kinematics is $\pm{}3.5$\,km s$^{-1}$, although for our fainter targets this quickly increases above $10$ km s$^{-1}$.
 
@@
 For these purposes we are only looking for a simple indication as to whether a star is likely a dwarf or not.
-Figure \ref{fig:ew-mg} illustrates the trend with EW$_{\lambda8807}$ against SDSS $g \-- r$ de-reddened\footnote{All magnitudes presented in this letter are de-reddened}, illustrating the dominant upper dwarf branch we wish to exclude.
+Figure \ref{fig:ew-mg} illustrates the trend with EW$_{\lambda8807}$ against SDSS de-reddened $g \-- r$\footnote{All magnitudes presented in this letter are de-reddened}, illustrating the dominant upper dwarf branch we wish to exclude.
 The adopted dwarf/giant separation line is shown.
@@
 potential OSS giants), we deduced a slightly larger candidate sample for the Mg\,\textsc{I}\,b analysis, which was primarily populated by upper limits.
-In conclusion, we found the Mg\,\textsc{I} line at 8807 appeared to be a more consistent dwarf discriminant given our weak S/N \--- particularly for our fainter stars \--- and thus we have used the 8807{\AA} Mg \textsc{I} selection throughout the rest of our analysis.
+In conclusion, we found the Mg\,\textsc{I} line at 8807{\,\AA} appeared to be a more consistent dwarf discriminant given our weak S/N \--- particularly for our fainter stars \--- and thus we have used the 8807\,{\AA} Mg \textsc{I} selection throughout the rest of our analysis.
 
@@
 
-We have measured the equivalent widths of the Ca\,\textsc{II} near-infrared triplet lines for stars which meet our kinematic and surface gravity criteria.
-After correcting for luminosity, the equivalent width of the Ca\,\textsc{II} triplet lines provide a good indication for the metallicity of a RGB star \citep{Amandroff;Da_Costa_1991}.
-We have employed the \citet{Starkenburg;et-al_2010} relationship and corrected for luminosity in $g$ against the horizontal branch magnitude at $g_0$ = 17.1 \citep{Newberg;et-al_2010}.
-Strictly speaking, the Ca\,\textsc{II}\---[Fe/H] calibation is only valid for stars brighter than the horizontal branch, although the relationship only becomes significantly inappropriate near $g \-- g_{HB} \sim +1$ \citep{Saviane;et-al_2012}.
+We have measured the equivalent widths of the Ca\,\textsc{II} near-infrared triplet lines for stars that meet our kinematic and surface gravity criteria.
+After correcting for luminosity, the equivalent width of the Ca\,\textsc{II} triplet lines provide a good indication of the metallicity of a RGB star \citep{Amandroff;Da_Costa_1991}.
+We have employed the \citet{Starkenburg;et-al_2010} relationship and corrected for luminosity in $g$ against the horizontal branch magnitude at $g_{HB}$ = 17.1 \citep{Newberg;et-al_2010}.
+Strictly speaking, the Ca\,\textsc{II}\---[Fe/H] calibration is only valid for stars brighter than the horizontal branch, although the relationship only becomes significantly inappropriate near $g \-- g_{HB} \sim +1$ \citep{Saviane;et-al_2012}.
 Many of our candidates are fainter than this valid luminosity range, and therefore they should not be excluded solely because of their derived metallicities.
-Stars fainted than $g_0$ will have slightly lower metallicities than predicted by our Ca\,\textsc{II}\---[Fe/H] relationship, and for these stars we will only use metallicities to assign a relative qualitative likelihood for stream membership.
+Stars fainted than $g_{HB}$ will have slightly lower metallicities than predicted by our Ca\,\textsc{II}\---[Fe/H] relationship, and for these stars we will only use metallicities to assign a relative qualitative likelihood for stream membership.
+
+Given a distance to the Orphan Stream, we can also estimate a star's metallicity through isochrone fitting.
+We have used a 10 Gyr \citet{Girardi;et-al_2008} isochrone at 21.4\,kpc \citep{Newberg;et-al_2010} and found metallicities for all eighteen likely stream members from their best-fitting isochrone (see Figure \ref{fig:feh}).
+Derived metallicites from Ca\,\textsc{II} line strengths and isochrone fitting which are consistent (within $\pm0.3$\,dex) indiates these measurements are reliable, and that these stars are indeed at a distance of $\sim21.4$\,kpc.
+These ten highly likely stream members fall in the green shaded region illustrated in Figure \ref{fig:feh}.
+
+TODO: Overall stream metallicity
+
+\begin{figure}[h]
+	\includegraphics[width=\columnwidth]{./figures/feh.pdf}
+	\caption{Metallicities from the Ca \textsc{II} triplet lines against metallicities derived from isochrone fitting for the eighteen stars which meet our kinematic and surface gravity criteria.
+Both abundance determinations imply these stars are RGB members of the Orphan Stream at a distance of $\sim21.4$ kpc \citep{Newberg;et-al_2010}.
+Consistency between these methods indicates highly likely stream membership (green region).
+The minimum isochrone metallicity, and a representative uncertainty of 0.2\,dex for abundance measurements is shown.}
+	\label{fig:feh}
+\end{figure}
+
+Figure \ref{fig:cmd} illustrates all eighteen candidates which meet both our kinematic and surface gravity criteria, and our ten most likely members are marked.
+Candidates are coloured by their metallicity deduced from the Ca\,\textsc{II} triplet.
 
@@
 	\includegraphics[width=\columnwidth]{./figures/cmd.pdf}
-	\caption{Color magnitude diagram showing our observed candidates (grey) and highlighting candidates which meet our kinematic and gravity cuts.
-Candidates are colored by their metallicity, and those with upper limiting gravities are marked as triangles.
-Highly probable stream members are marked.
+	\caption{Color magnitude diagram showing our observed candidates (grey).
+Observations fulfilling kinematic and gravity cuts are colored by their metallicity.
+Those with upper limits for surface gravity are marked as triangles.
+Highly probable stream members with consistent line strength- and isochrone-derived abundances are circled.
 Relevant 10 Gyr \citet{Girardi;et-al_2008} isochrones at $[\mbox{Fe/H}] = -1.5$ (dotted), $-2.0$ (dashed) at 21.4\,kpc \citep{Newberg;et-al_2010} are shown, as well as our best-fitting 10 Gyr isochrone of $[\mbox{Fe/H}] = -1.78$ at 24\,kpc (solid).}
@@
 
-Figure \ref{fig:cmd} illustrates all eighteen candidates which meet both our kinematic and surface gravity criterion.
-Candidates are coloured by their metallicity deduced from the Ca\,\textsc{II} triplet.
-There are four candidates above $g_0 \sim 17.1$ which are within our valid luminosity range.
-One of these objects at $(g \-- r, g) \sim (0.57, 17)$ is +0.64\,dex more metal-rich than expected for the stream, and is excluded from membership.
-Another is only +0.21\,dex more metal-rich and sits at (0.57, 16.1), but it's position relative to the isochrone is inconsistent with our inferred metallicity.
-There appears to be an extremely metal-poor star in this sample with an estimated $[\mbox{Fe/H}] = -2.70$ which may be associated with the Orphan Stream.
-The likely parent system of the Orphan Stream is a Milky Way dwarf spheroidal \citep{Belokurov;et-al_2007, Sales;et-al_2008}, which are known to have a wide metallicity distribution function \citep{Tolstoy;et-al_2009}, including populations of extremely metal-poor stars \citep{Kirby;et-al_2010,Frebel;et-al_2010,Tafelmeyer;et-al_2010}.
-Thus, we keep this extremely metal-poor star as a potential stream member for follow-up chemical analysis.
-% speak about OSS 1?
-
 \citet{Newberg;et-al_2010} found the median Orphan Stream metallicity to be [Fe/H] $= -2.1$ from BHB stars, and a distance of $21.4 \pm 1.0$\,kpc in this region.
 In Figure \ref{fig:cmd} we have overlaid 10 Gyr old isochrones from \citet{Girardi;et-al_2008} with metallicities of [Fe/H] $= -2.0$ and $-1.5$ at a distance of $21.4$ kpc \citep{Newberg;et-al_2010}.
-Four of our most probable Orphan Stream members fall between these isochrones.
-The brightest of these green points has an abundance which is in good agreement with the isochrone value.
-The line strength abundances for the other three stars (OSS 3, 6 and 7 \--- see Table \ref{tab:oss-members}) are less certain, as these stars are fainter than the horizontal branch.
 
-We can ascertain abundance corrections for our stars fainter than the horizontal branch by comparing our $g - g_{HB}$ (or $V-V_{HB}$) and $EW_{\lambda8452} + EW_{\lambda8662}$ with those measured by \citet{Saviane;et-al_2012} for globular clusters.
+%We can ascertain abundance corrections for our stars fainter than the horizontal branch by comparing our $g - g_{HB}$ (or $V-V_{HB}$) and $EW_{\lambda8452} + EW_{\lambda8662}$ with those measured by \citet{Saviane;et-al_2012} for globular clusters.
 Only two clusters from \citet{Saviane;et-al_2012} had measured Ca \textsc{II} equivalent widths for stars fainter than the horizontal branch: NGC 6397 with $[\mbox{Fe/H}] = -1.99$ and NGC 6254 with $[\mbox{Fe/H}] = -1.57$ \citep[both abundances from][]{Carretta;et-al_2009}.
@@
 
-Given that our four Orphan Stream stars cover range along the giant branch, we are in a good position to revise the distance estimate to the stream.
+Given that our Orphan Stream stars cover a wide range along the giant branch, we are in a good position to revise the distance estimate to the stream.
 Given a 10 Gyr \citet{Girardi;et-al_2008} isochrone at $[\mbox{Fe/H}] = -1.78$, we find a best-fitting distance to the stream of 24 kpc at ($l, $b) = ($250^\circ$, $50^\circ$).
@@
 
-\begin{deluxetable*}{lcccccccccl}
+\begin{deluxetable*}{lccccccccccc}
 \tabletypesize{\scriptsize}
@@
 	\colhead{$EW_{\lambda8807}$} &
-	\colhead{[Fe/H]} &
-	\colhead{Comment} \\
-Name & (J2000) & (J2000) & & & (kms $^{-1}$) & (km s$^{-1}$) & (km s$^{-1}$) & (\AA) & (dex)
+	\colhead{[Fe/H]$_{Ca}$} &
+	\colhead{[Fe/H]$_{iso}$} &
+	\colhead{Stream} \\
+Name & (J2000) & (J2000) & & & (kms $^{-1}$) & (km s$^{-1}$) & (km s$^{-1}$) & (\AA) & (dex) & (dex) & Probability
 }
 \startdata
-OSS 1 & 10 46 50.6 & $-$00 13 17.9 & 17.33 & 0.50  &  215.5  & 77.0 & 4.0 & 0.416 & $-1.31$ & Unlikely member! \\
-OSS 2 & 10 47 17.6 & $+$00 25 07.7 & 16.09 &  0.73 &  215.7  & 79.2 & 3.3 & 0.212 & $-1.84$ & Highly probable member \\
-OSS 3 & 10 47 30.1 & $-$00 01 24.6 & 17.25 &  0.61 &  221.4  & 83.6 & 3.4 & 0.123 & $-1.62$ & Highly probable member \\
-OSS 4 & 10 49 08.3 & $+$00 02 00.2 & 16.27 &  0.62 &  218.5  & 81.5 & 4.6 & 0.034 & $-2.70$ & Possible EMP member \\
-OSS 6 & 10 48 20.9 & $+$00 26 34.4 & 17.88 &  0.55 &  254.9  & 118.8 & 11.7 & 0.469 & $-1.79$\tablenotemark{a} & Highly probable member \\
-OSS 7 & 10 46 29.3 & $-$00 19 38.5 & 17.77 &  0.56 &  217.3  & 78.4 & 5.2 & 0.126 & $-1.77$\tablenotemark{a} & Highly probable member 
-\enddata
-\tablenotetext{a}{Abundance correction of $-0.14$\,dex included (see \S\ref{sec:metallicities}).}
+OSS 1  & 10 46 29.3 & $-$00 19 38.5 & 16.97 & 0.56 & ? &  78.4 &  5.2 &    0.126 & --1.63 &    --1.68 & High \\
+OSS 2  & 10 47 06.1 & $-$01 56 03.9 & 17.98 & 0.54 & ? &  74.9 & 17.6 &    0.452 & --1.12 &    --1.40 & High \\
+OSS 3  & 10 47 17.6 & $+$00 25 07.7 & 14.89 & 0.73 & ? &  79.2 &  3.0 &    0.213 & --1.77 &    --1.80 & High \\
+OSS 4  & 10 47 29.1 & $-$02 02 22.6 & 17.20 & 0.46 & ? &  93.2 & 29.8 & $<$0.22 & --2.82 & $<$--2.28 & High \\
+OSS 5  & 10 47 30.1 & $-$00 01 24.6 & 17.25 & 0.61 & ? &  83.5 &  3.2 &    0.123 & --1.62 &    --1.68 & High \\
+OSS 6  & 10 48 20.9 & $+$00 26 34.4 & 17.88 & 0.55 & ? & 118.8 & 11.7 &    0.467 & --1.65 &    --1.73 & High \\
+OSS 7  & 10 48 44.4 & $-$02 53 08.8 & 18.35 & 0.62 & ? & 108.1 &  9.0 &    0.183 & --1.01 &    --1.17 & High \\
+OSS 8  & 10 48 46.9 & $-$00 32 27.8 & 17.85 & 0.46 & ? & 109.3 &  8.1 &    0.324 & --2.37 & $<$--2.28 & High \\
+OSS 9  & 10 49 08.3 & $+$00 02 00.2 & 16.27 & 0.62 & ? &  81.5 &  4.6 &    0.034 & --2.70 & $<$--2.28 & High \\
+OSS 10 & 10 51 19.7 & $+$00 05 15.4 & 17.81 & 0.65 & ? &  82.6 &  5.0 &    0.198 & --1.16 &    --1.20 & High 
+\enddat
 \end{deluxetable*}
+
+%OSS 1 & 10 46 50.6 & $-$00 13 17.9 & 17.33 & 0.50  &  215.5  & 77.0 & 4.0 & 0.416 & $-1.31$ & Unlikely member! \\
+%OSS 2 & 10 47 17.6 & $+$00 25 07.7 & 16.09 &  0.73 &  215.7  & 79.2 & 3.3 & 0.212 & $-1.84$ & Highly probable member \\
+%OSS 3 & 10 47 30.1 & $-$00 01 24.6 & 17.25 &  0.61 &  221.4  & 83.6 & 3.4 & 0.123 & $-1.62$ & Highly probable member \\
+%OSS 4 & 10 49 08.3 & $+$00 02 00.2 & 16.27 &  0.62 &  218.5  & 81.5 & 4.6 & 0.034 & $-2.70$ & Possible EMP member \\
+%OSS 6 & 10 48 20.9 & $+$00 26 34.4 & 17.88 &  0.55 &  254.9  & 118.8 & 11.7 & 0.469 & $-1.79$\tablenotemark{a} & Highly probable member \\
+%OSS 7 & 10 46 29.3 & $-$00 19 38.5 & 17.77 &  0.56 &  217.3  & 78.4 & 5.2 & 0.126 & $-1.77$\tablenotemark{a} & Highly probable member
 
@@
 
-Although OSS 6 has an uncertain radial velocity, using a maximum-likelihood estimation we find the mean stream galactocentric velocity at $(l, b) = (250\,^\circ, 50\,^\circ)$ from five stars to be $V_{GSR} = 82 \pm 1.6$ km s$^{-1}$ and the intrinsic dispersion to be $0.3 \pm 3.3$ km s$^{-1}$, i.e., consistent with zero.
+Using a maximum-likelihood estimation we find the mean stream galactocentric velocity at $(l, b) = (250\,^\circ, 50\,^\circ)$ from five stars to be $V_{GSR} = 82 \pm 1.6$ km s$^{-1}$ and the intrinsic dispersion to be $0.3 \pm 3.3$ km s$^{-1}$, i.e., consistent with zero.
+If we exclude five stars with weak signal \--- and hence large velocity uncertainties \--- this dispersion is found to be $X \pm Y$\,km s$^{-1}$.
+
 For our four stars with low radial velocity errors this dispersion is found to be $0.00 \pm 2.4$ km s$^{-1}$.

### 2012-09-15 2012-oss-mrs/draft-oss-mrs.tex
Fixed small latex compilation bug
Added stream metallicity distribution text

@@
 In this letter we present a detailed, self-consistent analysis to identify K giant members of the Orphan Stream.
-Using our selection method we have catalogued the locations of X highly probable Orphan Stream candidates, all worthy of high resolution spectroscopic follow up.
+Using our selection method we have catalogued the locations of ten highly probable Orphan Stream candidates, all worthy of high resolution spectroscopic follow up.
 In the following section we outline our photometric target selection.
@@
 For these purposes we are only looking for a simple indication as to whether a star is likely a dwarf or not.
-Figure \ref{fig:ew-mg} illustrates the trend with EW$_{\lambda8807}$ against SDSS de-reddened $g \-- r$\footnote{All magnitudes presented in this letter are de-reddened}, illustrating the dominant upper dwarf branch we wish to exclude.
+Figure \ref{fig:ew-mg} illustrates the trend with EW$_{\lambda8807}$ against SDSS de-reddened\footnote{All magnitudes presented in this letter are de-reddened} $g \-- r$, illustrating the dominant upper dwarf branch we wish to exclude.
 The adopted dwarf/giant separation line is shown.
@@
 We have measured the equivalent widths of the Ca\,\textsc{II} near-infrared triplet lines for stars that meet our kinematic and surface gravity criteria.
-After correcting for luminosity, the equivalent width of the Ca\,\textsc{II} triplet lines provide a good indication of the metallicity of a RGB star \citep{Amandroff;Da_Costa_1991}.
+After correcting for luminosity, the equivalent width of the Ca\,\textsc{II} triplet lines provide a good indication of the overall metallicity of a RGB star \citep{Amandroff;Da_Costa_1991}.
 We have employed the \citet{Starkenburg;et-al_2010} relationship and corrected for luminosity in $g$ against the horizontal branch magnitude at $g_{HB}$ = 17.1 \citep{Newberg;et-al_2010}.
@@
 
-Given a distance to the Orphan Stream, we can also estimate a star's metallicity through isochrone fitting.
-We have used a 10 Gyr \citet{Girardi;et-al_2008} isochrone at 21.4\,kpc \citep{Newberg;et-al_2010} and found metallicities for all eighteen likely stream members from their best-fitting isochrone (see Figure \ref{fig:feh}).
-Derived metallicites from Ca\,\textsc{II} line strengths and isochrone fitting which are consistent (within $\pm0.3$\,dex) indiates these measurements are reliable, and that these stars are indeed at a distance of $\sim21.4$\,kpc.
-These ten highly likely stream members fall in the green shaded region illustrated in Figure \ref{fig:feh}.
-
-TODO: Overall stream metallicity
-
 \begin{figure}[h]
@@
 	\caption{Metallicities from the Ca \textsc{II} triplet lines against metallicities derived from isochrone fitting for the eighteen stars which meet our kinematic and surface gravity criteria.
-Both abundance determinations imply these stars are RGB members of the Orphan Stream at a distance of $\sim21.4$ kpc \citep{Newberg;et-al_2010}.
+Both abundance determinations imply these stars are RGB members of the Orphan Stream at a distance of $\sim21.4$\,kpc \citep{Newberg;et-al_2010}.
 Consistency between these methods indicates highly likely stream membership (green region).
@@
 
-Figure \ref{fig:cmd} illustrates all eighteen candidates which meet both our kinematic and surface gravity criteria, and our ten most likely members are marked.
-Candidates are coloured by their metallicity deduced from the Ca\,\textsc{II} triplet.
+Given a distance to the Orphan Stream, we can also estimate a star's metallicity through isochrone fitting.
+We have used a 10 Gyr \citet{Girardi;et-al_2008} isochrone at 21.4\,kpc \citep{Newberg;et-al_2010} and found metallicities for all eighteen likely stream members from their best-fitting isochrone (see Figure \ref{fig:feh}).
+Derived metallicities from Ca\,\textsc{II} line strengths and isochrone fitting which are consistent (within $\pm0.3$\,dex) indicates these measurements are reliable, and that these stars are indeed at a distance of $\sim21.4$\,kpc.
+We find ten highly likely stream members with consistently derived metallicities, and they fall within the green shaded region illustrated in Figure \ref{fig:feh}.
+
+We have adopted a final overall metallicity for each star based on the quality of our [Fe/H] measurements.
+Adopted values are tabulated in Table \ref{tab:oss-members}.
+From our ten highly likely stream members we find an overall stream metallicity of $[\mbox{Fe/H}] = -1.71$ with a dispersion of $\sigma = 0.56$ dex.
+This abundance spread is larger than typically seen in globular cluster stars and is more representative of the chemical spreads seen in dSph satellites.
+\citet{Newberg;et-al_2010} found a stream metallicity of $[\mbox{Fe/H}] = -2.1$ from BHB stars, which is not inconsistent with our measurement given the spread in Orphan Stream K-giant metallicities.
 
@@
 	\caption{Color magnitude diagram showing our observed candidates (grey).
-Observations fulfilling kinematic and gravity cuts are colored by their metallicity.
-Those with upper limits for surface gravity are marked as triangles.
-Highly probable stream members with consistent line strength- and isochrone-derived abundances are circled.
-Relevant 10 Gyr \citet{Girardi;et-al_2008} isochrones at $[\mbox{Fe/H}] = -1.5$ (dotted), $-2.0$ (dashed) at 21.4\,kpc \citep{Newberg;et-al_2010} are shown, as well as our best-fitting 10 Gyr isochrone of $[\mbox{Fe/H}] = -1.78$ at 24\,kpc (solid).}
+Observations fulfilling kinematic and gravity cuts are colored by their metallicity, and those with upper limits for surface gravity are marked as triangles ($\triangledown$).
+Highly probable stream members with consistent line strength- and isochrone-derived metallicities are circled.
+Relevant 10 Gyr \citet{Girardi;et-al_2008} isochrones at $[\mbox{Fe/H}] = -1.5$ (dotted), $-2.0$ (dashed) at 21.4\,kpc \citep{Newberg;et-al_2010} are shown, as well as our best-fitting 10 Gyr isochrone of $[\mbox{Fe/H}] = -1.71$ at YY\,kpc (solid).}
 	\label{fig:cmd}
@@
 
-\citet{Newberg;et-al_2010} found the median Orphan Stream metallicity to be [Fe/H] $= -2.1$ from BHB stars, and a distance of $21.4 \pm 1.0$\,kpc in this region.
-In Figure \ref{fig:cmd} we have overlaid 10 Gyr old isochrones from \citet{Girardi;et-al_2008} with metallicities of [Fe/H] $= -2.0$ and $-1.5$ at a distance of $21.4$ kpc \citep{Newberg;et-al_2010}.
-
-%We can ascertain abundance corrections for our stars fainter than the horizontal branch by comparing our $g - g_{HB}$ (or $V-V_{HB}$) and $EW_{\lambda8452} + EW_{\lambda8662}$ with those measured by \citet{Saviane;et-al_2012} for globular clusters.
-Only two clusters from \citet{Saviane;et-al_2012} had measured Ca \textsc{II} equivalent widths for stars fainter than the horizontal branch: NGC 6397 with $[\mbox{Fe/H}] = -1.99$ and NGC 6254 with $[\mbox{Fe/H}] = -1.57$ \citep[both abundances from][]{Carretta;et-al_2009}.
-OSS 6 and OSS 7 lie at the mid-point between these cluster stars, implying an abundance of $[\mbox{Fe/H}] \sim -1.78$, or a mean correction of $-0.14$ dex for OSS 6 and 7.
-Although OSS 3 is 0.15 magnitudes fainter than the horizontal branch, it has equivalent widths consistent with our inferred metallicity of $[\mbox{Fe/H}] = -1.62$, so no correction was made.
-With corrections included for OSS 6 and 7 we find a median stream metallicity from our four most probable stars of $[\mbox{Fe/H}] = -1.78 \pm 0.08$, which is slightly more metal-rich than the $[\mbox{Fe/H}] =-2.1$ found by \citet{Newberg;et-al_2010} from BHB stars.
-If we include our EMP candidate, the median decreases by 0.01 dex and the spread increases to 0.39\,dex.
-
-Given that our Orphan Stream stars cover a wide range along the giant branch, we are in a good position to revise the distance estimate to the stream.
-Given a 10 Gyr \citet{Girardi;et-al_2008} isochrone at $[\mbox{Fe/H}] = -1.78$, we find a best-fitting distance to the stream of 24 kpc at ($l, $b) = ($250^\circ$, $50^\circ$).
+Given that our Orphan Stream giants cover a wide evolutionary range along the giant branch (Figure \ref{fig:cmd}), we are in a good position to revise the distance estimate to the stream.
+Given a 10 Gyr \citet{Girardi;et-al_2008} isochrone at $[\mbox{Fe/H}] = -1.71$, we find a best-fitting distance to the stream of YY\,kpc at ($l, $b) = ($250^\circ$, $50^\circ$).
 This isochrone is also shown in Figure \ref{fig:cmd}, and it is clear that the four most probable member stars lie almost precisely on this isochrone.
@@
 
-\begin{deluxetable*}{lccccccccccc}
+\begin{deluxetable*}{lcccccccccccc}
 \tabletypesize{\scriptsize}
@@
 \tablehead{
-	\colhead{Star} &
 	\colhead{$\alpha$} &
@@
 	\colhead{$g \-- r$} &
-	\colhead{$V_{helio}$} &
+	\colhead{$V_{hel}$} &
 	\colhead{$V_{\textsc{gsr}}$} &
@@
 	\colhead{[Fe/H]$_{iso}$} &
+	\colhead{[Fe/H]\tablenotemark{a}} &
 	\colhead{Stream} \\
-Name & (J2000) & (J2000) & & & (kms $^{-1}$) & (km s$^{-1}$) & (km s$^{-1}$) & (\AA) & (dex) & (dex) & Probability
+(J2000) & (J2000) & & & (kms $^{-1}$) & (km s$^{-1}$) & (km s$^{-1}$) & (\AA) & (dex) & (dex) & (dex) & Prob.
 }
 \startdata
-OSS 1  & 10 46 29.3 & $-$00 19 38.5 & 16.97 & 0.56 & ? &  78.4 &  5.2 &    0.126 & --1.63 &    --1.68 & High \\
-OSS 2  & 10 47 06.1 & $-$01 56 03.9 & 17.98 & 0.54 & ? &  74.9 & 17.6 &    0.452 & --1.12 &    --1.40 & High \\
-OSS 3  & 10 47 17.6 & $+$00 25 07.7 & 14.89 & 0.73 & ? &  79.2 &  3.0 &    0.213 & --1.77 &    --1.80 & High \\
-OSS 4  & 10 47 29.1 & $-$02 02 22.6 & 17.20 & 0.46 & ? &  93.2 & 29.8 & $<$0.22 & --2.82 & $<$--2.28 & High \\
-OSS 5  & 10 47 30.1 & $-$00 01 24.6 & 17.25 & 0.61 & ? &  83.5 &  3.2 &    0.123 & --1.62 &    --1.68 & High \\
-OSS 6  & 10 48 20.9 & $+$00 26 34.4 & 17.88 & 0.55 & ? & 118.8 & 11.7 &    0.467 & --1.65 &    --1.73 & High \\
-OSS 7  & 10 48 44.4 & $-$02 53 08.8 & 18.35 & 0.62 & ? & 108.1 &  9.0 &    0.183 & --1.01 &    --1.17 & High \\
-OSS 8  & 10 48 46.9 & $-$00 32 27.8 & 17.85 & 0.46 & ? & 109.3 &  8.1 &    0.324 & --2.37 & $<$--2.28 & High \\
-OSS 9  & 10 49 08.3 & $+$00 02 00.2 & 16.27 & 0.62 & ? &  81.5 &  4.6 &    0.034 & --2.70 & $<$--2.28 & High \\
-OSS 10 & 10 51 19.7 & $+$00 05 15.4 & 17.81 & 0.65 & ? &  82.6 &  5.0 &    0.198 & --1.16 &    --1.20 & High 
-\enddat
+10 46 29.3 & $-$00 19 38.5 & 16.97 & 0.56 & ? &  78.4 &  5.2 &    0.126 & --1.63  &    --1.68 & --1.63 & High \\
+10 47 06.1 & $-$01 56 03.9 & 17.98 & 0.54 & ? &  74.9 & 17.6 &    0.452 & :--1.12\tablenotemark{b} &    --1.40 & --1.40 & High \\
+10 47 17.6 & $+$00 25 07.7 & 14.89 & 0.73 & ? &  79.2 &  3.0 &    0.213 & --1.77  &    --1.80 & --1.77 & High \\
+10 47 29.1 & $-$02 02 22.6 & 17.20 & 0.46 & ? &  93.2 & 29.8 & $<$0.22  & --2.82  & $<$--2.28 & --2.82 & High \\
+10 47 30.1 & $-$00 01 24.6 & 17.25 & 0.61 & ? &  83.5 &  3.2 &    0.123 & --1.62  &    --1.68 & --1.68 & High \\
+10 48 20.9 & $+$00 26 34.4 & 17.88 & 0.55 & ? & 118.8 & 11.7 &    0.467 & --1.65  &    --1.73 & --1.73 & High \\
+10 48 44.4 & $-$02 53 08.8 & 18.35 & 0.62 & ? & 108.1 &  9.0 &    0.183 & :--1.01\tablenotemark{b} &    --1.17 & --1.17 & High \\
+10 48 46.9 & $-$00 32 27.8 & 17.85 & 0.46 & ? & 109.3 &  8.1 &    0.324 & --2.37  & $<$--2.28 & --2.37 & High \\
+10 49 08.3 & $+$00 02 00.2 & 16.27 & 0.62 & ? &  81.5 &  4.6 &    0.034 & --2.70  & $<$--2.28 & --2.70 & High \\
+10 51 19.7 & $+$00 05 15.4 & 17.81 & 0.65 & ? &  82.6 &  5.0 &    0.198 & --1.16  &    --1.20 & --1.20 & High 
+\enddata
+\tablenotetext{a}{Final adopted [Fe/H] value based on quality of our derived metallicities.}
+\tablenotetext{b}{Sufficiently fainter than $g_{HB}$ to qualify this measurement as uncertain.}
 \end{deluxetable*}
-
-%OSS 1 & 10 46 50.6 & $-$00 13 17.9 & 17.33 & 0.50  &  215.5  & 77.0 & 4.0 & 0.416 & $-1.31$ & Unlikely member! \\
-%OSS 2 & 10 47 17.6 & $+$00 25 07.7 & 16.09 &  0.73 &  215.7  & 79.2 & 3.3 & 0.212 & $-1.84$ & Highly probable member \\
-%OSS 3 & 10 47 30.1 & $-$00 01 24.6 & 17.25 &  0.61 &  221.4  & 83.6 & 3.4 & 0.123 & $-1.62$ & Highly probable member \\
-%OSS 4 & 10 49 08.3 & $+$00 02 00.2 & 16.27 &  0.62 &  218.5  & 81.5 & 4.6 & 0.034 & $-2.70$ & Possible EMP member \\
-%OSS 6 & 10 48 20.9 & $+$00 26 34.4 & 17.88 &  0.55 &  254.9  & 118.8 & 11.7 & 0.469 & $-1.79$\tablenotemark{a} & Highly probable member \\
-%OSS 7 & 10 46 29.3 & $-$00 19 38.5 & 17.77 &  0.56 &  217.3  & 78.4 & 5.2 & 0.126 & $-1.77$\tablenotemark{a} & Highly probable member
 
@@
 Although each individual criterion is likely to induce some level contamination, their intersection reveals highly probable, self-consistent, Orphan Stream K giants.
-We deduce a stream metallicity of $[\mbox{Fe/H}] = -1.78 \pm 0.08$ which is not biased by spectral type.
-Recall that the metallicity determination was performed after kinematic and gravity cuts, and our most probable members lay perfectly on a 10 Gyr isochrone of $[\mbox{Fe/H}] = -1.78$.
-Our stream members indicate a revised distance to the stream of $24$\,kpc at $(l, b) = (250\,^\circ$, $50\,^\circ)$, slightly farther than that deduced by \citet{Newberg;et-al_2010}.
+We deduce a median stream metallicity of $[\mbox{Fe/H}] = -1.71$ which is not biased by spectral type, and find an intrinsically wide metallicity spread of $\sigma = 0.56$\,dex, indicative of a dSph origin.
+Recall that the metallicity determination was performed after kinematic and gravity cuts, and our most probable members lay perfectly on a 10 Gyr isochrone of $[\mbox{Fe/H}] = -1.71$.
+Our stream members indicate a revised distance to the stream of $YY$\,kpc at $(l, b) = (250\,^\circ$, $50\,^\circ)$, Z\,kpc slightly farther than that deduced by \citet{Newberg;et-al_2010}.
 
@@
 
-Using a maximum-likelihood estimation we find the mean stream galactocentric velocity at $(l, b) = (250\,^\circ, 50\,^\circ)$ from five stars to be $V_{GSR} = 82 \pm 1.6$ km s$^{-1}$ and the intrinsic dispersion to be $0.3 \pm 3.3$ km s$^{-1}$, i.e., consistent with zero.
-If we exclude five stars with weak signal \--- and hence large velocity uncertainties \--- this dispersion is found to be $X \pm Y$\,km s$^{-1}$.
-
-For our four stars with low radial velocity errors this dispersion is found to be $0.00 \pm 2.4$ km s$^{-1}$.
+Using a maximum-likelihood estimation we find the mean stream galactocentric velocity at $(l, b) = (250\,^\circ, 50\,^\circ)$ from five stars to be $V_{GSR} = ZZ.Z \pm Z.Z$ km s$^{-1}$ and the intrinsic dispersion to be $Z.Z \pm Z.Z$ km s$^{-1}$, i.e., consistent with zero.
+If we exclude five stars with weak signal \--- and hence large velocity uncertainties \--- this dispersion is found to be $Z \pm Z$\,km s$^{-1}$.
 These velocities indicate that the Orphan Stream is a very cold stream, and implies their motion is largely perpendicular to the line of sight.

### 2012-09-15 2012-oss-mrs/draft-oss-mrs.tex
Implemented requested changes from SCK

@@
 
-\title{Chemistry of the Orphan Stream I: Identifying Stream Members from Low Resolution Spectroscopy}
+\title{Chemistry of the Orphan Stream I: Identifying Stream Members from Low-Resolution Spectroscopy}
 
@@
 The metallicity dispersion in our stream sample is indicative that the Orphan Stream has a dSph origin.
-We find a revised stream distance of 24 kpc near the celestial equator, and our kinematic signature peaks at $V_{helio} \sim 218$\,km s$^{-1}$.
-The observed velocity dispersion of our highest probability members is consistent with arising from the velocity errors alone, indicating that, at least as regards the
+We find a revised stream distance of 24 kpc near the celestial equator, and our kinematic signature peaks at $V_{\textsc{GSR}} \sim ZZ$\,km s$^{-1}$.
+The observed velocity dispersion of our highest probability members is consistent with arising from the velocity uncertainties alone, indicating that, at least as regards the
 line-of-sight, the Orphan Stream is kinematically quite cold. We highlight likely members for high resolution spectroscopic follow-up.
@@
 This is largely to be expected given the absence of multi-band photometry in the southern sky and the low total luminosity of the stream, making it difficult to reliably seperate Orphan Stream members from halo stars.
-It is unlikely the full extent of the Orphan Stream will be established until the SkyMapper telescope \citep{Keller;et-al_2007} surveys this region.
+Further understanding the extent of the Orphan Stream awaits the SkyMapper and Pan-STARRS photometric surveys \citep{Keller;et-al_2007, Hodapp;et-al_2004}.
 
@@
 Interestingly, there are indications that  some fainter substructures like the Orphan Stream and the Palomar 5 tidal tails \citep{Odenkirchen;et-al_2009} have orbits which seem to be best-fit by Milky Way models with nearly 60\% less mass \citep{Newberg;et-al_2010} than generally reported by \citet{Xue;et-al_2008} and \citet{Koposov;et-al_2010}.
-Such a discrepancy in the mass of the Milky Way is worrying.
+Such a discrepancy in the mass of the Milky Way is troublesome.
 More complete photometric and kinematic maps of these low total luminosity streams may provide the best test as to whether this mass discrepancy is real, or an artefact of incomplete observations.
@@
 In this letter we present a detailed, self-consistent analysis to identify K giant members of the Orphan Stream.
-Using our selection method we have catalogued the locations of ten highly probable Orphan Stream candidates, all worthy of high resolution spectroscopic follow up.
+Using our selection method we have catalogued the locations of ten highly probable Orphan Stream candidates, all worthy of high-resolution spectroscopic follow up.
 In the following section we outline our photometric target selection.
-In \S\ref{sec:observations} we describe the low resolution spectroscopic observations.
+In \S\ref{sec:observations} we describe the low-resolution spectroscopic observations.
 The data analysis, including stream identification, is discussed in \S\ref{sec:analysis} and in \S\ref{sec:conclusions} the conclusions, predictions and future work are presented.
@@
 We have targeted K giant members of the Orphan Stream in order to investigate their detailed chemistry.
-Because K-giants are difficult to unambiguously detect from photometry alone, low resolution spectroscopy is required to estimate stellar parameters and determine radial velocities.
+Because K-giants are difficult to unambiguously detect from photometry alone, low-resolution spectroscopy is required to estimate stellar parameters and determine radial velocities.
 The Orphan Stream has a low spatial over-density on the order of $\sim10\%$, which makes it difficult to separate stream members from halo stars.
@@
 These two locations are unequivocally the best place to recover bright stream members.
-We have targeted two fields centered on ($\alpha$, $\delta$) = (10 48 15, 00 00 00) and (10 48 15, $-02$ 30 00), and employed a combination of colour cuts with the SDSS DR 7 \citep{Abazajian;et-al_2009} data set in order to identify likely K giants:
+We have targeted two fields centered on ($\alpha$, $\delta$) = (10:48:15, 00:00:00) and (10:48:15, $-$02:30:00), and employed a combination of colour cuts with the SDSS DR 7 \citep{Abazajian;et-al_2009} data set in order to identify likely K giants:
 \begin{eqnarray}
@@
 Observations took place on the Anglo-Astronomical Telescope using the AAOmega spectrograph in April 2009.
-AAOmega is a fibre-fed, dual beam multi-object spectrograph which is capable of simultaneously observing spectra of 400 (science and sky) targets across a $2^\circ$ field of view.
+AAOmega is a fibre-fed, dual beam multi-object spectrograph which is capable of simultaneously observing spectra of 392 (science and sky) targets across a $2^\circ$ field of view.
 We used the 5700\,{\AA} dichroic in combination with the 1000I grating in the red arm, and the 580V grating in the blue arm.
@@
 For these purposes we are only looking for a simple indication as to whether a star is likely a dwarf or not.
-Figure \ref{fig:ew-mg} illustrates the trend with EW$_{\lambda8807}$ against SDSS de-reddened\footnote{All magnitudes presented in this letter are de-reddened} $g \-- r$, illustrating the dominant upper dwarf branch we wish to exclude.
+Figure \ref{fig:ew-mg} illustrates the trend with EW$_{\lambda8807}$ against SDSS de-reddened\footnote{All magnitudes presented in this letter are de-reddened using the \citet{Schlegel;Finkbeiner;Davis_1998} dust maps.} $g \-- r$, illustrating the dominant upper dwarf branch we wish to exclude.
 The adopted dwarf/giant separation line is shown.
@@
 This fraction of giants ($\sim{}44\%$) is much larger than what would be expected given our selection criterion (e.g.
-see \citet{Casey;et-al_2012a}).
+see \citeauthor{Casey;et-al_2012} \citeyear{Casey;et-al_2012}a).
 Hence, our gravity criterion is extremely inclusive and susceptible to dwarf contamination.
@@
 
-We have presented a detailed analysis to isolate individual Orphan Stream K giants from low resolution spectroscopy using a combination of photometric, kinematic, gravity, and metallicity information.
-Although each individual criterion is likely to induce some level contamination, their intersection reveals highly probable, self-consistent, Orphan Stream K giants.
-We deduce a median stream metallicity of $[\mbox{Fe/H}] = -1.71$ which is not biased by spectral type, and find an intrinsically wide metallicity spread of $\sigma = 0.56$\,dex, indicative of a dSph origin.
+We have presented a detailed analysis to isolate individual Orphan Stream K giants from low-resolution spectroscopy using a combination of photometric, kinematic, gravity, and metallicity information.
+Although each individual criterion is likely to induce some level contamination, their intersection reveals 10 highly probable, self-consistent, Orphan Stream K giants.
+We deduce a median stream metallicity of $[\mbox{Fe/H}] = -1.71$ and find an intrinsically wide metallicity spread of $\sigma = 0.56$\,dex, indicative of a dSph origin.
+Unlike other stellar tracers, K-type giants can exist at all metallicities, hence our derived metallicity spread is likely representative of the true stream metallicity distribution function.
 Recall that the metallicity determination was performed after kinematic and gravity cuts, and our most probable members lay perfectly on a 10 Gyr isochrone of $[\mbox{Fe/H}] = -1.71$.
@@
 
-Using a maximum-likelihood estimation we find the mean stream galactocentric velocity at $(l, b) = (250\,^\circ, 50\,^\circ)$ from five stars to be $V_{GSR} = ZZ.Z \pm Z.Z$ km s$^{-1}$ and the intrinsic dispersion to be $Z.Z \pm Z.Z$ km s$^{-1}$, i.e., consistent with zero.
+Using a maximum-likelihood estimation we find the mean stream galactocentric velocity at $(l, b) = (250\,^\circ, 50\,^\circ)$ from five stars to be $V_{GSR} = ZZ.Z \pm Z.Z$ km s$^{-1}$ and the intrinsic dispersion to be $Z.Z \pm Z.Z$ km s$^{-1}$, i.e., comparable to our velocity resolution and consistent with zero.
 If we exclude five stars with weak signal \--- and hence large velocity uncertainties \--- this dispersion is found to be $Z \pm Z$\,km s$^{-1}$.
@@
 The K giants presented here can provide great insight into the chemistry, and history of the Orphan Stream.
-High resolution spectroscopic observations have been taken for our most highly probable members and a detailed chemical analysis will be presented in a forthcoming paper (Casey et al.
+High-resolution spectroscopic observations have been taken for our most highly probable members and a detailed chemical analysis will be presented in a forthcoming paper (Casey et al.
 2012c, in preparation).
 Detailed chemical abundances can help determine both the nature of the host system, and allow us to compare peculiar chemical signatures with those of the known Milky Way satellites in order to associate likely parents.
-However at least for the moment, the Orphan Stream remains appropriately named.
+However, at least for the moment, the Orphan Stream remains appropriately named.
 

### 2012-09-15 2012-oss-mrs/draft-oss-mrs.tex
Adopted final distance of 23.5 +/- 1.0 kpc

@@
 With modest S/N and independent cuts in photometry, kinematics, gravity and metallicity we yield self-consistent, highly probable stream members.
-Our data indicates an overall stream metallicity of [Fe/H] $= -1.78 \pm 0.08$ which is more metal-rich than previously found and unbiased by spectral type.
+Our data indicates an overall stream metallicity of [Fe/H] $= -1.71$ with an intrinsic dispersion of $\sigma = 0.56$\,dex which is more metal-rich than previously found and unbiased by spectral type.
 The metallicity dispersion in our stream sample is indicative that the Orphan Stream has a dSph origin.
-We find a revised stream distance of 24 kpc near the celestial equator, and our kinematic signature peaks at $V_{\textsc{GSR}} \sim ZZ$\,km s$^{-1}$.
-The observed velocity dispersion of our highest probability members is consistent with arising from the velocity uncertainties alone, indicating that, at least as regards the
-line-of-sight, the Orphan Stream is kinematically quite cold. We highlight likely members for high resolution spectroscopic follow-up.
+We find a revised stream distance of $23.5 \pm 1.0$\,kpc near the celestial equator, and our kinematic signature peaks at $V_{\textsc{GSR}} \sim ZZ$\,km s$^{-1}$.
+The observed velocity dispersion of our highest probability members is consistent with arising from the velocity uncertainties alone, indicating that, at least along the line-of-sight, the Orphan Stream is kinematically quite cold.
+We highlight likely members for high resolution spectroscopic follow-up.
 \end{abstract}
@@
 The Orphan Stream was independently detected by both \citet{Grillmair;Dionatos_2006} and \citet{Belokurov;et-al_2006}, and is distinct from other substructures in the halo.
-The stream stretches over $60\,^\circ$ in the sky, has a low surface brightness and a narrow stream width of only $\sim2^\circ$ and as the name suggests, the parent object largely remains a mystery.
+The stream stretches over $60\,^\circ$ in the sky, has a low surface brightness and a narrow stream width of only $\sim2\,^\circ$ and as the name suggests, the parent object largely remains a mystery.
 The stream extends past the celestial equator \--- outside the SDSS footprint \--- but has not been detected in existing southern surveys \citep{Newberg;et-al_2010}.
@@
 The median S/N obtained in the red arm for our fields is modest at 35 per pixel.
-With the presence of strong Ca \textsc{II} triplet lines in the red arm we are able to ascertain reliable radial velocities and reasonable estimates on overall metallicity \citep[][and references therein]{Starkenburg;et-al_2010}.
-Our spectral region also includes gravity-sensitive magnesium lines: Mg I at 8807\,{\AA}, and the Mg I\,b 3$p$-4$s$ triplet lines at $\sim$5178\,{\AA}.
+With the presence of strong Ca\,\textsc{II} triplet lines in the red arm we are able to ascertain reliable radial velocities and reasonable estimates on overall metallicity \citep[][and references therein]{Starkenburg;et-al_2010}.
+Our spectral region also includes gravity-sensitive magnesium lines: Mg\,\textsc{I} at 8807\,{\AA}, and the Mg\,\textsc{I}\,b 3$p$-4$s$ triplet lines at $\sim$5178\,{\AA}.
 As we demonstrate in the next section, these lines are sufficient to discriminate dwarfs from giants even with weak signal.
@@
 
-We have employed a combination of separate criterion to identify likely Orphan Stream members: kinematics, a giant/dwarf indication from Mg I lines, and consistent metallicities from isochrone fitting and the Ca\,\textsc{II} triplet lines.
+We have employed a combination of separate criterion to identify likely Orphan Stream members: kinematics, a giant/dwarf indication from Mg\,\textsc{I} lines, and consistent metallicities from isochrone fitting and the Ca\,\textsc{II} triplet lines.
 Each criterion is discussed here separately.
@@
 \subsection{Kinematics}
-Radial velocities were measured by cross-correlating our normalised spectra against a K-giant synthetic template with a temperature of $4500$\,K, $\log{g}$ = 1 and [Fe/H] = $-1.5$ across the range $845 \leq \lambda \leq 870$\,nm.
-Heliocentric velocities were translated to the galactic rest frame by adopting the local standard of rest velocity as 220\,km s$^{-1}$ towards $(l, b) = (53^\circ, 25^\circ)$ \citep{Kerr;Lynden-Bell_1986, Mihalas;Binney_1981}\footnote{Where $V_{\textsc{gsr}} = V_{\textsc{helio}} + 220\sin{l}\cos{b} + 16.5\times[\sin{b}\sin{25} + \cos{b}\cos{25}\cos{(l - 53)}]$}.
+Radial velocities were measured by cross-correlating our normalised spectra against a K-giant synthetic template with a temperature of 4500\,K, $\log{g}$ = 1 and $[\mbox{Fe/H}] = -1.5$ across the range $845 \leq \lambda \leq 870$\,nm.
+Heliocentric velocities were translated to the galactic rest frame by adopting the local standard of rest velocity as 220\,km s$^{-1}$ towards $(l, b) = (53\,^\circ, 25\,^\circ)$ \citep{Kerr;Lynden-Bell_1986, Mihalas;Binney_1981}\footnote{Where $V_{\textsc{gsr}} = V_{\textsc{helio}} + 220\sin{l}\cos{b} + 16.5\times[\sin{b}\sin{25} + \cos{b}\cos{25}\cos{(l - 53)}]$}.
 \citet{Newberg;et-al_2010} presented a comprehensive kinematic dataset on the Orphan Stream using BHB stars and employed a slightly different galactocentric transformation.
@@
 
-% Besan\c{c}on heliocentric velocities have been translated to a galactocentric frame in the same way as our targets.
 Figure \ref{fig:velocities} shows a histogram of our galactocentric velocities, compared to the predicted smooth line-of-sight velocity distribution for this region from the Besan\c{c}on model \citep{Robin;et-al_2003}.
@@
 To isolate potential Orphan Stream members we have nominated a relatively wide kinematic selection region between $75 \leq V_{\textsc{gsr}} \leq 135$ km s$^{-1}$, which yields 25 Orphan Stream candidates.
-The typical uncertainty in our kinematics is $\pm{}3.5$\,km s$^{-1}$, although for our fainter targets this quickly increases above $10$ km s$^{-1}$.
+The typical uncertainty in our kinematics is $\pm{}3.5$\,km s$^{-1}$, although for our fainter targets this quickly increases above 10\,km s$^{-1}$.
 
@@
 
-We have measured the equivalent widths of the gravity-sensitive Mg I line at 8807 \AA{} to distinguish dwarfs from giants \citep{Battaglia;Starkenburg_2012}.
-At a given temperature (or $g \-- r$) and metallicity, giant stars present narrower Mg I absorption lines than their dwarf contaminants.
+We have measured the equivalent widths of the gravity-sensitive Mg\,\textsc{I} line at 8807 \AA{} to distinguish dwarfs from giants \citep{Battaglia;Starkenburg_2012}.
+At a given temperature (or $g \-- r$) and metallicity, giant stars present narrower Mg\,\textsc{I} absorption lines than their dwarf contaminants.
 Given our target selection, our sample is likely to contain many more dwarfs than giants.
-In some cases no Mg I 8807 \AA{} line was apparent, so an upper limit was estimated based on the S/N.
+In some cases no Mg\,\textsc{I} 8807 \AA{} line was apparent, so an upper limit was estimated based on the S/N.
 In these cases the candidate was considered a ``non-dwarf" because we cannot exclusively rule out a metal-poor sub-giant with this criterion alone.
@@
 	\includegraphics[width=\columnwidth]{./figures/ew-mg.pdf}
-	\caption{De-reddened $g \-- r$ against the measured equivalent width of the Mg I transition at 8807 \AA{}.
+	\caption{De-reddened $g \-- r$ against the measured equivalent width of the Mg\,\textsc{I} transition at 8807 \AA{}.
 Dwarf contaminants occupy the more populous upper branch.
@@
 Both analyses were entirely consistent with each other: essentially the same candidate selection was found using both techniques.
-However, given slightly poorer signal at the Mg\,\textsc{I}\,b triplet, we were forced to adopt many more upper limits than when using the 8807 {\AA} line.
+However, given slightly poorer signal at the Mg\,\textsc{I}\,b triplet, we were forced to adopt many more upper limits than when using the 8807\,{\AA} line.
 Because we classify all upper limits as being ``non-dwarfs" (i.e.
 potential OSS giants), we deduced a slightly larger candidate sample for the Mg\,\textsc{I}\,b analysis, which was primarily populated by upper limits.
-In conclusion, we found the Mg\,\textsc{I} line at 8807{\,\AA} appeared to be a more consistent dwarf discriminant given our weak S/N \--- particularly for our fainter stars \--- and thus we have used the 8807\,{\AA} Mg \textsc{I} selection throughout the rest of our analysis.
+In conclusion, we found the Mg\,\textsc{I} line at 8807\,{\AA} appeared to be a more consistent dwarf discriminant given our weak S/N \--- particularly for our fainter stars \--- and thus we have used the 8807\,{\AA} Mg\,\textsc{I} selection throughout the rest of our analysis.
 
@@
 Highly probable stream members with consistent line strength- and isochrone-derived metallicities are circled.
-Relevant 10 Gyr \citet{Girardi;et-al_2008} isochrones at $[\mbox{Fe/H}] = -1.5$ (dotted), $-2.0$ (dashed) at 21.4\,kpc \citep{Newberg;et-al_2010} are shown, as well as our best-fitting 10 Gyr isochrone of $[\mbox{Fe/H}] = -1.71$ at YY\,kpc (solid).}
+Relevant 10 Gyr \citet{Girardi;et-al_2008} isochrones at $[\mbox{Fe/H}] = -1.5$ (dotted), $-2.0$ (dashed) at 21.4\,kpc \citep{Newberg;et-al_2010} are shown, as well as our best-fitting 10 Gyr isochrone of $[\mbox{Fe/H}] = -1.71$ at 23.5\,kpc (solid).}
 	\label{fig:cmd}
@@
 Given that our Orphan Stream giants cover a wide evolutionary range along the giant branch (Figure \ref{fig:cmd}), we are in a good position to revise the distance estimate to the stream.
-Given a 10 Gyr \citet{Girardi;et-al_2008} isochrone at $[\mbox{Fe/H}] = -1.71$, we find a best-fitting distance to the stream of YY\,kpc at ($l, $b) = ($250^\circ$, $50^\circ$).
+Given a 10\,Gyr \citet{Girardi;et-al_2008} isochrone at $[\mbox{Fe/H}] = -1.71$, we find a best-fitting distance to the stream of $23.5 \pm 1.0$\,kpc at ($l, $b) = ($250\,^\circ$, $50\,^\circ$).
 This isochrone is also shown in Figure \ref{fig:cmd}, and it is clear that the four most probable member stars lie almost precisely on this isochrone.
-Our derived distance is slightly farther than the $21.4 \pm 1.0$ kpc found by \citet{Newberg;et-al_2010}, but given the inherent uncertainties in determining distances we argue these measurements are largely in agreement.
+Our derived distance is slightly farther than the $21.4 \pm 1.0$\,kpc found by \citet{Newberg;et-al_2010}, although given the difficulty in measuring distances these values are largely in agreement.
 
@@
 Unlike other stellar tracers, K-type giants can exist at all metallicities, hence our derived metallicity spread is likely representative of the true stream metallicity distribution function.
-Recall that the metallicity determination was performed after kinematic and gravity cuts, and our most probable members lay perfectly on a 10 Gyr isochrone of $[\mbox{Fe/H}] = -1.71$.
-Our stream members indicate a revised distance to the stream of $YY$\,kpc at $(l, b) = (250\,^\circ$, $50\,^\circ)$, Z\,kpc slightly farther than that deduced by \citet{Newberg;et-al_2010}.
+Recall that the metallicity determination was performed after kinematic and gravity cuts, and our most probable members lay perfectly on a 10\,Gyr isochrone of $[\mbox{Fe/H}] = -1.71$.
+Our stream members indicate a revised distance to the stream of $23.5 \pm 1.0$\,kpc at $(l, b) = (250\,^\circ$, $50\,^\circ)$, slightly farther than that deduced by \citet{Newberg;et-al_2010}.
 
@@
 
-Using a maximum-likelihood estimation we find the mean stream galactocentric velocity at $(l, b) = (250\,^\circ, 50\,^\circ)$ from five stars to be $V_{GSR} = ZZ.Z \pm Z.Z$ km s$^{-1}$ and the intrinsic dispersion to be $Z.Z \pm Z.Z$ km s$^{-1}$, i.e., comparable to our velocity resolution and consistent with zero.
+Using a maximum-likelihood estimation we find the mean stream galactocentric velocity at $(l, b) = (250\,^\circ, 50\,^\circ)$ from five stars to be $V_{GSR} = ZZ.Z \pm Z.Z$\,km s$^{-1}$ and the intrinsic dispersion to be $Z.Z \pm Z.Z$\,km s$^{-1}$, i.e., comparable to our velocity resolution and consistent with zero.
 If we exclude five stars with weak signal \--- and hence large velocity uncertainties \--- this dispersion is found to be $Z \pm Z$\,km s$^{-1}$.

### 2012-09-16 2012-oss-mrs/draft-oss-mrs.tex
All corrections made

@@
 The metallicity dispersion in our stream sample is indicative that the Orphan Stream has a dSph origin.
-We find a revised stream distance of $23.5 \pm 1.0$\,kpc near the celestial equator, and our kinematic signature peaks at $V_{\textsc{GSR}} \sim ZZ$\,km s$^{-1}$.
+We find a revised stream distance of $23.5 \pm 1.0$\,kpc near the celestial equator, and our kinematic signature peaks at $V_{GSR} = 00.0$\,km s$^{-1}$.
 The observed velocity dispersion of our highest probability members is consistent with arising from the velocity uncertainties alone, indicating that, at least along the line-of-sight, the Orphan Stream is kinematically quite cold.
@@
 The data analysis, including stream identification, is discussed in \S\ref{sec:analysis} and in \S\ref{sec:conclusions} the conclusions, predictions and future work are presented.
+\newline
 
@@
 Radial velocities were measured by cross-correlating our normalised spectra against a K-giant synthetic template with a temperature of 4500\,K, $\log{g}$ = 1 and $[\mbox{Fe/H}] = -1.5$ across the range $845 \leq \lambda \leq 870$\,nm.
-Heliocentric velocities were translated to the galactic rest frame by adopting the local standard of rest velocity as 220\,km s$^{-1}$ towards $(l, b) = (53\,^\circ, 25\,^\circ)$ \citep{Kerr;Lynden-Bell_1986, Mihalas;Binney_1981}\footnote{Where $V_{\textsc{gsr}} = V_{\textsc{helio}} + 220\sin{l}\cos{b} + 16.5\times[\sin{b}\sin{25} + \cos{b}\cos{25}\cos{(l - 53)}]$}.
+Heliocentric velocities were translated to the galactic rest frame by adopting the local standard of rest velocity as 220\,km s$^{-1}$ towards $(l, b) = (53\,^\circ, 25\,^\circ)$ \citep{Kerr;Lynden-Bell_1986, Mihalas;Binney_1981}\footnote{Where $V_{GSR} = V_{\textsc{helio}} + 220\sin{l}\cos{b} + 16.5\times[\sin{b}\sin{25} + \cos{b}\cos{25}\cos{(l - 53)}]$}.
 \citet{Newberg;et-al_2010} presented a comprehensive kinematic dataset on the Orphan Stream using BHB stars and employed a slightly different galactocentric transformation.
 This systematic difference equates to our galactocentric rest frame velocities being on average $\sim5$\,km s$^{-1}$ lower than those of \citet{Newberg;et-al_2010}.
-
-Figure \ref{fig:velocities} shows a histogram of our galactocentric velocities, compared to the predicted smooth line-of-sight velocity distribution for this region from the Besan\c{c}on model \citep{Robin;et-al_2003}.
-We have selected predicted stars from the Besan\c{c}on model using the same criterion outlined in \S\ref{sec:target-selection} after using the \citet{Jordi;et-al_2006} colour transformations.
-It is clear that our target selection has yielded mostly nearby thick disk dwarf stars with $V_{\textsc{gsr}} \approx -120$\,km s$^{-1}$.
-The expected kinematic signature for the Orphan Stream, as \citet{Newberg;et-al_2010} reported, is labelled in Figure \ref{fig:velocities}.
-There is no sharp kinematic peak representative of the Orphan Stream exists in our sample.
-From kinematics alone, our targets appears largely indistinguishable from a smooth halo distribution.
 
@@
 
-In this region \citet{Newberg;et-al_2010} found the Orphan Stream to have $V_{\textsc{gsr}} = 110$ km s$^{-1}$ from BHB stars, approximately $105$\,km s$^{-1}$ on our scale.
-To isolate potential Orphan Stream members we have nominated a relatively wide kinematic selection region between $75 \leq V_{\textsc{gsr}} \leq 135$ km s$^{-1}$, which yields 25 Orphan Stream candidates.
+Figure \ref{fig:velocities} shows a histogram of our galactocentric velocities, compared to the predicted smooth line-of-sight velocity distribution for this region from the Besan\c{c}on model \citep{Robin;et-al_2003}.
+We have selected predicted stars from the Besan\c{c}on model using the same criterion outlined in \S\ref{sec:target-selection} after using the \citet{Jordi;et-al_2006} colour transformations.
+It is clear that our target selection has yielded mostly nearby thick disk dwarf stars with $V_{GSR} \approx -120$\,km s$^{-1}$.
+The expected kinematic signature for the Orphan Stream, as \citet{Newberg;et-al_2010} reported, is labelled in Figure \ref{fig:velocities}.
+There is no sharp kinematic peak representative of the Orphan Stream exists in our sample.
+From kinematics alone, our targets appears largely indistinguishable from a smooth halo distribution.
+
+In this region \citet{Newberg;et-al_2010} found the Orphan Stream to have $V_{GSR} = 110$ km s$^{-1}$ from BHB stars, approximately $105$\,km s$^{-1}$ on our scale.
+To isolate potential Orphan Stream members we have nominated a relatively wide kinematic selection region between $75 \leq V_{GSR} \leq 135$ km s$^{-1}$, which yields 25 Orphan Stream candidates.
 The typical uncertainty in our kinematics is $\pm{}3.5$\,km s$^{-1}$, although for our fainter targets this quickly increases above 10\,km s$^{-1}$.
@@
 Stars fainted than $g_{HB}$ will have slightly lower metallicities than predicted by our Ca\,\textsc{II}\---[Fe/H] relationship, and for these stars we will only use metallicities to assign a relative qualitative likelihood for stream membership.
-
-\begin{figure}[h]
-	\includegraphics[width=\columnwidth]{./figures/feh.pdf}
-	\caption{Metallicities from the Ca \textsc{II} triplet lines against metallicities derived from isochrone fitting for the eighteen stars which meet our kinematic and surface gravity criteria.
-Both abundance determinations imply these stars are RGB members of the Orphan Stream at a distance of $\sim21.4$\,kpc \citep{Newberg;et-al_2010}.
-Consistency between these methods indicates highly likely stream membership (green region).
-The minimum isochrone metallicity, and a representative uncertainty of 0.2\,dex for abundance measurements is shown.}
-	\label{fig:feh}
-\end{figure}
-
 Given a distance to the Orphan Stream, we can also estimate a star's metallicity through isochrone fitting.
 We have used a 10 Gyr \citet{Girardi;et-al_2008} isochrone at 21.4\,kpc \citep{Newberg;et-al_2010} and found metallicities for all eighteen likely stream members from their best-fitting isochrone (see Figure \ref{fig:feh}).
-Derived metallicities from Ca\,\textsc{II} line strengths and isochrone fitting which are consistent (within $\pm0.3$\,dex) indicates these measurements are reliable, and that these stars are indeed at a distance of $\sim21.4$\,kpc.
-We find ten highly likely stream members with consistently derived metallicities, and they fall within the green shaded region illustrated in Figure \ref{fig:feh}.
+Derived metallicities from Ca\,\textsc{II} line strengths and isochrone fitting that are consistent (within $\pm0.3$\,dex) indicates these measurements are reliable, and that these stars are indeed at a distance of $\sim21.4$\,kpc.
+We find ten highly likely stream members with consistently derived metallicities.
+They fall within the shaded region illustrated in Figure \ref{fig:feh}.
 
@@
 \citet{Newberg;et-al_2010} found a stream metallicity of $[\mbox{Fe/H}] = -2.1$ from BHB stars, which is not inconsistent with our measurement given the spread in Orphan Stream K-giant metallicities.
+
+\begin{figure}[h]
+	\includegraphics[width=\columnwidth]{./figures/feh.pdf}
+	\caption{Metallicities from the Ca\,\textsc{II} triplet lines versus those found from fitting isochrones to the eighteen stars that meet our kinematic and surface gravity criteria.
+Both abundance determinations imply these stars are RGB members of the Orphan Stream at a distance of $\sim$21.4\,kpc \citep{Newberg;et-al_2010}.
+Consistency between these methods indicates highly likely stream membership (green region).
+The minimum isochrone metallicity, and a representative uncertainty of 0.2\,dex for abundance measurements is shown.}
+	\label{fig:feh}
+\end{figure}
+
+Given that our Orphan Stream giants cover a wide evolutionary range along the giant branch (Figure \ref{fig:cmd}), we are in a good position to revise the distance estimate to the stream.
+Given a 10\,Gyr \citet{Girardi;et-al_2008} isochrone at $[\mbox{Fe/H}] = -1.71$, we find a best-fitting distance to the stream of $23.5 \pm 1.0$\,kpc at ($l, $b) = ($250\,^\circ$, $50\,^\circ$).
+This isochrone is also shown in Figure \ref{fig:cmd}, and it is clear that the four most probable member stars lie almost precisely on this isochrone.
+Our derived distance is slightly farther than the $21.4 \pm 1.0$\,kpc found by \citet{Newberg;et-al_2010}, although given the difficulty in measuring distances these values are largely in agreement.
 
@@
 
-Given that our Orphan Stream giants cover a wide evolutionary range along the giant branch (Figure \ref{fig:cmd}), we are in a good position to revise the distance estimate to the stream.
-Given a 10\,Gyr \citet{Girardi;et-al_2008} isochrone at $[\mbox{Fe/H}] = -1.71$, we find a best-fitting distance to the stream of $23.5 \pm 1.0$\,kpc at ($l, $b) = ($250\,^\circ$, $50\,^\circ$).
-This isochrone is also shown in Figure \ref{fig:cmd}, and it is clear that the four most probable member stars lie almost precisely on this isochrone.
-Our derived distance is slightly farther than the $21.4 \pm 1.0$\,kpc found by \citet{Newberg;et-al_2010}, although given the difficulty in measuring distances these values are largely in agreement.
-
-\begin{deluxetable*}{lcccccccccccc}
+\begin{deluxetable*}{ccccccccccccc}
 \tabletypesize{\scriptsize}
-\tablecaption{Identified Orphan Stream Members\label{tab:oss-members}}
+\tablecaption{Identified Orphan Stream Candidates\label{tab:oss-members}}
 \tablehead{
@@
 	\colhead{$V_{hel}$} &
-	\colhead{$V_{\textsc{gsr}}$} &
+	\colhead{$V_{GSR}$} &
 	\colhead{$V_{err}$} &
@@
 \startdata
-10 46 29.3 & $-$00 19 38.5 & 16.97 & 0.56 & ? &  78.4 &  5.2 &    0.126 & --1.63  &    --1.68 & --1.63 & High \\
-10 47 06.1 & $-$01 56 03.9 & 17.98 & 0.54 & ? &  74.9 & 17.6 &    0.452 & :--1.12\tablenotemark{b} &    --1.40 & --1.40 & High \\
-10 47 17.6 & $+$00 25 07.7 & 14.89 & 0.73 & ? &  79.2 &  3.0 &    0.213 & --1.77  &    --1.80 & --1.77 & High \\
-10 47 29.1 & $-$02 02 22.6 & 17.20 & 0.46 & ? &  93.2 & 29.8 & $<$0.22  & --2.82  & $<$--2.28 & --2.82 & High \\
-10 47 30.1 & $-$00 01 24.6 & 17.25 & 0.61 & ? &  83.5 &  3.2 &    0.123 & --1.62  &    --1.68 & --1.68 & High \\
-10 48 20.9 & $+$00 26 34.4 & 17.88 & 0.55 & ? & 118.8 & 11.7 &    0.467 & --1.65  &    --1.73 & --1.73 & High \\
-10 48 44.4 & $-$02 53 08.8 & 18.35 & 0.62 & ? & 108.1 &  9.0 &    0.183 & :--1.01\tablenotemark{b} &    --1.17 & --1.17 & High \\
-10 48 46.9 & $-$00 32 27.8 & 17.85 & 0.46 & ? & 109.3 &  8.1 &    0.324 & --2.37  & $<$--2.28 & --2.37 & High \\
-10 49 08.3 & $+$00 02 00.2 & 16.27 & 0.62 & ? &  81.5 &  4.6 &    0.034 & --2.70  & $<$--2.28 & --2.70 & High \\
-10 51 19.7 & $+$00 05 15.4 & 17.81 & 0.65 & ? &  82.6 &  5.0 &    0.198 & --1.16  &    --1.20 & --1.20 & High 
+10:46:21.9 & $+$00:43:21.8 & 17.52 & 0.50 & 209.2 &  73.3 &  9.3 & 0.273 & --1.78 &$<$--2.28& --1.78 & Low \\
+10:46:29.3 & $-$00:19:38.5 & 17.77 & 0.56 & 217.4 &  78.4 &  5.2 & 0.126 & --1.63 & --1.68  & --1.63 & High \\
+10:46:50.4 & $-$00:13:15.6 & 17.33 & 0.51 & 215.5 &  77.0 &  4.0 & 0.416 & --1.31 &$<$--2.28& --1.31 & Low \\
+10:47:06.1 & $-$01:56:03.9 & 18.74 & 0.54 & 218.4 &  74.9 & 17.6 & 0.452 &:--1.12\tablenotemark{b}& --1.40  & --1.40 & High \\
+10:47:15.0 & $-$03:15:03.9 & 18.66 & 0.54 & 256.8 & 109.5 &  9.0 &$<$0.19&:--1.85\tablenotemark{b}& --1.43  & --1.43 & Medium \\
+10:47:17.6 & $+$00:25:07.7 & 16.09 & 0.72 & 215.7 &  79.2 &  3.3 & 0.212 & --1.84 & --1.80  & --1.84 & High \\
+10:47:29.1 & $-$02:02:22.6 & 17.86 & 0.47 & 236.9 &  93.2 & 29.8 &$<$0.40& --2.82 &$<$--2.28& --2.82 & High \\
+10:47:30.1 & $-$00:01:24.5 & 17.25 & 0.61 & 221.3 &  83.6 &  3.5 & 0.123 & --1.62 & --1.68  & --1.62 & High \\
+10:48:20.9 & $+$00:26:34.4 & 17.88 & 0.55 & 254.9 & 118.9 & 11.7 & 0.467 & --1.65 & --1.73  & --1.65 & High \\
+10:48:27.8 & $+$00:55:24.0 & 17.72 & 0.51 & 259.1 & 124.5 &  6.7 & 0.182 & --1.48 &$<$--2.28& --1.48 & Low \\
+10:48:31.9 & $+$00:03:35.7 & 17.02 & 0.58 & 242.3 & 105.1 &  5.1 & 0.234 & --1.12 & --2.10  & --1.12 & Low \\
+10:48:44.4 & $-$02:53:08.8 & 18.35 & 0.62 & 253.9 & 108.2 &  9.0 & 0.183 &:--1.01\tablenotemark{b}& --1.17  & --1.17 & High \\
+10:48:46.9 & $-$00:32:27.8 & 17.85 & 0.46 & 248.2 & 109.3 &  8.1 & 0.324 & --2.37 &$<$--2.28& --2.37 & High \\
+10:49:08.3 & $+$00:02:00.2 & 16.27 & 0.62 & 218.5 &  81.5 &  4.6 & 0.034 & --2.70 &$<$--2.28& --2.70 & High \\
+10:50:13.1 & $+$00:33:52.7 & 16.13 & 0.58 & 229.7 &  94.7 &  5.1 & 0.391 & --1.54 &$<$--2.28& --1.54 & Low \\
+10:50:24.2 & $-$01:49:05.4 & 17.94 & 0.54 & 252.0 & 109.9 & 25.4 & 0.151 & --1.06 & --1.73  & --1.06 & Low \\
+10:50:33.8 & $+$00:12:19.1 & 17.82 & 0.60 & 233.5 &  97.5 &  5.9 & 0.596 & --0.90 & --1.43  & --0.90 & Medium \\
+10:51:19.7 & $+$00:05:15.5 & 17.81 & 0.65 & 218.7 &  82.7 &  5.0 & 0.198 & --1.16 & --1.20  & --1.16 & High 
 \enddata
-\tablenotetext{a}{Final adopted [Fe/H] value based on quality of our derived metallicities.}
+\tablenotetext{a}{Final adopted [Fe/H] value based on quality of two metallicity measurements.}
 \tablenotetext{b}{Sufficiently fainter than $g_{HB}$ to qualify this measurement as uncertain.}
@@
 
-Using a maximum-likelihood estimation we find the mean stream galactocentric velocity at $(l, b) = (250\,^\circ, 50\,^\circ)$ from five stars to be $V_{GSR} = ZZ.Z \pm Z.Z$\,km s$^{-1}$ and the intrinsic dispersion to be $Z.Z \pm Z.Z$\,km s$^{-1}$, i.e., comparable to our velocity resolution and consistent with zero.
-If we exclude five stars with weak signal \--- and hence large velocity uncertainties \--- this dispersion is found to be $Z \pm Z$\,km s$^{-1}$.
+Using a maximum-likelihood estimation we find the stream velocity at $(l, b) = (250\,^\circ, 50\,^\circ)$ from five stars to be $V_{GSR} = 00.0 \pm 0.0$\,km s$^{-1}$ and the intrinsic dispersion to be $0.0 \pm 0.0$\,km s$^{-1}$, i.e., comparable to our velocity resolution and consistent with zero.
+If we exclude five stars with weak signal \--- and hence large velocity uncertainties \--- this dispersion is found to be $0.0 \pm 0.0$\,km s$^{-1}$.
 These velocities indicate that the Orphan Stream is a very cold stream, and implies their motion is largely perpendicular to the line of sight.
@@
 High-resolution spectroscopic observations have been taken for our most highly probable members and a detailed chemical analysis will be presented in a forthcoming paper (Casey et al.
-2012c, in preparation).
+2012c, in prep.).
 Detailed chemical abundances can help determine both the nature of the host system, and allow us to compare peculiar chemical signatures with those of the known Milky Way satellites in order to associate likely parents.

### 2012-09-16 2012-oss-mrs/figures/cmd.py

@@ -14,7 +14,7 @@ good_candidate_oids.extend([917, 768, 76, 685, 932])
 upperlimit_candidate_oids = []
 dodgy_candidate_oid = False
 
-distance = 23.7 #kpc (my measurement)
+distance = 23.5 #kpc (my measurement)
 my_distance_modulus = 5 * np.log10(distance * 1000) - 5
 newberg_distance_modulus = 5 * np.log10(21.4 * 1000) - 5 # Newberg et al 2010 estimate distance at (l, b) = (250, 50) of 21.4 +/- 1.0 kpc
 
@@ -56,8 +56,8 @@ if dodgy_candidate_oid:
 g, r = np.loadtxt('giardi-10gyr-1.5.data', unpack=True)
 ax.plot(g - r, g + newberg_distance_modulus, 'k:', zorder=-10, label='[Fe/H] $=-1.5$ at $21.4$ kpc')
 
-g, r = np.loadtxt('giardi-10gyr-1.79.data', unpack=True)
-ax.plot(g - r, g + my_distance_modulus, 'k-', lw=2, zorder=-1, label='[Fe/H] $=-1.74$ at $24$ kpc')
+g, r = np.loadtxt('giardi-10gyr-1.71.data', unpack=True)
+ax.plot(g - r, g + my_distance_modulus, 'k-', lw=2, zorder=-1, label='[Fe/H] $=-1.71$ at $24$ kpc')
 
 g, r = np.loadtxt('giardi-10gyr-2.0.data', unpack=True)
 ax.plot(g - r, g + newberg_distance_modulus, 'k--', zorder=-10, label='[Fe/H] $=-2.0$ at $21.4$ kpc')
@@ -65,9 +65,12 @@ ax.plot(g - r, g + newberg_distance_modulus, 'k--', zorder=-10, label='[Fe/H] $=
 
 
 # Load in our candidates
-oid, g0, g, r0, ew, feh_cat, feh_iso, feh_iso_upperlimit = np.loadtxt('all-candidates.data', usecols=(0, 19, 9, 20, 5, 25, 26, 27), unpack=True)
+#oid, g0, r0, ew, feh_cat, feh_iso, feh_adpoted, feh_iso_upperlimit = np.loadtxt('all-candidates.data', usecols=(0, 19, 20, 5, 25, 26, 27, 28)
+cols = (0, 1, 2, 19, 20, 4, 3, 5, 25, 26, 27, 28)
 
[…]

### 2012-09-16 2012-oss-mrs/draft-oss-mrs.tex
Awaiting GDC velocity dispersions

@@
 
-\title{Chemistry of the Orphan Stream I: Identifying Stream Members from Low-Resolution Spectroscopy}
+\title{Chemistry of the Orphan Stream I: Identifying Stream Members \\ from Low-Resolution Spectroscopy}
 
@@
 Our data indicates an overall stream metallicity of [Fe/H] $= -1.71$ with an intrinsic dispersion of $\sigma = 0.56$\,dex which is more metal-rich than previously found and unbiased by spectral type.
-The metallicity dispersion in our stream sample is indicative that the Orphan Stream has a dSph origin.
+The metallicity dispersion in our stream sample suggests that the unidentified Orphan Stream parent is a dSph satellite.
 We find a revised stream distance of $23.5 \pm 1.0$\,kpc near the celestial equator, and our kinematic signature peaks at $V_{GSR} = 00.0$\,km s$^{-1}$.
-The observed velocity dispersion of our highest probability members is consistent with arising from the velocity uncertainties alone, indicating that, at least along the line-of-sight, the Orphan Stream is kinematically quite cold.
+The observed velocity dispersion of our highest probability members is consistent with arising from the velocity uncertainties alone, indicating that at least along the line-of-sight, the Orphan Stream is kinematically quite cold.
 We highlight likely members for high resolution spectroscopic follow-up.
@@
 The Orphan Stream was independently detected by both \citet{Grillmair;Dionatos_2006} and \citet{Belokurov;et-al_2006}, and is distinct from other substructures in the halo.
-The stream stretches over $60\,^\circ$ in the sky, has a low surface brightness and a narrow stream width of only $\sim2\,^\circ$ and as the name suggests, the parent object largely remains a mystery.
+The stream stretches over $60\,^\circ$ in the sky, has a low surface brightness and a narrow stream width of only $\sim$2\,$^\circ$ and as the name suggests, the parent object largely remains a mystery.
 The stream extends past the celestial equator \--- outside the SDSS footprint \--- but has not been detected in existing southern surveys \citep{Newberg;et-al_2010}.
@@
 In contrast, there has been relatively limited observational work on the Orphan Stream itself other than the original discovery papers \citep{Grillmair;Dionatos_2006, Belokurov;et-al_2006, Belokurov;et-al_2007} and the work of \citet{Newberg;et-al_2010}.
-This is largely to be expected given the absence of multi-band photometry in the southern sky and the low total luminosity of the stream, making it difficult to reliably seperate Orphan Stream members from halo stars.
-Further understanding the extent of the Orphan Stream awaits the SkyMapper and Pan-STARRS photometric surveys \citep{Keller;et-al_2007, Hodapp;et-al_2004}.
+This is largely to be expected given the absence of multi-band photometry in the southern sky and the low total luminosity of the stream, making it difficult to reliably separate Orphan Stream members from halo stars.
+Further understanding on the extent of the stream awaits the SkyMapper and Pan-STARRS photometric surveys \citep{Keller;et-al_2007, Hodapp;et-al_2004}.
 
-As \citet{Sales;et-al_2008} points out, there is a natural observational bias towards more massive and recent mergers like Sagittarius.
+As \citet{Sales;et-al_2008} point out, there is a natural observational bias towards more massive and recent mergers like Sagittarius.
 Consequently, the fainter end of this substructure distribution has yet to be fully recovered, or thoroughly examined.
@@
 The data analysis, including stream identification, is discussed in \S\ref{sec:analysis} and in \S\ref{sec:conclusions} the conclusions, predictions and future work are presented.
-\newline
 
@@
 Because K-giants are difficult to unambiguously detect from photometry alone, low-resolution spectroscopy is required to estimate stellar parameters and determine radial velocities.
-The Orphan Stream has a low spatial over-density on the order of $\sim10\%$, which makes it difficult to separate stream members from halo stars.
+The Orphan Stream has a low spatial over-density on the order of $\sim$10\%, which makes it difficult to separate stream members from halo stars.
 However, there is a well described distance gradient along the stream \citep{Belokurov;et-al_2007, Newberg;et-al_2010} which provides an indication on where we should focus our spectroscopic efforts.
@@
 \citet{Newberg;et-al_2010} presented a comprehensive kinematic dataset on the Orphan Stream using BHB stars and employed a slightly different galactocentric transformation.
-This systematic difference equates to our galactocentric rest frame velocities being on average $\sim5$\,km s$^{-1}$ lower than those of \citet{Newberg;et-al_2010}.
+This systematic difference equates to our galactocentric rest frame velocities being on average $\sim$5\,km s$^{-1}$ lower than those of \citet{Newberg;et-al_2010}.
 
@@
 In this region \citet{Newberg;et-al_2010} found the Orphan Stream to have $V_{GSR} = 110$ km s$^{-1}$ from BHB stars, approximately $105$\,km s$^{-1}$ on our scale.
-To isolate potential Orphan Stream members we have nominated a relatively wide kinematic selection region between $75 \leq V_{GSR} \leq 135$ km s$^{-1}$, which yields 25 Orphan Stream candidates.
-The typical uncertainty in our kinematics is $\pm{}3.5$\,km s$^{-1}$, although for our fainter targets this quickly increases above 10\,km s$^{-1}$.
+To isolate potential Orphan Stream members we have nominated a relatively wide kinematic selection region between $75 \leq V_{GSR} \leq 135$ km s$^{-1}$, which yields twenty-five Orphan Stream candidates.
+The typical uncertainty in our kinematics is $\pm{}5.0$\,km s$^{-1}$, although for our fainter targets this quickly increases above 10\,km s$^{-1}$.
 
@@
 We have measured the equivalent widths of the gravity-sensitive Mg\,\textsc{I} line at 8807 \AA{} to distinguish dwarfs from giants \citep{Battaglia;Starkenburg_2012}.
-At a given temperature (or $g \-- r$) and metallicity, giant stars present narrower Mg\,\textsc{I} absorption lines than their dwarf contaminants.
+At a given temperature (or $g - r$) and metallicity, giant stars present narrower Mg\,\textsc{I} absorption lines than their dwarf contaminants.
 Given our target selection, our sample is likely to contain many more dwarfs than giants.
@@
 For these purposes we are only looking for a simple indication as to whether a star is likely a dwarf or not.
-Figure \ref{fig:ew-mg} illustrates the trend with EW$_{\lambda8807}$ against SDSS de-reddened\footnote{All magnitudes presented in this letter are de-reddened using the \citet{Schlegel;Finkbeiner;Davis_1998} dust maps.} $g \-- r$, illustrating the dominant upper dwarf branch we wish to exclude.
+Figure \ref{fig:ew-mg} illustrates the trend with EW$_{\lambda8807}$ against SDSS de-reddened\footnote{All magnitudes presented in this letter are de-reddened using the \citet{Schlegel;Finkbeiner;Davis_1998} dust maps.} $g - r$, illustrating the dominant upper dwarf branch we wish to exclude.
 The adopted dwarf/giant separation line is shown.
@@
 	\includegraphics[width=\columnwidth]{./figures/ew-mg.pdf}
-	\caption{De-reddened $g \-- r$ against the measured equivalent width of the Mg\,\textsc{I} transition at 8807 \AA{}.
+	\caption{SDSS $g - r$ against the measured equivalent width of the Mg\,\textsc{I} transition at 8807\,\AA{}.
 Dwarf contaminants occupy the more populous upper branch.
@@
 Our dwarf/giant separation line in Figure \ref{fig:ew-mg} yields 425 potential giants.
-This fraction of giants ($\sim{}44\%$) is much larger than what would be expected given our selection criterion (e.g.
+This fraction of giants ($\sim$44\%) is much larger than what would be expected given our selection criterion (e.g.
 see \citeauthor{Casey;et-al_2012} \citeyear{Casey;et-al_2012}a).
@@
 Given a distance to the Orphan Stream, we can also estimate a star's metallicity through isochrone fitting.
-We have used a 10 Gyr \citet{Girardi;et-al_2008} isochrone at 21.4\,kpc \citep{Newberg;et-al_2010} and found metallicities for all eighteen likely stream members from their best-fitting isochrone (see Figure \ref{fig:feh}).
-Derived metallicities from Ca\,\textsc{II} line strengths and isochrone fitting that are consistent (within $\pm0.3$\,dex) indicates these measurements are reliable, and that these stars are indeed at a distance of $\sim21.4$\,kpc.
+We have used a 10\,Gyr \citet{Girardi;et-al_2008} isochrone at 21.4\,kpc \citep{Newberg;et-al_2010} and found metallicities for all eighteen likely stream members from their best-fitting isochrone (see Figure \ref{fig:feh}).
+Derived metallicities from Ca\,\textsc{II} line strengths and isochrone fitting that are consistent (within $\pm0.3$\,dex) indicates these measurements are reliable, and that these stars are indeed at a distance of $\sim$21.4\,kpc.
 We find ten highly likely stream members with consistently derived metallicities.
@@
 Highly probable stream members with consistent line strength- and isochrone-derived metallicities are circled.
-Relevant 10 Gyr \citet{Girardi;et-al_2008} isochrones at $[\mbox{Fe/H}] = -1.5$ (dotted), $-2.0$ (dashed) at 21.4\,kpc \citep{Newberg;et-al_2010} are shown, as well as our best-fitting 10 Gyr isochrone of $[\mbox{Fe/H}] = -1.71$ at 23.5\,kpc (solid).}
+Relevant 10\,Gyr \citet{Girardi;et-al_2008} isochrones at $[\mbox{Fe/H}] = -1.5$ (dotted), $-2.0$ (dashed) at 21.4\,kpc \citep{Newberg;et-al_2010} are shown, as well as our best-fitting 10\,Gyr isochrone of $[\mbox{Fe/H}] = -1.71$ at 23.5\,kpc (solid).}
 	\label{fig:cmd}
@@
 We have presented a detailed analysis to isolate individual Orphan Stream K giants from low-resolution spectroscopy using a combination of photometric, kinematic, gravity, and metallicity information.
-Although each individual criterion is likely to induce some level contamination, their intersection reveals 10 highly probable, self-consistent, Orphan Stream K giants.
+Although each individual criterion is likely to induce some level contamination, their intersection reveals ten highly probable, self-consistent, Orphan Stream K giants.
 We deduce a median stream metallicity of $[\mbox{Fe/H}] = -1.71$ and find an intrinsically wide metallicity spread of $\sigma = 0.56$\,dex, indicative of a dSph origin.
@@
 2012c, in prep.).
-Detailed chemical abundances can help determine both the nature of the host system, and allow us to compare peculiar chemical signatures with those of the known Milky Way satellites in order to associate likely parents.
+Detailed chemical abundances can help determine both the nature of the host system before it's discovered, and allows us to compare peculiar chemical signatures with those of the known Milky Way satellites in order to associate likely parents.
 However, at least for the moment, the Orphan Stream remains appropriately named.

### 2012-09-16 2012-oss-mrs/figures/cmd.py
Plots now all have the same font

@@ -1,3 +1,9 @@
+from matplotlib import rc
+rc('font',**{'family':'sans-serif','sans-serif':['Helvetica']})
+## for Palatino and other serif fonts use:
+#rc('font',**{'family':'serif','serif':['Palatino']})
+#rc('text', usetex=True)
+
 
 good_candidate_oids = [570, 169, 143, 604, 337]# 571, 76, 264]
 

### 2012-09-16 2012-oss-mrs/figures/vgsr-histogram.py

@@ -1,5 +1,12 @@
  # -*- coding: utf-8 -*-
 
+from matplotlib import rc
+rc('font',**{'family':'sans-serif','sans-serif':['Helvetica']})
+## for Palatino and other serif fonts use:
+#rc('font',**{'family':'serif','serif':['Palatino']})
+#rc('text', usetex=True)
+
+
 
 fontsize = 11
 labelsize = 11

### 2012-09-16 2012-oss-mrs/draft-oss-mrs.tex
Fixed ???? resolution to {1}-resolution

@@
 \begin{abstract}
-We present coordinates and properties of candidate K giant members in the Orphan Stream, which have been identified from low resolution spectroscopic data taken with AAOmega on the Anglo-Astronomical Telescope.
+We present coordinates and properties of candidate K giant members in the Orphan Stream, which have been identified from low-resolution spectroscopic data taken with AAOmega on the Anglo-Astronomical Telescope.
 With modest S/N and independent cuts in photometry, kinematics, gravity and metallicity we yield self-consistent, highly probable stream members.
@@
 The observed velocity dispersion of our highest probability members is consistent with arising from the velocity uncertainties alone, indicating that at least along the line-of-sight, the Orphan Stream is kinematically quite cold.
-We highlight likely members for high resolution spectroscopic follow-up.
+We highlight likely members for high-resolution spectroscopic follow-up.
 \end{abstract}

### 2012-09-19 2012-oss-mrs/Response_GDC_20120918.txt
Incorporated final GDC comments

Good morning Andy - here are what are hopefully my final comments on this paper.  Sure, it's taken a bit of too-ing and fro-ing but its a better paper for it.

Of course this version still doesn't have the couple of sentences that need to go in, probably in section 4.3, after the paragraph that ends "…fall within the shaded region illustrated in Figure 3." and before the para beginning "We have adopted…"

The text would be something like:
We have then investigated the status of these 10 stars in the PPMXL proper motion catalogue (ref), finding entries for 8 (?) of the candidates.  One star (OSS8) has a listed proper motion that is different from that of the others at the 3\sigma level [or whatever].  Consequently, we have reduced the membership likelihood  of this star from "High" to "Medium".

So then there should be 9 "High" classifications in Table 1, and the velocity measurements, etc, can note that they have been calculated for these 9 stars - removes any need discuss the fact that sigma goes down when OSS8 is excluded.  I think Table 1 should have a first column which gives an ID for the star - e.g. the OSS# we have used previously.  Saves quoting in the next paper complex ids like J1046219+004322!

OK, now specific comments.

1.  Author order.  We've never discussed this (well I don't recall any discussion) and normally I don't really care whether I am "et" or "al", but for this paper I do feel I have made quite a few contributions that have improved the science content.  So I wouldn't object to be listed second rather than third.  But you're in a better position to know whether that is appropriate or not, and I'm not going to lose any sleep over it if it remains as is.

2.  Abstract (yes, I know I'm being nit-picky again, sorry).
3rd line - you corrected Anglo, but not Astronomical as regards the telescope.  It's the Anglo-Australian Telescope.
3rd line - How about: "With modest S/N and" ==> "From modest S/N spectra and"
4th - 7th lines.  As it is now the "more metal-rich than previously found…" literally applies to the intrinsic dispersion.
I think it would be better to separate the mean and the dispersion sentences as, for example:
"Our data indicates… …stream metallicity of [Fe/H] = -1.71 +/- error, which is more metal-rich than previously found and unbiased by spectral type.  Further, the significant metallicity dispersion displayed by our probable members, 0.56 dex, suggests that the unidentified Orphan Stream parent was a dSph satellite."
(note that the error in the mean metallicity could simply be 0.56/sqrt(9) = 0.19, i.e., standard error of the mean.  But we definitely need to give some number for the uncertainty in the mean metallicity).
9th-10th lines.  The 0.2 +/- 3.1 kms-1 number is the estimate of the intrinsic velocity dispersion, not the observed dispersion.  I think you could drop the number and just say "The observed velocity dispersion….  is consistent with arising from the velocity uncertainties alone."
11th line "This is indicative" ==> "This indicates".

3.  Discussion at the end of 4.3.  You have "…it is clear that the four most probable members lie almost precisely on this isochrone".  I think this is a left-over from the previous approach.  We now have 9 most probable members and only a subset are precisely on this isochrone - the more metal-poorer and more metal-richer aren't.  So this bit needs slight revision - something like with this mean metallicity and adopted distance, 4 of the 9 stars are on the isochrone.  Or may drop it altogether?  Similarly the bit in Section 5 "our most probable members lay perfectly on a 10 Gys isochrone of [Fe/H] = -1.71" needs either revision or dropping.

4. Other minor things.
5 lines up from para starting "In this letter", right hand column page 1.  "full spatial extent of the stream" ==> "full spatial extent of the Orphan Stream"
2nd line, left column page 3.  "criterion outlined" ==> "criterion as outlined"
7th line, same place.  "There is no sharp kinematic" ==> "There is no obvious sharp kinematic"
next line - ditch "exists" - not required.
2nd last line before 4.2.  Change "kinematics" to "velocities"
1st line of 4.2 "widths" ==> "width"  (the line has only one width).
Second paragraph of Section 5.  You have two sentences both starting "If the…".  I suggest that maybe we could just drop the second one - i.e. simply remove the sentence "If the stream density… …Stripe 1540 field".  Reason - well it doesn't actually contain much information, and is largely implicit in what's said in the previous sentence.
Third para of Section 5. - again there's confusion between the intrinsic dispersion (i.e. with the contribution from the errors removed) and the observed dispersion, which contains the contribution from the velocity errors.  So I would suggest you use "intrinsic dispersion" for the 0.2 +/- 3.1 kms-1 [or whatever figure finally goes here] and drop the "i.e. comparable to our velocity resolution".  Or say that the observed dispersion is dominated by the velocity errors, indicating that the intrinsic dispersion is small.

Finally, if it doesn't kill us for space, can we add in the acknowledgements:
"GDaC is also grateful for the support received during an extended visit to the Institute of Astronomy, University of Cambridge, during which this work was completed."
(I'd like to acknowledge the support I have received here and this paper has the best combination of work I've done here and likelihood of being published on a reasonable timescale).

Cheers,
Gary

### 2012-09-19 2012-oss-mrs/draft-oss-mrs.tex
Incorporated final GDC comments

@@
 \documentclass{emulateapj}
-
 \usepackage{amssymb} % for resolution symbol
@@
 
-\author{Andrew R. Casey\altaffilmark{1,2}, Stefan C. Keller\altaffilmark{1}, Gary Da Costa\altaffilmark{1}, Elizabeth Maunder\altaffilmark{1}}
+\author{Andrew R. Casey\altaffilmark{1,2}, Gary Da Costa\altaffilmark{1}, Stefan C. Keller\altaffilmark{1}, Elizabeth Maunder\altaffilmark{1}}
 \altaffiltext{1}{Research School of Astronomy \& Astrophysics, Australian National University, Mount Stromlo Observatory, via Cotter Rd, Weston, ACT 2611, Australia; \email{acasey@mso.anu.edu.au}}
-\altaffiltext{2}{Massachusetts Institute of Technology, Kavli Institute for Astrophysics and Space Research,
-77 Massachusetts Avenue, Cambridge, MA 02139, USA}
+\altaffiltext{2}{Kavli Institute for Astrophysics and Space Research, Massachusetts Institute of Technology, 77 Massachusetts Avenue, Cambridge, MA 02139, USA}
 
 \begin{abstract}
-We present coordinates and properties of candidate K giant members in the Orphan Stream, which have been identified from low-resolution spectroscopic data taken with AAOmega on the Anglo-Astronomical Telescope.
-With modest S/N and independent cuts in photometry, kinematics, gravity and metallicity we yield self-consistent, highly probable stream members.
-Our data indicates an overall stream metallicity of [Fe/H] $= -1.71$ with an intrinsic dispersion of $\sigma = 0.56$\,dex which is more metal-rich than previously found and unbiased by spectral type.
-The metallicity dispersion in our stream sample suggests that the unidentified Orphan Stream parent is a dSph satellite.
-We find a revised stream distance of $23.5 \pm 1.0$\,kpc near the celestial equator, and our kinematic signature peaks at $V_{GSR} = 00.0$\,km s$^{-1}$.
-The observed velocity dispersion of our highest probability members is consistent with arising from the velocity uncertainties alone, indicating that at least along the line-of-sight, the Orphan Stream is kinematically quite cold.
+We present coordinates and properties of candidate K giant members in the Orphan Stream, which have been identified from low-resolution spectroscopic data taken with AAOmega on the Anglo-Australian Telescope.
+From modest S/N spectra and independent cuts in photometry, kinematics, gravity and metallicity we yield self-consistent, highly probable stream members.
+We find a revised stream distance of $22.5\,\pm\,1.0$\,kpc near the celestial equator, and our kinematic signature peaks at $V_{GSR} = 82.1\,\pm\,1.4$\,km s$^{-1}$.
+The observed velocity dispersion of our most probable members is consistent with arising from the velocity uncertainties alone.
+This indicates that at least along the line-of-sight, the Orphan Stream is kinematically quite cold.
+Our data indicates an overall stream metallicity of [Fe/H] $= -1.63\,\pm\,0.19$\,dex which is more metal-rich than previously found and unbiased by spectral type.
+Furthermore, the significant metallicity dispersion displayed by our probable members, $\sigma = 0.56$\,dex, suggests that the unidentified Orphan Stream parent was a dSph satellite.
 We highlight likely members for high-resolution spectroscopic follow-up.
@@
 Stars which were once gravitationally bound to the satellite are left behind in a stream of stars.
-Stream kinematics are sensitive to the shape of the galactic potential, allowing us to constrain the Milky Way potential, and reconstruct the formation history of the Milky Way.
+Stream kinematics are sensitive to the shape of the galactic potential, allowing us to constrain the Milky Way potential, and reconstruct the formation history of the Galaxy.
 The level of accreted substructure in the Milky Way has only recently become apparent through multi-band photometric surveys like the Sloan Digital Sky Survey (SDSS).
@@
 More complete photometric and kinematic maps of these low total luminosity streams may provide the best test as to whether this mass discrepancy is real, or an artefact of incomplete observations.
-Whilst the full spatial extent of the stream remains incomplete, we can examine the detailed chemistry of its members and investigate the stream history, as well as make predictions about the nature of the host system.
+Whilst the full spatial extent of the Orphan Stream remains incomplete, we can examine the detailed chemistry of its members and investigate the stream history, as well as make predictions about the nature of the host system.
 
 In this letter we present a detailed, self-consistent analysis to identify K giant members of the Orphan Stream.
-Using our selection method we have catalogued the locations of ten highly probable Orphan Stream candidates, all worthy of high-resolution spectroscopic follow up.
+Using our selection method we have catalogued the locations of nine highly probable Orphan Stream candidates, all worthy of high-resolution spectroscopic follow up.
 In the following section we outline our photometric target selection.
@@
 These two locations are unequivocally the best place to recover bright stream members.
-We have targeted two fields centered on ($\alpha$, $\delta$) = (10:48:15, 00:00:00) and (10:48:15, $-$02:30:00), and employed a combination of colour cuts with the SDSS DR 7 \citep{Abazajian;et-al_2009} data set in order to identify likely K giants:
+We have targeted two fields centered on $(\alpha, \delta) =$ (10:48:15, 00:00:00) and (10:48:15, $-$02:30:00), and employed a combination of colour cuts with the SDSS DR 7 \citep{Abazajian;et-al_2009} data set in order to identify likely K giants:
 \begin{eqnarray}
@@
 
-Observations took place on the Anglo-Astronomical Telescope using the AAOmega spectrograph in April 2009.
-AAOmega is a fibre-fed, dual beam multi-object spectrograph which is capable of simultaneously observing spectra of 392 (science and sky) targets across a $2^\circ$ field of view.
+Observations took place on the Anglo-Australian Telescope using the AAOmega spectrograph in April 2009.
+AAOmega is a fibre-fed, dual beam multi-object spectrograph which is capable of simultaneously observing spectra of 392 (science and sky) targets across a $2\,^\circ$ field of view.
 We used the 5700\,{\AA} dichroic in combination with the 1000I grating in the red arm, and the 580V grating in the blue arm.
@@
 Figure \ref{fig:velocities} shows a histogram of our galactocentric velocities, compared to the predicted smooth line-of-sight velocity distribution for this region from the Besan\c{c}on model \citep{Robin;et-al_2003}.
-We have selected predicted stars from the Besan\c{c}on model using the same criterion outlined in \S\ref{sec:target-selection} after using the \citet{Jordi;et-al_2006} colour transformations.
+We have selected predicted stars from the Besan\c{c}on model using the same criterion as outlined in \S\ref{sec:target-selection} after using the \citet{Jordi;et-al_2006} colour transformations.
 It is clear that our target selection has yielded mostly nearby thick disk dwarf stars with $V_{GSR} \approx -120$\,km s$^{-1}$.
 The expected kinematic signature for the Orphan Stream, as \citet{Newberg;et-al_2010} reported, is labelled in Figure \ref{fig:velocities}.
-There is no sharp kinematic peak representative of the Orphan Stream exists in our sample.
+There is no obvious sharp kinematic peak representative of the Orphan Stream in our sample.
 From kinematics alone, our targets appears largely indistinguishable from a smooth halo distribution.
@@
 To isolate potential Orphan Stream members we have nominated a relatively wide kinematic selection region between $75 \leq V_{GSR} \leq 135$ km s$^{-1}$, which yields twenty-five Orphan Stream candidates.
-The typical uncertainty in our kinematics is $\pm{}5.0$\,km s$^{-1}$, although for our fainter targets this quickly increases above 10\,km s$^{-1}$.
+The typical uncertainty in our velocities is $\pm{}5.0$\,km s$^{-1}$, although for our fainter targets this quickly increases above 10\,km s$^{-1}$.
 
@@
 
-We have measured the equivalent widths of the gravity-sensitive Mg\,\textsc{I} line at 8807 \AA{} to distinguish dwarfs from giants \citep{Battaglia;Starkenburg_2012}.
+We have measured the equivalent width of the gravity-sensitive Mg\,\textsc{I} line at 8807 \AA{} to distinguish dwarfs from giants \citep{Battaglia;Starkenburg_2012}.
 At a given temperature (or $g - r$) and metallicity, giant stars present narrower Mg\,\textsc{I} absorption lines than their dwarf contaminants.
@@
 Given a distance to the Orphan Stream, we can also estimate a star's metallicity through isochrone fitting.
-We have used a 10\,Gyr \citet{Girardi;et-al_2008} isochrone at 21.4\,kpc \citep{Newberg;et-al_2010} and found metallicities for all eighteen likely stream members from their best-fitting isochrone (see Figure \ref{fig:feh}).
+We have used a 10\,Gyr \citet{Girardi;et-al_2008} isochrone at 21.4\,kpc \citep{Newberg;et-al_2010} and found metallicities for all eighteen likely stream members from their best-fitting isochrone.
 Derived metallicities from Ca\,\textsc{II} line strengths and isochrone fitting that are consistent (within $\pm0.3$\,dex) indicates these measurements are reliable, and that these stars are indeed at a distance of $\sim$21.4\,kpc.
@@
 
+We have then investigated the status of these ten stars in the PPMXL proper motion catalogue \citep{Roeser;et-al_2010}, finding entries for nine of the candidates.
+One star (OSS-9 in Table \ref{tab:oss-members}) has a listed proper motion that is different from that of the others at the $6\,\sigma$ level.
+Consequently, we have reduced the membership likelihood of this star from ``High" to ``Medium".
+
 We have adopted a final overall metallicity for each star based on the quality of our [Fe/H] measurements.
 Adopted values are tabulated in Table \ref{tab:oss-members}.
-From our ten highly likely stream members we find an overall stream metallicity of $[\mbox{Fe/H}] = -1.71$ with a dispersion of $\sigma = 0.56$ dex.
+From our nine highly likely stream members we find an overall stream metallicity of $[\mbox{Fe/H}] = -1.63$ with a dispersion of $\sigma = 0.56$ dex.
 This abundance spread is larger than typically seen in globular cluster stars and is more representative of the chemical spreads seen in dSph satellites.
@@
 Consistency between these methods indicates highly likely stream membership (green region).
-The minimum isochrone metallicity, and a representative uncertainty of 0.2\,dex for abundance measurements is shown.}
+The minimum isochrone [Fe/H], and a representative uncertainty of 0.2\,dex for abundance measurements is shown.}
 	\label{fig:feh}
@@
 Given that our Orphan Stream giants cover a wide evolutionary range along the giant branch (Figure \ref{fig:cmd}), we are in a good position to revise the distance estimate to the stream.
-Given a 10\,Gyr \citet{Girardi;et-al_2008} isochrone at $[\mbox{Fe/H}] = -1.71$, we find a best-fitting distance to the stream of $23.5 \pm 1.0$\,kpc at ($l, $b) = ($250\,^\circ$, $50\,^\circ$).
-This isochrone is also shown in Figure \ref{fig:cmd}, and it is clear that the four most probable member stars lie almost precisely on this isochrone.
-Our derived distance is slightly farther than the $21.4 \pm 1.0$\,kpc found by \citet{Newberg;et-al_2010}, although given the difficulty in measuring distances these values are largely in agreement.
+Given a 10\,Gyr \citet{Girardi;et-al_2008} isochrone at $[\mbox{Fe/H}] = -1.63$, we find a best-fitting distance to the stream of $22.5 \pm 1.0$\,kpc at $(l, b) = (250\,^\circ,\,50\,^\circ)$.
+This isochrone is shown in Figure \ref{fig:cmd}, illustrating that three of our nine most probable member stars lie perfectly on this isochrone.
+Our derived distance is in reasonably good agreement with the $21.4 \pm 1.0$\,kpc deduced by \citet{Newberg;et-al_2010}.
 
@@
 Observations fulfilling kinematic and gravity cuts are colored by their metallicity, and those with upper limits for surface gravity are marked as triangles ($\triangledown$).
-Highly probable stream members with consistent line strength- and isochrone-derived metallicities are circled.
-Relevant 10\,Gyr \citet{Girardi;et-al_2008} isochrones at $[\mbox{Fe/H}] = -1.5$ (dotted), $-2.0$ (dashed) at 21.4\,kpc \citep{Newberg;et-al_2010} are shown, as well as our best-fitting 10\,Gyr isochrone of $[\mbox{Fe/H}] = -1.71$ at 23.5\,kpc (solid).}
+Highly probable stream members (see text) are circled.
+Relevant 10\,Gyr \citet{Girardi;et-al_2008} isochrones at $[\mbox{Fe/H}] = -1.5$ (dotted), $-2.0$ (dashed) at 21.4\,kpc \citep{Newberg;et-al_2010} are shown, as well as our best-fitting 10\,Gyr isochrone of $[\mbox{Fe/H}] = -1.63$ at 22.5\,kpc (solid).}
 	\label{fig:cmd}
 \end{figure}
-
-\begin{deluxetable*}{ccccccccccccc}
-\tabletypesize{\scriptsize}
-\tablecaption{Identified Orphan Stream Candidates\label{tab:oss-members}}
-\tablehead{
-	\colhead{$\alpha$} &
-	\colhead{$\delta$} &
-	\colhead{$g$} &
-	\colhead{$g \-- r$} &
-	\colhead{$V_{hel}$} &
-	\colhead{$V_{GSR}$} &
-	\colhead{$V_{err}$} &
-	\colhead{$EW_{\lambda8807}$} &
-	\colhead{[Fe/H]$_{Ca}$} &
-	\colhead{[Fe/H]$_{iso}$} &
-	\colhead{[Fe/H]\tablenotemark{a}} &
-	\colhead{Stream} \\
-(J2000) & (J2000) & & & (kms $^{-1}$) & (km s$^{-1}$) & (km s$^{-1}$) & (\AA) & (dex) & (dex) & (dex) & Prob.
-}
-\startdata
-10:46:21.9 & $+$00:43:21.8 & 17.52 & 0.50 & 209.2 &  73.3 &  9.3 & 0.273 & --1.78 &$<$--2.28& --1.78 & Low \\
-10:46:29.3 & $-$00:19:38.5 & 17.77 & 0.56 & 217.4 &  78.4 &  5.2 & 0.126 & --1.63 & --1.68  & --1.63 & High \\
-10:46:50.4 & $-$00:13:15.6 & 17.33 & 0.51 & 215.5 &  77.0 &  4.0 & 0.416 & --1.31 &$<$--2.28& --1.31 & Low \\
-10:47:06.1 & $-$01:56:03.9 & 18.74 & 0.54 & 218.4 &  74.9 & 17.6 & 0.452 &:--1.12\tablenotemark{b}& --1.40  & --1.40 & High \\
-10:47:15.0 & $-$03:15:03.9 & 18.66 & 0.54 & 256.8 & 109.5 &  9.0 &$<$0.19&:--1.85\tablenotemark{b}& --1.43  & --1.43 & Medium \\
-10:47:17.6 & $+$00:25:07.7 & 16.09 & 0.72 & 215.7 &  79.2 &  3.3 & 0.212 & --1.84 & --1.80  & --1.84 & High \\
-10:47:29.1 & $-$02:02:22.6 & 17.86 & 0.47 & 236.9 &  93.2 & 29.8 &$<$0.40& --2.82 &$<$--2.28& --2.82 & High \\
-10:47:30.1 & $-$00:01:24.5 & 17.25 & 0.61 & 221.3 &  83.6 &  3.5 & 0.123 & --1.62 & --1.68  & --1.62 & High \\
-10:48:20.9 & $+$00:26:34.4 & 17.88 & 0.55 & 254.9 & 118.9 & 11.7 & 0.467 & --1.65 & --1.73  & --1.65 & High \\
-10:48:27.8 & $+$00:55:24.0 & 17.72 & 0.51 & 259.1 & 124.5 &  6.7 & 0.182 & --1.48 &$<$--2.28& --1.48 & Low \\
-10:48:31.9 & $+$00:03:35.7 & 17.02 & 0.58 & 242.3 & 105.1 &  5.1 & 0.234 & --1.12 & --2.10  & --1.12 & Low \\
-10:48:44.4 & $-$02:53:08.8 & 18.35 & 0.62 & 253.9 & 108.2 &  9.0 & 0.183 &:--1.01\tablenotemark{b}& --1.17  & --1.17 & High \\
-10:48:46.9 & $-$00:32:27.8 & 17.85 & 0.46 & 248.2 & 109.3 &  8.1 & 0.324 & --2.37 &$<$--2.28& --2.37 & High \\
-10:49:08.3 & $+$00:02:00.2 & 16.27 & 0.62 & 218.5 &  81.5 &  4.6 & 0.034 & --2.70 &$<$--2.28& --2.70 & High \\
-10:50:13.1 & $+$00:33:52.7 & 16.13 & 0.58 & 229.7 &  94.7 &  5.1 & 0.391 & --1.54 &$<$--2.28& --1.54 & Low \\
-10:50:24.2 & $-$01:49:05.4 & 17.94 & 0.54 & 252.0 & 109.9 & 25.4 & 0.151 & --1.06 & --1.73  & --1.06 & Low \\
-10:50:33.8 & $+$00:12:19.1 & 17.82 & 0.60 & 233.5 &  97.5 &  5.9 & 0.596 & --0.90 & --1.43  & --0.90 & Medium \\
-10:51:19.7 & $+$00:05:15.5 & 17.81 & 0.65 & 218.7 &  82.7 &  5.0 & 0.198 & --1.16 & --1.20  & --1.16 & High 
-\enddata
-\tablenotetext{a}{Final adopted [Fe/H] value based on quality of two metallicity measurements.}
-\tablenotetext{b}{Sufficiently fainter than $g_{HB}$ to qualify this measurement as uncertain.}
-\end{deluxetable*}
 
@@
 
-We have presented a detailed analysis to isolate individual Orphan Stream K giants from low-resolution spectroscopy using a combination of photometric, kinematic, gravity, and metallicity information.
-Although each individual criterion is likely to induce some level contamination, their intersection reveals ten highly probable, self-consistent, Orphan Stream K giants.
-We deduce a median stream metallicity of $[\mbox{Fe/H}] = -1.71$ and find an intrinsically wide metallicity spread of $\sigma = 0.56$\,dex, indicative of a dSph origin.
+We have presented a detailed analysis to isolate individual Orphan Stream K giants from low-resolution spectroscopy using a combination of photometric, kinematic, gravity, metallicity, and proper motion information.
+Although each individual criterion is likely to induce some level contamination, their intersection reveals nine highly probable, self-consistent, Orphan Stream K giants.
+We deduce a median stream metallicity of $[\mbox{Fe/H}] = -1.63 \pm 0.19$ and find an intrinsically wide metallicity spread of $\sigma = 0.56$\,dex, indicative of a dSph origin.
 Unlike other stellar tracers, K-type giants can exist at all metallicities, hence our derived metallicity spread is likely representative of the true stream metallicity distribution function.
-Recall that the metallicity determination was performed after kinematic and gravity cuts, and our most probable members lay perfectly on a 10\,Gyr isochrone of $[\mbox{Fe/H}] = -1.71$.
-Our stream members indicate a revised distance to the stream of $23.5 \pm 1.0$\,kpc at $(l, b) = (250\,^\circ$, $50\,^\circ)$, slightly farther than that deduced by \citet{Newberg;et-al_2010}.
+Recall that the metallicity determination was performed after kinematic and gravity cuts, and three of our most probable members lay perfectly on a 10\,Gyr isochrone of $[\mbox{Fe/H}] = -1.63$.
+Our stream members indicate a distance to the stream of $22.5 \pm 1.0$\,kpc at $(l, b) = (250\,^\circ,\,50\,^\circ)$, in agreement with that deduced by \citet{Newberg;et-al_2010}.
 
-If the Orphan Stream continues through SEGUE Stripe 1540 at $(l, b) = (271\,^\circ$, $38\,^\circ)$ as \citet{Newberg;et-al_2010} found, then the stream is even closer there than in the region analysed here.
-Thus, if our observations and analyses are repeated at $(271\,^\circ$, $38\,^\circ)$, we predict K giant stream members of brighter apparent magnitude will be recovered.
-If the stream density is similar to or higher than what we observe at $(l, b) = (250\,^\circ, 50\,^\circ)$ then more K giant Orphan Stream members are likely to be recovered in the Stripe 1540 field.
+If the Orphan Stream continues through SEGUE Stripe 1540 at $(l, b) = (271\,^\circ,\,38\,^\circ)$ as \citet{Newberg;et-al_2010} found, then the stream is even closer there than in the region analysed here.
+Thus, if our observations and analyses are repeated at $(271\,^\circ,\,38\,^\circ)$, we predict K giant stream members of brighter apparent magnitude will be recovered.
 
-Using a maximum-likelihood estimation we find the stream velocity at $(l, b) = (250\,^\circ, 50\,^\circ)$ from five stars to be $V_{GSR} = 00.0 \pm 0.0$\,km s$^{-1}$ and the intrinsic dispersion to be $0.0 \pm 0.0$\,km s$^{-1}$, i.e., comparable to our velocity resolution and consistent with zero.
-If we exclude five stars with weak signal \--- and hence large velocity uncertainties \--- this dispersion is found to be $0.0 \pm 0.0$\,km s$^{-1}$.
-These velocities indicate that the Orphan Stream is a very cold stream, and implies their motion is largely perpendicular to the line of sight.
+Using a maximum-likelihood estimation we find the stream velocity at $(l, b) = (250\,^\circ, 50\,^\circ)$ from nine stars to be $V_{GSR} = 85.3 \pm 4.4$\,km s$^{-1}$ and the dispersion to be $6.5 \pm 7.0$\,km s$^{-1}$.
+If we exclude three stars with weak signal \--- and hence large ($> 10$\,km s$^{-1}$) velocity uncertainties \--- the peak occurs at $82.1 \pm 1.4$\,km s$^{-1}$ and the intrinsic dispersion is found to be $0.2\,\pm\,3.1$\,km s$^{-1}$.
+Hence, the observed stream dispersion is dominated by the velocity uncertainties, indicating that the intrinsic dispersion is small.
+Finally, these velocities indicate that the Orphan Stream is a very cold stream, and implies their motion is largely perpendicular to the line of sight.
 
 The K giants presented here can provide great insight into the chemistry, and history of the Orphan Stream.
-High-resolution spectroscopic observations have been taken for our most highly probable members and a detailed chemical analysis will be presented in a forthcoming paper (Casey et al.
-2012c, in prep.).
+High-resolution spectroscopic observations have been taken for some of our most highly probable members and a detailed chemical analysis will be presented in a forthcoming paper (Casey et al.
+2012c, in preparation).
 Detailed chemical abundances can help determine both the nature of the host system before it's discovered, and allows us to compare peculiar chemical signatures with those of the known Milky Way satellites in order to associate likely parents.
@@
 SK and GDaC acknowledge the financial support from the Australian Research Council through Discovery Programs DP0878137 and DP120101237.
+GDaC is also grateful for the support received during an extended visit to the Institute of Astronomy, University of Cambridge, during which this work was completed.
 
@@
 \bibliography{bibliography}
+
+\begin{deluxetable}{cccccrlrlcccccccc}
+\tabletypesize{\scriptsize}
+\tablecolumns{16}
+\tablewidth{0pt}
+\tablecaption{Identified Orphan Stream Candidates\label{tab:oss-members}}
+\tablehead{
+	\colhead{Star} &
+	\colhead{$\alpha$} &
+	\colhead{$\delta$} &
+	\colhead{$g$} &
+	\colhead{$g \-- r$} &
+	\multicolumn{2}{c}{$\mu_\alpha$} &
+	\multicolumn{2}{c}{$\mu_\delta$} &
+	\colhead{$V_{hel}$} &
+	\colhead{$V_{GSR}$} &
+	\colhead{$V_{err}$} &
+	\colhead{$EW_{\lambda8807}$} &
+	\colhead{[Fe/H]$_{Ca}$} &
+	\colhead{[Fe/H]$_{iso}$} &
+	\colhead{[Fe/H]\tablenotemark{a}} &
+	\colhead{Stream} \\
+Name & (J2000) & (J2000) & & & \multicolumn{2}{c}{(mas yr$^{-1}$)} &  \multicolumn{2}{c}{(mas yr$^{-1}$)} & (km s$^{-1}$) & (km s$^{-1}$) & (km s$^{-1}$) & (\AA) & (dex) & (dex) & (dex) & Prob.
+}
+\startdata
+OSS-1  & 10:46:21.9 & $+$00:43:21.8 & 17.52 & 0.50 &   4.1 &$\pm$ 4.5 &--34.0 &$\pm$ 4.5 & 209.2 &  73.3 &  9.3 & 0.273 & --1.78 &$<$--2.28& --1.78 & Low \\
+OSS-2  & 10:46:29.3 & $-$00:19:38.5 & 17.77 & 0.56 & --1.7 &$\pm$ 4.3 & --2.1 &$\pm$ 4.3 & 217.4 &  78.4 &  5.2 & 0.126 & --1.63 & --1.68  & --1.63 & High \\
+OSS-3  & 10:46:50.4 & $-$00:13:15.6 & 17.33 & 0.51 &   1.8 &$\pm$ 4.3 & --5.6 &$\pm$ 4.3 & 215.5 &  77.0 &  4.0 & 0.416 & --1.31 &$<$--2.28& --1.31 & Low \\
+OSS-4  & 10:47:06.1 & $-$01:56:03.9 & 18.74 & 0.54 & --6.3 &$\pm$ 4.9 &   4.6 &$\pm$ 4.9 & 218.4 &  74.9 & 17.6 & 0.452 &:--1.12\tablenotemark{b}& --1.40  & --1.40 & High \\
+OSS-5  & 10:47:15.0 & $-$03:15:03.9 & 18.66 & 0.54 & --8.2 &$\pm$ 5.2 &   1.7 &$\pm$ 5.2 & 256.8 & 109.5 &  9.0 &$<$0.19&:--1.85\tablenotemark{b}& --1.43  & --1.43 & Medium \\
+OSS-6  & 10:47:17.6 & $+$00:25:07.7 & 16.09 & 0.72 & --0.8 &$\pm$ 4.0 &   0.2 &$\pm$ 4.0 & 215.7 &  79.2 &  3.3 & 0.212 & --1.84 & --1.80  & --1.84 & High \\
+OSS-7  & 10:47:29.1 & $-$02:02:22.6 & 17.86 & 0.47 &\multicolumn{2}{c}{\nodata}&\multicolumn{2}{c}{\nodata}& 236.9 &  93.2 & 29.8 &$<$0.40& --2.82 &$<$--2.28& --2.82 & High \\
+OSS-8  & 10:47:30.1 & $-$00:01:24.5 & 17.25 & 0.61 & --4.0 &$\pm$ 4.2 & --5.2 &$\pm$ 4.2 & 221.3 &  83.6 &  3.5 & 0.123 & --1.62 & --1.68  & --1.62 & High \\
+OSS-9  & 10:48:20.9 & $+$00:26:34.4 & 17.88 & 0.55 & --8.1 &$\pm$ 4.3 & --5.4 &$\pm$ 4.3 & 254.9 & 118.9 & 11.7 & 0.467 & --1.65 & --1.73  & --1.65 & High \\
+OSS-10 & 10:48:27.8 & $+$00:55:24.0 & 17.72 & 0.51 &--14.4 &$\pm$ 4.6 & --5.3 &$\pm$ 4.6 & 259.1 & 124.5 &  6.7 & 0.182 & --1.48 &$<$--2.28& --1.48 & Low \\
+OSS-11 & 10:48:31.9 & $+$00:03:35.7 & 17.02 & 0.58 & --3.6 &$\pm$ 4.1 & --7.7 &$\pm$ 4.1 & 242.3 & 105.1 &  5.1 & 0.234 & --1.12 & --2.10  & --1.12 & Low \\
+OSS-12 & 10:48:44.4 & $-$02:53:08.8 & 18.35 & 0.62 & --3.4 &$\pm$ 4.7 & --1.8 &$\pm$ 4.7 & 253.9 & 108.2 &  9.0 & 0.183 &:--1.01\tablenotemark{b}& --1.17  & --1.17 & High \\
+OSS-13 & 10:48:46.9 & $-$00:32:27.8 & 17.85 & 0.46 &--28.4 &$\pm$ 4.8 &--12.3 &$\pm$ 4.8 & 248.2 & 109.3 &  8.1 & 0.324 & --2.37 &$<$--2.28& --2.37 & Medium \\
+OSS-14 & 10:49:08.3 & $+$00:02:00.2 & 16.27 & 0.62 &   4.9 &$\pm$ 4.0 & --6.0 &$\pm$ 4.0 & 218.5 &  81.5 &  4.6 & 0.034 & --2.70 &$<$--2.28& --2.70 & High \\
+OSS-15 & 10:50:13.1 & $+$00:33:52.7 & 16.13 & 0.58 & --3.4 &$\pm$ 4.0 & --7.7 &$\pm$ 4.0 & 229.7 &  94.7 &  5.1 & 0.391 & --1.54 &$<$--2.28& --1.54 & Low \\
+OSS-16 & 10:50:24.2 & $-$01:49:05.4 & 17.94 & 0.54 &   3.4 &$\pm$ 4.6 & --2.2 &$\pm$ 4.6 & 252.0 & 109.9 & 25.4 & 0.151 & --1.06 & --1.73  & --1.06 & Low \\
+OSS-17 & 10:50:33.8 & $+$00:12:19.1 & 17.82 & 0.60 & --7.4 &$\pm$ 5.0 & --3.3 &$\pm$ 5.0 & 233.5 &  97.5 &  5.9 & 0.596 & --0.90 & --1.43  & --0.90 & Medium \\
+OSS-18 & 10:51:19.7 & $+$00:05:15.5 & 17.81 & 0.65 &   4.2 &$\pm$ 4.7 &--11.8 &$\pm$ 4.7 & 218.7 &  82.7 &  5.0 & 0.198 & --1.16 & --1.20  & --1.16 & High 
+\enddata
+\tablenotetext{a}{Final adopted [Fe/H] value based on quality of two metallicity measurements.}
+\tablenotetext{b}{Sufficiently fainter than $g_{HB}$ to qualify this measurement as uncertain.}
+\end{deluxetable}
+
 \end{document}

### 2012-09-19 2012-oss-mrs/figures/cmd.py

@@ -5,7 +5,8 @@ rc('font',**{'family':'sans-serif','sans-serif':['Helvetica']})
 #rc('text', usetex=True)
 
 
-good_candidate_oids = [570, 169, 143, 604, 337]# 571, 76, 264]
+good_candidate_oids = [570, 169, 143, 337]# 571, 76, 264]
+# removed "OSS-9" or oid 604
 
 # Using isochrone consistency check
 good_candidate_oids.extend([917, 768, 76, 685, 932])
@@ -20,7 +21,7 @@ good_candidate_oids.extend([917, 768, 76, 685, 932])
 upperlimit_candidate_oids = []
 dodgy_candidate_oid = False
 
-distance = 23.5 #kpc (my measurement)
+distance = 22.5 #kpc (my measurement)
 my_distance_modulus = 5 * np.log10(distance * 1000) - 5
 newberg_distance_modulus = 5 * np.log10(21.4 * 1000) - 5 # Newberg et al 2010 estimate distance at (l, b) = (250, 50) of 21.4 +/- 1.0 kpc
 
@@ -62,7 +63,7 @@ if dodgy_candidate_oid:
 g, r = np.loadtxt('giardi-10gyr-1.5.data', unpack=True)
 ax.plot(g - r, g + newberg_distance_modulus, 'k:', zorder=-10, label='[Fe/H] $=-1.5$ at $21.4$ kpc')
 
-g, r = np.loadtxt('giardi-10gyr-1.71.data', unpack=True)
+g, r = np.loadtxt('giardi+10gyr-1.63.data', unpack=True)
 ax.plot(g - r, g + my_distance_modulus, 'k-', lw=2, zorder=-1, label='[Fe/H] $=-1.71$ at $24$ kpc')
 
 g, r = np.loadtxt('giardi-10gyr-2.0.data', unpack=True)

### 2012-09-19 2012-oss-mrs/figures/ew-mg.py

@@ -77,6 +77,6 @@ ax.plot(x, y, 'g', alpha=0.80, lw=5)
 ax.set_xlim((xlims[0], xlims[1] - 0.05))
 ax.set_ylim(ylims)
 
-ax.set_ylabel('$EW_{\lambda8807}$ [A]', fontsize=labelsize)
+ax.set_ylabel('EW$_{\lambda8807}$ [A]', fontsize=labelsize)
 ax.set_xlabel('$g - r$', fontsize=labelsize)
 plt.savefig('ew-mg.pdf')

### 2012-09-19 2012-oss-mrs/draft-oss-mrs.tex
Final version ready for distribution to SK, EM and referee

@@
 
-We have then investigated the status of these ten stars in the PPMXL proper motion catalogue \citep{Roeser;et-al_2010}, finding entries for nine of the candidates.
-One star (OSS-9 in Table \ref{tab:oss-members}) has a listed proper motion that is different from that of the others at the $6\,\sigma$ level.
+\begin{deluxetable*}{lccccccccccccc}
+\tabletypesize{\scriptsize}
+\tablecolumns{12}
+\tablewidth{0pt}
+\tablecaption{Identified Orphan Stream Candidates\label{tab:oss-members}}
+\tablehead{
+	\colhead{Star} &
+	\colhead{$\alpha$} &
+	\colhead{$\delta$} &
+	\colhead{$g$} &
+	\colhead{$g \-- r$} &
+	\colhead{$\mu_{total}$\tablenotemark{a}} &
+	\colhead{$V_{GSR}$} &
+	\colhead{$EW_{\lambda8807}$} &
+	\colhead{[Fe/H]$_{Ca}$} &
+	\colhead{[Fe/H]$_{iso}$} &
+	\colhead{[Fe/H]\tablenotemark{b}} &
+	\colhead{Stream} \\
+Name & (J2000) & (J2000) & & & (mas yr$^{-1}$) & (km s$^{-1}$) & (\AA) & (dex) & (dex) & (dex) & Prob.
+}
+\startdata
+OSS-1  & 10:46:21.9 & $+$00:43:21.8 & 17.52 & 0.50 &\phn6.1 $\pm$ 6.1 & \phn73.3 $\pm$ \phn9.3 & 0.273 & --1.78 &$<$--2.28& --1.78 & Low \\
+OSS-2  & 10:46:29.3 & $-$00:19:38.5 & 17.77 & 0.56 &\phn2.7 $\pm$ 6.1 & \phn78.4 $\pm$ \phn5.2 & 0.126 & --1.63 & --1.68  & --1.63 & High \\
+OSS-3  & 10:46:50.4 & $-$00:13:15.6 & 17.33 & 0.51 &\phn5.9 $\pm$ 6.1 & \phn77.0 $\pm$ \phn4.0 & 0.416 & --1.31 &$<$--2.28& --1.31 & Low \\
+OSS-4  & 10:47:06.1 & $-$01:56:03.9 & 18.74 & 0.54 &\phn7.8 $\pm$ 6.9 & \phn74.9 $\pm$    17.6 & 0.452 &:--1.12\tablenotemark{c}& --1.40  & --1.40 & High \\
+OSS-5  & 10:47:15.0 & $-$03:15:03.9 & 18.66 & 0.54 &\phn8.4 $\pm$ 7.4 &    109.5 $\pm$ \phn9.0 &$<$0.19&:--1.85\tablenotemark{c}& --1.43  & --1.43 & Medium \\
+OSS-6  & 10:47:17.6 & $+$00:25:07.7 & 16.09 & 0.72 &\phn0.8 $\pm$ 5.7 & \phn79.2 $\pm$ \phn3.3 & 0.212 & --1.84 & --1.80  & --1.84 & High \\
+OSS-7  & 10:47:29.1 & $-$02:02:22.6 & 17.86 & 0.47 &     \nodata      & \phn93.2 $\pm$    29.8 &$<$0.40& --2.82 &$<$--2.28& --2.82 & High \\
+OSS-8  & 10:47:30.1 & $-$00:01:24.5 & 17.25 & 0.61 &\phn6.6 $\pm$ 5.9 & \phn83.6 $\pm$ \phn3.5 & 0.123 & --1.62 & --1.68  & --1.62 & High \\
+OSS-9  & 10:48:20.9 & $+$00:26:34.4 & 17.88 & 0.55 &\phn9.7 $\pm$ 6.1 &    118.9 $\pm$    11.7 & 0.467 & --1.65 & --1.73  & --1.65 & High \\
+OSS-10 & 10:48:27.8 & $+$00:55:24.0 & 17.72 & 0.51 &   15.3 $\pm$ 6.5 &    124.5 $\pm$ \phn6.7 & 0.182 & --1.48 &$<$--2.28& --1.48 & Low \\
+OSS-11 & 10:48:31.9 & $+$00:03:35.7 & 17.02 & 0.58 &\phn8.5 $\pm$ 5.8 &    105.1 $\pm$ \phn5.1 & 0.234 & --1.12 & --2.10  & --1.12 & Low \\
+OSS-12 & 10:48:44.4 & $-$02:53:08.8 & 18.35 & 0.62 &\phn3.8 $\pm$ 6.6 &    108.2 $\pm$ \phn9.0 & 0.183 &:--1.01\tablenotemark{c}& --1.17  & --1.17 & High \\
+OSS-13 & 10:48:46.9 & $-$00:32:27.8 & 17.85 & 0.46 &   30.9 $\pm$ 6.8 &    109.3 $\pm$ \phn8.1 & 0.324 & --2.37 &$<$--2.28& --2.37 & Medium \\
+OSS-14 & 10:49:08.3 & $+$00:02:00.2 & 16.27 & 0.62 &\phn7.7 $\pm$ 5.7 & \phn81.5 $\pm$ \phn4.6 & 0.034 & --2.70 &$<$--2.28& --2.70 & High \\
+OSS-15 & 10:50:13.1 & $+$00:33:52.7 & 16.13 & 0.58 &\phn8.4 $\pm$ 5.7 & \phn94.7 $\pm$ \phn5.1 & 0.391 & --1.54 &$<$--2.28& --1.54 & Low \\
+OSS-16 & 10:50:24.2 & $-$01:49:05.4 & 17.94 & 0.54 &\phn4.0 $\pm$ 6.5 & 109.9    $\pm$    25.4 & 0.151 & --1.06 & --1.73  & --1.06 & Low \\
+OSS-17 & 10:50:33.8 & $+$00:12:19.1 & 17.82 & 0.60 &\phn8.1 $\pm$ 7.1 & \phn97.5 $\pm$ \phn5.9 & 0.596 & --0.90 & --1.43  & --0.90 & Medium \\
+OSS-18 & 10:51:19.7 & $+$00:05:15.5 & 17.81 & 0.65 &   12.5 $\pm$ 6.6 & \phn82.7 $\pm$ \phn5.0 & 0.198 & --1.16 & --1.20  & --1.16 & High 
+\enddata
+\tablenotetext{a}{Proper motions and uncertainties in $\alpha$ and $\delta$ added in quadrature.}
+\tablenotetext{b}{Final adopted [Fe/H] value based on quality of two metallicity measurements.}
+\tablenotetext{c}{Sufficiently fainter than $g_{HB}$ to qualify this measurement as uncertain.}
+\end{deluxetable*}
+
+\begin{figure}[h!]
+	\includegraphics[width=\columnwidth]{./figures/feh.pdf}
+	\caption{Metallicities from the Ca\,\textsc{II} triplet lines versus those found from fitting isochrones to the eighteen stars that meet our kinematic and surface gravity criteria.
+Both abundance determinations imply these stars are RGB members of the Orphan Stream at a distance of $\sim$21.4\,kpc \citep{Newberg;et-al_2010}.
+Consistency between these methods indicates highly likely stream membership (green region).
+The minimum isochrone [Fe/H], and a representative uncertainty of 0.2\,dex for abundance measurements is shown.}
+	\label{fig:feh}
+\end{figure}
+
+We have investigated the status of these ten stars in the PPMXL proper motion catalogue \citep{Roeser;et-al_2010}, finding entries for nine of the candidates.
+One star (OSS-13 in Table \ref{tab:oss-members}) has a listed proper motion that is different from that of the other nine members at the $6\,\sigma$ level.
 Consequently, we have reduced the membership likelihood of this star from ``High" to ``Medium".
@@
 
-\begin{figure}[h]
-	\includegraphics[width=\columnwidth]{./figures/feh.pdf}
-	\caption{Metallicities from the Ca\,\textsc{II} triplet lines versus those found from fitting isochrones to the eighteen stars that meet our kinematic and surface gravity criteria.
-Both abundance determinations imply these stars are RGB members of the Orphan Stream at a distance of $\sim$21.4\,kpc \citep{Newberg;et-al_2010}.
-Consistency between these methods indicates highly likely stream membership (green region).
-The minimum isochrone [Fe/H], and a representative uncertainty of 0.2\,dex for abundance measurements is shown.}
-	\label{fig:feh}
-\end{figure}
-
-Given that our Orphan Stream giants cover a wide evolutionary range along the giant branch (Figure \ref{fig:cmd}), we are in a good position to revise the distance estimate to the stream.
-Given a 10\,Gyr \citet{Girardi;et-al_2008} isochrone at $[\mbox{Fe/H}] = -1.63$, we find a best-fitting distance to the stream of $22.5 \pm 1.0$\,kpc at $(l, b) = (250\,^\circ,\,50\,^\circ)$.
-This isochrone is shown in Figure \ref{fig:cmd}, illustrating that three of our nine most probable member stars lie perfectly on this isochrone.
-Our derived distance is in reasonably good agreement with the $21.4 \pm 1.0$\,kpc deduced by \citet{Newberg;et-al_2010}.
-
-\begin{figure}[h]
+\begin{figure}[h!]
 	\includegraphics[width=\columnwidth]{./figures/cmd.pdf}
@@
 
-\section{Conclusion}
+Given that our Orphan Stream giants cover a wide evolutionary range along the giant branch (Figure \ref{fig:cmd}), we are in a good position to revise the distance estimate to the stream.
+Given a 10\,Gyr \citet{Girardi;et-al_2008} isochrone at $[\mbox{Fe/H}] = -1.63$, we find a best-fitting distance to the stream of $22.5 \pm 1.0$\,kpc at $(l, b) = (250\,^\circ,\,50\,^\circ)$.
+This isochrone is shown in Figure \ref{fig:cmd}, illustrating that three of our nine most probable member stars lie perfectly on this isochrone.
+Our derived distance is in reasonably good agreement with the $21.4 \pm 1.0$\,kpc deduced by \citet{Newberg;et-al_2010}.
+
+\section{Conclusions}
 \label{sec:conclusions}
@@
 
+% the final section of acknowledgements, "the University of Washington" does not show if I don't have \phn here.
+\phn
+
 \bibliographystyle{apj}
@@
 
-\begin{deluxetable}{cccccrlrlcccccccc}
-\tabletypesize{\scriptsize}
-\tablecolumns{16}
-\tablewidth{0pt}
-\tablecaption{Identified Orphan Stream Candidates\label{tab:oss-members}}
-\tablehead{
-	\colhead{Star} &
-	\colhead{$\alpha$} &
-	\colhead{$\delta$} &
-	\colhead{$g$} &
-	\colhead{$g \-- r$} &
-	\multicolumn{2}{c}{$\mu_\alpha$} &
-	\multicolumn{2}{c}{$\mu_\delta$} &
-	\colhead{$V_{hel}$} &
-	\colhead{$V_{GSR}$} &
-	\colhead{$V_{err}$} &
-	\colhead{$EW_{\lambda8807}$} &
-	\colhead{[Fe/H]$_{Ca}$} &
-	\colhead{[Fe/H]$_{iso}$} &
-	\colhead{[Fe/H]\tablenotemark{a}} &
-	\colhead{Stream} \\
-Name & (J2000) & (J2000) & & & \multicolumn{2}{c}{(mas yr$^{-1}$)} &  \multicolumn{2}{c}{(mas yr$^{-1}$)} & (km s$^{-1}$) & (km s$^{-1}$) & (km s$^{-1}$) & (\AA) & (dex) & (dex) & (dex) & Prob.
-}
-\startdata
-OSS-1  & 10:46:21.9 & $+$00:43:21.8 & 17.52 & 0.50 &   4.1 &$\pm$ 4.5 &--34.0 &$\pm$ 4.5 & 209.2 &  73.3 &  9.3 & 0.273 & --1.78 &$<$--2.28& --1.78 & Low \\
-OSS-2  & 10:46:29.3 & $-$00:19:38.5 & 17.77 & 0.56 & --1.7 &$\pm$ 4.3 & --2.1 &$\pm$ 4.3 & 217.4 &  78.4 &  5.2 & 0.126 & --1.63 & --1.68  & --1.63 & High \\
-OSS-3  & 10:46:50.4 & $-$00:13:15.6 & 17.33 & 0.51 &   1.8 &$\pm$ 4.3 & --5.6 &$\pm$ 4.3 & 215.5 &  77.0 &  4.0 & 0.416 & --1.31 &$<$--2.28& --1.31 & Low \\
-OSS-4  & 10:47:06.1 & $-$01:56:03.9 & 18.74 & 0.54 & --6.3 &$\pm$ 4.9 &   4.6 &$\pm$ 4.9 & 218.4 &  74.9 & 17.6 & 0.452 &:--1.12\tablenotemark{b}& --1.40  & --1.40 & High \\
-OSS-5  & 10:47:15.0 & $-$03:15:03.9 & 18.66 & 0.54 & --8.2 &$\pm$ 5.2 &   1.7 &$\pm$ 5.2 & 256.8 & 109.5 &  9.0 &$<$0.19&:--1.85\tablenotemark{b}& --1.43  & --1.43 & Medium \\
-OSS-6  & 10:47:17.6 & $+$00:25:07.7 & 16.09 & 0.72 & --0.8 &$\pm$ 4.0 &   0.2 &$\pm$ 4.0 & 215.7 &  79.2 &  3.3 & 0.212 & --1.84 & --1.80  & --1.84 & High \\
-OSS-7  & 10:47:29.1 & $-$02:02:22.6 & 17.86 & 0.47 &\multicolumn{2}{c}{\nodata}&\multicolumn{2}{c}{\nodata}& 236.9 &  93.2 & 29.8 &$<$0.40& --2.82 &$<$--2.28& --2.82 & High \\
-OSS-8  & 10:47:30.1 & $-$00:01:24.5 & 17.25 & 0.61 & --4.0 &$\pm$ 4.2 & --5.2 &$\pm$ 4.2 & 221.3 &  83.6 &  3.5 & 0.123 & --1.62 & --1.68  & --1.62 & High \\
-OSS-9  & 10:48:20.9 & $+$00:26:34.4 & 17.88 & 0.55 & --8.1 &$\pm$ 4.3 & --5.4 &$\pm$ 4.3 & 254.9 & 118.9 & 11.7 & 0.467 & --1.65 & --1.73  & --1.65 & High \\
-OSS-10 & 10:48:27.8 & $+$00:55:24.0 & 17.72 & 0.51 &--14.4 &$\pm$ 4.6 & --5.3 &$\pm$ 4.6 & 259.1 & 124.5 &  6.7 & 0.182 & --1.48 &$<$--2.28& --1.48 & Low \\
-OSS-11 & 10:48:31.9 & $+$00:03:35.7 & 17.02 & 0.58 & --3.6 &$\pm$ 4.1 & --7.7 &$\pm$ 4.1 & 242.3 & 105.1 &  5.1 & 0.234 & --1.12 & --2.10  & --1.12 & Low \\
-OSS-12 & 10:48:44.4 & $-$02:53:08.8 & 18.35 & 0.62 & --3.4 &$\pm$ 4.7 & --1.8 &$\pm$ 4.7 & 253.9 & 108.2 &  9.0 & 0.183 &:--1.01\tablenotemark{b}& --1.17  & --1.17 & High \\
-OSS-13 & 10:48:46.9 & $-$00:32:27.8 & 17.85 & 0.46 &--28.4 &$\pm$ 4.8 &--12.3 &$\pm$ 4.8 & 248.2 & 109.3 &  8.1 & 0.324 & --2.37 &$<$--2.28& --2.37 & Medium \\
-OSS-14 & 10:49:08.3 & $+$00:02:00.2 & 16.27 & 0.62 &   4.9 &$\pm$ 4.0 & --6.0 &$\pm$ 4.0 & 218.5 &  81.5 &  4.6 & 0.034 & --2.70 &$<$--2.28& --2.70 & High \\
-OSS-15 & 10:50:13.1 & $+$00:33:52.7 & 16.13 & 0.58 & --3.4 &$\pm$ 4.0 & --7.7 &$\pm$ 4.0 & 229.7 &  94.7 &  5.1 & 0.391 & --1.54 &$<$--2.28& --1.54 & Low \\
-OSS-16 & 10:50:24.2 & $-$01:49:05.4 & 17.94 & 0.54 &   3.4 &$\pm$ 4.6 & --2.2 &$\pm$ 4.6 & 252.0 & 109.9 & 25.4 & 0.151 & --1.06 & --1.73  & --1.06 & Low \\
-OSS-17 & 10:50:33.8 & $+$00:12:19.1 & 17.82 & 0.60 & --7.4 &$\pm$ 5.0 & --3.3 &$\pm$ 5.0 & 233.5 &  97.5 &  5.9 & 0.596 & --0.90 & --1.43  & --0.90 & Medium \\
-OSS-18 & 10:51:19.7 & $+$00:05:15.5 & 17.81 & 0.65 &   4.2 &$\pm$ 4.7 &--11.8 &$\pm$ 4.7 & 218.7 &  82.7 &  5.0 & 0.198 & --1.16 & --1.20  & --1.16 & High 
-\enddata
-\tablenotetext{a}{Final adopted [Fe/H] value based on quality of two metallicity measurements.}
-\tablenotetext{b}{Sufficiently fainter than $g_{HB}$ to qualify this measurement as uncertain.}
-\end{deluxetable}
-
 \end{document}

### 2012-09-19 2012-oss-mrs/Response_GDC_20120918.txt
Response to GDC

@@
-Good morning Andy - here are what are hopefully my final comments on this paper.  Sure, it's taken a bit of too-ing and fro-ing but its a better paper for it.
+>> So I did write in-line comments to each of these, and then at some stage I rebooted and hadn't saved the comments. These comments
+>> will be brief but they have all been implemented and there is nothing controversial that has changed except that the "four most
+>> probable members" that fit on the isochrone is now actually three! members because that high proper-motion one was near the base
+>> of the giant branch.
 
-Of course this version still doesn't have the couple of sentences that need to go in, probably in section 4.3, after the paragraph that ends "…fall within the shaded region illustrated in Figure 3." and before the para beginning "We have adopted…"
+Good morning Andy - here are what are hopefully my final comments on this paper.  Sure, it's taken a bit of too-ing and fro-ing but 
+its a better paper for it.
+
+Of course this version still doesn't have the couple of sentences that need to go in, probably in section 4.3, after the paragraph 
+that ends "…fall within the shaded region illustrated in Figure 3." and before the para beginning "We have adopted…"
 
 The text would be something like:
-We have then investigated the status of these 10 stars in the PPMXL proper motion catalogue (ref), finding entries for 8 (?) of the candidates.
-One star (OSS8) has a listed proper motion that is different from that of the others at the 3\sigma level [or whatever].
+We have then investigated the status of these 10 stars in the PPMXL proper motion catalogue (ref), finding entries for 8 (?) of the 
+candidates.  One star (OSS8) has a listed proper motion that is different from that of the others at the 3\sigma level [or whatever].  
 Consequently, we have reduced the membership likelihood  of this star from "High" to "Medium".
 
-So then there should be 9 "High" classifications in Table 1, and the velocity measurements, etc, can note that they have been calculated for these 9 stars - removes any need discuss the fact that sigma goes down when OSS8 is excluded.
-I think Table 1 should have a first column which gives an ID for the star - e.g.
-the OSS# we have used previously.
-Saves quoting in the next paper complex ids like J1046219+004322!
+>> Added.
+
+So then there should be 9 "High" classifications in Table 1, and the velocity measurements, etc, can note that they have been calculated 
+for these 9 stars - removes any need discuss the fact that sigma goes down when OSS8 is excluded.  I think Table 1 should have a first 
+column which gives an ID for the star - e.g. the OSS# we have used previously.  Saves quoting in the next paper complex ids like J1046219+004322!
+
+>> Done. I have had to make some adjustments to the Table to get it to fit in. Otherwise having it rotated meant an extra page, and
+>> effectively two half-pages of wasted space.
 
@@
 
-1.
-Author order.
-We've never discussed this (well I don't recall any discussion) and normally I don't really care whether I am "et" or "al", but for this paper I do feel I have made quite a few contributions that have improved the science content.
-So I wouldn't object to be listed second rather than third.
-But you're in a better position to know whether that is appropriate or not, and I'm not going to lose any sleep over it if it remains as is.
+1.  Author order.  We've never discussed this (well I don't recall any discussion) and normally I don't really care whether I am "et" or "al", 
+but for this paper I do feel I have made quite a few contributions that have improved the science content.  So I wouldn't object to be listed 
+second rather than third.  But you're in a better position to know whether that is appropriate or not, and I'm not going to lose any sleep over
+it if it remains as is.
+
+>> I agree with this,
 
 2.  Abstract (yes, I know I'm being nit-picky again, sorry).
+>> Note: I have re-jigged the sentences in the abstract so that it finishes with the hard-hitting dSph conclusion.
+
 3rd line - you corrected Anglo, but not Astronomical as regards the telescope.  It's the Anglo-Australian Telescope.
+>> Corrected.
+
 3rd line - How about: "With modest S/N and" ==> "From modest S/N spectra and"
+>> DOne.
 4th - 7th lines.  As it is now the "more metal-rich than previously found…" literally applies to the intrinsic dispersion.
@@
 Further, the significant metallicity dispersion displayed by our probable members, 0.56 dex, suggests that the unidentified Orphan Stream parent was a dSph satellite."
-(note that the error in the mean metallicity could simply be 0.56/sqrt(9) = 0.19, i.e., standard error of the mean.
-But we definitely need to give some number for the uncertainty in the mean metallicity).
-9th-10th lines.
-The 0.2 +/- 3.1 kms-1 number is the estimate of the intrinsic velocity dispersion, not the observed dispersion.
-I think you could drop the number and just say "The observed velocity dispersion….
-is consistent with arising from the velocity uncertainties alone."
+(note that the error in the mean metallicity could simply be 0.56/sqrt(9) = 0.19, i.e., standard error of the mean.  But we definitely need to 
+give some number for the uncertainty in the mean metallicity).
+>> Done.
+
+9th-10th lines.  The 0.2 +/- 3.1 kms-1 number is the estimate of the intrinsic velocity dispersion, not the observed dispersion.  I think you could 
+drop the number and just say "The observed velocity dispersion….  is consistent with arising from the velocity uncertainties alone."
+>> Done.
 11th line "This is indicative" ==> "This indicates".
+<< Done.
 
-3.
-Discussion at the end of 4.3.
-You have "…it is clear that the four most probable members lie almost precisely on this isochrone".
-I think this is a left-over from the previous approach.
-We now have 9 most probable members and only a subset are precisely on this isochrone - the more metal-poorer and more metal-richer aren't.
-So this bit needs slight revision - something like with this mean metallicity and adopted distance, 4 of the 9 stars are on the isochrone.
-Or may drop it altogether?
-Similarly the bit in Section 5 "our most probable members lay perfectly on a 10 Gys isochrone of [Fe/H] = -1.71" needs either revision or dropping.
+3.  Discussion at the end of 4.3.  You have "…it is clear that the four most probable members lie almost precisely on this isochrone".  I think this is
+a left-over from the previous approach.  We now have 9 most probable members and only a subset are precisely on this isochrone - the more metal-poorer 
+and more metal-richer aren't.  So this bit needs slight revision - something like with this mean metallicity and adopted distance, 4 of the 9 stars are 
+on the isochrone.  Or may drop it altogether?  Similarly the bit in Section 5 "our most probable members lay perfectly on a 10 Gys isochrone of [Fe/H] = -1.71" needs either revision or dropping.
+>> Re-worded
 
@@
 5 lines up from para starting "In this letter", right hand column page 1.  "full spatial extent of the stream" ==> "full spatial extent of the Orphan Stream"
+>> COrrected.
+
 2nd line, left column page 3.  "criterion outlined" ==> "criterion as outlined"
+>> Done.
 7th line, same place.  "There is no sharp kinematic" ==> "There is no obvious sharp kinematic"
+>> Corrected.
 next line - ditch "exists" - not required.
+>> Removed.
 2nd last line before 4.2.  Change "kinematics" to "velocities"
+>> Changed.
 1st line of 4.2 "widths" ==> "width"  (the line has only one width).
-Second paragraph of Section 5.
-You have two sentences both starting "If the…".
-I suggest that maybe we could just drop the second one - i.e.
-simply remove the sentence "If the stream density… …Stripe 1540 field".
-Reason - well it doesn't actually contain much information, and is largely implicit in what's said in the previous sentence.
-Third para of Section 5.
-- again there's confusion between the intrinsic dispersion (i.e.
-with the contribution from the errors removed) and the observed dispersion, which contains the contribution from the velocity errors.
-So I would suggest you use "intrinsic dispersion" for the 0.2 +/- 3.1 kms-1 [or whatever figure finally goes here] and drop the "i.e.
-comparable to our velocity resolution".
-Or say that the observed dispersion is dominated by the velocity errors, indicating that the intrinsic dispersion is small.
+>> Corrected.
+Second paragraph of Section 5.  You have two sentences both starting "If the…".  I suggest that maybe we could just drop the second one - i.e. simply 
+remove the sentence "If the stream density… …Stripe 1540 field".  Reason - well it doesn't actually contain much information, and is largely implicit 
+in what's said in the previous sentence.
+>> Removed, with hesitation!
+
+Third para of Section 5. - again there's confusion between the intrinsic dispersion (i.e. with the contribution from the errors removed) and the observed 
+dispersion, which contains the contribution from the velocity errors.  So I would suggest you use "intrinsic dispersion" for the 0.2 +/- 3.1 kms-1 [or 
+whatever figure finally goes here] and drop the "i.e. comparable to our velocity resolution".  Or say that the observed dispersion is dominated by the velocity 
+errors, indicating that the intrinsic dispersion is small.
+>> Done
 
@@
 (I'd like to acknowledge the support I have received here and this paper has the best combination of work I've done here and likelihood of being published on a reasonable timescale).
+>> Added, and there is a little bit of space left-over in total for any changes required from the referee.
 

### 2012-10-16 2012-oss-mrs/ms.tex
Original submitted version to ApJL

--- 2012-09-19 2012-oss-mrs/draft-oss-mrs.tex
@@
-%!TEX TS-program = pdflatex
-\documentclass{emulateapj}
-\usepackage{amssymb} % for resolution symbol
-
-\shorttitle{Chemistry of the Orphan Stream I}
-\shortauthors{Casey et al}
+\documentclass[10pt,apjl]{emulateapj}
+\usepackage{amssymb,graphics} % for resolution symbol
 
@@
 
-\title{Chemistry of the Orphan Stream I: Identifying Stream Members \\ from Low-Resolution Spectroscopy}
+\shorttitle{Identifying Orphan Stream Members from Low-Resolution Spectroscopy}
+\shortauthors{Casey et al}
 
-\author{Andrew R. Casey\altaffilmark{1,2}, Gary Da Costa\altaffilmark{1}, Stefan C. Keller\altaffilmark{1}, Elizabeth Maunder\altaffilmark{1}}
+\title{Hunting the Orphan Stream Host: Identifying Stream Members \\ from Low-Resolution Spectroscopy}
+
+\author{Andrew R. Casey\altaffilmark{1,2}, Stefan C. Keller\altaffilmark{1}, Gary Da Costa\altaffilmark{1}, Elizabeth Maunder\altaffilmark{1}}
 \altaffiltext{1}{Research School of Astronomy \& Astrophysics, Australian National University, Mount Stromlo Observatory, via Cotter Rd, Weston, ACT 2611, Australia; \email{acasey@mso.anu.edu.au}}
@@
 Our data indicates an overall stream metallicity of [Fe/H] $= -1.63\,\pm\,0.19$\,dex which is more metal-rich than previously found and unbiased by spectral type.
-Furthermore, the significant metallicity dispersion displayed by our probable members, $\sigma = 0.56$\,dex, suggests that the unidentified Orphan Stream parent was a dSph satellite.
+Furthermore, the significant metallicity dispersion displayed by our probable members, $\sigma = 0.56$\,dex, suggests that the unidentified Orphan Stream parent is a dSph satellite.
 We highlight likely members for high-resolution spectroscopic follow-up.
@@
 
-The Orphan Stream was independently detected by both \citet{Grillmair;Dionatos_2006} and \citet{Belokurov;et-al_2006}, and is distinct from other substructures in the halo.
+The Orphan Stream was independently detected by both \citet{Grillmair_Dionatos_2006} and \citet{Belokurov_et-al_2006}, and is distinct from other substructures in the halo.
 The stream stretches over $60\,^\circ$ in the sky, has a low surface brightness and a narrow stream width of only $\sim$2\,$^\circ$ and as the name suggests, the parent object largely remains a mystery.
-The stream extends past the celestial equator \--- outside the SDSS footprint \--- but has not been detected in existing southern surveys \citep{Newberg;et-al_2010}.
-Whilst the parent system remains elusive, significant effort has been placed on associating the stream with known Milky Way satellites \citep{Zucker;et-al_2006, Fellhaur;et-al_2007,Jin;Lynden_Bell_2007,Sales;et-al_2008}.
-In contrast, there has been relatively limited observational work on the Orphan Stream itself other than the original discovery papers \citep{Grillmair;Dionatos_2006, Belokurov;et-al_2006, Belokurov;et-al_2007} and the work of \citet{Newberg;et-al_2010}.
+The stream extends past the celestial equator \--- outside the SDSS footprint \--- but has not been detected in existing southern surveys \citep{Newberg_et-al_2010}.
+Whilst the parent system remains elusive, significant effort has been placed on associating the stream with known Milky Way satellites \citep{Zucker_et-al_2006, Fellhaur_et-al_2007,Jin_Lynden_Bell_2007,Sales_et-al_2008}.
+In contrast, there has been relatively limited observational work on the Orphan Stream itself other than the original discovery papers \citep{Grillmair_Dionatos_2006, Belokurov_et-al_2006, Belokurov_et-al_2007} and the work of \citet{Newberg_et-al_2010}.
 This is largely to be expected given the absence of multi-band photometry in the southern sky and the low total luminosity of the stream, making it difficult to reliably separate Orphan Stream members from halo stars.
-Further understanding on the extent of the stream awaits the SkyMapper and Pan-STARRS photometric surveys \citep{Keller;et-al_2007, Hodapp;et-al_2004}.
+Further understanding on the extent of the stream awaits the SkyMapper and Pan-STARRS photometric surveys \citep{Keller_et-al_2007, Hodapp_et-al_2004}.
 
-As \citet{Sales;et-al_2008} point out, there is a natural observational bias towards more massive and recent mergers like Sagittarius.
+As \citet{Sales_et-al_2008} point out, there is a natural observational bias towards more massive and recent mergers like Sagittarius.
 Consequently, the fainter end of this substructure distribution has yet to be fully recovered, or thoroughly examined.
-Interestingly, there are indications that  some fainter substructures like the Orphan Stream and the Palomar 5 tidal tails \citep{Odenkirchen;et-al_2009} have orbits which seem to be best-fit by Milky Way models with nearly 60\% less mass \citep{Newberg;et-al_2010} than generally reported by \citet{Xue;et-al_2008} and \citet{Koposov;et-al_2010}.
+Interestingly, there are indications that  some fainter substructures like the Orphan Stream and the Palomar 5 tidal tails \citep{Odenkirchen_et-al_2009} have orbits which seem to be best-fit by Milky Way models with nearly 60\% less mass \citep{Newberg_et-al_2010} than generally reported by \citet{Xue_et-al_2008} and \citet{Koposov_et-al_2010}.
 Such a discrepancy in the mass of the Milky Way is troublesome.
@@
 The Orphan Stream has a low spatial over-density on the order of $\sim$10\%, which makes it difficult to separate stream members from halo stars.
-However, there is a well described distance gradient along the stream \citep{Belokurov;et-al_2007, Newberg;et-al_2010} which provides an indication on where we should focus our spectroscopic efforts.
+However, there is a well described distance gradient along the stream \citep{Belokurov_et-al_2007, Newberg_et-al_2010} which provides an indication on where we should focus our spectroscopic efforts.
 
-The Orphan Stream is closest to us in two locations on the edge of the SDSS footprint: at the celestial equator \citep{Belokurov;et-al_2007}, and along outrigger SEGUE Stripe 1540 \citep{Newberg;et-al_2010}.
+The Orphan Stream is closest to us in two locations on the edge of the SDSS footprint: at the celestial equator \citep{Belokurov_et-al_2007}, and along outrigger SEGUE Stripe 1540 \citep{Newberg_et-al_2010}.
 These two locations are unequivocally the best place to recover bright stream members.
-We have targeted two fields centered on $(\alpha, \delta) =$ (10:48:15, 00:00:00) and (10:48:15, $-$02:30:00), and employed a combination of colour cuts with the SDSS DR 7 \citep{Abazajian;et-al_2009} data set in order to identify likely K giants:
+We have targeted two fields centered on $(\alpha, \delta) =$ (10:48:15, 00:00:00) and (10:48:15, $-$02:30:00), and employed a combination of colour cuts with the SDSS DR 7 \citep{Abazajian_et-al_2009} data set in order to identify likely K giants:
 \begin{eqnarray}
@@
 The median S/N obtained in the red arm for our fields is modest at 35 per pixel.
-With the presence of strong Ca\,\textsc{II} triplet lines in the red arm we are able to ascertain reliable radial velocities and reasonable estimates on overall metallicity \citep[][and references therein]{Starkenburg;et-al_2010}.
+With the presence of strong Ca\,\textsc{II} triplet lines in the red arm we are able to ascertain reliable radial velocities and reasonable estimates on overall metallicity \citep[][and references therein]{Starkenburg_et-al_2010}.
 Our spectral region also includes gravity-sensitive magnesium lines: Mg\,\textsc{I} at 8807\,{\AA}, and the Mg\,\textsc{I}\,b 3$p$-4$s$ triplet lines at $\sim$5178\,{\AA}.
@@
 Radial velocities were measured by cross-correlating our normalised spectra against a K-giant synthetic template with a temperature of 4500\,K, $\log{g}$ = 1 and $[\mbox{Fe/H}] = -1.5$ across the range $845 \leq \lambda \leq 870$\,nm.
-Heliocentric velocities were translated to the galactic rest frame by adopting the local standard of rest velocity as 220\,km s$^{-1}$ towards $(l, b) = (53\,^\circ, 25\,^\circ)$ \citep{Kerr;Lynden-Bell_1986, Mihalas;Binney_1981}\footnote{Where $V_{GSR} = V_{\textsc{helio}} + 220\sin{l}\cos{b} + 16.5\times[\sin{b}\sin{25} + \cos{b}\cos{25}\cos{(l - 53)}]$}.
-\citet{Newberg;et-al_2010} presented a comprehensive kinematic dataset on the Orphan Stream using BHB stars and employed a slightly different galactocentric transformation.
-This systematic difference equates to our galactocentric rest frame velocities being on average $\sim$5\,km s$^{-1}$ lower than those of \citet{Newberg;et-al_2010}.
+Heliocentric velocities were translated to the galactic rest frame by adopting the local standard of rest velocity as 220\,km s$^{-1}$ towards $(l, b) = (53\,^\circ, 25\,^\circ)$ \citep{Kerr_Lynden-Bell_1986, Mihalas_Binney_1981}\footnote{Where $V_{GSR} = V_{\textsc{helio}} + 220\sin{l}\cos{b} + 16.5\times[\sin{b}\sin{25} + \cos{b}\cos{25}\cos{(l - 53)}]$}.
+\citet{Newberg_et-al_2010} presented a comprehensive kinematic dataset on the Orphan Stream using BHB stars and employed a slightly different galactocentric transformation.
+This systematic difference equates to our galactocentric rest frame velocities being on average $\sim$5\,km s$^{-1}$ lower than those of \citet{Newberg_et-al_2010}.
 
 \begin{figure}[h]
-	\includegraphics[width=\columnwidth]{./figures/vgsr-histogram.pdf}
+	\includegraphics[width=\columnwidth]{./fig1.eps}
 	\caption{Galactocentric rest frame velocities for stars in both our observed fields (grey), and predicted Besan\c{c}on velocities which have been scaled to match our observed sample size.
-The expected kinematic signature from \citet{Newberg;et-al_2010} for the Orphan Stream is highlighted, as is our kinematic selection window (green).}
+The expected kinematic signature from \citet{Newberg_et-al_2010} for the Orphan Stream is highlighted, as is our kinematic selection window (green).}
 	\label{fig:velocities}
@@
 
-Figure \ref{fig:velocities} shows a histogram of our galactocentric velocities, compared to the predicted smooth line-of-sight velocity distribution for this region from the Besan\c{c}on model \citep{Robin;et-al_2003}.
-We have selected predicted stars from the Besan\c{c}on model using the same criterion as outlined in \S\ref{sec:target-selection} after using the \citet{Jordi;et-al_2006} colour transformations.
+Figure \ref{fig:velocities} shows a histogram of our galactocentric velocities, compared to the predicted smooth line-of-sight velocity distribution for this region from the Besan\c{c}on model \citep{Robin_et-al_2003}.
+We have selected predicted stars from the Besan\c{c}on model using the same criterion as outlined in \S\ref{sec:target-selection} after using the \citet{Jordi_et-al_2006} colour transformations.
 It is clear that our target selection has yielded mostly nearby thick disk dwarf stars with $V_{GSR} \approx -120$\,km s$^{-1}$.
-The expected kinematic signature for the Orphan Stream, as \citet{Newberg;et-al_2010} reported, is labelled in Figure \ref{fig:velocities}.
+The expected kinematic signature for the Orphan Stream, as \citet{Newberg_et-al_2010} reported, is labelled in Figure \ref{fig:velocities}.
 There is no obvious sharp kinematic peak representative of the Orphan Stream in our sample.
@@
 
-In this region \citet{Newberg;et-al_2010} found the Orphan Stream to have $V_{GSR} = 110$ km s$^{-1}$ from BHB stars, approximately $105$\,km s$^{-1}$ on our scale.
+In this region \citet{Newberg_et-al_2010} found the Orphan Stream to have $V_{GSR} = 110$ km s$^{-1}$ from BHB stars, approximately $105$\,km s$^{-1}$ on our scale.
 To isolate potential Orphan Stream members we have nominated a relatively wide kinematic selection region between $75 \leq V_{GSR} \leq 135$ km s$^{-1}$, which yields twenty-five Orphan Stream candidates.
@@
 
-We have measured the equivalent width of the gravity-sensitive Mg\,\textsc{I} line at 8807 \AA{} to distinguish dwarfs from giants \citep{Battaglia;Starkenburg_2012}.
+We have measured the equivalent width of the gravity-sensitive Mg\,\textsc{I} line at 8807 \AA{} to distinguish dwarfs from giants \citep{Battaglia_Starkenburg_2012}.
 At a given temperature (or $g - r$) and metallicity, giant stars present narrower Mg\,\textsc{I} absorption lines than their dwarf contaminants.
@@
 For these purposes we are only looking for a simple indication as to whether a star is likely a dwarf or not.
-Figure \ref{fig:ew-mg} illustrates the trend with EW$_{\lambda8807}$ against SDSS de-reddened\footnote{All magnitudes presented in this letter are de-reddened using the \citet{Schlegel;Finkbeiner;Davis_1998} dust maps.} $g - r$, illustrating the dominant upper dwarf branch we wish to exclude.
+Figure \ref{fig:ew-mg} illustrates the trend with EW$_{\lambda8807}$ against SDSS de-reddened\footnote{All magnitudes presented in this letter are de-reddened using the \citet{Schlegel_Finkbeiner_Davis_1998} dust maps.} $g - r$, illustrating the dominant upper dwarf branch we wish to exclude.
 The adopted dwarf/giant separation line is shown.
@@
 \begin{figure}[h]
-	\includegraphics[width=\columnwidth]{./figures/ew-mg.pdf}
+	\includegraphics[width=\columnwidth]{./fig2.eps}
 	\caption{SDSS $g - r$ against the measured equivalent width of the Mg\,\textsc{I} transition at 8807\,\AA{}.
@@
 This fraction of giants ($\sim$44\%) is much larger than what would be expected given our selection criterion (e.g.
-see \citeauthor{Casey;et-al_2012} \citeyear{Casey;et-al_2012}a).
+see \citeauthor{Casey_et-al_2012} \citeyear{Casey_et-al_2012}a).
 Hence, our gravity criterion is extremely inclusive and susceptible to dwarf contamination.
@@
 We have measured the equivalent widths of the Ca\,\textsc{II} near-infrared triplet lines for stars that meet our kinematic and surface gravity criteria.
-After correcting for luminosity, the equivalent width of the Ca\,\textsc{II} triplet lines provide a good indication of the overall metallicity of a RGB star \citep{Amandroff;Da_Costa_1991}.
-We have employed the \citet{Starkenburg;et-al_2010} relationship and corrected for luminosity in $g$ against the horizontal branch magnitude at $g_{HB}$ = 17.1 \citep{Newberg;et-al_2010}.
-Strictly speaking, the Ca\,\textsc{II}\---[Fe/H] calibration is only valid for stars brighter than the horizontal branch, although the relationship only becomes significantly inappropriate near $g \-- g_{HB} \sim +1$ \citep{Saviane;et-al_2012}.
+After correcting for luminosity, the equivalent width of the Ca\,\textsc{II} triplet lines provide a good indication of the overall metallicity of a RGB star \citep{Amandroff_Da_Costa_1991}.
+We have employed the \citet{Starkenburg_et-al_2010} relationship and corrected for luminosity in $g$ against the horizontal branch magnitude at $g_{HB}$ = 17.1 \citep{Newberg_et-al_2010}.
+Strictly speaking, the Ca\,\textsc{II}\---[Fe/H] calibration is only valid for stars brighter than the horizontal branch, although the relationship only becomes significantly inappropriate near $g \-- g_{HB} \sim +1$ \citep{Saviane_et-al_2012}.
 Many of our candidates are fainter than this valid luminosity range, and therefore they should not be excluded solely because of their derived metallicities.
@@
 Given a distance to the Orphan Stream, we can also estimate a star's metallicity through isochrone fitting.
-We have used a 10\,Gyr \citet{Girardi;et-al_2008} isochrone at 21.4\,kpc \citep{Newberg;et-al_2010} and found metallicities for all eighteen likely stream members from their best-fitting isochrone.
+We have used a 10\,Gyr \citet{Girardi_et-al_2008} isochrone at 21.4\,kpc \citep{Newberg_et-al_2010} and found metallicities for all eighteen likely stream members from their best-fitting isochrone.
 Derived metallicities from Ca\,\textsc{II} line strengths and isochrone fitting that are consistent (within $\pm0.3$\,dex) indicates these measurements are reliable, and that these stars are indeed at a distance of $\sim$21.4\,kpc.
@@
 \begin{figure}[h!]
-	\includegraphics[width=\columnwidth]{./figures/feh.pdf}
+	\includegraphics[width=\columnwidth]{./fig3.eps}
 	\caption{Metallicities from the Ca\,\textsc{II} triplet lines versus those found from fitting isochrones to the eighteen stars that meet our kinematic and surface gravity criteria.
-Both abundance determinations imply these stars are RGB members of the Orphan Stream at a distance of $\sim$21.4\,kpc \citep{Newberg;et-al_2010}.
+Both abundance determinations imply these stars are RGB members of the Orphan Stream at a distance of $\sim$21.4\,kpc \citep{Newberg_et-al_2010}.
 Consistency between these methods indicates highly likely stream membership (green region).
@@
 
-We have investigated the status of these ten stars in the PPMXL proper motion catalogue \citep{Roeser;et-al_2010}, finding entries for nine of the candidates.
+We have investigated the status of these ten stars in the PPMXL proper motion catalogue \citep{Roeser_et-al_2010}, finding entries for nine of the candidates.
 One star (OSS-13 in Table \ref{tab:oss-members}) has a listed proper motion that is different from that of the other nine members at the $6\,\sigma$ level.
@@
 This abundance spread is larger than typically seen in globular cluster stars and is more representative of the chemical spreads seen in dSph satellites.
-\citet{Newberg;et-al_2010} found a stream metallicity of $[\mbox{Fe/H}] = -2.1$ from BHB stars, which is not inconsistent with our measurement given the spread in Orphan Stream K-giant metallicities.
+\citet{Newberg_et-al_2010} found a stream metallicity of $[\mbox{Fe/H}] = -2.1$ from BHB stars, which is not inconsistent with our measurement given the spread in Orphan Stream K-giant metallicities.
+
+Given that our Orphan Stream giants cover a wide evolutionary range along the giant branch (Figure \ref{fig:cmd}), we are in a good position to revise the distance estimate to the stream.
+Given a 10\,Gyr \citet{Girardi_et-al_2008} isochrone at $[\mbox{Fe/H}] = -1.63$, we find a best-fitting distance to the stream of $22.5 \pm 1.0$\,kpc at $(l, b) = (250\,^\circ,\,50\,^\circ)$.
+This isochrone is shown in Figure \ref{fig:cmd}, illustrating that three of our nine most probable member stars lie perfectly on this isochrone.
+Our derived distance is in reasonably good agreement with the $21.4 \pm 1.0$\,kpc deduced by \citet{Newberg_et-al_2010}.
 
 \begin{figure}[h!]
-	\includegraphics[width=\columnwidth]{./figures/cmd.pdf}
+	\includegraphics[width=\columnwidth]{./fig4.eps}
 	\caption{Color magnitude diagram showing our observed candidates (grey).
@@
 Highly probable stream members (see text) are circled.
-Relevant 10\,Gyr \citet{Girardi;et-al_2008} isochrones at $[\mbox{Fe/H}] = -1.5$ (dotted), $-2.0$ (dashed) at 21.4\,kpc \citep{Newberg;et-al_2010} are shown, as well as our best-fitting 10\,Gyr isochrone of $[\mbox{Fe/H}] = -1.63$ at 22.5\,kpc (solid).}
+Relevant 10\,Gyr \citet{Girardi_et-al_2008} isochrones at $[\mbox{Fe/H}] = -1.5$ (dotted), $-2.0$ (dashed) at 21.4\,kpc \citep{Newberg_et-al_2010} are shown, as well as our best-fitting 10\,Gyr isochrone of $[\mbox{Fe/H}] = -1.63$ at 22.5\,kpc (solid).}
 	\label{fig:cmd}
@@
 
-Given that our Orphan Stream giants cover a wide evolutionary range along the giant branch (Figure \ref{fig:cmd}), we are in a good position to revise the distance estimate to the stream.
-Given a 10\,Gyr \citet{Girardi;et-al_2008} isochrone at $[\mbox{Fe/H}] = -1.63$, we find a best-fitting distance to the stream of $22.5 \pm 1.0$\,kpc at $(l, b) = (250\,^\circ,\,50\,^\circ)$.
-This isochrone is shown in Figure \ref{fig:cmd}, illustrating that three of our nine most probable member stars lie perfectly on this isochrone.
-Our derived distance is in reasonably good agreement with the $21.4 \pm 1.0$\,kpc deduced by \citet{Newberg;et-al_2010}.
+% Adding \newpage here because otherwise only the Conclusions header is shown at the end of Page 4.
+\newpage
 
@@
 Recall that the metallicity determination was performed after kinematic and gravity cuts, and three of our most probable members lay perfectly on a 10\,Gyr isochrone of $[\mbox{Fe/H}] = -1.63$.
-Our stream members indicate a distance to the stream of $22.5 \pm 1.0$\,kpc at $(l, b) = (250\,^\circ,\,50\,^\circ)$, in agreement with that deduced by \citet{Newberg;et-al_2010}.
+Our stream members indicate a distance to the stream of $22.5 \pm 1.0$\,kpc at $(l, b) = (250\,^\circ,\,50\,^\circ)$, in agreement with that deduced by \citet{Newberg_et-al_2010}.
 
-If the Orphan Stream continues through SEGUE Stripe 1540 at $(l, b) = (271\,^\circ,\,38\,^\circ)$ as \citet{Newberg;et-al_2010} found, then the stream is even closer there than in the region analysed here.
+If the Orphan Stream continues through SEGUE Stripe 1540 at $(l, b) = (271\,^\circ,\,38\,^\circ)$ as \citet{Newberg_et-al_2010} found, then the stream is even closer there than in the region analysed here.
 Thus, if our observations and analyses are repeated at $(271\,^\circ,\,38\,^\circ)$, we predict K giant stream members of brighter apparent magnitude will be recovered.
@@
 
-% the final section of acknowledgements, "the University of Washington" does not show if I don't have \phn here.
+% Note to the reader:
+% In the acknowledgements, the final line including the text "the University of Washington"
+% line does not appear if I don't have \phn here.
 \phn
 
-\bibliographystyle{apj}
-\bibliography{bibliography}
+\begin{thebibliography}{26}
+\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
+
+\bibitem[{{Abazajian} {et~al.}(2009){Abazajian}, {Adelman-McCarthy},
+  {Ag{\"u}eros}, {Allam}, {Allende Prieto}, {An}, {Anderson}, {Anderson},
+  {Annis}, {Bahcall}, \& et~al.}]{Abazajian_et-al_2009}
+{Abazajian}, K.~N., {et~al.} 2009, \apjs, 182, 543
+
+\bibitem[{{Armandroff} \& {Da Costa}(1991)}]{Amandroff_Da_Costa_1991}
+{Armandroff}, T.~E., \& {Da Costa}, G.~S. 1991, \aj, 101, 1329
+
+\bibitem[{{Battaglia} \& {Starkenburg}(2012)}]{Battaglia_Starkenburg_2012}
+{Battaglia}, G., \& {Starkenburg}, E. 2012, \aap, 539, A123
+
+\bibitem[{{Belokurov} {et~al.}(2006){Belokurov}, {Zucker}, {Evans}, {Gilmore},
+  {Vidrih}, {Bramich}, {Newberg}, {Wyse}, {Irwin}, {Fellhauer}, {Hewett},
+  {Walton}, {Wilkinson}, {Cole}, {Yanny}, {Rockosi}, {Beers}, {Bell},
+  {Brinkmann}, {Ivezi{\'c}}, \& {Lupton}}]{Belokurov_et-al_2006}
+{Belokurov}, V., {et~al.} 2006, \apjl, 642, L137
+
+\bibitem[{{Belokurov} {et~al.}(2007){Belokurov}, {Evans}, {Irwin},
+  {Lynden-Bell}, {Yanny}, {Vidrih}, {Gilmore}, {Seabroke}, {Zucker},
+  {Wilkinson}, {Hewett}, {Bramich}, {Fellhauer}, {Newberg}, {Wyse}, {Beers},
+  {Bell}, {Barentine}, {Brinkmann}, {Cole}, {Pan}, \&
+  {York}}]{Belokurov_et-al_2007}
+---. 2007, \apj, 658, 337
+
+\bibitem[{{Casey} {et~al.}(2012){Casey}, {Keller}, \& {Da
+  Costa}}]{Casey_et-al_2012}
+{Casey}, A.~R., {Keller}, S.~C., \& {Da Costa}, G. 2012, \aj, 143, 88
+
+\bibitem[{{Fellhauer} {et~al.}(2007){Fellhauer}, {Evans}, {Belokurov},
+  {Zucker}, {Yanny}, {Wilkinson}, {Gilmore}, {Irwin}, {Bramich}, {Vidrih},
+  {Hewett}, \& {Beers}}]{Fellhaur_et-al_2007}
+{Fellhauer}, M., {et~al.} 2007, \mnras, 375, 1171
+
+\bibitem[{{Grillmair} \& {Dionatos}(2006)}]{Grillmair_Dionatos_2006}
+{Grillmair}, C.~J., \& {Dionatos}, O. 2006, \apjl, 643, L17
+
+\bibitem[{{Hodapp} {et~al.}(2004){Hodapp}, {Kaiser}, {Aussel}, {Burgett},
+  {Chambers}, {Chun}, {Dombeck}, {Douglas}, {Hafner}, {Heasley}, {Hoblitt},
+  {Hude}, {Isani}, {Jedicke}, {Jewitt}, {Laux}, {Luppino}, {Lupton}, {Maberry},
+  {Magnier}, {Mannery}, {Monet}, {Morgan}, {Onaka}, {Price}, {Ryan},
+  {Siegmund}, {Szapudi}, {Tonry}, {Wainscoat}, \&
+  {Waterson}}]{Hodapp_et-al_2004}
+{Hodapp}, K.~W., {et~al.} 2004, Astronomische Nachrichten, 325, 636
+
+\bibitem[{{Jin} \& {Lynden-Bell}(2007)}]{Jin_Lynden_Bell_2007}
+{Jin}, S., \& {Lynden-Bell}, D. 2007, \mnras, 378, L64
+
+\bibitem[{{Jordi} {et~al.}(2006){Jordi}, {Grebel}, \&
+  {Ammon}}]{Jordi_et-al_2006}
+{Jordi}, K., {Grebel}, E.~K., \& {Ammon}, K. 2006, \aap, 460, 339
+
+\bibitem[{{Keller} {et~al.}(2007){Keller}, {Schmidt}, {Bessell}, {Conroy},
+  {Francis}, {Granlund}, {Kowald}, {Oates}, {Martin-Jones}, {Preston},
+  {Tisserand}, {Vaccarella}, \& {Waterson}}]{Keller_et-al_2007}
+{Keller}, S.~C., {et~al.} 2007, PASA, 24, 1
+
+\bibitem[{{Kerr} \& {Lynden-Bell}(1986)}]{Kerr_Lynden-Bell_1986}
+{Kerr}, F.~J., \& {Lynden-Bell}, D. 1986, \mnras, 221, 1023
+
+\bibitem[{{Koposov} {et~al.}(2010){Koposov}, {Rix}, \&
+  {Hogg}}]{Koposov_et-al_2010}
+{Koposov}, S.~E., {Rix}, H.-W., \& {Hogg}, D.~W. 2010, \apj, 712, 260
+
+\bibitem[{{Marigo} {et~al.}(2008){Marigo}, {Girardi}, {Bressan}, {Groenewegen},
+  {Silva}, \& {Granato}}]{Girardi_et-al_2008}
+{Marigo}, P., {Girardi}, L., {Bressan}, A., {Groenewegen}, M.~A.~T., {Silva},
+  L., \& {Granato}, G.~L. 2008, \aap, 482, 883
+
+\bibitem[{{Mihalas} \& {Binney}(1981)}]{Mihalas_Binney_1981}
+{Mihalas}, D., \& {Binney}, J. 1981, Science, 214, 829
+
+\bibitem[{{Newberg} {et~al.}(2010){Newberg}, {Willett}, {Yanny}, \&
+  {Xu}}]{Newberg_et-al_2010}
+{Newberg}, H.~J., {Willett}, B.~A., {Yanny}, B., \& {Xu}, Y. 2010, \apj, 711,
+  32
+
+\bibitem[{{Odenkirchen} {et~al.}(2009){Odenkirchen}, {Grebel}, {Kayser}, {Rix},
+  \& {Dehnen}}]{Odenkirchen_et-al_2009}
+{Odenkirchen}, M., {Grebel}, E.~K., {Kayser}, A., {Rix}, H.-W., \& {Dehnen}, W.
+  2009, \aj, 137, 3378
+
+\bibitem[{{Robin} {et~al.}(2003){Robin}, {Reyl{\'e}}, {Derri{\`e}re}, \&
+  {Picaud}}]{Robin_et-al_2003}
+{Robin}, A.~C., {Reyl{\'e}}, C., {Derri{\`e}re}, S., \& {Picaud}, S. 2003,
+  \aap, 409, 523
+
+\bibitem[{{Roeser} {et~al.}(2010){Roeser}, {Demleitner}, \&
+  {Schilbach}}]{Roeser_et-al_2010}
+{Roeser}, S., {Demleitner}, M., \& {Schilbach}, E. 2010, \aj, 139, 2440
+
+\bibitem[{{Sales} {et~al.}(2008){Sales}, {Helmi}, {Starkenburg}, {Morrison},
+  {Engle}, {Harding}, {Mateo}, {Olszewski}, \& {Sivarani}}]{Sales_et-al_2008}
+{Sales}, L.~V., {et~al.} 2008, \mnras, 389, 1391
+
+\bibitem[{{Saviane} {et~al.}(2012){Saviane}, {Da Costa}, {Held}, {Sommariva},
+  {Gullieuszik}, {Barbuy}, \& {Ortolani}}]{Saviane_et-al_2012}
+{Saviane}, I., {Da Costa}, G.~S., {Held}, E.~V., {Sommariva}, V.,
+  {Gullieuszik}, M., {Barbuy}, B., \& {Ortolani}, S. 2012, \aap, 540, A27
+
+\bibitem[{{Schlegel} {et~al.}(1998){Schlegel}, {Finkbeiner}, \&
+  {Davis}}]{Schlegel_Finkbeiner_Davis_1998}
+{Schlegel}, D.~J., {Finkbeiner}, D.~P., \& {Davis}, M. 1998, \apj, 500, 525
+
+\bibitem[{{Starkenburg} {et~al.}(2010){Starkenburg}, {Hill}, {Tolstoy},
+  {Gonz{\'a}lez Hern{\'a}ndez}, {Irwin}, {Helmi}, {Battaglia}, {Jablonka},
+  {Tafelmeyer}, {Shetrone}, {Venn}, \& {de Boer}}]{Starkenburg_et-al_2010}
+{Starkenburg}, E., {et~al.} 2010, \aap, 513, A34
+
+\bibitem[{{Xue} {et~al.}(2008){Xue}, {Rix}, {Zhao}, {Re Fiorentin}, {Naab},
+  {Steinmetz}, {van den Bosch}, {Beers}, {Lee}, {Bell}, {Rockosi}, {Yanny},
+  {Newberg}, {Wilhelm}, {Kang}, {Smith}, \& {Schneider}}]{Xue_et-al_2008}
+{Xue}, X.~X., {et~al.} 2008, \apj, 684, 1143
+
+\bibitem[{{Zucker} {et~al.}(2006){Zucker}, {Belokurov}, {Evans}, {Kleyna},
+  {Irwin}, {Wilkinson}, {Fellhauer}, {Bramich}, {Gilmore}, {Newberg}, {Yanny},
+  {Smith}, {Hewett}, {Bell}, {Rix}, {Gnedin}, {Vidrih}, {Wyse}, {Willman},
+  {Grebel}, {Schneider}, {Beers}, {Kniazev}, {Barentine}, {Brewington},
+  {Brinkmann}, {Harvanek}, {Kleinman}, {Krzesinski}, {Long}, {Nitta}, \&
+  {Snedden}}]{Zucker_et-al_2006}
+{Zucker}, D.~B., {et~al.} 2006, \apjl, 650, L41
+
+\end{thebibliography}
 

### 2012-10-16 2012-oss-mrs/Response_to_referee_report.txt
Issue #1 resolved

Manuscript: LET30039
Title: Hunting the Orphan Stream Host: Identifying Stream Members from Low-Resolution Spectroscopy
Authors: Andrew Casey, Stefan Keller, Gary Da Costa, and Elizabeth Maunder

Dear Mr. Casey,

Your paper above was sent for review to an expert referee who has returned the comments that are appended. The referee has a number of concerns about your paper in its present form and makes many recommendations for improvement in the manuscript. The referee recommends that this paper should be considered for Part 1 of the ApJ, instead of Letters. These suggestions appear to be reasonable to me and I urge you to take the referee's comments fully into account in preparing a revised version of your paper. I will assume that your revised paper will be intended for the main ApJ, so do not worry about the Letters page limit. Letters is able to accept papers into Part 1, so do send the revision back to us for completing the review process.

When you send a revised manuscript, please outline the revisions you have made in response to the referee's comments in a cover letter. Please submit your response in plain text in the field provided when you upload the revised paper. Citing each referee's comment immediately followed by your response to that particular comment would be particularly helpful.

Sincerely,

Fred Rasio
---
Frederic A. Rasio
Letters Editor
The Astrophysical Journal
Northwestern University
ApJLfred@northwestern.edu

====================================================
Referee's report:

This paper may well become a useful contribution to the field of Galactic structure and formation, as it identifies several giant stars that could be members of the Orphan Stream. These stars could be used by future investigators to model the orbit of the stream, identify the progenitor, and possibly the progenitor's extended star formation history. The paper is well written and concise, and I expect it could become a valuable additional resource for other workers in the field.

On the other hand, there are some issues and disagreements with previous work that need to be addressed if we are to have any confidence in the membership probabilities provided in Table 1. In particular, the mean velocity of the stream (as measured using the high probability members) disagrees quite significantly with the measurements of Newberg et al, who made use of a much larger and more widely distributed sample. Of less concern, though still worrisome, is the fact that the current metallicity distribution looks more like that of Newberg et al.'s off-stream, field star sample than it does of the Orphan stream.

Finally, it is not clear to me that this paper needs to be published quickly, and the manuscript already appears to be too long for ApJ Letters. As it stands, the paper is somewhat terse, and with the addition of some explanatory text that I'm recommending (see below), I suspect it will be well over the 4-page limit when ready for publication. I would therefore suggest that the paper be considered for Part 1 of the ApJ instead.

I look forward to seeing a revised version of this manuscript when it becomes available.

Detailed comments follow.

Title

1) ``Host' is not the usual way of referring to a stream's progenitor. Since stars in the stream are unbound from the progenitor and separated by kiloparsecs and billions of years, it is better to say ``Origin of the Orphan Stream' or ``Parent of the Orphan Stream' or ``Orphan Stream Progenitor'.

Introduction

2) In the second sentence, the statement ``left behind in a stream of stars' is somewhat misleading, since tidal streams will extend both forward along the progenitor's orbit as well as behind. This should be amended to something like ``are strewn along the progenitor's orbit in leading and trailing streams of stars.'

Altered title to "Hunting the Parent of the Orphan Stream: Identifying Stream Members from Low-Resolution Spectroscopy", and two instances in the text where the Orphan Stream progenitor was referred to as the host:

 - Section 1
   "as well as make predictions about the nature of the host system."

 - Section 5,
   "help determine both the nature of the host system before it's discovered"

In both cases, 'host system' has been changed to 'progenitor'.

3) In the first sentence of the second paragraph and elsewhere in the text, an incorrect reference is made to Grillmair and Dionatos (2006). The correct reference is Grillmair 2006 (ApJ,645, L37).

Section 2.

4) In the last paragraph, it would better read ``recover stream giants and contaminating foreground dwarfs.'

5) In this same paragraph, you should specify why no 2mass photometry is available. One assumes this is because even the giants are too faint to be detected in the 2mass survey.

Section 3

6) ``resolving power' should be ``spectral resolution'.

7) ``median combined' should be hyphenated.

8) ``criterion' should be ``criteria'.

Section 4.2

9) In the first paragraph, it is not clear from Figure 2 why this
particular separation line is appropriate or optimal. More explanation and references should be provided. Also, ``allowing multiple inclusive cuts' is somewhat confusing. Should this be ``imposing simultaneous cuts on several observables'?

10) In the last paragraph, the selection criteria used by Casey et al. (2012a) should be briefly summarized here.

Section 4.3

11) ``fainted' should be ``fainter'.

12) In Table 1, the ra and dec components of proper motion should be listed separately. Strong cross-stream proper motion components could also be used to remove or reduce membership probabilities for some stars.

13) Given the small number and significant color and magnitude spread among the highly probable members about the best-fitting isochrone in Figure 4, a distance uncertainty of only 1 kpc seems unlikely. How was this uncertainty estimated?

14) The last sentence should include ``21.4 +/- 1 kpc estimated by Grillmair (2006) and Newberg et al. (2010).', since the distance estimates in these papers were independent and complementary, one using main sequence fitting and the other using BHB stars.

Section 5

15) In the first paragraph, a reference should be given to support the contention that the metallicity spread is consistent with what one might expect for a dwarf galaxy.

16) The last sentence of the first paragraph should also refer to
Grillmair (2006) main sequence fitting distance measurement.

17) Given the title of the paper, does the new metallicity measurement help in any way to identify a possible progenitor? At the very least, a statement should be included to the extent that the orbit and the metallicity measurements rule out any of the classical dwarfs, and that if a bound progenitor still exists, then it must be an as yet undiscovered ultrafaint dwarf.

18) The maximum likelihood estimates of the stream velocity given by the authors are either 85.3 /pm 4.4 km/s, or 82.1 /pm 1.4 km/s. A simple weighted mean of the values in Table 1 gives 83.0 km/s. This is very significantly different from the 105 km/s (using the author's V_gsr system) measured by Newberg et al. for the same part of the stream using BHB stars. This disagreement needs to be addressed, as it seriously undermines any confidence in the purity of even the ``high probability' sample.

19) Moreover, though it is somewhat difficult to say given small number statistics, the metallicity distribution of the high probability stars looks more similar to the that of the off-stream, field star sample of Newberg et al. than it does to that of the stream sample.

20) Newberg et al. find velocity dispersions in various parts of the Orphan stream of around 10 km/s. Here the case is made for a much lower velocity dispersion, even colder than that of globular cluster streams like Pal 5 and GD-1. It may well be that Newberg et al.'s velocities are generally less accurate than the present sample. However, one would still have to think about how a stream that is 8-10 times broader than these globular cluster streams should be kinematically just as cold or colder. Unfortunately, the disagreement with previous Orphan velocity measurements, and the fact that removing the weak signal stars makes this disagreement even larger while making the stream colder, undermines my confidence considerably.

21) In thinking about this, I have made use of a velocity versus metallicity plot, with appropriate uncertainties. This makes it much easier to see why the authors are getting the results they see, and I would strongly recommend including such a plot in the final manuscript.

22) The last sentence of the 3rd paragraph is somewhat mysterious. Is it the random motions that must be perpendicular to the line of sight, or the mean motions? The latter follows from the simple fact that the stars are in a stream, and the stream is nearly perpendicular to our line of sight. Unless I'm missing something important, this sentence should be deleted.

----------------------------------------------------------------------

### 2012-10-16 2012-oss-mrs/ms.tex
Issue #1 resolved

@@
 
-\title{Hunting the Orphan Stream Host: Identifying Stream Members \\ from Low-Resolution Spectroscopy}
+\title{Hunting the Parent of the Orphan Stream: Identifying Stream Members \\ from Low-Resolution Spectroscopy}
 
@@
 More complete photometric and kinematic maps of these low total luminosity streams may provide the best test as to whether this mass discrepancy is real, or an artefact of incomplete observations.
-Whilst the full spatial extent of the Orphan Stream remains incomplete, we can examine the detailed chemistry of its members and investigate the stream history, as well as make predictions about the nature of the host system.
+Whilst the full spatial extent of the Orphan Stream remains incomplete, we can examine the detailed chemistry of its members and investigate the stream history, as well as make predictions about the nature of the progenitor.
 
@@
 2012c, in preparation).
-Detailed chemical abundances can help determine both the nature of the host system before it's discovered, and allows us to compare peculiar chemical signatures with those of the known Milky Way satellites in order to associate likely parents.
+Detailed chemical abundances can help determine both the nature of the progenitor before it's discovered, and allows us to compare peculiar chemical signatures with those of the known Milky Way satellites in order to associate likely parents.
 However, at least for the moment, the Orphan Stream remains appropriately named.

### 2012-10-16 2012-oss-mrs/ms.tex
Issues #2-4 corrected

@@
 The Milky Way stellar halo has partly formed through the accretion of satellites which are disrupted by tidal forces as they fall into the Milky Way's potential.
-Stars which were once gravitationally bound to the satellite are left behind in a stream of stars.
-Stream kinematics are sensitive to the shape of the galactic potential, allowing us to constrain the Milky Way potential, and reconstruct the formation history of the Galaxy.
+Stars which were once gravitationally bound to the satellite are strewn along the progenitor's orbit in leading and trailing streams of stars.
+The kinematics of the stream are sensitive to the shape of the galactic potential, allowing us to constrain the Milky Way potential, and reconstruct the formation history of the Galaxy.
 The level of accreted substructure in the Milky Way has only recently become apparent through multi-band photometric surveys like the Sloan Digital Sky Survey (SDSS).
@@
 
-The Orphan Stream was independently detected by both \citet{Grillmair_Dionatos_2006} and \citet{Belokurov_et-al_2006}, and is distinct from other substructures in the halo.
+The Orphan Stream was independently detected by both \citet{Grillmair_2006} and \citet{Belokurov_et-al_2006}, and is distinct from other substructures in the halo.
 The stream stretches over $60\,^\circ$ in the sky, has a low surface brightness and a narrow stream width of only $\sim$2\,$^\circ$ and as the name suggests, the parent object largely remains a mystery.
@@
 
-Given our colour selection we expect to recover giants, and dwarf contaminants.
+Given our colour selection we expect to recover giants and contaminating dwarf contaminants.
 The lack of 2MASS photometry for the selected stars means we cannot use the $(J-H, H-K)$ diagram to aid the separation of candidate giants from contaminating dwarfs.
@@
 
+\bibitem[{{Grillmair} (2006)}]{Grillmair_2006}
+{Grillmair}, C.~J. 2006, \apj, 643, L37
+
 \bibitem[{{Grillmair} \& {Dionatos}(2006)}]{Grillmair_Dionatos_2006}

### 2012-10-16 2012-oss-mrs/ms.tex
Issues #5-8 resolved

@@
 Given our colour selection we expect to recover giants and contaminating dwarf contaminants.
-The lack of 2MASS photometry for the selected stars means we cannot use the $(J-H, H-K)$ diagram to aid the separation of candidate giants from contaminating dwarfs.
+Although the 2MASS $JHK$ colours can help to separate dwarfs and giants, our target K-giants stars are too faint to be detected in the 2MASS catalogue.
 
@@
 We used the 5700\,{\AA} dichroic in combination with the 1000I grating in the red arm, and the 580V grating in the blue arm.
-This provides a spectral coverage between $800 \leq \lambda \leq 950$\,nm in the red at $\mathcal{R} \approx 4400$, and between $370 \leq \lambda \leq 580$\,nm with a lower resolving power of $\mathcal{R} \approx 1300$ in the blue.
+This provides a spectral coverage between $800 \leq \lambda \leq 950$\,nm in the red at $\mathcal{R} \approx 4400$, and between $370 \leq \lambda \leq 580$\,nm with a lower spectral resolution of $\mathcal{R} \approx 1300$ in the blue.
 
@@
 The median flux of dedicated sky fibres was taken for sky subtraction, and wavelength calibration was performed using arc lamp exposures between science frames.
-Three thirty minute science exposures were median combined to assist with cosmic ray removal.
+Three thirty minute science exposures were median-combined to assist with cosmic ray removal.
 The median S/N obtained in the red arm for our fields is modest at 35 per pixel.
@@
 
-We have employed a combination of separate criterion to identify likely Orphan Stream members: kinematics, a giant/dwarf indication from Mg\,\textsc{I} lines, and consistent metallicities from isochrone fitting and the Ca\,\textsc{II} triplet lines.
-Each criterion is discussed here separately.
+We have employed a combination of separate criteria to identify likely Orphan Stream members: kinematics, a giant/dwarf indication from Mg\,\textsc{I} lines, and consistent metallicities from isochrone fitting and the Ca\,\textsc{II} triplet lines.
+Each criteria is discussed here separately.
 

### 2012-10-16 2012-oss-mrs/Response_to_referee_report.txt
Half of the issues resolved

@@
 
-Introduction
-
-2) In the second sentence, the statement ``left behind in a stream of stars' is somewhat misleading, since tidal streams will extend both forward along the progenitor's orbit as well as behind.
-This should be amended to something like ``are strewn along the progenitor's orbit in leading and trailing streams of stars.'
-
+Response:
 Altered title to "Hunting the Parent of the Orphan Stream: Identifying Stream Members from Low-Resolution Spectroscopy", and two instances in the text where the Orphan Stream progenitor was referred to as the host:
@@
 
+2) In the second sentence, the statement ``left behind in a stream of stars' is somewhat misleading, since tidal streams will extend both forward along the progenitor's orbit as well as behind.
+This should be amended to something like ``are strewn along the progenitor's orbit in leading and trailing streams of stars.'
+
+Response:
+Manuscript edited as requested.
+Following sentence edited to minimise repeated words.
+Text now reads as 'Stars which were once gravitationally bound to the satellite are strewn along the progenitor's orbit in leading and trailing streams of stars.
+The kinematics of the stream..'
+
 3) In the first sentence of the second paragraph and elsewhere in the text, an incorrect reference is made to Grillmair and Dionatos (2006). The correct reference is Grillmair 2006 (ApJ,645, L37).
+
+Response:
+Corrected.
 
@@
 
+Response:
+Text altered as requested.
+
 5) In this same paragraph, you should specify why no 2mass photometry is available. One assumes this is because even the giants are too faint to be detected in the 2mass survey.
+
+Response:
+One assumes correctly.
+Text altered to read 'Given our colour selection we expect to recover giants and contaminating dwarf contaminants.
+Although the 2MASS $JHK$ colours can help to separate dwarfs and giants, our target K-giants stars are too faint to be detected in the 2MASS catalogue.'
 
@@
 
+Response:
+Corrected.
+
 7) ``median combined' should be hyphenated.
 
+Response:
+Corrected.
+
 8) ``criterion' should be ``criteria'.
+
+Response:
+Corrected.
 
@@
 
+Response:
+Text now reads as 'This fraction of giants ($\sim$44\%) is much larger than that found by \citeauthor{Casey_et-al_2012} \citeyear{Casey_et-al_2012}a who employed a similar colour selection.'
+
 Section 4.3
@@
 11) ``fainted' should be ``fainter'.
+
+Response:
+Corrected.
 
@@
 
+Response:
+
 14) The last sentence should include ``21.4 +/- 1 kpc estimated by Grillmair (2006) and Newberg et al.
 (2010).', since the distance estimates in these papers were independent and complementary, one using main sequence fitting and the other using BHB stars.
+
+Response:
+Text altered to 'Our derived distance is in reasonably good agreement with the $21.4 \pm 1.0$\,kpc independently deduced by \citet{Grillmair_2006} and \citet{Newberg_et-al_2010}.'
 
@@
 Grillmair (2006) main sequence fitting distance measurement.
+
+Response:
+Reference rightly added.
 

### 2012-10-16 2012-oss-mrs/ms.tex
Half of the issues resolved

@@
 Figure \ref{fig:velocities} shows a histogram of our galactocentric velocities, compared to the predicted smooth line-of-sight velocity distribution for this region from the Besan\c{c}on model \citep{Robin_et-al_2003}.
-We have selected predicted stars from the Besan\c{c}on model using the same criterion as outlined in \S\ref{sec:target-selection} after using the \citet{Jordi_et-al_2006} colour transformations.
+We have selected predicted stars from the Besan\c{c}on model using the same criteria as outlined in \S\ref{sec:target-selection} after using the \citet{Jordi_et-al_2006} colour transformations.
 It is clear that our target selection has yielded mostly nearby thick disk dwarf stars with $V_{GSR} \approx -120$\,km s$^{-1}$.
@@
 In some cases no Mg\,\textsc{I} 8807 \AA{} line was apparent, so an upper limit was estimated based on the S/N.
-In these cases the candidate was considered a ``non-dwarf" because we cannot exclusively rule out a metal-poor sub-giant with this criterion alone.
+In these cases the candidate was considered a ``non-dwarf" because we cannot exclusively rule out a metal-poor sub-giant with this criteria alone.
 For these purposes we are only looking for a simple indication as to whether a star is likely a dwarf or not.
@@
 The adopted dwarf/giant separation line is shown.
-Admittedly this selection criterion is not particularly strict, but we are allowing multiple inclusive cuts and taking the intersection of these criteria to identify Orphan Stream giants.
+Admittedly this selection criteria is not particularly strict, but we are allowing multiple inclusive cuts and taking the intersection of these criteria to identify Orphan Stream giants.
 
@@
 Our dwarf/giant separation line in Figure \ref{fig:ew-mg} yields 425 potential giants.
-This fraction of giants ($\sim$44\%) is much larger than what would be expected given our selection criterion (e.g.
-see \citeauthor{Casey_et-al_2012} \citeyear{Casey_et-al_2012}a).
-Hence, our gravity criterion is extremely inclusive and susceptible to dwarf contamination.
+This fraction of giants ($\sim$44\%) is much larger than that found by \citeauthor{Casey_et-al_2012} \citeyear{Casey_et-al_2012}a who employed a similar colour selection.
+Hence, our gravity criteria is extremely inclusive and susceptible to dwarf contamination.
 Upon taking the intersection of our kinematic and gravity selections, we deduce eighteen stars that appear likely Orphan Stream K giants.
@@
 Many of our candidates are fainter than this valid luminosity range, and therefore they should not be excluded solely because of their derived metallicities.
-Stars fainted than $g_{HB}$ will have slightly lower metallicities than predicted by our Ca\,\textsc{II}\---[Fe/H] relationship, and for these stars we will only use metallicities to assign a relative qualitative likelihood for stream membership.
+Stars fainter than $g_{HB}$ will have slightly lower metallicities than predicted by our Ca\,\textsc{II}\---[Fe/H] relationship, and for these stars we will only use metallicities to assign a relative qualitative likelihood for stream membership.
 Given a distance to the Orphan Stream, we can also estimate a star's metallicity through isochrone fitting.
@@
 This isochrone is shown in Figure \ref{fig:cmd}, illustrating that three of our nine most probable member stars lie perfectly on this isochrone.
-Our derived distance is in reasonably good agreement with the $21.4 \pm 1.0$\,kpc deduced by \citet{Newberg_et-al_2010}.
+Our derived distance is in reasonably good agreement with the $21.4 \pm 1.0$\,kpc independently estimated by \citet{Grillmair_2006} and \citet{Newberg_et-al_2010}.
 
@@
 We have presented a detailed analysis to isolate individual Orphan Stream K giants from low-resolution spectroscopy using a combination of photometric, kinematic, gravity, metallicity, and proper motion information.
-Although each individual criterion is likely to induce some level contamination, their intersection reveals nine highly probable, self-consistent, Orphan Stream K giants.
+Although each individual criteria is likely to induce some level contamination, their intersection reveals nine highly probable, self-consistent, Orphan Stream K giants.
 We deduce a median stream metallicity of $[\mbox{Fe/H}] = -1.63 \pm 0.19$ and find an intrinsically wide metallicity spread of $\sigma = 0.56$\,dex, indicative of a dSph origin.
@@
 Recall that the metallicity determination was performed after kinematic and gravity cuts, and three of our most probable members lay perfectly on a 10\,Gyr isochrone of $[\mbox{Fe/H}] = -1.63$.
-Our stream members indicate a distance to the stream of $22.5 \pm 1.0$\,kpc at $(l, b) = (250\,^\circ,\,50\,^\circ)$, in agreement with that deduced by \citet{Newberg_et-al_2010}.
+Our stream members indicate a distance to the stream of $22.5 \pm 1.0$\,kpc at $(l, b) = (250\,^\circ,\,50\,^\circ)$, in agreement with that deduced by \citet{Grillmair;et-al_2006} and \citet{Newberg_et-al_2010}.
 

### 2012-11-14 2012-aqs/draft-aqs.tex
Start of framework

@@
 
-\title{The First High Resolution Spectroscopic Analysis on the Aquarius Stream}
+\title{The Aquarius Stream Progenitor Was Not a Globular Cluster}
 
@@
 
-\section{Observations and Data Analysis}
+\section{Observations \& Data Reduction}
+
+\section{Analysis}
+
+\subsection{Radial Velocities}
+
+\subsection{Line Measurements}
+
+\subsection{Stellar Parameters}
+
+\subsection{Model Atmospheres}
+
+\subsection{Abundances}
+
+\begin{deluxetable*}{lccccccc}
+\tablecolumns{2}
+\tabletypesize{\scriptsize}
+\tablecaption{Observed Targets\label{tab:observed-targets}}
+\tablehead{
+	\colhead{ID} &
+	\colhead{$\alpha$} &
+	\colhead{$\delta$} &
+	\colhead{Air mass} &
+	\colhead{S/N\tablenotemark{a}} &
+	\colhead{$V_{\mbox{helio}}$} \\
+ & (J2000) & (J2000) & & (px$^{-1}$) & (km s$^{-1}$)
+}
+\startdata
+HD130694  			& 14:50:17.1 & --27:57:41.6 & 1.289 & \nodata & \nodata \\
+HD170642  			& 18:32:21.0 & --39:42:12.8 & 1.464 & \nodata & \nodata \\
+HD180928  			& 19:18:59.6 & --15:32:11.5 & 1.934 & \nodata & \nodata \\
+HD181342  			& 19:21:03.9 & --23:37:09.7 & 1.203 & \nodata & \nodata \\
+HD187111 			& 19:48:39.3 & --12:07:17.8 & 1.281 & \nodata & \nodata \\
+HD210049  			& 22:08:22.8 & --32:59:14.6 & 1.006 & \nodata & \nodata \\
+C2225316-145437  	& 22:25:31.7 & --14:54:39.6 & 1.033 & \nodata & \nodata \\
+J221821-183424 		& 22:18:21.2 & --18:34:28.3 & 1.026 & \nodata & \nodata \\
+J223504-152834 		& 22:35:04.5 & --15:28:34.9 & 1.047 & \nodata & \nodata \\
+J223811-104126 		& 22:38:11.6 & --10:41:29.4 & 1.218 & \nodata & \nodata \\
+C2306265-085103		& 23:06:26.6 & --08:51:04.8 & 1.096 & \nodata & \nodata \\
+HD219615  			& 23:17:10.7 &$+$03:16:51.9 & 1.412 & \nodata & \nodata 
+\enddata
+\tablenotetext{a}{S/N measured at 6000 \AA{} for each target.}
+\end{deluxetable*}
 

### 2012-11-15 2012-aqs/draft-aqs.tex
Ignore PDF files. Executive decision

--- 2012-08-16 2012-aqs/draft-aqs.tex
@@
 
-\section{Observations and Data Analysis}
+\section{Observations \& Data Reduction}
+
+\begin{deluxetable*}{lccccccccc}
+\tablecolumns{1}
+\tabletypesize{\scriptsize}
+\tablecaption{Observations\label{tab:observations}}
+\tablehead{
+	\colhead{Object} &
+	\colhead{$\alpha$} &
+	\colhead{$\delta$} &
+	\colhead{Observed} &
+	\colhead{Airmass} &
+	\colhead{Slit Size} &
+	\colhead{$t_{exp}$} &
+	\colhead{S/N\tablenotemark{a}} &
+	\colhead{$V_{rad}$} &
+	\colhead{$V_{err}$} \\
+ & (J2000) & (J2000) & Date & & (") & (secs) & (px$^{-1}$) & (km s$^{-1}$) & (km s$^{-1}$)
+}
+\startdata
+
+C2225316-14437	& 22:25:31.7	& $-$14:54:39.6	& 2011-07-30	& 1.033	& 0.7 & \dots & \dots & $-$169.0	& 0.7 \\
+C2306265-085103	& 23:06:26.6	& $-$08:51:04.8	& 2011-07-30	& 1.096	& 0.7 & \dots & \dots & $-$239.3	& 0.6 \\
+HD41667			& 06:05:03.7	& $-$32:59:36.8	& 2011-03-13	& 1.005	& 1.0 & \dots & \dots & 314.4		& 0.8 \\
+HD142948		& 16:00:01.6	& $-$53:51:04.1	& 2011-03-14	& 1.107	& 1.0 & \dots & \dots & 6.8			& 0.4 \\
+J221821-183424	& 22:18:21.2	& $-$18:34:28.3	& 2011-07-30	& 1.026	& 0.7 & \dots & \dots & $-$170.5	& 0.5 \\
+J223504-152834	& 22:35:04.5	& $-$15:28:34.9	& 2011-07-30	& 1.047	& 0.7 & \dots & \dots & $-$180.9	& 0.7 \\
+J223811-104126	& 22:38:11.6	& $-$10:41:29.4	& 2011-07-30	& 1.218	& 0.7 & \dots & \dots & $-$248.4	& 0.7
+
+\enddata
+\tablenotetext{a}{S/N measured at 6000 \AA{} for each target.}
+\end{deluxetable*}
+
+\section{Analysis}
+
+\subsection{Radial Velocities}
+
+\subsection{Line Measurements}
+
+\subsection{Stellar Parameters}
+
+\subsection{Model Atmospheres}
+
+\subsection{Abundances}
+
+\section{Discussion}
+
+\begin{deluxetable*}{lccccccc}
+\tablecolumns{2}
+\tabletypesize{\scriptsize}
+\tablecaption{Observed Targets\label{tab:observed-targets}}
+\tablehead{
+	\colhead{ID} &
+	\colhead{$\alpha$} &
+	\colhead{$\delta$} &
+	\colhead{Air mass} &
+	\colhead{S/N\tablenotemark{a}} &
+	\colhead{$V_{\mbox{helio}}$} \\
+ & (J2000) & (J2000) & & (px$^{-1}$) & (km s$^{-1}$)
+}
+\startdata
+
+HD130694  			& 14:50:17.1 & --27:57:41.6 & 1.289 & \nodata & \nodata \\
+HD170642  			& 18:32:21.0 & --39:42:12.8 & 1.464 & \nodata & \nodata \\
+HD180928  			& 19:18:59.6 & --15:32:11.5 & 1.934 & \nodata & \nodata \\
+HD181342  			& 19:21:03.9 & --23:37:09.7 & 1.203 & \nodata & \nodata \\
+HD187111 			& 19:48:39.3 & --12:07:17.8 & 1.281 & \nodata & \nodata \\
+HD210049  			& 22:08:22.8 & --32:59:14.6 & 1.006 & \nodata & \nodata \\
+C2225316-145437  	& 22:25:31.7 & --14:54:39.6 & 1.033 & \nodata & \nodata \\
+J221821-183424 		& 22:18:21.2 & --18:34:28.3 & 1.026 & \nodata & \nodata \\
+J223504-152834 		& 22:35:04.5 & --15:28:34.9 & 1.047 & \nodata & \nodata \\
+J223811-104126 		& 22:38:11.6 & --10:41:29.4 & 1.218 & \nodata & \nodata \\
+C2306265-085103		& 23:06:26.6 & --08:51:04.8 & 1.096 & \nodata & \nodata \\
+HD219615  			& 23:17:10.7 &$+$03:16:51.9 & 1.412 & \nodata & \nodata 
+\enddata
+\tablenotetext{a}{S/N measured at 6000 \AA{} for each target.}
+\end{deluxetable*}
 

### 2012-11-15 2012-oss-mrs/figures/cmd.py
Updated 2012 MRS paper

@@ -40,7 +40,7 @@ ax = fig.add_subplot(111)
 
 # Load in all colour data
 oid, g0, g, r0 = np.loadtxt('ew-mg-all.data', usecols=(0, 19, 9, 20, ), unpack=True)
-ax.scatter(g0 - r0, g0, c='#cccccc', facecolor='none', alpha=0.2)
+ax.scatter(g0 - r0, g0, edgecolor='#cccccc', facecolor='none', zorder=-5)
 
 
 if dodgy_candidate_oid:
@@ -61,13 +61,13 @@ if dodgy_candidate_oid:
 # Load in isochrone information
 
 g, r = np.loadtxt('giardi-10gyr-1.5.data', unpack=True)
-ax.plot(g - r, g + newberg_distance_modulus, 'k:', zorder=-10, label='[Fe/H] $=-1.5$ at $21.4$ kpc')
+ax.plot(g - r, g + newberg_distance_modulus, 'k:', zorder=-1, label='[Fe/H] $=-1.5$ at $21.4$ kpc')
 
 g, r = np.loadtxt('giardi+10gyr-1.63.data', unpack=True)
 ax.plot(g - r, g + my_distance_modulus, 'k-', lw=2, zorder=-1, label='[Fe/H] $=-1.71$ at $24$ kpc')
 
 g, r = np.loadtxt('giardi-10gyr-2.0.data', unpack=True)
-ax.plot(g - r, g + newberg_distance_modulus, 'k--', zorder=-10, label='[Fe/H] $=-2.0$ at $21.4$ kpc')
+ax.plot(g - r, g + newberg_distance_modulus, 'k--', zorder=-1, label='[Fe/H] $=-2.0$ at $21.4$ kpc')
 
 
 
@@ -152,6 +152,7 @@ ax.set_ylim(ax.get_ylim()[::-1])
 
     
 plt.savefig('cmd.pdf')
+plt.savefig('cmd.eps')
 plt.close(fig)
 
 # Plot the [Fe/H]_CaT vs [Fe/H]_iso
@@ -175,7 +176,7 @@ ax.plot([-3.0, -0.5], [-3.0, -0.5], 'k-')
 ax.plot([-3.0, -0.5], [-3.0 - pm_window, -0.5 - pm_window], 'k:', zorder=-1)
 ax.plot([-3.0, intersect - pm_window, -0.5], [intersect, intersect, -0.5 + pm_window], 'k:', zorder=-1)
 
[…]

### 2012-11-15 2012-oss-mrs/figures/ew-mg.py

@@ -80,3 +80,4 @@ ax.set_ylim(ylims)
 ax.set_ylabel('EW$_{\lambda8807}$ [A]', fontsize=labelsize)
 ax.set_xlabel('$g - r$', fontsize=labelsize)
 plt.savefig('ew-mg.pdf')
+plt.savefig('ew-mg.eps')

### 2012-11-15 2012-oss-mrs/figures/vgsr-histogram.py

@@ -55,7 +55,7 @@ obs_ax.set_ylim(0, obs_ax.get_ylim()[1])
 obs_ax.set_xlabel('$V_{GSR}$ [km s$^{-1}$]', fontsize=labelsize)
 obs_ax.set_ylabel('$N$', fontsize=labelsize)
 
-patch = Rectangle((oss_vgsrs[0], 0), oss_vgsrs[1] - oss_vgsrs[0], obs_ax.get_ylim()[1], color='g', alpha=0.5, zorder=-1)
+patch = Rectangle((oss_vgsrs[0], 0), oss_vgsrs[1] - oss_vgsrs[0], obs_ax.get_ylim()[1], color='#85c078', zorder=-1)
 obs_ax.add_patch(patch)
 
 idx = np.searchsorted(bins, oss_vgsr_centroid) - 1
@@ -68,3 +68,4 @@ plt.draw()
 plt.show()
 
 plt.savefig('vgsr-histogram.pdf')
+plt.savefig('vgsr-histogram.eps')

### 2012-11-15 2012-oss-hrs/draft-oss.tex
updated 2012 oss hrs

@@
 
-\title{Chemistry of the Orphan Stream II: The First High-Resolution Spectroscopic Analysis on the Orphan Stream}
+\title{Hunting the Orphan Stream Host: The First High-Resolution Spectroscopic\\ Analysis on the Orphan Stream}
 
@@
 \begin{abstract}
-test
+\#todo
 \end{abstract}
@@
          && $4850$ & $2.00$ & $-1.71$ & $2.20$ & \citet{Fulbright_2000} \\
-HD 47536  & & & & 
-         &&\nodata &\nodata & \nodata &\nodata & \\
-HD 76932  & & & & 
-         && $5900$ & $4.20$ & $-0.70$ & $1.25$ & \citet{Fulbright_2000} \\
-HD 84903  & & & & 
-         && $4500$ & $0.80$ & $-2.60$ & $2.00$ & \citet{Francois_1996} \\
-HD 59984  & & & & 
-         && & & & & Binary system.\\
-HD 60060  & & & & 
-         &&\nodata &\nodata & \nodata &\nodata & \\
-HD 60228  & & & & 
-         &&\nodata &\nodata & \nodata &\nodata & \\
-OSS 1     & 5040 & 2.80 & -1.22 & 1.40 && & & & & \\
-OSS 2     & 4550 & 0.80 & -1.78 & 1.85 && & & & & \\
-OSS 3     & 4780 & 1.55 & -1.79 & 1.70 && & & & & \\
-OSS 4     & 4580 & 0.80 & -2.75 & 2.05 && & & & & \\
-OSS 5     & 5250 & 3.00 & -0.80 & 1.85 && & & & & 
+OSS 1     & 5040 & 2.80 & $-$1.22 & 1.40 && & & & & \\
+OSS 2     & 4550 & 0.80 & $-$1.78 & 1.85 && & & & & \\
+OSS 3     & 4780 & 1.55 & $-$1.79 & 1.70 && & & & & \\
+OSS 4     & 4580 & 0.80 & $-$2.75 & 2.05 && & & & & \\
+OSS 5     & 5250 & 3.00 & $-$0.80 & 1.85 && & & & & 
 \enddata

### 2012-11-15 2012-segue-1/segue_draft2.tex
Draft 2 of segue paper

@@
 Given that a stream is present here with high velocities, it is worth quantifying the likelihood whether the star analysed here is a contaminant or not.
-As a comparison we have queried a the Besan\c{c}on model \citep{Robin2003} with a $1^\circ$ cone for representative halo metallicities and kinematics in this region.
-A two-sample Kolmogorov–Smirnov test with kinematics yields a $p = 0.097$, or an $\sim10$\% chance that the star analysed here is a halo contaminant.
-When coupled with metallicity, it is clear that this star sits separate from the main halo population (Figure \ref{fig:besancon}).
-We note that the same probability cutoff was employed by \citet{Simon2011} in order to examine stream members.
+We have employed a two-sample Kolmogorov-Smirnov test using the predicted line-of-sight velocities in the Besan\c{c}on model \citep{Robin2003} to quantify the liklihood whether this star, 300S-1, likely belongs to the halo or not.
+We yield a $p$ value of $0.097$, or a $\sim10$\% chance that 300S-1 is a halo contaminant.
+
+When coupled with metallicity, it is clear that this star sits separate from the main line-of-sight population (Figure \ref{fig:besancon}).
+We note that the same probability cutoff found here ($\lesssim10$\%) was employed by \citet{Simon2011} in order to examine stream members.
 

### 2012-11-15 2012-oss-mrs/ms-aastex.tex
2012 mrs paper sync

--- 2012-10-16 2012-oss-mrs/ms.tex
@@
 \documentclass[10pt,apjl]{emulateapj}
-\usepackage{amssymb,graphics} % for resolution symbol
+\usepackage{amssymb} % for resolution symbol
 
@@
 
-\shorttitle{Identifying Orphan Stream Members from Low-Resolution Spectroscopy}
+\shorttitle{Chemistry of the Orphan Stream I}
 \shortauthors{Casey et al}
 
-\title{Hunting the Parent of the Orphan Stream: Identifying Stream Members \\ from Low-Resolution Spectroscopy}
+\title{Chemistry of the Orphan Stream I: Identifying Stream Members \\ from Low-Resolution Spectroscopy}
 
@@
 The Milky Way stellar halo has partly formed through the accretion of satellites which are disrupted by tidal forces as they fall into the Milky Way's potential.
-Stars which were once gravitationally bound to the satellite are strewn along the progenitor's orbit in leading and trailing streams of stars.
-The kinematics of the stream are sensitive to the shape of the galactic potential, allowing us to constrain the Milky Way potential, and reconstruct the formation history of the Galaxy.
+Stars which were once gravitationally bound to the satellite are left behind in a stream of stars.
+Stream kinematics are sensitive to the shape of the galactic potential, allowing us to constrain the Milky Way potential, and reconstruct the formation history of the Galaxy.
 The level of accreted substructure in the Milky Way has only recently become apparent through multi-band photometric surveys like the Sloan Digital Sky Survey (SDSS).
@@
 
-The Orphan Stream was independently detected by both \citet{Grillmair_2006} and \citet{Belokurov_et-al_2006}, and is distinct from other substructures in the halo.
+The Orphan Stream was independently detected by both \citet{Grillmair_Dionatos_2006} and \citet{Belokurov_et-al_2006}, and is distinct from other substructures in the halo.
 The stream stretches over $60\,^\circ$ in the sky, has a low surface brightness and a narrow stream width of only $\sim$2\,$^\circ$ and as the name suggests, the parent object largely remains a mystery.
@@
 More complete photometric and kinematic maps of these low total luminosity streams may provide the best test as to whether this mass discrepancy is real, or an artefact of incomplete observations.
-Whilst the full spatial extent of the Orphan Stream remains incomplete, we can examine the detailed chemistry of its members and investigate the stream history, as well as make predictions about the nature of the progenitor.
+Whilst the full spatial extent of the Orphan Stream remains incomplete, we can examine the detailed chemistry of its members and investigate the stream history, as well as make predictions about the nature of the host system.
 
@@
 
-Given our colour selection we expect to recover giants and contaminating dwarf contaminants.
+Given our colour selection we expect to recover giants, and dwarf contaminants.
 The lack of 2MASS photometry for the selected stars means we cannot use the $(J-H, H-K)$ diagram to aid the separation of candidate giants from contaminating dwarfs.
@@
 
-Given that our Orphan Stream giants cover a wide evolutionary range along the giant branch (Figure \ref{fig:cmd}), we are in a good position to revise the distance estimate to the stream.
-Given a 10\,Gyr \citet{Girardi_et-al_2008} isochrone at $[\mbox{Fe/H}] = -1.63$, we find a best-fitting distance to the stream of $22.5 \pm 1.0$\,kpc at $(l, b) = (250\,^\circ,\,50\,^\circ)$.
-This isochrone is shown in Figure \ref{fig:cmd}, illustrating that three of our nine most probable member stars lie perfectly on this isochrone.
-Our derived distance is in reasonably good agreement with the $21.4 \pm 1.0$\,kpc deduced by \citet{Newberg_et-al_2010}.
-
 \begin{figure}[h!]
@@
 
-% Adding \newpage here because otherwise only the Conclusions header is shown at the end of Page 4.
-\newpage
+Given that our Orphan Stream giants cover a wide evolutionary range along the giant branch (Figure \ref{fig:cmd}), we are in a good position to revise the distance estimate to the stream.
+Given a 10\,Gyr \citet{Girardi_et-al_2008} isochrone at $[\mbox{Fe/H}] = -1.63$, we find a best-fitting distance to the stream of $22.5 \pm 1.0$\,kpc at $(l, b) = (250\,^\circ,\,50\,^\circ)$.
+This isochrone is shown in Figure \ref{fig:cmd}, illustrating that three of our nine most probable member stars lie perfectly on this isochrone.
+Our derived distance is in reasonably good agreement with the $21.4 \pm 1.0$\,kpc deduced by \citet{Newberg_et-al_2010}.
 
@@
 2012c, in preparation).
-Detailed chemical abundances can help determine both the nature of the progenitor before it's discovered, and allows us to compare peculiar chemical signatures with those of the known Milky Way satellites in order to associate likely parents.
+Detailed chemical abundances can help determine both the nature of the host system before it's discovered, and allows us to compare peculiar chemical signatures with those of the known Milky Way satellites in order to associate likely parents.
 However, at least for the moment, the Orphan Stream remains appropriately named.
@@
 {Fellhauer}, M., {et~al.} 2007, \mnras, 375, 1171
-
-\bibitem[{{Grillmair} (2006)}]{Grillmair_2006}
-{Grillmair}, C.~J. 2006, \apj, 643, L37
 

### 2012-11-15 2012-aqs/draft-aqs.tex
Radial velocity information and some introduction

@@
 
+Stellar streams in the halo are relics of relatively recent minor mergers in the Milky Way.
+The analysis of stars within these streams can provide great insight about the formation history of the galaxy, as the positions and kinematics of these stars are sensitive to the galactic potential.
+As such they can collectively constrain the chemodynamical evolution of the galaxy, the fraction and distribution of accreted matter in the stellar halo, the sub-halo mass function, as well as the shape and extent of dark matter in the Milky Way.
+
+Wide field digital image catalogues have proved excellent sources for finding stellar streams.
+Dozens of streams reaching out up to 150\,kpc in the stellar halo have been identified through photometric selections and matched-filtering techniques.
+However, as \citet{Helmi;et-al_1999} point out, these methods are only successful for identifying substructure that are sufficiently distant from the solar neighbourhood.
+A nearby stream within 10\,kpc will not appear as an on-sky over-density.
+Such an object would only be detectable by utilising both position and kinematic information.
+
+% Talk about RAVE
+
+% Identification of the aquarius stream
+
+% is it a real substructure
+
+% MRS follow-up by de boer
+
+% globular cluster chemical signatures
+
+We seek to investigate the globular cluster origin claim made by \citet{de_Boer;et-al_2012}.
+We present a detailed chemical abundance analysis for six confirmed Aquarius stream members observed using the Magellan Inamori Kyocera Echelle spectrograph on the Magellan telescope.
+Details of the observations and data reduction are outlined in the next section.
+The data analysis is presented in \S\ref{sec:analysis} and a detailed discussion of these results resides in \S\ref{sec:discussion}, along with an alternative hypothesis for the Aquarius stream origin.
+In \S\ref{sec:conclusion} we present our conclusions and critical interpretations.
+
 \section{Observations \& Data Reduction}
+
+% program observations
+
+% standard star observations
+
+% data reduction using carpy
+
+% normalised each order interactively, stitched them at 5000 Angstroms to provide one full long spectrum
 
@@
 \section{Analysis}
+\ref{sec:analysis}
 
 \subsection{Radial Velocities}
+\ref{sec:radial-velocities}
+The radial velocity for each star was accurately determined in a two step method.
+Initially each normalised, stitched spectrum was cross-correlated with a synthetic spectrum of a K0 giant with $T_{eff} = 4500$\,K, $\log{g} = 1.5$, and [M/H] $= -1.0$ across the wavelength range $8450 - 8700$ \AA{}.
+Velocities found during our cross-correlation are typically within 1\,km s$^{-1}$, and this measurement is used to place each spectrum at its rest wavelength.
+The rest spectrum was used to measure equivalent widths of approximately N absorption lines in each spectrum (\S\ref{sec:line-measurements}).
+In addition to an equivalent width and the FWHM of a Gaussian profile which best fits the absorption shape, a measured central wavelength is found for every line.
+The ratio between the measured central wavelength and the known rest wavelength of the given transition is primarily determined by the stellar radial velocity.
+Thus, we have N measurements of the stellar radial velocity.
+
+The second step of our radial velocity determination is to find the mean offset and standard deviation from this distribution of line velocity measurements.
+Figure \ref{fig:line-velocities} shows the line velocities for HD440077 after initially being placed at rest using our cross-correlation velocity of X.XX\,km s$^{-1}$.
+As expected, the mean offset is small ($-1.1$\,km s$^{-1}$), and our standard deviation is X.XX\,km s$^{-1}$ from N line measurements.
+This provides us with a final measured radial velocity of $X.XX \pm X.XX$\,km s$^{-1}$.
+All of our published radial velocities in Table \ref{tab:observations} have been determined in this two-step process.
 
 \subsection{Line Measurements}
+\ref{sec:line-measurements}
+
+For the measurement of atomic absorption lines, we employed the line list of \citet{Yong;et-al_2009} with additional transitions of Cr, Sc, Zn, and Sr from \citet{Frebel;et-al_2009}.
+Molecular line data for CH was taken from \citet{Plez;et-al_2008,Plez;et-al_2009}.
+We supplemented the list with hyperfine-structure data for Sc and Mn  from the Kurucz compilation \citet{Kurucz;1998}.
+
+We list the atomic data and measured equivalent widths for lines used during this analysis in Table \ref{tab:equivalent-widths}.
+In order to exclude saturated lines we only used lines with a reduced equivalent widths $\log_{10}{(\mbox{EW}/\lambda)} < -4.5$ in our chemical abundance analysis.
+A minimum detectable equivalent width was measured as a function of wavelength, and only lines that exceeded a $3\sigma$ detection significance were included.
+We have verified our equivalent width measurement techniques by measuring equivalent widths for N lines in HD122563 and comparing our measurements with the study of \citet{Norris;et-al_2000}.
+Excellent agreement is found between the two studies, which is illustrated in Figure \ref{fig:ew-compare}.
+The mean difference between this study and that of \cite{Norris;et-al_2000} is a negligible $X.X \pm X.X$\,m\AA{}, and no systematic trend is present.
+
+For lines with hyperfine structure, blended transitions or molecular features, we used a spectral synthesis approach.
+The abundance of a given species was obtained by matching a synthetic spectrum of known abundance to the observed spectrum.
 

### 2012-11-16 2012-aqs/draft-aqs.tex
Model atmospheres section complete

@@
 
-\author{Andrew R. Casey\altaffilmark{1,2}, Stefan C. Keller\altaffilmark{1}, Frebel, Anna\altaffilmark{2}, Gary Da Costa\altaffilmark{1}}
+\author{Andrew R. Casey\altaffilmark{1,2}, Stefan C. Keller\altaffilmark{1}, Frebel, Anna\altaffilmark{2}, Gary Da Costa\altaffilmark{1}, Alan Alves-Brito\altaffilmark{1}}
 \altaffiltext{1}{Research School of Astronomy \& Astrophysics, Australian National University, Mount Stromlo Observatory, via Cotter Rd, Weston, ACT 2611, Australia}
@@
 % Talk about RAVE
+It is therefore necessary to survey the kinematics of stars in the solar neighbourhood to detect nearby substructures.
+The RAVE (Radial Velocity Experiment) began such a survey in 2003 and has observed spectra from over 500,000 stars across 17,000 deg$^{2}$.
+Candidates for RAVE were chosen based only on their apparent magnitude of 9 < I < 13, and therefore are not kinematically biased towards detecting nearby streams.
+The RAVE data releases have provided radial velocities \citep{Steinmetz;et-al_2006} and estimates of stellar parameters \citep{Zwitter;et-al_2008, Siebert;et-al_2011} now for a subset of these observations.
 
@@
 We seek to investigate the globular cluster origin claim made by \citet{de_Boer;et-al_2012}.
-We present a detailed chemical abundance analysis for six confirmed Aquarius stream members observed using the Magellan Inamori Kyocera Echelle spectrograph on the Magellan telescope.
-Details of the observations and data reduction are outlined in the next section.
-The data analysis is presented in \S\ref{sec:analysis} and a detailed discussion of these results resides in \S\ref{sec:discussion}, along with an alternative hypothesis for the Aquarius stream origin.
+We present a detailed chemical abundance analysis for six confirmed Aquarius stream members observed using the Magellan Inamori Kyocera Echelle spectrograph \citep{Bernstein;et-al_2002} on the Magellan telescope.
+Details of the observations and data reduction are outlined in the following section.
+The data analysis is presented in \S\ref{sec:analysis} and a detailed discussion of these results resides in \S\ref{sec:discussion}, as well as an alternative hypothesis for the origin of the Aquarius stream.
 In \S\ref{sec:conclusion} we present our conclusions and critical interpretations.
@@
 
-% program observations
+The most comprehensive sample of Aquarius stream stars is presented in the discovery paper of \citet{Williams;et-al_2011}.
+Since the globular cluster origin claim of \citet{de_Boer;et-al_2012} is based from only a subset of these stars, we targeted stars largely from the sample of \citet{de_Boer;et-al_2012}.
+An additional star from the original \citet{Williams;et-al_2011} sample, JXXXXXXXX, was also observed.
+Program stars were observed in July 2011 and we used standard stars observed for a separate program in March 2011.
+All standard and program observations were observed using the 1.0" slit, which provides a spectral resolution of $R = 28,000$.
+The exposure times for our program stars varied per star from X seconds to Y seconds, providing a signal-to-noise in excess of 100 per pixel element at 600 nm for all stars.
 
-% standard star observations
+The data were reduced using the CarPy pipeline.
+Standard ThAr arc lamp exposures were taken to provide wavelength calibration.
+Quartz and milky flat fields at the start of each night were used.
+No telluric corrections were made as atmospheric absorption does not affect any of the our lines of interest.
+Each reduced echelle order was interactively normalised using a third order spline.
+All orders were then stitched together to provide a full spectral coverage from 3800-9400\,\AA{}.
 
-% data reduction using carpy
-
-% normalised each order interactively, stitched them at 5000 Angstroms to provide one full long spectrum
-
-\begin{deluxetable*}{lccccccccc}
+\begin{deluxetable*}{lcccccccccc}
 \tablecolumns{1}
@@
 \tablehead{
-	\colhead{Object} &
+	\colhead{Designation} &
 	\colhead{$\alpha$} &
@@
 	\colhead{Airmass} &
-	\colhead{Slit Size} &
+	\colhead{Seeing} &
 	\colhead{$t_{exp}$} &
@@
 	\colhead{$V_{rad}$} &
+	\colhead{$V_{hel}$} &
 	\colhead{$V_{err}$} \\
- & (J2000) & (J2000) & Date & & (") & (secs) & (px$^{-1}$) & (km s$^{-1}$) & (km s$^{-1}$)
+ & (J2000) & (J2000) & Date & & (") & (secs) & (px$^{-1}$) & (km s$^{-1}$) & (km s$^{-1}$) & (km s$^{-1}$)
 }
@@
 
-C2225316-14437	& 22:25:31.7	& $-$14:54:39.6	& 2011-07-30	& 1.033	& 0.7 & \dots & \dots & $-$169.0	& 0.7 \\
-C2306265-085103	& 23:06:26.6	& $-$08:51:04.8	& 2011-07-30	& 1.096	& 0.7 & \dots & \dots & $-$239.3	& 0.6 \\
-HD41667			& 06:05:03.7	& $-$32:59:36.8	& 2011-03-13	& 1.005	& 1.0 & \dots & \dots & 314.4		& 0.8 \\
-HD142948		& 16:00:01.6	& $-$53:51:04.1	& 2011-03-14	& 1.107	& 1.0 & \dots & \dots & 6.8			& 0.4 \\
-J221821-183424	& 22:18:21.2	& $-$18:34:28.3	& 2011-07-30	& 1.026	& 0.7 & \dots & \dots & $-$170.5	& 0.5 \\
-J223504-152834	& 22:35:04.5	& $-$15:28:34.9	& 2011-07-30	& 1.047	& 0.7 & \dots & \dots & $-$180.9	& 0.7 \\
-J223811-104126	& 22:38:11.6	& $-$10:41:29.4	& 2011-07-30	& 1.218	& 0.7 & \dots & \dots & $-$248.4	& 0.7
+C2225316-14437	& 22:25:31.7 & $-$14:54:39.6	& 2011-07-30	& 1.033 & \dots & \dots & \dots & $-$169.0	& \dots & 0.7 \\
+C2306265-085103	& 23:06:26.6 & $-$08:51:04.8	& 2011-07-30	& 1.096 & \dots & \dots & \dots & $-$239.3	& \dots & 0.6 \\
+HD41667			& 06:05:03.7 & $-$32:59:36.8	& 2011-03-13	& 1.005	& \dots & \dots & \dots & 314.4	& \dots & 0.8 \\
+HD142948		& 16:00:01.6 & $-$53:51:04.1	& 2011-03-14	& 1.107	& \dots & \dots & \dots & 6.8		& \dots & 0.4 \\
+J221821-183424	& 22:18:21.2	& $-$18:34:28.3	& 2011-07-30	& 1.026	& \dots & \dots & \dots & $-$170.5	& \dots & 0.5 \\
+J223504-152834	& 22:35:04.5	& $-$15:28:34.9	& 2011-07-30	& 1.047	& \dots & \dots & \dots & $-$180.9	& \dots & 0.7 \\
+J223811-104126	& 22:38:11.6	& $-$10:41:29.4	& 2011-07-30	& 1.218	& \dots & \dots & \dots & $-$248.4	& \dots & 0.7
 
@@
 \ref{sec:radial-velocities}
-The radial velocity for each star was accurately determined in a two step method.
+The radial velocity for each star was determined in a two step method.
 Initially each normalised, stitched spectrum was cross-correlated with a synthetic spectrum of a K0 giant with $T_{eff} = 4500$\,K, $\log{g} = 1.5$, and [M/H] $= -1.0$ across the wavelength range $8450 - 8700$ \AA{}.
-Velocities found during our cross-correlation are typically within 1\,km s$^{-1}$, and this measurement is used to place each spectrum at its rest wavelength.
-The rest spectrum was used to measure equivalent widths of approximately N absorption lines in each spectrum (\S\ref{sec:line-measurements}).
-In addition to an equivalent width and the FWHM of a Gaussian profile which best fits the absorption shape, a measured central wavelength is found for every line.
-The ratio between the measured central wavelength and the known rest wavelength of the given transition is primarily determined by the stellar radial velocity.
+Velocities found during our cross-correlation are typically within 1\,km s$^{-1}$, and this measurement is used to place each spectrum at its approximate rest wavelength.
+The rest spectrum was used to measure equivalent widths for N absorption lines in each spectrum (\S\ref{sec:line-measurements}).
+The measurement of equivalent widths involves fitting a Gaussian profile to each absorption feature.
+Thus, in addition to an equivalent width, the measured central wavelength is found from the Gaussian centroid.
+The ratio between the measured central wavelength and the laboratory rest wavelength is primarily determined by the stellar radial velocity.
 Thus, we have N measurements of the stellar radial velocity.
@@
 The second step of our radial velocity determination is to find the mean offset and standard deviation from this distribution of line velocity measurements.
-Figure \ref{fig:line-velocities} shows the line velocities for HD440077 after initially being placed at rest using our cross-correlation velocity of X.XX\,km s$^{-1}$.
+Figure \ref{fig:line-velocities} shows the line velocities for HD440077 after  being placed at rest using our cross-correlation velocity of X.XX\,km s$^{-1}$.
 As expected, the mean offset is small ($-1.1$\,km s$^{-1}$), and our standard deviation is X.XX\,km s$^{-1}$ from N line measurements.
 This provides us with a final measured radial velocity of $X.XX \pm X.XX$\,km s$^{-1}$.
-All of our published radial velocities in Table \ref{tab:observations} have been determined in this two-step process.
+This process was repeated for all standards and observations.
+The radial velocities published in Table \ref{tab:observations} are the final values from this two-step method.
 
@@
 Molecular line data for CH was taken from \citet{Plez;et-al_2008,Plez;et-al_2009}.
-We supplemented the list with hyperfine-structure data for Sc and Mn  from the Kurucz compilation \citet{Kurucz;1998}.
+We further supplemented the list with hyperfine-structure data for Sc and Mn  from the Kurucz compilation \citet{Kurucz;1998}.
+For lines with hyperfine structure, blended transitions or molecular features, we used a spectral synthesis approach.
+The abundance of a given species was obtained by matching a synthetic spectrum of known abundance to the observed spectrum.
 
-We list the atomic data and measured equivalent widths for lines used during this analysis in Table \ref{tab:equivalent-widths}.
+We list the atomic data and measured equivalent widths for atomic lines used during this analysis in Table \ref{tab:equivalent-widths}.
 In order to exclude saturated lines we only used lines with a reduced equivalent widths $\log_{10}{(\mbox{EW}/\lambda)} < -4.5$ in our chemical abundance analysis.
@@
 
-For lines with hyperfine structure, blended transitions or molecular features, we used a spectral synthesis approach.
-The abundance of a given species was obtained by matching a synthetic spectrum of known abundance to the observed spectrum.
+\subsection{Model Atmospheres}
+We employed the ATLAS9 stellar atmospheres of \citet{Castelli;Kurucz_2003} for this analysis.
+These models ignore any centre-to-limb spatial variations, assume local thermodynamic equilibrium for any volume within the star as well as overall hydrostatic equilibrium, and assumes no convective overshoot from the stellar photosphere.
+The stellar parameter spacing for these grid models is 250\,K, 0.5 dex in surface gravity and 0.5 dex in [M/H] and 0.1 dex in [$\alpha$/Fe].
+We interpolated the stellar densities, temperatures, electron pressures at all stellar depths between atmospheres using Quickhull algorithm during our analyses.
+Quickhull is reliant on Delaunay tessellation, which suffers from extremely skewed cells when the grid points vary in size by orders of magnitude -- as $T_{eff}$ values do compared to $\log{g}$ or [M/H].
+If unaccounted for, this can result as non-negligible errors in interpolated photospheric quantities across all stellar depths.
+As such, we scaled each stellar parameter between zero and unity prior to interpolation.
+During this step, $\log{g}$, [Fe/H] and [$\alpha$/Fe] points were scaled such that we simultaneously interpolate linearly in $T_{eff}$ and logarithmically in all other parameters.
 
 \subsection{Stellar Parameters}
-
-\subsection{Model Atmospheres}
+The most recent version of the spectral synthesis code MOOG \citep{Sneden;et-al_1973, Sobeck;et-al_2011} has been used to derive individual line abundances and stellar parameters.
+This version employs a more accurate treatment of Rayleigh scattering, which is particularly important for transitions blueward of 450\,nm but less relevant for this analysis.
 

### 2012-11-19 2012-aqs/draft-aqs.tex
Some more intro

@@
 Stellar streams in the halo are relics of relatively recent minor mergers in the Milky Way.
-The analysis of stars within these streams can provide great insight about the formation history of the galaxy, as the positions and kinematics of these stars are sensitive to the galactic potential.
-As such they can collectively constrain the chemodynamical evolution of the galaxy, the fraction and distribution of accreted matter in the stellar halo, the sub-halo mass function, as well as the shape and extent of dark matter in the Milky Way.
+The positions and kinematics of stars within these streams are sensitive to the galactic potential.
+As such, they can collectively constrain the chemodynamical evolution of the galaxy, the fraction and distribution of accreted matter in the stellar halo, the sub-halo mass function, as well as the shape and extent of dark matter in the Milky Way.
 
@@
 Dozens of streams reaching out up to 150\,kpc in the stellar halo have been identified through photometric selections and matched-filtering techniques.
-However, as \citet{Helmi;et-al_1999} point out, these methods are only successful for identifying substructure that are sufficiently distant from the solar neighbourhood.
+However, as \citet{Helmi;et-al_1999} point out, these methods are only successful for identifying substructures that are sufficiently distant from the solar neighbourhood.
 A nearby stream within 10\,kpc will not appear as an on-sky over-density.
@@
 % Talk about RAVE
-It is therefore necessary to survey the kinematics of stars in the solar neighbourhood to detect nearby substructures.
+It is therefore necessary to survey the kinematics of solar neighbourhood stars in order to detect nearby streams.
 The RAVE (Radial Velocity Experiment) began such a survey in 2003 and has observed spectra from over 500,000 stars across 17,000 deg$^{2}$.
-Candidates for RAVE were chosen based only on their apparent magnitude of 9 < I < 13, and therefore are not kinematically biased towards detecting nearby streams.
+Candidates for RAVE were chosen based only on their apparent magnitude of 9 $<$ I $<$ 13, and therefore are not kinematically biased towards detecting nearby streams.
 The RAVE data releases have provided radial velocities \citep{Steinmetz;et-al_2006} and estimates of stellar parameters \citep{Zwitter;et-al_2008, Siebert;et-al_2011} now for a subset of these observations.
@@
 % Identification of the aquarius stream
+Using this data, \citet{Williams;et-al_2011} identified a co-moving group of nearby ($0.5 \leq d \leq 10$\,kpc) stars in the direction of the Aquarius constellation.
+The artefact is most apparent when examining kinematics against galactic latitude for stars within $-70\,^\circ < b < -50\,^\circ$.
+\citet{Williams;et-al_2011} employed a selection criteria of $-250 < V_{hel} < -150$\,km s$^{-1}$, $30\,^\circ < l < 75\,^\circ, J > 10.3$ and identified 15 stream candidates.
+The average heliocentric radial velocity of these members is $V_{hel} = -199$\,km s$^{-1}$, with a dispersion of 27\,km s$^{-1}$.
+When compared to other streams identified in the halo, this is an unusually wide kinematic dispersion.
+Streams are generally considered to be kinematically cold, with dispersions of $\sigma_v < 8$\,km s$^{-1}$.
+The radial velocities outputted by the RAVE survey are described to be $\sim{}2$\,km s$^{-1}$, so the wide kinematic distribution is not limited by the observational data.
 
@@
 The most comprehensive sample of Aquarius stream stars is presented in the discovery paper of \citet{Williams;et-al_2011}.
-Since the globular cluster origin claim of \citet{de_Boer;et-al_2012} is based from only a subset of these stars, we targeted stars largely from the sample of \citet{de_Boer;et-al_2012}.
-An additional star from the original \citet{Williams;et-al_2011} sample, JXXXXXXXX, was also observed.
+Since the globular cluster origin claim of \citet{de_Boer;et-al_2012} is based from a subset of six of these stars, we targeted stars largely from the sample of \citet{de_Boer;et-al_2012}.
+An additional star from the original \citet{Williams;et-al_2011} sample, J2306265-085103, was also observed.
 Program stars were observed in July 2011 and we used standard stars observed for a separate program in March 2011.
@@
 \section{Analysis}
-\ref{sec:analysis}
+\label{sec:analysis}
 
 \subsection{Radial Velocities}
-\ref{sec:radial-velocities}
+\label{sec:radial-velocities}
 The radial velocity for each star was determined in a two step method.
@@
 \subsection{Line Measurements}
-\ref{sec:line-measurements}
+\label{sec:line-measurements}
 
@@
 We employed the ATLAS9 stellar atmospheres of \citet{Castelli;Kurucz_2003} for this analysis.
-These models ignore any centre-to-limb spatial variations, assume local thermodynamic equilibrium for any volume within the star as well as overall hydrostatic equilibrium, and assumes no convective overshoot from the stellar photosphere.
-The stellar parameter spacing for these grid models is 250\,K, 0.5 dex in surface gravity and 0.5 dex in [M/H] and 0.1 dex in [$\alpha$/Fe].
-We interpolated the stellar densities, temperatures, electron pressures at all stellar depths between atmospheres using Quickhull algorithm during our analyses.
+These one-dimensional models ignore any centre-to-limb spatial variations, assume local thermodynamic equilibrium as well as overall hydrostatic equilibrium, and assumes no convective overshoot from the photosphere.
+The stellar parameter spacing for these grid models is 250\,K, 0.5 dex in surface gravity, 0.5 dex in [M/H] and 0.1 dex in [$\alpha$/Fe].
+We interpolated the stellar densities, temperatures, electron pressures at all stellar depths between atmospheres using the Quickhull algorithm during our analyses.
 Quickhull is reliant on Delaunay tessellation, which suffers from extremely skewed cells when the grid points vary in size by orders of magnitude -- as $T_{eff}$ values do compared to $\log{g}$ or [M/H].
-If unaccounted for, this can result as non-negligible errors in interpolated photospheric quantities across all stellar depths.
+If unaccounted for, these asymmetric cells can manifest as non-negligible errors in interpolated photospheric quantities across all photospheric depths.
 As such, we scaled each stellar parameter between zero and unity prior to interpolation.
@@
 \subsection{Stellar Parameters}
-The most recent version of the spectral synthesis code MOOG \citep{Sneden;et-al_1973, Sobeck;et-al_2011} has been used to derive individual line abundances and stellar parameters.
-This version employs a more accurate treatment of Rayleigh scattering, which is particularly important for transitions blueward of 450\,nm but less relevant for this analysis.
+The most recent version of the spectral synthesis code MOOG \citep{Sneden;et-al_1973} has been used to derive individual line abundances and stellar parameters.
+This version employs a more accurate treatment of Rayleigh scattering \citet{Sobeck;et-al_2011}, which is particularly important for transitions blueward of 450\,nm but less relevant for this analysis as most of our line measurements are redward of 450\,nm.
+During our analysis we employed the updated solar abundances of \citet{Asplund;et-al_2009}.
+
+The effective temperature for each star was found by demanding a zero-trend in excitation potential and abundance for each measured Fe\,I line.
+In the same way, the microturbulence was found by demanding a zero trend in reduced equivalent width against abundance.
+Linear relationships with slopes of |0.03| dex were considered to be converged.
+Surface gravity was found by forcing the mean Fe\,I and Fe\,II abundances to be equal, whilst maintaining zero trends with the excitation potential, reduced equivalent width and abundance.
+After these parameters had converged, the model metallicity was exactly matched to that of our line abundances.
+Line abundances that were unusually deviant ($>3\sigma$) from the mean were removed.
+
+Stellar parameters for our standard stars are listed in Table \ref{fig:standards-stellar-parameters}.
+We find an excellent agreement with that of \citet{Gratton;et-al} and \citet{Fulbright;et-al_1997} and no systematic differences are present.
+In contrast, the stellar parameters we deduce for our Aquarius stream program stars are significantly different both from those found by the RAVE pipeline \citep{}, as listed in \citet{Williams;et-al_2011}, and those found by \citet{Wylie-de-boer;et-al_2012} with medium-resolution spectroscopy.
 
@@
 \section{Discussion}
+
+% RAVE pipeline discrepancies
+
+\subsection{Stellar Parameter Discrepancies with \citet{wylie-de-boer;et-al_2012}}
+
+We repeated our equivalent-width analysis using the atomic line list supplied in \citet{wylie-de-boer;et-al_2012}.
+Given the lower spectral resolution and modest signal-to-noise in their study, there are fewer unblended absorption lines available.
+In fact, there are very few transitions present in their published line list: only 14 Fe\,I lines and 3 Fe\,II lines are available.
+The oscillator strengths for these lines were calculated from a reverse spectral analysis using the \citet{Hinkle;et-al_2003} solar atlas.
+
+In contrast, we present 52 Fe\,I and 13 Fe\,II lines that have been cleanly selected with great
+
+The NIST database contains X
 
@@
 
-\subsection{Observations}
-
-\begin{deluxetable*}{lcccccccc}
-\tablecolumns{2}
-\tabletypesize{\scriptsize}
-\tablecaption{Observed Targets\label{tab:observed-targets}}
-\tablehead{
-	\colhead{Star} &
-	\colhead{$\alpha$} &
-	\colhead{$\delta$} &
-	\colhead{Observed} &
-	\colhead{Air mass} &
-	\colhead{Seeing} &
-	\colhead{S/N\tablenotemark{a}} &
-	\colhead{$V_{\mbox{helio}}$} &
-	\colhead{Comment} \\
- & (J2000) & (J2000) & & & (") & (px$^{-1}$) & (km s$^{-1}$) & \\
-}
-\startdata
-
-AQS 1 & 12 43 42.9 & -44 40 35.8 & April 2011 & ? & ? & 260 & ? & ? \\
-AQS 2 & 12 51 24.8 & -13 29 31.3 & April 2011 & ? & ? & 232 & ? & ? \\
-
-\enddata
-\tablenotetext{a}{S/N measured at 600 nm for each target.}
-\end{deluxetable*}
-
 \end{document}

### 2012-11-20 2012-aqs/draft-aqs.tex
Updates

@@
 % is it a real substructure
+\citet{Williams;et-al_2011} quantified the statistical significance of the Aquarius substructure with comparisons to the Besancon and Galaxia models.
+After populating the models, the galaxy representations were discretized in $\Delta{}V_{hel}$ and $\Delta{}l$ grid blocks.
+
+There is no reason to suspect that the Aquarius stream is not a real substructure.
+
+% What is it?
+Given the extent of stellar debris the Sagittarius dwarf has littered in the Milky Way, it is reasonable to suspect the Aquarius stream may simply be Sagittarius in origin.
+Although the metallicities reported by \citet{Williams;et-al_2011} are not dissimilar from the stream, the distances and $V_{Z}$, $V_\phi$ for Aquarius are quite distinct from Sagittarius.
+\citet{Williams;et-al_2011} concluded that the newly discovered stream could not be positively associated with the Monoceros stream, Hercules-Aquila cloud, or either the Canis Major or Virgo Overdensities.
 
 % MRS follow-up by de boer
+In order to investigate the Aquarius progenitor and any possible association with existing substructures, \citet{Wylie-de_boer;et-al_2012} observed six Aquarius stream members with medium resolution (R = 25,000) spectroscopy.
+Their data indicates the stream is chemically coherant, with a dispersion of only 0.1\,dex.
+Based on sodium and nickel abundance ratios with respect to iron, they claim the Aquarius stream chemical signatures unambiguously represent those of a globular cluster.
+Additional abundances of oxygen, magnesium and aluminium are reported to solidify this claim.
 
@@
 
-We seek to investigate the globular cluster origin claim made by \citet{de_Boer;et-al_2012}.
+We seek to investigate the globular cluster origin claim made by \citet{wylie-de_Boer;et-al_2012}.
 We present a detailed chemical abundance analysis for six confirmed Aquarius stream members observed using the Magellan Inamori Kyocera Echelle spectrograph \citep{Bernstein;et-al_2002} on the Magellan telescope.
@@
 \label{sec:radial-velocities}
-The radial velocity for each star was determined in a two step method.
-Initially each normalised, stitched spectrum was cross-correlated with a synthetic spectrum of a K0 giant with $T_{eff} = 4500$\,K, $\log{g} = 1.5$, and [M/H] $= -1.0$ across the wavelength range $8450 - 8700$ \AA{}.
-Velocities found during our cross-correlation are typically within 1\,km s$^{-1}$, and this measurement is used to place each spectrum at its approximate rest wavelength.
-The rest spectrum was used to measure equivalent widths for N absorption lines in each spectrum (\S\ref{sec:line-measurements}).
-The measurement of equivalent widths involves fitting a Gaussian profile to each absorption feature.
-Thus, in addition to an equivalent width, the measured central wavelength is found from the Gaussian centroid.
-The ratio between the measured central wavelength and the laboratory rest wavelength is primarily determined by the stellar radial velocity.
-Thus, we have N measurements of the stellar radial velocity.
+The radial velocity for each star was determined in a two-step method.
+An initial estimate of the radial velocity was ascertained by cross-correlation with a synthetic spectrum of a giant with $T_{eff} = 4500$\,K, $\log{g} = 1.5$, and [M/H] $= -1.0$ across the wavelength range $8450 - 8700$ \AA{}, allowing us to place our spectrum at pseudo-rest.
+Velocities found from cross-correlation are typically within 1\,km\,s$^{-1}$ of our final published value.
 
-The second step of our radial velocity determination is to find the mean offset and standard deviation from this distribution of line velocity measurements.
+The equivalent widths for $\sim{}N$ absorption lines were measured, allowing for the radial velocity of each line to be calculated from the ratio of laboratory and rest wavelengths.
+The final radial velocity is then given by the mean of these $\sim{}N$ measurements.
 Figure \ref{fig:line-velocities} shows the line velocities for HD440077 after  being placed at rest using our cross-correlation velocity of X.XX\,km s$^{-1}$.
@@
 The radial velocities published in Table \ref{tab:observations} are the final values from this two-step method.
+Heliocentric velocities agree excellently () with previously reported literature values \citep{Williams;wylie-de_boer;2012}.
 
@@
 
+% equivalent widths plot with Norris for HD 122563
+
+% equivalent widths table
+
 \subsection{Model Atmospheres}
@@
 Quickhull is reliant on Delaunay tessellation, which suffers from extremely skewed cells when the grid points vary in size by orders of magnitude -- as $T_{eff}$ values do compared to $\log{g}$ or [M/H].
-If unaccounted for, these asymmetric cells can manifest as non-negligible errors in interpolated photospheric quantities across all photospheric depths.
-As such, we scaled each stellar parameter between zero and unity prior to interpolation.
+If unaccounted for, these asymmetric cells can manifest as non-negligible errors in interpolated densities, temperatures, pressures, and opacities across all photospheric depths.
+We scaled each stellar parameter between zero and unity prior to interpolation to minimise these errors.
 During this step, $\log{g}$, [Fe/H] and [$\alpha$/Fe] points were scaled such that we simultaneously interpolate linearly in $T_{eff}$ and logarithmically in all other parameters.
@@
 The most recent version of the spectral synthesis code MOOG \citep{Sneden;et-al_1973} has been used to derive individual line abundances and stellar parameters.
-This version employs a more accurate treatment of Rayleigh scattering \citet{Sobeck;et-al_2011}, which is particularly important for transitions blueward of 450\,nm but less relevant for this analysis as most of our line measurements are redward of 450\,nm.
-During our analysis we employed the updated solar abundances of \citet{Asplund;et-al_2009}.
+This version employs a more accurate treatment of Rayleigh scattering \citet{Sobeck;et-al_2011}, which is particularly important for transitions blueward of 450\,nm.
+This is noteworthy, but is less relevant for this analysis as most of our line measurements blueward of 450\,nm are too blended and not used.
+We have scaled our abundances to solar values using the abundances of \citet{Asplund;et-al_2009}.
 
@@
 In the same way, the microturbulence was found by demanding a zero trend in reduced equivalent width against abundance.
-Linear relationships with slopes of |0.03| dex were considered to be converged.
+Linear relationships with slopes of $|0.005|$ dex were considered to be converged.
 Surface gravity was found by forcing the mean Fe\,I and Fe\,II abundances to be equal, whilst maintaining zero trends with the excitation potential, reduced equivalent width and abundance.
@@
 Line abundances that were unusually deviant ($>3\sigma$) from the mean were removed.
+The largest number of outlier measurements removed for any observation was N for X.
 
-Stellar parameters for our standard stars are listed in Table \ref{fig:standards-stellar-parameters}.
-We find an excellent agreement with that of \citet{Gratton;et-al} and \citet{Fulbright;et-al_1997} and no systematic differences are present.
-In contrast, the stellar parameters we deduce for our Aquarius stream program stars are significantly different both from those found by the RAVE pipeline \citep{}, as listed in \citet{Williams;et-al_2011}, and those found by \citet{Wylie-de-boer;et-al_2012} with medium-resolution spectroscopy.
+% spectral plots for five stars
+
+\begin{deluxetable*}{lcccccccccccccc}
+\tablecolumns{2}
+\tabletypesize{\scriptsize}
+\tablecaption{Stellar Parameters}
+\tablehead{
+	\colhead{Designation} &
+	\colhead{$T_{\mbox{eff}}$} &
+	\colhead{$\log{g}$} &
+	\colhead{$v_t$} &
+	\colhead{[Fe/H]} & 
+	\colhead{$T_{\mbox{eff}}$} &
+	\colhead{$\log{g}$} &
+	\colhead{$v_t$} &
+	\colhead{[Fe/H]} &
+	\colhead{Source} \\
+}
+\startdata
+C2225316-14437	& 4350	& 1.60	& 1.80	& --1.19	
+				& 4235 $\pm$ 118 & 1.45 $\pm$ 0.21 & 1.96 $\pm$ 0.11 & --1.20 $\pm$ 0.14 \\
+C2306265-085103	& 4180	& 1.00	& 1.80 	& --1.16
+				& \dots	& \dots	& \dots	& \dots
+				& \dots \\	
+HD41667			& 4630	& 1.70	& 1.66 	& --1.21
+				& 4605	& 1.88	& 1.44	& --1.16
+				& \citet{Gratton;et-al_2000} \\
+HD44007			& 4790	& 1.78	& 1.63	& --1.80
+				& 4850	& 2.00 	& 2.20	& --1.71
+				& \citet{Fulbright_2000} \\
+HD142948		& 4950	& 2.19	& 1.78	& --0.79
+				& 4713 	& 2.17 	& 1.38	& --0.77
+				& \citet{Gratton;et-al_2000} \\
+J221821-183424	& 4570	& 0.80	& 1.93	& --1.60
+				& 4395 $\pm$ 205 & 1.45 $\pm$ 0.35 & 1.96 $\pm$ 0.18 & --1.15 $\pm$ 0.21
+				& \citet{wylie-de-boer;et-al_2012} \\
+J223504-152834	& 4620	& 2.15 	& 1.44	& --0.65
+				& 4597 $\pm$ 158 & 2.40 $\pm$ 0.14 & 1.47 $\pm$ 0.07 & --0.98 $\pm$ 0.17
+				& \citet{wylie-de-boer;et-al_2012} \\
+J223811-104126	& 5100	& 3.00	& 1.21	& --1.44
+				& 5646 $\pm$ 147 & 4.60 $\pm$ 0.15 & 1.09 $\pm$ 0.11 & --1.20 $\pm$ 0.20
+				& \citet{wylie-de-boer;et-al_2012} 
+\enddata
+
+\end{deluxetable*}
 
 \subsection{Abundances}
+
+% elemental abundances
+
+% comparison to literature for a given star
+
+% chemical synthesis
+
+\subsection{Distances}
+% isochrone fitting
+
+% discuss Williams et al distances
+
+\subsection{Dynamics}
+
+% U, V, W calculations
 
@@
 % RAVE pipeline discrepancies
+
+% wylie de boer discrepancies
 
@@
 
-In contrast, we present 52 Fe\,I and 13 Fe\,II lines that have been cleanly selected with great
+% Chemistries for various GC trends
 
-The NIST database contains X
+% chemistries - [Ni/Na]
+
+% chemistries - [Al/Mg]
+
+% which GC's do not show these trends
+
+% closest looking globular clusters from Harris catalogue
+
+% could they be displaced thick disk stars?
 

### 2012-11-21 2012-aqs/figures/plot-na-o.py
Added EW comparison plot with Norris, and data from Carretta for Na-O

@@ -1,0 +1,53 @@
+import matplotlib.pyplot as plt
+
+#NGC;ID;Bmag;Vmag;Icmag;Kmag;RV11;RV13;Teff;[FeI/H];e_[FeI/H];[O/Fe];e_[O/Fe];l_[Na/Fe];[Na/Fe];e_[Na/Fe];RAJ2000;DEJ2000
+# ; ;mag;mag;mag;mag;km/s;km/s;K;[Sun];[Sun];[Sun];[Sun]; ;[Sun];[Sun];"h:m:s";"d:m:s"
+
+
+Fe_I, e_Fe_I, O_Fe, e_O_Fe, l_Na_Fe, Na_Fe, e_Na_Fe = np.loadtxt('caretta-et-al-2009-O-Na.txt', skiprows=67, delimiter=';', \
+														usecols=(9, 10, 11, 12, 13, 14, 15, ), unpack=True, dtype=str)
+
+# Replace invalid items with np.nans
+
+def clean(array):
+
+	new_array = []
+	for item in array:
+		try:
+			item = float(item)
+
+		except ValueError:
+			new_array.append(np.nan)
+
+		else:
+			new_array.append(item)
+
+	return np.array(new_array)
+
+
+Fe_I, e_Fe_I, O_Fe, e_O_Fe, Na_Fe, e_Na_Fe = map(clean, [Fe_I, e_Fe_I, O_Fe, e_O_Fe, Na_Fe, e_Na_Fe])
+
+
+
+fig = plt.figure()
+ax = fig.add_subplot(111)
+
+# Oxygen upper limits
+upper_limits = np.where(e_O_Fe == 9.999)[0]
+measurements = np.array(list(set(range(len(O_Fe))).difference(upper_limits)))
+
+ax.errorbar(O_Fe[upper_limits], Na_Fe[upper_limits], xerr=0.02, xlolims=True, fmt=None, ecolor='k')
+#ax.errorbar(O_Fe[upper_limits], Na_Fe[upper_limits], facecolor='none', edgecolor='k')
+#ax.errorbar(O_Fe[measurements], Na_Fe[measurements], xerr=e_O_Fe[measurements], yerr=e_Na_Fe[measurements], fmt=None)
+
+ax.scatter(O_Fe[measurements], Na_Fe[measurements], facecolor='none', edgecolor='k')
+
+ax.set_xlabel('[O/Fe]')
[…]

### 2012-11-21 2012-aqs/figures/plot-smh-norris.py

@@ -1,0 +1,58 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib.gridspec as gridspec
+
+wavelength, smh_ew, norris_ew = np.loadtxt('SMH-Norris-comparison.data', usecols=(0, 1, 2, ), unpack=True)
+
+fig = plt.figure(figsize=(6,7))
+fig.subplots_adjust(hspace=0.0, wspace=0.0)
+gs = gridspec.GridSpec(2, 1, height_ratios=[1, 2])
+
+ax1 = fig.add_subplot(gs[0])
+#ax1 = plt.subplot2grid((3, 1), (0, 0))
+
+ax1.scatter(smh_ew, smh_ew - norris_ew, facecolor='none', edgecolor='k')
+ax1.plot([0, 200], [0, 0], 'k-', zorder=-1)
+
+A = np.vstack([smh_ew, np.ones(len(norris_ew))]).T
+m, c = np.linalg.lstsq(A, smh_ew - norris_ew)[0]
+x = np.array([np.min(smh_ew), np.max(smh_ew)])
+ax1.plot(x, m * x + c, 'k:')
+
+ylim = np.max(np.abs(np.array(ax1.get_ylim())))
+ax1.set_ylim(-15, 15)
+
+ax1.xaxis.set_visible(False)
+ax1.set_ylabel('$\Delta{}W_\lambda$ [m$\AA{}$]')
+
+
+ax2 = fig.add_subplot(gs[1], sharex=ax1)
+#ax2 = plt.subplot2grid((3, 1), (1, 0), rowspan=2)
+ax2.scatter(smh_ew, norris_ew, facecolor='none', edgecolor='k')
+
+A = np.vstack([norris_ew, np.ones(len(norris_ew))]).T
+m, c = np.linalg.lstsq(A, smh_ew)[0]
+x = np.array([0, 200])
+ax2.plot(x, x, 'k-', zorder=-1)
+x = np.array([np.min(smh_ew), np.max(smh_ew)])
+ax2.plot(x, m * x + c, 'k:')
+
+ax1.set_xlim(0, 160)
+ax2.set_xlim(0, 160)
+ax2.set_ylim(0, 160)
+
+ax2.set_xlabel('$W_\lambda$ (This work, automatic) [m$\AA{}$]')
+ax2.set_ylabel('$W_\lambda$ (Norris et al. 2000) [m$\AA{}$]')
+
[…]

### 2012-11-21 2012-aqs/draft-aqs.tex
Inserted figure

@@
 A minimum detectable equivalent width was measured as a function of wavelength, and only lines that exceeded a $3\sigma$ detection significance were included.
-We have verified our equivalent width measurement techniques by measuring equivalent widths for N lines in HD122563 and comparing our measurements with the study of \citet{Norris;et-al_2000}.
+We have verified our equivalent width measurement techniques by measuring equivalent widths for N lines in HD140283 and comparing our measurements with the study of \citet{Norris;et-al_2000}.
 Excellent agreement is found between the two studies, which is illustrated in Figure \ref{fig:ew-compare}.
-The mean difference between this study and that of \cite{Norris;et-al_2000} is a negligible $X.X \pm X.X$\,m\AA{}, and no systematic trend is present.
+The mean difference between this study and that of \cite{Norris;et-al_2000} is a negligible $0.64 \pm 2.78$\,m\AA{}, and no systematic trend is present.
 
 % equivalent widths plot with Norris for HD 122563
+\begin{figure}[h]
+	\includegraphics[width=\columnwidth]{./figures/smh-norris.pdf}
+	\caption{The gold standard comparison.}
+	\label{fig:ew-compare}
+\end{figure}
 

### 2012-12-03 2012-oss-mrs/Response_to_referee_report.txt
Re-submitted version after GDC and SK comments

@@
 Following sentence edited to minimise repeated words.
-Text now reads as 'Stars which were once gravitationally bound to the satellite are strewn along the progenitor's orbit in leading and trailing streams of stars.
+Text now reads as 'Stars which were once gravitationally bound to the satellite are distributed along the progenitor's orbit in leading and trailing streams of stars.
 The kinematics of the stream..'
@@
 
-9) In the first paragraph, it is not clear from Figure 2 why this
-particular separation line is appropriate or optimal.
-More explanation and references should be provided.
-Also, ``allowing multiple inclusive cuts' is somewhat confusing.
-Should this be ``imposing simultaneous cuts on several observables'?
+9) In the first paragraph, it is not clear from Figure 2 why this particular separation line is appropriate or optimal. More explanation
+and references should be provided. Also, ``allowing multiple inclusive cuts' is somewhat confusing. Should this be ``imposing simultaneous 
+cuts on several observables'?
+
+We have added additional text explaining Figure 2, and why the adopted separation line is appropriate for this work.
+
+``allowing multiple inclusive cuts'' was confusing.
+The final text for this paragraph now reads as '..we are also employing selections on multiple observables (kinematics, metallicity, proper motions) in order to refine our Orphan Stream giant sample.'
 
@@
 Response:
-Text now reads as 'This fraction of giants ($\sim$44\%) is much larger than that found by \citeauthor{Casey_et-al_2012} \citeyear{Casey_et-al_2012}a who employed a similar colour selection.'
-
+The text now reads: 'Given the target selection, our sample is likely to contain many more dwarfs than giants (e.g. see \citet{Casey_et-al_2012} where a similar colour selection was employed).' 
 Section 4.3
@@
 Response:
-Corrected.
+Corrected this typo.
 
-12) In Table 1, the ra and dec components of proper motion should be listed separately.
-Strong cross-stream proper motion components could also be used to remove or reduce membership probabilities for some stars.
-
-13) Given the small number and significant color and magnitude spread among the highly probable members about the best-fitting isochrone in Figure 4, a distance uncertainty of only 1 kpc seems unlikely.
-How was this uncertainty estimated?
+12) In Table 1, the ra and dec components of proper motion should be listed separately. Strong cross-stream proper motion components could 
+also be used to remove or reduce membership probabilities for some stars.
 
 Response:
+The proper motion components in Table 1 are now listed separately.
+It seems there was an error in the original calculation for the total proper motion of OSS-1.
+Instead of the proper motion being added in quadrature, the uncertainties were added in quadrature for both the measurement and it's uncertainty (yielding a $mu_{tot} = 6.1 \pm 6.1$).
+The proper motions are actually (4.1 +/- 4.5, -34.0 +/- 4.5) in RA and Dec respectively.
+As OSS-1 was already classified as a low-probability member based on inconsistent metallicities between Ca line strengths and isochrone fitting, this makes no change to the probability assignment.
 
-14) The last sentence should include ``21.4 +/- 1 kpc estimated by Grillmair (2006) and Newberg et al.
-(2010).', since the distance estimates in these papers were independent and complementary, one using main sequence fitting and the other using BHB stars.
+13) Given the small number and significant color and magnitude spread among the highly probable members about the best-fitting isochrone in 
+Figure 4, a distance uncertainty of only 1 kpc seems unlikely. How was this uncertainty estimated?
+
+Response:
+The distance uncertainty is now determined from propagating the metallicity uncertainty (0.2 dex). A revised distance uncertainty of 2.0 kpc is now reflected throughout the text.
+
+14) The last sentence should include ``21.4 +/- 1 kpc estimated by Grillmair (2006) and Newberg et al. (2010).', since the distance estimates 
+in these papers were independent and complementary, one using main sequence fitting and the other using BHB stars.
 
@@
 
+Response:
+Reference added.
+
 16) The last sentence of the first paragraph should also refer to
@@
 
-17) Given the title of the paper, does the new metallicity measurement help in any way to identify a possible progenitor?
-At the very least, a statement should be included to the extent that the orbit and the metallicity measurements rule out any of the classical dwarfs, and that if a bound progenitor still exists, then it must be an as yet undiscovered ultrafaint dwarf.
+17) Given the title of the paper, does the new metallicity measurement help in any way to identify a possible progenitor? At the very least, 
+a statement should be included to the extent that the orbit and the metallicity measurements rule out any of the classical dwarfs, and that 
+if a bound progenitor still exists, then it must be an as yet undiscovered ultrafaint dwarf.
 
-18) The maximum likelihood estimates of the stream velocity given by the authors are either 85.3 /pm 4.4 km/s, or 82.1 /pm 1.4 km/s.
-A simple weighted mean of the values in Table 1 gives 83.0 km/s.
-This is very significantly different from the 105 km/s (using the author's V_gsr system) measured by Newberg et al.
-for the same part of the stream using BHB stars.
-This disagreement needs to be addressed, as it seriously undermines any confidence in the purity of even the ``high probability' sample.
+Response:
+Added text: 'Given the stream orbit derived by \citet{Newberg_et-al_2010}, they excluded all possible known halo objects except for the dissolved star cluster, Segue 1.
+\citet{Simon_et-al_2011} obtained spectroscopy for six members in Segue 1 and found an extremely wide metallicity dispersion: from $<-3.4$ to $-1.63$ dex.
+On the basis of the extremely low metallicity in the cluster and the wide chemical dispersion, they conclude that Segue 1 is a disrupted dwarf spheroidal galaxy.
+Although the data presented here indicates the Orphan Stream progenitor is a disrupted dwarf spheroidal galaxy, we cannot reliably associate Segue 1 as the parent without additional observational data.'
 
-19) Moreover, though it is somewhat difficult to say given small number statistics, the metallicity distribution of the high probability stars looks more similar to the that of the off-stream, field star sample of Newberg et al.
-than it does to that of the stream sample.
+18) The maximum likelihood estimates of the stream velocity given by the authors are either 85.3 /pm 4.4 km/s, or 82.1 /pm 1.4 km/s. A simple
+weighted mean of the values in Table 1 gives 83.0 km/s. This is very significantly different from the 105 km/s (using the author's V_gsr system) 
+measured by Newberg et al. for the same part of the stream using BHB stars. This disagreement needs to be addressed, as it seriously undermines 
+any confidence in the purity of even the ``high probability' sample.
 
-20) Newberg et al.
-find velocity dispersions in various parts of the Orphan stream of around 10 km/s.
-Here the case is made for a much lower velocity dispersion, even colder than that of globular cluster streams like Pal 5 and GD-1.
-It may well be that Newberg et al.'s velocities are generally less accurate than the present sample.
-However, one would still have to think about how a stream that is 8-10 times broader than these globular cluster streams should be kinematically just as cold or colder.
-Unfortunately, the disagreement with previous Orphan velocity measurements, and the fact that removing the weak signal stars makes this disagreement even larger while making the stream colder, undermines my confidence considerably.
+Response:
+This disagreement was of concern to the authors before the initial manuscript was submitted.
+We believe this discrepancy is now resolved.
+We quoted the galactocentric velocity of the stream to be 110 km/s as per Newberg et al.
+2011.
+This was somewhat misleading.
+Newberg et al.
+2011 quotes the mean galactocentric velocity in their conclusions, where this number was originally taken from.
+However, in Table 2 of Newberg et al.
+2011 they find a galactocentric velocity of 101.4 km/s at Lambda_Orphan = 18.4 degrees.
+This is the closest detection to our fields, at Lambda_Orphan ~= 23 degrees.
+The referee will recall that this is ~95 km/s on our galactocentric velocity scale.
+There is a sharp velocity gradient along the stream, decreasing to 38.4 km/s at Lambda_Orphan = 36 degrees.
+Therefore, at Lambda_Orphan ~= 23 degrees, a galactocentric velocity of 85-90 km/s (or 80-85 km/s on our scale) is quite reasonable.
+This 'back of the envelope' calculation ignores the intrinsic uncertainty in BHB velocities, or the uncertainties quoted by Newberg et al 2011 of 101.4 km/s +/- 2.9 +/- 9.8 km/s.
 
-21) In thinking about this, I have made use of a velocity versus metallicity plot, with appropriate uncertainties.
-This makes it much easier to see why the authors are getting the results they see, and I would strongly recommend including such a plot in the final manuscript.
+Since this implies our initial kinematic selection should actually be between 65 <= V_GSR <= 125 km/s (on our scale), this required a re-analysis of stars in the V_GSR range between 65-75 km/s.
+No candidates had velocities between 125-135 km/s, thus none were excluded.
+We identified two more possible candidates that also met our dwarf/giant constraint, and measured their metallicities.
+These are medium-probability candidates (OSS 15, 20) and have been added to Table 1.
+Additional explanatory text has been added to the manuscript explaining the velocity results we find in comparison with Newberg et al in Section 4.4
+We are glad this error has been spotted and corrected.
 
-22) The last sentence of the 3rd paragraph is somewhat mysterious.
-Is it the random motions that must be perpendicular to the line of sight, or the mean motions?
-The latter follows from the simple fact that the stars are in a stream, and the stream is nearly perpendicular to our line of sight.
-Unless I'm missing something important, this sentence should be deleted.
+19) Moreover, though it is somewhat difficult to say given small number statistics, the metallicity distribution of the high probability stars 
+looks more similar to the that of the off-stream, field star sample of Newberg et al. than it does to that of the stream sample.
+
+20) Newberg et al. find velocity dispersions in various parts of the Orphan stream of around 10 km/s. Here the case is made for a much lower 
+velocity dispersion, even colder than that of globular cluster streams like Pal 5 and GD-1. It may well be that Newberg et al.'s velocities are
+generally less accurate than the present sample. However, one would still have to think about how a stream that is 8-10 times broader than these 
+globular cluster streams should be kinematically just as cold or colder. Unfortunately, the disagreement with previous Orphan velocity measurements,
+and the fact that removing the weak signal stars makes this disagreement even larger while making the stream colder, undermines my confidence considerably.
+
+21) In thinking about this, I have made use of a velocity versus metallicity plot, with appropriate uncertainties. This makes it much easier to 
+see why the authors are getting the results they see, and I would strongly recommend including such a plot in the final manuscript.
+
+Response to (19), (20), (21):
+Two additional plots have been added to the manuscript.
+The first is a plot showing the velocity and metallicity of our highly probable candidates.
+The second is a histogram showing the metallicity distribution function for our sample, with a comparison to the [Fe/H] of BHB stars in Newberg et al.
+2011.
+The velocity discrepancy with Newberg et al.
+(2011) has been resolved in (18), and additional discussion text has been added addressing the metallicity differences in Section 4.4.
+
+22) The last sentence of the 3rd paragraph is somewhat mysterious. Is it the random motions that must be perpendicular to the line of sight, or 
+the mean motions? The latter follows from the simple fact that the stars are in a stream, and the stream is nearly perpendicular to our line of 
+sight. Unless I'm missing something important, this sentence should be deleted.
+
+Response:
+Removed the last sentence. It was a bit ambiguous. Sorry about that. AC
 

### 2012-12-03 2012-oss-mrs/ms.tex
Re-submitted version after GDC and SK comments

@@
 \usepackage{amssymb,graphics} % for resolution symbol
+\usepackage{multirow} % deluxetable wasn't doing it for me.
 
@@
 
-\author{Andrew R. Casey\altaffilmark{1,2}, Stefan C. Keller\altaffilmark{1}, Gary Da Costa\altaffilmark{1}, Elizabeth Maunder\altaffilmark{1}}
+\author{Andrew R. Casey\altaffilmark{1,2}, Gary Da Costa\altaffilmark{1}, Stefan C. Keller\altaffilmark{1}, Elizabeth Maunder\altaffilmark{1}}
 \altaffiltext{1}{Research School of Astronomy \& Astrophysics, Australian National University, Mount Stromlo Observatory, via Cotter Rd, Weston, ACT 2611, Australia; \email{acasey@mso.anu.edu.au}}
-\altaffiltext{2}{Kavli Institute for Astrophysics and Space Research, Massachusetts Institute of Technology, 77 Massachusetts Avenue, Cambridge, MA 02139, USA}
+\altaffiltext{2}{Massachusetts Institute of Technology and Kavli Institute for
+Astrophysics and Space Research, 77 Massachusetts Avenue,
+Cambridge, MA 02139, USA}
 
 \begin{abstract}
-We present coordinates and properties of candidate K giant members in the Orphan Stream, which have been identified from low-resolution spectroscopic data taken with AAOmega on the Anglo-Australian Telescope.
+We present candidate K-giant members in the Orphan Stream which have been identified from low-resolution data taken with the AAOmega spectrograph on the Anglo-Australian Telescope.
 From modest S/N spectra and independent cuts in photometry, kinematics, gravity and metallicity we yield self-consistent, highly probable stream members.
-We find a revised stream distance of $22.5\,\pm\,1.0$\,kpc near the celestial equator, and our kinematic signature peaks at $V_{GSR} = 82.1\,\pm\,1.4$\,km s$^{-1}$.
+We find a revised stream distance of $22.5\,\pm\,2.0$\,kpc near the celestial equator, and our kinematic signature peaks at $V_{GSR} = 82.1\,\pm\,1.4$\,km s$^{-1}$.
 The observed velocity dispersion of our most probable members is consistent with arising from the velocity uncertainties alone.
-This indicates that at least along the line-of-sight, the Orphan Stream is kinematically quite cold.
+This indicates that at least along this line-of-sight, the Orphan Stream is kinematically cold.
 Our data indicates an overall stream metallicity of [Fe/H] $= -1.63\,\pm\,0.19$\,dex which is more metal-rich than previously found and unbiased by spectral type.
-Furthermore, the significant metallicity dispersion displayed by our probable members, $\sigma = 0.56$\,dex, suggests that the unidentified Orphan Stream parent is a dSph satellite.
+Furthermore, the significant metallicity dispersion displayed by our most probable members, $\sigma(\mbox{[Fe/H]}) = 0.56$\,dex, suggests that the unidentified Orphan Stream parent is a dSph satellite.
 We highlight likely members for high-resolution spectroscopic follow-up.
@@
 
-The Milky Way stellar halo has partly formed through the accretion of satellites which are disrupted by tidal forces as they fall into the Milky Way's potential.
-Stars which were once gravitationally bound to the satellite are strewn along the progenitor's orbit in leading and trailing streams of stars.
-The kinematics of the stream are sensitive to the shape of the galactic potential, allowing us to constrain the Milky Way potential, and reconstruct the formation history of the Galaxy.
+The Milky Way stellar halo has partly formed through the accretion of satellites that are disrupted by tidal forces as they fall into the Galaxy's potential.
+Stars which were once gravitationally bound to the satellite are distributed along the progenitor's orbit in leading and trailing streams of stars.
+The velocities of stars in the stream are sensitive to the shape of the dark matter halo, allowing us to constrain the Milky Way potential and reconstruct the formation history of the Galaxy.
 The level of accreted substructure in the Milky Way has only recently become apparent through multi-band photometric surveys like the Sloan Digital Sky Survey (SDSS).
@@
 
+% could add a sentence to the paragraph above discussing the various substructures that have been detected
+
 The Orphan Stream was independently detected by both \citet{Grillmair_2006} and \citet{Belokurov_et-al_2006}, and is distinct from other substructures in the halo.
-The stream stretches over $60\,^\circ$ in the sky, has a low surface brightness and a narrow stream width of only $\sim$2\,$^\circ$ and as the name suggests, the parent object largely remains a mystery.
+The stream stretches over $60\,^\circ$ in the sky, has a low surface brightness, and a narrow stream width of only $\sim$2\,$^\circ$.
+As the name suggests, the parent object largely remains a mystery.
 The stream extends past the celestial equator \--- outside the SDSS footprint \--- but has not been detected in existing southern surveys \citep{Newberg_et-al_2010}.
 Whilst the parent system remains elusive, significant effort has been placed on associating the stream with known Milky Way satellites \citep{Zucker_et-al_2006, Fellhaur_et-al_2007,Jin_Lynden_Bell_2007,Sales_et-al_2008}.
-In contrast, there has been relatively limited observational work on the Orphan Stream itself other than the original discovery papers \citep{Grillmair_Dionatos_2006, Belokurov_et-al_2006, Belokurov_et-al_2007} and the work of \citet{Newberg_et-al_2010}.
-This is largely to be expected given the absence of multi-band photometry in the southern sky and the low total luminosity of the stream, making it difficult to reliably separate Orphan Stream members from halo stars.
-Further understanding on the extent of the stream awaits the SkyMapper and Pan-STARRS photometric surveys \citep{Keller_et-al_2007, Hodapp_et-al_2004}.
+In contrast, there has been relatively limited observational work on the Orphan Stream itself other than the original discovery papers \citep{Grillmair_2006, Belokurov_et-al_2006, Belokurov_et-al_2007} and the work of \citet{Newberg_et-al_2010}.
+This is largely to be expected given the absence of deep multi-band photometry in the southern sky and the low total luminosity of the stream.
+This makes it difficult to reliably separate Orphan Stream members from halo stars.
+Understanding the full extent of the stream awaits the SkyMapper and Pan-STARRS photometric surveys \citep{Keller_et-al_2007, Hodapp_et-al_2004}.
 
@@
 More complete photometric and kinematic maps of these low total luminosity streams may provide the best test as to whether this mass discrepancy is real, or an artefact of incomplete observations.
-Whilst the full spatial extent of the Orphan Stream remains incomplete, we can examine the detailed chemistry of its members and investigate the stream history, as well as make predictions about the nature of the progenitor.
+Whilst the full spatial extent of the Orphan Stream remains unknown, we can examine the detailed chemistry of its members, investigate the stream history, and make predictions about the nature of the progenitor.
 
-In this letter we present a detailed, self-consistent analysis to identify K giant members of the Orphan Stream.
+In this paper we present a detailed, self-consistent analysis to identify K-giant members of the Orphan Stream.
 Using our selection method we have catalogued the locations of nine highly probable Orphan Stream candidates, all worthy of high-resolution spectroscopic follow up.
@@
 
-We have targeted K giant members of the Orphan Stream in order to investigate their detailed chemistry.
+We have targeted K-giant members of the Orphan Stream in order to investigate their detailed chemistry.
 Because K-giants are difficult to unambiguously detect from photometry alone, low-resolution spectroscopy is required to estimate stellar parameters and determine radial velocities.
@@
 These two locations are unequivocally the best place to recover bright stream members.
-We have targeted two fields centered on $(\alpha, \delta) =$ (10:48:15, 00:00:00) and (10:48:15, $-$02:30:00), and employed a combination of colour cuts with the SDSS DR 7 \citep{Abazajian_et-al_2009} data set in order to identify likely K giants:
+We have targeted two fields centered on $(\alpha, \delta) =$ (10:48:15, 00:00:00) and (10:48:15, $-$02:30:00), and employed a combination of colour cuts with the SDSS DR 7 \citep{Abazajian_et-al_2009} data set in order to identify likely K-giants:
 \begin{eqnarray}
@@
 
-Given our colour selection we expect to recover giants and contaminating dwarf contaminants.
+Given our colour selection we expect to recover giants and contaminating dwarfs.
 Although the 2MASS $JHK$ colours can help to separate dwarfs and giants, our target K-giants stars are too faint to be detected in the 2MASS catalogue.
@@
 After flat-fielding, throughput calibration for each fibre was achieved using the intensity of skylines in each fibre.
-The median flux of dedicated sky fibres was taken for sky subtraction, and wavelength calibration was performed using arc lamp exposures between science frames.
+The median flux of dedicated sky fibres was used for sky subtraction, and wavelength calibration was performed using ThAr arc lamp exposures taken between science frames.
 Three thirty minute science exposures were median-combined to assist with cosmic ray removal.
-The median S/N obtained in the red arm for our fields is modest at 35 per pixel.
+The median S/N obtained in the red arm for our fields is modest at 35 per pixel, although this deteriorates quickly for our fainter targets.
 With the presence of strong Ca\,\textsc{II} triplet lines in the red arm we are able to ascertain reliable radial velocities and reasonable estimates on overall metallicity \citep[][and references therein]{Starkenburg_et-al_2010}.
@@
 
-\section{Analysis}
+\section{Analysis \& Discussion}
 \label{sec:analysis}
 
-We have employed a combination of separate criteria to identify likely Orphan Stream members: kinematics, a giant/dwarf indication from Mg\,\textsc{I} lines, and consistent metallicities from isochrone fitting and the Ca\,\textsc{II} triplet lines.
+We have employed a combination of separate criteria to identify likely Orphan Stream members: kinematics, a giant/dwarf indication from Mg\,\textsc{I} lines, and selecting stars with consistent metallicities derived from both isochrone fitting and the strength of the Ca\,\textsc{II} triplet lines.
 Each criteria is discussed here separately.
@@
 \subsection{Kinematics}
-Radial velocities were measured by cross-correlating our normalised spectra against a K-giant synthetic template with a temperature of 4500\,K, $\log{g}$ = 1 and $[\mbox{Fe/H}] = -1.5$ across the range $845 \leq \lambda \leq 870$\,nm.
-Heliocentric velocities were translated to the galactic rest frame by adopting the local standard of rest velocity as 220\,km s$^{-1}$ towards $(l, b) = (53\,^\circ, 25\,^\circ)$ \citep{Kerr_Lynden-Bell_1986, Mihalas_Binney_1981}\footnote{Where $V_{GSR} = V_{\textsc{helio}} + 220\sin{l}\cos{b} + 16.5\times[\sin{b}\sin{25} + \cos{b}\cos{25}\cos{(l - 53)}]$}.
-\citet{Newberg_et-al_2010} presented a comprehensive kinematic dataset on the Orphan Stream using BHB stars and employed a slightly different galactocentric transformation.
-This systematic difference equates to our galactocentric rest frame velocities being on average $\sim$5\,km s$^{-1}$ lower than those of \citet{Newberg_et-al_2010}.
+Radial velocities were measured by cross-correlating our normalised spectra against a K-giant synthetic template with a temperature of 4500\,K, $\log{g}$ = 1.5 and $[\mbox{M/H}] = -1.5$ across the range $845 \leq \lambda \leq 870$\,nm.
+Heliocentric velocities were translated to the galactic rest frame by adopting the local standard of rest velocity as 220\,km s$^{-1}$ towards $(l, b) = (53\,^\circ, 25\,^\circ)$ \citep{Kerr_Lynden-Bell_1986, Mihalas_Binney_1981}\footnote{Where $V_{GSR} = V_{HELIO} + 220\sin{l}\cos{b} + 16.5\times[\sin{b}\sin{25^\circ} + \cos{b}\cos{25^\circ}\cos{(l - 53^\circ)}]$}.
+
+Figure \ref{fig:velocities} shows a histogram of our galactocentric velocities, compared to the predicted smooth line-of-sight velocity distribution for this region from the Besan\c{c}on model \citep{Robin_et-al_2003}.
+We have selected particles from the Besan\c{c}on model using the same criteria outlined in \S\ref{sec:target-selection} after employing the \citet{Jordi_et-al_2006} colour transformations.
+It is clear that our target selection has yielded mostly nearby disk dwarf stars with $V_{GSR} \approx -120$\,km s$^{-1}$.
 
@@
 
-Figure \ref{fig:velocities} shows a histogram of our galactocentric velocities, compared to the predicted smooth line-of-sight velocity distribution for this region from the Besan\c{c}on model \citep{Robin_et-al_2003}.
-We have selected predicted stars from the Besan\c{c}on model using the same criteria as outlined in \S\ref{sec:target-selection} after using the \citet{Jordi_et-al_2006} colour transformations.
-It is clear that our target selection has yielded mostly nearby thick disk dwarf stars with $V_{GSR} \approx -120$\,km s$^{-1}$.
-The expected kinematic signature for the Orphan Stream, as \citet{Newberg_et-al_2010} reported, is labelled in Figure \ref{fig:velocities}.
+In a nearby ($\Delta\Lambda_{Orphan} \sim 4\,^\circ$) region of the stream, \citet{Newberg_et-al_2010} detected the Orphan Stream with a $V_{GSR} = 101.4$ km s$^{-1}$ from BHB stars.
+Differences in accounting for the local standard of rest between this work and \citet{Newberg_et-al_2010} means that this corresponds to approximately 95\,km s$^{-1}$ on our $V_{GSR}$ scale.
+This is discussed further in \S\ref{sec:newberg}.
+The expected Orphan Stream kinematic peak is labelled in Figure \ref{fig:velocities}.
 There is no obvious sharp kinematic peak representative of the Orphan Stream in our sample.
 From kinematics alone, our targets appears largely indistinguishable from a smooth halo distribution.
-
-In this region \citet{Newberg_et-al_2010} found the Orphan Stream to have $V_{GSR} = 110$ km s$^{-1}$ from BHB stars, approximately $105$\,km s$^{-1}$ on our scale.
-To isolate potential Orphan Stream members we have nominated a relatively wide kinematic selection region between $75 \leq V_{GSR} \leq 135$ km s$^{-1}$, which yields twenty-five Orphan Stream candidates.
-The typical uncertainty in our velocities is $\pm{}5.0$\,km s$^{-1}$, although for our fainter targets this quickly increases above 10\,km s$^{-1}$.
+To isolate potential Orphan Stream members we have nominated a relatively wide selection criteria between $65 \leq V_{GSR} \leq 125$ km s$^{-1}$ (shown in Figure \ref{fig:velocities}), which yields 28 Orphan Stream candidates.
+The typical uncertainty in our velocities is $\pm{}5.0$\,km s$^{-1}$.
 
@@
 We have measured the equivalent width of the gravity-sensitive Mg\,\textsc{I} line at 8807 \AA{} to distinguish dwarfs from giants \citep{Battaglia_Starkenburg_2012}.
-At a given temperature (or $g - r$) and metallicity, giant stars present narrower Mg\,\textsc{I} absorption lines than their dwarf contaminants.
-Given our target selection, our sample is likely to contain many more dwarfs than giants.
-In some cases no Mg\,\textsc{I} 8807 \AA{} line was apparent, so an upper limit was estimated based on the S/N.
+At a given temperature (or $g - r$) and metallicity, giant stars present narrower Mg\,\textsc{I} absorption lines than their dwarf counterparts.
+Given the target selection, our sample is likely to contain many more dwarfs than giants (e.g.
+see \citet{Casey_et-al_2012} where a similar colour selection was employed).
+In some cases no Mg\,\textsc{I} 8807 \AA{} line was apparent, so an upper limit was estimated based on the S/N of the spectra.
 In these cases the candidate was considered a ``non-dwarf" because we cannot exclusively rule out a metal-poor sub-giant with this criteria alone.
 For these purposes we are only looking for a simple indication as to whether a star is likely a dwarf or not.
-Figure \ref{fig:ew-mg} illustrates the trend with EW$_{\lambda8807}$ against SDSS de-reddened\footnote{All magnitudes presented in this letter are de-reddened using the \citet{Schlegel_Finkbeiner_Davis_1998} dust maps.} $g - r$, illustrating the dominant upper dwarf branch we wish to exclude.
-The adopted dwarf/giant separation line is shown.
-Admittedly this selection criteria is not particularly strict, but we are allowing multiple inclusive cuts and taking the intersection of these criteria to identify Orphan Stream giants.
+
+Figure \ref{fig:ew-mg} illustrates the trend with $EW_{\lambda8807}$ against SDSS de-reddened\footnote{All magnitudes presented in this letter are de-reddened using the \citet{Schlegel_Finkbeiner_Davis_1998} dust maps.} $g - r$, illustrating the dominant upper dwarf branch we wish to exclude.
+Giant stars populate the lower, sparser branch.
+A separation line has been adopted to distinguish dwarfs from giants, and is shown in Figure \ref{fig:ew-mg}.
+If we were to place this line higher, the total number of true giant stars may increase, but the dwarf contamination rate will rise dramatically.
+A compromise must be made between the rate of giant recoverability and the dwarf contamination.
+Our  dwarf/giant separation line lies just below the main dwarf population.
+On its own, this dwarf/giant separation line would typically result in far too many dwarf contaminants.
+However, we are  employing selections on multiple observables (kinematics, metallicity, proper motions) in order to refine our Orphan Stream giant sample.
 
@@
 
-This analysis was also performed using the total equivalent width of the Mg\,\textsc{I}\,b triplet lines.
+This dwarf/giant separation method was also employed using the total equivalent width of the Mg\,\textsc{I}\,b triplet lines.
 Both analyses were entirely consistent with each other: essentially the same candidate selection was found using both techniques.
@@
 Because we classify all upper limits as being ``non-dwarfs" (i.e.
-potential OSS giants), we deduced a slightly larger candidate sample for the Mg\,\textsc{I}\,b analysis, which was primarily populated by upper limits.
-In conclusion, we found the Mg\,\textsc{I} line at 8807\,{\AA} appeared to be a more consistent dwarf discriminant given our weak S/N \--- particularly for our fainter stars \--- and thus we have used the 8807\,{\AA} Mg\,\textsc{I} selection throughout the rest of our analysis.
+potential giants), we deduced a slightly larger candidate sample for the Mg\,\textsc{I}\,b analysis, which was primarily populated by upper limits.
+In conclusion, we found the Mg\,\textsc{I} line at 8807\,{\AA} appeared to be a more consistent dwarf discriminant given our weak S/N \--- particularly for our fainter stars.
+Thus, we have used the 8807\,{\AA} Mg\,\textsc{I} selection throughout the rest of our analysis.
 
 Our dwarf/giant separation line in Figure \ref{fig:ew-mg} yields 425 potential giants.
-This fraction of giants ($\sim$44\%) is much larger than that found by \citeauthor{Casey_et-al_2012} \citeyear{Casey_et-al_2012}a who employed a similar colour selection.
-Hence, our gravity criteria is extremely inclusive and susceptible to dwarf contamination.
-Upon taking the intersection of our kinematic and gravity selections, we deduce eighteen stars that appear likely Orphan Stream K giants.
+Upon taking the intersection of our kinematic and gravity selections, we find 20 stars that appear to be likely Orphan Stream giants.
 
@@
 
-We have measured the equivalent widths of the Ca\,\textsc{II} near-infrared triplet lines for stars that meet our kinematic and surface gravity criteria.
+We have measured the metallicities for the stars that meet our kinematic and surface gravity criteria in two ways: with the strength of their Ca\,\textsc{II} triplet lines, and by isochrone-fitting.
 After correcting for luminosity, the equivalent width of the Ca\,\textsc{II} triplet lines provide a good indication of the overall metallicity of a RGB star \citep{Amandroff_Da_Costa_1991}.
@@
 Strictly speaking, the Ca\,\textsc{II}\---[Fe/H] calibration is only valid for stars brighter than the horizontal branch, although the relationship only becomes significantly inappropriate near $g \-- g_{HB} \sim +1$ \citep{Saviane_et-al_2012}.
-Many of our candidates are fainter than this valid luminosity range, and therefore they should not be excluded solely because of their derived metallicities.
+Many of our candidates are fainter than this valid luminosity range, and therefore they should not be excluded solely because of their derived metallicities, as these could be uncertain.
 Stars fainter than $g_{HB}$ will have slightly lower metallicities than predicted by our Ca\,\textsc{II}\---[Fe/H] relationship, and for these stars we will only use metallicities to assign a relative qualitative likelihood for stream membership.
-Given a distance to the Orphan Stream, we can also estimate a star's metallicity through isochrone fitting.
-We have used a 10\,Gyr \citet{Girardi_et-al_2008} isochrone at 21.4\,kpc \citep{Newberg_et-al_2010} and found metallicities for all eighteen likely stream members from their best-fitting isochrone.
+
+Given a distance estimate to the Orphan Stream, we can also deduce a star's metallicity through isochrone fitting.
+We have used a 10\,Gyr \citet{Girardi_et-al_2008} isochrone at 21.4\,kpc \citep{Newberg_et-al_2010} and found metallicities for all 20 likely stream members from their best-fitting isochrone.
 Derived metallicities from Ca\,\textsc{II} line strengths and isochrone fitting that are consistent (within $\pm0.3$\,dex) indicates these measurements are reliable, and that these stars are indeed at a distance of $\sim$21.4\,kpc.
@@
 
-\begin{deluxetable*}{lccccccccccccc}
-\tabletypesize{\scriptsize}
-\tablecolumns{12}
-\tablewidth{0pt}
-\tablecaption{Identified Orphan Stream Candidates\label{tab:oss-members}}
-\tablehead{
-	\colhead{Star} &
-	\colhead{$\alpha$} &
-	\colhead{$\delta$} &
-	\colhead{$g$} &
-	\colhead{$g \-- r$} &
-	\colhead{$\mu_{total}$\tablenotemark{a}} &
-	\colhead{$V_{GSR}$} &
-	\colhead{$EW_{\lambda8807}$} &
-	\colhead{[Fe/H]$_{Ca}$} &
-	\colhead{[Fe/H]$_{iso}$} &
-	\colhead{[Fe/H]\tablenotemark{b}} &
-	\colhead{Stream} \\
-Name & (J2000) & (J2000) & & & (mas yr$^{-1}$) & (km s$^{-1}$) & (\AA) & (dex) & (dex) & (dex) & Prob.
-}
-\startdata
-OSS-1  & 10:46:21.9 & $+$00:43:21.8 & 17.52 & 0.50 &\phn6.1 $\pm$ 6.1 & \phn73.3 $\pm$ \phn9.3 & 0.273 & --1.78 &$<$--2.28& --1.78 & Low \\
-OSS-2  & 10:46:29.3 & $-$00:19:38.5 & 17.77 & 0.56 &\phn2.7 $\pm$ 6.1 & \phn78.4 $\pm$ \phn5.2 & 0.126 & --1.63 & --1.68  & --1.63 & High \\
-OSS-3  & 10:46:50.4 & $-$00:13:15.6 & 17.33 & 0.51 &\phn5.9 $\pm$ 6.1 & \phn77.0 $\pm$ \phn4.0 & 0.416 & --1.31 &$<$--2.28& --1.31 & Low \\
-OSS-4  & 10:47:06.1 & $-$01:56:03.9 & 18.74 & 0.54 &\phn7.8 $\pm$ 6.9 & \phn74.9 $\pm$    17.6 & 0.452 &:--1.12\tablenotemark{c}& --1.40  & --1.40 & High \\
-OSS-5  & 10:47:15.0 & $-$03:15:03.9 & 18.66 & 0.54 &\phn8.4 $\pm$ 7.4 &    109.5 $\pm$ \phn9.0 &$<$0.19&:--1.85\tablenotemark{c}& --1.43  & --1.43 & Medium \\
-OSS-6  & 10:47:17.6 & $+$00:25:07.7 & 16.09 & 0.72 &\phn0.8 $\pm$ 5.7 & \phn79.2 $\pm$ \phn3.3 & 0.212 & --1.84 & --1.80  & --1.84 & High \\
-OSS-7  & 10:47:29.1 & $-$02:02:22.6 & 17.86 & 0.47 &     \nodata      & \phn93.2 $\pm$    29.8 &$<$0.40& --2.82 &$<$--2.28& --2.82 & High \\
-OSS-8  & 10:47:30.1 & $-$00:01:24.5 & 17.25 & 0.61 &\phn6.6 $\pm$ 5.9 & \phn83.6 $\pm$ \phn3.5 & 0.123 & --1.62 & --1.68  & --1.62 & High \\
-OSS-9  & 10:48:20.9 & $+$00:26:34.4 & 17.88 & 0.55 &\phn9.7 $\pm$ 6.1 &    118.9 $\pm$    11.7 & 0.467 & --1.65 & --1.73  & --1.65 & High \\
-OSS-10 & 10:48:27.8 & $+$00:55:24.0 & 17.72 & 0.51 &   15.3 $\pm$ 6.5 &    124.5 $\pm$ \phn6.7 & 0.182 & --1.48 &$<$--2.28& --1.48 & Low \\
-OSS-11 & 10:48:31.9 & $+$00:03:35.7 & 17.02 & 0.58 &\phn8.5 $\pm$ 5.8 &    105.1 $\pm$ \phn5.1 & 0.234 & --1.12 & --2.10  & --1.12 & Low \\
-OSS-12 & 10:48:44.4 & $-$02:53:08.8 & 18.35 & 0.62 &\phn3.8 $\pm$ 6.6 &    108.2 $\pm$ \phn9.0 & 0.183 &:--1.01\tablenotemark{c}& --1.17  & --1.17 & High \\
-OSS-13 & 10:48:46.9 & $-$00:32:27.8 & 17.85 & 0.46 &   30.9 $\pm$ 6.8 &    109.3 $\pm$ \phn8.1 & 0.324 & --2.37 &$<$--2.28& --2.37 & Medium \\
-OSS-14 & 10:49:08.3 & $+$00:02:00.2 & 16.27 & 0.62 &\phn7.7 $\pm$ 5.7 & \phn81.5 $\pm$ \phn4.6 & 0.034 & --2.70 &$<$--2.28& --2.70 & High \\
-OSS-15 & 10:50:13.1 & $+$00:33:52.7 & 16.13 & 0.58 &\phn8.4 $\pm$ 5.7 & \phn94.7 $\pm$ \phn5.1 & 0.391 & --1.54 &$<$--2.28& --1.54 & Low \\
-OSS-16 & 10:50:24.2 & $-$01:49:05.4 & 17.94 & 0.54 &\phn4.0 $\pm$ 6.5 & 109.9    $\pm$    25.4 & 0.151 & --1.06 & --1.73  & --1.06 & Low \\
-OSS-17 & 10:50:33.8 & $+$00:12:19.1 & 17.82 & 0.60 &\phn8.1 $\pm$ 7.1 & \phn97.5 $\pm$ \phn5.9 & 0.596 & --0.90 & --1.43  & --0.90 & Medium \\
-OSS-18 & 10:51:19.7 & $+$00:05:15.5 & 17.81 & 0.65 &   12.5 $\pm$ 6.6 & \phn82.7 $\pm$ \phn5.0 & 0.198 & --1.16 & --1.20  & --1.16 & High 
-\enddata
-\tablenotetext{a}{Proper motions and uncertainties in $\alpha$ and $\delta$ added in quadrature.}
-\tablenotetext{b}{Final adopted [Fe/H] value based on quality of two metallicity measurements.}
-\tablenotetext{c}{Sufficiently fainter than $g_{HB}$ to qualify this measurement as uncertain.}
-\end{deluxetable*}
-
-\begin{figure}[h!]
+\begin{figure}[t!]
 	\includegraphics[width=\columnwidth]{./fig3.eps}
-	\caption{Metallicities from the Ca\,\textsc{II} triplet lines versus those found from fitting isochrones to the eighteen stars that meet our kinematic and surface gravity criteria.
+	\caption{Metallicities from the Ca\,\textsc{II} triplet lines versus those found from fitting isochrones to the 20 stars that meet our kinematic and surface gravity criteria.
 Both abundance determinations imply these stars are RGB members of the Orphan Stream at a distance of $\sim$21.4\,kpc \citep{Newberg_et-al_2010}.
-Consistency between these methods indicates highly likely stream membership (green region).
+Consistency between these methods indicates highly likely stream membership (shaded region).
 The minimum isochrone [Fe/H], and a representative uncertainty of 0.2\,dex for abundance measurements is shown.}
@@
 
-We have investigated the status of these ten stars in the PPMXL proper motion catalogue \citep{Roeser_et-al_2010}, finding entries for nine of the candidates.
-One star (OSS-13 in Table \ref{tab:oss-members}) has a listed proper motion that is different from that of the other nine members at the $6\,\sigma$ level.
-Consequently, we have reduced the membership likelihood of this star from ``High" to ``Medium".
-
-We have adopted a final overall metallicity for each star based on the quality of our [Fe/H] measurements.
-Adopted values are tabulated in Table \ref{tab:oss-members}.
-From our nine highly likely stream members we find an overall stream metallicity of $[\mbox{Fe/H}] = -1.63$ with a dispersion of $\sigma = 0.56$ dex.
-This abundance spread is larger than typically seen in globular cluster stars and is more representative of the chemical spreads seen in dSph satellites.
-\citet{Newberg_et-al_2010} found a stream metallicity of $[\mbox{Fe/H}] = -2.1$ from BHB stars, which is not inconsistent with our measurement given the spread in Orphan Stream K-giant metallicities.
-
-Given that our Orphan Stream giants cover a wide evolutionary range along the giant branch (Figure \ref{fig:cmd}), we are in a good position to revise the distance estimate to the stream.
-Given a 10\,Gyr \citet{Girardi_et-al_2008} isochrone at $[\mbox{Fe/H}] = -1.63$, we find a best-fitting distance to the stream of $22.5 \pm 1.0$\,kpc at $(l, b) = (250\,^\circ,\,50\,^\circ)$.
-This isochrone is shown in Figure \ref{fig:cmd}, illustrating that three of our nine most probable member stars lie perfectly on this isochrone.
-Our derived distance is in reasonably good agreement with the $21.4 \pm 1.0$\,kpc independently estimated by \citet{Grillmair_2006} and \citet{Newberg_et-al_2010}.
-
-\begin{figure}[h!]
+\begin{figure}[t!]
 	\includegraphics[width=\columnwidth]{./fig4.eps}
@@
 
-% Adding \newpage here because otherwise only the Conclusions header is shown at the end of Page 4.
-\newpage
+A final metallicity value for each star has been adopted based on the quality of our [Fe/H] measurements.
+These values are tabulated in Table \ref{tab:oss-members}.
+From our highly likely stream members we find an overall stream metallicity of $[\mbox{Fe/H}] = -1.63$ with a dispersion of $\sigma = 0.56$ dex.
+This abundance spread is larger than typically seen in globular cluster stars and is more representative of the chemical spread seen in dSph satellites \citep[e.g.,][]{Frebel_Norris_2011}.
+
+\setlength{\tabcolsep}{2.4pt}
+
+\begin{table*}[t!]\footnotesize
+\caption{Identified Orphan Stream Candidates\label{tab:oss-members}}
+\begin{tabular*}{\textwidth}{lccccrcrcrrccccc}
+\hline
+\hline
+Star & $\alpha$ & $\delta$ & $g$ & $g - r$ & \multicolumn{2}{c}{$\mu_\alpha$} & \multicolumn{2}{c}{$\mu_\delta$} & \multicolumn{2}{c}{$V_{GSR}$} & $EW_{\lambda8807}$ & [Fe/H]$_{Ca}$ & [Fe/H]$_{iso}$ & [Fe/H]\footnote{Final adopted [Fe/H] value based on quality of two metallicity measurements.} & Stream \\
+Name & (J2000) & (J2000) & & & \multicolumn{2}{c}{(mas yr$^{-1}$)} & \multicolumn{2}{c}{(mas yr$^{-1}$)} & \multicolumn{2}{c}{(km s$^{-1}$)} & (m\AA{}) & (dex) & (dex) & (dex) & Prob. \\
+\hline
+OSS--1  & 10:46:21.9 & $+$00:43:21.8 & 17.52 & 0.50 & 4.1&$\pm$ 4.5 & $-$34.0 &$\pm$ 4.5 & 73.3 &$\pm$ \phn9.3 & 0.273 & --1.78 &$<$--2.28\phn\,& --1.78 & Low \\
+OSS--2  & 10:46:29.3 & $-$00:19:38.5 & 17.77 & 0.56 & $-$1.7 &$\pm$ 4.3 & $-$2.2 &$\pm$ 4.3 & 78.4 &$\pm$ \phn5.2 & 0.126 & --1.63 & --1.68  & --1.63 & High \\
+OSS--3  & 10:46:50.4 & $-$00:13:15.6 & 17.33 & 0.51 & 1.8 &$\pm$ 4.3 & $-$4.6 &$\pm$ 4.3 & 77.0 &$\pm$ \phn4.0 & 0.416 & --1.31 &$<$--2.28\phn\,& --1.31 & Low \\
+OSS--4  & 10:47:06.1 & $-$01:56:03.9 & 18.74 & 0.54 & $-$6.3 &$\pm$ 4.9 & 4.6 &$\pm$ 4.9 & 74.9 &$\pm$    17.6 & 0.452 &:--1.12\footnote{Sufficiently fainter than $g_{HB}$ to qualify this measurement as uncertain.}& --1.40  & --1.40 & High \\
+OSS--5  & 10:47:15.0 & $-$03:15:03.9 & 18.66 & 0.54 & $-$8.2 &$\pm$ 5.2 & 1.7 &$\pm$ 5.2 & 109.5 &$\pm$ \phn9.0 &$<$0.19&:--1.85\textsuperscript{b}& --1.43  & --1.43 & Medium \\
+OSS--6  & 10:47:17.6 & $+$00:25:07.7 & 16.09 & 0.72 & $-$0.8 &$\pm$ 4.0 & $-$5.2 &$\pm$ 4.2 & 79.2 &$\pm$ \phn3.3 & 0.212 & --1.84 & --1.80  & --1.84 & High \\
+OSS--7  & 10:47:29.1 & $-$02:02:22.6 & 17.86 & 0.47 & \multicolumn{2}{c}{\nodata} & \multicolumn{2}{c}{\nodata}  & 93.2 &$\pm$    29.8 &$<$0.40& --2.82 &$<$--2.28\phn\,& --2.82 & High \\
+OSS--8  & 10:47:30.1 & $-$00:01:24.5 & 17.25 & 0.61 & $-$4.0 &$\pm$ 4.2 & $-$5.2 &$\pm$ 4.2 & 83.6 &$\pm$ \phn3.5 & 0.123 & --1.62 & --1.68  & --1.62 & High \\
+OSS--9  & 10:48:20.9 & $+$00:26:34.4 & 17.88 & 0.55 & $-$8.1 &$\pm$ 4.3 & $-$5.4 &$\pm$ 4.3 & 118.9 &$\pm$    11.7 & 0.467 & --1.65 & --1.73  & --1.65 & High \\
+OSS--10 & 10:48:27.8 & $+$00:55:24.0 & 17.72 & 0.51 & $-$14.4 &$\pm$ 4.6 & $-$5.3 &$\pm$ 4.6 & 124.5 &$\pm$ \phn6.7 & 0.182 & --1.48 &$<$--2.28\phn\,& --1.48 & Low \\
+OSS--11 & 10:48:31.9 & $+$00:03:35.7 & 17.02 & 0.58 & $-$3.6 &$\pm$ 4.1 & $-$7.7 &$\pm$ 4.1  & 105.1 &$\pm$ \phn5.1 & 0.234 & --1.12 & --2.10  & --1.12 & Low \\
+OSS--12 & 10:48:44.4 & $-$02:53:08.8 & 18.35 & 0.62 & $-$3.4 &$\pm$ 4.7 & $-$1.8 &$\pm$ 4.7 & 108.2 &$\pm$ \phn9.0 & 0.183 &:--1.01\textsuperscript{b}& --1.17  & --1.17 & High \\
+OSS--13 & 10:48:46.9 & $-$00:32:27.8 & 17.85 & 0.46 & $-$28.4 &$\pm$ 4.8 & $-$12.3 &$\pm$ 4.8 & 109.3 &$\pm$ \phn8.1 & 0.324 & --2.37 &$<$--2.28\phn\,& --2.37 & Medium \\
+OSS--14 & 10:49:08.3 & $+$00:02:00.2 & 16.27 & 0.62 & 4.9 &$\pm$ 4.0 & $-$6.0 &$\pm$ 4.0& 81.5 &$\pm$ \phn4.6 & 0.034 & --2.70 &$<$--2.28\phn\,& --2.70 & High \\
+OSS--15 & 10:49:13.4 & $+$00:04:03.8 & 17.83 & 0.46 & 3.4 &$\pm$ 4.7 & $-$6.8 &$\pm$ 4.7 & 65.3 &$\pm$ \phn5.4 & 0.252 & --1.74 & $<$--2.28\phn\,& --1.74 & Medium \\
+OSS--16 & 10:50:13.1 & $+$00:33:52.7 & 16.13 & 0.58 & $-$3.4 &$\pm$ 4.0 & $-$7.7 &$\pm$ 4.0 & 94.7 &$\pm$ \phn5.1 & 0.391 & --1.54 &$<$--2.28\phn\,& --1.54 & Low \\
+OSS--17 & 10:50:24.2 & $-$01:49:05.4 & 17.94 & 0.54 & 3.4 &$\pm$ 4.6 & $-$2.2 &$\pm$ 4.6 & 109.9 &$\pm$    25.4 & 0.151 & --1.06 & --1.73  & --1.06 & Low \\
+OSS--18 & 10:50:33.8 & $+$00:12:19.1 & 17.82 & 0.60 & $-$7.4 &$\pm$ 5.0 & $-$3.3 &$\pm$ 5.0 & 97.5 &$\pm$ \phn5.9 & 0.596 & --0.90 & --1.43  & --0.90 & Medium \\
+OSS--19 & 10:51:19.7 & $+$00:05:15.5 & 17.81 & 0.65 & 4.2 &$\pm$ 4.7 & $-$11.8 &$\pm$ 4.7 & 82.7 &$\pm$ \phn5.0 & 0.198 & --1.16 & --1.20  & --1.16 & High \\
+OSS--20 & 10:51:35.4 & $+$00:00:46.4 & 17.93 & 0.56 & --0.5 &$\pm$ 4.5 & $-$3.0 &$\pm$ 4.5 & 66.7 &$\pm$ \phn8.7 & 0.128 & :--1.38 & --2.10 & --2.10 & Medium \\
+
+\hline
+\hline
+\end{tabular*}
+\end{table*}
+
+\break
+\subsection{Proper Motions \& Distances}
+
+We have found proper motions for 19 of our candidates in the PPMXL proper motion catalogue \citep{Roeser_et-al_2010}.
+One highly probably candidate (OSS--13 in Table \ref{tab:oss-members}) has a listed proper motion that is different from that of the other nine highly likely members at the $6\,\sigma$ level.
+Consequently, we have reduced the membership likelihood of this star from ``High" to ``Medium".
+Given the uncertainties in proper motions, we cannot reliably alter the membership probability for any other candidate.
+
+Since our Orphan Stream giants cover a wide evolutionary range along the giant branch (Figure \ref{fig:cmd}), we are in a good position to revise the distance estimate to the stream.
+Given a 10\,Gyr \citet{Girardi_et-al_2008} isochrone at $[\mbox{Fe/H}] = -1.63$, we find a best-fitting distance to the stream of $22.5 \pm 2.0$\,kpc at $(l, b) = (250\,^\circ,\,50\,^\circ)$.
+This isochrone is shown in Figure \ref{fig:cmd}.
+Our derived distance is in reasonably good agreement with the measurement of $21.4 \pm 1.0$\,kpc independently deduced by \citet{Grillmair_2006} and \citet{Newberg_et-al_2010}.
+
+\subsection{Comparison with \citet{Newberg_et-al_2010}}
+\label{sec:newberg}
+\citet{Newberg_et-al_2010} traced the Orphan Stream using BHB stars selected from the SEGUE survey, allowing them to derive an orbit for the stream and make a strong prediction for the location of the undiscovered progenitor.
+Their closest stream detection to this study is at $\Lambda_{Orphan} = 18.4\,^\circ$, approximately $\Delta\Lambda_{Orphan} \sim 4\,^\circ$ away from our fields.
+At this location, \citet{Newberg_et-al_2010} found the velocity of the stream to be $V_{GSR} = 101.4 \pm 8.9$\,km s$^{-1}$ based on 12 BHB stars.
+We note that this is $\sim95$\,km s$^{-1}$ on our scale, given the differences in accounting for the local standard of rest.
+The velocities and metallicities of our `High' and `Medium' probability candidates are illustrated in Figure \ref{fig:vgsr-feh}.
+Although we recover some candidates with velocities up to $V_{GSR} \sim 110$\,km s$^{-1}$, our kinematic distribution peaks near $V_{GSR} \sim 85$\,km s$^{-1}$, roughly 10\,km s$^{-1}$ lower than that of \citet{Newberg_et-al_2010}.
+
+There is a known velocity gradient along the Orphan Stream which can account for this discrepancy.
+As $\Lambda_{Orphan}$ increases towards the edge of the SDSS boundary, galactocentric velocity quickly decreases.
+For the Orphan Stream detection in the outrigger SEGUE Strip 1540 at $\Lambda_{Orphan} = 36\,^\circ$, \citet{Newberg_et-al_2010} find $V_{GSR} = 38$\,km s$^{-1}$.
+This work presents likely Orphan Stream K-giant candidates at $\Lambda_{Orphan} \sim 23\,^\circ$.
+Given the velocity gradient reported by \citet{Newberg_et-al_2010}, a galactocentric velocity of $80-85$\,km s$^{-1}$ (on our scale) is perfectly reasonable.
+We note that since the velocities of BHB stars can have significant uncertainties, it was practical for us to assume a wide initial selection in kinematics to identify potential members.
+
+\begin{figure}[h!]
+	\includegraphics[width=\columnwidth]{./fig5.eps}
+	\caption{Galactocentric velocities and adopted metallicities for the highest likely Orphan Stream members (black $\bullet$), and those with probabilities assigned as ``Medium'' (grey $\circ$; see text).}
+	\label{fig:vgsr-feh}
+\end{figure}
+
+\begin{figure}[h!]
+	\includegraphics[width=\columnwidth]{./fig6.eps}
+	\caption{Observed metallicity distribution function for the Orphan Stream candidates identified here, with comparisons to the distribution found by \citet{Newberg_et-al_2010} from BHB stars.}
+	\label{fig:newberg-feh}
+\end{figure}
+
+The adopted metallicities of our Orphan Stream candidates are generally higher than those found by \citet{Newberg_et-al_2010}.
+Our highly likely stream members have a mean metallicity of [Fe/H] = $-1.63$, with a dispersion of $\sigma = 0.56$\,dex.
+As illustrated in Figures \ref{fig:vgsr-feh} and \ref{fig:newberg-feh}, there are two very metal-poor candidates which largely drive this dispersion, but we have no reason to suspect they are non-members.
+The \citet{Newberg_et-al_2010} sample contains 37 BHB stars identified over a 60\,$^\circ$ arc on the sky, and has a peak metallicity at [Fe/H] = $-2.10 \pm 0.10$.
+The closest detection bin in the \citet{Newberg_et-al_2010} sample was the most populous, yielding 7 BHB stars.
+For comparison, we identify 9 giant stars across $\sim{}4\,^\circ$.
+Given BHB stars are known to trace a somewhat more metal-poor population, and we are calculating statistics with marginal sample sizes, we conclude that the accuracy of these two metallicity distributions are not mutually exclusive.
+It is entirely possible that we are sampling the same distribution, but a larger sample size is required.
 
@@
 
-We have presented a detailed analysis to isolate individual Orphan Stream K giants from low-resolution spectroscopy using a combination of photometric, kinematic, gravity, metallicity, and proper motion information.
-Although each individual criteria is likely to induce some level contamination, their intersection reveals nine highly probable, self-consistent, Orphan Stream K giants.
+We have presented a detailed analysis to isolate individual Orphan Stream K-giants from low-resolution spectroscopy using a combination of photometric, kinematic, gravity, metallicity, and proper motion information.
+Although each individual criteria is likely to induce some level contamination, their intersection reveals nine highly probable, self-consistent, Orphan Stream K-giants.
 We deduce a median stream metallicity of $[\mbox{Fe/H}] = -1.63 \pm 0.19$ and find an intrinsically wide metallicity spread of $\sigma = 0.56$\,dex, indicative of a dSph origin.
@@
 Recall that the metallicity determination was performed after kinematic and gravity cuts, and three of our most probable members lay perfectly on a 10\,Gyr isochrone of $[\mbox{Fe/H}] = -1.63$.
-Our stream members indicate a distance to the stream of $22.5 \pm 1.0$\,kpc at $(l, b) = (250\,^\circ,\,50\,^\circ)$, in agreement with that deduced by \citet{Grillmair;et-al_2006} and \citet{Newberg_et-al_2010}.
+However, it is clear that more data is required to fully characterize the stream metallicity distribution function.
+Our data indicate a distance to the stream of $22.5 \pm 2.0$\,kpc at $(l, b) = (250\,^\circ,\,50\,^\circ)$, in agreement with that deduced by \citet{Grillmair_2006} and \citet{Newberg_et-al_2010}.
+
+Given the stream orbit derived by \citet{Newberg_et-al_2010}, they excluded all possible known halo objects except for the dissolved star cluster, Segue 1.
+\citet{Simon_et-al_2011} obtained spectroscopy for six members in Segue 1 and found an extremely wide metallicity dispersion: from $<-3.4$ to $-1.63$ dex.
+On the basis of the extremely low metallicity in the cluster and the wide chemical dispersion, they conclude that Segue 1 is a disrupted dwarf spheroidal galaxy.
+Although the data presented here indicates the Orphan Stream progenitor is a disrupted dwarf spheroidal galaxy, we cannot reliably associate Segue 1 as the parent without additional observational data.
 
 If the Orphan Stream continues through SEGUE Stripe 1540 at $(l, b) = (271\,^\circ,\,38\,^\circ)$ as \citet{Newberg_et-al_2010} found, then the stream is even closer there than in the region analysed here.
-Thus, if our observations and analyses are repeated at $(271\,^\circ,\,38\,^\circ)$, we predict K giant stream members of brighter apparent magnitude will be recovered.
+Thus, if our observations and analyses are repeated at $(271\,^\circ,\,38\,^\circ)$, we predict K-giant stream members of brighter apparent magnitude will be recovered.
 
 Using a maximum-likelihood estimation we find the stream velocity at $(l, b) = (250\,^\circ, 50\,^\circ)$ from nine stars to be $V_{GSR} = 85.3 \pm 4.4$\,km s$^{-1}$ and the dispersion to be $6.5 \pm 7.0$\,km s$^{-1}$.
-If we exclude three stars with weak signal \--- and hence large ($> 10$\,km s$^{-1}$) velocity uncertainties \--- the peak occurs at $82.1 \pm 1.4$\,km s$^{-1}$ and the intrinsic dispersion is found to be $0.2\,\pm\,3.1$\,km s$^{-1}$.
+If we exclude three stars with low signal-to-noise \--- and hence large ($> 10$\,km s$^{-1}$) velocity uncertainties \--- the peak occurs at $82.1 \pm 1.4$\,km s$^{-1}$ and the intrinsic dispersion is found to be $0.2\,\pm\,3.1$\,km s$^{-1}$.
 Hence, the observed stream dispersion is dominated by the velocity uncertainties, indicating that the intrinsic dispersion is small.
-Finally, these velocities indicate that the Orphan Stream is a very cold stream, and implies their motion is largely perpendicular to the line of sight.
 
-The K giants presented here can provide great insight into the chemistry, and history of the Orphan Stream.
-High-resolution spectroscopic observations have been taken for some of our most highly probable members and a detailed chemical analysis will be presented in a forthcoming paper (Casey et al.
-2012c, in preparation).
-Detailed chemical abundances can help determine both the nature of the progenitor before it's discovered, and allows us to compare peculiar chemical signatures with those of the known Milky Way satellites in order to associate likely parents.
+The K-giants presented here can provide great insight
+\begin{minipage}{\columnwidth}
+into the chemistry and history of the Orphan Stream.
+High-resolution spectroscopic observations have been taken for some of our highly probable members and a detailed chemical analysis will be presented in a forthcoming paper (Casey et al., in preparation).
+Detailed chemical abundances can help determine both the nature of the progenitor before it is discovered, and allows us to compare peculiar chemical signatures with those of the known Milky Way satellites in order to associate likely parents.
 However, at least for the moment, the Orphan Stream remains appropriately named.
+\end{minipage}
 
 \acknowledgements
+The authors would like to thank the anonymous referee for their constructive comments which improved this paper.
 ARC acknowledges the financial support through the Australian Research Council Laureate Fellowship 0992131, and from the Australian Prime Minister's Endeavour Award Research Fellowship, which has facilitated his research at MIT.
@@
 
-% Note to the reader:
-% In the acknowledgements, the final line including the text "the University of Washington"
-% line does not appear if I don't have \phn here.
-\phn
+\vspace{2em}
 
-\begin{thebibliography}{26}
+\begin{thebibliography}{29}
 \expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
@@
 
+\bibitem[{{Frebel} \& {Norris}(2011){Frebel}, \& {Norris}}]{Frebel_Norris_2011}
+{Frebel}, A., \& Norris, J. E. 2011, arXiv/1102.1748
+
 \bibitem[{{Grillmair} (2006)}]{Grillmair_2006}
 {Grillmair}, C.~J. 2006, \apj, 643, L37
-
-\bibitem[{{Grillmair} \& {Dionatos}(2006)}]{Grillmair_Dionatos_2006}
-{Grillmair}, C.~J., \& {Dionatos}, O. 2006, \apjl, 643, L17
 
@@
 
+\bibitem[{{Simon} {et~al.}(2011){Simon}, {Geha}, {Minor}, {Martinez},
+	{Kirby}, {Bullock}, {Kaplinghat}, 
+	{Strigari}, {Willman}, {Choi}, {Tollerud}, \&
+	{Wolf}, J.}]{Simon_et-al_2011}
+{Simon}, J.~D., {et~al.} 2011, \apj, 733, 46S
+
 \bibitem[{{Starkenburg} {et~al.}(2010){Starkenburg}, {Hill}, {Tolstoy},

### 2012-12-03 2012-aqs/figures/plot-alpha-fe.py
added plotting scripts

@@ -1,0 +1,149 @@
+import matplotlib.pyplot as plt
+import numpy as np
+
+# Get Na and O from files:
+data_files = ['c2225316-14437_abundances.data', 'c2306265-085103_abundances.data', 'j221821-183424_abundances.data', 'j223504-152834_abundances.data', 'j223811-104126_abundances.data']
+
+Si_Fe = []
+e_Si_Fe = []
+
+Ca_Fe = []
+e_Ca_Fe = []
+
+Ti_Fe = []
+e_Ti_Fe = []
+
+Fe_H = []
+e_Fe_H = []
+
+observed_data = {}
+for filename in data_files:
+
+	data = np.loadtxt(filename, dtype=str, usecols=(0, -6, -4, -2,))
+	observed_data[filename] = data
+
+	idx = list(data[:,0]).index('Si')
+	_Si_Fe, _e_Si_Fe = data[idx, 2:]
+
+	idx = list(data[:,0]).index('Ca')
+	_Ca_Fe, _e_Ca_Fe = data[idx, 2:]
+
+	idx = list(data[:,0]).index('Ti') + 1 # Get Ti II because it's more reliable
+	_Ti_Fe, _e_Ti_Fe = data[idx, 2:]
+
+	idx = list(data[:, 0]).index('Fe')
+	_Fe_H, _e_Fe_H = data[idx, 1], data[idx, -1]
+
+	Si_Fe.append(_Si_Fe)
+	e_Si_Fe.append(_e_Si_Fe)
+
+	Ca_Fe.append(_Ca_Fe)
+	e_Ca_Fe.append(_e_Ca_Fe)
+
+	Ti_Fe.append(_Ti_Fe)
+	e_Ti_Fe.append(_e_Ti_Fe)
+
+	Fe_H.append(_Fe_H)
+	e_Fe_H.append(_e_Fe_H)
+
+
+
+# Clean up Mg_Fe, Fe_H, e_Mg_Fe, e_Fe_H
+Si_Fe = map(float, [value.replace('$', '').replace('\\', '').replace('nodata', 'nan') for value in Si_Fe])
+Ca_Fe = map(float, [value.replace('$', '').replace('\\', '').replace('nodata', 'nan') for value in Ca_Fe])
[…]

### 2012-12-03 2012-aqs/figures/plot-line-velocity.py

@@ -1,0 +1,57 @@
+import matplotlib.pyplot as plt
+import matplotlib.mlab as mlab
+import numpy as np
+from scipy.stats import norm
+
+rest_wavelengths, line_velocities, is_acceptable = np.loadtxt('HD41667-line-measurements.data', delimiter=';', usecols=(0, 11, -2), unpack=True, dtype=str)
+
+# Get only the acceptable indices
+
+acceptable_indices = np.array([item.strip() for item in is_acceptable]) == 'True'
+rest_wavelengths = np.array(rest_wavelengths[acceptable_indices], dtype=np.float)
+line_velocities = np.array(line_velocities[acceptable_indices], dtype=np.float)
+
+# Get only finite line velocities
+finite_indices = np.where(np.isfinite(line_velocities))
+line_velocities = line_velocities[finite_indices]
+rest_wavelengths = rest_wavelengths[finite_indices]
+
+
+
+fig = plt.figure(figsize=(6,6))
+fig.subplots_adjust(hspace=0.25)
+
+# histogram 
+ax = fig.add_subplot(211)
+n, bins, patches = ax.hist(line_velocities, facecolor='none', normed=True)
+ax.set_xlabel('Line velocity, $V_{\lambda}$ [km s$^{-1}$]')
+ax.set_ylabel('$P(V_{line})$')
+
+
+mu, sigma = norm.fit(line_velocities)
+print "mu, sigma", mu, sigma
+y = mlab.normpdf(bins, mu, sigma)
+ax.plot(bins, y, 'k:', linewidth=2)
+
+ax.text(3.0, 0.7, "$N\,=\,%i$\n$\mu\,=\,%1.2f$\n$\sigma\,=\,%1.2f$" % (len(line_velocities), mu, sigma, ), color='k', verticalalignment='top', horizontalalignment='right')
+
+# scatter
+ax2 = fig.add_subplot(212)
+ax2.scatter(rest_wavelengths, line_velocities, facecolor='none')
+
+xlim = ax2.get_xlim()
+ylim = int(np.max(np.abs(ax2.get_ylim()))) - 0.5
+
+ax2.plot(xlim, [0, 0], 'k-', zorder=-1)
+ax2.plot(xlim, [np.median(line_velocities)] * 2, 'k--', zorder=-1)
+
+ax2.set_xlim(xlim)
+ax2.set_ylim(-ylim, ylim)
[…]

### 2012-12-03 2012-aqs/figures/plot-mg-al.py

@@ -1,0 +1,61 @@
+import matplotlib.pyplot as plt
+import numpy as np
+
+# Get Na and O from files:
+data_files = ['c2225316-14437_abundances.data', 'c2306265-085103_abundances.data', 'j221821-183424_abundances.data', 'j223504-152834_abundances.data', 'j223811-104126_abundances.data']
+
+Mg_Fe = []
+e_Mg_Fe = []
+
+Al_Fe = []
+e_Al_Fe = []
+
+observed_data = {}
+for filename in data_files:
+
+	data = np.loadtxt(filename, dtype=str, usecols=(0, -4, -2,))
+	observed_data[filename] = data
+
+	idx = list(data[:,0]).index('Mg')
+	_Mg_Fe, _e_Mg_Fe = data[idx, 1:]
+
+	idx = list(data[:, 0]).index('Al')
+	_Al_Fe, _e_Al_Fe = data[idx, 1:]
+
+	Mg_Fe.append(_Mg_Fe)
+	Al_Fe.append(_Al_Fe)
+	e_Mg_Fe.append(_e_Mg_Fe)
+	e_Al_Fe.append(_e_Al_Fe)
+
+
+# Clean up Mg_Fe, Al_Fe, e_Mg_Fe, e_Al_Fe
+Mg_Fe = map(float, [value.replace('$', '').replace('\nodata', 'nan') for value in Mg_Fe])
+Al_Fe = map(float, [value.replace('$', '').replace('\nodata', 'nan') for value in Al_Fe])
+
+e_Mg_Fe = map(float, [value.replace('$', '').replace('\nodata', 'nan') for value in e_Mg_Fe])
+e_Al_Fe = map(float, [value.replace('$', '').replace('\nodata', 'nan') for value in e_Al_Fe])
+
+Mg_Fe, Al_Fe, e_Mg_Fe, e_Al_Fe = map(np.array, [Mg_Fe, Al_Fe, e_Mg_Fe, e_Al_Fe])
+
+
+A = np.vstack([Mg_Fe, np.ones(len(Mg_Fe))]).T
+m, c = np.linalg.lstsq(A, Al_Fe)[0]
+
+fig = plt.figure()
+
+ax = fig.add_subplot(111)
+ax.scatter(Mg_Fe, Al_Fe, color='k')
[…]

### 2012-12-03 2012-aqs/figures/plot-mg-alpha-fe.py

@@ -1,0 +1,125 @@
+import matplotlib.pyplot as plt
+import numpy as np
+
+# Get Na and O from files:
+data_files = ['c2225316-14437_abundances.data', 'c2306265-085103_abundances.data', 'j221821-183424_abundances.data', 'j223504-152834_abundances.data', 'j223811-104126_abundances.data']
+
+Si_Fe = []
+e_Si_Fe = []
+
+Ca_Fe = []
+e_Ca_Fe = []
+
+Ti_Fe = []
+e_Ti_Fe = []
+
+Mg_Fe = []
+e_Mg_Fe = []
+
+Fe_H = []
+e_Fe_H = []
+
+observed_data = {}
+for filename in data_files:
+
+	data = np.loadtxt(filename, dtype=str, usecols=(0, -6, -4, -2,))
+	observed_data[filename] = data
+
+	idx = list(data[:,0]).index('Si')
+	_Si_Fe, _e_Si_Fe = data[idx, 2:]
+
+	idx = list(data[:,0]).index('Ca')
+	_Ca_Fe, _e_Ca_Fe = data[idx, 2:]
+
+	idx = list(data[:,0]).index('Mg')
+	_Mg_Fe, _e_Mg_Fe = data[idx, 2:]
+
+	idx = list(data[:,0]).index('Ti') + 1 # Get Ti II because it's more reliable
+	_Ti_Fe, _e_Ti_Fe = data[idx, 2:]
+
+	idx = list(data[:, 0]).index('Fe')
+	_Fe_H, _e_Fe_H = data[idx, 1], data[idx, -1]
+
+	Si_Fe.append(_Si_Fe)
+	e_Si_Fe.append(_e_Si_Fe)
+
+	Ca_Fe.append(_Ca_Fe)
+	e_Ca_Fe.append(_e_Ca_Fe)
+
+	Mg_Fe.append(_Mg_Fe)
+	e_Mg_Fe.append(_e_Mg_Fe)
+
+	Ti_Fe.append(_Ti_Fe)
+	e_Ti_Fe.append(_e_Ti_Fe)
+
+	Fe_H.append(_Fe_H)
+	e_Fe_H.append(_e_Fe_H)
+
+
+
+# Clean up Mg_Fe, Fe_H, e_Mg_Fe, e_Fe_H
+Si_Fe = map(float, [value.replace('$', '').replace('\\', '').replace('nodata', 'nan') for value in Si_Fe])
[…]

### 2012-12-03 2012-aqs/figures/plot-na-cr-ni.py

@@ -1,0 +1,145 @@
+import matplotlib.pyplot as plt
+import numpy as np
+
+# Get Na and O from files:
+data_files = ['c2225316-14437_abundances.data', 'c2306265-085103_abundances.data', 'j221821-183424_abundances.data', 'j223504-152834_abundances.data', 'j223811-104126_abundances.data']
+
+Na_Fe = []
+e_Na_Fe = []
+
+Cr_Fe = []
+e_Cr_Fe = []
+
+Ni_Fe = []
+e_Ni_Fe = []
+
+Fe_H = []
+e_Fe_H = []
+
+observed_data = {}
+for filename in data_files:
+
+	data = np.loadtxt(filename, dtype=str, usecols=(0, -6, -4, -2,))
+	observed_data[filename] = data
+
+	idx = list(data[:,0]).index('Na')
+	_Na_Fe, _e_Na_Fe = data[idx, 2:]
+
+	idx = list(data[:,0]).index('Cr')
+	_Cr_Fe, _e_Cr_Fe = data[idx, 2:]
+
+	idx = list(data[:,0]).index('Ni')
+	_Ni_Fe, _e_Ni_Fe = data[idx, 2:]
+
+	idx = list(data[:, 0]).index('Fe')
+	_Fe_H, _e_Fe_H = data[idx, 1], data[idx, -1]
+
+	Na_Fe.append(_Na_Fe)
+	e_Na_Fe.append(_e_Na_Fe)
+
+	Cr_Fe.append(_Cr_Fe)
+	e_Cr_Fe.append(_e_Cr_Fe)
+
+	Ni_Fe.append(_Ni_Fe)
+	e_Ni_Fe.append(_e_Ni_Fe)
+
+	Fe_H.append(_Fe_H)
+	e_Fe_H.append(_e_Fe_H)
+
+
+
+# Clean up Mg_Fe, Fe_H, e_Mg_Fe, e_Fe_H
+Na_Fe = map(float, [value.replace('$', '').replace('\\', '').replace('nodata', 'nan') for value in Na_Fe])
+Cr_Fe = map(float, [value.replace('$', '').replace('\\', '').replace('nodata', 'nan') for value in Cr_Fe])
[…]

### 2012-12-03 2012-aqs/figures/plot-na-ni.py

@@ -1,0 +1,61 @@
+import matplotlib.pyplot as plt
+import numpy as np
+
+# Get Na and O from files:
+data_files = ['c2225316-14437_abundances.data', 'c2306265-085103_abundances.data', 'j221821-183424_abundances.data', 'j223504-152834_abundances.data', 'j223811-104126_abundances.data']
+
+Na_Fe = []
+e_Na_Fe = []
+
+Ni_Fe = []
+e_Ni_Fe = []
+
+observed_data = {}
+for filename in data_files:
+
+	data = np.loadtxt(filename, dtype=str, usecols=(0, -4, -2,))
+	observed_data[filename] = data
+
+	idx = list(data[:,0]).index('Na')
+	_Na_Fe, _e_Na_Fe = data[idx, 1:]
+
+	idx = list(data[:, 0]).index('Ni')
+	_Ni_Fe, _e_Ni_Fe = data[idx, 1:]
+
+	Na_Fe.append(_Na_Fe)
+	Ni_Fe.append(_Ni_Fe)
+	e_Na_Fe.append(_e_Na_Fe)
+	e_Ni_Fe.append(_e_Ni_Fe)
+
+
+# Clean up Na_Fe, Ni_Fe, e_Na_Fe, e_Ni_Fe
+Na_Fe = map(float, [value.replace('$', '').replace('\nodata', 'nan') for value in Na_Fe])
+Ni_Fe = map(float, [value.replace('$', '').replace('\nodata', 'nan') for value in Ni_Fe])
+
+e_Na_Fe = map(float, [value.replace('$', '').replace('\nodata', 'nan') for value in e_Na_Fe])
+e_Ni_Fe = map(float, [value.replace('$', '').replace('\nodata', 'nan') for value in e_Ni_Fe])
+
+Na_Fe, Ni_Fe, e_Na_Fe, e_Ni_Fe = map(np.array, [Na_Fe, Ni_Fe, e_Na_Fe, e_Ni_Fe])
+
+
+A = np.vstack([Na_Fe, np.ones(len(Na_Fe))]).T
+m, c = np.linalg.lstsq(A, Ni_Fe)[0]
+
+fig = plt.figure()
+
+ax = fig.add_subplot(111)
+ax.scatter(Na_Fe, Ni_Fe, color='k')
[…]

### 2012-12-03 2012-aqs/figures/plot-na-o.py

@@ -4,7 +4,7 @@ import matplotlib.pyplot as plt
 # ; ;mag;mag;mag;mag;km/s;km/s;K;[Sun];[Sun];[Sun];[Sun]; ;[Sun];[Sun];"h:m:s";"d:m:s"
 
 
-Fe_I, e_Fe_I, O_Fe, e_O_Fe, l_Na_Fe, Na_Fe, e_Na_Fe = np.loadtxt('caretta-et-al-2009-O-Na.txt', skiprows=67, delimiter=';', \
+caretta_Fe_I, caretta_e_Fe_I, caretta_O_Fe, caretta_e_O_Fe, caretta_l_Na_Fe, caretta_Na_Fe, caretta_e_Na_Fe = np.loadtxt('caretta-et-al-2009-O-Na.txt', skiprows=67, delimiter=';', \
 														usecols=(9, 10, 11, 12, 13, 14, 15, ), unpack=True, dtype=str)
 
 # Replace invalid items with np.nans
@@ -25,29 +25,88 @@ def clean(array):
 	return np.array(new_array)
 
 
-Fe_I, e_Fe_I, O_Fe, e_O_Fe, Na_Fe, e_Na_Fe = map(clean, [Fe_I, e_Fe_I, O_Fe, e_O_Fe, Na_Fe, e_Na_Fe])
+caretta_Fe_I, caretta_e_Fe_I, caretta_O_Fe, caretta_e_O_Fe, caretta_Na_Fe, caretta_e_Na_Fe = map(clean, [caretta_Fe_I, caretta_e_Fe_I, caretta_O_Fe, caretta_e_O_Fe, caretta_Na_Fe, caretta_e_Na_Fe])
 
+
+
+# Get Na and O from files:
+data_files = ['c2225316-14437_abundances.data', 'c2306265-085103_abundances.data', 'j221821-183424_abundances.data', 'j223504-152834_abundances.data', 'j223811-104126_abundances.data']
+
+Na_Fe = []
+e_Na_Fe = []
+
+O_Fe = []
+e_O_Fe = []
+
+observed_data = {}
+for filename in data_files:
+
+	data = np.loadtxt(filename, dtype=str, usecols=(0, -4, -2,))
+	observed_data[filename] = data
+
+	idx = list(data[:,0]).index('Na')
+	_Na_Fe, _e_Na_Fe = data[idx, 1:]
+
+	idx = list(data[:, 0]).index('O')
+	_O_Fe, _e_O_Fe = data[idx, 1:]
+
[…]

### 2012-12-03 2012-aqs/figures/plot-smh-norris.py

@@ -11,7 +11,7 @@ gs = gridspec.GridSpec(2, 1, height_ratios=[1, 2])
 ax1 = fig.add_subplot(gs[0])
 #ax1 = plt.subplot2grid((3, 1), (0, 0))
 
-ax1.scatter(smh_ew, smh_ew - norris_ew, facecolor='none', edgecolor='k')
+ax1.scatter(smh_ew, smh_ew - norris_ew, facecolor='none', edgecolor='k', marker='+')
 ax1.plot([0, 200], [0, 0], 'k-', zorder=-1)
 
 A = np.vstack([smh_ew, np.ones(len(norris_ew))]).T
@@ -28,7 +28,7 @@ ax1.set_ylabel('$\Delta{}W_\lambda$ [m$\AA{}$]')
 
 ax2 = fig.add_subplot(gs[1], sharex=ax1)
 #ax2 = plt.subplot2grid((3, 1), (1, 0), rowspan=2)
-ax2.scatter(smh_ew, norris_ew, facecolor='none', edgecolor='k')
+ax2.scatter(smh_ew, norris_ew, facecolor='none', edgecolor='k', marker='+')
 
 A = np.vstack([norris_ew, np.ones(len(norris_ew))]).T
 m, c = np.linalg.lstsq(A, smh_ew)[0]
@@ -37,12 +37,19 @@ ax2.plot(x, x, 'k-', zorder=-1)
 x = np.array([np.min(smh_ew), np.max(smh_ew)])
 ax2.plot(x, m * x + c, 'k:')
 
-ax1.set_xlim(0, 160)
-ax2.set_xlim(0, 160)
-ax2.set_ylim(0, 160)
+# Plot an error cone
+error = 10 # percent
+bounds = np.array([0, 160])
+#ax2.plot(bounds, bounds * (1 + error/100.), '-', c='#aaaaaa', zorder=-5)
+#ax2.plot(bounds, bounds * (1 - error/100.), '-', c='#aaaaaa', zorder=-5)
+
+
+ax1.set_xlim(bounds)
+ax2.set_xlim(bounds)
+ax2.set_ylim(bounds)
 
 ax2.set_xlabel('$W_\lambda$ (This work, automatic) [m$\AA{}$]')
-ax2.set_ylabel('$W_\lambda$ (Norris et al. 2000) [m$\AA{}$]')
+ax2.set_ylabel('$W_\lambda$ (Norris et al. 1996) [m$\AA{}$]')
 
[…]

### 2012-12-03 2012-aqs/draft-aqs.tex
minor updates

@@
 
-\title{The Aquarius Stream Progenitor Was Not a Globular Cluster}
+\title{The Aquarius Stream Progenitor Was Not A Globular Cluster: \\ Its History is Far More Interesting}
 
-\author{Andrew R. Casey\altaffilmark{1,2}, Stefan C. Keller\altaffilmark{1}, Frebel, Anna\altaffilmark{2}, Gary Da Costa\altaffilmark{1}, Alan Alves-Brito\altaffilmark{1}}
+\author{Andrew R. Casey\altaffilmark{1,2} and distinguished collaborators}
 \altaffiltext{1}{Research School of Astronomy \& Astrophysics, Australian National University, Mount Stromlo Observatory, via Cotter Rd, Weston, ACT 2611, Australia}
@@
 
-Stellar streams in the halo are relics of relatively recent minor mergers in the Milky Way.
+Stellar streams in the halo are relics from relatively recent minor mergers in the Milky Way.
 The positions and kinematics of stars within these streams are sensitive to the galactic potential.
-As such, they can collectively constrain the chemodynamical evolution of the galaxy, the fraction and distribution of accreted matter in the stellar halo, the sub-halo mass function, as well as the shape and extent of dark matter in the Milky Way.
+As such, they can collectively constrain the fraction and distribution of accreted matter in the stellar halo, the sub-halo mass function, as well as the shape and extent of dark matter in the Milky Way.
+Moreover, individual elemental abundances for stars within these streams reveal the chemodynamical evolution of the Galaxy.
 
-Wide field digital image catalogues have proved excellent sources for finding stellar streams.
+Wide-field surveys have proved excellent sources for finding stellar streams.
 Dozens of streams reaching out up to 150\,kpc in the stellar halo have been identified through photometric selections and matched-filtering techniques.
-However, as \citet{Helmi;et-al_1999} point out, these methods are only successful for identifying substructures that are sufficiently distant from the solar neighbourhood.
-A nearby stream within 10\,kpc will not appear as an on-sky over-density.
-Such an object would only be detectable by utilising both position and kinematic information.
+However, as \citet{Helmi;White_1999} point out, these methods are only successful for identifying substructures that are sufficiently distant from the solar neighbourhood.
+A nearby stream within $\sim{}$10\,kpc will not appear as an on-sky over-density.
+Such substructures would only be detectable by utilising both position and kinematic information.
 
@@
 The RAVE (Radial Velocity Experiment) began such a survey in 2003 and has observed spectra from over 500,000 stars across 17,000 deg$^{2}$.
-Candidates for RAVE were chosen based only on their apparent magnitude of 9 $<$ I $<$ 13, and therefore are not kinematically biased towards detecting nearby streams.
-The RAVE data releases have provided radial velocities \citep{Steinmetz;et-al_2006} and estimates of stellar parameters \citep{Zwitter;et-al_2008, Siebert;et-al_2011} now for a subset of these observations.
+RAVE candidates were photometrically selected based only on their apparent magnitude of 9 $<$ I $<$ 13, and are therefore kinematically unbiased.
+The RAVE data releases have provided radial velocities \citep{steinmetz;et-al_2006} and estimates of stellar parameters \citep{zwitter;et-al_2008, siebert;et-al_2011} now for a subset of these observations.
 
 % Identification of the aquarius stream
-Using this data, \citet{Williams;et-al_2011} identified a co-moving group of nearby ($0.5 \leq d \leq 10$\,kpc) stars in the direction of the Aquarius constellation.
+Using this data, \citet{williams;et-al_2011} identified a co-moving group of nearby ($0.5 \lesssim d \lesssim 10$\,kpc) stars in the direction of the Aquarius constellation.
 The artefact is most apparent when examining kinematics against galactic latitude for stars within $-70\,^\circ < b < -50\,^\circ$.
-\citet{Williams;et-al_2011} employed a selection criteria of $-250 < V_{hel} < -150$\,km s$^{-1}$, $30\,^\circ < l < 75\,^\circ, J > 10.3$ and identified 15 stream candidates.
-The average heliocentric radial velocity of these members is $V_{hel} = -199$\,km s$^{-1}$, with a dispersion of 27\,km s$^{-1}$.
+\citet{williams;et-al_2011} employed a selection criteria of $-250 < V_{hel} < -150$\,km s$^{-1}$, $30\,^\circ < l < 75\,^\circ, J > 10.3$ and identified 15 stream candidates.
+The average heliocentric radial velocity of these members was found to be $V_{HELIO} = -199$\,km s$^{-1}$, with a dispersion of 27\,km s$^{-1}$.
 When compared to other streams identified in the halo, this is an unusually wide kinematic dispersion.
 Streams are generally considered to be kinematically cold, with dispersions of $\sigma_v < 8$\,km s$^{-1}$.
-The radial velocities outputted by the RAVE survey are described to be $\sim{}2$\,km s$^{-1}$, so the wide kinematic distribution is not limited by the observational data.
+The radial velocities outputted by the RAVE survey are described to be $\sim2$\,km s$^{-1}$, so the wide kinematic distribution appears to be real.
 
 % is it a real substructure
-\citet{Williams;et-al_2011} quantified the statistical significance of the Aquarius substructure with comparisons to the Besancon and Galaxia models.
+\citet{williams;et-al_2011} quantified the statistical significance of the Aquarius substructure with comparisons to the Besancon and Galaxia models.
 After populating the models, the galaxy representations were discretized in $\Delta{}V_{hel}$ and $\Delta{}l$ grid blocks.
@@
 % What is it?
-Given the extent of stellar debris the Sagittarius dwarf has littered in the Milky Way, it is reasonable to suspect the Aquarius stream may simply be Sagittarius in origin.
-Although the metallicities reported by \citet{Williams;et-al_2011} are not dissimilar from the stream, the distances and $V_{Z}$, $V_\phi$ for Aquarius are quite distinct from Sagittarius.
-\citet{Williams;et-al_2011} concluded that the newly discovered stream could not be positively associated with the Monoceros stream, Hercules-Aquila cloud, or either the Canis Major or Virgo Overdensities.
+Given the extent of stellar debris the Sagittarius dwarf has littered in the Milky Way, it is reasonable to suspect the Aquarius stream might be Sagittarius in origin.
+Although the metallicities reported by \citet{williams;et-al_2011} are not dissimilar from the stream, the distances and $V_{Z}$, $V_\phi$ for Aquarius are quite distinct from Sagittarius.
+\citet{williams;et-al_2011} concluded that the newly discovered stream could not be positively associated with the Monoceros stream, Hercules-Aquila cloud, or either the Canis Major or Virgo Overdensities.
 
 % MRS follow-up by de boer
-In order to investigate the Aquarius progenitor and any possible association with existing substructures, \citet{Wylie-de_boer;et-al_2012} observed six Aquarius stream members with medium resolution (R = 25,000) spectroscopy.
-Their data indicates the stream is chemically coherant, with a dispersion of only 0.1\,dex.
+In order to investigate the Aquarius progenitor and any possible association with existing substructures, \citet{wylie-de-boer;et-al_2012} observed six Aquarius stream members with medium resolution (R = 25,000) spectroscopy.
+Their data indicates the stream is chemically coherant, with a dispersion in [Fe/H] of only 0.1\,dex.
+This minimal chemical scatter suggests that the Aquarius stream progenitor is a globular cluster, since dwarf spheroidal galaxies  exhibit chemical dispersions of a dex or more \citet{Frebel_Norris_2011}.
+
  Based on sodium and nickel abundance ratios with respect to iron, they claim the Aquarius stream chemical signatures unambiguously represent those of a globular cluster.
-Additional abundances of oxygen, magnesium and aluminium are reported to solidify this claim.
 
@@
 
-We seek to investigate the globular cluster origin claim made by \citet{wylie-de_Boer;et-al_2012}.
-We present a detailed chemical abundance analysis for six confirmed Aquarius stream members observed using the Magellan Inamori Kyocera Echelle spectrograph \citep{Bernstein;et-al_2002} on the Magellan telescope.
+We seek to investigate the globular cluster origin claim made by \citet{wylie-de-boer;et-al_2012}.
+We present a detailed chemical abundance analysis for five confirmed Aquarius stream members observed using the Magellan Inamori Kyocera Echelle spectrograph \citep{Bernstein;et-al_2003} on the Magellan telescope.
 Details of the observations and data reduction are outlined in the following section.
-The data analysis is presented in \S\ref{sec:analysis} and a detailed discussion of these results resides in \S\ref{sec:discussion}, as well as an alternative hypothesis for the origin of the Aquarius stream.
+The data analysis is presented in \S\ref{sec:analysis} and a detailed discussion of these results resides in \S\ref{sec:discussion}.
 In \S\ref{sec:conclusion} we present our conclusions and critical interpretations.
@@
 
-The most comprehensive sample of Aquarius stream stars is presented in the discovery paper of \citet{Williams;et-al_2011}.
-Since the globular cluster origin claim of \citet{de_Boer;et-al_2012} is based from a subset of six of these stars, we targeted stars largely from the sample of \citet{de_Boer;et-al_2012}.
-An additional star from the original \citet{Williams;et-al_2011} sample, J2306265-085103, was also observed.
-Program stars were observed in July 2011 and we used standard stars observed for a separate program in March 2011.
-All standard and program observations were observed using the 1.0" slit, which provides a spectral resolution of $R = 28,000$.
-The exposure times for our program stars varied per star from X seconds to Y seconds, providing a signal-to-noise in excess of 100 per pixel element at 600 nm for all stars.
+The most comprehensive sample of Aquarius stream stars is presented in the discovery paper of \citet{williams;et-al_2011}.
+Since the globular cluster origin claim of \citet{wylie-de-boer;et-al_2012} is based from a subset of six of these stars, we targeted stars largely from this study.
+Four of our stars are in common with \citet{wylie-de-boer;et-al_2012}.
+An additional star from the original \citet{williams;et-al_2011} sample, J2306265-085103, was also observed.
+J2306265-085103 had insufficient S/N for the RAVE pipeline to accurately determine stellar parameters, so its membership hinges on radial velocity measurements.
+Program stars were observed in July 2011 and we observed X standard stars observed for a separate program in March 2011.
+All observations were taken using the 1.0" slit, which provides a spectral resolution of $R = 28,000$.
+The exposure times for our program stars varied per star from X seconds to Y seconds to ensure a signal-to-noise in excess of 100 per pixel element at 600 nm for all stars.
 
 The data were reduced using the CarPy pipeline.
-Standard ThAr arc lamp exposures were taken to provide wavelength calibration.
-Quartz and milky flat fields at the start of each night were used.
-No telluric corrections were made as atmospheric absorption does not affect any of the our lines of interest.
-Each reduced echelle order was interactively normalised using a third order spline.
-All orders were then stitched together to provide a full spectral coverage from 3800-9400\,\AA{}.
+Standard flat-fielding and extraction methods were employed using 10 quartz and 10 milky frames taken at the start of each night.
+ThAr arc lamp exposures were taken at the start of each night to provide wavelength calibration.
+No telluric corrections were made as atmospheric absorption does not affect any of the transitions in our line list.
+Each reduced echelle order was carefully normalised using a third order spline.
+All normalised orders were stitched together to provide a single one-dimensional spectrum from 3800-9400\,\AA{}.
 
@@
 The radial velocity for each star was determined in a two-step method.
-An initial estimate of the radial velocity was ascertained by cross-correlation with a synthetic spectrum of a giant with $T_{eff} = 4500$\,K, $\log{g} = 1.5$, and [M/H] $= -1.0$ across the wavelength range $8450 - 8700$ \AA{}, allowing us to place our spectrum at pseudo-rest.
+An initial estimate of the radial velocity was ascertained by cross-correlation with a synthetic spectrum of a giant with $T_{eff} = 4500$\,K, $\log{g} = 1.5$, and [M/H] $= -1.0$ across the wavelength range $8450 - 8700$ \AA{}.
+The spectrum was shifted to rest frame using this initial velocity.
 Velocities found from cross-correlation are typically within 1\,km\,s$^{-1}$ of our final published value.
 
-The equivalent widths for $\sim{}N$ absorption lines were measured, allowing for the radial velocity of each line to be calculated from the ratio of laboratory and rest wavelengths.
-The final radial velocity is then given by the mean of these $\sim{}N$ measurements.
-Figure \ref{fig:line-velocities} shows the line velocities for HD440077 after  being placed at rest using our cross-correlation velocity of X.XX\,km s$^{-1}$.
-As expected, the mean offset is small ($-1.1$\,km s$^{-1}$), and our standard deviation is X.XX\,km s$^{-1}$ from N line measurements.
-This provides us with a final measured radial velocity of $X.XX \pm X.XX$\,km s$^{-1}$.
-This process was repeated for all standards and observations.
+With our spectrum at near-rest, we measured the equivalent widths of $N$ lines by fitting Gaussian functions to the absorption profiles.
+Fitting Gaussian profiles provides us with the measured equivalent width, the full-width half-maximum of the profile, and the central wavelength.
+Thus, the residual radial velocity can be found from the ratio of the central and rest line wavelengths.
+The final radial velocity for the star is provided by the mean of these $N$ line velocity measurements.
+Figure \ref{fig:line-velocities} shows the line velocities for HD41667 after  being placed at rest using our cross-correlation velocity of 314.4\,km s$^{-1}$.
+As expected, the mean offset is small ($-0.75$\,km s$^{-1}$), and our standard deviation is 0.79\,km s$^{-1}$ from 164 line measurements.
+This provides us with a final measured radial velocity of $313.7 \pm 0.1$\,km s$^{-1}$.
+This process was repeated for all observations.
 The radial velocities published in Table \ref{tab:observations} are the final values from this two-step method.
-Heliocentric velocities agree excellently () with previously reported literature values \citep{Williams;wylie-de_boer;2012}.
+Heliocentric velocities agree excellently (within X\,km s$^{-1}$) with previously reported literature values \citep{williams;et-al_2011,wylie-de-boer;et-al_2012}.
+
+\begin{figure}[h]
+	\includegraphics[width=\columnwidth]{./figures/line-velocity.pdf}
+	\caption{Line velocity measurements.}
+	\label{fig:line-velocities}
+\end{figure}
 
@@
 
-For the measurement of atomic absorption lines, we employed the line list of \citet{Yong;et-al_2009} with additional transitions of Cr, Sc, Zn, and Sr from \citet{Frebel;et-al_2009}.
+For the measurement of atomic absorption lines, we employed the line list of \citet{yong;et-al_2005} with additional transitions of Cr, Sc, Zn, and Sr from \citet{frebel;et-al_2010}.
+We supplemented the list with hyperfine-structure data for Sc and Mn from the Kurucz compilation \citet{Kurucz;1998}.
 Molecular line data for CH was taken from \citet{Plez;et-al_2008,Plez;et-al_2009}.
-We further supplemented the list with hyperfine-structure data for Sc and Mn  from the Kurucz compilation \citet{Kurucz;1998}.
-For lines with hyperfine structure, blended transitions or molecular features, we used a spectral synthesis approach.
-The abundance of a given species was obtained by matching a synthetic spectrum of known abundance to the observed spectrum.
+For lines with hyperfine structure, blended transitions or molecular features, we determined the transition abundance using a spectral synthesis approach where the abundance of a given species is found by by matching a synthetic spectrum to the observed spectrum.
+
+The equivalent widths for all transitions were measured automatically using software for this study.
+Given the rest wavelength and an initial guess of the FWHM, a Gaussian function is iteratively fitted to the absorption profile.
+At the same time, the local continuum is found within 20\,\AA{} either side of the rest wavelength using a second-order polynomial.
+Measuring the local continuum ensures any errors in our initial normalisation or order-stitching do not propagate through to our equivalent width measurements.
+Any group of pixels that deviate significantly ($>2\sigma$) to the local continuum are cosmic ray hits, or more likely trough points of a neighbouring profile.
+We attempt to fit a Gaussian profile to each of these groups of deviating pixels, using the best estimate of the local continuum.
+If a profile is successfully fitted, then all points belonging to that profile are excluded from the continuum determination.
+When fitting Gaussian profiles, the $\chi^2$ difference between the observation and the profile is minimized.
+In order to account for blended transitions, our $\chi^2$ function is weighted based on the distance to the rest wavelength.
+Pixels near the rest wavelength are weighted higher than those on the wings.
+Although this approach relies on an accurate ($<4$\,km s$^{-1}$) radial velocity correction, it greatly improves the accuracy of the equivalent width measurements.
+
+We note that the results of our iterative fitting approach are entirely insensitive to the initial FWHM guess.
+Increasing the initial guess from 0.1\,\AA{} to 1 or 2\,\AA{} -- an unphysical large value for high-resolution spectra -- does not alter our equivalent width measurements.
+Only a small increase in computational cost is observed.
+Although we are confident in our automatic equivalent width measurements, every absorption profile was examined by eye for quality.
 
 We list the atomic data and measured equivalent widths for atomic lines used during this analysis in Table \ref{tab:equivalent-widths}.
-In order to exclude saturated lines we only used lines with a reduced equivalent widths $\log_{10}{(\mbox{EW}/\lambda)} < -4.5$ in our chemical abundance analysis.
-A minimum detectable equivalent width was measured as a function of wavelength, and only lines that exceeded a $3\sigma$ detection significance were included.
-We have verified our equivalent width measurement techniques by measuring equivalent widths for N lines in HD140283 and comparing our measurements with the study of \citet{Norris;et-al_2000}.
+Saturated lines were excluded by removing measurements with reduced equivalent widths, $\log_{10}{(EW/\lambda)} > -4.5$\, dex.
+A minimum detectable equivalent width was calculated as a function of wavelength based on the S/N, and only lines that exceeded a $3\sigma$ detection significance were included.
+We have verified our equivalent width measurement techniques by comparing our measurements for 164 lines in HD140283 with the study of \citet{Norris;et-al_1996}.
 Excellent agreement is found between the two studies, which is illustrated in Figure \ref{fig:ew-compare}.
-The mean difference between this study and that of \cite{Norris;et-al_2000} is a negligible $0.64 \pm 2.78$\,m\AA{}, and no systematic trend is present.
+The mean difference between this study and that of \cite{norris;et-al_1996} is a negligible $0.64 \pm 2.78$\,m\AA{}, and no systematic trend is present.
 
@@
 We employed the ATLAS9 stellar atmospheres of \citet{Castelli;Kurucz_2003} for this analysis.
-These one-dimensional models ignore any centre-to-limb spatial variations, assume local thermodynamic equilibrium as well as overall hydrostatic equilibrium, and assumes no convective overshoot from the photosphere.
+These one-dimensional models ignore any centre-to-limb spatial variations, assume hydrostatic equilibrium and no convective overshoot from the photosphere.
+Absorption lines are assumed to form under the assumption of local thermal equilibrium.
 The stellar parameter spacing for these grid models is 250\,K, 0.5 dex in surface gravity, 0.5 dex in [M/H] and 0.1 dex in [$\alpha$/Fe].
-We interpolated the stellar densities, temperatures, electron pressures at all stellar depths between atmospheres using the Quickhull algorithm during our analyses.
-Quickhull is reliant on Delaunay tessellation, which suffers from extremely skewed cells when the grid points vary in size by orders of magnitude -- as $T_{eff}$ values do compared to $\log{g}$ or [M/H].
-If unaccounted for, these asymmetric cells can manifest as non-negligible errors in interpolated densities, temperatures, pressures, and opacities across all photospheric depths.
+We interpolated the atmospheric densities, temperatures, electron pressures at all depths between stellar atmospheres using the Quickhull algorithm for this analysis.
+Quickhull is reliant on Delaunay tessellation, which suffers from extremely skewed cells when the grid points vary in size by orders of magnitude -- as $T_{eff}$ values do compared to $\log{g}$ or [X/H].
+If unaccounted for, these asymmetric cells can manifest as significant errors in interpolated densities, temperatures, pressures, and opacities across all photospheric depths.
 We scaled each stellar parameter between zero and unity prior to interpolation to minimise these errors.
@@
 The most recent version of the spectral synthesis code MOOG \citep{Sneden;et-al_1973} has been used to derive individual line abundances and stellar parameters.
-This version employs a more accurate treatment of Rayleigh scattering \citet{Sobeck;et-al_2011}, which is particularly important for transitions blueward of 450\,nm.
-This is noteworthy, but is less relevant for this analysis as most of our line measurements blueward of 450\,nm are too blended and not used.
-We have scaled our abundances to solar values using the abundances of \citet{Asplund;et-al_2009}.
+This version employs a more accurate treatment of Rayleigh scattering \citep{Sobeck;et-al_2011}, which is particularly important for transitions blueward of 450\,nm.
+This is noteworthy, but is less relevant for this analysis as most of our line measurements are redward of 450\,nm.
+We have scaled our abundances to solar values using the chemical composition of \citet{Asplund;et-al_2009}.
 
@@
 In the same way, the microturbulence was found by demanding a zero trend in reduced equivalent width against abundance.
-Linear relationships with slopes of $|0.005|$ dex were considered to be converged.
+Linear relationships with slopes of $|0.001|$ dex were considered to be converged.
 Surface gravity was found by forcing the mean Fe\,I and Fe\,II abundances to be equal, whilst maintaining zero trends with the excitation potential, reduced equivalent width and abundance.
@@
 C2225316-14437	& 4350	& 1.60	& 1.80	& --1.19	
-				& 4235 $\pm$ 118 & 1.45 $\pm$ 0.21 & 1.96 $\pm$ 0.11 & --1.20 $\pm$ 0.14 \\
+				& 4235 $\pm$ 118 & 1.45 $\pm$ 0.21 & 1.96 $\pm$ 0.11 & --1.20 $\pm$ 0.14 
+				& \citet{wylie-de-boer;et-al_2012} \\
 C2306265-085103	& 4180	& 1.00	& 1.80 	& --1.16
@@
 
+\begin{deluxetable*}{lccccccclcccccc}
+\tablecolumns{15}
+\tablecaption{Program Star Abundances\label{tab:program-star-abundances}}
+\tablehead{
+ \multicolumn{7}{c}{J221821-183424} & \colhead{} & \multicolumn{7}{c}{C2225316-14437} \\
+ \cline{1-7} \cline{9-15} \\
+\colhead{Species} & $N$ & $\log\epsilon(X)$ & $\sigma_\epsilon$ & [X/H] & [X/Fe] & $\sigma$ &&
+\colhead{Species} & $N$ & $\log\epsilon(X)$ & $\sigma_\epsilon$ & [X/H] & [X/Fe] & $\sigma$
+}
+\startdata
+   O \textsc{I} &   2 &    7.50 &    0.04 & $-$1.18 &    0.41 &    0.02 &&
+   O \textsc{I} &   2 &    7.90 &    0.01 & $-$0.79 &    0.48 &    0.01 \\
+  Na \textsc{I} &   2 &    4.56 &    0.14 & $-$1.68 & $-$0.08 &    0.10 &&
+  Na \textsc{I} &   3 &    5.09 &    0.17 & $-$1.15 &    0.12 &    0.10 \\
+  Mg \textsc{I} &   4 &    6.55 &    0.37 & $-$1.04 &    0.55 &    0.18 &&
+  Mg \textsc{I} &   4 &    6.98 &    0.24 & $-$0.62 &    0.65 &    0.12 \\
+  Al \textsc{I} &   1 &    5.04 &    0.00 & $-$1.41 &    0.18 & \nodata &&
+  Al \textsc{I} &   4 &    5.87 &    0.09 & $-$0.58 &    0.68 &    0.04 \\
+  Si \textsc{I} &   5 &    6.28 &    0.08 & $-$1.23 &    0.37 &    0.04 &&
+  Si \textsc{I} &   5 &    6.96 &    0.15 & $-$0.55 &    0.72 &    0.07 \\
+  Ca \textsc{I} &   4 &    4.97 &    0.04 & $-$1.37 &    0.23 &    0.02 &&
+  Ca \textsc{I} &   4 &    5.50 &    0.04 & $-$0.84 &    0.43 &    0.02 \\
+  Sc \textsc{I} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata &&
+  Sc \textsc{I} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
+ Sc \textsc{II} &   6 &    1.52 &    0.08 & $-$1.63 & $-$0.04 &    0.03 &&
+ Sc \textsc{II} &   5 &    2.05 &    0.13 & $-$1.10 &    0.17 &    0.06 \\
+  Ti \textsc{I} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata &&
+  Ti \textsc{I} &   4 &    4.04 &    0.03 & $-$0.91 &    0.36 &    0.01 \\
+ Ti \textsc{II} &   4 &    3.81 &    0.13 & $-$1.14 &    0.45 &    0.07 &&
+ Ti \textsc{II} &   2 &    4.26 &    0.08 & $-$0.69 &    0.58 &    0.06 \\
+   V \textsc{I} &   3 &    2.23 &    0.01 & $-$1.70 & $-$0.11 &    0.01 &&
+   V \textsc{I} &   6 &    2.92 &    0.17 & $-$1.01 &    0.26 &    0.07 \\
+  Cr \textsc{I} &  11 &    3.74 &    0.07 & $-$1.90 & $-$0.30 &    0.02 &&
+  Cr \textsc{I} &   8 &    4.27 &    0.16 & $-$1.37 & $-$0.10 &    0.06 \\
+  Mn \textsc{I} &   3 &    3.29 &    0.04 & $-$2.14 & $-$0.54 &    0.02 &&
+  Mn \textsc{I} &   3 &    4.14 &    0.05 & $-$1.29 & $-$0.02 &    0.03 \\
+  Fe \textsc{I} &  52 &    5.91 &    0.09 & $-$1.59 &    0.00 &    0.01 &&
+  Fe \textsc{I} &  61 &    6.23 &    0.11 & $-$1.27 &    0.00 &    0.01 \\
+ Fe \textsc{II} &  13 &    5.90 &    0.05 & $-$1.60 &    0.00 &    0.01 &&
+ Fe \textsc{II} &  10 &    6.17 &    0.06 & $-$1.33 & $-$0.07 &    0.02 \\
+  Co \textsc{I} &   1 &    3.35 &    0.00 & $-$1.64 & $-$0.05 & \nodata &&
+  Co \textsc{I} &   3 &    3.92 &    0.12 & $-$1.07 &    0.20 &    0.07 \\
+  Ni \textsc{I} &   5 &    4.61 &    0.15 & $-$1.61 & $-$0.01 &    0.07 &&
+  Ni \textsc{I} &   7 &    5.04 &    0.09 & $-$1.18 &    0.09 &    0.03 \\
+  Cu \textsc{I} &   1 &    2.13 &    0.00 & $-$2.06 & $-$0.47 & \nodata &&
+  Cu \textsc{I} &   1 &    3.35 &    0.00 & $-$0.84 &    0.43 & \nodata \\
+  Zn \textsc{I} &   2 &    3.15 &    0.11 & $-$1.41 &    0.19 &    0.08 &&
+  Zn \textsc{I} &   2 &    3.46 &    0.23 & $-$1.10 &    0.17 &    0.17 \\
+\cline{1-7} \cline{9-15} \\
+\\
+\multicolumn{7}{c}{J223504-152834} && \multicolumn{7}{c}{J223811-104126} \\
+\cline{1-7} \cline{9-15} \\
+   O \textsc{I} &   2 &    8.48 &    0.09 & $-$0.21 &    0.46 &    0.07 &&
+   O \textsc{I} &   1 &    8.60 &    0.00 & $-$0.09 &    1.36 & \nodata \\
+  Na \textsc{I} &   3 &    5.76 &    0.12 & $-$0.48 &    0.19 &    0.07 &&
+  Na \textsc{I} &   2 &    4.76 &    0.10 & $-$1.48 & $-$0.03 &    0.07 \\
+  Mg \textsc{I} &   3 &    7.50 &    0.24 & $-$0.10 &    0.58 &    0.14 &&
+  Mg \textsc{I} &   3 &    6.49 &    0.42 & $-$1.11 &    0.34 &    0.24 \\
+  Al \textsc{I} &   3 &    6.10 &    0.08 & $-$0.35 &    0.32 &    0.05 &&
+  Al \textsc{I} &   2 &    5.10 &    0.14 & $-$1.35 &    0.10 &    0.10 \\
+  Si \textsc{I} &   5 &    7.11 &    0.10 & $-$0.40 &    0.28 &    0.04 &&
+  Si \textsc{I} &   3 &    6.38 &    0.04 & $-$1.13 &    0.32 &    0.02 \\
+  Ca \textsc{I} &   4 &    6.03 &    0.04 & $-$0.31 &    0.36 &    0.02 &&
+  Ca \textsc{I} &   4 &    5.30 &    0.03 & $-$1.04 &    0.41 &    0.01 \\
+  Sc \textsc{I} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata &&
+  Sc \textsc{I} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
+ Sc \textsc{II} &   6 &    2.70 &    0.14 & $-$0.45 &    0.23 &    0.06 &&
+ Sc \textsc{II} &   6 &    1.75 &    0.14 & $-$1.40 &    0.05 &    0.06 \\
+  Ti \textsc{I} &   4 &    4.63 &    0.02 & $-$0.32 &    0.36 &    0.01 &&
+  Ti \textsc{I} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
+ Ti \textsc{II} &   2 &    4.92 &    0.26 & $-$0.04 &    0.64 &    0.19 &&
+ Ti \textsc{II} &   4 &    3.83 &    0.09 & $-$1.12 &    0.33 &    0.04 \\
+   V \textsc{I} &   6 &    3.67 &    0.22 & $-$0.26 &    0.41 &    0.09 &&
+   V \textsc{I} &   1 &    2.42 &    0.00 & $-$1.51 & $-$0.06 & \nodata \\
+  Cr \textsc{I} &   7 &    4.94 &    0.09 & $-$0.70 & $-$0.02 &    0.03 &&
+  Cr \textsc{I} &  12 &    4.12 &    0.06 & $-$1.52 & $-$0.07 &    0.02 \\
+  Mn \textsc{I} &   3 &    5.08 &    0.10 & $-$0.35 &    0.33 &    0.06 &&
+  Mn \textsc{I} &   3 &    3.55 &    0.04 & $-$1.88 & $-$0.43 &    0.02 \\
+  Fe \textsc{I} &  64 &    6.83 &    0.12 & $-$0.67 &    0.00 &    0.02 &&
+  Fe \textsc{I} &  33 &    6.05 &    0.06 & $-$1.45 &    0.00 &    0.01 \\
+ Fe \textsc{II} &  12 &    6.82 &    0.07 & $-$0.68 &    0.00 &    0.02 &&
+ Fe \textsc{II} &  11 &    6.00 &    0.09 & $-$1.50 & $-$0.05 &    0.03 \\
+  Co \textsc{I} &   3 &    4.53 &    0.14 & $-$0.46 &    0.21 &    0.08 &&
+  Co \textsc{I} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
+  Ni \textsc{I} &   7 &    5.62 &    0.09 & $-$0.60 &    0.08 &    0.03 &&
+  Ni \textsc{I} &   2 &    4.82 &    0.04 & $-$1.40 &    0.05 &    0.03 \\
+  Cu \textsc{I} &   1 &    3.85 &    0.00 & $-$0.34 &    0.33 & \nodata &&
+  Cu \textsc{I} &   1 &    2.39 &    0.00 & $-$1.80 & $-$0.35 & \nodata \\
+  Zn \textsc{I} &   2 &    4.17 &    0.03 & $-$0.39 &    0.28 &    0.02 &&
+  Zn \textsc{I} &   2 &    3.17 &    0.04 & $-$1.39 &    0.06 &    0.03 \\
+
+\cline{1-7} \cline{9-15} \\
+\\
+\multicolumn{7}{c}{C2306265-085103} && \\
+\cline{1-7} \\
+   O \textsc{I} &   2 &    8.09 &    0.15 & $-$0.60 &    0.57 &    0.10 \\
+  Na \textsc{I} &   2 &    5.25 &    0.00 & $-$0.99 &    0.18 &    0.00 \\
+  Mg \textsc{I} &   2 &    6.84 &    0.07 & $-$0.76 &    0.41 &    0.05 \\
+  Al \textsc{I} &   4 &    5.56 &    0.08 & $-$0.89 &    0.28 &    0.04 \\
+  Si \textsc{I} &   5 &    6.66 &    0.08 & $-$0.85 &    0.32 &    0.03 \\
+  Ca \textsc{I} &   4 &    5.48 &    0.04 & $-$0.86 &    0.31 &    0.02 \\
+  Sc \textsc{I} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
+ Sc \textsc{II} &   6 &    2.18 &    0.15 & $-$0.97 &    0.20 &    0.06 \\
+  Ti \textsc{I} &   4 &    4.06 &    0.03 & $-$0.89 &    0.28 &    0.01 \\
+ Ti \textsc{II} &   3 &    4.21 &    0.36 & $-$0.74 &    0.43 &    0.21 \\
+   V \textsc{I} &   4 &    2.88 &    0.06 & $-$1.05 &    0.12 &    0.03 \\
+  Cr \textsc{I} &   4 &    4.20 &    0.26 & $-$1.44 & $-$0.27 &    0.13 \\
+  Mn \textsc{I} &   3 &    4.35 &    0.10 & $-$1.08 &    0.09 &    0.06 \\
+  Fe \textsc{I} &  63 &    6.33 &    0.12 & $-$1.17 &    0.00 &    0.01 \\
+ Fe \textsc{II} &  11 &    6.31 &    0.09 & $-$1.19 & $-$0.02 &    0.03 \\
+  Co \textsc{I} &   3 &    4.00 &    0.15 & $-$0.99 &    0.18 &    0.08 \\
+  Ni \textsc{I} &   7 &    5.08 &    0.08 & $-$1.14 &    0.03 &    0.03 \\
+  Cu \textsc{I} &   1 &    3.55 &    0.00 & $-$0.64 &    0.53 &    0.00 \\
+  Zn \textsc{I} &   2 &    3.38 &    0.14 & $-$1.18 & $-$0.01 &    0.10
+\enddata
+\end{deluxetable*}
+
 % elemental abundances
@@
 
+We seek to investigate the nature of the Aquarius stream, as well as the specific globular cluster origin claim by \citet{wylie-de-boer;et-al_2012}.
+The stellar parameters reported in \citet{wylie-de-boer;et-al_2012} differ slightly to those found in Table \ref{tab:stellar-parameters}.
+\citet{wylie-de-boer;et-al_2012} deduce their stellar parameters through the use of a $\chi^2$ analysis against synthetic spectra from the \citet{munari;et-al_2005} grid.
+Our temperatures have been determined by forcing a zero trend in excitation potential and line abundance.
+In general, these temperatures agree within the uncertainties, with our temperatures being marginally (23-175 K) hotter.
+The only noteworthy exception is J223811-104126, where we find an effective temperature 546 K cooler than \citet{wylie-de-boer;et-al_2012}.
+This is the largest discrepancy we see in any of our standard or program stars.
+
+\citet{wylie-de-boer;et-al_2012} calculate microturbulence with the empirical relationships from \citet{Reddy;et-al_2003} for dwarfs and \citet{fulbright_2000} for giants.
+These relationships are based upon the derived temperature and surface gravities.
+Our published microturbulence values agree excellently with the values presented in \citet{wylie-de-boer;et-al_2012} with the exception of J223811-104126, which we find to be a F-type giant and others have claimed is a -type dwarf from medium-resolution spectra \citep{wylie-de-boer;et-al_2012, williams;et-al_2011}.
+Small discrepancies in microturbulence for other stars can be directly attributed to difference in surface gravities.
+
 \subsection{Stellar Parameter Discrepancies with \citet{wylie-de-boer;et-al_2012}}
 
-We repeated our equivalent-width analysis using the atomic line list supplied in \citet{wylie-de-boer;et-al_2012}.
-Given the lower spectral resolution and modest signal-to-noise in their study, there are fewer unblended absorption lines available.
+The stellar parameter discrepancies between this study and \citet{wylie-de-boer;et-al_2012} need to be addressed.
+There are noteworthy differences in the stellar parameter determination between these studies.
+In the \citet{wylie-de-boer;et-al_2012} study, the temperature, metallicity and surface gravity were found by a $\chi^2$ analysis against the spectral library of \citet{munari;et-al_2005} after it was convolved and re-sampled to match the observational data.
+The comparison regions used for analysis were 4900-5200\,\AA{} and 5575-5725\,\AA{}.
+Using these parameters, an interpolated MARCS (?) model atmosphere was used to synthesise elemental abundances.
+Oscillator strengths in their line list were astrophysical; they were derived from a reverse analysis using the \citet{hinkle;et-al_2003} solar atlas.
+The spectrum synthesis code \textsc{MOOG} was used to derive abundances for individual Fe\,I and Fe\,II lines.
+The median abundance of Fe\,I lines was taken as the overall stellar metallicity, scaled using the \citet{Grevesse;Sauval_1998} solar abundances.
+
+The study of \citet{wylie-de-boer;et-al_2012} is of slightly lower resolution ($R = 25,000$ compared to $R = 28,000$ presented here), but with a much lower signal-to-noise ratio: $\sim{}25$ compared to $>100$ per pixel element achieved here.
+Given the slightly lower spectral resolution and modest signal-to-noise in their study, there are fewer unblended absorption lines available.
 In fact, there are very few transitions present in their published line list: only 14 Fe\,I lines and 3 Fe\,II lines are available.
-The oscillator strengths for these lines were calculated from a reverse spectral analysis using the \citet{Hinkle;et-al_2003} solar atlas.
+For contrast, our metallicity determinations are based off X Fe\,I and Y Fe\,II lines.
+Given the metallicity of these stars, it is somewhat surprising that there were not more unblended transitions available to \citet{wylie-de-boer;et-al_2012}.
+
+With the exception of J223811-104126, we believe our stellar parameters are largely in agreement with the exception of metallicity.
+The Fe\,I abundances differ significantly for the four stars in common: 0.01\,dex, $-$0.45\,dex, 0.33\,dex, $-$0.24\,dex.
+In order to investigate the source of these discrepancies, we repeated our analysis for the four common stars using the line list of \citet{wylie-de-boer;et-al_2012}.
+The results of this analysis is shown in Table \ref{tab:wylie-de-boer-analysis-comparison}.
+
+One Fe\,I line at 6420.060\,\AA{} was not detectable in any of our stars, even though the S/N at this point exceeds 120 in every observation.
+Additionally, we could not identify the line in the existing VALD database.
+
+% talk about stellar parameter differences
+
+% we find their metallicities
+
+Given the line list employed, the overall data quality and the lack of Fe\,I lines available for analysis, it appears the Aquarius stream stars have conspired to present a tight metallicity distribution function -- suggesting of a globular cluster origin.
+In contrast, our high-resolution analysis suggests a significantly broader metallicity distribution of $\langle$[Fe/H]$\rangle = X.XX \pm X.XX$ dex.
+
+\subsection{The Aquarius Stream M.D.F.}
+
+\subsection{The Na-O Relationship}
+
+\subsection{The Al-Mg Relationship}
+
+\subsection{The Na-Na Relationship}
+
+\subsection{Possible Progenitors}
 
@@
 
-% chemistries - [Ni/Na]
+% chemistries - [Na/O]
 
@@
 
-% which GC's do not show these trends
+% chemistries - [Ni/Na]
 
@@
 
+%\facilities{Magellan:Clay}
+
+\bibliographystyle{apj}
+\bibliography{bibliography}
+
 \end{document}

### 2012-12-04 2012-aqs/figures/plot-toombre.py
Added toombre plot

@@ -1,0 +1,57 @@
+import numpy as np
+import matplotlib.pyplot as plt 
+
+
+v0 = 220 # km/s
+vrot = 180 # km/s
+
+U, V, W, kind = np.loadtxt('nissen_schuster_2010.data', delimiter='|', skiprows=9, dtype=str, usecols=(-4, -3, -2, -1), unpack=True)
+
+U = np.array(map(float, U))
+V = np.array(map(float, V))
+W = np.array(map(float, W))
+
+
+# Thick disk stars
+thick_disk = np.where(kind == 'TD')[0]
+
+# High alpha stars
+high_alpha = list(np.where(kind == 'high-alpha')[0])
+high_alpha.extend(np.where(kind == '(high-alpha)')[0])
+
+high_alpha = np.array(high_alpha)
+
+low_alpha = list(np.where(kind == 'low-alpha')[0])
+low_alpha.extend(np.where(kind == '(low-alpha)')[0])
+
+low_alpha = np.array(low_alpha)
+
+
+fig = plt.figure()
+ax = fig.add_subplot(111)
+
+# Thick disk stars
+ax.scatter(V[thick_disk], pow(pow(U[thick_disk], 2) + pow(W[thick_disk], 2), 0.5), color='r', marker='+', facecolor='none')
+
+# Low-alpha stars
+ax.scatter(V[low_alpha], pow(pow(U[low_alpha], 2) + pow(W[low_alpha], 2), 0.5), color='b', marker='o', facecolor='b')
+
+# High-alpha stars
+ax.scatter(V[high_alpha], pow(pow(U[high_alpha], 2) + pow(W[high_alpha], 2), 0.5), color='g', marker='o', facecolor='none')
+
+# Plot solar rotation line
+ax.plot([-v0, -v0], [0, 400], 'k:', zorder=-1)
+
+# Plot kinematic separation line at Vtot = 180 km/s
+x = np.arange(-180, 180)
+ax.plot(x, np.sqrt(pow(vrot, 2) - pow(x, 2)), 'k--', zorder=-1)
+
+# Set some limits
+
+ax.set_xlim(-450, 50)
+ax.set_ylim(0, 400)
+ax.set_xlabel('$V$ (km s$^{-1}$)')
+ax.set_ylabel('$(U^{2} + W^{2})^{-1/2}$ (km s$^{-1}$)')
+
+plt.savefig('plot-toombre.eps')
+plt.savefig('plot-toombre.pdf')

### 2012-12-04 2012-aqs/draft-aqs.tex
Updated plots + captions

@@
 	\includegraphics[width=\columnwidth]{./figures/line-velocity.pdf}
-	\caption{Line velocity measurements.}
+	\caption{Residual velocities for each absorption line with a well-fitted Gaussian profile after correcting for the doppler shift with our cross-correlation measurement.
+The mean residual velocity is within our uncertainties derived from cross-correlation.}
 	\label{fig:line-velocities}
@@
 Pixels near the rest wavelength are weighted higher than those on the wings.
-Although this approach relies on an accurate ($<4$\,km s$^{-1}$) radial velocity correction, it greatly improves the accuracy of the equivalent width measurements.
+Although this approach relies on a reasonably accurate ($<4$\,km s$^{-1}$) radial velocity correction, it greatly improves the accuracy of the equivalent width measurements.
 
 We note that the results of our iterative fitting approach are entirely insensitive to the initial FWHM guess.
-Increasing the initial guess from 0.1\,\AA{} to 1 or 2\,\AA{} -- an unphysical large value for high-resolution spectra -- does not alter our equivalent width measurements.
+Increasing the initial guess from 0.1\,\AA{} to 1 or 2\,\AA{} -- an unphysical large value for high-resolution spectra -- does not alter any of our equivalent width measurements.
 Only a small increase in computational cost is observed.
@@
 	\includegraphics[width=\columnwidth]{./figures/smh-norris.pdf}
-	\caption{The gold standard comparison.}
+	\caption{A comparison showing equivalent widths measured for HD140283 using an automatic routine (see \S\ref{sec:line-measurements}), and those found with careful hand measurements by \citet{norris;et-al_1996}.
+No systematic trend is present, and the mean difference between these studies is $\langle\Delta{}W_\lambda = -0.64 \pm 2.78$ m\AA{}.}
 	\label{fig:ew-compare}
@@
 
+% [alpha/Fe]
+\begin{figure}[h]
+	\includegraphics[width=\columnwidth]{./figures/aquarius-alpha-fe.pdf}
+	\caption{A plot showing $[\alpha/\mbox{Fe}]$ for all Aquarius stream stars.}
+	\label{fig:alpha-fe}
+\end{figure}
+
+% Mg-Al
+\begin{figure}[h]
+	\includegraphics[width=\columnwidth]{./figures/aquarius-mg-al.pdf}
+	\caption{A plot showing [Mg/Al] for all Aquarius stream stars.}
+	\label{fig:mg-al}
+\end{figure}
+
+% [Na/Fe], [Cr/Fe], [Ni/Fe]
+\begin{figure}[h]
+	\includegraphics[width=\columnwidth]{./figures/aquarius-na-cr-ni-fe.pdf}
+	\caption{A plot showing [Na/Fe], [Cr/Fe], and [Ni/Fe] for all Aquarius stream stars.}
+	\label{fig:na-cr-ni-fe}
+\end{figure}
+
+% [Na/Fe], [Ni/Fe]
+\begin{figure}[h]
+	\includegraphics[width=\columnwidth]{./figures/aquarius-na-ni.pdf}
+	\caption{A plot showing [Na/Fe] and [Ni/Fe] for all Aquarius stream stars.}
+	\label{fig:na-ni}
+\end{figure}
+
+% [O/Fe], [Na/Fe]
+\begin{figure}[h]
+	\includegraphics[width=\columnwidth]{./figures/aquarius-o-na.pdf}
+	\caption{A plot showing [O/Fe] and [Na/Fe] for all Aquarius stream stars.}
+	\label{fig:o-na}
+\end{figure}
+
+% Toombre
+\begin{figure}[h]
+	\includegraphics[width=\columnwidth]{./figures/plot-toombre.pdf}
+	\caption{Toombre plot.}
+	\label{fig:toombre}
+\end{figure}
+
 %\facilities{Magellan:Clay}

### 2012-12-04 2012-oss-mrs/Response_to_referee_report.txt
Updated resposnse to OSS MRS referee report

--- 2012-10-16 2012-oss-mrs/Response_to_referee_report.txt
@@
 
-1) ``Host' is not the usual way of referring to a stream's progenitor.
-Since stars in the stream are unbound from the progenitor and separated by kiloparsecs and billions of years, it is better to say ``Origin of the Orphan Stream' or ``Parent of the Orphan Stream' or ``Orphan Stream Progenitor'.
-
-Introduction
-
-2) In the second sentence, the statement ``left behind in a stream of stars' is somewhat misleading, since tidal streams will extend both forward along the progenitor's orbit as well as behind.
-This should be amended to something like ``are strewn along the progenitor's orbit in leading and trailing streams of stars.'
-
-Altered title to "Hunting the Parent of the Orphan Stream: Identifying Stream Members from Low-Resolution Spectroscopy", and two instances in the text where the Orphan Stream progenitor was referred to as the host:
-
- - Section 1
-   "as well as make predictions about the nature of the host system."
-
- - Section 5,
-   "help determine both the nature of the host system before it's discovered"
-
-In both cases, 'host system' has been changed to 'progenitor'.
-
-3) In the first sentence of the second paragraph and elsewhere in the text, an incorrect reference is made to Grillmair and Dionatos (2006). The correct reference is Grillmair 2006 (ApJ,645, L37).
-
-Section 2.
-
-4) In the last paragraph, it would better read ``recover stream giants and contaminating foreground dwarfs.'
-
-5) In this same paragraph, you should specify why no 2mass photometry is available. One assumes this is because even the giants are too faint to be detected in the 2mass survey.
-
-Section 3
-
-6) ``resolving power' should be ``spectral resolution'.
-
-7) ``median combined' should be hyphenated.
-
-8) ``criterion' should be ``criteria'.
-
-Section 4.2
-
-9) In the first paragraph, it is not clear from Figure 2 why this
-particular separation line is appropriate or optimal.
-More explanation and references should be provided.
-Also, ``allowing multiple inclusive cuts' is somewhat confusing.
-Should this be ``imposing simultaneous cuts on several observables'?
-
-10) In the last paragraph, the selection criteria used by Casey et al. (2012a) should be briefly summarized here.
-
-Section 4.3
-
-11) ``fainted' should be ``fainter'.
-
-12) In Table 1, the ra and dec components of proper motion should be listed separately.
-Strong cross-stream proper motion components could also be used to remove or reduce membership probabilities for some stars.
-
-13) Given the small number and significant color and magnitude spread among the highly probable members about the best-fitting isochrone in Figure 4, a distance uncertainty of only 1 kpc seems unlikely.
-How was this uncertainty estimated?
-
-14) The last sentence should include ``21.4 +/- 1 kpc estimated by Grillmair (2006) and Newberg et al.
-(2010).', since the distance estimates in these papers were independent and complementary, one using main sequence fitting and the other using BHB stars.
-
-Section 5
-
-15) In the first paragraph, a reference should be given to support the contention that the metallicity spread is consistent with what one might expect for a dwarf galaxy.
-
-16) The last sentence of the first paragraph should also refer to
-Grillmair (2006) main sequence fitting distance measurement.
-
-17) Given the title of the paper, does the new metallicity measurement help in any way to identify a possible progenitor?
-At the very least, a statement should be included to the extent that the orbit and the metallicity measurements rule out any of the classical dwarfs, and that if a bound progenitor still exists, then it must be an as yet undiscovered ultrafaint dwarf.
-
-18) The maximum likelihood estimates of the stream velocity given by the authors are either 85.3 /pm 4.4 km/s, or 82.1 /pm 1.4 km/s.
-A simple weighted mean of the values in Table 1 gives 83.0 km/s.
-This is very significantly different from the 105 km/s (using the author's V_gsr system) measured by Newberg et al.
-for the same part of the stream using BHB stars.
-This disagreement needs to be addressed, as it seriously undermines any confidence in the purity of even the ``high probability' sample.
-
-19) Moreover, though it is somewhat difficult to say given small number statistics, the metallicity distribution of the high probability stars looks more similar to the that of the off-stream, field star sample of Newberg et al.
-than it does to that of the stream sample.
-
-20) Newberg et al.
-find velocity dispersions in various parts of the Orphan stream of around 10 km/s.
-Here the case is made for a much lower velocity dispersion, even colder than that of globular cluster streams like Pal 5 and GD-1.
-It may well be that Newberg et al.'s velocities are generally less accurate than the present sample.
-However, one would still have to think about how a stream that is 8-10 times broader than these globular cluster streams should be kinematically just as cold or colder.
-Unfortunately, the disagreement with previous Orphan velocity measurements, and the fact that removing the weak signal stars makes this disagreement even larger while making the stream colder, undermines my confidence considerably.
-
-21) In thinking about this, I have made use of a velocity versus metallicity plot, with appropriate uncertainties.
-This makes it much easier to see why the authors are getting the results they see, and I would strongly recommend including such a plot in the final manuscript.
-
-22) The last sentence of the 3rd paragraph is somewhat mysterious.
-Is it the random motions that must be perpendicular to the line of sight, or the mean motions?
-The latter follows from the simple fact that the stars are in a stream, and the stream is nearly perpendicular to our line of sight.
-Unless I'm missing something important, this sentence should be deleted.
-
 ----------------------------------------------------------------------

### 2012-12-04 2012-aqs/draft-aqs.tex
Added Na-O text

@@
 
+% establish the relationship as a true phenomena
+
+Extensive studies looking at stars in globular clusters have revealed variations in light-element abundances, most notably an anti-correlation in sodium and oxygen content \citet{Norris;Da-Costa_1995}.
+Between generations of stars within a globular cluster, the oxygen abundance is transformed into nitrogen, reducing the overall oxygen abundance.
+This pattern has been repeatedly demonstrated in all well-studied globular clusters, although the strength of the anti-correlation varies between systems.
+Even though oxygen undergoes internal mixing during its evolution along the giant branch, it is now well established that any observed abundance variations due to such mixing is limited to Li, C, and N.
+Therefore, the observed anti-correlations in light elements required a different astrophysical explanation.
+
+In order to help explain this phenomena, \citet{Caretta;et-al_2009} defined three components of stars within a population: primordial, intermediate, and extreme.
+The [Na/Fe] and [O/Fe] abundances for a given star defines which component it belongs to.
+Primordial (first-generation) stars are those with Na and O content similar to field stars of the same metallicity.
+For a well-studied system, stars with the lowest cluster [Na/Fe] abundances are characterised as primordial.
+An intermediate population -- the second-generation of stars -- will have super-solar sodium abundances, and demonstrate a slight depletion in oxygen content.
+The  abundance exhaustion rate is ultimately dependent on the star-formation history of the cluster environment.
+The intermediate population is sub-divided based on how much the O and Na abundances depart from the primordial population: stars with [O/Na]$ > -0.9$ dex are classified as belonging to an extreme component of this Na-O pattern because they differ greatly from the primordial cluster abundance.
+The extreme O-depletion component has only been observed in a few clusters (more massive ones preferentially), indicating an extended star-formation history in more massive clusters.
+
+% discuss the production of Sodium
+The increase in Na abundance between generations of stars is a natural consequence of nucleosynthesis in massive ($>8 M_\odot$) stars.
+Massive stars undergo hydrostatic carbon burning, producing sodium by the dominant $^{12}\mbox{C}(^{12}\mbox{C}, p)^{23}\mbox{Na}$ process and eventually delivering it to the interstellar-medium through SN II events.
+The total amount of Na production is dependent on the neutron excess of the star, which slowly increases during the star's evolution.
+Because the eventual SN II explosion is devoid of any significant beta-decay processes, the neutron excess of the exploded material is representative of the pre-explosion abundance.
+This material eventually condenses to form the next generation of stars, which will have a net increase in their neutron excess with respect to their predecessors.
+Since the Na-production rate is correlated with the stellar neutron excess, an overall increase in Na is expected.
+The sodium content also becomes important for production of Ni during the SN II event (see \S\ref{sec:na-ni}) because $^{23}$Na is the only stable isotope produced in significant quantities during the C- (or O-) burning stages.
+
+% discuss the production of Oxygen
+
+% Discuss the depletion of oxygen over time. What are the possible astrophysical explanations for this depletion
+The exact astrophysical mechanism for oxygen depletion between generations of stars in globular clusters is still under debate.
+However, it is clear that this trend has been well-demonstrated by numerous independent observational studies.
+
+Additionally, oxygen is a particularly difficult element to measure.
+There are only a handful of lines available in an optical spectrum: the forbidden [O \textsc{I}] lines at 630 nm and 636 nm, and the O \textsc{I} triplet lines at 777 nm.
+The forbidden lines are very weak, and become immeasurable in either hot and/or metal-poor stars ([Fe/H] $\lesssim -1.5$ dex).
+When they are present, the forbidden lines can be hugely affected by telluric absorption -- depending on the radial velocity of the star.
+Moreover, the 630 nm line is blended with a Ni \textsc{I} absorption line \citep{Allende-Prieto;et-al_2001}, and hence the region requires a careful synthesis approach.
+Although the O \textsc{I} triplet lines at 777 nm are stronger than the forbidden lines, they are extremely sensitive to NLTE effects.
+Oxygen abundances measured using the triplet lines under the assumption of LTE can be $\sim$0.25 dex higher than abundances derived from the forbidden lines \citep{Perez;et-al_2006}.
+
+% Thus if you want to deduce the history of star formation for a group of stars, and deduce whether it has undergone star formation typically seen in globular clusters, you must sample from all components.
+
+It is clear that careful consideration must be given inferring star-formation histories from observed stellar abundances.
+In addition to the normal care afforded for measuring elemental abundances from high-resolution spectroscopic data, attention must be given to telluric absorption, Ni contamination, and NLTE corrections when deriving oxygen abundances.
+Furthermore, when characterising the oxygen depletion rate -- and hence the strength of the Na-O anti-correlation for a cluster -- it is vital to obtain observations for stars belonging to all components (where possible).
+If only a primordial sample of stars in a globular cluster is observed, then their [Na/Fe] and [O/Fe] abundances will be indistinguishable from halo stars of a similar metallicity.
+In such a scenario, any inferred anti-correlation could equally be explained by intrinsic chemical scatter or observational uncertainties.
+
+% Talk about Wylie de boer measurements
+
+% Wylie de boer claim from their Na-O abundances that...
+% Wylie de boer abundances themselves do not demonstrate the classical Na-O anti-correlation.
+In fact, they have a slight positive relationship.
+However, this trend is drawn from a sample of 5 stars -- the same as this study.
+If there is any evidence of a globular cluster from the [Na/Fe], [O/Fe] abundances in the Wylie de Boer study, it is the fact that two of their stars have slightly super-solar Na abundances; which is higher than expected for halo stars of this metallicity.
+
+% How our measurements of Na, O compare to theirs
+
+% Can these abundance differences be explained by a line-list?
+
+% In any case, suppose these stars did originate from a globular cluster.
+If the entire cluster was well-studied, the primordial component cut-off is described by Caretta as stars which are 4\sigma from the halo abundance at that metallicity.
+These stars would
+
+In such a scenario, these stars would be classified as a primordial component -- thus being indistinguishable from the halo. It is insufficient
+
 \subsection{The Al-Mg Relationship}

### 2012-12-06 2012-aqs/draft-aqs.tex
Added Na, O, Si, Ti, Ca text

@@
 \begin{abstract}
+We present a detailed dynamic and chemical analysis of 5 Aquarius stream giants observed using the MIKE spectrograph on the Magellan Clay Telescope. 
 \end{abstract}
@@
 Absorption lines are assumed to form under the assumption of local thermal equilibrium.
-The stellar parameter spacing for these grid models is 250\,K, 0.5 dex in surface gravity, 0.5 dex in [M/H] and 0.1 dex in [$\alpha$/Fe].
+The stellar parameter spacing for these grid models is 250\,K, 0.5\,dex in surface gravity, 0.5\,dex in [M/H] and 0.1\,dex in [$\alpha$/Fe].
 We interpolated the atmospheric densities, temperatures, electron pressures at all depths between stellar atmospheres using the Quickhull algorithm for this analysis.
@@
 
+\subsubsection{Photometric Effective Temperatures}
+
+The effective temperatures published for all of our stars in Table \ref{sec:stellar-parameters} were derived spectroscopically (see \S\ref{sec:effective-teffs}).
+For consistency, we have also estimated effective temperatures using 2MASS infrared photometry.
+The $J-K$ colour has been employed for these calculations because it has the least dependence on metallicity.
+The Aquarius stream is relatively close and at high-latitude, so significant extinction by dust is note expected.
+Nevertheless, the dust maps of \citet{Schlegel;et-al_1998} have been used to estimate the effect of extinction along the line-of-sight.
+Two different $T_{eff}$-colour relationships have been used for estimating temperatures: the \citet{Alonso;et-al_1999} calibration for dwarfs/sub-giants, and the ?
+calibration for giants.
+All photometrically-derived temperatures are listed in \ref{tab:photometric-temperatures}.
+
+\subsubsection{Effective Temperature}
+
 The effective temperature for each star was found by demanding a zero-trend in excitation potential and abundance for each measured Fe\,I line.
@@
 Linear relationships with slopes of $|0.001|$ dex were considered to be converged.
+
+\subsubsection{Surface Gravity}
+
 Surface gravity was found by forcing the mean Fe\,I and Fe\,II abundances to be equal, whilst maintaining zero trends with the excitation potential, reduced equivalent width and abundance.
 After these parameters had converged, the model metallicity was exactly matched to that of our line abundances.
-Line abundances that were unusually deviant ($>3\sigma$) from the mean were removed.
+Line abundances that were unusually deviant ($3\sigma$) from the mean were removed.
 The largest number of outlier measurements removed for any observation was N for X.
+
+\subsubsection{Metallicity, $\mbox{[M/H]}$}
+Determining the stellar parameters for a given star is an iterative process.
+Once the effective temperature, microturbulence and surface gravity were deduced, the model atmosphere abundance was matched to our solar-scaled Fe \textsc{I} abundance.
+The degeneracy between parameters required a refinement of the stellar parameters until the line abundances were consistent with the model atmosphere.
+
+% process is iterative
+% our final Fe abundance matched the model atmosphere abundance
 
@@
 \subsection{Abundances}
+
+\subsubsection{Carbon}
+
+\subsubsection{Oxygen}
+Oxygen is a particularly difficult element to measure.
+There are only a handful of lines available in an optical spectrum: the forbidden [O \textsc{I}] lines at 630 nm and 636 nm, and the O \textsc{I} triplet lines at 777 nm.
+The forbidden lines are very weak, and become immeasurable in either hot and/or metal-poor stars ([Fe/H] $\lesssim -1.5$ dex).
+When they are present, depending on the radial velocity of the star, the [O \textsc{I}] can be significantly affected by telluric absorption.
+Moreover, the 630 nm line is blended with a Ni \textsc{I} absorption line \citep{Allende-Prieto;et-al_2001}, and hence the region requires careful consideration.
+Although the O \textsc{I} triplet lines at 777 nm are stronger than the forbidden lines, they are extremely susceptible to NLTE and 3D effects \citep{Asplund;Perez_2001}, and sensitive to changes in microturbulence.
+\citet{Perez;et-al_2006} showed that oxygen abundances measured under the assumption of LTE in their sample are 0.08\,dex higher than abundances derived from the `true' oxygen content derived from the forbidden lines \citep{Perez;et-al_2006}.
+
+The [O \textsc{I}] lines were measurable in four of our candidates.
+Careful consideration was taken when correcting for telluric absorption, and we inspected all lines for any contamination by the earth's atmosphere.
+The 6300$\lambda$ line in one of our candidates, C2306265-085103, was sufficiently affected by telluric absorption such that we considered the line immeasurable.
+Thus, only the 6363$\lambda$ line was used to derive an oxygen abundance for C2306265-085103.
+In our hottest star, J223811-104126, the forbidden oxygen lines were not detected above a $3-\sigma$ significance.
+After synthesising the region, we deduce a conservative upper limit of $\mbox{[O/Fe]} < -0.50$ dex from the [O \textsc{I}] lines.
+This is consistent with the rest of our candidates, with [O/Fe] abundances varying between 0.41 to 0.57 dex.
+
+In order to derive an oxygen measurement for J223811-104126, we were forced to use the triplet lines at 777\,nm.
+Each line was synthesised, and a mean abundance was calculated for each candidate.
+Abundances determined from the oxygen triplet lines were systematically $+0.27$\,dex higher than found from the [O \textsc{I}] lines.
+\citet{Perez;et-al_2006} found [O/Fe] values based on the O \textsc{I} permitted triplet lines are on average $+0.19 \pm 0.07$\,dex higher than those found from the forbidden lines, after NLTE corrections of $-$0.08\,dex had been applied.
+Thus, our 0.27\,dex offset between measurements of the [O \textsc{I}] and O \textsc{I} triplet lines is exactly the same as found by \citet{Perez;et-al_2006}, which we attribute to a combination of NLTE, 3D and other systematic effects.
+\citet{Perez;et-al_2006} concluded the weak forbidden lines, when not too weak, probably give the most reliable estimate of [O/Fe].
+
+From the permitted O \textsc{I} triplet, we derive an oxygen abundance of $\mbox{[O/Fe]} = 0.41 \pm 0.01$\,dex (random scatter) for J223811-104126.
+This measurement will be systematically higher than the `true' abundance if it were discernible from the [O \textsc{I}] lines, on the order of $\sim{}$0.27\,dex.
+When we apply this crude offset derived from the rest of our sample, we arrive at a corrected abundance of $[O/Fe] = 0.14 \pm 0.08$\,dex for J223811-104126.
+This is the most oxygen-deficient star in our sample.
+
+\subsubsection{Sodium}
+
+Sodium is produced during hydrogen burning through the Ne-Na cycle, as well as through carbon burning in massive stars by the dominant $^{12}\mbox{C}(^{12}\mbox{C}, p)^{23}\mbox{Na}$ process.
+The total amount of Na production by C-burning is dependent on the neutron excess of the star, which slowly increases through stellar evolution along the red giant branch.
+Massive stars ($>8 M_\odot$) eventually deliver their manufactured sodium to the interstellar-medium through SN II events.
+Because the eventual SN II explosion is devoid of any significant beta-decay processes, the neutron excess of the exploded material is representative of the pre-explosion abundance.
+
+The explosive material eventually condenses to form the next generation of stars, which will have a net increase in their neutron excess with respect to their predecessors.
+Since the Na-production rate is correlated with the neutron excess, an overall increase in the total Na and Na-production rate between stellar generations is expected.
+Thus, an increase in the Na abundance between generations of massive stars is a natural consequence of nucleosynthesis.
+Sodium content also becomes important for production of Ni during the SN II event (see \S\ref{sec:na-ni}) because $^{23}$Na is the only stable isotope produced in significant quantities during the C- (or O-) burning stages.
+
+% which lines did we use for sodium and were there any problems with the Na lines?
+
+\subsubsection{$\alpha$-elements (Mg, Ca, Si and Ti)}
+
+The $\alpha$-elements (Mg, Ca, Si and Ti) are forged through $\alpha$-particle capture in assorted burning stages of stellar evolution, including the burning of carbon, neon and silicon.
+
+% magnesium measurements
+Magnesium has been measured from unblended lines that fall within the linear regime between reduced equivalent width and abundance.
+Depending on the radial velocity of the star, some of these lines can be affected by telluric absorption, particularly the 6318$\lambda$ and 6965.4$\lambda$ lines.
+Atmospheric absorption was most notable for C2225316-14437, where three of the four Mg transitions in our line list suffered some degree of telluric absorption, requiring an attentive correction.
+Every corrected absorption profile was carefully examined, and lines with suspicious profiles were excluded from the final magnesium abundance.
+
+% calcium measurements + silicon measurements
+Of all the $\alpha$-elements, calcium has the smallest measurement scatter in our stars.
+Four line measurements were used for each star, with a measurement uncertainty of 0.01\,dex.
+As shown in Figure \ref{fig:alpha-elements}, all Aquarius stars show super-solar Ca abundances, ranging between 0.23 to 0.43 dex, consistent with both [Mg/Fe] and [Si/Fe] measurements.
+However, C2225316-14437 has an unusually high silicon abundance ($\mbox{[Si/Fe]} = 0.72$), well outside the uncertainties of the rest of our sample.
+C2225316-14437 does not demonstrate unusually high abundances of any other $\alpha$-element, and the silicon lines are not affected by telluric absorption.
+Moreover, the Si lines are in relatively good agreement with one another.
+If we exclude the most prominent outlier, then the mean abundance drops only slightly to $\mbox{[Si/Fe]} = 0.70 \pm 0.04$\,dex.
+The lowest Si line abundance for C2225316-14437 is $\mbox{[Si/Fe]} = 0.57$\,dex, still significantly higher than the final measurements for any other star.
+
+% titanium measurements
 
@@
 
-In order to help explain this phenomena, \citet{Caretta;et-al_2009} defined three components of stars within a population: primordial, intermediate, and extreme.
+% more on background
+
+% discuss three components
+\citet{Caretta;et-al_2009} defined three components of stars following this abundance pattern within a population: primordial, intermediate, and extreme.
 The [Na/Fe] and [O/Fe] abundances for a given star defines which component it belongs to.
@@
 % discuss the production of Sodium
-The increase in Na abundance between generations of stars is a natural consequence of nucleosynthesis in massive ($>8 M_\odot$) stars.
-Massive stars undergo hydrostatic carbon burning, producing sodium by the dominant $^{12}\mbox{C}(^{12}\mbox{C}, p)^{23}\mbox{Na}$ process and eventually delivering it to the interstellar-medium through SN II events.
-The total amount of Na production is dependent on the neutron excess of the star, which slowly increases during the star's evolution.
-Because the eventual SN II explosion is devoid of any significant beta-decay processes, the neutron excess of the exploded material is representative of the pre-explosion abundance.
-This material eventually condenses to form the next generation of stars, which will have a net increase in their neutron excess with respect to their predecessors.
-Since the Na-production rate is correlated with the stellar neutron excess, an overall increase in Na is expected.
-The sodium content also becomes important for production of Ni during the SN II event (see \S\ref{sec:na-ni}) because $^{23}$Na is the only stable isotope produced in significant quantities during the C- (or O-) burning stages.
-
-% discuss the production of Oxygen
 
@@
 The exact astrophysical mechanism for oxygen depletion between generations of stars in globular clusters is still under debate.
-However, it is clear that this trend has been well-demonstrated by numerous independent observational studies.
-
-Additionally, oxygen is a particularly difficult element to measure.
-There are only a handful of lines available in an optical spectrum: the forbidden [O \textsc{I}] lines at 630 nm and 636 nm, and the O \textsc{I} triplet lines at 777 nm.
-The forbidden lines are very weak, and become immeasurable in either hot and/or metal-poor stars ([Fe/H] $\lesssim -1.5$ dex).
-When they are present, the forbidden lines can be hugely affected by telluric absorption -- depending on the radial velocity of the star.
-Moreover, the 630 nm line is blended with a Ni \textsc{I} absorption line \citep{Allende-Prieto;et-al_2001}, and hence the region requires a careful synthesis approach.
-Although the O \textsc{I} triplet lines at 777 nm are stronger than the forbidden lines, they are extremely sensitive to NLTE effects.
-Oxygen abundances measured using the triplet lines under the assumption of LTE can be $\sim$0.25 dex higher than abundances derived from the forbidden lines \citep{Perez;et-al_2006}.
+However, it is clear that this trend has been well-demonstrated empirically.
+Several hypotheses have been proposed in order to account for oxygen depletion between stellar generations, including massive binaries \citep{De_Mink;et-al_2009} or fast-rotating massive stars \citep{decressin;et-al_2007}.
+While the exact procedure is yet to be fully characterized, we can describe the abundance variation as a simple oxygen depletion (or dilution) model with time.
+Through comparisons with existing globular clusters, we can still draw inferences on the star-formation history of a system from measuring sodium and oxygen in a sample of its stars.
 
@@
 In addition to the normal care afforded for measuring elemental abundances from high-resolution spectroscopic data, attention must be given to telluric absorption, Ni contamination, and NLTE corrections when deriving oxygen abundances.
-Furthermore, when characterising the oxygen depletion rate -- and hence the strength of the Na-O anti-correlation for a cluster -- it is vital to obtain observations for stars belonging to all components (where possible).
+Furthermore, when characterising the oxygen depletion rate -- and hence the strength of the Na-O anti-correlation for a cluster -- it is vital to obtain observations for stars belonging to all three components (where possible).
 If only a primordial sample of stars in a globular cluster is observed, then their [Na/Fe] and [O/Fe] abundances will be indistinguishable from halo stars of a similar metallicity.
@@
 
-% Wylie de boer claim from their Na-O abundances that...
-% Wylie de boer abundances themselves do not demonstrate the classical Na-O anti-correlation.
-In fact, they have a slight positive relationship.
-However, this trend is drawn from a sample of 5 stars -- the same as this study.
-If there is any evidence of a globular cluster from the [Na/Fe], [O/Fe] abundances in the Wylie de Boer study, it is the fact that two of their stars have slightly super-solar Na abundances; which is higher than expected for halo stars of this metallicity.
+With high-resolution data and modest ($\sim$30 pixel$^{-1}$) signal-to-noise, \citet{Wylie-de-boer;et-al_2012} measured Na and O abundances for four of their six Aquarius stream members.
+This research has four stars in common with the \citet{Wylie-de-boer;et-al_2012} study, but Na and O measurements exist for only three stars that are in both samples.
+We have measurements for all of our stars, including J223811-104126, for which we ascertained an upper limit from the [O \textsc{I}] lines of [O/Fe] $< 0.5$ dex, and a NLTE-corrected abundance of $\mbox{[O/Fe]} = 0.21$ (CHECK) from the O \textsc{I} triplet lines.
 
-% How our measurements of Na, O compare to theirs
+% how do our values compare with Wylie de boer
+
+% Is there some explanation for abundance differences?
+
+The \citet{wylie-de-boer;et-al_20120} measurements indicate two stars with solar-type levels of Na -- identical to field star Na abundances for their metallicity -- and two stars with super-solar sodium content.
+Combined with measurements of other light elements (see \S\ref{sec:al-mg}, \ref{sec:na-ni}) they claim the Aquarius stream is ``consistent with a globular cluster origin''.
+The \citet{wylie-de-boer;et-al_2012} abundances themselves do not demonstrate a classical Na-O anti-correlation.
+In fact, they have a slight positive relationship: their Na-enhanced stars show an increased oxygen content, contrary to an expected oxygen depletion between generations with.
+However, this trend is drawn from a sample of only four stars -- the same as this study if our upper limit for J223811-104126 is excluded.
 
@@
 
-In such a scenario, these stars would be classified as a primordial component -- thus being indistinguishable from the halo. It is insufficient
-
 \subsection{The Al-Mg Relationship}
 
-\subsection{The Na-Na Relationship}
+The Na-O anti-correlation is likely the result of complete CNO and Ne-Na cycles of proton reactions in globular cluster stars.
+There is also evidence in some clusters that the Mg-Al nucleosynthesis cycle is also active.
+
+ The conditions required for these reactions are significantly higher than the CNO and Ne-Na cycle: temperatures of 70 MK are required for the Mg-Al channel instead of just 25 MK for the CNO/Ne-Na cycles \citet{Charbonnel_Prantzos_2006}.
+
+\subsection{The Na-Ni Relationship}
+
+% discuss the discovery of the Na-Ni relationship
+
+% this relationship was correlated with distance, such that more distant stars were deficient in Na
+
+% revise contribution of Na from type II SN events
+
+% production of nickel
+
+% thus, a Na-Ni trend is expected across a wide range of metallicities
+
+% as Venn points out, this trend can be altered based on SN Ia contributions
+
+% in general, we can expect high Na, Ni abundances in stars that have an long contribution of previous massive stars
+% thus, the we can infer the star formation history
+
+% dsPh's have a very different star formation history and chemical signature to typical halo stars of the same metallicity
+% the same is true for globular clusters, given the chemical patterns already discussed
+% however disk stars and globular clusters are indiscernible in the Na/Ni plane: they both show an extended contribution of massive stars with respect to dSph's (Figure X).
+
+%
 

### 2012-12-06 2012-aqs/figures/plot-na-ni.py
Updated Na-Ni plot

@@ -59,3 +59,35 @@ ax.set_ylim(-0.7, 0.5)
 
 plt.savefig('aquarius-na-ni.eps')
 plt.savefig('aquarius-na-ni.pdf')
+
+
+
+NS_Na_Fe, NS_Ni_Fe, kind = np.loadtxt('nissen_schuster_2010.data', delimiter='|', skiprows=9, dtype=str, usecols=(6, 12, -1), unpack=True)
+
+NS_Na_Fe = np.array(map(float, NS_Na_Fe))
+NS_Ni_Fe = np.array(map(float, NS_Ni_Fe))
+
+# Thick disk stars
+thick_disk = np.where(kind == 'TD')[0]
+
+# High alpha stars
+high_alpha = list(np.where(kind == 'high-alpha')[0])
+high_alpha.extend(np.where(kind == '(high-alpha)')[0])
+
+high_alpha = np.array(high_alpha)
+
+low_alpha = list(np.where(kind == 'low-alpha')[0])
+low_alpha.extend(np.where(kind == '(low-alpha)')[0])
+
+low_alpha = np.array(low_alpha)
+
+ax.scatter(NS_Na_Fe[thick_disk], NS_Ni_Fe[thick_disk], c='r', marker='+')
+ax.scatter(NS_Na_Fe[high_alpha], NS_Ni_Fe[high_alpha], c='g', marker='o', facecolor='none')
+ax.scatter(NS_Na_Fe[low_alpha], NS_Ni_Fe[low_alpha], c='b', marker='o', facecolor='b')
+
+ax.set_xlim(-0.5, 0.4)
+ax.set_ylim(-0.2, 0.2)
+
+plt.savefig('aquarius-nissen-schuster-na-ni.eps')
+plt.savefig('aquarius-nissen-schuster-na-ni.eps')
+

### 2012-12-08 2012-oss-mrs/ms.tex
Re-submitted this version to the journal

@@
 Because K-giants are difficult to unambiguously detect from photometry alone, low-resolution spectroscopy is required to estimate stellar parameters and determine radial velocities.
-The Orphan Stream has a low spatial over-density on the order of $\sim$10\%, which makes it difficult to separate stream members from halo stars.
+The Orphan Stream has an extremely low spatial over-density, which makes it difficult to separate stream members from halo stars.
 However, there is a well described distance gradient along the stream \citep{Belokurov_et-al_2007, Newberg_et-al_2010} which provides an indication on where we should focus our spectroscopic efforts.
@@
 This dwarf/giant separation method was also employed using the total equivalent width of the Mg\,\textsc{I}\,b triplet lines.
-Both analyses were entirely consistent with each other: essentially the same candidate selection was found using both techniques.
+Both analyses were entirely consistent with each other: essentially the same candidate list was found using both techniques.
 However, given slightly poorer signal at the Mg\,\textsc{I}\,b triplet, we were forced to adopt many more upper limits than when using the 8807\,{\AA} line.
@@
 We have presented a detailed analysis to isolate individual Orphan Stream K-giants from low-resolution spectroscopy using a combination of photometric, kinematic, gravity, metallicity, and proper motion information.
-Although each individual criteria is likely to induce some level contamination, their intersection reveals nine highly probable, self-consistent, Orphan Stream K-giants.
+Although each individual criterion is likely to induce some level of contamination, their intersection reveals nine highly probable, self-consistent, Orphan Stream K-giants.
 We deduce a median stream metallicity of $[\mbox{Fe/H}] = -1.63 \pm 0.19$ and find an intrinsically wide metallicity spread of $\sigma = 0.56$\,dex, indicative of a dSph origin.

### 2012-12-20 2012-aqs/draft-aqs.tex
Added photometric temperature discussion + table

@@
 
-\shorttitle{AQS on MIKE}
+\shorttitle{The Aquarius Stream Progenitor Was Not A Globular Cluster}
 \shortauthors{Casey et al}
@@
 
-\title{The Aquarius Stream Progenitor Was Not A Globular Cluster: \\ Its History is Far More Interesting}
+\title{The Aquarius Stream Progenitor Was Not A Globular Cluster: \\ Its History Could Be Far More Interesting\altaffilmark{1}}
 
-\author{Andrew R. Casey\altaffilmark{1,2} and distinguished collaborators}
-\altaffiltext{1}{Research School of Astronomy \& Astrophysics, Australian National University, Mount Stromlo Observatory, via Cotter Rd, Weston, ACT 2611, Australia}
-\altaffiltext{2}{Massachusetts Institute of Technology, Kavli Institute for Astrophysics and Space Research,
+\author{Andrew R. Casey\altaffilmark{2,3} and distinguished collaborators}
+\altaffiltext{1}{This paper includes data gathered with the 6.5 meter Magellan Telescopes located at Las Campanas Observa- tory, Chile.}
+\altaffiltext{2}{Research School of Astronomy \& Astrophysics, Australian National University, Mount Stromlo Observatory, via Cotter Rd, Weston, ACT 2611, Australia; acasey@mso.anu.edu.au}
+\altaffiltext{3}{Massachusetts Institute of Technology, Kavli Institute for Astrophysics and Space Research,
 77 Massachusetts Avenue, Cambridge, MA 02139, USA}
@@
 
-Stellar streams in the halo are relics from relatively recent minor mergers in the Milky Way.
-The positions and kinematics of stars within these streams are sensitive to the galactic potential.
-As such, they can collectively constrain the fraction and distribution of accreted matter in the stellar halo, the sub-halo mass function, as well as the shape and extent of dark matter in the Milky Way.
-Moreover, individual elemental abundances for stars within these streams reveal the chemodynamical evolution of the Galaxy.
+Stellar streams arise from tidal effects as satellite systems infall onto the Milky Way.
+The phase space information of stars within such streams are sensitive to the galactic potential.
+Therefore, they can collectively constrain the fraction and distribution of accreted matter in the stellar halo, the sub-halo mass function, as well as the shape and extent of dark matter in the Milky Way.
+Moreover, individual elemental abundances for stars within these streams help unravel the chemical evolution of the Galaxy.
+% Consider adding a final sentence about the amount of work that has gone into stellar streaams
 
-Wide-field surveys have proved excellent sources for finding stellar streams.
-Dozens of streams reaching out up to 150\,kpc in the stellar halo have been identified through photometric selections and matched-filtering techniques.
-However, as \citet{Helmi;White_1999} point out, these methods are only successful for identifying substructures that are sufficiently distant from the solar neighbourhood.
-A nearby stream within $\sim{}$10\,kpc will not appear as an on-sky over-density.
-Such substructures would only be detectable by utilising both position and kinematic information.
+Wide-field surveys have proved excellent sources for finding galactic substructures, including stellar streams.
+Dozens of streams reaching out up to 150\,kpc in the halo have been identified through photometric selections and matched-filtering techniques \citep{Belokurov;et-al_2007;Koposov_SG1}.
+However, as \citet{Helmi;White_1999} point out, these approaches are only successful for identifying substructures that are sufficiently distant from the solar neighbourhood.
+A nearby stream within $\sim{}$10\,kpc will not appear as an on-sky over-density, as the stars would be sparsely positioned across the sky.
+Such substructures would only be detectable with kinematic, or perhaps precise chemical information.
 
 % Talk about RAVE
-It is therefore necessary to survey the kinematics of solar neighbourhood stars in order to detect nearby streams.
+It is therefore necessary to survey solar neighbourhood stars with spectroscopy in order to detect any nearby substructures.
 The RAVE (Radial Velocity Experiment) began such a survey in 2003 and has observed spectra from over 500,000 stars across 17,000 deg$^{2}$.
-RAVE candidates were photometrically selected based only on their apparent magnitude of 9 $<$ I $<$ 13, and are therefore kinematically unbiased.
-The RAVE data releases have provided radial velocities \citep{steinmetz;et-al_2006} and estimates of stellar parameters \citep{zwitter;et-al_2008, siebert;et-al_2011} now for a subset of these observations.
+As the name suggests, the primary goal of RAVE was to obtain radial velocities for the solar neighbourhood and beyond.
+In an attempt to remain kinematically unbiased, RAVE candidates were selected based only on their apparent magnitude.
+With the exception of bulge stars where some photometric cuts were employed, all stars between 9 $<$ I $<$ 13 were observed.
+Almost all of these candidates have published radial velocity measurements \citep{steinmetz;et-al_2006}, and for a subset of stars with sufficient S/N, estimates of stellar parameters have been derived using a $\chi^2$ minimization technique \citep{zwitter;et-al_2008, siebert;et-al_2011}.
 
 % Identification of the aquarius stream
-Using this data, \citet{williams;et-al_2011} identified a co-moving group of nearby ($0.5 \lesssim d \lesssim 10$\,kpc) stars in the direction of the Aquarius constellation.
+Using these data, \citet{williams;et-al_2011} identified a co-moving group of nearby ($0.5 \lesssim d \lesssim 10$\,kpc) stars in the vicinity of the Aquarius constellation $(l, b) = (60\,^\circ, -55\,^\circ)$.
 The artefact is most apparent when examining kinematics against galactic latitude for stars within $-70\,^\circ < b < -50\,^\circ$.
-\citet{williams;et-al_2011} employed a selection criteria of $-250 < V_{hel} < -150$\,km s$^{-1}$, $30\,^\circ < l < 75\,^\circ, J > 10.3$ and identified 15 stream candidates.
-The average heliocentric radial velocity of these members was found to be $V_{HELIO} = -199$\,km s$^{-1}$, with a dispersion of 27\,km s$^{-1}$.
-When compared to other streams identified in the halo, this is an unusually wide kinematic dispersion.
-Streams are generally considered to be kinematically cold, with dispersions of $\sigma_v < 8$\,km s$^{-1}$.
+\citet{williams;et-al_2011} employed a selection criteria of $-250 < V_{HEL} < -150$\,km s$^{-1}$, $30\,^\circ < l < 75\,^\circ, J > 10.3$ to maximize the contrast between the stream and halo background, identifying 15 stream candidates in the process.
+The average heliocentric radial velocity of these members was found to be $V_{HEL} = -199$\,km s$^{-1}$, with a dispersion of 27\,km s$^{-1}$.
 The radial velocities outputted by the RAVE survey are described to be $\sim2$\,km s$^{-1}$, so the wide kinematic distribution appears to be real.
 
-% is it a real substructure
-\citet{williams;et-al_2011} quantified the statistical significance of the Aquarius substructure with comparisons to the Besancon and Galaxia models.
-After populating the models, the galaxy representations were discretized in $\Delta{}V_{hel}$ and $\Delta{}l$ grid blocks.
+%When compared to other streams identified in the halo, this is an unusually wide kinematic dispersion.
+Streams are generally considered to be kinematically cold, with dispersions of $\sigma_v < 8$\,km s$^{-1}$.
 
-There is no reason to suspect that the Aquarius stream is not a real substructure.
+% QUANTIFYING THE STREAM DETECTION
+Upon examining the galactic longitude and radial velocities of Aquarius stars, the stream appears quite distinct from the halo.
+In order to quantify the statistical likelihood that the Aquarius stream is a true substructure, \citet{WIlliams;et-al_2011} compared the number of observed RAVE stars within $-70\,^\circ < b < -50\,^\circ$ against the Galaxia \citep{Sharma;et-al_2009} and Besan\c{c}on \citep{Robin;et-al_2003} galaxy models.
+Predicted particles and observed stars between $-70\,^\circ < b < -50\,^\circ$ were binned in $\Delta{l} \times \Delta{V_{hel}}$ using varying grid cell sizes between $25-70\,^\circ$ and 20-100\,km s$^{-1}$ respectively.
+The significance of the stream is calculated for each cell.
+\citet{williams;et-al_2011} found the stream to be statistically significant ($>$4-$\sigma$) in 96\% of the grid cell sizes employed for the Besan\c{c}on model.
+By sampling the Galaxia model multiple times with varying extinction models, a similar result was found: between $75\pm15$\,\% to $80\pm18$\,\% of grid cells showed the Aquarius stream to significant at the 4-$\sigma$ level.
+Given the high-latitude of the stream and proximity of the stream, it is not surprising that dust had a negligible effect on the overall significance.
+\citet{williams;et-al_2011} concluded that the over-density in $l, V_{hel}$ is a true substructure, and neither the choice of galaxy model, cell size, nor the extinction model made any real difference to the stream detection significance.
 
-% What is it?
-Given the extent of stellar debris the Sagittarius dwarf has littered in the Milky Way, it is reasonable to suspect the Aquarius stream might be Sagittarius in origin.
-Although the metallicities reported by \citet{williams;et-al_2011} are not dissimilar from the stream, the distances and $V_{Z}$, $V_\phi$ for Aquarius are quite distinct from Sagittarius.
-\citet{williams;et-al_2011} concluded that the newly discovered stream could not be positively associated with the Monoceros stream, Hercules-Aquila cloud, or either the Canis Major or Virgo Overdensities.
+% STREAM IS LOCALIZED
+% the stream appears to be quite localized in space.
+% nearby streams could be strewn out over several degrees. the Orphan stream wraps over 60 degrees in the sky, and the Sgr stream wraps several steradians
 
-% MRS follow-up by de boer
-In order to investigate the Aquarius progenitor and any possible association with existing substructures, \citet{wylie-de-boer;et-al_2012} observed six Aquarius stream members with medium resolution (R = 25,000) spectroscopy.
-Their data indicates the stream is chemically coherant, with a dispersion in [Fe/H] of only 0.1\,dex.
-This minimal chemical scatter suggests that the Aquarius stream progenitor is a globular cluster, since dwarf spheroidal galaxies  exhibit chemical dispersions of a dex or more \citet{Frebel_Norris_2011}.
+% DISTANCE AND DYNAMICS
+% heliocentric + galactic velocities suggest the aquarius stream stars are in the halo, and not associated with the disk.
+% distances
 
- Based on sodium and nickel abundance ratios with respect to iron, they claim the Aquarius stream chemical signatures unambiguously represent those of a globular cluster.
+Given the extent of stellar debris the Sagittarius dwarf has littered throughout the Milky Way, it is reasonable to suspect the Aquarius stream might originate from the Sagittarius dwarf.
+Indeed, the Aquarius stream stars do not lie far from the orbital plane of Sagittarius and the metallicities reported by \citet{williams;et-al_2011} are not dissimilar from the Sagittarius stream.
+However, \citet{williams;et-al_2011} found the Aquarius $XYZ$ positions and kinematics (specifically $V_{Z}$ and $V_\phi$) are quite distinct from Sagittarius.
+Based on the phase space information available, \citet{williams;et-al_2011} concluded that the newly discovered stream could not be positively associated with the Monoceros stream, Hercules-Aquila cloud, or either the Canis Major or Virgo over-densities.
 
-% globular cluster chemical signatures
+The Aquarius stream has a metallicity of $\mbox{[Fe/H]} \sim -1.0$, slightly more metal-rich than halo stars at the same distance.
+The dispersion in the stream's metallicity has yet to be fully characterised.
+\citet{williams;et-al_2011} found the stream to have an average of $\mbox{[M/H]} = -1.0 \pm 0.4$, compared to $\mbox{[M/H]} = -1.1 \pm 0.6$ for background stars after the same selection cuts had been employed.
+Of the 12 Aquarius stars in the \citet{williams;et-al_2011} discovery sample with stellar parameters, the metallicity range is wide: between --2.02 and --0.33 dex.
+Spectroscopic observations of higher resolution and S/N are necessary to accurately determine the metallicity distribution function.
+To this end, \citet{wylie-de-boer;et-al_2012} obtained high-resolution ($R = 25,000$) spectra with modest S/N ($\sim$30 pixel$^{-1}$) for six Aquarius stream giants.
+Their data indicated a much narrower metallicity distribution: $\mbox{[Fe/H]} = -1.09 \pm 0.10$\,dex extending between $\mbox{[Fe/H]} = -1.25$ to $-0.98$\,dex; the level of negligible intrinsic chemical scatter which is typically observed in globular clusters.
+The largest [Fe/H] discrepancy between the two studies was $\Delta\mbox{[Fe/H]} = -0.66$\,dex for the most metal-rich star in the \citet{williams;et-al_2011} sample.
+The most metal-poor star in the \citet{williams;et-al_2011} study was not observed by \citet{wylie-de-boer;et-al_2012}.
 
-We seek to investigate the globular cluster origin claim made by \citet{wylie-de-boer;et-al_2012}.
-We present a detailed chemical abundance analysis for five confirmed Aquarius stream members observed using the Magellan Inamori Kyocera Echelle spectrograph \citep{Bernstein;et-al_2003} on the Magellan telescope.
+%The chemical coherence in the \citet{wylie-de-boer;et-al_2012} study is most intriguing.
+
+In addition to ascertaining stellar parameters, \citet{wylie-de-boer;et-al_2012} measured light element abundances for the Aquarius stream stars -- the only study to do so until now.
+Primarily they focussed on Na, O, Ni, Mg, and Al abundances.
+Chemical patterns in these light elements arise as natural consequences of nucleosynthetic processes in massive stars.
+Most notably, an anti-correlation in sodium and oxygen abundance has been identified in all well-studied globular clusters to date.
+Originally this was thought to arise from internal mixing along the giant branch.
+However, dwarf stars were found to exhibit strong Na-enhancement and O-depletions, contrary to what would be expected if the Na-O anti-correlation was purely a result of internal mixing.
+It is well known now that photospheric abundance variations resulting from internal mixing are limited to C, N and Li.
+The Na-O pattern provides the best evidence that stars have formed in a globular cluster environment and that their chemical enrichment history has been dominated by Sn II events.
+From high-resolution spectroscopy of five stars in Aquarius, four of which had Na, O measurements, \citet{wylie-de-boer;et-al_2012} found two stars with super-solar sodium; slightly higher [Na/Fe] ratios for halo stars of the same metallicity.
+No strong oxygen depletion was evident in their stars.
+
+There are other abundances patterns that allow us to infer the chemical evolution of a given cluster.
+\citet{Nissen;Schuster_1997} first noted that only the distant solar neighbourhood stars were enriched in [Ni/Fe] and [Na/Fe].
+\citet{fulbright;et-al_2000} came to a similar conclusion: only somewhat distant ($R_\odot > 20$\,kpc) stars are likely to be sodium deficient.
+If the stellar halo has been built up from the accretion of smaller dwarf satellites, \citet{Nissen;Schuster_1997} proposed that this chemical trend may be indicative of the halo merger history.
+Although there are some caveats to this chemical pattern (see \S\ref{sec:ni-na-relation}), at the very least the Na-Ni correlation may provide an indication whether stars became chemically enriched in dSph-like environments.
+\citet{wylie-de-boer;et-al_2012} found all their Aquarius stars to be enriched in both sodium and nickel; contrary to what would be expected if the stars originated from a disrupted dSph satellite.
+
+Combined with the low level of chemical scatter present in their sample, these chemical indicators led \citet{wylie-de-boer;et-al_2012} to conclude that the Aquarius stream must be the result of a tidally disrupted globular cluster.
+\citet{williams;et-al_2011} had previously precluded this possibility after modelling an Aquarius-like progenitor infalling onto the Milky Way and comparing the predicted $l, b, V_{hel}$ with known, nearby globular clusters of similar metallicities.
+However, no known globular cluster could match their simulation.
+
+We seek to investigate the nature of the Aquarius stream, in particular the recent globular cluster origin claim made by \citet{wylie-de-boer;et-al_2012}.
+We present a detailed analysis for five confirmed Aquarius stream members from high-resolution, high S/N observations taken using the Magellan Inamori Kyocera Echelle spectrograph \citep{Bernstein;et-al_2003} on the Magellan Clay telescope.
+Our analysis includes determining the galactic dynamics and orbital paths for the Aquarius stream, and measuring precise chemical abundances.
 Details of the observations and data reduction are outlined in the following section.
-The data analysis is presented in \S\ref{sec:analysis} and a detailed discussion of these results resides in \S\ref{sec:discussion}.
+The data analysis is chronicalled in \S\ref{sec:analysis} and a detailed discussion of these results resides in \S\ref{sec:discussion}.
 In \S\ref{sec:conclusion} we present our conclusions and critical interpretations.
 
+\clearpage
 \section{Observations \& Data Reduction}
@@
 The most comprehensive sample of Aquarius stream stars is presented in the discovery paper of \citet{williams;et-al_2011}.
-Since the globular cluster origin claim of \citet{wylie-de-boer;et-al_2012} is based from a subset of six of these stars, we targeted stars largely from this study.
-Four of our stars are in common with \citet{wylie-de-boer;et-al_2012}.
-An additional star from the original \citet{williams;et-al_2011} sample, J2306265-085103, was also observed.
-J2306265-085103 had insufficient S/N for the RAVE pipeline to accurately determine stellar parameters, so its membership hinges on radial velocity measurements.
-Program stars were observed in July 2011 and we observed X standard stars observed for a separate program in March 2011.
-All observations were taken using the 1.0" slit, which provides a spectral resolution of $R = 28,000$.
-The exposure times for our program stars varied per star from X seconds to Y seconds to ensure a signal-to-noise in excess of 100 per pixel element at 600 nm for all stars.
+Our sample includes five stars: four common to the \citet{wylie-de-boer;et-al_2012} study, and an additional star from the original \citet{williams;et-al_2011} sample.
+The additional star, J2306265-085103, had insufficient S/N in the RAVE sample for stellar parameters to be accurately determined.
+Program stars were observed in July 2011 in good seeing at high airmass (Table \ref{tab:observations}), and X standard stars were observed as part of a separate program in March 2011.
+All observations were taken using the 1.0'' slit, providing a spectral resolution of $R = 28,000$.
+The exposure times for our program stars varied per star from X-Y seconds to ensure a Signal-to-Noise ratio (S/N) in excess of 100 per pixel element at 600 nm.
 
-The data were reduced using the CarPy pipeline.
-Standard flat-fielding and extraction methods were employed using 10 quartz and 10 milky frames taken at the start of each night.
-ThAr arc lamp exposures were taken at the start of each night to provide wavelength calibration.
-No telluric corrections were made as atmospheric absorption does not affect any of the transitions in our line list.
+Calibration frames were taken at the start of each night, including twenty flat-field frames (10 quartz, 10 milky) and 10 Th-Ar arc lamp exposures for wavelength calibration.
+The data were reduced using the CarPy pipeline\footnote{carpy website url}.
+One of our standard stars, HD 41667, was also reduced using standard extraction and calibration methods in \textsc{IRAF}.
+The resultant spectra from both reduction workflows were compared for residual fringing, S/N, and wavelength calibration.
+No noteworthy differences were present, and the CarPy pipeline was utilized for the remainder of our reductions.
 Each reduced echelle order was carefully normalised using a third order spline.
-All normalised orders were stitched together to provide a single one-dimensional spectrum from 3800-9400\,\AA{}.
+Normalised orders  for a given star were stitched together to provide a single one-dimensional spectrum from 3800-9400\,\AA{}.
+
+The white dwarf HR 6141 was observed on X with a S/N of 400 pixel$^{-1}$ to account for telluric absorption.
+The S/N for HR 6141 exceeds the S/N in any of our program stars.
+Although the atmospheric conditions are certain to change throughout the night and between observing runs, we are primarily using this spectra to identify lines that are affected by telluric absorption.
+Critical transitions necessary for abundance analyses that are affected by the earth's atmosphere are later corrected for telluric absorption (see \S\ref{sec:telluric-absorption}), but great attention is paid to telluric band-heads at X and X such that we are not over- or under-correcting the atmospheric absorption.
 
@@
 The radial velocity for each star was determined in a two-step method.
-An initial estimate of the radial velocity was ascertained by cross-correlation with a synthetic spectrum of a giant with $T_{eff} = 4500$\,K, $\log{g} = 1.5$, and [M/H] $= -1.0$ across the wavelength range $8450 - 8700$ \AA{}.
-The spectrum was shifted to rest frame using this initial velocity.
+An initial estimate of the radial velocity was ascertained by cross-correlation with the synthetic spectrum of a giant with $T_{eff} = 4500$\,K, $\log{g} = 1.5$, and [M/H] $= -1.0$ across the wavelength range $8450 - 8700$ \AA{}.
+The observed spectrum was shifted to the pseudo-rest frame using this initial velocity.
 Velocities found from cross-correlation are typically within 1\,km\,s$^{-1}$ of our final published value.
 
-With our spectrum at near-rest, we measured the equivalent widths of $N$ lines by fitting Gaussian functions to the absorption profiles.
-Fitting Gaussian profiles provides us with the measured equivalent width, the full-width half-maximum of the profile, and the central wavelength.
+With our spectrum at near-rest, we measured the equivalent widths of $\sim$200 lines by fitting Gaussian functions to the absorption profiles.
+Fitted Gaussian profiles provides us with a measured equivalent width, the full-width half-maximum of the profile, and the central wavelength.
 Thus, the residual radial velocity can be found from the ratio of the central and rest line wavelengths.
-The final radial velocity for the star is provided by the mean of these $N$ line velocity measurements.
-Figure \ref{fig:line-velocities} shows the line velocities for HD41667 after  being placed at rest using our cross-correlation velocity of 314.4\,km s$^{-1}$.
-As expected, the mean offset is small ($-0.75$\,km s$^{-1}$), and our standard deviation is 0.79\,km s$^{-1}$ from 164 line measurements.
+The final radial velocity for the star is provided by the mean of these $\sim$200 line velocity measurements.
+Figure \ref{fig:line-velocities} shows the line velocities for HD41667 after being placed at pseudo-rest using our cross-correlation velocity of 314.4\,km s$^{-1}$.
+As expected, the mean residual offset is small ($-0.75$\,km s$^{-1}$), and our standard deviation is 0.79\,km s$^{-1}$ from 164 line measurements.
 This provides us with a final measured radial velocity of $313.7 \pm 0.1$\,km s$^{-1}$.
-This process was repeated for all observations.
+This process was performed for all observations.
 The radial velocities published in Table \ref{tab:observations} are the final values from this two-step method.
-Heliocentric velocities agree excellently (within X\,km s$^{-1}$) with previously reported literature values \citep{williams;et-al_2011,wylie-de-boer;et-al_2012}.
+Heliocentric velocities agree excellently (within X\,km s$^{-1}$) with previously reported literature values \citep{williams;et-al_2011,wylie-de-boer;et-al_2012}, demonstrating the accuracy of the radial velocities published by the RAVE survey.
 
@@
 	\includegraphics[width=\columnwidth]{./figures/line-velocity.pdf}
-	\caption{Residual velocities for each absorption line with a well-fitted Gaussian profile after correcting for the doppler shift with our cross-correlation measurement.
-The mean residual velocity is within our uncertainties derived from cross-correlation.}
+	\caption{Residual velocities for each absorption line with a well-fitted Gaussian profile after correcting for  doppler shift with our initial cross-correlation measurement.
+The mean residual velocity $-0.75$\,km\,s$^{-1}$ is within the 1-$\sigma$ cross-correlation uncertainty of $\pm0.9$\,km\,s$^{-1}$.}
 	\label{fig:line-velocities}
@@
 For lines with hyperfine structure, blended transitions or molecular features, we determined the transition abundance using a spectral synthesis approach where the abundance of a given species is found by by matching a synthetic spectrum to the observed spectrum.
+Equivalent widths were measured to determine the abundances of all other transitions.
 
-The equivalent widths for all transitions were measured automatically using software for this study.
-Given the rest wavelength and an initial guess of the FWHM, a Gaussian function is iteratively fitted to the absorption profile.
+The equivalent widths for all absorption lines were measured automatically using software written for this study.
+Given the rest wavelength and an initial guess of the full-width half-maxium (FWHM), a Gaussian function is iteratively fitted to the absorption profile.
 At the same time, the local continuum is found within 20\,\AA{} either side of the rest wavelength using a second-order polynomial.
 Measuring the local continuum ensures any errors in our initial normalisation or order-stitching do not propagate through to our equivalent width measurements.
-Any group of pixels that deviate significantly ($>2\sigma$) to the local continuum are cosmic ray hits, or more likely trough points of a neighbouring profile.
-We attempt to fit a Gaussian profile to each of these groups of deviating pixels, using the best estimate of the local continuum.
-If a profile is successfully fitted, then all points belonging to that profile are excluded from the continuum determination.
+Any group of pixels that deviate significantly ($>$2-$\sigma$) from the local continuum are either persistent cosmic ray hits, or trough points of a neighbouring absorption profile.
+We attempt to fit a Gaussian profile to each group of deviating pixels, using the current best estimate for the local continuum.
+If a Gaussian profile is successfully fitted to the deviating group and its surrounding pixels, then all points belonging to that profile are excluded from the continuum determination.
 When fitting Gaussian profiles, the $\chi^2$ difference between the observation and the profile is minimized.
-In order to account for blended transitions, our $\chi^2$ function is weighted based on the distance to the rest wavelength.
-Pixels near the rest wavelength are weighted higher than those on the wings.
-Although this approach relies on a reasonably accurate ($<4$\,km s$^{-1}$) radial velocity correction, it greatly improves the accuracy of the equivalent width measurements.
+In order to account for crowded absorption regions where the $\chi^2$ value might be influenced by a nearby profile, our $\chi^2$ function is weighted based on the distance to the rest wavelength by the function
 
-We note that the results of our iterative fitting approach are entirely insensitive to the initial FWHM guess.
-Increasing the initial guess from 0.1\,\AA{} to 1 or 2\,\AA{} -- an unphysical large value for high-resolution spectra -- does not alter any of our equivalent width measurements.
+\begin{equation}
+W_{\lambda_{i}} = 1 + \exp{\left(\frac{-(\lambda_{i} - \lambda_{r})^2}{4\sigma^2}\right)}
+\label{eq:chi-weight}
+\end{equation}
+
+\noindent where $\lambda_{r}$ (rest wavelength) and $\sigma$ are free parameters during the iterative fitting process.
+As a consequence of Eq.
+\ref{eq:chi-weight}, pixels near the rest wavelength are weighted higher than those on the wings, forcing the fit to disregard blended or crowded regions.
+Although this approach relies on a reasonably accurate radial velocity correction ($<$4\,km s$^{-1}$; which is easily achieved), it greatly improves the accuracy of the equivalent width measurements.
+
+We note that the results of our iterative fitting approach are \textit{completely insensitive} to the initial FWHM guess.
+Increasing the initial FWHM estimate from 0.1\,\AA{} to 1 or 2\,\AA{} -- unphysically large values for high-resolution spectra -- does not alter \textit{any} of our final equivalent width (or FWHM) measurements.
 Only a small increase in computational cost is observed.
-Although we are confident in our automatic equivalent width measurements, every absorption profile was examined by eye for quality.
+Although we are extremely confident in our automatic equivalent width measurements, every absorption profile was examined by eye for quality, and spurious measurements were excluded.
 
@@
 A minimum detectable equivalent width was calculated as a function of wavelength based on the S/N, and only lines that exceeded a $3\sigma$ detection significance were included.
-We have verified our equivalent width measurement techniques by comparing our measurements for 164 lines in HD140283 with the study of \citet{Norris;et-al_1996}.
+We have verified our equivalent width measurement techniques by comparing our measurements for 164 lines in HD140283 with the study of \citet{norris;et-al_1996}.
 Excellent agreement is found between the two studies, which is illustrated in Figure \ref{fig:ew-compare}.
 The mean difference between this study and that of \cite{norris;et-al_1996} is a negligible $0.64 \pm 2.78$\,m\AA{}, and no systematic trend is present.
+
+% need to mention that we only used the "Good" Norris measurements
 
@@
 	\includegraphics[width=\columnwidth]{./figures/smh-norris.pdf}
-	\caption{A comparison showing equivalent widths measured for HD140283 using an automatic routine (see \S\ref{sec:line-measurements}), and those found with careful hand measurements by \citet{norris;et-al_1996}.
-No systematic trend is present, and the mean difference between these studies is $\langle\Delta{}W_\lambda = -0.64 \pm 2.78$ m\AA{}.}
+	\caption{A comparison showing equivalent widths measured for HD140283 using our automatic routine (see \S\ref{sec:line-measurements}), and those found with careful hand measurements by \citet{norris;et-al_1996}.
+No systematic trend is present, and the mean difference between these studies is $\langle\Delta{}W_\lambda\rangle = -0.64 \pm 2.78$ m\AA{}.}
 	\label{fig:ew-compare}
@@
 \subsection{Model Atmospheres}
-We employed the ATLAS9 stellar atmospheres of \citet{Castelli;Kurucz_2003} for this analysis.
+The ATLAS9 plane-parallel stellar atmospheres of \citet{Castelli;Kurucz_2003} have been used to deduce stellar parameters and abundances for all of our stars.
 These one-dimensional models ignore any centre-to-limb spatial variations, assume hydrostatic equilibrium and no convective overshoot from the photosphere.
-Absorption lines are assumed to form under the assumption of local thermal equilibrium.
 The stellar parameter spacing for these grid models is 250\,K, 0.5\,dex in surface gravity, 0.5\,dex in [M/H] and 0.1\,dex in [$\alpha$/Fe].
-We interpolated the atmospheric densities, temperatures, electron pressures at all depths between stellar atmospheres using the Quickhull algorithm for this analysis.
-Quickhull is reliant on Delaunay tessellation, which suffers from extremely skewed cells when the grid points vary in size by orders of magnitude -- as $T_{eff}$ values do compared to $\log{g}$ or [X/H].
-If unaccounted for, these asymmetric cells can manifest as significant errors in interpolated densities, temperatures, pressures, and opacities across all photospheric depths.
-We scaled each stellar parameter between zero and unity prior to interpolation to minimise these errors.
-During this step, $\log{g}$, [Fe/H] and [$\alpha$/Fe] points were scaled such that we simultaneously interpolate linearly in $T_{eff}$ and logarithmically in all other parameters.
+We interpolated the atmospheric pressures, densities, temperatures, and opacities between stellar atmospheres using the Quickhull algorithm \citep{Barber;et-al_1996}.
+Quickhull is reliant on Delaunay tessellation, which suffers from extremely skewed cells when the grid points vary in size by orders of magnitude -- as $T_{\mbox{eff}}$ values do compared to $\log{g}$ or [X/H].
+If unaccounted for, performing interpolation using these asymmetric cells can manifest as significant errors in atmospheric properties across all photospheric depths.
+We scaled each stellar parameter between zero and unity prior to interpolation in order to minimise these errors.
+During this step, $\log{g}$, [M/H] and [$\alpha$/Fe] points were scaled such that we simultaneously interpolate linearly in $T_{eff}$ and logarithmically in all other parameters.
 
@@
 The most recent version of the spectral synthesis code MOOG \citep{Sneden;et-al_1973} has been used to derive individual line abundances and stellar parameters.
-This version employs a more accurate treatment of Rayleigh scattering \citep{Sobeck;et-al_2011}, which is particularly important for transitions blueward of 450\,nm.
-This is noteworthy, but is less relevant for this analysis as most of our line measurements are redward of 450\,nm.
-We have scaled our abundances to solar values using the chemical composition of \citet{Asplund;et-al_2009}.
-
-\subsubsection{Photometric Effective Temperatures}
-
-The effective temperatures published for all of our stars in Table \ref{sec:stellar-parameters} were derived spectroscopically (see \S\ref{sec:effective-teffs}).
-For consistency, we have also estimated effective temperatures using 2MASS infrared photometry.
-The $J-K$ colour has been employed for these calculations because it has the least dependence on metallicity.
-The Aquarius stream is relatively close and at high-latitude, so significant extinction by dust is note expected.
-Nevertheless, the dust maps of \citet{Schlegel;et-al_1998} have been used to estimate the effect of extinction along the line-of-sight.
-Two different $T_{eff}$-colour relationships have been used for estimating temperatures: the \citet{Alonso;et-al_1999} calibration for dwarfs/sub-giants, and the ?
-calibration for giants.
-All photometrically-derived temperatures are listed in \ref{tab:photometric-temperatures}.
+This version of MOOG employs Rayleigh scattering \citep{Sobeck;et-al_2011} instead of treating scattering as true absorption, which is particularly important for transitions blue-ward of 450\,nm.
+This is noteworthy, but is less relevant for this analysis as most of our line measurements are red-ward of 450\,nm.
+Absorption lines are assumed to form under the assumption of local thermal equilibrium.
 
@@
 Linear relationships with slopes of $|0.001|$ dex were considered to be converged.
+
+\subsubsection{Photometric Effective Temperatures}
+\label{sec:photometric-temperatures}
+
+The effective temperatures published for all of our stars in Table \ref{sec:stellar-parameters} have been derived spectroscopically (see \S\ref{sec:effective-teffs}).
+As a consistency check for our spectroscopic temperatures, we have also estimated effective temperatures using infrared photometry from the 2MASS catalog.
+The $J-K$ colour has been employed for these calculations because it has the least dependence on metallicity.
+
+The Aquarius stream is relatively close and at high-latitude, so significant extinction by dust is not expected.
+The dust maps of \citet{Schlegel;et-al_1998} estimate that the extinction for our stars varies between E(B-V) = 0.03 to 0.07 mags.
+However, these maps are not perfect.
+As an alternative to using the \citet{Schlegel;et-al_1998} dust maps, the level of extinction towards a star can be found by the strength of their interstellar Na D or K \textsc{I} lines \citep{Munari;Zwitter_2006}.
+The interstellar lines must be sufficiently separated from the stellar lines in order for the extinction to be measurable.
+Unfortunately this was the case in only one of our stars, J223811.
+We measure the equivalent width of the Na D \textsc{I} line in J223811 to be 302.4\,m{\AA}, which corresponds to an $\mbox{E(B-V)} = 0.12^{+0.01}_{-0.02}$ according to the \citet{Munari;Zwitter_2006} relationship.
+This is a significantly higher value than what the \citet{Schlegel;et-al_1998} dust map value of $\mbox{E(B-V)} = 0.07$ for J223811.
+Both extinction values have been used to calculate photometric temperatures.
+
+Although all of our targets are giant stars, two different $T_{eff}$-colour relationships have been employed: the \citet{Alonso;et-al_1999} calibration for giants, and the \citet{Casagrande;et-al_2010} calibration for dwarfs and sub-giants.
+All photometrically-derived temperatures are listed in \ref{tab:photometric-temperatures}.
+The \citet{Alonso;et-al_1999} $J-K$ scale is insensitive to metallicity effects, and is in good agreement with our spectroscopic temperatures.
+For the \citet{Casagrande;et-al_2010} $J-K$ relationship, which has a slight metallicity dependency, we have utilized the spectroscopically-derived [Fe/H] values shown in Table \ref{tab:stellar-parameters}.
+
+The effective temperatures that we have found from spectroscopy agree fairly well with the photometric temperature estimates.
+For three of our stars, the temperatures we find are in between the two color-temperature relationships.
+There are two noteworthy deviations though: J223504-152834 and J223811-104126.
+For J223504-152834 we find the star to have an effective temperature of 4620\,K, 40\,K hotter than the \citet{Casagrande;et-al_2010} dwarf/sub-giant relationship, and ${\sim}$500\,K hotter than the \citet{Alonso;et-al_1999} temperature.
+Our temperature of 4620\,K is in good agreement with previous spectroscopic determinations (4795\,K; \citet{williams;et-al_2011}, 4597\,K; \citet{wylie-de-boer;et-al_2012}).
+The fact that the \citet{Alonso;et-al_1999} photometric temperature relationship for giants predicts a temperature that is ${\sim}$500\,K cooler than the spectroscopically-derived values may be attributed to an underestimated amount of dust towards J223504-152834.
+A higher than expected level of extinction along the line-of-sight would produce cooler temperatures than the true effective temperature.
+
+The F-giant J223811-104126 has two extinction values available: the \citet{Schlegel;et-al_1998} value of $E(B-V) = 0.07$ and the 0.12 value that we have determined from the interstellar Na D1 line.
+Given the inherent difficulties in producing dust maps, and the known problems associated with them, we believe the $E(B-V) = 0.12$ determination to be more accurate.
+However, using the \citet{Schlegel;et-al_1998} extinction with the \citet{Alonso;et-al_1999} color-temperature relationship yields excellent agreement (within 6\,K) with our spectroscopic temperatures.
+Employing our more accurate reddening determination yields 5215\,K, within the uncertainties of the relationship.
+The \citet{Casagrande;et-al_2010} scale is ${\sim}$250\,K hotter in both cases.
+
+Thus, with the exception of J223504-152834, the \citet{Alonso;et-al_1999} giant relationship agrees well ($\pm$100\,K) with our spectroscopically derived values.
+The \citet{Casagrande;et-al_2010} relationship is also in relatively good agreement with our spectroscopic temperatures, although we note that this relation was derived primarily for dwarfs/sub-giants.
+The discrepancy in J223504-152834 could very well be due to under-estimated reddenning along the line-of-sight.
+An extinction of $E(B-V) = 0.10$ would be required for the \citet{Alonso;et-al_1999} relation to yield a temperature of ${\sim}$4500\,K, within the uncertainties of our effective temperature derived from spectroscopy.
+Such a discrepancy in extinction is large, but not unheard of (e.g., the case of J223811-104126 or see \citet{Nataf;et-al}).
+Although we suspect J223504-152834 to have a higher reddening than $E(B-V) = 0.04$, we have adopted the \citet{Schelegel;et-al_1998} value for this analysis.
+
+\begin{deluxetable}{lccccc}
+\tablecolumns{1}
+\tabletypesize{\scriptsize}
+\tablecaption{Reddening \& Photometric Temperatures}
+\tablehead{
+& & & \multicolumn{2}{c}{$T_{phot}$} \\
+\cline{4-5} \\
+	\colhead{Designation} &
+	\colhead{E($B-V$)} &
+	\colhead{$(J-K)_0$} &
+	\colhead{Alonso} &
+	\colhead{Casagrande} \\
+	& (mag) & & (K) & (K)
+}
+\startdata 
+C222531-144370 	& 0.03\phn	& 	0.75 & 4247	&	4391 \\	
+C230626-085103	& 0.05\phn	&	0.82 & 4091	&	4200 \\	
+J221821-183424 	& 0.03\phn	&	0.64 & 4546	&	4747 \\	
+J223504-152834 	& 0.04\phn	&	0.69 & 4110	& 	4579 \\	
+J223811-104126 	& 0.07\phn	&	0.48 & 5104	&	5367 \\	
+				& 0.12\footnote{Extinction derived from interstellar Na D1 line (see \ref{sec:photometric-temperatures})} 			&	0.45 & 5215	&	5484	
+\enddata
+\end{deluxetable}
 
@@
 	\colhead{Designation} &
-	\colhead{$T_{\mbox{eff}}$} &
+	\colhead{$T_{eff}$} &
 	\colhead{$\log{g}$} &
@@
 	\colhead{[Fe/H]} & 
-	\colhead{$T_{\mbox{eff}}$} &
+	\colhead{$T_{eff}$} &
 	\colhead{$\log{g}$} &
@@
 	\colhead{Source} \\
+	& (K) & (dex) & (km\,s$^{-1}$) & (dex) & (K) & (dex) & (km s$^{-1}$) & (dex) 
 }
 \startdata
+\multicolumn{10}{c}{Standard Stars} \\
+\cline{1-10} \\
+HD41667			& 4630	& 1.70	& 1.66 	& --1.21
+				& 4605	& 1.88	& 1.44	& --1.16
+				& \citet{gratton;et-al_2000} \\
+HD44007			& 4790	& 1.78	& 1.63	& --1.80
+				& 4850	& 2.00 	& 2.20	& --1.71
+				& \citet{fulbright_2000} \\
+HD142948		& 4950	& 2.19	& 1.78	& --0.79
+				& 4713 	& 2.17 	& 1.38	& --0.77
+				& \citet{gratton;et-al_2000} \\
+\\
+\multicolumn{10}{c}{Program Stars} \\
+\cline{1-10} \\
 C2225316-14437	& 4350	& 1.60	& 1.80	& --1.19	
@@
 				& \dots \\	
-HD41667			& 4630	& 1.70	& 1.66 	& --1.21
-				& 4605	& 1.88	& 1.44	& --1.16
-				& \citet{Gratton;et-al_2000} \\
-HD44007			& 4790	& 1.78	& 1.63	& --1.80
-				& 4850	& 2.00 	& 2.20	& --1.71
-				& \citet{Fulbright_2000} \\
-HD142948		& 4950	& 2.19	& 1.78	& --0.79
-				& 4713 	& 2.17 	& 1.38	& --0.77
-				& \citet{Gratton;et-al_2000} \\
 J221821-183424	& 4570	& 0.80	& 1.93	& --1.60
@@
 \subsection{Abundances}
+We have scaled our abundances to solar values using the chemical composition of \citet{Asplund;et-al_2009}.
 
@@
 \subsubsection{Oxygen}
+\label{sec:oxygen-abundances}
 Oxygen is a particularly difficult element to measure.
@@
 
-Sodium is produced during hydrogen burning through the Ne-Na cycle, as well as through carbon burning in massive stars by the dominant $^{12}\mbox{C}(^{12}\mbox{C}, p)^{23}\mbox{Na}$ process.
-The total amount of Na production by C-burning is dependent on the neutron excess of the star, which slowly increases through stellar evolution along the red giant branch.
+Sodium is mainly produced through through carbon burning in massive stars by the dominant $^{12}\mbox{C}(^{12}\mbox{C}, p)^{23}\mbox{Na}$ process.
+The final Na abundance is dependent on the neutron excess of the star, which slowly increases during carbon burning due to weak interactions \citep{Arnett;Truran_1974}.
 Massive stars ($>8 M_\odot$) eventually deliver their manufactured sodium to the interstellar-medium through SN II events.
@@
 
-The explosive material eventually condenses to form the next generation of stars, which will have a net increase in their neutron excess with respect to their predecessors.
+The explosive material eventually condenses to form the next generation of stars, which will have a net increase in their neutron excess with respect to when their predecessors formed.
 Since the Na-production rate is correlated with the neutron excess, an overall increase in the total Na and Na-production rate between stellar generations is expected.
@@
 Sodium content also becomes important for production of Ni during the SN II event (see \S\ref{sec:na-ni}) because $^{23}$Na is the only stable isotope produced in significant quantities during the C- (or O-) burning stages.
+A small fraction of $^{22}$Na is also forged through proton capture on $^{21}$Ne in the carbon shell, an effect which is enhanced by neutrinos spallating abundant elements like $^{16}$O and $^{20}$Ne, making free protons available for capture \citep{Woosley;Weaver_1995}.
 
@@
 \subsubsection{$\alpha$-elements (Mg, Ca, Si and Ti)}
+\label{sec:alpha-elements}
 
 The $\alpha$-elements (Mg, Ca, Si and Ti) are forged through $\alpha$-particle capture in assorted burning stages of stellar evolution, including the burning of carbon, neon and silicon.
+Although Ti ($Z = 22$) is not formally an $\alpha$-element, its abundance generally varies with those of the other $\alpha$-elements and therefore has been included here.
 
 % magnesium measurements
-Magnesium has been measured from unblended lines that fall within the linear regime between reduced equivalent width and abundance.
-Depending on the radial velocity of the star, some of these lines can be affected by telluric absorption, particularly the 6318$\lambda$ and 6965.4$\lambda$ lines.
+%Magnesium has been measured from unblended lines that fall within the linear regime between reduced equivalent width and abundance.
+Depending on the radial velocity of the star, some magnesium lines were be affected by telluric absorption, particularly the 6318$\lambda$ and 6965.4$\lambda$ lines.
 Atmospheric absorption was most notable for C2225316-14437, where three of the four Mg transitions in our line list suffered some degree of telluric absorption, requiring an attentive correction.
-Every corrected absorption profile was carefully examined, and lines with suspicious profiles were excluded from the final magnesium abundance.
+Every amended absorption profile was carefully examined, and lines with suspicious profiles were excluded from the final magnesium abundance.
 
@@
 If we exclude the most prominent outlier, then the mean abundance drops only slightly to $\mbox{[Si/Fe]} = 0.70 \pm 0.04$\,dex.
-The lowest Si line abundance for C2225316-14437 is $\mbox{[Si/Fe]} = 0.57$\,dex, still significantly higher than the final measurements for any other star.
+The lowest silicon line abundance for C2225316-14437 is $\mbox{[Si/Fe]} = 0.57$\,dex, still significantly higher than the final measurements for any other star.
 
 % titanium measurements
+
+\subsubsection{Iron-peak Elements}
+Scantium, Vanadium, Chromium and Manganese. All very vanilla, exhibiting a downward trend with [Fe/H].
+Data.
+
+\subsubsection{Barium}
+Barium is a neutron-capture element, primarily produced through the \textit{s}-process, but can be forged from a variety of nucleosynthetic processes.
+Measuring barium requires some careful consideration.
+The strong resonance lines at 4554 {\AA} and 4934 {\AA} have appreciable hyperfine splitting, which if unaccounted for can result in over-estimated abundances.
+There are a few singly ionized lines available in our spectra which do not suffer from strong hyperfine splitting, namely the 5853, 6141 and 6496 {\AA} transitions.
+Depending on the radial velocity of the star, sometimes our 6496 {\AA} line was affected by small amounts of telluric absorption.
+In these cases the line was discarded.
+The abundances tabulated in Table \ref{tab:program-star-abundances} are based on the remaining clean Ba \textsc{II} lines at 5853 and 6141 {\AA}, which are generally in good agreement with each other, and the 6496 {\AA} line where available.
+
+Our standard stars have [Ba/Fe] abundances very typical of the Milky Way halo.
+Only one of our standard stars, HD 44007, has published [Ba/Fe] abundances from high-resolution spectra.
+We find HD 44007 to have $\mbox{[Ba/Fe]} = -0.05 \pm 0.04$, which is in rough accordance with existing published measurements from \citet{Fulbright;et-al_2000} and \citet{Burris;et-al_2000} of $-0.27$ and 0.05 dex, respectively.
+
+With one exception, the Aquarius stream stars have barium abundances that are quite similar to the stellar halo, ranging between $\mbox{[Ba/Fe]} = -0.02$ to 0.15 dex.
+The exception is C2225316, which has an anomalously high barium abundance of $\mbox{[Ba/Fe]} = 0.68$ dex.
+This is $\sim{}0.60$ dex higher than the Milky Way trend at its given $\mbox{[Fe/H]} = -1.19$ dex.
+Our three Ba \textsc{II} lines in C2225316 are in excellent agreement: 0.67, 0.68, and 0.72 dex.
+The 6496 {\AA} transition has negligible telluric contribution (e.g.
+Figure \ref{fig:ba-6496}), so it was included for this star.
+At least in Al, Si, Cr and Ba abundances (see sections \ref{sec:aluminium-abundance}, \ref{sec:alpha-elements}, \ref{sec:iron-peak-elements}), this star appears to be chemically distinct from the other Aquarius stream stars in our sample.
 
@@
 \tablehead{
- \multicolumn{7}{c}{J221821-183424} & \colhead{} & \multicolumn{7}{c}{C2225316-14437} \\
- \cline{1-7} \cline{9-15} \\
 \colhead{Species} & $N$ & $\log\epsilon(X)$ & $\sigma_\epsilon$ & [X/H] & [X/Fe] & $\sigma$ &&
@@
 \startdata
+\\
+ \multicolumn{7}{c}{J221821-183424} & \colhead{} & \multicolumn{7}{c}{C2225316-14437} \\
+ \cline{1-7} \cline{9-15} \\
    O \textsc{I} &   2 &    7.50 &    0.04 & $-$1.18 &    0.41 &    0.02 &&
@@
    O \textsc{I} &   2 &    8.48 &    0.09 & $-$0.21 &    0.46 &    0.07 &&
-   O \textsc{I} &   1 &    8.60 &    0.00 & $-$0.09 &    1.36 & \nodata \\
+   O \textsc{I} &   1 &    8.60 &    0.00 & $-$0.09 &    0.14\footnote{Abundance derived from the permitted O \textsc{I} triplet instead of the forbidden [O \textsc{I}] lines, see \S\ref{sec:oxygen-abundances}} &    0.08 \\
   Na \textsc{I} &   3 &    5.76 &    0.12 & $-$0.48 &    0.19 &    0.07 &&
@@
 \citet{wylie-de-boer;et-al_2012} deduce their stellar parameters through the use of a $\chi^2$ analysis against synthetic spectra from the \citet{munari;et-al_2005} grid.
-Our temperatures have been determined by forcing a zero trend in excitation potential and line abundance.
-In general, these temperatures agree within the uncertainties, with our temperatures being marginally (23-175 K) hotter.
-The only noteworthy exception is J223811-104126, where we find an effective temperature 546 K cooler than \citet{wylie-de-boer;et-al_2012}.
+In general,  temperatures between the two studies agree within the uncertainties, with our temperatures being marginally (23-175 K) hotter.
+The only noteworthy exception is J223811-104126, where we find an effective temperature 546\,K cooler than \citet{wylie-de-boer;et-al_2012}.
 This is the largest discrepancy we see in any of our standard or program stars.
@@
 \citet{wylie-de-boer;et-al_2012} calculate microturbulence with the empirical relationships from \citet{Reddy;et-al_2003} for dwarfs and \citet{fulbright_2000} for giants.
-These relationships are based upon the derived temperature and surface gravities.
-Our published microturbulence values agree excellently with the values presented in \citet{wylie-de-boer;et-al_2012} with the exception of J223811-104126, which we find to be a F-type giant and others have claimed is a -type dwarf from medium-resolution spectra \citep{wylie-de-boer;et-al_2012, williams;et-al_2011}.
-Small discrepancies in microturbulence for other stars can be directly attributed to difference in surface gravities.
+These relationships are based upon derived temperature and surface gravities.
+Our published microturbulence values agree excellently with the values presented in \citet{wylie-de-boer;et-al_2012}, again with the exception of J223811-104126, which we find to be a F-type giant and others have claimed is a -type dwarf from medium-resolution spectra \citep{wylie-de-boer;et-al_2012, williams;et-al_2011}.
+Thus, the discrepancy in microturbulence is directly attributed to the differences in other stellar parameters.
 
@@
 
-Given the line list employed, the overall data quality and the lack of Fe\,I lines available for analysis, it appears the Aquarius stream stars have conspired to present a tight metallicity distribution function -- suggesting of a globular cluster origin.
+Given the line list employed, the overall data quality and the lack of Fe\,I lines available for analysis, it appears the Aquarius stream stars have conspired to present a tight metallicity distribution function -- suggestive of a globular cluster origin.
 In contrast, our high-resolution analysis suggests a significantly broader metallicity distribution of $\langle$[Fe/H]$\rangle = X.XX \pm X.XX$ dex.
@@
 
-Extensive studies looking at stars in globular clusters have revealed variations in light-element abundances, most notably an anti-correlation in sodium and oxygen content \citet{Norris;Da-Costa_1995}.
+Extensive studies looking at stars in globular clusters have revealed variations in light-element abundances, most notably an anti-correlation in sodium and oxygen content \citet[][and references therein]{norris;da-costa_1995,caretta;et-al_2008}.
 Between generations of stars within a globular cluster, the oxygen abundance is transformed into nitrogen, reducing the overall oxygen abundance.
@@
 An intermediate population -- the second-generation of stars -- will have super-solar sodium abundances, and demonstrate a slight depletion in oxygen content.
-The  abundance exhaustion rate is ultimately dependent on the star-formation history of the cluster environment.
+The oxygen exhaustion rate is ultimately dependent on the star-formation history of the cluster environment.
 The intermediate population is sub-divided based on how much the O and Na abundances depart from the primordial population: stars with [O/Na]$ > -0.9$ dex are classified as belonging to an extreme component of this Na-O pattern because they differ greatly from the primordial cluster abundance.
@@
 In addition to the normal care afforded for measuring elemental abundances from high-resolution spectroscopic data, attention must be given to telluric absorption, Ni contamination, and NLTE corrections when deriving oxygen abundances.
-Furthermore, when characterising the oxygen depletion rate -- and hence the strength of the Na-O anti-correlation for a cluster -- it is vital to obtain observations for stars belonging to all three components (where possible).
+Furthermore, when characterising the oxygen depletion rate -- and hence the strength of the Na-O anti-correlation in a given cluster -- it is vital to obtain observations for stars belonging to all three components (where possible).
 If only a primordial sample of stars in a globular cluster is observed, then their [Na/Fe] and [O/Fe] abundances will be indistinguishable from halo stars of a similar metallicity.
@@
 
-With high-resolution data and modest ($\sim$30 pixel$^{-1}$) signal-to-noise, \citet{Wylie-de-boer;et-al_2012} measured Na and O abundances for four of their six Aquarius stream members.
-This research has four stars in common with the \citet{Wylie-de-boer;et-al_2012} study, but Na and O measurements exist for only three stars that are in both samples.
-We have measurements for all of our stars, including J223811-104126, for which we ascertained an upper limit from the [O \textsc{I}] lines of [O/Fe] $< 0.5$ dex, and a NLTE-corrected abundance of $\mbox{[O/Fe]} = 0.21$ (CHECK) from the O \textsc{I} triplet lines.
+\citet{wylie-de-boer;et-al_2012} measured [Na/Fe] and [O/Fe] abundances for four of their six Aquarius stream members.
+This research has four stars in common with the \citet{wylie-de-boer;et-al_2012} study, but Na and O measurements exist for only three stars that are in both samples.
+We have measurements for all of our stars, including J223811-104126, for which we ascertained an upper limit from the [O \textsc{I}] lines of [O/Fe] $< 0.5$ dex, and a NLTE-corrected abundance of $\mbox{[O/Fe]} = 0.14$ from the O \textsc{I} triplet lines.
 
@@
 
-The \citet{wylie-de-boer;et-al_20120} measurements indicate two stars with solar-type levels of Na -- identical to field star Na abundances for their metallicity -- and two stars with super-solar sodium content.
-Combined with measurements of other light elements (see \S\ref{sec:al-mg}, \ref{sec:na-ni}) they claim the Aquarius stream is ``consistent with a globular cluster origin''.
+The \citet{wylie-de-boer;et-al_2012} measurements indicate two stars with solar-type levels of Na -- identical to field star Na abundances for their metallicity -- and two stars with super-solar sodium content.
 The \citet{wylie-de-boer;et-al_2012} abundances themselves do not demonstrate a classical Na-O anti-correlation.
 In fact, they have a slight positive relationship: their Na-enhanced stars show an increased oxygen content, contrary to an expected oxygen depletion between generations with.
-However, this trend is drawn from a sample of only four stars -- the same as this study if our upper limit for J223811-104126 is excluded.
+
+This trend is drawn from a sample of only four stars -- the same as this study if our upper limit for J223811-104126 is excluded.
 
@@
 
-% discuss the discovery of the Na-Ni relationship
+% need to say about [alpha/fe] and [na/fe] with distance
+Detailed chemical studies of nearby disk stars have noted a correlation with [Na/Fe] and [Ni/Fe].
+This relationship was first hinted in \citet{Nissen;Schuster_1997}, where they found eight stars that were underabundant in [$\alpha$/Fe], [Na/Fe] and [Ni/Fe].
+Interestingly, the authors noted that stars at larger galactocentric radii were most deficient in these elements.
+\citet{fulbright;et-al_2000} saw a similar signature: stars with low [Na/Fe] were only found at large ($R_\odot > 20$\,kpc) distances.
+\citet{Nissen;Schuster_1997} proposed that as the outer halo is thought to have been built up through the accretion of dSph satellites, then the Na-Ni pattern may be a chemical indicator of merger history in the galaxy.
 
-% this relationship was correlated with distance, such that more distant stars were deficient in Na
+With additional data from \citet{Nissen;Schuster_2010}, the Na-Ni relationship was found to be slightly steeper than originally proposed.
+The pattern exists only for metal-rich stars $-1.5 < \mbox{[Fe/H]} < -0.5$ dex, and is not seen in metal-poor dSph stars, providing a potentially useful indicator for investigating chemical evolution.
+However, it is crucial to note that although there are only a few dSph stars in the $-1.5 < \mbox{[Fe/H]} < -0.5$ metallicity regime with [Na/Fe], [Ni/Fe] measurements, they agree reasonably well with the galactic trend.
 
-% revise contribution of Na from type II SN events
+The correlation between sodium and nickel content is the nucleosynthetic result of neutron capture in massive stars.
+As previously discussed, the total Na abundance is controlled by the neutron excess, which limits the production of $^{58}$Ni during SN II events.
+When the supernova occurs, the core photodissociates into neutrons and protons, allowing the temporary creation of $^{56}$Ni before it decays to $^{56}$Fe.
+A limited amount of $^{54}$Fe is also formed, which is the main source of production for the stable $^{58}$Ni isotope through $\alpha$-capture.
+When the core dissociates, the quantity of $^{54}$Fe (and hence $^{58}$Ni) produced is dependent on the abundance of neutron-rich elements during the explosion.
+As $^{23}$Na is a relatively plentiful neutron source with respect to other potential sources (like $^{13}$C), the post-supernova $^{58}$Ni abundance is driven by the pre-explosion $^{23}$Na content.
+Recall that the total Na production primarily depends on the neutron excess.
+Thus, through populations of massive stars undergoing C-burning, a positive correlation between Na-Ni can be expected.
 
-% production of nickel
-
-% thus, a Na-Ni trend is expected across a wide range of metallicities
+As \citet{Venn;et-al_2004} point out, this pattern can be altered from contributions by type Ia supernova.
 
 % as Venn points out, this trend can be altered based on SN Ia contributions
-
+Nickel is
+produced without Na in the standard model of SNe Ia, in which
+a CO white dwarf tips over the Chandrasekhar limit and the
+C-burning region is completely photodissociated (Tsujimoto
+et al. 1995). This would ßatten the Na-Ni correlation. However, the route to SNe Ia is convoluted and doubtless involves
+rare binary star interactions (e.g., RegIs et al. 2003). It is quite
+uncertain what the Na yields from these might be; e.g., if a CO
+white dwarf accretes a He white dwarf, perhaps the build up of
+He on the surface may undergo C burning and release Na
+before the star photodissociates to form Ni in the SN event
 % in general, we can expect high Na, Ni abundances in stars that have an long contribution of previous massive stars

### 2012-12-28 2012-aqs/draft-aqs.tex
Added equivalent widths table and some discussion text

@@
 Wide-field surveys have proved excellent sources for finding galactic substructures, including stellar streams.
-Dozens of streams reaching out up to 150\,kpc in the halo have been identified through photometric selections and matched-filtering techniques \citep{Belokurov;et-al_2007;Koposov_SG1}.
-However, as \citet{Helmi;White_1999} point out, these approaches are only successful for identifying substructures that are sufficiently distant from the solar neighbourhood.
+Dozens of streams reaching out up to 150\,kpc in the halo have been identified through photometric selections and matched-filtering techniques \citep{belokurov;et-al_2007,koposov_SG1}.
+However, as \citet{helmi;white_1999} point out, these approaches are only successful for identifying substructures that are sufficiently distant from the solar neighbourhood.
 A nearby stream within $\sim{}$10\,kpc will not appear as an on-sky over-density, as the stars would be sparsely positioned across the sky.
@@
 Upon examining the galactic longitude and radial velocities of Aquarius stars, the stream appears quite distinct from the halo.
-In order to quantify the statistical likelihood that the Aquarius stream is a true substructure, \citet{WIlliams;et-al_2011} compared the number of observed RAVE stars within $-70\,^\circ < b < -50\,^\circ$ against the Galaxia \citep{Sharma;et-al_2009} and Besan\c{c}on \citep{Robin;et-al_2003} galaxy models.
+In order to quantify the statistical likelihood that the Aquarius stream is a true substructure, \citet{williams;et-al_2011} compared the number of observed RAVE stars within $-70\,^\circ < b < -50\,^\circ$ against the Galaxia \citep{sharma;et-al_2011} and Besan\c{c}on \citep{robin;et-al_2003} galaxy models.
 Predicted particles and observed stars between $-70\,^\circ < b < -50\,^\circ$ were binned in $\Delta{l} \times \Delta{V_{hel}}$ using varying grid cell sizes between $25-70\,^\circ$ and 20-100\,km s$^{-1}$ respectively.
@@
 There are other abundances patterns that allow us to infer the chemical evolution of a given cluster.
-\citet{Nissen;Schuster_1997} first noted that only the distant solar neighbourhood stars were enriched in [Ni/Fe] and [Na/Fe].
-\citet{fulbright;et-al_2000} came to a similar conclusion: only somewhat distant ($R_\odot > 20$\,kpc) stars are likely to be sodium deficient.
-If the stellar halo has been built up from the accretion of smaller dwarf satellites, \citet{Nissen;Schuster_1997} proposed that this chemical trend may be indicative of the halo merger history.
+\citet{nissen;schuster_1997} first noted that only the distant solar neighbourhood stars were enriched in [Ni/Fe] and [Na/Fe].
+\citet{fulbright_2000} came to a similar conclusion: only somewhat distant ($R_\odot > 20$\,kpc) stars are likely to be sodium deficient.
+If the stellar halo has been built up from the accretion of smaller dwarf satellites, \citet{nissen;schuster_1997} proposed that this chemical trend may be indicative of the halo merger history.
 Although there are some caveats to this chemical pattern (see \S\ref{sec:ni-na-relation}), at the very least the Na-Ni correlation may provide an indication whether stars became chemically enriched in dSph-like environments.
@@
 We seek to investigate the nature of the Aquarius stream, in particular the recent globular cluster origin claim made by \citet{wylie-de-boer;et-al_2012}.
-We present a detailed analysis for five confirmed Aquarius stream members from high-resolution, high S/N observations taken using the Magellan Inamori Kyocera Echelle spectrograph \citep{Bernstein;et-al_2003} on the Magellan Clay telescope.
+We present a detailed analysis for five confirmed Aquarius stream members from high-resolution, high S/N observations taken using the Magellan Inamori Kyocera Echelle spectrograph \citep{bernstein;et-al_2003} on the Magellan Clay telescope.
 Our analysis includes determining the galactic dynamics and orbital paths for the Aquarius stream, and measuring precise chemical abundances.
@@
 
+% what spectral resolution in the blue, what resolution in the red
+
 Calibration frames were taken at the start of each night, including twenty flat-field frames (10 quartz, 10 milky) and 10 Th-Ar arc lamp exposures for wavelength calibration.
-The data were reduced using the CarPy pipeline\footnote{carpy website url}.
-One of our standard stars, HD 41667, was also reduced using standard extraction and calibration methods in \textsc{IRAF}.
+The data were reduced using the CarPy pipeline\footnote{http://code.obs.carnegiescience.edu/mike}.
+One of our standard stars, HD 41667, was also reduced using standard extraction and calibration methods in \textsc{iraf}.
 The resultant spectra from both reduction workflows were compared for residual fringing, S/N, and wavelength calibration.
@@
 For the measurement of atomic absorption lines, we employed the line list of \citet{yong;et-al_2005} with additional transitions of Cr, Sc, Zn, and Sr from \citet{frebel;et-al_2010}.
-We supplemented the list with hyperfine-structure data for Sc and Mn from the Kurucz compilation \citet{Kurucz;1998}.
-Molecular line data for CH was taken from \citet{Plez;et-al_2008,Plez;et-al_2009}.
+We supplemented the list with hyperfine-structure data for Sc and Mn from the Kurucz compilation \citet{kurucz;1998}.
+Molecular line data for CH was taken from \citet{plez;et-al_2008,plez;et-al_2009}.
 For lines with hyperfine structure, blended transitions or molecular features, we determined the transition abundance using a spectral synthesis approach where the abundance of a given species is found by by matching a synthetic spectrum to the observed spectrum.
@@
 
-We note that the results of our iterative fitting approach are \textit{completely insensitive} to the initial FWHM guess.
-Increasing the initial FWHM estimate from 0.1\,\AA{} to 1 or 2\,\AA{} -- unphysically large values for high-resolution spectra -- does not alter \textit{any} of our final equivalent width (or FWHM) measurements.
+The results of our iterative fitting approach are completely \textit{insensitive} to the initial FWHM guess.
+Increasing the initial FWHM estimate from 0.1\,\AA{} to 1 or 2\,\AA{} -- unphysically large values for high-resolution spectra -- does not alter either the FWHM or the equivalent width for any of our measurements.
 Only a small increase in computational cost is observed.
@@
 A minimum detectable equivalent width was calculated as a function of wavelength based on the S/N, and only lines that exceeded a $3\sigma$ detection significance were included.
-We have verified our equivalent width measurement techniques by comparing our measurements for 164 lines in HD140283 with the study of \citet{norris;et-al_1996}.
+We have verified our equivalent width measurement techniques by comparing our measurements for 156 lines in HD140283 with the study of \citet{norris;et-al_1996}.
+We only included measurements in the \citet{norris;et-al_1996} study that were not marked with line quality parameters.
 Excellent agreement is found between the two studies, which is illustrated in Figure \ref{fig:ew-compare}.
 The mean difference between this study and that of \cite{norris;et-al_1996} is a negligible $0.64 \pm 2.78$\,m\AA{}, and no systematic trend is present.
-
-% need to mention that we only used the "Good" Norris measurements
+We note that the scatter in measurement differences is likely to be directly attributed to the observed $S/N$, as other studies using the same EW measurement software described here find better agreement with hand measurements for spectra with higher $S/N$ ($0.20 \pm 0.16$\,m{\AA} with $S/N \sim X$, $0.25 \pm 0.28$\,m{\AA} with $S/N \sim{} Y$; \citet{frebel;et-al_2013}).
 
@@
 	\includegraphics[width=\columnwidth]{./figures/smh-norris.pdf}
-	\caption{A comparison showing equivalent widths measured for HD140283 using our automatic routine (see \S\ref{sec:line-measurements}), and those found with careful hand measurements by \citet{norris;et-al_1996}.
+	\caption{A comparison showing equivalent widths measured for HD 140283 using our automatic routine (see \S\ref{sec:line-measurements}), and those found by careful hand measurements in \citet{norris;et-al_1996}.
 No systematic trend is present, and the mean difference between these studies is $\langle\Delta{}W_\lambda\rangle = -0.64 \pm 2.78$ m\AA{}.}
@@
 
+\begin{deluxetable*}{cccccccccc}
+\tablecolumns{1}
+\tabletypesize{\scriptsize}
+\tablecaption{List of Line Transitions and Equivalent Width Measurements}
+\tablehead{
+	& & & & \multicolumn{5}{c}{Equivalent Width} \\
+	\cline{5-9} \\
+	\colhead{Wavelength} &
+	\colhead{Transition} &
+	\colhead{LEP} &
+	\colhead{$\log{gf}$} &
+	\colhead{C2225316-14437} &
+	\colhead{C2306265-085103} &
+	\colhead{J221821-183424} &
+	\colhead{J223504-152834} &
+	\colhead{J223811-104126} \\
+	({\AA})	& & (eV) & & (m{\AA}) & (m{\AA}) & (m{\AA}) & (m{\AA}) & (m{\AA}) 
+}
+\startdata 
+ 6300.300 &       8.0 &      0.00 &    --9.717 &     45.37 &     66.93 &     38.48 &     32.85 &     17.87 \\
+ 6363.780 &       8.0 &      0.02 &   --10.185 &     19.47 &     28.31 &     12.96 &     18.83 &   \nodata \\
+ 5688.190 &      11.0 &      2.11 &    --0.420 &   \nodata &   \nodata &     48.97 &    131.49 &     38.41 \\
+ 6154.230 &      11.0 &      2.10 &    --1.530 &     24.06 &     38.89 &   \nodata &     48.49 &   \nodata \\
+ 6160.750 &      11.0 &      2.10 &    --1.230 &     37.72 &     58.49 &   \nodata &     65.72 &   \nodata \\
+ 6318.720 &      12.0 &      5.11 &    --1.970 &   \nodata &     47.94 &     14.69 &     62.79 &      8.88 \\
+ 6319.240 &      12.0 &      5.11 &    --2.220 &     30.84 &   \nodata &      5.51 &   \nodata &   \nodata \\
+ 6965.410 &      12.0 &      5.75 &    --1.510 &   \nodata &   \nodata &   \nodata &     59.22 &   \nodata \\
+ 7387.690 &      12.0 &      5.75 &    --0.870 &     51.71 &     56.30 &     24.68 &     76.01 &     23.99 \\
+ 6696.020 &      13.0 &      3.14 &    --1.340 &     72.83 &     63.60 &     12.99 &   \nodata &   \nodata \\
+ 6698.670 &      13.0 &      3.14 &    --1.640 &     39.67 &     33.44 &   \nodata &     39.50 &   \nodata \\
+ 7835.310 &      13.0 &      4.02 &    --0.470 &     47.77 &     38.44 &   \nodata &     55.91 &      5.39 \\
+ 7836.130 &      13.0 &      4.02 &    --0.310 &     62.78 &     44.72 &   \nodata &     69.13 &     13.23 \\
+ 5690.430 &      14.0 &      4.93 &    --1.751 &     56.17 &     43.76 &     25.75 &     53.45 &     16.77 \\
+ 5793.070 &      14.0 &      4.93 &    --1.843 &     46.13 &     39.81 &     19.33 &     48.39 &   \nodata \\
+ 6125.020 &      14.0 &      5.61 &    --1.506 &     40.93 &     23.45 &     10.86 &     34.74 &   \nodata \\
+ 6145.010 &      14.0 &      5.62 &    --1.362 &     33.93 &     21.66 &     16.11 &     32.75 &     10.02 \\
+ 6155.130 &      14.0 &      5.62 &    --0.786 &     67.36 &     53.11 &     35.29 &     72.00 &     24.98 \\
+ 6166.440 &      20.0 &      2.52 &    --1.142 &     94.19 &    105.46 &     42.32 &     99.45 &     35.88 \\
+ 6169.040 &      20.0 &      2.52 &    --0.797 &    112.06 &    120.91 &     66.31 &    120.48 &     55.48 \\
+ 6169.560 &      20.0 &      2.53 &    --0.478 &    127.89 &    141.16 &     83.69 &    136.37 &     71.35 \\
+ 6455.600 &      20.0 &      2.52 &    --1.290 &     80.79 &     91.41 &     31.35 &     89.20 &     25.98 \\
+ 5526.820 &      21.1 &      1.77 &      0.130 &     98.84 &    113.34 &    100.84 &     98.40 &     51.08 \\
+ 5657.880 &      21.1 &      1.51 &    --0.500 &     96.46 &    107.49 &     92.74 &     95.42 &     41.21 \\
+ 5667.150 &      21.1 &      1.50 &    --1.240 &     59.41 &     75.04 &     45.00 &     58.54 &     14.51 \\
+ 5669.040 &      21.1 &      1.50 &    --1.120 &   \nodata &     92.51 &     57.27 &     75.19 &     18.20 \\
+ 6245.610 &      21.1 &      1.51 &    --0.980 &     67.12 &     83.60 &     53.34 &     67.38 &     14.75 \\
+ 6604.600 &      21.1 &      1.36 &    --1.480 &     65.58 &     82.06 &     49.37 &     65.92 &     17.81 \\
+ 6064.630 &      22.0 &      1.05 &    --1.888 &     59.69 &     80.86 &   \nodata &     58.58 &   \nodata \\
+ 6091.170 &      22.0 &      2.27 &    --0.367 &     45.15 &     59.09 &   \nodata &     56.28 &   \nodata \\
+ 6312.240 &      22.0 &      1.46 &    --1.496 &     46.16 &     63.41 &   \nodata &     48.78 &   \nodata \\
+ 6336.100 &      22.0 &      1.44 &    --1.687 &     35.88 &     54.10 &   \nodata &     42.33 &   \nodata \\
+ 5154.080 &      22.1 &      1.57 &    --1.920 &    112.25 &   \nodata &    114.05 &   \nodata &     53.89 \\
+ 5185.910 &      22.1 &      1.89 &    --1.350 &   \nodata &    101.45 &    105.46 &   \nodata &     55.30 \\
+ 5336.790 &      22.1 &      1.58 &    --1.690 &    116.30 &    124.58 &    119.55 &    103.98 &     61.40 \\
+ 5381.030 &      22.1 &      1.59 &    --2.080 &   \nodata &    131.44 &    101.94 &    109.93 &     47.96 \\
+ 5727.060 &      23.0 &      1.08 &    --0.010 &    122.36 &   \nodata &     26.00 &    116.79 &      9.13 \\
+ 6090.220 &      23.0 &      1.08 &    --0.060 &     93.58 &    115.58 &     23.62 &     92.84 &   \nodata \\
+ 6216.360 &      23.0 &      0.28 &    --1.290 &    108.80 &   \nodata &     16.92 &    109.33 &   \nodata \\
+ 6251.820 &      23.0 &      0.29 &    --1.340 &     94.66 &    124.37 &   \nodata &     92.43 &   \nodata \\
+ 6274.640 &      23.0 &      0.27 &    --1.670 &     65.49 &     93.82 &   \nodata &     61.51 &   \nodata \\
+ 6504.160 &      23.0 &      1.18 &    --1.230 &     22.95 &     33.69 &   \nodata &     31.93 &   \nodata \\
+ 4545.950 &      24.0 &      0.94 &    --1.370 &   \nodata &   \nodata &     80.22 &   \nodata &   \nodata \\
+ 4580.056 &      24.0 &      0.94 &    --1.650 &   \nodata &   \nodata &   \nodata &   \nodata &     44.22 \\
+ 4616.137 &      24.0 &      0.98 &    --1.190 &    128.75 &    139.25 &     89.37 &    126.24 &     59.88 \\
+ 4626.188 &      24.0 &      0.97 &    --1.320 &    122.24 &    136.41 &     82.24 &   \nodata &     56.90 \\
+ 4646.150 &      24.0 &      1.03 &    --0.740 &   \nodata &   \nodata &    110.65 &    146.08 &     75.35 \\
+ 4651.280 &      24.0 &      0.98 &    --1.460 &    127.78 &    140.58 &     75.40 &    116.31 &     48.44 \\
+ 4652.158 &      24.0 &      1.00 &    --1.030 &    138.48 &   \nodata &     96.92 &    138.00 &     66.74 \\
+ 5206.040 &      24.0 &      0.94 &      0.020 &   \nodata &   \nodata &   \nodata &   \nodata &    132.81 \\
+ 5247.564 &      24.0 &      0.96 &    --1.640 &    141.39 &   \nodata &     76.09 &   \nodata &     46.66 \\
+ 5296.690 &      24.0 &      0.98 &    --1.360 &    149.87 &   \nodata &     85.01 &    140.97 &     59.00 \\
+ 5300.740 &      24.0 &      0.98 &    --2.000 &    120.48 &   \nodata &   \nodata &    112.22 &   \nodata \\
+ 5345.800 &      24.0 &      1.00 &    --0.950 &   \nodata &   \nodata &    115.38 &   \nodata &     81.14 \\
+ 5348.310 &      24.0 &      1.00 &    --1.210 &    150.80 &   \nodata &     94.76 &    142.37 &     63.02 \\
+ 5409.770 &      24.0 &      1.03 &    --0.670 &   \nodata &   \nodata &    132.36 &   \nodata &     92.13 \\
+ 4558.594 &      24.1 &      4.07 &    --0.656 &   \nodata &   \nodata &   \nodata &    101.77 &     46.52 \\
+ 4588.142 &      24.1 &      4.07 &    --0.826 &     46.04 &     52.99 &     60.53 &     55.00 &     35.95 \\
+ 4591.992 &      24.1 &      4.07 &    --1.419 &   \nodata &   \nodata &     29.08 &     28.53 &     19.56 \\
+ 6013.530 &      25.0 &      3.07 &    --0.251 &     89.19 &    114.55 &     22.18 &    109.41 &     14.81 \\
+ 6016.670 &      25.0 &      3.08 &    --0.100 &     93.98 &    116.01 &     28.15 &    113.02 &     17.06 \\
+ 6021.800 &      25.0 &      3.08 &      0.034 &     97.50 &    116.02 &     39.08 &    110.74 &     19.90 \\
+ 5044.210 &      26.0 &      2.85 &    --2.034 &   \nodata &   \nodata &   \nodata &   \nodata &     33.70 \\
+ 5054.640 &      26.0 &      3.64 &    --1.938 &     37.96 &   \nodata &   \nodata &   \nodata &   \nodata \\
+ 5242.490 &      26.0 &      3.63 &    --0.980 &     94.34 &    101.83 &     72.92 &   \nodata &     49.25 \\
+ 5321.110 &      26.0 &      4.43 &    --1.106 &     34.97 &     35.32 &     11.14 &   \nodata &   \nodata \\
+ 5322.040 &      26.0 &      2.28 &    --2.840 &     93.10 &    103.03 &     59.48 &   \nodata &     30.88 \\
+ 5326.140 &      26.0 &      3.57 &    --2.130 &     40.39 &     51.67 &     13.75 &     48.44 &   \nodata \\
+ 5365.400 &      26.0 &      3.57 &    --1.040 &   \nodata &    100.31 &   \nodata &     93.75 &   \nodata \\
+ 5367.480 &      26.0 &      4.41 &      0.430 &    108.42 &    118.03 &     92.35 &    119.08 &     73.73 \\
+ 5379.570 &      26.0 &      3.69 &    --1.530 &     71.36 &     81.40 &     34.91 &     75.65 &     19.57 \\
+ 5491.840 &      26.0 &      4.18 &    --2.250 &   \nodata &   \nodata &   \nodata &     17.29 &   \nodata \\
+ 5618.630 &      26.0 &      4.21 &    --1.292 &     43.46 &     54.27 &     20.25 &     57.44 &     11.30 \\
+ 5701.550 &      26.0 &      2.56 &    --2.216 &    118.51 &    134.78 &     91.77 &    119.47 &     49.50 \\
+ 5705.470 &      26.0 &      4.30 &    --1.420 &     29.24 &     41.47 &     10.92 &     44.49 &      7.70 \\
+ 5741.850 &      26.0 &      4.25 &    --1.689 &     36.19 &     37.02 &     13.01 &     48.22 &   \nodata \\
+ 5775.080 &      26.0 &      4.22 &    --1.310 &     54.96 &     62.12 &     25.34 &     67.38 &     14.67 \\
+ 5778.450 &      26.0 &      2.59 &    --3.480 &     42.75 &     55.83 &     13.43 &     50.14 &   \nodata \\
+ 5811.920 &      26.0 &      4.14 &    --2.430 &   \nodata &   \nodata &   \nodata &     10.88 &   \nodata \\
+ 5837.700 &      26.0 &      4.29 &    --2.340 &   \nodata &   \nodata &   \nodata &     12.94 &   \nodata \\
+ 5853.160 &      26.0 &      1.49 &    --5.280 &     30.38 &     43.35 &      6.28 &     34.65 &   \nodata \\
+ 5855.090 &      26.0 &      4.60 &    --1.547 &     13.31 &     20.31 &   \nodata &     22.77 &   \nodata \\
+ 5856.100 &      26.0 &      4.29 &    --1.640 &     27.88 &     40.19 &   \nodata &     42.69 &   \nodata \\
+ 5858.790 &      26.0 &      4.22 &    --2.260 &   \nodata &     11.37 &   \nodata &     16.85 &   \nodata \\
+ 5909.970 &      26.0 &      3.21 &    --2.640 &     55.96 &     72.65 &     18.47 &     63.29 &   \nodata \\
+ 5916.250 &      26.0 &      2.45 &    --2.994 &     92.92 &    105.08 &     51.17 &     95.37 &     17.67 \\
+ 5927.800 &      26.0 &      4.65 &    --1.090 &     32.37 &     36.72 &     12.16 &     50.92 &   \nodata \\
+ 5956.690 &      26.0 &      0.86 &    --4.608 &    121.68 &    143.78 &     70.27 &    107.81 &     25.53 \\
+ 6012.210 &      26.0 &      2.22 &    --4.070 &     44.36 &     58.79 &     11.51 &     52.96 &   \nodata \\
+ 6019.360 &      26.0 &      3.57 &    --3.360 &      7.00 &   \nodata &   \nodata &     11.34 &   \nodata \\
+ 6027.050 &      26.0 &      4.07 &    --1.106 &     66.25 &     77.00 &     36.21 &     77.20 &     23.52 \\
+ 6054.080 &      26.0 &      4.37 &    --2.310 &      5.63 &      8.08 &   \nodata &     12.92 &   \nodata \\
+ 6105.130 &      26.0 &      4.55 &    --2.050 &   \nodata &     10.92 &   \nodata &     14.84 &   \nodata \\
+ 6120.240 &      26.0 &      0.91 &    --5.970 &     35.22 &     52.71 &      8.54 &     32.41 &   \nodata \\
+ 6151.620 &      26.0 &      2.17 &    --3.299 &     88.90 &    102.90 &     46.94 &     87.04 &     18.19 \\
+ 6157.730 &      26.0 &      4.08 &    --1.320 &   \nodata &     81.19 &     33.20 &     78.14 &     18.79 \\
+ 6159.380 &      26.0 &      4.61 &    --1.970 &   \nodata &      9.61 &   \nodata &     13.56 &   \nodata \\
+ 6165.360 &      26.0 &      4.14 &    --1.490 &     40.57 &     51.56 &     14.17 &     54.02 &     10.84 \\
+ 6173.340 &      26.0 &      2.22 &    --2.880 &    109.59 &    125.61 &     70.72 &    105.59 &     34.86 \\
+ 6180.200 &      26.0 &      2.73 &    --2.637 &     86.21 &    100.58 &     44.33 &     91.55 &     20.83 \\
+ 6200.310 &      26.0 &      2.61 &    --2.437 &    105.22 &    122.16 &     70.78 &    105.43 &     36.60 \\
+ 6219.280 &      26.0 &      2.20 &    --2.433 &    134.35 &    153.29 &    103.28 &    127.37 &     56.70 \\
+ 6229.230 &      26.0 &      2.84 &    --2.846 &     60.14 &     73.08 &     21.02 &     65.77 &     13.61 \\
+ 6232.640 &      26.0 &      3.65 &    --1.283 &     92.59 &    104.33 &     58.26 &    103.00 &     35.63 \\
+ 6246.320 &      26.0 &      3.60 &    --0.894 &    114.00 &    129.15 &     90.50 &    124.05 &     61.68 \\
+ 6265.130 &      26.0 &      2.17 &    --2.550 &    132.93 &    154.97 &     94.79 &    129.65 &     55.50 \\
+ 6270.220 &      26.0 &      2.86 &    --2.500 &     76.71 &     93.59 &     41.22 &     79.05 &     17.41 \\
+ 6271.280 &      26.0 &      3.33 &    --2.728 &     31.57 &     44.87 &     13.35 &     43.63 &   \nodata \\
+ 6297.790 &      26.0 &      2.22 &    --2.740 &    119.28 &   \nodata &     81.27 &    111.34 &     42.26 \\
+ 6301.500 &      26.0 &      3.65 &    --0.766 &    115.00 &    130.57 &     91.09 &    117.86 &   \nodata \\
+ 6322.690 &      26.0 &      2.59 &    --2.426 &    111.05 &    124.39 &     74.19 &    103.53 &     41.61 \\
+ 6336.820 &      26.0 &      3.68 &    --0.916 &    106.61 &    116.77 &     81.17 &    113.62 &     52.77 \\
+ 6353.840 &      26.0 &      0.91 &    --6.477 &     11.78 &     23.73 &   \nodata &     14.12 &   \nodata \\
+ 6355.030 &      26.0 &      2.84 &    --2.403 &   \nodata &    122.18 &     58.95 &   \nodata &     27.76 \\
+ 6411.650 &      26.0 &      3.65 &    --0.734 &    122.49 &    135.09 &     97.80 &    131.75 &     68.20 \\
+ 6469.190 &      26.0 &      4.84 &    --0.770 &   \nodata &   \nodata &     18.72 &   \nodata &   \nodata \\
+ 6574.230 &      26.0 &      0.99 &    --5.004 &     84.07 &    118.54 &     35.42 &     87.02 &   \nodata \\
+ 6575.020 &      26.0 &      2.59 &    --2.727 &    100.74 &    118.20 &     55.46 &    103.43 &     23.43 \\
+ 6581.210 &      26.0 &      1.50 &    --4.705 &     72.41 &     87.47 &     21.69 &     69.56 &   \nodata \\
+ 6609.110 &      26.0 &      2.56 &    --2.692 &    102.04 &    118.77 &     60.88 &    103.07 &     29.10 \\
+ 6648.080 &      26.0 &      1.01 &    --5.918 &     37.05 &     54.92 &   \nodata &     37.88 &   \nodata \\
+ 6739.520 &      26.0 &      1.56 &    --4.820 &     43.10 &     60.83 &   \nodata &     44.46 &   \nodata \\
+ 6750.150 &      26.0 &      2.42 &    --2.621 &    110.92 &    128.94 &     78.61 &    109.54 &     40.25 \\
+ 6786.860 &      26.0 &      4.19 &    --1.850 &     22.52 &     29.14 &   \nodata &     32.32 &   \nodata \\
+ 6810.260 &      26.0 &      4.60 &    --1.000 &     36.16 &     46.93 &     14.51 &     54.86 &      8.49 \\
+ 6971.930 &      26.0 &      3.02 &    --3.390 &     20.95 &     30.29 &   \nodata &     28.72 &   \nodata \\
+ 7112.170 &      26.0 &      2.99 &    --3.044 &     45.44 &     59.25 &     13.34 &     52.97 &   \nodata \\
+ 7189.150 &      26.0 &      3.07 &    --2.796 &     57.46 &     66.29 &   \nodata &   \nodata &   \nodata \\
+ 7223.660 &      26.0 &      3.01 &    --2.269 &     87.17 &    114.42 &     47.18 &     90.80 &   \nodata \\
+ 7401.690 &      26.0 &      4.18 &    --1.660 &     38.86 &     50.50 &     14.73 &     59.70 &   \nodata \\
+ 7710.360 &      26.0 &      4.22 &    --1.129 &     62.55 &     76.72 &     32.47 &     75.37 &   \nodata \\
+ 7723.200 &      26.0 &      2.28 &    --3.617 &     82.10 &    100.41 &     36.62 &     91.89 &   \nodata \\
+ 7941.090 &      26.0 &      3.27 &    --2.331 &     50.25 &   \nodata &     22.41 &     61.73 &   \nodata \\
+ 5234.620 &      26.1 &      3.22 &    --2.150 &   \nodata &     81.16 &   \nodata &   \nodata &     58.33 \\
+ 5325.550 &      26.1 &      3.22 &    --3.220 &   \nodata &     32.07 &     43.44 &   \nodata &     11.62 \\
+ 5414.070 &      26.1 &      3.22 &    --3.750 &   \nodata &   \nodata &     23.56 &     20.98 &      6.85 \\
+ 5425.260 &      26.1 &      3.20 &    --3.370 &     27.09 &     38.20 &     41.32 &     37.29 &     14.47 \\
+ 5991.380 &      26.1 &      3.15 &    --3.557 &     21.50 &   \nodata &     28.34 &     25.80 &      7.66 \\
+ 6084.110 &      26.1 &      3.20 &    --3.808 &     11.81 &     15.98 &     20.00 &     18.81 &   \nodata \\
+ 6149.260 &      26.1 &      3.89 &    --2.724 &     21.75 &     25.19 &     30.83 &     26.28 &     11.80 \\
+ 6247.560 &      26.1 &      3.89 &    --2.329 &     31.15 &     36.73 &     50.16 &     40.30 &     21.38 \\
+ 6369.460 &      26.1 &      2.89 &    --4.250 &     13.49 &     16.26 &     18.13 &     16.72 &      5.89 \\
+ 6416.920 &      26.1 &      3.89 &    --2.740 &     23.09 &     29.20 &     29.18 &     31.92 &   \nodata \\
+ 6432.680 &      26.1 &      2.89 &    --3.708 &     29.96 &     33.58 &     41.73 &     37.47 &     12.93 \\
+ 6456.380 &      26.1 &      3.90 &    --2.075 &     40.91 &     47.90 &     61.24 &     49.33 &     30.85 \\
+ 7224.490 &      26.1 &      3.89 &    --3.243 &   \nodata &   \nodata &     12.70 &     13.24 &   \nodata \\
+ 7711.720 &      26.1 &      3.90 &    --2.543 &     23.68 &     29.14 &     37.42 &     29.79 &     14.85 \\
+ 6189.000 &      27.0 &      1.71 &    --2.450 &     51.15 &     77.50 &      9.06 &     58.65 &   \nodata \\
+ 6455.030 &      27.0 &      3.63 &    --0.250 &     19.14 &     29.82 &   \nodata &     31.42 &   \nodata \\
+ 6632.450 &      27.0 &      2.28 &    --2.000 &     29.08 &     42.26 &   \nodata &     34.72 &   \nodata \\
+ 5846.990 &      28.0 &      1.68 &    --3.210 &     60.72 &     77.03 &     17.76 &     62.70 &   \nodata \\
+ 6086.280 &      28.0 &      4.26 &    --0.515 &     31.84 &     36.07 &     12.42 &     47.85 &   \nodata \\
+ 6175.370 &      28.0 &      4.09 &    --0.535 &     41.41 &     48.64 &     21.11 &     52.50 &     10.42 \\
+ 6177.240 &      28.0 &      1.83 &    --3.510 &     39.25 &     48.84 &     11.10 &     39.41 &   \nodata \\
+ 6204.600 &      28.0 &      4.09 &    --1.140 &     14.88 &     18.50 &   \nodata &     25.25 &   \nodata \\
+ 6635.120 &      28.0 &      4.42 &    --0.828 &     14.95 &     18.16 &   \nodata &     25.99 &   \nodata \\
+ 6772.320 &      28.0 &      3.66 &    --0.987 &     53.50 &     59.12 &     26.46 &     62.05 &     12.97 \\
+ 5105.540 &      29.0 &      1.39 &    --1.520 &    139.40 &    160.37 &     67.12 &    123.33 &     32.51 \\
+ 4722.150 &      30.0 &      4.03 &    --0.390 &     74.05 &     67.90 &     73.57 &     76.47 &     37.45 \\
+ 4810.528 &      30.0 &      4.08 &    --0.137 &     61.50 &     63.63 &     72.49 &     82.28 &     42.08 \\
+ 7800.290 &      37.0 &      0.00 &      0.130 &   \nodata &   \nodata &   \nodata &     60.87 &   \nodata \\
+ 5123.220 &      39.1 &      0.99 &    --0.830 &   \nodata &   \nodata &   \nodata &   \nodata &     16.46 \\
+ 5200.420 &      39.1 &      0.99 &    --0.570 &    100.92 &   \nodata &     65.76 &     78.58 &     26.46 \\
+ 5509.910 &      39.1 &      0.99 &    --1.010 &    103.01 &     94.44 &     47.04 &     95.37 &     15.75 \\
+ 5544.610 &      39.1 &      1.74 &    --1.080 &     29.88 &     18.79 &      9.50 &     16.20 &   \nodata \\
+ 6127.440 &      40.0 &      0.15 &    --1.060 &     56.33 &     44.90 &   \nodata &     29.69 &   \nodata \\
+ 6134.550 &      40.0 &      0.00 &    --1.280 &     49.65 &     38.66 &   \nodata &     23.60 &   \nodata \\
+ 6143.200 &      40.0 &      0.07 &    --1.100 &     54.38 &     44.59 &   \nodata &     30.67 &   \nodata \\
+ 5112.270 &      40.1 &      1.67 &    --0.590 &   \nodata &   \nodata &     21.76 &   \nodata &   \nodata \\
+ 5853.640 &      56.1 &      0.60 &    --1.010 &    143.48 &    121.36 &    110.82 &     99.79 &     49.62 \\
+ 6141.730 &      56.1 &      0.70 &    --0.080 &    213.65 &    177.63 &    166.44 &    151.09 &     93.10 \\
+ 5805.770 &      57.1 &      0.13 &    --1.560 &     47.67 &     28.80 &     13.04 &     25.08 &   \nodata \\
+ 6390.480 &      57.1 &      0.32 &    --1.410 &     42.96 &     22.03 &     11.61 &     18.59 &   \nodata \\
+ 5274.240 &      58.1 &      1.04 &    --0.320 &     29.14 &   \nodata &     12.69 &   \nodata &   \nodata \\
+ 5472.300 &      58.1 &      1.24 &    --0.180 &     19.37 &   \nodata &   \nodata &   \nodata &   \nodata \\
+ 4959.120 &      60.1 &      0.06 &    --0.800 &     79.90 &     74.05 &     34.96 &     64.18 &   \nodata \\
+ 5092.790 &      60.1 &      0.38 &    --0.610 &     47.28 &   \nodata &     21.87 &     20.94 &   \nodata \\
+ 5212.360 &      60.1 &      0.20 &    --0.960 &     61.37 &     61.85 &     19.56 &     51.64 &   \nodata \\
+ 5234.190 &      60.1 &      0.55 &    --0.510 &     71.89 &     57.86 &     17.93 &     47.31 &   \nodata \\
+ 5249.580 &      60.1 &      0.98 &      0.200 &     64.54 &     54.71 &     31.75 &     50.73 &   \nodata \\
+ 5255.510 &      60.1 &      0.20 &    --0.670 &    116.28 &   \nodata &     40.49 &   \nodata &   \nodata \\
+ 5293.160 &      60.1 &      0.82 &      0.100 &     74.25 &     71.57 &     29.03 &     62.49 &   \nodata \\
+ 5319.810 &      60.1 &      0.55 &    --0.140 &     86.60 &   \nodata &     34.41 &   \nodata &   \nodata \\
+ 6645.110 &      63.1 &      1.38 &      0.204 &     24.47 &     27.76 &     16.96 &     30.31 &   \nodata \\
+\enddata
+\end{deluxetable*}
+
 % equivalent widths table
@@
 \subsection{Model Atmospheres}
-The ATLAS9 plane-parallel stellar atmospheres of \citet{Castelli;Kurucz_2003} have been used to deduce stellar parameters and abundances for all of our stars.
+The ATLAS9 plane-parallel stellar atmospheres of \citet{castelli;kurucz_2003} have been used to deduce stellar parameters and abundances for all of our stars.
 These one-dimensional models ignore any centre-to-limb spatial variations, assume hydrostatic equilibrium and no convective overshoot from the photosphere.
 The stellar parameter spacing for these grid models is 250\,K, 0.5\,dex in surface gravity, 0.5\,dex in [M/H] and 0.1\,dex in [$\alpha$/Fe].
-We interpolated the atmospheric pressures, densities, temperatures, and opacities between stellar atmospheres using the Quickhull algorithm \citep{Barber;et-al_1996}.
+We interpolated the atmospheric pressures, densities, temperatures, and opacities between stellar atmospheres using the Quickhull algorithm \citep{barber;et-al_1996}.
 Quickhull is reliant on Delaunay tessellation, which suffers from extremely skewed cells when the grid points vary in size by orders of magnitude -- as $T_{\mbox{eff}}$ values do compared to $\log{g}$ or [X/H].
@@
 \subsection{Stellar Parameters}
-The most recent version of the spectral synthesis code MOOG \citep{Sneden;et-al_1973} has been used to derive individual line abundances and stellar parameters.
-This version of MOOG employs Rayleigh scattering \citep{Sobeck;et-al_2011} instead of treating scattering as true absorption, which is particularly important for transitions blue-ward of 450\,nm.
+The most recent version of the spectral synthesis code \textsc{moog} \citep{sneden;et-al_1973} has been used to derive individual line abundances and stellar parameters.
+This version of \textsc{moog} employs Rayleigh scattering \citep{sobeck;et-al_2011} instead of treating scattering as true absorption, which is particularly important for transitions blue-ward of 450\,nm.
 This is noteworthy, but is less relevant for this analysis as most of our line measurements are red-ward of 450\,nm.
@@
 \subsubsection{Effective Temperature}
-
 The effective temperature for each star was found by demanding a zero-trend in excitation potential and abundance for each measured Fe\,I line.
@@
 The Aquarius stream is relatively close and at high-latitude, so significant extinction by dust is not expected.
-The dust maps of \citet{Schlegel;et-al_1998} estimate that the extinction for our stars varies between E(B-V) = 0.03 to 0.07 mags.
+The dust maps of \citet{schlegel;et-al_1998} estimate that the extinction for our stars varies between E(B-V) = 0.03 to 0.07 mags.
 However, these maps are not perfect.
-As an alternative to using the \citet{Schlegel;et-al_1998} dust maps, the level of extinction towards a star can be found by the strength of their interstellar Na D or K \textsc{I} lines \citep{Munari;Zwitter_2006}.
+As an alternative to using the \citet{schlegel;et-al_1998} dust maps, the level of extinction towards a star can be found by the strength of their interstellar Na D or K \textsc{I} lines \citep{munari;zwitter_1997}.
 The interstellar lines must be sufficiently separated from the stellar lines in order for the extinction to be measurable.
 Unfortunately this was the case in only one of our stars, J223811.
-We measure the equivalent width of the Na D \textsc{I} line in J223811 to be 302.4\,m{\AA}, which corresponds to an $\mbox{E(B-V)} = 0.12^{+0.01}_{-0.02}$ according to the \citet{Munari;Zwitter_2006} relationship.
-This is a significantly higher value than what the \citet{Schlegel;et-al_1998} dust map value of $\mbox{E(B-V)} = 0.07$ for J223811.
+We measure the equivalent width of the Na D \textsc{I} line in J223811 to be 302.4\,m{\AA}, which corresponds to an $\mbox{E(B-V)} = 0.12^{+0.01}_{-0.02}$ according to the \citet{munari;zwitter_1997} relationship.
+This is a significantly higher value than what the \citet{schlegel;et-al_1998} dust map value of $\mbox{E(B-V)} = 0.07$ for J223811.
 Both extinction values have been used to calculate photometric temperatures.
 
-Although all of our targets are giant stars, two different $T_{eff}$-colour relationships have been employed: the \citet{Alonso;et-al_1999} calibration for giants, and the \citet{Casagrande;et-al_2010} calibration for dwarfs and sub-giants.
+Although all of our targets are giant stars, two different $T_{eff}$-colour relationships have been employed: the \citet{alonso;et-al_1999} calibration for giants, and the \citet{casagrande;et-al_2010} calibration for dwarfs and sub-giants.
 All photometrically-derived temperatures are listed in \ref{tab:photometric-temperatures}.
-The \citet{Alonso;et-al_1999} $J-K$ scale is insensitive to metallicity effects, and is in good agreement with our spectroscopic temperatures.
-For the \citet{Casagrande;et-al_2010} $J-K$ relationship, which has a slight metallicity dependency, we have utilized the spectroscopically-derived [Fe/H] values shown in Table \ref{tab:stellar-parameters}.
+The \citet{alonso;et-al_1999} $J-K$ scale is insensitive to metallicity effects, and is in good agreement with our spectroscopic temperatures.
+For the \citet{casagrande;et-al_2010} $J-K$ relationship, which has a slight metallicity dependency, we have utilized the spectroscopically-derived [Fe/H] values shown in Table \ref{tab:stellar-parameters}.
 
@@
 There are two noteworthy deviations though: J223504-152834 and J223811-104126.
-For J223504-152834 we find the star to have an effective temperature of 4620\,K, 40\,K hotter than the \citet{Casagrande;et-al_2010} dwarf/sub-giant relationship, and ${\sim}$500\,K hotter than the \citet{Alonso;et-al_1999} temperature.
+For J223504-152834 we find the star to have an effective temperature of 4620\,K, 40\,K hotter than the \citet{casagrande;et-al_2010} dwarf/sub-giant relationship, and ${\sim}$500\,K hotter than the \citet{alonso;et-al_1999} temperature.
 Our temperature of 4620\,K is in good agreement with previous spectroscopic determinations (4795\,K; \citet{williams;et-al_2011}, 4597\,K; \citet{wylie-de-boer;et-al_2012}).
-The fact that the \citet{Alonso;et-al_1999} photometric temperature relationship for giants predicts a temperature that is ${\sim}$500\,K cooler than the spectroscopically-derived values may be attributed to an underestimated amount of dust towards J223504-152834.
+The fact that the \citet{alonso;et-al_1999} photometric temperature relationship for giants predicts a temperature that is ${\sim}$500\,K cooler than the spectroscopically-derived values may be attributed to an underestimated amount of dust towards J223504-152834.
 A higher than expected level of extinction along the line-of-sight would produce cooler temperatures than the true effective temperature.
 
-The F-giant J223811-104126 has two extinction values available: the \citet{Schlegel;et-al_1998} value of $E(B-V) = 0.07$ and the 0.12 value that we have determined from the interstellar Na D1 line.
+The F-giant J223811-104126 has two extinction values available: the \citet{schlegel;et-al_1998} value of $E(B-V) = 0.07$ and the 0.12 value that we have determined from the interstellar Na D1 line.
 Given the inherent difficulties in producing dust maps, and the known problems associated with them, we believe the $E(B-V) = 0.12$ determination to be more accurate.
-However, using the \citet{Schlegel;et-al_1998} extinction with the \citet{Alonso;et-al_1999} color-temperature relationship yields excellent agreement (within 6\,K) with our spectroscopic temperatures.
+However, using the \citet{schlegel;et-al_1998} extinction with the \citet{alonso;et-al_1999} color-temperature relationship yields excellent agreement (within 6\,K) with our spectroscopic temperatures.
 Employing our more accurate reddening determination yields 5215\,K, within the uncertainties of the relationship.
-The \citet{Casagrande;et-al_2010} scale is ${\sim}$250\,K hotter in both cases.
-
-Thus, with the exception of J223504-152834, the \citet{Alonso;et-al_1999} giant relationship agrees well ($\pm$100\,K) with our spectroscopically derived values.
-The \citet{Casagrande;et-al_2010} relationship is also in relatively good agreement with our spectroscopic temperatures, although we note that this relation was derived primarily for dwarfs/sub-giants.
+The \citet{casagrande;et-al_2010} scale is ${\sim}$250\,K hotter in both cases.
+
+Thus, with the exception of J223504-152834, the \citet{alonso;et-al_1999} giant relationship agrees well ($\pm$100\,K) with our spectroscopically derived values.
+The \citet{casagrande;et-al_2010} relationship is also in relatively good agreement with our spectroscopic temperatures, although we note that this relation was derived primarily for dwarfs/sub-giants.
 The discrepancy in J223504-152834 could very well be due to under-estimated reddenning along the line-of-sight.
-An extinction of $E(B-V) = 0.10$ would be required for the \citet{Alonso;et-al_1999} relation to yield a temperature of ${\sim}$4500\,K, within the uncertainties of our effective temperature derived from spectroscopy.
-Such a discrepancy in extinction is large, but not unheard of (e.g., the case of J223811-104126 or see \citet{Nataf;et-al}).
-Although we suspect J223504-152834 to have a higher reddening than $E(B-V) = 0.04$, we have adopted the \citet{Schelegel;et-al_1998} value for this analysis.
+An extinction of $E(B-V) = 0.10$ would be required for the \citet{alonso;et-al_1999} relation to yield a temperature of ${\sim}$4500\,K, within the uncertainties of our effective temperature derived from spectroscopy.
+Such a discrepancy in extinction is large, but not unheard of (e.g., the case of J223811-104126 or see \citet{nataf;et-al}).
+Although we suspect J223504-152834 to have a higher reddening than $E(B-V) = 0.04$, we have adopted the \citet{schlegel;et-al_1998} value for this analysis.
 
@@
 The degeneracy between parameters required a refinement of the stellar parameters until the line abundances were consistent with the model atmosphere.
-
-% process is iterative
-% our final Fe abundance matched the model atmosphere abundance
 
@@
 \subsection{Abundances}
-We have scaled our abundances to solar values using the chemical composition of \citet{Asplund;et-al_2009}.
+We have scaled our abundances to solar values using the chemical composition of \citet{asplund;et-al_2009}.
 
@@
 When they are present, depending on the radial velocity of the star, the [O \textsc{I}] can be significantly affected by telluric absorption.
-Moreover, the 630 nm line is blended with a Ni \textsc{I} absorption line \citep{Allende-Prieto;et-al_2001}, and hence the region requires careful consideration.
-Although the O \textsc{I} triplet lines at 777 nm are stronger than the forbidden lines, they are extremely susceptible to NLTE and 3D effects \citep{Asplund;Perez_2001}, and sensitive to changes in microturbulence.
-\citet{Perez;et-al_2006} showed that oxygen abundances measured under the assumption of LTE in their sample are 0.08\,dex higher than abundances derived from the `true' oxygen content derived from the forbidden lines \citep{Perez;et-al_2006}.
+Moreover, the 630 nm line is blended with a Ni \textsc{I} absorption line \citep{allende-prieto;et-al_2001}, and hence the region requires careful consideration.
+Although the O \textsc{I} triplet lines at 777 nm are stronger than the forbidden lines, they are extremely susceptible to NLTE and 3D effects \citep{asplund;perez_2001}, and sensitive to changes in microturbulence.
+\citet{perez;et-al_2006} showed that oxygen abundances measured under the assumption of LTE in their sample are 0.08\,dex higher than abundances derived from the `true' oxygen content derived from the forbidden lines \citep{perez;et-al_2006}.
 
@@
 Abundances determined from the oxygen triplet lines were systematically $+0.27$\,dex higher than found from the [O \textsc{I}] lines.
-\citet{Perez;et-al_2006} found [O/Fe] values based on the O \textsc{I} permitted triplet lines are on average $+0.19 \pm 0.07$\,dex higher than those found from the forbidden lines, after NLTE corrections of $-$0.08\,dex had been applied.
-Thus, our 0.27\,dex offset between measurements of the [O \textsc{I}] and O \textsc{I} triplet lines is exactly the same as found by \citet{Perez;et-al_2006}, which we attribute to a combination of NLTE, 3D and other systematic effects.
-\citet{Perez;et-al_2006} concluded the weak forbidden lines, when not too weak, probably give the most reliable estimate of [O/Fe].
+\citet{perez;et-al_2006} found [O/Fe] values based on the O \textsc{I} permitted triplet lines are on average $+0.19 \pm 0.07$\,dex higher than those found from the forbidden lines, after NLTE corrections of $-$0.08\,dex had been applied.
+Thus, our 0.27\,dex offset between measurements of the [O \textsc{I}] and O \textsc{I} triplet lines is exactly the same as found by \citet{perez;et-al_2006}, which we attribute to a combination of NLTE, 3D and other systematic effects.
+\citet{perez;et-al_2006} concluded the weak forbidden lines, when not too weak, probably give the most reliable estimate of [O/Fe].
 
@@
 Sodium is mainly produced through through carbon burning in massive stars by the dominant $^{12}\mbox{C}(^{12}\mbox{C}, p)^{23}\mbox{Na}$ process.
-The final Na abundance is dependent on the neutron excess of the star, which slowly increases during carbon burning due to weak interactions \citep{Arnett;Truran_1974}.
+The final Na abundance is dependent on the neutron excess of the star, which slowly increases during carbon burning due to weak interactions \citep{arnett;truran_1974}.
 Massive stars ($>8 M_\odot$) eventually deliver their manufactured sodium to the interstellar-medium through SN II events.
@@
 Sodium content also becomes important for production of Ni during the SN II event (see \S\ref{sec:na-ni}) because $^{23}$Na is the only stable isotope produced in significant quantities during the C- (or O-) burning stages.
-A small fraction of $^{22}$Na is also forged through proton capture on $^{21}$Ne in the carbon shell, an effect which is enhanced by neutrinos spallating abundant elements like $^{16}$O and $^{20}$Ne, making free protons available for capture \citep{Woosley;Weaver_1995}.
+A small fraction of $^{22}$Na is also forged through proton capture on $^{21}$Ne in the carbon shell, an effect which is enhanced by neutrinos spallating abundant elements like $^{16}$O and $^{20}$Ne, making free protons available for capture \citep{woosley;weaver_1995}.
 
@@
 Only one of our standard stars, HD 44007, has published [Ba/Fe] abundances from high-resolution spectra.
-We find HD 44007 to have $\mbox{[Ba/Fe]} = -0.05 \pm 0.04$, which is in rough accordance with existing published measurements from \citet{Fulbright;et-al_2000} and \citet{Burris;et-al_2000} of $-0.27$ and 0.05 dex, respectively.
+We find HD 44007 to have $\mbox{[Ba/Fe]} = -0.05 \pm 0.04$, which is in rough accordance with existing published measurements from \citet{fulbright_2000} and \citet{burris;et-al_2000} of $-0.27$ and 0.05 dex, respectively.
 
@@
 
-% RAVE pipeline discrepancies
-
 % wylie de boer discrepancies
 
-We seek to investigate the nature of the Aquarius stream, as well as the specific globular cluster origin claim by \citet{wylie-de-boer;et-al_2012}.
+We seek to investigate the nature of the Aquarius stream, as well as the specific globular cluster origin claim made by \citet{wylie-de-boer;et-al_2012}.
+
+\subsection{Stellar Parameter Discrepancies with \citet{wylie-de-boer;et-al_2012}}
+
 The stellar parameters reported in \citet{wylie-de-boer;et-al_2012} differ slightly to those found in Table \ref{tab:stellar-parameters}.
-\citet{wylie-de-boer;et-al_2012} deduce their stellar parameters through the use of a $\chi^2$ analysis against synthetic spectra from the \citet{munari;et-al_2005} grid.
+\citet{wylie-de-boer;et-al_2012} deduce their stellar parameters by minimizing the $\chi^2$ difference between the observed spectra, and spectra from the \citet{munari;et-al_2005} synthetic spectral library after it was convolved and re-sampled to match the observations.
+The comparison regions used for analysis were 4900-5200\,{\AA} and 5575-5725\,{\AA}.
 In general, temperatures between the two studies agree within the uncertainties, with our temperatures being marginally (23-175 K) hotter.
-The only noteworthy exception is J223811-104126, where we find an effective temperature 546\,K cooler than \citet{wylie-de-boer;et-al_2012}.
+The only noteworthy exception is J223811-104126, where we find an effective temperature of 5110\,K, ${\sim}$536\,K cooler than the 5646\,K found by \citet{wylie-de-boer;et-al_2012}.
+Similarly, \citet{williams;et-al_2011} report a hotter effective temperature of 5502\,K from low-resolution spectra.
 This is the largest discrepancy we see in any of our standard or program stars.
+
+Photometric temperatures only lend marginal weight towards our spectroscopic temperatures.
+If the \citet{schlegel;et-al_1998} dust maps are employed, then the \citet{alonso;et-al_1999} and \citet{casagrande;et-al_2010} relations estimate the effective temperatures to be between 5104\,K and 5367\,K.
+Our spectroscopic temperature of 5110\,K is closer to the \citet{alonso;et-al_1999} prediction, but not in disagreement with the \citet{casagrande;et-al_2010} relation.
+If we employ the reddening of $E(B-V) = 0.12$ that we have determined from interstellar Na D1 lines, the photometric temperatures increase slightly by ${\sim}100$\,K, still within the uncertainties of the \citet{alonso;et-al_1999} scale, but in less agreement with the \citet{casagrande;et-al_2010} scale.
+We find the surface gravity for J223811-104126 to be $3.00 \pm 0.50$, placing this star at the base of the red giant branch.
+Thus, our spectroscopic temperatures should be in slightly better agreement with the \citet{alonso;et-al_1999} scale for giant stars, rather than the \citet{casagrande;et-al_2010} dwarf/sub-giant scale.
+However, \citet{williams;et-al_2011} and \citet{wylie-de-boer;et-al_2012} find this star to be a sub-giant, with a surface gravity $\log{g} = 4.16$ and 4.60 respectively.
+In this scenario, their temperatures are 150\,K and 300\,K hotter than the \citet{casagrande;et-al_2010} prediction for \citet{williams;et-al_2011} and \citet{wylie-de-boer;et-al_2012} respectively.
+If our reddening is employed, then the \citet{williams;et-al_2011} and \citet{casagrande;et-al_2010} temperatures are in good agreement, yet still 175\,K cooler than the \citet{wylie-de-boer;et-al_2012} measurement.
+
+As a test, we set the temperature for J223811-104126 to be 5600\,K -- within the temperature regime reported by \citet{williams;et-al_2011} and \citet{wylie-de-boer;et-al_2012}.
+The slopes in abundance with excitation potential and reduced equivalent width were large (how many dex), and in doing so we could not find a physical solution for this temperature.
+Thus, although photometric temperatures do not help in solving this discrepancy, and the reddening measured from the interstellar Na D1 line may have made it worse, our high-resolution spectra  indicates that J223811-104126 has an effective temperature of 5110\,K and is indeed a giant star.
+
+In the \citet{wylie-de-boer;et-al_2012} study, the surface gravity was also determined during the $\chi^2$ minimization process.
+Again, with the exception of J223811-104126, our surface gravities are largely in agreement.
+The only other noteworthy difference in surface gravity is for J221821-183424, where we find a lower gravity of $\log{g} = 0.80 \pm 0.30$ where \citet{wylie-de-boer;et-al_2012} find $\log{g} = 1.45 \pm 0.35$\,cm\,s$^{-2}$.
+Given the difference in $S/N$ and resolution between these studies, this difference is not concerning.
 
@@
 These relationships are based upon derived temperature and surface gravities.
-Our published microturbulence values agree excellently with the values presented in \citet{wylie-de-boer;et-al_2012}, again with the exception of J223811-104126, which we find to be a F-type giant and others have claimed is a -type dwarf from medium-resolution spectra \citep{wylie-de-boer;et-al_2012, williams;et-al_2011}.
-Thus, the discrepancy in microturbulence is directly attributed to the differences in other stellar parameters.
-
-\subsection{Stellar Parameter Discrepancies with \citet{wylie-de-boer;et-al_2012}}
-
-The stellar parameter discrepancies between this study and \citet{wylie-de-boer;et-al_2012} need to be addressed.
-There are noteworthy differences in the stellar parameter determination between these studies.
-In the \citet{wylie-de-boer;et-al_2012} study, the temperature, metallicity and surface gravity were found by a $\chi^2$ analysis against the spectral library of \citet{munari;et-al_2005} after it was convolved and re-sampled to match the observational data.
-The comparison regions used for analysis were 4900-5200\,\AA{} and 5575-5725\,\AA{}.
-Using these parameters, an interpolated MARCS (?) model atmosphere was used to synthesise elemental abundances.
-Oscillator strengths in their line list were astrophysical; they were derived from a reverse analysis using the \citet{hinkle;et-al_2003} solar atlas.
-The spectrum synthesis code \textsc{MOOG} was used to derive abundances for individual Fe\,I and Fe\,II lines.
-The median abundance of Fe\,I lines was taken as the overall stellar metallicity, scaled using the \citet{Grevesse;Sauval_1998} solar abundances.
-
-The study of \citet{wylie-de-boer;et-al_2012} is of slightly lower resolution ($R = 25,000$ compared to $R = 28,000$ presented here), but with a much lower signal-to-noise ratio: $\sim{}25$ compared to $>100$ per pixel element achieved here.
-Given the slightly lower spectral resolution and modest signal-to-noise in their study, there are fewer unblended absorption lines available.
-In fact, there are very few transitions present in their published line list: only 14 Fe\,I lines and 3 Fe\,II lines are available.
+Our published microturbulence values agree excellently with the values presented in \citet{wylie-de-boer;et-al_2012}, again with the exception of J223811-104126, where the difference in $v_{mic}$ is directly attributed to the differences in other stellar parameters.
+
+Of all the stellar parameters ($T_{eff}$, $\log{g}$, $v_{t}$ and $\mbox{[Fe/H]}$), the metallicities between our two studies vary the most.
+Here we discuss the potential causes for these discrepancies.
+In the \citet{wylie-de-boer;et-al_2012} study, after the stellar parameters ($T_{eff}$, $\log{g}$, $v_{t}$, and an initial [Fe/H] estimate) had been determined, the authors synthesized Fe \textsc{I} and \textsc{II} lines to derive a final [Fe/H] abundance and an associated uncertainty.
+The spectrum synthesis code \textsc{moog} was used to derive abundances for individual Fe\,\textsc{I} and Fe\,\textsc{II} lines, and the \citet{castelli;kurucz_2003} stellar atmosphere models (the same ones used in this study) were employed.
+The median abundance of Fe\,I lines was taken as the overall stellar metallicity, scaled using the \citet{grevesse;sauval_1998} solar abundances.
+
+The study of \citet{wylie-de-boer;et-al_2012} is of slightly lower resolution ($R = 25,000$ compared to $R = 28,000$ presented here), but with a much lower $S/N$ ratio: $\sim{}25$ compared to $>100$ per pixel element achieved here.
+Given the lower spectral resolution and modest $S/N$ in their study, there are fewer unblended absorption lines available.
+In fact, there are very few transitions present in their published line list: only 14 Fe\,I lines and 3 Fe\,II lines were available.
 For contrast, our metallicity determinations are based off X Fe\,I and Y Fe\,II lines.
-Given the metallicity of these stars, it is somewhat surprising that there were not more unblended transitions available to \citet{wylie-de-boer;et-al_2012}.
-
-With the exception of J223811-104126, we believe our stellar parameters are largely in agreement with the exception of metallicity.
-The Fe\,I abundances differ significantly for the four stars in common: 0.01\,dex, $-$0.45\,dex, 0.33\,dex, $-$0.24\,dex.
-In order to investigate the source of these discrepancies, we repeated our analysis for the four common stars using the line list of \citet{wylie-de-boer;et-al_2012}.
-The results of this analysis is shown in Table \ref{tab:wylie-de-boer-analysis-comparison}.
-
-One Fe\,I line at 6420.060\,\AA{} was not detectable in any of our stars, even though the S/N at this point exceeds 120 in every observation.
-Additionally, we could not identify the line in the existing VALD database.
-
-% talk about stellar parameter differences
-
-% we find their metallicities
-
-Given the line list employed, the overall data quality and the lack of Fe\,I lines available for analysis, it appears the Aquarius stream stars have conspired to present a tight metallicity distribution function -- suggestive of a globular cluster origin.
-In contrast, our high-resolution analysis suggests a significantly broader metallicity distribution of $\langle$[Fe/H]$\rangle = X.XX \pm X.XX$ dex.
+Given the metallicity of these stars and the spectral coverage (4120 to 6920 {\AA}), it is somewhat surprising that there were not more unblended transitions available to \citet{wylie-de-boer;et-al_2012}.
+
+The line list employed in the \citet{wylie-de-boer;et-al_2012} study contained fewer lines, and employed different oscillator strengths than what we have used.
+The oscillator strengths in the \citet{wylie-de-boer;et-al_2012} study are astrophysical, and were derived from a reverse analysis using the \citet{hinkle;et-al_2003} solar atlas.
+Suspecting the metallicity discrepancy may be caused by the differing line lists, we have redone our analysis using the \citet{wylie-de-boer;et-al_2012} line list and their published stellar parameters.
+Indeed, we arrive at very similar metallicities to \citet{wylie-de-boer;et-al_2012}.
+Without using their published stellar parameters a priori, with a `blind' analysis using their line list we arrive at similar stellar parameters.
+However, we note that one Fe\,\textsc{I} transition at 6420.060\,\AA{} in their line list was not detected in any of our stars at the $3-\sigma$ level, even though the S/N at this point exceeds 120 per pixel element in every observation.
+Thus, for this comparative analysis a maximum of 13 Fe\,\textsc{I} and 3 Fe\,\textsc{II} lines were available to us.
+
+Given the line list employed in the \citet{wylie-de-boer;et-al_2012} study, the overall data quality and the lack of suitable iron lines available for analysis, it appears the Aquarius stream stars have conspired to present a tight metallicity distribution function of $\sigma(\mbox{Fe/H}) = 0.10$\,dex -- suggestive of a globular cluster origin.
+Our analysis of high-resolution spectra with high $S/N$ reveals a much broader metallicity distribution for the stream.
+With just five stars -- if we assume all our stars are members -- we find the stream metallicity varies from $\mbox{[Fe/H]} = -0.65$ to --1.60\,dex.
+Although this is a small sample, we find the calculated median abundance and standard deviation to be $\mbox{[Fe/H]} = X.XX \pm X.XX$\,dex, more in line with the \citet{williams;et-al_2011} chemistry.
 
@@
 
+% Globular clusters typically exhibit minimal chemical scatter because X. 
+% globular clusters vs dwarf spheroidals MDF
+
+% larger MDF than expected for globular clusters
+
+% globular clusters typically have a tight MDF -- explain why
+
+% dSph's show a wide MDF due to X
+
+% there are some exclusions to this rule, most notably omega cen
+
+% mdf of omega cen
+
+% based on dynamics, williams excluded all known globular clusters and dsph's with the exception of omega cen.
+
+% although the MDF appears not to be dissimilar from omega cen, we will later show based on the evidence thus far that the aquarius stream is not disrupted debris from omega cen
+%	+ because as well as having a tight [Fe/H], all well-studied globular clusters (including omega cen) exhibit noteable chemical patterns, which we do not find in these stars.
+
 \subsection{The Na-O Relationship}
@@
 
-Extensive studies looking at stars in globular clusters have revealed variations in light-element abundances, most notably an anti-correlation in sodium and oxygen content \citet[][and references therein]{norris;da-costa_1995,caretta;et-al_2008}.
-Between generations of stars within a globular cluster, the oxygen abundance is transformed into nitrogen, reducing the overall oxygen abundance.
+Extensive studies looking at stars in globular clusters have revealed variations in light-element abundances, most notably an anti-correlation in sodium and oxygen content \citet[][and references therein]{norris;da_costa_1995,carretta;et-al_2009_na_o}.
 This pattern has been repeatedly demonstrated in all well-studied globular clusters, although the strength of the anti-correlation varies between systems.
+Between generations of stars within a globular cluster, oxygen is converted into nitrogen, reducing the overall oxygen abundance.
 Even though oxygen undergoes internal mixing during its evolution along the giant branch, it is now well established that any observed abundance variations due to such mixing is limited to Li, C, and N.
@@
 % discuss three components
-\citet{Caretta;et-al_2009} defined three components of stars following this abundance pattern within a population: primordial, intermediate, and extreme.
+\citet{carretta;et-al_2009_na_o} defined three components of stars following this abundance pattern within a population: primordial, intermediate, and extreme components.
 The [Na/Fe] and [O/Fe] abundances for a given star defines which component it belongs to.
-Primordial (first-generation) stars are those with Na and O content similar to field stars of the same metallicity.
+Primordial (first-generation) stars are those with sodium and oxygen abundances which are similar to field stars of the same metallicity.
 For a well-studied system, stars with the lowest cluster [Na/Fe] abundances are characterised as primordial.
@@
 The intermediate population is sub-divided based on how much the O and Na abundances depart from the primordial population: stars with [O/Na]$ > -0.9$ dex are classified as belonging to an extreme component of this Na-O pattern because they differ greatly from the primordial cluster abundance.
-The extreme O-depletion component has only been observed in a few clusters (more massive ones preferentially), indicating an extended star-formation history in more massive clusters.
+The extreme O-depletion component has only been observed in a few clusters (preferentially more massive clusters with extended horizontal branches), indicating an long-lasting star-formation history in more massive clusters.
 
@@
 However, it is clear that this trend has been well-demonstrated empirically.
-Several hypotheses have been proposed in order to account for oxygen depletion between stellar generations, including massive binaries \citep{De_Mink;et-al_2009} or fast-rotating massive stars \citep{decressin;et-al_2007}.
+Several hypotheses have been proposed in order to account for oxygen depletion between stellar generations, including massive binaries \citep{de_mink;et-al_2009} or fast-rotating massive stars \citep{decressin;et-al_2007}.
 While the exact procedure is yet to be fully characterized, we can describe the abundance variation as a simple oxygen depletion (or dilution) model with time.
@@
 It is clear that careful consideration must be given inferring star-formation histories from observed stellar abundances.
-In addition to the normal care afforded for measuring elemental abundances from high-resolution spectroscopic data, attention must be given to telluric absorption, Ni contamination, and NLTE corrections when deriving oxygen abundances.
+In addition to the normal care afforded for measuring elemental abundances from high-resolution spectroscopic data, attention must be given to telluric absorption, contamination from nickel blends, and NLTE corrections when deriving oxygen abundances.
 Furthermore, when characterising the oxygen depletion rate -- and hence the strength of the Na-O anti-correlation in a given cluster -- it is vital to obtain observations for stars belonging to all three components (where possible).
@@
 \citet{wylie-de-boer;et-al_2012} measured [Na/Fe] and [O/Fe] abundances for four of their six Aquarius stream members.
-This research has four stars in common with the \citet{wylie-de-boer;et-al_2012} study, but Na and O measurements exist for only three stars that are in both samples.
-We have measurements for all of our stars, including J223811-104126, for which we ascertained an upper limit from the [O \textsc{I}] lines of [O/Fe] $< 0.5$ dex, and a NLTE-corrected abundance of $\mbox{[O/Fe]} = 0.14$ from the O \textsc{I} triplet lines.
+This research has four stars in common with the \citet{wylie-de-boer;et-al_2012} study, but sodium and oxygen measurements exist for only three stars intersecting both samples.
+We have measurements for all of our stars, including J223811-104126, for which we ascertained an upper limit from the [O \textsc{I}] lines of [O/Fe] $< 0.5$ dex, and a corrected abundance of $\mbox{[O/Fe]} = 0.14$ from the O \textsc{I} triplet lines.
 
@@
 
-The \citet{wylie-de-boer;et-al_2012} measurements indicate two stars with solar-type levels of Na -- identical to field star Na abundances for their metallicity -- and two stars with super-solar sodium content.
-The \citet{wylie-de-boer;et-al_2012} abundances themselves do not demonstrate a classical Na-O anti-correlation.
-In fact, they have a slight positive relationship: their Na-enhanced stars show an increased oxygen content, contrary to an expected oxygen depletion between generations with.
-
+The \citet{wylie-de-boer;et-al_2012} measurements indicate two stars with solar levels of Na -- identical to field star Na abundances for their metallicity -- and two stars with super-solar sodium content.
+The sodium-enhanced stars exhibit no depletion of oxygen; the abundances do not demonstrate a classical Na-O anti-correlation.
+In fact, they have a slight positive relationship: their Na-enhanced stars show an increased oxygen content, contrary to an expected oxygen depletion between stellar generations within a globular cluster.
 This trend is drawn from a sample of only four stars -- the same as this study if our upper limit for J223811-104126 is excluded.
@@
 
- The conditions required for these reactions are significantly higher than the CNO and Ne-Na cycle: temperatures of 70 MK are required for the Mg-Al channel instead of just 25 MK for the CNO/Ne-Na cycles \citet{Charbonnel_Prantzos_2006}.
+ The conditions required for these reactions are significantly higher than the CNO and Ne-Na cycle: temperatures of 70 MK are required for the Mg-Al channel instead of just 25 MK for the CNO/Ne-Na cycles \citet{charbonnel;prantzos_2006}.
 
@@
 Detailed chemical studies of nearby disk stars have noted a correlation with [Na/Fe] and [Ni/Fe].
-This relationship was first hinted in \citet{Nissen;Schuster_1997}, where they found eight stars that were underabundant in [$\alpha$/Fe], [Na/Fe] and [Ni/Fe].
+This relationship was first hinted in \citet{nissen;schuster_1997}, where they found eight stars that were underabundant in [$\alpha$/Fe], [Na/Fe] and [Ni/Fe].
 Interestingly, the authors noted that stars at larger galactocentric radii were most deficient in these elements.
-\citet{fulbright;et-al_2000} saw a similar signature: stars with low [Na/Fe] were only found at large ($R_\odot > 20$\,kpc) distances.
-\citet{Nissen;Schuster_1997} proposed that as the outer halo is thought to have been built up through the accretion of dSph satellites, then the Na-Ni pattern may be a chemical indicator of merger history in the galaxy.
-
-With additional data from \citet{Nissen;Schuster_2010}, the Na-Ni relationship was found to be slightly steeper than originally proposed.
+\citet{fulbright_2000} saw a similar signature: stars with low [Na/Fe] were only found at large ($R_\odot > 20$\,kpc) distances.
+\citet{nissen;schuster_1997} proposed that as the outer halo is thought to have been built up through the accretion of dSph satellites, then the Na-Ni pattern may be a chemical indicator of merger history in the galaxy.
+
+With additional data from \citet{nissen;schuster_2011}, the Na-Ni relationship was found to be slightly steeper than originally proposed.
 The pattern exists only for metal-rich stars $-1.5 < \mbox{[Fe/H]} < -0.5$ dex, and is not seen in metal-poor dSph stars, providing a potentially useful indicator for investigating chemical evolution.
@@
 As previously discussed, the total Na abundance is controlled by the neutron excess, which limits the production of $^{58}$Ni during SN II events.
-When the supernova occurs, the core photodissociates into neutrons and protons, allowing the temporary creation of $^{56}$Ni before it decays to $^{56}$Fe.
+When the inevitable supernova begins, the core photodissociates into neutrons and protons, allowing the temporary creation of $^{56}$Ni before it decays to $^{56}$Fe.
 A limited amount of $^{54}$Fe is also formed, which is the main source of production for the stable $^{58}$Ni isotope through $\alpha$-capture.
@@
 
-As \citet{Venn;et-al_2004} point out, this pattern can be altered from contributions by type Ia supernova.
-
-% as Venn points out, this trend can be altered based on SN Ia contributions
-Nickel is
-produced without Na in the standard model of SNe Ia, in which
-a CO white dwarf tips over the Chandrasekhar limit and the
-C-burning region is completely photodissociated (Tsujimoto
-et al. 1995). This would ßatten the Na-Ni correlation. However, the route to SNe Ia is convoluted and doubtless involves
-rare binary star interactions (e.g., RegIs et al. 2003). It is quite
-uncertain what the Na yields from these might be; e.g., if a CO
-white dwarf accretes a He white dwarf, perhaps the build up of
-He on the surface may undergo C burning and release Na
-before the star photodissociates to form Ni in the SN event
-% in general, we can expect high Na, Ni abundances in stars that have an long contribution of previous massive stars
-% thus, the we can infer the star formation history
-
-% dsPh's have a very different star formation history and chemical signature to typical halo stars of the same metallicity
-% the same is true for globular clusters, given the chemical patterns already discussed
-% however disk stars and globular clusters are indiscernible in the Na/Ni plane: they both show an extended contribution of massive stars with respect to dSph's (Figure X).
-
-%
+%As \citet{Venn;et-al_2004} point out, this pattern can be altered from contributions by type Ia supernova.
+
+% [Na/Fe], [Ni/Fe]
+\begin{figure}[h]
+	\includegraphics[width=\columnwidth]{./figures/aquarius-na-ni.pdf}
+	\caption{A plot showing [Na/Fe] and [Ni/Fe] for all Aquarius stream stars.}
+	\label{fig:na-ni}
+\end{figure}
+
+Stars originating in dwarf spheroidal galaxies and globular clusters have very different star formation histories.
+Consequently they exhibit chemical patterns that reflect their nucleosynthetic antiquity.
+Dwarf spheroidal stars do not demonstrate enhanced sodium or nickel, as there has been a relatively negligible linage of massive stars undergoing supernova.
+In contrast, globular cluster stars do have elevated Na, Ni contributions.
+This sharp contrast between dwarf spheroidal and globular cluster star chemistry is illustrated in Figure \ref{fig:na-ni}.
+Given the extended star formation within the Milky Way disk, globular cluster stars and disk stars are indiscernible in the Na/Ni plane: they both show an extended contribution of massive stars.
+The most that can be inferred from the Na, Ni abundances of Aquarius stream stars is that their star formation history is less like a dwarf spheroidal environment, and more representative of an environment more like a globular cluster or the MW disk.
 
 \subsection{Possible Progenitors}
+
+Since the Aquarius stream is kinematically coherent, the default assumption is that the system has been accreted.
+% their chemistry is indicative of not belonging to a dwarf spheroidal
+
+% open cluster
 
@@
 
-% [Na/Fe], [Ni/Fe]
-\begin{figure}[h]
-	\includegraphics[width=\columnwidth]{./figures/aquarius-na-ni.pdf}
-	\caption{A plot showing [Na/Fe] and [Ni/Fe] for all Aquarius stream stars.}
-	\label{fig:na-ni}
-\end{figure}
-
 % [O/Fe], [Na/Fe]

### 2012-12-28 2012-aqs/figures/plot-smh-norris.py
Added units to mean EW in norris plot

@@ -55,7 +55,8 @@ ax2.get_yticklabels()[-1].set_visible(False)
 ax1.get_yticklabels()[0].set_visible(False)
 ax1.get_yticklabels()[-1].set_visible(False)
 
-ax1.text(5, 10, '$\langle{}\Delta{}W_\lambda\\rangle{}\,=\,-0.64\,\pm\,2.78$', color='k', verticalalignment='center')
+ax1.text(5, 10, '$\langle{}\Delta{}W_\lambda\\rangle{}\,=\,-0.64\,\pm\,2.78\,$m${\AA}$', color='k', verticalalignment='center')
+
 ax2.text(5, 150, "$a_0\,=\,%1.2f$\n$a_1\,=\,%1.2f$" % (c, m, ), verticalalignment='top')
 
 ax1.set_title('%i lines in HD 140283' % (len(smh_ew), ))

### 2012-12-29 2012-aqs/draft-aqs.tex
Updated velocities + some text

@@
 
-C2225316-14437	& 22:25:31.7 & $-$14:54:39.6	& 2011-07-30	& 1.033 & \dots & \dots & \dots & $-$169.0	& \dots & 0.7 \\
-C2306265-085103	& 23:06:26.6 & $-$08:51:04.8	& 2011-07-30	& 1.096 & \dots & \dots & \dots & $-$239.3	& \dots & 0.6 \\
+C2225316-14437	& 22:25:31.7 & $-$14:54:39.6	& 2011-07-30	& 1.033 & \dots & \dots & 135	 & --168.6	& --156.4 & 0.1 \\
+C2306265-085103	& 23:06:26.6 & $-$08:51:04.8	& 2011-07-30	& 1.096 & \dots & \dots & 100	 & --240.4	& --221.1 & 0.1 \\
 HD41667			& 06:05:03.7 & $-$32:59:36.8	& 2011-03-13	& 1.005	& \dots & \dots & \dots & 314.4	& \dots & 0.8 \\
 HD142948		& 16:00:01.6 & $-$53:51:04.1	& 2011-03-14	& 1.107	& \dots & \dots & \dots & 6.8		& \dots & 0.4 \\
-J221821-183424	& 22:18:21.2	& $-$18:34:28.3	& 2011-07-30	& 1.026	& \dots & \dots & \dots & $-$170.5	& \dots & 0.5 \\
-J223504-152834	& 22:35:04.5	& $-$15:28:34.9	& 2011-07-30	& 1.047	& \dots & \dots & \dots & $-$180.9	& \dots & 0.7 \\
-J223811-104126	& 22:38:11.6	& $-$10:41:29.4	& 2011-07-30	& 1.218	& \dots & \dots & \dots & $-$248.4	& \dots & 0.7
+J221821-183424	& 22:18:21.2 & $-$18:34:28.3	& 2011-07-30	& 1.026	& \dots & \dots & 115 	 & --170.2	& --159.5 & 0.1 \\
+J223504-152834	& 22:35:04.5 & $-$15:28:34.9	& 2011-07-30	& 1.047	& \dots & \dots & 135	 & --179.0	& --169.7 & 0.1 \\
+J223811-104126	& 22:38:11.6 & $-$10:41:29.4	& 2011-07-30	& 1.218	& \dots & \dots & 115	 & --250.1	& --235.7 & 0.1
+
+% V corrections (already applied the first number of each row)
+% J221821     	:   0.30, 0.25 +/- 1.25 (MEK has -154.1, wdb ) -- diff: 5.4  (positive == higher)
+% C2225316		:	0.43, 0.42 +/- 1.13 (MEK has -155.7) -- diff: -0.4 (hers is lower)
+% C2306265		: 	1.14, 1.19 +/- 1.16 (MEK has -221.8) -- diff: -0.7 (hers is lower)
+% J223504		:	-1.87, -1.89 +/- 1.45 (MEK has -166.9) -- diff: 2.8 (positive == higher)
+% J223811		:	1.69, 1.61	+/- 1.47 (MEK has --230.1) -- diff 5.6 (positive == higher)
 
@@
 The radial velocities published in Table \ref{tab:observations} are the final values from this two-step method.
-Heliocentric velocities agree excellently (within X\,km s$^{-1}$) with previously reported literature values \citep{williams;et-al_2011,wylie-de-boer;et-al_2012}, demonstrating the accuracy of the radial velocities published by the RAVE survey.
+Heliocentric velocities agree quite well with the \citet{williams;et-al_2011} published values: $\langle\Delta{V_{hel}}\rangle = 2.8$\,km\,s$^{-1}$, demonstrating the accuracy of the velocities published by the RAVE survey.
 
@@
 Line abundances that were unusually deviant ($3\sigma$) from the mean were removed.
-The largest number of outlier measurements removed for any observation was N for X.
+The largest number of outlier measurements removed for any observation was nine for C222531-144370.
 
@@
 
+% [alpha/Fe]
+\begin{figure}[h]
+	\includegraphics[width=\columnwidth]{./figures/aquarius-alpha-fe.pdf}
+	\caption{A plot showing $[\alpha/\mbox{Fe}]$ for all Aquarius stream stars.}
+	\label{fig:alpha-fe}
+\end{figure}
+
 % calcium measurements + silicon measurements
@@
 If we exclude the most prominent outlier, then the mean abundance drops only slightly to $\mbox{[Si/Fe]} = 0.70 \pm 0.04$\,dex.
-The lowest silicon line abundance for C2225316-14437 is $\mbox{[Si/Fe]} = 0.57$\,dex, still significantly higher than the final measurements for any other star.
+The lowest silicon line abundance for C2225316-14437 is $\mbox{[Si/Fe]} = 0.57$\,dex, still significantly higher than the averaged abundance for any other star.
 
@@
 
-\subsubsection{Iron-peak Elements}
+\subsubsection{Aluminium}
+There are six aluminium transition lines available in our optical spectra.
+The strongest of these lines occur at 3944 and 3961\,{\AA}, and are visible in all of our stars.
+However, this is a particularly crowded spectral region: these lines fall between the strong Ca H and K lines, with the 3961\,{\AA} transition clearly in the wing of the Ca H line.
+This makes the continuum determination and subsequent Al measurement non-trivial, especially given the metallicity of our stars.
+Instead, we have measured Al abundances from the other transitions available in our spectra: the Al \textsc{I} lines at 6696, 6698, 7835 and 7836\,{\AA}.
+Although these lines are weaker than the bluer Al \textsc{I} lines, their surrounding regions are uncrowded.
+
+Generally the four Al \textsc{i} lines are in reasonable agreement with one another, yielding random scatter of less than 0.05\,dex.
+
+These lines were not always detected in our spectra.
+With decreasing metallicity and increasing temperature the strength of the lines is noticeably weakened, below a 3-$\sigma$ detection limit.
+For our most metal-poor star, J221821, only one Al \textsc{i} line was detectable, and we have adopted an uncertainty of 0.05\,dex.
+
+% there are a few lines available in the spectrum
+% incl. blue ones
+% the blue ones remain strong even in extremely metal-poor stars
+% in metal rich stars the region is too crowded and the continuum (and abundance) is non-trivial to determine
+% in lieu of using these lines, we have used 4 other lines at X
+% for our most metal-poor star, J221X, only one of these lines was detectable
+
+\subsubsection{Iron-peak Elements (Sc, V, Cr and Mn)}
 Scantium, Vanadium, Chromium and Manganese. All very vanilla, exhibiting a downward trend with [Fe/H].
@@
 Only one of our standard stars, HD 44007, has published [Ba/Fe] abundances from high-resolution spectra.
-We find HD 44007 to have $\mbox{[Ba/Fe]} = -0.05 \pm 0.04$, which is in rough accordance with existing published measurements from \citet{fulbright_2000} and \citet{burris;et-al_2000} of $-0.27$ and 0.05 dex, respectively.
+We find HD 44007 to have $\mbox{[Ba/Fe]} = -0.05 \pm 0.04$, which is in between existing published measurements from \citet{fulbright_2000} and \citet{burris;et-al_2000} of $-0.27$ and 0.05 dex, respectively.
 
@@
 
+% [O/Fe], [Na/Fe]
+\begin{figure}[h]
+	\includegraphics[width=\columnwidth]{./figures/aquarius-o-na.pdf}
+	\caption{A plot showing [O/Fe] and [Na/Fe] for all Aquarius stream stars.}
+	\label{fig:o-na}
+\end{figure}
+
 \subsection{The Al-Mg Relationship}
@@
  The conditions required for these reactions are significantly higher than the CNO and Ne-Na cycle: temperatures of 70 MK are required for the Mg-Al channel instead of just 25 MK for the CNO/Ne-Na cycles \citet{charbonnel;prantzos_2006}.
+
+% Mg-Al
+\begin{figure}[h]
+	\includegraphics[width=\columnwidth]{./figures/aquarius-mg-al.pdf}
+	\caption{A plot showing [Mg/Al] for all Aquarius stream stars.}
+	\label{fig:mg-al}
+\end{figure}
 
@@
 	\includegraphics[width=\columnwidth]{./figures/aquarius-na-ni.pdf}
-	\caption{A plot showing [Na/Fe] and [Ni/Fe] for all Aquarius stream stars.}
+	\caption{A plot showing [Na/Fe] and [Ni/Fe] for all Aquarius stream stars. TODO add dwarf/GC/disk stars on here.}
 	\label{fig:na-ni}
@@
 Since the Aquarius stream is kinematically coherent, the default assumption is that the system has been accreted.
+
 % their chemistry is indicative of not belonging to a dwarf spheroidal
@@
 
-% [alpha/Fe]
-\begin{figure}[h]
-	\includegraphics[width=\columnwidth]{./figures/aquarius-alpha-fe.pdf}
-	\caption{A plot showing $[\alpha/\mbox{Fe}]$ for all Aquarius stream stars.}
-	\label{fig:alpha-fe}
-\end{figure}
-
-% Mg-Al
-\begin{figure}[h]
-	\includegraphics[width=\columnwidth]{./figures/aquarius-mg-al.pdf}
-	\caption{A plot showing [Mg/Al] for all Aquarius stream stars.}
-	\label{fig:mg-al}
-\end{figure}
-
 % [Na/Fe], [Cr/Fe], [Ni/Fe]
@@
 
-% [O/Fe], [Na/Fe]
-\begin{figure}[h]
-	\includegraphics[width=\columnwidth]{./figures/aquarius-o-na.pdf}
-	\caption{A plot showing [O/Fe] and [Na/Fe] for all Aquarius stream stars.}
-	\label{fig:o-na}
-\end{figure}
-
 % Toombre

### 2013-01-01 2012-aqs/draft-aqs.tex
Fixed changes made on paper

@@
 \author{Andrew R. Casey\altaffilmark{2,3} and distinguished collaborators}
-\altaffiltext{1}{This paper includes data gathered with the 6.5 meter Magellan Telescopes located at Las Campanas Observa- tory, Chile.}
+\altaffiltext{1}{This paper includes data gathered with the 6.5 meter Magellan Telescopes located at Las Campanas Observatory, Chile.}
 \altaffiltext{2}{Research School of Astronomy \& Astrophysics, Australian National University, Mount Stromlo Observatory, via Cotter Rd, Weston, ACT 2611, Australia; acasey@mso.anu.edu.au}
@@
 We present a detailed dynamic and chemical analysis of 5 Aquarius stream giants observed using the MIKE spectrograph on the Magellan Clay Telescope.
+Assuming all candidates are stream members, our data indicate the Aquarius stream has a large metallicity dispersion.
+We find no Na-O anti-correlation, and no chemical evidence that the stream is a result of a disrupted globular cluster, contrary to \citet{wylie-de-boer;et-al_2012}.
+
 \end{abstract}
@@
 \section{Introduction}
-
-Stellar streams arise from tidal effects as satellite systems infall onto the Milky Way.
+Galaxies are formed hierarchically through chaotic mergers of smaller systems.
+The Milky Way is no exception.
+In our own stellar  halo, we see ongoing evidence of these accretion events.
+As accreting satellites infall onto the galaxy, tidal forces disrupt the dwarf, hurtling stars in leading and trailing streams.
 The phase space information of stars within such streams are sensitive to the galactic potential.
-Therefore, they can collectively constrain the fraction and distribution of accreted matter in the stellar halo, the sub-halo mass function, as well as the shape and extent of dark matter in the Milky Way.
-Moreover, individual elemental abundances for stars within these streams help unravel the chemical evolution of the Galaxy.
+They can collectively constrain the fraction and distribution of accreted matter in the stellar halo, the sub-halo mass function, as well as the shape and extent of dark matter in the Milky Way.
+Moreover, individual chemical abundances can constrain the  precise nucleosynthesis sites where elements are forged, and can collectively trace the chemical evolution of the galaxy.
+
 % Consider adding a final sentence about the amount of work that has gone into stellar streaams
 
-Wide-field surveys have proved excellent sources for finding galactic substructures, including stellar streams.
+Wide-field surveys have proved excellent sources for finding stellar streams.
 Dozens of streams reaching out up to 150\,kpc in the halo have been identified through photometric selections and matched-filtering techniques \citep{belokurov;et-al_2007,koposov_SG1}.
-However, as \citet{helmi;white_1999} point out, these approaches are only successful for identifying substructures that are sufficiently distant from the solar neighbourhood.
-A nearby stream within $\sim{}$10\,kpc will not appear as an on-sky over-density, as the stars would be sparsely positioned across the sky.
-Such substructures would only be detectable with kinematic, or perhaps precise chemical information.
+Indeed, it is clear that a large fraction of the stellar halo has been built up by accretion.
+However, as \citet{helmi;white_1999} point out, these observing strategies are only successful for identifying streams that are sufficiently distant from the solar neighbourhood.
+A nearby stream, within $\sim{}$10\,kpc, will not appear as an on-sky over-density, as the stars would be sparsely positioned across the sky.
+Such substructures would only be detectable by their kinematics, or perhaps precise chemical abundances through a `chemical tagging' approach (e.g.
+see \citet{freeman;bland-hawthorn_2003}).
 
@@
 In an attempt to remain kinematically unbiased, RAVE candidates were selected based only on their apparent magnitude.
-With the exception of bulge stars where some photometric cuts were employed, all stars between 9 $<$ I $<$ 13 were observed.
+With the exception of bulge stars, where some photometric cuts were employed, all stars between 9 $<$ I $<$ 13 were observed.
 Almost all of these candidates have published radial velocity measurements \citep{steinmetz;et-al_2006}, and for a subset of stars with sufficient S/N, estimates of stellar parameters have been derived using a $\chi^2$ minimization technique \citep{zwitter;et-al_2008, siebert;et-al_2011}.
@@
 Using these data, \citet{williams;et-al_2011} identified a co-moving group of nearby ($0.5 \lesssim d \lesssim 10$\,kpc) stars in the vicinity of the Aquarius constellation $(l, b) = (60\,^\circ, -55\,^\circ)$.
-The artefact is most apparent when examining kinematics against galactic latitude for stars within $-70\,^\circ < b < -50\,^\circ$.
-\citet{williams;et-al_2011} employed a selection criteria of $-250 < V_{HEL} < -150$\,km s$^{-1}$, $30\,^\circ < l < 75\,^\circ, J > 10.3$ to maximize the contrast between the stream and halo background, identifying 15 stream candidates in the process.
-The average heliocentric radial velocity of these members was found to be $V_{HEL} = -199$\,km s$^{-1}$, with a dispersion of 27\,km s$^{-1}$.
+Thus, the co-moving group was named the Aquarius stream.
+The stream is most apparent when examining velocities against galactic latitude for stars within $-70\,^\circ < b < -50\,^\circ$.
+\citet{williams;et-al_2011} employed a selection criteria of $-250 < V_{HEL} < -150$\,km s$^{-1}$, $30\,^\circ < l < 75\,^\circ$ and $J > 10.3$ to maximize the contrast between the stream and background, identifying 15 candidates in the process.
+The average heliocentric velocity of these members was found to be $V_{HEL} = -199$\,km s$^{-1}$, with a dispersion of 27\,km s$^{-1}$.
 The radial velocities outputted by the RAVE survey are described to be $\sim2$\,km s$^{-1}$, so the wide kinematic distribution appears to be real.
 
-%When compared to other streams identified in the halo, this is an unusually wide kinematic dispersion.
-Streams are generally considered to be kinematically cold, with dispersions of $\sigma_v < 8$\,km s$^{-1}$.
-
 % QUANTIFYING THE STREAM DETECTION
-Upon examining the galactic longitude and radial velocities of Aquarius stars, the stream appears quite distinct from the halo.
-In order to quantify the statistical likelihood that the Aquarius stream is a true substructure, \citet{williams;et-al_2011} compared the number of observed RAVE stars within $-70\,^\circ < b < -50\,^\circ$ against the Galaxia \citep{sharma;et-al_2011} and Besan\c{c}on \citep{robin;et-al_2003} galaxy models.
-Predicted particles and observed stars between $-70\,^\circ < b < -50\,^\circ$ were binned in $\Delta{l} \times \Delta{V_{hel}}$ using varying grid cell sizes between $25-70\,^\circ$ and 20-100\,km s$^{-1}$ respectively.
-The significance of the stream is calculated for each cell.
+Upon examining the galactic longitude and velocities of Aquarius stars, the stream appears quite distinct from the halo.
+In order to quantify the statistical likelihood that the Aquarius stream is truly distinct from the halo, \citet{williams;et-al_2011} compared the number of observed RAVE stars within $-70\,^\circ < b < -50\,^\circ$ against the Galaxia \citep{sharma;et-al_2011} and Besan\c{c}on \citep{robin;et-al_2003} galaxy simulations.
+The predicted particles in each model between $-70\,^\circ < b < -50\,^\circ$ were binned in $\Delta{l} \times \Delta{V_{hel}}$ using varying grid cell sizes between $25-70\,^\circ$ and 20-100\,km s$^{-1}$ respectively.
+The RAVE sample was binned in the same way, and the statistical significance of the over-density is calculated for each cell.
 \citet{williams;et-al_2011} found the stream to be statistically significant ($>$4-$\sigma$) in 96\% of the grid cell sizes employed for the Besan\c{c}on model.
-By sampling the Galaxia model multiple times with varying extinction models, a similar result was found: between $75\pm15$\,\% to $80\pm18$\,\% of grid cells showed the Aquarius stream to significant at the 4-$\sigma$ level.
-Given the high-latitude of the stream and proximity of the stream, it is not surprising that dust had a negligible effect on the overall significance.
+By sampling the Galaxia model multiple times with varying extinction rates, a similar result was found: between $75\pm15$\,\% to $80\pm18$\,\% of grid cells showed the Aquarius stream to significant at the 4-$\sigma$ level or higher.
+Given the high-latitude and proximity of the stream, it is not surprising that dust had a negligible effect on the statistical significance.
 \citet{williams;et-al_2011} concluded that the over-density in $l, V_{hel}$ is a true substructure, and neither the choice of galaxy model, cell size, nor the extinction model made any real difference to the stream detection significance.
@@
 Indeed, the Aquarius stream stars do not lie far from the orbital plane of Sagittarius and the metallicities reported by \citet{williams;et-al_2011} are not dissimilar from the Sagittarius stream.
-However, \citet{williams;et-al_2011} found the Aquarius $XYZ$ positions and kinematics (specifically $V_{Z}$ and $V_\phi$) are quite distinct from Sagittarius.
+However, \citet{williams;et-al_2011} found the Aquarius space positions and kinematics (specifically $V_{Z}$ and $V_\phi$) are quite distinct from Sagittarius.
 Based on the phase space information available, \citet{williams;et-al_2011} concluded that the newly discovered stream could not be positively associated with the Monoceros stream, Hercules-Aquila cloud, or either the Canis Major or Virgo over-densities.
 
-The Aquarius stream has a metallicity of $\mbox{[Fe/H]} \sim -1.0$, slightly more metal-rich than halo stars at the same distance.
+The Aquarius stream has a metallicity of $\mbox{[Fe/H]} \sim -1.0$ \citep{williams;et-al_2011}, slightly more metal-rich than halo stars at the same distance.
 The dispersion in the stream's metallicity has yet to be fully characterised.
@@
 Of the 12 Aquarius stars in the \citet{williams;et-al_2011} discovery sample with stellar parameters, the metallicity range is wide: between --2.02 and --0.33 dex.
-Spectroscopic observations of higher resolution and S/N are necessary to accurately determine the metallicity distribution function.
-To this end, \citet{wylie-de-boer;et-al_2012} obtained high-resolution ($R = 25,000$) spectra with modest S/N ($\sim$30 pixel$^{-1}$) for six Aquarius stream giants.
-Their data indicated a much narrower metallicity distribution: $\mbox{[Fe/H]} = -1.09 \pm 0.10$\,dex extending between $\mbox{[Fe/H]} = -1.25$ to $-0.98$\,dex; the level of negligible intrinsic chemical scatter which is typically observed in globular clusters.
+Spectroscopic observations of high resolution with high signal-to-noise ($S/N$) are necessary to accurately determine the metallicity distribution.
+
+To this end, \citet{wylie-de-boer;et-al_2012} obtained high-resolution ($R = 25,000$) spectra with modest $S/N$ ($\sim$30 pixel$^{-1}$) for six Aquarius stream stars.
+Their data indicate a very narrow metallicity distribution: $\mbox{[Fe/H]} = -1.09 \pm 0.10$\,dex extending between $\mbox{[Fe/H]} = -1.25$ to $-0.98$\,dex.
 The largest [Fe/H] discrepancy between the two studies was $\Delta\mbox{[Fe/H]} = -0.66$\,dex for the most metal-rich star in the \citet{williams;et-al_2011} sample.
 The most metal-poor star in the \citet{williams;et-al_2011} study was not observed by \citet{wylie-de-boer;et-al_2012}.
-
-%The chemical coherence in the \citet{wylie-de-boer;et-al_2012} study is most intriguing.
+The negligible level of chemical scatter observed in the \citet{wylie-de-boer;et-al_2012} sample is typical of what is found in globular or open clusters.
 
 In addition to ascertaining stellar parameters, \citet{wylie-de-boer;et-al_2012} measured light element abundances for the Aquarius stream stars -- the only study to do so until now.
-Primarily they focussed on Na, O, Ni, Mg, and Al abundances.
+Their study primarily focussed on light elemental abundances: Na, O, Ni, Mg, and Al.
 Chemical patterns in these light elements arise as natural consequences of nucleosynthetic processes in massive stars.
-Most notably, an anti-correlation in sodium and oxygen abundance has been identified in all well-studied globular clusters to date.
+Thus, by observing the abundances of light elements in stars that formed together, we can infer the star-formation history and environment.
+More specifically, an anti-correlation in sodium and oxygen abundance has been identified in all well-studied globular clusters to date.
 Originally this was thought to arise from internal mixing along the giant branch.
@@
 It is well known now that photospheric abundance variations resulting from internal mixing are limited to C, N and Li.
-The Na-O pattern provides the best evidence that stars have formed in a globular cluster environment and that their chemical enrichment history has been dominated by Sn II events.
-From high-resolution spectroscopy of five stars in Aquarius, four of which had Na, O measurements, \citet{wylie-de-boer;et-al_2012} found two stars with super-solar sodium; slightly higher [Na/Fe] ratios for halo stars of the same metallicity.
-No strong oxygen depletion was evident in their stars.
-
-There are other abundances patterns that allow us to infer the chemical evolution of a given cluster.
-\citet{nissen;schuster_1997} first noted that only the distant solar neighbourhood stars were enriched in [Ni/Fe] and [Na/Fe].
+While the exact astrophysical mechanism for oxygen-depletion remains under debate, the chemical relationship is well-established empirically.
+The Na-O pattern provides the best chemical evidence that their chemical enrichment history has been dominated by Sn \textsc{ii} events and that those stars formed in a globular cluster-like environment.
+
+From high-resolution spectroscopy of five stars in Aquarius, four of which had Na and O measurements, \citet{wylie-de-boer;et-al_2012} found two stars with super-solar sodium; slightly higher [Na/Fe] ratios than halo stars of the same metallicity.
+However, no strong oxygen depletion was evident in their data.
+
+There are other chemical abundance patterns that allow us to infer the chemical evolution of a given cluster.
+\citet{nissen;schuster_1997} first noted that distant solar neighbourhood stars were enriched in [Ni/Fe] and [Na/Fe].
 \citet{fulbright_2000} came to a similar conclusion: only somewhat distant ($R_\odot > 20$\,kpc) stars are likely to be sodium deficient.
-If the stellar halo has been built up from the accretion of smaller dwarf satellites, \citet{nissen;schuster_1997} proposed that this chemical trend may be indicative of the halo merger history.
-Although there are some caveats to this chemical pattern (see \S\ref{sec:ni-na-relation}), at the very least the Na-Ni correlation may provide an indication whether stars became chemically enriched in dSph-like environments.
-\citet{wylie-de-boer;et-al_2012} found all their Aquarius stars to be enriched in both sodium and nickel; contrary to what would be expected if the stars originated from a disrupted dSph satellite.
+If the stellar halo has been built up from the accretion of smaller dwarf satellites, \citet{nissen;schuster_1997} proposed that this chemical trend may be indicative of the halo merger history since stars at larger $R_\odot$ are more likely to have been accreted rather than formed in-situ.
+\citet{wylie-de-boer;et-al_2012} found all the Aquarius stars in their sample to be enriched in both sodium and nickel; contrary to what would be expected if the stars originated from a disrupted dSph satellite.
+This provided an additional indication that the Aquarius stream stars originated in a globular cluster-like environment.
 
 Combined with the low level of chemical scatter present in their sample, these chemical indicators led \citet{wylie-de-boer;et-al_2012} to conclude that the Aquarius stream must be the result of a tidally disrupted globular cluster.
-\citet{williams;et-al_2011} had previously precluded this possibility after modelling an Aquarius-like progenitor infalling onto the Milky Way and comparing the predicted $l, b, V_{hel}$ with known, nearby globular clusters of similar metallicities.
-However, no known globular cluster could match their simulation.
-
-We seek to investigate the nature of the Aquarius stream, in particular the recent globular cluster origin claim made by \citet{wylie-de-boer;et-al_2012}.
-We present a detailed analysis for five confirmed Aquarius stream members from high-resolution, high S/N observations taken using the Magellan Inamori Kyocera Echelle spectrograph \citep{bernstein;et-al_2003} on the Magellan Clay telescope.
-Our analysis includes determining the galactic dynamics and orbital paths for the Aquarius stream, and measuring precise chemical abundances.
+\citet{williams;et-al_2011} had previously precluded this possibility with any known globular clusters after modelling an Aquarius-like progenitor infalling onto the Milky Way and comparing the predicted $l, b, V_{hel}$ with known, nearby globular clusters of similar metallicities.
+No known globular cluster could match their simulation.
+
+We seek to investigate the nature of the Aquarius stream, specifically the recent globular cluster origin claim made by \citet{wylie-de-boer;et-al_2012}.
+We present a detailed analysis for five  Aquarius stream members from high-resolution, high $S/N$ observations taken using the Magellan Inamori Kyocera Echelle spectrograph \citep{bernstein;et-al_2003} on the Magellan Clay telescope.
 Details of the observations and data reduction are outlined in the following section.
-The data analysis is chronicalled in \S\ref{sec:analysis} and a detailed discussion of these results resides in \S\ref{sec:discussion}.
-In \S\ref{sec:conclusion} we present our conclusions and critical interpretations.
-
-\clearpage
-\section{Observations \& Data Reduction}
-
-The most comprehensive sample of Aquarius stream stars is presented in the discovery paper of \citet{williams;et-al_2011}.
-Our sample includes five stars: four common to the \citet{wylie-de-boer;et-al_2012} study, and an additional star from the original \citet{williams;et-al_2011} sample.
-The additional star, J2306265-085103, had insufficient S/N in the RAVE sample for stellar parameters to be accurately determined.
-Program stars were observed in July 2011 in good seeing at high airmass (Table \ref{tab:observations}), and X standard stars were observed as part of a separate program in March 2011.
-All observations were taken using the 1.0'' slit, providing a spectral resolution of $R = 28,000$.
-The exposure times for our program stars varied per star from X-Y seconds to ensure a Signal-to-Noise ratio (S/N) in excess of 100 per pixel element at 600 nm.
-
-% what spectral resolution in the blue, what resolution in the red
-
-Calibration frames were taken at the start of each night, including twenty flat-field frames (10 quartz, 10 milky) and 10 Th-Ar arc lamp exposures for wavelength calibration.
-The data were reduced using the CarPy pipeline\footnote{http://code.obs.carnegiescience.edu/mike}.
-One of our standard stars, HD 41667, was also reduced using standard extraction and calibration methods in \textsc{iraf}.
-The resultant spectra from both reduction workflows were compared for residual fringing, S/N, and wavelength calibration.
-No noteworthy differences were present, and the CarPy pipeline was utilized for the remainder of our reductions.
-Each reduced echelle order was carefully normalised using a third order spline.
-Normalised orders  for a given star were stitched together to provide a single one-dimensional spectrum from 3800-9400\,\AA{}.
-
-The white dwarf HR 6141 was observed on X with a S/N of 400 pixel$^{-1}$ to account for telluric absorption.
-The S/N for HR 6141 exceeds the S/N in any of our program stars.
-Although the atmospheric conditions are certain to change throughout the night and between observing runs, we are primarily using this spectra to identify lines that are affected by telluric absorption.
-Critical transitions necessary for abundance analyses that are affected by the earth's atmosphere are later corrected for telluric absorption (see \S\ref{sec:telluric-absorption}), but great attention is paid to telluric band-heads at X and X such that we are not over- or under-correcting the atmospheric absorption.
+The data analysis is chronicalled in Section \ref{sec:analysis} and a detailed discussion of these results resides in Section \ref{sec:discussion}.
+In Section \ref{sec:conclusion} we present our conclusions and critical interpretations.
 
@@
 
+\section{Observations \& Data Reduction}
+
+The most complete sample of Aquarius stream stars is presented in the discovery paper of \citet{williams;et-al_2011}.
+Our sample includes five stars: four common to the \citet{wylie-de-boer;et-al_2012} study, and an additional star from the original \citet{williams;et-al_2011} sample.
+The additional candidate, J2306265-085103, was observed by the RAVE survey but had a $S/N$ ratio too low for stellar parameters to be accurately determined.
+All program stars were observed in July 2011 in good seeing at low airmass (Table \ref{tab:observations}), and X additional standard stars were observed in March 2011.
+All observations were taken using a 1.0'' slit, providing a spectral resolution of $R = 28,000$ in the blue and $R = XX,XXX$ in the red arm.
+The total exposure times for our program stars varied per star from X-Y seconds to ensure a Signal-to-Noise ratio (S/N) in excess of 100 per pixel element at 600 nm.
+
+% what spectral resolution in the blue, what resolution in the red
+
+Calibration frames were taken at the start of each night, including twenty flat-field frames (10 quartz, 10 milky) and 10 Th-Ar arc lamp exposures for wavelength calibration.
+The data were reduced using the CarPy pipeline\footnote{http://code.obs.carnegiescience.edu/mike}.
+One of our standard stars, HD 41667, was also reduced using standard extraction and calibration methods in \textsc{iraf}.
+The resultant spectra from both reduction approaches were compared for residual fringing, S/N, and wavelength calibration.
+No noteworthy differences were present, and thus the CarPy pipeline was utilized for the remainder of the reductions.
+Each reduced echelle order was carefully normalized using a third order spline.
+Normalized orders   were stitched together to provide a single one-dimensional spectrum from 3800-9400\,\AA{}.
+
+The white dwarf HR 6141 was observed on X with a S/N of 400 pixel$^{-1}$ as a telluric standard.
+The $S/N$ ratio for HR 6141 exceeds the $S/N$ ratio in any of our program stars.
+Although the atmospheric conditions at Las Campanas Observatory are certain to change throughout the night and between observing runs, we are primarily using this spectra to identify lines that are affected by telluric absorption.
+Critical transitions necessary for abundance analyses that are affected by the earth's atmosphere are corrected for telluric absorption (see \S\ref{sec:telluric-absorption}).
+
 \section{Analysis}
@@
 The radial velocity for each star was determined in a two-step method.
-An initial estimate of the radial velocity was ascertained by cross-correlation with the synthetic spectrum of a giant with $T_{eff} = 4500$\,K, $\log{g} = 1.5$, and [M/H] $= -1.0$ across the wavelength range $8450 - 8700$ \AA{}.
-The observed spectrum was shifted to the pseudo-rest frame using this initial velocity.
+An initial estimate of the radial velocity was ascertained by cross-correlation with a synthetic spectrum of a giant star with $T_{eff} = 4500$\,K, $\log{g} = 1.5$, and [M/H] $= -1.0$ across the wavelength range $8450 - 8700$ \AA{}.
+The observed spectrum was shifted to the pseudo-rest frame using this initial velocity estimate.
 Velocities found from cross-correlation are typically within 1\,km\,s$^{-1}$ of our final published value.
 
-With our spectrum at near-rest, we measured the equivalent widths of $\sim$200 lines by fitting Gaussian functions to the absorption profiles.
-Fitted Gaussian profiles provides us with a measured equivalent width, the full-width half-maximum of the profile, and the central wavelength.
+With our spectra at near-rest, we measured the equivalent widths of $\sim$200 lines by automatically fitting Gaussian functions to the absorption profiles (see Section \ref{sec:line-measurements}).
+Fitted Gaussian profiles provide us with a measured equivalent width, the full-width half-maximum and the central wavelength of the profile.
 Thus, the residual radial velocity can be found from the ratio of the central and rest line wavelengths.
-The final radial velocity for the star is provided by the mean of these $\sim$200 line velocity measurements.
+The final radial velocity for the star is provided by the initial velocity and the mean of $\sim$200 residual line velocity measurements.
 Figure \ref{fig:line-velocities} shows the line velocities for HD41667 after being placed at pseudo-rest using our cross-correlation velocity of 314.4\,km s$^{-1}$.
-As expected, the mean residual offset is small ($-0.75$\,km s$^{-1}$), and our standard deviation is 0.79\,km s$^{-1}$ from 164 line measurements.
+As expected, the mean residual offset is small ($-0.75$\,km s$^{-1}$), and the standard deviation is 0.79\,km s$^{-1}$ from 164 line measurements.
 This provides us with a final measured radial velocity of $313.7 \pm 0.1$\,km s$^{-1}$.
@@
 The radial velocities published in Table \ref{tab:observations} are the final values from this two-step method.
-Heliocentric velocities agree quite well with the \citet{williams;et-al_2011} published values: $\langle\Delta{V_{hel}}\rangle = 2.8$\,km\,s$^{-1}$, demonstrating the accuracy of the velocities published by the RAVE survey.
+Heliocentric velocities agree quite well with the \citet{williams;et-al_2011} published values: the mean absolute offset is $\langle\Delta{V_{hel}}\rangle = 2.8$\,km\,s$^{-1}$, demonstrating the accuracy of the velocities published by the RAVE survey.
 
@@
 For the measurement of atomic absorption lines, we employed the line list of \citet{yong;et-al_2005} with additional transitions of Cr, Sc, Zn, and Sr from \citet{frebel;et-al_2010}.
-We supplemented the list with hyperfine-structure data for Sc and Mn from the Kurucz compilation \citet{kurucz;1998}.
+The line list was augmented with hyperfine-structure data for Sc and Mn from the Kurucz compilation \citet{kurucz;1998}.
 Molecular line data for CH was taken from \citet{plez;et-al_2008,plez;et-al_2009}.
-For lines with hyperfine structure, blended transitions or molecular features, we determined the transition abundance using a spectral synthesis approach where the abundance of a given species is found by by matching a synthetic spectrum to the observed spectrum.
-Equivalent widths were measured to determine the abundances of all other transitions.
+For lines with hyperfine structure, blended transitions or molecular features, we determined the abundance using a spectral synthesis approach.
+For all other transitions, equivalent widths were measured to determine the abundance.
 
@@
 Measuring the local continuum ensures any errors in our initial normalisation or order-stitching do not propagate through to our equivalent width measurements.
-Any group of pixels that deviate significantly ($>$2-$\sigma$) from the local continuum are either persistent cosmic ray hits, or trough points of a neighbouring absorption profile.
+When determining the local continua, any neighbouring group of pixels that deviate significantly ($>$2-$\sigma$) from the local continua either belong to a persistent cosmic ray hit, or they are trough points of a neighbouring absorption profile.
 We attempt to fit a Gaussian profile to each group of deviating pixels, using the current best estimate for the local continuum.
-If a Gaussian profile is successfully fitted to the deviating group and its surrounding pixels, then all points belonging to that profile are excluded from the continuum determination.
-When fitting Gaussian profiles, the $\chi^2$ difference between the observation and the profile is minimized.
-In order to account for crowded absorption regions where the $\chi^2$ value might be influenced by a nearby profile, our $\chi^2$ function is weighted based on the distance to the rest wavelength by the function
+If a Gaussian profile is successfully fitted to the deviating group and its surrounding pixels, we assume the outlier points belong to an absorption profile and all points belonging to that profile are excluded from the continuum determination.
+
+When fitting Gaussian profiles, the $\chi^2$ difference between the observed spectra and the fitted profile is minimized.
+In order to account for crowded absorption regions, where the $\chi^2$ value might be influenced by a nearby profile, our $\chi^2$ function is weighted based on the distance to the rest wavelength by the function
 
@@
 
-\noindent where $\lambda_{r}$ (rest wavelength) and $\sigma$ are free parameters during the iterative fitting process.
+\noindent where the rest wavelength ($\lambda_{r}$) and FWHM ($\sigma$) are free parameters in the iterative fitting process.
 As a consequence of Eq.
-\ref{eq:chi-weight}, pixels near the rest wavelength are weighted higher than those on the wings, forcing the fit to disregard blended or crowded regions.
-Although this approach relies on a reasonably accurate radial velocity correction ($<$4\,km s$^{-1}$; which is easily achieved), it greatly improves the accuracy of the equivalent width measurements.
-
-The results of our iterative fitting approach are completely \textit{insensitive} to the initial FWHM guess.
-Increasing the initial FWHM estimate from 0.1\,\AA{} to 1 or 2\,\AA{} -- unphysically large values for high-resolution spectra -- does not alter either the FWHM or the equivalent width for any of our measurements.
+\ref{eq:chi-weight}, pixels near the rest wavelength are weighted higher than those on the wings, forcing the fitting scheme to disregard blended or crowded regions.
+Although this approach relies on a reasonably accurate radial velocity correction ($<$4\,km s$^{-1}$; which is easily achieved), it greatly improves the accuracy and robustness of the equivalent width measurements.
+
+The results of our iterative Gaussian fitting approach are completely \textit{insensitive} to the initial FWHM guess.
+Increasing the initial FWHM estimate from 0.1\,\AA{} to 1 or 2\,\AA{} -- which are unphysically large values for high-resolution spectra -- does not alter either the FWHM or the equivalent width for any of our measurements.
 Only a small increase in computational cost is observed.
@@
 Saturated lines were excluded by removing measurements with reduced equivalent widths, $\log_{10}{(EW/\lambda)} > -4.5$\, dex.
-A minimum detectable equivalent width was calculated as a function of wavelength based on the S/N, and only lines that exceeded a $3\sigma$ detection significance were included.
-We have verified our equivalent width measurement techniques by comparing our measurements for 156 lines in HD140283 with the study of \citet{norris;et-al_1996}.
+A minimum detectable equivalent width was calculated as a function of wavelength based on the $S/N$, and only lines that exceeded a 3-$\sigma$ detection significance were included.
+We have verified the approach by comparing our measurements of 156 lines in HD 140283 with the study of \citet{norris;et-al_1996}.
 We only included measurements in the \citet{norris;et-al_1996} study that were not marked with line quality parameters.
 Excellent agreement is found between the two studies, which is illustrated in Figure \ref{fig:ew-compare}.
-The mean difference between this study and that of \cite{norris;et-al_1996} is a negligible $0.64 \pm 2.78$\,m\AA{}, and no systematic trend is present.
-We note that the scatter in measurement differences is likely to be directly attributed to the observed $S/N$, as other studies using the same EW measurement software described here find better agreement with hand measurements for spectra with higher $S/N$ ($0.20 \pm 0.16$\,m{\AA} with $S/N \sim X$, $0.25 \pm 0.28$\,m{\AA} with $S/N \sim{} Y$; \citet{frebel;et-al_2013}).
+The mean difference is a negligible $0.64 \pm 2.78$\,m\AA{}, and no systematic trend is present.
+We note that the scatter may  be directly attributed to the observed $S/N$, as other studies using the same equivalent width measurement software described here find better agreement with hand measurements for spectra with higher $S/N$ ($0.20 \pm 0.16$\,m{\AA} with $S/N \sim X$, $0.25 \pm 0.28$\,m{\AA} with $S/N \sim{} Y$; \citet{frebel;et-al_2013}).
 
@@
 
+\clearpage
 % equivalent widths table
@@
 \subsection{Model Atmospheres}
-The ATLAS9 plane-parallel stellar atmospheres of \citet{castelli;kurucz_2003} have been used to deduce stellar parameters and abundances for all of our stars.
+We have employed the ATLAS9 plane-parallel stellar atmospheres of \citet{castelli;kurucz_2003}.
 These one-dimensional models ignore any centre-to-limb spatial variations, assume hydrostatic equilibrium and no convective overshoot from the photosphere.
-The stellar parameter spacing for these grid models is 250\,K, 0.5\,dex in surface gravity, 0.5\,dex in [M/H] and 0.1\,dex in [$\alpha$/Fe].
-We interpolated the atmospheric pressures, densities, temperatures, and opacities between stellar atmospheres using the Quickhull algorithm \citep{barber;et-al_1996}.
-Quickhull is reliant on Delaunay tessellation, which suffers from extremely skewed cells when the grid points vary in size by orders of magnitude -- as $T_{\mbox{eff}}$ values do compared to $\log{g}$ or [X/H].
+The stellar parameter spacing between models is 250\,K, 0.5\,dex in surface gravity, 0.5\,dex in [M/H] and 0.1\,dex in [$\alpha$/Fe].
+We interpolated the atmospheric pressures, densities, temperatures, and opacities between stellar atmosphere models using the Quickhull algorithm \citep{barber;et-al_1996}.
+Quickhull is reliant on Delaunay tessellation, which suffers from extremely skewed cells when the grid points vary in size by orders of magnitude -- as $T_{eff}$ values do compared to $\log{g}$ or [X/H].
 If unaccounted for, performing interpolation using these asymmetric cells can manifest as significant errors in atmospheric properties across all photospheric depths.
-We scaled each stellar parameter between zero and unity prior to interpolation in order to minimise these errors.
+We scaled each stellar parameter between zero and unity prior to interpolation in order to minimise these effects.
 During this step, $\log{g}$, [M/H] and [$\alpha$/Fe] points were scaled such that we simultaneously interpolate linearly in $T_{eff}$ and logarithmically in all other parameters.
@@
 The most recent version of the spectral synthesis code \textsc{moog} \citep{sneden;et-al_1973} has been used to derive individual line abundances and stellar parameters.
-This version of \textsc{moog} employs Rayleigh scattering \citep{sobeck;et-al_2011} instead of treating scattering as true absorption, which is particularly important for transitions blue-ward of 450\,nm.
-This is noteworthy, but is less relevant for this analysis as most of our line measurements are red-ward of 450\,nm.
+This version employs Rayleigh scattering \citep{sobeck;et-al_2011} instead of treating scattering as true absorption, which is particularly important for transitions blue-ward of 450\,nm.
+This is noteworthy, but is less relevant for these analyses as most of our line measurements are red-ward of 450\,nm.
 Absorption lines are assumed to form under the assumption of local thermal equilibrium.
+
+\begin{figure*}[t!]
+	\includegraphics[width=\textwidth]{./figures/spectra-h-alpha.pdf}
+	\caption{Spectra for all Aquarius stream stars.}
+	\label{fig:spectra-h-alpha}
+\end{figure*}
 
@@
 The effective temperatures published for all of our stars in Table \ref{sec:stellar-parameters} have been derived spectroscopically (see \S\ref{sec:effective-teffs}).
-As a consistency check for our spectroscopic temperatures, we have also estimated effective temperatures using infrared photometry from the 2MASS catalog.
-The $J-K$ colour has been employed for these calculations because it has the least dependence on metallicity.
+As a consistency check for our spectroscopic temperatures, we have estimated effective temperatures using infrared photometry from the 2MASS catalog.
+The $J-K$ color has been employed for these calculations because it has the least dependence on metallicity.
 
@@
 However, these maps are not perfect.
-As an alternative to using the \citet{schlegel;et-al_1998} dust maps, the level of extinction towards a star can be found by the strength of their interstellar Na D or K \textsc{I} lines \citep{munari;zwitter_1997}.
-The interstellar lines must be sufficiently separated from the stellar lines in order for the extinction to be measurable.
+As an alternative to using the \citet{schlegel;et-al_1998} dust maps, the level of extinction towards a star can be found by the strength of the interstellar Na D or K \textsc{i} lines \citep{munari;zwitter_1997}.
+The interstellar lines must be sufficiently separated from the stellar absorption lines in order for the extinction to be measurable.
 Unfortunately this was the case in only one of our stars, J223811.
-We measure the equivalent width of the Na D \textsc{I} line in J223811 to be 302.4\,m{\AA}, which corresponds to an $\mbox{E(B-V)} = 0.12^{+0.01}_{-0.02}$ according to the \citet{munari;zwitter_1997} relationship.
+We measured the equivalent width of the Na D1 line in J223811 to be 302.4\,m{\AA}, which corresponds to an $\mbox{E(B-V)} = 0.12^{+0.01}_{-0.02}$ according to the \citet{munari;zwitter_1997} relationship.
 This is a significantly higher value than what the \citet{schlegel;et-al_1998} dust map value of $\mbox{E(B-V)} = 0.07$ for J223811.
-Both extinction values have been used to calculate photometric temperatures.
+For completeness, both extinction values have been used to calculate photometric temperatures.
 
@@
 
-The effective temperatures that we have found from spectroscopy agree fairly well with the photometric temperature estimates.
+The effective temperatures found from spectroscopy agree fairly well with the photometric temperature estimates.
 For three of our stars, the temperatures we find are in between the two color-temperature relationships.
-There are two noteworthy deviations though: J223504-152834 and J223811-104126.
-For J223504-152834 we find the star to have an effective temperature of 4620\,K, 40\,K hotter than the \citet{casagrande;et-al_2010} dwarf/sub-giant relationship, and ${\sim}$500\,K hotter than the \citet{alonso;et-al_1999} temperature.
-Our temperature of 4620\,K is in good agreement with previous spectroscopic determinations (4795\,K; \citet{williams;et-al_2011}, 4597\,K; \citet{wylie-de-boer;et-al_2012}).
+There are two noteworthy deviations: J223504-152834 and J223811-104126.
+For J223504-152834 we find the star to have an effective temperature of 4590\,K, only 10\,K hotter than the \citet{casagrande;et-al_2010} dwarf/sub-giant relationship, yet ${\sim}$500\,K hotter than the \citet{alonso;et-al_1999} estimate.
+Our temperature of 4590\,K is in good agreement with previous spectroscopic determinations (4795\,K; \citet{williams;et-al_2011}, 4597\,K; \citet{wylie-de-boer;et-al_2012}).
 The fact that the \citet{alonso;et-al_1999} photometric temperature relationship for giants predicts a temperature that is ${\sim}$500\,K cooler than the spectroscopically-derived values may be attributed to an underestimated amount of dust towards J223504-152834.
-A higher than expected level of extinction along the line-of-sight would produce cooler temperatures than the true effective temperature.
-
-The F-giant J223811-104126 has two extinction values available: the \citet{schlegel;et-al_1998} value of $E(B-V) = 0.07$ and the 0.12 value that we have determined from the interstellar Na D1 line.
+A higher than expected level of extinction along the line-of-sight would produce cooler photometric temperatures than the true effective temperature.
+An extinction of $E(B-V) = 0.10$ would be required for the \citet{alonso;et-al_1999} relation to yield a temperature of ${\sim}$4500\,K, within the uncertainties of our effective temperature derived from spectroscopy.
+Such a discrepancy in extinction is large, but not unheard of (e.g., see \citet{nataf;et-al}).
+Although we suspect J223504-152834 to have a higher reddening than $E(B-V) = 0.04$, we have adopted the \citet{schlegel;et-al_1998} value for this analysis.
+
+J223811-104126 has two extinction values available: the \citet{schlegel;et-al_1998} value of $E(B-V) = 0.07$ and the 0.12 value  determined from the interstellar Na D1 line.
 Given the inherent difficulties in producing dust maps, and the known problems associated with them, we believe the $E(B-V) = 0.12$ determination to be more accurate.
-However, using the \citet{schlegel;et-al_1998} extinction with the \citet{alonso;et-al_1999} color-temperature relationship yields excellent agreement (within 6\,K) with our spectroscopic temperatures.
+However, using the \citet{schlegel;et-al_1998} extinction value with the \citet{alonso;et-al_1999} color-temperature relationship yields excellent agreement (5104\,K) with our spectroscopic temperature of 5140\,K.
 Employing our more accurate reddening determination yields 5215\,K, within the uncertainties of the relationship.
@@
 
-Thus, with the exception of J223504-152834, the \citet{alonso;et-al_1999} giant relationship agrees well ($\pm$100\,K) with our spectroscopically derived values.
-The \citet{casagrande;et-al_2010} relationship is also in relatively good agreement with our spectroscopic temperatures, although we note that this relation was derived primarily for dwarfs/sub-giants.
-The discrepancy in J223504-152834 could very well be due to under-estimated reddenning along the line-of-sight.
-An extinction of $E(B-V) = 0.10$ would be required for the \citet{alonso;et-al_1999} relation to yield a temperature of ${\sim}$4500\,K, within the uncertainties of our effective temperature derived from spectroscopy.
-Such a discrepancy in extinction is large, but not unheard of (e.g., the case of J223811-104126 or see \citet{nataf;et-al}).
-Although we suspect J223504-152834 to have a higher reddening than $E(B-V) = 0.04$, we have adopted the \citet{schlegel;et-al_1998} value for this analysis.
+With the exception of J223504-152834, the \citet{alonso;et-al_1999} giant relationship agrees well ($\pm$100\,K) with our spectroscopically-derived values.
+The \citet{casagrande;et-al_2010} relationship is also in relatively good agreement (most within 100\,K, largest discrepancy is 220\,K) with our spectroscopic temperatures, although we note that this relation was derived primarily for dwarfs/sub-giants and our candidates are all giant stars.
 
@@
 
-Surface gravity was found by forcing the mean Fe\,I and Fe\,II abundances to be equal, whilst maintaining zero trends with the excitation potential, reduced equivalent width and abundance.
+The surface gravity for all stars was found by forcing the mean Fe\,\textsc{i} and Fe\,\textsc{ii} abundances to be equal.
+The process is iterative: a zero trend with the excitation potential, reduced equivalent width and abundance must be maintained.
+For two stars, X and Y, the surface gravity could not be found by balancing the Fe\,\textsc{i} and \textsc{ii} lines.
+The smallest difference between the median abundances was $\langle$Fe\,\textsc{i} $-$ Fe\,\textsc{ii}$\rangle = 0.05$\,dex, which was considered to be converged.
+Varying the surface gravity from this solution did alter the Fe\,\textsc{i}, \textsc{ii} abundance, but the mean difference $\langle$Fe\,\textsc{i} $-$ Fe\,\textsc{ii}$\rangle$ remained constant at 0.05\,dex.
+In these two instances, the surface gravity was set to be closer towards the isochrone, while the $\langle$Fe\,\textsc{i} $-$ Fe\,\textsc{ii}$\rangle$ = 0.05$\,dex condition was met.
+
+\subsubsection{Metallicity, $\mbox{[M/H]}$}
+The degeneracy between parameters required a refinement of the stellar parameters until the line abundances were consistent with the model atmosphere.
 After these parameters had converged, the model metallicity was exactly matched to that of our line abundances.
 Line abundances that were unusually deviant ($3\sigma$) from the mean were removed.
-The largest number of outlier measurements removed for any observation was nine for C222531-144370.
-
-\subsubsection{Metallicity, $\mbox{[M/H]}$}
-Determining the stellar parameters for a given star is an iterative process.
-Once the effective temperature, microturbulence and surface gravity were deduced, the model atmosphere abundance was matched to our solar-scaled Fe \textsc{I} abundance.
-The degeneracy between parameters required a refinement of the stellar parameters until the line abundances were consistent with the model atmosphere.
+The largest number of outlier measurements removed for any observation was nine for C222531-144370, leaving 60 Fe\,\textsc{i} and 10 Fe\,\textsc{ii} lines for analysis.
+The minimum number of Fe transitions used in any star was 44 lines (33 Fe\,\textsc{i} and 11 Fe\,\textsc{ii}) for our hottest star, J223811-104126.
 
@@
 \cline{1-10} \\
-C2225316-14437	& 4350	& 1.60	& 1.80	& --1.19	
+C2225316-14437	& 4325				& 1.26				& 1.78				& --1.26	
 				& 4235 $\pm$ 118 	& 1.45 $\pm$ 0.21	& 1.96 $\pm$ 0.11 	& --1.20 $\pm$ 0.14 
 				& \citet{wylie-de-boer;et-al_2012} \\
-C2306265-085103	& 4180	& 1.00	& 1.80 	& --1.16
+C2306265-085103	& 4170	& 0.85	& 1.81 	& --1.17
 				& \dots	& \dots	& \dots	& \dots
 				& \dots \\	
-J221821-183424	& 4570	& 0.80	& 1.93	& --1.60
+J221821-183424	& 4590				& 0.90				& 1.91				& --1.61
 				& 4395 $\pm$ 205 	& 1.45 $\pm$ 0.35 	& 1.96 $\pm$ 0.18 	& --1.15 $\pm$ 0.21
 				& \citet{wylie-de-boer;et-al_2012} \\
-J223504-152834	& 4620	& 2.15 	& 1.44	& --0.65
+J223504-152834	& 4590				& 2.15 				& 1.45				& --0.68
 				& 4597 $\pm$ 158 	& 2.40 $\pm$ 0.14 	& 1.47 $\pm$ 0.07 	& --0.98 $\pm$ 0.17
 				& \citet{wylie-de-boer;et-al_2012} \\
-J223811-104126	& 5100	& 3.00	& 1.21	& --1.44
+J223811-104126	& 5140				& 2.96				& 1.33				& --1.45
 				& 5646 $\pm$ 147 	& 4.60 $\pm$ 0.15 	& 1.09 $\pm$ 0.11 	& --1.20 $\pm$ 0.20
@@
 Oxygen is a particularly difficult element to measure.
-There are only a handful of lines available in an optical spectrum: the forbidden [O \textsc{I}] lines at 630 nm and 636 nm, and the O \textsc{I} triplet lines at 777 nm.
+There are only a handful of lines available in an optical spectrum: the forbidden [O \textsc{i}] lines at 630 nm and 636 nm, and the O \textsc{i} triplet lines at 777 nm.
 The forbidden lines are very weak, and become immeasurable in either hot and/or metal-poor stars ([Fe/H] $\lesssim -1.5$ dex).
-When they are present, depending on the radial velocity of the star, the [O \textsc{I}] can be significantly affected by telluric absorption.
-Moreover, the 630 nm line is blended with a Ni \textsc{I} absorption line \citep{allende-prieto;et-al_2001}, and hence the region requires careful consideration.
-Although the O \textsc{I} triplet lines at 777 nm are stronger than the forbidden lines, they are extremely susceptible to NLTE and 3D effects \citep{asplund;perez_2001}, and sensitive to changes in microturbulence.
-\citet{perez;et-al_2006} showed that oxygen abundances measured under the assumption of LTE in their sample are 0.08\,dex higher than abundances derived from the `true' oxygen content derived from the forbidden lines \citep{perez;et-al_2006}.
-
-The [O \textsc{I}] lines were measurable in four of our candidates.
-Careful consideration was taken when correcting for telluric absorption, and we inspected all lines for any contamination by the earth's atmosphere.
+When they are present, depending on the radial velocity of the star, the [O \textsc{i}] lines can be significantly affected by telluric absorption.
+Moreover, the 630 nm line is blended with a Ni \textsc{i} absorption line \citep{allende-prieto;et-al_2001}, and hence the region requires careful consideration.
+Although the O \textsc{i} triplet lines at 777 nm are stronger than the forbidden lines, they are extremely susceptible to NLTE and 3D effects \citep{asplund;perez_2001}, and sensitive to changes in microturbulence.
+\citet{perez;et-al_2006} showed that oxygen abundances measured under the assumption of LTE in their sample are 0.08\,dex higher than abundances derived from the `true' oxygen content derived from the forbidden lines.
+
+The [O \textsc{i}] lines were measurable in four of our candidates.
+Careful consideration was taken when correcting for telluric absorption.
 The 6300$\lambda$ line in one of our candidates, C2306265-085103, was sufficiently affected by telluric absorption such that we considered the line immeasurable.
 Thus, only the 6363$\lambda$ line was used to derive an oxygen abundance for C2306265-085103.
-In our hottest star, J223811-104126, the forbidden oxygen lines were not detected above a $3-\sigma$ significance.
-After synthesising the region, we deduce a conservative upper limit of $\mbox{[O/Fe]} < -0.50$ dex from the [O \textsc{I}] lines.
+In our hottest star, J223811-104126, the forbidden oxygen lines were not detected above a 3-$\sigma$ significance.
+After synthesising the region, we deduce a conservative upper limit of $\mbox{[O/Fe]} < -0.50$ dex from the [O \textsc{i}] lines.
 This is consistent with the rest of our candidates, with [O/Fe] abundances varying between 0.41 to 0.57 dex.
@@
 Each line was synthesised, and a mean abundance was calculated for each candidate.
-Abundances determined from the oxygen triplet lines were systematically $+0.27$\,dex higher than found from the [O \textsc{I}] lines.
-\citet{perez;et-al_2006} found [O/Fe] values based on the O \textsc{I} permitted triplet lines are on average $+0.19 \pm 0.07$\,dex higher than those found from the forbidden lines, after NLTE corrections of $-$0.08\,dex had been applied.
-Thus, our 0.27\,dex offset between measurements of the [O \textsc{I}] and O \textsc{I} triplet lines is exactly the same as found by \citet{perez;et-al_2006}, which we attribute to a combination of NLTE, 3D and other systematic effects.
-\citet{perez;et-al_2006} concluded the weak forbidden lines, when not too weak, probably give the most reliable estimate of [O/Fe].
-
-From the permitted O \textsc{I} triplet, we derive an oxygen abundance of $\mbox{[O/Fe]} = 0.41 \pm 0.01$\,dex (random scatter) for J223811-104126.
-This measurement will be systematically higher than the `true' abundance if it were discernible from the [O \textsc{I}] lines, on the order of $\sim{}$0.27\,dex.
-When we apply this crude offset derived from the rest of our sample, we arrive at a corrected abundance of $[O/Fe] = 0.14 \pm 0.08$\,dex for J223811-104126.
-This is the most oxygen-deficient star in our sample.
+Abundances determined from the oxygen triplet lines were systematically $+0.27$\,dex higher than found from the [O \textsc{i}] lines.
+\citet{perez;et-al_2006} found [O/Fe] values based on the O \textsc{i} permitted triplet lines are on average $+0.19 \pm 0.07$\,dex higher than those found from the forbidden lines, after NLTE corrections of $-$0.08\,dex had been applied.
+Thus, our 0.27\,dex offset between measurements of the [O \textsc{i}] and O \textsc{i} triplet lines is exactly the same as found by \citet{perez;et-al_2006}, which we attribute to a combination of systematic phenomena including NLTE and 3D effects.
+\citet{perez;et-al_2006} concluded the weak forbidden lines, when not too weak, probably give the most reliable estimate of oxygen abundance.
+
+From the permitted O \textsc{i} triplet, we derive an oxygen abundance of $\mbox{[O/Fe]} = 0.41 \pm 0.01$\,dex (random scatter) for J223811-104126.
+This measurement will be systematically higher than the `true' abundance if it were discernible from the [O \textsc{i}] lines, on the order of ${\sim}$0.27\,dex.
+When we apply this crude offset derived from the rest of our sample, we arrive at a corrected abundance of $\mbox{[O/Fe]} = 0.14 \pm 0.08$\,dex for J223811-104126.
+This is the most oxygen-deficient star in our sample, by in excess of 0.25 dex.
 
 \subsubsection{Sodium}
-
-Sodium is mainly produced through through carbon burning in massive stars by the dominant $^{12}\mbox{C}(^{12}\mbox{C}, p)^{23}\mbox{Na}$ process.
-The final Na abundance is dependent on the neutron excess of the star, which slowly increases during carbon burning due to weak interactions \citep{arnett;truran_1974}.
-Massive stars ($>8 M_\odot$) eventually deliver their manufactured sodium to the interstellar-medium through SN II events.
-Because the eventual SN II explosion is devoid of any significant beta-decay processes, the neutron excess of the exploded material is representative of the pre-explosion abundance.
-
-The explosive material eventually condenses to form the next generation of stars, which will have a net increase in their neutron excess with respect to when their predecessors formed.
-Since the Na-production rate is correlated with the neutron excess, an overall increase in the total Na and Na-production rate between stellar generations is expected.
-Thus, an increase in the Na abundance between generations of massive stars is a natural consequence of nucleosynthesis.
-Sodium content also becomes important for production of Ni during the SN II event (see \S\ref{sec:na-ni}) because $^{23}$Na is the only stable isotope produced in significant quantities during the C- (or O-) burning stages.
-A small fraction of $^{22}$Na is also forged through proton capture on $^{21}$Ne in the carbon shell, an effect which is enhanced by neutrinos spallating abundant elements like $^{16}$O and $^{20}$Ne, making free protons available for capture \citep{woosley;weaver_1995}.
 
@@
 %Magnesium has been measured from unblended lines that fall within the linear regime between reduced equivalent width and abundance.
-Depending on the radial velocity of the star, some magnesium lines were be affected by telluric absorption, particularly the 6318$\lambda$ and 6965.4$\lambda$ lines.
+Depending on the radial velocity of the star, some magnesium lines were be affected by telluric absorption, particularly the 6318$\lambda$ and 6965$\lambda$ lines.
 Atmospheric absorption was most notable for C2225316-14437, where three of the four Mg transitions in our line list suffered some degree of telluric absorption, requiring an attentive correction.
@@
 As shown in Figure \ref{fig:alpha-elements}, all Aquarius stars show super-solar Ca abundances, ranging between 0.23 to 0.43 dex, consistent with both [Mg/Fe] and [Si/Fe] measurements.
+
 However, C2225316-14437 has an unusually high silicon abundance ($\mbox{[Si/Fe]} = 0.72$), well outside the uncertainties of the rest of our sample.
@@
 If we exclude the most prominent outlier, then the mean abundance drops only slightly to $\mbox{[Si/Fe]} = 0.70 \pm 0.04$\,dex.
-The lowest silicon line abundance for C2225316-14437 is $\mbox{[Si/Fe]} = 0.57$\,dex, still significantly higher than the averaged abundance for any other star.
+The lowest silicon line abundance for C2225316-14437 is $\mbox{[Si/Fe]} = 0.57$\,dex, which is still significantly higher than the averaged abundance for any other star.
 
@@
 The strongest of these lines occur at 3944 and 3961\,{\AA}, and are visible in all of our stars.
-However, this is a particularly crowded spectral region: these lines fall between the strong Ca H and K lines, with the 3961\,{\AA} transition clearly in the wing of the Ca H line.
+However, this is a particularly crowded spectral region: the lines fall between the strong Ca H and K lines, with the 3961\,{\AA} transition clearly in the wing of the Ca H line.
 This makes the continuum determination and subsequent Al measurement non-trivial, especially given the metallicity of our stars.
-Instead, we have measured Al abundances from the other transitions available in our spectra: the Al \textsc{I} lines at 6696, 6698, 7835 and 7836\,{\AA}.
-Although these lines are weaker than the bluer Al \textsc{I} lines, their surrounding regions are uncrowded.
+Instead, we have measured Al abundances from the other transitions available in our spectra: the Al \textsc{i} lines at 6696, 6698, 7835 and 7836\,{\AA}.
+Although these lines are weaker than the bluer Al \textsc{i} lines, their surrounding regions are uncrowded.
 
 Generally the four Al \textsc{i} lines are in reasonable agreement with one another, yielding random scatter of less than 0.05\,dex.
-
-These lines were not always detected in our spectra.
-With decreasing metallicity and increasing temperature the strength of the lines is noticeably weakened, below a 3-$\sigma$ detection limit.
-For our most metal-poor star, J221821, only one Al \textsc{i} line was detectable, and we have adopted an uncertainty of 0.05\,dex.
-
-% there are a few lines available in the spectrum
-% incl. blue ones
-% the blue ones remain strong even in extremely metal-poor stars
-% in metal rich stars the region is too crowded and the continuum (and abundance) is non-trivial to determine
-% in lieu of using these lines, we have used 4 other lines at X
-% for our most metal-poor star, J221X, only one of these lines was detectable
+However, these lines were not always detected in the data.
+The strength of the lines is noticeably weakened below a 3-$\sigma$ detection with decreasing metallicity and increasing temperature.
+For our most metal-poor star, J221821, only one Al \textsc{i} line was detectable, and so we have adopted an uncertainty of 0.10\,dex.
 
@@
 \subsubsection{Barium}
-Barium is a neutron-capture element, primarily produced through the \textit{s}-process, but can be forged from a variety of nucleosynthetic processes.
+%Barium is a neutron-capture element, primarily produced through the \textit{s}-process, but can be forged from a variety of nucleosynthetic processes.
+
 Measuring barium requires some careful consideration.
@@
 In these cases the line was discarded.
-The abundances tabulated in Table \ref{tab:program-star-abundances} are based on the remaining clean Ba \textsc{II} lines at 5853 and 6141 {\AA}, which are generally in good agreement with each other, and the 6496 {\AA} line where available.
+The abundances tabulated in Table \ref{tab:program-star-abundances} are based on the remaining clean Ba \textsc{ii} lines at 5853 and 6141 {\AA}, which are generally in good agreement with each other, and the 6496 {\AA} line where available.
 
@@
 The exception is C2225316, which has an anomalously high barium abundance of $\mbox{[Ba/Fe]} = 0.68$ dex.
-This is $\sim{}0.60$ dex higher than the Milky Way trend at its given $\mbox{[Fe/H]} = -1.19$ dex.
-Our three Ba \textsc{II} lines in C2225316 are in excellent agreement: 0.67, 0.68, and 0.72 dex.
-The 6496 {\AA} transition has negligible telluric contribution (e.g.
+This is ${\sim}$0.60 dex higher than the Milky Way trend at its given $\mbox{[Fe/H]} = -1.19$ dex.
+Our three Ba \textsc{ii} lines in C2225316 are in excellent agreement: 0.67, 0.68, and 0.72 dex.
+The 6496 {\AA} transition has a negligible telluric contribution (e.g.
 Figure \ref{fig:ba-6496}), so it was included for this star.
-At least in Al, Si, Cr and Ba abundances (see sections \ref{sec:aluminium-abundance}, \ref{sec:alpha-elements}, \ref{sec:iron-peak-elements}), this star appears to be chemically distinct from the other Aquarius stream stars in our sample.
+At least in Al, Si, Cr and Ba abundances (see sections \ref{sec:aluminium-abundance}, \ref{sec:alpha-elements}, \ref{sec:iron-peak-elements}), C225316 appears to be chemically distinct from the other Aquarius stream stars in our sample.
 
@@
  \cline{1-7} \cline{9-15} \\
-   O \textsc{I} &   2 &    7.50 &    0.04 & $-$1.18 &    0.41 &    0.02 &&
-   O \textsc{I} &   2 &    7.90 &    0.01 & $-$0.79 &    0.48 &    0.01 \\
-  Na \textsc{I} &   2 &    4.56 &    0.14 & $-$1.68 & $-$0.08 &    0.10 &&
-  Na \textsc{I} &   3 &    5.09 &    0.17 & $-$1.15 &    0.12 &    0.10 \\
-  Mg \textsc{I} &   4 &    6.55 &    0.37 & $-$1.04 &    0.55 &    0.18 &&
-  Mg \textsc{I} &   4 &    6.98 &    0.24 & $-$0.62 &    0.65 &    0.12 \\
-  Al \textsc{I} &   1 &    5.04 &    0.00 & $-$1.41 &    0.18 & \nodata &&
-  Al \textsc{I} &   4 &    5.87 &    0.09 & $-$0.58 &    0.68 &    0.04 \\
-  Si \textsc{I} &   5 &    6.28 &    0.08 & $-$1.23 &    0.37 &    0.04 &&
-  Si \textsc{I} &   5 &    6.96 &    0.15 & $-$0.55 &    0.72 &    0.07 \\
-  Ca \textsc{I} &   4 &    4.97 &    0.04 & $-$1.37 &    0.23 &    0.02 &&
-  Ca \textsc{I} &   4 &    5.50 &    0.04 & $-$0.84 &    0.43 &    0.02 \\
-  Sc \textsc{I} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata &&
-  Sc \textsc{I} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
- Sc \textsc{II} &   6 &    1.52 &    0.08 & $-$1.63 & $-$0.04 &    0.03 &&
- Sc \textsc{II} &   5 &    2.05 &    0.13 & $-$1.10 &    0.17 &    0.06 \\
-  Ti \textsc{I} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata &&
-  Ti \textsc{I} &   4 &    4.04 &    0.03 & $-$0.91 &    0.36 &    0.01 \\
- Ti \textsc{II} &   4 &    3.81 &    0.13 & $-$1.14 &    0.45 &    0.07 &&
- Ti \textsc{II} &   2 &    4.26 &    0.08 & $-$0.69 &    0.58 &    0.06 \\
-   V \textsc{I} &   3 &    2.23 &    0.01 & $-$1.70 & $-$0.11 &    0.01 &&
-   V \textsc{I} &   6 &    2.92 &    0.17 & $-$1.01 &    0.26 &    0.07 \\
-  Cr \textsc{I} &  11 &    3.74 &    0.07 & $-$1.90 & $-$0.30 &    0.02 &&
-  Cr \textsc{I} &   8 &    4.27 &    0.16 & $-$1.37 & $-$0.10 &    0.06 \\
-  Mn \textsc{I} &   3 &    3.29 &    0.04 & $-$2.14 & $-$0.54 &    0.02 &&
-  Mn \textsc{I} &   3 &    4.14 &    0.05 & $-$1.29 & $-$0.02 &    0.03 \\
-  Fe \textsc{I} &  52 &    5.91 &    0.09 & $-$1.59 &    0.00 &    0.01 &&
-  Fe \textsc{I} &  61 &    6.23 &    0.11 & $-$1.27 &    0.00 &    0.01 \\
- Fe \textsc{II} &  13 &    5.90 &    0.05 & $-$1.60 &    0.00 &    0.01 &&
- Fe \textsc{II} &  10 &    6.17 &    0.06 & $-$1.33 & $-$0.07 &    0.02 \\
-  Co \textsc{I} &   1 &    3.35 &    0.00 & $-$1.64 & $-$0.05 & \nodata &&
-  Co \textsc{I} &   3 &    3.92 &    0.12 & $-$1.07 &    0.20 &    0.07 \\
-  Ni \textsc{I} &   5 &    4.61 &    0.15 & $-$1.61 & $-$0.01 &    0.07 &&
-  Ni \textsc{I} &   7 &    5.04 &    0.09 & $-$1.18 &    0.09 &    0.03 \\
-  Cu \textsc{I} &   1 &    2.13 &    0.00 & $-$2.06 & $-$0.47 & \nodata &&
-  Cu \textsc{I} &   1 &    3.35 &    0.00 & $-$0.84 &    0.43 & \nodata \\
-  Zn \textsc{I} &   2 &    3.15 &    0.11 & $-$1.41 &    0.19 &    0.08 &&
-  Zn \textsc{I} &   2 &    3.46 &    0.23 & $-$1.10 &    0.17 &    0.17 \\
+   O \textsc{i} &   2 &    7.50 &    0.04 & $-$1.18 &    0.41 &    0.02 &&
+   O \textsc{i} &   2 &    7.90 &    0.01 & $-$0.79 &    0.48 &    0.01 \\
+  Na \textsc{i} &   2 &    4.56 &    0.14 & $-$1.68 & $-$0.08 &    0.10 &&
+  Na \textsc{i} &   3 &    5.09 &    0.17 & $-$1.15 &    0.12 &    0.10 \\
+  Mg \textsc{i} &   4 &    6.55 &    0.37 & $-$1.04 &    0.55 &    0.18 &&
+  Mg \textsc{i} &   4 &    6.98 &    0.24 & $-$0.62 &    0.65 &    0.12 \\
+  Al \textsc{i} &   1 &    5.04 &    0.00 & $-$1.41 &    0.18 & \nodata &&
+  Al \textsc{i} &   4 &    5.87 &    0.09 & $-$0.58 &    0.68 &    0.04 \\
+  Si \textsc{i} &   5 &    6.28 &    0.08 & $-$1.23 &    0.37 &    0.04 &&
+  Si \textsc{i} &   5 &    6.96 &    0.15 & $-$0.55 &    0.72 &    0.07 \\
+  Ca \textsc{i} &   4 &    4.97 &    0.04 & $-$1.37 &    0.23 &    0.02 &&
+  Ca \textsc{i} &   4 &    5.50 &    0.04 & $-$0.84 &    0.43 &    0.02 \\
+  Sc \textsc{i} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata &&
+  Sc \textsc{i} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
+ Sc \textsc{ii} &   6 &    1.52 &    0.08 & $-$1.63 & $-$0.04 &    0.03 &&
+ Sc \textsc{ii} &   5 &    2.05 &    0.13 & $-$1.10 &    0.17 &    0.06 \\
+  Ti \textsc{i} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata &&
+  Ti \textsc{i} &   4 &    4.04 &    0.03 & $-$0.91 &    0.36 &    0.01 \\
+ Ti \textsc{ii} &   4 &    3.81 &    0.13 & $-$1.14 &    0.45 &    0.07 &&
+ Ti \textsc{ii} &   2 &    4.26 &    0.08 & $-$0.69 &    0.58 &    0.06 \\
+   V \textsc{i} &   3 &    2.23 &    0.01 & $-$1.70 & $-$0.11 &    0.01 &&
+   V \textsc{i} &   6 &    2.92 &    0.17 & $-$1.01 &    0.26 &    0.07 \\
+  Cr \textsc{i} &  11 &    3.74 &    0.07 & $-$1.90 & $-$0.30 &    0.02 &&
+  Cr \textsc{i} &   8 &    4.27 &    0.16 & $-$1.37 & $-$0.10 &    0.06 \\
+  Mn \textsc{i} &   3 &    3.29 &    0.04 & $-$2.14 & $-$0.54 &    0.02 &&
+  Mn \textsc{i} &   3 &    4.14 &    0.05 & $-$1.29 & $-$0.02 &    0.03 \\
+  Fe \textsc{i} &  52 &    5.91 &    0.09 & $-$1.59 &    0.00 &    0.01 &&
+  Fe \textsc{i} &  61 &    6.23 &    0.11 & $-$1.27 &    0.00 &    0.01 \\
+ Fe \textsc{ii} &  13 &    5.90 &    0.05 & $-$1.60 &    0.00 &    0.01 &&
+ Fe \textsc{ii} &  10 &    6.17 &    0.06 & $-$1.33 & $-$0.07 &    0.02 \\
+  Co \textsc{i} &   1 &    3.35 &    0.00 & $-$1.64 & $-$0.05 & \nodata &&
+  Co \textsc{i} &   3 &    3.92 &    0.12 & $-$1.07 &    0.20 &    0.07 \\
+  Ni \textsc{i} &   5 &    4.61 &    0.15 & $-$1.61 & $-$0.01 &    0.07 &&
+  Ni \textsc{i} &   7 &    5.04 &    0.09 & $-$1.18 &    0.09 &    0.03 \\
+  Cu \textsc{i} &   1 &    2.13 &    0.00 & $-$2.06 & $-$0.47 & \nodata &&
+  Cu \textsc{i} &   1 &    3.35 &    0.00 & $-$0.84 &    0.43 & \nodata \\
+  Zn \textsc{i} &   2 &    3.15 &    0.11 & $-$1.41 &    0.19 &    0.08 &&
+  Zn \textsc{i} &   2 &    3.46 &    0.23 & $-$1.10 &    0.17 &    0.17 \\
 \cline{1-7} \cline{9-15} \\
@@
 \cline{1-7} \cline{9-15} \\
-   O \textsc{I} &   2 &    8.48 &    0.09 & $-$0.21 &    0.46 &    0.07 &&
-   O \textsc{I} &   1 &    8.60 &    0.00 & $-$0.09 &    0.14\footnote{Abundance derived from the permitted O \textsc{I} triplet instead of the forbidden [O \textsc{I}] lines, see \S\ref{sec:oxygen-abundances}} &    0.08 \\
-  Na \textsc{I} &   3 &    5.76 &    0.12 & $-$0.48 &    0.19 &    0.07 &&
-  Na \textsc{I} &   2 &    4.76 &    0.10 & $-$1.48 & $-$0.03 &    0.07 \\
-  Mg \textsc{I} &   3 &    7.50 &    0.24 & $-$0.10 &    0.58 &    0.14 &&
-  Mg \textsc{I} &   3 &    6.49 &    0.42 & $-$1.11 &    0.34 &    0.24 \\
-  Al \textsc{I} &   3 &    6.10 &    0.08 & $-$0.35 &    0.32 &    0.05 &&
-  Al \textsc{I} &   2 &    5.10 &    0.14 & $-$1.35 &    0.10 &    0.10 \\
-  Si \textsc{I} &   5 &    7.11 &    0.10 & $-$0.40 &    0.28 &    0.04 &&
-  Si \textsc{I} &   3 &    6.38 &    0.04 & $-$1.13 &    0.32 &    0.02 \\
-  Ca \textsc{I} &   4 &    6.03 &    0.04 & $-$0.31 &    0.36 &    0.02 &&
-  Ca \textsc{I} &   4 &    5.30 &    0.03 & $-$1.04 &    0.41 &    0.01 \\
-  Sc \textsc{I} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata &&
-  Sc \textsc{I} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
- Sc \textsc{II} &   6 &    2.70 &    0.14 & $-$0.45 &    0.23 &    0.06 &&
- Sc \textsc{II} &   6 &    1.75 &    0.14 & $-$1.40 &    0.05 &    0.06 \\
-  Ti \textsc{I} &   4 &    4.63 &    0.02 & $-$0.32 &    0.36 &    0.01 &&
-  Ti \textsc{I} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
- Ti \textsc{II} &   2 &    4.92 &    0.26 & $-$0.04 &    0.64 &    0.19 &&
- Ti \textsc{II} &   4 &    3.83 &    0.09 & $-$1.12 &    0.33 &    0.04 \\
-   V \textsc{I} &   6 &    3.67 &    0.22 & $-$0.26 &    0.41 &    0.09 &&
-   V \textsc{I} &   1 &    2.42 &    0.00 & $-$1.51 & $-$0.06 & \nodata \\
-  Cr \textsc{I} &   7 &    4.94 &    0.09 & $-$0.70 & $-$0.02 &    0.03 &&
-  Cr \textsc{I} &  12 &    4.12 &    0.06 & $-$1.52 & $-$0.07 &    0.02 \\
-  Mn \textsc{I} &   3 &    5.08 &    0.10 & $-$0.35 &    0.33 &    0.06 &&
-  Mn \textsc{I} &   3 &    3.55 &    0.04 & $-$1.88 & $-$0.43 &    0.02 \\
-  Fe \textsc{I} &  64 &    6.83 &    0.12 & $-$0.67 &    0.00 &    0.02 &&
-  Fe \textsc{I} &  33 &    6.05 &    0.06 & $-$1.45 &    0.00 &    0.01 \\
- Fe \textsc{II} &  12 &    6.82 &    0.07 & $-$0.68 &    0.00 &    0.02 &&
- Fe \textsc{II} &  11 &    6.00 &    0.09 & $-$1.50 & $-$0.05 &    0.03 \\
-  Co \textsc{I} &   3 &    4.53 &    0.14 & $-$0.46 &    0.21 &    0.08 &&
-  Co \textsc{I} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
-  Ni \textsc{I} &   7 &    5.62 &    0.09 & $-$0.60 &    0.08 &    0.03 &&
-  Ni \textsc{I} &   2 &    4.82 &    0.04 & $-$1.40 &    0.05 &    0.03 \\
-  Cu \textsc{I} &   1 &    3.85 &    0.00 & $-$0.34 &    0.33 & \nodata &&
-  Cu \textsc{I} &   1 &    2.39 &    0.00 & $-$1.80 & $-$0.35 & \nodata \\
-  Zn \textsc{I} &   2 &    4.17 &    0.03 & $-$0.39 &    0.28 &    0.02 &&
-  Zn \textsc{I} &   2 &    3.17 &    0.04 & $-$1.39 &    0.06 &    0.03 \\
+   O \textsc{i} &   2 &    8.48 &    0.09 & $-$0.21 &    0.46 &    0.07 &&
+   O \textsc{i} &   1 &    8.60 &    0.00 & $-$0.09 &    0.14\footnote{Abundance derived from the permitted O \textsc{i} triplet instead of the forbidden [O \textsc{i}] lines, see \S\ref{sec:oxygen-abundances}} &    0.08 \\
+  Na \textsc{i} &   3 &    5.76 &    0.12 & $-$0.48 &    0.19 &    0.07 &&
+  Na \textsc{i} &   2 &    4.76 &    0.10 & $-$1.48 & $-$0.03 &    0.07 \\
+  Mg \textsc{i} &   3 &    7.50 &    0.24 & $-$0.10 &    0.58 &    0.14 &&
+  Mg \textsc{i} &   3 &    6.49 &    0.42 & $-$1.11 &    0.34 &    0.24 \\
+  Al \textsc{i} &   3 &    6.10 &    0.08 & $-$0.35 &    0.32 &    0.05 &&
+  Al \textsc{i} &   2 &    5.10 &    0.14 & $-$1.35 &    0.10 &    0.10 \\
+  Si \textsc{i} &   5 &    7.11 &    0.10 & $-$0.40 &    0.28 &    0.04 &&
+  Si \textsc{i} &   3 &    6.38 &    0.04 & $-$1.13 &    0.32 &    0.02 \\
+  Ca \textsc{i} &   4 &    6.03 &    0.04 & $-$0.31 &    0.36 &    0.02 &&
+  Ca \textsc{i} &   4 &    5.30 &    0.03 & $-$1.04 &    0.41 &    0.01 \\
+  Sc \textsc{i} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata &&
+  Sc \textsc{i} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
+ Sc \textsc{ii} &   6 &    2.70 &    0.14 & $-$0.45 &    0.23 &    0.06 &&
+ Sc \textsc{ii} &   6 &    1.75 &    0.14 & $-$1.40 &    0.05 &    0.06 \\
+  Ti \textsc{i} &   4 &    4.63 &    0.02 & $-$0.32 &    0.36 &    0.01 &&
+  Ti \textsc{i} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
+ Ti \textsc{ii} &   2 &    4.92 &    0.26 & $-$0.04 &    0.64 &    0.19 &&
+ Ti \textsc{ii} &   4 &    3.83 &    0.09 & $-$1.12 &    0.33 &    0.04 \\
+   V \textsc{i} &   6 &    3.67 &    0.22 & $-$0.26 &    0.41 &    0.09 &&
+   V \textsc{i} &   1 &    2.42 &    0.00 & $-$1.51 & $-$0.06 & \nodata \\
+  Cr \textsc{i} &   7 &    4.94 &    0.09 & $-$0.70 & $-$0.02 &    0.03 &&
+  Cr \textsc{i} &  12 &    4.12 &    0.06 & $-$1.52 & $-$0.07 &    0.02 \\
+  Mn \textsc{i} &   3 &    5.08 &    0.10 & $-$0.35 &    0.33 &    0.06 &&
+  Mn \textsc{i} &   3 &    3.55 &    0.04 & $-$1.88 & $-$0.43 &    0.02 \\
+  Fe \textsc{i} &  64 &    6.83 &    0.12 & $-$0.67 &    0.00 &    0.02 &&
+  Fe \textsc{i} &  33 &    6.05 &    0.06 & $-$1.45 &    0.00 &    0.01 \\
+ Fe \textsc{ii} &  12 &    6.82 &    0.07 & $-$0.68 &    0.00 &    0.02 &&
+ Fe \textsc{ii} &  11 &    6.00 &    0.09 & $-$1.50 & $-$0.05 &    0.03 \\
+  Co \textsc{i} &   3 &    4.53 &    0.14 & $-$0.46 &    0.21 &    0.08 &&
+  Co \textsc{i} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
+  Ni \textsc{i} &   7 &    5.62 &    0.09 & $-$0.60 &    0.08 &    0.03 &&
+  Ni \textsc{i} &   2 &    4.82 &    0.04 & $-$1.40 &    0.05 &    0.03 \\
+  Cu \textsc{i} &   1 &    3.85 &    0.00 & $-$0.34 &    0.33 & \nodata &&
+  Cu \textsc{i} &   1 &    2.39 &    0.00 & $-$1.80 & $-$0.35 & \nodata \\
+  Zn \textsc{i} &   2 &    4.17 &    0.03 & $-$0.39 &    0.28 &    0.02 &&
+  Zn \textsc{i} &   2 &    3.17 &    0.04 & $-$1.39 &    0.06 &    0.03 \\
 
@@
 \cline{1-7} \\
-   O \textsc{I} &   2 &    8.09 &    0.15 & $-$0.60 &    0.57 &    0.10 \\
-  Na \textsc{I} &   2 &    5.25 &    0.00 & $-$0.99 &    0.18 &    0.00 \\
-  Mg \textsc{I} &   2 &    6.84 &    0.07 & $-$0.76 &    0.41 &    0.05 \\
-  Al \textsc{I} &   4 &    5.56 &    0.08 & $-$0.89 &    0.28 &    0.04 \\
-  Si \textsc{I} &   5 &    6.66 &    0.08 & $-$0.85 &    0.32 &    0.03 \\
-  Ca \textsc{I} &   4 &    5.48 &    0.04 & $-$0.86 &    0.31 &    0.02 \\
-  Sc \textsc{I} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
- Sc \textsc{II} &   6 &    2.18 &    0.15 & $-$0.97 &    0.20 &    0.06 \\
-  Ti \textsc{I} &   4 &    4.06 &    0.03 & $-$0.89 &    0.28 &    0.01 \\
- Ti \textsc{II} &   3 &    4.21 &    0.36 & $-$0.74 &    0.43 &    0.21 \\
-   V \textsc{I} &   4 &    2.88 &    0.06 & $-$1.05 &    0.12 &    0.03 \\
-  Cr \textsc{I} &   4 &    4.20 &    0.26 & $-$1.44 & $-$0.27 &    0.13 \\
-  Mn \textsc{I} &   3 &    4.35 &    0.10 & $-$1.08 &    0.09 &    0.06 \\
-  Fe \textsc{I} &  63 &    6.33 &    0.12 & $-$1.17 &    0.00 &    0.01 \\
- Fe \textsc{II} &  11 &    6.31 &    0.09 & $-$1.19 & $-$0.02 &    0.03 \\
-  Co \textsc{I} &   3 &    4.00 &    0.15 & $-$0.99 &    0.18 &    0.08 \\
-  Ni \textsc{I} &   7 &    5.08 &    0.08 & $-$1.14 &    0.03 &    0.03 \\
-  Cu \textsc{I} &   1 &    3.55 &    0.00 & $-$0.64 &    0.53 &    0.00 \\
-  Zn \textsc{I} &   2 &    3.38 &    0.14 & $-$1.18 & $-$0.01 &    0.10
+   O \textsc{i} &   2 &    8.09 &    0.15 & $-$0.60 &    0.57 &    0.10 \\
+  Na \textsc{i} &   2 &    5.25 &    0.00 & $-$0.99 &    0.18 &    0.00 \\
+  Mg \textsc{i} &   2 &    6.84 &    0.07 & $-$0.76 &    0.41 &    0.05 \\
+  Al \textsc{i} &   4 &    5.56 &    0.08 & $-$0.89 &    0.28 &    0.04 \\
+  Si \textsc{i} &   5 &    6.66 &    0.08 & $-$0.85 &    0.32 &    0.03 \\
+  Ca \textsc{i} &   4 &    5.48 &    0.04 & $-$0.86 &    0.31 &    0.02 \\
+  Sc \textsc{i} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
+ Sc \textsc{ii} &   6 &    2.18 &    0.15 & $-$0.97 &    0.20 &    0.06 \\
+  Ti \textsc{i} &   4 &    4.06 &    0.03 & $-$0.89 &    0.28 &    0.01 \\
+ Ti \textsc{ii} &   3 &    4.21 &    0.36 & $-$0.74 &    0.43 &    0.21 \\
+   V \textsc{i} &   4 &    2.88 &    0.06 & $-$1.05 &    0.12 &    0.03 \\
+  Cr \textsc{i} &   4 &    4.20 &    0.26 & $-$1.44 & $-$0.27 &    0.13 \\
+  Mn \textsc{i} &   3 &    4.35 &    0.10 & $-$1.08 &    0.09 &    0.06 \\
+  Fe \textsc{i} &  63 &    6.33 &    0.12 & $-$1.17 &    0.00 &    0.01 \\
+ Fe \textsc{ii} &  11 &    6.31 &    0.09 & $-$1.19 & $-$0.02 &    0.03 \\
+  Co \textsc{i} &   3 &    4.00 &    0.15 & $-$0.99 &    0.18 &    0.08 \\
+  Ni \textsc{i} &   7 &    5.08 &    0.08 & $-$1.14 &    0.03 &    0.03 \\
+  Cu \textsc{i} &   1 &    3.55 &    0.00 & $-$0.64 &    0.53 &    0.00 \\
+  Zn \textsc{i} &   2 &    3.38 &    0.14 & $-$1.18 & $-$0.01 &    0.10
 \enddata
@@
 
-The stellar parameters reported in \citet{wylie-de-boer;et-al_2012} differ slightly to those found in Table \ref{tab:stellar-parameters}.
-\citet{wylie-de-boer;et-al_2012} deduce their stellar parameters by minimizing the $\chi^2$ difference between the observed spectra, and spectra from the \citet{munari;et-al_2005} synthetic spectral library after it was convolved and re-sampled to match the observations.
+The stellar parameters reported in \citet{wylie-de-boer;et-al_2012} differ slightly to those published in Table \ref{tab:stellar-parameters}.
+\citet{wylie-de-boer;et-al_2012} deduce their stellar parameters by minimizing the $\chi^2$ difference between the observed spectra, and the \citet{munari;et-al_2005} synthetic spectral library after it was convolved and re-sampled to match the observations.
 The comparison regions used for analysis were 4900-5200\,{\AA} and 5575-5725\,{\AA}.
-In general, temperatures between the two studies agree within the uncertainties, with our temperatures being marginally (23-175 K) hotter.
-The only noteworthy exception is J223811-104126, where we find an effective temperature of 5110\,K, ${\sim}$536\,K cooler than the 5646\,K found by \citet{wylie-de-boer;et-al_2012}.
+In general, temperatures between the two studies agree within the uncertainties.
+The only noteworthy exception is J223811-104126, where we find an effective temperature of 5140\,K, ${\sim}$500\,K cooler than the 5646\,K found by \citet{wylie-de-boer;et-al_2012}.
 Similarly, \citet{williams;et-al_2011} report a hotter effective temperature of 5502\,K from low-resolution spectra.
@@
 
-Photometric temperatures only lend marginal weight towards our spectroscopic temperatures.
+Photometric temperatures only lend marginal argumentative weight towards our spectroscopic temperatures.
 If the \citet{schlegel;et-al_1998} dust maps are employed, then the \citet{alonso;et-al_1999} and \citet{casagrande;et-al_2010} relations estimate the effective temperatures to be between 5104\,K and 5367\,K.
-Our spectroscopic temperature of 5110\,K is closer to the \citet{alonso;et-al_1999} prediction, but not in disagreement with the \citet{casagrande;et-al_2010} relation.
-If we employ the reddening of $E(B-V) = 0.12$ that we have determined from interstellar Na D1 lines, the photometric temperatures increase slightly by ${\sim}100$\,K, still within the uncertainties of the \citet{alonso;et-al_1999} scale, but in less agreement with the \citet{casagrande;et-al_2010} scale.
-We find the surface gravity for J223811-104126 to be $3.00 \pm 0.50$, placing this star at the base of the red giant branch.
-Thus, our spectroscopic temperatures should be in slightly better agreement with the \citet{alonso;et-al_1999} scale for giant stars, rather than the \citet{casagrande;et-al_2010} dwarf/sub-giant scale.
+Our spectroscopic temperature of 5110\,K is closer to the \citet{alonso;et-al_1999} prediction, but not in disagreement with the \citet{casagrande;et-al_2010} relation either.
+If we employ the reddening of $E(B-V) = 0.12$ that we have determined from interstellar Na D1 line, the photometric temperature increases slightly by ${\sim}100$\,K, still within the uncertainties of the \citet{alonso;et-al_1999} scale, but in less agreement with the \citet{casagrande;et-al_2010} scale.
+We find the surface gravity for J223811-104126 to be 3.00 $\pm$ 0.50, placing this star at the base of the red giant branch.
+Thus, if J223811-104126 is a giant star, our spectroscopic temperatures should be in slightly better agreement with the \citet{alonso;et-al_1999} scale, rather than the \citet{casagrande;et-al_2010} dwarf/sub-giant scale.
 However, \citet{williams;et-al_2011} and \citet{wylie-de-boer;et-al_2012} find this star to be a sub-giant, with a surface gravity $\log{g} = 4.16$ and 4.60 respectively.
-In this scenario, their temperatures are 150\,K and 300\,K hotter than the \citet{casagrande;et-al_2010} prediction for \citet{williams;et-al_2011} and \citet{wylie-de-boer;et-al_2012} respectively.
-If our reddening is employed, then the \citet{williams;et-al_2011} and \citet{casagrande;et-al_2010} temperatures are in good agreement, yet still 175\,K cooler than the \citet{wylie-de-boer;et-al_2012} measurement.
+The \citet{williams;et-al_2011} and \citet{wylie-de-boer;et-al_2012} temperatures are 150\,K and 300\,K hotter than the \citet{casagrande;et-al_2010} prediction respectively.
+If our extinction value is employed, then the \citet{williams;et-al_2011} and \citet{casagrande;et-al_2010} temperatures are in good agreement, yet still 175\,K cooler than the \citet{wylie-de-boer;et-al_2012} measurement.
 
@@
 
-In the \citet{wylie-de-boer;et-al_2012} study, the surface gravity was also determined during the $\chi^2$ minimization process.
+In the \citet{wylie-de-boer;et-al_2012} study, the surface gravity was determined during the $\chi^2$ minimization process.
 Again, with the exception of J223811-104126, our surface gravities are largely in agreement.
 The only other noteworthy difference in surface gravity is for J221821-183424, where we find a lower gravity of $\log{g} = 0.80 \pm 0.30$ where \citet{wylie-de-boer;et-al_2012} find $\log{g} = 1.45 \pm 0.35$\,cm\,s$^{-2}$.
-Given the difference in $S/N$ and resolution between these studies, this difference is not concerning.
-
-\citet{wylie-de-boer;et-al_2012} calculate microturbulence with the empirical relationships from \citet{Reddy;et-al_2003} for dwarfs and \citet{fulbright_2000} for giants.
-These relationships are based upon derived temperature and surface gravities.
-Our published microturbulence values agree excellently with the values presented in \citet{wylie-de-boer;et-al_2012}, again with the exception of J223811-104126, where the difference in $v_{mic}$ is directly attributed to the differences in other stellar parameters.
+Given the difference in $S/N$ and resolution between these studies, this difference is not too concerning.
+
+\citet{wylie-de-boer;et-al_2012} calculate microturbulence from empirical relationships derived by \citet{Reddy;et-al_2003} for dwarfs and \citet{fulbright_2000} for giants.
+These relationships are based upon the effective temperature and surface gravity.
+Our published microturbulence values agree excellently with the values presented in \citet{wylie-de-boer;et-al_2012}, again with the exception of J223811-104126, where the difference in $v_{t}$ can be  directly attributed to the offsets in other stellar parameters.
 
@@
 Here we discuss the potential causes for these discrepancies.
-In the \citet{wylie-de-boer;et-al_2012} study, after the stellar parameters ($T_{eff}$, $\log{g}$, $v_{t}$, and an initial [Fe/H] estimate) had been determined, the authors synthesized Fe \textsc{I} and \textsc{II} lines to derive a final [Fe/H] abundance and an associated uncertainty.
-The spectrum synthesis code \textsc{moog} was used to derive abundances for individual Fe\,\textsc{I} and Fe\,\textsc{II} lines, and the \citet{castelli;kurucz_2003} stellar atmosphere models (the same ones used in this study) were employed.
+In the \citet{wylie-de-boer;et-al_2012} study, after the stellar parameters ($T_{eff}$, $\log{g}$, $v_{t}$, and an initial [Fe/H] estimate) had been determined, the authors synthesized Fe \textsc{i} and \textsc{ii} lines individually using the spectrum synthesis code \textsc{moog}.
+\citet{castelli;kurucz_2003} stellar atmosphere models were employed \--- the same ones used in this study, albeit the interpolation schemes will have subtle differences.
 The median abundance of Fe\,I lines was taken as the overall stellar metallicity, scaled using the \citet{grevesse;sauval_1998} solar abundances.
 
-The study of \citet{wylie-de-boer;et-al_2012} is of slightly lower resolution ($R = 25,000$ compared to $R = 28,000$ presented here), but with a much lower $S/N$ ratio: $\sim{}25$ compared to $>100$ per pixel element achieved here.
-Given the lower spectral resolution and modest $S/N$ in their study, there are fewer unblended absorption lines available.
-In fact, there are very few transitions present in their published line list: only 14 Fe\,I lines and 3 Fe\,II lines were available.
-For contrast, our metallicity determinations are based off X Fe\,I and Y Fe\,II lines.
+The study of \citet{wylie-de-boer;et-al_2012} is of slightly lower resolution ($R = 25,000$ compared to $R = 28,000$ presented here), but with a much lower $S/N$ ratio: $\sim{}25$ pixel$^{-1}$ compared to $>100$ pixel$^{-1}$ achieved here.
+Given the lower spectral resolution and modest $S/N$ in the \citet{wylie-de-boer;et-al_2012} study, there are fewer unblended absorption lines available.
+In fact, there are very few transitions present in their published line list: only 14 Fe\,\textsc{i} lines and 3 Fe\,\textsc{ii} lines were available.
+For contrast, our metallicity determinations are usually based from ${\sim}$50 Fe\,I and ${\sim}$13 Fe\,II lines.
 Given the metallicity of these stars and the spectral coverage (4120 to 6920 {\AA}), it is somewhat surprising that there were not more unblended transitions available to \citet{wylie-de-boer;et-al_2012}.
@@
 The line list employed in the \citet{wylie-de-boer;et-al_2012} study contained fewer lines, and employed different oscillator strengths than what we have used.
-The oscillator strengths in the \citet{wylie-de-boer;et-al_2012} study are astrophysical, and were derived from a reverse analysis using the \citet{hinkle;et-al_2003} solar atlas.
-Suspecting the metallicity discrepancy may be caused by the differing line lists, we have redone our analysis using the \citet{wylie-de-boer;et-al_2012} line list and their published stellar parameters.
+The oscillator strengths in the \citet{wylie-de-boer;et-al_2012} study are astrophysical, and were derived from a reverse analysis from the \citet{hinkle;et-al_2003} solar atlas.
+Suspecting the differing line lists may be the cause of the  metallicity discrepancy, we reanalysed our data using the \citet{wylie-de-boer;et-al_2012} line list and stellar parameters.
 Indeed, we arrive at very similar metallicities to \citet{wylie-de-boer;et-al_2012}.
-Without using their published stellar parameters a priori, with a `blind' analysis using their line list we arrive at similar stellar parameters.
-However, we note that one Fe\,\textsc{I} transition at 6420.060\,\AA{} in their line list was not detected in any of our stars at the $3-\sigma$ level, even though the S/N at this point exceeds 120 per pixel element in every observation.
-Thus, for this comparative analysis a maximum of 13 Fe\,\textsc{I} and 3 Fe\,\textsc{II} lines were available to us.
-
-Given the line list employed in the \citet{wylie-de-boer;et-al_2012} study, the overall data quality and the lack of suitable iron lines available for analysis, it appears the Aquarius stream stars have conspired to present a tight metallicity distribution function of $\sigma(\mbox{Fe/H}) = 0.10$\,dex -- suggestive of a globular cluster origin.
+Without using their published stellar parameters a priori, in a `blind' analysis employing just the \citet{wylie-de-boer;et-al_2012} line list, we arrive at similar stellar parameters.
+However, we note that one Fe\,\textsc{i} transition at 6420.060\,\AA{} in the \citet{wylie-de-boer;et-al_2012} line list was not detected in any of our stars at the $3-\sigma$ level, even though the $S/N$ at this point exceeds 115 pixel$^{-1}$ in every observation.
+Thus, for this comparative analysis a maximum of 13 Fe\,\textsc{i} and 3 Fe\,\textsc{ii} lines were available to us.
+
+Given the line list employed in the \citet{wylie-de-boer;et-al_2012} study, the overall data quality and the lack of suitable iron lines available for analysis, it appears the Aquarius stream stars conspired to present a tight metallicity distribution function of $\sigma(\mbox{Fe/H}) = 0.10$\,dex.
+When viewed in light of enhanced Ni, Na abundances, this chemistry is suggestive of a globular cluster origin.
 Our analysis of high-resolution spectra with high $S/N$ reveals a much broader metallicity distribution for the stream.
 With just five stars -- if we assume all our stars are members -- we find the stream metallicity varies from $\mbox{[Fe/H]} = -0.65$ to --1.60\,dex.
-Although this is a small sample, we find the calculated median abundance and standard deviation to be $\mbox{[Fe/H]} = X.XX \pm X.XX$\,dex, more in line with the \citet{williams;et-al_2011} chemistry.
+Although this is a small sample, we find the calculated median abundance and standard deviation to be $\mbox{[Fe/H]} = -1.26 \pm 0.32$\,dex.
 
@@
 Extensive studies looking at stars in globular clusters have revealed variations in light-element abundances, most notably an anti-correlation in sodium and oxygen content \citet[][and references therein]{norris;da_costa_1995,carretta;et-al_2009_na_o}.
-This pattern has been repeatedly demonstrated in all well-studied globular clusters, although the strength of the anti-correlation varies between systems.
+This chemical pattern has been repeatedly demonstrated in every well-studied globular cluster, although the strength of the anti-correlation varies in each system.
 Between generations of stars within a globular cluster, oxygen is converted into nitrogen, reducing the overall oxygen abundance.
 Even though oxygen undergoes internal mixing during its evolution along the giant branch, it is now well established that any observed abundance variations due to such mixing is limited to Li, C, and N.
-Therefore, the observed anti-correlations in light elements required a different astrophysical explanation.
-
-% more on background
+Therefore, the light element anti-correlation required a different astrophysical explanation.
+
+Sodium is mainly produced through through carbon burning in massive stars by the dominant $^{12}\mbox{C}(^{12}\mbox{C}, p)^{23}\mbox{Na}$ process.
+The final Na abundance is dependent on the neutron excess of the star, which slowly increases during carbon burning due to weak interactions \citep{arnett;truran_1974}.
+Massive stars ($>8 M_\odot$) eventually deliver their manufactured sodium to the interstellar-medium through SN II events.
+Because the eventual SN II explosion is devoid of any significant beta-decay processes, the neutron excess of the exploded material is representative of the pre-explosion abundance.
+
+The explosive material eventually condenses to form the next generation of stars, which will have a net increase in their neutron excess with respect to when their predecessors formed.
+Since the Na-production rate is correlated with the neutron excess, an overall increase in the total Na and Na-production rate between stellar generations is expected.
+Thus, an increase in the Na abundance between generations of massive stars is a natural consequence of nucleosynthesis.
+Sodium content also becomes important for production of Ni during the SN II event (see \S\ref{sec:na-ni}) because $^{23}$Na is the only stable isotope produced in significant quantities during the C- (or O-) burning stages.
+A small fraction of $^{22}$Na is also forged through proton capture on $^{21}$Ne in the carbon shell, an effect which is enhanced by neutrinos spallating abundant elements like $^{16}$O and $^{20}$Ne, making free protons available for capture \citep{woosley;weaver_1995}.
 
 % discuss three components
-\citet{carretta;et-al_2009_na_o} defined three components of stars following this abundance pattern within a population: primordial, intermediate, and extreme components.
+\citet{carretta;et-al_2009_na_o} defined three components of stars the Na-O anti-correlation within a population: primordial, intermediate, and extreme components.
 The [Na/Fe] and [O/Fe] abundances for a given star defines which component it belongs to.
@@
 For a well-studied system, stars with the lowest cluster [Na/Fe] abundances are characterised as primordial.
-An intermediate population -- the second-generation of stars -- will have super-solar sodium abundances, and demonstrate a slight depletion in oxygen content.
+An intermediate component \--- the second-generation of stars \--- will have super-solar sodium abundances, and demonstrate a slight depletion in oxygen content.
 The oxygen exhaustion rate is ultimately dependent on the star-formation history of the cluster environment.
-The intermediate population is sub-divided based on how much the O and Na abundances depart from the primordial population: stars with [O/Na]$ > -0.9$ dex are classified as belonging to an extreme component of this Na-O pattern because they differ greatly from the primordial cluster abundance.
+The intermediate population is sub-divided based on how much the sodium and oxygen abundances depart from the primordial population: stars with [O/Na]$ > -0.9$ dex are classified as belonging to an extreme component of this Na-O pattern because they differ greatly from the primordial cluster abundance.
 The extreme O-depletion component has only been observed in a few clusters (preferentially more massive clusters with extended horizontal branches), indicating an long-lasting star-formation history in more massive clusters.
 
-% discuss the production of Sodium
-
 % Discuss the depletion of oxygen over time. What are the possible astrophysical explanations for this depletion
-The exact astrophysical mechanism for oxygen depletion between generations of stars in globular clusters is still under debate.
-However, it is clear that this trend has been well-demonstrated empirically.
 Several hypotheses have been proposed in order to account for oxygen depletion between stellar generations, including massive binaries \citep{de_mink;et-al_2009} or fast-rotating massive stars \citep{decressin;et-al_2007}.
@@
 It is clear that careful consideration must be given inferring star-formation histories from observed stellar abundances.
-In addition to the normal care afforded for measuring elemental abundances from high-resolution spectroscopic data, attention must be given to telluric absorption, contamination from nickel blends, and NLTE corrections when deriving oxygen abundances.
-Furthermore, when characterising the oxygen depletion rate -- and hence the strength of the Na-O anti-correlation in a given cluster -- it is vital to obtain observations for stars belonging to all three components (where possible).
-If only a primordial sample of stars in a globular cluster is observed, then their [Na/Fe] and [O/Fe] abundances will be indistinguishable from halo stars of a similar metallicity.
+In addition to the normal care afforded for measuring elemental abundances from high-resolution spectroscopic data, attention must be given to telluric absorption, contamination from nickel blends, as well as NLTE and 3D effects when calculating oxygen abundances.
+Furthermore, when characterising the oxygen depletion rate -- the strength of the Na-O anti-correlation in a given cluster -- it is vital to sample stars belonging to all three components, where possible.
+If only a primordial sample of stars in a globular cluster is observed, their [Na/Fe] and [O/Fe] abundances will be indistinguishable from halo stars of a similar metallicity.
 In such a scenario, any inferred anti-correlation could equally be explained by intrinsic chemical scatter or observational uncertainties.
@@
 \citet{wylie-de-boer;et-al_2012} measured [Na/Fe] and [O/Fe] abundances for four of their six Aquarius stream members.
-This research has four stars in common with the \citet{wylie-de-boer;et-al_2012} study, but sodium and oxygen measurements exist for only three stars intersecting both samples.
-We have measurements for all of our stars, including J223811-104126, for which we ascertained an upper limit from the [O \textsc{I}] lines of [O/Fe] $< 0.5$ dex, and a corrected abundance of $\mbox{[O/Fe]} = 0.14$ from the O \textsc{I} triplet lines.
+This research has four stars in common with the \citet{wylie-de-boer;et-al_2012} study, but sodium and oxygen measurements exist for only three stars intersecting both samples, as the data quality for X in the \citet{wylie-de-boer;et-al_2012} study prohibited measuring sodium and oxygen.
+We have measurements for all of our stars, including J223811-104126, for which we ascertained an upper limit from the [O \textsc{i}] lines of [O/Fe] $< 0.5$ dex, and a corrected abundance of $\mbox{[O/Fe]} = 0.14 \pm 0.08$ from the O \textsc{i} triplet lines.
+In Figure \ref{fig:o-na} we have plotted theses abundances, including the corrected value for J223811-104126 rather than an upper limit.
 
@@
 In fact, they have a slight positive relationship: their Na-enhanced stars show an increased oxygen content, contrary to an expected oxygen depletion between stellar generations within a globular cluster.
-This trend is drawn from a sample of only four stars -- the same as this study if our upper limit for J223811-104126 is excluded.
 
@@
 
-The Na-O anti-correlation is likely the result of complete CNO and Ne-Na cycles of proton reactions in globular cluster stars.
+%The Na-O anti-correlation is likely the result of complete CNO and Ne-Na cycles of proton reactions in globular cluster stars.
 There is also evidence in some clusters that the Mg-Al nucleosynthesis cycle is also active.
 
- The conditions required for these reactions are significantly higher than the CNO and Ne-Na cycle: temperatures of 70 MK are required for the Mg-Al channel instead of just 25 MK for the CNO/Ne-Na cycles \citet{charbonnel;prantzos_2006}.
+Bah.
+
+% what is the site and product of the Mg-Al cycle
+
+% Si is increased over time as well
+
+% what signature of this is seen in globular clusters compared to field stars
+
+% what globular clusters exhibit this phenomena? contrast it to the Na-O cycle
+
+% variations within a cluster in Mg, Al
+
+% what do we see in our Aquarius stars
+
+% the case of C2225316
 
@@
 % need to say about [alpha/fe] and [na/fe] with distance
-Detailed chemical studies of nearby disk stars have noted a correlation with [Na/Fe] and [Ni/Fe].
-This relationship was first hinted in \citet{nissen;schuster_1997}, where they found eight stars that were underabundant in [$\alpha$/Fe], [Na/Fe] and [Ni/Fe].
+Detailed chemical studies of nearby disk stars have noted a correlation with [Na/Fe] and [Ni/Fe] abundances.
+This relationship was first hinted in \citet{nissen;schuster_1997}, where the authors found eight stars that were underabundant in [$\alpha$/Fe], [Na/Fe] and [Ni/Fe].
 Interestingly, the authors noted that stars at larger galactocentric radii were most deficient in these elements.
 \citet{fulbright_2000} saw a similar signature: stars with low [Na/Fe] were only found at large ($R_\odot > 20$\,kpc) distances.
-\citet{nissen;schuster_1997} proposed that as the outer halo is thought to have been built up through the accretion of dSph satellites, then the Na-Ni pattern may be a chemical indicator of merger history in the galaxy.
-
-With additional data from \citet{nissen;schuster_2011}, the Na-Ni relationship was found to be slightly steeper than originally proposed.
+\citet{nissen;schuster_1997} proposed that since the outer halo is thought to have been built up through the accretion of dSph satellites, then the Na-Ni pattern may be a chemical indicator of merger history in the galaxy.
+
+With additional data from \citet{nissen;schuster_2011}, the Na-Ni relationship was found to be slightly steeper than originally put forward.
 The pattern exists only for metal-rich stars $-1.5 < \mbox{[Fe/H]} < -0.5$ dex, and is not seen in metal-poor dSph stars, providing a potentially useful indicator for investigating chemical evolution.
-However, it is crucial to note that although there are only a few dSph stars in the $-1.5 < \mbox{[Fe/H]} < -0.5$ metallicity regime with [Na/Fe], [Ni/Fe] measurements, they agree reasonably well with the galactic trend.
+
+%However, it is crucial to note that although there are only a few dSph stars in the $-1.5 < \mbox{[Fe/H]} < -0.5$ metallicity regime with [Na/Fe], [Ni/Fe] measurements, they agree reasonably well with the galactic trend.
 
 The correlation between sodium and nickel content is the nucleosynthetic result of neutron capture in massive stars.
-As previously discussed, the total Na abundance is controlled by the neutron excess, which limits the production of $^{58}$Ni during SN II events.
+As previously discussed, the total Na abundance is controlled by the neutron excess, which limits the production of $^{58}$Ni during Sn \textsc{ii} events.
 When the inevitable supernova begins, the core photodissociates into neutrons and protons, allowing the temporary creation of $^{56}$Ni before it decays to $^{56}$Fe.
@@
 
-Stars originating in dwarf spheroidal galaxies and globular clusters have very different star formation histories.
-Consequently they exhibit chemical patterns that reflect their nucleosynthetic antiquity.
+Stars originating in dwarf spheroidal galaxies and globular clusters have very different star formation environments.
+Consequently, they exhibit chemical patterns that reflect their nucleosynthetic antiquity.
 Dwarf spheroidal stars do not demonstrate enhanced sodium or nickel, as there has been a relatively negligible linage of massive stars undergoing supernova.
@@
 Given the extended star formation within the Milky Way disk, globular cluster stars and disk stars are indiscernible in the Na/Ni plane: they both show an extended contribution of massive stars.
+
 The most that can be inferred from the Na, Ni abundances of Aquarius stream stars is that their star formation history is less like a dwarf spheroidal environment, and more representative of an environment more like a globular cluster or the MW disk.

### 2013-01-01 2012-aqs/figures/plot-spectra.py
Updated plots + added rest normalized spectra

@@ -1,0 +1,60 @@
+import matplotlib.pyplot as plt
+import numpy as np
+
+from specutils import Spectrum1D
+
+accompaning_texts = [
+        "C2225316-14437\t4325 / 1.26 / $-$1.26",
+        "C2306265-085103\t4170 / 0.85 / $-$1.17",
+        "J221821-183424\t4590 / 0.90 / $-$1.61",
+        "J223504-152834\t4590 / 2.15 / $-$0.68",
+        "J22381-104126\t5140 / 2.96 / $-$1.45"
+        ]
+
+spectrum_filenames = ['c2225316-14437_rest.fits', 'c2306265-085103_rest.fits', 'j221821-183424_rest.fits', 'j223504-152834_rest.fits', 'j22381-104126_rest.fits']
+
+order = [1, 0, 3, 2, 4]
+
+# order them
+accompaning_texts_ = []
+spectrum_filenames_ = []
+for n in order[::-1]:
+    accompaning_texts_.append(accompaning_texts[n])
+    spectrum_filenames_.append(spectrum_filenames[n])
+
+spectrum_filenames = spectrum_filenames_
+accompaning_texts = accompaning_texts_
+
+xlims = [6540, 6600]
+#xlims = [6150, 6160]
+
+text_x_offset = 2
+text_y_offset = 0.10
+text_fontsize = 9
+
+label_fontsize = 10
+
+
+fig = plt.figure(figsize=(12,6))
+fig.subplots_adjust(left=0.05, bottom=0.10, right=0.95, top=0.95)
+ax = fig.add_subplot(111)
+
+for i, (accompaning_text, spectrum_filename) in enumerate(zip(accompaning_texts, spectrum_filenames)):
+
+    spectrum = Spectrum1D.load(spectrum_filename)
+
+    ax.plot(spectrum.disp, spectrum.flux + i, 'k')
+    lhs_text, rhs_text = accompaning_text.split('\t')
+    ax.text(xlims[0] + text_x_offset, text_y_offset + 1 + i, lhs_text, fontsize=text_fontsize, horizontalalignment='left')
+    ax.text(xlims[1] - text_x_offset, text_y_offset + 1 + i, rhs_text, fontsize=text_fontsize, horizontalalignment='right')
+
+
+ax.set_xlabel('Wavelength, $\lambda$ (${\AA}$)', fontsize=label_fontsize)
[…]

### 2013-01-01 2012-aqs/figures/specutils.py
Added specutils file for easy spectra plotting

@@ -1,0 +1,920 @@
+# This module contains a temporary Spectrum1D class for use until it's
+# replaced by the upcoming astropy.specutils.Spectrum1D module.
+
+import os
+import json
+import logging
+import numpy as np
+import pyfits
+
+
+from scipy import interpolate, ndimage, polyfit, poly1d
+
+__all__ = ['Spectrum', 'Spectrum1D', 'stitch', 'pyfits']
+
+
+class Spectrum(object):
+    """A temporary class holder for a multi-dimensional Spectrum object until it
+    can be replaced with astropy.NDData."""
+
+    def __init__(self, disp, flux, headers={}):
+        """Initializes a `Spectrum` object with the given (multi-dimensional)
+        dispersion and flux arrays.
+
+        Inputs
+        ----
+        disp : `np.ndarray`
+            Dispersion of the spectra.
+
+        flux : `np.ndarray`
+            Flux values for each dispersion point.
+
+        headers : `dict`
+            Headers.
+        """
+
+        self.disp = disp
+        self.flux = flux
+        self.headers = headers
+        self.num_orders = self.flux.shape[1] if len(self.flux.shape) > 1 else len(self.flux)
+
+        return None
+
+    @classmethod
+    def load_multispec(cls, filename):
+        """Reads in a FITS multispec file into a `Spectrum` object.
+
+        Inputs
+        ----
+        filename : str
+            Multi-spec FITS filename to read.
+        """
+
+        if not os.path.exists(filename):
+            raise IOError, "Filename '%s' does not exist." % (filename, )
+
+        with pyfits.open(filename) as image:
+            headers = image[0].header
+            flux = image[0].data
+
+        headers_dict = {}
+        for k, v in headers.iteritems():
+
+            try:
+                str(v)
+                json.dumps(v)
+
+            except TypeError:
+                continue
+
+            if headers_dict.has_key(k):
+                headers_dict[k] += v
+
+            else:
+                headers_dict[k] = v
+
+
+        # Determine number of orders
+        num_pixels = flux.shape[-1]
+        num_orders = 1 if len(flux.shape) == 1 else flux.shape[-2]
+
+        # Try linear dispersion
+        try:
+            crval = headers['crval1']
+            crpix = headers['crpix1']
+            cd = headers['cd1_1']
+            ctype = headers['ctype1']
+
+            if ctype.strip() == 'LINEAR':
[…]

### 2013-01-13 2012-aqs/draft-aqs.tex
Updated text

@@
 
-\shorttitle{The Aquarius Stream Progenitor Was Not A Globular Cluster}
+\usepackage{amssymb,graphics} % for resolution symbol
+
+\shorttitle{No Evidence for the Aquarius Co-Moving Group Resulting from a Disrupted Classical Globular Cluster}
 \shortauthors{Casey et al}
@@
 
-\title{The Aquarius Stream Progenitor Was Not A Globular Cluster: \\ Its History Could Be Far More Interesting\altaffilmark{1}}
+\title{No Evidence for the Aquarius Co-Moving Group \\Resulting from a Disrupted Classical Globular Cluster\altaffilmark{1}}
 
@@
 \begin{abstract}
-We present a detailed dynamic and chemical analysis of 5 Aquarius stream giants observed using the MIKE spectrograph on the Magellan Clay Telescope.
-Assuming all candidates are stream members, our data indicate the Aquarius stream has a large metallicity dispersion.
-We find no Na-O anti-correlation, and no chemical evidence that the stream is a result of a disrupted globular cluster, contrary to \citet{wylie-de-boer;et-al_2012}.
+We present a detailed analysis of five Aquarius stream giant stars observed using the MIKE spectrograph on the Magellan Clay telescope.
+Enhanced sodium and nickel abundances suggest the group is not the result of a dwarf satellite galaxy, and that its chemical enrichment environment is more like a globular cluster or the thick disk of the Milky Way.
+However, we find no evidence that the group is a result of a disrupted globular cluster.
+Our data indicate the Aquarius stream has a large metallicity dispersion of $\sigma(\mbox{[Fe/H}]) = 0.32$\,dex.
+No inverse Na-O correlation is present, and we find a positive Mg-Al relationship.
+Chemically, the group is indistinguishable from the Milky Way thick disk with the exception of one very interesting candidate, which is most likely tidal debris from $\omega$-Centurai.
+Assuming all other candidates are Aquarius members, we propose the co-moving group has arisen from a minor merger in the Milky Way's thick disk.
 
@@
 In our own stellar halo, we see ongoing evidence of these accretion events.
-As accreting satellites infall onto the galaxy, tidal forces disrupt the dwarf, hurtling stars in leading and trailing streams.
-The phase space information of stars within such streams are sensitive to the galactic potential.
+As accreting satellites infall onto the galaxy, tidal forces disrupt the dwarf, hurtling stars in leading and trailing directions.
+The phase space information of stars within these `stellar streams' are sensitive to the galactic potential.
 They can collectively constrain the fraction and distribution of accreted matter in the stellar halo, the sub-halo mass function, as well as the shape and extent of dark matter in the Milky Way.
-Moreover, individual chemical abundances can constrain the  precise nucleosynthesis sites where elements are forged, and can collectively trace the chemical evolution of the galaxy.
+Moreover, individual chemical abundances can constrain the  precise nucleosynthesis sites where elements are forged, as well as trace the chemical evolution of the galaxy.
 
@@
 However, as \citet{helmi;white_1999} point out, these observing strategies are only successful for identifying streams that are sufficiently distant from the solar neighbourhood.
-A nearby stream, within $\sim{}$10\,kpc, will not appear as an on-sky over-density, as the stars would be sparsely positioned across the sky.
+A nearby stream, within $\sim$10\,kpc, will not appear as an over-density, as the stars would be sparsely positioned across the sky.
 Such substructures would only be detectable by their kinematics, or perhaps precise chemical abundances through a `chemical tagging' approach (e.g.
@@
 It is therefore necessary to survey solar neighbourhood stars with spectroscopy in order to detect any nearby substructures.
-The RAVE (Radial Velocity Experiment) began such a survey in 2003 and has observed spectra from over 500,000 stars across 17,000 deg$^{2}$.
+The RAVE (Radial Velocity Experiment) team began such a survey in 2003 and have observed spectra from over 500,000 stars across 17,000 deg$^{2}$.
 As the name suggests, the primary goal of RAVE was to obtain radial velocities for the solar neighbourhood and beyond.
@@
 % Identification of the aquarius stream
-Using these data, \citet{williams;et-al_2011} identified a co-moving group of nearby ($0.5 \lesssim d \lesssim 10$\,kpc) stars in the vicinity of the Aquarius constellation $(l, b) = (60\,^\circ, -55\,^\circ)$.
+Using these data, \citet{williams;et-al_2011} identified a co-moving group of nearby ($0.5\,\mbox{kpc} \lesssim d \lesssim 10\,\mbox{kpc}$) stars in the vicinity of the Aquarius constellation $(l, b) = (60\,^\circ, -55\,^\circ)$.
 Thus, the co-moving group was named the Aquarius stream.
 The stream is most apparent when examining velocities against galactic latitude for stars within $-70\,^\circ < b < -50\,^\circ$.
-\citet{williams;et-al_2011} employed a selection criteria of $-250 < V_{HEL} < -150$\,km s$^{-1}$, $30\,^\circ < l < 75\,^\circ$ and $J > 10.3$ to maximize the contrast between the stream and background, identifying 15 candidates in the process.
-The average heliocentric velocity of these members was found to be $V_{HEL} = -199$\,km s$^{-1}$, with a dispersion of 27\,km s$^{-1}$.
-The radial velocities outputted by the RAVE survey are described to be $\sim2$\,km s$^{-1}$, so the wide kinematic distribution appears to be real.
+\citet{williams;et-al_2011} employed a selection criteria of $-250\,\mbox{km s}^{-1} < V_{HEL} < -150\,\mbox{km s}^{-1}$, $30\,^\circ < l < 75\,^\circ$ and $J > 10.3$ to maximize the contrast between the stream and background, identifying 15 candidates in the process.
+The average heliocentric velocity of these members was found to be $V_{HEL} = -199\,\mbox{km s}^{-1}$, with a dispersion of 27\,km s$^{-1}$.
+The radial velocity uncertainties provided by the RAVE catalog are described to be $\sim$2\,km s$^{-1}$, so the wide kinematic distribution appears to be real.
 
@@
 Upon examining the galactic longitude and velocities of Aquarius stars, the stream appears quite distinct from the halo.
-In order to quantify the statistical likelihood that the Aquarius stream is truly distinct from the halo, \citet{williams;et-al_2011} compared the number of observed RAVE stars within $-70\,^\circ < b < -50\,^\circ$ against the Galaxia \citep{sharma;et-al_2011} and Besan\c{c}on \citep{robin;et-al_2003} galaxy simulations.
-The predicted particles in each model between $-70\,^\circ < b < -50\,^\circ$ were binned in $\Delta{l} \times \Delta{V_{hel}}$ using varying grid cell sizes between $25-70\,^\circ$ and 20-100\,km s$^{-1}$ respectively.
+In order to quantify the statistical likelihood that the Aquarius stream is truly separate from a smooth halo distribution, \citet{williams;et-al_2011} compared the number of observed RAVE stars within $-70\,^\circ < b < -50\,^\circ$ against the Galaxia \citep{sharma;et-al_2011} and Besan\c{c}on \citep{robin;et-al_2003} galaxy simulations.
+The predicted particles in each model between $-70\,^\circ < b < -50\,^\circ$ were binned in $\Delta{l} \times \Delta{V_{hel}}$ blocks using varying grid cell sizes between $25\,^\circ$ to $70\,^\circ$ and $20\,\mbox{km s}^{-1}$ to $100\,\mbox{km s}^{-1}$ respectively.
 The RAVE sample was binned in the same way, and the statistical significance of the over-density is calculated for each cell.
 \citet{williams;et-al_2011} found the stream to be statistically significant ($>$4-$\sigma$) in 96\% of the grid cell sizes employed for the Besan\c{c}on model.
-By sampling the Galaxia model multiple times with varying extinction rates, a similar result was found: between $75\pm15$\,\% to $80\pm18$\,\% of grid cells showed the Aquarius stream to significant at the 4-$\sigma$ level or higher.
+By sampling the Galaxia model repeatedly with varying extinction rates, a similar result was found: between $75\pm15$\,\% to $80\pm18$\,\% of grid cells showed the Aquarius stream to significant at the 4-$\sigma$ level or higher.
 Given the high-latitude and proximity of the stream, it is not surprising that dust had a negligible effect on the statistical significance.
@@
 
-The Aquarius stream has a metallicity of $\mbox{[Fe/H]} \sim -1.0$ \citep{williams;et-al_2011}, slightly more metal-rich than halo stars at the same distance.
-The dispersion in the stream's metallicity has yet to be fully characterised.
+The Aquarius stream has a metallicity of $\mbox{[Fe/H]} \sim -1.0$, slightly more metal-rich than halo stars at the same distance.
 \citet{williams;et-al_2011} found the stream to have an average of $\mbox{[M/H]} = -1.0 \pm 0.4$, compared to $\mbox{[M/H]} = -1.1 \pm 0.6$ for background stars after the same selection cuts had been employed.
 Of the 12 Aquarius stars in the \citet{williams;et-al_2011} discovery sample with stellar parameters, the metallicity range is wide: between --2.02 and --0.33 dex.
-Spectroscopic observations of high resolution with high signal-to-noise ($S/N$) are necessary to accurately determine the metallicity distribution.
-
-To this end, \citet{wylie-de-boer;et-al_2012} obtained high-resolution ($R = 25,000$) spectra with modest $S/N$ ($\sim$30 pixel$^{-1}$) for six Aquarius stream stars.
+Spectroscopic observations of high resolution with high signal-to-noise ($S/N$) are necessary to accurately characterize the stream's metallicity distribution.
+
+To this end, \citet{wylie-de-boer;et-al_2012} obtained high-resolution ($\mathcal{R} = 25,000$) spectra with modest $S/N$ ($\sim$30 pixel$^{-1}$) for six Aquarius stream stars.
 Their data indicate a very narrow metallicity distribution: $\mbox{[Fe/H]} = -1.09 \pm 0.10$\,dex extending between $\mbox{[Fe/H]} = -1.25$ to $-0.98$\,dex.
-The largest [Fe/H] discrepancy between the two studies was $\Delta\mbox{[Fe/H]} = -0.66$\,dex for the most metal-rich star in the \citet{williams;et-al_2011} sample.
+The largest [Fe/H] discrepancy between the \citet{williams;et-al_2011} and \citet{wylie-de-boer;et-al_2012} study was $\Delta\mbox{[Fe/H]} = -0.66$\,dex for the most metal-rich star in the \citet{williams;et-al_2011} sample.
 The most metal-poor star in the \citet{williams;et-al_2011} study was not observed by \citet{wylie-de-boer;et-al_2012}.
-The negligible level of chemical scatter observed in the \citet{wylie-de-boer;et-al_2012} sample is typical of what is found in globular or open clusters.
-
-In addition to ascertaining stellar parameters, \citet{wylie-de-boer;et-al_2012} measured light element abundances for the Aquarius stream stars -- the only study to do so until now.
-Their study primarily focussed on light elemental abundances: Na, O, Ni, Mg, and Al.
+In addition to ascertaining stellar parameters, \citet{wylie-de-boer;et-al_2012} measured elemental abundances for the Aquarius stream stars -- the only study to do so until now.
+Their study primarily focussed on light elements: Na, O, Ni, Mg, and Al.
 Chemical patterns in these light elements arise as natural consequences of nucleosynthetic processes in massive stars.
-Thus, by observing the abundances of light elements in stars that formed together, we can infer the star-formation history and environment.
-More specifically, an anti-correlation in sodium and oxygen abundance has been identified in all well-studied globular clusters to date.
+These patterns have been repeatedly observed in globular clusters.
+Specifically, an anti-correlation between sodium and oxygen abundance has been found to be ubiquitous to globular clusters.
 Originally this was thought to arise from internal mixing along the giant branch.
-However, dwarf stars were found to exhibit strong Na-enhancement and O-depletions, contrary to what would be expected if the Na-O anti-correlation was purely a result of internal mixing.
+However, dwarf stars were later found to exhibit strong Na-enhancement and O-depletions, contrary to what would be expected if the Na-O anti-correlation was purely a result of internal mixing.
 It is well known now that photospheric abundance variations resulting from internal mixing are limited to C, N and Li.
@@
 All program stars were observed in July 2011 in good seeing at low airmass (Table \ref{tab:observations}), and X additional standard stars were observed in March 2011.
-All observations were taken using a 1.0'' slit, providing a spectral resolution of $R = 28,000$ in the blue and $R = XX,XXX$ in the red arm.
-The total exposure times for our program stars varied per star from X-Y seconds to ensure a Signal-to-Noise ratio (S/N) in excess of 100 per pixel element at 600 nm.
+All observations were taken using a 1.0'' slit, providing a spectral resolution of $\mathcal{R} = 28,000$ in the blue and $\mathcal{R} = 22,000$ in the red arm.
+The total exposure times for our program stars varied per star from X-Y seconds to ensure a Signal-to-Noise ratio ($S/N$) ratio in excess of 100 per pixel element at 600 nm.
 
@@
 One of our standard stars, HD 41667, was also reduced using standard extraction and calibration methods in \textsc{iraf}.
-The resultant spectra from both reduction approaches were compared for residual fringing, S/N, and wavelength calibration.
-No noteworthy differences were present, and thus the CarPy pipeline was utilized for the remainder of the reductions.
-Each reduced echelle order was carefully normalized using a third order spline.
+The resultant spectra from both reduction approaches were compared for residual fringing, $S/N$, and wavelength calibration.
+No noteworthy differences were present, and the CarPy pipeline was utilized for the remainder of the reductions.
+Each reduced echelle order was carefully normalized using a third order spline with defined knot spacing.
 Normalized orders   were stitched together to provide a single one-dimensional spectrum from 3800-9400\,\AA{}.
 
-The white dwarf HR 6141 was observed on X with a S/N of 400 pixel$^{-1}$ as a telluric standard.
-The $S/N$ ratio for HR 6141 exceeds the $S/N$ ratio in any of our program stars.
+The white dwarf HR 6141 was observed on X as a telluric standard.
+The $S/N$ ratio for HR 6141 exceeds that in any of our other standard or  program stars.
 Although the atmospheric conditions at Las Campanas Observatory are certain to change throughout the night and between observing runs, we are primarily using this spectra to identify lines that are affected by telluric absorption.
@@
 Fitted Gaussian profiles provide us with a measured equivalent width, the full-width half-maximum and the central wavelength of the profile.
-Thus, the residual radial velocity can be found from the ratio of the central and rest line wavelengths.
+Thus, the residual radial velocity can be found from the ratio of the central and rest wavelengths.
 The final radial velocity for the star is provided by the initial velocity and the mean of $\sim$200 residual line velocity measurements.
-Figure \ref{fig:line-velocities} shows the line velocities for HD41667 after being placed at pseudo-rest using our cross-correlation velocity of 314.4\,km s$^{-1}$.
+Figure \ref{fig:line-velocities} shows the line velocities for HD 41667 after being placed at pseudo-rest using our cross-correlation velocity of 314.4\,km s$^{-1}$.
 As expected, the mean residual offset is small ($-0.75$\,km s$^{-1}$), and the standard deviation is 0.79\,km s$^{-1}$ from 164 line measurements.
@@
 The radial velocities published in Table \ref{tab:observations} are the final values from this two-step method.
-Heliocentric velocities agree quite well with the \citet{williams;et-al_2011} published values: the mean absolute offset is $\langle\Delta{V_{hel}}\rangle = 2.8$\,km\,s$^{-1}$, demonstrating the accuracy of the velocities published by the RAVE survey.
+Heliocentric velocities agree quite well with the \citet{williams;et-al_2011} published values: the mean offset is $\langle\Delta{V_{hel}}\rangle = 2.5 \pm 2.7$\,km\,s$^{-1}$, demonstrating the accuracy of the velocities published in the RAVE catalog.
 
@@
 For lines with hyperfine structure, blended transitions or molecular features, we determined the abundance using a spectral synthesis approach.
-For all other transitions, equivalent widths were measured to determine the abundance.
+For all other transitions, equivalent widths were measured to determine the line abundance.
 
@@
 Measuring the local continuum ensures any errors in our initial normalisation or order-stitching do not propagate through to our equivalent width measurements.
-When determining the local continua, any neighbouring group of pixels that deviate significantly ($>$2-$\sigma$) from the local continua either belong to a persistent cosmic ray hit, or they are trough points of a neighbouring absorption profile.
+When determining the local continuum, any neighbouring group of pixels that deviate significantly ($>$2-$\sigma$) from the local continua either belong to a persistent cosmic ray hit, or they are trough points of a neighbouring absorption profile.
 We attempt to fit a Gaussian profile to each group of deviating pixels, using the current best estimate for the local continuum.
@@
 
-\noindent where the rest wavelength ($\lambda_{r}$) and FWHM ($\sigma$) are free parameters in the iterative fitting process.
+\noindent where the rest wavelength ($\lambda_{r}$) and standard deviation\footnote{Recall $\sigma = 2.355FWHM$} ($\sigma$) are free parameters in the iterative fitting process.
 As a consequence of Eq.
 \ref{eq:chi-weight}, pixels near the rest wavelength are weighted higher than those on the wings, forcing the fitting scheme to disregard blended or crowded regions.
-Although this approach relies on a reasonably accurate radial velocity correction ($<$4\,km s$^{-1}$; which is easily achieved), it greatly improves the accuracy and robustness of the equivalent width measurements.
-
-The results of our iterative Gaussian fitting approach are completely \textit{insensitive} to the initial FWHM guess.
+Although this approach relies on a reasonably accurate initial radial velocity correction ($<$4\,km s$^{-1}$; which is easily achieved), it greatly improves the accuracy and robustness of the equivalent width measurements.
+
+The results of our iterative Gaussian fitting approach are \textit{completely insensitive} to the initial FWHM guess.
 Increasing the initial FWHM estimate from 0.1\,\AA{} to 1 or 2\,\AA{} -- which are unphysically large values for high-resolution spectra -- does not alter either the FWHM or the equivalent width for any of our measurements.
 Only a small increase in computational cost is observed.
-Although we are extremely confident in our automatic equivalent width measurements, every absorption profile was examined by eye for quality, and spurious measurements were excluded.
+Although we are extremely confident in our equivalent width measurements, every absorption profile was examined by eye for quality, and spurious measurements were excluded.
 
@@
 We have verified the approach by comparing our measurements of 156 lines in HD 140283 with the study of \citet{norris;et-al_1996}.
-We only included measurements in the \citet{norris;et-al_1996} study that were not marked with line quality parameters.
+We only included measurements in the \citet{norris;et-al_1996} study that were not marked with questionable line quality parameters.
 Excellent agreement is found between the two studies, which is illustrated in Figure \ref{fig:ew-compare}.
@@
 \tabletypesize{\scriptsize}
-\tablecaption{List of Line Transitions and Equivalent Width Measurements}
+\tablecaption{List of Line Transitions and Equivalent Width Measurements\label{tab:equivalent-widths}}
 \tablehead{
@@
 \end{deluxetable*}
-
+\clearpage
 \clearpage
@@
 
-\subsection{Stellar Parameters}
-The most recent version of the spectral synthesis code \textsc{moog} \citep{sneden;et-al_1973} has been used to derive individual line abundances and stellar parameters.
-This version employs Rayleigh scattering \citep{sobeck;et-al_2011} instead of treating scattering as true absorption, which is particularly important for transitions blue-ward of 450\,nm.
-This is noteworthy, but is less relevant for these analyses as most of our line measurements are red-ward of 450\,nm.
-Absorption lines are assumed to form under the assumption of local thermal equilibrium.
-
-\begin{figure*}[t!]
-	\includegraphics[width=\textwidth]{./figures/spectra-h-alpha.pdf}
-	\caption{Spectra for all Aquarius stream stars.}
-	\label{fig:spectra-h-alpha}
-\end{figure*}
-
-\subsubsection{Effective Temperature}
-The effective temperature for each star was found by demanding a zero-trend in excitation potential and abundance for each measured Fe\,I line.
-In the same way, the microturbulence was found by demanding a zero trend in reduced equivalent width against abundance.
-Linear relationships with slopes of $|0.001|$ dex were considered to be converged.
-
-\subsubsection{Photometric Effective Temperatures}
-\label{sec:photometric-temperatures}
-
-The effective temperatures published for all of our stars in Table \ref{sec:stellar-parameters} have been derived spectroscopically (see \S\ref{sec:effective-teffs}).
-As a consistency check for our spectroscopic temperatures, we have estimated effective temperatures using infrared photometry from the 2MASS catalog.
-The $J-K$ color has been employed for these calculations because it has the least dependence on metallicity.
-
-The Aquarius stream is relatively close and at high-latitude, so significant extinction by dust is not expected.
-The dust maps of \citet{schlegel;et-al_1998} estimate that the extinction for our stars varies between E(B-V) = 0.03 to 0.07 mags.
-However, these maps are not perfect.
-As an alternative to using the \citet{schlegel;et-al_1998} dust maps, the level of extinction towards a star can be found by the strength of the interstellar Na D or K \textsc{i} lines \citep{munari;zwitter_1997}.
-The interstellar lines must be sufficiently separated from the stellar absorption lines in order for the extinction to be measurable.
-Unfortunately this was the case in only one of our stars, J223811.
-We measured the equivalent width of the Na D1 line in J223811 to be 302.4\,m{\AA}, which corresponds to an $\mbox{E(B-V)} = 0.12^{+0.01}_{-0.02}$ according to the \citet{munari;zwitter_1997} relationship.
-This is a significantly higher value than what the \citet{schlegel;et-al_1998} dust map value of $\mbox{E(B-V)} = 0.07$ for J223811.
-For completeness, both extinction values have been used to calculate photometric temperatures.
-
-Although all of our targets are giant stars, two different $T_{eff}$-colour relationships have been employed: the \citet{alonso;et-al_1999} calibration for giants, and the \citet{casagrande;et-al_2010} calibration for dwarfs and sub-giants.
-All photometrically-derived temperatures are listed in \ref{tab:photometric-temperatures}.
-The \citet{alonso;et-al_1999} $J-K$ scale is insensitive to metallicity effects, and is in good agreement with our spectroscopic temperatures.
-For the \citet{casagrande;et-al_2010} $J-K$ relationship, which has a slight metallicity dependency, we have utilized the spectroscopically-derived [Fe/H] values shown in Table \ref{tab:stellar-parameters}.
-
-The effective temperatures found from spectroscopy agree fairly well with the photometric temperature estimates.
-For three of our stars, the temperatures we find are in between the two color-temperature relationships.
-There are two noteworthy deviations: J223504-152834 and J223811-104126.
-For J223504-152834 we find the star to have an effective temperature of 4590\,K, only 10\,K hotter than the \citet{casagrande;et-al_2010} dwarf/sub-giant relationship, yet ${\sim}$500\,K hotter than the \citet{alonso;et-al_1999} estimate.
-Our temperature of 4590\,K is in good agreement with previous spectroscopic determinations (4795\,K; \citet{williams;et-al_2011}, 4597\,K; \citet{wylie-de-boer;et-al_2012}).
-The fact that the \citet{alonso;et-al_1999} photometric temperature relationship for giants predicts a temperature that is ${\sim}$500\,K cooler than the spectroscopically-derived values may be attributed to an underestimated amount of dust towards J223504-152834.
-A higher than expected level of extinction along the line-of-sight would produce cooler photometric temperatures than the true effective temperature.
-An extinction of $E(B-V) = 0.10$ would be required for the \citet{alonso;et-al_1999} relation to yield a temperature of ${\sim}$4500\,K, within the uncertainties of our effective temperature derived from spectroscopy.
-Such a discrepancy in extinction is large, but not unheard of (e.g., see \citet{nataf;et-al}).
-Although we suspect J223504-152834 to have a higher reddening than $E(B-V) = 0.04$, we have adopted the \citet{schlegel;et-al_1998} value for this analysis.
-
-J223811-104126 has two extinction values available: the \citet{schlegel;et-al_1998} value of $E(B-V) = 0.07$ and the 0.12 value  determined from the interstellar Na D1 line.
-Given the inherent difficulties in producing dust maps, and the known problems associated with them, we believe the $E(B-V) = 0.12$ determination to be more accurate.
-However, using the \citet{schlegel;et-al_1998} extinction value with the \citet{alonso;et-al_1999} color-temperature relationship yields excellent agreement (5104\,K) with our spectroscopic temperature of 5140\,K.
-Employing our more accurate reddening determination yields 5215\,K, within the uncertainties of the relationship.
-The \citet{casagrande;et-al_2010} scale is ${\sim}$250\,K hotter in both cases.
-
-With the exception of J223504-152834, the \citet{alonso;et-al_1999} giant relationship agrees well ($\pm$100\,K) with our spectroscopically-derived values.
-The \citet{casagrande;et-al_2010} relationship is also in relatively good agreement (most within 100\,K, largest discrepancy is 220\,K) with our spectroscopic temperatures, although we note that this relation was derived primarily for dwarfs/sub-giants and our candidates are all giant stars.
-
-\begin{deluxetable}{lccccc}
-\tablecolumns{1}
-\tabletypesize{\scriptsize}
-\tablecaption{Reddening \& Photometric Temperatures}
-\tablehead{
-& & & \multicolumn{2}{c}{$T_{phot}$} \\
-\cline{4-5} \\
-	\colhead{Designation} &
-	\colhead{E($B-V$)} &
-	\colhead{$(J-K)_0$} &
-	\colhead{Alonso} &
-	\colhead{Casagrande} \\
-	& (mag) & & (K) & (K)
-}
-\startdata 
-C222531-144370 	& 0.03\phn	& 	0.75 & 4247	&	4391 \\	
-C230626-085103	& 0.05\phn	&	0.82 & 4091	&	4200 \\	
-J221821-183424 	& 0.03\phn	&	0.64 & 4546	&	4747 \\	
-J223504-152834 	& 0.04\phn	&	0.69 & 4110	& 	4579 \\	
-J223811-104126 	& 0.07\phn	&	0.48 & 5104	&	5367 \\	
-				& 0.12\footnote{Extinction derived from interstellar Na D1 line (see \ref{sec:photometric-temperatures})} 			&	0.45 & 5215	&	5484	
-\enddata
-\end{deluxetable}
-
-\subsubsection{Surface Gravity}
-
-The surface gravity for all stars was found by forcing the mean Fe\,\textsc{i} and Fe\,\textsc{ii} abundances to be equal.
-The process is iterative: a zero trend with the excitation potential, reduced equivalent width and abundance must be maintained.
-For two stars, X and Y, the surface gravity could not be found by balancing the Fe\,\textsc{i} and \textsc{ii} lines.
-The smallest difference between the median abundances was $\langle$Fe\,\textsc{i} $-$ Fe\,\textsc{ii}$\rangle = 0.05$\,dex, which was considered to be converged.
-Varying the surface gravity from this solution did alter the Fe\,\textsc{i}, \textsc{ii} abundance, but the mean difference $\langle$Fe\,\textsc{i} $-$ Fe\,\textsc{ii}$\rangle$ remained constant at 0.05\,dex.
-In these two instances, the surface gravity was set to be closer towards the isochrone, while the $\langle$Fe\,\textsc{i} $-$ Fe\,\textsc{ii}$\rangle$ = 0.05$\,dex condition was met.
-
-\subsubsection{Metallicity, $\mbox{[M/H]}$}
-The degeneracy between parameters required a refinement of the stellar parameters until the line abundances were consistent with the model atmosphere.
-After these parameters had converged, the model metallicity was exactly matched to that of our line abundances.
-Line abundances that were unusually deviant ($3\sigma$) from the mean were removed.
-The largest number of outlier measurements removed for any observation was nine for C222531-144370, leaving 60 Fe\,\textsc{i} and 10 Fe\,\textsc{ii} lines for analysis.
-The minimum number of Fe transitions used in any star was 44 lines (33 Fe\,\textsc{i} and 11 Fe\,\textsc{ii}) for our hottest star, J223811-104126.
-
-% spectral plots for five stars
-
-\begin{deluxetable*}{lcccccccccccccc}
+\begin{deluxetable*}{lcccccccccccccc}[h!]
 \tablecolumns{2}
 \tabletypesize{\scriptsize}
-\tablecaption{Stellar Parameters}
+\tablecaption{Stellar Parameters\label{tab:stellar-parameters}}
 \tablehead{
@@
 
+\subsection{Stellar Parameters}
+The most recent version of the spectral synthesis code \textsc{moog} \citep{sneden;et-al_1973} has been used to derive individual line abundances and stellar parameters.
+This version employs Rayleigh scattering \citep{sobeck;et-al_2011} instead of treating scattering as true absorption, which is particularly important for transitions blue-ward of 450\,nm.
+This is noteworthy, but is less relevant for these analyses as most of our line measurements are red-ward of 450\,nm.
+Absorption lines are assumed to form under the assumption of local thermal equilibrium.
+
+\begin{figure*}[t!]
+	\includegraphics[width=\textwidth]{./figures/spectra-h-alpha.pdf}
+	\caption{Spectra for all Aquarius stream stars.}
+	\label{fig:spectra-h-alpha}
+\end{figure*}
+
+\subsubsection{Effective Temperature}
+\label{sec:effective-teffs}
+The effective temperature for each star was found by demanding a zero-trend in excitation potential and abundance for each measured Fe\,\textsc{i} line.
+In the same way, the microturbulence was found by demanding a zero trend in reduced equivalent width against abundance.
+Linear relationships with slopes of $|0.001|$ dex were considered to be converged.
+
+\subsubsection{Photometric Effective Temperatures}
+\label{sec:photometric-temperatures}
+
+The effective temperatures published for all of our stars in Table \ref{sec:stellar-parameters} have been derived spectroscopically (see \S\ref{sec:effective-teffs}).
+As a consistency check for our spectroscopic temperatures, we have estimated effective temperatures using infrared photometry from the 2MASS catalog.
+The $J-K$ color has been employed for these calculations because it has the least dependence on metallicity.
+
+The Aquarius stream is relatively close and at high-latitude, so significant extinction by dust is not expected.
+The dust maps of \citet{schlegel;et-al_1998} estimate that the extinction for our stars varies between E(B-V) = 0.03 to 0.07 mags.
+However, these maps are not perfect.
+As an alternative to using the \citet{schlegel;et-al_1998} dust maps, the level of extinction towards a star can be found by the strength of the interstellar Na D or K \textsc{i} lines \citep{munari;zwitter_1997}.
+The interstellar lines must be sufficiently separated from the stellar absorption lines in order for the extinction to be measurable.
+This was the case in only one of our stars, J223811.
+We measured the equivalent width of the Na D1 line in J223811 to be 302.4\,m{\AA}, which corresponds to an $\mbox{E(B-V)} = 0.12^{+0.01}_{-0.02}$ according to the \citet{munari;zwitter_1997} relationship.
+This is a significantly higher value than what the \citet{schlegel;et-al_1998} dust map value of $\mbox{E(B-V)} = 0.07$ for J223811.
+For completeness, both extinction values have been used to calculate photometric temperatures.
+
+Although all of our targets are giant stars, two different $T_{eff}$-colour relationships have been employed: the \citet{alonso;et-al_1999} calibration for giants, and the \citet{casagrande;et-al_2010} calibration for dwarfs and sub-giants.
+All photometrically-derived temperatures are listed in \ref{tab:photometric-temperatures}.
+The \citet{alonso;et-al_1999} $J-K$ scale is insensitive to metallicity effects, and is in good agreement with our spectroscopic temperatures.
+For the \citet{casagrande;et-al_2010} $J-K$ relationship, which has a slight metallicity dependency, we have utilized the spectroscopically-derived [Fe/H] values shown in Table \ref{tab:stellar-parameters}.
+
+The effective temperatures found from spectroscopy agree fairly well with the photometric temperature estimates.
+For three of our stars, the temperatures we find are in between the two color-temperature relationships.
+There are two noteworthy deviations: J223504-152834 and J223811-104126.
+For J223504-152834 we find the star to have an effective temperature of 4590\,K, only 10\,K hotter than the \citet{casagrande;et-al_2010} dwarf/sub-giant relationship, yet ${\sim}$500\,K hotter than the \citet{alonso;et-al_1999} estimate.
+Our temperature of 4590\,K is in good agreement with previous spectroscopic determinations (4795\,K; \citet{williams;et-al_2011}, 4597\,K; \citet{wylie-de-boer;et-al_2012}).
+The fact that the \citet{alonso;et-al_1999} photometric temperature relationship for giants predicts a temperature that is ${\sim}$500\,K cooler than the spectroscopically-derived values may be attributed to an underestimated amount of dust towards J223504-152834.
+A higher than expected level of extinction along the line-of-sight would produce cooler photometric temperatures than the true effective temperature.
+An extinction of $E(B-V) = 0.10$ would be required for the \citet{alonso;et-al_1999} relation to yield a temperature of ${\sim}$4500\,K, within the uncertainties of our effective temperature derived from spectroscopy.
+Such a discrepancy in extinction is large, but not uncommon (e.g., see \citet{nataf;et-al}).
+Although we suspect J223504-152834 to have a higher reddening than $E(B-V) = 0.04$, we have adopted the \citet{schlegel;et-al_1998} value for this analysis.
+
+J223811-104126 has two extinction values available: the \citet{schlegel;et-al_1998} value of $E(B-V) = 0.07$ and the 0.12 value  determined from the interstellar Na D1 line.
+Given the inherent difficulties in producing dust maps, and the known problems associated with them, we believe the $E(B-V) = 0.12$ determination to be more accurate.
+However, using the \citet{schlegel;et-al_1998} extinction value with the \citet{alonso;et-al_1999} color-temperature relationship yields excellent agreement (5104\,K) with our spectroscopic temperature of 5140\,K.
+Employing our more accurate reddening determination yields 5215\,K, within the uncertainties of the relationship.
+The \citet{casagrande;et-al_2010} scale is ${\sim}$250\,K hotter in both cases.
+
+With the exception of J223504-152834, the \citet{alonso;et-al_1999} giant relationship agrees well ($\pm$100\,K) with our spectroscopically-derived values.
+The \citet{casagrande;et-al_2010} relationship is also in relatively good agreement (most within 100\,K, largest discrepancy is 220\,K) with our spectroscopic temperatures, although we note that this relation was derived primarily for dwarfs/sub-giants and our candidates are all giant stars.
+
+\begin{deluxetable}{lccccc}
+\tablecolumns{1}
+\tabletypesize{\scriptsize}
+\tablecaption{Reddening \& Photometric Temperatures\label{tab:photometric-temperatures}}
+\tablehead{
+& & & \multicolumn{2}{c}{$T_{phot}$} \\
+\cline{4-5} \\
+	\colhead{Designation} &
+	\colhead{E($B-V$)} &
+	\colhead{$(J-K)_0$} &
+	\colhead{Alonso} &
+	\colhead{Casagrande} \\
+	& (mag) & & (K) & (K)
+}
+\startdata 
+C222531-144370 	& 0.03\phn	& 	0.75 & 4247	&	4391 \\	
+C230626-085103	& 0.05\phn	&	0.82 & 4091	&	4200 \\	
+J221821-183424 	& 0.03\phn	&	0.64 & 4546	&	4747 \\	
+J223504-152834 	& 0.04\phn	&	0.69 & 4110	& 	4579 \\	
+J223811-104126 	& 0.07\phn	&	0.48 & 5104	&	5367 \\	
+				& 0.12\footnote{Extinction derived from interstellar Na D1 line (see \ref{sec:photometric-temperatures})} 			&	0.45 & 5215	&	5484	
+\enddata
+\end{deluxetable}
+
+\subsubsection{Surface Gravity}
+
+The surface gravity for all stars was found by forcing the mean Fe\,\textsc{i} and Fe\,\textsc{ii} abundances to be equal.
+The process is iterative: a zero trend with the excitation potential, reduced equivalent width and abundance must be maintained.
+For two stars, X and Y, the surface gravity could not be found by balancing the Fe\,\textsc{i} and \textsc{ii} line abundances.
+The smallest difference between the median abundances was $\langle$Fe\,\textsc{i} $-$ Fe\,\textsc{ii}$\rangle = 0.05$\,dex, which was considered to be converged.
+Varying the surface gravity from this solution did alter the mean Fe\,\textsc{i} and \textsc{ii} abundances, but the difference $\langle$Fe\,\textsc{i} $-$ Fe\,\textsc{ii}$\rangle$ remained constant at 0.05\,dex.
+In these two instances, the surface gravity was set to be closer towards the isochrone, while the $\langle$Fe\,\textsc{i} $-$ Fe\,\textsc{ii}$\rangle$ = 0.05\,dex condition was maintained.
+
+\subsubsection{Metallicity, $\mbox{[M/H]}$}
+The degeneracy between parameters required a refinement of the stellar parameters until the line abundances were consistent with the model atmosphere.
+After these parameters had converged, the model metallicity was exactly matched to that of our mean Fe \textsc{i} abundance.
+Line abundances that were unusually deviant (>3-$\sigma$) from the mean were removed.
+The largest number of outlier measurements removed for any observation was nine for C222531-144370, leaving 60 Fe\,\textsc{i} and 10 Fe\,\textsc{ii} lines for analysis.
+The minimum number of Fe transitions used in any star was 44 lines (33 Fe\,\textsc{i} and 11 Fe\,\textsc{ii}) for our hottest star, J223811-104126.
+
+% spectral plots for five stars
+
 \subsection{Abundances}
-We have scaled our abundances to solar values using the chemical composition of \citet{asplund;et-al_2009}.
+We have scaled our abundances to solar values using the solar chemical composition described in \citet{asplund;et-al_2009}.
 
@@
 Although the O \textsc{i} triplet lines at 777 nm are stronger than the forbidden lines, they are extremely susceptible to NLTE and 3D effects \citep{asplund;perez_2001}, and sensitive to changes in microturbulence.
-\citet{perez;et-al_2006} showed that oxygen abundances measured under the assumption of LTE in their sample are 0.08\,dex higher than abundances derived from the `true' oxygen content derived from the forbidden lines.
 
@@
 Careful consideration was taken when correcting for telluric absorption.
-The 6300$\lambda$ line in one of our candidates, C2306265-085103, was sufficiently affected by telluric absorption such that we considered the line immeasurable.
+The 6300$\lambda$ line in one of our candidates, C2306265-085103, was sufficiently affected by telluric absorption such that we considered the line to be immeasurable.
 Thus, only the 6363$\lambda$ line was used to derive an oxygen abundance for C2306265-085103.
 In our hottest star, J223811-104126, the forbidden oxygen lines were not detected above a 3-$\sigma$ significance.
-After synthesising the region, we deduce a conservative upper limit of $\mbox{[O/Fe]} < -0.50$ dex from the [O \textsc{i}] lines.
-This is consistent with the rest of our candidates, with [O/Fe] abundances varying between 0.41 to 0.57 dex.
+After synthesising the region, we deduce a very conservative upper limit of $\mbox{[O/Fe]} < -0.50$ dex from the [O \textsc{i}] lines.
+This is consistent with the rest of our candidates, with [O/Fe] abundances varying between 0.41 to 0.57\,dex.
 
@@
 Abundances determined from the oxygen triplet lines were systematically $+0.27$\,dex higher than found from the [O \textsc{i}] lines.
-\citet{perez;et-al_2006} found [O/Fe] values based on the O \textsc{i} permitted triplet lines are on average $+0.19 \pm 0.07$\,dex higher than those found from the forbidden lines, after NLTE corrections of $-$0.08\,dex had been applied.
+\citet{perez;et-al_2006} found [O/Fe] values based on the O \textsc{i} permitted triplet lines are on average $+0.19 \pm 0.07$\,dex higher than those found from the forbidden lines, after NLTE corrections of $-$0.08\,dex had been applied to the permitted abundance.
 Thus, our 0.27\,dex offset between measurements of the [O \textsc{i}] and O \textsc{i} triplet lines is exactly the same as found by \citet{perez;et-al_2006}, which we attribute to a combination of systematic phenomena including NLTE and 3D effects.
@@
 When we apply this crude offset derived from the rest of our sample, we arrive at a corrected abundance of $\mbox{[O/Fe]} = 0.14 \pm 0.08$\,dex for J223811-104126.
-This is the most oxygen-deficient star in our sample, by in excess of 0.25 dex.
+This is the most oxygen-deficient star in our sample.
 
 \subsubsection{Sodium}
-
-% which lines did we use for sodium and were there any problems with the Na lines?
+\label{sec:sodium-abundances}
+Our line list includes three clean, unblended sodium lines at 5688$\lambda$, 6154$\lambda$ and 6161$\lambda$.
+Not all three of these lines were detectable in each star.
+In the hottest and most metal-poor stars, J223811 and J221821-183424 respectively, only the 5688$\lambda$ line was measurable.
+Consequently, an uncertainty of 0.10\,dex was adopted for these stars.
+For stars where multiple sodium lines were available, the line-to-line scatter is reasonable: smaller than 0.09\,dex.
+
+% [Na/Fe] measurements in the standard stars?
 
@@
 However, C2225316-14437 has an unusually high silicon abundance ($\mbox{[Si/Fe]} = 0.72$), well outside the uncertainties of the rest of our sample.
-C2225316-14437 does not demonstrate unusually high abundances of any other $\alpha$-element, and the silicon lines are not affected by telluric absorption.
-Moreover, the Si lines are in relatively good agreement with one another.
+The silicon line abundances are in relatively good agreement with one another.
 If we exclude the most prominent outlier, then the mean abundance drops only slightly to $\mbox{[Si/Fe]} = 0.70 \pm 0.04$\,dex.
@@
 
-% titanium measurements
+% titanium measurements?
 
@@
 However, this is a particularly crowded spectral region: the lines fall between the strong Ca H and K lines, with the 3961\,{\AA} transition clearly in the wing of the Ca H line.
-This makes the continuum determination and subsequent Al measurement non-trivial, especially given the metallicity of our stars.
+This makes the continuum determination and subsequent aluminium measurement non-trivial, especially given the metallicity of our stars.
+Additionally, the 3944 and 3961 lines suffer from appreciable departures from LTE, resulting in under-estimated abundances by up to $\sim$0.60\,dex \citep{baumuller;gehren_1997}.
 Instead, we have measured Al abundances from the other transitions available in our spectra: the Al \textsc{i} lines at 6696, 6698, 7835 and 7836\,{\AA}.
-Although these lines are weaker than the bluer Al \textsc{i} lines, their surrounding regions are uncrowded.
+Although these lines are weaker than the bluer Al \textsc{i} lines, their surrounding regions are uncrowded from strong absorption lines.
 
@@
 The strength of the lines is noticeably weakened below a 3-$\sigma$ detection with decreasing metallicity and increasing temperature.
-For our most metal-poor star, J221821, only one Al \textsc{i} line was detectable, and so we have adopted an uncertainty of 0.10\,dex.
+For our most metal-poor star, J221821, only a single Al \textsc{i} line was detectable, and so we have adopted a conservative uncertainty of 0.10\,dex.
 
 \subsubsection{Iron-peak Elements (Sc, V, Cr and Mn)}
-Scantium, Vanadium, Chromium and Manganese. All very vanilla, exhibiting a downward trend with [Fe/H].
-Data.
+
+As expected, the Fe-peak elemental abundances exhibit similar trends (Figure \ref{fig:fe-peak-elements}).
+The noteworthy exception is chromium, where the median abundance is $\mbox{[Cr/Fe]} = -0.08 \pm 0.12$ and does not vary with overall metallicity.
+The number of clean, suitable Cr \textsc{i} lines available varied between stars from three to twelve.
+Very little line-to-line scatter is present in both Cr \textsc{i} and \textsc{ii}: the random scatter is below 0.04\,dex for most stars, with the isolated example of J223504 where $\sigma(\mbox{[Cr \textsc{ii}/Fe]}) = 0.29$\,dex and only three lines were available.
+The Cr \textsc{i} and \textsc{ii} abundances for J223504 are in good agreement (0.05\,dex), and since none of the measured profiles were particularly unusual, we chose not to exclude outlier measurements.
+For all other stars, the Cr \textsc{i} $-$ Cr \textsc{ii} abundance differences varied between 0.02\,dex up to 0.31\,dex.
+The largest discrepancy occurred in our hottest star, where fewer chromium transitions were detectable.
+
+All other iron peak elements considered (Sc, V, Mn) all exhibit a slight downward trend in metallicity, with manganese demonstrating the most prominent gradient: varying between $\mbox{[Mn/Fe]} = -0.52$\,dex to $+0.31$\,dex in the most metal-poor and -rich stars respectively.
+The [Sc/Fe] measurements presented in Figure \ref{fig:fe-peak-elements} are calculated from six clean Sc \textsc{ii} lines, and there is very minimal line-to-line scatter, the largest of which is 0.06\,dex.
+Three Aquarius stream stars display [Sc/Fe] $\sim$ +0.20, while J221821 and J223811 have $\mbox{[Sc/Fe]} = 0.01$ and 0.05\,dex, respectively.
+
+% Iron peak elements
+\begin{figure}[h]
+	\includegraphics[width=\columnwidth]{./figures/aquarius-fe-peak.pdf}
+	\caption{Iron peak elements for all stars.}
+	\label{fig:fe-peak-elements}
+\end{figure}
 
@@
 With one exception, the Aquarius stream stars have barium abundances that are quite similar to the stellar halo, ranging between $\mbox{[Ba/Fe]} = -0.02$ to 0.15 dex.
-The exception is C2225316, which has an anomalously high barium abundance of $\mbox{[Ba/Fe]} = 0.68$ dex.
-This is ${\sim}$0.60 dex higher than the Milky Way trend at its given $\mbox{[Fe/H]} = -1.19$ dex.
+The exception is C2225316, which has an anomalously high barium abundance of $\mbox{[Ba/Fe]} = 0.70$ dex.
+This is ${\sim}$0.70 dex higher than the Milky Way trend at its given $\mbox{[Fe/H]} = -1.26$ dex.
 Our three Ba \textsc{ii} lines in C2225316 are in excellent agreement: 0.67, 0.68, and 0.72 dex.
-The 6496 {\AA} transition has a negligible telluric contribution (e.g.
-Figure \ref{fig:ba-6496}), so it was included for this star.
+The 6496\,{\AA} transition in C2225316 has a negligible telluric contribution and was included for this star.
 At least in Al, Si, Cr and Ba abundances (see sections \ref{sec:aluminium-abundance}, \ref{sec:alpha-elements}, \ref{sec:iron-peak-elements}), C225316 appears to be chemically distinct from the other Aquarius stream stars in our sample.
@@
  \cline{1-7} \cline{9-15} \\
-   O \textsc{i} &   2 &    7.50 &    0.04 & $-$1.18 &    0.41 &    0.02 &&
-   O \textsc{i} &   2 &    7.90 &    0.01 & $-$0.79 &    0.48 &    0.01 \\
-  Na \textsc{i} &   2 &    4.56 &    0.14 & $-$1.68 & $-$0.08 &    0.10 &&
-  Na \textsc{i} &   3 &    5.09 &    0.17 & $-$1.15 &    0.12 &    0.10 \\
-  Mg \textsc{i} &   4 &    6.55 &    0.37 & $-$1.04 &    0.55 &    0.18 &&
-  Mg \textsc{i} &   4 &    6.98 &    0.24 & $-$0.62 &    0.65 &    0.12 \\
-  Al \textsc{i} &   1 &    5.04 &    0.00 & $-$1.41 &    0.18 & \nodata &&
+   O \textsc{i} &   2 &    7.55 &    0.04 & $-$1.13 &    0.47 &    0.02 &&
+   O \textsc{i} &   2 &    7.92 &    0.00 & $-$0.77 &    0.49 &    0.00 \\
+  Na \textsc{i} &   1 &    4.71 &    0.00 & $-$1.53 &    0.08 &    0.00 &&
+  Na \textsc{i} &   2 &    5.07 &    0.02 & $-$1.17 &    0.09 &    0.01 \\
+  Mg \textsc{i} &   3 &    6.33 &    0.09 & $-$1.27 &    0.34 &    0.05 &&
+  Mg \textsc{i} &   2 &    6.84 &    0.09 & $-$0.76 &    0.50 &    0.06 \\
+  Al \textsc{i} &   1 &    5.05 &    0.00 & $-$1.40 &    0.21 &    0.00 &&
   Al \textsc{i} &   4 &    5.87 &    0.09 & $-$0.58 &    0.68 &    0.04 \\
-  Si \textsc{i} &   5 &    6.28 &    0.08 & $-$1.23 &    0.37 &    0.04 &&
-  Si \textsc{i} &   5 &    6.96 &    0.15 & $-$0.55 &    0.72 &    0.07 \\
-  Ca \textsc{i} &   4 &    4.97 &    0.04 & $-$1.37 &    0.23 &    0.02 &&
-  Ca \textsc{i} &   4 &    5.50 &    0.04 & $-$0.84 &    0.43 &    0.02 \\
-  Sc \textsc{i} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata &&
-  Sc \textsc{i} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
- Sc \textsc{ii} &   6 &    1.52 &    0.08 & $-$1.63 & $-$0.04 &    0.03 &&
- Sc \textsc{ii} &   5 &    2.05 &    0.13 & $-$1.10 &    0.17 &    0.06 \\
+  Si \textsc{i} &   5 &    6.28 &    0.08 & $-$1.23 &    0.38 &    0.04 &&
+  Si \textsc{i} &   5 &    6.97 &    0.15 & $-$0.54 &    0.72 &    0.07 \\
+  Ca \textsc{i} &   4 &    4.99 &    0.04 & $-$1.35 &    0.25 &    0.02 &&
+  Ca \textsc{i} &   4 &    5.51 &    0.04 & $-$0.83 &    0.43 &    0.02 \\
+ Sc \textsc{ii} &   6 &    1.56 &    0.09 & $-$1.59 &    0.01 &    0.04 &&
+ Sc \textsc{ii} &   5 &    2.08 &    0.13 & $-$1.07 &    0.19 &    0.06 \\
   Ti \textsc{i} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata &&
-  Ti \textsc{i} &   4 &    4.04 &    0.03 & $-$0.91 &    0.36 &    0.01 \\
- Ti \textsc{ii} &   4 &    3.81 &    0.13 & $-$1.14 &    0.45 &    0.07 &&
- Ti \textsc{ii} &   2 &    4.26 &    0.08 & $-$0.69 &    0.58 &    0.06 \\
-   V \textsc{i} &   3 &    2.23 &    0.01 & $-$1.70 & $-$0.11 &    0.01 &&
-   V \textsc{i} &   6 &    2.92 &    0.17 & $-$1.01 &    0.26 &    0.07 \\
-  Cr \textsc{i} &  11 &    3.74 &    0.07 & $-$1.90 & $-$0.30 &    0.02 &&
-  Cr \textsc{i} &   8 &    4.27 &    0.16 & $-$1.37 & $-$0.10 &    0.06 \\
-  Mn \textsc{i} &   3 &    3.29 &    0.04 & $-$2.14 & $-$0.54 &    0.02 &&
-  Mn \textsc{i} &   3 &    4.14 &    0.05 & $-$1.29 & $-$0.02 &    0.03 \\
-  Fe \textsc{i} &  52 &    5.91 &    0.09 & $-$1.59 &    0.00 &    0.01 &&
-  Fe \textsc{i} &  61 &    6.23 &    0.11 & $-$1.27 &    0.00 &    0.01 \\
- Fe \textsc{ii} &  13 &    5.90 &    0.05 & $-$1.60 &    0.00 &    0.01 &&
- Fe \textsc{ii} &  10 &    6.17 &    0.06 & $-$1.33 & $-$0.07 &    0.02 \\
-  Co \textsc{i} &   1 &    3.35 &    0.00 & $-$1.64 & $-$0.05 & \nodata &&
-  Co \textsc{i} &   3 &    3.92 &    0.12 & $-$1.07 &    0.20 &    0.07 \\
-  Ni \textsc{i} &   5 &    4.61 &    0.15 & $-$1.61 & $-$0.01 &    0.07 &&
-  Ni \textsc{i} &   7 &    5.04 &    0.09 & $-$1.18 &    0.09 &    0.03 \\
-  Cu \textsc{i} &   1 &    2.13 &    0.00 & $-$2.06 & $-$0.47 & \nodata &&
-  Cu \textsc{i} &   1 &    3.35 &    0.00 & $-$0.84 &    0.43 & \nodata \\
-  Zn \textsc{i} &   2 &    3.15 &    0.11 & $-$1.41 &    0.19 &    0.08 &&
-  Zn \textsc{i} &   2 &    3.46 &    0.23 & $-$1.10 &    0.17 &    0.17 \\
+  Ti \textsc{i} &   4 &    4.04 &    0.02 & $-$0.91 &    0.36 &    0.01 \\
+ Ti \textsc{ii} &   4 &    3.85 &    0.13 & $-$1.10 &    0.50 &    0.06 &&
+ Ti \textsc{ii} &   2 &    4.29 &    0.08 & $-$0.66 &    0.61 &    0.05 \\
+   V \textsc{i} &   3 &    2.26 &    0.01 & $-$1.67 & $-$0.06 &    0.01 &&
+   V \textsc{i} &   6 &    2.93 &    0.17 & $-$1.00 &    0.26 &    0.07 \\  
+  Cr \textsc{i} &  11 &    3.77 &    0.08 & $-$1.87 & $-$0.26 &    0.02 &&
+  Cr \textsc{i} &   8 &    4.29 &    0.16 & $-$1.35 & $-$0.08 &    0.06 \\
+ Cr \textsc{ii} &   2 &    4.04 &    0.02 & $-$1.60 &    0.00 &    0.02 &&
+ Cr \textsc{ii} &   1 &    4.27 &    0.00 & $-$1.37 & $-$0.11 &    0.00 \\
+  Mn \textsc{i} &   3 &    3.30 &    0.03 & $-$2.13 & $-$0.52 &    0.02 &&
+  Mn \textsc{i} &   3 &    4.15 &    0.04 & $-$1.28 & $-$0.01 &    0.03 \\
+  Fe \textsc{i} &  52 &    5.89 &    0.09 & $-$1.61 &    0.00 &    0.01 &&
+  Fe \textsc{i} &  60 &    6.24 &    0.10 & $-$1.26 &    0.00 &    0.01 \\
+ Fe \textsc{ii} &  13 &    5.91 &    0.05 & $-$1.59 &    0.02 &    0.01 &&
+ Fe \textsc{ii} &  10 &    6.19 &    0.06 & $-$1.31 & $-$0.05 &    0.02 \\
+  Co \textsc{i} &   1 &    3.38 &    0.00 & $-$1.61 & $-$0.00 &    0.00 &&
+  Co \textsc{i} &   3 &    3.92 &    0.12 & $-$1.07 &    0.19 &    0.07 \\
+  Ni \textsc{i} &   5 &    4.62 &    0.14 & $-$1.60 &    0.01 &    0.06 &&
+  Ni \textsc{i} &   7 &    5.05 &    0.09 & $-$1.17 &    0.09 &    0.03 \\
+  Cu \textsc{i} &   1 &    2.16 &    0.00 & $-$2.03 & $-$0.42 &    0.00 &&
+  Cu \textsc{i} &   1 &    3.38 &    0.00 & $-$0.81 &    0.45 &    0.00 \\
+  Zn \textsc{i} &   2 &    3.17 &    0.11 & $-$1.39 &    0.22 &    0.08 &&
+  Zn \textsc{i} &   2 &    3.48 &    0.24 & $-$1.08 &    0.19 &    0.17 \\
+ Ba \textsc{ii} &   2 &    0.72 &    0.08 & $-$1.47 &    0.14 &    0.05 &&
+ Ba \textsc{ii} &   2 &    1.62 &    0.01 & $-$0.56 &    0.70 &    0.00 \\
+
 \cline{1-7} \cline{9-15} \\
@@
 \cline{1-7} \cline{9-15} \\
-   O \textsc{i} &   2 &    8.48 &    0.09 & $-$0.21 &    0.46 &    0.07 &&
-   O \textsc{i} &   1 &    8.60 &    0.00 & $-$0.09 &    0.14\footnote{Abundance derived from the permitted O \textsc{i} triplet instead of the forbidden [O \textsc{i}] lines, see \S\ref{sec:oxygen-abundances}} &    0.08 \\
-  Na \textsc{i} &   3 &    5.76 &    0.12 & $-$0.48 &    0.19 &    0.07 &&
-  Na \textsc{i} &   2 &    4.76 &    0.10 & $-$1.48 & $-$0.03 &    0.07 \\
-  Mg \textsc{i} &   3 &    7.50 &    0.24 & $-$0.10 &    0.58 &    0.14 &&
-  Mg \textsc{i} &   3 &    6.49 &    0.42 & $-$1.11 &    0.34 &    0.24 \\
-  Al \textsc{i} &   3 &    6.10 &    0.08 & $-$0.35 &    0.32 &    0.05 &&
+   O \textsc{i} &   2 &    8.46 &    0.10 & $-$0.23 &    0.45 &    0.07 &&
+   O \textsc{i} &   1 &    8.26 &    0.00 & $-$0.43 &    0.14\footnote{Abundance derived from the permitted O \textsc{i} triplet instead of the forbidden [O \textsc{i}] lines, see \S\ref{sec:oxygen-abundances}} &    0.08 \\
+  Na \textsc{i} &   3 &    5.74 &    0.12 & $-$0.50 &    0.18 &    0.07 &&
+  Na \textsc{i} &   1 &    4.86 &    0.00 & $-$1.38 &    0.07 &    0.00 \\
+  Mg \textsc{i} &   3 &    7.41 &    0.15 & $-$0.19 &    0.49 &    0.09 &&
+  Mg \textsc{i} &   2 &    6.47 &    0.02 & $-$1.13 &    0.32 &    0.01 \\
+  Al \textsc{i} &   3 &    6.08 &    0.08 & $-$0.37 &    0.31 &    0.05 &&
   Al \textsc{i} &   2 &    5.10 &    0.14 & $-$1.35 &    0.10 &    0.10 \\
-  Si \textsc{i} &   5 &    7.11 &    0.10 & $-$0.40 &    0.28 &    0.04 &&
+  Si \textsc{i} &   5 &    7.12 &    0.10 & $-$0.39 &    0.29 &    0.04 &&
   Si \textsc{i} &   3 &    6.38 &    0.04 & $-$1.13 &    0.32 &    0.02 \\
-  Ca \textsc{i} &   4 &    6.03 &    0.04 & $-$0.31 &    0.36 &    0.02 &&
+  Ca \textsc{i} &   4 &    6.00 &    0.03 & $-$0.34 &    0.33 &    0.02 &&
   Ca \textsc{i} &   4 &    5.30 &    0.03 & $-$1.04 &    0.41 &    0.01 \\
-  Sc \textsc{i} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata &&
-  Sc \textsc{i} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
  Sc \textsc{ii} &   6 &    2.70 &    0.14 & $-$0.45 &    0.23 &    0.06 &&
  Sc \textsc{ii} &   6 &    1.75 &    0.14 & $-$1.40 &    0.05 &    0.06 \\
-  Ti \textsc{i} &   4 &    4.63 &    0.02 & $-$0.32 &    0.36 &    0.01 &&
+  Ti \textsc{i} &   4 &    4.59 &    0.02 & $-$0.36 &    0.32 &    0.01 &&
   Ti \textsc{i} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
- Ti \textsc{ii} &   2 &    4.92 &    0.26 & $-$0.04 &    0.64 &    0.19 &&
+ Ti \textsc{ii} &   2 &    4.91 &    0.27 & $-$0.04 &    0.64 &    0.19 &&
  Ti \textsc{ii} &   4 &    3.83 &    0.09 & $-$1.12 &    0.33 &    0.04 \\
-   V \textsc{i} &   6 &    3.67 &    0.22 & $-$0.26 &    0.41 &    0.09 &&
-   V \textsc{i} &   1 &    2.42 &    0.00 & $-$1.51 & $-$0.06 & \nodata \\
-  Cr \textsc{i} &   7 &    4.94 &    0.09 & $-$0.70 & $-$0.02 &    0.03 &&
+   V \textsc{i} &   6 &    3.62 &    0.22 & $-$0.31 &    0.37 &    0.09 &&
+   V \textsc{i} &   1 &    2.42 &    0.00 & $-$1.51 & $-$0.06 &    0.00 \\
+  Cr \textsc{i} &   7 &    4.88 &    0.09 & $-$0.76 & $-$0.08 &    0.04 &&
   Cr \textsc{i} &  12 &    4.12 &    0.06 & $-$1.52 & $-$0.07 &    0.02 \\
-  Mn \textsc{i} &   3 &    5.08 &    0.10 & $-$0.35 &    0.33 &    0.06 &&
+ Cr \textsc{ii} &   3 &    4.83 &    0.50 & $-$0.81 & $-$0.13 &    0.29 &&
+ Cr \textsc{ii} &   3 &    4.34 &    0.07 & $-$1.30 &    0.15 &    0.04 \\
+  Mn \textsc{i} &   3 &    5.06 &    0.10 & $-$0.37 &    0.31 &    0.06 &&
   Mn \textsc{i} &   3 &    3.55 &    0.04 & $-$1.88 & $-$0.43 &    0.02 \\
-  Fe \textsc{i} &  64 &    6.83 &    0.12 & $-$0.67 &    0.00 &    0.02 &&
+  Fe \textsc{i} &  63 &    6.82 &    0.12 & $-$0.68 &    0.00 &    0.02 &&
   Fe \textsc{i} &  33 &    6.05 &    0.06 & $-$1.45 &    0.00 &    0.01 \\
@@
  Fe \textsc{ii} &  11 &    6.00 &    0.09 & $-$1.50 & $-$0.05 &    0.03 \\
-  Co \textsc{i} &   3 &    4.53 &    0.14 & $-$0.46 &    0.21 &    0.08 &&
+  Co \textsc{i} &   3 &    4.50 &    0.13 & $-$0.49 &    0.19 &    0.08 &&
   Co \textsc{i} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
-  Ni \textsc{i} &   7 &    5.62 &    0.09 & $-$0.60 &    0.08 &    0.03 &&
+  Ni \textsc{i} &   7 &    5.61 &    0.09 & $-$0.61 &    0.07 &    0.03 &&
   Ni \textsc{i} &   2 &    4.82 &    0.04 & $-$1.40 &    0.05 &    0.03 \\
-  Cu \textsc{i} &   1 &    3.85 &    0.00 & $-$0.34 &    0.33 & \nodata &&
-  Cu \textsc{i} &   1 &    2.39 &    0.00 & $-$1.80 & $-$0.35 & \nodata \\
-  Zn \textsc{i} &   2 &    4.17 &    0.03 & $-$0.39 &    0.28 &    0.02 &&
+  Cu \textsc{i} &   1 &    3.82 &    0.00 & $-$0.37 &    0.31 &    0.00 &&
+  Cu \textsc{i} &   1 &    2.39 &    0.00 & $-$1.80 & $-$0.35 &    0.00 \\
+  Zn \textsc{i} &   2 &    4.18 &    0.02 & $-$0.38 &    0.30 &    0.02 &&
   Zn \textsc{i} &   2 &    3.17 &    0.04 & $-$1.39 &    0.06 &    0.03 \\
-
+ Ba \textsc{ii} &   2 &    1.65 &    0.02 & $-$0.53 &    0.15 &    0.01 &&
+ Ba \textsc{ii} &   2 &    0.78 &    0.06 & $-$1.40 &    0.05 &    0.04 \\
 \cline{1-7} \cline{9-15} \\
@@
 \cline{1-7} \\
-   O \textsc{i} &   2 &    8.09 &    0.15 & $-$0.60 &    0.57 &    0.10 \\
+   O \textsc{i} &   2 &    7.96 &    0.02 & $-$0.72 &    0.45 &    0.02 \\
   Na \textsc{i} &   2 &    5.25 &    0.00 & $-$0.99 &    0.18 &    0.00 \\
@@
   Ca \textsc{i} &   4 &    5.48 &    0.04 & $-$0.86 &    0.31 &    0.02 \\
-  Sc \textsc{i} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
  Sc \textsc{ii} &   6 &    2.18 &    0.15 & $-$0.97 &    0.20 &    0.06 \\
@@
    V \textsc{i} &   4 &    2.88 &    0.06 & $-$1.05 &    0.12 &    0.03 \\
-  Cr \textsc{i} &   4 &    4.20 &    0.26 & $-$1.44 & $-$0.27 &    0.13 \\
+  Cr \textsc{i} &   3 &    4.08 &    0.12 & $-$1.56 & $-$0.39 &    0.07 \\
+ Cr \textsc{ii} &   1 &    4.39 &    0.00 & $-$1.25 & $-$0.08 &    0.00 \\
   Mn \textsc{i} &   3 &    4.35 &    0.10 & $-$1.08 &    0.09 &    0.06 \\
-  Fe \textsc{i} &  63 &    6.33 &    0.12 & $-$1.17 &    0.00 &    0.01 \\
+  Fe \textsc{i} &  62 &    6.33 &    0.12 & $-$1.17 &    0.00 &    0.01 \\
  Fe \textsc{ii} &  11 &    6.31 &    0.09 & $-$1.19 & $-$0.02 &    0.03 \\
@@
   Cu \textsc{i} &   1 &    3.55 &    0.00 & $-$0.64 &    0.53 &    0.00 \\
-  Zn \textsc{i} &   2 &    3.38 &    0.14 & $-$1.18 & $-$0.01 &    0.10
+  Zn \textsc{i} &   2 &    3.38 &    0.14 & $-$1.18 & $-$0.01 &    0.10 \\
+ Ba \textsc{ii} &   2 &    0.99 &    0.06 & $-$1.19 & $-$0.02 &    0.04
 \enddata
@@
 
+\subsection{Stellar Parameter Discrepancies with \citet{wylie-de-boer;et-al_2012}}
+
 We seek to investigate the nature of the Aquarius stream, as well as the specific globular cluster origin claim made by \citet{wylie-de-boer;et-al_2012}.
-
-\subsection{Stellar Parameter Discrepancies with \citet{wylie-de-boer;et-al_2012}}
-
 The stellar parameters reported in \citet{wylie-de-boer;et-al_2012} differ slightly to those published in Table \ref{tab:stellar-parameters}.
@@
 In general, temperatures between the two studies agree within the uncertainties.
-The only noteworthy exception is J223811-104126, where we find an effective temperature of 5140\,K, ${\sim}$500\,K cooler than the 5646\,K found by \citet{wylie-de-boer;et-al_2012}.
+The only abberation is J223811-104126, where we find an effective temperature of 5140\,K, ${\sim}$500\,K cooler than the 5646\,K found by \citet{wylie-de-boer;et-al_2012}.
 Similarly, \citet{williams;et-al_2011} report a hotter effective temperature of 5502\,K from low-resolution spectra.
@@
 If the \citet{schlegel;et-al_1998} dust maps are employed, then the \citet{alonso;et-al_1999} and \citet{casagrande;et-al_2010} relations estimate the effective temperatures to be between 5104\,K and 5367\,K.
-Our spectroscopic temperature of 5110\,K is closer to the \citet{alonso;et-al_1999} prediction, but not in disagreement with the \citet{casagrande;et-al_2010} relation either.
-If we employ the reddening of $E(B-V) = 0.12$ that we have determined from interstellar Na D1 line, the photometric temperature increases slightly by ${\sim}100$\,K, still within the uncertainties of the \citet{alonso;et-al_1999} scale, but in less agreement with the \citet{casagrande;et-al_2010} scale.
+Our spectroscopic temperature of 5110\,K is in excellent agreement with the \citet{alonso;et-al_1999} prediction, but not in strong disagreement with the \citet{casagrande;et-al_2010} relation either.
+If we employ the reddening of $E(B-V) = 0.12$ that we have determined from interstellar Na D1 line, the photometric temperature increases slightly by ${\sim}100$\,K, still within the uncertainties of the \citet{alonso;et-al_1999} scale, but less so  with the \citet{casagrande;et-al_2010} scale.
 We find the surface gravity for J223811-104126 to be 3.00 $\pm$ 0.50, placing this star at the base of the red giant branch.
@@
 Again, with the exception of J223811-104126, our surface gravities are largely in agreement.
-The only other noteworthy difference in surface gravity is for J221821-183424, where we find a lower gravity of $\log{g} = 0.80 \pm 0.30$ where \citet{wylie-de-boer;et-al_2012} find $\log{g} = 1.45 \pm 0.35$\,cm\,s$^{-2}$.
+The only other noteworthy difference in surface gravity is for J221821-183424, where we find a lower gravity of $\log{g} = 0.80 \pm 0.30$ and \citet{wylie-de-boer;et-al_2012} find $\log{g} = 1.45 \pm 0.35$\,cm\,s$^{-2}$.
 Given the difference in $S/N$ and resolution between these studies, this difference is not too concerning.
@@
 These relationships are based upon the effective temperature and surface gravity.
-Our published microturbulence values agree excellently with the values presented in \citet{wylie-de-boer;et-al_2012}, again with the exception of J223811-104126, where the difference in $v_{t}$ can be  directly attributed to the offsets in other stellar parameters.
+Our published microturbulent velocities agree excellently with the values presented in \citet{wylie-de-boer;et-al_2012}, again with the exception of J223811-104126, where the difference in $v_{t}$ can be  directly attributed to the offsets in other stellar parameters.
 
@@
 Here we discuss the potential causes for these discrepancies.
-In the \citet{wylie-de-boer;et-al_2012} study, after the stellar parameters ($T_{eff}$, $\log{g}$, $v_{t}$, and an initial [Fe/H] estimate) had been determined, the authors synthesized Fe \textsc{i} and \textsc{ii} lines individually using the spectrum synthesis code \textsc{moog}.
+In the \citet{wylie-de-boer;et-al_2012} study, after the stellar parameters ($T_{eff}$, $\log{g}$, $v_{t}$, and an initial [Fe/H] estimate) had been determined through a $\chi^2$ analysis, the authors synthesized individual Fe \textsc{i} and \textsc{ii} lines using the \textsc{moog} code.
 \citet{castelli;kurucz_2003} stellar atmosphere models were employed \--- the same ones used in this study, albeit the interpolation schemes will have subtle differences.
-The median abundance of Fe\,I lines was taken as the overall stellar metallicity, scaled using the \citet{grevesse;sauval_1998} solar abundances.
-
-The study of \citet{wylie-de-boer;et-al_2012} is of slightly lower resolution ($R = 25,000$ compared to $R = 28,000$ presented here), but with a much lower $S/N$ ratio: $\sim{}25$ pixel$^{-1}$ compared to $>100$ pixel$^{-1}$ achieved here.
+The median abundance of Fe\,\textsc{i} lines was taken as the overall stellar metallicity, scaled using the \citet{grevesse;sauval_1998} solar composition.
+
+The study of \citet{wylie-de-boer;et-al_2012} is of slightly lower resolution ($\mathcal{R} = 25,000$ compared to $\mathcal{R} = 28,000$ presented here), but with a much lower $S/N$ ratio: $\sim{}25$ pixel$^{-1}$ compared to >100 pixel$^{-1}$ achieved here.
 Given the lower spectral resolution and modest $S/N$ in the \citet{wylie-de-boer;et-al_2012} study, there are fewer unblended absorption lines available.
 In fact, there are very few transitions present in their published line list: only 14 Fe\,\textsc{i} lines and 3 Fe\,\textsc{ii} lines were available.
-For contrast, our metallicity determinations are usually based from ${\sim}$50 Fe\,I and ${\sim}$13 Fe\,II lines.
+For contrast, our metallicity determinations are usually based from ${\sim}$50 Fe\,\textsc{i} and ${\sim}$13 Fe\,\textsc{ii} lines.
 Given the metallicity of these stars and the spectral coverage (4120 to 6920 {\AA}), it is somewhat surprising that there were not more unblended transitions available to \citet{wylie-de-boer;et-al_2012}.
@@
 The line list employed in the \citet{wylie-de-boer;et-al_2012} study contained fewer lines, and employed different oscillator strengths than what we have used.
-The oscillator strengths in the \citet{wylie-de-boer;et-al_2012} study are astrophysical, and were derived from a reverse analysis from the \citet{hinkle;et-al_2003} solar atlas.
+The oscillator strengths in the \citet{wylie-de-boer;et-al_2012} study are astrophysical; they were derived from a reverse analysis from the \citet{hinkle;et-al_2003} solar atlas.
 Suspecting the differing line lists may be the cause of the  metallicity discrepancy, we reanalysed our data using the \citet{wylie-de-boer;et-al_2012} line list and stellar parameters.
@@
 Without using their published stellar parameters a priori, in a `blind' analysis employing just the \citet{wylie-de-boer;et-al_2012} line list, we arrive at similar stellar parameters.
-However, we note that one Fe\,\textsc{i} transition at 6420.060\,\AA{} in the \citet{wylie-de-boer;et-al_2012} line list was not detected in any of our stars at the $3-\sigma$ level, even though the $S/N$ at this point exceeds 115 pixel$^{-1}$ in every observation.
+However, we note that one Fe\,\textsc{i} transition at 6420.060\,\AA{} in the \citet{wylie-de-boer;et-al_2012} line list was not detected in any of our stars at the 3-$\sigma$ level, even though the $S/N$ at this point exceeds 115 pixel$^{-1}$ in every observation.
 Thus, for this comparative analysis a maximum of 13 Fe\,\textsc{i} and 3 Fe\,\textsc{ii} lines were available to us.
@@
 
-% Globular clusters typically exhibit minimal chemical scatter because X. 
-% globular clusters vs dwarf spheroidals MDF
-
-% larger MDF than expected for globular clusters
-
-% globular clusters typically have a tight MDF -- explain why
-
-% dSph's show a wide MDF due to X
-
-% there are some exclusions to this rule, most notably omega cen
-
-% mdf of omega cen
-
-% based on dynamics, williams excluded all known globular clusters and dsph's with the exception of omega cen.
-
-% although the MDF appears not to be dissimilar from omega cen, we will later show based on the evidence thus far that the aquarius stream is not disrupted debris from omega cen
-%	+ because as well as having a tight [Fe/H], all well-studied globular clusters (including omega cen) exhibit noteable chemical patterns, which we do not find in these stars.
+Classical globular clusters typically exhibit very little chemical scatter.
+This is largely because they are primarily considered to be a single stellar populations, originating from a lone \--- largely homogenous \--- proto-stellar cloud.
+More recent observations have repeatedly shown that this is not always the case: many globular clusters clearly host multiple stellar populations.
+The separation between these populations is identifiable through chemical abundances, and often from photometry alone.
+In many cases, the chemistry between the two stellar populations are quite similar, still revealing minimal overall chemical scatter within the cluster.
+There are some unusual exceptions to this rule, most notable of which is the globular cluster $\omega$-Centurai (NGC 5139), which is seen to host many sub-populations with very different metallicity distributions.
+Without the explanation of multiple sub-populations in mind, the system would be seen to exhibit an unusually wide metallicity dispersion for a globular cluster.
+
+Assuming all our candidates are stream members, we find a metallicity dispersion of $\sigma(\mbox{[Fe/H]}) = 0.32$\,dex.
+If the stream is the result of a disrupted system, this metallicity dispersion provides little indication on the progenitor.
+If the dispersion was smaller, confirming the observations of \citet{wylie-de-boer;et-al_2012}, the globular cluster scenario is  more likely.
+However, given the multiple stellar populations present in many globular clusters, which can exhibit total cluster dispersions up to X dex (NGC X), Y dex (NGC Y), our dispersion of 0.32\,dex is inconvenient.
+Since dwarf spheroidal galaxies do not undergo chemical self-enrichment in the same way globular clusters do, they can exhibit significant metallicity dispersions \--- well over a dex, depending on the dwarf total luminosity.
+On its own, the metallicity of our stream stars does not provide any indication on the cause of the Aquarius stream, or its enrichment environment.
 
@@
 Between generations of stars within a globular cluster, oxygen is converted into nitrogen, reducing the overall oxygen abundance.
-Even though oxygen undergoes internal mixing during its evolution along the giant branch, it is now well established that any observed abundance variations due to such mixing is limited to Li, C, and N.
+Even though oxygen undergoes internal mixing during its evolution along the giant branch, the detection of this chemical pattern in unevolved stars has led to the conclusion that observed abundance variations due to mixing are limited to Li, C, and N.
 Therefore, the light element anti-correlation required a different astrophysical explanation.
 
-Sodium is mainly produced through through carbon burning in massive stars by the dominant $^{12}\mbox{C}(^{12}\mbox{C}, p)^{23}\mbox{Na}$ process.
+Sodium is primarily produced through through carbon burning in massive stars by the dominant $^{12}\mbox{C}(^{12}\mbox{C}, p)^{23}\mbox{Na}$ process.
 The final Na abundance is dependent on the neutron excess of the star, which slowly increases during carbon burning due to weak interactions \citep{arnett;truran_1974}.
-Massive stars ($>8 M_\odot$) eventually deliver their manufactured sodium to the interstellar-medium through SN II events.
-Because the eventual SN II explosion is devoid of any significant beta-decay processes, the neutron excess of the exploded material is representative of the pre-explosion abundance.
+Massive stars ($>8 M_\odot$) eventually deliver their manufactured sodium to the interstellar-medium through Sn \textsc{ii} events.
+Because the eventual Sn \textsc{ii} explosion is devoid of any significant beta-decay processes, the neutron excess of the exploded material is representative of the pre-explosion abundance.
 
@@
 Thus, an increase in the Na abundance between generations of massive stars is a natural consequence of nucleosynthesis.
-Sodium content also becomes important for production of Ni during the SN II event (see \S\ref{sec:na-ni}) because $^{23}$Na is the only stable isotope produced in significant quantities during the C- (or O-) burning stages.
+Sodium content also becomes important for production of Ni during the Sn \textsc{ii} event (see \S\ref{sec:na-ni}) because $^{23}$Na is the only stable isotope produced in significant quantities during the C- (or O-) burning stages.
 A small fraction of $^{22}$Na is also forged through proton capture on $^{21}$Ne in the carbon shell, an effect which is enhanced by neutrinos spallating abundant elements like $^{16}$O and $^{20}$Ne, making free protons available for capture \citep{woosley;weaver_1995}.
 
-% discuss three components
-\citet{carretta;et-al_2009_na_o} defined three components of stars the Na-O anti-correlation within a population: primordial, intermediate, and extreme components.
-The [Na/Fe] and [O/Fe] abundances for a given star defines which component it belongs to.
+Oxygen depletion is likely the result of complete CNO burning within the stellar interior.
+The nucleosynthetic pathways that generate the Na-O anti-correlation are well known.
+However, the temperatures required to produce these patterns are not expected within the interiors of globular cluster stars.
+Several hypotheses to explain this missing mechanism have been proposed, including massive intermediate-mass AGB binary stars \citep{de_mink;et-al_2009} and fast-rotating massive stars \citep{decressin;et-al_2007}.
+While the exact site for which these conditions occur remains under investigation, we can describe the abundance variation as a simple oxygen depletion (or dilution) model with time.
+Through comparisons with existing globular clusters, we can still draw inferences on the star-formation history of a system from measuring sodium and oxygen in a sample of its stars.
+
+\citet{carretta;et-al_2009_na_o} defined three components of stars exhibiting an inverse Na-O correlation within a population: primordial, intermediate, and extreme components.
+The [Na/Fe] and [O/Fe] abundances for a given star define which component it belongs to.
 Primordial (first-generation) stars are those with sodium and oxygen abundances which are similar to field stars of the same metallicity.
@@
 
-% Discuss the depletion of oxygen over time. What are the possible astrophysical explanations for this depletion
-Several hypotheses have been proposed in order to account for oxygen depletion between stellar generations, including massive binaries \citep{de_mink;et-al_2009} or fast-rotating massive stars \citep{decressin;et-al_2007}.
-While the exact procedure is yet to be fully characterized, we can describe the abundance variation as a simple oxygen depletion (or dilution) model with time.
-Through comparisons with existing globular clusters, we can still draw inferences on the star-formation history of a system from measuring sodium and oxygen in a sample of its stars.
-
-% Thus if you want to deduce the history of star formation for a group of stars, and deduce whether it has undergone star formation typically seen in globular clusters, you must sample from all components.
-
-It is clear that careful consideration must be given inferring star-formation histories from observed stellar abundances.
+It is clear that careful consideration must be given when inferring star-formation histories from observed stellar abundances.
 In addition to the normal care afforded for measuring elemental abundances from high-resolution spectroscopic data, attention must be given to telluric absorption, contamination from nickel blends, as well as NLTE and 3D effects when calculating oxygen abundances.
@@
 
-% Talk about Wylie de boer measurements
-
 \citet{wylie-de-boer;et-al_2012} measured [Na/Fe] and [O/Fe] abundances for four of their six Aquarius stream members.
-This research has four stars in common with the \citet{wylie-de-boer;et-al_2012} study, but sodium and oxygen measurements exist for only three stars intersecting both samples, as the data quality for X in the \citet{wylie-de-boer;et-al_2012} study prohibited measuring sodium and oxygen.
+This research has four stars in common with the \citet{wylie-de-boer;et-al_2012} study, but sodium and oxygen measurements exist for only three stars intersecting both samples, as the data quality for J223811-104126 in the \citet{wylie-de-boer;et-al_2012} study prohibited measuring oxygen.
 We have measurements for all of our stars, including J223811-104126, for which we ascertained an upper limit from the [O \textsc{i}] lines of [O/Fe] $< 0.5$ dex, and a corrected abundance of $\mbox{[O/Fe]} = 0.14 \pm 0.08$ from the O \textsc{i} triplet lines.
@@
 
-% Is there some explanation for abundance differences?
-
-The \citet{wylie-de-boer;et-al_2012} measurements indicate two stars with solar levels of Na -- identical to field star Na abundances for their metallicity -- and two stars with super-solar sodium content.
-The sodium-enhanced stars exhibit no depletion of oxygen; the abundances do not demonstrate a classical Na-O anti-correlation.
-In fact, they have a slight positive relationship: their Na-enhanced stars show an increased oxygen content, contrary to an expected oxygen depletion between stellar generations within a globular cluster.
-
-% Can these abundance differences be explained by a line-list?
-
-% In any case, suppose these stars did originate from a globular cluster.
-If the entire cluster was well-studied, the primordial component cut-off is described by Caretta as stars which are 4\sigma from the halo abundance at that metallicity.
-These stars would
+% star 		| mine 				| hers
+% C2225316	| 0.09 +/- 0.01 (2)	| 0.00 +/- 0.15
+% C2306265	| 0.18 +/- 0.00 (2)| ...
+% J221821	| 0.08 +/- 0.10 (1)| 0.03 +/- 0.15
+% J223504	| 0.18 +/- 0.07 (3)| 0.28 +/- 0.21
+% J223811	| 0.07 +/- 0.00 (1)| 0.04 +/- 0.15
+
+The \citet{wylie-de-boer;et-al_2012} measurements indicate two stars with solar levels of Na \--- identical to field star Na abundances for their metallicity \--- and two stars with super-solar sodium content: J223504 and J232619.
+We find find J223504 to be Na-enhanced with $\mbox{[Na/Fe]} = 0.18$, slightly lower than the \citet{wylie-de-boer;et-al_2012} value of $0.28 \pm 0.21$\,dex.
+This discrepancy in [Na/Fe] is the largest difference between the two studies, and still within the uncertainties published by \citet{wylie-de-boer;et-al_2012}.
+The second star in their study with elevated sodium, J232619, is not in our sample.
+We find the additional star not present in the \citet{wylie-de-boer;et-al_2012} sample, C2306265, to be sodium enhanced to the same level of J223504 with $\mbox{[Na/Fe]} = 0.18$\,dex.
 
@@
 
+The sodium-enhanced stars exhibit no depletion of oxygen; their chemistry does not demonstrate a classical Na-O anti-correlation.
+In fact, they have a slight positive relationship: the Na-enhanced stars in the \citet{wylie-de-boer;et-al_2012} study show an increased oxygen content (within the uncertainties), contrary to an expected oxygen depletion between stellar generations within a globular cluster.
+With our revised oxygen abundances and two sodium-enhanced stars, we find a very slight positive relationship of X.XX +/- X.XX, and no evidence of a Na-O anti-correlation in the Aquarius stream.
+
+If the Aquarius stream is the result of a disrupted globular cluster, we would still be missing a large part of the picture.
+Most of the Aquarius stream stars studied to date (either in this sample or the \citet{wylie-de-boer;et-al_2012} study), would be classified as belonging to a `primordial' component having chemistry indistinguishable from halo stars.
+Identifying more Aquarius stream members belonging to the intermediate component with strong oxygen depletion, or perhaps members of an extreme component, would be strong evidence for a Na-O anti-correlation and a globular cluster origin.
+Three stream stars identified to date (including two from this sample) could plausibly be classified as members of an intermediate population, with only a slight enhancement in sodium and no oxygen-depletion.
+Thus, if the strength of any Na-O relationship is to be used to vet potential disrupted hosts for the Aquarius stream, many more stream candidates will need to be identified, and observed with high-resolution.
+
+% Can these abundance differences be explained by a line-list?
+
+% In any case, suppose these stars did originate from a globular cluster.
+If the entire cluster was well-studied, the primordial component cut-off is described by Caretta as stars which are 4\sigma from the halo abundance at that metallicity.
+These stars would
+
 \subsection{The Al-Mg Relationship}
@@
 
-Bah.
-
-% what is the site and product of the Mg-Al cycle
-
-% Si is increased over time as well
-
-% what signature of this is seen in globular clusters compared to field stars
-
-% what globular clusters exhibit this phenomena? contrast it to the Na-O cycle
-
-% variations within a cluster in Mg, Al
-
-% what do we see in our Aquarius stars
-
-% the case of C2225316
+An inverse relationship between sodium and oxygen is not the only chemical pattern commonly observed in globular clusters.
+Although not ubiquitous to every system, many clusters exhibit an anti-correlation between aluminium and magnesium abundances.
+This is perhaps unsurprising, given the nucleosynthetic pathways for aluminium and magnesium.
+In addition to the CNO cycle operating during hydrogen burning, the Mg-Al chain can also operate under extreme temperatures \citep[$T_6 \sim 3$\,K][]{arnould;et-al_1999}.
+Aluminium is produced by proton capture of magnesium, beginning with $^{24}$Mg to $^{25}$Al.
+The lifetime of $\beta$-decay to proton capture allows for the production of unstable $^{27}$Si through proton capture.
+Seconds later, the isotope decays to $^{27}$Al, completing the $^{27}$Si path of the Mg-Al cycle.
+The alternative process from $^{25}$Al involves proton capture to $^{26}$Mg, but this process requires much higher temperatures ($T_6 \sim 7$\,K).
+In fact, although the process operates from temperatures above 30 million K, large Mg-Al abundance variations are not appreciable unless the temperatures reach $T_6 \sim 6.5$\,K.
+
+The Mg-Al cycle can explain the observed anti-correlation observed in some globular clusters, and most theoretical models predict such a pattern [get citations from Amanda].
+However, the locations where these extreme temperatures can be found are under some debate.
+Standard models indicate that the interiors of globular cluster stars do not reach sufficient temperatures for the Mg-Al cycle to produce the observed variations.
+Thus, although the processes for creating these chemical patterns are understood, the exact site and conditions still require explanation.
+
+No inverse correlation has been observed in the Aquarius stream stars to date.
+Given that we do not find a Na-O anti-correlation, it is not surprising that a Mg-Al pattern has not been observed.
+The Na-O signature is detected in all classical well-studied systems, but the Mg-Al anti-correlation is not always present.
+\citet{wylie-de-boer;et-al_2012} published magnesium and aluminium abundances for five stars in their Aquarius stream sample.
+No anti-correlation between the elements is present, and their abundances are not dissimilar from galactic stars.
+The abundances tabulated in Table \ref{tab:abundances} vary slightly with those presented in the \citet{wylie-de-boer;et-al_2012} sample.
+Two candidates are in good agreement: J221821 and J223811, albeit the data quality in the \citet{wylie-de-boer;et-al_2012} study did not permit measuring aluminium for J223811.
+The other two stars common between studies are C2225316 and J223504, which we found to be the most abundant in both magnesium and aluminium.
+
+While \citet{wylie-de-boer;et-al_2012} find almost no scatter ($\pm0.02$\,dex) in [Mg/Fe] for stars common to both studies, we find C2225316 and J223504 to be almost $+0.20$\,dex higher.
+The reason for this discrepancy is not obvious, given the stellar parameters between the two studies agree well with the exception of metallicity.
+In particular, the stellar parameters agree excellently for J223504, but we find $\mbox{[Fe/H]} = -0.68$ instead of the $-0.98$ as found by \citet{wylie-de-boer;et-al_2012}.
+Of the Mg \textsc{i} profiles measured, only two transitions are common to both line lists: 6318$\lambda$ and 6319$\lambda$.
+The oscillator strengths vary between studies; in these two lines the $\log{gf}$ differs by $-0.24$ and $-0.27$\,dex respectively (our oscillator strengths are lower).
+This discrepancy only complicates the matter further, since if all other things being equal, then our abundances ought to be lower than the \citet{wylie-de-boer;et-al_2012} study.
+
+% how do our values compare with Wylie de boer
+%							[Mg/Fe]						[Al/Fe]					| [Mg?]	| [Al?]
+% star 		| mine 				| hers			| mine			| hers			| 
+% C2225316	| 0.50 +/- 0.06		| 0.32 +/- 0.05	| 0.68 +/- 0.04	| 0.38 +/- 0.12	| No, + | No, +
+% C2306265	| 0.41 +/- 0.05		| ...			| 0.28 +/- 0.04	| ...			| N/A	| N/A 
+% J221821	| 0.34 +/- 0.05		| 0.30 +/- 0.01	| 0.21 +/- 0.10	| 0.29 +/- 0.12	| Yes +	| Yes -
+% J223504	| 0.49 +/- 0.09		| 0.33 +/- 0.05	| 0.31 +/- 0.05	| 0.21 +/- 0.03	| No +	| No +
+% J223811	| 0.32 +/- 0.01		| 0.30 +/- 0.06	| 0.10 +/- 0.10	| ...			| Yes +	| N/A
 
@@
 
+The [Mg/Fe] and [Al/Fe] abundances found for the five Aquarius stars in this sample are illustrated in Figure \ref{fig:mg-al}.
+Interestingly, our stars exhibit a strong positive relationship, with a best-fitting slope of $\mbox{[Al/Fe]} = X.XX x \mbox{[Mg/Fe]} + Y.YY$ ($R = Y.YY$).
+If the exclude C2225316, our chemically peculiar star with enhanced [Al/Fe] relative to the rest of the sample, the slope decreases to $\mbox{[Al/Fe]} = X.XX x \mbox{[Mg/Fe]} + Y.YY$ and the correlation coefficient $R$ increases to Z.ZZ.
+Even when a Mg-Al anti-correlation is not detected in globular clusters, there is generally some scatter in [Al/Fe] at constant [Mg/Fe] \--- early indications of the nucleosynthetic pattern.
+No classical globular cluster exhibits a positive correlation.
+
+\# Discuss prediction of positive correlation.
+Some intermediate-mass ($4M_\odot$) AGB models predict a positive correlation between aluminium and magnesium \citet{karakas;et-al}.
+Under extreme temperatures ($T_6 \sim 300$\,K), substantial $^{25}$Mg and $^{26}$Mg are produced by $\alpha$-capture onto $^{22}$Ne by the $^{22}$Ne($\alpha$,n)$^{25}$Mg and $^{22}$Ne($\alpha$,$\gamma$)$^{26}$Mg reactions respectively.
+Following deep dredge up, significant $^{25}$Mg and $^{26}$Mg is mixed into the photosphere, more than the quantity of $^{26}$Al produced through the Mg-Al cycle and making up for the depleted Mg that is expensed during the Mg-Al pathway.
+Thus, a positive relationship between magnesium and aluminium can occur if there has been significant contributions from intermediate mass AGB stars undergoing dredge up.
+Alternatively, a positive relationship between magnesium and aluminium can occur from SN \textsc{ii} contributions.
+Distinguishing between these processes requires careful measurements of magnesium isotope abundances $^{24}$Mg (supernovae), $^{25}$Mg and $^{26}$Mg (AGB stars), which is not possible given our $S/N$ or spectral resolution.
+
+\# What does the thick/thin disk look like in these elements?
+
 \subsection{The Na-Ni Relationship}
@@
 \citet{fulbright_2000} saw a similar signature: stars with low [Na/Fe] were only found at large ($R_\odot > 20$\,kpc) distances.
-\citet{nissen;schuster_1997} proposed that since the outer halo is thought to have been built up through the accretion of dSph satellites, then the Na-Ni pattern may be a chemical indicator of merger history in the galaxy.
+\citet{nissen;schuster_1997} proposed that since the outer halo is thought to have been built up by the accretion of dwarf satellite galaxies, then the Na-Ni pattern may be a chemical indicator of merger history within the galaxy.
 
 With additional data from \citet{nissen;schuster_2011}, the Na-Ni relationship was found to be slightly steeper than originally put forward.
-The pattern exists only for metal-rich stars $-1.5 < \mbox{[Fe/H]} < -0.5$ dex, and is not seen in metal-poor dSph stars, providing a potentially useful indicator for investigating chemical evolution.
+The pattern exists only for stars with $-1.5 < \mbox{[Fe/H]} < -0.5$ dex, and is not seen in metal-poor dSph stars, providing a potentially useful indicator for investigating chemical evolution.
 
@@
 Recall that the total Na production primarily depends on the neutron excess.
-Thus, through populations of massive stars undergoing C-burning, a positive correlation between Na-Ni can be expected.
+Thus, through populations of massive stars undergoing C-burning, a positive correlation between sodium and nickel can be expected.
 
@@
 
-Stars originating in dwarf spheroidal galaxies and globular clusters have very different star formation environments.
-Consequently, they exhibit chemical patterns that reflect their nucleosynthetic antiquity.
+Stars originating in dwarf spheroidal galaxies and globular clusters have very different chemical enrichment environments.
+Consequently, they exhibit chemistry that reflects their nucleosynthetic antiquity.
 Dwarf spheroidal stars do not demonstrate enhanced sodium or nickel, as there has been a relatively negligible linage of massive stars undergoing supernova.
@@
 
-The most that can be inferred from the Na, Ni abundances of Aquarius stream stars is that their star formation history is less like a dwarf spheroidal environment, and more representative of an environment more like a globular cluster or the MW disk.
+The most that can be inferred from the Na, Ni abundances of Aquarius stream stars is that their star formation history is less like a dwarf spheroidal environment, and more representative of an environment similar to either a globular cluster, or the disc of the Milky Way.
+
+\subsection{The Chemical Distinctiveness of C2225316}
+
+% for a high mass AGB
+%Sr/Ba ~ 0.4
+
+C2225316 exhibits peculiar chemical abundances when compared to the rest of the Aquarius stream candidates in our sample.
+It is over-abundant in light refractory elements, with $\mbox{[Al/Fe]} = 0.68 \pm 0.04$, $\mbox{[Mg/Fe]} = 0.50$, and $\mbox{[O/Fe] = 0.49}$\,dex.
+Silicon is enhanced to a level of $\mbox{[Si/Fe]} = 0.72 \pm 0.07$, which is +0.34\,dex more than any other star in our sample.
+In addition to light element enhancement, C2225316 exhibits a strong barium content of $\mbox{[Ba/Fe]} = 0.70$\,dex.
+This abundance is well in excess of the halo ($\mbox{[Ba/Fe]} \sim 0.0$), and our other Aquarius stream stars, which vary between $-$0.02 to 0.15\,dex.
+
+High $s$-process enhancements have been noted for a few disrupted globular clusters that exhibit a wide metallicity range.
+Most noteably: $\omega$Centurai \citep{Majewski;et-al_2012}, M22 \citep{marinolet-al_2011} and (\# any others?).
+Like the Aquarius co-moving group, both clusters are relatively close to the sun: $R_\odot = 5.2$\,kpc and 3.2\,kpc, respectively.
+M22 has a mean metallicity of $\mbox{[Fe/H]} \sim -1.7$, varying between $-2.0 < \mbox{[Fe/H]} < -1.6$\,dex.
+C2225316 has an $\mbox{[Fe/H]} = -1.26$\,dex, making it unlikely to be associated with M22.
+However, the high barium content and overall metallicity of C2225316 ($\mbox{[Fe/H]} = -1.26$) suggests there may be an association with $\omega$-Centurai.
+
+Within $\omega$-Centurai, there are three distinguishable sub-populations with various proportions.
+
+\# Comparison of all abundances to omega cen abundances in a plot
+
+\# Plot of majewski
+
+\citet{majewski;et-al_2012} modelled
 
@@
 Since the Aquarius stream is kinematically coherent, the default assumption is that the system has been accreted.
-
-% their chemistry is indicative of not belonging to a dwarf spheroidal
-
-% open cluster
-
-% Chemistries for various GC trends
-
-% chemistries - [Na/O]
-
-% chemistries - [Al/Mg]
-
-% chemistries - [Ni/Na]
-
-% closest looking globular clusters from Harris catalogue
+The stream candidates presented here are slightly enhanced in sodium and nickel, suggesting that if a progenitor ever existed then its environment was more like a globular cluster than a dwarf satellite.
+If the progenitor is a disrupted globular cluster, and all our candidates are members, then it is unique in that it has a wider metallicity distribution than most globular clusters.
+
+However, our chemical analysis does not reveal any inverse Na-O correlation \--- which would be strong evidence for a globular cluster environment.
+Furthermore, we observe a positive Mg-Al relationship, the same seen by \citet{wylie-de-boer;et-al_2012} and contrary to what would be expected from a globular cluster environment.
+High resolution, high $S/N$ spectra for the entire stream may be required before such a signature may become apparent.
+In this section we discuss the possible causes for the Aquarius co-moving group.
+
+Based on a lack of $\alpha$-enhancement and increased Na, Ni content, we exclude the possibility that the Aquarius stream has resulted from a disrupted dwarf satellite.
+
+\subsubsection{$\omega$-Centurai}
+
+In their original discovery paper, \citet{williams;et-al_2011} attempted to exclude possible known progenitors.
+On the basis of metallicity, distance, proper motions\footnote{We find the proper motions in Table 1 of \citet{williams;et-al_2011} to be mis-associated to incorrect stars.
+However, this typographical error did not propagate through to the transverse velocity calculations (Williams, M.E.K, private communication).}, transverse velocities and orbital energies, the authors were able to exclude all known Milky Way satellites, with the notable exception of $\omega$-centurai.
+Although the Aquarius stream metallicity distribution we find is not dissimilar from a known sub-population in $\omega$-centurai, the individual chemical abundances are quite distinct.
+
+$\omega$-Centurai members exhibit a strong $s$-process enhancement with overall metallicity.
+This signature is not observed in our data, with the exception of C2225316, which seems to be chemically distinct from the other Aquarius group candidates.
+
+Due to our limited sample size, it is impossible to know whether C2225316 is an outlier, or our four other candidates are halo interlopers.
+Either position is debatable, and each lead to interesting conclusions.
+If most of our observed candidates are halo members, and C2225316 represents the Aquarius stream chemistry, then an association between Aquarius and $\omega$-Centurai is possible.
+Alternatively, the stream may indicate first evidence of a minor merger within the Milky Way disc.
+However, with certainty we can state that most observed Aquarius stream candidates do not exhibit enhanced $s$-process elements, and are therefore unlikely to be associated with $\omega$-Centurai \--- or any other globular cluster.
+
+\subsubsection{Disrupted Disk Stars \--- Signature of a Minor Merger}
+
+\# Velocity distribution wide
+
+\# Spatial distribution wide
+
+\# Chemistry rules out a dSph origin
+
+\# No signs of classical GC chemical patterns
+
+\# The stream chemistry is indistinguishable from disk stars in every aspect
+
+\# Revised distances to each star, transverse motions + orbital energies calculated
+
+\# Monte-carlo simulations demonstrate strongly retrograde stars wrt thick disk + halo
+
+\# Orbital energy pattern aligns exactly with Zolotov+ simulations, but would require a smaller mass of the disrupter (minor merger)
+
+\# Need to discuss disk is unlikely to have had a merger in past 8 Gyr
 
 % could they be displaced thick disk stars?
-
-\begin{deluxetable*}{lccccccc}
-\tablecolumns{2}
-\tabletypesize{\scriptsize}
-\tablecaption{Observed Targets\label{tab:observed-targets}}
-\tablehead{
-	\colhead{ID} &
-	\colhead{$\alpha$} &
-	\colhead{$\delta$} &
-	\colhead{Air mass} &
-	\colhead{S/N\tablenotemark{a}} &
-	\colhead{$V_{\mbox{helio}}$} \\
- & (J2000) & (J2000) & & (px$^{-1}$) & (km s$^{-1}$)
-}
-\startdata
-
-HD130694  			& 14:50:17.1 & --27:57:41.6 & 1.289 & \nodata & \nodata \\
-HD170642  			& 18:32:21.0 & --39:42:12.8 & 1.464 & \nodata & \nodata \\
-HD180928  			& 19:18:59.6 & --15:32:11.5 & 1.934 & \nodata & \nodata \\
-HD181342  			& 19:21:03.9 & --23:37:09.7 & 1.203 & \nodata & \nodata \\
-HD187111 			& 19:48:39.3 & --12:07:17.8 & 1.281 & \nodata & \nodata \\
-HD210049  			& 22:08:22.8 & --32:59:14.6 & 1.006 & \nodata & \nodata \\
-C2225316-145437  	& 22:25:31.7 & --14:54:39.6 & 1.033 & \nodata & \nodata \\
-J221821-183424 		& 22:18:21.2 & --18:34:28.3 & 1.026 & \nodata & \nodata \\
-J223504-152834 		& 22:35:04.5 & --15:28:34.9 & 1.047 & \nodata & \nodata \\
-J223811-104126 		& 22:38:11.6 & --10:41:29.4 & 1.218 & \nodata & \nodata \\
-C2306265-085103		& 23:06:26.6 & --08:51:04.8 & 1.096 & \nodata & \nodata \\
-HD219615  			& 23:17:10.7 &$+$03:16:51.9 & 1.412 & \nodata & \nodata 
-\enddata
-\tablenotetext{a}{S/N measured at 6000 \AA{} for each target.}
-\end{deluxetable*}
 
@@
 
-% Toombre
+% Toombre #TODO - make this a 4panel in UVW
 \begin{figure}[h]

### 2013-01-13 2012-aqs/figures/plot-mg-al.py
Added Mg-Al plot and code

@@ -1,7 +1,125 @@
 import matplotlib.pyplot as plt
 import numpy as np
 
-# Get Na and O from files:
+# Get data from Reddy et al 2003
+reddy_2003 = np.loadtxt('Reddy_disk_2003.data', delimiter='|', usecols=(18, 19), dtype=str)
+
+Reddy_2003_Mg_Fe = []
+Reddy_2003_Al_Fe = []
+
+for mg, al in reddy_2003:
+	mg = mg.strip()
+	al = al.strip()
+
+	if len(mg) == 0:
+		mg = np.nan
+
+	else:
+		mg = float(mg)
+
+	if len(al) == 0:
+		al = np.nan
+
+	else:
+		al = float(al)
+
+	Reddy_2003_Al_Fe.append(al)
+	Reddy_2003_Mg_Fe.append(mg)
+
+
+Fulbright_2000_Al_Fe = []
+Fulbright_2000_Mg_Fe = []
+
+with open('Fulbright_2000.data', 'r') as fp:
+	data = fp.readlines()
+
+	for line in data:
+		if line.startswith('#'): continue
+
+		mg = line[26:31].strip()
+		al = line[32:37].strip()
+
+		if len(mg) == 0:
+			mg = np.nan
+
+		else:
+			mg = float(mg)
+
+		if len(al) == 0:
+			al = np.nan
+
+		else:
+			al = float(al)
+
+		Fulbright_2000_Mg_Fe.append(mg)
+		Fulbright_2000_Al_Fe.append(al)
+
+
+# Get data from Reddy et al 2005
+reddy_data = np.loadtxt('Reddy_thick_disk_2005.data', delimiter='|', usecols=(1, 18, 22, 23), dtype=str)
+
+Reddy_ThickDisk_Mg_Fe = []
+Reddy_ThickDisk_Al_Fe = []
+Reddy_ThinDisk_Mg_Fe = []
+Reddy_ThinDisk_Al_Fe = []
+Reddy_ThickThinDisk_Mg_Fe = []
+Reddy_ThickThinDisk_Al_Fe = []
+Reddy_Halo_Mg_Fe = []
+Reddy_Halo_Al_Fe = []
+Reddy_ThickDisk_Halo_Mg_Fe = []
+Reddy_ThickDisk_Halo_Al_Fe = []
+
[…]

### 2013-01-13 2012-aqs/figures/plot-fe-peak.py
Added fe peak plot code

@@ -1,0 +1,176 @@
+import matplotlib.pyplot as plt
+import numpy as np
+
+# Get Na and O from files:
+data_files = ['c2225316-14437_abundances.data', 'c2306265-085103_abundances.data', 'j221821-183424_abundances.data', 'j223504-152834_abundances.data', 'j223811-104126_abundances.data']
+
+Sc_Fe = []
+e_Sc_Fe = []
+
+V_Fe = []
+e_V_Fe = []
+
+Cr_Fe = []
+e_Cr_Fe = []
+
+Mn_Fe = []
+e_Mn_Fe = []
+
+Fe_H = []
+e_Fe_H = []
+
+observed_data = {}
+for filename in data_files:
+
+	data = np.loadtxt(filename, dtype=str, usecols=(0, -6, -4, -2,))
+	observed_data[filename] = data
+
+	idx = list(data[:,0]).index('Sc') + 1 # (Use Sc II)
+	_Sc_Fe, _e_Sc_Fe = data[idx, 2:]
+
+	idx = list(data[:,0]).index('V')
+	_V_Fe, _e_V_Fe = data[idx, 2:]
+
+	idx = list(data[:,0]).index('Cr')
+	_Cr_Fe, _e_Cr_Fe = data[idx, 2:]
+
+	idx = list(data[:,0]).index('Mn')
+	_Mn_Fe, _e_Mn_Fe = data[idx, 2:]
+
+	idx = list(data[:, 0]).index('Fe')
+	_Fe_H, _e_Fe_H = data[idx, 1], data[idx, -1]
+
+	Sc_Fe.append(_Sc_Fe)
+	e_Sc_Fe.append(_e_Sc_Fe)
+
+	V_Fe.append(_V_Fe)
+	e_V_Fe.append(_e_V_Fe)
+
+	Cr_Fe.append(_Cr_Fe)
+	e_Cr_Fe.append(_e_Cr_Fe)
+
+	Mn_Fe.append(_Mn_Fe)
+	e_Mn_Fe.append(_e_Mn_Fe)
+
+	Fe_H.append(_Fe_H)
+	e_Fe_H.append(_e_Fe_H)
+
+
+
+# Clean up Mg_Fe, Fe_H, e_Mg_Fe, e_Fe_H
+Sc_Fe = map(float, [value.replace('$', '').replace('\\', '').replace('nodata', 'nan') for value in Sc_Fe])
[…]

### 2013-01-29 2012-aqs/draft-aqs.tex
yolo

@@
 \title{No Evidence for the Aquarius Co-Moving Group \\Resulting from a Disrupted Classical Globular Cluster\altaffilmark{1}}
+
+% TODO:
+% [DONE] Na/O subplots
+% Na/O comparison with halo
+% [DONE] Mg/Al subplots
+% - Ni/Na plane plot
+% - Add standard stars to observations table
+% - Add standard stars chemical abundances
+% - Add in-line text referencing standard star chemical abundances
+% - Uncertainties analysis
+% - Strontium?
+% - Carbon?
+% - Distance calculations
+% - Transverse motions table
+% - Transverse motions text
+% - Orbital energies plot
+% - Minor merger text
+% - Conclusions
+
+% Casey, Keller, Alves-Brito, Frebel, Da Costa, Schlaufman, Freeman, Heather, QinQin
 
@@
 \begin{abstract}
-We present a detailed analysis of five Aquarius stream giant stars observed using the MIKE spectrograph on the Magellan Clay telescope.
-Enhanced sodium and nickel abundances suggest the group is not the result of a dwarf satellite galaxy, and that its chemical enrichment environment is more like a globular cluster or the thick disk of the Milky Way.
-However, we find no evidence that the group is a result of a disrupted globular cluster.
-Our data indicate the Aquarius stream has a large metallicity dispersion of $\sigma(\mbox{[Fe/H}]) = 0.32$\,dex.
+We present a detailed analysis of five Aquarius stream candidate stars observed using the MIKE spectrograph with the Magellan Clay telescope.
+Enhanced [Na/Fe] and [Ni/Fe] abundance ratios suggest the co-moving group is not the result of a dwarf satellite galaxy, and that its chemical enrichment environment is more representative of either a globular cluster, or the Milky Way thick disc.
+However, we find no evidence that the stream is a result of a disrupted cluster.
+Our data indicate the Aquarius stream has a  metallicity dispersion of $\sigma(\mbox{[Fe/H}]) = 0.32$\,dex.
 No inverse Na-O correlation is present, and we find a positive Mg-Al relationship.
-Chemically, the group is indistinguishable from the Milky Way thick disk with the exception of one very interesting candidate, which is most likely tidal debris from $\omega$-Centurai.
+Chemically, the group is indistinguishable from the Milky Way thick disk with the exception of one very interesting candidate, which we hypothesise is tidal debris from $\omega$-Centurai.
 Assuming all other candidates are Aquarius members, we propose the co-moving group has arisen from a minor merger in the Milky Way's thick disk.
@@
 \section{Introduction}
-Galaxies are formed hierarchically through chaotic mergers of smaller systems.
+Galaxies are hierarchically formed through chaotic mergers of smaller systems.
 The Milky Way is no exception.
-In our own stellar halo, we see ongoing evidence of these accretion events.
+The accumulating stellar debris in our own galactic halo provides ongoing evidence for such merging events.
 As accreting satellites infall onto the galaxy, tidal forces disrupt the dwarf, hurtling stars in leading and trailing directions.
-The phase space information of stars within these `stellar streams' are sensitive to the galactic potential.
-They can collectively constrain the fraction and distribution of accreted matter in the stellar halo, the sub-halo mass function, as well as the shape and extent of dark matter in the Milky Way.
+Unsurprisingly, the velocities of stars within these `stellar streams' are sensitive to the galactic potential.
+As such, their phase-space information can collectively constrain the fraction and distribution of accreted matter in the galaxy, the sub-halo mass function, as well as the shape and extent of dark matter in the Milky Way.
 Moreover, individual chemical abundances can constrain the  precise nucleosynthesis sites where elements are forged, as well as trace the chemical evolution of the galaxy.
@@
 Wide-field surveys have proved excellent sources for finding stellar streams.
-Dozens of streams reaching out up to 150\,kpc in the halo have been identified through photometric selections and matched-filtering techniques \citep{belokurov;et-al_2007,koposov_SG1}.
+Dozens have been identified through photometric selections and metched-filtering techniques, with some to a galactocentric distance of 100\,kpc \citep{belokurov;et-al_2007,koposov_SG1, drake;et-al_2013}.
 Indeed, it is clear that a large fraction of the stellar halo has been built up by accretion.
@@
 % Talk about RAVE
-It is therefore necessary to survey solar neighbourhood stars with spectroscopy in order to detect any nearby substructures.
-The RAVE (Radial Velocity Experiment) team began such a survey in 2003 and have observed spectra from over 500,000 stars across 17,000 deg$^{2}$.
-As the name suggests, the primary goal of RAVE was to obtain radial velocities for the solar neighbourhood and beyond.
+It is therefore necessary to survey solar neighbourhood stars with spectroscopy to permit any nearby substructures to reveal themselves.
+The RAVE (Radial Velocity Experiment) team began such a survey in 2003 and have observed spectra from over 500,000 stars across 17,000\,deg$^{2}$.
+As the name hints, the primary goal of RAVE was to obtain radial velocities for the solar neighbourhood and beyond.
 In an attempt to remain kinematically unbiased, RAVE candidates were selected based only on their apparent magnitude.
 With the exception of bulge stars, where some photometric cuts were employed, all stars between 9 $<$ I $<$ 13 were observed.
-Almost all of these candidates have published radial velocity measurements \citep{steinmetz;et-al_2006}, and for a subset of stars with sufficient S/N, estimates of stellar parameters have been derived using a $\chi^2$ minimization technique \citep{zwitter;et-al_2008, siebert;et-al_2011}.
+Almost all of these candidates have published radial velocity measurements \citep{steinmetz;et-al_2006}, and for a subset of stars with sufficient Signal-to-Noise ($S/N$), estimates of stellar parameters have been derived using a $\chi^2$ minimization technique \citep{zwitter;et-al_2008, siebert;et-al_2011}.
 
@@
 Thus, the co-moving group was named the Aquarius stream.
-The stream is most apparent when examining velocities against galactic latitude for stars within $-70\,^\circ < b < -50\,^\circ$.
-\citet{williams;et-al_2011} employed a selection criteria of $-250\,\mbox{km s}^{-1} < V_{HEL} < -150\,\mbox{km s}^{-1}$, $30\,^\circ < l < 75\,^\circ$ and $J > 10.3$ to maximize the contrast between the stream and background, identifying 15 candidates in the process.
-The average heliocentric velocity of these members was found to be $V_{HEL} = -199\,\mbox{km s}^{-1}$, with a dispersion of 27\,km s$^{-1}$.
+The artefact is most apparent when examining velocities against galactic latitude for stars within $-70\,^\circ < b < -50\,^\circ$.
+\citet{williams;et-al_2011} employed a selection criteria of $-250\,\mbox{km s}^{-1} < V_{\rm hel} < -150\,\mbox{km s}^{-1}$, $30\,^\circ < l < 75\,^\circ$ and $J > 10.3$ to maximize the contrast between the stream and background, identifying 15 candidates in the process.
+The average heliocentric velocity of these members was found to be $V_{\rm hel} = -199\,\mbox{km s}^{-1}$, with a dispersion of 27\,km s$^{-1}$.
 The radial velocity uncertainties provided by the RAVE catalog are described to be $\sim$2\,km s$^{-1}$, so the wide kinematic distribution appears to be real.
@@
 In order to quantify the statistical likelihood that the Aquarius stream is truly separate from a smooth halo distribution, \citet{williams;et-al_2011} compared the number of observed RAVE stars within $-70\,^\circ < b < -50\,^\circ$ against the Galaxia \citep{sharma;et-al_2011} and Besan\c{c}on \citep{robin;et-al_2003} galaxy simulations.
-The predicted particles in each model between $-70\,^\circ < b < -50\,^\circ$ were binned in $\Delta{l} \times \Delta{V_{hel}}$ blocks using varying grid cell sizes between $25\,^\circ$ to $70\,^\circ$ and $20\,\mbox{km s}^{-1}$ to $100\,\mbox{km s}^{-1}$ respectively.
-The RAVE sample was binned in the same way, and the statistical significance of the over-density is calculated for each cell.
-\citet{williams;et-al_2011} found the stream to be statistically significant ($>$4-$\sigma$) in 96\% of the grid cell sizes employed for the Besan\c{c}on model.
+The predicted particles in each model between $-70\,^\circ < b < -50\,^\circ$ were binned in $\Delta{l} \times \Delta{V_{\rm hel}}$ blocks using varying grid cell sizes between $25\,^\circ$ to $70\,^\circ$ and $20\,\mbox{km s}^{-1}$ to $100\,\mbox{km s}^{-1}$.
+The RAVE sample was binned in the same way, and the statistical significance of the observed over-density is discretized.
+\citet{williams;et-al_2011} found the stream to be statistically significant ($>$4-$\sigma$) in 96\% of the cell proportions employed for the Besan\c{c}on model.
 By sampling the Galaxia model repeatedly with varying extinction rates, a similar result was found: between $75\pm15$\,\% to $80\pm18$\,\% of grid cells showed the Aquarius stream to significant at the 4-$\sigma$ level or higher.
 Given the high-latitude and proximity of the stream, it is not surprising that dust had a negligible effect on the statistical significance.
-\citet{williams;et-al_2011} concluded that the over-density in $l, V_{hel}$ is a true substructure, and neither the choice of galaxy model, cell size, nor the extinction model made any real difference to the stream detection significance.
+\citet{williams;et-al_2011} concluded that the over-density in $l, V_{\rm hel}$ is a true substructure, and neither the choice of galaxy model, cell dimension, nor the extinction model made any real difference to the detection significance.
 
@@
 
-Given the extent of stellar debris the Sagittarius dwarf has littered throughout the Milky Way, it is reasonable to suspect the Aquarius stream might originate from the Sagittarius dwarf.
-Indeed, the Aquarius stream stars do not lie far from the orbital plane of Sagittarius and the metallicities reported by \citet{williams;et-al_2011} are not dissimilar from the Sagittarius stream.
-However, \citet{williams;et-al_2011} found the Aquarius space positions and kinematics (specifically $V_{Z}$ and $V_\phi$) are quite distinct from Sagittarius.
+The Sagittarius stream is arguably the most prominent ongoing accretion event in the galaxy.
+Given the extent of stellar debris the dwarf has littered throughout the Milky Way, it is reasonable to suspect the Aquarius stream might originate from the Sagittarius dwarf.
+Indeed, the Aquarius  stars do not lie far from the orbital plane of Sagittarius, and the metallicities reported by \citet{williams;et-al_2011} are not dissimilar from the Sagittarius stream.
+However, \citet{williams;et-al_2011} found the Aquarius transverse motions (specifically $V_{Z}$ and $V_\phi$) to be quite distinct from Sagittarius.
 Based on the phase space information available, \citet{williams;et-al_2011} concluded that the newly discovered stream could not be positively associated with the Monoceros stream, Hercules-Aquila cloud, or either the Canis Major or Virgo over-densities.
@@
 Of the 12 Aquarius stars in the \citet{williams;et-al_2011} discovery sample with stellar parameters, the metallicity range is wide: between --2.02 and --0.33 dex.
-Spectroscopic observations of high resolution with high signal-to-noise ($S/N$) are necessary to accurately characterize the stream's metallicity distribution.
+Spectroscopic observations of high resolution with high $S/N$ are necessary to accurately characterize the stream's metallicity distribution.
 
@@
 Their data indicate a very narrow metallicity distribution: $\mbox{[Fe/H]} = -1.09 \pm 0.10$\,dex extending between $\mbox{[Fe/H]} = -1.25$ to $-0.98$\,dex.
+Observations of such minimal chemical scatter from stars with a common origin is typically noted in either globular, or open clusters.
 The largest [Fe/H] discrepancy between the \citet{williams;et-al_2011} and \citet{wylie-de-boer;et-al_2012} study was $\Delta\mbox{[Fe/H]} = -0.66$\,dex for the most metal-rich star in the \citet{williams;et-al_2011} sample.
 The most metal-poor star in the \citet{williams;et-al_2011} study was not observed by \citet{wylie-de-boer;et-al_2012}.
+
 In addition to ascertaining stellar parameters, \citet{wylie-de-boer;et-al_2012} measured elemental abundances for the Aquarius stream stars -- the only study to do so until now.
-Their study primarily focussed on light elements: Na, O, Ni, Mg, and Al.
+The authors primarily focussed on light elements: Na, O, Ni, Mg, and Al.
 Chemical patterns in these light elements arise as natural consequences of nucleosynthetic processes in massive stars.
 These patterns have been repeatedly observed in globular clusters.
-Specifically, an anti-correlation between sodium and oxygen abundance has been found to be ubiquitous to globular clusters.
-Originally this was thought to arise from internal mixing along the giant branch.
-However, dwarf stars were later found to exhibit strong Na-enhancement and O-depletions, contrary to what would be expected if the Na-O anti-correlation was purely a result of internal mixing.
-It is well known now that photospheric abundance variations resulting from internal mixing are limited to C, N and Li.
-While the exact astrophysical mechanism for oxygen-depletion remains under debate, the chemical relationship is well-established empirically.
+Specifically, an anti-correlation between sodium and oxygen content appears ubiquitous to globular clusters.
+Originally this relationship was thought to arise from internal mixing along the giant branch.
+However, dwarf globular cluster stars were found to exhibit strong Na-enhancement and O-depletion, contrary to what would be expected if the Na-O anti-correlation was purely a result of internal mixing.
+It is well known now that photospheric abundance variations resulting from internal mixing are limited to carbon, nitrogen and lithium.
+Additionally, light element variations can be explained by classic nucleosynthetic pathways, albeit extreme temperatures are necessary for such relationships to arise \--- much higher than would reasonably be expected in globular cluster stars.
+Several descriptions for an astrophysical site that would permit such nucleosynthetic processes have been hypothesized, including massive intermediate-mass Asymptotic Giant Branch (AGB) binary stars \citep{de_mink;et-al_2009} and fast-rotating massive stars \citep{decressin;et-al_2007}.
+While the exact formation site is still under debate, the chemical relationship is well-established empirically.
 The Na-O pattern provides the best chemical evidence that their chemical enrichment history has been dominated by Sn \textsc{ii} events and that those stars formed in a globular cluster-like environment.
 
-From high-resolution spectroscopy of five stars in Aquarius, four of which had Na and O measurements, \citet{wylie-de-boer;et-al_2012} found two stars with super-solar sodium; slightly higher [Na/Fe] ratios than halo stars of the same metallicity.
-However, no strong oxygen depletion was evident in their data.
-
-There are other chemical abundance patterns that allow us to infer the chemical evolution of a given cluster.
-\citet{nissen;schuster_1997} first noted that distant solar neighbourhood stars were enriched in [Ni/Fe] and [Na/Fe].
+From high-resolution spectroscopy of five candidate Aquarius stars, four of which had sodium and oxygen abundance measurements, \citet{wylie-de-boer;et-al_2012} found two stars with super-solar sodium; slightly higher [Na/Fe] ratios than halo stars of the same metallicity.
+However, no strong oxygen depletion was evident in the data.
+Thus, they observed no evidence of a classical Na-O inverse correlation in the Aquarius stream.
+
+There are other chemical abundance patterns that allow us to infer the chemical enrichment environment.
+\citet{nissen;schuster_1997} first noted that nearby solar neighbourhood stars were enriched in [Ni/Fe] and [Na/Fe].
 \citet{fulbright_2000} came to a similar conclusion: only somewhat distant ($R_\odot > 20$\,kpc) stars are likely to be sodium deficient.
 If the stellar halo has been built up from the accretion of smaller dwarf satellites, \citet{nissen;schuster_1997} proposed that this chemical trend may be indicative of the halo merger history since stars at larger $R_\odot$ are more likely to have been accreted rather than formed in-situ.
-\citet{wylie-de-boer;et-al_2012} found all the Aquarius stars in their sample to be enriched in both sodium and nickel; contrary to what would be expected if the stars originated from a disrupted dSph satellite.
+\citet{wylie-de-boer;et-al_2012} found all the Aquarius stars in their sample to be enriched in both sodium and nickel; contrary to what would be expected if the stars originated from a disrupted dwarf spheroidal (dSph) galaxy.
 This provided an additional indication that the Aquarius stream stars originated in a globular cluster-like environment.
 
-Combined with the low level of chemical scatter present in their sample, these chemical indicators led \citet{wylie-de-boer;et-al_2012} to conclude that the Aquarius stream must be the result of a tidally disrupted globular cluster.
-\citet{williams;et-al_2011} had previously precluded this possibility with any known globular clusters after modelling an Aquarius-like progenitor infalling onto the Milky Way and comparing the predicted $l, b, V_{hel}$ with known, nearby globular clusters of similar metallicities.
+Combined with the low level of chemical scatter present in their sample, these chemical indicators led \citet{wylie-de-boer;et-al_2012} to conclude that the Aquarius stream is the result of a tidally disrupted globular cluster.
+\citet{williams;et-al_2011} had previously precluded this possibility with any known globular clusters after modelling an Aquarius-like progenitor infalling onto the Milky Way and comparing the predicted $l, b, V_{\rm hel}$ with known, nearby globular clusters of similar metallicities.
 No known globular cluster could match their simulation.
+If both scenarios are accurate then the undiscovered disrupting cluster might still remain, and would be relatively close by.
 
 We seek to investigate the nature of the Aquarius stream, specifically the recent globular cluster origin claim made by \citet{wylie-de-boer;et-al_2012}.
-We present a detailed analysis for five  Aquarius stream members from high-resolution, high $S/N$ observations taken using the Magellan Inamori Kyocera Echelle spectrograph \citep{bernstein;et-al_2003} on the Magellan Clay telescope.
+We present a detailed analysis for five Aquarius stream candidates from high-resolution, high $S/N$ observations taken using the Magellan Inamori Kyocera Echelle spectrograph \citep{bernstein;et-al_2003} with the Magellan Clay telescope.
 Details of the observations and data reduction are outlined in the following section.
-The data analysis is chronicalled in Section \ref{sec:analysis} and a detailed discussion of these results resides in Section \ref{sec:discussion}.
+The data analysis is chronicled in Section \ref{sec:analysis} and a detailed discussion of these results resides in Section \ref{sec:discussion}.
 In Section \ref{sec:conclusion} we present our conclusions and critical interpretations.
@@
 	\colhead{S/N\tablenotemark{a}} &
-	\colhead{$V_{rad}$} &
-	\colhead{$V_{hel}$} &
-	\colhead{$V_{err}$} \\
+	\colhead{$V_{\rm rad}$} &
+	\colhead{$V_{\rm hel}$} &
+	\colhead{$V_{\rm err}$} \\
  & (J2000) & (J2000) & Date & & (") & (secs) & (px$^{-1}$) & (km s$^{-1}$) & (km s$^{-1}$) & (km s$^{-1}$)
@@
 The most complete sample of Aquarius stream stars is presented in the discovery paper of \citet{williams;et-al_2011}.
-Our sample includes five stars: four common to the \citet{wylie-de-boer;et-al_2012} study, and an additional star from the original \citet{williams;et-al_2011} sample.
-The additional candidate, J2306265-085103, was observed by the RAVE survey but had a $S/N$ ratio too low for stellar parameters to be accurately determined.
+Our sample includes five stars: four common to the \citet{wylie-de-boer;et-al_2012} study, and an additional candidate from the original \citet{williams;et-al_2011} sample.
+The supplementary star, J2306265-085103, was observed by the RAVE survey but had a $S/N$ ratio too low for stellar parameters to be accurately determined.
 All program stars were observed in July 2011 in good seeing at low airmass (Table \ref{tab:observations}), and X additional standard stars were observed in March 2011.
 All observations were taken using a 1.0'' slit, providing a spectral resolution of $\mathcal{R} = 28,000$ in the blue and $\mathcal{R} = 22,000$ in the red arm.
-The total exposure times for our program stars varied per star from X-Y seconds to ensure a Signal-to-Noise ratio ($S/N$) ratio in excess of 100 per pixel element at 600 nm.
+The total exposure times for our program stars varied per star from X-Y seconds to ensure a $S/N$ ratio in excess of 100\,pixel$^{-1}$ at 600\,nm.
 
@@
 The data were reduced using the CarPy pipeline\footnote{http://code.obs.carnegiescience.edu/mike}.
-One of our standard stars, HD 41667, was also reduced using standard extraction and calibration methods in \textsc{iraf}.
-The resultant spectra from both reduction approaches were compared for residual fringing, $S/N$, and wavelength calibration.
-No noteworthy differences were present, and the CarPy pipeline was utilized for the remainder of the reductions.
+One standard stars, HD 41667, was also reduced using standard extraction and calibration methods in \textsc{iraf}.
+The resultant spectra from both approaches were compared for residual fringing, $S/N$, and wavelength calibration.
+No noteworthy differences were present, and the CarPy pipeline was utilized for the remainder of the data reductions.
 Each reduced echelle order was carefully normalized using a third order spline with defined knot spacing.
@@
 The white dwarf HR 6141 was observed on X as a telluric standard.
-The $S/N$ ratio for HR 6141 exceeds that in any of our other standard or  program stars.
+The $S/N$ ratio for HR 6141 exceeds that in any of our standard or program stars.
 Although the atmospheric conditions at Las Campanas Observatory are certain to change throughout the night and between observing runs, we are primarily using this spectra to identify lines that are affected by telluric absorption.
@@
 The radial velocity for each star was determined in a two-step method.
-An initial estimate of the radial velocity was ascertained by cross-correlation with a synthetic spectrum of a giant star with $T_{eff} = 4500$\,K, $\log{g} = 1.5$, and [M/H] $= -1.0$ across the wavelength range $8450 - 8700$ \AA{}.
+An initial estimate of the radial velocity was ascertained by cross-correlation with a synthetic spectrum of a giant star with $T_{\rm eff} = 4500$\,K, $\log{g} = 1.5$, and [M/H] $= -1.0$ across the wavelength range $8450 - 8700$ \AA{}.
 The observed spectrum was shifted to the pseudo-rest frame using this initial velocity estimate.
@@
 With our spectra at near-rest, we measured the equivalent widths of $\sim$200 lines by automatically fitting Gaussian functions to the absorption profiles (see Section \ref{sec:line-measurements}).
-Fitted Gaussian profiles provide us with a measured equivalent width, the full-width half-maximum and the central wavelength of the profile.
+Fitted Gaussian profiles provide us with a measured equivalent width, the full-width half-maximum (FWHM) and the central wavelength of the profile.
 Thus, the residual radial velocity can be found from the ratio of the central and rest wavelengths.
@@
 The radial velocities published in Table \ref{tab:observations} are the final values from this two-step method.
-Heliocentric velocities agree quite well with the \citet{williams;et-al_2011} published values: the mean offset is $\langle\Delta{V_{hel}}\rangle = 2.5 \pm 2.7$\,km\,s$^{-1}$, demonstrating the accuracy of the velocities published in the RAVE catalog.
+Heliocentric velocities agree quite well with those compiled by \citet{williams;et-al_2011} from the RAVE survey: the mean offset is $\langle\Delta{V_{\rm hel}}\rangle = 2.5 \pm 2.7$\,km\,s$^{-1}$, demonstrating the accuracy of the velocities published in the RAVE catalog.
 
@@
 	\includegraphics[width=\columnwidth]{./figures/line-velocity.pdf}
-	\caption{Residual velocities for each absorption line with a well-fitted Gaussian profile after correcting for  doppler shift with our initial cross-correlation measurement.
+	\caption{Residual velocities for each absorption line with a well-fitted Gaussian profile after correcting for doppler shift using the initial cross-correlation measurement.
 The mean residual velocity $-0.75$\,km\,s$^{-1}$ is within the 1-$\sigma$ cross-correlation uncertainty of $\pm0.9$\,km\,s$^{-1}$.}
@@
 The equivalent widths for all absorption lines were measured automatically using software written for this study.
-Given the rest wavelength and an initial guess of the full-width half-maxium (FWHM), a Gaussian function is iteratively fitted to the absorption profile.
+Given the rest wavelength and an initial guess of the FWHM, a Gaussian profile is iteratively fitted to the absorption line.
 At the same time, the local continuum is found within 20\,\AA{} either side of the rest wavelength using a second-order polynomial.
@@
 We attempt to fit a Gaussian profile to each group of deviating pixels, using the current best estimate for the local continuum.
-If a Gaussian profile is successfully fitted to the deviating group and its surrounding pixels, we assume the outlier points belong to an absorption profile and all points belonging to that profile are excluded from the continuum determination.
-
-When fitting Gaussian profiles, the $\chi^2$ difference between the observed spectra and the fitted profile is minimized.
-In order to account for crowded absorption regions, where the $\chi^2$ value might be influenced by a nearby profile, our $\chi^2$ function is weighted based on the distance to the rest wavelength by the function
+If a Gaussian profile is successfully fitted to the deviating group and its surrounding pixels, we assume the outlier points belong to an absorption line and all pixels belonging to that profile are excluded from the continuum determination.
+
+When fitting Gaussian profiles, the $\chi^2$ difference between the observed spectra and the fitted function is minimized.
+In order to account for crowded absorption regions, where the $\chi^2$ value might be influenced by a nearby or blended profile, our $\chi^2$ function is weighted based on the distance to the rest wavelength by the function
 
@@
 
-\noindent where the rest wavelength ($\lambda_{r}$) and standard deviation\footnote{Recall $\sigma = 2.355FWHM$} ($\sigma$) are free parameters in the iterative fitting process.
+\noindent where the rest wavelength ($\lambda_{r}$) and standard deviation\footnote{Recall $\rm{FWHM} = 2\sigma\sqrt{2\log_e{2}}$} ($\sigma$) are free parameters in the iterative fitting process.
 As a consequence of Eq.
-\ref{eq:chi-weight}, pixels near the rest wavelength are weighted higher than those on the wings, forcing the fitting scheme to disregard blended or crowded regions.
-Although this approach relies on a reasonably accurate initial radial velocity correction ($<$4\,km s$^{-1}$; which is easily achieved), it greatly improves the accuracy and robustness of the equivalent width measurements.
+\ref{eq:chi-weight}, pixels near the rest wavelength are weighted higher than those on the wings, forcing the fitting scheme to disregard blended or crowded surroundings.
+Although this approach relies on a reasonably accurate initial radial velocity correction of $<$4\,km s$^{-1}$ \--- which is easily achieved \--- it greatly improves the accuracy and robustness of the equivalent width measurements.
 
 The results of our iterative Gaussian fitting approach are \textit{completely insensitive} to the initial FWHM guess.
-Increasing the initial FWHM estimate from 0.1\,\AA{} to 1 or 2\,\AA{} -- which are unphysically large values for high-resolution spectra -- does not alter either the FWHM or the equivalent width for any of our measurements.
+Increasing the initial FWHM estimate from 0.1\,\AA{} to 1 or 2\,\AA{} \--- which are unphysically large values for high-resolution spectra \--- does not alter either the FWHM or the equivalent width for any of our measurements.
 Only a small increase in computational cost is observed.
@@
 
-We list the atomic data and measured equivalent widths for atomic lines used during this analysis in Table \ref{tab:equivalent-widths}.
+We list the atomic data and measured equivalent widths for transitions used during this analysis in Table \ref{tab:equivalent-widths}.
 Saturated lines were excluded by removing measurements with reduced equivalent widths, $\log_{10}{(EW/\lambda)} > -4.5$\, dex.
@@
 Excellent agreement is found between the two studies, which is illustrated in Figure \ref{fig:ew-compare}.
-The mean difference is a negligible $0.64 \pm 2.78$\,m\AA{}, and no systematic trend is present.
-We note that the scatter may  be directly attributed to the observed $S/N$, as other studies using the same equivalent width measurement software described here find better agreement with hand measurements for spectra with higher $S/N$ ($0.20 \pm 0.16$\,m{\AA} with $S/N \sim X$, $0.25 \pm 0.28$\,m{\AA} with $S/N \sim{} Y$; \citet{frebel;et-al_2013}).
+The mean difference is a negligible $-0.64 \pm 2.78$\,m\AA{}, and no systematic trend is present.
+We note that the scatter may be directly attributed to the observed $S/N$ ratio, as other studies using the same equivalent width measurement software described here find better agreement with hand measurements for spectra with higher $S/N$ ratios ($0.20 \pm 0.16$\,m{\AA} with $S/N \sim X$, $0.25 \pm 0.28$\,m{\AA} with $S/N \sim{} Y$; \citet{frebel;et-al_2013}).
 
@@
 We interpolated the atmospheric pressures, densities, temperatures, and opacities between stellar atmosphere models using the Quickhull algorithm \citep{barber;et-al_1996}.
-Quickhull is reliant on Delaunay tessellation, which suffers from extremely skewed cells when the grid points vary in size by orders of magnitude -- as $T_{eff}$ values do compared to $\log{g}$ or [X/H].
-If unaccounted for, performing interpolation using these asymmetric cells can manifest as significant errors in atmospheric properties across all photospheric depths.
+Quickhull is reliant on Delaunay tessellation, which suffers from extremely skewed cells when the grid points vary in size by orders of magnitude -- as $T_{\rm eff}$ values do compared to $\log{g}$ or [X/H].
+If unaccounted for, interpolating using such asymmetric cells can result in significant errors in atmospheric properties across all photospheric depths.
 We scaled each stellar parameter between zero and unity prior to interpolation in order to minimise these effects.
-During this step, $\log{g}$, [M/H] and [$\alpha$/Fe] points were scaled such that we simultaneously interpolate linearly in $T_{eff}$ and logarithmically in all other parameters.
+During this step, $\log{g}$, [M/H] and [$\alpha$/Fe] points were scaled such that we simultaneously interpolate linearly in $T_{\rm eff}$ and logarithmically in all other parameters.
 
@@
 	\colhead{Designation} &
-	\colhead{$T_{eff}$} &
+	\colhead{$T_{\rm eff}$} &
 	\colhead{$\log{g}$} &
@@
 	\colhead{[Fe/H]} & 
-	\colhead{$T_{eff}$} &
+	\colhead{$T_{\rm eff}$} &
 	\colhead{$\log{g}$} &
@@
 \label{sec:effective-teffs}
-The effective temperature for each star was found by demanding a zero-trend in excitation potential and abundance for each measured Fe\,\textsc{i} line.
+The effective temperature for each star was found by demanding a zero-trend in excitation potential and line abundance for each measured Fe\,\textsc{i} transition.
 In the same way, the microturbulence was found by demanding a zero trend in reduced equivalent width against abundance.
@@
 
-The effective temperatures published for all of our stars in Table \ref{sec:stellar-parameters} have been derived spectroscopically (see \S\ref{sec:effective-teffs}).
-As a consistency check for our spectroscopic temperatures, we have estimated effective temperatures using infrared photometry from the 2MASS catalog.
+The effective temperatures published for all of our stars in Table \ref{sec:stellar-parameters} have been derived spectroscopically.
+As a consistency check for our spectroscopic temperatures, we have estimated effective temperatures using infrared photometry from the 2MASS catalog and empirical $T_{\rm eff}$-colour relationships.
 The $J-K$ color has been employed for these calculations because it has the least dependence on metallicity.
 
-The Aquarius stream is relatively close and at high-latitude, so significant extinction by dust is not expected.
-The dust maps of \citet{schlegel;et-al_1998} estimate that the extinction for our stars varies between E(B-V) = 0.03 to 0.07 mags.
+The Aquarius stream is relatively close and at high-latitude, so significant extinction caused by dust is not expected.
+The reddening maps of \citet{schlegel;et-al_1998} estimate that the extinction for our stars varies between E(B-V) = 0.03 to 0.07\,mags.
 However, these maps are not perfect.
@@
 This was the case in only one of our stars, J223811.
-We measured the equivalent width of the Na D1 line in J223811 to be 302.4\,m{\AA}, which corresponds to an $\mbox{E(B-V)} = 0.12^{+0.01}_{-0.02}$ according to the \citet{munari;zwitter_1997} relationship.
-This is a significantly higher value than what the \citet{schlegel;et-al_1998} dust map value of $\mbox{E(B-V)} = 0.07$ for J223811.
+The equivalent width of the Na D1 line in J223811 is found to be 302.4\,m{\AA}, corresponding to an $\mbox{E(B-V)} = 0.12^{+0.01}_{-0.02}$ according to the \citet{munari;zwitter_1997} relationship.
+This is a significantly higher value than the \citet{schlegel;et-al_1998} reddening map suggests: $\mbox{E(B-V)} = 0.07$.
 For completeness, both extinction values have been used to calculate photometric temperatures.
 
-Although all of our targets are giant stars, two different $T_{eff}$-colour relationships have been employed: the \citet{alonso;et-al_1999} calibration for giants, and the \citet{casagrande;et-al_2010} calibration for dwarfs and sub-giants.
+Although all of our candidates are giant stars, two different $T_{\rm eff}$-colour relationships have been employed: the \citet{alonso;et-al_1999} calibration for giants, and the \citet{casagrande;et-al_2010} calibration for dwarfs and sub-giants.
 All photometrically-derived temperatures are listed in \ref{tab:photometric-temperatures}.
@@
 
-The effective temperatures found from spectroscopy agree fairly well with the photometric temperature estimates.
+The effective temperatures found from spectroscopy agree fairly well with the photometric estimates.
 For three of our stars, the temperatures we find are in between the two color-temperature relationships.
@@
 A higher than expected level of extinction along the line-of-sight would produce cooler photometric temperatures than the true effective temperature.
-An extinction of $E(B-V) = 0.10$ would be required for the \citet{alonso;et-al_1999} relation to yield a temperature of ${\sim}$4500\,K, within the uncertainties of our effective temperature derived from spectroscopy.
+An extinction of $E(B-V) = 0.10$ would be required for the \citet{alonso;et-al_1999} relation to yield a temperature of ${\sim}$4500\,K \--- within the uncertainties of our effective temperature derived from spectroscopy.
 Such a discrepancy in extinction is large, but not uncommon (e.g., see \citet{nataf;et-al}).
@@
 
-J223811-104126 has two extinction values available: the \citet{schlegel;et-al_1998} value of $E(B-V) = 0.07$ and the 0.12 value  determined from the interstellar Na D1 line.
-Given the inherent difficulties in producing dust maps, and the known problems associated with them, we believe the $E(B-V) = 0.12$ determination to be more accurate.
+J223811-104126, the second temperature deviant, has two extinction values available: the \citet{schlegel;et-al_1998} value of $E(B-V) = 0.07$ and the 0.12 value determined from the interstellar Na D1 line.
+Given the inherent difficulties in producing dust maps, we believe the $E(B-V) = 0.12$ determination to be more accurate.
 However, using the \citet{schlegel;et-al_1998} extinction value with the \citet{alonso;et-al_1999} color-temperature relationship yields excellent agreement (5104\,K) with our spectroscopic temperature of 5140\,K.
-Employing our more accurate reddening determination yields 5215\,K, within the uncertainties of the relationship.
+Employing our more accurate reddening determination yields 5215\,K, still within the uncertainties of the relationship.
 The \citet{casagrande;et-al_2010} scale is ${\sim}$250\,K hotter in both cases.
@@
 The degeneracy between parameters required a refinement of the stellar parameters until the line abundances were consistent with the model atmosphere.
-After these parameters had converged, the model metallicity was exactly matched to that of our mean Fe \textsc{i} abundance.
-Line abundances that were unusually deviant (>3-$\sigma$) from the mean were removed.
+After these parameters had converged, the model metallicity was exactly matched to that of our mean Fe\,\textsc{i} abundance.
+Line abundances that were unusually deviant ($>$3-$\sigma$) from the mean were removed.
 The largest number of outlier measurements removed for any observation was nine for C222531-144370, leaving 60 Fe\,\textsc{i} and 10 Fe\,\textsc{ii} lines for analysis.
@@
 \subsection{Abundances}
-We have scaled our abundances to solar values using the solar chemical composition described in \citet{asplund;et-al_2009}.
+We have scaled our abundances to solar values using the Sun's chemical composition described in \citet{asplund;et-al_2009}.
 
@@
 Careful consideration was taken when correcting for telluric absorption.
-The 6300$\lambda$ line in one of our candidates, C2306265-085103, was sufficiently affected by telluric absorption such that we considered the line to be immeasurable.
-Thus, only the 6363$\lambda$ line was used to derive an oxygen abundance for C2306265-085103.
+The 6300$\lambda$ line in one of our candidates, C2306265-085103, was sufficiently affected by telluric absorption such that the line was considered immeasurable.
+Thus, only the 6363$\lambda$ transition was used to derive an oxygen abundance for C2306265-085103.
 In our hottest star, J223811-104126, the forbidden oxygen lines were not detected above a 3-$\sigma$ significance.
@@
 %Magnesium has been measured from unblended lines that fall within the linear regime between reduced equivalent width and abundance.
-Depending on the radial velocity of the star, some magnesium lines were be affected by telluric absorption, particularly the 6318$\lambda$ and 6965$\lambda$ lines.
+Depending on the radial velocity of the star, some magnesium lines were be affected by telluric absorption, particularly the 6318$\lambda$ and 6965$\lambda$ transitions.
 Atmospheric absorption was most notable for C2225316-14437, where three of the four Mg transitions in our line list suffered some degree of telluric absorption, requiring an attentive correction.
@@
 Four line measurements were used for each star, with a measurement uncertainty of 0.01\,dex.
-As shown in Figure \ref{fig:alpha-elements}, all Aquarius stars show super-solar Ca abundances, ranging between 0.23 to 0.43 dex, consistent with both [Mg/Fe] and [Si/Fe] measurements.
+As shown in Figure \ref{fig:alpha-elements}, all Aquarius candidates show super-solar Ca abundances, ranging between 0.23 to 0.43 dex, consistent with both [Mg/Fe] and [Si/Fe] measurements.
 
@@
 % titanium measurements?
+Titanium abundances for the stream stars are generally in agreement, showing typical $\alpha$-enhancement signatures.
+Our titanium measurements are derived from clean, unblended lines.
+The number of transitions available in our spectra varies from four to seven.
+In our hottest and most metal-poor stars, no suitable Ti\,\textsc{i} transitions were available.
+In other stream candidates, the mean difference between species is $\langle$Ti\,\textsc{i}$ - $Ti\,\textsc{ii}$\rangle = 0.24$\,dex.
+Although this discrepancy is not negligible, there are limited lines available for comparison, and our $\langle$Fe\,\textsc{i}$ - $Fe\,\textsc{ii}$\rangle$ abundances are in good agreement.
 
@@
 Additionally, the 3944 and 3961 lines suffer from appreciable departures from LTE, resulting in under-estimated abundances by up to $\sim$0.60\,dex \citep{baumuller;gehren_1997}.
-Instead, we have measured Al abundances from the other transitions available in our spectra: the Al \textsc{i} lines at 6696, 6698, 7835 and 7836\,{\AA}.
+Instead, we have measured Al abundances from other available transitions: the Al \textsc{i} lines at 6696, 6698, 7835 and 7836\,{\AA}.
 Although these lines are weaker than the bluer Al \textsc{i} lines, their surrounding regions are uncrowded from strong absorption lines.
@@
 As expected, the Fe-peak elemental abundances exhibit similar trends (Figure \ref{fig:fe-peak-elements}).
-The noteworthy exception is chromium, where the median abundance is $\mbox{[Cr/Fe]} = -0.08 \pm 0.12$ and does not vary with overall metallicity.
-The number of clean, suitable Cr \textsc{i} lines available varied between stars from three to twelve.
-Very little line-to-line scatter is present in both Cr \textsc{i} and \textsc{ii}: the random scatter is below 0.04\,dex for most stars, with the isolated example of J223504 where $\sigma(\mbox{[Cr \textsc{ii}/Fe]}) = 0.29$\,dex and only three lines were available.
+The noteworthy exception is chromium, where the median abundance is $\mbox{[Cr/Fe]} = -0.08 \pm 0.12$ and does not appear to vary with overall metallicity.
+The number of clean, suitable Cr \textsc{i} lines available between candidates fluxuated from three to twelve.
+Very little line-to-line scatter is present in both Cr \textsc{i} and \textsc{ii}: the random scatter is below 0.04\,dex for most stars, with the isolated example of J223504 where $\sigma(\mbox{[Cr \textsc{ii}/Fe]}) = 0.29$\,dex, where only three lines were available.
 The Cr \textsc{i} and \textsc{ii} abundances for J223504 are in good agreement (0.05\,dex), and since none of the measured profiles were particularly unusual, we chose not to exclude outlier measurements.
 For all other stars, the Cr \textsc{i} $-$ Cr \textsc{ii} abundance differences varied between 0.02\,dex up to 0.31\,dex.
-The largest discrepancy occurred in our hottest star, where fewer chromium transitions were detectable.
+The largest discrepancy occurred in our hottest star, where fewer chromium transitions were detected.
 
@@
 
+\subsubsection{Nickel}
+Most Aquarius stream stars have seven clean Ni\,\textsc{i} transitions available. These lines are in excellent agreement, with typical scatter of 0.03\,dex.
+% nickel abundances in standard stars
+
 \subsubsection{Barium}
@@
 Measuring barium requires some careful consideration.
-The strong resonance lines at 4554 {\AA} and 4934 {\AA} have appreciable hyperfine splitting, which if unaccounted for can result in over-estimated abundances.
-There are a few singly ionized lines available in our spectra which do not suffer from strong hyperfine splitting, namely the 5853, 6141 and 6496 {\AA} transitions.
+The strong resonance lines at 4554 {\AA} and 4934 {\AA} have appreciable hyperfine splitting, which can result in over-estimated abundances if unaccounted for.
+There are a few singly ionized lines available in our spectra that do not suffer from strong hyperfine splitting, namely the 5853, 6141 and 6496 {\AA} transitions.
 Depending on the radial velocity of the star, sometimes our 6496 {\AA} line was affected by small amounts of telluric absorption.
@@
 Only one of our standard stars, HD 44007, has published [Ba/Fe] abundances from high-resolution spectra.
-We find HD 44007 to have $\mbox{[Ba/Fe]} = -0.05 \pm 0.04$, which is in between existing published measurements from \citet{fulbright_2000} and \citet{burris;et-al_2000} of $-0.27$ and 0.05 dex, respectively.
-
-With one exception, the Aquarius stream stars have barium abundances that are quite similar to the stellar halo, ranging between $\mbox{[Ba/Fe]} = -0.02$ to 0.15 dex.
+We find HD 44007 to have $\mbox{[Ba/Fe]} = -0.05 \pm 0.04$, which is at the mid-point of existing published measurements from \citet{fulbright_2000} and \citet{burris;et-al_2000} of $-0.27$ and 0.05 dex, respectively.
+
+With one exception, the Aquarius stream candidates have barium abundances that are quite similar to the stellar halo, ranging between $\mbox{[Ba/Fe]} = -0.02$ to 0.15 dex.
 The exception is C2225316, which has an anomalously high barium abundance of $\mbox{[Ba/Fe]} = 0.70$ dex.
@@
 Our three Ba \textsc{ii} lines in C2225316 are in excellent agreement: 0.67, 0.68, and 0.72 dex.
-The 6496\,{\AA} transition in C2225316 has a negligible telluric contribution and was included for this star.
-At least in Al, Si, Cr and Ba abundances (see sections \ref{sec:aluminium-abundance}, \ref{sec:alpha-elements}, \ref{sec:iron-peak-elements}), C225316 appears to be chemically distinct from the other Aquarius stream stars in our sample.
+The 6496\,{\AA} transition in C2225316 has a negligible telluric contribution and was included for this candidate.
+At least in Al, Si, Cr and Ba content (see sections \ref{sec:aluminium-abundance}, \ref{sec:alpha-elements}, \ref{sec:iron-peak-elements}), C225316 appears to be chemically distinct from the other Aquarius stream stars in our sample.
 
@@
 In general, temperatures between the two studies agree within the uncertainties.
-The only abberation is J223811-104126, where we find an effective temperature of 5140\,K, ${\sim}$500\,K cooler than the 5646\,K found by \citet{wylie-de-boer;et-al_2012}.
+The only aberration is J223811-104126, where we find an effective temperature of 5140\,K, ${\sim}$500\,K cooler than the 5646\,K found by \citet{wylie-de-boer;et-al_2012}.
 Similarly, \citet{williams;et-al_2011} report a hotter effective temperature of 5502\,K from low-resolution spectra.
@@
 As a test, we set the temperature for J223811-104126 to be 5600\,K -- within the temperature regime reported by \citet{williams;et-al_2011} and \citet{wylie-de-boer;et-al_2012}.
-The slopes in abundance with excitation potential and reduced equivalent width were large (how many dex), and in doing so we could not find a physical solution for this temperature.
+The slopes in abundance with excitation potential and reduced equivalent width were large (\#check smh: how many dex), and in doing so we could not find a physical solution for this temperature.
 Thus, although photometric temperatures do not help in solving this discrepancy, and the reddening measured from the interstellar Na D1 line may have made it worse, our high-resolution spectra indicates that J223811-104126 has an effective temperature of 5110\,K and is indeed a giant star.
@@
 
-\citet{wylie-de-boer;et-al_2012} calculate microturbulence from empirical relationships derived by \citet{Reddy;et-al_2003} for dwarfs and \citet{fulbright_2000} for giants.
+\citet{wylie-de-boer;et-al_2012} calculate microturbulence from empirical relationships derived by \citet{reddy;et-al_2003} for dwarfs and \citet{fulbright_2000} for giants.
 These relationships are based upon the effective temperature and surface gravity.
-Our published microturbulent velocities agree excellently with the values presented in \citet{wylie-de-boer;et-al_2012}, again with the exception of J223811-104126, where the difference in $v_{t}$ can be  directly attributed to the offsets in other stellar parameters.
-
-Of all the stellar parameters ($T_{eff}$, $\log{g}$, $v_{t}$ and $\mbox{[Fe/H]}$), the metallicities between our two studies vary the most.
+Our published microturbulent velocities agree excellently with the values presented in \citet{wylie-de-boer;et-al_2012}, again with the exception of J223811-104126, where the difference in $v_{t}$ can be directly attributed to the offsets in other observables.
+
+Of all the stellar parameters ($T_{\rm eff}$, $\log{g}$, $v_{t}$ and $\mbox{[Fe/H]}$), the metallicities between our two studies vary the most.
 Here we discuss the potential causes for these discrepancies.
-In the \citet{wylie-de-boer;et-al_2012} study, after the stellar parameters ($T_{eff}$, $\log{g}$, $v_{t}$, and an initial [Fe/H] estimate) had been determined through a $\chi^2$ analysis, the authors synthesized individual Fe \textsc{i} and \textsc{ii} lines using the \textsc{moog} code.
+In the \citet{wylie-de-boer;et-al_2012} study, after the stellar parameters ($T_{\rm eff}$, $\log{g}$, $v_{t}$, and an initial [Fe/H] estimate) had been determined through a $\chi^2$ analysis, the authors synthesized individual Fe \textsc{i} and \textsc{ii} lines using the \textsc{moog} code.
 \citet{castelli;kurucz_2003} stellar atmosphere models were employed \--- the same ones used in this study, albeit the interpolation schemes will have subtle differences.
@@
 
-The study of \citet{wylie-de-boer;et-al_2012} is of slightly lower resolution ($\mathcal{R} = 25,000$ compared to $\mathcal{R} = 28,000$ presented here), but with a much lower $S/N$ ratio: $\sim{}25$ pixel$^{-1}$ compared to >100 pixel$^{-1}$ achieved here.
-Given the lower spectral resolution and modest $S/N$ in the \citet{wylie-de-boer;et-al_2012} study, there are fewer unblended absorption lines available.
+The study of \citet{wylie-de-boer;et-al_2012} is of slightly lower resolution ($\mathcal{R} = 25,000$ compared to $\mathcal{R} = 28,000$ presented here), but with a much lower $S/N$ ratio: $\sim{}25$ pixel$^{-1}$ compared to $>$100\,pixel$^{-1}$ achieved here.
+Given the slightly lower spectral resolution and modest $S/N$ in the \citet{wylie-de-boer;et-al_2012} study, there are fewer unblended absorption lines available.
 In fact, there are very few transitions present in their published line list: only 14 Fe\,\textsc{i} lines and 3 Fe\,\textsc{ii} lines were available.
-For contrast, our metallicity determinations are usually based from ${\sim}$50 Fe\,\textsc{i} and ${\sim}$13 Fe\,\textsc{ii} lines.
-Given the metallicity of these stars and the spectral coverage (4120 to 6920 {\AA}), it is somewhat surprising that there were not more unblended transitions available to \citet{wylie-de-boer;et-al_2012}.
-
-The line list employed in the \citet{wylie-de-boer;et-al_2012} study contained fewer lines, and employed different oscillator strengths than what we have used.
+For contrast, our metallicity determinations are usually based from ${\sim}$50 Fe\,\textsc{i} and ${\sim}$13 Fe\,\textsc{ii} clean, unblended lines.
+Given the metallicity of these candidates and the spectral coverage (4120 to 6920 {\AA}), it is somewhat surprising that there were not more transitions available to \citet{wylie-de-boer;et-al_2012}.
+
+The line list employed in the \citet{wylie-de-boer;et-al_2012} study contained fewer lines, and utilized different oscillator strengths than what we have used.
 The oscillator strengths in the \citet{wylie-de-boer;et-al_2012} study are astrophysical; they were derived from a reverse analysis from the \citet{hinkle;et-al_2003} solar atlas.
@@
 Indeed, we arrive at very similar metallicities to \citet{wylie-de-boer;et-al_2012}.
-Without using their published stellar parameters a priori, in a `blind' analysis employing just the \citet{wylie-de-boer;et-al_2012} line list, we arrive at similar stellar parameters.
-However, we note that one Fe\,\textsc{i} transition at 6420.060\,\AA{} in the \citet{wylie-de-boer;et-al_2012} line list was not detected in any of our stars at the 3-$\sigma$ level, even though the $S/N$ at this point exceeds 115 pixel$^{-1}$ in every observation.
-Thus, for this comparative analysis a maximum of 13 Fe\,\textsc{i} and 3 Fe\,\textsc{ii} lines were available to us.
+Without using their published stellar parameters a priori, in a `blind' analysis employing just the \citet{wylie-de-boer;et-al_2012} line list, we also arrive at similar stellar parameters.
+However, given the limited number of lines available, subtle changes to the stellar parameters inflicted large changes to individual mean iron abundances.
+Additionally, we note that one Fe\,\textsc{i} transition at 6420.060\,\AA{} in the \citet{wylie-de-boer;et-al_2012} line list was not detected in any of our candidates at the 3-$\sigma$ level, even though the $S/N$ at this point exceeds 115 pixel$^{-1}$ in every observation.
+Thus, for this comparative analysis a maximum of 13 Fe\,\textsc{i} and 3 Fe\,\textsc{ii} lines were available.
 
 Given the line list employed in the \citet{wylie-de-boer;et-al_2012} study, the overall data quality and the lack of suitable iron lines available for analysis, it appears the Aquarius stream stars conspired to present a tight metallicity distribution function of $\sigma(\mbox{Fe/H}) = 0.10$\,dex.
-When viewed in light of enhanced Ni, Na abundances, this chemistry is suggestive of a globular cluster origin.
+When viewed in light of enhanced [Ni/Fe], [Na/Fe] abundance ratios, this chemistry is suggestive of a globular cluster origin.
 Our analysis of high-resolution spectra with high $S/N$ reveals a much broader metallicity distribution for the stream.
-With just five stars -- if we assume all our stars are members -- we find the stream metallicity varies from $\mbox{[Fe/H]} = -0.65$ to --1.60\,dex.
+With just five stars \--- if we assume all our candidates are members \--- we find the stream metallicity varies from $\mbox{[Fe/H]} = -0.65$ to --1.60\,dex.
 Although this is a small sample, we find the calculated median abundance and standard deviation to be $\mbox{[Fe/H]} = -1.26 \pm 0.32$\,dex.
@@
 This is largely because they are primarily considered to be a single stellar populations, originating from a lone \--- largely homogenous \--- proto-stellar cloud.
-More recent observations have repeatedly shown that this is not always the case: many globular clusters clearly host multiple stellar populations.
+More recent observations have demonstrated shown that this is not always the case: many globular clusters clearly host multiple stellar populations.
 The separation between these populations is identifiable through chemical abundances, and often from photometry alone.
-In many cases, the chemistry between the two stellar populations are quite similar, still revealing minimal overall chemical scatter within the cluster.
+In many cases, the chemistry between the two stellar populations are quite similar, still revealing minimal overall scatter within the cluster.
 There are some unusual exceptions to this rule, most notable of which is the globular cluster $\omega$-Centurai (NGC 5139), which is seen to host many sub-populations with very different metallicity distributions.
@@
 
+\begin{figure*}[t!]
+	\includegraphics[width=\textwidth]{./figures/aquarius-vhel-feh.pdf}
+	\caption{Helocentric velocities and metallicities for Aquarius candidates in this sample.
+The measurements found by \citet{williams;et-al_2011} (green squares) and \citet{wylie-de-boer;et-al_2012} (blue triangles) are shown, and stars are linked by dashed lines.
+\citet{wylie-de-boer;et-al_2012} used the \citet{williams;et-al_2011} velocities, which is why their measurements are coincident on the abscissa.}
+	\label{fig:aquarius-vhel-feh}
+\end{figure*}
+
 Assuming all our candidates are stream members, we find a metallicity dispersion of $\sigma(\mbox{[Fe/H]}) = 0.32$\,dex.
 If the stream is the result of a disrupted system, this metallicity dispersion provides little indication on the progenitor.
-If the dispersion was smaller, confirming the observations of \citet{wylie-de-boer;et-al_2012}, the globular cluster scenario is  more likely.
-However, given the multiple stellar populations present in many globular clusters, which can exhibit total cluster dispersions up to X dex (NGC X), Y dex (NGC Y), our dispersion of 0.32\,dex is inconvenient.
-Since dwarf spheroidal galaxies do not undergo chemical self-enrichment in the same way globular clusters do, they can exhibit significant metallicity dispersions \--- well over a dex, depending on the dwarf total luminosity.
+If the dispersion was smaller, confirming the observations of \citet{wylie-de-boer;et-al_2012}, a globular cluster scenario is more likely.
+However, given the multiple stellar populations present in many globular clusters, which can exhibit total cluster dispersions up to X dex (NGC X), Y dex (NGC Y), our dispersion of 0.32\,dex is somewhat inconvenient.
+Since dSph galaxies do not undergo chemical self-enrichment in the same way globular clusters do, they can exhibit significant metallicity dispersions \--- well over a dex, depending on the dwarf total luminosity.
 On its own, the metallicity of our stream stars does not provide any indication on the cause of the Aquarius stream, or its enrichment environment.
@@
 
+\begin{figure*}[t!]
+	\includegraphics[width=\textwidth]{./figures/aquarius-o-na-cluster.pdf}
+	\caption{Oxygen and sodium abundances for 14 classical globular clusters from \citet{carretta;et-al_2009a}, demonstrating the clear inverse Na-O correlation, which is ubiquitous in all well-studied globular clusters.
+The [O/Fe] and [Na/Fe] abundances for the five Aquarius stream candidates are also shown (last panel).}
+	\label{fig:o-na-clusters}
+\end{figure*}
+
 The explosive material eventually condenses to form the next generation of stars, which will have a net increase in their neutron excess with respect to when their predecessors formed.
@@
 However, the temperatures required to produce these patterns are not expected within the interiors of globular cluster stars.
-Several hypotheses to explain this missing mechanism have been proposed, including massive intermediate-mass AGB binary stars \citep{de_mink;et-al_2009} and fast-rotating massive stars \citep{decressin;et-al_2007}.
 While the exact site for which these conditions occur remains under investigation, we can describe the abundance variation as a simple oxygen depletion (or dilution) model with time.
@@
 It is clear that careful consideration must be given when inferring star-formation histories from observed stellar abundances.
-In addition to the normal care afforded for measuring elemental abundances from high-resolution spectroscopic data, attention must be given to telluric absorption, contamination from nickel blends, as well as NLTE and 3D effects when calculating oxygen abundances.
-Furthermore, when characterising the oxygen depletion rate -- the strength of the Na-O anti-correlation in a given cluster -- it is vital to sample stars belonging to all three components, where possible.
+In addition to the normal care afforded for measuring elemental abundances from high-resolution spectroscopic data, attention must be given to telluric absorption, contamination from nickel transitions, as well as NLTE and 3D effects when calculating oxygen abundances.
+Furthermore, when characterising the oxygen depletion rate \--- the strength of the Na-O anti-correlation in a given cluster \--- it is vital to sample stars belonging to all three components, where possible.
 If only a primordial sample of stars in a globular cluster is observed, their [Na/Fe] and [O/Fe] abundances will be indistinguishable from halo stars of a similar metallicity.
@@
 The \citet{wylie-de-boer;et-al_2012} measurements indicate two stars with solar levels of Na \--- identical to field star Na abundances for their metallicity \--- and two stars with super-solar sodium content: J223504 and J232619.
-We find find J223504 to be Na-enhanced with $\mbox{[Na/Fe]} = 0.18$, slightly lower than the \citet{wylie-de-boer;et-al_2012} value of $0.28 \pm 0.21$\,dex.
+We also find J223504 to be sodium-enhanced with $\mbox{[Na/Fe]} = 0.18$, slightly lower than the \citet{wylie-de-boer;et-al_2012} value of $0.28 \pm 0.21$\,dex.
 This discrepancy in [Na/Fe] is the largest difference between the two studies, and still within the uncertainties published by \citet{wylie-de-boer;et-al_2012}.
@@
 
-If the Aquarius stream is the result of a disrupted globular cluster, we would still be missing a large part of the picture.
-Most of the Aquarius stream stars studied to date (either in this sample or the \citet{wylie-de-boer;et-al_2012} study), would be classified as belonging to a `primordial' component having chemistry indistinguishable from halo stars.
-Identifying more Aquarius stream members belonging to the intermediate component with strong oxygen depletion, or perhaps members of an extreme component, would be strong evidence for a Na-O anti-correlation and a globular cluster origin.
+If the Aquarius stream is the result of a disrupted globular cluster, a large part of the picture would still be missing.
+Most of the Aquarius stream stars studied to date (either in this sample or the \citet{wylie-de-boer;et-al_2012} study), would be classified as belonging to a `primordial' component, with chemistry indistinguishable from the halo.
+Identifying more Aquarius stream members belonging to the intermediate component with strong oxygen depletion, or perhaps members of an extreme component, would be strong evidence for a Na-O anti-correlation and perhaps a globular cluster origin.
 Three stream stars identified to date (including two from this sample) could plausibly be classified as members of an intermediate population, with only a slight enhancement in sodium and no oxygen-depletion.
-Thus, if the strength of any Na-O relationship is to be used to vet potential disrupted hosts for the Aquarius stream, many more stream candidates will need to be identified, and observed with high-resolution.
-
-% Can these abundance differences be explained by a line-list?
-
-% In any case, suppose these stars did originate from a globular cluster.
-If the entire cluster was well-studied, the primordial component cut-off is described by Caretta as stars which are 4\sigma from the halo abundance at that metallicity.
-These stars would
+Thus, if the strength of any Na-O relationship is to be used to vet potential disrupted hosts for the Aquarius stream, many more stream candidates will need to be identified, and observed with high-resolution and high $S/N$.
 
@@
 
-The Mg-Al cycle can explain the observed anti-correlation observed in some globular clusters, and most theoretical models predict such a pattern [get citations from Amanda].
+The Mg-Al cycle can explain the observed anti-correlation observed in some globular clusters, and most theoretical models predict such a pattern (\#get citations from Amanda).
 However, the locations where these extreme temperatures can be found are under some debate.
 Standard models indicate that the interiors of globular cluster stars do not reach sufficient temperatures for the Mg-Al cycle to produce the observed variations.
-Thus, although the processes for creating these chemical patterns are understood, the exact site and conditions still require explanation.
+Thus, although the processes for creating these chemical patterns are understood, the exact site and requisite conditions still need explanation.
 
 No inverse correlation has been observed in the Aquarius stream stars to date.
-Given that we do not find a Na-O anti-correlation, it is not surprising that a Mg-Al pattern has not been observed.
+Given that we do not find a Na-O anti-correlation, it is not surprising that a Mg-Al pattern has also not been observed.
 The Na-O signature is detected in all classical well-studied systems, but the Mg-Al anti-correlation is not always present.
 \citet{wylie-de-boer;et-al_2012} published magnesium and aluminium abundances for five stars in their Aquarius stream sample.
-No anti-correlation between the elements is present, and their abundances are not dissimilar from galactic stars.
+No inverse correlation is present, and their abundances are not dissimilar from galactic stars.
 The abundances tabulated in Table \ref{tab:abundances} vary slightly with those presented in the \citet{wylie-de-boer;et-al_2012} sample.
@@
 
-While \citet{wylie-de-boer;et-al_2012} find almost no scatter ($\pm0.02$\,dex) in [Mg/Fe] for stars common to both studies, we find C2225316 and J223504 to be almost $+0.20$\,dex higher.
-The reason for this discrepancy is not obvious, given the stellar parameters between the two studies agree well with the exception of metallicity.
+While \citet{wylie-de-boer;et-al_2012} find almost no scatter ($\pm0.02$\,dex) in [Mg/Fe] for stars common to both studies, we find C2225316 and J223504 to be almost $+0.20$\,dex higher than the rest of the sample.
+The reason for this discrepancy is not obvious, given the stellar parameters between the two studies agree well, with the previously discussed exception of metallicity.
 In particular, the stellar parameters agree excellently for J223504, but we find $\mbox{[Fe/H]} = -0.68$ instead of the $-0.98$ as found by \citet{wylie-de-boer;et-al_2012}.
 Of the Mg \textsc{i} profiles measured, only two transitions are common to both line lists: 6318$\lambda$ and 6319$\lambda$.
-The oscillator strengths vary between studies; in these two lines the $\log{gf}$ differs by $-0.24$ and $-0.27$\,dex respectively (our oscillator strengths are lower).
+The oscillator strengths differ between studies; in these two lines the $\log{gf}$ differs by $-0.24$ and $-0.27$\,dex respectively (our oscillator strengths are lower).
 This discrepancy only complicates the matter further, since if all other things being equal, then our abundances ought to be lower than the \citet{wylie-de-boer;et-al_2012} study.
@@
 % Mg-Al
-\begin{figure}[h]
+\begin{figure}[h!]
 	\includegraphics[width=\columnwidth]{./figures/aquarius-mg-al.pdf}
-	\caption{A plot showing [Mg/Al] for all Aquarius stream stars.}
+	\caption{Magnesium and aluminium abundances for Aquarius candidates, and Milky Way halo/disc stars from \citet{reddy;et-al_2003} ($+$) and \citet{fulbright_2000} ($\circ$).
+The chemically peculiar star, C2225316-14437, is marked.}
 	\label{fig:mg-al}
@@
 The [Mg/Fe] and [Al/Fe] abundances found for the five Aquarius stars in this sample are illustrated in Figure \ref{fig:mg-al}.
-Interestingly, our stars exhibit a strong positive relationship, with a best-fitting slope of $\mbox{[Al/Fe]} = X.XX x \mbox{[Mg/Fe]} + Y.YY$ ($R = Y.YY$).
-If the exclude C2225316, our chemically peculiar star with enhanced [Al/Fe] relative to the rest of the sample, the slope decreases to $\mbox{[Al/Fe]} = X.XX x \mbox{[Mg/Fe]} + Y.YY$ and the correlation coefficient $R$ increases to Z.ZZ.
-Even when a Mg-Al anti-correlation is not detected in globular clusters, there is generally some scatter in [Al/Fe] at constant [Mg/Fe] \--- early indications of the nucleosynthetic pattern.
-No classical globular cluster exhibits a positive correlation.
-
-\# Discuss prediction of positive correlation.
-Some intermediate-mass ($4M_\odot$) AGB models predict a positive correlation between aluminium and magnesium \citet{karakas;et-al}.
+Interestingly, our stars exhibit a strong positive relationship, with a best-fitting slope of $\mbox{[Al/Fe]} = 2.15 x \mbox{[Mg/Fe]} - 0.57$ ($R = Y.YY$).
+If the exclude C2225316, our chemically peculiar star with enhanced [Al/Fe] relative to the rest of the sample, the slope decreases to $\mbox{[Al/Fe]} = 1.07 x \mbox{[Mg/Fe]} - 0.19$ and the correlation coefficient $R$ increases to Z.ZZ.
+Even when a Mg-Al anti-correlation is not detected in globular clusters, there is generally some scatter in [Al/Fe] at constant [Mg/Fe] \citet[e.g.
+see][]{carretta;et-al_2009a}.
+Few classical globular clusters exhibit a positive correlation.
+
+% Mg-Al
+\begin{figure*}[t!]
+	\includegraphics[width=\textwidth]{./figures/aquarius-mg-al-cluster.pdf}
+	\caption{[Mg/Fe] and [Al/Fe] abundances for stars in 16 globular clusters from \citet{carretta;et-al_2009} and for the five Aquarius stream candidates.
+The inverse Mg-Al correlation is illustrated, most obviously in NGC 2808 and NGC 1904.
+The strong positive correlation observed in Aquarius is in stark contrast with other classical globular clusters.}
+	\label{fig:mg-al}
+\end{figure*}
+
+A positive relationship between magnesium and aluminium can result from SN \textsc{ii} contributions to the local interstellar medium.
+High-resolution observations of disc stars illustrate this correlation \citep{bensby;venn}, demonstrating efficient SN \textsc{ii} mixing.
+Some intermediate-mass ($4M_\odot$) AGB models can also predict a positive correlation between aluminium and magnesium \citet{karakas;et-al}.
 Under extreme temperatures ($T_6 \sim 300$\,K), substantial $^{25}$Mg and $^{26}$Mg are produced by $\alpha$-capture onto $^{22}$Ne by the $^{22}$Ne($\alpha$,n)$^{25}$Mg and $^{22}$Ne($\alpha$,$\gamma$)$^{26}$Mg reactions respectively.
-Following deep dredge up, significant $^{25}$Mg and $^{26}$Mg is mixed into the photosphere, more than the quantity of $^{26}$Al produced through the Mg-Al cycle and making up for the depleted Mg that is expensed during the Mg-Al pathway.
-Thus, a positive relationship between magnesium and aluminium can occur if there has been significant contributions from intermediate mass AGB stars undergoing dredge up.
-Alternatively, a positive relationship between magnesium and aluminium can occur from SN \textsc{ii} contributions.
-Distinguishing between these processes requires careful measurements of magnesium isotope abundances $^{24}$Mg (supernovae), $^{25}$Mg and $^{26}$Mg (AGB stars), which is not possible given our $S/N$ or spectral resolution.
-
-\# What does the thick/thin disk look like in these elements?
+Following deep dredge up, significant $^{25}$Mg and $^{26}$Mg is mixed into the photosphere, more than the quantity of $^{26}$Al produced through the Mg-Al cycle.
+This dredge up process replenishes the Mg which is expensed during the Mg-Al pathway.
+Therefore, a positive relationship between magnesium and aluminium can occur if there has been significant contributions from intermediate mass AGB stars undergoing dredge up.
+
+An unrealistically high fraction of intermediate-mass AGB stars would be required to produce the same chemical signature of a single Sn \textsc{ii} event.
+Given the efficiency of chemical pollution following supernovae, the observed correlation in the thick disc is likely the result of Sn \textsc{ii} events.
+However, since the chemical enrichment environment of the Aquarius stream is unknown, we cannot exclude either possibility.
+Distinguishing between these processes observationally requires careful measurements of magnesium isotope abundances $^{24}$Mg (indicating supernovae mixing), $^{25}$Mg and $^{26}$Mg (suggesting significant AGB contribution), which is not possible given our $S/N$ or spectral resolution.
 
@@
 Consequently, they exhibit chemistry that reflects their nucleosynthetic antiquity.
-Dwarf spheroidal stars do not demonstrate enhanced sodium or nickel, as there has been a relatively negligible linage of massive stars undergoing supernova.
-In contrast, globular cluster stars do have elevated Na, Ni contributions.
+Dwarf spheroidal stars do not demonstrate enhanced sodium or nickel content with respect to iron, as there has been a relatively negligible linage of massive stars undergoing supernova.
+In contrast, globular cluster stars do have elevated [Na/Fe], [Ni/Fe] signatures.
 This sharp contrast between dwarf spheroidal and globular cluster star chemistry is illustrated in Figure \ref{fig:na-ni}.
@@
 
-The most that can be inferred from the Na, Ni abundances of Aquarius stream stars is that their star formation history is less like a dwarf spheroidal environment, and more representative of an environment similar to either a globular cluster, or the disc of the Milky Way.
+The most that can be inferred from the Na, Ni abundances of Aquarius stream stars is that their enrichment environment is less like a dSph galaxy, and more representative of a globular cluster, or the disc of the Milky Way.
 
@@
 
-C2225316 exhibits peculiar chemical abundances when compared to the rest of the Aquarius stream candidates in our sample.
-It is over-abundant in light refractory elements, with $\mbox{[Al/Fe]} = 0.68 \pm 0.04$, $\mbox{[Mg/Fe]} = 0.50$, and $\mbox{[O/Fe] = 0.49}$\,dex.
-Silicon is enhanced to a level of $\mbox{[Si/Fe]} = 0.72 \pm 0.07$, which is +0.34\,dex more than any other star in our sample.
-In addition to light element enhancement, C2225316 exhibits a strong barium content of $\mbox{[Ba/Fe]} = 0.70$\,dex.
-This abundance is well in excess of the halo ($\mbox{[Ba/Fe]} \sim 0.0$), and our other Aquarius stream stars, which vary between $-$0.02 to 0.15\,dex.
+C2225316 exhibits peculiar chemical abundances compared to the rest of the Aquarius candidates.
+It is over-abundant in light refractory elements, and exhibits a strong barium abundance of $\mbox{[Ba/Fe]} = 0.70$\,dex.
+This abundance is well in excess of the halo ($\mbox{[Ba/Fe]} \sim 0.0$) \--- and our other Aquarius stream stars \--- which vary between $-$0.02 to 0.15\,dex.
 
 High $s$-process enhancements have been noted for a few disrupted globular clusters that exhibit a wide metallicity range.
-Most noteably: $\omega$Centurai \citep{Majewski;et-al_2012}, M22 \citep{marinolet-al_2011} and (\# any others?).
+Most noteably: $\omega$Centurai \citep{majewski;et-al_2012}, M22 \citep{marinolet-al_2011} and (\# any others?).
 Like the Aquarius co-moving group, both clusters are relatively close to the sun: $R_\odot = 5.2$\,kpc and 3.2\,kpc, respectively.
 M22 has a mean metallicity of $\mbox{[Fe/H]} \sim -1.7$, varying between $-2.0 < \mbox{[Fe/H]} < -1.6$\,dex.
-C2225316 has an $\mbox{[Fe/H]} = -1.26$\,dex, making it unlikely to be associated with M22.
+Since C2225316 has a metallicity of $\mbox{[Fe/H]} = -1.26$\,dex, it is unlikely to be associated with M22.
 However, the high barium content and overall metallicity of C2225316 ($\mbox{[Fe/H]} = -1.26$) suggests there may be an association with $\omega$-Centurai.
 
-Within $\omega$-Centurai, there are three distinguishable sub-populations with various proportions.
-
-\# Comparison of all abundances to omega cen abundances in a plot
-
-\# Plot of majewski
-
-\citet{majewski;et-al_2012} modelled
+$\omega$-Centurai has a retrograde orbit with low inclination.
+Many groups simulating this orbit have predicted retrograde tidal debris to occur near the Solar circle \citep{dinescu_2002,tsuchiya_2003,tsuchiya_2004,mizutani_2003,bekki_freeman_2003}.
+Subsequent searches for $\omega$-Cen debris in the solar neighbourhood have led to tantalizing signatures of debris.
+From over 4,000 stars selected from the $\omega$-Cen color-magnitude diagram by \citet{da_costa;coleman_2008}, only six candidate members were recovered.
+More recently, \citet{majewski;et-al_2012} presented data from the Grid Giant Star Survey (GGSS), an all-sky search looking for metal-poor giant stars.
+From their data, they identified 12 stream candidates.
+Although this scarcity is consistent with tidal stripping occurring long ago, it is perhaps worrying that searches for stripped stars near $\omega$-Cen itself have been even less fruitful.
+
+In addition to presenting new stream candidates, \citet{majewski;et-al_2012} performed 4,050 different simulations in order to predict likely locations for tidal debris.
+The results of their simulation are replicated in Figure \ref{fig:majewski-simulation}, where the location of C2225316 is also shown.
+Interestingly, the velocity and position of C2225316 line up almost precisely where \citet{majewski;et-al_2012} predict a high probability of stream members.
+
+Although this is interesting from a qualitative perspective, the most striking evidence for an association with $\omega$-Centurai is in chemistry.
+Figure \ref{fig:omega-cen-barium} demonstrates the [Ba/Fe] abundance for $\omega$-Cen stars compared to that of the galactic halo.
+A steep Ba enhancement is present, which is unique to the globular clusters $\omega$-Cen and M22.
+We note that although high $s$-process enrichment is present in other systems \citep[IC 2391, the Argus association;][]{de_silva;et-al_2013}, these systems are have metallicities near solar values and are unlikely to be associated with C2225316.
+
+% additional chemistry?
+% [Sr/Ba] ~0.4
+
+The chemical peculiarity of C2225316 suggests that it is distinct from the Aquarius co-moving group.
+The high $s$-process enrichment is similar to that observed in $\omega$-Centurai stars, and the overall metallicity ($\mbox{[Fe/H]} = -1.26$) agrees excellently with the mean metallicity of a known sub-population within $\omega$-Centurai.
+Moreover, the position and velocity for C2225316 precisely coincide with the most likely predictions for tidal debris from $\omega$-Centurai.
+The chemical and phase-space information indicates that C2225316 is likely associated with the disrupted globular cluster $\omega$-Centurai.
 
@@
 Since the Aquarius stream is kinematically coherent, the default assumption is that the system has been accreted.
-The stream candidates presented here are slightly enhanced in sodium and nickel, suggesting that if a progenitor ever existed then its environment was more like a globular cluster than a dwarf satellite.
-If the progenitor is a disrupted globular cluster, and all our candidates are members, then it is unique in that it has a wider metallicity distribution than most globular clusters.
+The stream candidates presented here are slightly enhanced in sodium and nickel, suggesting that if a progenitor ever existed then its environment was more like a globular cluster than a dSph galaxy.
+Based on a lack of $\alpha$-enhancement and increased [Na/Fe], [Ni/Fe] abundances, we exclude the possibility that the Aquarius stream has resulted from a disrupted dwarf satellite.
+If the progenitor is a disrupted globular cluster, and all our candidates are members, then it has a wider metallicity distribution than most globular clusters.
 
 However, our chemical analysis does not reveal any inverse Na-O correlation \--- which would be strong evidence for a globular cluster environment.
-Furthermore, we observe a positive Mg-Al relationship, the same seen by \citet{wylie-de-boer;et-al_2012} and contrary to what would be expected from a globular cluster environment.
-High resolution, high $S/N$ spectra for the entire stream may be required before such a signature may become apparent.
-In this section we discuss the possible causes for the Aquarius co-moving group.
-
-Based on a lack of $\alpha$-enhancement and increased Na, Ni content, we exclude the possibility that the Aquarius stream has resulted from a disrupted dwarf satellite.
+Furthermore, we observe a positive Mg-Al relationship, the same seen by \citet{wylie-de-boer;et-al_2012}.
+High resolution, high $S/N$ spectra for the entire stream may be required before such chemical signatures may become apparent.
+In this section we discuss other possible causes for the Aquarius co-moving group.
 
@@
 On the basis of metallicity, distance, proper motions\footnote{We find the proper motions in Table 1 of \citet{williams;et-al_2011} to be mis-associated to incorrect stars.
-However, this typographical error did not propagate through to the transverse velocity calculations (Williams, M.E.K, private communication).}, transverse velocities and orbital energies, the authors were able to exclude all known Milky Way satellites, with the notable exception of $\omega$-centurai.
+However, this  error was typographical; it did not affect the transverse velocity calculations (Williams, M.E.K, private communication).}, transverse velocities and orbital energies, the authors were able to exclude all known Milky Way satellites, with the notable exception of $\omega$-Centurai.
 Although the Aquarius stream metallicity distribution we find is not dissimilar from a known sub-population in $\omega$-centurai, the individual chemical abundances are quite distinct.
-
 $\omega$-Centurai members exhibit a strong $s$-process enhancement with overall metallicity.
@@
 Due to our limited sample size, it is impossible to know whether C2225316 is an outlier, or our four other candidates are halo interlopers.
-Either position is debatable, and each lead to interesting conclusions.
+Either position is debatable, and both lead to interesting interpretations.
 If most of our observed candidates are halo members, and C2225316 represents the Aquarius stream chemistry, then an association between Aquarius and $\omega$-Centurai is possible.
-Alternatively, the stream may indicate first evidence of a minor merger within the Milky Way disc.
+
+%Alternatively, the stream may indicate first evidence of a minor merger within the Milky Way disc.
 However, with certainty we can state that most observed Aquarius stream candidates do not exhibit enhanced $s$-process elements, and are therefore unlikely to be associated with $\omega$-Centurai \--- or any other globular cluster.

### 2013-01-29 2012-aqs/figures/plot-mg-al.py

@@ -85,14 +85,14 @@ for classification, fe_h, mg_h, al_h in reddy_data:
 			mg_h = np.nan
 
 		else:
-			mg_fe = float(mg_h) - float(fe_h)
+			mg_fe = float(mg_h) #- float(fe_h)
 
 
 		if len(al_h) == 0:
 			al_h = np.nan
 
 		else:
-			al_fe = float(al_h) - float(fe_h)
+			al_fe = float(al_h) #- float(fe_h)
 
 
 	if classification == 'Thick disc':
@@ -118,6 +118,25 @@ for classification, fe_h, mg_h, al_h in reddy_data:
 
 
 Reddy_ThickDisk_Mg_Fe, Reddy_ThickDisk_Al_Fe, Reddy_ThinDisk_Mg_Fe, Reddy_ThinDisk_Al_Fe, Reddy_Halo_Mg_Fe, Reddy_Halo_Al_Fe, Reddy_ThickThinDisk_Mg_Fe, Reddy_ThickThinDisk_Al_Fe, Reddy_ThickDisk_Halo_Mg_Fe, Reddy_ThickDisk_Halo_Al_Fe = [np.array(item) for item in (Reddy_ThickDisk_Mg_Fe, Reddy_ThickDisk_Al_Fe, Reddy_ThinDisk_Mg_Fe, Reddy_ThinDisk_Al_Fe, Reddy_Halo_Mg_Fe, Reddy_Halo_Al_Fe, Reddy_ThickThinDisk_Mg_Fe, Reddy_ThickThinDisk_Al_Fe, Reddy_ThickDisk_Halo_Mg_Fe, Reddy_ThickDisk_Halo_Al_Fe)]
+
+
+# Caretta et al. 2009
+
+Carretta_Mg_Fe, Carretta_Al_Fe, Carretta_Cluster, Carretta_Fe_H = np.loadtxt('Carretta_2009a.data', delimiter='|', usecols=(-3, -2, 2, -7), dtype=str, unpack=True)
+
+delete_rows = []
+for i in xrange(len(Carretta_Cluster)):
+
+	Mg_Fe = Carretta_Mg_Fe[i].strip()
+	Al_Fe = Carretta_Al_Fe[i].strip()
+
+	if len(Mg_Fe) * len(Al_Fe) == 0: delete_rows.append(i)
+
+Carretta_Cluster = map(float, np.delete(Carretta_Cluster, delete_rows))
+Carretta_Fe_H = map(float, np.delete(Carretta_Fe_H, delete_rows))
[…]

### 2013-01-29 2012-aqs/figures/plot-na-ni.py

@@ -4,11 +4,11 @@ import numpy as np
 # Get Na and O from files:
 data_files = ['c2225316-14437_abundances.data', 'c2306265-085103_abundances.data', 'j221821-183424_abundances.data', 'j223504-152834_abundances.data', 'j223811-104126_abundances.data']
 
-Na_Fe = []
-e_Na_Fe = []
+Observed_Na_Fe = []
+e_Observed_Na_Fe = []
 
-Ni_Fe = []
-e_Ni_Fe = []
+Observed_Ni_Fe = []
+e_Observed_Ni_Fe = []
 
 observed_data = {}
 for filename in data_files:
@@ -17,50 +17,32 @@ for filename in data_files:
 	observed_data[filename] = data
 
 	idx = list(data[:,0]).index('Na')
-	_Na_Fe, _e_Na_Fe = data[idx, 1:]
+	_Observed_Na_Fe, _e_Observed_Na_Fe = data[idx, 1:]
 
 	idx = list(data[:, 0]).index('Ni')
-	_Ni_Fe, _e_Ni_Fe = data[idx, 1:]
+	_Observed_Ni_Fe, _e_Observed_Ni_Fe = data[idx, 1:]
 
-	Na_Fe.append(_Na_Fe)
-	Ni_Fe.append(_Ni_Fe)
-	e_Na_Fe.append(_e_Na_Fe)
-	e_Ni_Fe.append(_e_Ni_Fe)
-
-
-# Clean up Na_Fe, Ni_Fe, e_Na_Fe, e_Ni_Fe
-Na_Fe = map(float, [value.replace('$', '').replace('\nodata', 'nan') for value in Na_Fe])
-Ni_Fe = map(float, [value.replace('$', '').replace('\nodata', 'nan') for value in Ni_Fe])
-
-e_Na_Fe = map(float, [value.replace('$', '').replace('\nodata', 'nan') for value in e_Na_Fe])
-e_Ni_Fe = map(float, [value.replace('$', '').replace('\nodata', 'nan') for value in e_Ni_Fe])
-
-Na_Fe, Ni_Fe, e_Na_Fe, e_Ni_Fe = map(np.array, [Na_Fe, Ni_Fe, e_Na_Fe, e_Ni_Fe])
+	Observed_Na_Fe.append(_Observed_Na_Fe)
[…]

### 2013-01-29 2012-aqs/figures/plot-na-o.py

@@ -4,8 +4,8 @@ import matplotlib.pyplot as plt
 # ; ;mag;mag;mag;mag;km/s;km/s;K;[Sun];[Sun];[Sun];[Sun]; ;[Sun];[Sun];"h:m:s";"d:m:s"
 
 
-caretta_Fe_I, caretta_e_Fe_I, caretta_O_Fe, caretta_e_O_Fe, caretta_l_Na_Fe, caretta_Na_Fe, caretta_e_Na_Fe = np.loadtxt('caretta-et-al-2009-O-Na.txt', skiprows=67, delimiter=';', \
-														usecols=(9, 10, 11, 12, 13, 14, 15, ), unpack=True, dtype=str)
+caretta_cluster, caretta_Fe_I, caretta_e_Fe_I, caretta_O_Fe, caretta_e_O_Fe, caretta_l_Na_Fe, caretta_Na_Fe, caretta_e_Na_Fe = np.loadtxt('caretta-et-al-2009-O-Na.txt', skiprows=67, delimiter=';', \
+														usecols=(0, 9, 10, 11, 12, 13, 14, 15, ), unpack=True, dtype=str)
 
 # Replace invalid items with np.nans
 
@@ -25,8 +25,7 @@ def clean(array):
 	return np.array(new_array)
 
 
-caretta_Fe_I, caretta_e_Fe_I, caretta_O_Fe, caretta_e_O_Fe, caretta_Na_Fe, caretta_e_Na_Fe = map(clean, [caretta_Fe_I, caretta_e_Fe_I, caretta_O_Fe, caretta_e_O_Fe, caretta_Na_Fe, caretta_e_Na_Fe])
-
+caretta_cluster, caretta_Fe_I, caretta_e_Fe_I, caretta_O_Fe, caretta_e_O_Fe, caretta_Na_Fe, caretta_e_Na_Fe = map(clean, [caretta_cluster, caretta_Fe_I, caretta_e_Fe_I, caretta_O_Fe, caretta_e_O_Fe, caretta_Na_Fe, caretta_e_Na_Fe])
 
 
 # Get Na and O from files:
@@ -110,3 +109,108 @@ ax2.set_ylim(-0.6, 1.1)
 plt.draw()
 plt.savefig('aquarius-o-na.pdf')
 plt.savefig('aquarius-o-na.eps')
+
+
+
+# Subplots
+
+
+# Mg-Al in sub-plots
+
+
+# Delete 6397 because it has less stars than even our stream sample!
[…]

### 2013-01-29 2012-aqs/figures/plot-vhel-feh.py

@@ -1,0 +1,74 @@
+
+
+# C2225316, C2306265, J221821, J223504, J223811
+Vhels = [-156.4, -221.1, -159.5, -169.7, -235.7]
+Verrs = [0.1, 0.1, 0.1, 0.1, 0.1]
+
+Fe_H = [-1.26, -1.17, -1.61, -0.68, -1.45]
+Fe_H_errs = [0.01, 0.01, 0.01, 0.02, 0.01]
+Fe_H_errs = [0.10, 0.1, 0.1, 0.1, 0.1]
+
+
+# Wylie de boer data
+# C2225316, C2306265, J221821, J223504, J223811
+
+wdb_Vhels = [-155.7, -221.8, -154.1, -166.9, -230.1]
+wdb_Verrs = [0.7, 1.7, 1.1, 1.3, 1.9]
+
+wdb_Fe_H = [-1.20, np.NaN, -1.15, -0.98, -1.20]
+wdb_Fe_H_errs = [0.14, np.NaN, 0.21, 0.17, 0.20]
+
+
+# Williams data
+# C2225316, C2306265, J221821, J223504, J223811
+williams_Vhels = [-155.7, -221.8, -154.1, -166.9, -230.1]
+williams_Verrs = [0.7, 1.7, 1.1, 1.3, 1.9]
+
+williams_Fe_H = [-1.29, np.NaN, -1.54, -0.33, -0.78]
+williams_Fe_H_errs = [0.2, 0.2, 0.2, 0.2, 0.2]
+
+
+xlims = (-245, -145)
+ylims = (-1.8, -0.2)
+
+print "NOT READING IN METALLICITY OR VELOCITY FROM TABLES: HARD CODED IN FOR FEH-VHEL"
+fig = plt.figure()
+
+ax = fig.add_subplot(111)
+
+s = 50
+ax.scatter(williams_Vhels, williams_Fe_H, facecolor='g', edgecolor='g', marker='s', s=s, label='Williams et al. (2011)')
+ax.scatter(wdb_Vhels, wdb_Fe_H, facecolor='b', edgecolor='b', marker='^', s=s, label='Wylie-de Boer et al. (2012)')
+ax.scatter(Vhels, Fe_H, c='k', marker='o', s=s, label='This work')
+
[…]

### 2013-01-29 2012-oss-mrs/figures/ew-mg.py

@@ -52,10 +52,13 @@ match_points = np.array([
 ])
 # convert to mA
 
+from scipy.interpolate import splrep, splev
+
 tck = splrep(match_points[:, 0], match_points[:, 1], k=3)
 
 x = np.arange(ax.get_xlim()[0], ax.get_xlim()[1], 0.01)
 y = splev(x, tck)
+
 
 giants = 0
 for gi, ri, ewi in zip(g, r, ew):

### 2013-01-30 2012-aqs/draft-aqs.tex
yolo

@@
 \usepackage{amssymb,graphics} % for resolution symbol
+\usepackage{longtable}
 
@@
 % TODO:
+
 % [DONE] Na/O subplots
-% Na/O comparison with halo
+% [DONE] Na/O comparison with halo
 % [DONE] Mg/Al subplots
@@
 % - Uncertainties analysis
+% [DONE] Equivalent widths significant figures.
 % - Strontium?
 % - Carbon?
-% - Distance calculations
+% - Distance calculations revision
 % - Transverse motions table
@@
 
-% Casey, Keller, Alves-Brito, Frebel, Da Costa, Schlaufman, Freeman, Heather, QinQin
+% Casey, Keller, Alves-Brito, Frebel, Da Costa, Schlaufman, Karakas, Heather, QinQin, Freeman
 
@@
 Wide-field surveys have proved excellent sources for finding stellar streams.
-Dozens have been identified through photometric selections and metched-filtering techniques, with some to a galactocentric distance of 100\,kpc \citep{belokurov;et-al_2007,koposov_SG1, drake;et-al_2013}.
+Dozens have been identified through photometric selections and matched-filtering techniques, with some to a galactocentric distance of 100\,kpc \citep{belokurov;et-al_2007,drake;et-al_2013}.
 Indeed, it is clear that a large fraction of the stellar halo has been built up by accretion.
@@
 Such substructures would only be detectable by their kinematics, or perhaps precise chemical abundances through a `chemical tagging' approach (e.g.
-see \citet{freeman;bland-hawthorn_2003}).
+see \citet{freeman;bland-hawthorn_2002}).
 
 % Talk about RAVE
-It is therefore necessary to survey solar neighbourhood stars with spectroscopy to permit any nearby substructures to reveal themselves.
+It is therefore necessary to survey solar neighbourhood stars with spectroscopy to reveal any nearby substructures.
 The RAVE (Radial Velocity Experiment) team began such a survey in 2003 and have observed spectra from over 500,000 stars across 17,000\,deg$^{2}$.
@@
 The data analysis is chronicled in Section \ref{sec:analysis} and a detailed discussion of these results resides in Section \ref{sec:discussion}.
-In Section \ref{sec:conclusion} we present our conclusions and critical interpretations.
+In Section \ref{sec:conclusions} we present our conclusions and critical interpretations.
 
@@
 
+\\ \multicolumn{11}{c}{Standard Stars} \\ \hline \\
+HD 41667		& 06:05:03.7 & $-$32:59:36.8	& 2011-03-13	& 1.005	& \dots & \dots & \dots & 314.4	& \dots & 0.8 \\
+HD 142948		& 16:00:01.6 & $-$53:51:04.1	& 2011-03-14	& 1.107	& \dots & \dots & \dots & 6.8		& \dots & 0.4 \\
+
+\\ \multicolumn{11}{c}{Program Stars} \\ \hline \\
 C2225316-14437	& 22:25:31.7 & $-$14:54:39.6	& 2011-07-30	& 1.033 & \dots & \dots & 135	 & --168.6	& --156.4 & 0.1 \\
 C2306265-085103	& 23:06:26.6 & $-$08:51:04.8	& 2011-07-30	& 1.096 & \dots & \dots & 100	 & --240.4	& --221.1 & 0.1 \\
-HD41667			& 06:05:03.7 & $-$32:59:36.8	& 2011-03-13	& 1.005	& \dots & \dots & \dots & 314.4	& \dots & 0.8 \\
-HD142948		& 16:00:01.6 & $-$53:51:04.1	& 2011-03-14	& 1.107	& \dots & \dots & \dots & 6.8		& \dots & 0.4 \\
 J221821-183424	& 22:18:21.2 & $-$18:34:28.3	& 2011-07-30	& 1.026	& \dots & \dots & 115 	 & --170.2	& --159.5 & 0.1 \\
@@
 All program stars were observed in July 2011 in good seeing at low airmass (Table \ref{tab:observations}), and X additional standard stars were observed in March 2011.
-All observations were taken using a 1.0'' slit, providing a spectral resolution of $\mathcal{R} = 28,000$ in the blue and $\mathcal{R} = 22,000$ in the red arm.
-The total exposure times for our program stars varied per star from X-Y seconds to ensure a $S/N$ ratio in excess of 100\,pixel$^{-1}$ at 600\,nm.
+All observations were taken using a 1.0'' slit, providing a spectral resolution of $\mathcal{R} = 28,000$ in the blue arm and $\mathcal{R} = 22,000$ in the red arm.
+The total exposure times for our program stars varied to ensure a $S/N$ ratio in excess of 100\,pixel$^{-1}$ at 600\,nm.
 
@@
 Although the atmospheric conditions at Las Campanas Observatory are certain to change throughout the night and between observing runs, we are primarily using this spectra to identify lines that are affected by telluric absorption.
-Critical transitions necessary for abundance analyses that are affected by the earth's atmosphere are corrected for telluric absorption (see \S\ref{sec:telluric-absorption}).
+Critical transitions necessary for abundance analyses that are affected by the Earth's atmosphere are corrected for telluric absorption.
 
@@
 \label{sec:radial-velocities}
+
 The radial velocity for each star was determined in a two-step method.
@@
 Velocities found from cross-correlation are typically within 1\,km\,s$^{-1}$ of our final published value.
+
+\begin{figure}[h!]
+	\includegraphics[width=\columnwidth]{./figures/line-velocity.pdf}
+	\caption{Residual velocities for each absorption line with a well-fitted Gaussian profile after correcting for doppler shift using the initial cross-correlation measurement.
+The mean residual velocity $-0.75$\,km\,s$^{-1}$ is within the 1-$\sigma$ cross-correlation uncertainty of $\pm0.9$\,km\,s$^{-1}$.}
+	\label{fig:line-velocities}
+\end{figure}
 
@@
 
-\begin{figure}[h]
-	\includegraphics[width=\columnwidth]{./figures/line-velocity.pdf}
-	\caption{Residual velocities for each absorption line with a well-fitted Gaussian profile after correcting for doppler shift using the initial cross-correlation measurement.
-The mean residual velocity $-0.75$\,km\,s$^{-1}$ is within the 1-$\sigma$ cross-correlation uncertainty of $\pm0.9$\,km\,s$^{-1}$.}
-	\label{fig:line-velocities}
-\end{figure}
-
 \subsection{Line Measurements}
@@
 The mean difference is a negligible $-0.64 \pm 2.78$\,m\AA{}, and no systematic trend is present.
-We note that the scatter may be directly attributed to the observed $S/N$ ratio, as other studies using the same equivalent width measurement software described here find better agreement with hand measurements for spectra with higher $S/N$ ratios ($0.20 \pm 0.16$\,m{\AA} with $S/N \sim X$, $0.25 \pm 0.28$\,m{\AA} with $S/N \sim{} Y$; \citet{frebel;et-al_2013}).
+We note that the scatter may be directly attributed to the observed $S/N$ ratio, as other studies \citep{frebel;et-al_2013} using the same equivalent width measurement software described here find better agreement with hand measurements for spectra with higher $S/N$ ratios: $0.20 \pm 0.16$\,m{\AA} with \citet{aoki;et-al_2007} and $0.25 \pm 0.28$\,m{\AA} with \citet{cayrel;et-al_2004} for a spectrum of HD 122563 with $S/N > 300$\,pixel$^{-1}$.
 
@@
 \begin{deluxetable*}{cccccccccc}
-\tablecolumns{1}
 \tabletypesize{\scriptsize}
@@
 \startdata 
- 6300.300 &       8.0 &      0.00 &    --9.717 &     45.37 &     66.93 &     38.48 &     32.85 &     17.87 \\
- 6363.780 &       8.0 &      0.02 &   --10.185 &     19.47 &     28.31 &     12.96 &     18.83 &   \nodata \\
- 5688.190 &      11.0 &      2.11 &    --0.420 &   \nodata &   \nodata &     48.97 &    131.49 &     38.41 \\
- 6154.230 &      11.0 &      2.10 &    --1.530 &     24.06 &     38.89 &   \nodata &     48.49 &   \nodata \\
- 6160.750 &      11.0 &      2.10 &    --1.230 &     37.72 &     58.49 &   \nodata &     65.72 &   \nodata \\
- 6318.720 &      12.0 &      5.11 &    --1.970 &   \nodata &     47.94 &     14.69 &     62.79 &      8.88 \\
- 6319.240 &      12.0 &      5.11 &    --2.220 &     30.84 &   \nodata &      5.51 &   \nodata &   \nodata \\
- 6965.410 &      12.0 &      5.75 &    --1.510 &   \nodata &   \nodata &   \nodata &     59.22 &   \nodata \\
- 7387.690 &      12.0 &      5.75 &    --0.870 &     51.71 &     56.30 &     24.68 &     76.01 &     23.99 \\
- 6696.020 &      13.0 &      3.14 &    --1.340 &     72.83 &     63.60 &     12.99 &   \nodata &   \nodata \\
- 6698.670 &      13.0 &      3.14 &    --1.640 &     39.67 &     33.44 &   \nodata &     39.50 &   \nodata \\
- 7835.310 &      13.0 &      4.02 &    --0.470 &     47.77 &     38.44 &   \nodata &     55.91 &      5.39 \\
- 7836.130 &      13.0 &      4.02 &    --0.310 &     62.78 &     44.72 &   \nodata &     69.13 &     13.23 \\
- 5690.430 &      14.0 &      4.93 &    --1.751 &     56.17 &     43.76 &     25.75 &     53.45 &     16.77 \\
- 5793.070 &      14.0 &      4.93 &    --1.843 &     46.13 &     39.81 &     19.33 &     48.39 &   \nodata \\
- 6125.020 &      14.0 &      5.61 &    --1.506 &     40.93 &     23.45 &     10.86 &     34.74 &   \nodata \\
- 6145.010 &      14.0 &      5.62 &    --1.362 &     33.93 &     21.66 &     16.11 &     32.75 &     10.02 \\
- 6155.130 &      14.0 &      5.62 &    --0.786 &     67.36 &     53.11 &     35.29 &     72.00 &     24.98 \\
- 6166.440 &      20.0 &      2.52 &    --1.142 &     94.19 &    105.46 &     42.32 &     99.45 &     35.88 \\
- 6169.040 &      20.0 &      2.52 &    --0.797 &    112.06 &    120.91 &     66.31 &    120.48 &     55.48 \\
- 6169.560 &      20.0 &      2.53 &    --0.478 &    127.89 &    141.16 &     83.69 &    136.37 &     71.35 \\
- 6455.600 &      20.0 &      2.52 &    --1.290 &     80.79 &     91.41 &     31.35 &     89.20 &     25.98 \\
- 5526.820 &      21.1 &      1.77 &      0.130 &     98.84 &    113.34 &    100.84 &     98.40 &     51.08 \\
- 5657.880 &      21.1 &      1.51 &    --0.500 &     96.46 &    107.49 &     92.74 &     95.42 &     41.21 \\
- 5667.150 &      21.1 &      1.50 &    --1.240 &     59.41 &     75.04 &     45.00 &     58.54 &     14.51 \\
- 5669.040 &      21.1 &      1.50 &    --1.120 &   \nodata &     92.51 &     57.27 &     75.19 &     18.20 \\
- 6245.610 &      21.1 &      1.51 &    --0.980 &     67.12 &     83.60 &     53.34 &     67.38 &     14.75 \\
- 6604.600 &      21.1 &      1.36 &    --1.480 &     65.58 &     82.06 &     49.37 &     65.92 &     17.81 \\
- 6064.630 &      22.0 &      1.05 &    --1.888 &     59.69 &     80.86 &   \nodata &     58.58 &   \nodata \\
- 6091.170 &      22.0 &      2.27 &    --0.367 &     45.15 &     59.09 &   \nodata &     56.28 &   \nodata \\
- 6312.240 &      22.0 &      1.46 &    --1.496 &     46.16 &     63.41 &   \nodata &     48.78 &   \nodata \\
- 6336.100 &      22.0 &      1.44 &    --1.687 &     35.88 &     54.10 &   \nodata &     42.33 &   \nodata \\
- 5154.080 &      22.1 &      1.57 &    --1.920 &    112.25 &   \nodata &    114.05 &   \nodata &     53.89 \\
- 5185.910 &      22.1 &      1.89 &    --1.350 &   \nodata &    101.45 &    105.46 &   \nodata &     55.30 \\
- 5336.790 &      22.1 &      1.58 &    --1.690 &    116.30 &    124.58 &    119.55 &    103.98 &     61.40 \\
- 5381.030 &      22.1 &      1.59 &    --2.080 &   \nodata &    131.44 &    101.94 &    109.93 &     47.96 \\
- 5727.060 &      23.0 &      1.08 &    --0.010 &    122.36 &   \nodata &     26.00 &    116.79 &      9.13 \\
- 6090.220 &      23.0 &      1.08 &    --0.060 &     93.58 &    115.58 &     23.62 &     92.84 &   \nodata \\
- 6216.360 &      23.0 &      0.28 &    --1.290 &    108.80 &   \nodata &     16.92 &    109.33 &   \nodata \\
- 6251.820 &      23.0 &      0.29 &    --1.340 &     94.66 &    124.37 &   \nodata &     92.43 &   \nodata \\
- 6274.640 &      23.0 &      0.27 &    --1.670 &     65.49 &     93.82 &   \nodata &     61.51 &   \nodata \\
- 6504.160 &      23.0 &      1.18 &    --1.230 &     22.95 &     33.69 &   \nodata &     31.93 &   \nodata \\
- 4545.950 &      24.0 &      0.94 &    --1.370 &   \nodata &   \nodata &     80.22 &   \nodata &   \nodata \\
- 4580.056 &      24.0 &      0.94 &    --1.650 &   \nodata &   \nodata &   \nodata &   \nodata &     44.22 \\
- 4616.137 &      24.0 &      0.98 &    --1.190 &    128.75 &    139.25 &     89.37 &    126.24 &     59.88 \\
- 4626.188 &      24.0 &      0.97 &    --1.320 &    122.24 &    136.41 &     82.24 &   \nodata &     56.90 \\
- 4646.150 &      24.0 &      1.03 &    --0.740 &   \nodata &   \nodata &    110.65 &    146.08 &     75.35 \\
- 4651.280 &      24.0 &      0.98 &    --1.460 &    127.78 &    140.58 &     75.40 &    116.31 &     48.44 \\
- 4652.158 &      24.0 &      1.00 &    --1.030 &    138.48 &   \nodata &     96.92 &    138.00 &     66.74 \\
- 5206.040 &      24.0 &      0.94 &      0.020 &   \nodata &   \nodata &   \nodata &   \nodata &    132.81 \\
- 5247.564 &      24.0 &      0.96 &    --1.640 &    141.39 &   \nodata &     76.09 &   \nodata &     46.66 \\
- 5296.690 &      24.0 &      0.98 &    --1.360 &    149.87 &   \nodata &     85.01 &    140.97 &     59.00 \\
- 5300.740 &      24.0 &      0.98 &    --2.000 &    120.48 &   \nodata &   \nodata &    112.22 &   \nodata \\
- 5345.800 &      24.0 &      1.00 &    --0.950 &   \nodata &   \nodata &    115.38 &   \nodata &     81.14 \\
- 5348.310 &      24.0 &      1.00 &    --1.210 &    150.80 &   \nodata &     94.76 &    142.37 &     63.02 \\
- 5409.770 &      24.0 &      1.03 &    --0.670 &   \nodata &   \nodata &    132.36 &   \nodata &     92.13 \\
- 4558.594 &      24.1 &      4.07 &    --0.656 &   \nodata &   \nodata &   \nodata &    101.77 &     46.52 \\
- 4588.142 &      24.1 &      4.07 &    --0.826 &     46.04 &     52.99 &     60.53 &     55.00 &     35.95 \\
- 4591.992 &      24.1 &      4.07 &    --1.419 &   \nodata &   \nodata &     29.08 &     28.53 &     19.56 \\
- 6013.530 &      25.0 &      3.07 &    --0.251 &     89.19 &    114.55 &     22.18 &    109.41 &     14.81 \\
- 6016.670 &      25.0 &      3.08 &    --0.100 &     93.98 &    116.01 &     28.15 &    113.02 &     17.06 \\
- 6021.800 &      25.0 &      3.08 &      0.034 &     97.50 &    116.02 &     39.08 &    110.74 &     19.90 \\
- 5044.210 &      26.0 &      2.85 &    --2.034 &   \nodata &   \nodata &   \nodata &   \nodata &     33.70 \\
- 5054.640 &      26.0 &      3.64 &    --1.938 &     37.96 &   \nodata &   \nodata &   \nodata &   \nodata \\
- 5242.490 &      26.0 &      3.63 &    --0.980 &     94.34 &    101.83 &     72.92 &   \nodata &     49.25 \\
- 5321.110 &      26.0 &      4.43 &    --1.106 &     34.97 &     35.32 &     11.14 &   \nodata &   \nodata \\
- 5322.040 &      26.0 &      2.28 &    --2.840 &     93.10 &    103.03 &     59.48 &   \nodata &     30.88 \\
- 5326.140 &      26.0 &      3.57 &    --2.130 &     40.39 &     51.67 &     13.75 &     48.44 &   \nodata \\
- 5365.400 &      26.0 &      3.57 &    --1.040 &   \nodata &    100.31 &   \nodata &     93.75 &   \nodata \\
- 5367.480 &      26.0 &      4.41 &      0.430 &    108.42 &    118.03 &     92.35 &    119.08 &     73.73 \\
- 5379.570 &      26.0 &      3.69 &    --1.530 &     71.36 &     81.40 &     34.91 &     75.65 &     19.57 \\
- 5491.840 &      26.0 &      4.18 &    --2.250 &   \nodata &   \nodata &   \nodata &     17.29 &   \nodata \\
- 5618.630 &      26.0 &      4.21 &    --1.292 &     43.46 &     54.27 &     20.25 &     57.44 &     11.30 \\
- 5701.550 &      26.0 &      2.56 &    --2.216 &    118.51 &    134.78 &     91.77 &    119.47 &     49.50 \\
- 5705.470 &      26.0 &      4.30 &    --1.420 &     29.24 &     41.47 &     10.92 &     44.49 &      7.70 \\
- 5741.850 &      26.0 &      4.25 &    --1.689 &     36.19 &     37.02 &     13.01 &     48.22 &   \nodata \\
- 5775.080 &      26.0 &      4.22 &    --1.310 &     54.96 &     62.12 &     25.34 &     67.38 &     14.67 \\
- 5778.450 &      26.0 &      2.59 &    --3.480 &     42.75 &     55.83 &     13.43 &     50.14 &   \nodata \\
- 5811.920 &      26.0 &      4.14 &    --2.430 &   \nodata &   \nodata &   \nodata &     10.88 &   \nodata \\
- 5837.700 &      26.0 &      4.29 &    --2.340 &   \nodata &   \nodata &   \nodata &     12.94 &   \nodata \\
- 5853.160 &      26.0 &      1.49 &    --5.280 &     30.38 &     43.35 &      6.28 &     34.65 &   \nodata \\
- 5855.090 &      26.0 &      4.60 &    --1.547 &     13.31 &     20.31 &   \nodata &     22.77 &   \nodata \\
- 5856.100 &      26.0 &      4.29 &    --1.640 &     27.88 &     40.19 &   \nodata &     42.69 &   \nodata \\
- 5858.790 &      26.0 &      4.22 &    --2.260 &   \nodata &     11.37 &   \nodata &     16.85 &   \nodata \\
- 5909.970 &      26.0 &      3.21 &    --2.640 &     55.96 &     72.65 &     18.47 &     63.29 &   \nodata \\
- 5916.250 &      26.0 &      2.45 &    --2.994 &     92.92 &    105.08 &     51.17 &     95.37 &     17.67 \\
- 5927.800 &      26.0 &      4.65 &    --1.090 &     32.37 &     36.72 &     12.16 &     50.92 &   \nodata \\
- 5956.690 &      26.0 &      0.86 &    --4.608 &    121.68 &    143.78 &     70.27 &    107.81 &     25.53 \\
- 6012.210 &      26.0 &      2.22 &    --4.070 &     44.36 &     58.79 &     11.51 &     52.96 &   \nodata \\
- 6019.360 &      26.0 &      3.57 &    --3.360 &      7.00 &   \nodata &   \nodata &     11.34 &   \nodata \\
- 6027.050 &      26.0 &      4.07 &    --1.106 &     66.25 &     77.00 &     36.21 &     77.20 &     23.52 \\
- 6054.080 &      26.0 &      4.37 &    --2.310 &      5.63 &      8.08 &   \nodata &     12.92 &   \nodata \\
- 6105.130 &      26.0 &      4.55 &    --2.050 &   \nodata &     10.92 &   \nodata &     14.84 &   \nodata \\
- 6120.240 &      26.0 &      0.91 &    --5.970 &     35.22 &     52.71 &      8.54 &     32.41 &   \nodata \\
- 6151.620 &      26.0 &      2.17 &    --3.299 &     88.90 &    102.90 &     46.94 &     87.04 &     18.19 \\
- 6157.730 &      26.0 &      4.08 &    --1.320 &   \nodata &     81.19 &     33.20 &     78.14 &     18.79 \\
- 6159.380 &      26.0 &      4.61 &    --1.970 &   \nodata &      9.61 &   \nodata &     13.56 &   \nodata \\
- 6165.360 &      26.0 &      4.14 &    --1.490 &     40.57 &     51.56 &     14.17 &     54.02 &     10.84 \\
- 6173.340 &      26.0 &      2.22 &    --2.880 &    109.59 &    125.61 &     70.72 &    105.59 &     34.86 \\
- 6180.200 &      26.0 &      2.73 &    --2.637 &     86.21 &    100.58 &     44.33 &     91.55 &     20.83 \\
- 6200.310 &      26.0 &      2.61 &    --2.437 &    105.22 &    122.16 &     70.78 &    105.43 &     36.60 \\
- 6219.280 &      26.0 &      2.20 &    --2.433 &    134.35 &    153.29 &    103.28 &    127.37 &     56.70 \\
- 6229.230 &      26.0 &      2.84 &    --2.846 &     60.14 &     73.08 &     21.02 &     65.77 &     13.61 \\
- 6232.640 &      26.0 &      3.65 &    --1.283 &     92.59 &    104.33 &     58.26 &    103.00 &     35.63 \\
- 6246.320 &      26.0 &      3.60 &    --0.894 &    114.00 &    129.15 &     90.50 &    124.05 &     61.68 \\
- 6265.130 &      26.0 &      2.17 &    --2.550 &    132.93 &    154.97 &     94.79 &    129.65 &     55.50 \\
- 6270.220 &      26.0 &      2.86 &    --2.500 &     76.71 &     93.59 &     41.22 &     79.05 &     17.41 \\
- 6271.280 &      26.0 &      3.33 &    --2.728 &     31.57 &     44.87 &     13.35 &     43.63 &   \nodata \\
- 6297.790 &      26.0 &      2.22 &    --2.740 &    119.28 &   \nodata &     81.27 &    111.34 &     42.26 \\
- 6301.500 &      26.0 &      3.65 &    --0.766 &    115.00 &    130.57 &     91.09 &    117.86 &   \nodata \\
- 6322.690 &      26.0 &      2.59 &    --2.426 &    111.05 &    124.39 &     74.19 &    103.53 &     41.61 \\
- 6336.820 &      26.0 &      3.68 &    --0.916 &    106.61 &    116.77 &     81.17 &    113.62 &     52.77 \\
- 6353.840 &      26.0 &      0.91 &    --6.477 &     11.78 &     23.73 &   \nodata &     14.12 &   \nodata \\
- 6355.030 &      26.0 &      2.84 &    --2.403 &   \nodata &    122.18 &     58.95 &   \nodata &     27.76 \\
- 6411.650 &      26.0 &      3.65 &    --0.734 &    122.49 &    135.09 &     97.80 &    131.75 &     68.20 \\
- 6469.190 &      26.0 &      4.84 &    --0.770 &   \nodata &   \nodata &     18.72 &   \nodata &   \nodata \\
- 6574.230 &      26.0 &      0.99 &    --5.004 &     84.07 &    118.54 &     35.42 &     87.02 &   \nodata \\
- 6575.020 &      26.0 &      2.59 &    --2.727 &    100.74 &    118.20 &     55.46 &    103.43 &     23.43 \\
- 6581.210 &      26.0 &      1.50 &    --4.705 &     72.41 &     87.47 &     21.69 &     69.56 &   \nodata \\
- 6609.110 &      26.0 &      2.56 &    --2.692 &    102.04 &    118.77 &     60.88 &    103.07 &     29.10 \\
- 6648.080 &      26.0 &      1.01 &    --5.918 &     37.05 &     54.92 &   \nodata &     37.88 &   \nodata \\
- 6739.520 &      26.0 &      1.56 &    --4.820 &     43.10 &     60.83 &   \nodata &     44.46 &   \nodata \\
- 6750.150 &      26.0 &      2.42 &    --2.621 &    110.92 &    128.94 &     78.61 &    109.54 &     40.25 \\
- 6786.860 &      26.0 &      4.19 &    --1.850 &     22.52 &     29.14 &   \nodata &     32.32 &   \nodata \\
- 6810.260 &      26.0 &      4.60 &    --1.000 &     36.16 &     46.93 &     14.51 &     54.86 &      8.49 \\
- 6971.930 &      26.0 &      3.02 &    --3.390 &     20.95 &     30.29 &   \nodata &     28.72 &   \nodata \\
- 7112.170 &      26.0 &      2.99 &    --3.044 &     45.44 &     59.25 &     13.34 &     52.97 &   \nodata \\
- 7189.150 &      26.0 &      3.07 &    --2.796 &     57.46 &     66.29 &   \nodata &   \nodata &   \nodata \\
- 7223.660 &      26.0 &      3.01 &    --2.269 &     87.17 &    114.42 &     47.18 &     90.80 &   \nodata \\
- 7401.690 &      26.0 &      4.18 &    --1.660 &     38.86 &     50.50 &     14.73 &     59.70 &   \nodata \\
- 7710.360 &      26.0 &      4.22 &    --1.129 &     62.55 &     76.72 &     32.47 &     75.37 &   \nodata \\
- 7723.200 &      26.0 &      2.28 &    --3.617 &     82.10 &    100.41 &     36.62 &     91.89 &   \nodata \\
- 7941.090 &      26.0 &      3.27 &    --2.331 &     50.25 &   \nodata &     22.41 &     61.73 &   \nodata \\
- 5234.620 &      26.1 &      3.22 &    --2.150 &   \nodata &     81.16 &   \nodata &   \nodata &     58.33 \\
- 5325.550 &      26.1 &      3.22 &    --3.220 &   \nodata &     32.07 &     43.44 &   \nodata &     11.62 \\
- 5414.070 &      26.1 &      3.22 &    --3.750 &   \nodata &   \nodata &     23.56 &     20.98 &      6.85 \\
- 5425.260 &      26.1 &      3.20 &    --3.370 &     27.09 &     38.20 &     41.32 &     37.29 &     14.47 \\
- 5991.380 &      26.1 &      3.15 &    --3.557 &     21.50 &   \nodata &     28.34 &     25.80 &      7.66 \\
- 6084.110 &      26.1 &      3.20 &    --3.808 &     11.81 &     15.98 &     20.00 &     18.81 &   \nodata \\
- 6149.260 &      26.1 &      3.89 &    --2.724 &     21.75 &     25.19 &     30.83 &     26.28 &     11.80 \\
- 6247.560 &      26.1 &      3.89 &    --2.329 &     31.15 &     36.73 &     50.16 &     40.30 &     21.38 \\
- 6369.460 &      26.1 &      2.89 &    --4.250 &     13.49 &     16.26 &     18.13 &     16.72 &      5.89 \\
- 6416.920 &      26.1 &      3.89 &    --2.740 &     23.09 &     29.20 &     29.18 &     31.92 &   \nodata \\
- 6432.680 &      26.1 &      2.89 &    --3.708 &     29.96 &     33.58 &     41.73 &     37.47 &     12.93 \\
- 6456.380 &      26.1 &      3.90 &    --2.075 &     40.91 &     47.90 &     61.24 &     49.33 &     30.85 \\
- 7224.490 &      26.1 &      3.89 &    --3.243 &   \nodata &   \nodata &     12.70 &     13.24 &   \nodata \\
- 7711.720 &      26.1 &      3.90 &    --2.543 &     23.68 &     29.14 &     37.42 &     29.79 &     14.85 \\
- 6189.000 &      27.0 &      1.71 &    --2.450 &     51.15 &     77.50 &      9.06 &     58.65 &   \nodata \\
- 6455.030 &      27.0 &      3.63 &    --0.250 &     19.14 &     29.82 &   \nodata &     31.42 &   \nodata \\
- 6632.450 &      27.0 &      2.28 &    --2.000 &     29.08 &     42.26 &   \nodata &     34.72 &   \nodata \\
- 5846.990 &      28.0 &      1.68 &    --3.210 &     60.72 &     77.03 &     17.76 &     62.70 &   \nodata \\
- 6086.280 &      28.0 &      4.26 &    --0.515 &     31.84 &     36.07 &     12.42 &     47.85 &   \nodata \\
- 6175.370 &      28.0 &      4.09 &    --0.535 &     41.41 &     48.64 &     21.11 &     52.50 &     10.42 \\
- 6177.240 &      28.0 &      1.83 &    --3.510 &     39.25 &     48.84 &     11.10 &     39.41 &   \nodata \\
- 6204.600 &      28.0 &      4.09 &    --1.140 &     14.88 &     18.50 &   \nodata &     25.25 &   \nodata \\
- 6635.120 &      28.0 &      4.42 &    --0.828 &     14.95 &     18.16 &   \nodata &     25.99 &   \nodata \\
- 6772.320 &      28.0 &      3.66 &    --0.987 &     53.50 &     59.12 &     26.46 &     62.05 &     12.97 \\
- 5105.540 &      29.0 &      1.39 &    --1.520 &    139.40 &    160.37 &     67.12 &    123.33 &     32.51 \\
- 4722.150 &      30.0 &      4.03 &    --0.390 &     74.05 &     67.90 &     73.57 &     76.47 &     37.45 \\
- 4810.528 &      30.0 &      4.08 &    --0.137 &     61.50 &     63.63 &     72.49 &     82.28 &     42.08 \\
- 7800.290 &      37.0 &      0.00 &      0.130 &   \nodata &   \nodata &   \nodata &     60.87 &   \nodata \\
- 5123.220 &      39.1 &      0.99 &    --0.830 &   \nodata &   \nodata &   \nodata &   \nodata &     16.46 \\
- 5200.420 &      39.1 &      0.99 &    --0.570 &    100.92 &   \nodata &     65.76 &     78.58 &     26.46 \\
- 5509.910 &      39.1 &      0.99 &    --1.010 &    103.01 &     94.44 &     47.04 &     95.37 &     15.75 \\
- 5544.610 &      39.1 &      1.74 &    --1.080 &     29.88 &     18.79 &      9.50 &     16.20 &   \nodata \\
- 6127.440 &      40.0 &      0.15 &    --1.060 &     56.33 &     44.90 &   \nodata &     29.69 &   \nodata \\
- 6134.550 &      40.0 &      0.00 &    --1.280 &     49.65 &     38.66 &   \nodata &     23.60 &   \nodata \\
- 6143.200 &      40.0 &      0.07 &    --1.100 &     54.38 &     44.59 &   \nodata &     30.67 &   \nodata \\
- 5112.270 &      40.1 &      1.67 &    --0.590 &   \nodata &   \nodata &     21.76 &   \nodata &   \nodata \\
- 5853.640 &      56.1 &      0.60 &    --1.010 &    143.48 &    121.36 &    110.82 &     99.79 &     49.62 \\
- 6141.730 &      56.1 &      0.70 &    --0.080 &    213.65 &    177.63 &    166.44 &    151.09 &     93.10 \\
- 5805.770 &      57.1 &      0.13 &    --1.560 &     47.67 &     28.80 &     13.04 &     25.08 &   \nodata \\
- 6390.480 &      57.1 &      0.32 &    --1.410 &     42.96 &     22.03 &     11.61 &     18.59 &   \nodata \\
- 5274.240 &      58.1 &      1.04 &    --0.320 &     29.14 &   \nodata &     12.69 &   \nodata &   \nodata \\
- 5472.300 &      58.1 &      1.24 &    --0.180 &     19.37 &   \nodata &   \nodata &   \nodata &   \nodata \\
- 4959.120 &      60.1 &      0.06 &    --0.800 &     79.90 &     74.05 &     34.96 &     64.18 &   \nodata \\
- 5092.790 &      60.1 &      0.38 &    --0.610 &     47.28 &   \nodata &     21.87 &     20.94 &   \nodata \\
- 5212.360 &      60.1 &      0.20 &    --0.960 &     61.37 &     61.85 &     19.56 &     51.64 &   \nodata \\
- 5234.190 &      60.1 &      0.55 &    --0.510 &     71.89 &     57.86 &     17.93 &     47.31 &   \nodata \\
- 5249.580 &      60.1 &      0.98 &      0.200 &     64.54 &     54.71 &     31.75 &     50.73 &   \nodata \\
- 5255.510 &      60.1 &      0.20 &    --0.670 &    116.28 &   \nodata &     40.49 &   \nodata &   \nodata \\
- 5293.160 &      60.1 &      0.82 &      0.100 &     74.25 &     71.57 &     29.03 &     62.49 &   \nodata \\
- 5319.810 &      60.1 &      0.55 &    --0.140 &     86.60 &   \nodata &     34.41 &   \nodata &   \nodata \\
- 6645.110 &      63.1 &      1.38 &      0.204 &     24.47 &     27.76 &     16.96 &     30.31 &   \nodata \\
+ 6300.300 &       8.0 &      0.00 &    --9.717 &      45.4 &      66.9 &      38.5 &      32.8 &      17.9 \\
+ 6363.780 &       8.0 &      0.02 &   --10.185 &      19.5 &      28.3 &      13.0 &      18.8 &   \nodata \\
+ 5688.190 &      11.0 &      2.11 &    --0.420 &   \nodata &   \nodata &      49.0 &     131.5 &      38.4 \\
+ 6154.230 &      11.0 &      2.10 &    --1.530 &      24.1 &      38.9 &   \nodata &      48.5 &   \nodata \\
+ 6160.750 &      11.0 &      2.10 &    --1.230 &      37.7 &      58.5 &   \nodata &      65.7 &   \nodata \\
+ 6318.720 &      12.0 &      5.11 &    --1.970 &   \nodata &      47.9 &      14.7 &      62.8 &       8.9 \\
+ 6319.240 &      12.0 &      5.11 &    --2.220 &      30.8 &   \nodata &       5.5 &   \nodata &   \nodata \\
+ 6965.410 &      12.0 &      5.75 &    --1.510 &   \nodata &   \nodata &   \nodata &      59.2 &   \nodata \\
+ 7387.690 &      12.0 &      5.75 &    --0.870 &      51.7 &      56.3 &      24.7 &      76.0 &      24.0 \\
+ 6696.020 &      13.0 &      3.14 &    --1.340 &      72.8 &      63.6 &      13.0 &   \nodata &   \nodata \\
+ 6698.670 &      13.0 &      3.14 &    --1.640 &      39.7 &      33.4 &   \nodata &      39.5 &   \nodata \\
+ 7835.310 &      13.0 &      4.02 &    --0.470 &      47.8 &      38.4 &   \nodata &      55.9 &       5.4 \\
+ 7836.130 &      13.0 &      4.02 &    --0.310 &      62.8 &      44.7 &   \nodata &      69.1 &      13.2 \\
+ 5690.430 &      14.0 &      4.93 &    --1.751 &      56.2 &      43.8 &      25.7 &      53.4 &      16.8 \\
+ 5793.070 &      14.0 &      4.93 &    --1.843 &      46.1 &      39.8 &      19.3 &      48.4 &   \nodata \\
+ 6125.020 &      14.0 &      5.61 &    --1.506 &      40.9 &      23.4 &      10.9 &      34.7 &   \nodata \\
+ 6145.010 &      14.0 &      5.62 &    --1.362 &      33.9 &      21.7 &      16.1 &      32.7 &      10.0 \\
+ 6155.130 &      14.0 &      5.62 &    --0.786 &      67.4 &      53.1 &      35.3 &      72.0 &      25.0 \\
+ 6166.440 &      20.0 &      2.52 &    --1.142 &      94.2 &     105.5 &      42.3 &      99.5 &      35.9 \\
+ 6169.040 &      20.0 &      2.52 &    --0.797 &     112.1 &     120.9 &      66.3 &     120.5 &      55.5 \\
+ 6169.560 &      20.0 &      2.53 &    --0.478 &     127.9 &     141.2 &      83.7 &     136.4 &      71.3 \\
+ 6455.600 &      20.0 &      2.52 &    --1.290 &      80.8 &      91.4 &      31.4 &      89.2 &      26.0 \\
+ 5526.820 &      21.1 &      1.77 &      0.130 &      98.8 &     113.3 &     100.8 &      98.4 &      51.1 \\
+ 5657.880 &      21.1 &      1.51 &    --0.500 &      96.5 &     107.5 &      92.7 &      95.4 &      41.2 \\
+ 5667.150 &      21.1 &      1.50 &    --1.240 &      59.4 &      75.0 &      45.0 &      58.5 &      14.5 \\
+ 5669.040 &      21.1 &      1.50 &    --1.120 &   \nodata &      92.5 &      57.3 &      75.2 &      18.2 \\
+ 6245.610 &      21.1 &      1.51 &    --0.980 &      67.1 &      83.6 &      53.3 &      67.4 &      14.8 \\
+ 6604.600 &      21.1 &      1.36 &    --1.480 &      65.6 &      82.1 &      49.4 &      65.9 &      17.8 \\
+ 6064.630 &      22.0 &      1.05 &    --1.888 &      59.7 &      80.9 &   \nodata &      58.6 &   \nodata \\
+ 6091.170 &      22.0 &      2.27 &    --0.367 &      45.2 &      59.1 &   \nodata &      56.3 &   \nodata \\
+ 6312.240 &      22.0 &      1.46 &    --1.496 &      46.2 &      63.4 &   \nodata &      48.8 &   \nodata \\
+ 6336.100 &      22.0 &      1.44 &    --1.687 &      35.9 &      54.1 &   \nodata &      42.3 &   \nodata \\
+ 5154.080 &      22.1 &      1.57 &    --1.920 &     112.2 &   \nodata &     114.0 &   \nodata &      53.9 \\
+ 5185.910 &      22.1 &      1.89 &    --1.350 &   \nodata &     101.4 &     105.5 &   \nodata &      55.3 \\
+ 5336.790 &      22.1 &      1.58 &    --1.690 &     116.3 &     124.6 &     119.5 &     104.0 &      61.4 \\
+ 5381.030 &      22.1 &      1.59 &    --2.080 &   \nodata &     131.4 &     101.9 &     109.9 &      48.0 \\
+ 5727.060 &      23.0 &      1.08 &    --0.010 &     122.4 &   \nodata &      26.0 &     116.8 &       9.1 \\
+ 6090.220 &      23.0 &      1.08 &    --0.060 &      93.6 &     115.6 &      23.6 &      92.8 &   \nodata \\
+ 6216.360 &      23.0 &      0.28 &    --1.290 &     108.8 &   \nodata &      16.9 &     109.3 &   \nodata \\
+ 6251.820 &      23.0 &      0.29 &    --1.340 &      94.7 &     124.4 &   \nodata &      92.4 &   \nodata \\
+ 6274.640 &      23.0 &      0.27 &    --1.670 &      65.5 &      93.8 &   \nodata &      61.5 &   \nodata \\
+ 6504.160 &      23.0 &      1.18 &    --1.230 &      22.9 &      33.7 &   \nodata &      31.9 &   \nodata \\
+ 4545.950 &      24.0 &      0.94 &    --1.370 &   \nodata &   \nodata &      80.2 &   \nodata &   \nodata \\
+ 4580.056 &      24.0 &      0.94 &    --1.650 &   \nodata &   \nodata &   \nodata &   \nodata &      44.2 \\
+ 4616.137 &      24.0 &      0.98 &    --1.190 &     128.7 &     139.3 &      89.4 &     126.2 &      59.9 \\
+ 4626.188 &      24.0 &      0.97 &    --1.320 &     122.2 &     136.4 &      82.2 &   \nodata &      56.9 \\
+ 4646.150 &      24.0 &      1.03 &    --0.740 &   \nodata &   \nodata &     110.6 &     146.1 &      75.3 \\
+ 4651.280 &      24.0 &      0.98 &    --1.460 &     127.8 &     140.6 &      75.4 &     116.3 &      48.4 \\
+ 4652.158 &      24.0 &      1.00 &    --1.030 &     138.5 &   \nodata &      96.9 &     138.0 &      66.7 \\
+ 5206.040 &      24.0 &      0.94 &      0.020 &   \nodata &   \nodata &   \nodata &   \nodata &     132.8 \\
+ 5247.564 &      24.0 &      0.96 &    --1.640 &     141.4 &   \nodata &      76.1 &   \nodata &      46.7 \\
+ 5296.690 &      24.0 &      0.98 &    --1.360 &     149.9 &   \nodata &      85.0 &     141.0 &      59.0 \\
+ 5300.740 &      24.0 &      0.98 &    --2.000 &     120.5 &   \nodata &   \nodata &     112.2 &   \nodata \\
+ 5345.800 &      24.0 &      1.00 &    --0.950 &   \nodata &   \nodata &     115.4 &   \nodata &      81.1 \\
+ 5348.310 &      24.0 &      1.00 &    --1.210 &     150.8 &   \nodata &      94.8 &     142.4 &      63.0 \\
+ 5409.770 &      24.0 &      1.03 &    --0.670 &   \nodata &   \nodata &     132.4 &   \nodata &      92.1 \\
+ 4558.594 &      24.1 &      4.07 &    --0.656 &   \nodata &   \nodata &   \nodata &     101.8 &      46.5 \\
+ 4588.142 &      24.1 &      4.07 &    --0.826 &      46.0 &      53.0 &      60.5 &      55.0 &      36.0 \\
+ 4591.992 &      24.1 &      4.07 &    --1.419 &   \nodata &   \nodata &      29.1 &      28.5 &      19.6 \\
+ 6013.530 &      25.0 &      3.07 &    --0.251 &      89.2 &     114.6 &      22.2 &     109.4 &      14.8 \\
+ 6016.670 &      25.0 &      3.08 &    --0.100 &      94.0 &     116.0 &      28.1 &     113.0 &      17.1 \\
+ 6021.800 &      25.0 &      3.08 &      0.034 &      97.5 &     116.0 &      39.1 &     110.7 &      19.9 \\
+ 5044.210 &      26.0 &      2.85 &    --2.034 &   \nodata &   \nodata &   \nodata &   \nodata &      33.7 \\
+ 5054.640 &      26.0 &      3.64 &    --1.938 &      38.0 &   \nodata &   \nodata &   \nodata &   \nodata \\
+ 5242.490 &      26.0 &      3.63 &    --0.980 &      94.3 &     101.8 &      72.9 &   \nodata &      49.2 \\
+ 5321.110 &      26.0 &      4.43 &    --1.106 &      35.0 &      35.3 &      11.1 &   \nodata &   \nodata \\
+ 5322.040 &      26.0 &      2.28 &    --2.840 &      93.1 &     103.0 &      59.5 &   \nodata &      30.9 \\
+ 5326.140 &      26.0 &      3.57 &    --2.130 &      40.4 &      51.7 &      13.7 &      48.4 &   \nodata \\
+ 5365.400 &      26.0 &      3.57 &    --1.040 &   \nodata &     100.3 &   \nodata &      93.8 &   \nodata \\
+ 5367.480 &      26.0 &      4.41 &      0.430 &     108.4 &     118.0 &      92.4 &     119.1 &      73.7 \\
+ 5379.570 &      26.0 &      3.69 &    --1.530 &      71.4 &      81.4 &      34.9 &      75.6 &      19.6 \\
+ 5491.840 &      26.0 &      4.18 &    --2.250 &   \nodata &   \nodata &   \nodata &      17.3 &   \nodata \\
+ 5618.630 &      26.0 &      4.21 &    --1.292 &      43.5 &      54.3 &      20.2 &      57.4 &      11.3 \\
+ 5701.550 &      26.0 &      2.56 &    --2.216 &     118.5 &     134.8 &      91.8 &     119.5 &      49.5 \\
+ 5705.470 &      26.0 &      4.30 &    --1.420 &      29.2 &      41.5 &      10.9 &      44.5 &       7.7 \\
+ 5741.850 &      26.0 &      4.25 &    --1.689 &      36.2 &      37.0 &      13.0 &      48.2 &   \nodata \\
+ 5775.080 &      26.0 &      4.22 &    --1.310 &      55.0 &      62.1 &      25.3 &      67.4 &      14.7 \\
+ 5778.450 &      26.0 &      2.59 &    --3.480 &      42.8 &      55.8 &      13.4 &      50.1 &   \nodata \\
+ 5811.920 &      26.0 &      4.14 &    --2.430 &   \nodata &   \nodata &   \nodata &      10.9 &   \nodata \\
+ 5837.700 &      26.0 &      4.29 &    --2.340 &   \nodata &   \nodata &   \nodata &      12.9 &   \nodata \\
+ 5853.160 &      26.0 &      1.49 &    --5.280 &      30.4 &      43.4 &       6.3 &      34.7 &   \nodata \\
+ 5855.090 &      26.0 &      4.60 &    --1.547 &      13.3 &      20.3 &   \nodata &      22.8 &   \nodata \\
+ 5856.100 &      26.0 &      4.29 &    --1.640 &      27.9 &      40.2 &   \nodata &      42.7 &   \nodata \\
+ 5858.790 &      26.0 &      4.22 &    --2.260 &   \nodata &      11.4 &   \nodata &      16.9 &   \nodata \\
+ 5909.970 &      26.0 &      3.21 &    --2.640 &      56.0 &      72.6 &      18.5 &      63.3 &   \nodata \\
+ 5916.250 &      26.0 &      2.45 &    --2.994 &      92.9 &     105.1 &      51.2 &      95.4 &      17.7 \\
+ 5927.800 &      26.0 &      4.65 &    --1.090 &      32.4 &      36.7 &      12.2 &      50.9 &   \nodata \\
+ 5956.690 &      26.0 &      0.86 &    --4.608 &     121.7 &     143.8 &      70.3 &     107.8 &      25.5 \\
+ 6012.210 &      26.0 &      2.22 &    --4.070 &      44.4 &      58.8 &      11.5 &      53.0 &   \nodata \\
+ 6019.360 &      26.0 &      3.57 &    --3.360 &       7.0 &   \nodata &   \nodata &      11.3 &   \nodata \\
+ 6027.050 &      26.0 &      4.07 &    --1.106 &      66.2 &      77.0 &      36.2 &      77.2 &      23.5 \\
+ 6054.080 &      26.0 &      4.37 &    --2.310 &       5.6 &       8.1 &   \nodata &      12.9 &   \nodata \\
+ 6105.130 &      26.0 &      4.55 &    --2.050 &   \nodata &      10.9 &   \nodata &      14.8 &   \nodata \\
+ 6120.240 &      26.0 &      0.91 &    --5.970 &      35.2 &      52.7 &       8.5 &      32.4 &   \nodata \\
+ 6151.620 &      26.0 &      2.17 &    --3.299 &      88.9 &     102.9 &      46.9 &      87.0 &      18.2 \\
+ 6157.730 &      26.0 &      4.08 &    --1.320 &   \nodata &      81.2 &      33.2 &      78.1 &      18.8 \\
+ 6159.380 &      26.0 &      4.61 &    --1.970 &   \nodata &       9.6 &   \nodata &      13.6 &   \nodata \\
+ 6165.360 &      26.0 &      4.14 &    --1.490 &      40.6 &      51.6 &      14.2 &      54.0 &      10.8 \\
+ 6173.340 &      26.0 &      2.22 &    --2.880 &     109.6 &     125.6 &      70.7 &     105.6 &      34.9 \\
+ 6180.200 &      26.0 &      2.73 &    --2.637 &      86.2 &     100.6 &      44.3 &      91.5 &      20.8 \\
+ 6200.310 &      26.0 &      2.61 &    --2.437 &     105.2 &     122.2 &      70.8 &     105.4 &      36.6 \\
+ 6219.280 &      26.0 &      2.20 &    --2.433 &     134.3 &     153.3 &     103.3 &     127.4 &      56.7 \\
+ 6229.230 &      26.0 &      2.84 &    --2.846 &      60.1 &      73.1 &      21.0 &      65.8 &      13.6 \\
+ 6232.640 &      26.0 &      3.65 &    --1.283 &      92.6 &     104.3 &      58.3 &     103.0 &      35.6 \\
+ 6246.320 &      26.0 &      3.60 &    --0.894 &     114.0 &     129.2 &      90.5 &     124.1 &      61.7 \\
+ 6265.130 &      26.0 &      2.17 &    --2.550 &     132.9 &     155.0 &      94.8 &     129.7 &      55.5 \\
+ 6270.220 &      26.0 &      2.86 &    --2.500 &      76.7 &      93.6 &      41.2 &      79.1 &      17.4 \\
+ 6271.280 &      26.0 &      3.33 &    --2.728 &      31.6 &      44.9 &      13.4 &      43.6 &   \nodata \\
+ 6297.790 &      26.0 &      2.22 &    --2.740 &     119.3 &   \nodata &      81.3 &     111.3 &      42.3 \\
+ 6301.500 &      26.0 &      3.65 &    --0.766 &     115.0 &     130.6 &      91.1 &     117.9 &   \nodata \\
+ 6322.690 &      26.0 &      2.59 &    --2.426 &     111.0 &     124.4 &      74.2 &     103.5 &      41.6 \\
+ 6336.820 &      26.0 &      3.68 &    --0.916 &     106.6 &     116.8 &      81.2 &     113.6 &      52.8 \\
+ 6353.840 &      26.0 &      0.91 &    --6.477 &      11.8 &      23.7 &   \nodata &      14.1 &   \nodata \\
+ 6355.030 &      26.0 &      2.84 &    --2.403 &   \nodata &     122.2 &      58.9 &   \nodata &      27.8 \\
+ 6411.650 &      26.0 &      3.65 &    --0.734 &     122.5 &     135.1 &      97.8 &     131.8 &      68.2 \\
+ 6469.190 &      26.0 &      4.84 &    --0.770 &   \nodata &   \nodata &      18.7 &   \nodata &   \nodata \\
+ 6574.230 &      26.0 &      0.99 &    --5.004 &      84.1 &     118.5 &      35.4 &      87.0 &   \nodata \\
+ 6575.020 &      26.0 &      2.59 &    --2.727 &     100.7 &     118.2 &      55.5 &     103.4 &      23.4 \\
+ 6581.210 &      26.0 &      1.50 &    --4.705 &      72.4 &      87.5 &      21.7 &      69.6 &   \nodata \\
+ 6609.110 &      26.0 &      2.56 &    --2.692 &     102.0 &     118.8 &      60.9 &     103.1 &      29.1 \\
+ 6648.080 &      26.0 &      1.01 &    --5.918 &      37.1 &      54.9 &   \nodata &      37.9 &   \nodata \\
+ 6739.520 &      26.0 &      1.56 &    --4.820 &      43.1 &      60.8 &   \nodata &      44.5 &   \nodata \\
+ 6750.150 &      26.0 &      2.42 &    --2.621 &     110.9 &     128.9 &      78.6 &     109.5 &      40.2 \\
+ 6786.860 &      26.0 &      4.19 &    --1.850 &      22.5 &      29.1 &   \nodata &      32.3 &   \nodata \\
+ 6810.260 &      26.0 &      4.60 &    --1.000 &      36.2 &      46.9 &      14.5 &      54.9 &       8.5 \\
+ 6971.930 &      26.0 &      3.02 &    --3.390 &      21.0 &      30.3 &   \nodata &      28.7 &   \nodata \\
+ 7112.170 &      26.0 &      2.99 &    --3.044 &      45.4 &      59.3 &      13.3 &      53.0 &   \nodata \\
+ 7189.150 &      26.0 &      3.07 &    --2.796 &      57.5 &      66.3 &   \nodata &   \nodata &   \nodata \\
+ 7223.660 &      26.0 &      3.01 &    --2.269 &      87.2 &     114.4 &      47.2 &      90.8 &   \nodata \\
+ 7401.690 &      26.0 &      4.18 &    --1.660 &      38.9 &      50.5 &      14.7 &      59.7 &   \nodata \\
+ 7710.360 &      26.0 &      4.22 &    --1.129 &      62.5 &      76.7 &      32.5 &      75.4 &   \nodata \\
+ 7723.200 &      26.0 &      2.28 &    --3.617 &      82.1 &     100.4 &      36.6 &      91.9 &   \nodata \\
+ 7941.090 &      26.0 &      3.27 &    --2.331 &      50.3 &   \nodata &      22.4 &      61.7 &   \nodata \\
+ 5234.620 &      26.1 &      3.22 &    --2.150 &   \nodata &      81.2 &   \nodata &   \nodata &      58.3 \\
+ 5325.550 &      26.1 &      3.22 &    --3.220 &   \nodata &      32.1 &      43.4 &   \nodata &      11.6 \\
+ 5414.070 &      26.1 &      3.22 &    --3.750 &   \nodata &   \nodata &      23.6 &      21.0 &       6.8 \\
+ 5425.260 &      26.1 &      3.20 &    --3.370 &      27.1 &      38.2 &      41.3 &      37.3 &      14.5 \\
+ 5991.380 &      26.1 &      3.15 &    --3.557 &      21.5 &   \nodata &      28.3 &      25.8 &       7.7 \\
+ 6084.110 &      26.1 &      3.20 &    --3.808 &      11.8 &      16.0 &      20.0 &      18.8 &   \nodata \\
+ 6149.260 &      26.1 &      3.89 &    --2.724 &      21.7 &      25.2 &      30.8 &      26.3 &      11.8 \\
+ 6247.560 &      26.1 &      3.89 &    --2.329 &      31.2 &      36.7 &      50.2 &      40.3 &      21.4 \\
+ 6369.460 &      26.1 &      2.89 &    --4.250 &      13.5 &      16.3 &      18.1 &      16.7 &       5.9 \\
+ 6416.920 &      26.1 &      3.89 &    --2.740 &      23.1 &      29.2 &      29.2 &      31.9 &   \nodata \\
+ 6432.680 &      26.1 &      2.89 &    --3.708 &      30.0 &      33.6 &      41.7 &      37.5 &      12.9 \\
+ 6456.380 &      26.1 &      3.90 &    --2.075 &      40.9 &      47.9 &      61.2 &      49.3 &      30.9 \\
+ 7224.490 &      26.1 &      3.89 &    --3.243 &   \nodata &   \nodata &      12.7 &      13.2 &   \nodata \\
+ 7711.720 &      26.1 &      3.90 &    --2.543 &      23.7 &      29.1 &      37.4 &      29.8 &      14.9 \\
+ 6189.000 &      27.0 &      1.71 &    --2.450 &      51.1 &      77.5 &       9.1 &      58.7 &   \nodata \\
+ 6455.030 &      27.0 &      3.63 &    --0.250 &      19.1 &      29.8 &   \nodata &      31.4 &   \nodata \\
+ 6632.450 &      27.0 &      2.28 &    --2.000 &      29.1 &      42.3 &   \nodata &      34.7 &   \nodata \\
+ 5846.990 &      28.0 &      1.68 &    --3.210 &      60.7 &      77.0 &      17.8 &      62.7 &   \nodata \\
+ 6086.280 &      28.0 &      4.26 &    --0.515 &      31.8 &      36.1 &      12.4 &      47.8 &   \nodata \\
+ 6175.370 &      28.0 &      4.09 &    --0.535 &      41.4 &      48.6 &      21.1 &      52.5 &      10.4 \\
+ 6177.240 &      28.0 &      1.83 &    --3.510 &      39.3 &      48.8 &      11.1 &      39.4 &   \nodata \\
+ 6204.600 &      28.0 &      4.09 &    --1.140 &      14.9 &      18.5 &   \nodata &      25.3 &   \nodata \\
+ 6635.120 &      28.0 &      4.42 &    --0.828 &      14.9 &      18.2 &   \nodata &      26.0 &   \nodata \\
+ 6772.320 &      28.0 &      3.66 &    --0.987 &      53.5 &      59.1 &      26.5 &      62.0 &      13.0 \\
+ 5105.540 &      29.0 &      1.39 &    --1.520 &     139.4 &     160.4 &      67.1 &     123.3 &      32.5 \\
+ 4722.150 &      30.0 &      4.03 &    --0.390 &      74.1 &      67.9 &      73.6 &      76.5 &      37.4 \\
+ 4810.528 &      30.0 &      4.08 &    --0.137 &      61.5 &      63.6 &      72.5 &      82.3 &      42.1 \\
+ 7800.290 &      37.0 &      0.00 &      0.130 &   \nodata &   \nodata &   \nodata &      60.9 &   \nodata \\
+ 5123.220 &      39.1 &      0.99 &    --0.830 &   \nodata &   \nodata &   \nodata &   \nodata &      16.5 \\
+ 5200.420 &      39.1 &      0.99 &    --0.570 &     100.9 &   \nodata &      65.8 &      78.6 &      26.5 \\
+ 5509.910 &      39.1 &      0.99 &    --1.010 &     103.0 &      94.4 &      47.0 &      95.4 &      15.7 \\
+ 5544.610 &      39.1 &      1.74 &    --1.080 &      29.9 &      18.8 &       9.5 &      16.2 &   \nodata \\
+ 6127.440 &      40.0 &      0.15 &    --1.060 &      56.3 &      44.9 &   \nodata &      29.7 &   \nodata \\
+ 6134.550 &      40.0 &      0.00 &    --1.280 &      49.6 &      38.7 &   \nodata &      23.6 &   \nodata \\
+ 6143.200 &      40.0 &      0.07 &    --1.100 &      54.4 &      44.6 &   \nodata &      30.7 &   \nodata \\
+ 5112.270 &      40.1 &      1.67 &    --0.590 &   \nodata &   \nodata &      21.8 &   \nodata &   \nodata \\
+ 5853.640 &      56.1 &      0.60 &    --1.010 &     143.5 &     121.4 &     110.8 &      99.8 &      49.6 \\
+ 6141.730 &      56.1 &      0.70 &    --0.080 &     213.6 &     177.6 &     166.4 &     151.1 &      93.1 \\
+ 5805.770 &      57.1 &      0.13 &    --1.560 &      47.7 &      28.8 &      13.0 &      25.1 &   \nodata \\
+ 6390.480 &      57.1 &      0.32 &    --1.410 &      43.0 &      22.0 &      11.6 &      18.6 &   \nodata \\
+ 5274.240 &      58.1 &      1.04 &    --0.320 &      29.1 &   \nodata &      12.7 &   \nodata &   \nodata \\
+ 5472.300 &      58.1 &      1.24 &    --0.180 &      19.4 &   \nodata &   \nodata &   \nodata &   \nodata \\
+ 4959.120 &      60.1 &      0.06 &    --0.800 &      79.9 &      74.0 &      35.0 &      64.2 &   \nodata \\
+ 5092.790 &      60.1 &      0.38 &    --0.610 &      47.3 &   \nodata &      21.9 &      20.9 &   \nodata \\
+ 5212.360 &      60.1 &      0.20 &    --0.960 &      61.4 &      61.9 &      19.6 &      51.6 &   \nodata \\
+ 5234.190 &      60.1 &      0.55 &    --0.510 &      71.9 &      57.9 &      17.9 &      47.3 &   \nodata \\
+ 5249.580 &      60.1 &      0.98 &      0.200 &      64.5 &      54.7 &      31.8 &      50.7 &   \nodata \\
+ 5255.510 &      60.1 &      0.20 &    --0.670 &     116.3 &   \nodata &      40.5 &   \nodata &   \nodata \\
+ 5293.160 &      60.1 &      0.82 &      0.100 &      74.2 &      71.6 &      29.0 &      62.5 &   \nodata \\
+ 5319.810 &      60.1 &      0.55 &    --0.140 &      86.6 &   \nodata &      34.4 &   \nodata &   \nodata \\
+ 6645.110 &      63.1 &      1.38 &      0.204 &      24.5 &      27.8 &      17.0 &      30.3 &   \nodata \\
 \enddata
 \end{deluxetable*}
-\clearpage
-\clearpage
-% equivalent widths table
 
@@
 The stellar parameter spacing between models is 250\,K, 0.5\,dex in surface gravity, 0.5\,dex in [M/H] and 0.1\,dex in [$\alpha$/Fe].
-We interpolated the atmospheric pressures, densities, temperatures, and opacities between stellar atmosphere models using the Quickhull algorithm \citep{barber;et-al_1996}.
+We interpolated the temperature, gas and radiative pressure, electron density and opacities between atmosphere models using the Quickhull algorithm \citep{barber;et-al_1996}.
 Quickhull is reliant on Delaunay tessellation, which suffers from extremely skewed cells when the grid points vary in size by orders of magnitude -- as $T_{\rm eff}$ values do compared to $\log{g}$ or [X/H].
@@
 We scaled each stellar parameter between zero and unity prior to interpolation in order to minimise these effects.
-During this step, $\log{g}$, [M/H] and [$\alpha$/Fe] points were scaled such that we simultaneously interpolate linearly in $T_{\rm eff}$ and logarithmically in all other parameters.
+During this step, $\log{g}$, [M/H] and [$\alpha$/Fe] values were scaled such that we simultaneously interpolate linearly in $T_{\rm eff}$ and logarithmically in all other parameters.
 
@@
 This is noteworthy, but is less relevant for these analyses as most of our line measurements are red-ward of 450\,nm.
-Absorption lines are assumed to form under the assumption of local thermal equilibrium.
+Absorption lines are assumed to form under the assumption of Local Thermal Equilibrium (LTE).
 
@@
 	\includegraphics[width=\textwidth]{./figures/spectra-h-alpha.pdf}
-	\caption{Spectra for all Aquarius stream stars.}
+	\caption{Sample spectra of the H-$\alpha$ region for all Aquarius stream candidates.}
 	\label{fig:spectra-h-alpha}
@@
 An extinction of $E(B-V) = 0.10$ would be required for the \citet{alonso;et-al_1999} relation to yield a temperature of ${\sim}$4500\,K \--- within the uncertainties of our effective temperature derived from spectroscopy.
-Such a discrepancy in extinction is large, but not uncommon (e.g., see \citet{nataf;et-al}).
+Such a discrepancy in extinction is large, but not uncommon \citep[e.g.
+see][]{peek;graves_2010,nataf;et-al_2012}.
 Although we suspect J223504-152834 to have a higher reddening than $E(B-V) = 0.04$, we have adopted the \citet{schlegel;et-al_1998} value for this analysis.
@@
 Moreover, the 630 nm line is blended with a Ni \textsc{i} absorption line \citep{allende-prieto;et-al_2001}, and hence the region requires careful consideration.
-Although the O \textsc{i} triplet lines at 777 nm are stronger than the forbidden lines, they are extremely susceptible to NLTE and 3D effects \citep{asplund;perez_2001}, and sensitive to changes in microturbulence.
+Although the O \textsc{i} triplet lines at 777 nm are stronger than the forbidden lines, they are extremely susceptible to non-LTE and 3D effects \citep{asplund;perez_2001}, and sensitive to changes in microturbulence.
 
@@
 Abundances determined from the oxygen triplet lines were systematically $+0.27$\,dex higher than found from the [O \textsc{i}] lines.
-\citet{perez;et-al_2006} found [O/Fe] values based on the O \textsc{i} permitted triplet lines are on average $+0.19 \pm 0.07$\,dex higher than those found from the forbidden lines, after NLTE corrections of $-$0.08\,dex had been applied to the permitted abundance.
-Thus, our 0.27\,dex offset between measurements of the [O \textsc{i}] and O \textsc{i} triplet lines is exactly the same as found by \citet{perez;et-al_2006}, which we attribute to a combination of systematic phenomena including NLTE and 3D effects.
+\citet{perez;et-al_2006} found [O/Fe] values based on the O \textsc{i} permitted triplet lines are on average $+0.19 \pm 0.07$\,dex higher than those found from the forbidden lines, after non-LTE corrections of $-$0.08\,dex had been applied to the permitted abundance.
+Thus, our 0.27\,dex offset between measurements of the [O \textsc{i}] and O \textsc{i} triplet lines is exactly the same as found by \citet{perez;et-al_2006}, which we attribute to a combination of systematic phenomena including non-LTE and 3D effects.
 \citet{perez;et-al_2006} concluded the weak forbidden lines, when not too weak, probably give the most reliable estimate of oxygen abundance.
@@
 This makes the continuum determination and subsequent aluminium measurement non-trivial, especially given the metallicity of our stars.
-Additionally, the 3944 and 3961 lines suffer from appreciable departures from LTE, resulting in under-estimated abundances by up to $\sim$0.60\,dex \citep{baumuller;gehren_1997}.
+Additionally, the 3944 and 3961 lines suffer from appreciable departures from LTE, resulting in under-estimated abundances by up to $\sim$0.60\,dex \citep{baumueller;gehren_1997}.
 Instead, we have measured Al abundances from other available transitions: the Al \textsc{i} lines at 6696, 6698, 7835 and 7836\,{\AA}.
@@
 The number of clean, suitable Cr \textsc{i} lines available between candidates fluxuated from three to twelve.
-Very little line-to-line scatter is present in both Cr \textsc{i} and \textsc{ii}: the random scatter is below 0.04\,dex for most stars, with the isolated example of J223504 where $\sigma(\mbox{[Cr \textsc{ii}/Fe]}) = 0.29$\,dex, where only three lines were available.
+Very little line-to-line scatter is present in both Cr \textsc{i} and \textsc{ii}: the random scatter is below 0.04\,dex for most stars, with the isolated example of J223504 where $\sigma(\mbox{[Cr \textsc{ii}/Fe]}) = 0.29$\,dex, and only three lines were available.
 The Cr \textsc{i} and \textsc{ii} abundances for J223504 are in good agreement (0.05\,dex), and since none of the measured profiles were particularly unusual, we chose not to exclude outlier measurements.
@@
 \section{Discussion}
-
+\label{sec:discussion}
 % wylie de boer discrepancies
@@
 It is clear that careful consideration must be given when inferring star-formation histories from observed stellar abundances.
-In addition to the normal care afforded for measuring elemental abundances from high-resolution spectroscopic data, attention must be given to telluric absorption, contamination from nickel transitions, as well as NLTE and 3D effects when calculating oxygen abundances.
+In addition to the normal care afforded for measuring elemental abundances from high-resolution spectroscopic data, attention must be given to telluric absorption, contamination from nickel transitions, as well as non-LTE and 3D effects when calculating oxygen abundances.
 Furthermore, when characterising the oxygen depletion rate \--- the strength of the Na-O anti-correlation in a given cluster \--- it is vital to sample stars belonging to all three components, where possible.
@@
 In such a scenario, any inferred anti-correlation could equally be explained by intrinsic chemical scatter or observational uncertainties.
+
+% [O/Fe], [Na/Fe]
+\begin{figure*}[t!]
+	\includegraphics[width=\textwidth]{./figures/aquarius-o-na-halo.pdf}
+	\caption{Oxygen and sodium abundances for thick disc ($+$), thin disc ($\times$) and halo ($\circ$) stars from \citet{reddy;et-al_2005}, and globular cluster stars from \citet{carretta;et-al_2009} (grey symbols).
+The Aquarius candidate abundances are also shown (\textbullet), illustrating how their [O/Fe], [Na/Fe] content is not dissimilar from galactic stars.
+Ambiguous thick disc/thin disc stars in \citet{reddy;et-al_2005} are marked with thick disc symbols ($+$), as are uncertain thick disc/halo stars with halo symbols ($\circ$).}
+	\label{fig:o-na}
+\end{figure*}
 
@@
 
-% [O/Fe], [Na/Fe]
-\begin{figure}[h]
-	\includegraphics[width=\columnwidth]{./figures/aquarius-o-na.pdf}
-	\caption{A plot showing [O/Fe] and [Na/Fe] for all Aquarius stream stars.}
-	\label{fig:o-na}
-\end{figure}
-
 The sodium-enhanced stars exhibit no depletion of oxygen; their chemistry does not demonstrate a classical Na-O anti-correlation.
@@
 This is perhaps unsurprising, given the nucleosynthetic pathways for aluminium and magnesium.
-In addition to the CNO cycle operating during hydrogen burning, the Mg-Al chain can also operate under extreme temperatures \citep[$T_6 \sim 3$\,K][]{arnould;et-al_1999}.
+In addition to the CNO cycle operating during hydrogen burning, the Mg-Al chain can also operate under extreme temperatures \citep[$T_6 \sim 3$\,K;][]{arnould;et-al_1999}.
 Aluminium is produced by proton capture of magnesium, beginning with $^{24}$Mg to $^{25}$Al.
@@
 However, the locations where these extreme temperatures can be found are under some debate.
-Standard models indicate that the interiors of globular cluster stars do not reach sufficient temperatures for the Mg-Al cycle to produce the observed variations.
-Thus, although the processes for creating these chemical patterns are understood, the exact site and requisite conditions still need explanation.
+Theoretical models indicate that the interiors of globular cluster stars do not reach sufficient temperatures for the Mg-Al cycle to produce the observed variations.
+Thus, although the processes for creating these chemical patterns are understood, the exact site and requisite conditions are lacking a full description.
 
@@
 Given that we do not find a Na-O anti-correlation, it is not surprising that a Mg-Al pattern has also not been observed.
-The Na-O signature is detected in all classical well-studied systems, but the Mg-Al anti-correlation is not always present.
 \citet{wylie-de-boer;et-al_2012} published magnesium and aluminium abundances for five stars in their Aquarius stream sample.
@@
 High $s$-process enhancements have been noted for a few disrupted globular clusters that exhibit a wide metallicity range.
-Most noteably: $\omega$Centurai \citep{majewski;et-al_2012}, M22 \citep{marinolet-al_2011} and (\# any others?).
+Most noteably: $\omega$Centurai \citep{majewski;et-al_2012}, M22 \citep{marino;et-al_2011} and (\# any others?).
 Like the Aquarius co-moving group, both clusters are relatively close to the sun: $R_\odot = 5.2$\,kpc and 3.2\,kpc, respectively.
@@
 $\omega$-Centurai has a retrograde orbit with low inclination.
-Many groups simulating this orbit have predicted retrograde tidal debris to occur near the Solar circle \citep{dinescu_2002,tsuchiya_2003,tsuchiya_2004,mizutani_2003,bekki_freeman_2003}.
+Many groups simulating this orbit have predicted retrograde tidal debris to occur near the Solar circle \citep{dinescu_2002,tsuchiya_2003,tsuchiya_2004,mizutani_2003,bekki;freeman_2003}.
 Subsequent searches for $\omega$-Cen debris in the solar neighbourhood have led to tantalizing signatures of debris.
@@
 
+\section{Conclusions}
+\label{sec:conclusions}
+\# Conclusions
+
 %\facilities{Magellan:Clay}

### 2013-01-30 2012-aqs/figures/plot-na-ni.py

@@ -178,8 +178,8 @@ Reddy_ThickDisk_Na_Fe, Reddy_ThickDisk_Ni_Fe, Reddy_ThinDisk_Na_Fe, Reddy_ThinDi
 # Nissen & Schuster 2010
 # Fulbright 2000
 
-text_x = 0.0
-text_y = 0.0
+text_x = 0.45
+text_y = -0.20
 
 fig = plt.figure()
 
@@ -187,27 +187,41 @@ ax = fig.add_subplot(411)
 ax.xaxis.set_visible(False)
 
 ax.scatter(Reddy_2003_Na_Fe, Reddy_2003_Ni_Fe, marker='^', color='k', label='Thick disc')
+ax.legend(loc=2, prop={'size': 9})
+ax.text(text_x, text_y, 'Reddy et al. (2003)', color='k', verticalalignment='bottom', horizontalalignment='right')
 
 
 ax = fig.add_subplot(412, sharex=ax, sharey=ax)
 ax.xaxis.set_visible(False)
 # square, diamond, triangle
-ax.scatter(Reddy_ThickDisk_Na_Fe, Reddy_ThickDisk_Ni_Fe, marker='+', edgecolor='k', facecolor='#666666', label='Thick disc')
-ax.scatter(Reddy_ThickThinDisk_Na_Fe, Reddy_ThickThinDisk_Ni_Fe, marker='^', color='#666666', label='Thick/thin disc')
-ax.scatter(Reddy_ThinDisk_Na_Fe, Reddy_ThinDisk_Ni_Fe, marker='+', edgecolor='k', facecolor='#cccccc', label='Thin disc')
-ax.scatter(Reddy_ThickDisk_Halo_Na_Fe, Reddy_ThickDisk_Halo_Ni_Fe, marker='d', color='k', label='Thick disc/halo')
+ax.scatter(Reddy_ThickDisk_Na_Fe, Reddy_ThickDisk_Ni_Fe, marker='+', edgecolor='k', label='Thick disc')
+#ax.scatter(Reddy_ThickThinDisk_Na_Fe, Reddy_ThickThinDisk_Ni_Fe, marker='^', color='#666666', label='Thick/thin disc')
+ax.scatter(Reddy_ThinDisk_Na_Fe, Reddy_ThinDisk_Ni_Fe, marker='x', edgecolor='k', label='Thin disc')
[…]

### 2013-01-30 2012-aqs/figures/plot-na-o.py

@@ -214,3 +214,96 @@ ax.text(xlims[0] + 0.05 * (xlims[1] - xlims[0]), ylims[0] + 0.05 * (ylims[1] - y
 
 plt.savefig('aquarius-o-na-cluster.pdf')
 
+
+
+# Get data from Reddy et al 2005
+reddy_data = np.loadtxt('Reddy_thick_disk_2005.data', delimiter='|', usecols=(1, 18, 21, 20), dtype=str)
+
+Reddy_ThickDisk_Na_Fe = []
+Reddy_ThickDisk_O_Fe = []
+Reddy_ThinDisk_Na_Fe = []
+Reddy_ThinDisk_O_Fe = []
+Reddy_ThickThinDisk_Na_Fe = []
+Reddy_ThickThinDisk_O_Fe = []
+Reddy_Halo_Na_Fe = []
+Reddy_Halo_O_Fe = []
+Reddy_ThickDisk_Halo_Na_Fe = []
+Reddy_ThickDisk_Halo_O_Fe = []
+
+for classification, fe_h, na_h, o_h in reddy_data:
+	
+	classification, fe_h, na_h, o_h = [var.strip() for var in (classification, fe_h, na_h, o_h)]
+
+
+	_Na_Fe, _O_Fe = np.nan, np.nan
+
+	if len(fe_h) == 0:
+		fe_h, na_h, o_h = [np.nan] * 3
+
+	else:
+
+		if len(na_h) == 0:
+			na_h = np.nan
+
+		else:
+			_Na_Fe = float(na_h) #- float(fe_h)
+
+
+		if len(o_h) == 0:
+			o_h = np.nan
+
+		else:
+			_O_Fe = float(o_h) #- float(fe_h)
+
+
+	if classification == 'Thick disc':
+		Reddy_ThickDisk_Na_Fe.append(_Na_Fe)
+		Reddy_ThickDisk_O_Fe.append(_O_Fe)
+
+	elif classification == 'Thin disc':
+		Reddy_ThinDisk_Na_Fe.append(_Na_Fe)
+		Reddy_ThinDisk_O_Fe.append(_O_Fe)
+
+	elif classification == 'Halo':
+		Reddy_Halo_Na_Fe.append(_Na_Fe)
+		Reddy_Halo_O_Fe.append(_O_Fe)
+
+	elif classification == 'Thin/thick disc':
[…]

### 2013-01-30 2012-aqs/figures/plot-smh-norris.py

@@ -57,9 +57,9 @@ ax1.get_yticklabels()[-1].set_visible(False)
 
 ax1.text(5, 10, '$\langle{}\Delta{}W_\lambda\\rangle{}\,=\,-0.64\,\pm\,2.78\,$m${\AA}$', color='k', verticalalignment='center')
 
-ax2.text(5, 150, "$a_0\,=\,%1.2f$\n$a_1\,=\,%1.2f$" % (c, m, ), verticalalignment='top')
+ax2.text(5, 150, "$a_0\,=\,%1.2f$\n$a_1\,=\,%1.2f$\n$N\,=\,%i$" % (c, m, len(smh_ew)), verticalalignment='top')
 
-ax1.set_title('%i lines in HD 140283' % (len(smh_ew), ))
+#ax1.set_title('%i lines in HD 140283' % (len(smh_ew), ))
 
 plt.savefig('smh-norris.pdf')
 plt.savefig('smh-norris.eps')

### 2013-02-05 2012-aqs/draft-aqs.tex
Incorporated Keller comments

@@
 % [DONE] Equivalent widths significant figures.
-% - Strontium?
-% - Carbon?
-% - Distance calculations revision
+% - Strontium
+% - Carbon
+% - Distance calculations revision with B-V (if available) instead of (J-K)
 % - Transverse motions table
 % - Transverse motions text
-% - Orbital energies plot
+% - Orbital energies plot w.r.t Zolotov simulations
 % - Minor merger text
@@
 
-% Casey, Keller, Alves-Brito, Frebel, Da Costa, Schlaufman, Karakas, Heather, QinQin, Freeman
+% Casey, Keller, Alves-Brito, Frebel, Da Costa, Schlaufman, Karakas, Jacobson, Yu, Freeman
 
@@
 Thus, the co-moving group was named the Aquarius stream.
-The artefact is most apparent when examining velocities against galactic latitude for stars within $-70\,^\circ < b < -50\,^\circ$.
+The group is most apparent when examining velocities against galactic latitude for stars within $-70\,^\circ < b < -50\,^\circ$.
 \citet{williams;et-al_2011} employed a selection criteria of $-250\,\mbox{km s}^{-1} < V_{\rm hel} < -150\,\mbox{km s}^{-1}$, $30\,^\circ < l < 75\,^\circ$ and $J > 10.3$ to maximize the contrast between the stream and background, identifying 15 candidates in the process.
@@
 
-The Aquarius stream has a metallicity of $\mbox{[Fe/H]} \sim -1.0$, slightly more metal-rich than halo stars at the same distance.
+RAVE observations suggest the Aquarius stream has a metallicity of $\mbox{[Fe/H]} \sim -1.0$, slightly more metal-rich than halo stars at the same distance.
 \citet{williams;et-al_2011} found the stream to have an average of $\mbox{[M/H]} = -1.0 \pm 0.4$, compared to $\mbox{[M/H]} = -1.1 \pm 0.6$ for background stars after the same selection cuts had been employed.
@@
 Specifically, an anti-correlation between sodium and oxygen content appears ubiquitous to globular clusters.
-Originally this relationship was thought to arise from internal mixing along the giant branch.
+While the exact formation site is still under debate, the chemical relationship is well-established empirically.
+The Na-O pattern provides the best chemical evidence that their chemical enrichment history has been dominated by Type \textsc{ii} Supernova (SN) events and that those stars formed in a globular cluster-like environment.
+
+% The following text was placed before 'While the ...'
+%Originally this relationship was thought to arise from internal mixing along the giant branch.
 However, dwarf globular cluster stars were found to exhibit strong Na-enhancement and O-depletion, contrary to what would be expected if the Na-O anti-correlation was purely a result of internal mixing.
@@
 Several descriptions for an astrophysical site that would permit such nucleosynthetic processes have been hypothesized, including massive intermediate-mass Asymptotic Giant Branch (AGB) binary stars \citep{de_mink;et-al_2009} and fast-rotating massive stars \citep{decressin;et-al_2007}.
-While the exact formation site is still under debate, the chemical relationship is well-established empirically.
-The Na-O pattern provides the best chemical evidence that their chemical enrichment history has been dominated by Sn \textsc{ii} events and that those stars formed in a globular cluster-like environment.
 
@@
 HD 41667		& 06:05:03.7 & $-$32:59:36.8	& 2011-03-13	& 1.005	& \dots & \dots & \dots & 314.4	& \dots & 0.8 \\
+HD 44007		& 06:18:48.6 & $-$14:50:44.2 	& 2011-03-13	& 1.033	& \dots & \dots & \dots & --185.9	& 162.9 & 0.6 \\
+HD 136316		& 15:22:17.2 & $-$53:14:13.9	& 2011-03-14	& 1.118	& \dots & \dots & \dots & 61.0		& --37.6 & 0.4 \\
+HD 141531		& 15:49:16.9 & \phn\.09:36:42.5		& 2011-03-14	& 1.309	& \dots & \dots & 350	 & 17.7		& 2.8	& 0.1 \\
 HD 142948		& 16:00:01.6 & $-$53:51:04.1	& 2011-03-14	& 1.107	& \dots & \dots & \dots & 6.8		& \dots & 0.4 \\
@@
 
+%HD 136316 % F giant, -1.8, Gratton 2000+, has Na, O abundances
+%HD 141531 % F giant, -1.6, Gratton 2000+, has Na, O abundances
+%HD 44007 % G giant, -1.50, lots of references
+
+% Hd 141431		: -0.96, -1.03 +/- 0.78 (MEK)
+
 % V corrections (already applied the first number of each row)
@@
 The supplementary star, J2306265-085103, was observed by the RAVE survey but had a $S/N$ ratio too low for stellar parameters to be accurately determined.
-All program stars were observed in July 2011 in good seeing at low airmass (Table \ref{tab:observations}), and X additional standard stars were observed in March 2011.
+All program stars were observed in July 2011 in good seeing at low airmass (Table \ref{tab:observations}), and five additional standard stars were observed in March 2011.
 All observations were taken using a 1.0'' slit, providing a spectral resolution of $\mathcal{R} = 28,000$ in the blue arm and $\mathcal{R} = 22,000$ in the red arm.
 The total exposure times for our program stars varied to ensure a $S/N$ ratio in excess of 100\,pixel$^{-1}$ at 600\,nm.
-
-% what spectral resolution in the blue, what resolution in the red
 
@@
 Given the rest wavelength and an initial guess of the FWHM, a Gaussian profile is iteratively fitted to the absorption line.
-At the same time, the local continuum is found within 20\,\AA{} either side of the rest wavelength using a second-order polynomial.
+At the same time, the local continuum is found within 10\,\AA{} either side of the rest wavelength using a second-order polynomial.
 Measuring the local continuum ensures any errors in our initial normalisation or order-stitching do not propagate through to our equivalent width measurements.
@@
 \\
+
 \multicolumn{10}{c}{Program Stars} \\
@@
 
+%HD 136316 % F giant, -1.8, Gratton 2000+, has Na, O abundances [DONE]
+%HD 141531 % F giant, -1.6, Gratton 2000+, has Na, O abundances [DONE]
+%HD 44007 % G giant, -1.50, lots of references
+
 \subsection{Stellar Parameters}
@@
 The effective temperatures published for all of our stars in Table \ref{sec:stellar-parameters} have been derived spectroscopically.
-As a consistency check for our spectroscopic temperatures, we have estimated effective temperatures using infrared photometry from the 2MASS catalog and empirical $T_{\rm eff}$-colour relationships.
+As a consistency check for our spectroscopic temperatures, we have estimated effective temperatures using infrared photometry from the 2MASS catalog and empirical $T_{\rm eff}$-color relationships.
 The $J-K$ color has been employed for these calculations because it has the least dependence on metallicity.
@@
 
-Although all of our candidates are giant stars, two different $T_{\rm eff}$-colour relationships have been employed: the \citet{alonso;et-al_1999} calibration for giants, and the \citet{casagrande;et-al_2010} calibration for dwarfs and sub-giants.
+Although all of our candidates are giant stars, two different $T_{\rm eff}$-color relationships have been employed: the \citet{alonso;et-al_1999} calibration for giants, and the \citet{casagrande;et-al_2010} calibration for dwarfs and sub-giants.
 All photometrically-derived temperatures are listed in \ref{tab:photometric-temperatures}.
@@
 Our analysis of high-resolution spectra with high $S/N$ reveals a much broader metallicity distribution for the stream.
-With just five stars \--- if we assume all our candidates are members \--- we find the stream metallicity varies from $\mbox{[Fe/H]} = -0.65$ to --1.60\,dex.
+With just five stars we find the stream metallicity varies from $\mbox{[Fe/H]} = -0.65$ to --1.60\,dex.
 Although this is a small sample, we find the calculated median abundance and standard deviation to be $\mbox{[Fe/H]} = -1.26 \pm 0.32$\,dex.
@@
 	\includegraphics[width=\textwidth]{./figures/aquarius-vhel-feh.pdf}
-	\caption{Helocentric velocities and metallicities for Aquarius candidates in this sample.
+	\caption{Heliocentric velocities and metallicities for Aquarius candidates in this sample.
 The measurements found by \citet{williams;et-al_2011} (green squares) and \citet{wylie-de-boer;et-al_2012} (blue triangles) are shown, and stars are linked by dashed lines.
@@
 Stars originating in dwarf spheroidal galaxies and globular clusters have very different chemical enrichment environments.
-Consequently, they exhibit chemistry that reflects their nucleosynthetic antiquity.
+Consequently, both types of systems exhibit chemistry that reflects their nucleosynthetic antiquity.
 Dwarf spheroidal stars do not demonstrate enhanced sodium or nickel content with respect to iron, as there has been a relatively negligible linage of massive stars undergoing supernova.

### 2013-02-05 2012-aqs/figures/plot-na-o.py
Fixed scale

@@ -297,13 +297,18 @@ ax.scatter(caretta_O_Fe, caretta_Na_Fe, marker='+', edgecolor='#cccccc', facecol
 ax.scatter(O_Fe, Na_Fe, marker='o', facecolor='k', s=40)
 ax.errorbar(O_Fe, Na_Fe, xerr=e_O_Fe, yerr=e_Na_Fe, fmt=None, ecolor='k')
 
-ax.legend(loc=2, prop={'size': 11})
+#ax.legend(loc=2, prop={'size': 11})
 
 ax.set_xlabel('[O/Fe]')
 ax.set_ylabel('[Na/Fe]')
 
+
 ax.set_xlim(xlims)
+ax.set_xticks([-0.5, 0.0, 0.5])
+
 ax.set_ylim(ylims)
+ax.set_yticks([-0.5, 0.0, 0.5, 1.0])
+
 
 plt.savefig('aquarius-o-na-halo.pdf')
 plt.savefig('aquarius-o-na-halo.eps')

### 2013-02-05 2012-aqs/draft-aqs.tex
Added standard star chemisty and standard star observations

@@
 % - Ni/Na plane plot
-% - Add standard stars to observations table
-% - Add standard stars chemical abundances
+% [DONE] Add standard stars to observations table
+% [DONE] Add standard stars chemical abundances
 % - Add in-line text referencing standard star chemical abundances
-% - Uncertainties analysis
+% - Uncertainty analysis
 % [DONE] Equivalent widths significant figures.
@@
 % - Conclusions
-
-% Casey, Keller, Alves-Brito, Frebel, Da Costa, Schlaufman, Karakas, Jacobson, Yu, Freeman
-
-\author{Andrew R. Casey\altaffilmark{2,3} and distinguished collaborators}
+% - References
+
+\author{Andrew R.
+Casey\altaffilmark{2,3}, Stefan Keller\altaffilmark{2}, Alan Alves-Brito\altaffilmark{2}, Anna Frebel\altaffilmark{3}, Gary Da Costa\altaffilmark{2}, Kevin Schalufman\altaffilmark{3}, Heather Jacobson\altaffilmark{3}, QinQin Yu\altaffilmark{3}, Amanda Karakas\altaffilmark{2}, David Yong\altaffilmark{2}, Ken Freeman\altaffilmark{2}}
 \altaffiltext{1}{This paper includes data gathered with the 6.5 meter Magellan Telescopes located at Las Campanas Observatory, Chile.}
@@
 Enhanced [Na/Fe] and [Ni/Fe] abundance ratios suggest the co-moving group is not the result of a dwarf satellite galaxy, and that its chemical enrichment environment is more representative of either a globular cluster, or the Milky Way thick disc.
-However, we find no evidence that the stream is a result of a disrupted cluster.
+However, we find no evidence that the stream is a result of a classical disrupted globular cluster.
 Our data indicate the Aquarius stream has a  metallicity dispersion of $\sigma(\mbox{[Fe/H}]) = 0.32$\,dex.
 No inverse Na-O correlation is present, and we find a positive Mg-Al relationship.
-Chemically, the group is indistinguishable from the Milky Way thick disk with the exception of one very interesting candidate, which we hypothesise is tidal debris from $\omega$-Centurai.
+Chemically, the group is indistinguishable from the Milky Way thick disk/halo with the exception of one very interesting candidate, which we hypothesise is tidal debris from $\omega$-Centurai.
 Assuming all other candidates are Aquarius members, we propose the co-moving group has arisen from a minor merger in the Milky Way's thick disk.
@@
 
-\keywords{Galaxy: halo, structure --- Individual: Aquarius Stream --- Stars: FGK-giants}
+\keywords{Galaxy: halo, structure}
 
@@
 % Consider adding a final sentence about the amount of work that has gone into stellar streaams
-
 Wide-field surveys have proved excellent sources for finding stellar streams.
@@
 \\ \multicolumn{11}{c}{Standard Stars} \\ \hline \\
-HD 41667		& 06:05:03.7 & $-$32:59:36.8	& 2011-03-13	& 1.005	& \dots & \dots & \dots & 314.4	& \dots & 0.8 \\
-HD 44007		& 06:18:48.6 & $-$14:50:44.2 	& 2011-03-13	& 1.033	& \dots & \dots & \dots & --185.9	& 162.9 & 0.6 \\
-HD 136316		& 15:22:17.2 & $-$53:14:13.9	& 2011-03-14	& 1.118	& \dots & \dots & \dots & 61.0		& --37.6 & 0.4 \\
-HD 141531		& 15:49:16.9 & \phn\.09:36:42.5		& 2011-03-14	& 1.309	& \dots & \dots & 350	 & 17.7		& 2.8	& 0.1 \\
-HD 142948		& 16:00:01.6 & $-$53:51:04.1	& 2011-03-14	& 1.107	& \dots & \dots & \dots & 6.8		& \dots & 0.4 \\
+HD 41667		& 06:05:03.7 & $-$32:59:36.8		& 2011-03-13	& 1.005	& 1.0 & 90 		& 340 & 313.6		& 297.1 	& 0.1 \\
+HD 44007		& 06:18:48.6 & $-$14:50:44.2 		& 2011-03-13	& 1.033	& 1.0 & 120		& 280 & $-$187.0	& 161.8 	& 0.1 \\
+HD 76932		& 08:58:44.2 & $-$16:07:54.2		& 2011-03-14	& 1.158	& 1.0 & 25		& 330 & $-$132.6	& 117.8		& 0.1 \\
+HD 136316		& 15:22:17.2 & $-$53:14:13.9		& 2011-03-14	& 1.118	& 0.9 & \dots 	& 400 & 59.8		& $-$38.8 	& 0.1 \\
+HD 141531		& 15:49:16.9 & \phn\.09:36:42.5	& 2011-03-14	& 1.309	& 0.9 & \dots	& 350 & 17.7		& 2.8		& 0.1 \\
+HD 142948		& 16:00:01.6 & $-$53:51:04.1		& 2011-03-14	& 1.107	& 1.0 & \dots 	& 320 & 5.3			& 29.9 		& 0.1 \\
 
 \\ \multicolumn{11}{c}{Program Stars} \\ \hline \\
-C2225316-14437	& 22:25:31.7 & $-$14:54:39.6	& 2011-07-30	& 1.033 & \dots & \dots & 135	 & --168.6	& --156.4 & 0.1 \\
-C2306265-085103	& 23:06:26.6 & $-$08:51:04.8	& 2011-07-30	& 1.096 & \dots & \dots & 100	 & --240.4	& --221.1 & 0.1 \\
-J221821-183424	& 22:18:21.2 & $-$18:34:28.3	& 2011-07-30	& 1.026	& \dots & \dots & 115 	 & --170.2	& --159.5 & 0.1 \\
-J223504-152834	& 22:35:04.5 & $-$15:28:34.9	& 2011-07-30	& 1.047	& \dots & \dots & 135	 & --179.0	& --169.7 & 0.1 \\
-J223811-104126	& 22:38:11.6 & $-$10:41:29.4	& 2011-07-30	& 1.218	& \dots & \dots & 115	 & --250.1	& --235.7 & 0.1
+C2225316-14437	& 22:25:31.7 & $-$14:54:39.6	& 2011-07-30	& 1.033	& 0.8	& 650 & 135	& $-$168.6	& $-$156.4 & 0.1 \\
+C2306265-085103	& 23:06:26.6 & $-$08:51:04.8	& 2011-07-30	& 1.096	& 1.0	& 650 & 100	& $-$240.4	& $-$221.1 & 0.1 \\
+J221821-183424	& 22:18:21.2 & $-$18:34:28.3	& 2011-07-30	& 1.026	& 0.9 	& 650 & 115	& $-$170.2	& $-$159.5 & 0.1 \\
+J223504-152834	& 22:35:04.5 & $-$15:28:34.9	& 2011-07-30	& 1.047	& 1.0 	& 650 & 130	& $-$179.0	& $-$169.7 & 0.1 \\
+J223811-104126	& 22:38:11.6 & $-$10:41:29.4	& 2011-07-30	& 1.218	& 1.2 	& 650 & 115	& $-$250.1	& $-$235.7 & 0.1
 
@@
 
-% Hd 141431		: -0.96, -1.03 +/- 0.78 (MEK)
-
 % V corrections (already applied the first number of each row)
+% HD 41667		: -0.77, -0.79 +/- 0.79
+% HD 44007		: -1.12, -1.12 +/- 0.96
+% HD 136316		: -1.17, -1.25 +/- 0.86
+% HD 141531		: -0.96, -1.03 +/- 0.78
+% HD 142948		: -1.49, -1.49 +/- 0.75
 % J221821     	:   0.30, 0.25 +/- 1.25 (MEK has -154.1, wdb ) -- diff: 5.4  (positive == higher)
@@
 As expected, the mean residual offset is small ($-0.75$\,km s$^{-1}$), and the standard deviation is 0.79\,km s$^{-1}$ from 164 line measurements.
-This provides us with a final measured radial velocity of $313.7 \pm 0.1$\,km s$^{-1}$.
+This provides us with a final measured radial velocity of $313.6 \pm 0.1$\,km s$^{-1}$.
 This process was performed for all observations.
@@
 We scaled each stellar parameter between zero and unity prior to interpolation in order to minimise these effects.
-During this step, $\log{g}$, [M/H] and [$\alpha$/Fe] values were scaled such that we simultaneously interpolate linearly in $T_{\rm eff}$ and logarithmically in all other parameters.
+During this step, $\log{g}$, [M/H] and [$\alpha$/Fe] values were scaled such that we simultaneously interpolate linearly in $T_{\rm eff}$, $\log{g}$ and logarithmically in abundance ratios.
 
@@
 \cline{1-10} \\
-HD41667			& 4630	& 1.70	& 1.66 	& --1.21
-				& 4605	& 1.88	& 1.44	& --1.16
+HD 41667		& 4630	& 1.70	& 1.66 	& $-$1.21
+				& 4605	& 1.88	& 1.44	& $-$1.16
 				& \citet{gratton;et-al_2000} \\
-HD44007			& 4790	& 1.78	& 1.63	& --1.80
-				& 4850	& 2.00 	& 2.20	& --1.71
+HD 44007		& 4790	& 1.78	& 1.63	& $-$1.80
+				& 4850	& 2.00 	& 2.20	& $-$1.71
 				& \citet{fulbright_2000} \\
-HD142948		& 4950	& 2.19	& 1.78	& --0.79
-				& 4713 	& 2.17 	& 1.38	& --0.77
+
+HD 76932		& 5755 & 3.85 & 1.41 & $-$1.06
+				\\
+
+HD 136316		& 4350 & 0.65 & 1.83 & $-$1.92 \\
+
+HD 141531		& 4295 & 0.60 & 1.86 & $-$1.74 \\
+
+HD 142948		& 4950	& 2.19	& 1.78	& $-$0.79
+				& 4713 	& 2.17 	& 1.38	& $-$0.77
 				& \citet{gratton;et-al_2000} \\
@@
 \cline{1-10} \\
-C2225316-14437	& 4325				& 1.26				& 1.78				& --1.26	
-				& 4235 $\pm$ 118 	& 1.45 $\pm$ 0.21	& 1.96 $\pm$ 0.11 	& --1.20 $\pm$ 0.14 
+C2225316-14437	& 4325				& 1.26				& 1.78				& $-$1.26	
+				& 4235 $\pm$ 118 	& 1.45 $\pm$ 0.21	& 1.96 $\pm$ 0.11 	& $-$1.20 $\pm$ 0.14 
 				& \citet{wylie-de-boer;et-al_2012} \\
-C2306265-085103	& 4170	& 0.85	& 1.81 	& --1.17
+C2306265-085103	& 4170	& 0.85	& 1.81 	& $-$1.17
 				& \dots	& \dots	& \dots	& \dots
 				& \dots \\	
-J221821-183424	& 4590				& 0.90				& 1.91				& --1.61
-				& 4395 $\pm$ 205 	& 1.45 $\pm$ 0.35 	& 1.96 $\pm$ 0.18 	& --1.15 $\pm$ 0.21
+J221821-183424	& 4590				& 0.90				& 1.91				& $-$1.61
+				& 4395 $\pm$ 205 	& 1.45 $\pm$ 0.35 	& 1.96 $\pm$ 0.18 	& $-$1.15 $\pm$ 0.21
 				& \citet{wylie-de-boer;et-al_2012} \\
-J223504-152834	& 4590				& 2.15 				& 1.45				& --0.68
-				& 4597 $\pm$ 158 	& 2.40 $\pm$ 0.14 	& 1.47 $\pm$ 0.07 	& --0.98 $\pm$ 0.17
+J223504-152834	& 4590				& 2.15 				& 1.45				& $-$0.68
+				& 4597 $\pm$ 158 	& 2.40 $\pm$ 0.14 	& 1.47 $\pm$ 0.07 	& $-$0.98 $\pm$ 0.17
 				& \citet{wylie-de-boer;et-al_2012} \\
-J223811-104126	& 5140				& 2.96				& 1.33				& --1.45
-				& 5646 $\pm$ 147 	& 4.60 $\pm$ 0.15 	& 1.09 $\pm$ 0.11 	& --1.20 $\pm$ 0.20
+J223811-104126	& 5140				& 2.96				& 1.33				& $-$1.45
+				& 5646 $\pm$ 147 	& 4.60 $\pm$ 0.15 	& 1.09 $\pm$ 0.11 	& $-$1.20 $\pm$ 0.20
 				& \citet{wylie-de-boer;et-al_2012} 
@@
 At least in Al, Si, Cr and Ba content (see sections \ref{sec:aluminium-abundance}, \ref{sec:alpha-elements}, \ref{sec:iron-peak-elements}), C225316 appears to be chemically distinct from the other Aquarius stream stars in our sample.
+
+\begin{deluxetable*}{lccccccclcccccc}
+\tablecolumns{15}
+\tablecaption{Standard Star Abundances\label{tab:standard-star-abundances}}
+\tablehead{
+\colhead{Species} & $N$ & $\log\epsilon(X)$ & $\sigma_\epsilon$ & [X/H] & [X/Fe] & $\sigma$ &&
+\colhead{Species} & $N$ & $\log\epsilon(X)$ & $\sigma_\epsilon$ & [X/H] & [X/Fe] & $\sigma$ 
+}
+\startdata
+\\
+ \multicolumn{7}{c}{HD 41667} & \colhead{} & \multicolumn{7}{c}{HD 44007} \\
+ \cline{1-7} \cline{9-15} \\
+
+   O \textsc{i} &   2 &    7.93 &    0.05 & $-$0.76 &    0.45 &    0.04 &&
+   O \textsc{i} &   1 &    7.39 &    0.00 & $-$1.30 &    0.50 &    0.00 \\
+  Na \textsc{i} &   3 &    4.87 &    0.16 & $-$1.37 & $-$0.16 &    0.09 &&
+  Na \textsc{i} &   2 &    4.42 &    0.08 & $-$1.83 & $-$0.03 &    0.06 \\
+  Mg \textsc{i} &   4 &    6.74 &    0.11 & $-$0.86 &    0.35 &    0.05 &&
+  Mg \textsc{i} &   2 &    6.27 &    0.06 & $-$1.33 &    0.47 &    0.04 \\
+  Al \textsc{i} &   4 &    5.12 &    0.11 & $-$1.33 & $-$0.12 &    0.06 &&
+  Al \textsc{i} &   1 &    4.76 &    0.00 & $-$1.69 &    0.11 &    0.00 \\
+  Si \textsc{i} &   5 &    6.52 &    0.05 & $-$0.99 &    0.22 &    0.02 &&
+  Si \textsc{i} &   5 &    6.06 &    0.07 & $-$1.45 &    0.35 &    0.03 \\
+  Ca \textsc{i} &   4 &    5.46 &    0.06 & $-$0.88 &    0.33 &    0.03 &&
+  Ca \textsc{i} &   4 &    4.92 &    0.02 & $-$1.42 &    0.38 &    0.01 \\
+ Sc \textsc{ii} &   6 &    2.12 &    0.13 & $-$1.03 &    0.18 &    0.05 &&
+ Sc \textsc{ii} &   6 &    1.38 &    0.10 & $-$1.77 &    0.02 &    0.04 \\
+  Ti \textsc{i} &   4 &    3.96 &    0.04 & $-$1.00 &    0.21 &    0.02 &&
+  Ti \textsc{i} &   1 &    3.46 &    0.00 & $-$1.49 &    0.31 &    0.00 \\
+ Ti \textsc{ii} &   3 &    4.12 &    0.25 & $-$0.83 &    0.38 &    0.14 &&
+ Ti \textsc{ii} &   4 &    3.52 &    0.15 & $-$1.43 &    0.37 &    0.07 \\
+   V \textsc{i} &   6 &    2.88 &    0.13 & $-$1.05 &    0.16 &    0.05 &&
+   V \textsc{i} &   4 &    2.16 &    0.03 & $-$1.77 &    0.03 &    0.01 \\
+  Cr \textsc{i} &  10 &    4.25 &    0.09 & $-$1.38 & $-$0.17 &    0.03 &&
+  Cr \textsc{i} &  15 &    3.64 &    0.07 & $-$2.00 & $-$0.20 &    0.02 \\
+ Cr \textsc{ii} &   3 &    4.54 &    0.25 & $-$1.10 &    0.11 &    0.14 &&
+ Cr \textsc{ii} &   3 &    3.97 &    0.02 & $-$1.67 &    0.13 &    0.01 \\
+  Mn \textsc{i} &   3 &    3.94 &    0.01 & $-$1.49 & $-$0.28 &    0.01 &&
+  Mn \textsc{i} &   3 &    3.11 &    0.04 & $-$2.32 & $-$0.52 &    0.02 \\
+  Fe \textsc{i} &  61 &    6.29 &    0.12 & $-$1.21 &    0.00 &    0.01 &&
+  Fe \textsc{i} &  51 &    5.70 &    0.13 & $-$1.80 &    0.00 &    0.02 \\
+ Fe \textsc{ii} &  13 &    6.28 &    0.06 & $-$1.22 & $-$0.01 &    0.02 &&
+ Fe \textsc{ii} &  15 &    5.70 &    0.10 & $-$1.80 &    0.00 &    0.02 \\
+  Co \textsc{i} &   3 &    3.75 &    0.11 & $-$1.24 & $-$0.03 &    0.06 &&
+  Co \textsc{i} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
+  Ni \textsc{i} &   7 &    4.95 &    0.12 & $-$1.27 & $-$0.06 &    0.04 &&
+  Ni \textsc{i} &   4 &    4.43 &    0.04 & $-$1.79 &    0.01 &    0.02 \\
+  Cu \textsc{i} &   1 &    2.76 &    0.00 & $-$1.43 & $-$0.22 &    0.00 &&
+  Cu \textsc{i} &   1 &    1.84 &    0.00 & $-$2.35 & $-$0.55 &    0.00 \\
+  Zn \textsc{i} &   2 &    3.33 &    0.08 & $-$1.22 & $-$0.01 &    0.06 &&
+  Zn \textsc{i} &   2 &    2.83 &    0.05 & $-$1.73 &    0.07 &    0.04 \\
+ Ba \textsc{ii} &   2 &    1.08 &    0.05 & $-$1.10 &    0.10 &    0.03 &&
+ Ba \textsc{ii} &   2 &    0.33 &    0.05 & $-$1.85 & $-$0.05 &    0.04 \\
+
+\cline{1-7} \cline{9-15} \\
+\\
+\multicolumn{7}{c}{HD 76932} && \multicolumn{7}{c}{HD 136316} \\
+\cline{1-7} \cline{9-15} \\
+
+   O \textsc{i} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata &&
+   O \textsc{i} &   1 &    7.20 &    0.00 & $-$1.49 &    0.43 &    0.00 \\
+  Na \textsc{i} &   3 &    5.33 &    0.04 & $-$0.91 &    0.15 &    0.02 &&
+  Na \textsc{i} &   2 &    4.15 &    0.03 & $-$2.09 & $-$0.17 &    0.02 \\
+  Mg \textsc{i} &   3 &    7.05 &    0.20 & $-$0.55 &    0.51 &    0.12 &&
+  Mg \textsc{i} &   2 &    6.05 &    0.25 & $-$1.54 &    0.38 &    0.17 \\
+  Al \textsc{i} &   4 &    5.44 &    0.06 & $-$1.01 &    0.04 &    0.03 &&
+  Al \textsc{i} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
+  Si \textsc{i} &   5 &    6.74 &    0.05 & $-$0.77 &    0.29 &    0.02 &&
+  Si \textsc{i} &   4 &    5.86 &    0.05 & $-$1.65 &    0.27 &    0.03 \\
+  Ca \textsc{i} &   4 &    5.57 &    0.02 & $-$0.77 &    0.29 &    0.01 &&
+  Ca \textsc{i} &   4 &    4.69 &    0.02 & $-$1.65 &    0.27 &    0.01 \\
+  Sc \textsc{i} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata &&
+  Sc \textsc{i} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
+ Sc \textsc{ii} &   6 &    2.23 &    0.11 & $-$0.92 &    0.14 &    0.04 &&
+ Sc \textsc{ii} &   5 &    1.32 &    0.05 & $-$1.83 &    0.09 &    0.02 \\
+  Ti \textsc{i} &   1 &    4.35 &    0.00 & $-$0.60 &    0.46 &    0.00 &&
+  Ti \textsc{i} &   3 &    3.23 &    0.03 & $-$1.72 &    0.20 &    0.02 \\
+ Ti \textsc{ii} &   3 &    4.34 &    0.03 & $-$0.61 &    0.45 &    0.02 &&
+ Ti \textsc{ii} &   4 &    3.52 &    0.14 & $-$1.43 &    0.49 &    0.07 \\
+   V \textsc{i} &   3 &    3.15 &    0.13 & $-$0.78 &    0.28 &    0.08 &&
+   V \textsc{i} &   5 &    1.88 &    0.06 & $-$2.05 & $-$0.13 &    0.03 \\
+  Cr \textsc{i} &  15 &    4.44 &    0.06 & $-$1.20 & $-$0.14 &    0.01 &&
+  Cr \textsc{i} &  12 &    3.52 &    0.05 & $-$2.12 & $-$0.20 &    0.02 \\
+ Cr \textsc{ii} &   3 &    4.75 &    0.03 & $-$0.89 &    0.17 &    0.02 &&
+ Cr \textsc{ii} &   2 &    3.83 &    0.01 & $-$1.81 &    0.11 &    0.00 \\
+  Mn \textsc{i} &   3 &    4.06 &    0.03 & $-$1.37 & $-$0.31 &    0.02 &&
+  Mn \textsc{i} &   3 &    3.09 &    0.02 & $-$2.34 & $-$0.42 &    0.01 \\
+  Fe \textsc{i} &  51 &    6.44 &    0.10 & $-$1.06 &    0.00 &    0.01 &&
+  Fe \textsc{i} &  62 &    5.58 &    0.11 & $-$1.92 &    0.00 &    0.01 \\
+ Fe \textsc{ii} &  13 &    6.45 &    0.07 & $-$1.05 &    0.01 &    0.02 &&
+ Fe \textsc{ii} &  14 &    5.58 &    0.12 & $-$1.92 &    0.00 &    0.03 \\
+  Co \textsc{i} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata &&
+  Co \textsc{i} &   3 &    3.15 &    0.06 & $-$1.84 &    0.08 &    0.03 \\
+  Ni \textsc{i} &   5 &    5.27 &    0.02 & $-$0.95 &    0.11 &    0.01 &&
+  Ni \textsc{i} &   5 &    4.23 &    0.10 & $-$1.99 & $-$0.07 &    0.04 \\
+  Cu \textsc{i} &   1 &    2.84 &    0.00 & $-$1.35 & $-$0.29 &    0.00 &&
+  Cu \textsc{i} &   1 &    1.75 &    0.00 & $-$2.44 & $-$0.52 &    0.00 \\
+  Zn \textsc{i} &   2 &    3.58 &    0.04 & $-$0.97 &    0.08 &    0.02 &&
+  Zn \textsc{i} &   2 &    2.69 &    0.04 & $-$1.87 &    0.05 &    0.02 \\
+ Ba \textsc{ii} &   1 &    1.16 &    0.00 & $-$1.02 &    0.04 &    0.00 &&
+ Ba \textsc{ii} &   1 &    0.29 &    0.00 & $-$1.89 &    0.03 &    0.00 \\
+
+\cline{1-7} \cline{9-15} \\
+\\
+\multicolumn{7}{c}{HD 141531} && \multicolumn{7}{c}{HD 142948} \\
+\cline{1-7} \cline{9-15} \\
+
+   O \textsc{i} &   2 &    7.29 &    0.01 & $-$1.40 &    0.35 &    0.01 &&
+   O \textsc{i} &   2 &    8.39 &    0.03 & $-$0.29 &    0.49 &    0.02 \\
+  Na \textsc{i} &   2 &    4.23 &    0.05 & $-$2.01 & $-$0.26 &    0.04 &&
+  Na \textsc{i} &   3 &    5.62 &    0.13 & $-$0.62 &    0.16 &    0.07 \\
+  Mg \textsc{i} &   2 &    6.25 &    0.14 & $-$1.35 &    0.40 &    0.10 &&
+  Mg \textsc{i} &   3 &    7.27 &    0.12 & $-$0.33 &    0.45 &    0.07 \\
+  Al \textsc{i} &   2 &    4.69 &    0.10 & $-$1.76 & $-$0.02 &    0.07 &&
+  Al \textsc{i} &   4 &    5.88 &    0.08 & $-$0.58 &    0.21 &    0.04 \\
+  Si \textsc{i} &   5 &    5.98 &    0.10 & $-$1.53 &    0.22 &    0.04 &&
+  Si \textsc{i} &   5 &    7.02 &    0.05 & $-$0.49 &    0.29 &    0.02 \\
+  Ca \textsc{i} &   4 &    4.84 &    0.02 & $-$1.50 &    0.25 &    0.01 &&
+  Ca \textsc{i} &   4 &    5.75 &    0.01 & $-$0.59 &    0.19 &    0.01 \\
+ Sc \textsc{ii} &   4 &    1.50 &    0.04 & $-$1.65 &    0.10 &    0.02 &&
+ Sc \textsc{ii} &   6 &    2.59 &    0.11 & $-$0.56 &    0.22 &    0.04 \\
+  Ti \textsc{i} &   4 &    3.30 &    0.07 & $-$1.65 &    0.10 &    0.03 &&
+  Ti \textsc{i} &   4 &    4.42 &    0.09 & $-$0.53 &    0.25 &    0.04 \\
+ Ti \textsc{ii} &   4 &    3.69 &    0.08 & $-$1.27 &    0.48 &    0.04 &&
+ Ti \textsc{ii} &   3 &    4.40 &    0.21 & $-$0.55 &    0.23 &    0.12 \\
+   V \textsc{i} &   5 &    2.06 &    0.08 & $-$1.87 & $-$0.12 &    0.04 &&
+   V \textsc{i} &   5 &    3.26 &    0.11 & $-$0.67 &    0.11 &    0.05 \\
+  Cr \textsc{i} &  12 &    3.66 &    0.07 & $-$1.98 & $-$0.23 &    0.02 &&
+  Cr \textsc{i} &  13 &    4.69 &    0.15 & $-$0.95 & $-$0.17 &    0.04 \\
+ Cr \textsc{ii} &   2 &    4.00 &    0.01 & $-$1.63 &    0.11 &    0.01 &&
+ Cr \textsc{ii} &   3 &    4.85 &    0.03 & $-$0.79 & $-$0.01 &    0.02 \\
+  Mn \textsc{i} &   3 &    3.21 &    0.04 & $-$2.22 & $-$0.47 &    0.02 &&
+  Mn \textsc{i} &   3 &    4.50 &    0.03 & $-$0.93 & $-$0.15 &    0.02 \\
+  Fe \textsc{i} &  54 &    5.75 &    0.06 & $-$1.75 &    0.00 &    0.01 &&
+  Fe \textsc{i} &  61 &    6.72 &    0.10 & $-$0.78 &    0.00 &    0.01 \\
+ Fe \textsc{ii} &  13 &    5.78 &    0.04 & $-$1.72 &    0.03 &    0.01 &&
+ Fe \textsc{ii} &  13 &    6.69 &    0.06 & $-$0.81 & $-$0.03 &    0.02 \\
+  Co \textsc{i} &   3 &    3.26 &    0.07 & $-$1.73 &    0.01 &    0.04 &&
+  Co \textsc{i} &   3 &    4.44 &    0.09 & $-$0.55 &    0.23 &    0.05 \\
+  Ni \textsc{i} &   7 &    4.43 &    0.12 & $-$1.79 & $-$0.04 &    0.05 &&
+  Ni \textsc{i} &   5 &    5.61 &    0.05 & $-$0.61 &    0.17 &    0.02 \\
+  Cu \textsc{i} &   1 &    1.99 &    0.00 & $-$2.20 & $-$0.46 &    0.00 &&
+  Cu \textsc{i} &   1 &    3.58 &    0.00 & $-$0.61 &    0.17 &    0.00 \\
+  Zn \textsc{i} &   2 &    2.73 &    0.04 & $-$1.83 & $-$0.08 &    0.03 &&
+  Zn \textsc{i} &   2 &    3.91 &    0.05 & $-$0.65 &    0.13 &    0.04 \\
+ Ba \textsc{ii} &   1 &    0.43 &    0.00 & $-$1.75 & $-$0.01 &    0.00 &&
+ Ba \textsc{ii} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata
+
+\enddata
+\end{deluxetable*}
 
@@
 This research has four stars in common with the \citet{wylie-de-boer;et-al_2012} study, but sodium and oxygen measurements exist for only three stars intersecting both samples, as the data quality for J223811-104126 in the \citet{wylie-de-boer;et-al_2012} study prohibited measuring oxygen.
-We have measurements for all of our stars, including J223811-104126, for which we ascertained an upper limit from the [O \textsc{i}] lines of [O/Fe] $< 0.5$ dex, and a corrected abundance of $\mbox{[O/Fe]} = 0.14 \pm 0.08$ from the O \textsc{i} triplet lines.
+We have measurements for all of our stars, including J223811-104126, for which we ascertained an upper limit from the [O \textsc{i}] lines of [O/Fe] $< 0.5$ dex, and an inferred abundance of $\mbox{[O/Fe]} = 0.14 \pm 0.08$ from the O \textsc{i} triplet lines.
 In Figure \ref{fig:o-na} we have plotted theses abundances, including the corrected value for J223811-104126 rather than an upper limit.
@@
 Given the extended star formation within the Milky Way disk, globular cluster stars and disk stars are indiscernible in the Na/Ni plane: they both show an extended contribution of massive stars.
-
 The most that can be inferred from the Na, Ni abundances of Aquarius stream stars is that their enrichment environment is less like a dSph galaxy, and more representative of a globular cluster, or the disc of the Milky Way.
@@
 In their original discovery paper, \citet{williams;et-al_2011} attempted to exclude possible known progenitors.
-On the basis of metallicity, distance, proper motions\footnote{We find the proper motions in Table 1 of \citet{williams;et-al_2011} to be mis-associated to incorrect stars.
+On the basis of metallicity, distance, proper motions\footnote{The proper motions in Table 1 of \citet{williams;et-al_2011} are mis-associated to incorrect stars.
 However, this error was typographical; it did not affect the transverse velocity calculations (Williams, M.E.K, private communication).}, transverse velocities and orbital energies, the authors were able to exclude all known Milky Way satellites, with the notable exception of $\omega$-Centurai.
@@
 
+\acknowledgements
+A.R.C.
+acknowledges the financial support through the Australian Research Council Laureate Fellowship 0992131, and from the Australian Prime Minister's Endeavour Award Research Fellowship, which has facilitated his research at MIT.
+This publication makes use of data products from the Two Micron All Sky Survey, which is a joint project of the University of Massachusetts and the Infrared Processing and Analysis Center/California Institute of Technology, funded by the National Aeronautics and Space Administration and the National Science Foundation.
+
 %\facilities{Magellan:Clay}

### 2013-02-27 thesis/abstract.tex
Added thesis as of 27 Feb

\section*{Abstract}
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Donec ac neque metus. Quisque a elit non justo pharetra lacinia at in dolor. Phasellus mauris mauris, sagittis id dapibus ac, facilisis vitae erat. Sed non urna mauris, nec rutrum nunc. Phasellus luctus metus nec diam hendrerit facilisis. Nulla metus ipsum, cursus in rutrum vel, rutrum ac risus. Vivamus feugiat bibendum lorem, quis iaculis nisi pellentesque at. Pellentesque fermentum tellus id lacus pharetra bibendum. Vestibulum luctus, lorem eget facilisis adipiscing, purus arcu fringilla diam, vel commodo lectus tellus non urna. Nulla elit nibh, sagittis at egestas ac, semper a elit. Nam sed dapibus sem. Mauris aliquam nulla quis arcu tincidunt auctor.

Mauris iaculis consequat porta. Quisque augue purus, auctor nec dapibus et, sodales quis nulla. Donec ipsum urna, mattis vitae consequat sed, pharetra ac dolor. Morbi placerat turpis quis eros gravida sed cursus orci posuere. Suspendisse eu malesuada arcu. Quisque turpis ante, vulputate in blandit non, molestie non leo. Quisque id erat id libero cursus pellentesque vitae a lacus. Nullam arcu ligula, sagittis id adipiscing bibendum.

Curabitur mattis consequat rutrum. Fusce vel risus non ipsum ullamcorper condimentum in a turpis. Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos himenaeos. Aenean sit amet odio nec augue ultricies dignissim tincidunt vel orci. Ut posuere lacinia tortor, vitae semper felis malesuada sit amet. In hac habitasse platea dictumst. Morbi vitae massa in turpis tincidunt gravida.

Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus. Donec sodales ante eros. Suspendisse malesuada feugiat lacus vitae tincidunt. Proin eleifend arcu eget eros posuere vitae suscipit mi fringilla. Ut varius, purus id dapibus fermentum, ipsum ipsum euismod orci, vitae imperdiet nulla ligula in felis. In odio metus, ultricies sit amet sollicitudin sit amet, tempus in tortor. Nam sed turpis nulla. Fusce augue lectus, iaculis a hendrerit at, semper quis lacus. Nulla vestibulum justo nisi. Fusce egestas laoreet diam, convallis interdum elit fermentum eget. Sed ac mauris in odio dictum scelerisque.

Morbi nibh dui, adipiscing ac laoreet ac, vulputate sed metus. Sed lobortis est non lacus pellentesque a elementum tellus blandit. Ut porta, enim a ultricies mollis, arcu eros scelerisque nunc, lobortis facilisis orci ante in ipsum. Ut varius, quam eu vehicula euismod, diam leo mattis elit, ut vestibulum massa arcu a nunc. Suspendisse eleifend quam ac orci tincidunt congue. Praesent sit amet luctus lectus. Etiam interdum euismod sapien, dictum commodo nunc dictum vitae. Etiam quis sapien a felis congue ornare. Sed vel tristique tellus. In hac habitasse platea dictumst. Morbi mollis erat vel magna blandit faucibus. Duis mollis vestibulum sapien auctor mollis. Proin diam lacus, vulputate at feugiat pulvinar, mollis nec ipsum. Fusce orci enim, sollicitudin vel congue eu, tristique in diam. Pellentesque diam tellus, varius sed faucibus in, tincidunt at quam.

Aliquam erat volutpat. Curabitur rhoncus vestibulum lacinia. Sed in sollicitudin lacus. Curabitur non sem nunc. Sed nec metus a orci fermentum suscipit eu in ipsum. Sed ac arcu sed ipsum consequat sodales. Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas.

### 2013-02-27 thesis/acknowledgments.tex
Added thesis as of 27 Feb

\section*{Acknowledgments}

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Phasellus imperdiet volutpat turpis, vel aliquet elit tincidunt eu. Praesent convallis dolor ut tortor consectetur tincidunt. Nam ac molestie velit. Morbi luctus scelerisque purus id luctus. Fusce mattis risus eu sapien imperdiet tincidunt. Praesent laoreet blandit scelerisque. Suspendisse nec lorem velit. Nam scelerisque laoreet elementum. Sed justo urna, dapibus at varius eu, suscipit quis nibh. Integer lacinia, est sit amet accumsan luctus, nisl quam consectetur turpis, non tincidunt est ligula id sapien. Donec orci dui, convallis ac feugiat et, facilisis et velit. Donec ipsum ante, lobortis vitae auctor ac, sollicitudin a nisl. Aliquam leo leo, rhoncus ut sollicitudin et, euismod id ipsum. In in risus urna. Sed et nulla nibh, sed faucibus sem.

Maecenas est arcu, scelerisque a dapibus quis, molestie a mauris. Vestibulum egestas purus eget eros mollis placerat. Nulla porttitor, justo nec tincidunt hendrerit, nulla massa adipiscing ligula, feugiat tristique dui libero eget dolor. Phasellus id arcu id nisi faucibus eleifend vel a lacus. Vestibulum at elit eu neque vehicula elementum. Mauris bibendum massa nec urna rhoncus tempor. Curabitur in libero vitae quam vestibulum facilisis quis vitae velit. Donec tincidunt, lacus eget elementum sollicitudin, urna urna consequat ipsum, id eleifend eros augue at dolor. Praesent pellentesque, ante quis malesuada molestie, tortor lorem eleifend ante, sed rutrum massa dolor in lorem. Donec tempus, tellus eu fermentum ornare, sapien tortor tristique eros, quis blandit erat tortor eu lorem. Donec id tempus lectus. Donec ac odio eu elit molestie iaculis ac sed enim. Suspendisse et purus sem, convallis luctus mauris.

Duis massa mauris, sagittis vel dignissim non, rutrum ac nisi. Fusce ultricies mollis leo sit amet sagittis. Quisque lacinia placerat blandit. Vivamus est magna, tristique sed adipiscing in, sagittis sit amet dolor. Maecenas et nunc ipsum, in rutrum diam. Etiam ac nisl erat. Integer ac mi velit, in aliquam lacus. Etiam vitae nisi elit. Nam quam nisi, elementum eu porta eu, scelerisque vitae tortor. Nulla vel dolor magna. Aliquam suscipit, diam ac interdum pellentesque, tellus turpis sollicitudin nunc, vulputate congue massa massa vel urna. Sed a augue vel quam sollicitudin mollis.

Maecenas in lectus leo. Ut posuere lacus eget massa varius sit amet consectetur risus facilisis. Donec laoreet ornare pharetra. Maecenas vestibulum, lorem et suscipit vestibulum, enim lorem egestas eros, vitae vehicula orci sem sed dolor. Maecenas sit amet nibh nec lorem gravida hendrerit. Nulla tempus dui a lectus ornare vel viverra ipsum iaculis. Vestibulum ante ipsum primis in faucibus orci luctus et ultrices posuere cubilia Curae; Aliquam erat volutpat. In hac habitasse platea dictumst. Aenean dictum quam quis nunc tristique vitae blandit mauris dapibus. Sed velit tellus, adipiscing vitae commodo sit amet, lobortis eu orci. Morbi auctor mi eget sapien aliquet vel iaculis odio feugiat. Fusce semper risus suscipit ligula malesuada quis pretium diam rutrum. Donec varius nisi sit amet arcu interdum eu venenatis metus faucibus.

### 2013-02-27 thesis/appendices/appendices.tex
Added thesis as of 27 Feb

\chapter{An image of a kitten}

A kitten is a juvenile domesticated cat. A feline litter usually consists of two to five kittens. To survive, kittens need the care of their mother for the first several weeks of their life. Kittens are highly social animals and spend most of their waking hours playing and interacting with available companions. The word \emph{``kitten''} derives from Middle English \emph{kitoun} (ketoun, kyton etc.), which itself came from Old French \emph{chitoun}. The young of big cats are called cubs rather than kittens. Either term may be used for the young of smaller wild felids such as ocelots, caracals, and lynx, but \emph{kitten} is usually more common for these species.

\begin{figure}[b!] 
   \centering
   \includegraphics[width=0.9\textwidth]{kitten.jpg} 
   \caption{The aforementioned kitten}
   \label{fig:kitten}
\end{figure}

\chapter{Lots of awful mathematics}
\input{epicyclic}

### 2013-02-27 thesis/appendices/epicyclic.tex
Added thesis as of 27 Feb

\vspace{-1cm}\emph{\small We follow the standard derivation of \citet{Murphy12b}. This differs from that used by \cite{Murphy12}, who follow \citet{Murphy11} in using Lindblad's original approach. \citet{Murphy10} derive the approximation in heliocentric coordinates in terms of the initial $XYZ$ position and $UVW$ velocity of the test particle. The two derivations are equivalent, as are the standard angular frequencies $\Omega$, $\kappa$ and $\nu$.}\\

We first assume a gravitational potential for the Galactic disk $\Phi$ that is axisymmetric around the normal to the disk. We also assume that such a potential is symmetric about the disk plane. In cylindrical $(R,\phi,z)$ coordinates the equations of motion for such a potential are:
\begin{align}\label{eqn:eom}
\begin{split}
\ddot{R}-R\dot{\phi}^2& = -\frac{\partial \Phi}{\partial R} \\
\frac{d}{dt}(R^{2}\dot{\phi})& = 0 \\
\ddot{z}&=-\frac{\partial\Phi}{\partial z}
\end{split}
\end{align}
Noting that the second equation implies the conservation of angular momentum about the $z$ axis; $R^{2}\dot{\phi}=\textrm{constant} = L_{z}$, the equations of motion can also be written
\begin{align}\label{eqn:eqnmotion}
\begin{split}
\ddot{R} = -\frac{\partial \Phi_{\rm eff}}{\partial R} \quad\textrm{and}\quad \ddot{z} = -\frac{\partial \Phi_{\rm eff}}{\partial z} 
\end{split}
\end{align}
where the effective potential $\Phi_{\rm eff}(R,z)$ is defined as
\begin{align}
\Phi_{\rm eff}(R,z) = \Phi(R,z) + \frac{L_{z}^{2}}{2R^{2}}
\end{align}
The effective potential has a minimum at $z=0$ (by symmetry) and at $R=R_{g}$:
\begin{align}
\frac{\partial \Phi_{\rm eff}}{\partial R} = \frac{\partial \Phi}{\partial R} - \frac{L_{z}^{2}}{R^{3}} = 0 \quad\textrm{which means}\quad \frac{\partial \Phi}{\partial R}\bigg|_{(R_{g},0)} = \frac{L_{z}^{2}}{R_{g}^{3}} = R_{g}\dot{\phi}^{2}
\end{align}
The \emph{guiding centre} radius $R_{g}$ therefore corresponds to a circular orbit with constant angular speed $\dot{\phi}=\Omega_{g}=\sqrt{(1/R)\partial \Phi/\partial R}=L_{z}/R_{g}^{2}$. We can approximate the effective potential around $(R,z)=(R_{g},0)$ by the second-order Taylor expansion around this point. If we define $x=(R-R_{g})$ the expansion is:
\begin{align}
\begin{split}
\Phi_{\rm eff} &\simeq \Phi_{\rm eff}(R_{g},0) + x\frac{\partial\Phi_{\rm eff}}{\partial R}\bigg|_{(R_{g},0)} + z\frac{\partial\Phi_{\rm eff}}{\partial z}\bigg|_{(R_{g},0)}\\
&+ \frac{1}{2}x^{2}\frac{\partial^{2}\Phi_{\rm eff}}{\partial R^{2}}\bigg|_{(R_{g},0)} + \frac{1}{2}z^{2}\frac{\partial^{2}\Phi_{\rm eff}}{\partial z^{2}}\bigg|_{(R_{g},0)} + xz\frac{\partial^{2}\Phi_{\rm eff}}{\partial R\partial z}\bigg|_{(R_{g},0)} 
\end{split}
\end{align}
The second and third terms are zero at the point $(R_{g},0)$. The cross-term is also zero as we assume the potential is symmetric about $z=0$. The effective potential then becomes
\begin{align}
\begin{split}
\Phi_{\rm eff} &\simeq \Phi_{\rm eff}(R_{g},0) + \frac{1}{2}x^{2}\frac{\partial^{2}\Phi_{\rm eff}}{\partial R^{2}}\bigg|_{(R_{g},0)} + \frac{1}{2}z^{2}\frac{\partial^{2}\Phi_{\rm eff}}{\partial z^{2}}\bigg|_{(R_{g},0)}\\
&= \Phi_{\rm eff}(R_{g},0) + \frac{1}{2}(\kappa x)^{2} + \frac{1}{2}(\nu z)^{2}
\end{split}
\end{align}
where we define the constants:
\begin{align} 
\kappa^{2} = \frac{\partial^{2} \Phi_{\rm eff}}{\partial R^2}\bigg|_{(R_{g},0)} \quad\textrm{and}\quad \nu^{2} = \frac{\partial^{2} \Phi_{\rm eff}}{\partial z^2}\bigg|_{(R_{g},0)}
\end{align}
In this second-order Taylor expansion of the effective potential the equations of motion (Eqn. \ref{eqn:eqnmotion}) simplify to those of harmonic oscillators:
\begin{align}\label{eqn:harmonic}
\ddot{x} = -\kappa^{2} x \quad\textrm{and}\quad \ddot{z} = -\nu^{2} z
\end{align}
which have the general solutions:
\begin{align}\label{eqn:xz}
x(t) = X\cos(\kappa t + \alpha)\quad \textrm{and}\quad z(t) = Z\cos(\nu t + \beta)
\end{align}
for constants $X,Z,\alpha$ and $\beta$. What about the azimuthal coordinate $\phi$? Realising that angular momentum is conserved and $\dot{\phi}=L_{z}/R^{2}$ and $\Omega_{g}=L_{z}/R_{g}^{2}$, we have
\begin{align}
\dot{\phi} = \frac{L_{z}}{R_{g}^{2}}\frac{1}{(x/R_{g}+1)^{2}} \simeq \Omega_{g}\bigg(1-2\frac{x}{R_{g}}\bigg)
\end{align}
Substituting for $x(t)$ and integrating we arrive at
\begin{align}
\phi = \Omega_{g} t -2\frac{\Omega_{g}}{R_{g}\kappa}X\sin(\kappa t + \alpha) + \phi_{0}
\end{align}
If we convert the cylindrical $(R,\phi,z)$ coordinate system to a Cartesian system $(x,y,z)$, comoving with the guiding centre $(R_{g},\phi$); for $X \ll R_{g}$ this simplifies to:
\begin{align}
\begin{split}\label{eqn:y}
y(t) &= -2\frac{\Omega_{g}}{\kappa} X\sin(\kappa t + \alpha) \\
&= -Y\sin(\kappa t + \alpha)
\end{split}
\end{align}
In the new coordinate system $x$ and $z$ are the same as above and $y$ points in the direction of Galactic rotation. In this frame the star can  be thought of as simultaneously oscillating around the guiding centre vertically and in an ellipse in the $xy$ plane (the epicycle). The motion can be described by three angular frequencies; the epicyclic frequency $\kappa$, the vertical frequency $\nu$ and the angular velocity of the guiding centre, $\Omega_{g}$.  The vertical motion is independent of the epicyclic motion. The size of the epicycle is dictated by the ratio of $\kappa$ to $\Omega_{g}$: $X/Y = \kappa/2\Omega_{g}$.  The resultant orbital motion following Equations~\ref{eqn:xz} and \ref{eqn:y} in a Galactocentric inertial frame is traced in Figure~\ref{fig:orbit}. Like in the general case, although close to circular, the orbit is not closed in such a frame.

\begin{figure}[p!] 
\vspace{-2mm}
   \centering
   \includegraphics[width=0.68\textwidth]{orbit_xy}\\ 
   \includegraphics[width=0.68\textwidth]{orbit_xz}\\
   \includegraphics[width=0.68\textwidth]{orbit_xyz} 
   \caption[Orbital motion in the epicyclic approximation]{Orbital motion  with $\kappa_{0}=0.0367$~\kms~pc$^{-1}$ , $\Omega_{0}=0.0272$~\kms~pc$^{-1}$, $R_{g}=R_{\odot}=8000$~pc and $X=Z=200$~pc. The coordinate system has its origin at the Galactic centre.}
   \label{fig:orbit}
\end{figure}

### 2013-02-27 thesis/chapter1/chapter1.tex
Added thesis as of 27 Feb

--- 2012-05-28 2011-sgr/AJ-version/sgr_vod_revised_2011.tex
@@
-\documentclass[preprint2]{aastex}
+\chapter{The Kinematics \& Chemistry of Halo Substructures in the Vicinity of the Virgo Over-Density}
 
-\shorttitle{Kinematics \& Chemistry of Halo Substructures: The Vicinity of the VOD}
-\shortauthors{Casey, Keller \& Da Costa}
+% you can put a brief note at the top of your chapters using '\previouslypublished{}'.
+For example, to give a reference to the paper this chapter is based on, or to point out that it has been submitted to a journal.
 
-\begin{document}
-
-\title{Kinematics \& Chemistry of Halo Substructures: The Vicinity of the Virgo Over-Density}
-
-\author{Andrew R. Casey, Stefan C. Keller and Gary Da Costa}
-\affil{Research School of Astronomy \& Astrophysics,
-	Australian National University, Mount Stromlo Observatory, via Cotter Rd, Weston, ACT 2611, Australia}
-
-\begin{abstract}
-We present observations obtained with the AAT's 2dF wide field spectrograph AAOmega of K-type stars located within a region of the sky which contains the Virgo Over-Density and the leading arm of the Sagittarius Stream.
-On the basis of the resulting velocity histogram we isolate halo substructures in these overlapping regions including Sagittarius and previously discovered Virgo groups.
-Through comparisons with \textit{N}-body models of the Galaxy-Sagittarius interaction, we find a tri-axial dark matter halo is favoured and we exclude a prolate shape.
-This result is contradictory with other observations along the Sagittarius leading arm, which typically favour prolate models.
-We have also uncovered K-giant members of Sagittarius that are notably more metal poor ($\langle[$Fe/H$]\rangle = -1.7\,\pm\,0.3$ dex) than previous studies.
-This suggests a significantly wider metallicity distribution exists in the Sagittarius Stream than formerly considered.
-We also present data on five carbon stars which were discovered in our sample.
-\end{abstract}
-
-\keywords{Galaxy: halo, structure --- Individual: Sagittarius, Virgo Stellar Stream --- Stars: carbon, K-giants}
+\previouslypublished{Parts of this chapter have been previously published as \href{http://adsabs.harvard.edu/abs/2012AJ....143...88C}{`Kinematics \& Chemistry of Halo Substructures: The Vicinity of the Virgo Over-Density', {Casey}, A.~R., {Keller}, S.~C., {Da Costa}, G., 2012, AJ, 143, 88C}.
+The work is presented here in expanded and updated form.}
 
 \section{Introduction}
-\label{sec:introduction}
-
 The proportion of substructure recently uncovered in the Galaxy has highlighted the crucial involvement accretion has played in the formation of the Milky Way \citep[see][and references therein]{Helmi_2008}.
@@
 The first over-density in the vicinity of the VOD was observed as a group of RR Lyrae stars by the QUEST survey \citep{Vivas;et-al_2001}.
-The collaboration later named this the ``$12\fh4$ clump'' \citep{Zinn;et-al_2004}.
+The collaboration later named this the ``$12{\mbox{$.\!\!^{\mathrm h}$}}4$ clump'' \citep{Zinn;et-al_2004}.
 The broad nature of the VOD was later uncovered from the SDSS catalogue as a diffuse over-density of main-sequence turnoff stars centered at $r_\odot \sim18$ kpc \citep[which ][dubbed as S297+63-20.5]{Newberg;et-al_2002}.
@@
 The difficulty arises in accurately distinguishing the VOD as there are multiple substructures along this line-of-sight.
-\citet{Duffau;et-al_2006} took observations of BHB and RR Lyrae within the ``$12\fh4$ clump'' and found a common velocity of $V_{GSR} = 99.8$ km s$^{-1}$ with $\sigma_{v} = 17.3$ km s$^{-1}$.
+\citet{Duffau;et-al_2006} took observations of BHB and RR Lyrae within the ``$12{\mbox{$.\!\!^{\mathrm h}$}}4$ clump'' and found a common velocity of $V_{GSR} = 99.8$ km s$^{-1}$ with $\sigma_{v} = 17.3$ km s$^{-1}$.
 It should be noted that the dispersion in kinematics measured by \citet{Duffau;et-al_2006} is essentially their velocity precision, so the substructure may possess a much smaller kinematic dispersion.
@@
 Target selection methodology is outlined in the next section which is followed with details regarding the observations.
-Techniques used to separate K-giants from dwarfs are discussed in \S\ref{sec:dwarf-giant-separation}, and our analysis procedure for kinematics (\S\ref{sec:kinematics}) and metallicities (\S\ref{sec:metallicities}) follows.
-A discussion of substructures is outlined in \S\ref{sec:discussion}, and in \S\ref{sec:carbon-stars} we report the carbon stars discovered in our sample.
-In \S\ref{sec:conclusions} we conclude with some final remarks and critical interpretations.
+Techniques used to separate K-giants from dwarfs are discussed in \S\ref{sec:ch1-dwarf-giant-separation}, and our analysis procedure for kinematics (\S\ref{sec:ch1-kinematics}) and metallicities (\S\ref{sec:ch1-metallicities}) follows.
+A discussion of substructures is outlined in \S\ref{sec:ch1-discussion}, and in \S\ref{sec:ch1-carbon-stars} we report the carbon stars discovered in our sample.
+In \S\ref{sec:ch1-conclusions} we conclude with some final remarks and critical interpretations.
 
 \section{Target Selection}
-\label{sec:target-selection}
+\label{sec:ch1-target-selection}
 
@@
 Field dwarfs are expected to contaminate the sample due to their similarity in colors.
-Although K-dwarfs are difficult to distinguish photometrically we can spectroscopically separate these through the equivalent width (EW) of the  gravity-sensitive Mg I triplet lines at 5167.3, 5172.7, and 5183.6 \AA\ (see \S\ref{sec:dwarf-giant-separation}).
+Although K-dwarfs are difficult to distinguish photometrically we can spectroscopically separate these through the equivalent width (EW) of the  gravity-sensitive Mg I triplet lines at 5167.3, 5172.7, and 5183.6 \AA\ (see \S\ref{sec:ch1-dwarf-giant-separation}).
 
 \begin{figure}[h]
-	\includegraphics[width=\columnwidth]{./cmd.eps}
+	\includegraphics[width=\columnwidth]{chapter1/cmd.pdf}
 	\caption{CMD of our observed regions from SDSS DR7, overlaid with the color selection criterion used to target K-giants.
@@
 
-\section{Observations}
-\label{sec:observations}
+\section{AAT Observations with AAOmega}
+\label{sec:ch1-observations}
 
@@
 Multiple configurations were observed for most fields to permit measurements of bright ($i < 16$) and faint ($i > 16$) stars, as well as repeat observations on a subset of stars.
-
-% NOTE TO THE EDITOR - This table ought to be in a single column.
-
-\begin{deluxetable}{cccc}
-\tablecolumns{1}
-\tablewidth{0pt}
-\tabletypesize{\scriptsize}
-\tablecaption{Observed fields\label{tab:observations}}
-\tablehead{
-	\colhead{Field} &
-	\colhead{$\alpha$-center} &
-	\colhead{$\delta$-center} &
-	\colhead{Field} \\ 
-	& (J2000.0) & (J2000.0) & Configurations
-}
-\startdata
-A & 12 00 00 & $+00$ 00 00 & 1 \\ 
-B & 12 20 00 & $-01$ 00 00 & 2 \\ 
-C & 12 40 00 & $-02$ 00 00 & 3 \\ 
-D & 12 56 00 & $-02$ 42 00 & 6 \\ 
-\enddata
-\end{deluxetable}
 
@@
 \section{Dwarf / Giant separation}
-\label{sec:dwarf-giant-separation}
+\label{sec:ch1-dwarf-giant-separation}
 
@@
 \begin{figure}[h]
-	\includegraphics[width=\columnwidth]{./dwarfgiant.eps}
+	\includegraphics[width=\columnwidth]{chapter1/dwarfgiant.pdf}
 	\caption{The sum of the Mg I triplet EWs for observations and synthetic spectra shown against the Sloan $g\,-\,i$ color.
@@
 \section{Radial Velocities}
-\label{sec:kinematics}
+\label{sec:ch1-kinematics}
 
@@
 \section{Metallicities}
-\label{sec:metallicities}
+\label{sec:ch1-metallicities}
 
@@
 Only K-giants within the valid calibration range ($0 > V-V_{HB} > -3$) were considered for metallicities.
-We assume that we have two dominant substructures present in our observations; the leading arm of Sgr and the Virgo Over-Density (see \S\ref{sec:substructure-identification}).
+We assume that we have two dominant substructures present in our observations; the leading arm of Sgr and the Virgo Over-Density (see \S\ref{sec:ch1-substructure-identification}).
 The Sgr stream dominates our negative $V_{GSR}$ population, and our positive kinematic space primarily comprises VOD and VSS members.
@@
 Typical $V_{HB}$ magnitude derived for the Sgr members is $18.7$, corresponding to a distance of $\sim{}41$ kpc.
-Reddening is accounted for using the \citet{Schlegel;Finkbeiner;Davis_1998} maps with \citet{Schlafly;Finkbeiner_2011} corrections as described in \S\ref{sec:dwarf-giant-separation}.
+Reddening is accounted for using the \citet{Schlegel;Finkbeiner;Davis_1998} maps with \citet{Schlafly;Finkbeiner_2011} corrections as described in \S\ref{sec:ch1-dwarf-giant-separation}.
 Uncertainties in distance are not interpolated; they are taken as the largest published uncertainty of the closest neighbouring data points, and this is propagated through to our reported metallicity uncertainties.
@@
 \section{Discussion}
-\label{sec:discussion}
+\label{sec:ch1-discussion}
 
 	\subsection{Substructure Identification}
-	\label{sec:substructure-identification}
+	\label{sec:ch1-substructure-identification}
 
@@
 	\begin{figure}[h!]
-		\includegraphics[width=\columnwidth]{./velocity_halo.eps}
+		\includegraphics[width=\columnwidth]{chapter1/velocity_halo.pdf}
 		\caption{Generalised histogram of $V_{GSR}$ for our 178 K-type giants, highlighting the substructure present.
@@
 
-		\begin{figure*}[t!]
-		\includegraphics[width=\textwidth]{./monte_carlo.eps}
-		\caption{The observed data for the 178 giant star sample (left panel).
+%\begin{figure}[h]
+%		\includegraphics[width=\columnwidth]{chapter1/monte_carlo.pdf}
+%		\caption{The observed data for the 178 giant star sample (left panel).
 Monte-Carlo simulation results illustrating the number of times simulations could reproduce our observed data in the equivalent multi-dimensional bin (right panel).
 Significant features discussed in the text are labelled.}
-		\label{fig:monte-carlo}
-	\end{figure*}
+%		\label{fig:monte-carlo}
+%	\end{figure}
 
@@
 Another feature where grid blocks were never reproduced in our simulations was Feature C.
-This feature may also be attributed to Sgr debris and is discussed further in \S\ref{sec:feature-c}.
+This feature may also be attributed to Sgr debris and is discussed further in \S\ref{sec:ch1-feature-c}.
 
@@
 We attribute these stars to the Virgo Stellar Stream, as they are coincident in spatial position, velocity, and metallicity with previously reported values of the VSS obtained by F turnoff/BHB stars \citep{Newberg;et-al_2007} and RR Lyrae stars \citep{Prior;et-al_2009a}.
-Feature B is discussed in \S\ref{sec:the-vss}.
+Feature B is discussed in \S\ref{sec:ch1-the-vss}.
 
-	\begin{figure*}[t!]
-		\includegraphics[width=\textwidth]{./adapted_belokurov_2006.eps}
-		\caption{Observed fields are outlined upon a panoramic view of the Sgr stream, to demonstrate our field locations in context with the Sgr stream.
+%	\begin{figure}
+%		\includegraphics[width=\columnwidth]{chapter1/adapted_belokurov_2006.pdf}
+%		\caption{Observed fields are outlined upon a panoramic view of the Sgr stream, to demonstrate our field locations in context with the Sgr stream.
 This plot is an adaptation of Figure 2 in \citet{Belokurov;et-al_2006}, which uses the 2MASS M-giant sample of \citet{Majewski;et-al_2003}.}
-		\label{fig:sgr-field-of-streams}
-	\end{figure*}
+%		\label{fig:sgr-field-of-streams}
+%\end{figure}
 
 	\subsection{Feature A \--- Sagittarius Debris}
-	\label{sec:sgr-debris}
+	\label{sec:ch1-sgr-debris}
 
@@
 	\begin{figure}[t!]
-		\includegraphics[width=\columnwidth]{./law_spatial.eps}
+		\includegraphics[width=\columnwidth]{chapter1/law_spatial.pdf}
 		\caption{Our fields and observed bounds are shown with the simulated particles from multiple \textit{N}-body simulations by LJM05 and LM10.
@@
 	\begin{figure*}[t!]
-		\includegraphics[width=\textwidth]{./sgr_velocities.eps}
+		\includegraphics[width=\textwidth]{chapter1/sgr_velocities.pdf}
 		\caption{A generalised histogram (left) of the galactocentric rest frame velocities in our sample (dotted line) compared to the velocities (solid line) from the \textit{N}-body models of LJM05, LM10 of particles within the same spatial coverage and distance range (up to $r_\odot \sim 60$ kpc) of our observed sample.
@@
 	\subsubsection{A Metal-Poor Population Uncovered in Sagittarius Debris}
-	\label{sec:sgr-metal-poor}
+	\label{sec:ch1-sgr-metal-poor}
 
@@
 	\begin{figure}[h]
-		\includegraphics[width=\columnwidth]{./sgr_feh_hist.eps}
+		\includegraphics[width=\columnwidth]{chapter1/sgr_feh_hist.pdf}
 		\caption{Metallicity histograms for K-giant members in our negative galactocentric velocity sample, which is largely populated by Sgr debris from the Northern leading arm.}
@@
 	\subsection{Feature B \--- The Virgo Stellar Stream}
-	\label{sec:the-vss}
+	\label{sec:ch1-the-vss}
 
@@
 	\subsection{Feature C \--- Sagittarius debris?}
-	\label{sec:feature-c}
+	\label{sec:ch1-feature-c}
 
@@
 \section{Carbon Stars}
-\label{sec:carbon-stars}
+\label{sec:ch1-carbon-stars}
 
@@
 \begin{figure}[h!]
-	\includegraphics[width=\columnwidth]{./carbon_stars.eps}
+	\includegraphics[width=\columnwidth]{chapter1/carbon_stars.pdf}
 	\caption{Sloan \textit{u \--- g} and \textit{g \--- r} colors for our carbon stars, and the identified carbon stars and classifications by \citet{Downes;et-al_2004}.
@@
 
-\begin{deluxetable}{cccccccccccc}
-\tablewidth{0pt}
-\tabletypesize{\scriptsize}
-\tablecaption{Properties of carbon stars found in our sample \label{tb:carbon-stars}}
-\tablehead{
-	\colhead{SDSS Name J+\tablenotemark{a}} & 
-	\colhead{$M_g$} &
-	\colhead{\it{u-g}} &
-	\colhead{\it{g-r}} &
-	\colhead{\it{r-i}} &
-	\colhead{\it{i-z}} &
-	\colhead{\it{H-K}} &
-	\colhead{\it{J-H}} &
-	\colhead{$\mu_{\alpha\cos{\delta}}\tablenotemark{c}$} &
-	\colhead{$\mu_\delta\tablenotemark{c}$} &
-	\colhead{$V_{GSR}$} & 
-	\colhead{Likely} \\
-	& & & & & & & & (mas yr$^{-1}$) & (mas yr$^{-1}$) & (km s$^{-1}$) & dwarf?
-}
+%\begin{deluxetable}{cccccccccccc}
+%\tablewidth{0pt}
+%\tabletypesize{\scriptsize}
+%\tablecaption{Properties of carbon stars found in our sample \label{tb:carbon-stars}}
+%\tablehead{
+%	\colhead{SDSS Name J+\tablenotemark{a}} & 
+%	\colhead{$M_g$} &
+%	\colhead{\it{u-g}} &
+%	\colhead{\it{g-r}} &
+%	\colhead{\it{r-i}} &
+%	\colhead{\it{i-z}} &
+%	\colhead{\it{H-K}} &
+%	\colhead{\it{J-H}} &
+%	\colhead{$\mu_{\alpha\cos{\delta}}\tablenotemark{c}$} &
+%	\colhead{$\mu_\delta\tablenotemark{c}$} &
+%	\colhead{$V_{GSR}$} & 
+%	\colhead{Likely} \\
+%	& & & & & & & & (mas yr$^{-1}$) & (mas yr$^{-1}$) & (km s$^{-1}$) & dwarf?
+%}
 
-\startdata
-121740.94-001839.5 & 18.66 & 1.10 & 0.54 & 0.16 & 0.05 & ...\tablenotemark{b}& ...\tablenotemark{b} & \phn$-3.0 \pm 5.4$  & $-18.0 \pm 5.4$\phn & $\phn-71 \pm 34$ & Yes\\
-121853.18-004628.4 & 17.71 & 1.67 & 0.73 & 0.22 & 0.11 & \phd0.24 & 0.36 &  \phn$-3.7 \pm 4.5$ & $-0.5 \pm 4.5$ & $+176 \pm 9$ & - \\
-122053.71-011709.5 & 17.65 & 1.79 & 0.80 & 0.26 & 0.13 & \phd0.16 & 0.56 &  \phn$-7.3 \pm 4.3$ & $-3.9 \pm 4.3$ & $\phn+31 \pm 11$ & - \\
-125410.80-032744.0 & 18.59 & 1.43 & 0.64 & 0.22 & 0.05 & \phd0.56 & 0.32 &$-21.1 \pm 5.0 $ & $-7.7 \pm 5.0$ & $\phn-41 \pm 9\phn$ & Yes \\ 
-125416.52-031437.6 & 16.85 & 1.72 & 0.73 & 0.25 & 0.11 & -0.11 & 0.50 & $-19.8 \pm 4.2$ & \phd\phn$8.7 \pm 4.2$& $\phn+15 \pm 4\phn$ & Yes \\
-\enddata
-\tablenotetext{a}{To keep with convention, positional information has been truncated. Full information available through the SDSS archive.}
-\tablenotetext{b}{No \textit{JHK} photometry is available for this object as it is fainter than the 2MASS survey limit.}
-\tablenotetext{c}{Proper motions taken from the PPMXL Catalog \citep{Roser;et-al_2010}.}
-\end{deluxetable}
+%\startdata
+%121740.94-001839.5 & 18.66 & 1.10 & 0.54 & 0.16 & 0.05 & ...\tablenotemark{b}& ...\tablenotemark{b} & \phn$-3.0 \pm 5.4$  & $-18.0 \pm 5.4$\phn & $\phn-71 \pm 34$ & Yes\\
+%121853.18-004628.4 & 17.71 & 1.67 & 0.73 & 0.22 & 0.11 & \phd0.24 & 0.36 &  \phn$-3.7 \pm 4.5$ & $-0.5 \pm 4.5$ & $+176 \pm 9$ & - \\
+%122053.71-011709.5 & 17.65 & 1.79 & 0.80 & 0.26 & 0.13 & \phd0.16 & 0.56 &  \phn$-7.3 \pm 4.3$ & $-3.9 \pm 4.3$ & $\phn+31 \pm 11$ & - \\
+%125410.80-032744.0 & 18.59 & 1.43 & 0.64 & 0.22 & 0.05 & \phd0.56 & 0.32 &$-21.1 \pm 5.0 $ & $-7.7 \pm 5.0$ & $\phn-41 \pm 9\phn$ & Yes \\ 
+%125416.52-031437.6 & 16.85 & 1.72 & 0.73 & 0.25 & 0.11 & -0.11 & 0.50 & $-19.8 \pm 4.2$ & \phd\phn$8.7 \pm 4.2$& $\phn+15 \pm 4\phn$ & Yes \\
+%\enddata
+%\tablenotetext{a}{To keep with convention, positional information has been truncated. Full information available through the SDSS archive.}
+%\tablenotetext{b}{No \textit{JHK} photometry is available for this object as it is fainter than the 2MASS survey limit.}
+%\tablenotetext{c}{Proper motions taken from the PPMXL Catalog \citep{Roser;et-al_2010}.}
+%\end{deluxetable}
 
@@
 \section{Conclusions}
-\label{sec:conclusions}
+\label{sec:ch1-conclusions}
 
@@
 These observations also demonstrate that the Sgr stream likely hosts a substantially larger abundance range than previously found, including a previously un-detected metal-poor population of K-giants.
-
-\section{Acknowledgements}
-ARC acknowledges the financial support through the Australian Research Council Laureate Fellowship 0992131.
-SK and GDaC acknowledge the financial support from the Australian Research Council through Discovery Program DP0878137.
-
-This publication makes use of data products from the Two Micron All Sky Survey, which is a joint project of the University of Massachusetts and the Infrared Processing and Analysis Center/California Institute of Technology, funded by the National Aeronautics and Space Administration and the National Science Foundation.
-
-Funding for the SDSS and SDSS-II has been provided by the Alfred P.
-Sloan Foundation, the Participating Institutions, the National Science Foundation, the U.S.
-Department of Energy, the National Aeronautics and Space Administration, the Japanese Monbukagakusho, the Max Planck Society, and the Higher Education Funding Council for England.
-The SDSS Web Site is http://www.sdss.org/.
-
-The SDSS is managed by the Astrophysical Research Consortium for the Participating Institutions.
-The Participating Institutions are the American Museum of Natural History, Astrophysical Institute Potsdam, University of Basel, University of Cambridge, Case Western Reserve University, University of Chicago, Drexel University, Fermilab, the Institute for Advanced Study, the Japan Participation Group, Johns Hopkins University, the Joint Institute for Nuclear Astrophysics, the Kavli Institute for Particle Astrophysics and Cosmology, the Korean Scientist Group, the Chinese Academy of Sciences (LAMOST), Los Alamos National Laboratory, the Max-Planck-Institute for Astronomy (MPIA), the Max-Planck-Institute for Astrophysics (MPA), New Mexico State University, Ohio State University, University of Pittsburgh, University of Portsmouth, Princeton University, the United States Naval Observatory, and the University of Washington.
-\bibliographystyle{apj}
-\bibliography{bibliography}
-
-\end{document}

### 2013-02-27 thesis/chapter2/chapter2.tex
Added thesis as of 27 Feb

--- 2012-12-08 2012-oss-mrs/ms.tex
@@
-\documentclass[10pt,apjl]{emulateapj}
-\usepackage{amssymb,graphics} % for resolution symbol
-\usepackage{multirow} % deluxetable wasn't doing it for me.
+\chapter{Hunting the Parent of the Orphan Stream}
 
-\begin{document}
+% you can put a brief note at the top of your chapters using '\previouslypublished{}'.
+For example, to give a reference to the paper this chapter is based on, or to point out that it has been submitted to a journal.
 
-\shorttitle{Identifying Orphan Stream Members from Low-Resolution Spectroscopy}
-\shortauthors{Casey et al}
+\previouslypublished{Parts of this chapter have been previously published as \href{http://adsabs.harvard.edu/abs/2013ApJ...764...39C}{`Hunting the Parent of the Orphan Stream: Identifying Stream Members from Low-Resolution Spectroscopy', {Casey}, A.~R., {Da Costa}, G., {Keller}, S.~C., {Maunder}, E., 2013, ApJ, 764, 39C}.
+The work is presented here in expanded and updated form.}
 
-\title{Hunting the Parent of the Orphan Stream: Identifying Stream Members \\ from Low-Resolution Spectroscopy}
-
-\author{Andrew R. Casey\altaffilmark{1,2}, Gary Da Costa\altaffilmark{1}, Stefan C. Keller\altaffilmark{1}, Elizabeth Maunder\altaffilmark{1}}
-\altaffiltext{1}{Research School of Astronomy \& Astrophysics, Australian National University, Mount Stromlo Observatory, via Cotter Rd, Weston, ACT 2611, Australia; \email{acasey@mso.anu.edu.au}}
-\altaffiltext{2}{Massachusetts Institute of Technology and Kavli Institute for
-Astrophysics and Space Research, 77 Massachusetts Avenue,
-Cambridge, MA 02139, USA}
-
-\begin{abstract}
+\section{Introduction}
 We present candidate K-giant members in the Orphan Stream which have been identified from low-resolution data taken with the AAOmega spectrograph on the Anglo-Australian Telescope.
@@
 \section{Introduction}
-\label{sec:introduction}
+\label{sec:ch2-introduction}
 
@@
 In the following section we outline our photometric target selection.
-In \S\ref{sec:observations} we describe the low-resolution spectroscopic observations.
-The data analysis, including stream identification, is discussed in \S\ref{sec:analysis} and in \S\ref{sec:conclusions} the conclusions, predictions and future work are presented.
+In \S\ref{sec:ch2-observations} we describe the low-resolution spectroscopic observations.
+The data analysis, including stream identification, is discussed in \S\ref{sec:ch2-analysis} and in \S\ref{sec:ch2-conclusions} the conclusions, predictions and future work are presented.
 
 \section{Target Selection}
-\label{sec:target-selection}
+\label{sec:ch2-target-selection}
 
@@
 \section{Observations}
-\label{sec:observations}
+\label{sec:ch2-observations}
 
@@
 \section{Analysis \& Discussion}
-\label{sec:analysis}
+\label{sec:ch2-analysis}
 
@@
 
-Figure \ref{fig:velocities} shows a histogram of our galactocentric velocities, compared to the predicted smooth line-of-sight velocity distribution for this region from the Besan\c{c}on model \citep{Robin_et-al_2003}.
-We have selected particles from the Besan\c{c}on model using the same criteria outlined in \S\ref{sec:target-selection} after employing the \citet{Jordi_et-al_2006} colour transformations.
+Figure \ref{fig:ch2-velocities} shows a histogram of our galactocentric velocities, compared to the predicted smooth line-of-sight velocity distribution for this region from the Besan\c{c}on model \citep{Robin_et-al_2003}.
+We have selected particles from the Besan\c{c}on model using the same criteria outlined in \S\ref{sec:ch2-target-selection} after employing the \citet{Jordi_et-al_2006} colour transformations.
 It is clear that our target selection has yielded mostly nearby disk dwarf stars with $V_{GSR} \approx -120$\,km s$^{-1}$.
@@
 Differences in accounting for the local standard of rest between this work and \citet{Newberg_et-al_2010} means that this corresponds to approximately 95\,km s$^{-1}$ on our $V_{GSR}$ scale.
-This is discussed further in \S\ref{sec:newberg}.
-The expected Orphan Stream kinematic peak is labelled in Figure \ref{fig:velocities}.
+This is discussed further in \S\ref{sec:ch2-newberg}.
+The expected Orphan Stream kinematic peak is labelled in Figure \ref{fig:ch2-velocities}.
 There is no obvious sharp kinematic peak representative of the Orphan Stream in our sample.
 From kinematics alone, our targets appears largely indistinguishable from a smooth halo distribution.
-To isolate potential Orphan Stream members we have nominated a relatively wide selection criteria between $65 \leq V_{GSR} \leq 125$ km s$^{-1}$ (shown in Figure \ref{fig:velocities}), which yields 28 Orphan Stream candidates.
+To isolate potential Orphan Stream members we have nominated a relatively wide selection criteria between $65 \leq V_{GSR} \leq 125$ km s$^{-1}$ (shown in Figure \ref{fig:ch2-velocities}), which yields 28 Orphan Stream candidates.
 The typical uncertainty in our velocities is $\pm{}5.0$\,km s$^{-1}$.
@@
 \subsection{Dwarf/Giant Discrimination}
-\label{sec:dwarf-giant}
+\label{sec:ch2-dwarf-giant}
 
@@
 
-Figure \ref{fig:ew-mg} illustrates the trend with $EW_{\lambda8807}$ against SDSS de-reddened\footnote{All magnitudes presented in this letter are de-reddened using the \citet{Schlegel_Finkbeiner_Davis_1998} dust maps.} $g - r$, illustrating the dominant upper dwarf branch we wish to exclude.
+Figure \ref{fig:ch2-ew-mg} illustrates the trend with $EW_{\lambda8807}$ against SDSS de-reddened\footnote{All magnitudes presented in this letter are de-reddened using the \citet{Schlegel_Finkbeiner_Davis_1998} dust maps.} $g - r$, illustrating the dominant upper dwarf branch we wish to exclude.
 Giant stars populate the lower, sparser branch.
-A separation line has been adopted to distinguish dwarfs from giants, and is shown in Figure \ref{fig:ew-mg}.
+A separation line has been adopted to distinguish dwarfs from giants, and is shown in Figure \ref{fig:ch2-ew-mg}.
 If we were to place this line higher, the total number of true giant stars may increase, but the dwarf contamination rate will rise dramatically.
@@
 
-Our dwarf/giant separation line in Figure \ref{fig:ew-mg} yields 425 potential giants.
+Our dwarf/giant separation line in Figure \ref{fig:ch2-ew-mg} yields 425 potential giants.
 Upon taking the intersection of our kinematic and gravity selections, we find 20 stars that appear to be likely Orphan Stream giants.
@@
 \subsection{Metallicities}
-\label{sec:metallicities}
+\label{sec:ch2-metallicities}
 
@@
 We find ten highly likely stream members with consistently derived metallicities.
-They fall within the shaded region illustrated in Figure \ref{fig:feh}.
+They fall within the shaded region illustrated in Figure \ref{fig:ch2-feh}.
 
@@
 
-Since our Orphan Stream giants cover a wide evolutionary range along the giant branch (Figure \ref{fig:cmd}), we are in a good position to revise the distance estimate to the stream.
+Since our Orphan Stream giants cover a wide evolutionary range along the giant branch (Figure \ref{fig:ch2-cmd}), we are in a good position to revise the distance estimate to the stream.
 Given a 10\,Gyr \citet{Girardi_et-al_2008} isochrone at $[\mbox{Fe/H}] = -1.63$, we find a best-fitting distance to the stream of $22.5 \pm 2.0$\,kpc at $(l, b) = (250\,^\circ,\,50\,^\circ)$.
-This isochrone is shown in Figure \ref{fig:cmd}.
+This isochrone is shown in Figure \ref{fig:ch2-cmd}.
 Our derived distance is in reasonably good agreement with the measurement of $21.4 \pm 1.0$\,kpc independently deduced by \citet{Grillmair_2006} and \citet{Newberg_et-al_2010}.
@@
 \subsection{Comparison with \citet{Newberg_et-al_2010}}
-\label{sec:newberg}
+\label{sec:ch2-newberg}
 \citet{Newberg_et-al_2010} traced the Orphan Stream using BHB stars selected from the SEGUE survey, allowing them to derive an orbit for the stream and make a strong prediction for the location of the undiscovered progenitor.
@@
 We note that this is $\sim95$\,km s$^{-1}$ on our scale, given the differences in accounting for the local standard of rest.
-The velocities and metallicities of our `High' and `Medium' probability candidates are illustrated in Figure \ref{fig:vgsr-feh}.
+The velocities and metallicities of our `High' and `Medium' probability candidates are illustrated in Figure \ref{fig:ch2-vgsr-feh}.
 Although we recover some candidates with velocities up to $V_{GSR} \sim 110$\,km s$^{-1}$, our kinematic distribution peaks near $V_{GSR} \sim 85$\,km s$^{-1}$, roughly 10\,km s$^{-1}$ lower than that of \citet{Newberg_et-al_2010}.
@@
 Our highly likely stream members have a mean metallicity of [Fe/H] = $-1.63$, with a dispersion of $\sigma = 0.56$\,dex.
-As illustrated in Figures \ref{fig:vgsr-feh} and \ref{fig:newberg-feh}, there are two very metal-poor candidates which largely drive this dispersion, but we have no reason to suspect they are non-members.
+As illustrated in Figures \ref{fig:ch2-vgsr-feh} and \ref{fig:ch2-newberg-feh}, there are two very metal-poor candidates which largely drive this dispersion, but we have no reason to suspect they are non-members.
 The \citet{Newberg_et-al_2010} sample contains 37 BHB stars identified over a 60\,$^\circ$ arc on the sky, and has a peak metallicity at [Fe/H] = $-2.10 \pm 0.10$.
@@
 \section{Conclusions}
-\label{sec:conclusions}
+\label{sec:ch2-conclusions}
 
@@
 \citet{Simon_et-al_2011} obtained spectroscopy for six members in Segue 1 and found an extremely wide metallicity dispersion: from $<-3.4$ to $-1.63$ dex.
-On the basis of the extremely low metallicity in the cluster and the wide chemical dispersion, they conclude that Segue 1 is a disrupted dwarf spheroidal galaxy.
+On the basis of the extremely low metallicity in the cluster and the wide chemical dispersion, they conclude that Segue 1 is a dwarf spheroidal galaxy.
 Although the data presented here indicates the Orphan Stream progenitor is a disrupted dwarf spheroidal galaxy, we cannot reliably associate Segue 1 as the parent without additional observational data.
@@
 
-The K-giants presented here can provide great insight
-\begin{minipage}{\columnwidth}
-into the chemistry and history of the Orphan Stream.
+The K-giants presented here can provide great insight into the chemistry and history of the Orphan Stream.
 High-resolution spectroscopic observations have been taken for some of our highly probable members and a detailed chemical analysis will be presented in a forthcoming paper (Casey et al., in preparation).
@@
 However, at least for the moment, the Orphan Stream remains appropriately named.
-\end{minipage}
-
-\acknowledgements
-The authors would like to thank the anonymous referee for their constructive comments which improved this paper.
-ARC acknowledges the financial support through the Australian Research Council Laureate Fellowship 0992131, and from the Australian Prime Minister's Endeavour Award Research Fellowship, which has facilitated his research at MIT.
-SK and GDaC acknowledge the financial support from the Australian Research Council through Discovery Programs DP0878137 and DP120101237.
-GDaC is also grateful for the support received during an extended visit to the Institute of Astronomy, University of Cambridge, during which this work was completed.
-
-Funding for the SDSS and SDSS-II has been provided by the Alfred P.
-Sloan Foundation, the Participating Institutions, the National Science Foundation, the U.S.
-Department of Energy, the National Aeronautics and Space Administration, the Japanese Monbukagakusho, the Max Planck Society, and the Higher Education Funding Council for England.
-The SDSS Web Site is http://www.sdss.org/.
-
-The SDSS is managed by the Astrophysical Research Consortium for the Participating Institutions.
-The Participating Institutions are the American Museum of Natural History, Astrophysical Institute Potsdam, University of Basel, University of Cambridge, Case Western Reserve University, University of Chicago, Drexel University, Fermilab, the Institute for Advanced Study, the Japan Participation Group, Johns Hopkins University, the Joint Institute for Nuclear Astrophysics, the Kavli Institute for Particle Astrophysics and Cosmology, the Korean Scientist Group, the Chinese Academy of Sciences (LAMOST), Los Alamos National Laboratory, the Max-Planck-Institute for Astronomy (MPIA), the Max-Planck-Institute for Astrophysics (MPA), New Mexico State University, Ohio State University, University of Pittsburgh, University of Portsmouth, Princeton University, the United States Naval Observatory, and the University of Washington.
-
-\vspace{2em}
-
-\begin{thebibliography}{29}
-\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
-
-\bibitem[{{Abazajian} {et~al.}(2009){Abazajian}, {Adelman-McCarthy},
-  {Ag{\"u}eros}, {Allam}, {Allende Prieto}, {An}, {Anderson}, {Anderson},
-  {Annis}, {Bahcall}, \& et~al.}]{Abazajian_et-al_2009}
-{Abazajian}, K.~N., {et~al.} 2009, \apjs, 182, 543
-
-\bibitem[{{Armandroff} \& {Da Costa}(1991)}]{Amandroff_Da_Costa_1991}
-{Armandroff}, T.~E., \& {Da Costa}, G.~S. 1991, \aj, 101, 1329
-
-\bibitem[{{Battaglia} \& {Starkenburg}(2012)}]{Battaglia_Starkenburg_2012}
-{Battaglia}, G., \& {Starkenburg}, E. 2012, \aap, 539, A123
-
-\bibitem[{{Belokurov} {et~al.}(2006){Belokurov}, {Zucker}, {Evans}, {Gilmore},
-  {Vidrih}, {Bramich}, {Newberg}, {Wyse}, {Irwin}, {Fellhauer}, {Hewett},
-  {Walton}, {Wilkinson}, {Cole}, {Yanny}, {Rockosi}, {Beers}, {Bell},
-  {Brinkmann}, {Ivezi{\'c}}, \& {Lupton}}]{Belokurov_et-al_2006}
-{Belokurov}, V., {et~al.} 2006, \apjl, 642, L137
-
-\bibitem[{{Belokurov} {et~al.}(2007){Belokurov}, {Evans}, {Irwin},
-  {Lynden-Bell}, {Yanny}, {Vidrih}, {Gilmore}, {Seabroke}, {Zucker},
-  {Wilkinson}, {Hewett}, {Bramich}, {Fellhauer}, {Newberg}, {Wyse}, {Beers},
-  {Bell}, {Barentine}, {Brinkmann}, {Cole}, {Pan}, \&
-  {York}}]{Belokurov_et-al_2007}
----. 2007, \apj, 658, 337
-
-\bibitem[{{Casey} {et~al.}(2012){Casey}, {Keller}, \& {Da
-  Costa}}]{Casey_et-al_2012}
-{Casey}, A.~R., {Keller}, S.~C., \& {Da Costa}, G. 2012, \aj, 143, 88
-
-\bibitem[{{Fellhauer} {et~al.}(2007){Fellhauer}, {Evans}, {Belokurov},
-  {Zucker}, {Yanny}, {Wilkinson}, {Gilmore}, {Irwin}, {Bramich}, {Vidrih},
-  {Hewett}, \& {Beers}}]{Fellhaur_et-al_2007}
-{Fellhauer}, M., {et~al.} 2007, \mnras, 375, 1171
-
-\bibitem[{{Frebel} \& {Norris}(2011){Frebel}, \& {Norris}}]{Frebel_Norris_2011}
-{Frebel}, A., \& Norris, J. E. 2011, arXiv/1102.1748
-
-\bibitem[{{Grillmair} (2006)}]{Grillmair_2006}
-{Grillmair}, C.~J. 2006, \apj, 643, L37
-
-\bibitem[{{Hodapp} {et~al.}(2004){Hodapp}, {Kaiser}, {Aussel}, {Burgett},
-  {Chambers}, {Chun}, {Dombeck}, {Douglas}, {Hafner}, {Heasley}, {Hoblitt},
-  {Hude}, {Isani}, {Jedicke}, {Jewitt}, {Laux}, {Luppino}, {Lupton}, {Maberry},
-  {Magnier}, {Mannery}, {Monet}, {Morgan}, {Onaka}, {Price}, {Ryan},
-  {Siegmund}, {Szapudi}, {Tonry}, {Wainscoat}, \&
-  {Waterson}}]{Hodapp_et-al_2004}
-{Hodapp}, K.~W., {et~al.} 2004, Astronomische Nachrichten, 325, 636
-
-\bibitem[{{Jin} \& {Lynden-Bell}(2007)}]{Jin_Lynden_Bell_2007}
-{Jin}, S., \& {Lynden-Bell}, D. 2007, \mnras, 378, L64
-
-\bibitem[{{Jordi} {et~al.}(2006){Jordi}, {Grebel}, \&
-  {Ammon}}]{Jordi_et-al_2006}
-{Jordi}, K., {Grebel}, E.~K., \& {Ammon}, K. 2006, \aap, 460, 339
-
-\bibitem[{{Keller} {et~al.}(2007){Keller}, {Schmidt}, {Bessell}, {Conroy},
-  {Francis}, {Granlund}, {Kowald}, {Oates}, {Martin-Jones}, {Preston},
-  {Tisserand}, {Vaccarella}, \& {Waterson}}]{Keller_et-al_2007}
-{Keller}, S.~C., {et~al.} 2007, PASA, 24, 1
-
-\bibitem[{{Kerr} \& {Lynden-Bell}(1986)}]{Kerr_Lynden-Bell_1986}
-{Kerr}, F.~J., \& {Lynden-Bell}, D. 1986, \mnras, 221, 1023
-
-\bibitem[{{Koposov} {et~al.}(2010){Koposov}, {Rix}, \&
-  {Hogg}}]{Koposov_et-al_2010}
-{Koposov}, S.~E., {Rix}, H.-W., \& {Hogg}, D.~W. 2010, \apj, 712, 260
-
-\bibitem[{{Marigo} {et~al.}(2008){Marigo}, {Girardi}, {Bressan}, {Groenewegen},
-  {Silva}, \& {Granato}}]{Girardi_et-al_2008}
-{Marigo}, P., {Girardi}, L., {Bressan}, A., {Groenewegen}, M.~A.~T., {Silva},
-  L., \& {Granato}, G.~L. 2008, \aap, 482, 883
-
-\bibitem[{{Mihalas} \& {Binney}(1981)}]{Mihalas_Binney_1981}
-{Mihalas}, D., \& {Binney}, J. 1981, Science, 214, 829
-
-\bibitem[{{Newberg} {et~al.}(2010){Newberg}, {Willett}, {Yanny}, \&
-  {Xu}}]{Newberg_et-al_2010}
-{Newberg}, H.~J., {Willett}, B.~A., {Yanny}, B., \& {Xu}, Y. 2010, \apj, 711,
-  32
-
-\bibitem[{{Odenkirchen} {et~al.}(2009){Odenkirchen}, {Grebel}, {Kayser}, {Rix},
-  \& {Dehnen}}]{Odenkirchen_et-al_2009}
-{Odenkirchen}, M., {Grebel}, E.~K., {Kayser}, A., {Rix}, H.-W., \& {Dehnen}, W.
-  2009, \aj, 137, 3378
-
-\bibitem[{{Robin} {et~al.}(2003){Robin}, {Reyl{\'e}}, {Derri{\`e}re}, \&
-  {Picaud}}]{Robin_et-al_2003}
-{Robin}, A.~C., {Reyl{\'e}}, C., {Derri{\`e}re}, S., \& {Picaud}, S. 2003,
-  \aap, 409, 523
-
-\bibitem[{{Roeser} {et~al.}(2010){Roeser}, {Demleitner}, \&
-  {Schilbach}}]{Roeser_et-al_2010}
-{Roeser}, S., {Demleitner}, M., \& {Schilbach}, E. 2010, \aj, 139, 2440
-
-\bibitem[{{Sales} {et~al.}(2008){Sales}, {Helmi}, {Starkenburg}, {Morrison},
-  {Engle}, {Harding}, {Mateo}, {Olszewski}, \& {Sivarani}}]{Sales_et-al_2008}
-{Sales}, L.~V., {et~al.} 2008, \mnras, 389, 1391
-
-\bibitem[{{Saviane} {et~al.}(2012){Saviane}, {Da Costa}, {Held}, {Sommariva},
-  {Gullieuszik}, {Barbuy}, \& {Ortolani}}]{Saviane_et-al_2012}
-{Saviane}, I., {Da Costa}, G.~S., {Held}, E.~V., {Sommariva}, V.,
-  {Gullieuszik}, M., {Barbuy}, B., \& {Ortolani}, S. 2012, \aap, 540, A27
-
-\bibitem[{{Schlegel} {et~al.}(1998){Schlegel}, {Finkbeiner}, \&
-  {Davis}}]{Schlegel_Finkbeiner_Davis_1998}
-{Schlegel}, D.~J., {Finkbeiner}, D.~P., \& {Davis}, M. 1998, \apj, 500, 525
-
-\bibitem[{{Simon} {et~al.}(2011){Simon}, {Geha}, {Minor}, {Martinez},
-	{Kirby}, {Bullock}, {Kaplinghat}, 
-	{Strigari}, {Willman}, {Choi}, {Tollerud}, \&
-	{Wolf}, J.}]{Simon_et-al_2011}
-{Simon}, J.~D., {et~al.} 2011, \apj, 733, 46S
-
-\bibitem[{{Starkenburg} {et~al.}(2010){Starkenburg}, {Hill}, {Tolstoy},
-  {Gonz{\'a}lez Hern{\'a}ndez}, {Irwin}, {Helmi}, {Battaglia}, {Jablonka},
-  {Tafelmeyer}, {Shetrone}, {Venn}, \& {de Boer}}]{Starkenburg_et-al_2010}
-{Starkenburg}, E., {et~al.} 2010, \aap, 513, A34
-
-\bibitem[{{Xue} {et~al.}(2008){Xue}, {Rix}, {Zhao}, {Re Fiorentin}, {Naab},
-  {Steinmetz}, {van den Bosch}, {Beers}, {Lee}, {Bell}, {Rockosi}, {Yanny},
-  {Newberg}, {Wilhelm}, {Kang}, {Smith}, \& {Schneider}}]{Xue_et-al_2008}
-{Xue}, X.~X., {et~al.} 2008, \apj, 684, 1143
-
-\bibitem[{{Zucker} {et~al.}(2006){Zucker}, {Belokurov}, {Evans}, {Kleyna},
-  {Irwin}, {Wilkinson}, {Fellhauer}, {Bramich}, {Gilmore}, {Newberg}, {Yanny},
-  {Smith}, {Hewett}, {Bell}, {Rix}, {Gnedin}, {Vidrih}, {Wyse}, {Willman},
-  {Grebel}, {Schneider}, {Beers}, {Kniazev}, {Barentine}, {Brewington},
-  {Brinkmann}, {Harvanek}, {Kleinman}, {Krzesinski}, {Long}, {Nitta}, \&
-  {Snedden}}]{Zucker_et-al_2006}
-{Zucker}, D.~B., {et~al.} 2006, \apjl, 650, L41
-
-\end{thebibliography}
-
-\end{document}

### 2013-02-27 thesis/conclusions/conclusions.tex
Added thesis as of 27 Feb

\chapter{Conclusions}\label{conclusions}

\epigraph{Although the Universe is under no obligation to make sense, students in pursuit of the Ph.D. are.}{-- Robert P. Kirshner\footnotemark}

\footnotetext{\emph{Quarterly Journal of the Royal Astronomical Society.} 1991, Vol.\ 32, No.\ 3, p233} Lorem ipsum dolor sit amet, consectetur adipiscing elit. Duis posuere tellus eu quam pellentesque ut varius purus egestas. Nam hendrerit malesuada sapien, non molestie risus cursus at. Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas. Sed dignissim sodales sem sed volutpat. Ut laoreet, ante sed dictum vestibulum, lacus sapien semper dui, nec rutrum velit justo eu enim. Fusce vehicula blandit ipsum, ac volutpat libero vestibulum in. Sed quis lacus mauris. Quisque congue elit in nisi lacinia ac condimentum eros pellentesque. Quisque et nisl odio, vitae eleifend neque. In volutpat sapien non leo egestas ut sodales elit malesuada. Proin suscipit, lacus a suscipit euismod, neque velit pellentesque urna, eget ullamcorper felis neque sit amet erat. Phasellus in est et ligula accumsan lacinia sit amet et nisl. Aliquam interdum, arcu sed dictum gravida, mi justo iaculis mi, vel scelerisque nulla nunc in justo \citep{Murphy12}.

Phasellus erat libero, lobortis vitae iaculis nec, congue et tortor. Donec tempus leo et nisl tincidunt porta. Nulla velit sapien, sollicitudin sit amet accumsan a, facilisis a est. Phasellus scelerisque convallis sapien, nec viverra dui tincidunt a. Nulla ligula velit, laoreet fringilla condimentum sed, euismod a est. Fusce leo sapien, rhoncus a ultricies nec, porttitor ut lectus. Sed vestibulum turpis risus, nec vestibulum diam. Morbi quis quam quis enim cursus aliquam scelerisque quis tellus. Pellentesque accumsan lectus cursus massa ultrices placerat. Nulla facilisi. Praesent fermentum erat in augue sagittis condimentum. Nullam posuere blandit urna a mollis. Cras malesuada lectus a turpis sollicitudin volutpat. Morbi semper, nisl vel mattis vehicula, sapien sapien adipiscing tortor, in accumsan tortor dolor non neque. Maecenas varius, nunc ut euismod volutpat, mauris ante faucibus magna, ac eleifend elit tortor sed arcu.

\section{Future prospects}

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Duis posuere tellus eu quam pellentesque ut varius purus egestas. Nam hendrerit malesuada sapien, non molestie risus cursus at. Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas. Sed dignissim sodales sem sed volutpat.

\subsection{What you were going to do in your Ph.D.}

Ut laoreet, ante sed dictum vestibulum, lacus sapien semper dui, nec rutrum velit justo eu enim. Fusce vehicula blandit ipsum, ac volutpat libero vestibulum in. Sed quis lacus mauris. Quisque congue elit in nisi lacinia ac condimentum eros pellentesque. Quisque et nisl odio, vitae eleifend neque. In volutpat sapien non leo egestas ut sodales elit malesuada. Proin suscipit, lacus a suscipit euismod, neque velit pellentesque urna, eget ullamcorper felis neque sit amet erat. Phasellus in est et ligula accumsan lacinia sit amet et nisl. Aliquam interdum, arcu sed dictum gravida, mi justo iaculis mi, vel scelerisque nulla nunc in justo.

Phasellus erat libero, lobortis vitae iaculis nec, congue et tortor. Donec tempus leo et nisl tincidunt porta. Nulla velit sapien, sollicitudin sit amet accumsan a, facilisis a est. Phasellus scelerisque convallis sapien, nec viverra dui tincidunt a. Nulla ligula velit, laoreet fringilla condimentum sed, euismod a est. Fusce leo sapien, rhoncus a ultricies nec, porttitor ut lectus. Sed vestibulum turpis risus, nec vestibulum diam. Morbi quis quam quis enim cursus aliquam scelerisque quis tellus. Pellentesque accumsan lectus cursus massa ultrices placerat. Nulla facilisi. Praesent fermentum erat in augue sagittis condimentum. Nullam posuere blandit urna a mollis. Cras malesuada lectus a turpis sollicitudin volutpat. Morbi semper, nisl vel mattis vehicula, sapien sapien adipiscing tortor, in accumsan tortor dolor non neque. Maecenas varius, nunc ut euismod volutpat, mauris ante faucibus magna, ac eleifend elit tortor sed arcu.

\subsection{Save some work for your first post-doc}

Vestibulum sed orci nec diam euismod vehicula vitae et mauris. Phasellus sagittis justo quis mauris adipiscing auctor. Suspendisse nibh erat, cursus vitae aliquam in, rutrum sed est. Nunc mollis quam quis velit vehicula fringilla. Quisque convallis, neque ut faucibus luctus, nisl ante porttitor ante, at venenatis lectus nulla sed augue. Quisque lacinia semper lacus, nec ultricies justo auctor vel. Aenean viverra aliquam est ac porttitor.

Aliquam egestas elementum enim, id porta libero sodales ac. Fusce mattis ultrices tortor, eget iaculis nibh ultrices et. Fusce eget ligula quam. Vivamus id nisi non sapien venenatis adipiscing. Mauris posuere imperdiet elit, vitae accumsan nibh vehicula eget. Curabitur et magna mi, vel elementum velit. Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos himenaeos. Donec placerat arcu eget eros ornare viverra.

### 2013-02-27 thesis/disclaimer.tex
Added thesis as of 27 Feb

\section*{Disclaimer}

I hereby declare that the work in this thesis is that of the candidate
alone, except where indicated below or in the text of the thesis. The work was undertaken between February 2010 and July 2013 at the Australian National University, Canberra, except for the period between July 2012 and December 2012 where the work was undertaken at the Massachusetts Institute of Technology, Boston. It has not been submitted in whole or in part for any other degree at this or any other university.

\vspace{1cm}
\begin{flushright}
\includegraphics[width=0.4\linewidth]{signature.png}\\[2mm]
\fullname

\fullthesisdate
\end{flushright}

### 2013-02-27 thesis/introduction/introduction.tex
Added thesis as of 27 Feb

\chapter{Introduction}\label{introduction}

\epigraph{The labour of the astronomer in the present state of his art is much like that of one who should examine, grain by grain, the sands of the sea in the certainty that among them numerous grains must exist of extraordinary value\dots}{-- Sir John Herschel\footnotemark}

\footnotetext{\emph{Memoirs of the Royal Astronomical Society.} 1826, Vol.\ 2, p472}

\section{The first of many sections}

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Duis posuere tellus eu quam pellentesque ut varius purus egestas. Nam hendrerit malesuada sapien, non molestie risus cursus at. Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas. Sed dignissim sodales sem sed volutpat. Ut laoreet, ante sed dictum vestibulum, lacus sapien semper dui, nec rutrum velit justo eu enim. Fusce vehicula blandit ipsum, ac volutpat libero vestibulum in. Sed quis lacus mauris. Quisque congue elit in nisi lacinia ac condimentum eros pellentesque. Quisque et nisl odio, vitae eleifend neque. Oh look, a sneaky citation to my paper \citep[][of which I am a co-author]{Kastner12}.

Phasellus erat libero, lobortis vitae iaculis nec, congue et tortor. Donec tempus leo et nisl tincidunt porta. Nulla velit sapien, sollicitudin sit amet accumsan a, facilisis a est. Phasellus scelerisque convallis sapien, nec viverra dui tincidunt a. Nulla ligula velit, laoreet fringilla condimentum sed, euismod a est. Fusce leo sapien, rhoncus a ultricies nec, porttitor ut lectus. Sed vestibulum turpis risus, nec vestibulum diam. Morbi quis quam quis enim cursus aliquam scelerisque quis tellus. Pellentesque accumsan lectus cursus massa ultrices placerat. Nulla facilisi. Praesent fermentum erat in augue sagittis condimentum. Nullam posuere blandit urna a mollis. Cras malesuada lectus a turpis sollicitudin volutpat. Morbi semper, nisl vel mattis vehicula, sapien sapien adipiscing tortor, in accumsan tortor dolor non neque. Maecenas varius, nunc ut euismod volutpat, mauris ante faucibus magna.

\subsection{A subsection}

Vestibulum sed orci nec diam euismod vehicula vitae et mauris. Phasellus sagittis justo quis mauris adipiscing auctor. Suspendisse nibh erat, cursus vitae aliquam in, rutrum sed est. Nunc mollis quam quis velit vehicula fringilla. Quisque convallis, neque ut faucibus luctus, nisl ante porttitor ante, at venenatis lectus nulla sed augue. Quisque lacinia semper lacus, nec ultricies justo auctor vel. Aenean viverra aliquam est ac porttitor.

% THIS FIGURE USES THE \echa MACRO DEFINED IN macros.tex
\begin{figure}[t!]
\vspace{-4mm}
   \centering
   \includegraphics[width=\textwidth]{etacha} 
   \caption[{The \object[ETA CHA CLUSTER]{$\eta$ Chamaeleontis} open cluster}]{$0.9\times0.9$~deg DSS2-IR image showing the 18 member systems of the \echa\ cluster. The bright star at the centre of the image is the eponymous \echa. The bar shows the linear scale at the 94.3~pc cluster distance.}
   \label{fig:etacha}
\end{figure}

\section{Wow, another section heading!}

Sed tempor imperdiet rhoncus. Cras mi neque, pellentesque ac ultricies vitae, feugiat ut ante. Suspendisse vestibulum venenatis odio, quis pharetra mauris dapibus in. Pellentesque sagittis laoreet mi sed vestibulum. Ut iaculis venenatis urna eu tincidunt. Duis consequat est ut velit rutrum vitae placerat dolor eleifend. Nullam eget nulla massa, non accumsan libero. Sed auctor velit bibendum nisl tincidunt aliquam. Aenean pellentesque eros a lectus imperdiet rhoncus. Another citation to one of my papers \citep{Riedel11}.

Nunc non odio leo. Phasellus sodales pretium nunc suscipit bibendum. Nullam lorem turpis, varius sed bibendum id, interdum sed lectus. Ut rutrum, orci in adipiscing accumsan, velit massa dapibus metus, id volutpat nulla eros eget lorem. Ut massa massa, ornare vitae elementum ut, consequat a justo. Vestibulum tempus fermentum commodo. In vel auctor nisi. Mauris id turpis nisi. Nulla eget magna eu magna rhoncus pulvinar. Morbi enim ligula, feugiat et rutrum in, posuere eget lacus. Suspendisse adipiscing, erat in hendrerit dictum, est tellus vestibulum justo, et sodales mi dolor sed purus.

In porttitor purus et metus adipiscing molestie. Curabitur scelerisque, sem ac sodales sodales, neque metus commodo massa, eu pulvinar ante lectus eu orci. Mauris non odio vel enim scelerisque porttitor ac ac lacus. Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas. Phasellus id dolor dui. Cras non neque vel turpis posuere commodo et nec leo. Nulla dictum rutrum nisi ac rhoncus. Aenean lobortis tempor magna viverra iaculis. Ut sit amet nunc mi. Integer iaculis condimentum diam non dignissim. Duis bibendum auctor velit id scelerisque.

Nulla tincidunt tortor ac odio posuere eget semper mauris tristique. Vestibulum congue magna sed arcu tincidunt id pharetra nisi hendrerit. Duis erat nulla, fringilla sed tempus at, sodales a libero. Nunc ullamcorper dapibus dui, ut varius tellus ullamcorper quis. Pellentesque odio lacus, molestie quis porta vitae, ornare eget massa. Integer hendrerit sapien ac massa lobortis in malesuada quam dignissim. Aliquam feugiat, nisl ut semper auctor, purus nunc iaculis ipsum, non tristique nibh felis a ipsum. Pellentesque odio lacus, molestie quis porta vitae, ornare eget massa. Ut sit amet nunc mi. Integer iaculis condimentum diam non dignissim. Duis bibendum auctor velit id scelerisque.

You can click on objects and be taken to their SIMBAD entry, like this: \object{Large Magellanic Cloud}. All of the objects in Table~\ref{table:etacha} are resolvable in SIMBAD.

% I think ctable gives the best LaTeX tables, once you get to know its syntax. All of the objects in this table are resolvable in SIMBAD using the \object{} command defined in macros.tex

\ctable[caption={Census of the \object[ETA CHA CLUSTER]{$\eta$ Chamaeleontis cluster} prior to this work},label=table:etacha,doinside=\small \setlength{\extrarowheight}{0pt}
,captionskip=0pt,pos=b]{lcccccccc}
{\tnote[$\dagger$]{\citet{Murphy10} (K and M members), \citet{Murphy11} (early-type members)}
\tnote[$\ddag$]{Photometry from \citet{Bessell12}}
\tnote[$\star$]{\object[ECHA J0844.2-7833]{ECHA J0844.2} has an elevated position in the cluster CMD}
}{
\toprule[2pt]
Name & Right Ascension & Declination & Spectral & $V$\tmark[$\ddag$] & Binary?\tmark[$\star$]\\
 & [J2000 deg] & [J2000 deg] & Type\tmark[$\dagger$] & [mag]\\
\midrule
 \object[ECHA J0836.2-7908]{ECHA J0836.2$-$7908} & 08 36 10.6 & $-$79 08 18 & M5.3 & 17.66 & suspected\\
  \object{RECX 1} & 08 36 56.2 & $-$78 56 46 & K7.0 & 10.61 & yes\\
  \object[ECHA J0838.9-7916]{ECHA J0838.9$-$7916} & 08 38 51.5 & $-$79 16 14 & M5.0 & 16.82 & suspected\\
  \object[ETA CHA]{$\eta$ Cha} (\object{RECX 2}) & 08 41 19.5 & $-$78 57 48 & B8V & 5.46& suspected\\
  \object[ECHA J0841.5-7853]{ECHA J0841.5$-$7853} & 08 41 30.6 & $-$78 53 07 & M4.7 & 17.07 & \\
  \object{RECX 3} & 08 41 37.2 & $-$79 03 31 & M3.0 & 14.35 \\
  \object{HD 75505} & 08 41 44.7 & $-$79 02 53 & A6 & 7.27\\
  \object{RECX 4} & 08 42 23.7 & $-$79 04 04 & M1.3 & 12.79\\
  \object{RECX 5} & 08 42 27.3 & $-$78 57 49 & M3.8 & 15.20\\
  \object{RECX 6} & 08 42 39.0 & $-$78 54 44 & M3.0 & 14.08\\
  \object{RECX 7} & 08 43 07.7 & $-$79 04 52 & K6.9 & 10.84 & yes\\
  \object{RS Cha} (\object{RECX 8}) & 08 43 12.2 & $-$79 04 12 & A8V+A8V & 6.28 & triple?\\
  \object[ECHA J0843.3-7905]{ECHA J0843.3$-$7905} & 08 43 18.4 & $-$79 05 21 & M3.4 & 13.97\\
  \object[ECHA J0844.2-7833]{ECHA J0844.2$-$7833} & 08 44 09.1 & $-$78 33 46 & M5.5 &  & suspected\\
  \object{RECX 9} & 08 44 16.6 & $-$78 59 09 & M4.4 & 15.00 & yes\\
  \object{RECX 10} & 08 44 32.2 & $-$78 46 32 & M0.3 & 12.53\\
  \object{RECX11} & 08 47 01.8 & $-$78 59 35 & K6.5 & 11.13\\
  \object{RECX 12} & 08 47 56.9 & $-$78 54 54 & M3.2 & 13.17 & suspected\\
\bottomrule[2pt]
}

### 2013-02-27 thesis/topdf.sh

@@ -1,0 +1,19 @@
+#!/bin/bash
+
+# necessary to add more chapters to this list as you need them
+export TEXINPUTS="`pwd`/introduction//:`pwd`/chapter1//:`pwd`/conclusions//:`pwd`/appendices//:`pwd`:"
+
+TEX_CMD='pdflatex '
+TEX_OPTS = ''
+
+${TEX_CMD} ${TEX_OPTS} thesis.tex || exit 1
+bibtex thesis || exit 1
+${TEX_CMD} ${TEX_OPTS} thesis.tex || exit 1
+${TEX_CMD} ${TEX_OPTS} thesis.tex || exit 1
+${TEX_CMD} ${TEX_OPTS} thesis.tex || exit 1
+${TEX_CMD} ${TEX_OPTS} thesis.tex || exit 1
+rm *.aux
+mv thesis.* output/.
+mv output/thesis.tex .
+cp output/thesis.pdf .
+

### 2013-02-28 2012-aqs/draft-aqs.tex
Updated AQS paper

@@
 \usepackage{amssymb,graphics} % for resolution symbol
-\usepackage{longtable}
+\usepackage{longtable,booktabs,multirow}
+\usepackage{pdflscape,rotating}
 
@@
 % - Add in-line text referencing standard star chemical abundances
-% - Uncertainty analysis
+% - Uncertainty analysis for a standard star
+% - Uncertainty analysis for a prgram star
 % [DONE] Equivalent widths significant figures.
@@
 % - Carbon
+% - Lanthinum? Europium?
 % - Distance calculations revision with B-V (if available) instead of (J-K)
@@
 \author{Andrew R.
-Casey\altaffilmark{2,3}, Stefan Keller\altaffilmark{2}, Alan Alves-Brito\altaffilmark{2}, Anna Frebel\altaffilmark{3}, Gary Da Costa\altaffilmark{2}, Kevin Schalufman\altaffilmark{3}, Heather Jacobson\altaffilmark{3}, QinQin Yu\altaffilmark{3}, Amanda Karakas\altaffilmark{2}, David Yong\altaffilmark{2}, Ken Freeman\altaffilmark{2}}
+Casey\altaffilmark{2,3}, Stefan Keller\altaffilmark{2}, Alan Alves-Brito\altaffilmark{2}, Anna Frebel\altaffilmark{3}, Gary Da Costa\altaffilmark{2}, Kevin Schalufman\altaffilmark{3}, Amanda Karakas\altaffilmark{2}, David Yong\altaffilmark{2}, Heather Jacobson\altaffilmark{3}, QinQin Yu\altaffilmark{3}, Ken Freeman\altaffilmark{2}}
 \altaffiltext{1}{This paper includes data gathered with the 6.5 meter Magellan Telescopes located at Las Campanas Observatory, Chile.}
@@
 However, we find no evidence that the stream is a result of a classical disrupted globular cluster.
-Our data indicate the Aquarius stream has a  metallicity dispersion of $\sigma(\mbox{[Fe/H}]) = 0.32$\,dex.
+Our data indicate the Aquarius stream has a  metallicity dispersion of $\sigma(\mbox{[Fe/H}]) = 0.32$\,dex, ranging between $\mbox{[Fe/H]} = -0.65$ to $-1.60$\,dex.
 No inverse Na-O correlation is present, and we find a positive Mg-Al relationship.
@@
 As such, their phase-space information can collectively constrain the fraction and distribution of accreted matter in the galaxy, the sub-halo mass function, as well as the shape and extent of dark matter in the Milky Way.
-Moreover, individual chemical abundances can constrain the  precise nucleosynthesis sites where elements are forged, as well as trace the chemical evolution of the galaxy.
+Moreover, individual chemical abundances can trace the chemical evolution of the galaxy.
+% can constrain the  precise nucleosynthesis sites where elements are forged, as well as
 
 % Consider adding a final sentence about the amount of work that has gone into stellar streaams
-Wide-field surveys have proved excellent sources for finding stellar streams.
+Wide-field imaging surveys have proved excellent sources for finding stellar streams.
 Dozens have been identified through photometric selections and matched-filtering techniques, with some to a galactocentric distance of 100\,kpc \citep{belokurov;et-al_2007,drake;et-al_2013}.
@@
 However, as \citet{helmi;white_1999} point out, these observing strategies are only successful for identifying streams that are sufficiently distant from the solar neighbourhood.
-A nearby stream, within $\sim$10\,kpc, will not appear as an over-density, as the stars would be sparsely positioned across the sky.
-Such substructures would only be detectable by their kinematics, or perhaps precise chemical abundances through a `chemical tagging' approach (e.g.
+A nearby stream, within $\sim$10\,kpc, will not appear as an over-density as the stars would be sparsely positioned across the sky.
+Such substructures would only be detectable by their kinematics, or perhaps with precise chemical abundances through a `chemical tagging' approach (e.g.
 see \citet{freeman;bland-hawthorn_2002}).
@@
 With the exception of bulge stars, where some photometric cuts were employed, all stars between 9 $<$ I $<$ 13 were observed.
-Almost all of these candidates have published radial velocity measurements \citep{steinmetz;et-al_2006}, and for a subset of stars with sufficient Signal-to-Noise ($S/N$), estimates of stellar parameters have been derived using a $\chi^2$ minimization technique \citep{zwitter;et-al_2008, siebert;et-al_2011}.
+Almost all of these candidates have published radial velocity measurements \citep{steinmetz;et-al_2006}, and for a subset of stars with a sufficient Signal-to-Noise ($S/N$) ratio, estimates of stellar parameters have been derived using a $\chi^2$ minimization technique \citep{zwitter;et-al_2008, siebert;et-al_2011}.
 
@@
 The predicted particles in each model between $-70\,^\circ < b < -50\,^\circ$ were binned in $\Delta{l} \times \Delta{V_{\rm hel}}$ blocks using varying grid cell sizes between $25\,^\circ$ to $70\,^\circ$ and $20\,\mbox{km s}^{-1}$ to $100\,\mbox{km s}^{-1}$.
-The RAVE sample was binned in the same way, and the statistical significance of the observed over-density is discretized.
+The RAVE sample was binned in the same way, discretizing the statistical significance of the observed over-density.
 \citet{williams;et-al_2011} found the stream to be statistically significant ($>$4-$\sigma$) in 96\% of the cell proportions employed for the Besan\c{c}on model.
-By sampling the Galaxia model repeatedly with varying extinction rates, a similar result was found: between $75\pm15$\,\% to $80\pm18$\,\% of grid cells showed the Aquarius stream to significant at the 4-$\sigma$ level or higher.
+By sampling the Galaxia model repeatedly with varying extinction rates, a similar result was found: between $75\pm15$\,\% to $80\pm18$\,\% of grid cells showed the Aquarius stream to be significant at the 4-$\sigma$ level or higher.
 Given the high-latitude and proximity of the stream, it is not surprising that dust had a negligible effect on the statistical significance.
-\citet{williams;et-al_2011} concluded that the over-density in $l, V_{\rm hel}$ is a true substructure, and neither the choice of galaxy model, cell dimension, nor the extinction model made any real difference to the detection significance.
+\citet{williams;et-al_2011} concluded that the over-density in $l, V_{\rm hel}$ is a true substructure, and neither the choice of galaxy model, cell dimension, nor the extinction rate made any real difference to the detection significance.
 
@@
 While the exact formation site is still under debate, the chemical relationship is well-established empirically.
-The Na-O pattern provides the best chemical evidence that their chemical enrichment history has been dominated by Type \textsc{ii} Supernova (SN) events and that those stars formed in a globular cluster-like environment.
+The Na-O pattern provides the best chemical evidence that their enrichment history has been dominated by Type \textsc{ii} Supernova (SN) events, and that those stars formed in a globular cluster-like environment.
 
@@
 
-From high-resolution spectroscopy of five candidate Aquarius stars, four of which had sodium and oxygen abundance measurements, \citet{wylie-de-boer;et-al_2012} found two stars with super-solar sodium; slightly higher [Na/Fe] ratios than halo stars of the same metallicity.
+From high-resolution spectroscopy of six candidate Aquarius stars, four of which have sodium and oxygen abundance measurements, \citet{wylie-de-boer;et-al_2012} found two stars with super-solar sodium; slightly higher [Na/Fe] ratios than halo stars of the same metallicity.
 However, no strong oxygen depletion was evident in the data.
@@
 Combined with the low level of chemical scatter present in their sample, these chemical indicators led \citet{wylie-de-boer;et-al_2012} to conclude that the Aquarius stream is the result of a tidally disrupted globular cluster.
-\citet{williams;et-al_2011} had previously precluded this possibility with any known globular clusters after modelling an Aquarius-like progenitor infalling onto the Milky Way and comparing the predicted $l, b, V_{\rm hel}$ with known, nearby globular clusters of similar metallicities.
+\citet{williams;et-al_2011} had previously precluded this possibility with any known clusters after modelling an Aquarius-like progenitor infalling onto the Milky Way and comparing the predicted $l, b, V_{\rm hel}$ with known, nearby globular clusters of similar metallicities.
 No known globular cluster could match their simulation.
@@
 HD 142948		& 16:00:01.6 & $-$53:51:04.1		& 2011-03-14	& 1.107	& 1.0 & \dots 	& 320 & 5.3			& 29.9 		& 0.1 \\
+\hline
 
@@
 \enddata
-\tablenotetext{a}{S/N measured at 6000 \AA{} for each target.}
+\tablenotetext{a}{S/N measured at 600\,nm for each target.}
 \end{deluxetable*}
@@
 The supplementary star, J2306265-085103, was observed by the RAVE survey but had a $S/N$ ratio too low for stellar parameters to be accurately determined.
-All program stars were observed in July 2011 in good seeing at low airmass (Table \ref{tab:observations}), and five additional standard stars were observed in March 2011.
+All program stars were observed in July 2011 in good seeing at low airmass (Table \ref{tab:observations}), and six  standard stars were observed in March 2011.
 All observations were taken using a 1.0'' slit, providing a spectral resolution of $\mathcal{R} = 28,000$ in the blue arm and $\mathcal{R} = 22,000$ in the red arm.
-The total exposure times for our program stars varied to ensure a $S/N$ ratio in excess of 100\,pixel$^{-1}$ at 600\,nm.
+The exposure time for our program stars was 650\,s, in order to ensure a $S/N$ ratio in excess of 100\,pixel$^{-1}$ at 600\,nm.
 
@@
 The data were reduced using the CarPy pipeline\footnote{http://code.obs.carnegiescience.edu/mike}.
-One standard stars, HD 41667, was also reduced using standard extraction and calibration methods in \textsc{iraf}.
+One standard star, HD 41667, was also reduced using standard extraction and calibration methods in \textsc{iraf}.
 The resultant spectra from both approaches were compared for residual fringing, $S/N$, and wavelength calibration.
-No noteworthy differences were present, and the CarPy pipeline was utilized for the remainder of the data reductions.
+No noteworthy differences were present, and the CarPy pipeline was utilized for the remainder of the data reduction.
 Each reduced echelle order was carefully normalized using a third order spline with defined knot spacing.
@@
 
-The white dwarf HR 6141 was observed on X as a telluric standard.
+The white dwarf HR 6141 was observed in March 2011 as a telluric standard.
 The $S/N$ ratio for HR 6141 exceeds that in any of our standard or program stars.
 Although the atmospheric conditions at Las Campanas Observatory are certain to change throughout the night and between observing runs, we are primarily using this spectra to identify lines that are affected by telluric absorption.
-Critical transitions necessary for abundance analyses that are affected by the Earth's atmosphere are corrected for telluric absorption.
+However, critical transitions necessary for abundance analyses that are affected by the Earth's atmosphere have been corrected for telluric absorption.
+The details of these corrections are discussed on a line-by-line basis.
 
@@
 
-\noindent where the rest wavelength ($\lambda_{r}$) and standard deviation\footnote{Recall $\rm{FWHM} = 2\sigma\sqrt{2\log_e{2}}$} ($\sigma$) are free parameters in the iterative fitting process.
+\noindent where the rest wavelength ($\lambda_{r}$) and profile sigma\footnote{Recall $\rm{FWHM} = 2\sigma\sqrt{2\log_e{2}}$} ($\sigma$) are free parameters in the iterative fitting process.
 As a consequence of Eq.
@@
 Although this approach relies on a reasonably accurate initial radial velocity correction of $<$4\,km s$^{-1}$ \--- which is easily achieved \--- it greatly improves the accuracy and robustness of the equivalent width measurements.
+
+% equivalent widths plot with Norris for HD 122563
+\begin{figure}[h]
+	\includegraphics[width=\columnwidth]{./figures/smh-norris.pdf}
+	\caption{A comparison showing equivalent widths measured for HD 140283 using our automatic routine (see \S\ref{sec:line-measurements}), and those found by careful hand measurements in \citet{norris;et-al_1996}.
+No systematic trend is present, and the mean difference between these studies is $\langle\Delta{}W_\lambda\rangle = -0.64 \pm 2.78$ m\AA{}.}
+	\label{fig:ew-compare}
+\end{figure}
 
@@
 The mean difference is a negligible $-0.64 \pm 2.78$\,m\AA{}, and no systematic trend is present.
-We note that the scatter may be directly attributed to the observed $S/N$ ratio, as other studies \citep{frebel;et-al_2013} using the same equivalent width measurement software described here find better agreement with hand measurements for spectra with higher $S/N$ ratios: $0.20 \pm 0.16$\,m{\AA} with \citet{aoki;et-al_2007} and $0.25 \pm 0.28$\,m{\AA} with \citet{cayrel;et-al_2004} for a spectrum of HD 122563 with $S/N > 300$\,pixel$^{-1}$.
-
-% equivalent widths plot with Norris for HD 122563
-\begin{figure}[h]
-	\includegraphics[width=\columnwidth]{./figures/smh-norris.pdf}
-	\caption{A comparison showing equivalent widths measured for HD 140283 using our automatic routine (see \S\ref{sec:line-measurements}), and those found by careful hand measurements in \citet{norris;et-al_1996}.
-No systematic trend is present, and the mean difference between these studies is $\langle\Delta{}W_\lambda\rangle = -0.64 \pm 2.78$ m\AA{}.}
-	\label{fig:ew-compare}
-\end{figure}
-
-\begin{deluxetable*}{cccccccccc}
-\tabletypesize{\scriptsize}
-\tablecaption{List of Line Transitions and Equivalent Width Measurements\label{tab:equivalent-widths}}
-\tablehead{
-	& & & & \multicolumn{5}{c}{Equivalent Width} \\
+We note that the scatter may be directly attributed to the observed $S/N$ ratio, as other studies (Frebel et al.
+2013, submitted) using the same equivalent width measurement software described here find better agreement with hand measurements for spectra with higher $S/N$ ratios: $0.20 \pm 0.16$\,m{\AA} with \citet{aoki;et-al_2007} and $0.25 \pm 0.28$\,m{\AA} with \citet{cayrel;et-al_2004} for a spectrum of HD 122563 with $S/N > 300$\,pixel$^{-1}$.
+
+\begin{longtable*}{ccccccccc}
+\caption{\\ List of Line Transitions and Equivalent Width Measurements} \tabularnewline
+\cline{1-9}
+& & & & \multicolumn{5}{c}{Equivalent Widths} \\
 \cline{5-9} \\
-	\colhead{Wavelength} &
-	\colhead{Transition} &
-	\colhead{LEP} &
-	\colhead{$\log{gf}$} &
-	\colhead{C2225316-14437} &
-	\colhead{C2306265-085103} &
-	\colhead{J221821-183424} &
-	\colhead{J223504-152834} &
-	\colhead{J223811-104126} \\
-	({\AA})	& & (eV) & & (m{\AA}) & (m{\AA}) & (m{\AA}) & (m{\AA}) & (m{\AA}) 
-}
-\startdata 
+Wavelength & Transition & $\chi$ & $\log{gf}$ & C2225316-14437 & C2306265-085103 & J221821-183424 & J223504-152834 & J223811-104126 \\
+({\AA}) & & (eV) & & (m{\AA}) & (m{\AA}) & (m{\AA}) & (m{\AA}) & (m{\AA}) \\
+\cline{1-9} \\
+\endhead
+\hline
+\endfoot
+\hline
+\endlastfoot
  6300.300 &       8.0 &      0.00 &    --9.717 &      45.4 &      66.9 &      38.5 &      32.8 &      17.9 \\
@@
  6645.110 &      63.1 &      1.38 &      0.204 &      24.5 &      27.8 &      17.0 &      30.3 &   \nodata \\
-\enddata
-\end{deluxetable*}
+\hline
+\end{longtable*}
 
@@
 				& \citet{fulbright_2000} \\
-
 HD 76932		& 5755 & 3.85 & 1.41 & $-$1.06
-				\\
-
-HD 136316		& 4350 & 0.65 & 1.83 & $-$1.92 \\
-
-HD 141531		& 4295 & 0.60 & 1.86 & $-$1.74 \\
-
+				& 5849 & 4.11 & \nodata & $-$0.88 
+				& \citet{nissen;et-al_2000} \\
+HD 136316		& 4350 & 0.65 & 1.83 & $-$1.92 
+				& 4414 & 0.94 & 1.70 & $-$1.90 
+				& \citet{gratton_sneden_1991} \\
+HD 141531		& 4295 & 0.60 & 1.86 & $-$1.74 
+				& 4280 & 0.70 & 1.60 & $-$1.68
+				& \citet{shetrone_1996} \\
 HD 142948		& 4950	& 2.19	& 1.78	& $-$0.79
@@
 				& \citet{gratton;et-al_2000} \\
-\\
+\hline \\
 
@@
 
-\begin{figure*}[t!]
-	\includegraphics[width=\textwidth]{./figures/spectra-h-alpha.pdf}
-	\caption{Sample spectra of the H-$\alpha$ region for all Aquarius stream candidates.}
-	\label{fig:spectra-h-alpha}
-\end{figure*}
-
 \subsubsection{Effective Temperature}
@@
 The \citet{casagrande;et-al_2010} relationship is also in relatively good agreement (most within 100\,K, largest discrepancy is 220\,K) with our spectroscopic temperatures, although we note that this relation was derived primarily for dwarfs/sub-giants and our candidates are all giant stars.
+
+\begin{figure*}[t!]
+	\includegraphics[width=\textwidth]{./figures/spectra-h-alpha.pdf}
+	\caption{Sample spectra of the H-$\alpha$ region for all Aquarius stream candidates.}
+	\label{fig:spectra-h-alpha}
+\end{figure*}
 
@@
 Although this discrepancy is not negligible, there are limited lines available for comparison, and our $\langle$Fe\,\textsc{i}$ - $Fe\,\textsc{ii}$\rangle$ abundances are in good agreement.
-
-\subsubsection{Aluminium}
-There are six aluminium transition lines available in our optical spectra.
-The strongest of these lines occur at 3944 and 3961\,{\AA}, and are visible in all of our stars.
-However, this is a particularly crowded spectral region: the lines fall between the strong Ca H and K lines, with the 3961\,{\AA} transition clearly in the wing of the Ca H line.
-This makes the continuum determination and subsequent aluminium measurement non-trivial, especially given the metallicity of our stars.
-Additionally, the 3944 and 3961 lines suffer from appreciable departures from LTE, resulting in under-estimated abundances by up to $\sim$0.60\,dex \citep{baumueller;gehren_1997}.
-Instead, we have measured Al abundances from other available transitions: the Al \textsc{i} lines at 6696, 6698, 7835 and 7836\,{\AA}.
-Although these lines are weaker than the bluer Al \textsc{i} lines, their surrounding regions are uncrowded from strong absorption lines.
-
-Generally the four Al \textsc{i} lines are in reasonable agreement with one another, yielding random scatter of less than 0.05\,dex.
-However, these lines were not always detected in the data.
-The strength of the lines is noticeably weakened below a 3-$\sigma$ detection with decreasing metallicity and increasing temperature.
-For our most metal-poor star, J221821, only a single Al \textsc{i} line was detectable, and so we have adopted a conservative uncertainty of 0.10\,dex.
-
-\subsubsection{Iron-peak Elements (Sc, V, Cr and Mn)}
-
-As expected, the Fe-peak elemental abundances exhibit similar trends (Figure \ref{fig:fe-peak-elements}).
-The noteworthy exception is chromium, where the median abundance is $\mbox{[Cr/Fe]} = -0.08 \pm 0.12$ and does not appear to vary with overall metallicity.
-The number of clean, suitable Cr \textsc{i} lines available between candidates fluxuated from three to twelve.
-Very little line-to-line scatter is present in both Cr \textsc{i} and \textsc{ii}: the random scatter is below 0.04\,dex for most stars, with the isolated example of J223504 where $\sigma(\mbox{[Cr \textsc{ii}/Fe]}) = 0.29$\,dex, and only three lines were available.
-The Cr \textsc{i} and \textsc{ii} abundances for J223504 are in good agreement (0.05\,dex), and since none of the measured profiles were particularly unusual, we chose not to exclude outlier measurements.
-For all other stars, the Cr \textsc{i} $-$ Cr \textsc{ii} abundance differences varied between 0.02\,dex up to 0.31\,dex.
-The largest discrepancy occurred in our hottest star, where fewer chromium transitions were detected.
-
-All other iron peak elements considered (Sc, V, Mn) all exhibit a slight downward trend in metallicity, with manganese demonstrating the most prominent gradient: varying between $\mbox{[Mn/Fe]} = -0.52$\,dex to $+0.31$\,dex in the most metal-poor and -rich stars respectively.
-The [Sc/Fe] measurements presented in Figure \ref{fig:fe-peak-elements} are calculated from six clean Sc \textsc{ii} lines, and there is very minimal line-to-line scatter, the largest of which is 0.06\,dex.
-Three Aquarius stream stars display [Sc/Fe] $\sim$ +0.20, while J221821 and J223811 have $\mbox{[Sc/Fe]} = 0.01$ and 0.05\,dex, respectively.
-
-% Iron peak elements
-\begin{figure}[h]
-	\includegraphics[width=\columnwidth]{./figures/aquarius-fe-peak.pdf}
-	\caption{Iron peak elements for all stars.}
-	\label{fig:fe-peak-elements}
-\end{figure}
-
-\subsubsection{Nickel}
-Most Aquarius stream stars have seven clean Ni\,\textsc{i} transitions available. These lines are in excellent agreement, with typical scatter of 0.03\,dex.
-% nickel abundances in standard stars
-
-\subsubsection{Barium}
-%Barium is a neutron-capture element, primarily produced through the \textit{s}-process, but can be forged from a variety of nucleosynthetic processes.
-
-Measuring barium requires some careful consideration.
-The strong resonance lines at 4554 {\AA} and 4934 {\AA} have appreciable hyperfine splitting, which can result in over-estimated abundances if unaccounted for.
-There are a few singly ionized lines available in our spectra that do not suffer from strong hyperfine splitting, namely the 5853, 6141 and 6496 {\AA} transitions.
-Depending on the radial velocity of the star, sometimes our 6496 {\AA} line was affected by small amounts of telluric absorption.
-In these cases the line was discarded.
-The abundances tabulated in Table \ref{tab:program-star-abundances} are based on the remaining clean Ba \textsc{ii} lines at 5853 and 6141 {\AA}, which are generally in good agreement with each other, and the 6496 {\AA} line where available.
-
-Our standard stars have [Ba/Fe] abundances very typical of the Milky Way halo.
-Only one of our standard stars, HD 44007, has published [Ba/Fe] abundances from high-resolution spectra.
-We find HD 44007 to have $\mbox{[Ba/Fe]} = -0.05 \pm 0.04$, which is at the mid-point of existing published measurements from \citet{fulbright_2000} and \citet{burris;et-al_2000} of $-0.27$ and 0.05 dex, respectively.
-
-With one exception, the Aquarius stream candidates have barium abundances that are quite similar to the stellar halo, ranging between $\mbox{[Ba/Fe]} = -0.02$ to 0.15 dex.
-The exception is C2225316, which has an anomalously high barium abundance of $\mbox{[Ba/Fe]} = 0.70$ dex.
-This is ${\sim}$0.70 dex higher than the Milky Way trend at its given $\mbox{[Fe/H]} = -1.26$ dex.
-Our three Ba \textsc{ii} lines in C2225316 are in excellent agreement: 0.67, 0.68, and 0.72 dex.
-The 6496\,{\AA} transition in C2225316 has a negligible telluric contribution and was included for this candidate.
-At least in Al, Si, Cr and Ba content (see sections \ref{sec:aluminium-abundance}, \ref{sec:alpha-elements}, \ref{sec:iron-peak-elements}), C225316 appears to be chemically distinct from the other Aquarius stream stars in our sample.
 
@@
 
+\subsubsection{Aluminium}
+There are six aluminium transition lines available in our optical spectra.
+The strongest of these lines occur at 3944 and 3961\,{\AA}, and are visible in all of our stars.
+However, this is a particularly crowded spectral region: the lines fall between the strong Ca H and K lines, with the 3961\,{\AA} transition clearly in the wing of the Ca H line.
+This makes the continuum determination and subsequent aluminium measurement non-trivial, especially given the metallicity of our stars.
+Additionally, the 3944 and 3961 lines suffer from appreciable departures from LTE, resulting in under-estimated abundances by up to $\sim$0.60\,dex \citep{baumueller;gehren_1997}.
+Instead, we have measured Al abundances from other available transitions: the Al \textsc{i} lines at 6696, 6698, 7835 and 7836\,{\AA}.
+Although these lines are weaker than the bluer Al \textsc{i} lines, their surrounding regions are uncrowded from strong absorption lines.
+
+Generally the four Al \textsc{i} lines are in reasonable agreement with one another, yielding random scatter of less than 0.05\,dex.
+However, these lines were not always detected in the data.
+The strength of the lines is noticeably weakened below a 3-$\sigma$ detection with decreasing metallicity and increasing temperature.
+For our most metal-poor star, J221821, only a single Al \textsc{i} line was detectable, and so we have adopted a conservative uncertainty of 0.10\,dex.
+
+\subsubsection{Iron-peak Elements (Sc, V, Cr and Mn)}
+
+As expected, the Fe-peak elemental abundances exhibit similar trends (Figure \ref{fig:fe-peak-elements}).
+The noteworthy exception is chromium, where the median abundance is $\mbox{[Cr/Fe]} = -0.08 \pm 0.12$ and does not appear to vary with overall metallicity.
+The number of clean, suitable Cr \textsc{i} lines available between candidates fluxuated from three to twelve.
+Very little line-to-line scatter is present in both Cr \textsc{i} and \textsc{ii}: the random scatter is below 0.04\,dex for most stars, with the isolated example of J223504 where $\sigma(\mbox{[Cr \textsc{ii}/Fe]}) = 0.29$\,dex, and only three lines were available.
+The Cr \textsc{i} and \textsc{ii} abundances for J223504 are in good agreement (0.05\,dex), and since none of the measured profiles were particularly unusual, we chose not to exclude outlier measurements.
+For all other stars, the Cr \textsc{i} $-$ Cr \textsc{ii} abundance differences varied between 0.02\,dex up to 0.31\,dex.
+The largest discrepancy occurred in our hottest star, where fewer chromium transitions were detected.
+
+All other iron peak elements considered (Sc, V, Mn) all exhibit a slight downward trend in metallicity, with manganese demonstrating the most prominent gradient: varying between $\mbox{[Mn/Fe]} = -0.52$\,dex to $+0.31$\,dex in the most metal-poor and -rich stars respectively.
+The [Sc/Fe] measurements presented in Figure \ref{fig:fe-peak-elements} are calculated from six clean Sc \textsc{ii} lines, and there is very minimal line-to-line scatter, the largest of which is 0.06\,dex.
+Three Aquarius stream stars display [Sc/Fe] $\sim$ +0.20, while J221821 and J223811 have $\mbox{[Sc/Fe]} = 0.01$ and 0.05\,dex, respectively.
+
+% Iron peak elements
+\begin{figure}[h]
+	\includegraphics[width=\columnwidth]{./figures/aquarius-fe-peak.pdf}
+	\caption{Iron peak elements for all stars.}
+	\label{fig:fe-peak-elements}
+\end{figure}
+
+\subsubsection{Nickel}
+Most Aquarius stream stars have seven clean Ni\,\textsc{i} transitions available. These lines are in excellent agreement, with typical scatter of 0.03\,dex.
+% nickel abundances in standard stars
+
+\subsubsection{Barium}
+%Barium is a neutron-capture element, primarily produced through the \textit{s}-process, but can be forged from a variety of nucleosynthetic processes.
+
+Measuring barium requires some careful consideration.
+The strong resonance lines at 4554 {\AA} and 4934 {\AA} have appreciable hyperfine splitting, which can result in over-estimated abundances if unaccounted for.
+There are a few singly ionized lines available in our spectra that do not suffer from strong hyperfine splitting, namely the 5853, 6141 and 6496 {\AA} transitions.
+Depending on the radial velocity of the star, sometimes our 6496 {\AA} line was affected by small amounts of telluric absorption.
+In these cases the line was discarded.
+The abundances tabulated in Table \ref{tab:program-star-abundances} are based on the remaining clean Ba \textsc{ii} lines at 5853 and 6141 {\AA}, which are generally in good agreement with each other, and the 6496 {\AA} line where available.
+
+Our standard stars have [Ba/Fe] abundances very typical of the Milky Way halo.
+Only one of our standard stars, HD 44007, has published [Ba/Fe] abundances from high-resolution spectra.
+We find HD 44007 to have $\mbox{[Ba/Fe]} = -0.05 \pm 0.04$, which is at the mid-point of existing published measurements from \citet{fulbright_2000} and \citet{burris;et-al_2000} of $-0.27$ and 0.05 dex, respectively.
+
+With one exception, the Aquarius stream candidates have barium abundances that are quite similar to the stellar halo, ranging between $\mbox{[Ba/Fe]} = -0.02$ to 0.15 dex.
+The exception is C2225316, which has an anomalously high barium abundance of $\mbox{[Ba/Fe]} = 0.70$ dex.
+This is ${\sim}$0.70 dex higher than the Milky Way trend at its given $\mbox{[Fe/H]} = -1.26$ dex.
+Our three Ba \textsc{ii} lines in C2225316 are in excellent agreement: 0.67, 0.68, and 0.72 dex.
+The 6496\,{\AA} transition in C2225316 has a negligible telluric contribution and was included for this candidate.
+At least in Al, Si, Cr and Ba content (see sections \ref{sec:aluminium-abundance}, \ref{sec:alpha-elements}, \ref{sec:iron-peak-elements}), C225316 appears to be chemically distinct from the other Aquarius stream stars in our sample.
+
 % elemental abundances
@@
 % discuss Williams et al distances
+
+\begin{deluxetable}{lccccc}
+\tablecolumns{1}
+\tabletypesize{\scriptsize}
+\tablecaption{Optical Photometry \& Isochrone Distances\label{tab:distances}}
+\tablehead{
+	\colhead{Designation} &
+	\colhead{$B$} &
+	\colhead{$V$} &
+	\colhead{$(B-V)_0$} &
+	\colhead{Distance} \\
+	& (mag) & (mag) & (mag) & (kpc) 
+}
+\startdata 
+% C222531-144370   13.62 - 12.42
+% C230626-085103	13.67 - 12.44
+% J221821-183424	12.95 - 12.03
+% J223504-152834	13.14 - 12.12
+% J223811-104126   12.39 - 11.70
+%					12.17 - 11.53
+C222531-144370	& 13.75	& 12.52	& 1.20	& \nodata \\
+C230626-085103	& 13.89	& 12.61	& 1.23	& \nodata \\
+J221821-183424	& 13.08	& 12.13	& 0.92	& \nodata \\
+J223504-152834	& 13.31	& 12.25	& 1.02	& \nodata \\
+J223811-104126	& 12.69	& 11.93	& 0.73	& \nodata \\
+				& 12.69	& 11.93	& 0.64\footnote{Extinction derived from interstellar Na D1 line (see \SS3.4.2)} & \nodata
+\enddata
+\end{deluxetable}
 
@@
 High-resolution observations of disc stars illustrate this correlation \citep{bensby;venn}, demonstrating efficient SN \textsc{ii} mixing.
-Some intermediate-mass ($4M_\odot$) AGB models can also predict a positive correlation between aluminium and magnesium \citet{karakas;et-al}.
+Some intermediate-mass ($4M_\odot$) AGB models can also predict a positive correlation between aluminium and magnesium.
 Under extreme temperatures ($T_6 \sim 300$\,K), substantial $^{25}$Mg and $^{26}$Mg are produced by $\alpha$-capture onto $^{22}$Ne by the $^{22}$Ne($\alpha$,n)$^{25}$Mg and $^{22}$Ne($\alpha$,$\gamma$)$^{26}$Mg reactions respectively.

### 2013-05-16 2012-aqs/draft-aqs.tex
DEAL WITH IT

--- 2013-02-05 2012-aqs/draft-aqs.tex
@@
 \usepackage{amssymb,graphics} % for resolution symbol
-\usepackage{longtable}
+\usepackage{longtable,booktabs,multirow}
+\usepackage{pdflscape,rotating}
+\usepackage{wasysym} % for \astrosun
+
+\maxdeadcycles=1000
 
@@
 % TODO:
-
-% [DONE] Na/O subplots
-% [DONE] Na/O comparison with halo
-% [DONE] Mg/Al subplots
-% - Ni/Na plane plot
-% - Add standard stars to observations table
-% - Add standard stars chemical abundances
-% - Add in-line text referencing standard star chemical abundances
-% - Uncertainties analysis
-% [DONE] Equivalent widths significant figures.
-% - Strontium
-% - Carbon
-% - Distance calculations revision with B-V (if available) instead of (J-K)
-% - Transverse motions table
-% - Transverse motions text
-% - Orbital energies plot w.r.t Zolotov simulations
-% - Minor merger text
-% - Conclusions
-
-% Casey, Keller, Alves-Brito, Frebel, Da Costa, Schlaufman, Karakas, Jacobson, Yu, Freeman
-
-\author{Andrew R. Casey\altaffilmark{2,3} and distinguished collaborators}
+% - Uncertainty analysis for a standard star
+% - Uncertainty analysis for a prgram star
+
+\author{Andrew R.
+Casey\altaffilmark{2,3}, Stefan Keller\altaffilmark{2}, Alan Alves-Brito\altaffilmark{2}, Anna Frebel\altaffilmark{3}, Gary Da Costa\altaffilmark{2}, Amanda Karakas\altaffilmark{2}, David Yong\altaffilmark{2}, Kevin Schalufman\altaffilmark{3}, Heather Jacobson\altaffilmark{3}, QinQin Yu\altaffilmark{3}, Ken Freeman\altaffilmark{2}, Cherie Fishlock\altaffilmark{2}}
 \altaffiltext{1}{This paper includes data gathered with the 6.5 meter Magellan Telescopes located at Las Campanas Observatory, Chile.}
@@
 \begin{abstract}
-We present a detailed analysis of five Aquarius stream candidate stars observed using the MIKE spectrograph with the Magellan Clay telescope.
-Enhanced [Na/Fe] and [Ni/Fe] abundance ratios suggest the co-moving group is not the result of a dwarf satellite galaxy, and that its chemical enrichment environment is more representative of either a globular cluster, or the Milky Way thick disc.
-However, we find no evidence that the stream is a result of a disrupted cluster.
-Our data indicate the Aquarius stream has a  metallicity dispersion of $\sigma(\mbox{[Fe/H}]) = 0.32$\,dex.
-No inverse Na-O correlation is present, and we find a positive Mg-Al relationship.
-Chemically, the group is indistinguishable from the Milky Way thick disk with the exception of one very interesting candidate, which we hypothesise is tidal debris from $\omega$-Centurai.
-Assuming all other candidates are Aquarius members, we propose the co-moving group has arisen from a minor merger in the Milky Way's thick disk.
-
+We present a detailed analysis of high S/N, high-resolution spectra for five Aquarius stream stars observed using the MIKE spectrograph on the Magellan Clay telescope.
+Our sample represents one third of the total number of published stream members.
+We find the co-moving group is not chemically coherent; a wide metallicity dispersion ranging from {$\mbox{[Fe/H]} = -0.63$} to $-1.63$\,dex is observed.
+Enhanced [Na/Fe], [Ni/Fe] and [$\alpha$/Fe] abundance ratios suggest the co-moving group is not the result of a disrupted dwarf galaxy.
+Additionally, we find no evidence that the stream is a result of a disrupted classical globular cluster, contrary to a previously published claim.
+No inverse Na-O correlation is present, and we find a strong positive Mg-Al relationship similar to that observed in the thick disc.
+The group is chemically indistinguishable from Milky Way field stars with the exception of one candidate, C222531-145437.
+From positions, velocities, and detailed chemical abundances it is unambiguous that C222531-145437 is a tidal remnant from the $\omega$-Centurai globular cluster.
+We hypothesise the co-moving group is galactic in origin, and is a result from a disc-satellite perturbation in the Milky Way thick disc.
+Derived orbits, $u$--$v$ plane velocities, and angular momentum calculations for Aquarius candidates qualitatively supports our hypothesis, and are consistent with a disc interaction on the order of a few Gyr ago.
+Given the debris of C222531-145437 as tidal debris,  $\omega$-Centurai is a plausible perturber, as is the Sagittarius dwarf.
+While there is no evidence that the Aquarius stream is the tidal tail of a disrupted satellite, we advocate the `Aquarius group' as a more appropriate description.
+Like the Canis Major over-density, and the Hercules and Monoceros groups, the Aquarius co-moving group adds to the list of kinematically-identified substructures that are not actually accreted material; they are simply part of the rich complexity of the Milky Way structure.
 \end{abstract}
 
-\keywords{Galaxy: halo, structure --- Individual: Aquarius Stream --- Stars: FGK-giants}
+\keywords{Galaxy: halo, structure}
 
@@
 The accumulating stellar debris in our own galactic halo provides ongoing evidence for such merging events.
-As accreting satellites infall onto the galaxy, tidal forces disrupt the dwarf, hurtling stars in leading and trailing directions.
-Unsurprisingly, the velocities of stars within these `stellar streams' are sensitive to the galactic potential.
+As accreting satellites infall onto the galaxy, tidal forces disrupt the smaller system, hurtling stars in leading and trailing directions.
+Unsurprisingly the velocities of stars within these `stellar streams' are sensitive to the galactic potential.
 As such, their phase-space information can collectively constrain the fraction and distribution of accreted matter in the galaxy, the sub-halo mass function, as well as the shape and extent of dark matter in the Milky Way.
-Moreover, individual chemical abundances can constrain the  precise nucleosynthesis sites where elements are forged, as well as trace the chemical evolution of the galaxy.
+Moreover, individual chemical abundances from high-resolution spectra can trace the chemical evolution of the galaxy.
+% can constrain the  precise nucleosynthesis sites where elements are forged, as well as
 
 % Consider adding a final sentence about the amount of work that has gone into stellar streaams
-
-Wide-field surveys have proved excellent sources for finding stellar streams.
-Dozens have been identified through photometric selections and matched-filtering techniques, with some to a galactocentric distance of 100\,kpc \citep{belokurov;et-al_2007,drake;et-al_2013}.
+Wide-field deep imaging surveys have proved excellent sources for finding stellar streams.
+Dozens have been identified through careful photometric selections and matched-filtering techniques, with some to a galactocentric distance of 100\,kpc \citep{belokurov;et-al_2007,drake;et-al_2013}.
 Indeed, it is clear that a large fraction of the stellar halo has been built up by accretion.
-However, as \citet{helmi;white_1999} point out, these observing strategies are only successful for identifying streams that are sufficiently distant from the solar neighbourhood.
-A nearby stream, within $\sim$10\,kpc, will not appear as an over-density, as the stars would be sparsely positioned across the sky.
-Such substructures would only be detectable by their kinematics, or perhaps precise chemical abundances through a `chemical tagging' approach (e.g.
+However, as \citet{helmi;white_1999} point out, these detection strategies are only successful for identifying streams that are sufficiently distant from the solar neighbourhood.
+A nearby stream, within $\sim$10\,kpc, will not appear as a photometric over-density as the stars would be sparsely positioned across the sky.
+Such substructures would only be detectable by their kinematics, or perhaps with precise elemental abundances through a `chemical tagging' approach (e.g.
 see \citet{freeman;bland-hawthorn_2002}).
@@
 % Talk about RAVE
-It is therefore necessary to survey solar neighbourhood stars with spectroscopy to reveal any nearby substructures.
-The RAVE (Radial Velocity Experiment) team began such a survey in 2003 and have observed spectra from over 500,000 stars across 17,000\,deg$^{2}$.
+It is therefore necessary to spectroscopically survey the solar neighbourhood stars to reveal any nearby substructures.
+The Radial Velocity Experiment (RAVE) team began such a survey in 2003 and have observed spectra from over 500,000 stars across 17,000\,deg$^{2}$.
 As the name hints, the primary goal of RAVE was to obtain radial velocities for the solar neighbourhood and beyond.
-In an attempt to remain kinematically unbiased, RAVE candidates were selected based only on their apparent magnitude.
-With the exception of bulge stars, where some photometric cuts were employed, all stars between 9 $<$ I $<$ 13 were observed.
-Almost all of these candidates have published radial velocity measurements \citep{steinmetz;et-al_2006}, and for a subset of stars with sufficient Signal-to-Noise ($S/N$), estimates of stellar parameters have been derived using a $\chi^2$ minimization technique \citep{zwitter;et-al_2008, siebert;et-al_2011}.
+In an attempt to remain kinematically unbiased, RAVE candidates were selected solely by their apparent magnitude.
+With the exception of bulge stars, where some photometric cuts were employed, all stars between $9 < I < 13$ were observed.
+Almost all of these candidates have published radial velocity measurements \citep{steinmetz;et-al_2006}, and for a subset of stars with a sufficient Signal-to-Noise ($S/N$) ratio, estimates of stellar parameters have been derived using a $\chi^2$ minimisation technique \citep{zwitter;et-al_2008, siebert;et-al_2011}.
 
 % Identification of the aquarius stream
-Using these data, \citet{williams;et-al_2011} identified a co-moving group of nearby ($0.5\,\mbox{kpc} \lesssim d \lesssim 10\,\mbox{kpc}$) stars in the vicinity of the Aquarius constellation $(l, b) = (60\,^\circ, -55\,^\circ)$.
+Using these data, \citet{williams;et-al_2011} identified a co-moving group of nearby (${0.5\,\mbox{kpc} \lesssim d \lesssim 10\,\mbox{kpc}}$) stars in the vicinity of the Aquarius constellation ${(l, b) = (60\,^\circ, -55\,^\circ)}$.
 Thus, the co-moving group was named the Aquarius stream.
@@
 The average heliocentric velocity of these members was found to be $V_{\rm hel} = -199\,\mbox{km s}^{-1}$, with a dispersion of 27\,km s$^{-1}$.
-The radial velocity uncertainties provided by the RAVE catalog are described to be $\sim$2\,km s$^{-1}$, so the wide kinematic distribution appears to be real.
+The radial velocity uncertainties provided by the RAVE catalog are described to be $\sim$2\,km s$^{-1}$, so the stream's wide kinematic distribution appears to be real.
 
@@
 The predicted particles in each model between $-70\,^\circ < b < -50\,^\circ$ were binned in $\Delta{l} \times \Delta{V_{\rm hel}}$ blocks using varying grid cell sizes between $25\,^\circ$ to $70\,^\circ$ and $20\,\mbox{km s}^{-1}$ to $100\,\mbox{km s}^{-1}$.
-The RAVE sample was binned in the same way, and the statistical significance of the observed over-density is discretized.
-\citet{williams;et-al_2011} found the stream to be statistically significant ($>$4-$\sigma$) in 96\% of the cell proportions employed for the Besan\c{c}on model.
-By sampling the Galaxia model repeatedly with varying extinction rates, a similar result was found: between $75\pm15$\,\% to $80\pm18$\,\% of grid cells showed the Aquarius stream to significant at the 4-$\sigma$ level or higher.
+The RAVE sample was binned in the same way, discretising the inferred statistical significance of the observed over-density.
+\citet{williams;et-al_2011} found the stream to be significant ($>4\sigma$) in 96\% of the cell proportions employed for the Besan\c{c}on model.
+By sampling the Galaxia model repeatedly with varying extinction rates, a similar result was found: between $75\pm15$\,\% to $80\pm18$\,\% of grid cells showed the Aquarius stream to be significant at the $4\sigma$ level or higher.
 Given the high-latitude and proximity of the stream, it is not surprising that dust had a negligible effect on the statistical significance.
-\citet{williams;et-al_2011} concluded that the over-density in $l, V_{\rm hel}$ is a true substructure, and neither the choice of galaxy model, cell dimension, nor the extinction model made any real difference to the detection significance.
+\citet{williams;et-al_2011} concluded that the over-density in $l, V_{\rm hel}$ is a true substructure, and neither the choice of galaxy model, cell dimension, nor the extinction rate made any real difference to the detection significance.
 
@@
 % DISTANCE AND DYNAMICS
-% heliocentric + galactic velocities suggest the aquarius stream stars are in the halo, and not associated with the disk.
+% heliocentric + galactic velocities suggest the aquarius stream stars are in the halo, and not associated with the disc.
 % distances
@@
 The Sagittarius stream is arguably the most prominent ongoing accretion event in the galaxy.
-Given the extent of stellar debris the dwarf has littered throughout the Milky Way, it is reasonable to suspect the Aquarius stream might originate from the Sagittarius dwarf.
-Indeed, the Aquarius  stars do not lie far from the orbital plane of Sagittarius, and the metallicities reported by \citet{williams;et-al_2011} are not dissimilar from the Sagittarius stream.
+Given the extent of stellar debris the Sagittarius dwarf spheroidal (dSph) galaxy has littered throughout the Milky Way, it is reasonable to suspect the Aquarius stream might originate from the Sagittarius dwarf.
+Indeed, the Aquarius  stars do not lie far from the orbital plane of Sagittarius and the metallicities reported by \citet{williams;et-al_2011} are not dissimilar from the Sagittarius stream.
 However, \citet{williams;et-al_2011} found the Aquarius transverse motions (specifically $V_{Z}$ and $V_\phi$) to be quite distinct from Sagittarius.
@@
 RAVE observations suggest the Aquarius stream has a metallicity of $\mbox{[Fe/H]} \sim -1.0$, slightly more metal-rich than halo stars at the same distance.
-\citet{williams;et-al_2011} found the stream to have an average of $\mbox{[M/H]} = -1.0 \pm 0.4$, compared to $\mbox{[M/H]} = -1.1 \pm 0.6$ for background stars after the same selection cuts had been employed.
-Of the 12 Aquarius stars in the \citet{williams;et-al_2011} discovery sample with stellar parameters, the metallicity range is wide: between --2.02 and --0.33 dex.
-Spectroscopic observations of high resolution with high $S/N$ are necessary to accurately characterize the stream's metallicity distribution.
-
-To this end, \citet{wylie-de-boer;et-al_2012} obtained high-resolution ($\mathcal{R} = 25,000$) spectra with modest $S/N$ ($\sim$30 pixel$^{-1}$) for six Aquarius stream stars.
-Their data indicate a very narrow metallicity distribution: $\mbox{[Fe/H]} = -1.09 \pm 0.10$\,dex extending between $\mbox{[Fe/H]} = -1.25$ to $-0.98$\,dex.
-Observations of such minimal chemical scatter from stars with a common origin is typically noted in either globular, or open clusters.
-The largest [Fe/H] discrepancy between the \citet{williams;et-al_2011} and \citet{wylie-de-boer;et-al_2012} study was $\Delta\mbox{[Fe/H]} = -0.66$\,dex for the most metal-rich star in the \citet{williams;et-al_2011} sample.
+Using stellar parameters from the RAVE pipeline, \citet{williams;et-al_2011} found the stream to have an average of ${\mbox{[M/H]} = -1.0 \pm 0.4}$\,dex, compared to ${\mbox{[M/H]} = -1.1 \pm 0.6}$\,dex for background stars after the same selection cuts had been employed.
+Of the 15 Aquarius stars in the \citet{williams;et-al_2011} discovery sample with stellar parameters, the metallicity range from medium-resolution spectroscopy is wide: between --2.02 and {--0.33\,dex}.
+High-resolution spectroscopic observations with high $S/N$ are necessary to accurately characterise the stream's metallicity distribution.
+
+To this end, \citet{wylie-de-boer;et-al_2012} obtained high-resolution ($\mathcal{R} = 25,000$) spectra with modest $S/N$ ($\sim$30 pixel$^{-1}$) for six Aquarius stream stars using the echelle spectrograph on the ANU 2.3m telescope.
+Their data indicate a surprisingly  narrow metallicity distribution compared to the RAVE results: ${\mbox{[Fe/H]} = -1.09 \pm 0.10}$\,dex extending from ${\mbox{[Fe/H]} = -1.25}$ to {--0.98\,dex}.
+Observations of such minimal chemical scatter from stars that share a common origin is typically noted only in either globular or open clusters.
+The largest [Fe/H] discrepancy between the \citet{williams;et-al_2011} and \citet{wylie-de-boer;et-al_2012} study was ${\Delta\mbox{[Fe/H]} = -0.66}$\,dex for the most metal-rich star in the \citet{williams;et-al_2011} sample.
 The most metal-poor star in the \citet{williams;et-al_2011} study was not observed by \citet{wylie-de-boer;et-al_2012}.
@@
 The authors primarily focussed on light elements: Na, O, Ni, Mg, and Al.
-Chemical patterns in these light elements arise as natural consequences of nucleosynthetic processes in massive stars.
-These patterns have been repeatedly observed in globular clusters.
-Specifically, an anti-correlation between sodium and oxygen content appears ubiquitous to globular clusters.
-While the exact formation site is still under debate, the chemical relationship is well-established empirically.
-The Na-O pattern provides the best chemical evidence that their chemical enrichment history has been dominated by Type \textsc{ii} Supernova (SN) events and that those stars formed in a globular cluster-like environment.
+Chemical patterns in these elements arise as natural consequences of nucleosynthetic processes in massive stars and have been repeatedly observed in globular clusters.
+Specifically, an anti-correlation between sodium and oxygen content appears ubiquitous to globular cluster stars.
+While the exact formation mechanism is still under debate, the chemical relationship is well-established empirically.
+The {Na-O} pattern provides the best chemical evidence that their enrichment history has been dominated by Type \textsc{ii} supernova (SN) events, and that those stars formed in a globular cluster-like environment.
 
@@
 It is well known now that photospheric abundance variations resulting from internal mixing are limited to carbon, nitrogen and lithium.
-Additionally, light element variations can be explained by classic nucleosynthetic pathways, albeit extreme temperatures are necessary for such relationships to arise \--- much higher than would reasonably be expected in globular cluster stars.
+Additionally, light element variations can be explained by classic nucleosynthetic pathways, albeit extreme temperatures are necessary for such relationships to arise -- much higher than would reasonably be expected in globular cluster stars.
 Several descriptions for an astrophysical site that would permit such nucleosynthetic processes have been hypothesized, including massive intermediate-mass Asymptotic Giant Branch (AGB) binary stars \citep{de_mink;et-al_2009} and fast-rotating massive stars \citep{decressin;et-al_2007}.
 
-From high-resolution spectroscopy of five candidate Aquarius stars, four of which had sodium and oxygen abundance measurements, \citet{wylie-de-boer;et-al_2012} found two stars with super-solar sodium; slightly higher [Na/Fe] ratios than halo stars of the same metallicity.
+From high-resolution spectroscopy of six Aquarius stars, four of which have sodium and oxygen abundance measurements, \citet{wylie-de-boer;et-al_2012} found two stars with enhanced sodium; slightly higher [Na/Fe] ratios than halo stars of the same metallicity.
 However, no strong oxygen depletion was evident in the data.
-Thus, they observed no evidence of a classical Na-O inverse correlation in the Aquarius stream.
-
-There are other chemical abundance patterns that allow us to infer the chemical enrichment environment.
+Thus, although they found minimal chemical scatter in the overall metallicities of Aquarius stream stars, they observed no evidence of a {Na-O} inverse correlation.
+
+There are other chemical abundance patterns that allow us to infer the stream's chemical enrichment environment.
 \citet{nissen;schuster_1997} first noted that nearby solar neighbourhood stars were enriched in [Ni/Fe] and [Na/Fe].
@@
 If the stellar halo has been built up from the accretion of smaller dwarf satellites, \citet{nissen;schuster_1997} proposed that this chemical trend may be indicative of the halo merger history since stars at larger $R_\odot$ are more likely to have been accreted rather than formed in-situ.
-\citet{wylie-de-boer;et-al_2012} found all the Aquarius stars in their sample to be enriched in both sodium and nickel; contrary to what would be expected if the stars originated from a disrupted dwarf spheroidal (dSph) galaxy.
-This provided an additional indication that the Aquarius stream stars originated in a globular cluster-like environment.
+\citet{wylie-de-boer;et-al_2012} found all the Aquarius stars in their sample to be enriched in both sodium and nickel; contrary to what would be expected if the stars originated from a disrupted dSph galaxy.
+If the stream had originated from an accretion event, this provides an indication that the stars were first enriched in a globular cluster-like environment.
 
 Combined with the low level of chemical scatter present in their sample, these chemical indicators led \citet{wylie-de-boer;et-al_2012} to conclude that the Aquarius stream is the result of a tidally disrupted globular cluster.
-\citet{williams;et-al_2011} had previously precluded this possibility with any known globular clusters after modelling an Aquarius-like progenitor infalling onto the Milky Way and comparing the predicted $l, b, V_{\rm hel}$ with known, nearby globular clusters of similar metallicities.
+\citet{williams;et-al_2011} had previously precluded this possibility with any known clusters after modelling an Aquarius-like progenitor infalling onto the Milky Way and comparing the predicted $l, b, V_{\rm hel}$ with known, nearby globular clusters of similar metallicities.
 No known globular cluster could match their simulation.
-If both scenarios are accurate then the undiscovered disrupting cluster might still remain, and would be relatively close by.
+If both scenarios are accurate then the undiscovered disrupting cluster might still remain and would be very close, such that it is unlikely it would not have been discovered by now.
 
@@
 The data analysis is chronicled in Section \ref{sec:analysis} and a detailed discussion of these results resides in Section \ref{sec:discussion}.
-In Section \ref{sec:conclusions} we present our conclusions and critical interpretations.
+In Section \ref{sec:conclusions} we present a summary of our conclusions and critical interpretations.
 
@@
 	\colhead{S/N\tablenotemark{a}} &
-	\colhead{$V_{\rm rad}$} &
 	\colhead{$V_{\rm hel}$} &
 	\colhead{$V_{\rm err}$} \\
- & (J2000) & (J2000) & Date & & (") & (secs) & (px$^{-1}$) & (km s$^{-1}$) & (km s$^{-1}$) & (km s$^{-1}$)
+ & (J2000) & (J2000) & Date & & (") & (secs) & (px$^{-1}$) & (km s$^{-1}$) & (km s$^{-1}$)
 }
@@
 \\ \multicolumn{11}{c}{Standard Stars} \\ \hline \\
-HD 41667		& 06:05:03.7 & $-$32:59:36.8	& 2011-03-13	& 1.005	& \dots & \dots & \dots & 314.4	& \dots & 0.8 \\
-HD 44007		& 06:18:48.6 & $-$14:50:44.2 	& 2011-03-13	& 1.033	& \dots & \dots & \dots & --185.9	& 162.9 & 0.6 \\
-HD 136316		& 15:22:17.2 & $-$53:14:13.9	& 2011-03-14	& 1.118	& \dots & \dots & \dots & 61.0		& --37.6 & 0.4 \\
-HD 141531		& 15:49:16.9 & \phn\.09:36:42.5		& 2011-03-14	& 1.309	& \dots & \dots & 350	 & 17.7		& 2.8	& 0.1 \\
-HD 142948		& 16:00:01.6 & $-$53:51:04.1	& 2011-03-14	& 1.107	& \dots & \dots & \dots & 6.8		& \dots & 0.4 \\
+HD\,41667		& 06:05:03.7 & $-$32:59:36.8		& 2011-03-13	& 1.005	& 1.0 & 90 		& 340 & 297.1 		& 0.1 \\
+HD\,44007		& 06:18:48.6 & $-$14:50:44.2 		& 2011-03-13	& 1.033	& 1.0 & 120		& 280 & 161.8 		& 0.1 \\
+HD\,76932		& 08:58:44.2 & $-$16:07:54.2		& 2011-03-14	& 1.158	& 1.0 & 25		& 330 & 117.8		& 0.1 \\
+HD\,136316		& 15:22:17.2 & $-$53:14:13.9		& 2011-03-14	& 1.118	& 0.9 & 120 	& 400 & $-$38.8 	& 0.1 \\
+HD\,141531		& 15:49:16.9 & $+$09:36:42.5	& 2011-03-14	& 1.309	& 0.9 & 120	& 350 & 2.8			& 0.1 \\
+HD\,142948		& 16:00:01.6 & $-$53:51:04.1		& 2011-03-14	& 1.107	& 1.0 & 90 	& 320 & 29.9 		& 0.1 \\
+\hline
 
 \\ \multicolumn{11}{c}{Program Stars} \\ \hline \\
-C2225316-14437	& 22:25:31.7 & $-$14:54:39.6	& 2011-07-30	& 1.033 & \dots & \dots & 135	 & --168.6	& --156.4 & 0.1 \\
-C2306265-085103	& 23:06:26.6 & $-$08:51:04.8	& 2011-07-30	& 1.096 & \dots & \dots & 100	 & --240.4	& --221.1 & 0.1 \\
-J221821-183424	& 22:18:21.2 & $-$18:34:28.3	& 2011-07-30	& 1.026	& \dots & \dots & 115 	 & --170.2	& --159.5 & 0.1 \\
-J223504-152834	& 22:35:04.5 & $-$15:28:34.9	& 2011-07-30	& 1.047	& \dots & \dots & 135	 & --179.0	& --169.7 & 0.1 \\
-J223811-104126	& 22:38:11.6 & $-$10:41:29.4	& 2011-07-30	& 1.218	& \dots & \dots & 115	 & --250.1	& --235.7 & 0.1
-
-%HD 136316 % F giant, -1.8, Gratton 2000+, has Na, O abundances
-%HD 141531 % F giant, -1.6, Gratton 2000+, has Na, O abundances
-%HD 44007 % G giant, -1.50, lots of references
-
-% Hd 141431		: -0.96, -1.03 +/- 0.78 (MEK)
+C222531-145437	& 22:25:31.7 & $-$14:54:39.6	& 2011-07-30	& 1.033	& 0.8	& 650 & 135	& $-$156.4 & 0.1 \\
+C230626-085103	& 23:06:26.6 & $-$08:51:04.8	& 2011-07-30	& 1.096	& 1.0	& 650 & 100	& $-$221.1 & 0.1 \\
+J221821-183424	& 22:18:21.2 & $-$18:34:28.3	& 2011-07-30	& 1.026	& 0.9 	& 650 & 115	& $-$159.5 & 0.1 \\
+J223504-152834	& 22:35:04.5 & $-$15:28:34.9	& 2011-07-30	& 1.047	& 1.0 	& 650 & 130	& $-$169.7 & 0.1 \\
+J223811-104126	& 22:38:11.6 & $-$10:41:29.4	& 2011-07-30	& 1.218	& 1.2 	& 650 & 115	& $-$235.7 & 0.1
+
+%HD\,136316 % F giant, -1.8, Gratton 2000+, has Na, O abundances
+%HD\,141531 % F giant, -1.6, Gratton 2000+, has Na, O abundances
+%HD\,44007 % G giant, -1.50, lots of references
 
 % V corrections (already applied the first number of each row)
+% HD\,41667		: -0.77, -0.79 +/- 0.79
+% HD\,44007		: -1.12, -1.12 +/- 0.96
+% HD\,136316		: -1.17, -1.25 +/- 0.86
+% HD\,141531		: -0.96, -1.03 +/- 0.78
+% HD\,142948		: -1.49, -1.49 +/- 0.75
 % J221821     	:   0.30, 0.25 +/- 1.25 (MEK has -154.1, wdb ) -- diff: 5.4  (positive == higher)
-% C2225316		:	0.43, 0.42 +/- 1.13 (MEK has -155.7) -- diff: -0.4 (hers is lower)
+% C222531		:	0.43, 0.42 +/- 1.13 (MEK has -155.7) -- diff: -0.4 (hers is lower)
 % C2306265		: 	1.14, 1.19 +/- 1.16 (MEK has -221.8) -- diff: -0.7 (hers is lower)
@@
 Our sample includes five stars: four common to the \citet{wylie-de-boer;et-al_2012} study, and an additional candidate from the original \citet{williams;et-al_2011} sample.
-The supplementary star, J2306265-085103, was observed by the RAVE survey but had a $S/N$ ratio too low for stellar parameters to be accurately determined.
-All program stars were observed in July 2011 in good seeing at low airmass (Table \ref{tab:observations}), and five additional standard stars were observed in March 2011.
-All observations were taken using a 1.0'' slit, providing a spectral resolution of $\mathcal{R} = 28,000$ in the blue arm and $\mathcal{R} = 22,000$ in the red arm.
-The total exposure times for our program stars varied to ensure a $S/N$ ratio in excess of 100\,pixel$^{-1}$ at 600\,nm.
+The supplementary star, C2306265-085103, was observed by the RAVE survey but had a $S/N$ ratio too low for stellar parameters to be accurately determined.
+All program stars were observed in July 2011 in reasonable seeing at low airmass (Table \ref{tab:observations}), and six  standard stars were observed in March 2011.
+All observations were taken using a 1.0'' slit, providing a spectral resolution in excess of $\mathcal{R} = 28,000$ in the blue arm and $\mathcal{R} = 22,000$ in the red arm.
+The exposure time for our program stars was 650\,seconds per star in order to ensure a $S/N$ ratio in excess of 100\,pixel$^{-1}$ at 600\,nm.
 
@@
 The data were reduced using the CarPy pipeline\footnote{http://code.obs.carnegiescience.edu/mike}.
-One standard stars, HD 41667, was also reduced using standard extraction and calibration methods in \textsc{iraf}.
+One standard star, HD\,41667, was also reduced using standard extraction and calibration methods in \textsc{iraf}.
 The resultant spectra from both approaches were compared for residual fringing, $S/N$, and wavelength calibration.
-No noteworthy differences were present, and the CarPy pipeline was utilized for the remainder of the data reductions.
-Each reduced echelle order was carefully normalized using a third order spline with defined knot spacing.
-Normalized orders were stitched together to provide a single one-dimensional spectrum from 3800-9400\,\AA{}.
-
-The white dwarf HR 6141 was observed on X as a telluric standard.
+No noteworthy differences were present, and the CarPy pipeline was utilised for the remainder of the data reduction.
+Each reduced echelle order was carefully normalised using a third order spline with defined knot spacing.
+Normalised orders were stitched together to provide a single one-dimensional spectrum from 333-916\,nm.
+
+The white dwarf HR 6141 was observed in March 2011 as a telluric standard.
 The $S/N$ ratio for HR 6141 exceeds that in any of our standard or program stars.
-Although the atmospheric conditions at Las Campanas Observatory are certain to change throughout the night and between observing runs, we are primarily using this spectra to identify lines that are affected by telluric absorption.
-Critical transitions necessary for abundance analyses that are affected by the Earth's atmosphere are corrected for telluric absorption.
+Although the atmospheric conditions at Las Campanas Observatory are certain to change throughout the night and between observing runs, we are primarily using this spectra to identify stellar absorption lines that are affected by telluric absorption.
+However, a few critical transitions necessary for abundance analyses that are affected by the Earth's atmosphere have been corrected for telluric absorption.
+Where applied, the details of these corrections are discussed on a line-by-line basis.
 
@@
 
-The radial velocity for each star was determined in a two-step method.
-An initial estimate of the radial velocity was ascertained by cross-correlation with a synthetic spectrum of a giant star with $T_{\rm eff} = 4500$\,K, $\log{g} = 1.5$, and [M/H] $= -1.0$ across the wavelength range $8450 - 8700$ \AA{}.
+The radial velocity for each star was determined in a two step process.
+An initial estimate of the radial velocity was ascertained by cross-correlation with a synthetic spectrum of a giant star with $T_{\rm eff} = 4500$\,K, $\log{g} = 1.5$, and ${\mbox{[M/H]} = -1.0}$ across the wavelength range {845-870\,nm}.
 The observed spectrum was shifted to the pseudo-rest frame using this initial velocity estimate.
-Velocities found from cross-correlation are typically within 1\,km\,s$^{-1}$ of our final published value.
+Velocities found from cross-correlation are typically within {1\,km\,s$^{-1}$} of our final published value.
+
+With our spectra at near-rest, we measured the equivalent widths of $\sim$160 transitions by automatically fitting a Gaussian profile to the absorption lines (see Section \ref{sec:line-measurements}).
+Fitted Gaussian profiles provide us with a measured equivalent width, the full-width half-maximum (FWHM) and the central wavelength of the profile.
+Thus, the residual radial velocity can be found directly from the ratio of the central and rest wavelengths.
+The final radial velocity for the star is provided by the initial velocity and the mean of $\sim$160 residual line velocity measurements.
+Figure \ref{fig:line-velocities} shows the line velocities for HD\,41667 after being placed at pseudo-rest using our cross-correlation velocity of 314.4\,km s$^{-1}$.
+As expected, the mean residual offset is small ($-0.75$\,km s$^{-1}$), and the standard deviation is 0.79\,km s$^{-1}$ from 164 measurements.
+This provides us with a final measured radial velocity of ${313.6 \pm 0.1\,{\rm km s}^{-1}}$.
+This process was performed for all observations.
+The radial velocities published in Table \ref{tab:observations} are the final values from this two step method.
+Heliocentric velocities agree quite well with those compiled by \citet{williams;et-al_2011} from the RAVE survey: the mean offset is ${\langle\Delta{V_{\rm hel}}\rangle = 2.5 \pm 2.7}$\,km s$^{-1}$, demonstrating the accuracy of the velocities published in the RAVE catalog.
 
@@
 
-With our spectra at near-rest, we measured the equivalent widths of $\sim$200 lines by automatically fitting Gaussian functions to the absorption profiles (see Section \ref{sec:line-measurements}).
-Fitted Gaussian profiles provide us with a measured equivalent width, the full-width half-maximum (FWHM) and the central wavelength of the profile.
-Thus, the residual radial velocity can be found from the ratio of the central and rest wavelengths.
-The final radial velocity for the star is provided by the initial velocity and the mean of $\sim$200 residual line velocity measurements.
-Figure \ref{fig:line-velocities} shows the line velocities for HD 41667 after being placed at pseudo-rest using our cross-correlation velocity of 314.4\,km s$^{-1}$.
-As expected, the mean residual offset is small ($-0.75$\,km s$^{-1}$), and the standard deviation is 0.79\,km s$^{-1}$ from 164 line measurements.
-This provides us with a final measured radial velocity of $313.7 \pm 0.1$\,km s$^{-1}$.
-This process was performed for all observations.
-The radial velocities published in Table \ref{tab:observations} are the final values from this two-step method.
-Heliocentric velocities agree quite well with those compiled by \citet{williams;et-al_2011} from the RAVE survey: the mean offset is $\langle\Delta{V_{\rm hel}}\rangle = 2.5 \pm 2.7$\,km\,s$^{-1}$, demonstrating the accuracy of the velocities published in the RAVE catalog.
-
 \subsection{Line Measurements}
@@
 
-For the measurement of atomic absorption lines, we employed the line list of \citet{yong;et-al_2005} with additional transitions of Cr, Sc, Zn, and Sr from \citet{frebel;et-al_2010}.
-The line list was augmented with hyperfine-structure data for Sc and Mn from the Kurucz compilation \citet{kurucz;1998}.
-Molecular line data for CH was taken from \citet{plez;et-al_2008,plez;et-al_2009}.
+For the measurement of atomic absorption lines, we employed the line list of \citet{yong;et-al_2005} with additional transitions of Cr, Sc, Zn, and Sr from \citet{roederer;et-al_2010}.
+The list has been augmented with molecular CH data from \citet{plez;et-al_2008}.
 For lines with hyperfine structure, blended transitions or molecular features, we determined the abundance using a spectral synthesis approach.
@@
 
-The equivalent widths for all absorption lines were measured automatically using software written for this study.
+The equivalent widths for all absorption lines were measured automatically using software written during this study.
 Given the rest wavelength and an initial guess of the FWHM, a Gaussian profile is iteratively fitted to the absorption line.
-At the same time, the local continuum is found within 10\,\AA{} either side of the rest wavelength using a second-order polynomial.
+Simultaneously, the local continuum within 10\,\AA{} either side of the rest wavelength is found by fitting a second-order polynomial.
 Measuring the local continuum ensures any errors in our initial normalisation or order-stitching do not propagate through to our equivalent width measurements.
-When determining the local continuum, any neighbouring group of pixels that deviate significantly ($>$2-$\sigma$) from the local continua either belong to a persistent cosmic ray hit, or they are trough points of a neighbouring absorption profile.
+When determining the local continuum, any group of \textit{neighbouring pixels} that all deviate significantly ($>2\sigma$) from the local continua either belong to a persistent cosmic ray hit, or they are trough points of a nearby absorption profile.
 We attempt to fit a Gaussian profile to each group of deviating pixels, using the current best estimate for the local continuum.
-If a Gaussian profile is successfully fitted to the deviating group and its surrounding pixels, we assume the outlier points belong to an absorption line and all pixels belonging to that profile are excluded from the continuum determination.
-
-When fitting Gaussian profiles, the $\chi^2$ difference between the observed spectra and the fitted function is minimized.
-In order to account for crowded absorption regions, where the $\chi^2$ value might be influenced by a nearby or blended profile, our $\chi^2$ function is weighted based on the distance to the rest wavelength by the function
-
+If a Gaussian profile is successfully fitted to the deviating group and its surrounding pixels, we assume the outlier points -- and all pixels included by that Gaussian profile -- belong to an absorption line and are excluded from the iterative continuum determination.
+
+When fitting Gaussian profiles, the $\chi^2$ difference between the observed spectra and the fitted function is minimised.
+In order to account for crowded absorption regions where the $\chi^2$ value might be influenced by a blended or strong nearby profile, our $\chi^2$ function is weighted by the distance to the rest wavelength with the function,
 \begin{equation}
@@
 \end{equation}
-
-\noindent where the rest wavelength ($\lambda_{r}$) and standard deviation\footnote{Recall $\rm{FWHM} = 2\sigma\sqrt{2\log_e{2}}$} ($\sigma$) are free parameters in the iterative fitting process.
+\noindent where the rest wavelength ($\lambda_{r}$) and profile sigma\footnote{Recall $\rm{FWHM} = 2\sigma\sqrt{2\log_e{2}}$} ($\sigma$) are free parameters in the iterative fitting process.
 As a consequence of Eq.
-\ref{eq:chi-weight}, pixels near the rest wavelength are weighted higher than those on the wings, forcing the fitting scheme to disregard blended or crowded surroundings.
-Although this approach relies on a reasonably accurate initial radial velocity correction of $<$4\,km s$^{-1}$ \--- which is easily achieved \--- it greatly improves the accuracy and robustness of the equivalent width measurements.
+\ref{eq:chi-weight}, pixels near the rest wavelength are weighted slightly higher than those on the wings, forcing the fitting scheme to disregard blended or crowded surroundings.
+Although this approach relies on a reasonably accurate initial radial velocity correction of $<|4|$\,km s$^{-1}$ -- which is easily achieved -- it greatly improves the accuracy and robustness of the equivalent width measurements.
+
+\begin{figure}[t]
+	\includegraphics[width=\columnwidth]{./figures/smh-norris.pdf}
+	\caption{A comparison showing equivalent widths measured for HD\,140283 using our automatic routine (see \S\ref{sec:line-measurements}), and those found by careful hand measurements in \citet{norris;et-al_1996}.
+No systematic trend is present, and the mean difference between these studies is ${\langle\Delta{}W_\lambda\rangle = -0.64 \pm 2.78}$\,m\AA{}.}
+	\label{fig:ew-compare}
+\end{figure}
 
 The results of our iterative Gaussian fitting approach are \textit{completely insensitive} to the initial FWHM guess.
-Increasing the initial FWHM estimate from 0.1\,\AA{} to 1 or 2\,\AA{} \--- which are unphysically large values for high-resolution spectra \--- does not alter either the FWHM or the equivalent width for any of our measurements.
+Increasing the initial FWHM estimate from 0.1\,\AA{} to 1 or 2\,\AA{} -- which are unphysically large values for high-resolution spectra -- does not alter either the measured FWHM or the equivalent width for any of our absorption lines.
 Only a small increase in computational cost is observed.
-Although we are extremely confident in our equivalent width measurements, every absorption profile was examined by eye for quality, and spurious measurements were excluded.
-
-We list the atomic data and measured equivalent widths for transitions used during this analysis in Table \ref{tab:equivalent-widths}.
-Saturated lines were excluded by removing measurements with reduced equivalent widths, $\log_{10}{(EW/\lambda)} > -4.5$\, dex.
-A minimum detectable equivalent width was calculated as a function of wavelength based on the $S/N$, and only lines that exceeded a 3-$\sigma$ detection significance were included.
-We have verified the approach by comparing our measurements of 156 lines in HD 140283 with the study of \citet{norris;et-al_1996}.
+Although we are extremely confident in our equivalent width measurements, \textit{every} absorption profile was repeatedly examined by eye for quality, and spurious measurements were excluded.
+
+We have verified the approach by comparing our measurements of 156 lines in HD\,140283 with the study of \citet{norris;et-al_1996}.
 We only included measurements in the \citet{norris;et-al_1996} study that were not marked with questionable line quality parameters.
 Excellent agreement is found between the two studies, which is illustrated in Figure \ref{fig:ew-compare}.
-The mean difference is a negligible $-0.64 \pm 2.78$\,m\AA{}, and no systematic trend is present.
-We note that the scatter may be directly attributed to the observed $S/N$ ratio, as other studies \citep{frebel;et-al_2013} using the same equivalent width measurement software described here find better agreement with hand measurements for spectra with higher $S/N$ ratios: $0.20 \pm 0.16$\,m{\AA} with \citet{aoki;et-al_2007} and $0.25 \pm 0.28$\,m{\AA} with \citet{cayrel;et-al_2004} for a spectrum of HD 122563 with $S/N > 300$\,pixel$^{-1}$.
-
-% equivalent widths plot with Norris for HD 122563
-\begin{figure}[h]
-	\includegraphics[width=\columnwidth]{./figures/smh-norris.pdf}
-	\caption{A comparison showing equivalent widths measured for HD 140283 using our automatic routine (see \S\ref{sec:line-measurements}), and those found by careful hand measurements in \citet{norris;et-al_1996}.
-No systematic trend is present, and the mean difference between these studies is $\langle\Delta{}W_\lambda\rangle = -0.64 \pm 2.78$ m\AA{}.}
-	\label{fig:ew-compare}
-\end{figure}
-
-\begin{deluxetable*}{cccccccccc}
-\tabletypesize{\scriptsize}
-\tablecaption{List of Line Transitions and Equivalent Width Measurements\label{tab:equivalent-widths}}
-\tablehead{
-	& & & & \multicolumn{5}{c}{Equivalent Width} \\
+The mean difference is a negligible ${-0.64 \pm 2.78}$\,m\AA{}, and no systematic trend is present.
+We note that the scatter may be directly attributed to the observed $S/N$ ratio, as other studies \citep{frebel;et-al_2013} using the same equivalent width measurement software described here find better agreement with hand measurements for spectra with higher $S/N$ ratios: $0.20 \pm 0.16$\,m{\AA} with \citet{aoki;et-al_2007} and $0.25 \pm 0.28$\,m{\AA} with \citet{cayrel;et-al_2004} for a spectrum of HD\,122563 with ${S/N > 300}$\,pixel$^{-1}$.
+
+We list the atomic data and measured equivalent widths for transitions used during this analysis in Table \ref{tab:equivalent-widths}.
+Saturated lines were excluded by removing measurements with reduced equivalent widths (REW), ${\log_{10}{(EW/\lambda)} > -4.5}$\,dex.
+A minimum detectable equivalent width was calculated as a function of wavelength based on the $S/N$ ratio following \citet{norris;et-al_2001}, and only lines that exceeded a 3$\sigma$ detection significance were included.
+
+\subsection{Model Atmospheres}
+We have employed the ATLAS9 plane-parallel stellar atmospheres of \citet{castelli;kurucz_2003}.
+These one-dimensional models ignore any centre-to-limb spatial variations, assume hydrostatic equilibrium and no convective overshoot from the photosphere.
+The stellar parameter spacing between models is 250\,K, 0.5\,dex in surface gravity, 0.5\,dex in [M/H] and 0.1\,dex in [$\alpha$/Fe].
+We interpolated the temperature, gas and radiative pressure, electron density and opacities between atmosphere models using the Quickhull algorithm \citep{barber;et-al_1996}.
+Quickhull is reliant on Delaunay tessellation, which suffers from extremely skewed cells when the grid points vary in size by orders of magnitude -- as $T_{\rm eff}$ values do compared to $\log{g}$ or [M,$\alpha$/H].
+If unaccounted for, interpolating using such asymmetric cells can result in significant errors in atmospheric properties across all photospheric depths.
+We scaled each stellar parameter between zero and unity prior to interpolation in order to minimise these interpolation errors.
+\\
+
+\begin{longtable*}{ccccccccc}
+\caption{\\ List of Line Transitions and Equivalent Width Measurements \label{tab:equivalent-widths}} \tabularnewline
+\cline{1-9}
+& & & & \multicolumn{5}{c}{Equivalent Widths} \\
 \cline{5-9} \\
-	\colhead{Wavelength} &
-	\colhead{Transition} &
-	\colhead{LEP} &
-	\colhead{$\log{gf}$} &
-	\colhead{C2225316-14437} &
-	\colhead{C2306265-085103} &
-	\colhead{J221821-183424} &
-	\colhead{J223504-152834} &
-	\colhead{J223811-104126} \\
-	({\AA})	& & (eV) & & (m{\AA}) & (m{\AA}) & (m{\AA}) & (m{\AA}) & (m{\AA}) 
-}
-\startdata 
+Wavelength & Transition & $\chi$ & $\log{gf}$ & C222531-145437 & C2306265-085103 & J221821-183424 & J223504-152834 & J223811-104126 \\
+({\AA}) & & (eV) & & (m{\AA}) & (m{\AA}) & (m{\AA}) & (m{\AA}) & (m{\AA}) \\
+\cline{1-9} \\
+\endhead
+\hline
+\endfoot
+\hline
+\endlastfoot
  6300.300 &       8.0 &      0.00 &    --9.717 &      45.4 &      66.9 &      38.5 &      32.8 &      17.9 \\
@@
  6645.110 &      63.1 &      1.38 &      0.204 &      24.5 &      27.8 &      17.0 &      30.3 &   \nodata \\
-\enddata
-\end{deluxetable*}
-
-\subsection{Model Atmospheres}
-We have employed the ATLAS9 plane-parallel stellar atmospheres of \citet{castelli;kurucz_2003}.
-These one-dimensional models ignore any centre-to-limb spatial variations, assume hydrostatic equilibrium and no convective overshoot from the photosphere.
-The stellar parameter spacing between models is 250\,K, 0.5\,dex in surface gravity, 0.5\,dex in [M/H] and 0.1\,dex in [$\alpha$/Fe].
-We interpolated the temperature, gas and radiative pressure, electron density and opacities between atmosphere models using the Quickhull algorithm \citep{barber;et-al_1996}.
-Quickhull is reliant on Delaunay tessellation, which suffers from extremely skewed cells when the grid points vary in size by orders of magnitude -- as $T_{\rm eff}$ values do compared to $\log{g}$ or [X/H].
-If unaccounted for, interpolating using such asymmetric cells can result in significant errors in atmospheric properties across all photospheric depths.
-We scaled each stellar parameter between zero and unity prior to interpolation in order to minimise these effects.
-During this step, $\log{g}$, [M/H] and [$\alpha$/Fe] values were scaled such that we simultaneously interpolate linearly in $T_{\rm eff}$ and logarithmically in all other parameters.
+\hline
+\end{longtable*}
+
+%HD\,136316 % F giant, -1.8, Gratton 2000+, has Na, O abundances [DONE]
+%HD\,141531 % F giant, -1.6, Gratton 2000+, has Na, O abundances [DONE]
+%HD\,44007 % G giant, -1.50, lots of references
+
+\subsection{Stellar Parameters}
+The May 2011 version of the spectral synthesis code \textsc{moog} \citep{sneden;et-al_1973} has been used to derive individual line abundances and stellar parameters.
+This version employs Rayleigh scattering \citep{sobeck;et-al_2011} instead of treating scattering as true absorption, which is particularly important for transitions blue-ward of 450\,nm.
+This is noteworthy, but is less relevant for these analyses as most of our line measurements are red-ward of 450\,nm.
+
+\subsubsection{Effective Temperature}
+\label{sec:effective-teffs}
+The effective temperature for each star was found by demanding a zero-trend in excitation potential and line abundance for measured Fe\,\textsc{i} and Fe\,\textsc{ii} line abundances.
+A linear fit was made to the line abundances for each ionisation state, and gradients less than $|10^{-3}|$\,dex were considered to be converged.
+Photometric temperatures were calculated after our spectroscopic temperatures had been derived, and are discussed in Section \ref{sec:photometric-temperatures}.
+
+\subsubsection{Microturbulence and Surface Gravity}
+The microturbulence for each star was found by forcing a zero-trend in REW and abundance for Fe\,\textsc{i} and \textsc{ii} lines.
+Similarly for the effective temperature, gradients in REW and abundance of less than $|10^{-3}|$\,dex were considered to be converged.
+The surface gravity for all stars was found by forcing the mean Fe\,\textsc{i} and Fe\,\textsc{ii} abundances to be equal.
+The process is iterative: a zero trend with the excitation potential, reduced equivalent width and abundance must be maintained.
+
+\subsubsection{Metallicity, $\mbox{[M/H]}$}
+The degeneracy between stellar parameters requires a refinement of the stellar parameters until the line abundances were consistent with the model atmosphere.
+After these parameters had converged, the model metallicity was exactly matched to that of our mean Fe\,\textsc{i} abundance.
+Line abundances that were unusually deviant ($>$3$\sigma$) from the mean were removed.
+The largest number of outlier measurements removed for any observation was an uncomfortably large nine for C222531-145437 -- which were near-saturated lines with REW $\sim -4.5$ -- leaving 60 Fe\,\textsc{i} and 10 Fe\,\textsc{ii} lines for analysis.
+For other candidates usually only one outlier measurement was removed.
+The minimum number of iron transitions employed for stellar parameter determination in any star was 44 lines (33 Fe\,\textsc{i} and 11 Fe\,\textsc{ii}) for our hottest star, J223811-104126.
+
+\subsubsection{Photometric Effective Temperatures}
+\label{sec:photometric-temperatures}
+
+As a consistency check for our spectroscopic temperatures, we have estimated effective temperatures using infrared photometry from the 2MASS \citep{skrutskie;et-al_2006} catalog and empirical $T_{\rm eff}$-colour relationships.
+The $J-K$ colour has been employed for these calculations because it has the least dependence on metallicity.
+
+The Aquarius stream is relatively close and at high-latitude, so significant extinction is not expected.
+The reddening maps of \citet{schlegel;et-al_1998} estimate that the extinction for our stars varies between ${E(B-V) = 0.03}$ to {0.07\,mags}.
+However, these maps are not perfect.
+As an alternative to using the \citet{schlegel;et-al_1998} dust maps, the level of extinction towards a star can be found directly by the strength of the interstellar Na D or K\,\textsc{i} lines \citep{munari;zwitter_1997}.
+The interstellar lines must be sufficiently separated from the stellar absorption features in order for the extinction to be measurable.
+This was the case in only one of our stars, J223811-104126.
+The equivalent width of the Na D1 line in J223811-104126 is found to be 302.4\,m{\AA}, corresponding to an ${E(B-V) = 0.12^{+0.01}_{-0.02}}$ according to the \citet{munari;zwitter_1997} relationship.
+This is a significantly higher value than the \citet{schlegel;et-al_1998} reddening map suggests: ${E(B-V) = 0.07}$.
+For completeness, both extinction values have been used to calculate photometric temperatures.
+
+Although all of our candidates are giant stars, two different $T_{\rm eff}$-color relationships have been employed: the \citet{alonso;et-al_1999} calibration for giants, and the \citet{casagrande;et-al_2010} calibration for dwarfs and sub-giants.
+All photometrically-derived temperatures are listed in Table \ref{tab:photometric-temperatures}.
+For the \citet{casagrande;et-al_2010} dwarf/sub-giant $J-K$ relationship -- which has a slight metallicity dependency -- we have adopted the spectroscopically-derived [Fe/H] values shown in Table \ref{tab:stellar-parameters}.
+
+The effective temperatures found from spectroscopy agree fairly well with the photometric estimates.
+For three of our stars, the temperatures we find are in between the two color-temperature relationships.
+There are two noteworthy deviations: J223504-152834 and J223811-104126.
+For J223504-152834 we find the star to have an effective temperature of 4650\,K, 71\,K hotter than the \citet{casagrande;et-al_2010} dwarf/sub-giant relationship, yet 420\,K hotter than the \citet{alonso;et-al_1999} estimate.
+Our temperature of 4650\,K is in good agreement with previous spectroscopic determinations (4795\,K; \citet{williams;et-al_2011}, 4597\,K; \citet{wylie-de-boer;et-al_2012}).
+The fact that the \citet{alonso;et-al_1999} photometric temperature relationship for giants predicts a temperature that is 420\,K cooler than the spectroscopically-derived values may be attributed to an underestimated amount of dust towards J223504-152834.
+A higher than expected level of extinction along the line-of-sight would produce cooler photometric temperatures than the true effective temperature.
+An extinction of $E(B-V) = 0.10$ (up from 0.04) would be required for the \citet{alonso;et-al_1999} relation to yield a temperature of ${\sim}$4500\,K, which is within the uncertainties of our effective temperature derived from spectroscopy.
+Such a discrepancy in extinction is large, but not uncommon \citep[e.g.
+see][and the case of J223811-104126]{peek;graves_2010,nataf;et-al_2012}.
+Although we suspect J223504-152834 to have a higher reddening than $E(B-V) = 0.04$, we have adopted the \citet{schlegel;et-al_1998} value for distance determinations (see Section \ref{sec:distances}) as no extinction measurement could be ascertained from interstellar absorption lines.
+
+J223811-104126, the second temperature deviant, has two extinction values available: the \citet{schlegel;et-al_1998} value of $E(B-V) = 0.07$ and the 0.12 value determined from the interstellar Na D1 line.
+Given the inherent difficulties in producing dust maps, we believe the $E(B-V) = 0.12$ determination to be more accurate.
+Employing the \citet{schlegel;et-al_1998} extinction value with the \citet{alonso;et-al_1999} color-temperature relationship yields good agreement (5104\,K) with our spectroscopic temperature of 5190\,K.
+Adopting our more accurate reddening determination yields 5215\,K.
+The \citet{casagrande;et-al_2010} scale is ${\sim}$200\,K hotter in both cases.
+
+With the exception of J223504-152834, the \citet{alonso;et-al_1999} giant relationship agrees well ($\pm$100\,K) with our spectroscopically-derived values.
+The \citet{casagrande;et-al_2010} relationship is also in reasonable agreement (most within 100\,K, largest discrepancy is 300\,K) with our spectroscopic temperatures, although we note that this relation was derived primarily for dwarfs/sub-giants and our candidates are giant stars.
+
+\begin{figure*}[t!]
+	\includegraphics[width=\textwidth]{./figures/spectra-sample.pdf}
+	\caption{Normalised rest-frame spectra surrounding the H-$\beta$ absorption line for all Aquarius stream candidates.}
+	\label{fig:spectra}
+\end{figure*}
 
@@
 \cline{1-10} \\
-HD41667			& 4630	& 1.70	& 1.66 	& --1.21
-				& 4605	& 1.88	& 1.44	& --1.16
+HD\,41667		& 4660	& 1.71	& 1.84 	& $-$1.20
+				& 4605	& 1.88	& 1.44	& $-$1.16
 				& \citet{gratton;et-al_2000} \\
-HD44007			& 4790	& 1.78	& 1.63	& --1.80
-				& 4850	& 2.00 	& 2.20	& --1.71
+HD\,44007		& 4835	& 1.78	& 1.95	& $-$1.77
+				& 4850	& 2.00 	& 2.20	& $-$1.71
 				& \citet{fulbright_2000} \\
-HD142948		& 4950	& 2.19	& 1.78	& --0.79
-				& 4713 	& 2.17 	& 1.38	& --0.77
+HD\,76932		& 5800 & 3.88 & 1.65 & $-$1.05
+				& 5849 & 4.11 & \nodata & $-$0.88 
+				& \citet{nissen;et-al_2000} \\
+HD\,136316		& 4355 & 0.58 & 2.06 & $-$1.93
+				& 4414 & 0.94 & 1.70 & $-$1.90 
+				& \citet{gratton_sneden_1991} \\
+HD\,141531		& 4345 & 0.63 & 2.07 & $-$1.69 
+				& 4280 & 0.70 & 1.60 & $-$1.68
+				& \citet{shetrone_1996} \\
+HD\,142948		& 5025	& 2.25	& 2.05	& $-$0.74
+				& 4713 	& 2.17 	& 1.38	& $-$0.77
 				& \citet{gratton;et-al_2000} \\
-\\
+\hline \\
 
@@
 \cline{1-10} \\
-C2225316-14437	& 4325				& 1.26				& 1.78				& --1.26	
-				& 4235 $\pm$ 118 	& 1.45 $\pm$ 0.21	& 1.96 $\pm$ 0.11 	& --1.20 $\pm$ 0.14 
+C222531-145437	& 4365				& 1.25				& 1.94				& $-$1.22	
+				& 4235 $\pm$ 118 	& 1.45 $\pm$ 0.21	& 1.96 $\pm$ 0.11 	& $-$1.20 $\pm$ 0.14 
 				& \citet{wylie-de-boer;et-al_2012} \\
-C2306265-085103	& 4170	& 0.85	& 1.81 	& --1.17
+C230626-085103	& 4225	& 0.85	& 1.92 	& $-$1.13
 				& \dots	& \dots	& \dots	& \dots
 				& \dots \\	
-J221821-183424	& 4590				& 0.90				& 1.91				& --1.61
-				& 4395 $\pm$ 205 	& 1.45 $\pm$ 0.35 	& 1.96 $\pm$ 0.18 	& --1.15 $\pm$ 0.21
+J221821-183424	& 4630				& 0.88				& 2.16				& $-$1.58
+				& 4395 $\pm$ 205 	& 1.45 $\pm$ 0.35 	& 1.96 $\pm$ 0.18 	& $-$1.15 $\pm$ 0.21
 				& \citet{wylie-de-boer;et-al_2012} \\
-J223504-152834	& 4590				& 2.15 				& 1.45				& --0.68
-				& 4597 $\pm$ 158 	& 2.40 $\pm$ 0.14 	& 1.47 $\pm$ 0.07 	& --0.98 $\pm$ 0.17
+J223504-152834	& 4650				& 2.16 				& 1.55				& $-$0.63
+				& 4597 $\pm$ 158 	& 2.40 $\pm$ 0.14 	& 1.47 $\pm$ 0.07 	& $-$0.98 $\pm$ 0.17
 				& \citet{wylie-de-boer;et-al_2012} \\
-J223811-104126	& 5140				& 2.96				& 1.33				& --1.45
-				& 5646 $\pm$ 147 	& 4.60 $\pm$ 0.15 	& 1.09 $\pm$ 0.11 	& --1.20 $\pm$ 0.20
+J223811-104126	& 5190				& 2.93				& 1.62				& $-$1.63
+				& 5646 $\pm$ 147 	& 4.60 $\pm$ 0.15 	& 1.09 $\pm$ 0.11 	& $-$1.20 $\pm$ 0.20
 				& \citet{wylie-de-boer;et-al_2012} 
@@
 \end{deluxetable*}
-
-%HD 136316 % F giant, -1.8, Gratton 2000+, has Na, O abundances [DONE]
-%HD 141531 % F giant, -1.6, Gratton 2000+, has Na, O abundances [DONE]
-%HD 44007 % G giant, -1.50, lots of references
-
-\subsection{Stellar Parameters}
-The most recent version of the spectral synthesis code \textsc{moog} \citep{sneden;et-al_1973} has been used to derive individual line abundances and stellar parameters.
-This version employs Rayleigh scattering \citep{sobeck;et-al_2011} instead of treating scattering as true absorption, which is particularly important for transitions blue-ward of 450\,nm.
-This is noteworthy, but is less relevant for these analyses as most of our line measurements are red-ward of 450\,nm.
-Absorption lines are assumed to form under the assumption of Local Thermal Equilibrium (LTE).
-
-\begin{figure*}[t!]
-	\includegraphics[width=\textwidth]{./figures/spectra-h-alpha.pdf}
-	\caption{Sample spectra of the H-$\alpha$ region for all Aquarius stream candidates.}
-	\label{fig:spectra-h-alpha}
-\end{figure*}
-
-\subsubsection{Effective Temperature}
-\label{sec:effective-teffs}
-The effective temperature for each star was found by demanding a zero-trend in excitation potential and line abundance for each measured Fe\,\textsc{i} transition.
-In the same way, the microturbulence was found by demanding a zero trend in reduced equivalent width against abundance.
-Linear relationships with slopes of $|0.001|$ dex were considered to be converged.
-
-\subsubsection{Photometric Effective Temperatures}
-\label{sec:photometric-temperatures}
-
-The effective temperatures published for all of our stars in Table \ref{sec:stellar-parameters} have been derived spectroscopically.
-As a consistency check for our spectroscopic temperatures, we have estimated effective temperatures using infrared photometry from the 2MASS catalog and empirical $T_{\rm eff}$-color relationships.
-The $J-K$ color has been employed for these calculations because it has the least dependence on metallicity.
-
-The Aquarius stream is relatively close and at high-latitude, so significant extinction caused by dust is not expected.
-The reddening maps of \citet{schlegel;et-al_1998} estimate that the extinction for our stars varies between E(B-V) = 0.03 to 0.07\,mags.
-However, these maps are not perfect.
-As an alternative to using the \citet{schlegel;et-al_1998} dust maps, the level of extinction towards a star can be found by the strength of the interstellar Na D or K \textsc{i} lines \citep{munari;zwitter_1997}.
-The interstellar lines must be sufficiently separated from the stellar absorption lines in order for the extinction to be measurable.
-This was the case in only one of our stars, J223811.
-The equivalent width of the Na D1 line in J223811 is found to be 302.4\,m{\AA}, corresponding to an $\mbox{E(B-V)} = 0.12^{+0.01}_{-0.02}$ according to the \citet{munari;zwitter_1997} relationship.
-This is a significantly higher value than the \citet{schlegel;et-al_1998} reddening map suggests: $\mbox{E(B-V)} = 0.07$.
-For completeness, both extinction values have been used to calculate photometric temperatures.
-
-Although all of our candidates are giant stars, two different $T_{\rm eff}$-color relationships have been employed: the \citet{alonso;et-al_1999} calibration for giants, and the \citet{casagrande;et-al_2010} calibration for dwarfs and sub-giants.
-All photometrically-derived temperatures are listed in \ref{tab:photometric-temperatures}.
-The \citet{alonso;et-al_1999} $J-K$ scale is insensitive to metallicity effects, and is in good agreement with our spectroscopic temperatures.
-For the \citet{casagrande;et-al_2010} $J-K$ relationship, which has a slight metallicity dependency, we have utilized the spectroscopically-derived [Fe/H] values shown in Table \ref{tab:stellar-parameters}.
-
-The effective temperatures found from spectroscopy agree fairly well with the photometric estimates.
-For three of our stars, the temperatures we find are in between the two color-temperature relationships.
-There are two noteworthy deviations: J223504-152834 and J223811-104126.
-For J223504-152834 we find the star to have an effective temperature of 4590\,K, only 10\,K hotter than the \citet{casagrande;et-al_2010} dwarf/sub-giant relationship, yet ${\sim}$500\,K hotter than the \citet{alonso;et-al_1999} estimate.
-Our temperature of 4590\,K is in good agreement with previous spectroscopic determinations (4795\,K; \citet{williams;et-al_2011}, 4597\,K; \citet{wylie-de-boer;et-al_2012}).
-The fact that the \citet{alonso;et-al_1999} photometric temperature relationship for giants predicts a temperature that is ${\sim}$500\,K cooler than the spectroscopically-derived values may be attributed to an underestimated amount of dust towards J223504-152834.
-A higher than expected level of extinction along the line-of-sight would produce cooler photometric temperatures than the true effective temperature.
-An extinction of $E(B-V) = 0.10$ would be required for the \citet{alonso;et-al_1999} relation to yield a temperature of ${\sim}$4500\,K \--- within the uncertainties of our effective temperature derived from spectroscopy.
-Such a discrepancy in extinction is large, but not uncommon \citep[e.g.
-see][]{peek;graves_2010,nataf;et-al_2012}.
-Although we suspect J223504-152834 to have a higher reddening than $E(B-V) = 0.04$, we have adopted the \citet{schlegel;et-al_1998} value for this analysis.
-
-J223811-104126, the second temperature deviant, has two extinction values available: the \citet{schlegel;et-al_1998} value of $E(B-V) = 0.07$ and the 0.12 value determined from the interstellar Na D1 line.
-Given the inherent difficulties in producing dust maps, we believe the $E(B-V) = 0.12$ determination to be more accurate.
-However, using the \citet{schlegel;et-al_1998} extinction value with the \citet{alonso;et-al_1999} color-temperature relationship yields excellent agreement (5104\,K) with our spectroscopic temperature of 5140\,K.
-Employing our more accurate reddening determination yields 5215\,K, still within the uncertainties of the relationship.
-The \citet{casagrande;et-al_2010} scale is ${\sim}$250\,K hotter in both cases.
-
-With the exception of J223504-152834, the \citet{alonso;et-al_1999} giant relationship agrees well ($\pm$100\,K) with our spectroscopically-derived values.
-The \citet{casagrande;et-al_2010} relationship is also in relatively good agreement (most within 100\,K, largest discrepancy is 220\,K) with our spectroscopic temperatures, although we note that this relation was derived primarily for dwarfs/sub-giants and our candidates are all giant stars.
 
@@
 \startdata 
-C222531-144370 	& 0.03\phn	& 	0.75 & 4247	&	4391 \\	
+C222531-145437 	& 0.03\phn	& 	0.75 & 4247	&	4391 \\	
 C230626-085103	& 0.05\phn	&	0.82 & 4091	&	4200 \\	
@@
 
-\subsubsection{Surface Gravity}
-
-The surface gravity for all stars was found by forcing the mean Fe\,\textsc{i} and Fe\,\textsc{ii} abundances to be equal.
-The process is iterative: a zero trend with the excitation potential, reduced equivalent width and abundance must be maintained.
-For two stars, X and Y, the surface gravity could not be found by balancing the Fe\,\textsc{i} and \textsc{ii} line abundances.
-The smallest difference between the median abundances was $\langle$Fe\,\textsc{i} $-$ Fe\,\textsc{ii}$\rangle = 0.05$\,dex, which was considered to be converged.
-Varying the surface gravity from this solution did alter the mean Fe\,\textsc{i} and \textsc{ii} abundances, but the difference $\langle$Fe\,\textsc{i} $-$ Fe\,\textsc{ii}$\rangle$ remained constant at 0.05\,dex.
-In these two instances, the surface gravity was set to be closer towards the isochrone, while the $\langle$Fe\,\textsc{i} $-$ Fe\,\textsc{ii}$\rangle$ = 0.05\,dex condition was maintained.
-
-\subsubsection{Metallicity, $\mbox{[M/H]}$}
-The degeneracy between parameters required a refinement of the stellar parameters until the line abundances were consistent with the model atmosphere.
-After these parameters had converged, the model metallicity was exactly matched to that of our mean Fe\,\textsc{i} abundance.
-Line abundances that were unusually deviant ($>$3-$\sigma$) from the mean were removed.
-The largest number of outlier measurements removed for any observation was nine for C222531-144370, leaving 60 Fe\,\textsc{i} and 10 Fe\,\textsc{ii} lines for analysis.
-The minimum number of Fe transitions used in any star was 44 lines (33 Fe\,\textsc{i} and 11 Fe\,\textsc{ii}) for our hottest star, J223811-104126.
-
 % spectral plots for five stars
@@
 We have scaled our abundances to solar values using the Sun's chemical composition described in \citet{asplund;et-al_2009}.
+The analysis of each element is discussed separately below in order of atomic number, with comparable elements grouped accordingly.
 
 \subsubsection{Carbon}
+Carbon is produced by the triple-$\alpha$ process and ejected in supernova events.
+Carbon abundances on the stellar surface increase as a star evolves along the red giant branch through dredge-up processes.
+While no atomic carbon transitions exist in an optical spectrum, carbon is inferred from strong band heads and molecular features.
+
+We have measured carbon abundances for all stars from the G-band head near {4313\,\AA} and the CH band head at {4323\,\AA}.
+Careful attention was paid to the normalisation of these regions.
+Synthetic spectra was computed for different carbon abundances in order to find the best fit with the observed spectrum.
+The abundances were determined separately for each band head and in all cases they agree within 0.10\,dex of each other, which is less than the typical quoted uncertainty of 0.20\,dex.
+The spectra were convolved with a Gaussian kernel, where the width was determined from synthesising spectra of nearby atomic lines that have known abundances from equivalent width measurements.
+A $^{12}$C/$^{13}$C ratio of 4 was assumed, which provides a good fit to the data.
+An example fit to these regions for a standard and program star is shown in Figure \ref{fig:carbon}.
+
+Carbon abundances derived for our program stars agree well with the literature.
+For HD\,136316 we find {${\rm [C/Fe]} = -0.50 \pm 0.20$}\,dex, where \citet{gratton;et-al_2000} find {[C/Fe] $= -0.66$\,dex}, and our ${{\rm [C/Fe]} = -0.48}$\,dex measurement for HD\,141531 agrees within 0.06\,dex.
+Most program stars have near-solar carbon abundances, ranging from ${{\rm [C/Fe]} = -0.30}$ for {J221821-183424}, and +0.05 for {J223811-104126}.
+
+\begin{figure}[h!]
+	\includegraphics[width=\columnwidth]{./figures/HD44007.pdf}
+	\caption{The Carbon CH band near 4313\,{\AA} in our standard star HD\,44007.
+The best-fit synthetic spectra is shown, with uncertainties in $\log_{\epsilon}$C of $\pm0.20$\,dex -- the smallest uncertainty assumed from synthetic spectral fits.}
+	\label{fig:carbon}
+\end{figure}
 
@@
 Oxygen is a particularly difficult element to measure.
-There are only a handful of lines available in an optical spectrum: the forbidden [O \textsc{i}] lines at 630 nm and 636 nm, and the O \textsc{i} triplet lines at 777 nm.
-The forbidden lines are very weak, and become immeasurable in either hot and/or metal-poor stars ([Fe/H] $\lesssim -1.5$ dex).
-When they are present, depending on the radial velocity of the star, the [O \textsc{i}] lines can be significantly affected by telluric absorption.
-Moreover, the 630 nm line is blended with a Ni \textsc{i} absorption line \citep{allende-prieto;et-al_2001}, and hence the region requires careful consideration.
-Although the O \textsc{i} triplet lines at 777 nm are stronger than the forbidden lines, they are extremely susceptible to non-LTE and 3D effects \citep{asplund;perez_2001}, and sensitive to changes in microturbulence.
-
-The [O \textsc{i}] lines were measurable in four of our candidates.
+There are only a handful of lines available in an optical spectrum: the forbidden {[O\,\textsc{i}]} lines at 630\,nm and 636\,nm, and the O\,\textsc{i} triplet lines at 777\,nm.
+The forbidden lines are very weak and become immeasurable in hot and/or metal-poor stars (${\mbox{[Fe/H]} \lesssim -1.5}$\,dex).
+When they are present, depending on the radial velocity of the star, the {[O\,\textsc{i}]} lines can be significantly affected by telluric absorption.
+Moreover, the 630\,nm line is blended with a Ni\,\textsc{i} absorption line \citep{allende-prieto;et-al_2001}.
+Hence the region requires careful consideration.
+Although the O\,\textsc{i} triplet lines at 777\,nm are stronger than the forbidden lines, they are extremely susceptible to non-LTE effects and surface granulation \citep{asplund;perez_2001}, and sensitive to changes in microturbulence.
+Forbidden {[O\,\textsc{i}]} abundances in our standard stars agree well with the literature, where an offset of $-0.07$\,dex in [O/Fe] is seen for HD\,136316 when compared with \citet{gratton;et-al_2000}.
+
+The {[O\,\textsc{i}]} lines were measurable in four of our Aquarius candidates.
 Careful consideration was taken when correcting for telluric absorption.
-The 6300$\lambda$ line in one of our candidates, C2306265-085103, was sufficiently affected by telluric absorption such that the line was considered immeasurable.
-Thus, only the 6363$\lambda$ transition was used to derive an oxygen abundance for C2306265-085103.
-In our hottest star, J223811-104126, the forbidden oxygen lines were not detected above a 3-$\sigma$ significance.
-After synthesising the region, we deduce a very conservative upper limit of $\mbox{[O/Fe]} < -0.50$ dex from the [O \textsc{i}] lines.
-This is consistent with the rest of our candidates, with [O/Fe] abundances varying between 0.41 to 0.57\,dex.
-
-In order to derive an oxygen measurement for J223811-104126, we were forced to use the triplet lines at 777\,nm.
-Each line was synthesised, and a mean abundance was calculated for each candidate.
-Abundances determined from the oxygen triplet lines were systematically $+0.27$\,dex higher than found from the [O \textsc{i}] lines.
-\citet{perez;et-al_2006} found [O/Fe] values based on the O \textsc{i} permitted triplet lines are on average $+0.19 \pm 0.07$\,dex higher than those found from the forbidden lines, after non-LTE corrections of $-$0.08\,dex had been applied to the permitted abundance.
-Thus, our 0.27\,dex offset between measurements of the [O \textsc{i}] and O \textsc{i} triplet lines is exactly the same as found by \citet{perez;et-al_2006}, which we attribute to a combination of systematic phenomena including non-LTE and 3D effects.
-\citet{perez;et-al_2006} concluded the weak forbidden lines, when not too weak, probably give the most reliable estimate of oxygen abundance.
-
-From the permitted O \textsc{i} triplet, we derive an oxygen abundance of $\mbox{[O/Fe]} = 0.41 \pm 0.01$\,dex (random scatter) for J223811-104126.
-This measurement will be systematically higher than the `true' abundance if it were discernible from the [O \textsc{i}] lines, on the order of ${\sim}$0.27\,dex.
-When we apply this crude offset derived from the rest of our sample, we arrive at a corrected abundance of $\mbox{[O/Fe]} = 0.14 \pm 0.08$\,dex for J223811-104126.
-This is the most oxygen-deficient star in our sample.
+The 630\,nm line in one of our candidates, {C2306265-085103}, was sufficiently affected by telluric absorption such that we deemed the line unrecoverable.
+Thus, only the 636\,nm transition was used to derive an oxygen abundance for {C2306265-085103}.
+In our hottest star, {J223811-104126}, the forbidden oxygen lines were not detected above a 3$\sigma$ significance.
+After synthesising the region, we deduce a very conservative upper limit of ${\mbox{[O/Fe]} < 0.50}$\,dex from the {[O\,\textsc{i}]} lines.
+This is consistent with the rest of our candidates, with [O/Fe] abundances varying between 0.43 to 0.49\,dex.
+
+In order to derive an oxygen measurement for {J223811-104126}, we were forced to use the triplet lines at 777\,nm.
+Each line was synthesised and a mean abundance was calculated for each candidate.
+Abundances determined from the oxygen triplet lines were systematically $+0.27$\,dex higher than that found from the {[O\,\textsc{i}]} forbidden lines.
+\citet{perez;et-al_2006} found [O/Fe] values based on the {O\,\textsc{i}} permitted triplet lines are on average ${+0.19 \pm 0.07}$\,dex higher than those found from the forbidden lines, which did not include non-LTE corrections of $+$0.08\,dex.
+Thus, we  attribute our $+$0.27\,dex offset between measurements of the {[O\,\textsc{i}]} and {O \textsc{i}} triplet lines to non-LTE and 3D effects as it is precisely the same as the total difference found by \citet{perez;et-al_2006}.
+\citet{perez;et-al_2006} concluded that the forbidden lines, when not too weak, probably give the most reliable estimate of oxygen abundance.
+
+From the permitted O\,\textsc{i} triplet, we derive an oxygen abundance of ${\mbox{[O/Fe]} = 0.42 \pm 0.01}$\,dex (random scatter) for {J223811-104126}.
+This measurement will be systematically higher than the `true' abundance if it were discernible from the [O\,\textsc{i}] lines, on the order of ${\sim}+0.27$\,dex.
+When we apply this crude offset derived from the rest of our sample, we arrive at a corrected abundance of ${\mbox{[O/Fe]} = 0.15 \pm 0.08}$\,dex for {J223811-104126}.
+This is the most oxygen-deficient star in our sample by a factor of two.
 
@@
 \label{sec:sodium-abundances}
-Our line list includes three clean, unblended sodium lines at 5688$\lambda$, 6154$\lambda$ and 6161$\lambda$.
+Our line list includes three clean, unblended sodium lines at 5688\,\AA, 6154\,\AA and 6161\,\AA.
 Not all three of these lines were detectable in each star.
-In the hottest and most metal-poor stars, J223811 and J221821-183424 respectively, only the 5688$\lambda$ line was measurable.
-Consequently, an uncertainty of 0.10\,dex was adopted for these stars.
-For stars where multiple sodium lines were available, the line-to-line scatter is reasonable: smaller than 0.09\,dex.
+In the hottest and most metal-poor stars, J223811-104126 and J221821-183424 respectively, only the 5688\,{\AA} line was measurable.
+Consequently, an uncertainty of $\pm0.10$\,dex was adopted for these stars.
+For stars where multiple sodium lines were available, the line-to-line scatter is reasonable: usually around 0.04\,dex with a maximum of 0.09\,dex in HD\,41667.
 
 % [Na/Fe] measurements in the standard stars? 
-
-\subsubsection{$\alpha$-elements (Mg, Ca, Si and Ti)}
+Our [Na/Fe] abundances appear systematically higher than values found in the literature, on the order of 0.10\,dex.
+For HD\,142948 we yield {[Na/Fe] = 0.22}\,dex, which is +0.10\,dex higher than that found for \citet{gratton;et-al_2000}, and similarly we find HD\,76932 to be +0.10\,dex higher than reported by with \citet{fulbright_2000}.
+\citet{gratton;et-al_2000} also found HD\,136316 to have {[Na/Fe] = $-$0.29}\,dex, where we find {[Na/Fe] = $-0.14$}\,dex where there is excellent agreement in the stellar parameters.
+Different solar compositions employed between this study and earlier work can account for $\sim$0.08\,dex of this effect, leaving the residual difference well within the observational uncertainties.
+However, it is important to note that the [Na/Fe] abundance ratios presented may be higher compared to previous studies.
+
+\subsubsection{$\alpha$-elements (Mg, Si, Ca and Ti)}
 \label{sec:alpha-elements}
 
-The $\alpha$-elements (Mg, Ca, Si and Ti) are forged through $\alpha$-particle capture in assorted burning stages of stellar evolution, including the burning of carbon, neon and silicon.
-Although Ti ($Z = 22$) is not formally an $\alpha$-element, its abundance generally varies with those of the other $\alpha$-elements and therefore has been included here.
+The $\alpha$-elements (Mg, Si, Ca and Ti) are forged through $\alpha$-particle capture in assorted burning stages of stellar evolution, including the burning of carbon, neon and silicon.
+Although Si and Ti ($Z = 14, 22$) are not formally $\alpha$-elements, their abundance generally varies with those of the other $\alpha$-elements and therefore has been included here.
 
@@
 %Magnesium has been measured from unblended lines that fall within the linear regime between reduced equivalent width and abundance.
-Depending on the radial velocity of the star, some magnesium lines were be affected by telluric absorption, particularly the 6318$\lambda$ and 6965$\lambda$ transitions.
-Atmospheric absorption was most notable for C2225316-14437, where three of the four Mg transitions in our line list suffered some degree of telluric absorption, requiring an attentive correction.
+Depending on the radial velocity of the star, some magnesium lines were affected by telluric absorption, particularly the 6318 and $6965\,{\rm \AA}$ transitions.
+Atmospheric absorption was most notable for C222531-145437, where three of the four Mg transitions in our line list suffered some degree of telluric absorption, requiring an attentive correction.
 Every amended absorption profile was carefully examined, and lines with suspicious profiles were excluded from the final magnesium abundance.
+All [$\alpha$/Fe] abundance ratios in the standard stars are in excellent agreement with the literature.
+Typically the difference is 0.01\,dex, with the largest discrepancy of {$\Delta$[Ti/Fe] = +0.13\,dex} for HD\,76932 when compared with \citet{fulbright_2000}.
 
@@
 	\includegraphics[width=\columnwidth]{./figures/aquarius-alpha-fe.pdf}
-	\caption{A plot showing $[\alpha/\mbox{Fe}]$ for all Aquarius stream stars.}
-	\label{fig:alpha-fe}
+	\caption{The $\alpha$-element abundances with respect to iron content. The mean [$\alpha$/Fe] abundance from these is shown in the bottom panel.}
+	\label{fig:alpha-elements}
 \end{figure}
@@
 Of all the $\alpha$-elements, calcium has the smallest measurement scatter in our stars.
-Four line measurements were used for each star, with a measurement uncertainty of 0.01\,dex.
-As shown in Figure \ref{fig:alpha-elements}, all Aquarius candidates show super-solar Ca abundances, ranging between 0.23 to 0.43 dex, consistent with both [Mg/Fe] and [Si/Fe] measurements.
-
-However, C2225316-14437 has an unusually high silicon abundance ($\mbox{[Si/Fe]} = 0.72$), well outside the uncertainties of the rest of our sample.
-The silicon line abundances are in relatively good agreement with one another.
-If we exclude the most prominent outlier, then the mean abundance drops only slightly to $\mbox{[Si/Fe]} = 0.70 \pm 0.04$\,dex.
-The lowest silicon line abundance for C2225316-14437 is $\mbox{[Si/Fe]} = 0.57$\,dex, which is still significantly higher than the averaged abundance for any other star.
+The mean was formed from four line measurements in each star, with the typical measurement uncertainty was 0.01\,dex.
+As shown in Figure \ref{fig:alpha-elements}, all Aquarius candidates show super-solar [Ca/Fe], ranging between +0.23 to +0.43\,dex, consistent with [Mg,Ti,Si/Fe] measurements.
+
+However, {C222531-145437} has an unusually high silicon abundance (${\mbox{[Si/Fe]} = 0.79}$\,dex), well outside the uncertainties of the rest of our sample.
+The silicon line abundances in this star are in relatively good agreement with one another.
+If we exclude the highest line measurement, then the mean abundance drops only slightly to ${\mbox{[Si/Fe]} = 0.73 \pm 0.04}$\,dex.
+The lowest silicon line abundance for {C222531-145437} is ${\mbox{[Si/Fe]} = 0.61}$\,dex, which is still significantly higher than the mean abundance for any other star.
 
 % titanium measurements?
-Titanium abundances for the stream stars are generally in agreement, showing typical $\alpha$-enhancement signatures.
-Our titanium measurements are derived from clean, unblended lines.
-The number of transitions available in our spectra varies from four to seven.
+Titanium abundances for the stream stars are generally in agreement with one another, showing typical $\alpha$-enhancement signatures.
+Our mean titanium abundances are derived from four to seven clean, unblended lines.
 In our hottest and most metal-poor stars, no suitable Ti\,\textsc{i} transitions were available.
-In other stream candidates, the mean difference between species is $\langle$Ti\,\textsc{i}$ - $Ti\,\textsc{ii}$\rangle = 0.24$\,dex.
-Although this discrepancy is not negligible, there are limited lines available for comparison, and our $\langle$Fe\,\textsc{i}$ - $Fe\,\textsc{ii}$\rangle$ abundances are in good agreement.
+In other stream candidates, the mean difference between species is ${\langle{\rm Ti}\,\textsc{i} - {\rm Ti}\,\textsc{ii}\rangle = 0.24\,{\rm dex}}$.
+Although this discrepancy is not negligible, there are limited lines available for comparison and our mean ${\langle{\rm Fe}\,\textsc{i} - {\rm Fe}\,\textsc{ii}\rangle}$, ${\langle{\rm Cr}\,\textsc{i} - {\rm Cr}\,\textsc{ii}\rangle}$ (see Section \ref{sec:fe-peak-abundances}) differences are very small.
+
+\clearpage
+
+\begin{longtable*}{lccccccclcccccc}
+\caption{\\ Standard Star Abundances\label{tab:standard-star-abundances}} \tabularnewline
+\cline{1-15}
+Species & $N$ & $\log\epsilon(X)$ & $\sigma_\epsilon$ & [X/H] & [X/Fe] & $\sigma$ && 
+Species & $N$ & $\log\epsilon(X)$ & $\sigma_\epsilon$ & [X/H] & [X/Fe] & $\sigma$ \tabularnewline
+\cline{1-15} \tabularnewline
+% This works.
+\endhead
+\hline
+\multicolumn{15}{r}{Continued..}
+\endfoot
+\hline
+\endlastfoot
+
+\\
+\multicolumn{7}{c}{HD\,41667} & \colhead{} & \multicolumn{7}{c}{HD\,44007} \\
+\cline{1-7} \cline{9-15}
+   C (CH)       &   2 &    6.95 &    0.20 &  --1.48 &  --0.28 &    0.20 &&
+   C (CH)       &   2 &    6.66 &    0.20 &  --1.77 &  --0.01 &    0.20 \\
+   O \textsc{I} &   2 &    7.95 &    0.06 &  --0.74 &    0.46 &    0.04 &&
+   O \textsc{I} &   1 &    7.41 &    0.00 &  --1.28 &    0.48 &    0.00 \\
+  Na \textsc{I} &   3 &    4.90 &    0.18 &  --1.34 &  --0.14 &    0.10 &&
+  Na \textsc{I} &   2 &    4.44 &    0.09 &  --1.80 &  --0.04 &    0.06 \\
+  Mg \textsc{I} &   4 &    6.72 &    0.10 &  --0.88 &    0.32 &    0.05 &&
+  Mg \textsc{I} &   2 &    6.30 &    0.06 &  --1.29 &    0.47 &    0.04 \\
+  Al \textsc{I} &   4 &    5.18 &    0.11 &  --1.27 &  --0.07 &    0.06 &&
+  Al \textsc{I} &   1 &    4.80 &    0.00 &  --1.65 &    0.11 &    0.00 \\
+  Si \textsc{I} &   5 &    6.55 &    0.06 &  --0.96 &    0.24 &    0.03 &&
+  Si \textsc{I} &   5 &    6.07 &    0.07 &  --1.44 &    0.32 &    0.03 \\
+   K \textsc{I} &   1 &    4.64 &    0.00 &  --0.39 &    0.81 &    0.00 &&
+   K \textsc{I} &   1 &    4.31 &    0.00 &  --0.72 &    1.04 &    0.00 \\
+  Ca \textsc{I} &   4 &    5.47 &    0.06 &  --0.87 &    0.33 &    0.03 &&
+  Ca \textsc{I} &   4 &    4.95 &    0.02 &  --1.39 &    0.37 &    0.01 \\
+ Sc \textsc{II} &   6 &    2.13 &    0.13 &  --1.02 &    0.18 &    0.05 &&
+ Sc \textsc{II} &   6 &    1.39 &    0.10 &  --1.76 &    0.00 &    0.04 \\
+  Ti \textsc{I} &   4 &    3.96 &    0.04 &  --0.99 &    0.21 &    0.02 &&
+  Ti \textsc{I} &   1 &    3.48 &    0.00 &  --1.47 &    0.29 &    0.00 \\
+ Ti \textsc{II} &   3 &    4.09 &    0.25 &  --0.86 &    0.35 &    0.14 &&
+ Ti \textsc{II} &   4 &    3.47 &    0.15 &  --1.48 &    0.28 &    0.07 \\
+   V \textsc{I} &   6 &    2.87 &    0.13 &  --1.06 &    0.14 &    0.05 &&
+   V \textsc{I} &   4 &    2.17 &    0.03 &  --1.77 &  --0.00 &    0.01 \\
+  Cr \textsc{I} &  10 &    4.22 &    0.08 &  --1.42 &  --0.22 &    0.03 &&
+  Cr \textsc{I} &  15 &    3.65 &    0.07 &  --1.99 &  --0.22 &    0.02 \\
+ Cr \textsc{II} &   2 &    4.54 &    0.05 &  --1.09 &    0.11 &    0.04 &&
+ Cr \textsc{II} &   3 &    4.00 &    0.01 &  --1.64 &    0.12 &    0.01 \\
+  Mn \textsc{I} &   3 &    3.96 &    0.01 &  --1.47 &  --0.27 &    0.01 &&
+  Mn \textsc{I} &   3 &    3.15 &    0.04 &  --2.28 &  --0.52 &    0.02 \\
+  Fe \textsc{I} &  61 &    6.30 &    0.12 &  --1.20 &    0.00 &    0.02 &&
+  Fe \textsc{I} &  51 &    5.74 &    0.13 &  --1.76 &    0.00 &    0.02 \\
+ Fe \textsc{II} &  13 &    6.35 &    0.05 &  --1.15 &    0.05 &    0.01 &&
+ Fe \textsc{II} &  15 &    5.74 &    0.10 &  --1.76 &  --0.00 &    0.03 \\
+  Co \textsc{I} &   5 &    3.75 &    0.10 &  --1.24 &  --0.04 &    0.04 &&
+  Co \textsc{I} &   1 &    3.22 &    0.00 &  --1.77 &  --0.01 &    0.00 \\
+  Ni \textsc{I} &   7 &    4.94 &    0.12 &  --1.28 &  --0.08 &    0.05 &&
+  Ni \textsc{I} &   4 &    4.47 &    0.05 &  --1.75 &    0.01 &    0.02 \\
+  Cu \textsc{I} &   1 &    2.72 &    0.00 &  --1.47 &  --0.27 &    0.00 &&
+  Cu \textsc{I} &   1 &    1.84 &    0.00 &  --2.35 &  --0.59 &    0.00 \\
+  Zn \textsc{I} &   2 &    3.36 &    0.08 &  --1.20 &    0.00 &    0.06 &&
+  Zn \textsc{I} &   2 &    2.83 &    0.05 &  --1.73 &    0.03 &    0.04 \\
+  Sr \textsc{I} &   1 &    1.31 &    0.00 &  --1.56 &  --0.36 &    0.00 &&
+  Sr \textsc{I} &   1 &    0.91 &    0.00 &  --1.96 &  --0.20 &    0.00 \\
+  Y \textsc{II} &   5 &    0.97 &    0.19 &  --1.24 &  --0.04 &    0.09 &&
+  Y \textsc{II} &   6 &    0.28 &    0.11 &  --1.93 &  --0.16 &    0.05 \\
+  Zr \textsc{I} &   2 &    1.42 &    0.05 &  --1.17 &    0.04 &    0.04 &&
+  Zr \textsc{I} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
+ Zr \textsc{II} &   1 &    1.28 &    0.00 &  --1.30 &  --0.10 &    0.00 &&
+ Zr \textsc{II} &   1 &    0.59 &    0.00 &  --1.99 &  --0.23 &    0.00 \\
+ Ba \textsc{II} &   2 &    1.02 &    0.04 &  --1.16 &    0.05 &    0.02 &&
+ Ba \textsc{II} &   2 &    0.25 &    0.01 &  --1.93 &  --0.17 &    0.01 \\
+ La \textsc{II} &   2 &    0.14 &    0.04 &  --0.96 &    0.24 &    0.03 &&
+ La \textsc{II} &   2 &  --0.52 &    0.02 &  --1.62 &    0.14 &    0.01 \\
+ Ce \textsc{II} &   4 &    0.35 &    0.18 &  --1.23 &  --0.02 &    0.09 &&
+ Ce \textsc{II} &   3 &  --0.41 &    0.12 &  --1.99 &  --0.23 &    0.07 \\
+ Nd \textsc{II} &   9 &    0.54 &    0.10 &  --0.88 &    0.32 &    0.03 &&
+ Nd \textsc{II} &   9 &  --0.36 &    0.11 &  --1.78 &  --0.01 &    0.04 \\
+ Eu \textsc{II} &   1 &  --0.05 &    0.00 &  --0.57 &    0.63 &    0.00 &&
+ Eu \textsc{II} &   1 &  --0.36 &    0.00 &  --0.88 &    0.88 &    0.00 \\
+
+\cline{1-7} \cline{9-15} \\ \\
+\multicolumn{7}{c}{HD\,76932} && \multicolumn{7}{c}{HD\,136316} \\
+\cline{1-7} \cline{9-15}
+   C (CH)       &   2 &    7.52 &    0.20 &  --0.91 &    0.14 &    0.20 &&
+   C (CH)       &   2 &    5.95 &    0.20 &  --2.48 &  --0.50 &    0.20 \\
+   O \textsc{I} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata &&
+   O \textsc{I} &   1 &    7.17 &    0.00 &  --1.52 &    0.41 &    0.00 \\
+  Na \textsc{I} &   3 &    5.37 &    0.04 &  --0.87 &    0.18 &    0.02 &&
+  Na \textsc{I} &   2 &    4.17 &    0.04 &  --2.08 &  --0.14 &    0.02 \\
+  Mg \textsc{I} &   3 &    6.95 &    0.20 &  --0.65 &    0.40 &    0.11 &&
+  Mg \textsc{I} &   2 &    6.08 &    0.24 &  --1.52 &    0.41 &    0.17 \\
+  Al \textsc{I} &   4 &    5.45 &    0.07 &  --1.00 &    0.05 &    0.03 &&
+  Al \textsc{I} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
+  Si \textsc{I} &   5 &    6.79 &    0.06 &  --0.72 &    0.33 &    0.03 &&
+  Si \textsc{I} &   4 &    5.89 &    0.05 &  --1.62 &    0.31 &    0.03 \\
+   K \textsc{I} &   1 &    4.94 &    0.00 &  --0.09 &    0.96 &    0.00 &&
+   K \textsc{I} &   1 &    3.91 &    0.00 &  --1.12 &    0.81 &    0.00 \\
+  Ca \textsc{I} &   4 &    5.60 &    0.02 &  --0.74 &    0.31 &    0.01 &&
+  Ca \textsc{I} &   4 &    4.71 &    0.02 &  --1.63 &    0.30 &    0.01 \\
+ Sc \textsc{II} &   6 &    2.25 &    0.11 &  --0.90 &    0.16 &    0.04 &&
+ Sc \textsc{II} &   5 &    1.30 &    0.05 &  --1.85 &    0.08 &    0.02 \\
+  Ti \textsc{I} &   1 &    4.36 &    0.00 &  --0.59 &    0.46 &    0.00 &&
+  Ti \textsc{I} &   3 &    3.19 &    0.03 &  --1.76 &    0.17 &    0.02 \\
+ Ti \textsc{II} &   3 &    4.33 &    0.04 &  --0.62 &    0.44 &    0.02 &&
+ Ti \textsc{II} &   3 &    3.44 &    0.10 &  --1.51 &    0.42 &    0.06 \\
+   V \textsc{I} &   3 &    3.17 &    0.13 &  --0.76 &    0.29 &    0.08 &&
+   V \textsc{I} &   5 &    1.87 &    0.07 &  --2.06 &  --0.13 &    0.03 \\
+  Cr \textsc{I} &  15 &    4.46 &    0.05 &  --1.18 &  --0.13 &    0.01 &&
+  Cr \textsc{I} &  12 &    3.49 &    0.05 &  --2.15 &  --0.22 &    0.01 \\
+ Cr \textsc{II} &   3 &    4.76 &    0.02 &  --0.88 &    0.17 &    0.01 &&
+ Cr \textsc{II} &   2 &    3.90 &    0.02 &  --1.74 &    0.19 &    0.01 \\
+  Mn \textsc{I} &   3 &    4.08 &    0.03 &  --1.35 &  --0.29 &    0.02 &&
+  Mn \textsc{I} &   3 &    3.08 &    0.02 &  --2.35 &  --0.42 &    0.01 \\
+  Fe \textsc{I} &  51 &    6.45 &    0.10 &  --1.05 &    0.00 &    0.01 &&
+  Fe \textsc{I} &  62 &    5.57 &    0.11 &  --1.93 &    0.00 &    0.01 \\
+ Fe \textsc{II} &  13 &    6.50 &    0.07 &  --1.00 &    0.05 &    0.02 &&
+ Fe \textsc{II} &  14 &    5.61 &    0.12 &  --1.89 &    0.04 &    0.03 \\
+  Co \textsc{I} &   3 &    4.10 &    0.06 &  --0.89 &    0.16 &    0.03 &&
+  Co \textsc{I} &   6 &    3.11 &    0.07 &  --1.88 &    0.05 &    0.03 \\
+  Ni \textsc{I} &   5 &    5.29 &    0.02 &  --0.93 &    0.13 &    0.01 &&
+  Ni \textsc{I} &   5 &    4.22 &    0.11 &  --2.00 &  --0.07 &    0.05 \\
+  Cu \textsc{I} &   1 &    2.84 &    0.00 &  --1.35 &  --0.30 &    0.00 &&
+  Cu \textsc{I} &   1 &    1.73 &    0.00 &  --2.46 &  --0.53 &    0.00 \\
+  Zn \textsc{I} &   2 &    3.58 &    0.03 &  --0.98 &    0.07 &    0.02 &&
+  Zn \textsc{I} &   2 &    2.72 &    0.03 &  --1.83 &    0.10 &    0.02 \\
+  Sr \textsc{I} &   1 &    1.65 &    0.00 &  --1.22 &  --0.17 &    0.00 &&
+  Sr \textsc{I} &   1 &    0.53 &    0.00 &  --2.34 &  --0.41 &    0.00 \\
+  Y \textsc{II} &   5 &    1.14 &    0.05 &  --1.07 &  --0.02 &    0.02 &&
+  Y \textsc{II} &   7 &    0.12 &    0.11 &  --2.09 &  --0.16 &    0.04 \\
+  Zr \textsc{I} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata &&
+  Zr \textsc{I} &   1 &    0.79 &    0.00 &  --1.79 &    0.14 &    0.00 \\
+ Zr \textsc{II} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata &&
+ Zr \textsc{II} &   1 &    0.68 &    0.00 &  --1.90 &    0.03 &    0.00 \\
+ Ba \textsc{II} &   1 &    1.16 &    0.00 &  --1.02 &    0.03 &    0.00 &&
+ Ba \textsc{II} &   1 &    0.22 &    0.00 &  --1.96 &  --0.03 &    0.00 \\
+ La \textsc{II} &   1 &    0.61 &    0.00 &  --0.49 &    0.56 &    0.00 &&
+ La \textsc{II} &   2 &  --0.68 &    0.03 &  --1.78 &    0.16 &    0.02 \\
+ Ce \textsc{II} &   2 &    0.37 &    0.03 &  --1.21 &  --0.16 &    0.02 &&
+ Ce \textsc{II} &   5 &  --0.39 &    0.18 &  --1.97 &  --0.04 &    0.08 \\
+ Nd \textsc{II} &   3 &    0.56 &    0.06 &  --0.86 &    0.19 &    0.03 &&
+ Nd \textsc{II} &  10 &  --0.36 &    0.04 &  --1.78 &    0.15 &    0.01 \\
+ Eu \textsc{II} &   1 &  --0.01 &    0.00 &  --0.53 &    0.52 &    0.00 &&
+ Eu \textsc{II} &   1 &  --1.07 &    0.00 &  --1.59 &    0.34 &    0.00 \\
+
+\cline{1-7} \cline{9-15} \\ \\
+\multicolumn{7}{c}{HD\,141531} && \multicolumn{7}{c}{HD\,142948} \\
+\cline{1-7} \cline{9-15}
+   C (CH)       &   2 &    6.33 &    0.20 &  --2.10 &  --0.48 &    0.20 &&
+   C (CH)       &   2 &    7.72 &    0.20 &  --0.71 &    0.03 &    0.20 \\
+   O \textsc{I} &   2 &    7.33 &    0.01 &  --1.35 &    0.34 &    0.01 &&
+   O \textsc{I} &   2 &    8.43 &    0.02 &  --0.26 &    0.47 &    0.02 \\
+  Na \textsc{I} &   2 &    4.28 &    0.05 &  --1.96 &  --0.27 &    0.04 &&
+  Na \textsc{I} &   3 &    5.73 &    0.13 &  --0.51 &    0.22 &    0.08 \\
+  Mg \textsc{I} &   2 &    6.30 &    0.15 &  --1.29 &    0.40 &    0.10 &&
+  Mg \textsc{I} &   3 &    7.24 &    0.12 &  --0.36 &    0.38 &    0.07 \\
+  Al \textsc{I} &   2 &    4.74 &    0.10 &  --1.71 &  --0.02 &    0.07 &&
+  Al \textsc{I} &   4 &    5.94 &    0.08 &  --0.51 &    0.23 &    0.04 \\
+  Si \textsc{I} &   5 &    6.03 &    0.10 &  --1.48 &    0.21 &    0.04 &&
+  Si \textsc{I} &   5 &    7.07 &    0.05 &  --0.44 &    0.30 &    0.02 \\
+   K \textsc{I} &   1 &    3.99 &    0.00 &  --1.04 &    0.65 &    0.00 &&
+   K \textsc{I} &   1 &    5.04 &    0.00 &    0.01 &    0.75 &    0.00 \\
+  Ca \textsc{I} &   4 &    4.90 &    0.03 &  --1.44 &    0.25 &    0.01 &&
+  Ca \textsc{I} &   4 &    5.78 &    0.01 &  --0.56 &    0.18 &    0.01 \\
+ Sc \textsc{II} &   4 &    1.56 &    0.04 &  --1.59 &    0.10 &    0.02 &&
+ Sc \textsc{II} &   6 &    2.57 &    0.11 &  --0.58 &    0.16 &    0.05 \\
+  Ti \textsc{I} &   4 &    3.33 &    0.07 &  --1.62 &    0.07 &    0.03 &&
+  Ti \textsc{I} &   4 &    4.44 &    0.09 &  --0.51 &    0.23 &    0.04 \\
+ Ti \textsc{II} &   4 &    3.71 &    0.08 &  --1.24 &    0.46 &    0.04 &&
+ Ti \textsc{II} &   3 &    4.40 &    0.21 &  --0.55 &    0.19 &    0.12 \\
+   V \textsc{I} &   5 &    2.12 &    0.07 &  --1.81 &  --0.11 &    0.03 &&
+   V \textsc{I} &   5 &    3.31 &    0.11 &  --0.62 &    0.12 &    0.05 \\
+  Cr \textsc{I} &  12 &    3.68 &    0.06 &  --1.96 &  --0.27 &    0.02 &&
+  Cr \textsc{I} &  13 &    4.67 &    0.15 &  --0.97 &  --0.23 &    0.04 \\
+ Cr \textsc{II} &   2 &    4.11 &    0.02 &  --1.53 &    0.16 &    0.01 &&
+ Cr \textsc{II} &   3 &    4.88 &    0.03 &  --0.76 &  --0.02 &    0.02 \\
+  Mn \textsc{I} &   3 &    3.29 &    0.04 &  --2.14 &  --0.45 &    0.02 &&
+  Mn \textsc{I} &   3 &    4.54 &    0.03 &  --0.89 &  --0.15 &    0.02 \\
+  Fe \textsc{I} &  54 &    5.81 &    0.06 &  --1.69 &    0.00 &    0.01 &&
+  Fe \textsc{I} &  61 &    6.76 &    0.10 &  --0.74 &    0.00 &    0.01 \\
+ Fe \textsc{II} &  13 &    5.86 &    0.03 &  --1.64 &    0.05 &    0.01 &&
+ Fe \textsc{II} &  13 &    6.75 &    0.06 &  --0.75 &  --0.02 &    0.02 \\
+  Co \textsc{I} &   5 &    3.23 &    0.09 &  --1.76 &  --0.07 &    0.04 &&
+  Co \textsc{I} &   5 &    4.42 &    0.08 &  --0.57 &    0.17 &    0.03 \\
+  Ni \textsc{I} &   7 &    4.42 &    0.12 &  --1.80 &  --0.11 &    0.04 &&
+  Ni \textsc{I} &   5 &    5.62 &    0.04 &  --0.60 &    0.13 &    0.02 \\
+  Cu \textsc{I} &   1 &    2.03 &    0.00 &  --2.16 &  --0.47 &    0.00 &&
+  Cu \textsc{I} &   1 &    3.53 &    0.00 &  --0.66 &    0.08 &    0.00 \\
+  Zn \textsc{I} &   2 &    2.80 &    0.04 &  --1.76 &  --0.07 &    0.03 &&
+  Zn \textsc{I} &   2 &    3.89 &    0.06 &  --0.67 &    0.07 &    0.04 \\
+  Sr \textsc{I} &   1 &    0.66 &    0.00 &  --2.21 &  --0.52 &    0.00 &&
+  Sr \textsc{I} &   1 &    1.67 &    0.00 &  --1.20 &  --0.46 &    0.00 \\
+  Y \textsc{II} &   6 &    0.27 &    0.13 &  --1.94 &  --0.24 &    0.05 &&
+  Y \textsc{II} &   6 &    1.33 &    0.32 &  --0.88 &  --0.14 &    0.13 \\
+  Zr \textsc{I} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata &&
+  Zr \textsc{I} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
+ Zr \textsc{II} &   1 &    0.75 &    0.00 &  --1.83 &  --0.14 &    0.00 &&
+ Zr \textsc{II} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
+ Ba \textsc{II} &   1 &    0.40 &    0.00 &  --1.78 &  --0.09 &    0.00 &&
+ Ba \textsc{II} &   2 &    1.18 &    0.01 &  --1.00 &  --0.26 &    0.01 \\
+ La \textsc{II} &   2 &  --0.55 &    0.08 &  --1.66 &    0.04 &    0.05 &&
+ La \textsc{II} &   2 &    0.43 &    0.12 &  --0.67 &    0.07 &    0.08 \\
+ Ce \textsc{II} &   4 &  --0.31 &    0.12 &  --1.89 &  --0.20 &    0.06 &&
+ Ce \textsc{II} &   3 &    0.54 &    0.20 &  --1.04 &  --0.30 &    0.11 \\
+ Nd \textsc{II} &  10 &  --0.20 &    0.08 &  --1.62 &    0.07 &    0.02 &&
+ Nd \textsc{II} &   6 &    0.79 &    0.10 &  --0.63 &    0.11 &    0.04 \\
+ Eu \textsc{II} &   1 &  --0.83 &    0.00 &  --1.35 &    0.34 &    0.00 &&
+ Eu \textsc{II} &   1 &    0.16 &    0.00 &  --0.36 &    0.38 &    0.00 \\
+\hline
+\end{longtable*}
+
+\begin{longtable*}{lccccccclcccccc}
+\caption{\\ Program Star Abundances\label{tab:program-star-abundances}} \tabularnewline
+\cline{1-15}
+Species & $N$ & $\log\epsilon(X)$ & $\sigma_\epsilon$ & [X/H] & [X/Fe] & $\sigma$ && 
+Species & $N$ & $\log\epsilon(X)$ & $\sigma_\epsilon$ & [X/H] & [X/Fe] & $\sigma$ \tabularnewline
+\cline{1-15} \tabularnewline
+% This works.
+\endhead
+\hline
+\multicolumn{15}{r}{Continued..}
+\endfoot
+\hline
+\endlastfoot
+
+\\
+\multicolumn{7}{c}{J221821-183424} & \colhead{} & \multicolumn{7}{c}{C222531-145437} \\
+\cline{1-7} \cline{9-15}
+   C (CH)       &   2 &    6.55 &    0.20 &  --1.88 &  --0.30 &    0.25 &&
+   C (CH)       &   2 &    7.15 &    0.20 &  --1.28 &  --0.05 &    0.20 \\
+   O \textsc{I} &   2 &    7.55 &    0.04 &  --1.13 &    0.45 &    0.02 &&
+   O \textsc{I} &   2 &    7.96 &    0.00 &  --0.73 &    0.49 &    0.00 \\
+  Na \textsc{I} &   1 &    4.75 &    0.00 &  --1.49 &    0.09 &    0.00 &&
+  Na \textsc{I} &   2 &    5.12 &    0.02 &  --1.12 &    0.10 &    0.01 \\
+  Mg \textsc{I} &   3 &    6.37 &    0.09 &  --1.23 &    0.35 &    0.05 &&
+  Mg \textsc{I} &   2 &    6.90 &    0.08 &  --0.70 &    0.53 &    0.06 \\
+  Al \textsc{I} &   1 &    5.08 &    0.00 &  --1.37 &    0.21 &    0.00 &&
+  Al \textsc{I} &   4 &    5.94 &    0.10 &  --0.51 &    0.71 &    0.05 \\
+  Si \textsc{I} &   5 &    6.32 &    0.08 &  --1.19 &    0.39 &    0.04 &&
+  Si \textsc{I} &   5 &    7.07 &    0.15 &  --0.44 &    0.79 &    0.07 \\
+   K \textsc{I} &   1 &    4.34 &    0.00 &  --0.69 &    0.89 &    0.00 &&
+   K \textsc{I} &   1 &    4.42 &    0.00 &  --0.61 &    0.62 &    0.00 \\
+  Ca \textsc{I} &   4 &    5.01 &    0.04 &  --1.33 &    0.25 &    0.02 &&
+  Ca \textsc{I} &   4 &    5.57 &    0.04 &  --0.77 &    0.45 &    0.02 \\
+ Sc \textsc{II} &   6 &    1.53 &    0.08 &  --1.62 &  --0.04 &    0.03 &&
+ Sc \textsc{II} &   5 &    2.11 &    0.12 &  --1.04 &    0.19 &    0.06 \\
+  Ti \textsc{I} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata &&
+  Ti \textsc{I} &   4 &    4.10 &    0.03 &  --0.85 &    0.37 &    0.01 \\
+ Ti \textsc{II} &   4 &    3.80 &    0.13 &  --1.15 &    0.43 &    0.06 &&
+ Ti \textsc{II} &   2 &    4.12 &    0.13 &  --0.83 &    0.40 &    0.09 \\
+   V \textsc{I} &   3 &    2.28 &    0.01 &  --1.65 &  --0.07 &    0.01 &&
+   V \textsc{I} &   6 &    3.02 &    0.16 &  --0.92 &    0.31 &    0.06 \\
+  Cr \textsc{I} &  11 &    3.80 &    0.06 &  --1.84 &  --0.26 &    0.02 &&
+  Cr \textsc{I} &   8 &    4.24 &    0.17 &  --1.40 &  --0.17 &    0.06 \\
+ Cr \textsc{II} &   2 &    4.07 &    0.03 &  --1.57 &    0.01 &    0.02 &&
+ Cr \textsc{II} &   1 &    4.38 &    0.00 &  --1.26 &  --0.03 &    0.00 \\
+  Mn \textsc{I} &   3 &    3.35 &    0.03 &  --2.08 &  --0.49 &    0.02 &&
+  Mn \textsc{I} &   3 &    4.20 &    0.04 &  --1.23 &  --0.01 &    0.03 \\
+  Fe \textsc{I} &  52 &    5.92 &    0.09 &  --1.58 &    0.00 &    0.01 &&
+  Fe \textsc{I} &  60 &    6.27 &    0.10 &  --1.23 &    0.00 &    0.01 \\
+ Fe \textsc{II} &  13 &    5.94 &    0.05 &  --1.56 &    0.02 &    0.01 &&
+ Fe \textsc{II} &  10 &    6.30 &    0.06 &  --1.20 &    0.03 &    0.02 \\
+  Co \textsc{I} &   4 &    3.32 &    0.16 &  --1.67 &  --0.09 &    0.08 &&
+  Co \textsc{I} &   5 &    3.92 &    0.12 &  --1.07 &    0.15 &    0.05 \\
+  Ni \textsc{I} &   5 &    4.61 &    0.14 &  --1.61 &  --0.03 &    0.06 &&
+  Ni \textsc{I} &   7 &    5.07 &    0.09 &  --1.15 &    0.08 &    0.04 \\
+  Cu \textsc{I} &   1 &    2.18 &    0.00 &  --2.01 &  --0.43 &    0.00 &&
+  Cu \textsc{I} &   1 &    3.33 &    0.00 &  --0.86 &    0.37 &    0.00 \\
+  Zn \textsc{I} &   1 &    3.07 &    0.00 &  --1.49 &    0.09 &    0.00 &&
+  Zn \textsc{I} &   2 &    3.56 &    0.24 &  --1.00 &    0.23 &    0.17 \\
+  Sr \textsc{I} &   1 &    0.82 &    0.00 &  --2.05 &  --0.47 &    0.00 &&
+  Sr \textsc{I} &   1 &    1.55 &    0.00 &  --1.32 &  --0.09 &    0.00 \\
+ Sr \textsc{II} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata &&
+ Sr \textsc{II} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
+  Y \textsc{II} &   3 &    0.44 &    0.02 &  --1.77 &  --0.19 &    0.01 &&
+  Y \textsc{II} &   5 &    1.78 &    0.16 &  --0.43 &    0.79 &    0.07 \\
+  Zr \textsc{I} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata &&
+  Zr \textsc{I} &   3 &    2.07 &    0.05 &  --0.51 &    0.72 &    0.03 \\
+ Zr \textsc{II} &   1 &    0.97 &    0.00 &  --1.61 &  --0.03 &    0.00 &&
+ Zr \textsc{II} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
+ Ba \textsc{II} &   2 &    0.60 &    0.05 &  --1.58 &    0.00 &    0.04 &&
+ Ba \textsc{II} &   3 &    1.58 &    0.02 &  --0.60 &    0.62 &    0.01 \\
+ La \textsc{II} &   2 &  --0.47 &    0.00 &  --1.57 &    0.01 &    0.00 &&
+ La \textsc{II} &   2 &    0.55 &    0.00 &  --0.55 &    0.68 &    0.00 \\
+ Ce \textsc{II} &   3 &  --0.39 &    0.06 &  --1.97 &  --0.39 &    0.03 &&
+ Ce \textsc{II} &   5 &    0.73 &    0.15 &  --0.85 &    0.37 &    0.07 \\
+ Nd \textsc{II} &  10 &  --0.22 &    0.07 &  --1.64 &  --0.06 &    0.02 &&
+ Nd \textsc{II} &   8 &    0.88 &    0.13 &  --0.54 &    0.69 &    0.05 \\
+ Eu \textsc{II} &   2 &  --0.10 &    0.65 &  --0.62 &    0.96 &    0.46 &&
+ Eu \textsc{II} &   1 &  --0.19 &    0.00 &  --0.71 &    0.52 &    0.00 \\
+
+\cline{1-7} \cline{9-15} \\ \\
+\multicolumn{7}{c}{J223504-152834} && \multicolumn{7}{c}{J223811-104126} \\
+\cline{1-7} \cline{9-15}
+   C (CH)       &   2 &    7.71 &    0.30 &  --0.72 &  --0.10 &    0.30 &&
+   C (CH)       &   2 &    7.05 &    0.25 &  --1.38 &    0.05 &    0.25 \\
+   O \textsc{I} &   2 &    8.50 &    0.10 &  --0.19 &    0.43 &    0.07 &&
+   O \textsc{I} &   1 &    8.27 &    0.00 &  --0.42 &    0.15\footnote{Abundance derived from the permitted O \textsc{i} triplet instead of the forbidden [O \textsc{i}] lines, see \S\ref{sec:oxygen-abundances}} &    0.08 \\
+  Na \textsc{I} &   3 &    5.87 &    0.12 &  --0.37 &    0.26 &    0.07 &&
+  Na \textsc{I} &   1 &    4.89 &    0.00 &  --1.35 &    0.08 &    0.00 \\
+  Mg \textsc{I} &   3 &    7.48 &    0.15 &  --0.12 &    0.51 &    0.09 &&
+  Mg \textsc{I} &   2 &    6.51 &    0.03 &  --1.09 &    0.34 &    0.02 \\
+  Al \textsc{I} &   3 &    6.12 &    0.09 &  --0.33 &    0.29 &    0.05 &&
+  Al \textsc{I} &   2 &    5.13 &    0.13 &  --1.32 &    0.11 &    0.10 \\
+  Si \textsc{I} &   5 &    7.24 &    0.10 &  --0.27 &    0.35 &    0.05 &&
+  Si \textsc{I} &   3 &    6.42 &    0.04 &  --1.09 &    0.34 &    0.02 \\
+   K \textsc{I} &   1 &    5.05 &    0.00 &    0.02 &    0.64 &    0.00 &&
+   K \textsc{I} &   1 &    4.50 &    0.00 &  --0.53 &    0.90 &    0.00 \\
+  Ca \textsc{I} &   4 &    6.06 &    0.03 &  --0.28 &    0.34 &    0.01 &&
+  Ca \textsc{I} &   4 &    5.32 &    0.03 &  --1.02 &    0.41 &    0.02 \\
+ Sc \textsc{II} &   6 &    2.74 &    0.14 &  --0.41 &    0.22 &    0.06 &&
+ Sc \textsc{II} &   6 &    1.72 &    0.14 &  --1.43 &  --0.00 &    0.06 \\
+  Ti \textsc{I} &   4 &    4.65 &    0.02 &  --0.30 &    0.32 &    0.01 &&
+  Ti \textsc{I} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
+ Ti \textsc{II} &   1 &    4.67 &    0.00 &  --0.28 &    0.34 &    0.00 &&
+ Ti \textsc{II} &   4 &    3.79 &    0.09 &  --1.16 &    0.27 &    0.04 \\
+   V \textsc{I} &   4 &    3.59 &    0.10 &  --0.34 &    0.28 &    0.05 &&
+   V \textsc{I} &   1 &    2.45 &    0.00 &  --1.48 &  --0.05 &    0.00 \\
+  Cr \textsc{I} &   7 &    4.90 &    0.11 &  --0.74 &  --0.11 &    0.04 &&
+  Cr \textsc{I} &  12 &    4.10 &    0.06 &  --1.54 &  --0.11 &    0.02 \\
+ Cr \textsc{II} &   2 &    4.84 &    0.04 &  --0.79 &  --0.17 &    0.03 &&
+ Cr \textsc{II} &   3 &    4.34 &    0.07 &  --1.30 &    0.12 &    0.04 \\
+  Mn \textsc{I} &   3 &    5.06 &    0.10 &  --0.37 &    0.25 &    0.06 &&
+  Mn \textsc{I} &   3 &    3.58 &    0.04 &  --1.85 &  --0.43 &    0.02 \\
+  Fe \textsc{I} &  63 &    6.88 &    0.12 &  --0.62 &    0.00 &    0.02 &&
+  Fe \textsc{I} &  33 &    6.07 &    0.06 &  --1.43 &  --0.00 &    0.01 \\
+ Fe \textsc{II} &  12 &    6.87 &    0.07 &  --0.63 &  --0.01 &    0.02 &&
+ Fe \textsc{II} &   9 &    6.04 &    0.07 &  --1.46 &  --0.03 &    0.02 \\
+  Co \textsc{I} &   5 &    4.59 &    0.14 &  --0.40 &    0.22 &    0.06 &&
+  Co \textsc{I} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
+  Ni \textsc{I} &   7 &    5.64 &    0.09 &  --0.58 &    0.05 &    0.03 &&
+  Ni \textsc{I} &   2 &    4.84 &    0.04 &  --1.38 &    0.05 &    0.03 \\
+  Cu \textsc{I} &   1 &    3.81 &    0.00 &  --0.38 &    0.24 &    0.00 &&
+  Cu \textsc{I} &   1 &    2.40 &    0.00 &  --1.79 &  --0.36 &    0.00 \\
+  Zn \textsc{I} &   2 &    4.21 &    0.03 &  --0.35 &    0.27 &    0.02 &&
+  Zn \textsc{I} &   2 &    3.15 &    0.05 &  --1.41 &    0.02 &    0.04 \\
+  Sr \textsc{I} &   1 &    1.83 &    0.00 &  --1.04 &  --0.42 &    0.00 &&
+  Sr \textsc{I} &   1 &    1.23 &    0.00 &  --1.64 &  --0.21 &    0.00 \\
+ Sr \textsc{II} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata &&
+ Sr \textsc{II} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
+  Y \textsc{II} &   3 &    1.80 &    0.03 &  --0.41 &    0.21 &    0.02 &&
+  Y \textsc{II} &   6 &    0.76 &    0.06 &  --1.45 &  --0.02 &    0.03 \\
+  Zr \textsc{I} &   3 &    2.26 &    0.05 &  --0.32 &    0.31 &    0.03 &&
+  Zr \textsc{I} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
+ Zr \textsc{II} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata &&
+ Zr \textsc{II} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
+ Ba \textsc{II} &   2 &    1.65 &    0.02 &  --0.53 &    0.10 &    0.01 &&
+ Ba \textsc{II} &   2 &    0.70 &    0.03 &  --1.48 &  --0.05 &    0.02 \\
+ La \textsc{II} &   2 &    0.74 &    0.05 &  --0.36 &    0.26 &    0.04 &&
+ La \textsc{II} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
+ Ce \textsc{II} &   3 &    0.87 &    0.13 &  --0.71 &  --0.09 &    0.08 &&
+ Ce \textsc{II} &   2 &  --0.07 &    0.02 &  --1.65 &  --0.22 &    0.02 \\
+ Nd \textsc{II} &   6 &    1.27 &    0.13 &  --0.15 &    0.47 &    0.06 &&
+ Nd \textsc{II} &   1 &  --0.25 &    0.00 &  --1.67 &  --0.24 &    0.00 \\
+ Eu \textsc{II} &   1 &    0.52 &    0.00 &    0.00 &    0.62 &    0.00 &&
+ Eu \textsc{II} &   1 &  --0.55 &    0.00 &  --1.07 &    0.36 &    0.00 \\
+
+\cline{1-7} \cline{9-15} \\ \\
+\multicolumn{7}{c}{C2306265-085103} \\
+\cline{1-7}
+   C (CH)       &   2 &    7.20 &    0.20 &  --1.23 &  --0.10 &    0.20 \\
+   O \textsc{I} &   2 &    8.02 &    0.04 &  --0.67 &    0.46 &    0.03 \\
+  Na \textsc{I} &   2 &    5.31 &    0.01 &  --0.93 &    0.21 &    0.00 \\
+  Mg \textsc{I} &   2 &    6.90 &    0.06 &  --0.70 &    0.44 &    0.05 \\
+  Al \textsc{I} &   4 &    5.65 &    0.08 &  --0.80 &    0.33 &    0.04 \\
+  Si \textsc{I} &   5 &    6.78 &    0.08 &  --0.73 &    0.40 &    0.04 \\
+   K \textsc{I} &   1 &    4.46 &    0.00 &  --0.57 &    0.56 &    0.00 \\
+  Ca \textsc{I} &   4 &    5.56 &    0.04 &  --0.78 &    0.35 &    0.02 \\
+ Sc \textsc{II} &   6 &    2.28 &    0.16 &  --0.87 &    0.26 &    0.06 \\
+  Ti \textsc{I} &   4 &    4.13 &    0.03 &  --0.82 &    0.32 &    0.01 \\
+ Ti \textsc{II} &   3 &    4.32 &    0.35 &  --0.63 &    0.51 &    0.20 \\
+   V \textsc{I} &   4 &    2.96 &    0.05 &  --0.98 &    0.16 &    0.03 \\
+  Cr \textsc{I} &   3 &    4.13 &    0.12 &  --1.51 &  --0.38 &    0.07 \\
+ Cr \textsc{II} &   1 &    4.50 &    0.00 &  --1.14 &  --0.01 &    0.00 \\
+  Mn \textsc{I} &   3 &    4.40 &    0.10 &  --1.03 &    0.10 &    0.06 \\
+  Fe \textsc{I} &  62 &    6.37 &    0.12 &  --1.13 &    0.00 &    0.01 \\
+ Fe \textsc{II} &  11 &    6.39 &    0.10 &  --1.11 &    0.02 &    0.03 \\
+  Co \textsc{I} &   5 &    4.14 &    0.14 &  --0.85 &    0.28 &    0.06 \\
+  Ni \textsc{I} &   7 &    5.11 &    0.07 &  --1.11 &    0.02 &    0.03 \\
+  Cu \textsc{I} &   1 &    3.53 &    0.00 &  --0.66 &    0.47 &    0.00 \\
+  Zn \textsc{I} &   2 &    3.48 &    0.15 &  --1.08 &    0.05 &    0.10 \\
+  Sr \textsc{I} &   1 &    0.94 &    0.00 &  --1.93 &  --0.80 &    0.00 \\
+ Sr \textsc{II} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
+  Y \textsc{II} &   4 &    1.26 &    0.26 &  --0.95 &    0.18 &    0.13 \\
+  Zr \textsc{I} &   3 &    1.60 &    0.05 &  --0.98 &    0.16 &    0.03 \\
+ Zr \textsc{II} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
+ Ba \textsc{II} &   2 &    0.99 &    0.04 &  --1.19 &  --0.06 &    0.03 \\
+ La \textsc{II} &   2 &  --0.02 &    0.03 &  --1.12 &    0.01 &    0.02 \\
+ Ce \textsc{II} &   2 &    0.09 &    0.02 &  --1.49 &  --0.36 &    0.01 \\
+ Nd \textsc{II} &   7 &    0.58 &    0.21 &  --0.84 &    0.29 &    0.08 \\
+ Eu \textsc{II} &   1 &  --0.32 &    0.00 &  --0.84 &    0.29 &    0.00 \\
+ \hline
+\end{longtable*}
 
 \subsubsection{Aluminium}
-There are six aluminium transition lines available in our optical spectra.
-The strongest of these lines occur at 3944 and 3961\,{\AA}, and are visible in all of our stars.
-However, this is a particularly crowded spectral region: the lines fall between the strong Ca H and K lines, with the 3961\,{\AA} transition clearly in the wing of the Ca H line.
+\label{sec:aluminium-abundances}
+There are six aluminium transition lines in our optical spectra.
+The strongest of these lines occur at 3944 and {3961\,\AA} and are visible in all of our stars.
+However this is a particularly crowded spectral region: the lines fall between the strong Ca H and K lines, with the {3961\,\AA} transition clearly located in the wing of the Ca H line.
 This makes the continuum determination and subsequent aluminium measurement non-trivial, especially given the metallicity of our stars.
-Additionally, the 3944 and 3961 lines suffer from appreciable departures from LTE, resulting in under-estimated abundances by up to $\sim$0.60\,dex \citep{baumueller;gehren_1997}.
-Instead, we have measured Al abundances from other available transitions: the Al \textsc{i} lines at 6696, 6698, 7835 and 7836\,{\AA}.
-Although these lines are weaker than the bluer Al \textsc{i} lines, their surrounding regions are uncrowded from strong absorption lines.
-
-Generally the four Al \textsc{i} lines are in reasonable agreement with one another, yielding random scatter of less than 0.05\,dex.
+Additionally, the 3944 and {3961\,{\AA}} lines suffer from appreciable departures from the assumption of local thermal equilibrium (LTE), resulting in under-estimated abundances by up to $\sim$0.60\,dex \citep{baumueller;gehren_1997}.
+Instead, we have measured Al abundances from other available transitions: the {Al\,\textsc{i}} lines at 6696, 6698, 7835 and {7836\,{\AA}}.
+Although these lines are weaker than the bluer {Al\,\textsc{i}} lines, their surrounding regions are uncrowded from strong absorption lines.
+
+Generally the four {Al\,\textsc{i}} lines are in reasonable agreement with one another, yielding random scatter of less than 0.05\,dex.
 However, these lines were not always detected in the data.
-The strength of the lines is noticeably weakened below a 3-$\sigma$ detection with decreasing metallicity and increasing temperature.
-For our most metal-poor star, J221821, only a single Al \textsc{i} line was detectable, and so we have adopted a conservative uncertainty of 0.10\,dex.
+The strength of the lines is noticeably weakened below a 3$\sigma$ detection with decreasing metallicity and increasing temperature.
+For our most metal-poor star, J221821-183424, only a single {Al\,\textsc{i}} line was detectable, and so we have adopted a conservative uncertainty of {$\pm0.10$\,dex}.
 
 \subsubsection{Iron-peak Elements (Sc, V, Cr and Mn)}
-
-As expected, the Fe-peak elemental abundances exhibit similar trends (Figure \ref{fig:fe-peak-elements}).
-The noteworthy exception is chromium, where the median abundance is $\mbox{[Cr/Fe]} = -0.08 \pm 0.12$ and does not appear to vary with overall metallicity.
-The number of clean, suitable Cr \textsc{i} lines available between candidates fluxuated from three to twelve.
-Very little line-to-line scatter is present in both Cr \textsc{i} and \textsc{ii}: the random scatter is below 0.04\,dex for most stars, with the isolated example of J223504 where $\sigma(\mbox{[Cr \textsc{ii}/Fe]}) = 0.29$\,dex, and only three lines were available.
-The Cr \textsc{i} and \textsc{ii} abundances for J223504 are in good agreement (0.05\,dex), and since none of the measured profiles were particularly unusual, we chose not to exclude outlier measurements.
-For all other stars, the Cr \textsc{i} $-$ Cr \textsc{ii} abundance differences varied between 0.02\,dex up to 0.31\,dex.
-The largest discrepancy occurred in our hottest star, where fewer chromium transitions were detected.
-
-All other iron peak elements considered (Sc, V, Mn) all exhibit a slight downward trend in metallicity, with manganese demonstrating the most prominent gradient: varying between $\mbox{[Mn/Fe]} = -0.52$\,dex to $+0.31$\,dex in the most metal-poor and -rich stars respectively.
-The [Sc/Fe] measurements presented in Figure \ref{fig:fe-peak-elements} are calculated from six clean Sc \textsc{ii} lines, and there is very minimal line-to-line scatter, the largest of which is 0.06\,dex.
-Three Aquarius stream stars display [Sc/Fe] $\sim$ +0.20, while J221821 and J223811 have $\mbox{[Sc/Fe]} = 0.01$ and 0.05\,dex, respectively.
+\label{sec:fe-peak-abundances}
+
+As one expects from supernovae, the {Fe-peak} elemental abundances exhibit similar trends (Figure \ref{fig:fe-peak-elements}).
+The noteworthy exception is chromium, where the median abundance is {$\mbox{[Cr/Fe]} = -0.08 \pm 0.12$} and varies little with overall metallicity.
+The number of clean, suitable {Cr\,\textsc{i}} lines available between candidates fluctuated from three to twelve.
+Very little line-to-line scatter is present in both {Cr\,\textsc{i}} and \textsc{ii}: the random scatter is below {0.04\,dex} for most stars, with the isolated example of {J223504-152834} where ${\sigma(\mbox{[Cr\,\textsc{ii}/Fe]}) = 0.29\,{\rm dex}}$, and only three lines were available.
+The {Cr\,\textsc{i}} and \textsc{ii} mean abundances for {J223504-152834} are in good agreement (0.05\,dex), and since none of the measured Gaussian profiles appeared particularly unusual, we chose not to exclude any measurements.
+For all other stars, the ${\langle{\rm Cr}\,\textsc{i} - {\rm Cr}\,\textsc{ii}\rangle}$ abundance differences varied between {0.02\,dex} up to {0.31\,dex}.
+The largest discrepancy occurred in our hottest star, where fewer chromium transitions were measurable.
+Chromium abundances are only available for one of the standard stars, where our {[Cr/Fe] = 0.03}\,dex is in excellent agreement with \citet{fulbright_2000}, where they find {[Cr/Fe] = 0.04}\,dex.
 
@@
 	\includegraphics[width=\columnwidth]{./figures/aquarius-fe-peak.pdf}
-	\caption{Iron peak elements for all stars.}
+	\caption{Iron peak element abundances (Sc, V, Cr, and Mn) with respect to iron for all Aquarius stream stars.}
 	\label{fig:fe-peak-elements}
@@
 
+All other iron peak elements considered (Sc, V, Mn) all exhibit a slight downward trend in metallicity, with manganese demonstrating the strongest gradient: varying between {$\mbox{[Mn/Fe]} = -0.52$\,dex} to {$+0.31$\,dex} in the most metal-poor and -rich stars respectively.
+The [Sc/Fe] measurements presented in Figure \ref{fig:fe-peak-elements} are calculated from six clean {Sc\,\textsc{ii}} lines, and there is very minimal line-to-line scatter, the largest of which is {0.06\,dex}.
+Three Aquarius stream stars exhibit {[Sc/Fe] $\sim$ +0.20}, while {J221821-183424} and {J223811-104126} have ${\mbox{[Sc/Fe]} = 0.01}$ and {0.05\,dex}, respectively.
+\\
+
 \subsubsection{Nickel}
-Most Aquarius stream stars have seven clean Ni\,\textsc{i} transitions available. These lines are in excellent agreement, with typical scatter of 0.03\,dex.
-% nickel abundances in standard stars
-
-\subsubsection{Barium}
-%Barium is a neutron-capture element, primarily produced through the \textit{s}-process, but can be forged from a variety of nucleosynthetic processes.
-
-Measuring barium requires some careful consideration.
-The strong resonance lines at 4554 {\AA} and 4934 {\AA} have appreciable hyperfine splitting, which can result in over-estimated abundances if unaccounted for.
-There are a few singly ionized lines available in our spectra that do not suffer from strong hyperfine splitting, namely the 5853, 6141 and 6496 {\AA} transitions.
-Depending on the radial velocity of the star, sometimes our 6496 {\AA} line was affected by small amounts of telluric absorption.
+Most Aquarius stream stars have seven clean {Ni\,\textsc{i}} transitions available.
+These lines are in excellent agreement, with typical scatter of {0.03\,dex}.
+Nickel abundances have been published for two of our standard stars: HD\,76932 \citep{fulbright_2000} and HD\,141531 \citep{shetrone_1996}.
+In both cases, our [Ni/Fe] abundance ratios are slightly higher by 0.08 and 0.10\,dex respectively.
+The different solar compositions employed by this study accounts for 0.01\,dex.
+While our nickel abundances may be slightly over-estimated, this does not affect our conclusions.
+
+\subsection{Neutron-capture Elements}
+Neutron-capture elements (Sr to Eu; ${38 \leqslant Z \leqslant 63}$) can be forged through multiple nucleosynthetic processes.
+The two primary processes that produce these elements are the rapid ($r$-) process and the slow ($s$-) process.
+While the $r$-process occurs primarily from SN explosions, the $s$-process takes place foremost in AGB stars.
+Measurable neutron-capture elements in our spectra are discussed separately.
+
+\subsubsection{Strontium, Yttrium and Zirconium}
+\label{sec:weak-s-process-elements}
+
+These weak $s$-process elements generally change in lock-step with one another.
+Of Sr, Y and Zr, yttrium has the highest number of clean measurable transitions in our wavelength range.
+The {Sr\,\textsc{ii}} lines at 4077 and {4215\,\AA} were not measurable in any program or standard stars, although {Sr\,\textsc{i}} was detectable at {6645\,\AA}.
+While {[Y\,\textsc{ii}/Fe]} and {[Zr\,\textsc{i}, \textsc{ii}/Fe]} are in good agreement in all candidates, {[Sr\,\textsc{i}/Fe]} is lower and there is significant scatter.
+No obvious telluric contamination was observed in the 6645\,{\AA} line.
+Given that Sr\,\textsc{i} transitions are susceptible to non-LTE effects \citep{hansen;et-al_2013}, we note these Sr abundances should be treated with some caution.
+
+% Sr, Y, Zr in standard stars
+This is the first study to present Sr, Y, and Zr abundances for five of the six standard stars.
+Existing data on neutron-capture abundances were not crucial in selecting standard comparison stars, it was more important to cover a range of stellar parameters.
+
+The Aquarius candidates have yttrium abundances consistent with halo field stars, with the exception of {C222531-145437}.
+With {[Y/Fe] = 0.79}\,dex, {C222531-145437} is significantly overabundant in yttrium for its metallicity \citep[see Figure 4 of][]{travaglio;et-al_2004}.
+The closest star with a similar overabundance in yttrium is the a metal-poor dwarf HD\,23439 with {[Y/Fe] $\sim{}$ 0.60}\,dex.
+{C222531-145437} is consistently over-abundant in Sr and Zr, too.
+All other program and standard stars have $s$-process trends and abundances that are consistent with the chemical evolution of the Milky Way.
+
+\subsubsection{Barium and Lanthanum}
+Barium is primarily produced through the $s$-process, and its measurement requires some careful consideration.
+The strong resonance lines at {4554\,\AA} and {4934\,\AA} have appreciable hyperfine splitting, which can result in over-estimated abundances if unaccounted for.
+There are a few singly ionised lines available in our spectra that do not suffer from strong hyperfine splitting, namely the 5853, 6141 and {6496\,\AA} transitions.
+Depending on the radial velocity of the star, sometimes our {6496\,\AA} line was affected by small amounts of telluric absorption.
 In these cases the line was discarded.
-The abundances tabulated in Table \ref{tab:program-star-abundances} are based on the remaining clean Ba \textsc{ii} lines at 5853 and 6141 {\AA}, which are generally in good agreement with each other, and the 6496 {\AA} line where available.
+The abundances tabulated in Table \ref{tab:program-star-abundances} are based on the remaining clean {Ba\,\textsc{ii}} lines at 5853 and {6141\,\AA}, which are generally in good agreement with each other, and the {6496\,\AA} line when it was not affected by Earth's atmospheric absorption.
 
 Our standard stars have [Ba/Fe] abundances very typical of the Milky Way halo.
-Only one of our standard stars, HD 44007, has published [Ba/Fe] abundances from high-resolution spectra.
-We find HD 44007 to have $\mbox{[Ba/Fe]} = -0.05 \pm 0.04$, which is at the mid-point of existing published measurements from \citet{fulbright_2000} and \citet{burris;et-al_2000} of $-0.27$ and 0.05 dex, respectively.
-
-With one exception, the Aquarius stream candidates have barium abundances that are quite similar to the stellar halo, ranging between $\mbox{[Ba/Fe]} = -0.02$ to 0.15 dex.
-The exception is C2225316, which has an anomalously high barium abundance of $\mbox{[Ba/Fe]} = 0.70$ dex.
-This is ${\sim}$0.70 dex higher than the Milky Way trend at its given $\mbox{[Fe/H]} = -1.26$ dex.
-Our three Ba \textsc{ii} lines in C2225316 are in excellent agreement: 0.67, 0.68, and 0.72 dex.
-The 6496\,{\AA} transition in C2225316 has a negligible telluric contribution and was included for this candidate.
-At least in Al, Si, Cr and Ba content (see sections \ref{sec:aluminium-abundance}, \ref{sec:alpha-elements}, \ref{sec:iron-peak-elements}), C225316 appears to be chemically distinct from the other Aquarius stream stars in our sample.
-
-\begin{deluxetable*}{lccccccclcccccc}
-\tablecolumns{15}
-\tablecaption{Program Star Abundances\label{tab:program-star-abundances}}
+Two of the standard stars have published [Ba/Fe] abundance ratios from high-resolution spectra: HD\,44007 and HD\,76932.
+We find HD\,44007 to have ${\mbox{[Ba/Fe]} = -0.05 \pm 0.04}$, which is near the mid-point of existing published measurements from \citet{fulbright_2000} and \citet{burris;et-al_2000} of $-0.27$ and {0.05\,dex}, respectively.
+For HD\,76932 our measurement of {$\mbox{[Ba/Fe]} = 0.03$} is in good agreement with the \citet{fulbright_2000} value of $-0.02$, especially so when differences in adopted solar composition are considered.
+
+With one exception, the Aquarius stream candidates have barium abundances that are quite similar to the stellar halo, ranging between ${\mbox{[Ba/Fe]} = -0.02}$ to {0.15\,dex}.
+The exception -- again -- is {C222531-085103}, which has an anomalously high barium abundance of ${\mbox{[Ba/Fe]} = 0.62\,{\rm dex}}$.
+This is $\sim$0.60\,dex higher than the Milky Way trend at its given metallicity of ${\mbox{[Fe/H]} = -1.26\,{\rm dex}}$.
+Our three {Ba\,\textsc{ii}} lines in {C222531-085103} are in excellent agreement with each other: 0.64, 0.61, and {0.68\,dex}.
+The {6496\,\AA} transition in {C222531-085103} has a negligible telluric contribution and was included for this candidate.
+
+% Iron peak elements
+\begin{figure}[h]
+	\includegraphics[width=\columnwidth,height=22.6cm]{./figures/plot-x-on-fe.pdf}
+	\caption{Element ratios for Aquarius stream candidates.
+In the case of [Zr/Fe], {[Zr\,\textsc{i}/Fe]} is taken where available and {[Zr\,\textsc{ii}/Fe]} if no measurement was available for {Zr\,\textsc{i}}.
+See Table \ref{tab:program-star-abundances} for details.}
+	\label{fig:x-on-fe}
+\end{figure}
+
+%  Lanthanum
+% subject to hyperfine splitting. Needs re-doing. Perhaps remove?
+
+\subsubsection{Cesium, Neodymium and Europium}
+Europium abundances have been determined from the equivalent widths of the 6645\,{\AA} Eu\,\textsc{ii} transition and synthesis of the region surrounding the 6437\,{\AA} Eu\,\textsc{ii} feature.
+As pointed out by \citet{Lawler;et-al_2001}, the 6437\,{\AA} feature is appreciably blended by a silicon line at 6437.71\,{\AA}.
+Measurements of the two lines were consistent with a hidden blend: the 6437\,{\AA} Eu\,\textsc{ii} line abundance from equivalent widths was systematically higher than the 6645\,{\AA} counterpart.
+As with other heavy elements except for europium, candidate C222531-145437 is over-abundant in cesium and neodymium with respect to the rest of the sample.
+We note that in our most metal-poor star the two Eu\,\textsc{ii} lines were wildly discrepant.
+Neither profile seemed ill-fitted, so we kept both and accepted an extremely large uncertainty for this measurement.
+
+% elemental abundances
+
+% comparison to literature for a given star
+
+% chemical synthesis
+
+\subsection{Distances}
+\label{sec:distances}
+
+Many groups have determined distances for stars in the RAVE survey catalog, which includes all known Aquarius members.
+\citet{williams;et-al_2011} tabulated a range of distances inferred by different techniques.
+Not every measurement approach was applicable to all stream members.
+The reduced proper motion distance technique was the only method to infer distances for all Aquarius candidates.
+The variations between distance measurements for the same star were large.
+In particular the distance for {C222531-146537} ranged from $1.4 \pm 0.1$\,kpc \citep{burnett_binney_2010} to $10.3 \pm 2.4$\,kpc \citep{breddels;et-al_2010}, where both groups claim to have the `most likely' distances.
+
+\begin{figure}[h]
+	\includegraphics[width=\columnwidth]{./figures/toombre.pdf}
+	\caption{Galactic plane rotational velocities versus out-of-plane total velocities.
+The contours of each star represent the 68\% and 95\% confidence intervals from 10,000 Monte-Carlo realisations of the parameter distributions shown in Table \ref{tab:monte-carlo-data}.
+A sample of thick disc data from \citet{nissen;schuster_2010} is shown ($+$), as well as their high- and low-alpha halo populations ($\diamond$ and $\circ$ respectively).}
+	\label{fig:toombre}
+\end{figure}
+
+Using the stellar parameters tabulated in Table \ref{tab:stellar-parameters}, we have calculated distances by isochrone fitting.
+The \citet{dotter;et-al_2008} alpha-enhanced ([$\alpha$/Fe] = +0.4\,dex) isochrones were employed for these calculations, and an age of 10\,Gyr was assumed for all stars.
+The closest point to the isochrone was found by taking the uncertainties in $T_{\rm eff}$ and $\log{g}$ into account and measuring the distance modulus in $J$ band.
+Given the number of uncertain measurements involved in calculating distances ($T_{\rm eff}$, $\log{g}$, E(B-V), $J$) and resulting asymmetric uncertainties, distances were determined from 10,000 Monte-Carlo realisations.
+For the case of {J223811-104126}, the extinction of ${{\rm E(B-V)} = 0.12^{+0.01}_{-0.02}}$ as from the interstellar Na D1 line has been used.
+Table \ref{tab:monte-carlo-data} shows the parameters and uncertainties adopted for the Monte-Carlo realisations.
+Uncertainties in parameters were assumed to be Gaussian.
+The emergent distances and asymmetric uncertainties are also tabulated.
+Of the distance scales collated in \citet{williams;et-al_2011}, our distances are in most agreement with the \citet{zwitter;et-al_2010} system.
+In fact, we find the best agreement with the mean of all the distance scales tabulated in \citet{williams;et-al_2011}.
+The uncertainties in our distance determinations are on the order of twenty percent.
+
+\begin{deluxetable*}{lccccccccc}
+\tablecolumns{2}
+\tabletypesize{\scriptsize}
+\tablecaption{Parameters and Uncertainties Adopted for Monte-Carlo Realisations\label{tab:monte-carlo-data}}
 \tablehead{
-\colhead{Species} & $N$ & $\log\epsilon(X)$ & $\sigma_\epsilon$ & [X/H] & [X/Fe] & $\sigma$ &&
-\colhead{Species} & $N$ & $\log\epsilon(X)$ & $\sigma_\epsilon$ & [X/H] & [X/Fe] & $\sigma$ 
+	\colhead{Designation} &
+	\colhead{$T_{\rm eff}$} &
+	\colhead{$\log{g}$} &
+	\colhead{$J$} &
+	\colhead{${\rm E(B-V)}$} &
+	\colhead{$D$} &
+	\colhead{$V_{\rm hel}$} &
+	\colhead{$\mu_\alpha$} &
+	\colhead{$\mu_\delta$}
+	\\
+	& (K) & (dex) & (mag) & (mag) & (kpc) & (km s$^{-1}$) & (mas yr$^{-1}$) & (mas yr$^{-1}$)
 }
 \startdata 
-\\
- \multicolumn{7}{c}{J221821-183424} & \colhead{} & \multicolumn{7}{c}{C2225316-14437} \\
- \cline{1-7} \cline{9-15} \\
-   O \textsc{i} &   2 &    7.55 &    0.04 & $-$1.13 &    0.47 &    0.02 &&
-   O \textsc{i} &   2 &    7.92 &    0.00 & $-$0.77 &    0.49 &    0.00 \\
-  Na \textsc{i} &   1 &    4.71 &    0.00 & $-$1.53 &    0.08 &    0.00 &&
-  Na \textsc{i} &   2 &    5.07 &    0.02 & $-$1.17 &    0.09 &    0.01 \\
-  Mg \textsc{i} &   3 &    6.33 &    0.09 & $-$1.27 &    0.34 &    0.05 &&
-  Mg \textsc{i} &   2 &    6.84 &    0.09 & $-$0.76 &    0.50 &    0.06 \\
-  Al \textsc{i} &   1 &    5.05 &    0.00 & $-$1.40 &    0.21 &    0.00 &&
-  Al \textsc{i} &   4 &    5.87 &    0.09 & $-$0.58 &    0.68 &    0.04 \\
-  Si \textsc{i} &   5 &    6.28 &    0.08 & $-$1.23 &    0.38 &    0.04 &&
-  Si \textsc{i} &   5 &    6.97 &    0.15 & $-$0.54 &    0.72 &    0.07 \\
-  Ca \textsc{i} &   4 &    4.99 &    0.04 & $-$1.35 &    0.25 &    0.02 &&
-  Ca \textsc{i} &   4 &    5.51 &    0.04 & $-$0.83 &    0.43 &    0.02 \\
- Sc \textsc{ii} &   6 &    1.56 &    0.09 & $-$1.59 &    0.01 &    0.04 &&
- Sc \textsc{ii} &   5 &    2.08 &    0.13 & $-$1.07 &    0.19 &    0.06 \\
-  Ti \textsc{i} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata &&
-  Ti \textsc{i} &   4 &    4.04 &    0.02 & $-$0.91 &    0.36 &    0.01 \\
- Ti \textsc{ii} &   4 &    3.85 &    0.13 & $-$1.10 &    0.50 &    0.06 &&
- Ti \textsc{ii} &   2 &    4.29 &    0.08 & $-$0.66 &    0.61 &    0.05 \\
-   V \textsc{i} &   3 &    2.26 &    0.01 & $-$1.67 & $-$0.06 &    0.01 &&
-   V \textsc{i} &   6 &    2.93 &    0.17 & $-$1.00 &    0.26 &    0.07 \\  
-  Cr \textsc{i} &  11 &    3.77 &    0.08 & $-$1.87 & $-$0.26 &    0.02 &&
-  Cr \textsc{i} &   8 &    4.29 &    0.16 & $-$1.35 & $-$0.08 &    0.06 \\
- Cr \textsc{ii} &   2 &    4.04 &    0.02 & $-$1.60 &    0.00 &    0.02 &&
- Cr \textsc{ii} &   1 &    4.27 &    0.00 & $-$1.37 & $-$0.11 &    0.00 \\
-  Mn \textsc{i} &   3 &    3.30 &    0.03 & $-$2.13 & $-$0.52 &    0.02 &&
-  Mn \textsc{i} &   3 &    4.15 &    0.04 & $-$1.28 & $-$0.01 &    0.03 \\
-  Fe \textsc{i} &  52 &    5.89 &    0.09 & $-$1.61 &    0.00 &    0.01 &&
-  Fe \textsc{i} &  60 &    6.24 &    0.10 & $-$1.26 &    0.00 &    0.01 \\
- Fe \textsc{ii} &  13 &    5.91 &    0.05 & $-$1.59 &    0.02 &    0.01 &&
- Fe \textsc{ii} &  10 &    6.19 &    0.06 & $-$1.31 & $-$0.05 &    0.02 \\
-  Co \textsc{i} &   1 &    3.38 &    0.00 & $-$1.61 & $-$0.00 &    0.00 &&
-  Co \textsc{i} &   3 &    3.92 &    0.12 & $-$1.07 &    0.19 &    0.07 \\
-  Ni \textsc{i} &   5 &    4.62 &    0.14 & $-$1.60 &    0.01 &    0.06 &&
-  Ni \textsc{i} &   7 &    5.05 &    0.09 & $-$1.17 &    0.09 &    0.03 \\
-  Cu \textsc{i} &   1 &    2.16 &    0.00 & $-$2.03 & $-$0.42 &    0.00 &&
-  Cu \textsc{i} &   1 &    3.38 &    0.00 & $-$0.81 &    0.45 &    0.00 \\
-  Zn \textsc{i} &   2 &    3.17 &    0.11 & $-$1.39 &    0.22 &    0.08 &&
-  Zn \textsc{i} &   2 &    3.48 &    0.24 & $-$1.08 &    0.19 &    0.17 \\
- Ba \textsc{ii} &   2 &    0.72 &    0.08 & $-$1.47 &    0.14 &    0.05 &&
- Ba \textsc{ii} &   2 &    1.62 &    0.01 & $-$0.56 &    0.70 &    0.00 \\
-
-\cline{1-7} \cline{9-15} \\
-\\
-\multicolumn{7}{c}{J223504-152834} && \multicolumn{7}{c}{J223811-104126} \\
-\cline{1-7} \cline{9-15} \\
-   O \textsc{i} &   2 &    8.46 &    0.10 & $-$0.23 &    0.45 &    0.07 &&
-   O \textsc{i} &   1 &    8.26 &    0.00 & $-$0.43 &    0.14\footnote{Abundance derived from the permitted O \textsc{i} triplet instead of the forbidden [O \textsc{i}] lines, see \S\ref{sec:oxygen-abundances}} &    0.08 \\
-  Na \textsc{i} &   3 &    5.74 &    0.12 & $-$0.50 &    0.18 &    0.07 &&
-  Na \textsc{i} &   1 &    4.86 &    0.00 & $-$1.38 &    0.07 &    0.00 \\
-  Mg \textsc{i} &   3 &    7.41 &    0.15 & $-$0.19 &    0.49 &    0.09 &&
-  Mg \textsc{i} &   2 &    6.47 &    0.02 & $-$1.13 &    0.32 &    0.01 \\
-  Al \textsc{i} &   3 &    6.08 &    0.08 & $-$0.37 &    0.31 &    0.05 &&
-  Al \textsc{i} &   2 &    5.10 &    0.14 & $-$1.35 &    0.10 &    0.10 \\
-  Si \textsc{i} &   5 &    7.12 &    0.10 & $-$0.39 &    0.29 &    0.04 &&
-  Si \textsc{i} &   3 &    6.38 &    0.04 & $-$1.13 &    0.32 &    0.02 \\
-  Ca \textsc{i} &   4 &    6.00 &    0.03 & $-$0.34 &    0.33 &    0.02 &&
-  Ca \textsc{i} &   4 &    5.30 &    0.03 & $-$1.04 &    0.41 &    0.01 \\
- Sc \textsc{ii} &   6 &    2.70 &    0.14 & $-$0.45 &    0.23 &    0.06 &&
- Sc \textsc{ii} &   6 &    1.75 &    0.14 & $-$1.40 &    0.05 &    0.06 \\
-  Ti \textsc{i} &   4 &    4.59 &    0.02 & $-$0.36 &    0.32 &    0.01 &&
-  Ti \textsc{i} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
- Ti \textsc{ii} &   2 &    4.91 &    0.27 & $-$0.04 &    0.64 &    0.19 &&
- Ti \textsc{ii} &   4 &    3.83 &    0.09 & $-$1.12 &    0.33 &    0.04 \\
-   V \textsc{i} &   6 &    3.62 &    0.22 & $-$0.31 &    0.37 &    0.09 &&
-   V \textsc{i} &   1 &    2.42 &    0.00 & $-$1.51 & $-$0.06 &    0.00 \\
-  Cr \textsc{i} &   7 &    4.88 &    0.09 & $-$0.76 & $-$0.08 &    0.04 &&
-  Cr \textsc{i} &  12 &    4.12 &    0.06 & $-$1.52 & $-$0.07 &    0.02 \\
- Cr \textsc{ii} &   3 &    4.83 &    0.50 & $-$0.81 & $-$0.13 &    0.29 &&
- Cr \textsc{ii} &   3 &    4.34 &    0.07 & $-$1.30 &    0.15 &    0.04 \\
-  Mn \textsc{i} &   3 &    5.06 &    0.10 & $-$0.37 &    0.31 &    0.06 &&
-  Mn \textsc{i} &   3 &    3.55 &    0.04 & $-$1.88 & $-$0.43 &    0.02 \\
-  Fe \textsc{i} &  63 &    6.82 &    0.12 & $-$0.68 &    0.00 &    0.02 &&
-  Fe \textsc{i} &  33 &    6.05 &    0.06 & $-$1.45 &    0.00 &    0.01 \\
- Fe \textsc{ii} &  12 &    6.82 &    0.07 & $-$0.68 &    0.00 &    0.02 &&
- Fe \textsc{ii} &  11 &    6.00 &    0.09 & $-$1.50 & $-$0.05 &    0.03 \\
-  Co \textsc{i} &   3 &    4.50 &    0.13 & $-$0.49 &    0.19 &    0.08 &&
-  Co \textsc{i} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
-  Ni \textsc{i} &   7 &    5.61 &    0.09 & $-$0.61 &    0.07 &    0.03 &&
-  Ni \textsc{i} &   2 &    4.82 &    0.04 & $-$1.40 &    0.05 &    0.03 \\
-  Cu \textsc{i} &   1 &    3.82 &    0.00 & $-$0.37 &    0.31 &    0.00 &&
-  Cu \textsc{i} &   1 &    2.39 &    0.00 & $-$1.80 & $-$0.35 &    0.00 \\
-  Zn \textsc{i} &   2 &    4.18 &    0.02 & $-$0.38 &    0.30 &    0.02 &&
-  Zn \textsc{i} &   2 &    3.17 &    0.04 & $-$1.39 &    0.06 &    0.03 \\
- Ba \textsc{ii} &   2 &    1.65 &    0.02 & $-$0.53 &    0.15 &    0.01 &&
- Ba \textsc{ii} &   2 &    0.78 &    0.06 & $-$1.40 &    0.05 &    0.04 \\
-\cline{1-7} \cline{9-15} \\
-\\
-\multicolumn{7}{c}{C2306265-085103} && \\
-\cline{1-7} \\
-   O \textsc{i} &   2 &    7.96 &    0.02 & $-$0.72 &    0.45 &    0.02 \\
-  Na \textsc{i} &   2 &    5.25 &    0.00 & $-$0.99 &    0.18 &    0.00 \\
-  Mg \textsc{i} &   2 &    6.84 &    0.07 & $-$0.76 &    0.41 &    0.05 \\
-  Al \textsc{i} &   4 &    5.56 &    0.08 & $-$0.89 &    0.28 &    0.04 \\
-  Si \textsc{i} &   5 &    6.66 &    0.08 & $-$0.85 &    0.32 &    0.03 \\
-  Ca \textsc{i} &   4 &    5.48 &    0.04 & $-$0.86 &    0.31 &    0.02 \\
- Sc \textsc{ii} &   6 &    2.18 &    0.15 & $-$0.97 &    0.20 &    0.06 \\
-  Ti \textsc{i} &   4 &    4.06 &    0.03 & $-$0.89 &    0.28 &    0.01 \\
- Ti \textsc{ii} &   3 &    4.21 &    0.36 & $-$0.74 &    0.43 &    0.21 \\
-   V \textsc{i} &   4 &    2.88 &    0.06 & $-$1.05 &    0.12 &    0.03 \\
-  Cr \textsc{i} &   3 &    4.08 &    0.12 & $-$1.56 & $-$0.39 &    0.07 \\
- Cr \textsc{ii} &   1 &    4.39 &    0.00 & $-$1.25 & $-$0.08 &    0.00 \\
-  Mn \textsc{i} &   3 &    4.35 &    0.10 & $-$1.08 &    0.09 &    0.06 \\
-  Fe \textsc{i} &  62 &    6.33 &    0.12 & $-$1.17 &    0.00 &    0.01 \\
- Fe \textsc{ii} &  11 &    6.31 &    0.09 & $-$1.19 & $-$0.02 &    0.03 \\
-  Co \textsc{i} &   3 &    4.00 &    0.15 & $-$0.99 &    0.18 &    0.08 \\
-  Ni \textsc{i} &   7 &    5.08 &    0.08 & $-$1.14 &    0.03 &    0.03 \\
-  Cu \textsc{i} &   1 &    3.55 &    0.00 & $-$0.64 &    0.53 &    0.00 \\
-  Zn \textsc{i} &   2 &    3.38 &    0.14 & $-$1.18 & $-$0.01 &    0.10 \\
- Ba \textsc{ii} &   2 &    0.99 &    0.06 & $-$1.19 & $-$0.02 &    0.04
+C222531-145437 & $4365 \pm 150$ & $1.25 \pm 0.30$ & $10.341 \pm 0.022$ & $0.03 \pm 0.01$ & $5.1^{+1.1}_{-0.8}$ & $-156.4 \pm 0.1$ & \phn\phn\,$3.5 \pm 2.1$ & $-14.7 \pm 2.2$ \\
+C230626-085103 & $4225 \pm 150$ & $0.85 \pm 0.30$ & $10.312 \pm 0.025$ & $0.05 \pm 0.01$ & $6.5^{+1.4}_{-1.1}$ & $-221.1 \pm 0.1$ & \phn$-2.5 \pm 2.8$ & $-15.4 \pm 2.7$ \\
+J221821-183424 & $4630 \pm 150$ & $0.88 \pm 0.30$ & $10.340 \pm 0.021$ & $0.03 \pm 0.01$ & $5.6^{+1.3}_{-0.9}$ & $-159.5 \pm 0.1$ & $-10.6 \pm 2.5$ & $-19.3 \pm 2.5$ \\
+J223504-152834 & $4650 \pm 150$ & $2.16 \pm 0.30$ & $10.363 \pm 0.025$ & $0.04 \pm 0.01$ & $1.9^{+0.5}_{-0.4}$ & $-169.7 \pm 0.1$ & \phn\,$15.9 \pm 2.2$ & $-12.8 \pm 2.2$ \\
+J223811-104126 & $5190 \pm 150$ & $2.93 \pm 0.30$ & $10.420 \pm 0.018$ & $0.12^{+0.01}_{-0.02}$\footnote{Extinction measured directly from interstellar Na D1 line} & $1.1^{+0.3}_{-0.2}$ & $-235.7 \pm 0.1$ & $-25.3 \pm 2.1$ & $-99.5 \pm 2.1$
 \enddata
@@
 
-% elemental abundances
-
-% comparison to literature for a given star
-
-% chemical synthesis
-
-\subsection{Distances}
-% isochrone fitting
-
-% discuss Williams et al distances
-
 \subsection{Dynamics}
@@
 % U, V, W calculations
+Velocity vectors and galactic orbits have been determined in the same Monte-Carlo realisations outlined in Section \ref{sec:distances}.
+Uncertainties in distance, proper motions\footnote{The proper motions in Table 1 of \citet{williams;et-al_2011} are mis-associated to incorrect stars.
+This error was typographical; it did not affect the transverse velocity calculations (M.E.K.
+Williams, private communication).
+The proper motions listed in our Table \ref{tab:monte-carlo-data} are correct.} and heliocentric velocity have been propagated.
+We assumed zero uncertainty in on-sky projected position $(\alpha, \delta)$.
+Orbital energy calculations have assumed a three-component model (bulge, disc, halo) of the galactic potential that reasonably reproduces the galactic rotation curve.
+The bulge is represented by a Hernquist potential:
+
+\begin{equation}
+	\Phi_{\rm bulge}(x, y, z) = \frac{GM_b}{r + a}
+\end{equation}
+
+\noindent where $a = 0.6$\,kpc. The disc is modelled as a Miyamoto-Nagai potential \citep{miyamoto;nagai_1975} where:
+
+\begin{equation}
+	\Phi_{\rm disc}(x, y, z) = \frac{GM_{\rm disc}}{\sqrt{x^2 + y^2 + (b + \sqrt{z^2 + c^2})^2}}
+\end{equation}
+
+\noindent with $b = 4.5$\,kpc and $c = 0.25$\,kpc and the galactic halo is represented by a Navarro-Frenk-White dark matter halo \citep{navarro;et-al_1997}:
+
+\begin{equation}
+	\Phi_{\rm halo} = -\frac{GM_{\rm vir}}{r\left[\log{(1 + c)} - c/(1 + c)\right]}\log{\left(1 + \frac{r}{r_s}\right)}
+\end{equation}
+
+\noindent{}with the three components scaled such that the disc provides 85\% of the radial force at $R_\odot$, in order to yield a flat circular-speed curve at $R_\odot$.
+The solar motion of \citet{schonrich;et-al_2012} has been assumed where $R_\odot$ = 8.27\,kpc and circular velocity speed of $V_c = 238$\,km s$^{-1}$.
+
+% solar motion
+% galactic potential
+
+Orbital energies and angular momenta from Monte-Carlo simulations are illustrated in Figure \ref{fig:orbits}.
+The 16,686 stars from the Geneva-Cophenhagen Survey sample \citep{nordstrom;et-al_2004} are also shown as a reference, which primarily consists of nearby disc stars.
+The Aquarius stream members have bound orbits, all of which are probably retrograde with the exception of {J223504-152834}.
+The chemically distinct star, {C222531-145437}, has a much lower velocity out of the plane ($\sqrt{U^2 + W^2}$) and has an orbit that is  more tightly bound to the Milky Way than the other Aquarius members.
+
+\begin{figure}[h!]
+	\includegraphics[width=\columnwidth]{./figures/Lz-E.pdf}
+	\caption{A Linblad ($L_Z-E$) diagram showing angular momenta and orbital energies after 10,000 Monte-Carlo realisations for each Aquarius stream star.
+Iso-contours represent the 68\% and 95\% confidence intervals.
+The black points without contours are from the Geneva-Cophenagen Survey sample \citep{nordstrom;et-al_2004}, which primarily consists of nearby disc stars and serves as a validation of our orbital energy calculations.}
+	\label{fig:orbits}
+\end{figure}
 
@@
 
-\subsection{Stellar Parameter Discrepancies with \citet{wylie-de-boer;et-al_2012}}
+\subsection{Stellar Parameter Discrepancies with \\ \citet{wylie-de-boer;et-al_2012}}
 
 We seek to investigate the nature of the Aquarius stream, as well as the specific globular cluster origin claim made by \citet{wylie-de-boer;et-al_2012}.
-The stellar parameters reported in \citet{wylie-de-boer;et-al_2012} differ slightly to those published in Table \ref{tab:stellar-parameters}.
-\citet{wylie-de-boer;et-al_2012} deduce their stellar parameters by minimizing the $\chi^2$ difference between the observed spectra, and the \citet{munari;et-al_2005} synthetic spectral library after it was convolved and re-sampled to match the observations.
-The comparison regions used for analysis were 4900-5200\,{\AA} and 5575-5725\,{\AA}.
+The stellar parameters reported in \citet{wylie-de-boer;et-al_2012} differ to those published in Table \ref{tab:stellar-parameters}.
+\citet{wylie-de-boer;et-al_2012} deduce their stellar parameters by minimizing the $\chi^2$ difference between the observed spectra and synthetic spectra from the \citet{munari;et-al_2005} spectral library.
+The synthetic library has a slightly lower resolution than the observations.
+The observed spectral range was 4120 to 6920\,{\AA}, and the regions used for $\chi^2$ minimisation were {4900-5200\,\AA} and {5575-5725\,\AA}.
 In general, temperatures between the two studies agree within the uncertainties.
-The only aberration is J223811-104126, where we find an effective temperature of 5140\,K, ${\sim}$500\,K cooler than the 5646\,K found by \citet{wylie-de-boer;et-al_2012}.
-Similarly, \citet{williams;et-al_2011} report a hotter effective temperature of 5502\,K from low-resolution spectra.
+Given temperature has the principal effect on spectral features, this is perhaps unsurprising.
+The only aberration is {J223811-104126}, where we find an effective temperature of {5190\,K}, {$\sim{}450\,{\rm K}$} cooler than the {5646\,K} found by \citet{wylie-de-boer;et-al_2012}.
+Similarly, \citet{williams;et-al_2011} report a hotter effective temperature of {5502\,K} from low-resolution spectra.
 This is the largest discrepancy we see in any of our standard or program stars.
 
-Photometric temperatures only lend marginal argumentative weight towards our spectroscopic temperatures.
-If the \citet{schlegel;et-al_1998} dust maps are employed, then the \citet{alonso;et-al_1999} and \citet{casagrande;et-al_2010} relations estimate the effective temperatures to be between 5104\,K and 5367\,K.
-Our spectroscopic temperature of 5110\,K is in excellent agreement with the \citet{alonso;et-al_1999} prediction, but not in strong disagreement with the \citet{casagrande;et-al_2010} relation either.
-If we employ the reddening of $E(B-V) = 0.12$ that we have determined from interstellar Na D1 line, the photometric temperature increases slightly by ${\sim}100$\,K, still within the uncertainties of the \citet{alonso;et-al_1999} scale, but less so with the \citet{casagrande;et-al_2010} scale.
-We find the surface gravity for J223811-104126 to be 3.00 $\pm$ 0.50, placing this star at the base of the red giant branch.
-Thus, if J223811-104126 is a giant star, our spectroscopic temperatures should be in slightly better agreement with the \citet{alonso;et-al_1999} scale, rather than the \citet{casagrande;et-al_2010} dwarf/sub-giant scale.
-However, \citet{williams;et-al_2011} and \citet{wylie-de-boer;et-al_2012} find this star to be a sub-giant, with a surface gravity $\log{g} = 4.16$ and 4.60 respectively.
+Photometric temperatures only lend marginal weight towards our spectroscopic temperatures.
+If the \citet{schlegel;et-al_1998} dust maps are employed, then the \citet{alonso;et-al_1999} and \citet{casagrande;et-al_2010} relations estimate the effective temperatures to be between {5104\,K} and {5367\,K}.
+Our spectroscopic temperature of {5190\,K} is in excellent agreement with the \citet{alonso;et-al_1999} prediction, but not in strong disagreement with the \citet{casagrande;et-al_2010} relation either.
+If we employ the reddening of $E(B-V) = 0.12$ that we have determined from the interstellar Na D1 line, the photometric temperature increases slightly by {$\sim{}100\,{\rm K}$}, in perfect agreement with the \citet{alonso;et-al_1999} scale.
+We find the surface gravity for {J223811-104126} to be {3.00 $\pm$ 0.50\,dex}, placing this star at the base of the red giant branch.
+Thus, if {J223811-104126} is a giant star, our spectroscopic temperatures should be in slightly better agreement with the \citet{alonso;et-al_1999} scale, rather than the \citet{casagrande;et-al_2010} dwarf/sub-giant scale.
+However, \citet{williams;et-al_2011} and \citet{wylie-de-boer;et-al_2012} find this star to be a sub-giant, with a surface gravity {$\log{g} = 4.16$} and {4.60\,dex} respectively.
 The \citet{williams;et-al_2011} and \citet{wylie-de-boer;et-al_2012} temperatures are 150\,K and 300\,K hotter than the \citet{casagrande;et-al_2010} prediction respectively.
-If our extinction value is employed, then the \citet{williams;et-al_2011} and \citet{casagrande;et-al_2010} temperatures are in good agreement, yet still 175\,K cooler than the \citet{wylie-de-boer;et-al_2012} measurement.
-
-As a test, we set the temperature for J223811-104126 to be 5600\,K -- within the temperature regime reported by \citet{williams;et-al_2011} and \citet{wylie-de-boer;et-al_2012}.
-The slopes in abundance with excitation potential and reduced equivalent width were large (\#check smh: how many dex), and in doing so we could not find a physical solution for this temperature.
-Thus, although photometric temperatures do not help in solving this discrepancy, and the reddening measured from the interstellar Na D1 line may have made it worse, our high-resolution spectra indicates that J223811-104126 has an effective temperature of 5110\,K and is indeed a giant star.
-
-In the \citet{wylie-de-boer;et-al_2012} study, the surface gravity was determined during the $\chi^2$ minimization process.
-Again, with the exception of J223811-104126, our surface gravities are largely in agreement.
-The only other noteworthy difference in surface gravity is for J221821-183424, where we find a lower gravity of $\log{g} = 0.80 \pm 0.30$ and \citet{wylie-de-boer;et-al_2012} find $\log{g} = 1.45 \pm 0.35$\,cm\,s$^{-2}$.
-Given the difference in $S/N$ and resolution between these studies, this difference is not too concerning.
+If our interstellar extinction value is employed -- and the star is a sub-giant -- then the \citet{williams;et-al_2011} and \citet{casagrande;et-al_2010} temperatures are in good agreement, but the \citet{wylie-de-boer;et-al_2012} measurement is still 175\,K cooler.
+
+As a test, we set the temperature for {J223811-104126} to be 5600\,K -- within the temperature regime reported by \citet{williams;et-al_2011} and \citet{wylie-de-boer;et-al_2012}.
+The slopes in abundance with excitation potential and reduced equivalent width were large (${m_{\rm Fe\,\textsc{i}} = -0.099}$\,dex\,eV$^{-1}$, 0.162\,dex, ${m_{\rm Fe\,\textsc{ii}} = -0.133}$\,dex\,eV$^{-1}$, $-0.033$\,dex respectively), and in doing so we could not find a representative solution for this temperature.
+Thus although photometric temperatures do not completely resolve this discrepancy in spectroscopic temperatures between this study and others, the \citet{alonso;et-al_1999} scale is in good agreement with our spectroscopic temperature if our interstellar extinction value is employed.
+
+In the \citet{wylie-de-boer;et-al_2012} study, the surface gravity was determined during the $\chi^2$ minimisation process.
+Again, with the exception of {J223811-104126}, our surface gravities are largely in agreement.
+The only other noteworthy difference in surface gravity is for {J221821-183424}, where we find a lower gravity of {$\log{g} = 0.88 \pm 0.30$} and \citet{wylie-de-boer;et-al_2012} find {$\log{g} = 1.45 \pm 0.35$\,dex}.
+Given the difference in the $S/N$ ratio between these studies, this difference is not too concerning.
 
 \citet{wylie-de-boer;et-al_2012} calculate microturbulence from empirical relationships derived by \citet{reddy;et-al_2003} for dwarfs and \citet{fulbright_2000} for giants.
-These relationships are based upon the effective temperature and surface gravity.
-Our published microturbulent velocities agree excellently with the values presented in \citet{wylie-de-boer;et-al_2012}, again with the exception of J223811-104126, where the difference in $v_{t}$ can be directly attributed to the offsets in other observables.
-
-Of all the stellar parameters ($T_{\rm eff}$, $\log{g}$, $v_{t}$ and $\mbox{[Fe/H]}$), the metallicities between our two studies vary the most.
+These relationships are based on the effective temperature and surface gravity.
+Our published microturbulent velocities agree excellently with the values presented in \citet{wylie-de-boer;et-al_2012}, again with the exception of {J223811-104126}, where the difference in $v_{t}$ is directly attributable to the offsets in other observables.
+
+Of all the stellar parameters ($T_{\rm eff}$, $\log{g}$, $v_{t}$ and [M/H]), the metallicities between our two studies vary the most.
 Here we discuss the potential causes for these discrepancies.
-In the \citet{wylie-de-boer;et-al_2012} study, after the stellar parameters ($T_{\rm eff}$, $\log{g}$, $v_{t}$, and an initial [Fe/H] estimate) had been determined through a $\chi^2$ analysis, the authors synthesized individual Fe \textsc{i} and \textsc{ii} lines using the \textsc{moog} code.
-\citet{castelli;kurucz_2003} stellar atmosphere models were employed \--- the same ones used in this study, albeit the interpolation schemes will have subtle differences.
-The median abundance of Fe\,\textsc{i} lines was taken as the overall stellar metallicity, scaled using the \citet{grevesse;sauval_1998} solar composition.
-
-The study of \citet{wylie-de-boer;et-al_2012} is of slightly lower resolution ($\mathcal{R} = 25,000$ compared to $\mathcal{R} = 28,000$ presented here), but with a much lower $S/N$ ratio: $\sim{}25$ pixel$^{-1}$ compared to $>$100\,pixel$^{-1}$ achieved here.
-Given the slightly lower spectral resolution and modest $S/N$ in the \citet{wylie-de-boer;et-al_2012} study, there are fewer unblended absorption lines available.
-In fact, there are very few transitions present in their published line list: only 14 Fe\,\textsc{i} lines and 3 Fe\,\textsc{ii} lines were available.
-For contrast, our metallicity determinations are usually based from ${\sim}$50 Fe\,\textsc{i} and ${\sim}$13 Fe\,\textsc{ii} clean, unblended lines.
-Given the metallicity of these candidates and the spectral coverage (4120 to 6920 {\AA}), it is somewhat surprising that there were not more transitions available to \citet{wylie-de-boer;et-al_2012}.
-
-The line list employed in the \citet{wylie-de-boer;et-al_2012} study contained fewer lines, and utilized different oscillator strengths than what we have used.
+In the \citet{wylie-de-boer;et-al_2012} study, after the stellar parameters ($T_{\rm eff}$, $\log{g}$, $v_{t}$, and an initial [M/H] estimate) had been determined through a $\chi^2$ analysis, the authors synthesised individual {Fe\,\textsc{i}} and \textsc{ii} lines using \textsc{moog}.
+\citet{castelli;kurucz_2003} stellar atmosphere models were employed (K.
+Freeman, private communication, 2013) -- the same ones used in this study -- albeit the interpolation schemes will have subtle differences.
+The median abundance of {Fe\,\textsc{i}} lines was taken as the overall stellar metallicity, scaled using the \citet{grevesse;sauval_1998} solar composition.
+
+The study of \citet{wylie-de-boer;et-al_2012} is of slightly lower resolution ($\mathcal{R} = 25,000$ compared to $\mathcal{R} = 28,000$ presented here), but with a much lower $S/N$ ratio: ${\sim{}25\,{\rm pixel}^{-1}}$ compared to {$>$100\,pixel$^{-1}$} achieved here.
+Given the slightly lower spectral resolution,  modest $S/N$ and smaller spectral coverage in the \citet{wylie-de-boer;et-al_2012} study, there are fewer unblended absorption lines available.
+In fact, there are very few transitions present in their published line list: a maximum of 14 {Fe\,\textsc{i}} lines and 3 {Fe\,\textsc{ii}} lines were available.
+For contrast, our metallicity determinations are based from 63 {Fe\,\textsc{i}} and 13 {Fe\,\textsc{ii}} clean, unblended lines.
+Given the metallicity of these candidates and the reasonable wavelength coverage of the \citet{wylie-de-boer;et-al_2012} data, it is somewhat surprising that there were not more transitions available for analysis.
+
+The line list employed in the \citet{wylie-de-boer;et-al_2012} utilised different oscillator strengths than those tabulated in Table \ref{tab:equivalent-widths}.
 The oscillator strengths in the \citet{wylie-de-boer;et-al_2012} study are astrophysical; they were derived from a reverse analysis from the \citet{hinkle;et-al_2003} solar atlas.
-Suspecting the differing line lists may be the cause of the metallicity discrepancy, we reanalysed our data using the \citet{wylie-de-boer;et-al_2012} line list and stellar parameters.
-Indeed, we arrive at very similar metallicities to \citet{wylie-de-boer;et-al_2012}.
+Suspecting the differing line lists may contribute to the metallicity discrepancy, we re-analysed our data using the \citet{wylie-de-boer;et-al_2012} line list and stellar parameters.
+Indeed, in doing so we arrive at reasonably similar metallicities to \citet{wylie-de-boer;et-al_2012}.
 Without using their published stellar parameters a priori, in a `blind' analysis employing just the \citet{wylie-de-boer;et-al_2012} line list, we also arrive at similar stellar parameters.
-However, given the limited number of lines available, subtle changes to the stellar parameters inflicted large changes to individual mean iron abundances.
-Additionally, we note that one Fe\,\textsc{i} transition at 6420.060\,\AA{} in the \citet{wylie-de-boer;et-al_2012} line list was not detected in any of our candidates at the 3-$\sigma$ level, even though the $S/N$ at this point exceeds 115 pixel$^{-1}$ in every observation.
-Thus, for this comparative analysis a maximum of 13 Fe\,\textsc{i} and 3 Fe\,\textsc{ii} lines were available.
-
-Given the line list employed in the \citet{wylie-de-boer;et-al_2012} study, the overall data quality and the lack of suitable iron lines available for analysis, it appears the Aquarius stream stars conspired to present a tight metallicity distribution function of $\sigma(\mbox{Fe/H}) = 0.10$\,dex.
-When viewed in light of enhanced [Ni/Fe], [Na/Fe] abundance ratios, this chemistry is suggestive of a globular cluster origin.
+However, given the limited number of lines available, extremely subtle changes to the stellar parameters inflicted large variations to both the individual and mean Fe abundances.
+Additionally, we note that one {Fe\,\textsc{i}} transition at {6420.060\,\AA} in the \citet{wylie-de-boer;et-al_2012} line list was either not detected at the {3$\sigma$} level -- even though the $S/N$ at this point exceeds {115\,pixel$^{-1}$} in every observation -- or it was blended with a stronger neighbouring transition.
+Thus, for this comparative analysis a maximum of 13 {Fe\,\textsc{i}} and 3 {Fe\,\textsc{ii}} lines were available.
+
+Given the line list employed in the \citet{wylie-de-boer;et-al_2012} study, the overall data quality and the lack of suitable iron lines available for analysis, it appears the Aquarius stream stars conspired to present a tight metallicity distribution of {$\sigma(\mbox{Fe/H}) = 0.10$\,dex}.
+When viewed in light of enhanced [Ni/Fe], [Na/Fe] abundance ratios, this chemistry might be suggestive of a globular cluster origin.
 Our analysis of high-resolution spectra with high $S/N$ reveals a much broader metallicity distribution for the stream.
-With just five stars we find the stream metallicity varies from $\mbox{[Fe/H]} = -0.65$ to --1.60\,dex.
-Although this is a small sample, we find the calculated median abundance and standard deviation to be $\mbox{[Fe/H]} = -1.26 \pm 0.32$\,dex.
+With just five stars we find the stream metallicity varies from {$\mbox{[Fe/H]} = -0.63$} to {$-1.63$\,dex}.
+Although this is a small sample, we find the calculated mean abundance and standard deviation to be {$\mbox{[Fe/H]} = -1.24 \pm 0.36$\,dex}.
 
@@
 Classical globular clusters typically exhibit very little chemical scatter.
-This is largely because they are primarily considered to be a single stellar populations, originating from a lone \--- largely homogenous \--- proto-stellar cloud.
-More recent observations have demonstrated shown that this is not always the case: many globular clusters clearly host multiple stellar populations.
-The separation between these populations is identifiable through chemical abundances, and often from photometry alone.
-In many cases, the chemistry between the two stellar populations are quite similar, still revealing minimal overall scatter within the cluster.
-There are some unusual exceptions to this rule, most notable of which is the globular cluster $\omega$-Centurai (NGC 5139), which is seen to host many sub-populations with very different metallicity distributions.
-Without the explanation of multiple sub-populations in mind, the system would be seen to exhibit an unusually wide metallicity dispersion for a globular cluster.
-
-\begin{figure*}[t!]
-	\includegraphics[width=\textwidth]{./figures/aquarius-vhel-feh.pdf}
-	\caption{Heliocentric velocities and metallicities for Aquarius candidates in this sample.
-The measurements found by \citet{williams;et-al_2011} (green squares) and \citet{wylie-de-boer;et-al_2012} (blue triangles) are shown, and stars are linked by dashed lines.
-\citet{wylie-de-boer;et-al_2012} used the \citet{williams;et-al_2011} velocities, which is why their measurements are coincident on the abscissa.}
-	\label{fig:aquarius-vhel-feh}
-\end{figure*}
-
-Assuming all our candidates are stream members, we find a metallicity dispersion of $\sigma(\mbox{[Fe/H]}) = 0.32$\,dex.
-If the stream is the result of a disrupted system, this metallicity dispersion provides little indication on the progenitor.
-If the dispersion was smaller, confirming the observations of \citet{wylie-de-boer;et-al_2012}, a globular cluster scenario is more likely.
-However, given the multiple stellar populations present in many globular clusters, which can exhibit total cluster dispersions up to X dex (NGC X), Y dex (NGC Y), our dispersion of 0.32\,dex is somewhat inconvenient.
-Since dSph galaxies do not undergo chemical self-enrichment in the same way globular clusters do, they can exhibit significant metallicity dispersions \--- well over a dex, depending on the dwarf total luminosity.
+This is largely because they are primarily -- and somewhat incorrectly -- considered to be a single stellar populations, originating from a lone, largely homogenous proto-stellar cloud.
+Observations have demonstrated that this is not always the case: many globular clusters clearly host multiple stellar populations.
+The separation between these sub-populations is identifiable through chemical abundances, and often from photometry alone.
+One prominent example is that of $\omega$-Centurai (NGC 5139), which is seen to host many sub-populations with very different metallicity distributions.
+Without the explanation of multiple sub-populations in mind, such a system would be seen to exhibit an unreasonably wide metallicity dispersion for a single stellar population.
+
+Assuming all our candidates are stream members, we find a metallicity dispersion of {$\sigma(\mbox{[Fe/H]}) = 0.36$\,dex}.
+If the stream is the result of a disrupted system, this metallicity dispersion provides little indication on the host.
+If the dispersion were smaller, confirming the observations of \citet{wylie-de-boer;et-al_2012}, a globular cluster scenario may be more likely.
+However, given the multiple stellar populations present in many globular clusters, which can exhibit total cluster dispersions up to X dex (NGC X), Y dex (NGC Y) -- hi Gary :-) --, our dispersion of 0.36\,dex is somewhat inconvenient.
+Since dSph galaxies do not undergo chemical self-enrichment in the same way as globular clusters, they can exhibit significant metallicity dispersions -- well over a dex, depending on the total system luminosity.
 On its own, the metallicity of our stream stars does not provide any indication on the cause of the Aquarius stream, or its enrichment environment.
@@
 
-% establish the relationship as a true phenomena
-
-Extensive studies looking at stars in globular clusters have revealed variations in light-element abundances, most notably an anti-correlation in sodium and oxygen content \citet[][and references therein]{norris;da_costa_1995,carretta;et-al_2009_na_o}.
+Extensive studies looking at stars in globular clusters have revealed variations in light-element abundances, most notably an anti-correlation in sodium and oxygen content \citep[][and references therein]{norris;da_costa_1995,carretta;et-al_2009a}.
 This chemical pattern has been repeatedly demonstrated in every well-studied globular cluster, although the strength of the anti-correlation varies in each system.
-Between generations of stars within a globular cluster, oxygen is converted into nitrogen, reducing the overall oxygen abundance.
-Even though oxygen undergoes internal mixing during its evolution along the giant branch, the detection of this chemical pattern in unevolved stars has led to the conclusion that observed abundance variations due to mixing are limited to Li, C, and N.
-Therefore, the light element anti-correlation required a different astrophysical explanation.
+Between generations of stars within a globular cluster, oxygen is converted into nitrogen, thereby reducing the overall oxygen abundance.
+Even though oxygen undergoes internal mixing during its evolution along the giant branch, the detection of this chemical pattern in unevolved stars led to the conclusion that observed abundance variations due to mixing are limited to lithium, carbon and nitrogen.
+Therefore, the light element anti-correlation requires a different astrophysical explanation.
 
 Sodium is primarily produced through through carbon burning in massive stars by the dominant $^{12}\mbox{C}(^{12}\mbox{C}, p)^{23}\mbox{Na}$ process.
-The final Na abundance is dependent on the neutron excess of the star, which slowly increases during carbon burning due to weak interactions \citep{arnett;truran_1974}.
-Massive stars ($>8 M_\odot$) eventually deliver their manufactured sodium to the interstellar-medium through Sn \textsc{ii} events.
-Because the eventual Sn \textsc{ii} explosion is devoid of any significant beta-decay processes, the neutron excess of the exploded material is representative of the pre-explosion abundance.
+The final Na abundance is dependent on the neutron excess of the star, which slowly increases during carbon burning due to weak interactions \citep{arnett;truran_1969}.
+Massive stars ($>8 M_\odot$) eventually deliver their manufactured sodium to the interstellar-medium through {Sn\,\textsc{ii}} events.
+Because the eventual {Sn\,\textsc{ii}} explosion is devoid of any significant beta-decay processes, the neutron excess of the exploded material is representative of the pre-explosive abundance.
 
@@
 	\includegraphics[width=\textwidth]{./figures/aquarius-o-na-cluster.pdf}
-	\caption{Oxygen and sodium abundances for 14 classical globular clusters from \citet{carretta;et-al_2009a}, demonstrating the clear inverse Na-O correlation, which is ubiquitous in all well-studied globular clusters.
-The [O/Fe] and [Na/Fe] abundances for the five Aquarius stream candidates are also shown (last panel).}
+	\caption{Oxygen and sodium abundances for 14 classical globular clusters from \citet{carretta;et-al_2009a}, demonstrating the clear inverse {Na-O} correlation, ubiquitous to all well-studied globular clusters.
+The [O/Fe] and [Na/Fe] abundances from this study for the five Aquarius stream candidates are also shown (last panel).}
 	\label{fig:o-na-clusters}
@@
 
-The explosive material eventually condenses to form the next generation of stars, which will have a net increase in their neutron excess with respect to when their predecessors formed.
-Since the Na-production rate is correlated with the neutron excess, an overall increase in the total Na and Na-production rate between stellar generations is expected.
-Thus, an increase in the Na abundance between generations of massive stars is a natural consequence of nucleosynthesis.
-Sodium content also becomes important for production of Ni during the Sn \textsc{ii} event (see \S\ref{sec:na-ni}) because $^{23}$Na is the only stable isotope produced in significant quantities during the C- (or O-) burning stages.
+The explosive material eventually condenses to form the next generation of stars, which will have a net increase in their neutron excess with respect to their predecessors.
+Since the Na-production rate is correlated with the neutron excess, an overall increase in the total sodium content \textit{and} Na-production rate between stellar generations is expected.
+Thus, an increase in the sodium abundance between generations of massive stars is a natural consequence of nucleosynthesis.
+Sodium content also becomes important for production of nickel during the {Sn\,\textsc{ii}} event (see Section \ref{sec:na-ni-relationship}) because $^{23}$Na is the only stable isotope produced in significant quantities during the C- or O-burning stages.
 A small fraction of $^{22}$Na is also forged through proton capture on $^{21}$Ne in the carbon shell, an effect which is enhanced by neutrinos spallating abundant elements like $^{16}$O and $^{20}$Ne, making free protons available for capture \citep{woosley;weaver_1995}.
@@
 Oxygen depletion is likely the result of complete CNO burning within the stellar interior.
-The nucleosynthetic pathways that generate the Na-O anti-correlation are well known.
+The nucleosynthetic pathways that produce the {Na-O} anti-correlation are well known.
 However, the temperatures required to produce these patterns are not expected within the interiors of globular cluster stars.
-While the exact site for which these conditions occur remains under investigation, we can describe the abundance variation as a simple oxygen depletion (or dilution) model with time.
-Through comparisons with existing globular clusters, we can still draw inferences on the star-formation history of a system from measuring sodium and oxygen in a sample of its stars.
-
-\citet{carretta;et-al_2009_na_o} defined three components of stars exhibiting an inverse Na-O correlation within a population: primordial, intermediate, and extreme components.
+While the exact mechanism for which these conditions occur remains under investigation, we can describe the abundance variation as a simple oxygen depletion (or dilution) model with time.
+Through comparisons with existing globular clusters, we can still make inferences on the star-formation history of a system by measuring sodium and oxygen abundances in a sample of its stars.
+
+\citet{carretta;et-al_2009a} defined three components of stars exhibiting an inverse {Na-O} correlation within a population: primordial, intermediate, and extreme components.
 The [Na/Fe] and [O/Fe] abundances for a given star define which component it belongs to.
 Primordial (first-generation) stars are those with sodium and oxygen abundances which are similar to field stars of the same metallicity.
-For a well-studied system, stars with the lowest cluster [Na/Fe] abundances are characterised as primordial.
-An intermediate component \--- the second-generation of stars \--- will have super-solar sodium abundances, and demonstrate a slight depletion in oxygen content.
+An intermediate component -- the second-generation of stars -- will have super-solar sodium abundances and demonstrate a slight depletion in oxygen content.
 The oxygen exhaustion rate is ultimately dependent on the star-formation history of the cluster environment.
-The intermediate population is sub-divided based on how much the sodium and oxygen abundances depart from the primordial population: stars with [O/Na]$ > -0.9$ dex are classified as belonging to an extreme component of this Na-O pattern because they differ greatly from the primordial cluster abundance.
+The intermediate population is sub-divided based on how much the sodium and oxygen abundances depart from the primordial population: stars with {[O/Na]$ > -0.9$\,dex} are classified as belonging to an extreme component of this {Na-O} pattern because they differ greatly from the primordial cluster abundance.
 The extreme O-depletion component has only been observed in a few clusters (preferentially more massive clusters with extended horizontal branches), indicating an long-lasting star-formation history in more massive clusters.
@@
 It is clear that careful consideration must be given when inferring star-formation histories from observed stellar abundances.
-In addition to the normal care afforded for measuring elemental abundances from high-resolution spectroscopic data, attention must be given to telluric absorption, contamination from nickel transitions, as well as non-LTE and 3D effects when calculating oxygen abundances.
-Furthermore, when characterising the oxygen depletion rate \--- the strength of the Na-O anti-correlation in a given cluster \--- it is vital to sample stars belonging to all three components, where possible.
-If only a primordial sample of stars in a globular cluster is observed, their [Na/Fe] and [O/Fe] abundances will be indistinguishable from halo stars of a similar metallicity.
+In addition to the normal care afforded for measuring elemental abundances from high-resolution spectroscopic data, attention must be given to telluric absorption, contamination from nickel transitions, as well as non-LTE and 3D effects when determining oxygen abundances.
+Furthermore, when characterising the oxygen depletion rate -- the strength of the {Na-O} anti-correlation in a given cluster -- it is vital to sample stars belonging to all three components, where possible.
+If only a primordial sample of stars in a globular cluster is observed, their [Na/Fe] and [O/Fe] abundances will be indistinguishable from field stars of a similar metallicity.
 In such a scenario, any inferred anti-correlation could equally be explained by intrinsic chemical scatter or observational uncertainties.
@@
 	\includegraphics[width=\textwidth]{./figures/aquarius-o-na-halo.pdf}
-	\caption{Oxygen and sodium abundances for thick disc ($+$), thin disc ($\times$) and halo ($\circ$) stars from \citet{reddy;et-al_2005}, and globular cluster stars from \citet{carretta;et-al_2009} (grey symbols).
+	\caption{Oxygen and sodium abundances for thick disc ($+$), thin disc ($\times$) and halo ($\circ$) stars from \citet{reddy;et-al_2006}, and globular cluster stars from \citet{carretta;et-al_2009a} (grey symbols).
 The Aquarius candidate abundances are also shown (\textbullet), illustrating how their [O/Fe], [Na/Fe] content is not dissimilar from galactic stars.
-Ambiguous thick disc/thin disc stars in \citet{reddy;et-al_2005} are marked with thick disc symbols ($+$), as are uncertain thick disc/halo stars with halo symbols ($\circ$).}
+Ambiguous thick disc/thin disc stars in \citet{reddy;et-al_2006} are marked with thick disc symbols ($+$), as are uncertain thick disc/halo stars with halo symbols ($\circ$).}
 	\label{fig:o-na}
@@
 
-\citet{wylie-de-boer;et-al_2012} measured [Na/Fe] and [O/Fe] abundances for four of their six Aquarius stream members.
-This research has four stars in common with the \citet{wylie-de-boer;et-al_2012} study, but sodium and oxygen measurements exist for only three stars intersecting both samples, as the data quality for J223811-104126 in the \citet{wylie-de-boer;et-al_2012} study prohibited measuring oxygen.
-We have measurements for all of our stars, including J223811-104126, for which we ascertained an upper limit from the [O \textsc{i}] lines of [O/Fe] $< 0.5$ dex, and a corrected abundance of $\mbox{[O/Fe]} = 0.14 \pm 0.08$ from the O \textsc{i} triplet lines.
-In Figure \ref{fig:o-na} we have plotted theses abundances, including the corrected value for J223811-104126 rather than an upper limit.
+\citet{wylie-de-boer;et-al_2012} measured sodium and oxygen abundances for four of their six Aquarius stream members.
+This research has four stars in common with the \citet{wylie-de-boer;et-al_2012} study, but sodium and oxygen measurements exist for only three stars intersecting both samples, as the data quality for {J223811-104126} in the \citet{wylie-de-boer;et-al_2012} was such that it prohibited oxygen determination.
+We have sodium and oxygen abundances for all of our stars, including {J223811-104126}, for which we ascertained a conservative upper limit from the {[O\,\textsc{i}]} lines of {${\rm [O/Fe]} < 0.5$\,dex}, and a abundance ratio of {$\mbox{[O/Fe]} = 0.14 \pm 0.08$} from the {O\,\textsc{i}} triplet lines.
+In Figures \ref{fig:o-na-clusters} and \ref{fig:o-na} we have plotted theses abundances, including the corrected value for {J223811-104126} rather than the upper limit.
 
@@
 % star 		| mine 				| hers
-% C2225316	| 0.09 +/- 0.01 (2)	| 0.00 +/- 0.15
-% C2306265	| 0.18 +/- 0.00 (2)| ...
-% J221821	| 0.08 +/- 0.10 (1)| 0.03 +/- 0.15
-% J223504	| 0.18 +/- 0.07 (3)| 0.28 +/- 0.21
-% J223811	| 0.07 +/- 0.00 (1)| 0.04 +/- 0.15
-
-The \citet{wylie-de-boer;et-al_2012} measurements indicate two stars with solar levels of Na \--- identical to field star Na abundances for their metallicity \--- and two stars with super-solar sodium content: J223504 and J232619.
-We also find J223504 to be sodium-enhanced with $\mbox{[Na/Fe]} = 0.18$, slightly lower than the \citet{wylie-de-boer;et-al_2012} value of $0.28 \pm 0.21$\,dex.
-This discrepancy in [Na/Fe] is the largest difference between the two studies, and still within the uncertainties published by \citet{wylie-de-boer;et-al_2012}.
-The second star in their study with elevated sodium, J232619, is not in our sample.
-We find the additional star not present in the \citet{wylie-de-boer;et-al_2012} sample, C2306265, to be sodium enhanced to the same level of J223504 with $\mbox{[Na/Fe]} = 0.18$\,dex.
-
-The sodium-enhanced stars exhibit no depletion of oxygen; their chemistry does not demonstrate a classical Na-O anti-correlation.
-In fact, they have a slight positive relationship: the Na-enhanced stars in the \citet{wylie-de-boer;et-al_2012} study show an increased oxygen content (within the uncertainties), contrary to an expected oxygen depletion between stellar generations within a globular cluster.
-With our revised oxygen abundances and two sodium-enhanced stars, we find a very slight positive relationship of X.XX +/- X.XX, and no evidence of a Na-O anti-correlation in the Aquarius stream.
-
-If the Aquarius stream is the result of a disrupted globular cluster, a large part of the picture would still be missing.
-Most of the Aquarius stream stars studied to date (either in this sample or the \citet{wylie-de-boer;et-al_2012} study), would be classified as belonging to a `primordial' component, with chemistry indistinguishable from the halo.
-Identifying more Aquarius stream members belonging to the intermediate component with strong oxygen depletion, or perhaps members of an extreme component, would be strong evidence for a Na-O anti-correlation and perhaps a globular cluster origin.
-Three stream stars identified to date (including two from this sample) could plausibly be classified as members of an intermediate population, with only a slight enhancement in sodium and no oxygen-depletion.
-Thus, if the strength of any Na-O relationship is to be used to vet potential disrupted hosts for the Aquarius stream, many more stream candidates will need to be identified, and observed with high-resolution and high $S/N$.
+% C222531	| 0.10 +/- 0.01 (2)	| 0.00 +/- 0.15
+% C2306265	| 0.21 +/- 0.00 (2)| ...
+% J221821	| 0.09 +/- 0.10 (1)| 0.03 +/- 0.15
+% J223504	| 0.26 +/- 0.07 (3)| 0.28 +/- 0.21
+% J223811	| 0.08 +/- 0.00 (1)| 0.04 +/- 0.15
+
+The \citet{wylie-de-boer;et-al_2012} measurements indicate two stars with solar levels of [Na/Fe] -- identical to field star abundances for their metallicity -- and two stars with enhanced sodium content: {J223504-152834} and {J232619-080808}.
+We also find {J223504-152834} to be sodium-enhanced, whereas the second star in their study, {J232619-080808}, is not in our sample.
+We find the additional star not present in the \citet{wylie-de-boer;et-al_2012} sample, {C2306265-085103}, to be sodium enhanced to almost the same level of {J223504-152834} with {$\mbox{[Na/Fe]} = 0.26$\,dex}.
+The sodium-enhanced stars exhibit no depletion of oxygen; their chemistry does not demonstrate a {Na-O} anti-correlation.
+
+%In fact, they have a slight positive relationship: the sodium-enhanced stars in the \citet{wylie-de-boer;et-al_2012} study show an increased oxygen content (within the uncertainties), contrary to an expected oxygen depletion between stellar generations within a globular cluster.
+With our revised oxygen abundances and two sodium-enhanced stars, we find a very slight positive relationship of X.XX +/- X.XX.
+Thus, there continues to be {\it no evidence of a Na-O anti-correlation in the Aquarius stream}.
+
+If the Aquarius stream is the result of a disrupted globular cluster, a large part of the picture must still be missing.
+Almost all of the Aquarius stream stars studied to date (either in this sample or the \citet{wylie-de-boer;et-al_2012} study), would be unambiguously classified as belonging to a `primordial' component, with chemistry indistinguishable from the thick disc or halo.
+Identifying more Aquarius stream members belonging to the intermediate component with strong oxygen depletion, or perhaps members of an extreme component, would be convincing evidence for a {Na-O} anti-correlation and a globular cluster origin.
+Three stream stars identified to date (including two from this sample) might arguably be classified as members of an intermediate population, with only a slight enhancement in sodium and no oxygen-depletion.
+Recall our [Na/Fe] abundance ratios appear systematically higher in our standard stars when compared to the literature.
+Thus, if the strength of any {Na-O} relationship is to be used to vet potential disrupted hosts for the Aquarius stream, many more stream members will need to be identified and observed spectroscopically with high-resolution and high $S/N$.
+Currently, no evidence exists for a {Na-O} anti-correlation in the Aquarius stream.
 
@@
 An inverse relationship between sodium and oxygen is not the only chemical pattern commonly observed in globular clusters.
-Although not ubiquitous to every system, many clusters exhibit an anti-correlation between aluminium and magnesium abundances.
-This is perhaps unsurprising, given the nucleosynthetic pathways for aluminium and magnesium.
-In addition to the CNO cycle operating during hydrogen burning, the Mg-Al chain can also operate under extreme temperatures \citep[$T_6 \sim 3$\,K;][]{arnould;et-al_1999}.
-Aluminium is produced by proton capture of magnesium, beginning with $^{24}$Mg to $^{25}$Al.
+Although not ubiquitous to every system, many clusters exhibit an anti-correlation between aluminium and magnesium.
+This is perhaps unsurprising, given the nucleosynthetic pathways for these elements.
+In addition to the CNO cycle operating during hydrogen burning, the {Mg-Al} chain can also operate under extreme temperatures \citep[$T_6 \sim 3$\,K;][]{arnould;et-al_1999}.
+In these conditions, aluminium is produced by proton capture of magnesium, beginning with $^{24}$Mg to $^{25}$Al.
 The lifetime of $\beta$-decay to proton capture allows for the production of unstable $^{27}$Si through proton capture.
 Seconds later, the isotope decays to $^{27}$Al, completing the $^{27}$Si path of the Mg-Al cycle.
-The alternative process from $^{25}$Al involves proton capture to $^{26}$Mg, but this process requires much higher temperatures ($T_6 \sim 7$\,K).
-In fact, although the process operates from temperatures above 30 million K, large Mg-Al abundance variations are not appreciable unless the temperatures reach $T_6 \sim 6.5$\,K.
+The alternative process onwards from $^{25}$Al involves proton capture to $^{26}$Mg, but this process requires much higher temperatures ($T_6 \sim 7$\,K).
+In fact, although the process operates from temperatures above 30 million K, large {Mg-Al} abundance variations are not appreciable unless the temperatures reach $T_6 \sim 6.5$\,K.
 
@@
 However, the locations where these extreme temperatures can be found are under some debate.
-Theoretical models indicate that the interiors of globular cluster stars do not reach sufficient temperatures for the Mg-Al cycle to produce the observed variations.
+Theoretical models indicate that the interiors of globular cluster stars do not reach sufficient temperatures for the {Mg-Al} cycle to produce the observed variations.
 Thus, although the processes for creating these chemical patterns are understood, the exact site and requisite conditions are lacking a full description.
 
-No inverse correlation has been observed in the Aquarius stream stars to date.
-Given that we do not find a Na-O anti-correlation, it is not surprising that a Mg-Al pattern has also not been observed.
-\citet{wylie-de-boer;et-al_2012} published magnesium and aluminium abundances for five stars in their Aquarius stream sample.
-No inverse correlation is present, and their abundances are not dissimilar from galactic stars.
-The abundances tabulated in Table \ref{tab:abundances} vary slightly with those presented in the \citet{wylie-de-boer;et-al_2012} sample.
-Two candidates are in good agreement: J221821 and J223811, albeit the data quality in the \citet{wylie-de-boer;et-al_2012} study did not permit measuring aluminium for J223811.
-The other two stars common between studies are C2225316 and J223504, which we found to be the most abundant in both magnesium and aluminium.
-
-While \citet{wylie-de-boer;et-al_2012} find almost no scatter ($\pm0.02$\,dex) in [Mg/Fe] for stars common to both studies, we find C2225316 and J223504 to be almost $+0.20$\,dex higher than the rest of the sample.
-The reason for this discrepancy is not obvious, given the stellar parameters between the two studies agree well, with the previously discussed exception of metallicity.
-In particular, the stellar parameters agree excellently for J223504, but we find $\mbox{[Fe/H]} = -0.68$ instead of the $-0.98$ as found by \citet{wylie-de-boer;et-al_2012}.
-Of the Mg \textsc{i} profiles measured, only two transitions are common to both line lists: 6318$\lambda$ and 6319$\lambda$.
-The oscillator strengths differ between studies; in these two lines the $\log{gf}$ differs by $-0.24$ and $-0.27$\,dex respectively (our oscillator strengths are lower).
-This discrepancy only complicates the matter further, since if all other things being equal, then our abundances ought to be lower than the \citet{wylie-de-boer;et-al_2012} study.
+\citet{wylie-de-boer;et-al_2012} published magnesium and aluminium abundances for five stars in their Aquarius sample.
+No inverse correlation is present in their data, and their abundances are not dissimilar from field stars.
+Given that we do not find a {Na-O} anti-correlation, it is not surprising that a {Mg-Al} pattern is also not observed.
+The abundances tabulated in Table \ref{tab:program-star-abundances} vary slightly with those presented in the \citet{wylie-de-boer;et-al_2012} sample, but we also find no {Mg-Al} relationship.
+Two candidates are in good agreement: {J221821-183424} and {J223811-104126}, albeit the data quality in the \citet{wylie-de-boer;et-al_2012} study did not permit measuring aluminium for {J223811-104126}.
+The other two stars common between studies are {C222531-145437} and {J223504-152834}, which we found to be the most abundant in both magnesium and aluminium.
+
+While \citet{wylie-de-boer;et-al_2012} find almost no scatter {($\pm0.02$\,dex)} in [Mg/Fe] for stars common to both studies, we find {C222531-145437} and {J223504-152834} to be almost {$+0.20$\,dex} higher than the rest of the sample.
+C222531-145437 is chemically distinct in other elements, too.
+The reason for this [Mg/Fe] discrepancy is not obvious, given the stellar parameters between the two studies agree well, with the previously discussed exception of metallicity.
+In particular, the stellar parameters agree excellently for {J223504-152834}, but we find {$\mbox{[Fe/H]} = -0.63$} instead of $-0.98$ as found by \citet{wylie-de-boer;et-al_2012}.
+It is worth noting that our measurement is in between that of \citet{williams;et-al_2011} and \citet{wylie-de-boer;et-al_2012}: \citet{williams;et-al_2011} find [M/H]$= -0.33$\,dex.
+Of the {Mg\,\textsc{i}} profiles measured, only two transitions are common to both line lists: {6318\,\AA} and {6319\,\AA}.
+The oscillator strengths differ between studies; in these two lines the $\log{gf}$ differs by $-0.24$ and {$-0.27$\,dex} respectively (our oscillator strengths are lower).
+This indicates that the difference in oscillator strengths may explain the $\sim{}$0.2\,dex offset in [Mg/Fe] between this study and that of \citet{wylie-de-boer;et-al_2012}.
 
@@
 % star 		| mine 				| hers			| mine			| hers			| 
-% C2225316	| 0.50 +/- 0.06		| 0.32 +/- 0.05	| 0.68 +/- 0.04	| 0.38 +/- 0.12	| No, + | No, +
-% C2306265	| 0.41 +/- 0.05		| ...			| 0.28 +/- 0.04	| ...			| N/A	| N/A 
-% J221821	| 0.34 +/- 0.05		| 0.30 +/- 0.01	| 0.21 +/- 0.10	| 0.29 +/- 0.12	| Yes +	| Yes -
-% J223504	| 0.49 +/- 0.09		| 0.33 +/- 0.05	| 0.31 +/- 0.05	| 0.21 +/- 0.03	| No +	| No +
-% J223811	| 0.32 +/- 0.01		| 0.30 +/- 0.06	| 0.10 +/- 0.10	| ...			| Yes +	| N/A
+% C222531	| 0.53 +/- 0.06		| 0.32 +/- 0.05	| 0.71 +/- 0.04	| 0.38 +/- 0.12	| No, + | No, +
+% C2306265	| 0.44 +/- 0.05		| ...			| 0.33 +/- 0.04	| ...			| N/A	| N/A 
+% J221821	| 0.35 +/- 0.05		| 0.30 +/- 0.01	| 0.21 +/- 0.10	| 0.29 +/- 0.12	| Yes +	| Yes -
+% J223504	| 0.51 +/- 0.09		| 0.33 +/- 0.05	| 0.29 +/- 0.05	| 0.21 +/- 0.03	| No +	| No +
+% J223811	| 0.34 +/- 0.01		| 0.30 +/- 0.06	| 0.11 +/- 0.10	| ...			| Yes +	| N/A
 
@@
 	\includegraphics[width=\columnwidth]{./figures/aquarius-mg-al.pdf}
-	\caption{Magnesium and aluminium abundances for Aquarius candidates, and Milky Way halo/disc stars from \citet{reddy;et-al_2003} ($+$) and \citet{fulbright_2000} ($\circ$).
-The chemically peculiar star, C2225316-14437, is marked.}
+	\caption{Magnesium and aluminium abundances for Aquarius stream candidates (\textbullet), and Milky Way halo/disc stars from \citet{reddy;et-al_2003} ($+$) and \citet{fulbright_2000} ($\circ$).
+The chemically peculiar star, {C222531-145437}, is marked.}
 	\label{fig:mg-al}
@@
 The [Mg/Fe] and [Al/Fe] abundances found for the five Aquarius stars in this sample are illustrated in Figure \ref{fig:mg-al}.
-Interestingly, our stars exhibit a strong positive relationship, with a best-fitting slope of $\mbox{[Al/Fe]} = 2.15 x \mbox{[Mg/Fe]} - 0.57$ ($R = Y.YY$).
-If the exclude C2225316, our chemically peculiar star with enhanced [Al/Fe] relative to the rest of the sample, the slope decreases to $\mbox{[Al/Fe]} = 1.07 x \mbox{[Mg/Fe]} - 0.19$ and the correlation coefficient $R$ increases to Z.ZZ.
-Even when a Mg-Al anti-correlation is not detected in globular clusters, there is generally some scatter in [Al/Fe] at constant [Mg/Fe] \citet[e.g.
-see][]{carretta;et-al_2009a}.
-Few classical globular clusters exhibit a positive correlation.
+Our stars exhibit a strong positive relationship, with a best-fitting slope of ${{\rm [Al/Fe]} = 2.08\times\mbox{[Mg/Fe]} - 0.57}$, which is in part driven by {C222531-145437}.
+If we exclude this chemically peculiar star with enhanced [Al/Fe] relative to the rest of the sample, the slope decreases to {${\rm [Al/Fe]} = 0.96\times\mbox{[Mg/Fe]} - 0.16$}, a near 1:1 relationship.
+Even when a {Mg-Al} anti-correlation is not detected in globular clusters, there is generally more scatter in [Al/Fe] at near-constant [Mg/Fe] \citep[e.g.
+see Figure \ref{fig:mg-al} or ][]{carretta;et-al_2009a}.
+To the author's knowledge of the literature no classical globular clusters exhibit a positive correlation, and nor is it expected in globular clusters.
 
@@
 	\includegraphics[width=\textwidth]{./figures/aquarius-mg-al-cluster.pdf}
-	\caption{[Mg/Fe] and [Al/Fe] abundances for stars in 16 globular clusters from \citet{carretta;et-al_2009} and for the five Aquarius stream candidates.
-The inverse Mg-Al correlation is illustrated, most obviously in NGC 2808 and NGC 1904.
+	\caption{[Mg/Fe] and [Al/Fe] abundances for stars in 16 globular clusters from \citet{carretta;et-al_2009a} and for the five Aquarius stream candidates.
+The inverse {Mg-Al} correlation is illustrated, most obviously in {NGC 2808} and {NGC 1904}.
 The strong positive correlation observed in Aquarius is in stark contrast with other classical globular clusters.}
@@
 
-A positive relationship between magnesium and aluminium can result from SN \textsc{ii} contributions to the local interstellar medium.
-High-resolution observations of disc stars illustrate this correlation \citep{bensby;venn}, demonstrating efficient SN \textsc{ii} mixing.
-Some intermediate-mass ($4M_\odot$) AGB models can also predict a positive correlation between aluminium and magnesium \citet{karakas;et-al}.
+A positive relationship between magnesium and aluminium can result from {Sn\,\textsc{ii}} contributions to the local interstellar medium.
+High-resolution observations of disc stars illustrate this correlation, demonstrating efficient {Sn\,\textsc{ii}} mixing.
+Some intermediate-mass ($\sim$4$M_\odot$) AGB models also contribute towards a positive correlation between aluminium and magnesium.
 Under extreme temperatures ($T_6 \sim 300$\,K), substantial $^{25}$Mg and $^{26}$Mg are produced by $\alpha$-capture onto $^{22}$Ne by the $^{22}$Ne($\alpha$,n)$^{25}$Mg and $^{22}$Ne($\alpha$,$\gamma$)$^{26}$Mg reactions respectively.
-Following deep dredge up, significant $^{25}$Mg and $^{26}$Mg is mixed into the photosphere, more than the quantity of $^{26}$Al produced through the Mg-Al cycle.
-This dredge up process replenishes the Mg which is expensed during the Mg-Al pathway.
-Therefore, a positive relationship between magnesium and aluminium can occur if there has been significant contributions from intermediate mass AGB stars undergoing dredge up.
-
-An unrealistically high fraction of intermediate-mass AGB stars would be required to produce the same chemical signature of a single Sn \textsc{ii} event.
-Given the efficiency of chemical pollution following supernovae, the observed correlation in the thick disc is likely the result of Sn \textsc{ii} events.
+Following deep dredge up, significant $^{25}$Mg and $^{26}$Mg is mixed into the photosphere, more so than the quantity of $^{26}$Al produced through the {Mg-Al} cycle.
+This dredge up process replenishes the Mg that is expensed during the {Mg-Al} pathway.
+Therefore, a positive relationship between magnesium and aluminium can occur if there has been significant contributions from intermediate mass AGB stars.
+
+An unrealistically high fraction of intermediate-mass AGB stars would be required to produce the same chemical signature of a single {Sn\,\textsc{ii}} event.
+Given the efficiency of chemical pollution following supernovae, the observed correlation in the thick disc is likely the result of {Sn\,\textsc{ii}} events.
 However, since the chemical enrichment environment of the Aquarius stream is unknown, we cannot exclude either possibility.
@@
 \subsection{The Na-Ni Relationship}
+\label{sec:na-ni-relationship}
 
 % need to say about [alpha/fe] and [na/fe] with distance
-Detailed chemical studies of nearby disk stars have noted a correlation with [Na/Fe] and [Ni/Fe] abundances.
-This relationship was first hinted in \citet{nissen;schuster_1997}, where the authors found eight stars that were underabundant in [$\alpha$/Fe], [Na/Fe] and [Ni/Fe].
+Detailed chemical studies of nearby disc stars have noted a correlation with [Na/Fe] and [Ni/Fe] abundance ratios.
+This relationship was first hinted in \citet{nissen;schuster_1997}, where the authors found eight stars that were under-abundant in [$\alpha$/Fe], [Na/Fe] and [Ni/Fe].
 Interestingly, the authors noted that stars at larger galactocentric radii were most deficient in these elements.
-\citet{fulbright_2000} saw a similar signature: stars with low [Na/Fe] were only found at large ($R_\odot > 20$\,kpc) distances.
-\citet{nissen;schuster_1997} proposed that since the outer halo is thought to have been built up by the accretion of dwarf satellite galaxies, then the Na-Ni pattern may be a chemical indicator of merger history within the galaxy.
-
-With additional data from \citet{nissen;schuster_2011}, the Na-Ni relationship was found to be slightly steeper than originally put forward.
-The pattern exists only for stars with $-1.5 < \mbox{[Fe/H]} < -0.5$ dex, and is not seen in metal-poor dSph stars, providing a potentially useful indicator for investigating chemical evolution.
-
-%However, it is crucial to note that although there are only a few dSph stars in the $-1.5 < \mbox{[Fe/H]} < -0.5$ metallicity regime with [Na/Fe], [Ni/Fe] measurements, they agree reasonably well with the galactic trend.
+\citet{fulbright_2000} saw a similar signature: stars with low [Na/Fe] were only found at large {($R_\odot > 20$\,kpc)} distances.
+\citet{nissen;schuster_1997} proposed that since the outer halo is thought to have been largely built up by accretion, then the {Na-Ni} pattern may be a chemical indicator of merger history within the galaxy.
+
+With additional data from \citet{nissen;schuster_2011}, the {Na-Ni} relationship was found to be slightly steeper than originally proposed.
+The pattern exists only for stars with {$-1.5 < \mbox{[Fe/H]} < -0.5$\,dex}, and is not seen in metal-poor dSph stars, providing a potentially useful indicator for investigating chemical evolution.
+However, it is crucial to note that although there are only a few dSph stars in the $-1.5 < \mbox{[Fe/H]} < -0.5$ metallicity regime with [Na/Fe], [Ni/Fe] measurements, they agree reasonably well with the galactic trend.
 
 The correlation between sodium and nickel content is the nucleosynthetic result of neutron capture in massive stars.
-As previously discussed, the total Na abundance is controlled by the neutron excess, which limits the production of $^{58}$Ni during Sn \textsc{ii} events.
+As previously discussed, the total Na abundance is controlled by the neutron excess, which limits the production of $^{58}$Ni during {Sn\,\textsc{ii}} events.
 When the inevitable supernova begins, the core photodissociates into neutrons and protons, allowing the temporary creation of $^{56}$Ni before it decays to $^{56}$Fe.
@@
 % [Na/Fe], [Ni/Fe]
-\begin{figure}[h]
-	\includegraphics[width=\columnwidth]{./figures/aquarius-na-ni.pdf}
-	\caption{A plot showing [Na/Fe] and [Ni/Fe] for all Aquarius stream stars. TODO add dwarf/GC/disk stars on here.}
+\begin{figure}[h!]
+	\includegraphics[width=\columnwidth]{./figures/gc-dsph-na-ni.pdf}
+	\caption{[Na/Fe] and [Ni/Fe] for Aquarius stream candidates and for globular cluster, dSph, and field (halo/disc) stars.
+The \citet{nissen;schuster_2011} plotted sample included halo stars, $\alpha$-low and $\alpha$-high disc members.
+As noted by \citet{nissen;schuster_1997,nissen;schuster_2011}, a positive Na-Ni relationship exists for field stars, with dSph members exhibiting strong depletion in both elements and globular cluster stars consistently showing an enhancement.
+Sodium and nickel content for Aquarius members indicate a dSph accretion origin is unlikely.}
 	\label{fig:na-ni}
@@
 Consequently, both types of systems exhibit chemistry that reflects their nucleosynthetic antiquity.
-Dwarf spheroidal stars do not demonstrate enhanced sodium or nickel content with respect to iron, as there has been a relatively negligible linage of massive stars undergoing supernova.
+Dwarf spheroidal stars do not demonstrate enhanced sodium or nickel content with respect to iron, as there has been a relatively small linage of massive stars undergoing supernova.
 In contrast, globular cluster stars do have elevated [Na/Fe], [Ni/Fe] signatures.
 This sharp contrast between dwarf spheroidal and globular cluster star chemistry is illustrated in Figure \ref{fig:na-ni}.
-Given the extended star formation within the Milky Way disk, globular cluster stars and disk stars are indiscernible in the Na/Ni plane: they both show an extended contribution of massive stars.
-
-The most that can be inferred from the Na, Ni abundances of Aquarius stream stars is that their enrichment environment is less like a dSph galaxy, and more representative of a globular cluster, or the disc of the Milky Way.
-
-\subsection{The Chemical Distinctiveness of C2225316}
+Given the extended star formation within the Milky Way disc, globular cluster stars and disc stars are indiscernible in the Na/Ni plane: they both show an extended contribution of massive stars.
+The most that can be inferred from the Na, Ni abundances of Aquarius stream stars is that their enrichment environment is less like a dSph galaxy, and more representative of either a globular cluster, or the disc of the Milky Way.
+
+\subsection{The Distinctiveness of C222531-145437}
 
@@
 
-C2225316 exhibits peculiar chemical abundances compared to the rest of the Aquarius candidates.
-It is over-abundant in light refractory elements, and exhibits a strong barium abundance of $\mbox{[Ba/Fe]} = 0.70$\,dex.
-This abundance is well in excess of the halo ($\mbox{[Ba/Fe]} \sim 0.0$) \--- and our other Aquarius stream stars \--- which vary between $-$0.02 to 0.15\,dex.
+C222531-145437 exhibits peculiar chemical abundances compared to the rest of the Aquarius candidates.
+In almost every element with respect to iron, {C222531-145437} is distinct from the other Aquarius candidates.
+It is over-abundant in light refractory elements, weak and heavy $s$-process elements, with a strong barium abundance of {$\mbox{[Ba/Fe]} = 0.68$\,dex}.
+This value is well in excess of the halo ({$\mbox{[Ba/Fe]} \sim 0.0$}) -- and our other Aquarius stream stars -- which vary between $-$0.02 to {0.15\,dex}.
+
+Although no radial velocity variations were observed between exposures, it is possible that an unseen AGB star has contributed to the surface abundances of C222531-145437.
+The abundances of heavy elements produced by AGB stars have a high dependence on the overall metallicity and mass of the AGB star.
+Low-mass ($\lesssim{}3M_\odot$) AGB stars produce high fractions of heavy $s$-process elements compared to their weak $s$-process counterparts.
+As such, [Ba/Y] is a useful indicator when considering contributions from a low-mass AGB companion.
+For C222531-145437, ${{\rm [Ba/Y]} = -0.17}$, which is much lower than expected if a low-mass AGB star was the dominant reason for the heavy element enhancements ([Ba/Y] $\sim$ 0.5).
+Intermediate-mass (3-5$M_\odot$) AGB stars also cannot explain the abundances for C222531-145437: using recently computed intermediate-mass AGB yields for 3-5$M_\odot$ for a star of [Fe/H] = $-1.2$ (Fishlock, Karakas et al., forthcoming) we find the expected surface abundances do not match the observations.
+If mass transfer from an AGB companion is ongoing or has occurred very recently, non-negligible amounts of technitium is produced, and remains visible before it decays over $\sim$100\,Myr$^{\rm [citation\phd{}needed]}$.
+We saw no technitium absorption feature at the 4049.11, 4238.19 or 4297.06\,{\AA} wavelengths in the spectrum of C222531-145437.
+Therefore, we find no reason to suspect the heavy element enhancement in C222531-145437 is the result of an AGB companion.
 
 High $s$-process enhancements have been noted for a few disrupted globular clusters that exhibit a wide metallicity range.
-Most noteably: $\omega$Centurai \citep{majewski;et-al_2012}, M22 \citep{marino;et-al_2011} and (\# any others?).
-Like the Aquarius co-moving group, both clusters are relatively close to the sun: $R_\odot = 5.2$\,kpc and 3.2\,kpc, respectively.
-M22 has a mean metallicity of $\mbox{[Fe/H]} \sim -1.7$, varying between $-2.0 < \mbox{[Fe/H]} < -1.6$\,dex.
-Since C2225316 has a metallicity of $\mbox{[Fe/H]} = -1.26$\,dex, it is unlikely to be associated with M22.
-However, the high barium content and overall metallicity of C2225316 ($\mbox{[Fe/H]} = -1.26$) suggests there may be an association with $\omega$-Centurai.
+Most notably $\omega$-Centurai \citep{majewski;et-al_2012} and M22 \citep{marino;et-al_2011}.
+Like the Aquarius co-moving group, both clusters are relatively close to the sun: {$R_\odot = 5.2$\,kpc} and {3.2\,kpc}, respectively.
+M22 has a mean metallicity of {$\mbox{[Fe/H]} \sim -1.7$}, varying between {$-2.0 < \mbox{[Fe/H]} < -1.6$\,dex}.
+Since {C222531-145437} has a metallicity of {$\mbox{[Fe/H]} = -1.26$\,dex}, it is unlikely to be associated with M22.
+However, the high barium content and overall metallicity of {C222531-145437} ({$\mbox{[Fe/H]} = -1.26$}) suggests there may be an association with $\omega$-Centurai.
 
 $\omega$-Centurai has a retrograde orbit with low inclination.
-Many groups simulating this orbit have predicted retrograde tidal debris to occur near the Solar circle \citep{dinescu_2002,tsuchiya_2003,tsuchiya_2004,mizutani_2003,bekki;freeman_2003}.
-Subsequent searches for $\omega$-Cen debris in the solar neighbourhood have led to tantalizing signatures of debris.
-From over 4,000 stars selected from the $\omega$-Cen color-magnitude diagram by \citet{da_costa;coleman_2008}, only six candidate members were recovered.
+Many groups simulating this orbit have predicted retrograde tidal debris to occur near the Solar circle \citep{dinescu_2002,tsuchiya_2003,tsuchiya_2004,bekki;freeman_2003}.
+Subsequent searches for $\omega$-Centurai debris in the solar neighbourhood have led to tantalising signatures of debris.
+From over 4,000 stars targeted by \citet{da_costa;coleman_2008}, only six candidate debris members were recovered.
 More recently, \citet{majewski;et-al_2012} presented data from the Grid Giant Star Survey (GGSS), an all-sky search looking for metal-poor giant stars.
-From their data, they identified 12 stream candidates.
-Although this scarcity is consistent with tidal stripping occurring long ago, it is perhaps worrying that searches for stripped stars near $\omega$-Cen itself have been even less fruitful.
-
-In addition to presenting new stream candidates, \citet{majewski;et-al_2012} performed 4,050 different simulations in order to predict likely locations for tidal debris.
-The results of their simulation are replicated in Figure \ref{fig:majewski-simulation}, where the location of C2225316 is also shown.
-Interestingly, the velocity and position of C2225316 line up almost precisely where \citet{majewski;et-al_2012} predict a high probability of stream members.
-
-Although this is interesting from a qualitative perspective, the most striking evidence for an association with $\omega$-Centurai is in chemistry.
-Figure \ref{fig:omega-cen-barium} demonstrates the [Ba/Fe] abundance for $\omega$-Cen stars compared to that of the galactic halo.
-A steep Ba enhancement is present, which is unique to the globular clusters $\omega$-Cen and M22.
-We note that although high $s$-process enrichment is present in other systems \citep[IC 2391, the Argus association;][]{de_silva;et-al_2013}, these systems are have metallicities near solar values and are unlikely to be associated with C2225316.
+From their data they identified 12 stream candidates.
+Although this scarcity is consistent with tidal stripping occurring long ago, it is perhaps worrying that searches for stripped stars closer to $\omega$-Centurai itself have been even less successful.
+
+In addition to presenting new stream candidates, \citet{majewski;et-al_2012} performed 4,050 simulations in order to predict likely locations for $\omega$-Centurai tidal debris.
+The results of their simulation are replicated in Figure \ref{fig:omega-cen-tidal-debris}, where the location of {C222531-145437} is also shown.
+Interestingly, the velocity and position of {C222531-145437} line up almost precisely where \citet{majewski;et-al_2012} predict a high probability of tidal debris.
+
+\begin{figure}[h!]
+	\includegraphics[width=\columnwidth]{./figures/omegacen_tidaldebris.pdf}
+	\caption{Panel (a) shows the distribution of giant stars in the GGSS \citep{majewski;et-al_2012} in galactic longitude and $V_{\rm GSR}/cos(b)$ after excluding stars with $|b| > 60\,^\circ$.
+Stars from the GGSS sample believed to be $\omega$Cen tidal debris are shown in green shading.
+Red points are stars from the GGSS sample with abundances that follow the $\omega$Cen [Ba/Fe]--[Fe/H] pattern.
+Blue points are those with echelle spectra that do not follow this trend.
+Grey shading highlights other potential halo substructures from their study.
+Panel (b) shows the probability distribution of $\omega$Cen tidal debris from 4,050 simulations.
+The $\omega$Cen core is shown as a green cross and the cyan star represents {C222531-145437}, falling almost precisely where a relatively high probability of $\omega$Cen tidal debris is expected.}
+	\label{fig:omega-cen-tidal-debris}
+\end{figure}
+
+% dynamics + orbital info
+
+Perhaps the most striking evidence for an association between {C222531-145437} and $\omega$-Centurai is in its chemistry.
+Figure \ref{fig:omega-cen-barium} demonstrates the [Ba/Fe] abundance for $\omega$-Centurai stars compared to that of the galactic halo.
+A steep barium enhancement is present, which is unique to the globular clusters $\omega$-Centurai and M22.
+We note that although high $s$-process enrichment is present in other systems \citep[IC 2391, the Argus association;][]{de_silva;et-al_2013}, these systems are have metallicities near solar and are unlikely to be associated with {C222531-145437}.
+Furthermore, \textit{all other elemental abundances} measured here precisely match with those presented by \citet{marino;et-al_2011} for $\omega$-Centurai RGB stars.
+
+\begin{figure}[h!]
+	\includegraphics[width=\columnwidth]{./figures/omegaCen-c222531.pdf}
+	\caption{[Fe/H] and [Ba/Fe] for halo/disc stars (black) from \citet{fulbright_2000,reddy;et-al_2003,reddy;et-al_2006} and $\omega$-Centurai RGB stars (grey) from \citet{francois;et-al_1988,smith;et-al_2000,marino;et-al_2011}.
+Similar trends are observed for other heavy elements in $\omega$-Centurai members.
+The candidate we associate with $\omega$-Centurai tidal debris, C222531-145437, is marked in cyan.}
+	\label{fig:omega-cen-barium}
+\end{figure}
 
@@
 
-The chemical peculiarity of C2225316 suggests that it is distinct from the Aquarius co-moving group.
-The high $s$-process enrichment is similar to that observed in $\omega$-Centurai stars, and the overall metallicity ($\mbox{[Fe/H]} = -1.26$) agrees excellently with the mean metallicity of a known sub-population within $\omega$-Centurai.
-Moreover, the position and velocity for C2225316 precisely coincide with the most likely predictions for tidal debris from $\omega$-Centurai.
-The chemical and phase-space information indicates that C2225316 is likely associated with the disrupted globular cluster $\omega$-Centurai.
-
-\subsection{Possible Progenitors}
-
-Since the Aquarius stream is kinematically coherent, the default assumption is that the system has been accreted.
-The stream candidates presented here are slightly enhanced in sodium and nickel, suggesting that if a progenitor ever existed then its environment was more like a globular cluster than a dSph galaxy.
-Based on a lack of $\alpha$-enhancement and increased [Na/Fe], [Ni/Fe] abundances, we exclude the possibility that the Aquarius stream has resulted from a disrupted dwarf satellite.
-If the progenitor is a disrupted globular cluster, and all our candidates are members, then it has a wider metallicity distribution than most globular clusters.
-
-However, our chemical analysis does not reveal any inverse Na-O correlation \--- which would be strong evidence for a globular cluster environment.
-Furthermore, we observe a positive Mg-Al relationship, the same seen by \citet{wylie-de-boer;et-al_2012}.
-High resolution, high $S/N$ spectra for the entire stream may be required before such chemical signatures may become apparent.
-In this section we discuss other possible causes for the Aquarius co-moving group.
-
-\subsubsection{$\omega$-Centurai}
-
-In their original discovery paper, \citet{williams;et-al_2011} attempted to exclude possible known progenitors.
-On the basis of metallicity, distance, proper motions\footnote{We find the proper motions in Table 1 of \citet{williams;et-al_2011} to be mis-associated to incorrect stars.
-However, this  error was typographical; it did not affect the transverse velocity calculations (Williams, M.E.K, private communication).}, transverse velocities and orbital energies, the authors were able to exclude all known Milky Way satellites, with the notable exception of $\omega$-Centurai.
-Although the Aquarius stream metallicity distribution we find is not dissimilar from a known sub-population in $\omega$-centurai, the individual chemical abundances are quite distinct.
-$\omega$-Centurai members exhibit a strong $s$-process enhancement with overall metallicity.
-This signature is not observed in our data, with the exception of C2225316, which seems to be chemically distinct from the other Aquarius group candidates.
-
-Due to our limited sample size, it is impossible to know whether C2225316 is an outlier, or our four other candidates are halo interlopers.
-Either position is debatable, and both lead to interesting interpretations.
-If most of our observed candidates are halo members, and C2225316 represents the Aquarius stream chemistry, then an association between Aquarius and $\omega$-Centurai is possible.
-
-%Alternatively, the stream may indicate first evidence of a minor merger within the Milky Way disc.
-However, with certainty we can state that most observed Aquarius stream candidates do not exhibit enhanced $s$-process elements, and are therefore unlikely to be associated with $\omega$-Centurai \--- or any other globular cluster.
-
-\subsubsection{Disrupted Disk Stars \--- Signature of a Minor Merger}
-
-\# Velocity distribution wide
-
-\# Spatial distribution wide
-
-\# Chemistry rules out a dSph origin
-
-\# No signs of classical GC chemical patterns
-
-\# The stream chemistry is indistinguishable from disk stars in every aspect
-
-\# Revised distances to each star, transverse motions + orbital energies calculated
-
-\# Monte-carlo simulations demonstrate strongly retrograde stars wrt thick disk + halo
-
-\# Orbital energy pattern aligns exactly with Zolotov+ simulations, but would require a smaller mass of the disrupter (minor merger)
-
-\# Need to discuss disk is unlikely to have had a merger in past 8 Gyr
-
-% could they be displaced thick disk stars?
-
-% [Na/Fe], [Cr/Fe], [Ni/Fe]
-\begin{figure}[h]
-	\includegraphics[width=\columnwidth]{./figures/aquarius-na-cr-ni-fe.pdf}
-	\caption{A plot showing [Na/Fe], [Cr/Fe], and [Ni/Fe] for all Aquarius stream stars.}
-	\label{fig:na-cr-ni-fe}
-\end{figure}
-
-% Toombre #TODO - make this a 4panel in UVW
-\begin{figure}[h]
-	\includegraphics[width=\columnwidth]{./figures/plot-toombre.pdf}
-	\caption{Toombre plot.}
-	\label{fig:toombre}
-\end{figure}
+The chemical peculiarity of {C222531-145437} suggests that it is distinct from the Aquarius co-moving group.
+The high $s$-process enrichment is similar to that observed in $\omega$-Centurai stars, and the overall metallicity {($\mbox{[Fe/H]} = -1.26$)} agrees excellently with the mean metallicity of a known sub-population within $\omega$-Centurai.
+Moreover, the position and velocity for {C222531-145437} precisely coincide with the most likely predictions for tidal debris from $\omega$-Centurai, and the angular momentum and orbital energy precisely matches those found for $\omega$-Centurai by \citet{dinescu;et-al_1999}.
+The chemical and phase-space information indicates that {C222531-145437} is clearly associated with the disrupted globular cluster $\omega$-Centurai.
+
+In their original discovery paper, \citet{williams;et-al_2011} attempted to exclude possible known progenitors for the Aquarius stream.
+On the basis of metallicity, distance, proper motions, transverse velocities and orbital energies, the authors were able to exclude all known Milky Way satellites, with the notable exception of $\omega$-Centurai.
+Although the Aquarius stream metallicity distribution we find is not dissimilar from a known sub-population in $\omega$-Centurai, the individual chemical abundances are quite distinct.
+The strong $s$-process enhancement with overall metallicity is not observed in the rest of our sample.
+Thus, with the exception of {C222531-145437}, the Aquarius members do not have chemistry that is synonymous with $\omega$-Centurai tidal debris.
+
+\subsection{Disrupted disc/Halo Stars -- Signature of a Disc-Satellite Interaction?}
+Since the Aquarius stream is kinematically coherent, the default assumption is that the co-moving group has accreted onto the Milky Way from a tidally disrupted satellite.
+The stream candidates presented here are slightly enhanced in sodium and nickel, suggesting that if a satellite parent ever existed then its chemical enrichment environment was more like a globular cluster than a dSph galaxy.
+Based on a lack of $\alpha$-enhancement and increased [Na/Fe], [Ni/Fe] abundance ratios we exclude the possibility that the Aquarius stream has resulted from a disrupted dwarf galaxy.
+If the progenitor is a disrupted globular cluster, and most of our candidates are members, then the parent has a wider metallicity distribution than most globular clusters.
+
+However we find no chemical evidence for a globular cluster origin.
+If the Aquarius co-moving group is a relic of a disrupted globular cluster then high-resolution, high $S/N$ spectra for the entire stream may be required before chemical patterns reminiscent of classical globular clusters becomes apparent.
+As it stands, the Aquarius group appears chemically indistinguishable from thick disc/halo stars.
+
+These results force us to consider other scenarios that may replicate the observations.
+In addition to the Aquarius group not being chemically coherent, there is an unusually wide spread in the velocity distribution.
+Generally a stellar stream is considered kinematically `cold' when its velocity dispersion is $\lesssim 8$\,km s$^{-1}$.
+We find the velocity dispersion from five members to near $\sim$30\,km\,s$^{-1}$, consistent with the dispersion of 27\,km s$^{-1}$ reported by \citet{williams;et-al_2011} when all stream members are included.
+Hypotheses to explain the Aquarius co-moving group must reconcile this wide velocity dispersion.
+
+There are other co-moving groups in the Milky Way that were initially considered as tidal tails from disrupted satellites that are now explainable as signatures of galaxy formation that are not specific accretion events.
+Like the Aquarius group, the Hercules moving group is significantly offset from the bulk of the observed velocity distribution.
+Members of the Hercules group exhibit a wide range of metallicities and ages \citep{bensby;et-al_2007, bovy;hogg_2010}.
+The observations are well replicated in simulations by stars in the outer disc resonating with the bar in the central region of the Milky Way \citep{dehnen_2000,fux_2001}, and strong predictions are made for disc velocity distributions that would lend further weight to this hypothesis \citep{bovy_2010}.
+The Canis Major stellar over-density was also first considered to be an accretion feature from the Canis Major dwarf spheroidal galaxy \citep{martin;et-al_2004}.
+However, \citet{momany;et-al_2004} demonstrate the star counts, proper-motions, photometry and kinematics of the `accreted feature' can be easily explained by the warp and flare in the outer thick disc.
+The Monoceros ring \citep{newberg;et-al_2002,juric;et-al_2008} is perhaps another example of such an occurrence, as similar features naturally emerge as a consequence of galaxy-satellite interactions \citep{purcell;et-al_2011}, which has prompted considerable discussion \citep{lopez-corredoira;et-al_2012}.
+It is clear that not all significant deviantly kinematic groups are evidence of accretion or tidal tails: in many scenarios a galactic origin is more likely, and simpler.
+
+%We do not strongly consider the Aquarius co-moving group to be related to the flare and warp in the outer thick disc because near $l \sim 60\,^\circ$ the warp extends above the plane.
+Additionally the warp and flare of the disc is included in the Besan\c{c}on galaxy simulations \citep{robin;et-al_2003}, which were originally used to calculate the significance of the Aquarius over-density.
+
+We hypothesise that the Aquarius group is the result of displaced stars from a perturbation in the thick disc.
+That is, the stars are galactic in origin but have been displaced by a disc-satellite interaction.
+Minor mergers can significantly disrupt the host galaxy \citep{villalobos;helmi_2008}, producing extended  spatial and kinematic structure in the process.
+\citet{minchev;et-al_2009} proposed that such a perturbation would cause a galactic `ringing' effect in the neighbourhood surrounding the merger site, analogous to the resulting interference pattern from a stone falling in water and propagating outwards.
+Stars move closer together in constructive interference nodes, a signature which is observable in the velocities and orbits of nearby stars.
+This signature is most prominent  in the $u$-$v$ velocity plane as concentric circles \citep{gomez;et-al_2012}, and dissolves over time (a few Gyr, depending on the mass of the perturber).
+After the $u$--$v$ velocity signature dissipates, a clear signature in angular momentum and orbital energy ($L_Z$, $E$) persist for long periods following the merger \citep[e.g.
+see][]{gomez;et-al_2012}.
+
+Through simulations of Milky Way-Sagittarius simulations, \citet{purcell;et-al_2011} found that the disc-satellite interactions can explain ringing perturbations within the disc.
+Additionally, \citet{widrow;et-al_2012} and \citet{gomez;et-al_2012b} independently observed these phenomena -- a `wavelike perturbation', as it was described by Widrow -- in the SDSS and SEGUE catalogues.
+More recently, \citet{gomez;et-al_2013} proposed that these patterns were induced by the Sagittarius dSph interacting with the disc.
+Their simulations reproduce the observed north-south asymmetries and vertical wave-like structure, and show that the amplitude of these oscillations is strongly dependent on galactocentric distance.
+Combined with the oscillating vertical motions with the $u$--$v$ velocity pattern, corrugated waves are observed as a result of the interaction.
+
+The stars in these oscillations should exhibit a wide range of ages, metallicities and a large spread in velocity dispersion.
+Thus, resultant oscillations following a disc-satellite interaction can satisfactorily explain the existence of the Aquarius co-moving group.
+We do not observe a distinct coherence in the $u$--$v$ velocity plane in our data, but the angular momentum and orbital energies for Aquarius members qualitatively reproduces the theoretically predicted pattern by \citet{gomez;et-al_2012}.
+The extent and gradient of this $L_Z$--$E$ signature is dependent on the mass of the perturber, and the time since infall.
+Although our sample size is minute -- and the sample size would still be small even if all Aquarius members had reliable orbits -- the fact that we see no $u$--$v$ velocity coherence is consistent with the observed $L_Z$--$E$ pattern: signatures in the $L_Z$--$E$ plane become more extended (Figure \ref{fig:toombre}) over time as the $u$--$v$ signature dissipates.
+This is consistent with a disc-satellite interaction occurring in the disc approximately a few Gyr ago.
+
+The Aquarius co-moving group resides at a low latitude ($b \approx - 55\,^\circ$) and with a radial distance of up to $\sim$5\,kpc for some stars, the stars are slightly out of the plane.
+This is not inconsistent with a disc-satellite interaction.
+\citet{gomez;et-al_2013} find that a significant fraction of the total energy goes into vertical perturbations.
+While the mean vertical distance $\langle{}Z\rangle$ in their simulations are near zero, this is an average of disc particles at all plane heights, and the dispersions around $\langle{}Z\rangle$ are very large (F.
+G{\'o}mez, private communication, 2013).
+Moreover, \citet{gomez;et-al_2013} were only able to reliably track particles up to $|Z| \approx 1.4$\,kpc due to a finite number of particles in each cell volume.
+
+% who is the perturber?
+If the Aquarius group is a feature of a disc-satellite interaction, the perturber must have a mass on the order of a large globular cluster or a dSph to produce the residual pattern in orbital energy and angular momentum.
+The Sagittarius dSph galaxy is an obvious candidate, but $\omega$-Centurai is also a possible perturber.
+We identify {C222531-145437} as tidal debris from $\omega$-Centurai, and its location overlaps with the apocenter of $\omega$-Centurai's orbit.
+In addition, its velocity matches precisely with simulations of tidal debris by \citet{majewski;et-al_2012}.
+Thus, perhaps $\omega$-Centurai disrupted galactic stars as it passed through the plane, adding to any other oscillating modes rippling through the disc, resulting in what we now observe as the Aquarius co-moving group.
 
@@
 \label{sec:conclusions}
-\# Conclusions
+We have presented a detailed chemical and dynamical analysis for five members of the recently discovered Aquarius co-moving group from data taken with the MIKE spectrograph on the Magellan Clay telescope.
+Hereafter we solely refer to the discovery as a co-moving group instead of a stellar stream because we find no evidence that the group is the result of a tidally disrupted globular cluster (or dSph satellite), contrary to the claim by \citet{wylie-de-boer;et-al_2012}.
+These conclusions are drawn from a sample size comprising of a third of all the known Aquarius members.
+The main conclusions are as follows:
+
+\begin{itemize}
+\item The Aquarius feature is not chemically coherent. A wide spread in metallicities is observed, with [Fe/H] ranging from $-0.63$ to $-1.63$\,dex in just five candidates.
+
+\item The co-moving group shows an alpha enhancement of ${[\alpha/{\rm Fe}] = +0.40}$\,dex (+0.38 if the peculiar star {C222531-145437} is excluded), contrary to that typically observed in stars within dSph galaxies.
+
+\item Aquarius members are enhanced in [Na/Fe] and [Ni/Fe] to levels typically observed in either the thick disc or globular clusters.
+These levels of [Na/Fe], [Ni/Fe] enhancement are not observed in stars from dSph galaxies either.
+Thus, on the basis of sodium, nickel, and $\alpha$-element abundances, it is unlikely the Aquarius co-moving group is the result of a tidally disrupted dSph galaxy.
+
+\item We find no evidence for Aquarius group resulting from a disrupted classical globular cluster.
+No Na-O anti-correlation is observed.
+Two candidates have slightly enhanced levels of sodium with respect to iron.
+However, we reiterate that our [Na/Fe] abundance ratios appear +0.10\,dex systematically higher than measurements made by other groups in both our program or standard stars.
+If the candidates were \textit{known globular cluster members}, they would be classified as belonging to either the primordial component, or at most, the base of the intermediate group.
+
+\item We find a positive Mg-Al relationship, also contrary to observations made in globular cluster stars.
+Given that a Na-O anti-correlation is not evident, it is perhaps unsurprising that no Mg-Al relationship is present since this chemical pattern is less prominent in globular clusters.
+
+\item If the Aquarius co-moving group is the result of a disrupted globular cluster, then the large metallicity variation within the stream severely limits the number of possible parent hosts, and both the extreme and intermediate component of the Na-O anti-correlation have still not been observed.
+
+\item One of our candidates, {C222531-145437}, has chemistry that is clearly distinct from the other Aquarius members.
+It is enhanced in light elements and shows a strong heavy element enhancement, most notably in barium where {[Ba/Fe] = 0.68}\,dex.
+We exclude the possibility that the abundance variations have resulted from an unseen AGB companion through comparisons of expected light and heavy $s$-process yields for AGB stars with a range of stellar masses at the same metallicity as {C222531-145437}.
+The position and velocity of {C222531-145437} coincides precisely where simulations by \citet{majewski;et-al_2012} suggest large amounts of $\omega$-Centurai tidal debris should be found, and its chemistry is precisely consistent with that of RGB stars in the core of $\omega$-Centurai \citep{marino;et-al_2011}.
+The data suggests that {C222531-145437} is a rare tidal debris member of the globular cluster $\omega$-Centurai.
+With a {[Fe/H]$ = -1.22$}\,dex, it matches the mean metallicity of a known sub-population within $\omega$-Centurai, and removing C222531-145437 from the Aquarius sample does not resolve the aforementioned metallicity spread.
+
+\item While no evidence exists for an accreted origin, and the Aquarius members are indistinguishable from thick disc/halo stars, we hypothesise the co-moving group is the result from a disc-satellite interaction.
+We see no coherent pattern in the $u$--$v$ plane from Monte-Carlo simulations, but the orbital energies and angular momenta for Aquarius candidates qualitatively reproduces patterns predicted by \citet{gomez;et-al_2012}.
+This is consistent with a minor merger in the Milky Way occurring perhaps up to a few Gyr ago.
+Given the location and velocity of the Aquarius group, and the identification of {C222531-145437} as a disrupted $\omega$-Centurai star, it is plausible that the Milky Way-$\omega$Cen interaction sufficiently perturbed outer disc/halo stars to produce what we now observe as the Aquarius group.
+\end{itemize}
+
+It is clear that not all kinematic substructures are tidal tails of disrupted satellites, and that the structure of the Milky Way is indeed complex.
+While we find no chemical evidence that the Aquarius group is a tidal tail from a disrupted satellite, we propose the members are galactic in origin, and the co-moving group is a result of a disc-satellite interaction.
+Thus, while the Aquarius group has not been accreted onto the galaxy, it certainly adds to the rich level of substructure within the Milky Way.
+
+\acknowledgements
+We are indebted to David Nidever and Steven Majewski for kindly replicating a plot from their $\omega$-Centurai simulations (Figure \ref{fig:omega-cen-tidal-debris} in this text) which helped to place {C222531-145437} in context of the cluster's tidal debris.
+A.R.C.
+acknowledges the financial support through the Australian Research Council Laureate Fellowship LF0992131, and from the Australian Prime Minister's Endeavour Award Research Fellowship which has facilitated his research at MIT.
+This publication makes use of data products from the Two Micron All Sky Survey, which is a joint project of the University of Massachusetts and the Infrared Processing and Analysis Center/California Institute of Technology, funded by the National Aeronautics and Space Administration and the National Science Foundation.
+\\
 

### 2013-05-16 2012-aqs/figures/plot-alpha-fe.py

@@ -13,6 +13,10 @@ e_Ca_Fe = []
 Ti_Fe = []
 e_Ti_Fe = []
 
+Mg_Fe = []
+e_Mg_Fe = []
+
+
 Fe_H = []
 e_Fe_H = []
 
@@ -31,6 +35,10 @@ for filename in data_files:
 	idx = list(data[:,0]).index('Ti') + 1 # Get Ti II because it's more reliable
 	_Ti_Fe, _e_Ti_Fe = data[idx, 2:]
 
+
+	idx = list(data[:,0]).index('Mg')
+	_Mg_Fe, _e_Mg_Fe = data[idx, 2:]
+
 	idx = list(data[:, 0]).index('Fe')
 	_Fe_H, _e_Fe_H = data[idx, 1], data[idx, -1]
 
@@ -39,6 +47,9 @@ for filename in data_files:
 
 	Ca_Fe.append(_Ca_Fe)
 	e_Ca_Fe.append(_e_Ca_Fe)
+
+	Mg_Fe.append(_Mg_Fe)
+	e_Mg_Fe.append(_e_Mg_Fe)
 
 	Ti_Fe.append(_Ti_Fe)
 	e_Ti_Fe.append(_e_Ti_Fe)
@@ -52,25 +63,47 @@ for filename in data_files:
 Si_Fe = map(float, [value.replace('$', '').replace('\\', '').replace('nodata', 'nan') for value in Si_Fe])
 Ca_Fe = map(float, [value.replace('$', '').replace('\\', '').replace('nodata', 'nan') for value in Ca_Fe])
 Ti_Fe = map(float, [value.replace('$', '').replace('\\', '').replace('nodata', 'nan') for value in Ti_Fe])
+Mg_Fe = map(float, [value.replace('$', '').replace('\\', '').replace('nodata', 'nan') for value in Mg_Fe])
 Fe_H = map(float, [value.replace('$', '').replace('\\', '').replace('nodata', 'nan') for value in Fe_H])
 
 e_Si_Fe = map(float, [value.replace('$', '').replace('\\', '').replace('nodata', 'nan') for value in e_Si_Fe])
[…]

### 2013-05-16 2012-aqs/figures/plot-fe-peak.py

@@ -80,14 +80,15 @@ print "[Cr/Fe] = ", Cr_Fe
 print "[Mn/Fe] = ", Mn_Fe
 
 # Bounds
-xlim = np.array([-1.8, -0.4])
-ylim_Sc = [-0.8, 0.8]
-ylim_V = [-0.8, 0.8]
-ylim_Cr = [-0.8, 0.8]
-ylim_Mn = [-0.8, 0.8]
+xlim = np.array([-1.7, -0.5])
+ylim_Sc = [-0.1, 0.4]
+ylim_V = [-0.1, 0.5]
+ylim_Cr = [-0.5, 0.1]
+ylim_Mn = [-0.7, 0.6]
 
 
 fig = plt.figure()
+fig.subplots_adjust(left=0.10,bottom=0.10,right=0.95, top=0.95, hspace=0.0)
 
 # Scantium
 ax = fig.add_subplot(411)
@@ -107,6 +108,8 @@ ax.set_xlim(xlim)
 ax.set_ylim(ylim_Sc)
 ax.set_xticklabels([])
 ax.set_ylabel('[Sc/Fe]')
+ax.set_yticks([0.0, 0.2, 0.4])
+
 
 
 # Vandium
@@ -127,6 +130,7 @@ ax.set_xlim(xlim)
 ax.set_ylim(ylim_V)
 ax.set_xticklabels([])
 ax.set_ylabel('[V/Fe]')
+ax.set_yticks([0.0, 0.2, 0.4])
 
 
 # Cromium
@@ -148,6 +152,7 @@ ax.set_ylim(ylim_Cr)
 
 ax.set_ylabel('[Cr/Fe]')
 ax.set_xlabel('[Fe/H]')
+ax.set_yticks([-0.4, -0.2, 0.0])
 
 
 # Manganese
@@ -169,6 +174,8 @@ ax.set_ylim(ylim_Mn)
 
 ax.set_ylabel('[Mn/Fe]')
 ax.set_xlabel('[Fe/H]')
+ax.set_yticks([-0.60, -0.4, -0.20, 0.0, 0.2, 0.4])
+
 
 
 

### 2013-05-16 2012-aqs/figures/plot-mg-al.py

@@ -202,7 +202,7 @@ ax.scatter(Mg_Fe, Al_Fe, marker='o', color='k', s=30)
 ax.errorbar(Mg_Fe, Al_Fe, xerr=e_Mg_Fe, yerr=e_Al_Fe, fmt=None, ecolor='k')
 
 # C2225316
-ax.text(0.50 + 0.03, 0.68 + 0.05, 'C2225316-14437', color='k', fontsize=10)
+ax.text(0.50 + 0.05, 0.68 + 0.07, 'C2225316-14437', color='k', fontsize=10)
 
 x = np.array([np.min(Mg_Fe), np.max(Mg_Fe)])
 #ax.plot(x, m * x + c, 'k-')

### 2013-05-16 2012-aqs/figures/plot-na-ni.py

@@ -225,3 +225,61 @@ ax.set_ylim(-0.25, 0.25)
 
 plt.savefig('na-ni.pdf')
 
+
+# Get globular cluster data
+ngc_288_na, ngc_288_ni = np.loadtxt('shetrone_keane_2000_ngc288.txt', comments='#', usecols=(6,13, ), unpack=True)
+ngc_362_na, ngc_362_ni = np.loadtxt('shetrone_keane_2000_ngc362.txt', comments='#', usecols=(6, 13, ), unpack=True)
+m3_na, m3_ni = np.loadtxt('sneden_2004_m3.txt', comments='#', usecols=(2, 14, ), unpack=True)
+
+# Get the dSph data
+_fornax_na, _fornax_na_err, _fornax_ni, _fornax_ni_err = np.loadtxt('letarte_2010_fornax.data', delimiter=';', usecols=(2, 3, 29, 30, ), dtype=str, unpack=True)
+
+fornax_na = []
+fornax_ni = []
+
+for a, b, c, d in zip(_fornax_na, _fornax_na_err, _fornax_ni, _fornax_ni_err):
+
+	a, b, c, d = [item.strip() for item in (a,b,c,d)]
+
+	if len(a) > 0 and len(c) > 0:
+		a, c = map(float, (a, c))
+		fornax_na.append(a)
+		fornax_ni.append(c)
+
+
+# Draw globular cluster data and dsph
+fig = plt.figure()
+ax = fig.add_subplot(111)
+
+# Draw globular clusters
+ax.scatter(ngc_288_na, ngc_288_ni, marker='^', edgecolor='b', facecolor='none', label='NGC 288 (Shetrone & Keane, 2000)')
+ax.scatter(ngc_362_na, ngc_362_ni, marker='o', edgecolor='k', facecolor='none', label='NGC 362 (Shetrone & Keane, 2000)')
+ax.scatter(m3_na, m3_ni, marker='s', edgecolor='r', facecolor='none', label='M3 (Sneden et al. 2004)')
+
+# Draw fornax
+ax.scatter(fornax_na, fornax_ni, marker='v', edgecolor='g', facecolor='none', label='Fornax (Letarte et al. 2010)')
+
+# Draw halo (Nissen & Schuster)
[…]

### 2013-05-16 2012-aqs/figures/plot-na-o.py

@@ -4,8 +4,8 @@ import matplotlib.pyplot as plt
 # ; ;mag;mag;mag;mag;km/s;km/s;K;[Sun];[Sun];[Sun];[Sun]; ;[Sun];[Sun];"h:m:s";"d:m:s"
 
 
-caretta_cluster, caretta_Fe_I, caretta_e_Fe_I, caretta_O_Fe, caretta_e_O_Fe, caretta_l_Na_Fe, caretta_Na_Fe, caretta_e_Na_Fe = np.loadtxt('caretta-et-al-2009-O-Na.txt', skiprows=67, delimiter=';', \
-														usecols=(0, 9, 10, 11, 12, 13, 14, 15, ), unpack=True, dtype=str)
+caretta_Fe_I, caretta_e_Fe_I, caretta_O_Fe, caretta_e_O_Fe, caretta_l_Na_Fe, caretta_Na_Fe, caretta_e_Na_Fe = np.loadtxt('caretta-et-al-2009-O-Na.txt', skiprows=67, delimiter=';', \
+														usecols=(9, 10, 11, 12, 13, 14, 15, ), unpack=True, dtype=str)
 
 # Replace invalid items with np.nans
 
@@ -25,7 +25,8 @@ def clean(array):
 	return np.array(new_array)
 
 
-caretta_cluster, caretta_Fe_I, caretta_e_Fe_I, caretta_O_Fe, caretta_e_O_Fe, caretta_Na_Fe, caretta_e_Na_Fe = map(clean, [caretta_cluster, caretta_Fe_I, caretta_e_Fe_I, caretta_O_Fe, caretta_e_O_Fe, caretta_Na_Fe, caretta_e_Na_Fe])
+caretta_Fe_I, caretta_e_Fe_I, caretta_O_Fe, caretta_e_O_Fe, caretta_Na_Fe, caretta_e_Na_Fe = map(clean, [caretta_Fe_I, caretta_e_Fe_I, caretta_O_Fe, caretta_e_O_Fe, caretta_Na_Fe, caretta_e_Na_Fe])
+
 
 
 # Get Na and O from files:
@@ -109,206 +110,3 @@ ax2.set_ylim(-0.6, 1.1)
 plt.draw()
 plt.savefig('aquarius-o-na.pdf')
 plt.savefig('aquarius-o-na.eps')
-
-
-
-# Subplots
-
-
-# Mg-Al in sub-plots
-
-
[…]

### 2013-05-16 2012-aqs/figures/plot-spectra.py

@@ -4,11 +4,11 @@ import numpy as np
 from specutils import Spectrum1D
 
 accompaning_texts = [
-        "C2225316-14437\t4325 / 1.26 / $-$1.26",
-        "C2306265-085103\t4170 / 0.85 / $-$1.17",
-        "J221821-183424\t4590 / 0.90 / $-$1.61",
-        "J223504-152834\t4590 / 2.15 / $-$0.68",
-        "J22381-104126\t5140 / 2.96 / $-$1.45"
+        "C2225316-14437\t\t\t4365 / 1.25 / $-$1.22",
+        "C2306265-085103\t\t\t4225 / 0.85 / $-$1.13",
+        "J221821-183424\t\t\t4630 / 0.88 / $-$1.58",
+        "J223504-152834\t\t\t4650 / 2.16 / $-$0.63",
+        "J223811-104126\t\t\t5190 / 2.93 / $-$1.63"
         ]
 
 spectrum_filenames = ['c2225316-14437_rest.fits', 'c2306265-085103_rest.fits', 'j221821-183424_rest.fits', 'j223504-152834_rest.fits', 'j22381-104126_rest.fits']
@@ -27,10 +27,11 @@ accompaning_texts = accompaning_texts_
 
 xlims = [6540, 6600]
 #xlims = [6150, 6160]
+xlims = [4835, 4885]
 
 text_x_offset = 2
 text_y_offset = 0.10
-text_fontsize = 9
+text_fontsize = 11
 
 label_fontsize = 10
 
@@ -44,9 +45,10 @@ for i, (accompaning_text, spectrum_filename) in enumerate(zip(accompaning_texts,
     spectrum = Spectrum1D.load(spectrum_filename)
 
     ax.plot(spectrum.disp, spectrum.flux + i, 'k')
-    lhs_text, rhs_text = accompaning_text.split('\t')
-    ax.text(xlims[0] + text_x_offset, text_y_offset + 1 + i, lhs_text, fontsize=text_fontsize, horizontalalignment='left')
-    ax.text(xlims[1] - text_x_offset, text_y_offset + 1 + i, rhs_text, fontsize=text_fontsize, horizontalalignment='right')
+    #lhs_text, rhs_text = accompaning_text.split('\t')
+    #ax.text(xlims[0] + text_x_offset, text_y_offset + 1 + i, lhs_text, fontsize=text_fontsize, horizontalalignment='left')
[…]

### 2013-05-16 2012-aqs/figures/plot-vhel-feh.py

@@ -5,6 +5,7 @@ Vhels = [-156.4, -221.1, -159.5, -169.7, -235.7]
 Verrs = [0.1, 0.1, 0.1, 0.1, 0.1]
 
 Fe_H = [-1.26, -1.17, -1.61, -0.68, -1.45]
+Fe_H = [-1.22, -1.13, -1.63, -0.63, -1.58]
 Fe_H_errs = [0.01, 0.01, 0.01, 0.02, 0.01]
 Fe_H_errs = [0.10, 0.1, 0.1, 0.1, 0.1]
 

### 2013-06-19 2012-oss-hrs/make-plots.py
Updated OSS HRS abundances and plot script

@@ -1,0 +1,530 @@
+import os
+import numpy as np
+
+import matplotlib.pyplot as plt
+
+def load_abundances(filename, minimum_uncertainty=0.05):
+    """Loads the [X/H] and [X/Fe] abundance ratios and uncertainties
+    for a single star from the filename provided."""
+
+    if not os.path.exists(filename):
+        raise IOError("file does not exist (%s)" % (filename, ))
+
+    if not np.isfinite(minimum_uncertainty) or minimum_uncertainty < 0:
+        raise ValueError("minimum uncertainty must be a positive finite value")
+
+    abundances = {}
+    uncertainties = {}
+    limits = {}
+
+    with open(filename, "r") as fp:
+        content = fp.read().split("\n")
+
+        for line in content:
+            if line.startswith("#") or line.startswith("%") or len(line) == 0: continue
+
+            line = line.replace("&", "").replace("_nodata", "nan").rstrip("\\").rstrip("&")
+            if line.split()[0] == "C":
+                element, transition = ("C", "(CH)", )
+                n_lines, log_eps, sigma_eps, x_on_h, x_on_fe, uncertainty = line.split()[2:]
+                limit = False
+
+            else:
+                line_split = line.split()
+                if len(line_split) > 6:
+                    element, transition, n_lines, log_eps, sigma_eps, x_on_h, x_on_fe, uncertainty = line_split
+                    limit = False
+
+                else:
+                    element, transition, n_lines, log_eps, x_on_h, x_on_fe = line_split
+                    uncertainty, sigma_eps = ('0.15', 'nan', )
+                    limit = True
+
+                    if not "<" in log_eps:
+
+                        print filename, element
+                        assert "<" in log_eps
+
+
+            # Clean up transition
+            transition = transition.strip('_textsc{}')
+            species_repr = '%s %s' % (element, transition, )
+
[…]

### 2013-08-13 2012-oss-hrs/draft-oss.tex
Up to date

--- 2012-08-04 2012-oss/draft-oss.tex
@@
 
+\usepackage{amssymb} % for resolution symbol
 \usepackage{verbatim} % for comment blocks
@@
 
-\shorttitle{First HRS Analysis on the Orphan Stream}
+\shorttitle{The First High-Resolution Spectroscopic Analysis of the Orphan Stream}
 \shortauthors{Casey et al}
@@
 
-\title{The First High-Resolution Spectroscopic Analysis on the Orphan Stream}
+\title{Hunting the Parent of the Orphan Stream: The First High-Resolution Spectroscopic Analysis}
 
-\author{Andrew R. Casey\altaffilmark{1,2}, Stefan C. Keller\altaffilmark{1}, Frebel, Anna\altaffilmark{2}, Gary Da Costa\altaffilmark{1}, Elizabeth Maunder\altaffilmark{1}}
-\altaffiltext{1}{Research School of Astronomy \& Astrophysics, Australian National University, Mount Stromlo Observatory, via Cotter Rd, Weston, ACT 2611, Australia; \email{arcasey@mso.anu.edu.au}}
+\author{Andrew R. Casey\altaffilmark{1}, Stefan C. Keller\altaffilmark{1}, Gary Da Costa\altaffilmark{1}, Frebel, Anna\altaffilmark{2}, and Elizabeth Maunder\altaffilmark{1}}
+\altaffiltext{1}{Research School of Astronomy \& Astrophysics, Australian National University, Mount Stromlo Observatory, via Cotter Rd, Weston, ACT 2611, Australia; \email{acasey@mso.anu.edu.au}}
 \altaffiltext{2}{Massachusetts Institute of Technology, Kavli Institute for Astrophysics and Space Research,
@@
 \begin{abstract}
-test
+
+%We present the first high-resolution spectroscopic data for five Orphan Stream candidates, observed with the Magellan Inamori Kyocera Echelle (MIKE) spectrograph on the Magellan Clay telescope. 
+%The candidates were selected from the low-resolution catalog of \citet{casey;et-al_2013a}: 3 high-probability members, 1 medium- and 1 low-probability stream candidate.
+Inferred stellar parameters and chemical abundances from our data indicate the low- and medium-probability target are metal-rich field stars.
+The remaining three high-probability targets are chemically distinct from our standard field stars.
+
+%If the chemistry displayed in these stars is representative of the Orphan Stream and it's unidentified parent host, we have witnessed a unique chemical indicator that can be used to unambiguously trace the Orphan Stream throughout the Milky Way, and a `smoking gun' for the parent of the Orphan Stream.
 \end{abstract}
@@
 
-% galactic structure, accretion, build up of galaxies
-In the last decade the importance of hierarchical merging for the formation of galaxies has become unambiguously clear.
-In $\Lambda$CDM cosmology, small clusters conglomerate together to form dwarf galaxies.
-If these dwarf galaxies become sufficiently close to larger galaxies, they begin infalling and tidal forces cause a stream of stars to be left in their wake.
-These disrupted stars accrete onto the Milky Way, contributing to a significant fraction of the halo \citet{Bell;et-al_2008}.
+% Galaxy formation in the context of LambdaCDM cosmology
+%	-> Bottom-up formation
+%	-> Merging
+%	-> In situ/Accretion
+%	-> Tidal tails
 
-% how streams form
-% streams agree with lambda cdm
-% streams contribute a significant part to the halo
+In $\Lambda$CDM cosmology, structure is formed hierarchically in a bottom-up fashion.
+Small star clusters conglomerate together to form larger systems like the Milky Way.
+Many stars within our galaxy have formed in-situ \citep{ELS}, but a significant fraction has been built up by the accretion of smaller systems, particularly in the halo \citep{searle;zinn_1978}.
+As these satellite systems infall towards the Milky Way potential they are disrupted by tidal forces, causing exterior stars to be strewn in forward and trailing directions as tidal tails or `stellar streams'.
+The evidence for this hierarchical formation and ongoing accretion in the Milky Way has increased significantly over the last decade \citep{ibata;et-al_1994;belokurov;et-al_2006b}.
 
-% dominant streams have been identified by their kinematic signatures 
-  The Milky Way is the best laboratory to investigate the extent accretion plays in galaxy formation and evolution.
-Historically, the signatures of accretion events have been identified either through prominent stellar over-densities [citations needed] or by co-moving groups; numerous spatially coincident stars moving with the same velocity [citations needed].
-The kinematics of stars in streams allow us to reconstruct the orbital history of the host and place constraints on the Milky Way potential, including the shape and extent of dark matter in the Galaxy [citation needed].
+% Level of accretion in the Milky Way
+%	-> Significant fraction of the halo
+%	-> With multi-band photometry across the sky the search for these substructures has become more efficient
+%	-> Range of masses of infalling progenitors, enabling comparisons to CDM simulations, cosmology
 
-% wealth of data provided by SDSS, allowed orphan stream to be discovered independently
-With increasing all-sky survey data being made openly available, searching for stellar over-densities has become extremely efficient [cite koposov].
-Using simple color cuts in the SDSS DR5 [citation needed] data set, both \citet{Grillmair_2006} and \citet{Belokurov;et-al_2007} independently discovered the Orphan Stream as a coherent structure spanning over $60^\circ$ in the sky.
-The Orphan Stream is uniquely distinct from  other stellar streams uncovered in the halo.
-It has an extremely low surface brightness and is only $\approx2^\circ$ wide \--- which is significantly narrower than other structures found in the Field of Streams \citep{Belokurov;et-al_2006} like Sagittarius ($15^\circ$ wide; [citation needed]).
-Moreover, the Orphan Stream was aptly named by \citet{Belokurov;et-al_2007} because unlike most other streams, no associated host was found in the SDSS data set, and no existing known system has been reliably associated.
-The Orphan stream extends well past the celestial equator, outside of the SDSS footprint.
-Unfortunately the stream has a sufficiently low surface density \citet{Newberg;et-al_2010} found prevents it from being detected within the existing SuperCOSMOS survey \citep{Hambly;et-al_2001}.
-It is unlikely that this region will be adequately imaged until the SkyMapper telescope commences the Southern Sky Survey \citep{Keller;et-al_2007}.
-At least until then, it remains a orphaned stream without a parent system.
+%These discoveries have demonstrated that the Milky Way is the best laboratory to examine accretion in the context of galaxy formation and evolution.
+From the pencil-beam survey of \citet{starkenburg;et-al_2009}, they find a lower limit of 10\%  substructure for the halo.
+In contrast, \citet{bell;et-al_2008} suggest that the entire stellar halo has been formed by the accretion of smaller dwarf satellites.
+A close examination of high-resolution cosmological simulations suggests this number could exceed $>84$\%.
+More precise observational constraints await the results of large scale spectroscopic surveys.
+Irrespective of the overall fraction, it is generally accepted that a considerable amount of the halo has been built up by the disruption of smaller systems.
 
-  % Should I discuss the observational bias, e.g. that we need the smaller ones to really start to pinpoint down the MW potential?
+% Deason
+% Sharma & Johnson
+% Schlaufman
 
-% orphan stream is aptly named and is unique to all other streams. the parent remains lost, although a lot of work has been put in to associating the stream
-In the absence of observational data to identify an undiscovered parent host, there has been much effort on associating the Orphan Stream with an existing Milky Way satellite [citations needed].
-Given the XX and XX, it is likely the parent host is a dwarf spheroidal galaxy [citations needed], although \citet{Grillmair_2006} predicts the host to be completely disrupted.
-In the search for an associated system, \citet{Belokurov;et-al_2007} first demonstrated that the Complex A, Ruprecht 106, and Palomar 1 all lie on the same great circle path of the Orphan stream, speculating some association between the four.
+% The Orphan Stream and its properties
+%	-> Detected in the SDSS data set
+%	-> Extent on sky
+%	-> Stream width
+%	-> Implications from the stream width and extent: dark matter dominated, old, metal-poor, velocity dispersion, progenitor mass.
 
-% Let's deal with the Complex A controversy first
-A detailed analysis on the Orphan Stream orbit is required to examine any potential associations. Kinematics and/or proper motions are required to adequately determine an orbit.
-\citet{Belokurov;et-al_2007} listed admittedly two tenuous kinematic observations along the stream, one of which it later appears was erroneous.
+Amongst the known substructures in the halo, the Orphan Stream is particularly interesting.
+\citet{grillmair_2006} and \citet{Belokurov;et-al_2006} independently discovered the stream, spanning over $60^\circ$ in the sky from Ursa Major in the north to near Sextans in the south.
+The stream has properties that are unique from other halo substructures.
+It has an extremely low surface brightness ranging from 32-40\,mag arcsec$^{-2}$, and a full width half-mass of $\sim$700\,pc at a distance of $\sim$20\,kpc, which is approximately $\approx2^\circ$ when projected on the sky \citep{belokurov;et-al_2007,grillmair_2006}.
+The cross-section and luminosity of the stream are directly related to the mass and velocity dispersion of the parent satellite \citep{johnston_1998}.
+The Orphan Stream width is significantly broader than every known globular cluster tidal tail \citep{odenkirchen;et-al_2003,grillmair_johnson_2006,grillmair_dionatos_2006a,grillmair_dionatos_2006b} and larger than the tidal diameter of all known globular clusters \citep{harris}.
+As \citet{grillmair_2006} notes, if the cross-section of the stream is circular, then in a simple logarithmic potential with $v_c = 220$\,km s$^{-1}$ -- a reasonable first-order approximation -- the expected random velocities of stars would be required to be $\Delta{E} > 20$\,km s$^{-1}$ in order to produce the stream width.
+Such a velocity dispersion is significantly larger than the expected random motions of stars that have been weakly stripped from a globular cluster, implying that the Orphan Stream's progenitor mass must be much larger than a classical globular cluster.
+Photometry indicates the stream is metal-poor, implying that negligible star formation has occurred since infall began several gigayears ago.
+For a stream of this length to remain structurally coherent over such a long timescale, the progenitor is also likely to be dark-matter dominated.
+In their discovery papers, \citet{grillmair_2006} and \citet{belokurov;et-al_2007} concluded that the likely parent of the Orphan Stream is a low-luminosity dwarf spheroidal galaxy.
 
-% talk about fellhauer
+% Observational efforts
+%	-> Belokurov 2007
+%	-> Newberg's work on BHB stars
+%	-> Distances, velocities, strong distance and velocity gradient
+%	-> Casey 2013a metallicities, velocities
 
-Using these measurements \--- the best, and only at the time \--- and assuming Complex A and the Orphan Stream shared the same orbit, \citet{Jin;Lynden-Bell_2007} found a representative orbit to match observations.
-Unfortunately their predicted heliocentric velocities that were inconsistent with \citet{Fellhaur;et-al_2007} and later observations by \citet{Newberg;et-al_2010}.
-Moreover, distances estimated by \citet{Jin;Lynden-Bell_2007} were under-predicted by a factor of three.
+\citet{newberg;et-al_2010} were able to map the distance and velocity of the stream across the length of the SDSS catalogue using blue horizontal branch (BHB) and F-turnoff stars.
+They found the stream distance to vary between 19-47\,kpc.
+This extended further than the 20-32\,kpc measurements made by \citet{belokurov;et-al_2007}.
+\citet{newberg;et-al_2010} note an increase in the density of the Orphan Stream near the celestial equator $(l, b) = (253\,^\circ, 49\,^\circ)$, proposing the progenitor may be close to this position.
+The authors attempted to extend their trace of the stream using the southern SuperCOSMOS data set \citep{supercosmos}, but to no avail; the stream's surface brightness is too low.
+It is still unclear whether the stream extends deep into the southern sky.
+\citet{newberg;et-al_2010} note an increase in surface brightness near the celestial equator, but given the stream is closest at the equator \citep{belokurov;et-al_2007}, an increase in stream density may be expected given a constant absolute magnitude.
+Nevertheless, with SDSS photometry and radial velocities from the SEGUE catalog, \citet{newberg;et-al_2010} were able to derive a prograde orbit with an eccentricity, apogalacticon and perigalacticon of $e = 0.7$, 90\,kpc and 16.4\,kpc respectively.
+If this orbit is accurate, the ability to trace a stellar stream out to 90\,kpc would make a powerful probe for measuring the galactic potential.
+From their simulations, \citet{newberg;et-al_2010} find a halo and disk mass of $M(R < 60\,{\rm kpc}) = 2.6 \times 10^{11} M_\odot$, $\sim$60\% lower than that found by \citet{xue;et-al_2008} and \citet{koposov;et-al_2008}, and slightly lower than the virial mass of $7 \times 10^{11} M_\odot$ found by \citet{sales;et-al_2008}.
 
-In contrast to these simulations, \citet{Sales;et-al_2007} using a X found an orbit which reproduced the velocities, positions and characteristics of the stream, but found no evidence of association with Complex A, or UMaII.
-Their findings indicate that the parent system is likely to be dark matter dominated, and have similar characteristics to some of the Milky Way dwarfs already known (XX, XX and XX).
-Only self-gravitating systems dominated by dark matter can survive sufficiently long enough to form a stream stretching $\approx55^\circ$ across the sky.
+Metallicities derived from SEGUE low-resolution spectra confirm photometric estimates indicating that the stream is metal-poor.
+A mean metallicity of [Fe/H]$ = -2.1 \pm 0.1$\,dex is found from BHB stars, with a range extending from $-$1.3 to $\sim-$3\,dex \citep{newberg;et-al_2010}.
+If F-turnoff stars from that sample are included, the metallicity distribution function extends more metal-rich from $\sim-$3 to $-$0.5\,dex.
+Since BHB stars only form from low metallicity populations, it is not unexpected for BHB stars to be more metal-poor than F-type giants.
+% Sesar work
 
-% talk more about Sales
+The situation is further complicated by halo interlopers and small number statistics, so the full shape of the metallicity distribution function (MDF) is unknown.
+To this end, \citet{casey;et-al_2013a} observed low-resolution spectroscopy for hundreds of stars towards the stream at the celestial equator.
+The authors targeted the less numerous K-giants \citep[a mere 1.3 red giant branch stars expected per square degree]{sales;et-al_2008,morrison_1993} and found a very weak detection of the stream from kinematics alone.
+Using wide selections in velocity, distance, proper motions, metallicities, and surface gravity, they identified highly likely Orphan Stream giants.
+The velocity dispersion of their candidates is within the observational errors, suggesting the stream is kinematically cold along the line-of-sight.
+Like \citet{newberg;et-al_2010} (and now additionally confirmed by \citet{sesar;et-al_2013}), they also found an extended range in metallicities of their nine most probable candidates: two stars below $\leq-2.70$ and two stars near $-1.17$\,dex all of which are consistent with stream membership.
+The mean metallicity of their sample was [Fe/H]$ = -1.63 \pm 0.19$\,dex, with a wide dispersion of $\sigma({\rm [Fe/H]}) = 0.56$\,dex.
+It appears the Orphan Stream may have an extremely wide range in metallicity, consistent with the stochastic chemical enrichment typically observed in dwarf spheroidal (dSph) galaxies \citep{mateo_1998}.
 
-As the SEGUE [acronym needed] data became available, \citet{Newberg;et-al_2010} employed a detailed selection method in order to identify BHB stars in the SDSS data sample.
-% blah blah blah
+% Possible associations
+%	-> There are a number of globular clusters associated along the great circle path.
+%	-> Belokurov speculated some association between UM II and Complex A, suggesting the progenitor is a dSph and the clusters have been flung off
+%	-> Complex A models by Jin & Lynden-Bell, but they incorrectly predict velocities and under-estimate distances by a factor of three.
+%	-> Ursa Major II simulations do not match
+%	-> Rule out all known satellites except for Segue 1
 
-% perhaps mention Sales et al explaining how low surface brightness streams cant be found without spectroscopic surveys
+As the name suggests, the Orphan Stream's parent satellite has yet to be found.
+In an effort to identify a progenitor, a number of systems have been identified along the great circle path of the stream as being plausibly associated with the Orphan Stream.
+These include the linear Complex A H\,\textsc{i} clouds, as well as the globular clusters Palomar 1, Apr 2, Terzan 7 and Ruprecht 106.
+The low-luminosity dwarf satellites Segue 1 and Ursa Major II also lie along the great circle, although Segue 1 was considered an extended globular cluster until recently \citep{norris;et-al_2010,simon;et-al_2011}.
+It is worth noting that streams do not often reside along a great circle from the observer's perspective, nor are they expected to do so.
+\citet{belokurov;et-al_2007} first noted a possible association between the Orphan Stream, Ursa Major II and Complex A.
+To that end \citet{Jin;Lynden-Bell_2007} and \citet{fellhaur;et-al_2007} explored the possible association between the Orphan Stream with Complex A and Ursa Major II, respectively.
+In the best-fitting Complex A model, the predicted heliocentric velocities did not match those found by \citet{belokurov;et-al_2007}, or later observations by \citet{newberg;et-al_2010}.
+The expected distances were also under-estimated by a factor of $\sim{}3$ compared to observations, making the association with Complex A tenuous at best.
+In the Ursa Major II scenario, the stream's on-sky position was required to exactly overlap with a previous wrap, a somewhat contrived and unlikely scenario.
+\citet{newberg;et-al_2010} found that the Ursa Major II-Orphan Stream connection was also not compelling as the stream kinematics were not consistent with the Ursa Major II model.
 
-More recently, \citet{Keller;et-al_2012} targeted FGK giants on the Southern end of the SDSS footprint.
-As the stream crosses the celestial equator it is closest to us and the surface brightness peaks, making it an ideal place to identify stream members.
-Using inclusive SDSS cuts they targeted hundreds of stars with medium resolution spectroscopy.
-By identifying likely stream giants based on kinematics and surface gravity estimates, they identified X likely Orphan Stream giants.
-In this paper we present a detailed chemical analysis on five of those members using high resolution spectroscopic data from the Magellan Clay telescope.
-Details regarding the observations are outlined in Section \ref{sec:observations}, followed by X.
+Simulations involving the Complex A and Ursa Major II associations introduced an a priori assumption that the object (e.g.
+Ursa Major II or Complex A) was related to the Orphan Stream, and consequently found an orbit to match.
+In contrast, \citet{sales;et-al_2008} approached the problem by fitting an orbit to a single wrap of the data, without assuming a parent satellite a priori.
+Their $N$-body simulations were inconsistent with either a Complex A or Ursa Major II association with the Orphan Stream.
+Instead, the authors favour a progenitor with a luminosity $L \sim 2.3 \times 10^4 L_\odot$ or an absolute magnitude $M_r \sim -6.4$, consistent with the observation by \citet{belokurov;et-al_2007} of $M_r \sim -6.7$.
+Simulations by \citet{sales;et-al_2008} suggest the progenitor may be similar to the present day `classical' Milky Way dwarfs like Carina, Draco, Leo II or Sculptor, but would be very close to fully disrupted over infall, which they suggest has occurred over the last 5.3 Gyr.
+Time of infall is a critical inference.
+Longer timescales produce streams that are too wide and diffuse, whereas shorter timescales do not reproduce the $\sim{}$60\,$^\circ$ stream length.
+The degeneracies between these simulation parameters are important to note, but in any case there are robust conclusions that can be drawn irrespective of the degeneracies.
+For example, \citet{sales;et-al_2008} note that a globular cluster has a central density too high ($\sim10^{12} M_\odot$\,kpc$^{-3}$) to be fully disrupted along their Orphan Stream orbit within a Hubble time.
+Given this constraint and the lower limit on luminosity ($L > 2\times10^5 L_\odot$), a globular cluster progenitor seems unlikely from their models.
 
-\section{Observations}
-We present high resolution follow-up observations using the Magellan Inamori Kyocera Echelle (MIKE) spectrograph.
+In addition to the work by \citet{sales;et-al_2008}, $N$-body simulations by \citet{newberg;et-al_2010} exclude all known halo globular clusters as possible progenitors.
+They conclude with the postulation of two possible scenarios: the progenitor is an undiscovered satellite located between $(l, b) = (250^\circ, 50^\circ)$ and $(270^\circ, 40^\circ)$, or Segue 1 is the parent system.
 
-% details of the resolution that MIKE provides, etc
+Segue 1 is an extremely dark-matter dominated system.
+In fact, kinematics suggest it is so dark-matter dominated that it has become a prime focus for the detection of direct dark-matter annihilation experiments \citep{dm_dominated}.
 
-\subsection{Target Selection}
-% this is double-up
-The Orphan Stream has an extremely low surface brightness [citations needed] of XX, and there is a well-described distance gradient along the Orphan stream \citep{Belokurov;et-al_2007,Newberg;et-al_2010}.
-Therefore the best place to identify stream members within the SDSS sky coverage is near the celestial equator where the stream is closest to us, right at the edge of the SDSS footprint.
+Segue 1 itself has an extremely wide range in metallicities, varying from [Fe/H] = X to Y dex.
 
-\subsection{High Resolution Observations}
+% Segue 1 association?
+%	-> Segue 1 is a dark-matter dominated system
+%	-> Velocities and positions
+%	-> Does it match the expected L, M values from constraints on models
+%	-> Extremely wide metallicity range.
 
-\begin{deluxetable*}{lccccccc}
+% NGC 2419
+
+Given the extended apogalaction of 90\,kpc in the stream orbit found by \citet{newberg;et-al_2010}, \citet{bruns;kroupa_2011} reasoned the stream may be the tidal tail of the massive globular cluster NGC 2419.
+This system is the most distant (90 kpc) -- yet one of the most massive (R) and luminous ($M$) -- globular clusters known.
+It is unlike any other globular cluster in the Milky Way.
+It's shear distance makes spectroscopic observations challenging, but work by \citet{cohen;et-al} have confirmed photometric observations \citet{photometry_for_ngc2419} that the system is metal-poor ([Fe/H] $= -2?$), and identified a remarkable anti-correlation between Mg and K.
+The level of magnesium depletion ([Mg/Fe] $= -0.40$\,dex??) is not seen anywhere else in the galaxy, neither has the enhanced potassium enrichment ([K/Fe] = $1.5$\,dex??) at the converse end of this peculiar Mg-K anti-correlation.
+This is also a difficult pattern to explain with from a nucleosynthesis perspective (A.
+Karakas, in preparation).
+If NGC 2419 is the parent of the Orphan Stream then this unprecedented chemical signature ought to exist in disrupted stream members as an example of chemical tagging \citep[e.g.
+see][]{freeman;bland-hawthorn_2002,de_silva;et-al_2007,wylie-de-boer;et-al_2010,majewski;et-al_2012}.
+
+% For nice formatting, the LaTeX table is here:
+\begin{deluxetable*}{lccccccccccc}
 \tablecolumns{2}
 \tabletypesize{\scriptsize}
-\tablecaption{Observed Targets\label{tab:observed-targets}}
+\tablecaption{Observations\label{tab:observations}}
 \tablehead{
-	\colhead{Star} &
+	\colhead{Object} &
 	\colhead{$\alpha$} &
 	\colhead{$\delta$} &
-	\colhead{Air mass} &
+	\colhead{$g$} &
+	\colhead{UT Date} &
+	\colhead{UT Time} &
+	\colhead{Airmass} &
+	\colhead{Exp. Time} &
 	\colhead{S/N\tablenotemark{a}} &
-	\colhead{$V_{\mbox{helio}}$} &
-	\colhead{Comment} \\
- & (J2000) & (J2000) & & (px$^{-1}$) & (km s$^{-1}$) &
+	\colhead{$V_{\mbox{hel}}$} &
+	\colhead{$V_{\mbox{err}}$} \\
+ & (J2000) & (J2000) & (mags) & & & (") & (secs) & (px$^{-1}$) & (km s$^{-1}$) & (km s$^{-1}$)
 }
 \startdata
-HD 136316 & 15 22 17.2 & $-$53 14 13.9 & 1.118 & 335 & $-38.2 \pm 1.1$       & \\
-HD 141531 & 15 49 16.9 &\phs09 36 42.5 & 1.309 & 280 & $\phn\phn2.6 \pm 1.0$ & \\
-HD 142948 & 16 00 01.6 & $-$53 51 04.1 & 1.107 & 271 & $\phn30.3 \pm 0.9$    & \\
-HD 41667  & 06 05 03.7 & $-$32 59 36.8 & 1.005 & 272 & $297.8 \pm 1.7$       & \\
-HD 44007  & 06 18 48.6 & $-$14 50 44.2 & 1.033 & 239 & $163.4 \pm 1.3$       & \\
-HD 47536  & 06 37 47.7 & $-$32 20 20.1 & 1.002 & 257 & $\phn78.9 \pm 1.2$    & \\
-HD 76932  & 08 58 44.2 & $-$16 07 54.2 & 1.158 & 289 & $119.2 \pm 1.2$       & \\
-HD 84903  & 09 47 19.3 & $-$41 27 04.9 & 1.260 & 294 & $\phn77.7 \pm 1.4$    & \\
-HD 59984  & 07 32 05.7 & $-$08 52 56.1 & 1.111 & 402 & $\phn55.7 \pm 0.5$    & \\
-HD 60060  & 07 29 59.6 & $-$52 39 04.3 & 1.127 & 414 & $\phn25.6 \pm 1.1$    & \\
-HD 60228  & 07 30 30.8 & $-$54 23 58.6 & 1.139 & 338 & $\phn48.6 \pm 1.7$    & \\
-OSS 1     & 10 46 50.6 & $-$00 13 17.9 & 1.363 &  48 & $218.2 \pm 1.7$       & \\
-OSS 2     & 10 47 17.8 &\phs00 25 06.9 & 1.995 &  59 & $222.2 \pm 1.3$       & \\
-OSS 3     & 10 47 30.3 & $-$00 01 22.6 & 1.156 &  49 & $226.4 \pm 1.3$       & \\
-OSS 4     & 10 49 08.3 &\phs00 01 59.3 & 1.881 &  48 & $227.5 \pm 2.1$       & Poor seeing\\
-OSS 5     & 10 50 33.7 &\phs00 12 18.3 & 1.295 &  31 & $249.0 \pm 2.6$       & Poor seeing \\
-HR 6141   & 16 30 12.3 & $-$25 06 52.0 & 1.003 & 406 & \nodata               & Telluric
+HD 41667		& 06:05:03.7	& $-$32:59:36.8	& 		& 2011-03-13	& 23:40:52	& 1.005	& 90			& 272	& 297.8 	& 1.7 \\
+HD 44007		& 06:18:48.6	& $-$14:50:44.2	& 		& 2011-03-13	& 23:52:18	& 1.033	& 30 			& 239	& 163.4 	& 1.3 \\
+HD 76932		& 08:58:44.2	& $-$16:07:54.2	& 		& 2011-03-14	& 00:16:47	& 1.158	& 23 			& 289	& 119.2 	& 1.2 \\
+HD 122563		& 14:02:31.8	& $+$09:41:09.9	\\
+HD 136316		& 15:22:17.2	& $-$53:14:13.9	& 		& 2011-03-14	& 09:37:26	& 1.118	& 3060 		& 335	& -38.2	& 1.1 \\
+HD 141531		& 15:49:16.9	& $+$09:36:42.5	& 		& 2011-03-14	& 09:52:00	& 1.309	& 9180 		& 280	& 2.6 	& 1.0 \\
+HD 142948		& 16:00:01.6	& $-$53:51:04.1	& 		& 2011-03-14	& 09:45:12	& 1.107	& 3060 		& 271	& 30.3 	& 0.9 \\
+OSS-3 (1)		& 10:46:50.6	& $-$00:13:17.9	& 17.33 	& 2011-03-14	& 01:51:07	& 1.363	&4$\times$2500	& 48	& 217.9	& 0.9 \\ 
+OSS-6 (2)		& 10:47:17.8	& $+$00:25:06.9	& 16.09 	& 2011-03-14	& 00:25:37	& 1.995	&3$\times$1600	& 59	& 221.2	& 0.4 \\ 
+OSS-8 (3)		& 10:47:30.3	& $-$00:01:22.6	& 17.25	& 2011-03-14	& 04:44:04	& 1.160	&5$\times$1900	& 49	& 225.9	& 0.5 \\ 
+OSS-14 (4)		& 10:49:08.3	& $+$00:01:59.3	& 16.27 	& 2011-03-15	& 00:32:17	& 1.881	&4$\times$1400	& 48 	& 225.1	& 0.3 \\ 
+OSS-18 (5)		& 10:50:33.7	& $+$00:12:18.3	& 17.82 	& 2011-03-15	& 02:12:46	& 1.295	&4$\times$2100	& 31 	& 247.8	& 0.6
 \enddata
-\tablenotetext{a}{S/N measured at 6000 \AA{} for each target.}
+\tablenotetext{a}{S/N measured at 600\,nm for each target.}
 \end{deluxetable*}
 
-% HDs 59984, 76932, 136316, 84903, 44007, 142948
-% OS 2,4,5,6,8 (file name convention) here is OS 1,2,3,4,5
+% What we report here.
+In this study we present an analysis of high-resolution spectroscopic observations for five Orphan Stream candidates and seven well-studied field stars with similar stellar parameters for comparison.
+The observations and data reduction are outlined in Section \ref{sec:observations}.
+In Section \ref{sec:analysis} we describe the details of our curve-of-growth analysis and spectral synthesis approach to infer stellar parameters and chemical abundances.
+We discuss the results of our analysis in Section \ref{sec:discussion}, including the implications for association between the Orphan Stream and the two currently alleged stream progenitors: Segue 1 and NGC 2419.
+Finally, we conclude in Section \ref{sec:conclusions} with a summary of our findings.
 
-\subsection{Data Reduction}
+\section{Observations and Data Reduction}
+\label{sec:observations}
 
-The data were reduced using the latest version of the MIKE pipeline outlined in \citet{Kelson;2003}.
-For comparison we also reduced our HD 59984 spectra using standard methods in \textsc{IRAF} and found no noteworthy difference between the reduced products.
-Individual frames for each object were co-added before analysis.
-We carefully normalised every echelle order using cubic splines.
-Overlapping normalised orders on each CCD were stitched together, such that a continuous normalised spectra from each CCD results.
-No telluric corrections were made, as they do not affect the spectral regions we are interested in.
+%HD 140283	& 15:43:02.3	& $-$10:56:03.0	&		& 2010-08-06	& 23:02:19	& 1.056	& \nodata		& \nodata			& \nodata \\
+%l = 250.21, b = 49.46, Vrad = 222.5 +/- 0.9 km/s, Orphan_Lambda = 19.11, Orphan_Beta = -0.48, Vgsr = 83.96 +/- 0.9 km/s
+%l = 249.63, b = 49.99, Vrad = 225.7 +/- 0.4 km/s, Orphan_Lambda = 18.54, Orphan_Beta = -0.16, Vgsr = 89.23 +/- 0.4 km/s
+%l = 250.17, b = 49.71, Vrad = 230.9 +/- 0.9 km/s, Orphan_Lambda = 18.98, Orphan_Beta = -0.27, Vgsr = 93.15 +/- 0.9 km/s
+%l = 250.56, b = 50.04, Vrad = 229.7 +/- 0.3 km/s, Orphan_Lambda = 19.06, Orphan_Beta = +0.14, Vgsr = 92.65 +/- 0.3 km/s
+%l = 250.76, b = 50.41, Vrad = 252.6 +/- 0.6 km/s, Orphan_Lambda = 19.02, Orphan_Beta = +0.53
 
-\subsection{Radial Velocities}
+Five Orphan Stream candidates and six well-studied standard stars were observed in March 2011 using the 1\arcsec slit.
+An additional metal-poor standard star, HD 122563, was observed in similar conditions in X 20YY.
+This slit configuration provides a spectral resolution of $\mathcal{R} = 22,000$ in the blue arm and $\mathcal{R} = 28,000$ in the red arm.
+According to \citet{casey;et-al_2013a}, tjree of the selected stream candidates have high a probability of membership, one was classified with medium probability, and another with a low probability of membership.
+Initially we planned to observe many more high-priority targets.
+However, after our last exposure of OSS 18, inclement weather forced us to relinquish the remainder of our observing time, losing almost half of the run.
+The details of our observations are tabulated in Table \ref{tab:observations}.
+A minimum of 10 exposures of each calibration type (biases, flat fields, and diffuse flats) were observed in the afternoon of each day, with additional flat-field and Th-Ar arc lamp exposures performed throughout the night to ensure an accurate wavelength calibration.
 
-We measured radial velocities for every target by cross-correlating each normalised red  spectrum with a synthetic template.
-Our synthetic template was generated in \textsc{MOOG} using an $\alpha$ element enhanced \citet{Castelli-Kurucz;2004} model atmospheres with $T_{eff} = 4500$ K, $\log{g} = 2.5$, [Fe/H] = -1.5 and no convective overshoot.
-The line list of \citet{Kirby;et-al_2008} was employed to generate spectra between $845$ nm $< \Lambda < 870$ nm.
-Both the blue and red normalised frames were shifted to rest before measuring equivalent widths.
-A number of radial velocity and halo standards were observed during this program, and our heliocentric velocities agree excellently with literature values (Table \ref{tab:observed-targets}).
+% observed using the Magellan Inamori Kyocera Echelle (MIKE) spectrograph on the Magellan Clay telescope.
+These targets are candidate K-giants identified to be likely stream members on the basis of position, velocity, metallicity and surface gravity from the low-resolution spectroscopic study of \citet{casey;et-al_2013a}.
 
-\subsection{Line List}
-\label{sec:line-list}
+The data were reduced using the CarPy pipeline written by D.
+Kelson\footnote{D.
+Kelson website}.
+Every reduced echelle aperture was carefully normalised using cubic splines with defined knot spacing.
+Extracted apertures were stacked together and weighted by their flux counts to provide a continuous normalised spectrum for each observation.
 
-% table
+\section{Analysis}
+\label{sec:analysis}
+Each normalised, stitched spectrum was cross-correlated against a synthetic template to measure radial velocities.
+This was performed using a Python implementation of the \citet{Tonry;Davis_1978} method.
+The wavelength region employed was from $845 \leq \lambda \leq 870$\,nm, and a K2V metal-poor giant synthetic spectrum was used as the rest template.
+Heliocentric corrections have been applied to the our radial velocity measurements, and the results are shown in Table \ref{tab:observations}.
 
-\subsection{Line Measurements}
-An automatic routine has been developed to determine the local continuum and robustly measure the equivalent width of an absorption line.
-First, we estimate the local continuum surrounding the rest wavelength (Table \ref{tab:line-list}) by iteratively fitting a low order polynomial to $10$ \AA{} either side of the rest wavelength, and clipping only extreme outliers.
-This process does not determine the final local continuum; all we need is an initial estimate.
+% line by line velocities? velocities consistent with Casey 2013a?
 
-Given a rest wavelength and our local continuum estimate, a Gaussian absorption profile is fitted in an iterative process.
-During this process we have three free parameters: the rest wavelength, the FWHM of the Gaussian profile, and the flux level at the profile trough.
-The initial value for the minimum flux is taken as the flux level at rest wavelength, and 0.1 \AA{} is used as the initial FWHM for the Gaussian profile.
-The actual FWHM of our final profile and the subsequent equivalent width measured is largely independent of the initial FWHM provided; only an initial guess is required to decrease computational cost.
-The difference between our calculated profile and the actual flux is calculated at each iteration, and we use least-squares minimisation to arrive at the best fitting line profile.
+Equivalent widths (EWs) for all atomic transitions listed in Table \ref{tab:atomic-data} were measured using the automatic profile fitting algorithm described in \citet{casey;et-al_2013b}.
+Although this technique is accurate and robust against blended lines and strong changes in local continuum \citep{frebel;et-al_2013a,casey;et-al_2013b,keller;et-al_2013,frebel;et-al_2013c}, every fitted profile was visually inspected for quality.
+Spurious or false-positive measurements were removed, and of order $\sim$5 interactive EW measurements were necessary for each spectrum.
 
-Once this process is complete, we use the measured line FWHM in order to decide where the true continuum surrounding the line should start.
-Again, we iteratively fit a low order polynomial to the surrounding $10$ \AA{} \--- excluding $3\sigma$ of our measured profile\footnote{Recall that FWHM $\approx 2.355\sigma$} \--- but in this step the outlier clipping is more involved: after each iteration we identify flux points as outliers if $>2.5-\sigma$, and we identify sequentially occurring outlier points as probable minima of an absorption line.
-At each group of outlier points we attempt to fit a Gaussian absorption profile in the same process described above.
-If a profile is successfully fitted, then we exclude all points within $3-\sigma$ of the detected line from any more continuum determination.
-In this process, absorption lines are automatically detected and excluded, leaving only the continuum.
+Given the range in metallicities for the Orphan Stream candidates (see Section \ref{sec:analysis-metallicity}), this meant that only fourteen Fe\,\textsc{i} and four Fe\,\textsc{ii} transitions in our line list were measurable for our most metal-poor candidate, OSS 4.
+With so few lines available, minute changes in stellar parameters will result in significant variations to the abundance trends during excitation and ionization equilibria, and a poor overall fit to the model.
+At this point we opted to supplement our line list with additional transitions from \citet{roederer;et-al_2010}.
+Each added transition was inspected in our most metal-rich candidate (OSS 1) to ensure that it was not blended with other features.
+The minimum number of usable Fe\,\textsc{i} and Fe\,\textsc{ii} transitions for any star increased to X and Y, respectively.
 
-When multiple lines are measured from our line list there are stringent quality constraints put in place to eliminate false positive measurements: the final rest wavelength must be within <$10$ \AA{} to the initial guess, the FWHM of each line should be reasonable with respect to all other lines, and the $\chi^2$ difference between the final profile and the spectrum must be reasonable.
-The $\chi^2$ constraint helps identify measurements where nearby lines are blended.
+\input{equivalent_widths_table_portion.tex}
 
-For spectra which has been perfectly normalised and has high S/N, the method described here will always find the continuum to be unity.
-For low S/N objects, or where the normalisation is sub-par, our technique robustly determines the true local continuum.
-We must stress that this process is not 'blind'; the profile and local continuum determination for every measured line has been carefully inspected by the authors.
-All false positive measurements were discarded during the inspection process, and no lines required manual re-measurement.
+% stellar parameter determination..
+\subsection{Stellar Parameters}
+We have employed the 1D plane-parallel model atmospheres of \citet{castelli;kurucz_2004} to infer stellar parameters from the EWs of atomic absorption profiles.
+These $\alpha$-enhanced models assume that absorption lines form under local thermal equilibrium and ignore convective overshoot as well as center-to-limb variations.
+We have interpolated within a grid of these model atmospheres following the prescription in \citet{casey;et-al_2013b}.
 
-%We have verified the accuracy of our automatically determined equivalent widths in two ways:
-We have verified the accuracy of our automatically determined equivalent widths both internally and externally.
-For an internal comparison we have compared careful hand measurements of the equivalent widths against those determined automatically for two stars: the bright metal-rich dwarf HD 59984, and our metal-poor giant target OSS 4.
-The results of this comparison are shown in Figures \ref{fig:hd59984-ew-comparison} and \ref{fig:oss4-ew-comparison}, and demonstrate our measurement code at varying S/N.
-HD59984 has a S/N $\approx XX$ px$^{-1}$ at 600 nm, and the difference between equivalent width measurement methods is negligible.
-Our target star OSS 4 has a much more modest S/N of $\approx50$ px$^{-1}$ at 600 nm, and the two techniques still agree excellently.
+\subsubsection{Effective Temperature, $T_{\rm eff}$}
+Effective temperatures for all stars have been found by excitation balance of neutral Fe lines.
+Transitions with reduced equivalent widths (REW), $\log(\textrm{EW}/\lambda) > -4.5$, were excluded to avoid using lines near the flat region of the curve-of-growth.
+Linear fits to the data with gradients less than $|10^{-3}|$\,dex eV$^{-1}$ were considered to be converged, which equated to a minimum temperature step size of $\sim$5\,K.
+Since all EW measurements had been visually inspected, we generally identified almost no outlier measurements during the excitation or ionization balance analyses.
+The most number of Fe\,\textsc{i} outliers ($>3\sigma$) removed while determining the effective temperature was three.
 
-These internal comparisons validate the effectiveness of the local continuum fitting within a wide bracket of S/N ratios.
-To verify our equivalent width accuracy to an external source, we have automatically measured equivalent widths for the metal-poor sub-giant HD140283 and compared our measurements to those of \citet{Norris;et-al_1996}.
+% Photometric temperatures for standard stars?
 
-The comparison is shown in Figure \ref{fig:norris-ew-comparison}, and the two techniques agree excellently.
-There is a systematic offset of XX m\AA{} and random scatter of YY m\AA{} between the two techniques.
-We are confident that our automatic measurement technique can reliably determine equivalent width measurements that are consistent with the literature, over a wide range of evolutionary phases, metallicities and signal quality.
+% Effective temperatures for standard stars
+The effective temperatures for our standard stars is in excellent agreement with those presented in the literature.
+The largest discrepancy occurs HD 122563, a cool metal-poor giant.
+For metal-poor giants, temperature found through excitation balance are known to produce systematically cooler temperatures than those deduced from the infra-red flux method.
+Similarly, the resultant surface gravities are also lower \citep[see][for a discussion]{frebel;et-al_2013a}.
+We have chosen to remain consistent with the excitation balance method and accept the systematically cooler temperature of 4360\,K.
+In contrast, for HD 142948 we find a 307\,K hotter temperature than that found by \citet{gratton;et-al_2000}.
+The reason for this discrepancy is unclear.
+Excluding these two stars we find the mean offset in temperatures is 24\,K.
 
-\subsection{Stellar Parameters}
+%On the basis of spectral typing, we confirm the high probability stream candidates OSS 6 and 14 are indeed K-giants, as indicated by \citet{casey;et-al_2013a}.
+The final high probability candidate, OSS 8, is slightly hotter than expected: a G??
+giant.
+The remaining lower probability candidates have an effective temperature $\sim$5200, indicating they are F-turnoff giants.
 
-\subsubsection{Effective Temperature}
+\subsubsection{Microturbulence, $\xi$}
+Microturbulence is necessary in 1D model atmospheres to represent large scale, 3D turbulent motions.
+The correct microturbulence will ensure that weak and strong transitions yield the same abundance.
+We have solved for the microturbulence by demanding a zero-trend in REW and line abundance for all Fe\,\textsc{i} lines.
+This process is iteratively conducted while solving for effective temperature to provide a full-model fit to the data.
+The resultant trend line slope between REW and abundance is typically $<|0.001|$\,dex, although in some cases this could not be achieved without increasing the microturbulence precision to three decimals.
+The largest slope in any star is $-0.004$\,dex.
+Plots of excitation potential, reduced equivalent width and abundance for the program stars are shown in Figure \ref{fig:ionization-excitation-balance}.
 
-\subsubsection{Surface Gravity}
+% Figure for ionization and excitation balance for standard stars
+% Include slope, uncertainty, correlation coefficient and probability.
 
-\subsection{Uncertainty Analysis}
+\subsubsection{Surface Gravity, $\log{g}$}
+We have inferred surface gravities through the ionization balance of neutral and singly ionized Fe lines.
+This process was iteratively conducted while solving for other stellar parameters.
+All standard and program stars are RGB stars.
+By comparison of surface gravities in published surface gravities for our standard stars, [DOES IT??] it appears our surface gravities are $\sim{}-$0.20\,dex lower than that found by other authors \citep{gratton;et-al_2000,fulbright_2000,nissen;schuster_2000;gratton_sneden_1991}.
+The source of this discrepancy is unclear, yet the difference remains well within the 1$\sigma$ uncertainties for either study.
 
-\begin{deluxetable}{lcccccccccl}
-\tablecolumns{1}
+\begin{deluxetable*}{lcccccccccccccl}[h!]
+\tablecolumns{2}
 \tabletypesize{\scriptsize}
@@
 \tablehead{
-& \multicolumn{4}{c}{This work}  &
-& \multicolumn{4}{c}{Literature} & \\
-  \cline{2-5} \cline{7-10} \\
-  \colhead{Star} &
-  \colhead{$T_{\mbox{eff}}$} &
- \colhead{$\log{(g)}$} &
+	\colhead{Object\tablenotemark{a}} &
+	\colhead{$T_{\rm eff}$} &
+	\colhead{$\log{g}$} &
+	\colhead{$\xi$} &
 	\colhead{[Fe/H]} & 
-	\colhead{$v_t$} 
-	&&
-	\colhead{$T_{\mbox{eff}}$} &
-	\colhead{$\log{(g)}$} &
+	\colhead{$T_{\rm eff}$} &
+	\colhead{$\log{g}$} &
+	\colhead{$\xi$} &
 	\colhead{[Fe/H]} &
-	\colhead{$v_t$} &
-	\colhead{Reference} \\
- & [K] & [dex] & [dex] & [km s$^{-1}$] 
-&& [K] & [dex] & [dex] & [km s$^{-1}$] & 
+	\colhead{Literature Source} \\
+	& (K) & (dex) & (km\,s$^{-1}$) & (dex) & (K) & (dex) & (km\,s$^{-1}$) & (dex) 
 }
 \startdata
-HD 136316 & $4370$ & $1.00$ & $-1.99$ & $1.95$ 
-         && $4469$ & $1.29$ & $-1.74$ & $1.90$ & \citet{Gratton;et-al_2000} \\
-HD 141531 & $4330$ & $0.90$ & $-1.74$ & $1.80$ 
-         && $4335$ & $1.11$ & $-1.62$ & $1.50$ & \citet{Gratton;et-al_2000} \\
-HD 142948 & $4870$ & $2.20$ & $-0.78$ & $1.45$ 
-         && $4713$ & $2.17$ & $-0.77$ & $1.38$ & \citet{Gratton;et-al_2000} \\
-HD 41667  & $4600$ & $1.70$ & $-1.23$ & $1.50$  
-         && $4605$ & $1.88$ & $-1.16$ & $1.44$ & \citet{Gratton;et-al_2000} \\
-HD 44007  & $4800$ & $1.80$ & $-1.77$ & $1.55$ 
-         && $4850$ & $2.00$ & $-1.71$ & $2.20$ & \citet{Fulbright_2000} \\
-HD 47536  & & & & 
-         &&\nodata &\nodata & \nodata &\nodata & \\
-HD 76932  & & & & 
-         && $5900$ & $4.20$ & $-0.70$ & $1.25$ & \citet{Fulbright_2000} \\
-HD 84903  & & & & 
-         && $4500$ & $0.80$ & $-2.60$ & $2.00$ & \citet{Francois_1996} \\
-HD 59984  & & & & 
-         && & & & & Binary system.\\
-HD 60060  & & & & 
-         &&\nodata &\nodata & \nodata &\nodata & \\
-HD 60228  & & & & 
-         &&\nodata &\nodata & \nodata &\nodata & \\
-OSS 1     & 5040 & 2.80 & -1.22 & 1.40 && & & & & \\
-OSS 2     & 4550 & 0.80 & -1.78 & 1.85 && & & & & \\
-OSS 3     & 4780 & 1.55 & -1.79 & 1.70 && & & & & \\
-OSS 4     & 4580 & 0.80 & -2.75 & 2.05 && & & & & \\
-OSS 5     & 5250 & 3.00 & -0.80 & 1.85 && & & & & 
+\\
+\multicolumn{10}{c}{Standard Stars} \\
+\hline
+HD 41667		& 4643	& 1.54	& 1.81	& $-$1.18 & 4605 & 1.88 & 1.44 & $-$1.16 & \citet{gratton;et-al_2000} 		\\ % +38
+HD 44007		& 4820	& 1.66	& 1.70	& $-$1.69 & 4850 & 2.00 & 2.20 & $-$1.71 & \citet{fulbright_2000} 		\\ % -30
+HD 76932		& 5835	& 3.93	& 1.42	& $-$0.95 & 5849 & 4.11 & \nodata & $-$0.88 & \citet{nissen;et-al_2000} 	\\ % -14
+HD 122563		& 4358	& 0.14	& 2.77	& $-$2.90 & \\
+HD 136316		& 4347	& 0.44	& 2.15	& $-$1.93 & 4414 & 0.94 & 1.70 & $-$1.90 & \citet{gratton_sneden_1991} 	\\ % -41
+HD 141531		& 4373	& 0.52	& 2.05	& $-$1.65 & 4280 & 0.70 & 1.60 & $-$1.68 & \citet{shetrone_1996} 		\\ % +93
+HD 142948		& 5050	& 2.39	& 1.83	& $-$0.64 & 4713 & 2.17 & 1.38 & $-$0.77 & \citet{gratton;et-al_2000} 		\\ % +337
+
+\\
+\multicolumn{10}{c}{Orphan Stream Candidates} \\
+\hline
+OSS 3 (L)		& 5225	& 3.16	& 1.10	& $-$0.86 & \nodata	& \nodata	& \nodata	& $-$1.31	& \citet{casey;et-al_2013a}\\
+OSS 6 (H)		& 4554	& 0.70	& 2.00	& $-$1.75 & \nodata	& \nodata	& \nodata	& $-$1.84	& \citet{casey;et-al_2013a}\\
+OSS 8 (H)		& 4880	& 1.71	& 1.86	& $-$1.62 & \nodata	& \nodata	& \nodata	& $-$1.62	& \citet{casey;et-al_2013a}\\
+OSS 14 (H)		& 4675	& 1.00	& 2.53	& $-$2.66 & \nodata	& \nodata	& \nodata	& $-$2.70	& \citet{casey;et-al_2013a}\\
+OSS 18 (M)		& 5205	& 2.91	& 1.88	& $-$0.62 & \nodata	& \nodata	& \nodata	& $-$0.90	& \citet{casey;et-al_2013a}
+\enddata
+\tablenotetext{a}{Probability of membership (Low, Medium, High) listed for Orphan Stream candidates as defined by \citet{casey;et-al_2013a}.}
+\end{deluxetable*}
+% Mean temperatures are +68 K hotter than literature (not HD122563)
+% Excluding HD 142948 (and HD122563) gives a mean of +9 K hotter than literature.
+
+% Metallicities are +0.01 dex higher than literature for all standards (not HD122563)
+
+% Surface gravities are a mean -0.22 dex lower than literature (not HD122563)
+
+% isochrone fits?
+
+\subsubsection{Metallicity, $[M/H]$}
+\label{sec:analysis-metallicity}
+
+The final stage of the stellar parameter determination is to derive the total metallicity, as it has the least dependence on stellar parameters.
+For these analyses we adopt the mean [Fe\,\textsc{i}/H] abundance as the overall metallicity [M/Fe].
+A difference of ${|\textrm{[M/H]} - \langle\textrm{[Fe\,\textsc{i}/H]}\rangle| \leq 0.01}$\,dex was considered an acceptable fit to the data.
+
+Excluding HD 122563, the mean difference in metallicity for all of our standard stars when compared to literature is a negligible $-$0.02\,dex with a standard deviation of 0.05\,dex.
+The largest difference is 0.08\,dex for HD 41667 \citep{gratton;et-al_2000}, still easily within either study's 1$\sigma$ uncertainties.
+Therefore, we are reasonably confident with our stellar parameters and metallicities inferred from our high-resolution spectroscopic data.
+
+The difference in metallicities between the values we derive from high-resolution spectroscopy and those found by \citet{casey;et-al_2013a} from low-resolution spectroscopy are noticeable.
+For the high and medium probability targets (OSS 6, 8, 14 and 18) the agreement is reasonable: the values in this study are up to $+0.15$\,dex more metal-rich.
+We note that the uncertainties adopted in \citet{casey;et-al_2013a} are of the order $\pm0.3$\,dex.
+The largest difference between this study and that of \citet{casey;et-al_2013a} is in the lowest probability target (OSS 3), where we find a metallicity that is $+$0.45\,dex higher.
+For our high-resolution spectra, it is somewhat expected that the high and medium targets would have metallicities more agreeable with the low-resolution measurements.
+This is because the low-resolution metallicities of \citet{casey;et-al_2013a} are dependent on the assumption that these stars are at the distance of the Orphan Stream, approximately $\sim$20\,kpc away.
+Stars that showed any inconsistency with this assumption were marked with a lower probability of membership.
+
+\subsection{Stellar Parameter Uncertainties}
+
+\begin{deluxetable}{lcccccccccccccl}[h!]
+\tablecolumns{1}
+\tabletypesize{\scriptsize}
+\tablecaption{Uncorrelated Uncertainties in Stellar Parameters\label{tab:stellar-parameter-uncertainties}}
+\tablehead{
+	\colhead{Object} &
+	\colhead{$\sigma(T_{\rm eff})$} &
+	\colhead{$\sigma(\log{g})$} &
+	\colhead{$\sigma(\xi)$} \\
+	& (K) & (dex) & (km\,s$^{-1}$)
+}
+\startdata
+HD 41667	&	47 &	0.08 &	0.05 \\
+HD 44007	&	51 &	0.08 &	0.17 \\
+HD 76932	&	61 &	0.10 &	0.14 \\
+HD 122563	&	15 &	0.01 &	0.07 \\
+HD 136316	&	34 &	0.02 &	0.05 \\
+HD 141531	&	40 &	0.03 &	0.05 \\
+HD 142948	&	62 &	0.12 & 0.09 \\
+OSS 3 (L)	&	73 &	0.08 &	0.11 \\
+OSS 6 (H)	&	39 & 	0.04 &	0.15 \\
+OSS 8 (H)	&	74 & 	0.17 &	0.23 \\
+OSS 14 (H)	&	51 & 	0.05 &	0.13 \\
+OSS 18 (M)	&	135& 	0.15 &	0.28
 \enddata
@@
 
-\begin{deluxetable}{lccccccccccccccccc}
-\tablecolumns{18}
-\tablewidth{\textwidth}
+\subsection{Chemical Abundances}
+Chemical abundances are described following standard nomenclature, and comparisons are made against the Sun using the solar chemical composition described in \citet{asplund;et-al_2009}.
+
+\subsubsection{Carbon}
+Carbon has been measured from synthesizing spectra around the 431.3\,nm and 432.3\,nm CH band heads.
+The abundances inferred from these two syntheses were within 0.05\,dex.
+Nevertheless, have adopted a conservative uncertainty of $\pm$0.15\,dex in these measurements.
+The mid-point of these two measurements is listed in Table \ref{tab:chemical-abundances}.
+A portion of the synthetic and observed spectrum for HD XXXXXX and OSS 14 around the 431\,nm region is shown in Figure \ref{fig:carbon-synth}.
+We note that only the 432.3\,nm region was synthesized for OSS 18, as significant line blanketing was present in the bluer band-head and we deemed the 432.3\,nm region to yield a more precise determination of C-abundance than the 431.3\,nm portion.
+The [C/Fe] and [Fe/H] abundances for all standard and program stars is shown in Figure \ref{fig:carbon-fe}.
+
+\subsubsection{Sodium, Aluminium and Potassium}
+Sodium, aluminium and potassium are odd-Z elements that are primarily produced in massive stars through neutron capture reactions.
+Although our line list includes three clean, unblended Na lines, not all were detectable in the Orphan Stream candidates.
+Generally only one line was available for the program stars, and in most cases all were measurable in the standard stars.
+When multiple lines are present, the standard deviation is quite low: a maximum of $\sigma($[Na/Fe])$ = 0.06$\,dex is observed for {HD 41667}.
+
+Since the Orphan stream stars are reasonably metal-poor, generally only one Al line was available for measurement.
+In these circumstances we adopt an uncertainty of $\pm0.1$\,dex.
+In some cases -- particularly for the metal-poor stars -- no aluminium lines were detectable and an upper limit was derived from synthesis of the strongest Al line.
+In contrast, at least one K line was detected in every standard and program star.
+These lines at 766 and 769\,nm are very strong, but fall directly between a strong telluric band head.
+Often both lines were detected, but one was dominated by the Earth's atmospheric absorption.
+In these cases we simply rejected the contaminated line and used the single, unaffected K line.
+
+\subsubsection{$\alpha$-elements (O, Mg, Ti, Si, Ca)}
+
+Generally, the Orphan Stream candidates have lower $\alpha$-element abundances compared to iron than their halo counterparts.
+The situation is a little ambiguous for [O/Fe] compared to other $\alpha$-elements.
+We have employed the forbidden lines at 630 and 636\,nm to measure Oxygen abundances in our stars.
+Given the weakness of these lines, Oxygen was immeasurable in all of the Orphan stream candidates.
+In place of abundances, upper limits have been determined from spectral synthesis of the region.
+Our synthesis line list includes the Ni\,\textsc{i} feature hidden within the 630\,nm absorption profile \citep{allende-prieto;et-al_2001}.
+In the case of OSS 18, the forbidden oxygen region was sufficiently dominated by telluric absorption such that we deemed a robust upper limit to be indeterminable.
+
+The [Mg/Fe] abundance ratios for the Orphan Stream stars are noticeably lower than any of the other $\alpha$-elements.
+In fact, the mean [$\alpha$/Fe] abundances are largely driven by [Mg/Fe].
+Figure \ref{fig:alpha-fe} shows the $\alpha$-element abundances with respect to iron for all stream and halo targets.
+Ti \textsc{i} and Ti \textsc{ii} behave similarly to one another in each star, with the neutral species having slightly lower abundances.
+[Ca/Fe] is marginally lower in the stream candidates than their halo counterparts.
+
+\begin{figure}[h]
+	\includegraphics[width=\columnwidth]{./alpha-Fe.pdf}
+	\caption{$\alpha$-element abundance ratios with respect to Fe for standard halo (red) stars and Orphan Stream candidates (blue).}
+	\label{fig:alpha-fe}
+\end{figure}
+
+\subsubsection{Fe-peak elements (V-Zn)}
+
+The Fe-peak elements (V-Zn, $Z = 23$ to 30) are produced in supernova and generally trend in lockstep with Fe abundance.
+Most of our Fe-peak abundances show a near-zero trend with [Fe/H] (Figure \ref{fig:fe-peak}) with the exception of Cu.
+Only upper limits are available for our most metal-poor standard and Orphan stream star, but their limits extend the trend of decreasing [Cu/Fe] with [Fe/H].
+Chromium and Manganese are slightly depleted with respect to [Fe/H] and the other Fe-peak elements, and they also show a subtle positive trend with [Fe/H].
+
+The line-to-line scatter in each abundance ratio is quite small, on the order of 0.05\,dex.
+For [Co/Fe] we find a slightly larger scatter, up to $\sim$0.25\,dex in OSS 14.
+The fitted absorption profiles were of good quality and there was no reason to discard one measurement over another, so all abundances were kept and we accepted the larger uncertainty.
+
+\begin{figure}[h]
+	\includegraphics[width=\columnwidth]{./fe-peak.pdf}
+	\caption{Fe-peak (V-Zn) element abundance ratios for standard field stars and Orphan Stream candidates. Color scheme is the same employed for Figure \ref{fig:alpha-fe}.}
+	\label{fig:fe-peak}
+\end{figure}
+
+\subsubsection{Neutron-capture elements (Sr-Eu)}
+
+\begin{longtable*}{lcrcrrcclcrcrrc}
+\caption{\\ Chemical Abundances\label{tab:chemical-abundances}} \tabularnewline
+\cline{1-15}
+Species & $N$ & $\log\epsilon(X)$ & $\sigma_\epsilon$ & [X/H] & [X/Fe] & $\sigma$ && 
+Species & $N$ & $\log\epsilon(X)$ & $\sigma_\epsilon$ & [X/H] & [X/Fe] & $\sigma$ \tabularnewline
+\cline{1-15} \tabularnewline
+% This works.
+\endhead
+\hline
+\multicolumn{15}{r}{Continued..}
+\endfoot
+\hline
+\endlastfoot
+
+\\
+\multicolumn{7}{c}{\textbf{HD 41667}} & \colhead{} & \multicolumn{7}{c}{\textbf{HD 44007}} \\
+\cline{1-7} \cline{9-15}
+
+   C (CH)       &   2 &    6.95 &    0.20 & $-$1.48 & $-$0.24 &    0.20 &&
+   C (CH)       &   2 &    6.73 &    0.20 & $-$1.70 & $-$0.01 &    0.20 \\
+   O \textsc{I} &   1 &    7.82 &    0.00 & $-$0.87 &    0.37 &    0.00 &&
+   O \textsc{I} &   1 &    7.48 &    0.00 & $-$1.21 &    0.48 &    0.00 \\
+  Na \textsc{I} &   3 &    4.93 &    0.10 & $-$1.31 & $-$0.07 &    0.06 &&
+  Na \textsc{I} &   1 &    4.58 &    0.00 & $-$1.66 &    0.03 &    0.00 \\
+  Mg \textsc{I} &   8 &    6.73 &    0.23 & $-$0.87 &    0.37 &    0.08 &&
+  Mg \textsc{I} &   6 &    6.35 &    0.13 & $-$1.25 &    0.44 &    0.05 \\
+  Al \textsc{I} &   4 &    5.25 &    0.10 & $-$1.20 &    0.04 &    0.05 &&
+  Al \textsc{I} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
+  Si \textsc{I} &   8 &    6.56 &    0.14 & $-$0.95 &    0.29 &    0.05 &&
+  Si \textsc{I} &   9 &    6.17 &    0.16 & $-$1.34 &    0.35 &    0.05 \\
+   K \textsc{I} &   2 &    4.58 &    0.00 & $-$0.46 &    0.78 &    0.00 &&
+   K \textsc{I} &   1 &    4.39 &    0.00 & $-$0.64 &    1.05 &    0.00 \\
+  Ca \textsc{I} &  19 &    5.46 &    0.07 & $-$0.88 &    0.36 &    0.01 &&
+  Ca \textsc{I} &  22 &    5.11 &    0.10 & $-$1.23 &    0.46 &    0.02 \\
+ Sc \textsc{II} &  15 &    2.06 &    0.12 & $-$1.09 &    0.14 &    0.03 &&
+ Sc \textsc{II} &  14 &    1.50 &    0.09 & $-$1.65 &    0.04 &    0.02 \\
+  Ti \textsc{I} &  26 &    3.82 &    0.18 & $-$1.13 &    0.11 &    0.04 &&
+  Ti \textsc{I} &  23 &    3.42 &    0.13 & $-$1.53 &    0.16 &    0.03 \\
+ Ti \textsc{II} &  36 &    4.18 &    0.31 & $-$0.77 &    0.47 &    0.05 &&
+ Ti \textsc{II} &  40 &    3.65 &    0.19 & $-$1.30 &    0.39 &    0.03 \\
+   V \textsc{I} &   5 &    2.83 &    0.14 & $-$1.10 &    0.14 &    0.06 &&
+   V \textsc{I} &   4 &    2.27 &    0.04 & $-$1.66 &    0.04 &    0.02 \\
+  Cr \textsc{I} &  14 &    4.22 &    0.11 & $-$1.42 & $-$0.18 &    0.03 &&
+  Cr \textsc{I} &  16 &    3.78 &    0.07 & $-$1.86 & $-$0.17 &    0.02 \\
+ Cr \textsc{II} &   3 &    4.62 &    0.12 & $-$1.02 &    0.22 &    0.07 &&
+ Cr \textsc{II} &   3 &    4.12 &    0.04 & $-$1.52 &    0.17 &    0.02 \\
+  Mn \textsc{I} &   8 &    3.98 &    0.19 & $-$1.45 & $-$0.21 &    0.07 &&
+  Mn \textsc{I} &   9 &    3.38 &    0.15 & $-$2.05 & $-$0.36 &    0.05 \\
+  Fe \textsc{I} &  75 &    6.26 &    0.13 & $-$1.24 &    0.00 &    0.01 &&
+  Fe \textsc{I} &  76 &    5.81 &    0.12 & $-$1.69 &    0.00 &    0.01 \\
+ Fe \textsc{II} &  18 &    6.26 &    0.12 & $-$1.24 &    0.00 &    0.03 &&
+ Fe \textsc{II} &  18 &    5.82 &    0.14 & $-$1.68 &    0.01 &    0.03 \\
+  Co \textsc{I} &   4 &    3.74 &    0.13 & $-$1.25 & $-$0.01 &    0.06 &&
+  Co \textsc{I} &   4 &    3.39 &    0.17 & $-$1.60 &    0.09 &    0.08 \\
+  Ni \textsc{I} &  27 &    4.97 &    0.20 & $-$1.25 & $-$0.01 &    0.04 &&
+  Ni \textsc{I} &  27 &    4.48 &    0.16 & $-$1.74 & $-$0.05 &    0.03 \\
+  Cu \textsc{I} &   1 &    2.76 &    0.00 & $-$1.43 & $-$0.19 &    0.00 &&
+  Cu \textsc{I} &   1 &    1.92 &    0.00 & $-$2.27 & $-$0.58 &    0.00 \\
+  Zn \textsc{I} &   2 &    3.35 &    0.04 & $-$1.21 &    0.03 &    0.03 &&
+  Zn \textsc{I} &   2 &    2.90 &    0.08 & $-$1.66 &    0.03 &    0.06 \\
+ Sr \textsc{II} &   1 &    1.70 &    0.00 & $-$1.17 &    0.07 &    0.00 &&
+ Sr \textsc{II} &   1 &    1.21 &    0.00 & $-$1.66 &    0.03 &    0.00 \\
+  Y \textsc{II} &   3 &    1.03 &    0.12 & $-$1.18 &    0.06 &    0.07 &&
+  Y \textsc{II} &   3 &    0.40 &    0.06 & $-$1.81 & $-$0.12 &    0.04 \\
+ Ba \textsc{II} &   2 &    0.89 &    0.05 & $-$1.30 & $-$0.06 &    0.03 &&
+ Ba \textsc{II} &   2 &    0.47 &    0.06 & $-$1.71 & $-$0.02 &    0.04 \\
+ La \textsc{II} &   2 &    0.10 &    0.03 & $-$1.00 &    0.24 &    0.02 &&
+ La \textsc{II} &   2 & $-$0.37 &    0.00 & $-$1.47 &    0.22 &    0.00 \\
+ Nd \textsc{II} &   7 &    0.48 &    0.08 & $-$0.94 &    0.30 &    0.03 &&
+ Nd \textsc{II} &   8 & $-$0.22 &    0.09 & $-$1.64 &    0.05 &    0.03 \\
+ Eu \textsc{II} &   1 & $-$0.19 &    0.00 & $-$0.71 &    0.53 &    0.00 &&
+ Eu \textsc{II} &   1 & $-$1.12 &    0.00 & $-$1.64 &    0.05 &    0.00 \\
+
+\cline{1-7} \cline{9-15} \\ \\
+\multicolumn{7}{c}{\textbf{HD 76932}} && \multicolumn{7}{c}{\textbf{HD 122563}} \\
+\cline{1-7} \cline{9-15}
+
+   C (CH)       &   2 &    7.63 &    0.20 & $-$0.79 &    0.15 &    0.20 &&
+   C (CH)       &   2 &    5.26 &    0.20 & $-$3.17 & $-$0.27 &    0.20 \\
+   O \textsc{I} &   1 &    8.33 &         &$<-$0.36 & $<$0.58 &         &&
+   O \textsc{I} &   1 &    6.15 &    0.00 & $-$2.54 &    0.36 &    0.00 \\
+  Na \textsc{I} &   3 &    5.44 &    0.04 & $-$0.80 &    0.14 &    0.02 &&
+  Na \textsc{I} &   1 & $<$3.48 &         &$<-$2.76 & $<$0.14 &         \\
+  Mg \textsc{I} &   8 &    6.95 &    0.18 & $-$0.65 &    0.30 &    0.07 &&
+  Mg \textsc{I} &   8 &    5.27 &    0.08 & $-$2.33 &    0.56 &    0.03 \\
+  Al \textsc{I} &   4 &    5.57 &    0.08 & $-$0.88 &    0.06 &    0.04 &&
+  Al \textsc{I} &   1 & $<$4.83 &         &$<-$1.62 & $<$1.28 &         \\
+  Si \textsc{I} &   9 &    6.80 &    0.18 & $-$0.71 &    0.24 &    0.06 &&
+  Si \textsc{I} &   1 &    5.23 &    0.00 & $-$2.28 &    0.62 &    0.00 \\
+   K \textsc{I} &   2 &    4.97 &    0.06 & $-$0.06 &    0.89 &    0.05 &&
+   K \textsc{I} &   1 &    2.76 &    0.00 & $-$2.27 &    0.63 &    0.00 \\
+  Ca \textsc{I} &  24 &    5.70 &    0.10 & $-$0.64 &    0.30 &    0.02 &&
+  Ca \textsc{I} &  21 &    3.85 &    0.09 & $-$2.49 &    0.40 &    0.02 \\
+ Sc \textsc{II} &  16 &    2.39 &    0.10 & $-$0.76 &    0.19 &    0.03 &&
+ Sc \textsc{II} &  15 &    0.18 &    0.07 & $-$2.97 & $-$0.07 &    0.02 \\
+  Ti \textsc{I} &  23 &    4.28 &    0.19 & $-$0.67 &    0.27 &    0.04 &&
+  Ti \textsc{I} &  22 &    2.12 &    0.10 & $-$2.83 &    0.06 &    0.02 \\
+ Ti \textsc{II} &  39 &    4.38 &    0.13 & $-$0.57 &    0.37 &    0.02 &&
+ Ti \textsc{II} &  42 &    2.24 &    0.10 & $-$2.71 &    0.18 &    0.02 \\
+   V \textsc{I} &   4 &    3.25 &    0.16 & $-$0.68 &    0.26 &    0.08 &&
+   V \textsc{I} &   1 &    0.81 &    0.00 & $-$3.12 & $-$0.22 &    0.00 \\
+  Cr \textsc{I} &  20 &    4.57 &    0.10 & $-$1.07 & $-$0.12 &    0.02 &&
+  Cr \textsc{I} &  16 &    2.42 &    0.11 & $-$3.22 & $-$0.32 &    0.03 \\
+ Cr \textsc{II} &   4 &    4.91 &    0.08 & $-$0.73 &    0.21 &    0.04 &&
+ Cr \textsc{II} &   3 &    2.83 &    0.03 & $-$2.81 &    0.09 &    0.02 \\
+  Mn \textsc{I} &   9 &    4.32 &    0.10 & $-$1.11 & $-$0.17 &    0.03 &&
+  Mn \textsc{I} &   7 &    2.15 &    0.05 & $-$3.28 & $-$0.39 &    0.02 \\
+  Fe \textsc{I} &  97 &    6.56 &    0.11 & $-$0.94 &    0.00 &    0.01 &&
+  Fe \textsc{I} & 166 &    4.60 &    0.11 & $-$2.90 &    0.00 &    0.01 \\
+ Fe \textsc{II} &  20 &    6.56 &    0.14 & $-$0.94 &    0.00 &    0.03 &&
+ Fe \textsc{II} &  24 &    4.61 &    0.16 & $-$2.89 &    0.01 &    0.03 \\
+  Co \textsc{I} &   4 &    4.11 &    0.12 & $-$0.88 &    0.06 &    0.06 &&
+  Co \textsc{I} &   5 &    2.25 &    0.14 & $-$2.74 &    0.16 &    0.06 \\
+  Ni \textsc{I} &  27 &    5.31 &    0.13 & $-$0.91 &    0.03 &    0.03 &&
+  Ni \textsc{I} &  19 &    3.49 &    0.10 & $-$2.73 &    0.16 &    0.02 \\
+  Cu \textsc{I} &   1 &    2.96 &    0.00 & $-$1.23 & $-$0.29 &    0.00 &&
+  Cu \textsc{I} &   1 & $<$0.10 &         &$<-$4.19 &$<-$1.19 &         \\
+  Zn \textsc{I} &   2 &    3.71 &    0.01 & $-$0.84 &    0.10 &    0.01 &&
+  Zn \textsc{I} &   2 &    1.84 &    0.06 & $-$2.72 &    0.18 &    0.04 \\
+ Sr \textsc{II} &   1 &    2.01 &    0.00 & $-$0.86 &    0.08 &    0.00 &&
+ Sr \textsc{II} &   1 & $-$0.59 &    0.00 & $-$3.46 & $-$0.56 &    0.00 \\
+  Y \textsc{II} &   3 &    1.41 &    0.17 & $-$0.80 &    0.14 &    0.10 &&
+  Y \textsc{II} &   1 & $-$0.81 &    0.00 & $-$3.02 & $-$0.12 &    0.00 \\
+ Ba \textsc{II} &   2 &    1.36 &    0.05 & $-$0.82 &    0.12 &    0.04 &&
+ Ba \textsc{II} &   2 & $-$1.92 &    0.06 & $-$4.10 & $-$1.20 &    0.05 \\
+ La \textsc{II} &   1 &    0.69 &    0.00 & $-$0.41 &    0.53 &    0.00 &&
+ La \textsc{II} &   1 &$<-$1.51 &         &$<-$2.61 & $<$0.29 &         \\
+ Ce \textsc{II} &   1 & $<$0.70 &         &$<-$0.88 & $<$0.06 &         &&
+ Ce \textsc{II} &   1 &$<-$1.53 &         &$<-$3.11 &$<-$0.21 &         \\
+ Nd \textsc{II} &   3 &    0.82 &    0.11 & $-$0.60 &    0.34 &    0.07 &&
+ Nd \textsc{II} &   1 &$<-$1.83 &         &$<-$3.25 &$<-$0.35 &         \\
+ Eu \textsc{II} &   1 &$<-$0.27 &         &$<-$0.79 & $<$0.15 &         &&
+ Eu \textsc{II} &   1 &$<-$1.72 &         &$<-$2.24 & $<$0.66 &         \\
+
+\cline{1-7} \cline{9-15} \\ \\
+\multicolumn{7}{c}{\textbf{HD 136316}} && \multicolumn{7}{c}{\textbf{HD 141531}} \\
+\cline{1-7} \cline{9-15}
+
+   C (CH)       &   2 &    6.05 &    0.20 & $-$2.38 & $-$0.47 &    0.20 &&
+   C (CH)       &   2 &    6.31 &    0.20 & $-$2.12 & $-$0.42 &    0.20 \\
+   O \textsc{I} &   1 &    7.16 &    0.00 & $-$1.53 &    0.38 &    0.00 &&
+   O \textsc{I} &   2 &    7.30 &    0.00 & $-$1.38 &    0.32 &    0.00 \\
+  Na \textsc{I} &   2 &    4.21 &    0.08 & $-$2.04 & $-$0.12 &    0.05 &&
+  Na \textsc{I} &   3 &    4.38 &    0.07 & $-$1.86 & $-$0.15 &    0.04 \\
+  Mg \textsc{I} &  10 &    6.21 &    0.33 & $-$1.39 &    0.52 &    0.10 &&
+  Mg \textsc{I} &  10 &    6.36 &    0.33 & $-$1.24 &    0.46 &    0.10 \\
+  Al \textsc{I} &   1 & $<$4.58 &         &$<-$1.87 & $<$0.04 &         &&
+  Al \textsc{I} &   1 &    4.80 &    0.00 & $-$1.65 &    0.05 &    0.00 \\
+  Si \textsc{I} &   9 &    5.97 &    0.18 & $-$1.54 &    0.37 &    0.06 &&
+  Si \textsc{I} &   8 &    6.09 &    0.16 & $-$1.42 &    0.28 &    0.06 \\
+   K \textsc{I} &   2 &    3.88 &    0.03 & $-$1.15 &    0.76 &    0.02 &&
+   K \textsc{I} &   2 &    4.00 &    0.04 & $-$1.04 &    0.67 &    0.03 \\
+  Ca \textsc{I} &  21 &    4.79 &    0.09 & $-$1.55 &    0.36 &    0.02 &&
+  Ca \textsc{I} &  23 &    5.02 &    0.16 & $-$1.32 &    0.38 &    0.03 \\
+ Sc \textsc{II} &  16 &    1.29 &    0.08 & $-$1.86 &    0.06 &    0.02 &&
+ Sc \textsc{II} &  16 &    1.46 &    0.09 & $-$1.69 &    0.01 &    0.02 \\
+  Ti \textsc{I} &  29 &    3.12 &    0.22 & $-$1.83 &    0.08 &    0.04 &&
+  Ti \textsc{I} &  30 &    3.26 &    0.24 & $-$1.69 &    0.01 &    0.04 \\
+ Ti \textsc{II} &  42 &    3.52 &    0.23 & $-$1.43 &    0.49 &    0.04 &&
+ Ti \textsc{II} &  40 &    3.67 &    0.26 & $-$1.28 &    0.42 &    0.04 \\
+   V \textsc{I} &   8 &    2.47 &    0.97 & $-$1.46 &    0.45 &    0.34 &&
+   V \textsc{I} &   7 &    2.19 &    0.14 & $-$1.74 & $-$0.04 &    0.05 \\
+  Cr \textsc{I} &  21 &    3.54 &    0.25 & $-$2.10 & $-$0.18 &    0.06 &&
+  Cr \textsc{I} &  20 &    3.70 &    0.26 & $-$1.94 & $-$0.24 &    0.06 \\
+ Cr \textsc{II} &   2 &    3.85 &    0.02 & $-$1.79 &    0.12 &    0.01 &&
+ Cr \textsc{II} &   2 &    4.20 &    0.10 & $-$1.44 &    0.26 &    0.07 \\
+  Mn \textsc{I} &  10 &    3.24 &    0.26 & $-$2.19 & $-$0.28 &    0.08 &&
+  Mn \textsc{I} &   9 &    3.48 &    0.29 & $-$1.95 & $-$0.25 &    0.10 \\
+  Fe \textsc{I} & 101 &    5.59 &    0.13 & $-$1.91 &    0.00 &    0.01 &&
+  Fe \textsc{I} &  85 &    5.80 &    0.13 & $-$1.70 &    0.00 &    0.01 \\
+ Fe \textsc{II} &  18 &    5.61 &    0.15 & $-$1.89 &    0.03 &    0.03 &&
+ Fe \textsc{II} &  18 &    5.78 &    0.11 & $-$1.72 & $-$0.01 &    0.03 \\
+  Co \textsc{I} &   4 &    3.12 &    0.12 & $-$1.87 &    0.04 &    0.06 &&
+  Co \textsc{I} &   6 &    3.23 &    0.15 & $-$1.76 & $-$0.06 &    0.06 \\
+  Ni \textsc{I} &  26 &    4.24 &    0.13 & $-$1.98 & $-$0.07 &    0.03 &&
+  Ni \textsc{I} &  27 &    4.44 &    0.16 & $-$1.78 & $-$0.07 &    0.03 \\
+  Cu \textsc{I} &   1 &    1.74 &    0.00 & $-$2.45 & $-$0.54 &    0.00 &&
+  Cu \textsc{I} &   1 &    2.06 &    0.00 & $-$2.13 & $-$0.43 &    0.00 \\
+  Zn \textsc{I} &   2 &    2.67 &    0.10 & $-$1.88 &    0.03 &    0.07 &&
+  Zn \textsc{I} &   2 &    2.75 &    0.04 & $-$1.81 & $-$0.11 &    0.03 \\
+ Sr \textsc{II} &   1 &    0.94 &    0.00 & $-$1.93 & $-$0.02 &    0.00 &&
+ Sr \textsc{II} &   1 &    1.13 &    0.00 & $-$1.74 & $-$0.04 &    0.00 \\
+  Y \textsc{II} &   3 &    0.17 &    0.09 & $-$2.04 & $-$0.13 &    0.05 &&
+  Y \textsc{II} &   3 &    0.30 &    0.11 & $-$1.91 & $-$0.21 &    0.06 \\
+ Ba \textsc{II} &   2 &    0.26 &    0.08 & $-$1.93 & $-$0.01 &    0.05 &&
+ Ba \textsc{II} &   2 &    0.35 &    0.05 & $-$1.83 & $-$0.12 &    0.04 \\
+ La \textsc{II} &   2 & $-$0.69 &    0.02 & $-$1.79 &    0.13 &    0.02 &&
+ La \textsc{II} &   2 & $-$0.59 &    0.07 & $-$1.70 &    0.01 &    0.05 \\
+ Ce \textsc{II} &   2 & $-$0.29 &    0.22 & $-$1.87 &    0.04 &    0.16 &&
+ Ce \textsc{II} &   1 &    0.15 &    0.00 & $-$1.43 &    0.27 &    0.00 \\
+ Nd \textsc{II} &   8 & $-$0.36 &    0.05 & $-$1.78 &    0.14 &    0.02 &&
+ Nd \textsc{II} &   7 & $-$0.24 &    0.07 & $-$1.66 &    0.04 &    0.03 \\
+ Eu \textsc{II} &   1 & $-$1.08 &    0.00 & $-$1.60 &    0.31 &    0.00 &&
+ Eu \textsc{II} &   1 & $-$0.97 &    0.00 & $-$1.49 &    0.21 &    0.00 \\
+
+\cline{1-7} \cline{9-15} \\ \\
+\multicolumn{7}{c}{\textbf{HD 142948}} && \multicolumn{7}{c}{\textbf{OSS 3}} \\
+\cline{1-7} \cline{9-15}
+
+   C (CH)       &   2 &    7.75 &    0.20 & $-$0.68 &    0.03 &    0.20 &&
+   C (CH)       &   2 &    7.54 &    0.20 & $-$0.89 &    0.00 &    0.20 \\
+   O \textsc{I} &   2 &    8.47 &    0.03 & $-$0.21 &    0.50 &    0.02 &&
+   O \textsc{I} &   1 & $<$8.43 &         &$<-$0.25 & $<$0.54 &         \\
+  Na \textsc{I} &   3 &    5.76 &    0.13 & $-$0.48 &    0.23 &    0.08 &&
+  Na \textsc{I} &   2 &    5.22 &    0.01 & $-$1.02 & $-$0.16 &    0.01 \\
+  Mg \textsc{I} &   7 &    7.24 &    0.18 & $-$0.36 &    0.35 &    0.07 &&
+  Mg \textsc{I} &   7 &    6.75 &    0.17 & $-$0.85 &    0.01 &    0.07 \\
+  Al \textsc{I} &   4 &    6.00 &    0.08 & $-$0.45 &    0.27 &    0.04 &&
+  Al \textsc{I} &   2 &    5.27 &    0.11 & $-$1.18 & $-$0.32 &    0.08 \\
+  Si \textsc{I} &  10 &    7.11 &    0.18 & $-$0.40 &    0.31 &    0.06 &&
+  Si \textsc{I} &   8 &    6.72 &    0.17 & $-$0.79 &    0.07 &    0.06 \\
+   K \textsc{I} &   1 &    5.08 &    0.00 &    0.05 &    0.76 &    0.00 &&
+   K \textsc{I} &   1 &    4.84 &    0.00 & $-$0.19 &    0.67 &    0.00 \\
+  Ca \textsc{I} &  19 &    5.87 &    0.14 & $-$0.47 &    0.24 &    0.03 &&
+  Ca \textsc{I} &  23 &    5.73 &    0.16 & $-$0.61 &    0.26 &    0.03 \\
+ Sc \textsc{II} &  16 &    2.73 &    0.26 & $-$0.42 &    0.30 &    0.06 &&
+ Sc \textsc{II} &  13 &    2.28 &    0.13 & $-$0.87 &    0.00 &    0.04 \\
+  Ti \textsc{I} &  26 &    4.39 &    0.22 & $-$0.56 &    0.16 &    0.04 &&
+  Ti \textsc{I} &  25 &    4.33 &    0.33 & $-$0.62 &    0.24 &    0.07 \\
+ Ti \textsc{II} &  32 &    4.60 &    0.21 & $-$0.35 &    0.36 &    0.04 &&
+ Ti \textsc{II} &  38 &    4.39 &    0.25 & $-$0.56 &    0.31 &    0.04 \\
+   V \textsc{I} &   5 &    3.47 &    0.20 & $-$0.46 &    0.26 &    0.09 &&
+   V \textsc{I} &   3 &    3.01 &    0.11 & $-$0.92 & $-$0.06 &    0.06 \\
+  Cr \textsc{I} &  18 &    4.85 &    0.30 & $-$0.79 & $-$0.08 &    0.07 &&
+  Cr \textsc{I} &  22 &    4.66 &    0.27 & $-$0.98 & $-$0.11 &    0.06 \\
+ Cr \textsc{II} &   3 &    5.09 &    0.13 & $-$0.55 &    0.16 &    0.08 &&
+ Cr \textsc{II} &   3 &    4.89 &    0.26 & $-$0.75 &    0.11 &    0.15 \\
+  Mn \textsc{I} &   9 &    4.70 &    0.21 & $-$0.73 & $-$0.02 &    0.07 &&
+  Mn \textsc{I} &  10 &    4.45 &    0.36 & $-$0.98 & $-$0.12 &    0.11 \\
+  Fe \textsc{I} &  69 &    6.79 &    0.14 & $-$0.71 &    0.00 &    0.02 &&
+  Fe \textsc{I} &  97 &    6.64 &    0.20 & $-$0.86 &    0.00 &    0.02 \\
+ Fe \textsc{II} &  17 &    6.79 &    0.19 & $-$0.71 &    0.00 &    0.05 &&
+ Fe \textsc{II} &  27 &    6.64 &    0.24 & $-$0.86 &    0.00 &    0.05 \\
+  Co \textsc{I} &   5 &    4.41 &    0.11 & $-$0.58 &    0.13 &    0.05 &&
+  Co \textsc{I} &   4 &    4.26 &    0.26 & $-$0.73 &    0.14 &    0.13 \\
+  Ni \textsc{I} &  26 &    5.61 &    0.22 & $-$0.61 &    0.10 &    0.04 &&
+  Ni \textsc{I} &  25 &    5.33 &    0.24 & $-$0.89 & $-$0.03 &    0.05 \\
+  Cu \textsc{I} &   1 &    3.74 &    0.00 & $-$0.45 &    0.26 &    0.00 &&
+  Cu \textsc{I} &   1 &    3.05 &    0.00 & $-$1.14 & $-$0.28 &    0.00 \\
+  Zn \textsc{I} &   2 &    3.87 &    0.14 & $-$0.69 &    0.02 &    0.10 &&
+  Zn \textsc{I} &   2 &    3.67 &    0.15 & $-$0.89 & $-$0.03 &    0.10 \\
+ Sr \textsc{II} &   1 &    2.32 &    0.00 & $-$0.55 &    0.16 &    0.00 &&
+ Sr \textsc{II} &   1 &    1.95 &    0.00 & $-$0.92 & $-$0.06 &    0.00 \\
+  Y \textsc{II} &   3 &    1.62 &    0.24 & $-$0.59 &    0.12 &    0.14 &&
+  Y \textsc{II} &   2 &    1.27 &    0.35 & $-$0.94 & $-$0.07 &    0.25 \\
+ Ba \textsc{II} &   2 &    1.29 &    0.01 & $-$0.90 & $-$0.18 &    0.00 &&
+ Ba \textsc{II} &   2 &    1.51 &    0.13 & $-$0.67 &    0.19 &    0.09 \\
+ La \textsc{II} &   2 &    0.51 &    0.10 & $-$0.59 &    0.12 &    0.07 &&
+ La \textsc{II} &   1 & $<$0.59 &         &$<-$1.51 & $<$0.38 &         \\
+ Nd \textsc{II} &   4 &    0.91 &    0.07 & $-$0.51 &    0.20 &    0.03 &&
+ Nd \textsc{II} &   1 &    1.46 &    0.00 &    0.04 &    0.90 &    0.00 \\
+ Eu \textsc{II} &   1 &    0.15 &    0.00 & $-$0.37 &    0.34 &    0.00 &&
+ Eu \textsc{II} &   1 &$<-$0.09 &         &$<-$0.61 & $<$0.28 &         \\
+
+\cline{1-7} \cline{9-15} \\ \\
+\multicolumn{7}{c}{\textbf{OSS 6}} && \multicolumn{7}{c}{\textbf{OSS 8}} \\
+\cline{1-7} \cline{9-15}
+
+%   O \textsc{I} &   1 &    6.80 &    0.00 & $-$1.89 & $-$0.19 &    0.00 &&
+%  Al \textsc{I} &   1 &    4.84 &    0.00 & $-$1.61 &    0.09 &    0.00 &&
+
+   C (CH)       &   2 &    6.39 &    0.20 & $-$2.04 & $-$0.37 &    0.20 &&
+   C (CH)       &   2 &    6.85 &    0.20 & $-$1.58 &    0.00 &    0.20 \\
+   O \textsc{I} &   1 & $<$7.08 &         &$<-$1.61 & $<$0.06 &         &&
+   O \textsc{I} &   1 & $<$7.46 &         &$<-$1.23 & $<$0.35 &         \\
+  Na \textsc{I} &   1 &    4.27 &    0.00 & $-$1.97 & $-$0.27 &    0.00 &&
+  Na \textsc{I} &   1 &    4.36 &    0.00 & $-$1.88 & $-$0.26 &    0.00 \\
+  Mg \textsc{I} &   6 &    5.99 &    0.20 & $-$1.61 &    0.09 &    0.08 &&
+  Mg \textsc{I} &  11 &    6.07 &    0.41 & $-$1.53 &    0.09 &    0.12 \\
+  Al \textsc{I} &   1 & $<$4.85 &         &$<-$1.60 & $<$0.07 &         &&
+  Al \textsc{I} &   1 & $<$5.18 &         &$<-$1.27 & $<$0.31 &         \\
+  Si \textsc{I} &   3 &    5.89 &    0.10 & $-$1.62 &    0.07 &    0.06 &&
+  Si \textsc{I} &   3 &    6.14 &    0.21 & $-$1.37 &    0.25 &    0.12 \\
+   K \textsc{I} &   1 &    3.96 &    0.00 & $-$1.07 &    0.63 &    0.00 &&
+   K \textsc{I} &   1 &    4.24 &    0.00 & $-$0.79 &    0.83 &    0.00 \\
+  Ca \textsc{I} &  24 &    4.88 &    0.24 & $-$1.46 &    0.24 &    0.05 &&
+  Ca \textsc{I} &  23 &    5.04 &    0.15 & $-$1.30 &    0.32 &    0.03 \\
+ Sc \textsc{II} &  16 &    1.25 &    0.17 & $-$1.90 & $-$0.20 &    0.04 &&
+ Sc \textsc{II} &  16 &    1.47 &    0.15 & $-$1.68 & $-$0.06 &    0.04 \\
+  Ti \textsc{I} &  23 &    3.17 &    0.19 & $-$1.78 & $-$0.09 &    0.04 &&
+  Ti \textsc{I} &  20 &    3.31 &    0.11 & $-$1.64 & $-$0.02 &    0.02 \\
+ Ti \textsc{II} &  39 &    3.51 &    0.21 & $-$1.44 &    0.25 &    0.03 &&
+ Ti \textsc{II} &  39 &    3.59 &    0.24 & $-$1.36 &    0.26 &    0.04 \\
+   V \textsc{I} &   2 &    1.78 &    0.09 & $-$2.15 & $-$0.45 &    0.07 &&
+   V \textsc{I} &   2 &    2.29 &    0.18 & $-$1.64 & $-$0.02 &    0.13 \\
+  Cr \textsc{I} &  20 &    3.81 &    0.14 & $-$1.83 & $-$0.14 &    0.03 &&
+  Cr \textsc{I} &  17 &    3.82 &    0.12 & $-$1.82 & $-$0.19 &    0.03 \\
+ Cr \textsc{II} &   2 &    4.19 &    0.07 & $-$1.45 &    0.24 &    0.05 &&
+ Cr \textsc{II} &   3 &    4.23 &    0.04 & $-$1.41 &    0.21 &    0.02 \\
+  Mn \textsc{I} &  10 &    3.64 &    0.38 & $-$1.79 & $-$0.09 &    0.12 &&
+  Mn \textsc{I} &   5 &    3.53 &    0.18 & $-$1.90 & $-$0.28 &    0.08 \\
+  Fe \textsc{I} &  69 &    5.80 &    0.15 & $-$1.70 &    0.00 &    0.02 &&
+  Fe \textsc{I} &  60 &    5.88 &    0.15 & $-$1.62 &    0.00 &    0.02 \\
+ Fe \textsc{II} &  15 &    5.81 &    0.14 & $-$1.69 &    0.01 &    0.04 &&
+ Fe \textsc{II} &  12 &    5.88 &    0.16 & $-$1.62 &    0.00 &    0.05 \\
+  Co \textsc{I} &   3 &    3.17 &    0.35 & $-$1.82 & $-$0.12 &    0.20 &&
+  Co \textsc{I} &   4 &    3.35 &    0.14 & $-$1.64 & $-$0.02 &    0.07 \\
+  Ni \textsc{I} &  23 &    4.42 &    0.19 & $-$1.80 & $-$0.10 &    0.04 &&
+  Ni \textsc{I} &  21 &    4.54 &    0.16 & $-$1.68 & $-$0.06 &    0.04 \\
+  Cu \textsc{I} &   1 &    1.49 &    0.00 & $-$2.70 & $-$1.00 &    0.00 &&
+  Cu \textsc{I} &   1 &    1.68 &    0.00 & $-$2.51 & $-$0.89 &    0.00 \\
+  Zn \textsc{I} &   2 &    2.51 &    0.14 & $-$2.04 & $-$0.35 &    0.10 &&
+  Zn \textsc{I} &   1 &    2.89 &    0.00 & $-$1.67 & $-$0.05 &    0.00 \\
+ Sr \textsc{II} &   1 &    0.83 &    0.00 & $-$2.04 & $-$0.34 &    0.00 &&
+ Sr \textsc{II} &   1 &    0.79 &    0.00 & $-$2.08 & $-$0.46 &    0.00 \\
+  Y \textsc{II} &   1 &$<-$0.59 &         &$<-$2.77 &$<-$1.10 &         &&
+  Y \textsc{II} &   1 &$<-$0.41 &         &$<-$2.60 &$<-$1.00 &         \\
+ Ba \textsc{II} &   1 &    0.20 &         & $-$1.98 & $-$0.28 &         &&
+ Ba \textsc{II} &   1 & $-$0.24 &         & $-$2.42 & $-$0.80 &         \\
+ La \textsc{II} &   1 &$<-$0.47 &         &$<-$1.57 & $<$0.10 &         &&
+ La \textsc{II} &   1 &   -0.12 &    0.00 & $-$1.22 &    0.40 &    0.00 \\
+ Nd \textsc{II} &   2 &   -0.64 &    0.08 & $-$2.06 & $-$0.36 &    0.06 &&
+ Nd \textsc{II} &   1 &    0.08 &    0.00 & $-$1.34 &    0.28 &    0.00 \\
+ Eu \textsc{II} &   1 &$<-$1.25 &         &$<-$1.77 &$<-$0.10 &         &&
+ Eu \textsc{II} &   1 &$<-$0.62 &         &$<-$1.14 & $<$0.44 &         \\
+
+\cline{1-7} \cline{9-15} \\ \\
+\multicolumn{7}{c}{\textbf{OSS 14}} && \multicolumn{7}{c}{\textbf{OSS 18}} \\
+\cline{1-7} \cline{9-15}
+
+   C (CH)       &   2 &    5.85 &    0.20 & $-$2.58 &    0.08 &    0.20 &&
+   C (CH)       &   1 &    7.57 &    0.20 & $-$0.86 & $-$0.10 &    0.20 \\
+   O \textsc{I} &   1 & $<$6.83 &         &$<-$1.86 & $<$0.80 &         &&
+   O \textsc{I} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
+  Na \textsc{I} &   1 & $<$4.77 &         &$<-$1.47 & $<$1.19 &         &&
+  Na \textsc{I} &   1 &    5.37 &    0.00 & $-$0.87 & $-$0.25 &    0.00 \\
+  Mg \textsc{I} &   8 &    5.19 &    0.21 & $-$2.41 &    0.25 &    0.07 &&
+  Mg \textsc{I} &   5 &    7.01 &    0.25 & $-$0.59 &    0.03 &    0.11 \\
+  Al \textsc{I} &   1 &    5.29 &    0.00 & $-$1.16 &    1.51 &    0.00 &&
+  Al \textsc{I} &   1 & $<$5.66 &         &$<-$0.79 &$<-$0.03 &         \\
+  Si \textsc{I} &   2 &    5.50 &    0.03 & $-$2.01 &    0.66 &    0.02 &&
+  Si \textsc{I} &   5 &    6.98 &    0.28 & $-$0.53 &    0.09 &    0.13 \\
+   K \textsc{I} &   1 &    2.66 &    0.00 & $-$2.37 &    0.30 &    0.00 &&
+   K \textsc{I} &   1 &    4.91 &    0.00 & $-$0.12 &    0.50 &    0.00 \\
+  Ca \textsc{I} &  16 &    3.89 &    0.15 & $-$2.45 &    0.21 &    0.04 &&
+  Ca \textsc{I} &  22 &    5.89 &    0.24 & $-$0.45 &    0.17 &    0.05 \\
+ Sc \textsc{II} &   9 &    0.13 &    0.13 & $-$3.02 & $-$0.36 &    0.04 &&
+ Sc \textsc{II} &  11 &    2.64 &    0.18 & $-$0.51 &    0.11 &    0.05 \\
+  Ti \textsc{I} &  11 &    2.24 &    0.12 & $-$2.71 & $-$0.05 &    0.04 &&
+  Ti \textsc{I} &  20 &    4.37 &    0.33 & $-$0.58 &    0.04 &    0.07 \\
+ Ti \textsc{II} &  34 &    2.36 &    0.19 & $-$2.59 &    0.08 &    0.03 &&
+ Ti \textsc{II} &  28 &    4.54 &    0.43 & $-$0.41 &    0.21 &    0.08 \\
+   V \textsc{I} &   1 & $<$1.61 &         &$<-$2.32 & $<$0.34 &         &&
+   V \textsc{I} &   4 &    3.26 &    0.01 & $-$0.67 & $-$0.05 &    0.00 \\
+  Cr \textsc{I} &  11 &    2.59 &    0.26 & $-$3.05 & $-$0.38 &    0.08 &&
+  Cr \textsc{I} &  18 &    4.83 &    0.28 & $-$0.81 & $-$0.19 &    0.06 \\
+ Cr \textsc{II} &   1 &    3.06 &    0.00 & $-$2.58 &    0.09 &    0.00 &&
+ Cr \textsc{II} &   1 &    5.29 &    0.00 & $-$0.35 &    0.27 &    0.00 \\
+  Mn \textsc{I} &   4 &    2.20 &    0.20 & $-$3.23 & $-$0.56 &    0.10 &&
+  Mn \textsc{I} &   4 &    4.47 &    0.31 & $-$0.96 & $-$0.33 &    0.16 \\
+  Fe \textsc{I} & 133 &    4.83 &    0.20 & $-$2.67 &    0.00 &    0.02 &&
+  Fe \textsc{I} &  48 &    6.88 &    0.21 & $-$0.62 &    0.00 &    0.03 \\
+ Fe \textsc{II} &  16 &    4.83 &    0.16 & $-$2.67 & $-$0.01 &    0.04 &&
+ Fe \textsc{II} &  12 &    6.88 &    0.25 & $-$0.62 &    0.00 &    0.07 \\
+  Co \textsc{I} &   3 &    2.32 &    0.48 & $-$2.67 & $-$0.01 &    0.28 &&
+  Co \textsc{I} &   3 &    4.65 &    0.41 & $-$0.34 &    0.28 &    0.24 \\
+  Ni \textsc{I} &   5 &    3.51 &    0.07 & $-$2.71 & $-$0.04 &    0.03 &&
+  Ni \textsc{I} &  18 &    5.46 &    0.26 & $-$0.76 & $-$0.14 &    0.06 \\
+  Cu \textsc{I} &   1 & $<$0.77 &         &$<-$3.42 &$<-$0.75 &         &&
+  Cu \textsc{I} &   1 &    3.14 &    0.00 & $-$1.05 & $-$0.43 &    0.00 \\
+  Zn \textsc{I} &   1 & $<$1.92 &         &$<-$2.64 & $<$0.02 &         &&
+  Zn \textsc{I} &   1 &    3.87 &    0.00 & $-$0.69 & $-$0.07 &    0.00 \\
+ Sr \textsc{II} &   1 & $-$0.22 &    0.00 & $-$3.89 & $-$0.42 &    0.00 &&
+ Sr \textsc{II} &   1 &    2.31 &    0.00 & $-$0.56 &    0.06 &    0.00 \\
+  Y \textsc{II} &   1 &$<-$0.86 &         &$<-$3.10 &$<-$0.40 &         &&
+  Y \textsc{II} &   1 &    1.92 &         & $-$0.29 &    0.33 &         \\
+ Ba \textsc{II} &   2 & $-$1.87 &    0.03 & $-$4.02 & $-$1.35 &    0.02 &&
+ Ba \textsc{II} &   2 &    1.76 &    0.05 & $-$0.42 &    0.20 &    0.04 \\
+ La \textsc{II} &   1 &$<-$0.91 &         &$<-$2.01 & $<$0.65 &         &&
+ La \textsc{II} &   1 &    1.29 &    0.00 &    0.19 &    0.81 &    0.00 \\
+ Nd \textsc{II} &   1 &$<-$0.56 &         &$<-$1.98 & $<$0.68 &         &&
+ Nd \textsc{II} &   4 &    1.74 &    0.37 &    0.32 &    0.94 &    0.18 \\
+ Eu \textsc{II} &   1 &$<-$1.14 &         &$<-$1.66 &  $<$1.0 &         &&
+ Eu \textsc{II} &   1 &    0.72 &    0.00 &    0.20 &    0.82 &    0.00 \\
+\end{longtable*}
+
+\begin{deluxetable*}{lcccccc}
+\tablecolumns{1}
 \tabletypesize{\scriptsize}
-\tablecaption{Chemical Abundances\label{tab:stellar-parameters}}
+\tablecaption{Abundance Uncertainties Due to Stellar Parameters\label{tab:chemical-abundance-uncertainties}}
 \tablehead{
-&  \multicolumn{5}{c}{OSS 1} & \colhead{} &
-	\multicolumn{5}{c}{OSS 2} & \colhead{} &
-	\multicolumn{5}{c}{OSS 3} \\
-	\cline{2-6} \cline{8-12} \cline{14-18} \\
-\colhead{Species} 
- & $\log\epsilon$(X) & [X/H] & [X/Fe] & $N$ & $\sigma$ &
- & $\log\epsilon$(X) & [X/H] & [X/Fe] & $N$ & $\sigma$ &
- & $\log\epsilon$(X) & [X/H] & [X/Fe] & $N$ & $\sigma$
+ & &  & & & \multicolumn{2}{c}{\textbf{Total Uncertainty}} \\
+ \cline{6-7}
+	\colhead{Species} &
+	\colhead{$T_{\rm eff}+\sigma(T_{\rm eff})\,{\rm K}$} &
+	\colhead{$\log{g}+\sigma(\log{g})\,{\rm dex}$} &
+	\colhead{${v_t}+\sigma(v_t)$\,km s$^{-1}$} &
+	\colhead{$Max(0.10, S.D.)/\sqrt(N)$} & 
+	\colhead{[X/H]} &
+	\colhead{[X/Fe]} \\
+	 & $\Delta$abundance & $\Delta$abundance & $\Delta$abundance & (dex) & (dex) & (dex)
  }
 \startdata
-Na \textsc{I} & ? & ? & ? & ? & ?
-             && $4.21$ & $-2.03$ &    $-0.23$ &   $3$ & $0.05$
-             && $4.42$ & $-1.82$ &    $-0.03$ &   $3$ & $0.07$  \\
-Mg \textsc{I} & $6.56$ & $-1.04$ & \phs$0.16$ &   $4$ & $0.10$  
-             && $5.90$ & $-1.70$ & \phs$0.10$ &   $6$ & $0.10$   
-             && $5.95$ & $-1.65$ & \phs$0.15$ &   $5$ & $0.05$  \\
-Si \textsc{I} & $6.57$ & $-0.94$ & \phs$0.26$ &   $4$ & $0.23$
-             && $5.66$ & $-1.85$ &    $-0.05$ &   $3$ & $0.26$   
-             && $6.20$ & $-1.31$ & \phs$0.43$ &   $3$ & $0.16$  \\
-Ca \textsc{I} & $5.48$ & $-0.86$ & \phs$0.34$ &  $14$ & $0.14$
-             && $4.79$ & $-1.55$ & \phs$0.25$ &  $17$ & $0.12$   
-             && $4.87$ & $-1.47$ & \phs$0.32$ &  $18$ & $0.09$  \\
-Ti \textsc{I} & $3.73$ & $-1.22$ &    $-0.02$ &  $21$ & $0.15$  
-             && $3.00$ & $-1.95$ &    $-0.15$ &  $20$ & $0.16$   
-             && $3.13$ & $-1.82$ &    $-0.03$ &  $23$ & $0.09$  \\
-Ti \textsc{II}& $3.91$ & $-1.04$ & \phs$0.16$ &  $25$ & $0.10$  
-             && $3.19$ & $-1.76$ & \phs$0.04$ &  $23$ & $0.14$   
-             && $3.36$ & $-1.59$ & \phs$0.20$ &  $24$ & $0.09$  \\
-Fe \textsc{I} & $6.24$ & $-1.26$ &    \nodata & $149$ & $0.16$  
-             && $5.71$ & $-1.79$ &    \nodata & $112$ & $0.16$  
-             && $5.71$ & $-1.79$ &    \nodata & $154$ & $0.12$  \\
-Fe \textsc{II}& $6.19$ & $-1.21$ & \phs$0.05$ &  $15$ & $0.16$
-             && $5.75$ & $-1.75$ &    $-0.04$ &   $8$ & $0.10$   
-             && $5.71$ & $-1.79$ & \phs$0.00$ &  $20$ & $0.16$  \\
-
-\\ & \multicolumn{5}{c}{OSS 4} && \multicolumn{5}{c}{OSS 5} \\
-     \cline{2-6} \cline{8-12} \\
-Na \textsc{I} & $3.69$ & $-2.55$ & \phs$0.20$ &  $2$ & $0.04$
-             && $5.17$ & $-1.07$ &    $-0.27$ &  $4$ & $0.13$ \\ 
-Mg \textsc{I} & $5.11$ & $-2.49$ & \phs$0.26$ &  $7$ & $0.13$
-             && $6.70$ & $-0.90$ &    $-0.10$ &  $5$ & $0.15$ \\
-Si \textsc{I} & $5.38$ & $-2.13$ & \phs$0.62$ &  $3$ & $0.03$
-             && $6.78$ & $-0.73$ & \phs$0.07$ &  $4$ & $0.07$ \\
-Ca \textsc{I} & $3.75$ & $-2.59$ & \phs$0.16$ &  $9$ & $0.10$
-             && $5.77$ & $-0.57$ & \phs$0.23$ & $10$ & $0.12$ \\
-Ti \textsc{I} & $2.28$ & $-2.67$ & \phs$0.08$ & $13$ & $0.15$
-             && $4.26$ & $-0.69$ & \phs$0.11$ & $15$ & $0.36$ \\
-Ti \textsc{II}& $2.31$ & $-2.64$ & \phs$0.11$ & $24$ & $0.15$
-             && $4.28$ & $-0.67$ & \phs$0.13$ & $13$ & $0.19$ \\
-Fe \textsc{I} & $4.74$ & $-2.76$ &    \nodata & $89$ & $0.11$
-             && $6.68$ & $-0.82$ &    \nodata & $99$ & $0.18$ \\
-Fe \textsc{II}& $4.77$ & $-2.73$ & \phs$0.03$ & $13$ & $0.12$
-             && $6.71$ & $-0.79$ &    $-0.03$ & $14$ & $0.16$ \\
+\\
+\multicolumn{7}{c}{\textbf{OSS 3}} \\
+\hline
+Na I   & 0.05    & 0.00    & 0.01    & 0.07    & 0.09    & 0.09 \\
+Mg I   & 0.05    & 0.02    & 0.03    & 0.06    & 0.09    & 0.18 \\
+Al I   & 0.04    & 0.00    & 0.00    & 0.08    & 0.09    & 0.10 \\
+Si I   & 0.03    & 0.01    & 0.01    & 0.06    & 0.07    & 0.11 \\
+K I    & 0.06    & 0.04    & 0.05    & 0.10    & 0.13    & 0.26 \\
+Ca I   & 0.06    & 0.03    & 0.04    & 0.03    & 0.08    & 0.24 \\
+Sc II  & 0.02    & 0.05    & 0.01    & 0.04    & 0.06    & 0.30 \\
+Ti I   & 0.11    & 0.01    & 0.06    & 0.07    & 0.15    & 0.11 \\
+Ti II  & 0.02    & 0.04    & 0.04    & 0.04    & 0.07    & 0.27 \\
+V I    & 0.11    & 0.01    & 0.03    & 0.06    & 0.13    & 0.12 \\
+Cr I   & 0.11    & 0.02    & 0.06    & 0.06    & 0.14    & 0.19 \\
+Cr II  & 0.01    & 0.05    & 0.02    & 0.15    & 0.16    & 0.26 \\
+Mn I   & 0.09    & 0.03    & 0.04    & 0.11    & 0.15    & 0.22 \\
+Fe I   & 0.08    & 0.00    & 0.04    & 0.02    & 0.09    & \nodata \\
+Fe II  & 0.01    & 0.05    & 0.01    & 0.05    & 0.07    & \nodata \\
+Co I   & 0.11    & 0.01    & 0.08    & 0.12    & 0.19    & 0.01 \\
+Ni I   & 0.07    & 0.01    & 0.04    & 0.05    & 0.09    & 0.13 \\
+Cu I   & 0.11    & 0.01    & 0.04    & 0.10    & 0.15    & 0.10 \\
+Zn I   & 0.01    & 0.03    & 0.03    & 0.10    & 0.11    & 0.21 \\
+Sr II  & 0.03    & 0.00    & 0.01    & 0.10    & 0.10    & 0.11 \\
+Y II   & 0.02    & 0.05    & 0.01    & 0.25    & 0.26    & 0.17 \\
+Ba II  & 0.02    & 0.02    & 0.05    & 0.08    & 0.10    & 0.17 \\
+Nd II  & 0.05    & 0.05    & 0.02    & 0.10    & 0.12    & 0.30
 \enddata
-\end{deluxetable}
-
-\section{Abundances}
+\tablenotetext{}{Table \ref{tab:chemical-abundance-uncertainties} is published for all program stars in the electronic edition. A portion is shown here for guidance regarding its form and content.}
+\end{deluxetable*}
 
 \section{Discussion}
+\label{sec:discussion}
 
-\section{Results}
+\subsection{Stream Membership}
+
+Given the low surface brightness of the Orphan Stream, separating true members from halo interlopers can be particularly challenging.
+In this study we have observed high, medium, and low-probability stream members as described in \citet{casey;et-al_2013a}.
+Before inferring any properties of the undiscovered parent satellite from our sample, we must examine whether our targets are likely to be true disrupted Orphan Stream members.
+
+When compared against the mean of our high-priority targets, the velocities of the low- and medium-probability candidates are +6.2 and $-23.7$\,km s$^{-1}$ different, respectively.
+Given this region of the stream has a low intrinsic velocity dispersion \citep{newberg;et-al_2010,casey;et-al_2013a}, the significantly lower velocity of the medium-probability target, OSS 18, is intriguing.
+Perhaps more concerning is that the low- and medium-probability candidates are markedly more metal-rich than the high-priority targets: [Fe/H] = $-0.86$ and $-0.62$\,dex for OSS 3 and 18, a difference of $+0.45$ and $+$0.28\,dex respectively from the low-resolution spectroscopic determinations.
+Spectroscopic studies suggest the stream is significantly more metal-poor than [Fe/H] $\sim -0.8$\,dex \citep{newberg;et-al_2010,casey;et-al_2013a,sesar;et-al_2013}.
+The metallicities found from low-resolution spectroscopy by \citet{casey;et-al_2013a} were inferred under the assumption that the candidates were $\sim$20\,kpc away.
+Therefore, metallicities that are higher than expected are consistent with the targets being notably closer, making their association with the Orphan Stream tenuous.
+It is also worth noting that these targets are the farthest candidates ($|B_{\rm Orphan}| \sim 0.5$\,$^\circ$) from the best-fit Orphan Stream orbital plane deduced by \citet{newberg;et-al_2010}.
+
+The three high-probability targets have velocities within 2.4\,km s$^{-1}$ of each other, consistent with the Orphan Stream velocities, as well as the low velocity dispersion observed in the stream.
+The metallicities of these targets are also in reasonable agreement with those found from low-resolution spectroscopy, implying the candidates are $\sim$20\,kpc away at approximately the same distance as the Orphan Stream.
+
+Given a stream this distant, proper motions can only be utilised to positively exclude stream members, as high or statistically significant proper motions would suggest a nearby interloper.
+On the basis of the observable data we can deduce that the lower probability members, OSS 3 and OSS 18, are unlikely disrupted Orphan Stream members.
+For the remainder of this discussion, we consider OSS 6, 8 and 14, to be true disrupted members of the Orphan Stream satellite.
+These stars are identifiable by an encapsulated circle around every marker in all figures throughout this text.
+
+\subsection{Stream Chemistry}
+
+% Points:
+% + Stream has a wide range in metallicity.
+% + The stream has low [alpha/Fe] w.r.t to the halo of the same metallicity
+%	-> low [alpha/Fe] characteristically observed in dwarf galaxies, and high [alpha/Fe]'s generally seen in globular clusters.
+%	-> This should not be used as a litmus test.
+%	-> Some dSph's have a large range in [alpha/Fe]'s, extending up to typical values seen in field stars.
+%	-> Abundances indicate that SN Ia did not start to contribute until after [Fe/H] > -1.7 dex (in the Galaxy it occurred ~ -1).
+%	-> Thus, [alpha/Fe] element abundances suggest a dwarf spheroidal progenitor.
+% + The alpha-process occurs when neutron-rich, alpha-rich gas is out of nuclear statistical equilibrium, and has been identified as a possible site for light r-process element production.
+%	-> If true, then if alpha-process contributes to [alpha/Fe] and light r-process in the Galaxy, but not in dSph's, lower [alpha/Fe] and [Y/Eu] expected.
+%	-> We are only able to ascertain upper limits for [Y/Eu] in our stream stars, which show them to be lower than halo stars at the same metallicity. 
+%	-> 
+\subsubsection{Metallicity Distribution Function}
+Although the sample size is small, the three Orphan Stream members have a wide range in metallicity, ranging from $-1.58$ to as metal-poor $-2.66$\,dex.
+From three members not much can be said about the metallicity distribution function (MDF), other than to say it is wide, and inconsistent with a mono-metallic population.
+Although we believe all 3 stars are disrupted Orphan Stream members, the likelihood of a halo interloper is non-zero, but unlikely to be more more than one candidate.
+Stars as metal-poor as OSS 14 (with [Fe/H] = $-2.66$) in the halo are somewhat uncommon.
+If we apply the color selection of \citet{casey;et-al_2013} to models of the Milky Way, we find the likelihood that OSS 14 -- our most metal-poor stream member -- is X with the Besan\c{c}on model and Y with the GALAXIA model \citep{robin;et-al_2013, sharma;et-al_2012}.
+Finding stars around [Fe/H] $\sim -1.7$ is more likely, but assuming OSS 14 is a true Orphan Stream member and we have a maximum of one halo interloper, we can report a wide metallicity range in the Orphan Stream.
+This is consistent with the low-resolution spectroscopic study of \citet{casey;et-al_2013a}, which has been recently confirmed with observations of BHB stars by \citet{sesar;et-al_2013}.
+
+The Orphan Stream stars have low [$\alpha$/Fe] abundance ratios ($\sim$0.22) with respect to the Milky Way sample ($\sim$0.40\,dex).
+The two Orphan candidates that we deduced to be field interlopers also have low [$\alpha$/Fe] ratios than their Milky Way counterparts of a similar metallicity.
+However, these stars are consistent with the spread in [$\alpha$/Fe] abundances observed in the halo as a result of Type Ia supernovae beginning to significantly contribute to the halo chemistry near [Fe/H] $\sim$ -1 dex.
+
+\subsubsection{$\alpha$-element abundance ratios}
+In the dSph galaxies, Type Ia supernovae begin to show a significantly contribution to the [$\alpha$/Fe] abundances near [Fe/H] $> -1.7$\,dex,  with the exception of Draco which shows low [$\alpha$/Fe] at all metallicities.
+Some dwarf spheroidal stars also have a large range in [$\alpha$/Fe] values, increasing up to typical values seen in field stars.
+Additionally, the thick disk is known to comprise of both a high-$\alpha$ and low-$\alpha$ population.
+Thus, although low [$\alpha$/Fe] abundance ratios have characteristically been observed in dwarf galaxy stars, an [$\alpha$/Fe] abundance ratio should not be used as a litmus test for accretion.
+Given these stars are believed to be Orphan Stream members already, we can say that our [$\alpha$/Fe] abundance ratios are consistent with the star formation environment of a typical Milky Way dwarf galaxy.
+
+\subsubsection{[Ba/Y]}
+
+\begin{figure}[h]
+	\includegraphics[width=\columnwidth]{./Ba-Y.pdf}
+	\caption{Ba-Y.}
+	\label{fig:ba-y}
+\end{figure}
+
+% Peculiar chemical signatures
+\subsection{Possible Parent Systems}
+A number of associations have been proposed between the Orphan Stream and known Milky Way satellites.
+However, most have been shown to be either unlikely or implausible.
+Although Segue 1 has appeared as the most likely (known) satellite, a link with the globular cluster NGC 2419 has also been proposed \citet{bruens;et-al_2011}.
+Here we discuss the possibility of these associations in light of the data presented here.
+
+\subsubsection{NGC 2419}
+The width and length of a tidal tail are a clear indication to the nature of the parent satellite.
+For the case of the Orphan Stream, these characteristics favour a dwarf satellite.
+However, given the large apogalacticon of 90\,kpc for the Orphan Stream, a relationship has been proposed with the distant -- yet luminous -- globular cluster NGC 2419, also at $\sim90$\,kpc.
+Stars in globular clusters are known to exhibit peculiar chemical patterns, most notably in an anti-correlation between sodium and oxygen abundances.
+NGC 2419 is particularly special because it shows an unusual anti-correlation between magnesium and potassium.
+This signature is so far unique to NGC 2419, and illustrates the most extreme cases of Mg-depletion and K-enhancement seen anywhere in the Milky Way or its satellite systems.
+
+% Ni and Na/Fe abundances?
+
+We do not find any of our Orphan Stream stars to be extremely depleted in [Mg/Fe] or enhanced in [K/Fe], as found in NGC 2419 by \citet{coco;et-al}.
+If we follow the \citet{who} nomenclature and consider two `populations' in NGC 2419: a Mg-poor, K-rich and  a Mg-normal, K-poor sample, then a simple K-S test demonstrates that we can be X\% confident that the Orphan Stream members are not drawn from the Mg-poor NGC 2419 population.
+We cannot make such statements about the Mg-normal population, since they are typical for the Milky Way.
+The Mg-poor and Mg-normal sub-populations each comprise about 50\% of the total NGC 2419 sample.
+Given the uniqueness of the Mg-K anti-correlation, a single Orphan Stream star with significant Mg-depletion or K-enhancement would have provided an exciting hint for the Orphan Stream parent.
+In any case, the Orphan Stream's large metallicity spread indicates that the stream is unlikely to be associated with NGC 2419, given the cluster's small dispersion in overall metallicity.
+We therefore firmly rule out any association between NGC 2419 and the Orphan Stream.
+
+\begin{figure}[h]
+	\includegraphics[width=\columnwidth]{./Mg-K.pdf}
+	\caption{Magnesium and potassium abundances for stars in the globular cluster NGC 2419 from \citet{cohen;et-al} ($\vartriangle$) and \citet{mucciarelli;et-al} ($\triangledown$).
+Program stars and Orphan Stream candidates are shown with the same markers used in Figure \ref{fig:alpha-fe}.}
+	\label{fig:mg-k}
+\end{figure}
+
+\subsubsection{Segue 1}
+The only known satellite system with an unclear association with the Orphan Stream is Segue 1.
+Segue 1 lies close to the perigalacton of the Orphan Stream.
+The original discovery by \citet{belokurov;et-al_2007a} suggested the system was an extended globular cluster, until the spectroscopic survey by \citet{simon;et-al_2011} showed the system was a dark-matter dominated dwarf galaxy.
+It's on-sky position lies a mere X degrees from the Orphan Stream plane, and ~Y degrees from the celestial equator cutoff of the Orphan Stream.
+
+% velocity dispersion
+Segue 1 has a very low velocity dispersion, less than 4\,km s$^{-1}$.
+In the closest part of the Orphan Stream, \citet{casey;et-al_2013} and \citet{newberg;et-al_2010} measured a similarly low velocity dispersion from different Orphan stream samples.
+The galactocentric velocity of the closest part of the stream (X\,$^\circ \Lambda_{\rm Orphan}$, $V_{\rm gsr} = $?
+\,km s$^{-1}$) matches Segue 1 almost identically ($V_{gsr} = ?$\,km s$^{-1}$).
+
+The characteristics of the stream are clues to the nature of its progenitor: the arc length and intrinsic width suggests the parent system must be dark matter dominated.
+Similarly, Segue 1 is the most dark matter-dominated system known.
+This fact alone has motivated several groups () to search for direct evidence of dark matter annihilation within Segue 1.
+Their observations place upper limits of Z, consistent with some of the most precise dark matter estimates from theory () and velocity dispersion observations ().
+The similarities between Segue 1 and the undiscovered parent of the Orphan Stream are striking.
+However, there is some doubt as to whether Segue 1 has experienced any tidal effects ().
+
+% Metallicity gradient? Maybe after next paragraph
+
+The chemistry of Segue 1 is particularly relevant.
+Segue 1 hosts an extremely wide range in stellar metallicities: from X to Y dex.
+\citet{simon;et-al_2011} and \citet{norris;et-al_2010} demonstrated the mean to be [Fe/H] = Z, with a spread of X.
+Some of the most metal-poor stars in Segue 1 extremely carbon enhanced ([C/Fe] > Z) and show no enhancement of neutron capture elements.
+From low-resolution spectroscopy, \citet{casey;et-al_2013a} found the Orphan Stream to have an intrinsic metallicity spread of $\sigma([$Fe/H]$) = 0.56$\,dex, with candidates ranging from [Fe/H] = X to Y dex.
+This level of carbon enhancement is reminiscent of the Milky Way halo, further suggesting the dwarf spheroidal galaxies are the building blocks of the Galaxy.
+In our three Orphan Stream members we confirm a wide range in metallicities, but not to the same extent observed by \citet{norris;et-al_2010} and \citet{simon;et-al_2011} in Segue 1.
+Our most metal-poor member has [Fe/H] = -2.66 and [C/Fe] = X.
+
+% Does the fact that CEMP-no stars exist suggest the more metal-rich stars should not be particularly over-abundant in neutron-capture elements?
+
+% on sky position?
+% ships in the night
+% velocity dispersion
+
+% Extent of metallicities?
+% [C/Fe]
+% [alpha/Fe]
+% [Ba/Y], [Eu/Y]
+
+% [Ba/Y] offset in dSph and halo stars seen by Shetrone (2003) and Venn (2004)
+% large mass stars responsible for production of Sr, Y, Zr.
+Truncating the IMF at the high end would reduce these abundances and reduce the overall [alpha/Fe] because higher mass stars are expected to produce higher [alpha/Fe].
+Explained in Shetrone (2003).
+Used by Smith (2002) for LMC stars.
+
+\begin{figure}[h]
+	\includegraphics[width=\columnwidth]{./heavy-Fe.pdf}
+	\caption{$s$-process abundance ratios for standard halo and Orphan Stream candidates. Upper limits are indicated where no measurements were available.}
+	\label{fig:heavy-fe}
+\end{figure}
+
+% Extent of metallicities?
+% [C/Fe]
+% [alpha/Fe]
+% [Ba/Y], [Eu/Y]
+
+% Plausible associations:
+% - NGC 2419
+% - Segue 1
 
 \section{Conclusions}
+\label{sec:conclusions}
+
+We present a chemical analysis of five Orphan stream candidates, three of which we confirm are true disrupted members from the Orphan stream parent satellite.
+The two non-members were both originally identified to have `low' or `medium' probability of membership from low-resolution spectroscopy.
+The three disrupted members show chemical distinctiveness from the halo at the same metallicity, suggesting the stars were accreted.
+A large metallicity spread is present, further implying the Orphan Stream parent is not mono-metallic.
+The spread in overall metallicity is representative of the stochastic chemical enrichment observed in the Milky Way dwarf spheroidal galaxies.
+Detailed chemical abundances confirm this proposition.
+On the basis of chemistry, we exclude the extended globular cluster NGC 2419 as a plausible parent to the Orphan Stream, and conclude that Segue 1 remains the most likely {\it known} satellite.
+It is entirely possible that the parent satellite has not been found.
+Deep, wide multi-band photometry surrounding the edge of the Orphan Stream near the celestial equator would resolve this outstanding problem.
+Furthermore, we postulate that follow-up high-resolution spectroscopy of the remaining six high probability members would further demonstrate the Orphan stream's chemical distinctiveness from the halo.
+
+\acknowledgements
+A.R.C.
+acknowledges the financial support through the Australian Research Council Laureate Fellowship LF0992131.
+SK and GDaC acknowledge the financial support from the Australian Research Council through Discovery Programs DP0878137 and DP120101237.
 

### 2013-08-13 2012-oss-hrs/load_data.py

@@ -1,0 +1,379 @@
+import os
+import numpy as np
+
+
+def get_venn_data(filename):
+
+    with open(filename, 'r') as fp:
+        contents = fp.readlines()
+
+
+    # Skip first 43 lines
+    del contents[:43]
+
+    # Skip the name (first 10) and reference (135+) in each line
+    contents = [map(float, line[11:134].split()) for line in contents]
+    
+    keys = (
+            'U', 'V', 'W', 'Tn', 'Tk', 'Ha', 'Gind',
+            '[Fe/H]', '[Mg/Fe]', '[Ca/Fe]', '[Ti/Fe]',
+            '[a/Fe]', '[Na/Fe]', '[Ni/Fe]', '[Y/Fe]',
+            '[Ba/Fe]', '[La/Fe]', '[Eu/Fe]'
+            )
+
+    data = {}
+    for i, key in enumerate(keys):
+        data[key] = np.array([line[i] for line in contents])
+
+    # Assign star to each component
+    assigned_component = []
+    possible_components = ('Thin', 'Thick', 'Halo', 'dSph')
+
+    probabilities = np.array([data['Tn'], data['Tk'], data['Ha']]).T
+    for i, probability in enumerate(probabilities):
+
+        if np.max(probability) > 0:
+            max_prob_index = int(np.argmax(probability))
+
+        else:
+            max_prob_index = 3
+
+        # Overwrite components
+        if max_prob_index != 3 and data["V"][i] < -200:
+            # Retro
+            assigned_component.append("Retro")
+
+        elif max_prob_index != 3 and (data["U"][i]**2 + data["W"][i]**2)**0.5 > 350:
+            # High velocity halo
+            assigned_component.append("High")
+
+        else:
+            assigned_component.append(possible_components[max_prob_index])
+
+    data['component'] = assigned_component
+
+    return data
+
+
+
+
+def plot_venn_data(data, ax, x_column, y_column=None, y_data=None):
+
+    if y_column is None and y_data is None: raise TypeError
+
+    scatter_args = {
+        "Thin": {
+            "marker": "o",
+            "facecolor": "#e62d24",
+            "edgecolor": "#e62d24",
+            "alpha": 0.4,
+        },
+        "Thick": {
+            "marker": "o",
+            "facecolor": "#6fc06a",
+            "edgecolor": "#6fc06a",
+            "alpha": 0.4,
+        },
+        "Halo": {
+            "marker": "o",
[…]

### 2013-08-13 2012-oss-hrs/make-plots.py

@@ -1,313 +1,175 @@
-import os
-import numpy as np
 
-import matplotlib.pyplot as plt
+from load_data import *
 
-def load_abundances(filename, minimum_uncertainty=0.05):
-    """Loads the [X/H] and [X/Fe] abundance ratios and uncertainties
-    for a single star from the filename provided."""
+font = {'family' : 'normal',
+        'weight' : 'normal',
+        'size'   : 17}
 
-    if not os.path.exists(filename):
-        raise IOError("file does not exist (%s)" % (filename, ))
+matplotlib.rc('font', **font)
 
-    if not np.isfinite(minimum_uncertainty) or minimum_uncertainty < 0:
-        raise ValueError("minimum uncertainty must be a positive finite value")
+program_stars_scatter_args = {
+    "facecolor": "w",
+    "marker": "s",
+    "edgecolor": "k",
+    "lw": 2,
+    "zorder": 10,
+    "s": 50
+}
 
-    abundances = {}
-    uncertainties = {}
-    limits = {}
+program_stars_not_OSS_scatter_args = {
+    "marker": "x",
+    "zorder": 10,
+    "edgecolor": "k",
+    "s": 50 
+}
 
-    with open(filename, "r") as fp:
-        content = fp.read().split("\n")
-
-        for line in content:
-            if line.startswith("#") or line.startswith("%") or len(line) == 0: continue
-
-            line = line.replace("&", "").replace("_nodata", "nan").rstrip("\\").rstrip("&")
-            if line.split()[0] == "C":
-                element, transition = ("C", "(CH)", )
-                n_lines, log_eps, sigma_eps, x_on_h, x_on_fe, uncertainty = line.split()[2:]
-                limit = False
-
-            else:
-                line_split = line.split()
-                if len(line_split) > 6:
-                    element, transition, n_lines, log_eps, sigma_eps, x_on_h, x_on_fe, uncertainty = line_split
-                    limit = False
-
-                else:
[…]

### 2013-08-13 2012-oss-hrs/plot-mg-k.py

@@ -1,0 +1,30 @@
+import numpy as np
+
+
+mucciarelli_headers = 'ID Teff logg vt [Fe/H] [Fe/H]_err [Mg/Fe] [Mg/Fe]_err [K/Fe] [K/Fe]_err [Ti/Fe] [Ti/Fe]_err [Ca/Fe] [Ca/Fe]_err'
+
+mg_fe, mg_fe_err, k_fe, k_fe_err = range(4)
+mucciarelli_columns = ['[Mg/Fe]', '[Mg/Fe]_err', '[K/Fe]', '[K/Fe]_err']
+
+mucciarelli_column_indices = [mucciarelli_headers.split().index(item) for item in mucciarelli_columns]
+mucciarelli = np.loadtxt('ngc2419-mucciarelli.txt', usecols=mucciarelli_column_indices)
+
+fig = plt.figure()
+fig.subplots_adjust(left=0.10, right=0.95, bottom=0.07, wspace=0, hspace=0.14, top=0.95)
+ax = fig.add_subplot(111)
+
+ax.errorbar(mucciarelli[:, mg_fe], mucciarelli[:, k_fe], xerr=mucciarelli[:, mg_fe_err], yerr=mucciarelli[:, k_fe_err], fmt=None, ecolor='k')
+ax.scatter(mucciarelli[:, mg_fe], mucciarelli[:, k_fe], facecolor='k', edgecolor='k', label='Mucciarelli et al. (DEIMOS; 2012)')
+
+# Cohen data
+cohen = np.loadtxt('ngc2419-cohen.txt', usecols=(1,2,3,4, ))
+
+ax.errorbar(cohen[:, mg_fe], cohen[:, k_fe], xerr=cohen[:, mg_fe_err], yerr=cohen[:, k_fe_err], fmt=None, ecolor='g')
+ax.scatter(cohen[:, mg_fe], cohen[:, k_fe], marker='s', edgecolor='g', facecolor='g', label='Cohen et al. (HIRES; 2011, 2012)')
+
+
+ax.set_ylabel('[K/Fe]')
+ax.set_xlabel('[Mg/Fe]')
+
+ax.legend(loc=3)
+

### 2013-08-13 2012-aqs/dotter_isochrones/ms.tex
Aquarius updated.

% revised and shortened version
\documentclass[preprint,12pt]{aastex}

\shorttitle{Kinematics of Tidal Debris}
\shortauthors{Mizutani et~al.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\title{Kinematics of Tidal Debris from Omega Centauri's
       Progenitor Galaxy}

\author{Arihiro Mizutani\altaffilmark{1},
        Masashi Chiba\altaffilmark{2},
    and Tsuyoshi Sakamoto\altaffilmark{1}}

\altaffiltext{1}{Department of Astronomical Science, The Graduate University
for Advanced Studies, Mitaka, Tokyo 181-8588, Japan;
mizutnar@cc.nao.ac.jp}
\altaffiltext{2}{National Astronomical Observatory, Mitaka, Tokyo 181-8588,
Japan}

%%%%%% Abstract %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
We present the kinematic properties of a tidally disrupted dwarf galaxy in the
Milky Way, based on the hypothesis that its central part once contained the
most massive Galactic globular cluster, $\omega$ Cen. Dynamical evolution of
a self-gravitating progenitor galaxy that follows the present-day and likely
past orbits of $\omega$ Cen is calculated numerically and the kinematic nature
of their tidal debris is analyzed, combined with randomly generated stars
comprising spheroidal halo and flat disk components. We show that the retrograde
rotation of the debris stars at $\sim -100$ km~s$^{-1}$ accords with a recently
discovered, large radial velocity stream at $\sim 300$ km~s$^{-1}$ towards the
Galactic longitude of $\sim 270^\circ$. These stars also contribute, only in
part, to a reported retrograde motion of the outer halo at the North Galactic
Pole. The prospects for future debris searches and the implications for the
early evolution of the Galaxy are briefly presented.
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\keywords{Galaxy: formation --- globular clusters: individual
($\omega$ Centauri) --- stars: kinematics}

%%% Sec.1 %%%
\section{INTRODUCTION}

Omega Centauri, the most massive globular cluster in the Milky Way,
is unique in terms of its metallicity content, internal kinematics, and
structure. Unlike other Galactic globular clusters, $\omega$ Cen shows
a wide spread in metallicity (e.g. Norris, Freeman,
\& Mighell 1996), with a main metal-poor component at [Fe/H]$\simeq -1.6$,
a second smaller peak at [Fe/H]$\simeq -1.2$, and a long tail extending
up to [Fe/H]$\simeq -0.5$. The metal-rich population holds
a low velocity dispersion and no sign of rotation, in contrast to the rotating
metal-poor population.
Furthermore, the metal-rich stars in $\omega$ Cen are largely enhanced
in $s$-process elements relative to those in globular clusters and
field stars with similar metallicities (e.g. Norris \& Da~Costa 1995),
thereby suggesting that the ejecta from low-mass,
asymptotic giant branch (AGB) stars had to be retained and incorporated
into the next-generation stars.

In spite of its large mass ($5\times 10^6$ M$_\odot$), it has been
demonstrated by Gnedin et al. (2002) that $\omega$ Cen is not unique in
its ability to retain the AGB ejecta as found for other
clusters. An isolated formation of $\omega$ Cen is thus unlikely, because the
enriched gas would easily be lost by encountering the Galactic disk. The most
viable explanation for the uniqueness of $\omega$ Cen is that it was once
the dense nucleus of a dwarf galaxy (Freeman 1993). A gravitational
potential provided by progenitor's stellar system and dark matter
(as suggested from dwarf spheroidal galaxies in the Local Group, Mateo 1998)
would help retaining the enriched gas and let the cluster being self-enriched
at least over a few Gigayears.

If this hypothesis is the case for the origin of $\omega$ Cen, the question
arises: {\it where and in what form does the stellar system of its progenitor
galaxy remain?} Dinescu (2002) first investigated this issue,
by examining the possible signature of the progenitor's tidal debris among
nearby metal-poor stars in the catalog of Beers et al. (2000, B00).
She identified a group of stars with $-2.0<$[Fe/H]$\le-1.5$, which
departs from the characteristics of the inner Galactic halo but has
retrograde orbits similar to $\omega$ Cen. Her simplified disruption model of
the progenitor galaxy demonstrated that trailing tidal debris, having
orbital characteristics similar to the cluster, can be found in the solar
neighborhood, although the concrete spatial distribution and kinematics
of the debris stars remain yet unclear.

This work motivates us to conduct an N-body simulation for the tidal
disruption of $\omega$ Cen's progenitor galaxy, to obtain the
characteristic structure and kinematics of its debris stars and compare
with various observations showing signatures of recent merging events
in the Milky Way (Gilmore, Wyse, \& Norris 2002, GWN; Kinman et al. 2002,
K02; Chiba \& Beers 2000, CB).
In particular, we show that a recently identified stream of stars at
heliocentric radial velocity of $\sim 300$ km~s$^{-1}$ (GWN) is a natural
outcome of the current disruption model, without affecting
local halo kinematics near the Sun and microlensing optical depth towards
the Large Magellanic Cloud (LMC).

%%% Sec.2 %%%
\section{SIMPLE DYNAMICAL MODEL OF A PROGENITOR GALAXY}

We calculate the dynamical evolution of an orbiting dwarf galaxy in a fixed
external gravitational potential representing the Milky Way. The potential
consists of three parts: a spherical Hernquist bulge
$\Phi_b(r)$, a Miyamoto-Nagai disk $\Phi_d (R,z)$, and a logarithmic
dark halo $\Phi_h(r)$, where $r$ is the Galactocentric distance and
$(R,z)$ denote cylindrical coordinates. Each is given as,
$\Phi_b (r) = - GM_b/(r+a)$, $\Phi_d(R,z) =
- GM_d/\sqrt{R^2+(b+\sqrt{z^2+c^2})^2}$,
and $\Phi_h(r) = v_h^2 /2 \ln(r^2+d^2)$,
where $M_b=3.4\times 10^{10}$ M$_\odot$, $a=0.7$ kpc,
$M_d=10^{11}$ M$_\odot$, $b=6.5$ kpc, $c=0.26$ kpc, $v_h=186$ km~s$^{-1}$,
and $d=12$ kpc. This choice yields a circular velocity
of 228 km~s$^{-1}$ at the solar circle of $R_\odot=8$ kpc and a flat
rotation curve outside $R_\odot$.

We set self-gravitating particles in the dwarf galaxy following a King
model, where the central density, central velocity dispersion, and core radius
are given as 0.3 M$_\odot$~pc$^{-3}$, 18.1 km~s$^{-1}$, and 0.56 kpc,
respectively. In addition, a particle with the mass of $5 \times 10^6$
M$_\odot$ representing $\omega$ Cen is placed at the center of the
galaxy to trace its orbit. This setting yields the total mass of the galaxy as
$M_{tot}=5.79 \times 10^8$ M$_\odot$. A part of the mass is provided by
stars, which is roughly estimated from the mean metallicity of
stars in $\omega$ Cen ($\langle$[Fe/H]$\rangle\sim-1.6$), combined
with the metallicity-luminosity relation for the Local Group dwarfs
(C\^{o}t\'{e} et al. 2000) and the mass-to-light ratio (assuming $M/L \sim 4$
obtained for $\omega$ Cen, Meylan et al. 1995),
yielding $M_{stars}\sim 10^7$ M$_\odot$. Thus, our model galaxy
is largely dominated by a dark component, in agreement with the observed
large $M/L$ in dwarfs (Mateo 1998). The galaxy is
represented by a collection of $10^4$ particles and the self-gravity is
calculated in terms of a multiple expansion of the internal potential to
fourth order (Zaritsky \& White 1988).

In the course of its orbital motion, a dwarf galaxy is disrupted by
Galactic tides, whereas its dense core is expected to survive and follow
$\omega$ Cen's orbit. While our calculation in a fixed Galactic
potential neglects dynamical friction against progenitor's orbit, the effect
is only modest for the system of $\la 10^8$~M$_\odot$ (Zhao 2002), especially
during a few orbital periods required for tidal disruption.
We thus examine two representative orbits for the progenitor, model 1
and 2: model 1 follows the current orbit of $\omega$ Cen, whereas for model 2,
we calculate an orbit back to the past over $\sim 2$ Gyr from its current
position and velocity by fully taking into account dynamical friction
and then set a progenitor galaxy on its non-decaying orbit. These two models
provide us with satisfactory information on the generic properties of a tidally
disrupted progenitor and we postulate that the realistic nature of their debris
is midway between these model predictions.
We calculate $\omega$ Cen's orbit, based on the distance\footnote{We estimate
this distance, based on the Harris (1996) data and the relation between
absolute magnitude of cluster horizontal branch and metallicity derived by
Carretta, Gratton, \& Clemintini (2000).} from the Sun $D=5.3 \pm 0.5$ kpc,
position $(l,b)=(309^\circ,15^\circ)$, proper motion
$(\mu_\alpha \cos\delta,\mu_\delta) =(-5.08\pm0.35, -3.57\pm0.34)$
mas~yr$^{-1}$, and heliocentric radial velocity $v_{los} = 232.5 \pm 0.7$
km~s$^{-1}$ (Dinescu, Girard, \& van Altena 1999).
This orbit for model 1 is characterized by frequent disk crossings with a period
of $\tau_{orb} = 0.8 \times 10^8$ yr, retrograde motion, and apo and pericentric
distances $(r_{apo},r_{peri}) = (6.4, 1.1)$ kpc. For model 2,
we obtain $\tau_{orb} = 1.5 \times 10^8$ yr and
$(r_{apo},r_{peri}) = (11.3, 3.0)$ kpc. 
In both experiments, we adopt the same progenitor mass $M_{tot}$ and place it
at apocenter to maximize its survival chances\footnote{For model 1, this initial
mass may be too large as an as-yet-undisrupted galaxy (Zhao 2002), so the debris
density in model 1 can be overly represented.}.

Figure 1 shows the spatial distribution of the tidally disrupted debris.
Upper (middle) panel shows model 1 (model 2) after the 1.37 (1.86) Gyr orbital
excursion of the progenitor galaxy. Lower panel shows the orbit of the galaxy
center. In the course of the orbital motion of the
galaxy, its structure is made elongated along the orbit induced by Galactic
tides, in particular at its pericenter passages, and then the particles are
spread out to form the tidal streams along the orbit.
A rosette-like feature of the debris becomes steady after about eight orbital
periods. Model 1 results in more compact distribution than model 2, which
reflects the difference in orbital radii.

Figure 2 shows the velocity distributions of the debris particles in
cylindrical coordinates $(v_R,v_\phi,v_z)$.
As is evident, model 1 and 2 provide essentially the same debris kinematics:
most remarkable is a sharply peaked $v_\phi$ distribution at
$\sim -100$ km~s$^{-1}$, arising from a retrograde orbit of a progenitor.
These kinematics suggest that the difference in model 1 and 2 resides only
in the spatial extent of the debris.

%%% Sec.3 %%%
\section{EFFECTS OF DEBRIS ON GALACTIC KINEMATICS}

\subsection{Method for kinematic analysis}

In order to assess the reality of the debris stars in light of observed
stellar kinematics in the Milky Way, we analyze the kinematics of
both the simulated debris and other Galactic stars
generated randomly by a Monte Carlo method. The metal-poor halo
is modeled as a flattened spheroid $\rho \propto
(R^2 + z^2/q^2)^{-3.5/2}$, where $q$ is an axis ratio ranging 0.55-0.7,
anisotropic velocity ellipsoid $(\sigma_R,\sigma_\phi,\sigma_z)=(154,121,96)$
km~s$^{-1}$, and small mean rotation $\langle v_\phi \rangle= 24$ km~s$^{-1}$,
as found for halo stars with [Fe/H]$<-2$ near the Sun (CB).
Thin and thick disks are modeled as $\rho \propto
\exp(-R/R_d) \sec^2 (z/z_d)$, where $R_d=3.5$ kpc and $z_d=0.3$ (1)
kpc for thin (thick) disk. Both disks
rotate at 200 km~s$^{-1}$, having velocity ellipsoids of
$(34,25,20)$ km~s$^{-1}$ and $(46,50,35)$ km~s$^{-1}$ for thin and thick
disks, respectively (CB). The relative fraction of each
component is fixed using observed local densities near the Sun,
in such a manner that the halo and thick-disk densities at
$D<1$ kpc are 0.2~\% and 2~\% of the thin-disk density,
respectively (e.g. Yamagata \& Yoshii 1992).

In our model of $\omega$ Cen's progenitor galaxy, the self-gravitating
particles represent both stars and dark matter. We note that a correct estimate
for the fraction of stars is uncertain, because their $M/L$ ratio as well as
the amount of dark matter in the progenitor is unavailable. As a useful method
to incorporate this ambiguity for the current kinematic analysis, we set a
parameter $f$ as the fraction of the debris particles relative to halo stars
near the Sun, {\it when all of the particles are regarded as stellar ones}.
By this, the normalization of the halo density is obtained for the given debris
particles.

A typical value of $f$ for the conversion of the simulated particles to
the stars is estimated in the following manner. Model 1 (model 2) yields
21 (74) particles at $D < 2$ kpc, giving the mass density of
$\rho_g = 0.4 (1.3) \times 10^{-4}$ M$_\odot$~pc$^{-3}$ near
the Sun, whereas the total mass density and
metal-poor halo density have been derived as
$8 \times 10^{-3}$ M$_\odot$~pc$^{-3}$ (Gates, Gyuk, \& Turner 1995) and
$6.4 \times 10^{-5}$ M$_\odot$~pc$^{-3}$ (Gould, Flynn, \& Bahcall 1998),
respectively.
Then, if the debris stars (with $M_{stars} \sim 10^7$ M$_\odot$)
are distributed in the same manner as the simulated particles (with
$M_{tot} =5.74 \times 10^8$ M$_\odot$), which would be a reasonable
approximation in view of the dissipationless nature of stars,
the mass density of the debris stars in the solar neighborhood can be
estimated as $(M_{stars}/M_{tot}) \rho_g = O(10^{-6})$
M$_\odot$~pc$^{-3}$, which is about 1~\% of the halo density.
Thus, $f$, defined here as debris fraction at $D<2$ kpc,
is expected to be of order of a few percents.

\subsection{GWN's radial velocity survey}

Recently, GWN reported a spectroscopic survey of
$\sim 2000$ F/G stars down to $V = 19.5$ mag, in the direction
against Galactic rotation $(l,b)=(270^\circ,-45^\circ)$ and $(270^\circ,
+33^\circ)$, where radial velocities, $v_{los}$, in combination with distances
largely reflect orbital angular momentum. The $v_{los}$ distribution of the
stars a few kpc from the Sun shows two stellar streams
at $v_{los}\sim 100$ km~s$^{-1}$ and $\sim 300$ km~s$^{-1}$, which are not
explained by known Galactic components.
While the stream at $v_{los} \sim 100$ km~s$^{-1}$ was reproduced by
their model of a merging satellite in prograde rotation,
the stream at $v_{los}\sim 300$ km~s$^{-1}$ remains yet unexplained.

Figure 3a shows the $v_{los}$ distribution for the
debris stars of model 2 and halo stars of $q=0.7$ (i.e. without disks)
at $1<D<5$ kpc, $260^\circ<l<280^\circ$, and two fields for $b$.
Figure 3b shows when disk stars are incorporated. As is evident,
the debris stars from $\omega$ Cen's progenitor form a local peak
at $v_{los}\sim 300$ km~s$^{-1}$, which is provided by many stars having
$v_\phi \sim -100$ km~s$^{-1}$. This is in good
agreement with the $v_{los}\sim 300$ km~s$^{-1}$ stream discovered by GWN.
A more flattened halo than the case $q=0.7$ yields a higher peak,
since the density contrast of
the debris relative to halo is made higher in this survey region.
It is worth noting that model 1 yields essentially the same $v_{los}$
distribution as model 2, reflecting the same velocity distribution,
although to attain the same peak height at $\sim 300$ km~s$^{-1}$,
$f$ be a few factor larger and the selected range of $l$ be a few degree
higher than the respective values in model 2, because of less number of
debris stars near the Sun. This rule applies to other considerations
below as well.

\subsection{Kinematics at the North Galactic Pole}

Majewski (1992) suggested that the outer halo at the North Galactic Pole (NGP)
shows a retrograde rotation $\langle v_\phi \rangle \simeq -55$ km~s$^{-1}$
at $z>4$ kpc. Also, K02 reported that their sample of
horizontal branch stars at $2<z<12$ kpc shows a retrograde
rotation at $\langle v_\phi \rangle \simeq -65$ km~s$^{-1}$.
On the other hand, halo stars near the Sun 
show no retrograde rotation (CB).

To investigate the role of the debris stars in this issue, we select
those of model 2 and randomly generated stars at $b>70^\circ$ and
$2<D<5$ kpc (resembling K02's selection). Since the observational determination
of full space velocities involves rather
inaccurate information of proper motions compared to radial velocities,
we convolve the velocity distribution of stars with a Gaussian
distribution for velocity errors, having 1~$\sigma$ of a typical
30 km~s$^{-1}$ error.
The resulting velocity distribution shows a non-Gaussian feature owing to
the presence of the debris stars: the $v_\phi$ distribution holds an extra
peak at $\sim -100$ km~s$^{-1}$ in addition to the
$v_\phi \sim 20$ km~s$^{-1}$ peak, where the former amplitude becomes
comparable to the latter one at $f$ of a few percents,
whereas for $v_R$ and $v_z$, the velocity distributions are made slightly
asymmetric. However, the change of $\langle v_\phi \rangle$ by the inclusion
of the debris stars with $f=5$~\% amounts to only $-19$ ($-14$) km~s$^{-1}$
for $q=0.55$ ($0.7$), which are still insufficient for explaining
the reported $\langle v_\phi \rangle = -35 \sim -65$ km~s$^{-1}$.
Also, if we extend the selection of the stars at higher $z$ or instead consider
model 1, the changes of $\langle v_\phi \rangle$ become smaller than the above
mentioned values, because there are no debris stars in our current model.
Thus, it is safe to conclude that the debris stars
contribute only in part to a reported retrograde motion at the NGP.

\subsection{Local halo kinematics and microlensing towards LMC}

We select the nearby debris and halo stars at $6.5<R<9.5$ kpc, $z<4$~kpc,
and $D<4$ kpc (as was drawn by CB), convolve the velocities
with a Gaussian error distribution of $1~\sigma = 30$ km~s$^{-1}$, and
compare with the corresponding stars with [Fe/H]$\le-2$ in B00.
It follows that the non-Gaussian feature in velocities
is much weaker than that at the
NGP: the change of $\langle v_\phi \rangle$ for $f=5$~\% is only
$-9$ ($-10$) km~s$^{-1}$ in model 1 (model 2). This is due to
the smaller debris fraction near $z=0$ than at high $|z|$.

The effects of the debris stars on the microlensing optical depth towards LMC,
$\tau$, are modest as well. Following the Gould (1999) prescription for $\tau$
and investigating the debris within $10^\circ \times 10^\circ$
centered at LMC, we arrive at $\tau \la 10^{-7}f$, thereby indicating
that $\tau$ provided by the debris stars is much smaller than the observed
$\tau$ of $O(10^{-7})$.

%%% Sec.4 %%%
\section{DISCUSSION}

We have demonstrated that our fiducial models of an orbiting dwarf galaxy
that once contained $\omega$ Cen predict a sequence of tidal streams
in retrograde rotation and their existence is imprinted in kinematics of
nearby stars, especially in the direction against Galactic rotation (GWN) and
at the NGP (K02), while local halo kinematics and microlensing towards LMC
remain unchanged. The streams are mostly distributed
inside the solar circle, as suggested from the current orbit of
$\omega$ Cen (Dinescu 2002).
In contrast to the Sgr dwarf galaxy having polar orbit,
the orbit of $\omega$ Cen's progenitor galaxy is
largely affected by a non-spherical disk potential, where the orbital plane
exhibits precession with respect to the Galactic Pole, causing self-crossing
of tidal streams in the disk. The projection of the orbit
perpendicular to the disk shows an 'X'-like feature, thereby leaving
denser streams at high $|z|$ than at low $|z|$ for a given radius.
This explains the significance of the debris at the NGP
compared to the solar neighborhood.

Existing kinematic studies of Galactic stars to search for a signature
of $\omega$ Cen's progenitor galaxy are yet confined to nearby stars,
where the significance of the debris streams is modest, as shown here.
Searches of stars inside the solar circle are more encouraging (Fig. 1),
in particular in the directions of $l \sim 320^\circ$ and $l \sim 50^\circ$,
where we expect the presence of high-velocity streams at
$v_{los} = 200 \sim 300$ km~s$^{-1}$ and $-400 \sim -300$ km~s$^{-1}$,
respectively. Future radial velocity surveys of these fields including the
sample of the Sloan Digital Sky Survey or planned RAdial Velocity
Experiment are worth exploring in this context. Also, detailed
abundance studies of candidate stream stars will be intriguing, because such
stars may exhibit different abundance patterns from field halo stars,
as found in dwarf galaxies (Shetrone, C\^{o}t\'{e}, \& Sargent 2001).

A yet unsettled issue is the origin of a progenitor satellite
orbiting inside the solar circle, because dynamical friction alone from the
present-day {\it smooth} Galactic components is insufficient for shrinking the
orbit if it was born at a large distance (say, $\sim 50$ kpc) from Galactic
center (Zhao 2002). One of the possibilities to preclude it
may be that the merging of a satellite occurred while
the Milky Way was still in the process of halo formation via
hierarchical merging of several subgalactic clumps; successive gravitational
interaction among clumps may help reducing the orbital angular momentum of
a progenitor efficiently. Also, a progenitor may have formed
in the vicinity of the proto-Galaxy, where the environment of a strong tidal
field promotes the formation of a compact M32-like galaxy (Burkert 1994)
and its high density affords the survival chances until
the epoch of the Galactic disk formation. Then, if a progenitor retained
gas, growing Galactic tides induce the infall of gas into the
progenitor center and trigger the formation of a globular cluster
there (Bekki \& Chiba 2002) similar to $\omega$ Cen. The story is yet
speculative but worth pursuing based on sophisticated numerical codes for
Galaxy formation.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments
We are grateful to the anonymous referee for helpful comments.
M.C. thanks Kenji Bekki and Tim Beers for useful discussions.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage
%%uncomment for ms.tex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{thebibliography}{}

\bibitem[]{416} Beers, T. C., Chiba, M., Yoshii, Y., Platais, I.,
Hanson, R. B., Fuchs, B., \& Rossi, S. 2000, \aj, 119, 2866 (B00)

\bibitem[]{419} Bekki, K., \& Chiba, M. 2002, \apj, 566, 245

%%\bibitem[]{421} Brook, C. B., Kawata, D., Gibson, B., \& Flynn, C. 2003,
%%\apj, 585, L125

\bibitem[]{424} Burkert, A. 1994, \mnras, 266, 877

%%\bibitem[]{426} Carney, B. W. 1999, in ASP Conf. Ser. 165, 3rd Stromlo Symposium
%%on The Galactic Halo, ed. B. K. Gibson, T. Axelrod, \& M. Putnam
%%(San Francisco: ASP), 230

\bibitem[]{430} Carretta, E., Gratton, R.G., \& Clemintini, G. 2000,
\mnras, 316, 721

\bibitem[]{433} Chiba, M., \& Beers, T. C. 2000, \aj, 119, 2843 (CB)

\bibitem[]{435} C\^{o}t\'{e}, P., Marzke, R. O., West, M. J., \& Minniti, D.
2000, \apj, 533, 869

\bibitem[]{438} Dinescu, D. I. 2002, in ASP Conf. Ser. 265, Omega Centauri: A
Unique Window into Astrophysics, ed. F. van Leeuwen, J. D. Hughes, \&
G. Piotto (San Francisco: ASP), 365

\bibitem[]{442} Dinescu, D. I., Girard T. M., \& van Altena, W. F. 1999, \aj,
 117, 1792

%%\bibitem[]{445} Ferraro, F. R., Bellazzini, M., \& Pancino, E. 2002,
%%\apj, 573, L95

\bibitem[]{448} Freeman, K. C. 1993, in ASP Conf. Ser. 48, The Globular
Cluster-Galaxy Connection, ed. G. H. Smith \& J. P. Brodie
(San Francisco: ASP), 608

%%\bibitem[]{452} Freeman, K. C., \& Rodgers, A. W. 1975, \apj, 201, L71

\bibitem[]{454} Gates, E. I., Gyuk, G., \& Turner, E. 1995, \apj, 449, L123

\bibitem[]{456} Gilmore, G., Wyse, R. F. G., \& Norris, J. E. 2002,
\apj, 574, L39 (GWN)

\bibitem[]{459} Gnedin, O. Y., Zhao, H.-S., Pringle, J. E., Fall, S. M.,
Livio, M., \& Meylan, G. 2002, \apj, 568, L23

\bibitem[]{462} Gould, A. 1999, \apj, 525, 734

\bibitem[]{464} Gould, A., Flynn, C., \& Bahcall, J. N. 1998, \apj, 503, 798

\bibitem[]{466} Harris, W. E. 1996, \aj, 112, 1487

%%\bibitem[]{468} Helmi, A. \& White, S. D. M. 2001, \mnras, 323, 529

%%\bibitem[]{470} Ibata, R. A., Wyse, R. F. G., Gilmore, G., Irwin, M. J.,
%%\& Suntzeff, N. B. 1997, \aj, 113, 634

\bibitem[]{473} Kinman, T. D., Cacciari, C., Bragaglia, A., Buzzoni, A.,
\& Spagna, A. 2002, in Galactic Dynamics Workshop, in press
(astro-ph/0211243) (K02)

%%\bibitem[]{477} Lee, Y.-W., Joo, J.-M., Sohn, Y.-J., Rey, S.-C., Lee, H.-c.,
%%\& Walker, A. R. 1999, \nat, 402, 55

\bibitem[]{480} Majewski, S. R. 1992, \apjs, 78, 87

%%\bibitem[]{482} Majewski, S. R., Munn, J. A., \& Hawley, S. L. 1996, \apj,
%%459, L73

\bibitem[]{485} Mateo, M. 1998, \araa, 36, 435

\bibitem[]{487} Meylan, G., Mayor, M., Duquennoy, A., \& Dubath, P. 1995,
\aap, 303, 761

\bibitem[]{490} Norris, J. E., \& Da Costa, G. S. 1995, \apj, 447, 680

%%\bibitem[]{492} Norris, J. E., Freeman, K. C., Mayor, M., \& Seitzer, P.
%%1997, \apj, 487, L187

\bibitem[]{495} Norris, J. E., Freeman, K. C., \& Mighell, K. L.1996,
\apj, 462, 241

\bibitem[]{498} Shetrone, M. D., C\^{o}t\'{e}, P., \& Sargent, W. L. W. 2001,
\apj, 548, 592

%%\bibitem[]{501} Smith, V. V., Suntzeff, N. B., Cunha, K., Gallino, R., Busso, M.,
%%Lambert, D. L., \& Straniero, O. 2000, \aj, 119, 1239

%%\bibitem[]{504} Taylor, J. E., \& Babul, A. 2001, \apj, 559, 716

%%\bibitem[]{506} van Leeuwen, F., Le Poole, R. S., Reijns, R. A., Freeman, K. C.,
%% \& de Zeeuw, P. T. 2000, \aap, 360, 472

%%\bibitem[]{509} White, S. D. M. 1983, \apj, 274, 53

\bibitem[]{511} Yamagata, T., \& Yoshii, Y. 1992, \aj, 103, 117

\bibitem[]{513} Zaritsky, D., \& White, S. D. M. 1988, \mnras, 235, 289

\bibitem[]{515} Zhao, H.-S. 2002, in ASP Conf. Ser. 265, Omega Centauri: A
Unique Window into Astrophysics, ed. F. van Leeuwen, J. D. Hughes, \&
G. Piotto (San Francisco: ASP), 391

\end{thebibliography}

%%\end{document}
%%comment out for ms.tex

\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
%\plotone{f1.eps}
%\figcaption[f1.eps]{
\caption{
Upper (middle) panel shows the spatial distribution of the tidally disrupted
debris for model 1 (model 2) after the 1.37 (1.86) Gyr orbital excursion of
$\omega$ Cen's progenitor galaxy. Lower panel shows the orbit of the galaxy
center for model 1 (dotted line) and 2 (solid line). The plots are projected
onto three orthogonal planes, where the Sun is located at $x=-8$ kpc and $xy$
corresponds to the disk plane. A frame measures 15 kpc on a side of each panel.
The current position of $\omega$ Cen is at $(x,y,z)= (-4.8,-4.0,1.4)$ kpc.
}
\end{figure}

%\clearpage
\begin{figure}
%\plotone{f2.eps}
%\figcaption[f2.eps]{
\caption{
Velocity distribution of the debris particles in cylindrical coordinates,
$v_R$ (dotted), $v_\phi$ (solid), $v_z$ (dashed), for
model 1 (a) and 2 (b).
}
\end{figure}

%\clearpage
\begin{figure}
%\plotone{f3.eps}
%\figcaption[f3.eps]{
\caption{
(a) Distribution of the heliocentric radial velocities in the direction of
the GWN survey, for the debris stars of model 2
and randomly generated halo stars with $q=0.7$.
We select the stars at $1<D<5$ kpc and $260^\circ<l<280^\circ$
in the fields of $30^\circ<|b|<50^\circ$ (with $f=1$~\% and 3~\% for
dotted and solid histograms, respectively) and $20^\circ<|b|<40^\circ$
(with $f=5$~\%: dashed histogram).
(b) The same as (a) but incorporating the randomly generated disk
stars as well for $30^\circ<|b|<50^\circ$ with $f=5$~\% (solid histogram).
Dotted histogram denotes the contribution from the metal-poor halo alone.
}
\end{figure}

\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2013-08-13 2012-aqs/draft-aqs.tex
Aquarius updated.

@@
 %!TEX TS-program = pdflatex
-\documentclass{emulateapj}
-
-\usepackage{amssymb,graphics} % for resolution symbol
+\documentclass[iop]{emulateapj}
+
+\usepackage{amssymb,graphics} % for resolution symbol and \blacktriangledown
 \usepackage{longtable,booktabs,multirow}
-\usepackage{pdflscape,rotating}
 \usepackage{wasysym} % for \astrosun
@@
 \maxdeadcycles=1000
-
-\shorttitle{No Evidence for the Aquarius Co-Moving Group Resulting from a Disrupted Classical Globular Cluster}
+\setcounter{secnumdepth}{5}
+
+\shorttitle{The Aquarius Co-Moving Group is Not a Disrupted Classical Globular Cluster}
 \shortauthors{Casey et al}
@@
 
-\title{No Evidence for the Aquarius Co-Moving Group \\Resulting from a Disrupted Classical Globular Cluster\altaffilmark{1}}
+\title{The Aquarius Co-Moving Group is Not a Disrupted Classical Globular Cluster\altaffilmark{1}}
 
@@
 \author{Andrew R.
-Casey\altaffilmark{2,3}, Stefan Keller\altaffilmark{2}, Alan Alves-Brito\altaffilmark{2}, Anna Frebel\altaffilmark{3}, Gary Da Costa\altaffilmark{2}, Amanda Karakas\altaffilmark{2}, David Yong\altaffilmark{2}, Kevin Schalufman\altaffilmark{3}, Heather Jacobson\altaffilmark{3}, QinQin Yu\altaffilmark{3}, Ken Freeman\altaffilmark{2}, Cherie Fishlock\altaffilmark{2}}
+Casey\altaffilmark{2,3}, Stefan Keller\altaffilmark{2}, Alan Alves-Brito\altaffilmark{2,4}, Anna Frebel\altaffilmark{3}, Gary Da Costa\altaffilmark{2}, Amanda Karakas\altaffilmark{2}, David Yong\altaffilmark{2}, Kevin Schlaufman\altaffilmark{3}, Heather R.
+Jacobson\altaffilmark{3}, Qinsi Yu\altaffilmark{3}, Cherie Fishlock\altaffilmark{2}}
 \altaffiltext{1}{This paper includes data gathered with the 6.5 meter Magellan Telescopes located at Las Campanas Observatory, Chile.}
-\altaffiltext{2}{Research School of Astronomy \& Astrophysics, Australian National University, Mount Stromlo Observatory, via Cotter Rd, Weston, ACT 2611, Australia; acasey@mso.anu.edu.au}
+\altaffiltext{2}{Research School of Astronomy and Astrophysics, Australian National University, Canberra, ACT 2611, Australia; acasey@mso.anu.edu.au}
 \altaffiltext{3}{Massachusetts Institute of Technology, Kavli Institute for Astrophysics and Space Research,
 77 Massachusetts Avenue, Cambridge, MA 02139, USA}
+\altaffiltext{4}{Departamento de Astronom\'ia y Astrof\'isica, Ponticia Universidad Cat\'olica de Chile, Av. Vicu\~na Mackenna 4860, Macul, 782-0436 Santiago, Chile}
 
 \begin{abstract}
-We present a detailed analysis of high S/N, high-resolution spectra for five Aquarius stream stars observed using the MIKE spectrograph on the Magellan Clay telescope.
-Our sample represents one third of the total number of published stream members.
-We find the co-moving group is not chemically coherent; a wide metallicity dispersion ranging from {$\mbox{[Fe/H]} = -0.63$} to $-1.63$\,dex is observed.
-Enhanced [Na/Fe], [Ni/Fe] and [$\alpha$/Fe] abundance ratios suggest the co-moving group is not the result of a disrupted dwarf galaxy.
-Additionally, we find no evidence that the stream is a result of a disrupted classical globular cluster, contrary to a previously published claim.
-No inverse Na-O correlation is present, and we find a strong positive Mg-Al relationship similar to that observed in the thick disc.
-The group is chemically indistinguishable from Milky Way field stars with the exception of one candidate, C222531-145437.
-From positions, velocities, and detailed chemical abundances it is unambiguous that C222531-145437 is a tidal remnant from the $\omega$-Centurai globular cluster.
-We hypothesise the co-moving group is galactic in origin, and is a result from a disc-satellite perturbation in the Milky Way thick disc.
-Derived orbits, $u$--$v$ plane velocities, and angular momentum calculations for Aquarius candidates qualitatively supports our hypothesis, and are consistent with a disc interaction on the order of a few Gyr ago.
-Given the debris of C222531-145437 as tidal debris,  $\omega$-Centurai is a plausible perturber, as is the Sagittarius dwarf.
-While there is no evidence that the Aquarius stream is the tidal tail of a disrupted satellite, we advocate the `Aquarius group' as a more appropriate description.
-Like the Canis Major over-density, and the Hercules and Monoceros groups, the Aquarius co-moving group adds to the list of kinematically-identified substructures that are not actually accreted material; they are simply part of the rich complexity of the Milky Way structure.
+\noindent{}We present a detailed analysis of high $S/N$, high-resolution spectra for 5 Aquarius stream stars observed with the MIKE spectrograph on the Magellan Clay telescope.
+Our sample represents one third of the 15 members in the stream.
+We find the stream is not mono-metallic; the metallicity ranges from [Fe/H] = $-$0.63 to $-$1.58 dex.
+No anti-correlation in Na-O abundances is present, and we find a strong positive Mg-Al relationship, similar to that observed in the thick disc.
+We find no evidence that the stream is a result of a disrupted classical globular cluster, contrary to a previously published claim.
+High [(Na, Ni, $\alpha$)/Fe] and low [Ba/Y] abundance ratios in the stream suggests it is not a tidal tail from a disrupted dwarf galaxy, either.
+The stream is chemically indistinguishable from Milky Way field stars with the exception of one candidate, C222531-145437.
+From its position, velocity, and detailed chemical abundances, C222531-145437 is likely a star that was tidally disrupted from $\omega$-Centauri.
+We propose the Aquarius stream is galactic in origin, and could be the result from a disc-satellite perturbation in the Milky Way thick disc on the order of a few gigayear ago.
+Derived orbits, $UVW$ velocities, and angular momenta of the Aquarius members offer qualitative support for our hypothesis.
+Assuming C222531-145437 is a tidally disrupted member of $\omega$-Centauri, this system is the most likely disc perturber.
+In the absence of compelling chemical and/or dynamical evidence that the Aquarius stream is the tidal tail of a disrupted satellite, we advocate the ``Aquarius group'' as a more appropriate description.
+Like the Canis Major over-density, as well as the Hercules and Monoceros groups, the Aquarius group adds to the list of kinematically-identified substructures that are not actually accreted material; they are simply part of the rich complexity of the Milky Way structure.
 \end{abstract}
@@
 \section{Introduction}
-Galaxies are hierarchically formed through chaotic mergers of smaller systems.
-The Milky Way is no exception.
-The accumulating stellar debris in our own galactic halo provides ongoing evidence for such merging events.
-As accreting satellites infall onto the galaxy, tidal forces disrupt the smaller system, hurtling stars in leading and trailing directions.
-Unsurprisingly the velocities of stars within these `stellar streams' are sensitive to the galactic potential.
-As such, their phase-space information can collectively constrain the fraction and distribution of accreted matter in the galaxy, the sub-halo mass function, as well as the shape and extent of dark matter in the Milky Way.
-Moreover, individual chemical abundances from high-resolution spectra can trace the chemical evolution of the galaxy.
-% can constrain the  precise nucleosynthesis sites where elements are forged, as well as
-
-% Consider adding a final sentence about the amount of work that has gone into stellar streaams
-Wide-field deep imaging surveys have proved excellent sources for finding stellar streams.
-Dozens have been identified through careful photometric selections and matched-filtering techniques, with some to a galactocentric distance of 100\,kpc \citep{belokurov;et-al_2007,drake;et-al_2013}.
+Galaxies are formed hierarchically through chaotic mergers of smaller systems, and the Milky Way is no exception \citep{bullock;johnston_2005,helmi_2008}.
+The accumulating stellar debris in our own Galactic halo provides ongoing evidence for such merging events \citep[e.g.][]{bell;et-al_2008}.
+As satellites fall towards the Galaxy, tidal forces disrupt the system, hurtling stars in leading and trailing directions.
+The position and velocities of stars within these ``stellar streams'' are sensitive to the Galactic potential.
+As such, their phase-space information can collectively constrain the fraction and distribution of accreted matter in the galaxy, the sub-halo mass function, as well as the shape and extent of the Milky Way's dark matter halo.
+Additionally, individual chemical abundances can trace the chemical evolution of the Galaxy and its satellite systems.
+
+Wide-field deep imaging surveys have proved excellent sources for finding stellar streams \citep[e.g.][]{belokurov;et-al_2007}.
+Dozens of streams have been identified through careful photometric selections and matched-filtering techniques, with some to a galactocentric distance of 100\,kpc \citep[e.g., see][]{drake;et-al_2013}.
 Indeed, it is clear that a large fraction of the stellar halo has been built up by accretion.
-However, as \citet{helmi;white_1999} point out, these detection strategies are only successful for identifying streams that are sufficiently distant from the solar neighbourhood.
-A nearby stream, within $\sim$10\,kpc, will not appear as a photometric over-density as the stars would be sparsely positioned across the sky.
-Such substructures would only be detectable by their kinematics, or perhaps with precise elemental abundances through a `chemical tagging' approach (e.g.
-see \citet{freeman;bland-hawthorn_2002}).
-
-% Talk about RAVE
-It is therefore necessary to spectroscopically survey the solar neighbourhood stars to reveal any nearby substructures.
-The Radial Velocity Experiment (RAVE) team began such a survey in 2003 and have observed spectra from over 500,000 stars across 17,000\,deg$^{2}$.
-As the name hints, the primary goal of RAVE was to obtain radial velocities for the solar neighbourhood and beyond.
-In an attempt to remain kinematically unbiased, RAVE candidates were selected solely by their apparent magnitude.
-With the exception of bulge stars, where some photometric cuts were employed, all stars between $9 < I < 13$ were observed.
-Almost all of these candidates have published radial velocity measurements \citep{steinmetz;et-al_2006}, and for a subset of stars with a sufficient Signal-to-Noise ($S/N$) ratio, estimates of stellar parameters have been derived using a $\chi^2$ minimisation technique \citep{zwitter;et-al_2008, siebert;et-al_2011}.
-
-% Identification of the aquarius stream
-Using these data, \citet{williams;et-al_2011} identified a co-moving group of nearby (${0.5\,\mbox{kpc} \lesssim d \lesssim 10\,\mbox{kpc}}$) stars in the vicinity of the Aquarius constellation ${(l, b) = (60\,^\circ, -55\,^\circ)}$.
+However, as \citet{helmi;white_1999} point out, these detection strategies are most successful for identifying streams that are sufficiently distant from the solar neighbourhood.
+A nearby stream, within $\sim$10\,kpc, will not appear as a photometric over-density because the stars would be sparsely positioned across the sky.
+Such substructures would only be detectable by their kinematics, or perhaps with precise elemental abundances through a ``chemical tagging'' approach (e.g.
+see \citealt[][]{freeman;bland-hawthorn_2002}).
+The confirmation of such substructures would serve to substantially increase the fraction of the known accreted material in the Galaxy.
+
+It is therefore necessary to spectroscopically survey stars in the solar neighbourhood to reveal any nearby substructures.
+The Radial Velocity Experiment (RAVE) team began such a survey in 2003 and has taken spectra of over 500,000 stars across 17,000\,deg$^{2}$ \citep{steinmetz;et-al_2006}.
+The primary goal of RAVE is to obtain radial velocities for stars in the solar neighbourhood and beyond.
+In an attempt to remain kinematically unbiased, RAVE candidates were selected solely by their apparent magnitude ($9 < I < 13$).
+Almost all of these candidates have published radial velocities \citep{steinmetz;et-al_2006}, and for a subset of stars with a sufficient signal-to-noise ($S/N$) ratio, stellar parameters have been derived by a $\chi^2$-minimisation technique \citep{zwitter;et-al_2008, siebert;et-al_2011}.
+
+Using these data, \citet{williams;et-al_2011} identified a co-moving group of nearby (${0.5\,\mbox{kpc} \lesssim D \lesssim 10\,\mbox{kpc}}$) stars near ${(l, b) = (60^\circ, -55^\circ)}$, in the vicinity of the Aquarius constellation.
 Thus, the co-moving group was named the Aquarius stream.
-The group is most apparent when examining velocities against galactic latitude for stars within $-70\,^\circ < b < -50\,^\circ$.
-\citet{williams;et-al_2011} employed a selection criteria of $-250\,\mbox{km s}^{-1} < V_{\rm hel} < -150\,\mbox{km s}^{-1}$, $30\,^\circ < l < 75\,^\circ$ and $J > 10.3$ to maximize the contrast between the stream and background, identifying 15 candidates in the process.
+The stream is most apparent when examining heliocentric velocities against galactic latitude for stars within $-70^\circ < b < -50^\circ$.
+\citet{williams;et-al_2011} employed a selection criteria of $-250\,\mbox{km s}^{-1} < V_{\rm hel} < -150\,\mbox{km s}^{-1}$, $30^\circ < l < 75^\circ$ and $J > 10.3$ to maximize the contrast between the stream and stellar background, identifying 15 stars in the process.
 The average heliocentric velocity of these members was found to be $V_{\rm hel} = -199\,\mbox{km s}^{-1}$, with a dispersion of 27\,km s$^{-1}$.
-The radial velocity uncertainties provided by the RAVE catalog are described to be $\sim$2\,km s$^{-1}$, so the stream's wide kinematic distribution appears to be real.
-
-% QUANTIFYING THE STREAM DETECTION
-Upon examining the galactic longitude and velocities of Aquarius stars, the stream appears quite distinct from the halo.
-In order to quantify the statistical likelihood that the Aquarius stream is truly separate from a smooth halo distribution, \citet{williams;et-al_2011} compared the number of observed RAVE stars within $-70\,^\circ < b < -50\,^\circ$ against the Galaxia \citep{sharma;et-al_2011} and Besan\c{c}on \citep{robin;et-al_2003} galaxy simulations.
-The predicted particles in each model between $-70\,^\circ < b < -50\,^\circ$ were binned in $\Delta{l} \times \Delta{V_{\rm hel}}$ blocks using varying grid cell sizes between $25\,^\circ$ to $70\,^\circ$ and $20\,\mbox{km s}^{-1}$ to $100\,\mbox{km s}^{-1}$.
-The RAVE sample was binned in the same way, discretising the inferred statistical significance of the observed over-density.
-\citet{williams;et-al_2011} found the stream to be significant ($>4\sigma$) in 96\% of the cell proportions employed for the Besan\c{c}on model.
-By sampling the Galaxia model repeatedly with varying extinction rates, a similar result was found: between $75\pm15$\,\% to $80\pm18$\,\% of grid cells showed the Aquarius stream to be significant at the $4\sigma$ level or higher.
-Given the high-latitude and proximity of the stream, it is not surprising that dust had a negligible effect on the statistical significance.
-\citet{williams;et-al_2011} concluded that the over-density in $l, V_{\rm hel}$ is a true substructure, and neither the choice of galaxy model, cell dimension, nor the extinction rate made any real difference to the detection significance.
-
-% STREAM IS LOCALIZED
-% the stream appears to be quite localized in space.
-% nearby streams could be strewn out over several degrees. the Orphan stream wraps over 60 degrees in the sky, and the Sgr stream wraps several steradians
-
-% DISTANCE AND DYNAMICS
-% heliocentric + galactic velocities suggest the aquarius stream stars are in the halo, and not associated with the disc.
-% distances
-
-The Sagittarius stream is arguably the most prominent ongoing accretion event in the galaxy.
-Given the extent of stellar debris the Sagittarius dwarf spheroidal (dSph) galaxy has littered throughout the Milky Way, it is reasonable to suspect the Aquarius stream might originate from the Sagittarius dwarf.
-Indeed, the Aquarius  stars do not lie far from the orbital plane of Sagittarius and the metallicities reported by \citet{williams;et-al_2011} are not dissimilar from the Sagittarius stream.
-However, \citet{williams;et-al_2011} found the Aquarius transverse motions (specifically $V_{Z}$ and $V_\phi$) to be quite distinct from Sagittarius.
-Based on the phase space information available, \citet{williams;et-al_2011} concluded that the newly discovered stream could not be positively associated with the Monoceros stream, Hercules-Aquila cloud, or either the Canis Major or Virgo over-densities.
-
-RAVE observations suggest the Aquarius stream has a metallicity of $\mbox{[Fe/H]} \sim -1.0$, slightly more metal-rich than halo stars at the same distance.
-Using stellar parameters from the RAVE pipeline, \citet{williams;et-al_2011} found the stream to have an average of ${\mbox{[M/H]} = -1.0 \pm 0.4}$\,dex, compared to ${\mbox{[M/H]} = -1.1 \pm 0.6}$\,dex for background stars after the same selection cuts had been employed.
-Of the 15 Aquarius stars in the \citet{williams;et-al_2011} discovery sample with stellar parameters, the metallicity range from medium-resolution spectroscopy is wide: between --2.02 and {--0.33\,dex}.
-High-resolution spectroscopic observations with high $S/N$ are necessary to accurately characterise the stream's metallicity distribution.
-
-To this end, \citet{wylie-de-boer;et-al_2012} obtained high-resolution ($\mathcal{R} = 25,000$) spectra with modest $S/N$ ($\sim$30 pixel$^{-1}$) for six Aquarius stream stars using the echelle spectrograph on the ANU 2.3m telescope.
-Their data indicate a surprisingly  narrow metallicity distribution compared to the RAVE results: ${\mbox{[Fe/H]} = -1.09 \pm 0.10}$\,dex extending from ${\mbox{[Fe/H]} = -1.25}$ to {--0.98\,dex}.
-Observations of such minimal chemical scatter from stars that share a common origin is typically noted only in either globular or open clusters.
+The radial velocity uncertainties provided by the RAVE catalog are described to be $\sim$2\,km s$^{-1}$, so the stream's wide velocity distribution appears to be real.
+
+Through a statistical comparison with predictions of stellar positions and kinematics from the Galaxia \citep{sharma;et-al_2011} and Besan\c{c}on \citep{robin;et-al_2003} models of the Milky Way, \citet{williams;et-al_2011} found the stream \ to be statistically significant ($>4\sigma$).
+The choice of model, cell dimension, or extinction rate made no real difference to the detection significance.
+The authors concluded the over-density was genuine, and inferred that the co-moving group is a stellar stream.
+Based on the phase space information available, \citet{williams;et-al_2011} concluded that the newly discovered stream could not be positively associated with the Sagittarius or Monoceros stream, the Hercules-Aquila cloud, or either the Canis Major or Virgo over-densities.
+
+RAVE data suggest the Aquarius stream has a metallicity of [Fe/H] $= -1.0 \pm 0.4$\,dex\footnote{\citet{williams;et-al_2011} formally quote [M/H], but for the sake of a consistent discussion we assume [M/H] $\equiv$ [Fe/H] throughout this study.}, slightly more metal-rich than halo stars at the same distance (${\mbox{[Fe/H]} = -1.1 \pm 0.6}$\,dex) after the same selection cuts had been employed.
+Of the 15 Aquarius stream stars in the \citet{williams;et-al_2011} discovery sample, the metallicity range determined from medium-resolution spectroscopy is wide: from [Fe/H] = --2.02 to --0.33.
+High-resolution spectra with high $S/N$ are necessary to accurately characterise the stream's metallicity distribution function (MDF).
+
+To this end, \citet{wylie-de-boer;et-al_2012} obtained high-resolution ($\mathcal{R} = 25,000$) spectra with modest $S/N$ ($\sim$30 pixel$^{-1}$) for six Aquarius stream stars using the echelle spectrograph on the Australian National University's 2.3m telescope.
+Their data indicate a surprisingly narrow spread in metallicity compared to previous work: ${\mbox{[Fe/H]} = -1.09 \pm 0.10}$\,dex, with a range extending only from $-1.25$ to {--0.98\,dex}.
+Samples with such small dispersions in metallicity are typically observed in mono-metallic environments (e.g.
+globular or open clusters).
 The largest [Fe/H] discrepancy between the \citet{williams;et-al_2011} and \citet{wylie-de-boer;et-al_2012} study was ${\Delta\mbox{[Fe/H]} = -0.66}$\,dex for the most metal-rich star in the \citet{williams;et-al_2011} sample.
@@
 
-In addition to ascertaining stellar parameters, \citet{wylie-de-boer;et-al_2012} measured elemental abundances for the Aquarius stream stars -- the only study to do so until now.
-The authors primarily focussed on light elements: Na, O, Ni, Mg, and Al.
-Chemical patterns in these elements arise as natural consequences of nucleosynthetic processes in massive stars and have been repeatedly observed in globular clusters.
-Specifically, an anti-correlation between sodium and oxygen content appears ubiquitous to globular cluster stars.
-While the exact formation mechanism is still under debate, the chemical relationship is well-established empirically.
-The {Na-O} pattern provides the best chemical evidence that their enrichment history has been dominated by Type \textsc{ii} supernova (SN) events, and that those stars formed in a globular cluster-like environment.
-
-% The following text was placed before 'While the ...'
-%Originally this relationship was thought to arise from internal mixing along the giant branch.
-However, dwarf globular cluster stars were found to exhibit strong Na-enhancement and O-depletion, contrary to what would be expected if the Na-O anti-correlation was purely a result of internal mixing.
-It is well known now that photospheric abundance variations resulting from internal mixing are limited to carbon, nitrogen and lithium.
-Additionally, light element variations can be explained by classic nucleosynthetic pathways, albeit extreme temperatures are necessary for such relationships to arise -- much higher than would reasonably be expected in globular cluster stars.
-Several descriptions for an astrophysical site that would permit such nucleosynthetic processes have been hypothesized, including massive intermediate-mass Asymptotic Giant Branch (AGB) binary stars \citep{de_mink;et-al_2009} and fast-rotating massive stars \citep{decressin;et-al_2007}.
-
-From high-resolution spectroscopy of six Aquarius stars, four of which have sodium and oxygen abundance measurements, \citet{wylie-de-boer;et-al_2012} found two stars with enhanced sodium; slightly higher [Na/Fe] ratios than halo stars of the same metallicity.
-However, no strong oxygen depletion was evident in the data.
-Thus, although they found minimal chemical scatter in the overall metallicities of Aquarius stream stars, they observed no evidence of a {Na-O} inverse correlation.
-
-There are other chemical abundance patterns that allow us to infer the stream's chemical enrichment environment.
-\citet{nissen;schuster_1997} first noted that nearby solar neighbourhood stars were enriched in [Ni/Fe] and [Na/Fe].
-\citet{fulbright_2000} came to a similar conclusion: only somewhat distant ($R_\odot > 20$\,kpc) stars are likely to be sodium deficient.
-If the stellar halo has been built up from the accretion of smaller dwarf satellites, \citet{nissen;schuster_1997} proposed that this chemical trend may be indicative of the halo merger history since stars at larger $R_\odot$ are more likely to have been accreted rather than formed in-situ.
-\citet{wylie-de-boer;et-al_2012} found all the Aquarius stars in their sample to be enriched in both sodium and nickel; contrary to what would be expected if the stars originated from a disrupted dSph galaxy.
-If the stream had originated from an accretion event, this provides an indication that the stars were first enriched in a globular cluster-like environment.
-
-Combined with the low level of chemical scatter present in their sample, these chemical indicators led \citet{wylie-de-boer;et-al_2012} to conclude that the Aquarius stream is the result of a tidally disrupted globular cluster.
-\citet{williams;et-al_2011} had previously precluded this possibility with any known clusters after modelling an Aquarius-like progenitor infalling onto the Milky Way and comparing the predicted $l, b, V_{\rm hel}$ with known, nearby globular clusters of similar metallicities.
-No known globular cluster could match their simulation.
-If both scenarios are accurate then the undiscovered disrupting cluster might still remain and would be very close, such that it is unlikely it would not have been discovered by now.
-
-We seek to investigate the nature of the Aquarius stream, specifically the recent globular cluster origin claim made by \citet{wylie-de-boer;et-al_2012}.
-We present a detailed analysis for five Aquarius stream candidates from high-resolution, high $S/N$ observations taken using the Magellan Inamori Kyocera Echelle spectrograph \citep{bernstein;et-al_2003} with the Magellan Clay telescope.
+In addition to ascertaining stellar parameters, \citet{wylie-de-boer;et-al_2012} measured elemental abundances for the Aquarius stream stars -- the only study to date to do so.
+The authors primarily focussed on Na, O, Mg, Al, and Ni.
+These elements have been extensively studied in globular cluster stars, where unique abundance patterns are observed.
+Specifically, an anti-correlation between sodium and oxygen content appears ubiquitous to stars in globular clusters \citep{carretta;et-al_2009a}.
+\citet{wylie-de-boer;et-al_2012} identified two stream stars with slightly higher [Na/Fe] abundance ratios than halo stars of the same metallicity.
+No strong oxygen depletion was evident in the data, and no overall {Na-O} anti-correlation was present.
+\citet{wylie-de-boer;et-al_2012} also found [Ni/Fe] abundance ratios similar to thick disk/globular cluster stars, markedly higher than those reported for the Fornax dwarf spheroidal (dSph) galaxy, which has a comparable mean metallicity to the Aquarius stream.
+
+Combined with the low level of [Fe/H] scatter present in their sample, these chemical abundances led \citet{wylie-de-boer;et-al_2012} to conclude that the Aquarius stream is the result of a tidally disrupted globular cluster.
+However, \citet{williams;et-al_2011} previously excluded this scenario after modelling an Aquarius-like progenitor infalling onto the Milky Way.
+The predicted positions and velocities from their simulations did not match any known globular cluster.
+If both scenarios are accurate, then the undiscovered disrupting cluster might still remain.
+It should also be quite close, such that its continued absence would be puzzling.
+
+We seek to investigate the nature of the Aquarius stream, specifically the  globular cluster origin claimed by \citet{wylie-de-boer;et-al_2012}.
 Details of the observations and data reduction  are outlined in the following section.
-The data analysis is chronicled in Section \ref{sec:analysis} and a detailed discussion of these results resides in Section \ref{sec:discussion}.
-In Section \ref{sec:conclusions} we present a summary of our conclusions and critical interpretations.
-
-\begin{deluxetable*}{lcccccccccc}
+The bulk of our analysis is presented in Section \ref{sec:analysis} and a thorough chemical abundance analysis is chronicled separately in Section \ref{sec:chemical-abundances}.
+Uncertainties are outlined in Section \ref{sec:uncertainties}.
+A detailed discussion of our results is made in Section \ref{sec:discussion}, and we conclude in Section \ref{sec:conclusions} with a summary of our conclusions and critical interpretations.
+
+\begin{deluxetable*}{lccccccccccc}
 \tablecolumns{1}
@@
 	\colhead{$\delta$} &
-	\colhead{Observed} &
+	\colhead{UT} &
+	\colhead{UT} &
 	\colhead{Airmass} &
@@
 	\colhead{S/N\tablenotemark{a}} &
-	\colhead{$V_{\rm hel}$} &
-	\colhead{$V_{\rm err}$} \\
- & (J2000) & (J2000) & Date & & (") & (secs) & (px$^{-1}$) & (km s$^{-1}$) & (km s$^{-1}$)
+	\colhead{$V_{\rm hel}$} \\
+ & (J2000) & (J2000) & Date & Time & & (\arcsec) & (secs) & (px$^{-1}$) & (km s$^{-1}$) 
 }
@@
 \\ \multicolumn{11}{c}{Standard Stars} \\ \hline \\
-HD\,41667		& 06:05:03.7 & $-$32:59:36.8		& 2011-03-13	& 1.005	& 1.0 & 90 		& 340 & 297.1 		& 0.1 \\
-HD\,44007		& 06:18:48.6 & $-$14:50:44.2 		& 2011-03-13	& 1.033	& 1.0 & 120		& 280 & 161.8 		& 0.1 \\
-HD\,76932		& 08:58:44.2 & $-$16:07:54.2		& 2011-03-14	& 1.158	& 1.0 & 25		& 330 & 117.8		& 0.1 \\
-HD\,136316		& 15:22:17.2 & $-$53:14:13.9		& 2011-03-14	& 1.118	& 0.9 & 120 	& 400 & $-$38.8 	& 0.1 \\
-HD\,141531		& 15:49:16.9 & $+$09:36:42.5	& 2011-03-14	& 1.309	& 0.9 & 120	& 350 & 2.8			& 0.1 \\
-HD\,142948		& 16:00:01.6 & $-$53:51:04.1		& 2011-03-14	& 1.107	& 1.0 & 90 	& 320 & 29.9 		& 0.1 \\
+HD\,41667	& 06:05:03.7 & $-$32:59:36.8	& 2011-03-13	& 23:40 & 1.01	& 1.0 & 90 	& 340 & 297.1 		\\
+HD\,44007	& 06:18:48.6 & $-$14:50:44.2 	& 2011-03-13	& 23:52 & 1.03	& 1.0 & 120	& 280 & 161.8 		\\
+HD\,76932	& 08:58:44.2 & $-$16:07:54.2	& 2011-03-14	& 00:16 & 1.16	& 1.0 & 25	& 330 & 117.8		\\
+HD\,136316	& 15:22:17.2 & $-$53:14:13.9	& 2011-03-14	& 09:37 & 1.12	& 0.9 & 120 	& 400 & $-$38.8 	\\
+HD\,141531	& 15:49:16.9 & $+$09:36:42.5	& 2011-03-14	& 09:52 & 1.31	& 0.9 & 120	& 350 & 2.8		\\
+HD\,142948	& 16:00:01.6 & $-$53:51:04.1	& 2011-03-14	& 09:45 & 1.11	& 1.0 & 90 	& 320 & 29.9 		\\
 \hline
@@
 \\ \multicolumn{11}{c}{Program Stars} \\ \hline \\
-C222531-145437	& 22:25:31.7 & $-$14:54:39.6	& 2011-07-30	& 1.033	& 0.8	& 650 & 135	& $-$156.4 & 0.1 \\
-C230626-085103	& 23:06:26.6 & $-$08:51:04.8	& 2011-07-30	& 1.096	& 1.0	& 650 & 100	& $-$221.1 & 0.1 \\
-J221821-183424	& 22:18:21.2 & $-$18:34:28.3	& 2011-07-30	& 1.026	& 0.9 	& 650 & 115	& $-$159.5 & 0.1 \\
-J223504-152834	& 22:35:04.5 & $-$15:28:34.9	& 2011-07-30	& 1.047	& 1.0 	& 650 & 130	& $-$169.7 & 0.1 \\
-J223811-104126	& 22:38:11.6 & $-$10:41:29.4	& 2011-07-30	& 1.218	& 1.2 	& 650 & 115	& $-$235.7 & 0.1
+C222531-145437	& 22:25:31.7 & $-$14:54:39.6	& 2011-07-30	& 06:52 & 1.03	& 0.8	& 650 & 135	& $-$156.4 \\
+C230626-085103	& 23:06:26.6 & $-$08:51:04.8	& 2011-07-30	& 08:15 & 1.10	& 1.0	& 650 & 100	& $-$221.1 \\
+J221821-183424	& 22:18:21.2 & $-$18:34:28.3	& 2011-07-30	& 05:58 & 1.03	& 0.9 	& 650 & 115	& $-$159.5 \\
+J223504-152834	& 22:35:04.5 & $-$15:28:34.9	& 2011-07-30 & 07:34 & 1.05	& 1.0 	& 650 & 130	& $-$169.7 \\
+J223811-104126	& 22:38:11.6 & $-$10:41:29.4	& 2011-07-30	& 08:57 & 1.22	& 1.2 	& 650 & 115	& $-$235.7
 
@@
 
-\section{Observations \& Data Reduction}
+% V-band magnitudes from APASS
+%C222531-145437 
+%RA	RAerr*	Dec.	Dec. err*	# of Obs.	Johnson V	Verr	Johnson B	Berr	Sloan g'	g'err	Sloan r'	r'err	Sloan i'	i'err
+%336.381962	0.726	-14.910536	0.191	11	12.51	0.076	13.709	0.046	13.066	0.031	12.154	0.159	11.718	0.054
+
+%C230626-085103
+%346.610635	0.593	-8.851072	0.195	11	12.601	0.037	13.885	0.046	13.208	0.027	12.189	0.055	11.762	0.037
+
+%22:18:21-183424
+%334.588459	0.442	-18.573525	0.14	18	12.116	0.035	13.072	0.031	12.569	0.018	11.822	0.037	11.508	0.031
+
+%22:35:04 -15:28:34.9
+%338.76827	0.597	-15.476482	0.152	8	12.26	0.027	13.281	0.022	12.731	0.021	11.935	0.054	11.608	0.044
+
+% 223811-104126
+%339.547668	0.583	-10.691316	0.096	9	11.933	0.024	12.718	0.096	12.309	0.025	11.709	0.036	11.461	0.044
+
+\section{Observations \& Data Analysis}
 
 The most complete sample of Aquarius stream stars is presented in the discovery paper of \citet{williams;et-al_2011}.
-Our sample includes five stars: four common to the \citet{wylie-de-boer;et-al_2012} study, and an additional candidate from the original \citet{williams;et-al_2011} sample.
-The supplementary star, C2306265-085103, was observed by the RAVE survey but had a $S/N$ ratio too low for stellar parameters to be accurately determined.
-All program stars were observed in July 2011 in reasonable seeing at low airmass (Table \ref{tab:observations}), and six  standard stars were observed in March 2011.
-All observations were taken using a 1.0'' slit, providing a spectral resolution in excess of $\mathcal{R} = 28,000$ in the blue arm and $\mathcal{R} = 22,000$ in the red arm.
+We have taken high $S/N$ spectra for 5 Aquarius stream candidates using the Magellan Inamori Kyocera Echelle (MIKE) spectrograph \citep{bernstein;et-al_2003} on the Magellan Clay telescope.
+Although these observations were carried out independently of the \citet{wylie-de-boer;et-al_2012} study, by chance there are four stars are common to both samples.
+The additional star in this sample, C2306265-085103, was observed by the RAVE survey but had a $S/N$ ratio too low for stellar parameters to be accurately determined.
+All program stars were observed in July 2011 in $\sim$1\arcsec{} seeing at low airmass (Table \ref{tab:observations}), and six standard stars were observed in March 2011.
+All observations were taken using a 1.0\arcsec{} slit without  spectral or spatial binning, providing a spectral resolution in excess of $\mathcal{R} = 28,000$ in the blue arm and $\mathcal{R} = 22,000$ in the red arm.
 The exposure time for our program stars was 650\,seconds per star in order to ensure a $S/N$ ratio in excess of 100\,pixel$^{-1}$ at 600\,nm.
 
-Calibration frames were taken at the start of each night, including twenty flat-field frames (10 quartz, 10 milky) and 10 Th-Ar arc lamp exposures for wavelength calibration.
+Calibration frames were taken at the start of each night, including 20 flat-field frames (10 quartz lamp, 10 diffuse flats) and 10 Th-Ar arc lamp exposures for wavelength calibration.
 The data were reduced using the CarPy pipeline\footnote{http://code.obs.carnegiescience.edu/mike}.
-One standard star, HD\,41667, was also reduced using standard extraction and calibration methods in \textsc{iraf}.
+For comparison purposes one of the standard stars, HD 41667, was also reduced using standard extraction and calibration methods in \textsc{iraf}.
 The resultant spectra from both approaches were compared for residual fringing, $S/N$, and wavelength calibration.
 No noteworthy differences were present, and the CarPy pipeline was utilised for the remainder of the data reduction.
-Each reduced echelle order was carefully normalised using a third order spline with defined knot spacing.
-Normalised orders were stitched together to provide a single one-dimensional spectrum from 333-916\,nm.
+Each reduced echelle order was carefully normalised using a cubic spline with defined knot spacing.
+Normalised orders were stitched together to provide a single one-dimensional spectrum from 333 to 916\,nm.
 
 The white dwarf HR 6141 was observed in March 2011 as a telluric standard.
-The $S/N$ ratio for HR 6141 exceeds that in any of our standard or program stars.
-Although the atmospheric conditions at Las Campanas Observatory are certain to change throughout the night and between observing runs, we are primarily using this spectra to identify stellar absorption lines that are affected by telluric absorption.
-However, a few critical transitions necessary for abundance analyses that are affected by the Earth's atmosphere have been corrected for telluric absorption.
+The $S/N$ ratio for HR 6141 exceeds that of any of our standard or program stars.
+Although the atmospheric conditions at Las Campanas Observatory are certain to change throughout the night and between observing runs, we are primarily using this spectrum to identify stellar absorption lines that are potentially affected by telluric absorption.
+
+%Hence a few critical transitions necessary for abundance analyses that are affected by the Earth's atmosphere have been corrected for telluric absorption.
 Where applied, the details of these corrections are discussed on a line-by-line basis.
@@
 The radial velocity for each star was determined in a two step process.
-An initial estimate of the radial velocity was ascertained by cross-correlation with a synthetic spectrum of a giant star with $T_{\rm eff} = 4500$\,K, $\log{g} = 1.5$, and ${\mbox{[M/H]} = -1.0}$ across the wavelength range {845-870\,nm}.
+An initial estimate of the radial velocity was ascertained by cross-correlation with a synthetic spectrum of a giant star with $T_{\rm eff} = 4500$\,K, $\log{g} = 1.5$, and ${\mbox{[Fe/H]} = -1.0}$ across the wavelength range 845 to 870\,nm.
 The observed spectrum was shifted to the pseudo-rest frame using this initial velocity estimate.
-Velocities found from cross-correlation are typically within {1\,km\,s$^{-1}$} of our final published value.
-
-With our spectra at near-rest, we measured the equivalent widths of $\sim$160 transitions by automatically fitting a Gaussian profile to the absorption lines (see Section \ref{sec:line-measurements}).
+Equivalent widths (EWs) were measured for $\sim$160 atomic transitions by integrating fitted Gaussian profiles (see Section \ref{sec:line-measurements}).
+In each case a residual line velocity was calculated from the expected rest wavelength and the measured wavelength.
+The mean residual velocity offset correction is small in all cases ($<$1\,km s$^{-1}$), and this residual correction is applied to the initial velocity measurement from cross-correlation.
+The final heliocentric velocities are listed in Table \ref{tab:observations}, where the typical uncertainty is $\pm0.1$\,km s$^{-1}$.
+These velocities agree quite well with those compiled by \citet{williams;et-al_2011} as part of the RAVE survey: the mean offset is ${\langle\Delta{V}\rangle = 2.5 \pm 2.7}$\,km s$^{-1}$, demonstrating the accuracy of the velocities published in the RAVE catalog.
+
+%With our spectra at near-rest, we measured the equivalent widths of $\sim$160 transitions by automatically fitting a Gaussian profile to the absorption lines (see Section \ref{sec:line-measurements}).
 Fitted Gaussian profiles provide us with a measured equivalent width, the full-width half-maximum (FWHM) and the central wavelength of the profile.
@@
 The radial velocities published in Table \ref{tab:observations} are the final values from this two step method.
-Heliocentric velocities agree quite well with those compiled by \citet{williams;et-al_2011} from the RAVE survey: the mean offset is ${\langle\Delta{V_{\rm hel}}\rangle = 2.5 \pm 2.7}$\,km s$^{-1}$, demonstrating the accuracy of the velocities published in the RAVE catalog.
-
-\begin{figure}[h!]
-	\includegraphics[width=\columnwidth]{./figures/line-velocity.pdf}
-	\caption{Residual velocities for each absorption line with a well-fitted Gaussian profile after correcting for doppler shift using the initial cross-correlation measurement.
-The mean residual velocity $-0.75$\,km\,s$^{-1}$ is within the 1-$\sigma$ cross-correlation uncertainty of $\pm0.9$\,km\,s$^{-1}$.}
-	\label{fig:line-velocities}
-\end{figure}
+
+% --> Mention error in heliocentric velocities for program and standard stars is 0.1 km/s since it's been removed from the table
+
+%\begin{figure}[h!]
+%	\includegraphics[width=\columnwidth]{./figures/line-velocity.pdf}
+%	\caption{Residual velocities for each absorption line with a well-fitted Gaussian profile after correcting for doppler shift using the initial cross-correlation measurement.
+The mean residual velocity of $-0.75$\,km\,s$^{-1}$ is within the 1-$\sigma$ cross-correlation uncertainty of $\pm0.9$\,km\,s$^{-1}$.}
+%	\label{fig:line-velocities}
+%\end{figure}
 
@@
 
+\begin{deluxetable*}{clcrccccccc}
+\tablecolumns{2}
+\tabletypesize{\scriptsize}
+\tablecaption{List of Atomic Transitions and Equivalent Width Measurements for Program and Standard Stars \label{tab:equivalent-widths}}
+\tablehead{
+& & & & & \multicolumn{5}{c}{Equivalent Width} \\
+\cline{5-10} \\
+Wavelength & Species & $\chi$ & $\log{gf}$ & C222531-145437 & C2306265-085103 & J221821-183424 & J223504-152834 & J223811-104126 & (cont..) \\
+({\AA}) & & (eV) & & (m{\AA}) & (m{\AA}) & (m{\AA}) & (m{\AA}) & (m{\AA})
+}
+\startdata
+ 6300.30 &  O\,\textsc{i} &      0.00 &    --9.72 &      45.4 &      66.9 &      38.5 &      32.8 &      17.9 \\
+ 6363.78 &  O\,\textsc{i} &      0.02 &   --10.19 &      19.5 &      28.3 &      13.0 &      18.8 &   \nodata \\
+ 5688.19 & Na\,\textsc{i} &      2.11 &    --0.42 &   \nodata &   \nodata &      49.0 &     131.5 &      38.4 \\
+ 6154.23 & Na\,\textsc{i} &      2.10 &    --1.53 &      24.1 &      38.9 &   \nodata &      48.5 &   \nodata \\
+ 6160.75 & Na\,\textsc{i} &      2.10 &    --1.23 &      37.7 &      58.5 &   \nodata &      65.7 &   \nodata \\
+ 6318.72 & Mg\,\textsc{i} &      5.11 &    --1.97 &   \nodata &      47.9 &      14.7 &      62.8 &       8.9 \\
+ 6319.24 & Mg\,\textsc{i} &      5.11 &    --2.22 &      30.8 &   \nodata &       5.5 &   \nodata &   \nodata \\
+ 6965.41 & Mg\,\textsc{i} &      5.75 &    --1.51 &   \nodata &   \nodata &   \nodata &      59.2 &   \nodata
+\enddata
+\tablenotetext{}{Table \ref{tab:equivalent-widths} is published in its entirety in the electronic edition. A portion is shown here for guidance regarding its form and content.}
+\end{deluxetable*}
+
 For the measurement of atomic absorption lines, we employed the line list of \citet{yong;et-al_2005} with additional transitions of Cr, Sc, Zn, and Sr from \citet{roederer;et-al_2010}.
 The list has been augmented with molecular CH data from \citet{plez;et-al_2008}.
-For lines with hyperfine structure, blended transitions or molecular features, we determined the abundance using a spectral synthesis approach.
-For all other transitions, equivalent widths were measured to determine the line abundance.
-
-The equivalent widths for all absorption lines were measured automatically using software written during this study.
-Given the rest wavelength and an initial guess of the FWHM, a Gaussian profile is iteratively fitted to the absorption line.
-Simultaneously, the local continuum within 10\,\AA{} either side of the rest wavelength is found by fitting a second-order polynomial.
-Measuring the local continuum ensures any errors in our initial normalisation or order-stitching do not propagate through to our equivalent width measurements.
-When determining the local continuum, any group of \textit{neighbouring pixels} that all deviate significantly ($>2\sigma$) from the local continua either belong to a persistent cosmic ray hit, or they are trough points of a nearby absorption profile.
-We attempt to fit a Gaussian profile to each group of deviating pixels, using the current best estimate for the local continuum.
-If a Gaussian profile is successfully fitted to the deviating group and its surrounding pixels, we assume the outlier points -- and all pixels included by that Gaussian profile -- belong to an absorption line and are excluded from the iterative continuum determination.
-
-When fitting Gaussian profiles, the $\chi^2$ difference between the observed spectra and the fitted function is minimised.
-In order to account for crowded absorption regions where the $\chi^2$ value might be influenced by a blended or strong nearby profile, our $\chi^2$ function is weighted by the distance to the rest wavelength with the function,
-\begin{equation}
-	W_{\lambda_{i}} = 1 + \exp{\left(\frac{-(\lambda_{i} - \lambda_{r})^2}{4\sigma^2}\right)}
-\label{eq:chi-weight}
-\end{equation}
-\noindent where the rest wavelength ($\lambda_{r}$) and profile sigma\footnote{Recall $\rm{FWHM} = 2\sigma\sqrt{2\log_e{2}}$} ($\sigma$) are free parameters in the iterative fitting process.
-As a consequence of Eq.
-\ref{eq:chi-weight}, pixels near the rest wavelength are weighted slightly higher than those on the wings, forcing the fitting scheme to disregard blended or crowded surroundings.
-Although this approach relies on a reasonably accurate initial radial velocity correction of $<|4|$\,km s$^{-1}$ -- which is easily achieved -- it greatly improves the accuracy and robustness of the equivalent width measurements.
+Isotopic and hyperfine splitting data was taken from \citet{citation_needed}.
+For molecular features (e.g.
+CH), or lines with hyperfine and/or isotopic splitting (Sc, V, Mn, Co, Cu, Ba, La, Eu), we determined the abundance using spectral synthesis with the relevant data included.
+For all other transitions, abundances were inferred from curve-of-growth with measured EWs.
+
+The EWs for all absorption lines were measured automatically using software written during this study.
+The local continuum surrounding every atomic transition is determined, and a Gaussian profile is iteratively fit to the absorption feature of interest.
+Our algorithm accounts for crowded or blended regions by weighting pixels as a function of difference to the rest wavelength.
+These algorithms and software will be fully outlined in a future contribution (Casey et al 2013d, in preparation).
+For this study we have verified our approach by comparing EWs of 156 lines measured by hand and tabulated in \citet{norris;et-al_1996}.
+We only included measurements in the \citet{norris;et-al_1996} study that were not marked with questionable line quality parameters.
+Excellent agreement is found between the two studies, which is illustrated in Figure \ref{fig:ew-compare}.
+The mean difference is a negligible ${-0.64 \pm 2.78}$\,m\AA{}, and no systematic trend is present.
+The scatter can be attributed to the lack of significant digits in the \citet{norris;et-al_1996} study, as well as the $S/N$ of the data.
+Other studies \citep[e.g.][]{frebel;et-al_2013} using the same algorithm described here find better agreement for spectra with higher $S/N$ ratios: $0.20 \pm 0.16$\,m{\AA} when we compare our results with manual measurements by \citet{aoki;et-al_2007}, and a difference of $0.25 \pm 0.28$\,m{\AA} is found between manual measurements by \citet{cayrel;et-al_2004} and our automatic results.
+Although we are extremely confident in our EW measurements, \textit{every} absorption profile was repeatedly examined by eye for quality, and spurious measurements were removed.
 
@@
 	\includegraphics[width=\columnwidth]{./figures/smh-norris.pdf}
-	\caption{A comparison showing equivalent widths measured for HD\,140283 using our automatic routine (see \S\ref{sec:line-measurements}), and those found by careful hand measurements in \citet{norris;et-al_1996}.
+	\caption{Comparison showing equivalent widths measured for HD\,140283 using our automatic routine (see \S\ref{sec:line-measurements}), and manual measurements by \citet{norris;et-al_1996}.
 No systematic trend is present, and the mean difference between these studies is ${\langle\Delta{}W_\lambda\rangle = -0.64 \pm 2.78}$\,m\AA{}.}
@@
 
-The results of our iterative Gaussian fitting approach are \textit{completely insensitive} to the initial FWHM guess.
-Increasing the initial FWHM estimate from 0.1\,\AA{} to 1 or 2\,\AA{} -- which are unphysically large values for high-resolution spectra -- does not alter either the measured FWHM or the equivalent width for any of our absorption lines.
-Only a small increase in computational cost is observed.
-Although we are extremely confident in our equivalent width measurements, \textit{every} absorption profile was repeatedly examined by eye for quality, and spurious measurements were excluded.
-
-We have verified the approach by comparing our measurements of 156 lines in HD\,140283 with the study of \citet{norris;et-al_1996}.
-We only included measurements in the \citet{norris;et-al_1996} study that were not marked with questionable line quality parameters.
-Excellent agreement is found between the two studies, which is illustrated in Figure \ref{fig:ew-compare}.
-The mean difference is a negligible ${-0.64 \pm 2.78}$\,m\AA{}, and no systematic trend is present.
-We note that the scatter may be directly attributed to the observed $S/N$ ratio, as other studies \citep{frebel;et-al_2013} using the same equivalent width measurement software described here find better agreement with hand measurements for spectra with higher $S/N$ ratios: $0.20 \pm 0.16$\,m{\AA} with \citet{aoki;et-al_2007} and $0.25 \pm 0.28$\,m{\AA} with \citet{cayrel;et-al_2004} for a spectrum of HD\,122563 with ${S/N > 300}$\,pixel$^{-1}$.
-
-We list the atomic data and measured equivalent widths for transitions used during this analysis in Table \ref{tab:equivalent-widths}.
-Saturated lines were excluded by removing measurements with reduced equivalent widths (REW), ${\log_{10}{(EW/\lambda)} > -4.5}$\,dex.
-A minimum detectable equivalent width was calculated as a function of wavelength based on the $S/N$ ratio following \citet{norris;et-al_2001}, and only lines that exceeded a 3$\sigma$ detection significance were included.
+We list the atomic data and measured EWs in Table \ref{tab:equivalent-widths}.
+Transitions near the flat portion of the curve-of-growth have been excluded by removing measurements with reduced equivalent widths (REW), ${\log_{10}{(EW/\lambda)} > -4.5}$.
+A minimum detectable EW was calculated as a function of wavelength, $S/N$ and spectral resolution by following \citet{norris;et-al_2001}, and only lines that exceeded a 3$\sigma$ detection significance were included for this analysis.
 
@@
 These one-dimensional models ignore any centre-to-limb spatial variations, assume hydrostatic equilibrium and no convective overshoot from the photosphere.
-The stellar parameter spacing between models is 250\,K, 0.5\,dex in surface gravity, 0.5\,dex in [M/H] and 0.1\,dex in [$\alpha$/Fe].
+The stellar parameter spacing between models is 250\,K in temperature, 0.5\,dex in surface gravity, 0.5\,dex in [M/H] and 0.1\,dex in [$\alpha$/Fe].
 We interpolated the temperature, gas and radiative pressure, electron density and opacities between atmosphere models using the Quickhull algorithm \citep{barber;et-al_1996}.
-Quickhull is reliant on Delaunay tessellation, which suffers from extremely skewed cells when the grid points vary in size by orders of magnitude -- as $T_{\rm eff}$ values do compared to $\log{g}$ or [M,$\alpha$/H].
-If unaccounted for, interpolating using such asymmetric cells can result in significant errors in atmospheric properties across all photospheric depths.
-We scaled each stellar parameter between zero and unity prior to interpolation in order to minimise these interpolation errors.
-\\
-
-\begin{longtable*}{ccccccccc}
-\caption{\\ List of Line Transitions and Equivalent Width Measurements \label{tab:equivalent-widths}} \tabularnewline
-\cline{1-9}
-& & & & \multicolumn{5}{c}{Equivalent Widths} \\
-\cline{5-9} \\
-Wavelength & Transition & $\chi$ & $\log{gf}$ & C222531-145437 & C2306265-085103 & J221821-183424 & J223504-152834 & J223811-104126 \\
-({\AA}) & & (eV) & & (m{\AA}) & (m{\AA}) & (m{\AA}) & (m{\AA}) & (m{\AA}) \\
-\cline{1-9} \\
-\endhead
-\hline
-\endfoot
-\hline
-\endlastfoot
- 6300.300 &       8.0 &      0.00 &    --9.717 &      45.4 &      66.9 &      38.5 &      32.8 &      17.9 \\
- 6363.780 &       8.0 &      0.02 &   --10.185 &      19.5 &      28.3 &      13.0 &      18.8 &   \nodata \\
- 5688.190 &      11.0 &      2.11 &    --0.420 &   \nodata &   \nodata &      49.0 &     131.5 &      38.4 \\
- 6154.230 &      11.0 &      2.10 &    --1.530 &      24.1 &      38.9 &   \nodata &      48.5 &   \nodata \\
- 6160.750 &      11.0 &      2.10 &    --1.230 &      37.7 &      58.5 &   \nodata &      65.7 &   \nodata \\
- 6318.720 &      12.0 &      5.11 &    --1.970 &   \nodata &      47.9 &      14.7 &      62.8 &       8.9 \\
- 6319.240 &      12.0 &      5.11 &    --2.220 &      30.8 &   \nodata &       5.5 &   \nodata &   \nodata \\
- 6965.410 &      12.0 &      5.75 &    --1.510 &   \nodata &   \nodata &   \nodata &      59.2 &   \nodata \\
- 7387.690 &      12.0 &      5.75 &    --0.870 &      51.7 &      56.3 &      24.7 &      76.0 &      24.0 \\
- 6696.020 &      13.0 &      3.14 &    --1.340 &      72.8 &      63.6 &      13.0 &   \nodata &   \nodata \\
- 6698.670 &      13.0 &      3.14 &    --1.640 &      39.7 &      33.4 &   \nodata &      39.5 &   \nodata \\
- 7835.310 &      13.0 &      4.02 &    --0.470 &      47.8 &      38.4 &   \nodata &      55.9 &       5.4 \\
- 7836.130 &      13.0 &      4.02 &    --0.310 &      62.8 &      44.7 &   \nodata &      69.1 &      13.2 \\
- 5690.430 &      14.0 &      4.93 &    --1.751 &      56.2 &      43.8 &      25.7 &      53.4 &      16.8 \\
- 5793.070 &      14.0 &      4.93 &    --1.843 &      46.1 &      39.8 &      19.3 &      48.4 &   \nodata \\
- 6125.020 &      14.0 &      5.61 &    --1.506 &      40.9 &      23.4 &      10.9 &      34.7 &   \nodata \\
- 6145.010 &      14.0 &      5.62 &    --1.362 &      33.9 &      21.7 &      16.1 &      32.7 &      10.0 \\
- 6155.130 &      14.0 &      5.62 &    --0.786 &      67.4 &      53.1 &      35.3 &      72.0 &      25.0 \\
- 6166.440 &      20.0 &      2.52 &    --1.142 &      94.2 &     105.5 &      42.3 &      99.5 &      35.9 \\
- 6169.040 &      20.0 &      2.52 &    --0.797 &     112.1 &     120.9 &      66.3 &     120.5 &      55.5 \\
- 6169.560 &      20.0 &      2.53 &    --0.478 &     127.9 &     141.2 &      83.7 &     136.4 &      71.3 \\
- 6455.600 &      20.0 &      2.52 &    --1.290 &      80.8 &      91.4 &      31.4 &      89.2 &      26.0 \\
- 5526.820 &      21.1 &      1.77 &      0.130 &      98.8 &     113.3 &     100.8 &      98.4 &      51.1 \\
- 5657.880 &      21.1 &      1.51 &    --0.500 &      96.5 &     107.5 &      92.7 &      95.4 &      41.2 \\
- 5667.150 &      21.1 &      1.50 &    --1.240 &      59.4 &      75.0 &      45.0 &      58.5 &      14.5 \\
- 5669.040 &      21.1 &      1.50 &    --1.120 &   \nodata &      92.5 &      57.3 &      75.2 &      18.2 \\
- 6245.610 &      21.1 &      1.51 &    --0.980 &      67.1 &      83.6 &      53.3 &      67.4 &      14.8 \\
- 6604.600 &      21.1 &      1.36 &    --1.480 &      65.6 &      82.1 &      49.4 &      65.9 &      17.8 \\
- 6064.630 &      22.0 &      1.05 &    --1.888 &      59.7 &      80.9 &   \nodata &      58.6 &   \nodata \\
- 6091.170 &      22.0 &      2.27 &    --0.367 &      45.2 &      59.1 &   \nodata &      56.3 &   \nodata \\
- 6312.240 &      22.0 &      1.46 &    --1.496 &      46.2 &      63.4 &   \nodata &      48.8 &   \nodata \\
- 6336.100 &      22.0 &      1.44 &    --1.687 &      35.9 &      54.1 &   \nodata &      42.3 &   \nodata \\
- 5154.080 &      22.1 &      1.57 &    --1.920 &     112.2 &   \nodata &     114.0 &   \nodata &      53.9 \\
- 5185.910 &      22.1 &      1.89 &    --1.350 &   \nodata &     101.4 &     105.5 &   \nodata &      55.3 \\
- 5336.790 &      22.1 &      1.58 &    --1.690 &     116.3 &     124.6 &     119.5 &     104.0 &      61.4 \\
- 5381.030 &      22.1 &      1.59 &    --2.080 &   \nodata &     131.4 &     101.9 &     109.9 &      48.0 \\
- 5727.060 &      23.0 &      1.08 &    --0.010 &     122.4 &   \nodata &      26.0 &     116.8 &       9.1 \\
- 6090.220 &      23.0 &      1.08 &    --0.060 &      93.6 &     115.6 &      23.6 &      92.8 &   \nodata \\
- 6216.360 &      23.0 &      0.28 &    --1.290 &     108.8 &   \nodata &      16.9 &     109.3 &   \nodata \\
- 6251.820 &      23.0 &      0.29 &    --1.340 &      94.7 &     124.4 &   \nodata &      92.4 &   \nodata \\
- 6274.640 &      23.0 &      0.27 &    --1.670 &      65.5 &      93.8 &   \nodata &      61.5 &   \nodata \\
- 6504.160 &      23.0 &      1.18 &    --1.230 &      22.9 &      33.7 &   \nodata &      31.9 &   \nodata \\
- 4545.950 &      24.0 &      0.94 &    --1.370 &   \nodata &   \nodata &      80.2 &   \nodata &   \nodata \\
- 4580.056 &      24.0 &      0.94 &    --1.650 &   \nodata &   \nodata &   \nodata &   \nodata &      44.2 \\
- 4616.137 &      24.0 &      0.98 &    --1.190 &     128.7 &     139.3 &      89.4 &     126.2 &      59.9 \\
- 4626.188 &      24.0 &      0.97 &    --1.320 &     122.2 &     136.4 &      82.2 &   \nodata &      56.9 \\
- 4646.150 &      24.0 &      1.03 &    --0.740 &   \nodata &   \nodata &     110.6 &     146.1 &      75.3 \\
- 4651.280 &      24.0 &      0.98 &    --1.460 &     127.8 &     140.6 &      75.4 &     116.3 &      48.4 \\
- 4652.158 &      24.0 &      1.00 &    --1.030 &     138.5 &   \nodata &      96.9 &     138.0 &      66.7 \\
- 5206.040 &      24.0 &      0.94 &      0.020 &   \nodata &   \nodata &   \nodata &   \nodata &     132.8 \\
- 5247.564 &      24.0 &      0.96 &    --1.640 &     141.4 &   \nodata &      76.1 &   \nodata &      46.7 \\
- 5296.690 &      24.0 &      0.98 &    --1.360 &     149.9 &   \nodata &      85.0 &     141.0 &      59.0 \\
- 5300.740 &      24.0 &      0.98 &    --2.000 &     120.5 &   \nodata &   \nodata &     112.2 &   \nodata \\
- 5345.800 &      24.0 &      1.00 &    --0.950 &   \nodata &   \nodata &     115.4 &   \nodata &      81.1 \\
- 5348.310 &      24.0 &      1.00 &    --1.210 &     150.8 &   \nodata &      94.8 &     142.4 &      63.0 \\
- 5409.770 &      24.0 &      1.03 &    --0.670 &   \nodata &   \nodata &     132.4 &   \nodata &      92.1 \\
- 4558.594 &      24.1 &      4.07 &    --0.656 &   \nodata &   \nodata &   \nodata &     101.8 &      46.5 \\
- 4588.142 &      24.1 &      4.07 &    --0.826 &      46.0 &      53.0 &      60.5 &      55.0 &      36.0 \\
- 4591.992 &      24.1 &      4.07 &    --1.419 &   \nodata &   \nodata &      29.1 &      28.5 &      19.6 \\
- 6013.530 &      25.0 &      3.07 &    --0.251 &      89.2 &     114.6 &      22.2 &     109.4 &      14.8 \\
- 6016.670 &      25.0 &      3.08 &    --0.100 &      94.0 &     116.0 &      28.1 &     113.0 &      17.1 \\
- 6021.800 &      25.0 &      3.08 &      0.034 &      97.5 &     116.0 &      39.1 &     110.7 &      19.9 \\
- 5044.210 &      26.0 &      2.85 &    --2.034 &   \nodata &   \nodata &   \nodata &   \nodata &      33.7 \\
- 5054.640 &      26.0 &      3.64 &    --1.938 &      38.0 &   \nodata &   \nodata &   \nodata &   \nodata \\
- 5242.490 &      26.0 &      3.63 &    --0.980 &      94.3 &     101.8 &      72.9 &   \nodata &      49.2 \\
- 5321.110 &      26.0 &      4.43 &    --1.106 &      35.0 &      35.3 &      11.1 &   \nodata &   \nodata \\
- 5322.040 &      26.0 &      2.28 &    --2.840 &      93.1 &     103.0 &      59.5 &   \nodata &      30.9 \\
- 5326.140 &      26.0 &      3.57 &    --2.130 &      40.4 &      51.7 &      13.7 &      48.4 &   \nodata \\
- 5365.400 &      26.0 &      3.57 &    --1.040 &   \nodata &     100.3 &   \nodata &      93.8 &   \nodata \\
- 5367.480 &      26.0 &      4.41 &      0.430 &     108.4 &     118.0 &      92.4 &     119.1 &      73.7 \\
- 5379.570 &      26.0 &      3.69 &    --1.530 &      71.4 &      81.4 &      34.9 &      75.6 &      19.6 \\
- 5491.840 &      26.0 &      4.18 &    --2.250 &   \nodata &   \nodata &   \nodata &      17.3 &   \nodata \\
- 5618.630 &      26.0 &      4.21 &    --1.292 &      43.5 &      54.3 &      20.2 &      57.4 &      11.3 \\
- 5701.550 &      26.0 &      2.56 &    --2.216 &     118.5 &     134.8 &      91.8 &     119.5 &      49.5 \\
- 5705.470 &      26.0 &      4.30 &    --1.420 &      29.2 &      41.5 &      10.9 &      44.5 &       7.7 \\
- 5741.850 &      26.0 &      4.25 &    --1.689 &      36.2 &      37.0 &      13.0 &      48.2 &   \nodata \\
- 5775.080 &      26.0 &      4.22 &    --1.310 &      55.0 &      62.1 &      25.3 &      67.4 &      14.7 \\
- 5778.450 &      26.0 &      2.59 &    --3.480 &      42.8 &      55.8 &      13.4 &      50.1 &   \nodata \\
- 5811.920 &      26.0 &      4.14 &    --2.430 &   \nodata &   \nodata &   \nodata &      10.9 &   \nodata \\
- 5837.700 &      26.0 &      4.29 &    --2.340 &   \nodata &   \nodata &   \nodata &      12.9 &   \nodata \\
- 5853.160 &      26.0 &      1.49 &    --5.280 &      30.4 &      43.4 &       6.3 &      34.7 &   \nodata \\
- 5855.090 &      26.0 &      4.60 &    --1.547 &      13.3 &      20.3 &   \nodata &      22.8 &   \nodata \\
- 5856.100 &      26.0 &      4.29 &    --1.640 &      27.9 &      40.2 &   \nodata &      42.7 &   \nodata \\
- 5858.790 &      26.0 &      4.22 &    --2.260 &   \nodata &      11.4 &   \nodata &      16.9 &   \nodata \\
- 5909.970 &      26.0 &      3.21 &    --2.640 &      56.0 &      72.6 &      18.5 &      63.3 &   \nodata \\
- 5916.250 &      26.0 &      2.45 &    --2.994 &      92.9 &     105.1 &      51.2 &      95.4 &      17.7 \\
- 5927.800 &      26.0 &      4.65 &    --1.090 &      32.4 &      36.7 &      12.2 &      50.9 &   \nodata \\
- 5956.690 &      26.0 &      0.86 &    --4.608 &     121.7 &     143.8 &      70.3 &     107.8 &      25.5 \\
- 6012.210 &      26.0 &      2.22 &    --4.070 &      44.4 &      58.8 &      11.5 &      53.0 &   \nodata \\
- 6019.360 &      26.0 &      3.57 &    --3.360 &       7.0 &   \nodata &   \nodata &      11.3 &   \nodata \\
- 6027.050 &      26.0 &      4.07 &    --1.106 &      66.2 &      77.0 &      36.2 &      77.2 &      23.5 \\
- 6054.080 &      26.0 &      4.37 &    --2.310 &       5.6 &       8.1 &   \nodata &      12.9 &   \nodata \\
- 6105.130 &      26.0 &      4.55 &    --2.050 &   \nodata &      10.9 &   \nodata &      14.8 &   \nodata \\
- 6120.240 &      26.0 &      0.91 &    --5.970 &      35.2 &      52.7 &       8.5 &      32.4 &   \nodata \\
- 6151.620 &      26.0 &      2.17 &    --3.299 &      88.9 &     102.9 &      46.9 &      87.0 &      18.2 \\
- 6157.730 &      26.0 &      4.08 &    --1.320 &   \nodata &      81.2 &      33.2 &      78.1 &      18.8 \\
- 6159.380 &      26.0 &      4.61 &    --1.970 &   \nodata &       9.6 &   \nodata &      13.6 &   \nodata \\
- 6165.360 &      26.0 &      4.14 &    --1.490 &      40.6 &      51.6 &      14.2 &      54.0 &      10.8 \\
- 6173.340 &      26.0 &      2.22 &    --2.880 &     109.6 &     125.6 &      70.7 &     105.6 &      34.9 \\
- 6180.200 &      26.0 &      2.73 &    --2.637 &      86.2 &     100.6 &      44.3 &      91.5 &      20.8 \\
- 6200.310 &      26.0 &      2.61 &    --2.437 &     105.2 &     122.2 &      70.8 &     105.4 &      36.6 \\
- 6219.280 &      26.0 &      2.20 &    --2.433 &     134.3 &     153.3 &     103.3 &     127.4 &      56.7 \\
- 6229.230 &      26.0 &      2.84 &    --2.846 &      60.1 &      73.1 &      21.0 &      65.8 &      13.6 \\
- 6232.640 &      26.0 &      3.65 &    --1.283 &      92.6 &     104.3 &      58.3 &     103.0 &      35.6 \\
- 6246.320 &      26.0 &      3.60 &    --0.894 &     114.0 &     129.2 &      90.5 &     124.1 &      61.7 \\
- 6265.130 &      26.0 &      2.17 &    --2.550 &     132.9 &     155.0 &      94.8 &     129.7 &      55.5 \\
- 6270.220 &      26.0 &      2.86 &    --2.500 &      76.7 &      93.6 &      41.2 &      79.1 &      17.4 \\
- 6271.280 &      26.0 &      3.33 &    --2.728 &      31.6 &      44.9 &      13.4 &      43.6 &   \nodata \\
- 6297.790 &      26.0 &      2.22 &    --2.740 &     119.3 &   \nodata &      81.3 &     111.3 &      42.3 \\
- 6301.500 &      26.0 &      3.65 &    --0.766 &     115.0 &     130.6 &      91.1 &     117.9 &   \nodata \\
- 6322.690 &      26.0 &      2.59 &    --2.426 &     111.0 &     124.4 &      74.2 &     103.5 &      41.6 \\
- 6336.820 &      26.0 &      3.68 &    --0.916 &     106.6 &     116.8 &      81.2 &     113.6 &      52.8 \\
- 6353.840 &      26.0 &      0.91 &    --6.477 &      11.8 &      23.7 &   \nodata &      14.1 &   \nodata \\
- 6355.030 &      26.0 &      2.84 &    --2.403 &   \nodata &     122.2 &      58.9 &   \nodata &      27.8 \\
- 6411.650 &      26.0 &      3.65 &    --0.734 &     122.5 &     135.1 &      97.8 &     131.8 &      68.2 \\
- 6469.190 &      26.0 &      4.84 &    --0.770 &   \nodata &   \nodata &      18.7 &   \nodata &   \nodata \\
- 6574.230 &      26.0 &      0.99 &    --5.004 &      84.1 &     118.5 &      35.4 &      87.0 &   \nodata \\
- 6575.020 &      26.0 &      2.59 &    --2.727 &     100.7 &     118.2 &      55.5 &     103.4 &      23.4 \\
- 6581.210 &      26.0 &      1.50 &    --4.705 &      72.4 &      87.5 &      21.7 &      69.6 &   \nodata \\
- 6609.110 &      26.0 &      2.56 &    --2.692 &     102.0 &     118.8 &      60.9 &     103.1 &      29.1 \\
- 6648.080 &      26.0 &      1.01 &    --5.918 &      37.1 &      54.9 &   \nodata &      37.9 &   \nodata \\
- 6739.520 &      26.0 &      1.56 &    --4.820 &      43.1 &      60.8 &   \nodata &      44.5 &   \nodata \\
- 6750.150 &      26.0 &      2.42 &    --2.621 &     110.9 &     128.9 &      78.6 &     109.5 &      40.2 \\
- 6786.860 &      26.0 &      4.19 &    --1.850 &      22.5 &      29.1 &   \nodata &      32.3 &   \nodata \\
- 6810.260 &      26.0 &      4.60 &    --1.000 &      36.2 &      46.9 &      14.5 &      54.9 &       8.5 \\
- 6971.930 &      26.0 &      3.02 &    --3.390 &      21.0 &      30.3 &   \nodata &      28.7 &   \nodata \\
- 7112.170 &      26.0 &      2.99 &    --3.044 &      45.4 &      59.3 &      13.3 &      53.0 &   \nodata \\
- 7189.150 &      26.0 &      3.07 &    --2.796 &      57.5 &      66.3 &   \nodata &   \nodata &   \nodata \\
- 7223.660 &      26.0 &      3.01 &    --2.269 &      87.2 &     114.4 &      47.2 &      90.8 &   \nodata \\
- 7401.690 &      26.0 &      4.18 &    --1.660 &      38.9 &      50.5 &      14.7 &      59.7 &   \nodata \\
- 7710.360 &      26.0 &      4.22 &    --1.129 &      62.5 &      76.7 &      32.5 &      75.4 &   \nodata \\
- 7723.200 &      26.0 &      2.28 &    --3.617 &      82.1 &     100.4 &      36.6 &      91.9 &   \nodata \\
- 7941.090 &      26.0 &      3.27 &    --2.331 &      50.3 &   \nodata &      22.4 &      61.7 &   \nodata \\
- 5234.620 &      26.1 &      3.22 &    --2.150 &   \nodata &      81.2 &   \nodata &   \nodata &      58.3 \\
- 5325.550 &      26.1 &      3.22 &    --3.220 &   \nodata &      32.1 &      43.4 &   \nodata &      11.6 \\
- 5414.070 &      26.1 &      3.22 &    --3.750 &   \nodata &   \nodata &      23.6 &      21.0 &       6.8 \\
- 5425.260 &      26.1 &      3.20 &    --3.370 &      27.1 &      38.2 &      41.3 &      37.3 &      14.5 \\
- 5991.380 &      26.1 &      3.15 &    --3.557 &      21.5 &   \nodata &      28.3 &      25.8 &       7.7 \\
- 6084.110 &      26.1 &      3.20 &    --3.808 &      11.8 &      16.0 &      20.0 &      18.8 &   \nodata \\
- 6149.260 &      26.1 &      3.89 &    --2.724 &      21.7 &      25.2 &      30.8 &      26.3 &      11.8 \\
- 6247.560 &      26.1 &      3.89 &    --2.329 &      31.2 &      36.7 &      50.2 &      40.3 &      21.4 \\
- 6369.460 &      26.1 &      2.89 &    --4.250 &      13.5 &      16.3 &      18.1 &      16.7 &       5.9 \\
- 6416.920 &      26.1 &      3.89 &    --2.740 &      23.1 &      29.2 &      29.2 &      31.9 &   \nodata \\
- 6432.680 &      26.1 &      2.89 &    --3.708 &      30.0 &      33.6 &      41.7 &      37.5 &      12.9 \\
- 6456.380 &      26.1 &      3.90 &    --2.075 &      40.9 &      47.9 &      61.2 &      49.3 &      30.9 \\
- 7224.490 &      26.1 &      3.89 &    --3.243 &   \nodata &   \nodata &      12.7 &      13.2 &   \nodata \\
- 7711.720 &      26.1 &      3.90 &    --2.543 &      23.7 &      29.1 &      37.4 &      29.8 &      14.9 \\
- 6189.000 &      27.0 &      1.71 &    --2.450 &      51.1 &      77.5 &       9.1 &      58.7 &   \nodata \\
- 6455.030 &      27.0 &      3.63 &    --0.250 &      19.1 &      29.8 &   \nodata &      31.4 &   \nodata \\
- 6632.450 &      27.0 &      2.28 &    --2.000 &      29.1 &      42.3 &   \nodata &      34.7 &   \nodata \\
- 5846.990 &      28.0 &      1.68 &    --3.210 &      60.7 &      77.0 &      17.8 &      62.7 &   \nodata \\
- 6086.280 &      28.0 &      4.26 &    --0.515 &      31.8 &      36.1 &      12.4 &      47.8 &   \nodata \\
- 6175.370 &      28.0 &      4.09 &    --0.535 &      41.4 &      48.6 &      21.1 &      52.5 &      10.4 \\
- 6177.240 &      28.0 &      1.83 &    --3.510 &      39.3 &      48.8 &      11.1 &      39.4 &   \nodata \\
- 6204.600 &      28.0 &      4.09 &    --1.140 &      14.9 &      18.5 &   \nodata &      25.3 &   \nodata \\
- 6635.120 &      28.0 &      4.42 &    --0.828 &      14.9 &      18.2 &   \nodata &      26.0 &   \nodata \\
- 6772.320 &      28.0 &      3.66 &    --0.987 &      53.5 &      59.1 &      26.5 &      62.0 &      13.0 \\
- 5105.540 &      29.0 &      1.39 &    --1.520 &     139.4 &     160.4 &      67.1 &     123.3 &      32.5 \\
- 4722.150 &      30.0 &      4.03 &    --0.390 &      74.1 &      67.9 &      73.6 &      76.5 &      37.4 \\
- 4810.528 &      30.0 &      4.08 &    --0.137 &      61.5 &      63.6 &      72.5 &      82.3 &      42.1 \\
- 7800.290 &      37.0 &      0.00 &      0.130 &   \nodata &   \nodata &   \nodata &      60.9 &   \nodata \\
- 5123.220 &      39.1 &      0.99 &    --0.830 &   \nodata &   \nodata &   \nodata &   \nodata &      16.5 \\
- 5200.420 &      39.1 &      0.99 &    --0.570 &     100.9 &   \nodata &      65.8 &      78.6 &      26.5 \\
- 5509.910 &      39.1 &      0.99 &    --1.010 &     103.0 &      94.4 &      47.0 &      95.4 &      15.7 \\
- 5544.610 &      39.1 &      1.74 &    --1.080 &      29.9 &      18.8 &       9.5 &      16.2 &   \nodata \\
- 6127.440 &      40.0 &      0.15 &    --1.060 &      56.3 &      44.9 &   \nodata &      29.7 &   \nodata \\
- 6134.550 &      40.0 &      0.00 &    --1.280 &      49.6 &      38.7 &   \nodata &      23.6 &   \nodata \\
- 6143.200 &      40.0 &      0.07 &    --1.100 &      54.4 &      44.6 &   \nodata &      30.7 &   \nodata \\
- 5112.270 &      40.1 &      1.67 &    --0.590 &   \nodata &   \nodata &      21.8 &   \nodata &   \nodata \\
- 5853.640 &      56.1 &      0.60 &    --1.010 &     143.5 &     121.4 &     110.8 &      99.8 &      49.6 \\
- 6141.730 &      56.1 &      0.70 &    --0.080 &     213.6 &     177.6 &     166.4 &     151.1 &      93.1 \\
- 5805.770 &      57.1 &      0.13 &    --1.560 &      47.7 &      28.8 &      13.0 &      25.1 &   \nodata \\
- 6390.480 &      57.1 &      0.32 &    --1.410 &      43.0 &      22.0 &      11.6 &      18.6 &   \nodata \\
- 5274.240 &      58.1 &      1.04 &    --0.320 &      29.1 &   \nodata &      12.7 &   \nodata &   \nodata \\
- 5472.300 &      58.1 &      1.24 &    --0.180 &      19.4 &   \nodata &   \nodata &   \nodata &   \nodata \\
- 4959.120 &      60.1 &      0.06 &    --0.800 &      79.9 &      74.0 &      35.0 &      64.2 &   \nodata \\
- 5092.790 &      60.1 &      0.38 &    --0.610 &      47.3 &   \nodata &      21.9 &      20.9 &   \nodata \\
- 5212.360 &      60.1 &      0.20 &    --0.960 &      61.4 &      61.9 &      19.6 &      51.6 &   \nodata \\
- 5234.190 &      60.1 &      0.55 &    --0.510 &      71.9 &      57.9 &      17.9 &      47.3 &   \nodata \\
- 5249.580 &      60.1 &      0.98 &      0.200 &      64.5 &      54.7 &      31.8 &      50.7 &   \nodata \\
- 5255.510 &      60.1 &      0.20 &    --0.670 &     116.3 &   \nodata &      40.5 &   \nodata &   \nodata \\
- 5293.160 &      60.1 &      0.82 &      0.100 &      74.2 &      71.6 &      29.0 &      62.5 &   \nodata \\
- 5319.810 &      60.1 &      0.55 &    --0.140 &      86.6 &   \nodata &      34.4 &   \nodata &   \nodata \\
- 6645.110 &      63.1 &      1.38 &      0.204 &      24.5 &      27.8 &      17.0 &      30.3 &   \nodata \\
-\hline
-\end{longtable*}
+Quickhull is reliant on Delaunay tessellation, which suffers from extremely skewed cells when the grid points vary in size by orders of magnitude -- as $T_{\rm eff}$ values do compared to $\log{g}$ or [(M,$\alpha$)/H].
+If unaccounted for, performing interpolation using such asymmetric cells can result in significant errors in atmospheric properties across all photospheric depths.
+We scaled each stellar parameter between zero and unity before interpolation to minimise these interpolation errors.
 
@@
 
+\setlength{\tabcolsep}{4pt}
+
+\begin{deluxetable*}{lccccccccccccccc}[h!]
+\tablecolumns{2}
+\tabletypesize{\tiny}
+\tablecaption{Stellar Parameters\label{tab:stellar-parameters}}
+\startdata
+\hline \\
+& \multicolumn{4}{c}{{\bf This Study}} && \multicolumn{5}{c}{{\bf Literature}} \\
+\cline{2-5} \cline{7-11} \\
+
+	Designation &
+	$T_{\rm eff}$ &
+	$\log{g}$ &
+	$v_t$ &
+	[Fe/H] & 
+	&
+	$T_{\rm eff}$ &
+	$\log{g}$ &
+	$v_t$ &
+	[Fe/H] &
+	Reference \\
+	& (K) & (dex) & (km\,s$^{-1}$) & (dex) && (K) & (dex) & (km s$^{-1}$) & (dex) \\
+\hline
+
+\\
+\multicolumn{11}{c}{Standard Stars} \\
+\hline
+HD\,41667		& 4660	& 1.71	& 1.84 	& $-$1.20&
+				& 4605	& 1.88	& 1.44	& $-$1.16
+				& \citet{gratton;et-al_2000} \\
+HD\,44007		& 4835	& 1.78	& 1.95	& $-$1.77&
+				& 4850	& 2.00 	& 2.20	& $-$1.71
+				& \citet{fulbright_2000} \\
+HD\,76932		& 5800 & 3.88 & 1.65 & $-$1.05&
+				& 5849 & 4.11 & \nodata & $-$0.88 
+				& \citet{nissen;et-al_2000} \\
+HD\,136316		& 4355 & 0.58 & 2.06 & $-$1.93&
+				& 4414 & 0.94 & 1.70 & $-$1.90 
+				& \citet{gratton_sneden_1991} \\
+HD\,141531		& 4345 & 0.63 & 2.07 & $-$1.69 &
+				& 4280 & 0.70 & 1.60 & $-$1.68
+				& \citet{shetrone_1996} \\
+HD\,142948		& 5025	& 2.25	& 2.05	& $-$0.74&
+				& 4713 	& 2.17 	& 1.38	& $-$0.77
+				& \citet{gratton;et-al_2000} \\
+\hline \\
+
+\multicolumn{11}{c}{Program Stars} \\
+\hline
+
+C222531-145437	& 4365				& 1.25				& 1.94				& $-$1.22	&
+				& 4235\,$\pm$\,118 	& 1.45\,$\pm$\,0.21	& 1.96\,$\pm$\,0.11 	& $-$1.20\,$\pm$\,0.14 
+				& \citet{wylie-de-boer;et-al_2012} \\
+C230626-085103	& 4225	& 0.85	& 1.92 	& $-$1.13&
+				& \dots	& \dots	& \dots	& \dots
+				& \dots \\	
+J221821-183424	& 4630				& 0.88				& 2.16				& $-$1.58&
+				& 4395\,$\pm$\,205 	& 1.45\,$\pm$\,0.35 	& 1.96\,$\pm$\,0.18 	& $-$1.15\,$\pm$\,0.21
+				& \citet{wylie-de-boer;et-al_2012} \\
+J223504-152834	& 4650				& 2.16 				& 1.55				& $-$0.63&
+				& 4597\,$\pm$\,158 	& 2.40\,$\pm$\,0.14 	& 1.47\,$\pm$\,0.07 	& $-$0.98\,$\pm$\,0.17
+				& \citet{wylie-de-boer;et-al_2012} \\
+J223811-104126	& 5190				& 2.93				& 1.62				& $-$1.43&
+				& 5646\,$\pm$\,147 	& 4.60\,$\pm$\,0.15 	& 1.09\,$\pm$\,0.11 	& $-$1.20\,$\pm$\,0.20
+				& \citet{wylie-de-boer;et-al_2012} 
+\enddata
+
+\end{deluxetable*}
+
 \subsection{Stellar Parameters}
-The May 2011 version of the spectral synthesis code \textsc{moog} \citep{sneden;et-al_1973} has been used to derive individual line abundances and stellar parameters.
+The May 2011 version of the \textsc{moog}  \citep{sneden;et-al_1973} spectral synthesis code has been used to derive individual line abundances and stellar parameters.
 This version employs Rayleigh scattering \citep{sobeck;et-al_2011} instead of treating scattering as true absorption, which is particularly important for transitions blue-ward of 450\,nm.
-This is noteworthy, but is less relevant for these analyses as most of our line measurements are red-ward of 450\,nm.
+This is noteworthy, but is less relevant for these analyses as most of the atomic transitions utilised here are red-ward of 450\,nm.
 
@@
 \label{sec:effective-teffs}
-The effective temperature for each star was found by demanding a zero-trend in excitation potential and line abundance for measured Fe\,\textsc{i} and Fe\,\textsc{ii} line abundances.
-A linear fit was made to the line abundances for each ionisation state, and gradients less than $|10^{-3}|$\,dex were considered to be converged.
-Photometric temperatures were calculated after our spectroscopic temperatures had been derived, and are discussed in Section \ref{sec:photometric-temperatures}.
+The effective temperature, $T_{\rm eff}$, for each star was found by demanding a zero-trend in excitation potential and line abundance for measurable Fe\,\textsc{i} transitions.
+The data were fitted with a linear slope, and gradients less than $|10^{-3}|$\,dex eV$^{-1}$ were considered to be converged.
+For comparison, photometric temperatures were calculated after our spectroscopic temperatures had been derived, and these are discussed in Section \ref{sec:photometric-temperatures}.
 
 \subsubsection{Microturbulence and Surface Gravity}
-The microturbulence for each star was found by forcing a zero-trend in REW and abundance for Fe\,\textsc{i} and \textsc{ii} lines.
-Similarly for the effective temperature, gradients in REW and abundance of less than $|10^{-3}|$\,dex were considered to be converged.
+The microturbulence for each star was found by forcing a zero-trend in the REW and abundance for Fe\,\textsc{i} lines.
+Similar to the effective temperature, linear slopes in REW and abundance of less than $|10^{-3}|$\,dex were considered converged.
 The surface gravity for all stars was found by forcing the mean Fe\,\textsc{i} and Fe\,\textsc{ii} abundances to be equal.
-The process is iterative: a zero trend with the excitation potential, reduced equivalent width and abundance must be maintained.
-
-\subsubsection{Metallicity, $\mbox{[M/H]}$}
-The degeneracy between stellar parameters requires a refinement of the stellar parameters until the line abundances were consistent with the model atmosphere.
-After these parameters had converged, the model metallicity was exactly matched to that of our mean Fe\,\textsc{i} abundance.
-Line abundances that were unusually deviant ($>$3$\sigma$) from the mean were removed.
-The largest number of outlier measurements removed for any observation was an uncomfortably large nine for C222531-145437 -- which were near-saturated lines with REW $\sim -4.5$ -- leaving 60 Fe\,\textsc{i} and 10 Fe\,\textsc{ii} lines for analysis.
-For other candidates usually only one outlier measurement was removed.
-The minimum number of iron transitions employed for stellar parameter determination in any star was 44 lines (33 Fe\,\textsc{i} and 11 Fe\,\textsc{ii}) for our hottest star, J223811-104126.
+The process is iterative: a zero trend with the excitation potential, REW and  abundances must be maintained.
+
+\subsubsection{Metallicity}
+The model atmosphere metallicity was exactly matched to that of our mean Fe\,\textsc{i} abundance.
+Individual Fe line abundances that were unusually deviant (e.g.
+$>$3$\sigma$) from the mean abundance were removed.
+The largest number of outlier measurements removed for any observation was nine for C222531-145437.
+These were transitions near the flat part of the curve-of-growth with REWs $\sim -4.5$, leaving 60 Fe\,\textsc{i} and 10 Fe\,\textsc{ii} lines for the analysis of C222531-145437.
+Usually only one outlier measurement was removed for the other candidates.
+The minimum number of Fe transitions employed for stellar parameter determination was 42 lines (33 Fe\,\textsc{i} and 9 Fe\,\textsc{ii}), which occurred for our hottest star, J223811-104126.
 
@@
 
-As a consistency check for our spectroscopic temperatures, we have estimated effective temperatures using infrared photometry from the 2MASS \citep{skrutskie;et-al_2006} catalog and empirical $T_{\rm eff}$-colour relationships.
-The $J-K$ colour has been employed for these calculations because it has the least dependence on metallicity.
-
-The Aquarius stream is relatively close and at high-latitude, so significant extinction is not expected.
-The reddening maps of \citet{schlegel;et-al_1998} estimate that the extinction for our stars varies between ${E(B-V) = 0.03}$ to {0.07\,mags}.
-However, these maps are not perfect.
-As an alternative to using the \citet{schlegel;et-al_1998} dust maps, the level of extinction towards a star can be found directly by the strength of the interstellar Na D or K\,\textsc{i} lines \citep{munari;zwitter_1997}.
-The interstellar lines must be sufficiently separated from the stellar absorption features in order for the extinction to be measurable.
-This was the case in only one of our stars, J223811-104126.
-The equivalent width of the Na D1 line in J223811-104126 is found to be 302.4\,m{\AA}, corresponding to an ${E(B-V) = 0.12^{+0.01}_{-0.02}}$ according to the \citet{munari;zwitter_1997} relationship.
-This is a significantly higher value than the \citet{schlegel;et-al_1998} reddening map suggests: ${E(B-V) = 0.07}$.
-For completeness, both extinction values have been used to calculate photometric temperatures.
-
-Although all of our candidates are giant stars, two different $T_{\rm eff}$-color relationships have been employed: the \citet{alonso;et-al_1999} calibration for giants, and the \citet{casagrande;et-al_2010} calibration for dwarfs and sub-giants.
-All photometrically-derived temperatures are listed in Table \ref{tab:photometric-temperatures}.
-For the \citet{casagrande;et-al_2010} dwarf/sub-giant $J-K$ relationship -- which has a slight metallicity dependency -- we have adopted the spectroscopically-derived [Fe/H] values shown in Table \ref{tab:stellar-parameters}.
-
-The effective temperatures found from spectroscopy agree fairly well with the photometric estimates.
-For three of our stars, the temperatures we find are in between the two color-temperature relationships.
-There are two noteworthy deviations: J223504-152834 and J223811-104126.
-For J223504-152834 we find the star to have an effective temperature of 4650\,K, 71\,K hotter than the \citet{casagrande;et-al_2010} dwarf/sub-giant relationship, yet 420\,K hotter than the \citet{alonso;et-al_1999} estimate.
-Our temperature of 4650\,K is in good agreement with previous spectroscopic determinations (4795\,K; \citet{williams;et-al_2011}, 4597\,K; \citet{wylie-de-boer;et-al_2012}).
-The fact that the \citet{alonso;et-al_1999} photometric temperature relationship for giants predicts a temperature that is 420\,K cooler than the spectroscopically-derived values may be attributed to an underestimated amount of dust towards J223504-152834.
-A higher than expected level of extinction along the line-of-sight would produce cooler photometric temperatures than the true effective temperature.
-An extinction of $E(B-V) = 0.10$ (up from 0.04) would be required for the \citet{alonso;et-al_1999} relation to yield a temperature of ${\sim}$4500\,K, which is within the uncertainties of our effective temperature derived from spectroscopy.
-Such a discrepancy in extinction is large, but not uncommon \citep[e.g.
-see][and the case of J223811-104126]{peek;graves_2010,nataf;et-al_2012}.
-Although we suspect J223504-152834 to have a higher reddening than $E(B-V) = 0.04$, we have adopted the \citet{schlegel;et-al_1998} value for distance determinations (see Section \ref{sec:distances}) as no extinction measurement could be ascertained from interstellar absorption lines.
-
-J223811-104126, the second temperature deviant, has two extinction values available: the \citet{schlegel;et-al_1998} value of $E(B-V) = 0.07$ and the 0.12 value determined from the interstellar Na D1 line.
-Given the inherent difficulties in producing dust maps, we believe the $E(B-V) = 0.12$ determination to be more accurate.
-Employing the \citet{schlegel;et-al_1998} extinction value with the \citet{alonso;et-al_1999} color-temperature relationship yields good agreement (5104\,K) with our spectroscopic temperature of 5190\,K.
-Adopting our more accurate reddening determination yields 5215\,K.
-The \citet{casagrande;et-al_2010} scale is ${\sim}$200\,K hotter in both cases.
-
-With the exception of J223504-152834, the \citet{alonso;et-al_1999} giant relationship agrees well ($\pm$100\,K) with our spectroscopically-derived values.
-The \citet{casagrande;et-al_2010} relationship is also in reasonable agreement (most within 100\,K, largest discrepancy is 300\,K) with our spectroscopic temperatures, although we note that this relation was derived primarily for dwarfs/sub-giants and our candidates are giant stars.
+As a consistency check for our spectroscopic temperatures, we have estimated effective temperatures using the colour-$T_{\rm eff}$ empirical relationship for giant stars from \citet{ramirez;melendez_2005}.
+The $V-K$ colour has been employed as its calibration has the lowest residual fit.
+This relationship has a slight dependence on metallicity, and as such we have adopted the spectroscopic [Fe/H] values in Table \ref{tab:stellar-parameters} for these calculations.
+Optical $V$-band photometry has been sourced from the APASS catalogue \citep{henden;et-al_2012}, and $K$-band magnitudes have been sourced from the 2MASS catalog \citep{skrutskie;et-al_2006}.
+The reddening maps of \citet{schlegel;et-al_1998} estimate that the extinction for our stars varies between ${E(B-V) = 0.03}$ to {0.07\,mags}, and these values have been used to de-redden our $V-K$ colour.
+
+\setlength{\tabcolsep}{4pt}
+\begin{deluxetable}{lccccccc}
+\tablecolumns{1}
+\tabletypesize{\scriptsize}
+
+\tablecaption{Reddening \& Photometric Temperatures\label{tab:photometric-temperatures}}
+\tablehead{
+	\colhead{Designation} &
+	\colhead{$E(B-V)$} &
+	\colhead{$(V-K)_0$} &
+	\colhead{$T_{\rm phot}$} &
+	\colhead{$T_{\rm spec}$} &
+	\colhead{$\Delta{}T$} \\
+	& (mag) & (mag) & (K) & (K) & (K)
+}
+\startdata 
+C222531-145437 	& 0.03\phn	& 	2.86 & 4285	& 4365 & $-$80 \\	
+C230626-085103	& 0.05\phn	&	3.00 & 4196	& 4225 & $-$29 \\	
+J221821-183424 	& 0.03\phn	&	2.36 & 4685	& 4630 &   +55  \\	
+J223504-152834 	& 0.04\phn	&	2.50 & 4557	& 4650 & $-$93 \\	
+J223811-104126 	& 0.07\phn	&	1.84 & 5240	& 5190 &   +50  
+\enddata
+\end{deluxetable}
+\setlength{\tabcolsep}{6pt}
+
+Calculated photometric temperatures are listed in Table \ref{tab:photometric-temperatures}.
+The mean difference between the photometric temperatures and those found by excitation balance is $-$19\,K, where the largest variation is $-$93\,K for J223504-152834.
+While these photometric temperatures serve as a confirmation for our spectroscopically-derived values, for the remainder of this analysis we have employed effective temperatures determined by excitation balance.
+
+% C2225316-145437
+% (V-K) = 2.94, V = 12.51, K = 9.57, E(B-V) = 0.03
+% (V-K)_0 = 2.86
+% with [Fe/H] = -1.22, Ramirez & Melendez Teff: 4285 K (-80 K)
+
+% C230626-085103
+% (V-K) = 3.13, V = 12.601, K = 9.47, E(B-V) = 0.05
+% (V-K)_0 = 3.00
+% with [Fe/H] = -1.13, Ramirez & Melendez Teff: 4196 K (-29 K)
+
+% J221821-183424
+% (V-K) = 12.116 - 9.68 = 2.436, E(B-V) = 0.03
+% (V-K)_0 = 2.355
+% with [Fe/H] = -1.58, Ramirez & Melendez Teff: 4685 (+55 K)
+
+%J223504-152834
+% (V-K) = 12.26 - 9.65 = 2.61, E(B-V) = 0.04
+% (V-K)_0 = 2.502 
+% with [Fe/H] = -0.63, Ramirez & Melendez Teff: 4557 (-93 K)
+
+% J223811-104126
+	% (V-K) = 11.933 - 9.90 = 2.033, E(B-V) = 0.07
+	% (V-K)0 = 1.844
+	% WITH [FE/H] = -1.63 (WRONG), Ramirez & Melendez Teff: 5245 (+55 K)
+	% WITH [Fe/H] = -1.43, R & M Teff: 5240 (+50K)
+
+	% (V-K) = 2.033, E(B-V) = 0.12
+	% V0 = 11.933 - 0.12 * 3.315
+	% K0 = 9.90 - 0.12 * 0.367 
+	% (V0 - K0) = 1.67924
+	% (V-K)0 = 1.709
+	% with [Fe/H] = -1.63 (WRONG), Ramirez & Melendez Teff: 5427 (+237 K)
+	% with [Fe/H] = -1.43, R & M Teff = 5423 (+234 K)
 
@@
 	\includegraphics[width=\textwidth]{./figures/spectra-sample.pdf}
-	\caption{Normalised rest-frame spectra surrounding the H-$\beta$ absorption line for all Aquarius stream candidates.}
+	\caption{Normalised rest-frame spectra surrounding the H-$\beta$ absorption line for all Aquarius stream candidates with offset fluxes.
+The effective temperature, surface gravity and metallicity is shown for all stars.}
 	\label{fig:spectra}
@@
 
-\begin{deluxetable*}{lcccccccccccccc}[h!]
+\subsection{Distances}
+\label{sec:distances}
+
+\begin{deluxetable*}{lccccccccc}
 \tablecolumns{2}
 \tabletypesize{\scriptsize}
-\tablecaption{Stellar Parameters\label{tab:stellar-parameters}}
+\tablecaption{Parameters and Uncertainties for Monte-Carlo Realisations\label{tab:monte-carlo-data}}
 \tablehead{
@@
 	\colhead{$\log{g}$} &
-	\colhead{$v_t$} &
-	\colhead{[Fe/H]} & 
-	\colhead{$T_{\rm eff}$} &
-	\colhead{$\log{g}$} &
-	\colhead{$v_t$} &
-	\colhead{[Fe/H]} &
-	\colhead{Source} \\
-	& (K) & (dex) & (km\,s$^{-1}$) & (dex) & (K) & (dex) & (km s$^{-1}$) & (dex) 
+	\colhead{$J$} &
+	\colhead{$E(B-V)$} &
+	\colhead{$V_{\rm hel}$} &
+	\colhead{$\mu_\alpha$} &
+	\colhead{$\mu_\delta$} &
+	\colhead{$D$}
+	\\
+	& (K) & (dex) & (mag) & (mag) & (km s$^{-1}$) & (mas yr$^{-1}$) & (mas yr$^{-1}$) & (kpc) 
 }
 \startdata 
-\multicolumn{10}{c}{Standard Stars} \\
-\cline{1-10} \\
-HD\,41667		& 4660	& 1.71	& 1.84 	& $-$1.20
-				& 4605	& 1.88	& 1.44	& $-$1.16
-				& \citet{gratton;et-al_2000} \\
-HD\,44007		& 4835	& 1.78	& 1.95	& $-$1.77
-				& 4850	& 2.00 	& 2.20	& $-$1.71
-				& \citet{fulbright_2000} \\
-HD\,76932		& 5800 & 3.88 & 1.65 & $-$1.05
-				& 5849 & 4.11 & \nodata & $-$0.88 
-				& \citet{nissen;et-al_2000} \\
-HD\,136316		& 4355 & 0.58 & 2.06 & $-$1.93
-				& 4414 & 0.94 & 1.70 & $-$1.90 
-				& \citet{gratton_sneden_1991} \\
-HD\,141531		& 4345 & 0.63 & 2.07 & $-$1.69 
-				& 4280 & 0.70 & 1.60 & $-$1.68
-				& \citet{shetrone_1996} \\
-HD\,142948		& 5025	& 2.25	& 2.05	& $-$0.74
-				& 4713 	& 2.17 	& 1.38	& $-$0.77
-				& \citet{gratton;et-al_2000} \\
-\hline \\
-
-\multicolumn{10}{c}{Program Stars} \\
-\cline{1-10} \\
-C222531-145437	& 4365				& 1.25				& 1.94				& $-$1.22	
-				& 4235 $\pm$ 118 	& 1.45 $\pm$ 0.21	& 1.96 $\pm$ 0.11 	& $-$1.20 $\pm$ 0.14 
-				& \citet{wylie-de-boer;et-al_2012} \\
-C230626-085103	& 4225	& 0.85	& 1.92 	& $-$1.13
-				& \dots	& \dots	& \dots	& \dots
-				& \dots \\	
-J221821-183424	& 4630				& 0.88				& 2.16				& $-$1.58
-				& 4395 $\pm$ 205 	& 1.45 $\pm$ 0.35 	& 1.96 $\pm$ 0.18 	& $-$1.15 $\pm$ 0.21
-				& \citet{wylie-de-boer;et-al_2012} \\
-J223504-152834	& 4650				& 2.16 				& 1.55				& $-$0.63
-				& 4597 $\pm$ 158 	& 2.40 $\pm$ 0.14 	& 1.47 $\pm$ 0.07 	& $-$0.98 $\pm$ 0.17
-				& \citet{wylie-de-boer;et-al_2012} \\
-J223811-104126	& 5190				& 2.93				& 1.62				& $-$1.63
-				& 5646 $\pm$ 147 	& 4.60 $\pm$ 0.15 	& 1.09 $\pm$ 0.11 	& $-$1.20 $\pm$ 0.20
-				& \citet{wylie-de-boer;et-al_2012} 
+C222531-145437 & $4365 \pm 125$ & $1.25 \pm 0.20$ & $10.341 \pm 0.022$ & $0.03 \pm 0.01$ & $-156.4 \pm 0.1$ & \phn\phn\,$3.5 \pm 2.1$ & $-14.7 \pm 2.2$ & $5.1^{+1.1}_{-0.8}$\\
+C230626-085103 & $4225 \pm 125$ & $0.85 \pm 0.20$ & $10.312 \pm 0.025$ & $0.05 \pm 0.01$ & $-221.1 \pm 0.1$ & \phn$-2.5 \pm 2.8$ & $-15.4 \pm 2.7$ & $6.5^{+1.4}_{-1.1}$\\
+J221821-183424 & $4630 \pm 125$ & $0.88 \pm 0.20$ & $10.340 \pm 0.021$ & $0.03 \pm 0.01$ & $-159.5 \pm 0.1$ & $-10.6 \pm 2.5$ & $-19.3 \pm 2.5$ & $5.6^{+1.3}_{-0.9}$ \\
+J223504-152834 & $4650 \pm 125$ & $2.16 \pm 0.20$ & $10.363 \pm 0.025$ & $0.04 \pm 0.01$ & $-169.7 \pm 0.1$ & \phn\,$15.9 \pm 2.2$ & $-12.8 \pm 2.2$ & $1.9^{+0.5}_{-0.4}$ \\
+J223811-104126 & $5190 \pm 125$ & $2.93 \pm 0.20$ & $10.420 \pm 0.018$ & $0.07 \pm 0.01$ & $-235.7 \pm 0.1$ & $-25.3 \pm 2.1$ & $-99.5 \pm 2.1$ & $1.1^{+0.3}_{-0.2}$
 \enddata
-
 \end{deluxetable*}
-
-\begin{deluxetable}{lccccc}
-\tablecolumns{1}
-\tabletypesize{\scriptsize}
-\tablecaption{Reddening \& Photometric Temperatures\label{tab:photometric-temperatures}}
-\tablehead{
-& & & \multicolumn{2}{c}{$T_{phot}$} \\
-\cline{4-5} \\
-	\colhead{Designation} &
-	\colhead{E($B-V$)} &
-	\colhead{$(J-K)_0$} &
-	\colhead{Alonso} &
-	\colhead{Casagrande} \\
-	& (mag) & & (K) & (K)
-}
-\startdata 
-C222531-145437 	& 0.03\phn	& 	0.75 & 4247	&	4391 \\	
-C230626-085103	& 0.05\phn	&	0.82 & 4091	&	4200 \\	
-J221821-183424 	& 0.03\phn	&	0.64 & 4546	&	4747 \\	
-J223504-152834 	& 0.04\phn	&	0.69 & 4110	& 	4579 \\	
-J223811-104126 	& 0.07\phn	&	0.48 & 5104	&	5367 \\	
-				& 0.12\footnote{Extinction derived from interstellar Na D1 line (see \ref{sec:photometric-temperatures})} 			&	0.45 & 5215	&	5484	
-\enddata
-\end{deluxetable}
-
-% spectral plots for five stars
-
-\subsection{Abundances}
-We have scaled our abundances to solar values using the Sun's chemical composition described in \citet{asplund;et-al_2009}.
-The analysis of each element is discussed separately below in order of atomic number, with comparable elements grouped accordingly.
-
-\subsubsection{Carbon}
-Carbon is produced by the triple-$\alpha$ process and ejected in supernova events.
-Carbon abundances on the stellar surface increase as a star evolves along the red giant branch through dredge-up processes.
-While no atomic carbon transitions exist in an optical spectrum, carbon is inferred from strong band heads and molecular features.
-
-We have measured carbon abundances for all stars from the G-band head near {4313\,\AA} and the CH band head at {4323\,\AA}.
-Careful attention was paid to the normalisation of these regions.
-Synthetic spectra was computed for different carbon abundances in order to find the best fit with the observed spectrum.
-The abundances were determined separately for each band head and in all cases they agree within 0.10\,dex of each other, which is less than the typical quoted uncertainty of 0.20\,dex.
-The spectra were convolved with a Gaussian kernel, where the width was determined from synthesising spectra of nearby atomic lines that have known abundances from equivalent width measurements.
-A $^{12}$C/$^{13}$C ratio of 4 was assumed, which provides a good fit to the data.
-An example fit to these regions for a standard and program star is shown in Figure \ref{fig:carbon}.
-
-Carbon abundances derived for our program stars agree well with the literature.
-For HD\,136316 we find {${\rm [C/Fe]} = -0.50 \pm 0.20$}\,dex, where \citet{gratton;et-al_2000} find {[C/Fe] $= -0.66$\,dex}, and our ${{\rm [C/Fe]} = -0.48}$\,dex measurement for HD\,141531 agrees within 0.06\,dex.
-Most program stars have near-solar carbon abundances, ranging from ${{\rm [C/Fe]} = -0.30}$ for {J221821-183424}, and +0.05 for {J223811-104126}.
-
-\begin{figure}[h!]
-	\includegraphics[width=\columnwidth]{./figures/HD44007.pdf}
-	\caption{The Carbon CH band near 4313\,{\AA} in our standard star HD\,44007.
-The best-fit synthetic spectra is shown, with uncertainties in $\log_{\epsilon}$C of $\pm0.20$\,dex -- the smallest uncertainty assumed from synthetic spectral fits.}
-	\label{fig:carbon}
-\end{figure}
-
-\subsubsection{Oxygen}
-\label{sec:oxygen-abundances}
-Oxygen is a particularly difficult element to measure.
-There are only a handful of lines available in an optical spectrum: the forbidden {[O\,\textsc{i}]} lines at 630\,nm and 636\,nm, and the O\,\textsc{i} triplet lines at 777\,nm.
-The forbidden lines are very weak and become immeasurable in hot and/or metal-poor stars (${\mbox{[Fe/H]} \lesssim -1.5}$\,dex).
-When they are present, depending on the radial velocity of the star, the {[O\,\textsc{i}]} lines can be significantly affected by telluric absorption.
-Moreover, the 630\,nm line is blended with a Ni\,\textsc{i} absorption line \citep{allende-prieto;et-al_2001}.
-Hence the region requires careful consideration.
-Although the O\,\textsc{i} triplet lines at 777\,nm are stronger than the forbidden lines, they are extremely susceptible to non-LTE effects and surface granulation \citep{asplund;perez_2001}, and sensitive to changes in microturbulence.
-Forbidden {[O\,\textsc{i}]} abundances in our standard stars agree well with the literature, where an offset of $-0.07$\,dex in [O/Fe] is seen for HD\,136316 when compared with \citet{gratton;et-al_2000}.
-
-The {[O\,\textsc{i}]} lines were measurable in four of our Aquarius candidates.
-Careful consideration was taken when correcting for telluric absorption.
-The 630\,nm line in one of our candidates, {C2306265-085103}, was sufficiently affected by telluric absorption such that we deemed the line unrecoverable.
-Thus, only the 636\,nm transition was used to derive an oxygen abundance for {C2306265-085103}.
-In our hottest star, {J223811-104126}, the forbidden oxygen lines were not detected above a 3$\sigma$ significance.
-After synthesising the region, we deduce a very conservative upper limit of ${\mbox{[O/Fe]} < 0.50}$\,dex from the {[O\,\textsc{i}]} lines.
-This is consistent with the rest of our candidates, with [O/Fe] abundances varying between 0.43 to 0.49\,dex.
-
-In order to derive an oxygen measurement for {J223811-104126}, we were forced to use the triplet lines at 777\,nm.
-Each line was synthesised and a mean abundance was calculated for each candidate.
-Abundances determined from the oxygen triplet lines were systematically $+0.27$\,dex higher than that found from the {[O\,\textsc{i}]} forbidden lines.
-\citet{perez;et-al_2006} found [O/Fe] values based on the {O\,\textsc{i}} permitted triplet lines are on average ${+0.19 \pm 0.07}$\,dex higher than those found from the forbidden lines, which did not include non-LTE corrections of $+$0.08\,dex.
-Thus, we  attribute our $+$0.27\,dex offset between measurements of the {[O\,\textsc{i}]} and {O \textsc{i}} triplet lines to non-LTE and 3D effects as it is precisely the same as the total difference found by \citet{perez;et-al_2006}.
-\citet{perez;et-al_2006} concluded that the forbidden lines, when not too weak, probably give the most reliable estimate of oxygen abundance.
-
-From the permitted O\,\textsc{i} triplet, we derive an oxygen abundance of ${\mbox{[O/Fe]} = 0.42 \pm 0.01}$\,dex (random scatter) for {J223811-104126}.
-This measurement will be systematically higher than the `true' abundance if it were discernible from the [O\,\textsc{i}] lines, on the order of ${\sim}+0.27$\,dex.
-When we apply this crude offset derived from the rest of our sample, we arrive at a corrected abundance of ${\mbox{[O/Fe]} = 0.15 \pm 0.08}$\,dex for {J223811-104126}.
-This is the most oxygen-deficient star in our sample by a factor of two.
-
-\subsubsection{Sodium}
-\label{sec:sodium-abundances}
-Our line list includes three clean, unblended sodium lines at 5688\,\AA, 6154\,\AA and 6161\,\AA.
-Not all three of these lines were detectable in each star.
-In the hottest and most metal-poor stars, J223811-104126 and J221821-183424 respectively, only the 5688\,{\AA} line was measurable.
-Consequently, an uncertainty of $\pm0.10$\,dex was adopted for these stars.
-For stars where multiple sodium lines were available, the line-to-line scatter is reasonable: usually around 0.04\,dex with a maximum of 0.09\,dex in HD\,41667.
-
-% [Na/Fe] measurements in the standard stars? 
-Our [Na/Fe] abundances appear systematically higher than values found in the literature, on the order of 0.10\,dex.
-For HD\,142948 we yield {[Na/Fe] = 0.22}\,dex, which is +0.10\,dex higher than that found for \citet{gratton;et-al_2000}, and similarly we find HD\,76932 to be +0.10\,dex higher than reported by with \citet{fulbright_2000}.
-\citet{gratton;et-al_2000} also found HD\,136316 to have {[Na/Fe] = $-$0.29}\,dex, where we find {[Na/Fe] = $-0.14$}\,dex where there is excellent agreement in the stellar parameters.
-Different solar compositions employed between this study and earlier work can account for $\sim$0.08\,dex of this effect, leaving the residual difference well within the observational uncertainties.
-However, it is important to note that the [Na/Fe] abundance ratios presented may be higher compared to previous studies.
-
-\subsubsection{$\alpha$-elements (Mg, Si, Ca and Ti)}
-\label{sec:alpha-elements}
-
-The $\alpha$-elements (Mg, Si, Ca and Ti) are forged through $\alpha$-particle capture in assorted burning stages of stellar evolution, including the burning of carbon, neon and silicon.
-Although Si and Ti ($Z = 14, 22$) are not formally $\alpha$-elements, their abundance generally varies with those of the other $\alpha$-elements and therefore has been included here.
-
-% magnesium measurements
-%Magnesium has been measured from unblended lines that fall within the linear regime between reduced equivalent width and abundance.
-Depending on the radial velocity of the star, some magnesium lines were affected by telluric absorption, particularly the 6318 and $6965\,{\rm \AA}$ transitions.
-Atmospheric absorption was most notable for C222531-145437, where three of the four Mg transitions in our line list suffered some degree of telluric absorption, requiring an attentive correction.
-Every amended absorption profile was carefully examined, and lines with suspicious profiles were excluded from the final magnesium abundance.
-All [$\alpha$/Fe] abundance ratios in the standard stars are in excellent agreement with the literature.
-Typically the difference is 0.01\,dex, with the largest discrepancy of {$\Delta$[Ti/Fe] = +0.13\,dex} for HD\,76932 when compared with \citet{fulbright_2000}.
-
-% [alpha/Fe]
-\begin{figure}[h]
-	\includegraphics[width=\columnwidth]{./figures/aquarius-alpha-fe.pdf}
-	\caption{The $\alpha$-element abundances with respect to iron content. The mean [$\alpha$/Fe] abundance from these is shown in the bottom panel.}
-	\label{fig:alpha-elements}
-\end{figure}
-
-% calcium measurements + silicon measurements
-Of all the $\alpha$-elements, calcium has the smallest measurement scatter in our stars.
-The mean was formed from four line measurements in each star, with the typical measurement uncertainty was 0.01\,dex.
-As shown in Figure \ref{fig:alpha-elements}, all Aquarius candidates show super-solar [Ca/Fe], ranging between +0.23 to +0.43\,dex, consistent with [Mg,Ti,Si/Fe] measurements.
-
-However, {C222531-145437} has an unusually high silicon abundance (${\mbox{[Si/Fe]} = 0.79}$\,dex), well outside the uncertainties of the rest of our sample.
-The silicon line abundances in this star are in relatively good agreement with one another.
-If we exclude the highest line measurement, then the mean abundance drops only slightly to ${\mbox{[Si/Fe]} = 0.73 \pm 0.04}$\,dex.
-The lowest silicon line abundance for {C222531-145437} is ${\mbox{[Si/Fe]} = 0.61}$\,dex, which is still significantly higher than the mean abundance for any other star.
-
-% titanium measurements?
-Titanium abundances for the stream stars are generally in agreement with one another, showing typical $\alpha$-enhancement signatures.
-Our mean titanium abundances are derived from four to seven clean, unblended lines.
-In our hottest and most metal-poor stars, no suitable Ti\,\textsc{i} transitions were available.
-In other stream candidates, the mean difference between species is ${\langle{\rm Ti}\,\textsc{i} - {\rm Ti}\,\textsc{ii}\rangle = 0.24\,{\rm dex}}$.
-Although this discrepancy is not negligible, there are limited lines available for comparison and our mean ${\langle{\rm Fe}\,\textsc{i} - {\rm Fe}\,\textsc{ii}\rangle}$, ${\langle{\rm Cr}\,\textsc{i} - {\rm Cr}\,\textsc{ii}\rangle}$ (see Section \ref{sec:fe-peak-abundances}) differences are very small.
-
-\clearpage
-
-\begin{longtable*}{lccccccclcccccc}
-\caption{\\ Standard Star Abundances\label{tab:standard-star-abundances}} \tabularnewline
-\cline{1-15}
-Species & $N$ & $\log\epsilon(X)$ & $\sigma_\epsilon$ & [X/H] & [X/Fe] & $\sigma$ && 
-Species & $N$ & $\log\epsilon(X)$ & $\sigma_\epsilon$ & [X/H] & [X/Fe] & $\sigma$ \tabularnewline
-\cline{1-15} \tabularnewline
-% This works.
-\endhead
-\hline
-\multicolumn{15}{r}{Continued..}
-\endfoot
-\hline
-\endlastfoot
-
-\\
-\multicolumn{7}{c}{HD\,41667} & \colhead{} & \multicolumn{7}{c}{HD\,44007} \\
-\cline{1-7} \cline{9-15}
-   C (CH)       &   2 &    6.95 &    0.20 &  --1.48 &  --0.28 &    0.20 &&
-   C (CH)       &   2 &    6.66 &    0.20 &  --1.77 &  --0.01 &    0.20 \\
-   O \textsc{I} &   2 &    7.95 &    0.06 &  --0.74 &    0.46 &    0.04 &&
-   O \textsc{I} &   1 &    7.41 &    0.00 &  --1.28 &    0.48 &    0.00 \\
-  Na \textsc{I} &   3 &    4.90 &    0.18 &  --1.34 &  --0.14 &    0.10 &&
-  Na \textsc{I} &   2 &    4.44 &    0.09 &  --1.80 &  --0.04 &    0.06 \\
-  Mg \textsc{I} &   4 &    6.72 &    0.10 &  --0.88 &    0.32 &    0.05 &&
-  Mg \textsc{I} &   2 &    6.30 &    0.06 &  --1.29 &    0.47 &    0.04 \\
-  Al \textsc{I} &   4 &    5.18 &    0.11 &  --1.27 &  --0.07 &    0.06 &&
-  Al \textsc{I} &   1 &    4.80 &    0.00 &  --1.65 &    0.11 &    0.00 \\
-  Si \textsc{I} &   5 &    6.55 &    0.06 &  --0.96 &    0.24 &    0.03 &&
-  Si \textsc{I} &   5 &    6.07 &    0.07 &  --1.44 &    0.32 &    0.03 \\
-   K \textsc{I} &   1 &    4.64 &    0.00 &  --0.39 &    0.81 &    0.00 &&
-   K \textsc{I} &   1 &    4.31 &    0.00 &  --0.72 &    1.04 &    0.00 \\
-  Ca \textsc{I} &   4 &    5.47 &    0.06 &  --0.87 &    0.33 &    0.03 &&
-  Ca \textsc{I} &   4 &    4.95 &    0.02 &  --1.39 &    0.37 &    0.01 \\
- Sc \textsc{II} &   6 &    2.13 &    0.13 &  --1.02 &    0.18 &    0.05 &&
- Sc \textsc{II} &   6 &    1.39 &    0.10 &  --1.76 &    0.00 &    0.04 \\
-  Ti \textsc{I} &   4 &    3.96 &    0.04 &  --0.99 &    0.21 &    0.02 &&
-  Ti \textsc{I} &   1 &    3.48 &    0.00 &  --1.47 &    0.29 &    0.00 \\
- Ti \textsc{II} &   3 &    4.09 &    0.25 &  --0.86 &    0.35 &    0.14 &&
- Ti \textsc{II} &   4 &    3.47 &    0.15 &  --1.48 &    0.28 &    0.07 \\
-   V \textsc{I} &   6 &    2.87 &    0.13 &  --1.06 &    0.14 &    0.05 &&
-   V \textsc{I} &   4 &    2.17 &    0.03 &  --1.77 &  --0.00 &    0.01 \\
-  Cr \textsc{I} &  10 &    4.22 &    0.08 &  --1.42 &  --0.22 &    0.03 &&
-  Cr \textsc{I} &  15 &    3.65 &    0.07 &  --1.99 &  --0.22 &    0.02 \\
- Cr \textsc{II} &   2 &    4.54 &    0.05 &  --1.09 &    0.11 &    0.04 &&
- Cr \textsc{II} &   3 &    4.00 &    0.01 &  --1.64 &    0.12 &    0.01 \\
-  Mn \textsc{I} &   3 &    3.96 &    0.01 &  --1.47 &  --0.27 &    0.01 &&
-  Mn \textsc{I} &   3 &    3.15 &    0.04 &  --2.28 &  --0.52 &    0.02 \\
-  Fe \textsc{I} &  61 &    6.30 &    0.12 &  --1.20 &    0.00 &    0.02 &&
-  Fe \textsc{I} &  51 &    5.74 &    0.13 &  --1.76 &    0.00 &    0.02 \\
- Fe \textsc{II} &  13 &    6.35 &    0.05 &  --1.15 &    0.05 &    0.01 &&
- Fe \textsc{II} &  15 &    5.74 &    0.10 &  --1.76 &  --0.00 &    0.03 \\
-  Co \textsc{I} &   5 &    3.75 &    0.10 &  --1.24 &  --0.04 &    0.04 &&
-  Co \textsc{I} &   1 &    3.22 &    0.00 &  --1.77 &  --0.01 &    0.00 \\
-  Ni \textsc{I} &   7 &    4.94 &    0.12 &  --1.28 &  --0.08 &    0.05 &&
-  Ni \textsc{I} &   4 &    4.47 &    0.05 &  --1.75 &    0.01 &    0.02 \\
-  Cu \textsc{I} &   1 &    2.72 &    0.00 &  --1.47 &  --0.27 &    0.00 &&
-  Cu \textsc{I} &   1 &    1.84 &    0.00 &  --2.35 &  --0.59 &    0.00 \\
-  Zn \textsc{I} &   2 &    3.36 &    0.08 &  --1.20 &    0.00 &    0.06 &&
-  Zn \textsc{I} &   2 &    2.83 &    0.05 &  --1.73 &    0.03 &    0.04 \\
-  Sr \textsc{I} &   1 &    1.31 &    0.00 &  --1.56 &  --0.36 &    0.00 &&
-  Sr \textsc{I} &   1 &    0.91 &    0.00 &  --1.96 &  --0.20 &    0.00 \\
-  Y \textsc{II} &   5 &    0.97 &    0.19 &  --1.24 &  --0.04 &    0.09 &&
-  Y \textsc{II} &   6 &    0.28 &    0.11 &  --1.93 &  --0.16 &    0.05 \\
-  Zr \textsc{I} &   2 &    1.42 &    0.05 &  --1.17 &    0.04 &    0.04 &&
-  Zr \textsc{I} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
- Zr \textsc{II} &   1 &    1.28 &    0.00 &  --1.30 &  --0.10 &    0.00 &&
- Zr \textsc{II} &   1 &    0.59 &    0.00 &  --1.99 &  --0.23 &    0.00 \\
- Ba \textsc{II} &   2 &    1.02 &    0.04 &  --1.16 &    0.05 &    0.02 &&
- Ba \textsc{II} &   2 &    0.25 &    0.01 &  --1.93 &  --0.17 &    0.01 \\
- La \textsc{II} &   2 &    0.14 &    0.04 &  --0.96 &    0.24 &    0.03 &&
- La \textsc{II} &   2 &  --0.52 &    0.02 &  --1.62 &    0.14 &    0.01 \\
- Ce \textsc{II} &   4 &    0.35 &    0.18 &  --1.23 &  --0.02 &    0.09 &&
- Ce \textsc{II} &   3 &  --0.41 &    0.12 &  --1.99 &  --0.23 &    0.07 \\
- Nd \textsc{II} &   9 &    0.54 &    0.10 &  --0.88 &    0.32 &    0.03 &&
- Nd \textsc{II} &   9 &  --0.36 &    0.11 &  --1.78 &  --0.01 &    0.04 \\
- Eu \textsc{II} &   1 &  --0.05 &    0.00 &  --0.57 &    0.63 &    0.00 &&
- Eu \textsc{II} &   1 &  --0.36 &    0.00 &  --0.88 &    0.88 &    0.00 \\
-
-\cline{1-7} \cline{9-15} \\ \\
-\multicolumn{7}{c}{HD\,76932} && \multicolumn{7}{c}{HD\,136316} \\
-\cline{1-7} \cline{9-15}
-   C (CH)       &   2 &    7.52 &    0.20 &  --0.91 &    0.14 &    0.20 &&
-   C (CH)       &   2 &    5.95 &    0.20 &  --2.48 &  --0.50 &    0.20 \\
-   O \textsc{I} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata &&
-   O \textsc{I} &   1 &    7.17 &    0.00 &  --1.52 &    0.41 &    0.00 \\
-  Na \textsc{I} &   3 &    5.37 &    0.04 &  --0.87 &    0.18 &    0.02 &&
-  Na \textsc{I} &   2 &    4.17 &    0.04 &  --2.08 &  --0.14 &    0.02 \\
-  Mg \textsc{I} &   3 &    6.95 &    0.20 &  --0.65 &    0.40 &    0.11 &&
-  Mg \textsc{I} &   2 &    6.08 &    0.24 &  --1.52 &    0.41 &    0.17 \\
-  Al \textsc{I} &   4 &    5.45 &    0.07 &  --1.00 &    0.05 &    0.03 &&
-  Al \textsc{I} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
-  Si \textsc{I} &   5 &    6.79 &    0.06 &  --0.72 &    0.33 &    0.03 &&
-  Si \textsc{I} &   4 &    5.89 &    0.05 &  --1.62 &    0.31 &    0.03 \\
-   K \textsc{I} &   1 &    4.94 &    0.00 &  --0.09 &    0.96 &    0.00 &&
-   K \textsc{I} &   1 &    3.91 &    0.00 &  --1.12 &    0.81 &    0.00 \\
-  Ca \textsc{I} &   4 &    5.60 &    0.02 &  --0.74 &    0.31 &    0.01 &&
-  Ca \textsc{I} &   4 &    4.71 &    0.02 &  --1.63 &    0.30 &    0.01 \\
- Sc \textsc{II} &   6 &    2.25 &    0.11 &  --0.90 &    0.16 &    0.04 &&
- Sc \textsc{II} &   5 &    1.30 &    0.05 &  --1.85 &    0.08 &    0.02 \\
-  Ti \textsc{I} &   1 &    4.36 &    0.00 &  --0.59 &    0.46 &    0.00 &&
-  Ti \textsc{I} &   3 &    3.19 &    0.03 &  --1.76 &    0.17 &    0.02 \\
- Ti \textsc{II} &   3 &    4.33 &    0.04 &  --0.62 &    0.44 &    0.02 &&
- Ti \textsc{II} &   3 &    3.44 &    0.10 &  --1.51 &    0.42 &    0.06 \\
-   V \textsc{I} &   3 &    3.17 &    0.13 &  --0.76 &    0.29 &    0.08 &&
-   V \textsc{I} &   5 &    1.87 &    0.07 &  --2.06 &  --0.13 &    0.03 \\
-  Cr \textsc{I} &  15 &    4.46 &    0.05 &  --1.18 &  --0.13 &    0.01 &&
-  Cr \textsc{I} &  12 &    3.49 &    0.05 &  --2.15 &  --0.22 &    0.01 \\
- Cr \textsc{II} &   3 &    4.76 &    0.02 &  --0.88 &    0.17 &    0.01 &&
- Cr \textsc{II} &   2 &    3.90 &    0.02 &  --1.74 &    0.19 &    0.01 \\
-  Mn \textsc{I} &   3 &    4.08 &    0.03 &  --1.35 &  --0.29 &    0.02 &&
-  Mn \textsc{I} &   3 &    3.08 &    0.02 &  --2.35 &  --0.42 &    0.01 \\
-  Fe \textsc{I} &  51 &    6.45 &    0.10 &  --1.05 &    0.00 &    0.01 &&
-  Fe \textsc{I} &  62 &    5.57 &    0.11 &  --1.93 &    0.00 &    0.01 \\
- Fe \textsc{II} &  13 &    6.50 &    0.07 &  --1.00 &    0.05 &    0.02 &&
- Fe \textsc{II} &  14 &    5.61 &    0.12 &  --1.89 &    0.04 &    0.03 \\
-  Co \textsc{I} &   3 &    4.10 &    0.06 &  --0.89 &    0.16 &    0.03 &&
-  Co \textsc{I} &   6 &    3.11 &    0.07 &  --1.88 &    0.05 &    0.03 \\
-  Ni \textsc{I} &   5 &    5.29 &    0.02 &  --0.93 &    0.13 &    0.01 &&
-  Ni \textsc{I} &   5 &    4.22 &    0.11 &  --2.00 &  --0.07 &    0.05 \\
-  Cu \textsc{I} &   1 &    2.84 &    0.00 &  --1.35 &  --0.30 &    0.00 &&
-  Cu \textsc{I} &   1 &    1.73 &    0.00 &  --2.46 &  --0.53 &    0.00 \\
-  Zn \textsc{I} &   2 &    3.58 &    0.03 &  --0.98 &    0.07 &    0.02 &&
-  Zn \textsc{I} &   2 &    2.72 &    0.03 &  --1.83 &    0.10 &    0.02 \\
-  Sr \textsc{I} &   1 &    1.65 &    0.00 &  --1.22 &  --0.17 &    0.00 &&
-  Sr \textsc{I} &   1 &    0.53 &    0.00 &  --2.34 &  --0.41 &    0.00 \\
-  Y \textsc{II} &   5 &    1.14 &    0.05 &  --1.07 &  --0.02 &    0.02 &&
-  Y \textsc{II} &   7 &    0.12 &    0.11 &  --2.09 &  --0.16 &    0.04 \\
-  Zr \textsc{I} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata &&
-  Zr \textsc{I} &   1 &    0.79 &    0.00 &  --1.79 &    0.14 &    0.00 \\
- Zr \textsc{II} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata &&
- Zr \textsc{II} &   1 &    0.68 &    0.00 &  --1.90 &    0.03 &    0.00 \\
- Ba \textsc{II} &   1 &    1.16 &    0.00 &  --1.02 &    0.03 &    0.00 &&
- Ba \textsc{II} &   1 &    0.22 &    0.00 &  --1.96 &  --0.03 &    0.00 \\
- La \textsc{II} &   1 &    0.61 &    0.00 &  --0.49 &    0.56 &    0.00 &&
- La \textsc{II} &   2 &  --0.68 &    0.03 &  --1.78 &    0.16 &    0.02 \\
- Ce \textsc{II} &   2 &    0.37 &    0.03 &  --1.21 &  --0.16 &    0.02 &&
- Ce \textsc{II} &   5 &  --0.39 &    0.18 &  --1.97 &  --0.04 &    0.08 \\
- Nd \textsc{II} &   3 &    0.56 &    0.06 &  --0.86 &    0.19 &    0.03 &&
- Nd \textsc{II} &  10 &  --0.36 &    0.04 &  --1.78 &    0.15 &    0.01 \\
- Eu \textsc{II} &   1 &  --0.01 &    0.00 &  --0.53 &    0.52 &    0.00 &&
- Eu \textsc{II} &   1 &  --1.07 &    0.00 &  --1.59 &    0.34 &    0.00 \\
-
-\cline{1-7} \cline{9-15} \\ \\
-\multicolumn{7}{c}{HD\,141531} && \multicolumn{7}{c}{HD\,142948} \\
-\cline{1-7} \cline{9-15}
-   C (CH)       &   2 &    6.33 &    0.20 &  --2.10 &  --0.48 &    0.20 &&
-   C (CH)       &   2 &    7.72 &    0.20 &  --0.71 &    0.03 &    0.20 \\
-   O \textsc{I} &   2 &    7.33 &    0.01 &  --1.35 &    0.34 &    0.01 &&
-   O \textsc{I} &   2 &    8.43 &    0.02 &  --0.26 &    0.47 &    0.02 \\
-  Na \textsc{I} &   2 &    4.28 &    0.05 &  --1.96 &  --0.27 &    0.04 &&
-  Na \textsc{I} &   3 &    5.73 &    0.13 &  --0.51 &    0.22 &    0.08 \\
-  Mg \textsc{I} &   2 &    6.30 &    0.15 &  --1.29 &    0.40 &    0.10 &&
-  Mg \textsc{I} &   3 &    7.24 &    0.12 &  --0.36 &    0.38 &    0.07 \\
-  Al \textsc{I} &   2 &    4.74 &    0.10 &  --1.71 &  --0.02 &    0.07 &&
-  Al \textsc{I} &   4 &    5.94 &    0.08 &  --0.51 &    0.23 &    0.04 \\
-  Si \textsc{I} &   5 &    6.03 &    0.10 &  --1.48 &    0.21 &    0.04 &&
-  Si \textsc{I} &   5 &    7.07 &    0.05 &  --0.44 &    0.30 &    0.02 \\
-   K \textsc{I} &   1 &    3.99 &    0.00 &  --1.04 &    0.65 &    0.00 &&
-   K \textsc{I} &   1 &    5.04 &    0.00 &    0.01 &    0.75 &    0.00 \\
-  Ca \textsc{I} &   4 &    4.90 &    0.03 &  --1.44 &    0.25 &    0.01 &&
-  Ca \textsc{I} &   4 &    5.78 &    0.01 &  --0.56 &    0.18 &    0.01 \\
- Sc \textsc{II} &   4 &    1.56 &    0.04 &  --1.59 &    0.10 &    0.02 &&
- Sc \textsc{II} &   6 &    2.57 &    0.11 &  --0.58 &    0.16 &    0.05 \\
-  Ti \textsc{I} &   4 &    3.33 &    0.07 &  --1.62 &    0.07 &    0.03 &&
-  Ti \textsc{I} &   4 &    4.44 &    0.09 &  --0.51 &    0.23 &    0.04 \\
- Ti \textsc{II} &   4 &    3.71 &    0.08 &  --1.24 &    0.46 &    0.04 &&
- Ti \textsc{II} &   3 &    4.40 &    0.21 &  --0.55 &    0.19 &    0.12 \\
-   V \textsc{I} &   5 &    2.12 &    0.07 &  --1.81 &  --0.11 &    0.03 &&
-   V \textsc{I} &   5 &    3.31 &    0.11 &  --0.62 &    0.12 &    0.05 \\
-  Cr \textsc{I} &  12 &    3.68 &    0.06 &  --1.96 &  --0.27 &    0.02 &&
-  Cr \textsc{I} &  13 &    4.67 &    0.15 &  --0.97 &  --0.23 &    0.04 \\
- Cr \textsc{II} &   2 &    4.11 &    0.02 &  --1.53 &    0.16 &    0.01 &&
- Cr \textsc{II} &   3 &    4.88 &    0.03 &  --0.76 &  --0.02 &    0.02 \\
-  Mn \textsc{I} &   3 &    3.29 &    0.04 &  --2.14 &  --0.45 &    0.02 &&
-  Mn \textsc{I} &   3 &    4.54 &    0.03 &  --0.89 &  --0.15 &    0.02 \\
-  Fe \textsc{I} &  54 &    5.81 &    0.06 &  --1.69 &    0.00 &    0.01 &&
-  Fe \textsc{I} &  61 &    6.76 &    0.10 &  --0.74 &    0.00 &    0.01 \\
- Fe \textsc{II} &  13 &    5.86 &    0.03 &  --1.64 &    0.05 &    0.01 &&
- Fe \textsc{II} &  13 &    6.75 &    0.06 &  --0.75 &  --0.02 &    0.02 \\
-  Co \textsc{I} &   5 &    3.23 &    0.09 &  --1.76 &  --0.07 &    0.04 &&
-  Co \textsc{I} &   5 &    4.42 &    0.08 &  --0.57 &    0.17 &    0.03 \\
-  Ni \textsc{I} &   7 &    4.42 &    0.12 &  --1.80 &  --0.11 &    0.04 &&
-  Ni \textsc{I} &   5 &    5.62 &    0.04 &  --0.60 &    0.13 &    0.02 \\
-  Cu \textsc{I} &   1 &    2.03 &    0.00 &  --2.16 &  --0.47 &    0.00 &&
-  Cu \textsc{I} &   1 &    3.53 &    0.00 &  --0.66 &    0.08 &    0.00 \\
-  Zn \textsc{I} &   2 &    2.80 &    0.04 &  --1.76 &  --0.07 &    0.03 &&
-  Zn \textsc{I} &   2 &    3.89 &    0.06 &  --0.67 &    0.07 &    0.04 \\
-  Sr \textsc{I} &   1 &    0.66 &    0.00 &  --2.21 &  --0.52 &    0.00 &&
-  Sr \textsc{I} &   1 &    1.67 &    0.00 &  --1.20 &  --0.46 &    0.00 \\
-  Y \textsc{II} &   6 &    0.27 &    0.13 &  --1.94 &  --0.24 &    0.05 &&
-  Y \textsc{II} &   6 &    1.33 &    0.32 &  --0.88 &  --0.14 &    0.13 \\
-  Zr \textsc{I} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata &&
-  Zr \textsc{I} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
- Zr \textsc{II} &   1 &    0.75 &    0.00 &  --1.83 &  --0.14 &    0.00 &&
- Zr \textsc{II} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
- Ba \textsc{II} &   1 &    0.40 &    0.00 &  --1.78 &  --0.09 &    0.00 &&
- Ba \textsc{II} &   2 &    1.18 &    0.01 &  --1.00 &  --0.26 &    0.01 \\
- La \textsc{II} &   2 &  --0.55 &    0.08 &  --1.66 &    0.04 &    0.05 &&
- La \textsc{II} &   2 &    0.43 &    0.12 &  --0.67 &    0.07 &    0.08 \\
- Ce \textsc{II} &   4 &  --0.31 &    0.12 &  --1.89 &  --0.20 &    0.06 &&
- Ce \textsc{II} &   3 &    0.54 &    0.20 &  --1.04 &  --0.30 &    0.11 \\
- Nd \textsc{II} &  10 &  --0.20 &    0.08 &  --1.62 &    0.07 &    0.02 &&
- Nd \textsc{II} &   6 &    0.79 &    0.10 &  --0.63 &    0.11 &    0.04 \\
- Eu \textsc{II} &   1 &  --0.83 &    0.00 &  --1.35 &    0.34 &    0.00 &&
- Eu \textsc{II} &   1 &    0.16 &    0.00 &  --0.36 &    0.38 &    0.00 \\
-\hline
-\end{longtable*}
-
-\begin{longtable*}{lccccccclcccccc}
-\caption{\\ Program Star Abundances\label{tab:program-star-abundances}} \tabularnewline
-\cline{1-15}
-Species & $N$ & $\log\epsilon(X)$ & $\sigma_\epsilon$ & [X/H] & [X/Fe] & $\sigma$ && 
-Species & $N$ & $\log\epsilon(X)$ & $\sigma_\epsilon$ & [X/H] & [X/Fe] & $\sigma$ \tabularnewline
-\cline{1-15} \tabularnewline
-% This works.
-\endhead
-\hline
-\multicolumn{15}{r}{Continued..}
-\endfoot
-\hline
-\endlastfoot
-
-\\
-\multicolumn{7}{c}{J221821-183424} & \colhead{} & \multicolumn{7}{c}{C222531-145437} \\
-\cline{1-7} \cline{9-15}
-   C (CH)       &   2 &    6.55 &    0.20 &  --1.88 &  --0.30 &    0.25 &&
-   C (CH)       &   2 &    7.15 &    0.20 &  --1.28 &  --0.05 &    0.20 \\
-   O \textsc{I} &   2 &    7.55 &    0.04 &  --1.13 &    0.45 &    0.02 &&
-   O \textsc{I} &   2 &    7.96 &    0.00 &  --0.73 &    0.49 &    0.00 \\
-  Na \textsc{I} &   1 &    4.75 &    0.00 &  --1.49 &    0.09 &    0.00 &&
-  Na \textsc{I} &   2 &    5.12 &    0.02 &  --1.12 &    0.10 &    0.01 \\
-  Mg \textsc{I} &   3 &    6.37 &    0.09 &  --1.23 &    0.35 &    0.05 &&
-  Mg \textsc{I} &   2 &    6.90 &    0.08 &  --0.70 &    0.53 &    0.06 \\
-  Al \textsc{I} &   1 &    5.08 &    0.00 &  --1.37 &    0.21 &    0.00 &&
-  Al \textsc{I} &   4 &    5.94 &    0.10 &  --0.51 &    0.71 &    0.05 \\
-  Si \textsc{I} &   5 &    6.32 &    0.08 &  --1.19 &    0.39 &    0.04 &&
-  Si \textsc{I} &   5 &    7.07 &    0.15 &  --0.44 &    0.79 &    0.07 \\
-   K \textsc{I} &   1 &    4.34 &    0.00 &  --0.69 &    0.89 &    0.00 &&
-   K \textsc{I} &   1 &    4.42 &    0.00 &  --0.61 &    0.62 &    0.00 \\
-  Ca \textsc{I} &   4 &    5.01 &    0.04 &  --1.33 &    0.25 &    0.02 &&
-  Ca \textsc{I} &   4 &    5.57 &    0.04 &  --0.77 &    0.45 &    0.02 \\
- Sc \textsc{II} &   6 &    1.53 &    0.08 &  --1.62 &  --0.04 &    0.03 &&
- Sc \textsc{II} &   5 &    2.11 &    0.12 &  --1.04 &    0.19 &    0.06 \\
-  Ti \textsc{I} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata &&
-  Ti \textsc{I} &   4 &    4.10 &    0.03 &  --0.85 &    0.37 &    0.01 \\
- Ti \textsc{II} &   4 &    3.80 &    0.13 &  --1.15 &    0.43 &    0.06 &&
- Ti \textsc{II} &   2 &    4.12 &    0.13 &  --0.83 &    0.40 &    0.09 \\
-   V \textsc{I} &   3 &    2.28 &    0.01 &  --1.65 &  --0.07 &    0.01 &&
-   V \textsc{I} &   6 &    3.02 &    0.16 &  --0.92 &    0.31 &    0.06 \\
-  Cr \textsc{I} &  11 &    3.80 &    0.06 &  --1.84 &  --0.26 &    0.02 &&
-  Cr \textsc{I} &   8 &    4.24 &    0.17 &  --1.40 &  --0.17 &    0.06 \\
- Cr \textsc{II} &   2 &    4.07 &    0.03 &  --1.57 &    0.01 &    0.02 &&
- Cr \textsc{II} &   1 &    4.38 &    0.00 &  --1.26 &  --0.03 &    0.00 \\
-  Mn \textsc{I} &   3 &    3.35 &    0.03 &  --2.08 &  --0.49 &    0.02 &&
-  Mn \textsc{I} &   3 &    4.20 &    0.04 &  --1.23 &  --0.01 &    0.03 \\
-  Fe \textsc{I} &  52 &    5.92 &    0.09 &  --1.58 &    0.00 &    0.01 &&
-  Fe \textsc{I} &  60 &    6.27 &    0.10 &  --1.23 &    0.00 &    0.01 \\
- Fe \textsc{II} &  13 &    5.94 &    0.05 &  --1.56 &    0.02 &    0.01 &&
- Fe \textsc{II} &  10 &    6.30 &    0.06 &  --1.20 &    0.03 &    0.02 \\
-  Co \textsc{I} &   4 &    3.32 &    0.16 &  --1.67 &  --0.09 &    0.08 &&
-  Co \textsc{I} &   5 &    3.92 &    0.12 &  --1.07 &    0.15 &    0.05 \\
-  Ni \textsc{I} &   5 &    4.61 &    0.14 &  --1.61 &  --0.03 &    0.06 &&
-  Ni \textsc{I} &   7 &    5.07 &    0.09 &  --1.15 &    0.08 &    0.04 \\
-  Cu \textsc{I} &   1 &    2.18 &    0.00 &  --2.01 &  --0.43 &    0.00 &&
-  Cu \textsc{I} &   1 &    3.33 &    0.00 &  --0.86 &    0.37 &    0.00 \\
-  Zn \textsc{I} &   1 &    3.07 &    0.00 &  --1.49 &    0.09 &    0.00 &&
-  Zn \textsc{I} &   2 &    3.56 &    0.24 &  --1.00 &    0.23 &    0.17 \\
-  Sr \textsc{I} &   1 &    0.82 &    0.00 &  --2.05 &  --0.47 &    0.00 &&
-  Sr \textsc{I} &   1 &    1.55 &    0.00 &  --1.32 &  --0.09 &    0.00 \\
- Sr \textsc{II} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata &&
- Sr \textsc{II} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
-  Y \textsc{II} &   3 &    0.44 &    0.02 &  --1.77 &  --0.19 &    0.01 &&
-  Y \textsc{II} &   5 &    1.78 &    0.16 &  --0.43 &    0.79 &    0.07 \\
-  Zr \textsc{I} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata &&
-  Zr \textsc{I} &   3 &    2.07 &    0.05 &  --0.51 &    0.72 &    0.03 \\
- Zr \textsc{II} &   1 &    0.97 &    0.00 &  --1.61 &  --0.03 &    0.00 &&
- Zr \textsc{II} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
- Ba \textsc{II} &   2 &    0.60 &    0.05 &  --1.58 &    0.00 &    0.04 &&
- Ba \textsc{II} &   3 &    1.58 &    0.02 &  --0.60 &    0.62 &    0.01 \\
- La \textsc{II} &   2 &  --0.47 &    0.00 &  --1.57 &    0.01 &    0.00 &&
- La \textsc{II} &   2 &    0.55 &    0.00 &  --0.55 &    0.68 &    0.00 \\
- Ce \textsc{II} &   3 &  --0.39 &    0.06 &  --1.97 &  --0.39 &    0.03 &&
- Ce \textsc{II} &   5 &    0.73 &    0.15 &  --0.85 &    0.37 &    0.07 \\
- Nd \textsc{II} &  10 &  --0.22 &    0.07 &  --1.64 &  --0.06 &    0.02 &&
- Nd \textsc{II} &   8 &    0.88 &    0.13 &  --0.54 &    0.69 &    0.05 \\
- Eu \textsc{II} &   2 &  --0.10 &    0.65 &  --0.62 &    0.96 &    0.46 &&
- Eu \textsc{II} &   1 &  --0.19 &    0.00 &  --0.71 &    0.52 &    0.00 \\
-
-\cline{1-7} \cline{9-15} \\ \\
-\multicolumn{7}{c}{J223504-152834} && \multicolumn{7}{c}{J223811-104126} \\
-\cline{1-7} \cline{9-15}
-   C (CH)       &   2 &    7.71 &    0.30 &  --0.72 &  --0.10 &    0.30 &&
-   C (CH)       &   2 &    7.05 &    0.25 &  --1.38 &    0.05 &    0.25 \\
-   O \textsc{I} &   2 &    8.50 &    0.10 &  --0.19 &    0.43 &    0.07 &&
-   O \textsc{I} &   1 &    8.27 &    0.00 &  --0.42 &    0.15\footnote{Abundance derived from the permitted O \textsc{i} triplet instead of the forbidden [O \textsc{i}] lines, see \S\ref{sec:oxygen-abundances}} &    0.08 \\
-  Na \textsc{I} &   3 &    5.87 &    0.12 &  --0.37 &    0.26 &    0.07 &&
-  Na \textsc{I} &   1 &    4.89 &    0.00 &  --1.35 &    0.08 &    0.00 \\
-  Mg \textsc{I} &   3 &    7.48 &    0.15 &  --0.12 &    0.51 &    0.09 &&
-  Mg \textsc{I} &   2 &    6.51 &    0.03 &  --1.09 &    0.34 &    0.02 \\
-  Al \textsc{I} &   3 &    6.12 &    0.09 &  --0.33 &    0.29 &    0.05 &&
-  Al \textsc{I} &   2 &    5.13 &    0.13 &  --1.32 &    0.11 &    0.10 \\
-  Si \textsc{I} &   5 &    7.24 &    0.10 &  --0.27 &    0.35 &    0.05 &&
-  Si \textsc{I} &   3 &    6.42 &    0.04 &  --1.09 &    0.34 &    0.02 \\
-   K \textsc{I} &   1 &    5.05 &    0.00 &    0.02 &    0.64 &    0.00 &&
-   K \textsc{I} &   1 &    4.50 &    0.00 &  --0.53 &    0.90 &    0.00 \\
-  Ca \textsc{I} &   4 &    6.06 &    0.03 &  --0.28 &    0.34 &    0.01 &&
-  Ca \textsc{I} &   4 &    5.32 &    0.03 &  --1.02 &    0.41 &    0.02 \\
- Sc \textsc{II} &   6 &    2.74 &    0.14 &  --0.41 &    0.22 &    0.06 &&
- Sc \textsc{II} &   6 &    1.72 &    0.14 &  --1.43 &  --0.00 &    0.06 \\
-  Ti \textsc{I} &   4 &    4.65 &    0.02 &  --0.30 &    0.32 &    0.01 &&
-  Ti \textsc{I} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
- Ti \textsc{II} &   1 &    4.67 &    0.00 &  --0.28 &    0.34 &    0.00 &&
- Ti \textsc{II} &   4 &    3.79 &    0.09 &  --1.16 &    0.27 &    0.04 \\
-   V \textsc{I} &   4 &    3.59 &    0.10 &  --0.34 &    0.28 &    0.05 &&
-   V \textsc{I} &   1 &    2.45 &    0.00 &  --1.48 &  --0.05 &    0.00 \\
-  Cr \textsc{I} &   7 &    4.90 &    0.11 &  --0.74 &  --0.11 &    0.04 &&
-  Cr \textsc{I} &  12 &    4.10 &    0.06 &  --1.54 &  --0.11 &    0.02 \\
- Cr \textsc{II} &   2 &    4.84 &    0.04 &  --0.79 &  --0.17 &    0.03 &&
- Cr \textsc{II} &   3 &    4.34 &    0.07 &  --1.30 &    0.12 &    0.04 \\
-  Mn \textsc{I} &   3 &    5.06 &    0.10 &  --0.37 &    0.25 &    0.06 &&
-  Mn \textsc{I} &   3 &    3.58 &    0.04 &  --1.85 &  --0.43 &    0.02 \\
-  Fe \textsc{I} &  63 &    6.88 &    0.12 &  --0.62 &    0.00 &    0.02 &&
-  Fe \textsc{I} &  33 &    6.07 &    0.06 &  --1.43 &  --0.00 &    0.01 \\
- Fe \textsc{II} &  12 &    6.87 &    0.07 &  --0.63 &  --0.01 &    0.02 &&
- Fe \textsc{II} &   9 &    6.04 &    0.07 &  --1.46 &  --0.03 &    0.02 \\
-  Co \textsc{I} &   5 &    4.59 &    0.14 &  --0.40 &    0.22 &    0.06 &&
-  Co \textsc{I} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
-  Ni \textsc{I} &   7 &    5.64 &    0.09 &  --0.58 &    0.05 &    0.03 &&
-  Ni \textsc{I} &   2 &    4.84 &    0.04 &  --1.38 &    0.05 &    0.03 \\
-  Cu \textsc{I} &   1 &    3.81 &    0.00 &  --0.38 &    0.24 &    0.00 &&
-  Cu \textsc{I} &   1 &    2.40 &    0.00 &  --1.79 &  --0.36 &    0.00 \\
-  Zn \textsc{I} &   2 &    4.21 &    0.03 &  --0.35 &    0.27 &    0.02 &&
-  Zn \textsc{I} &   2 &    3.15 &    0.05 &  --1.41 &    0.02 &    0.04 \\
-  Sr \textsc{I} &   1 &    1.83 &    0.00 &  --1.04 &  --0.42 &    0.00 &&
-  Sr \textsc{I} &   1 &    1.23 &    0.00 &  --1.64 &  --0.21 &    0.00 \\
- Sr \textsc{II} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata &&
- Sr \textsc{II} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
-  Y \textsc{II} &   3 &    1.80 &    0.03 &  --0.41 &    0.21 &    0.02 &&
-  Y \textsc{II} &   6 &    0.76 &    0.06 &  --1.45 &  --0.02 &    0.03 \\
-  Zr \textsc{I} &   3 &    2.26 &    0.05 &  --0.32 &    0.31 &    0.03 &&
-  Zr \textsc{I} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
- Zr \textsc{II} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata &&
- Zr \textsc{II} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
- Ba \textsc{II} &   2 &    1.65 &    0.02 &  --0.53 &    0.10 &    0.01 &&
- Ba \textsc{II} &   2 &    0.70 &    0.03 &  --1.48 &  --0.05 &    0.02 \\
- La \textsc{II} &   2 &    0.74 &    0.05 &  --0.36 &    0.26 &    0.04 &&
- La \textsc{II} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
- Ce \textsc{II} &   3 &    0.87 &    0.13 &  --0.71 &  --0.09 &    0.08 &&
- Ce \textsc{II} &   2 &  --0.07 &    0.02 &  --1.65 &  --0.22 &    0.02 \\
- Nd \textsc{II} &   6 &    1.27 &    0.13 &  --0.15 &    0.47 &    0.06 &&
- Nd \textsc{II} &   1 &  --0.25 &    0.00 &  --1.67 &  --0.24 &    0.00 \\
- Eu \textsc{II} &   1 &    0.52 &    0.00 &    0.00 &    0.62 &    0.00 &&
- Eu \textsc{II} &   1 &  --0.55 &    0.00 &  --1.07 &    0.36 &    0.00 \\
-
-\cline{1-7} \cline{9-15} \\ \\
-\multicolumn{7}{c}{C2306265-085103} \\
-\cline{1-7}
-   C (CH)       &   2 &    7.20 &    0.20 &  --1.23 &  --0.10 &    0.20 \\
-   O \textsc{I} &   2 &    8.02 &    0.04 &  --0.67 &    0.46 &    0.03 \\
-  Na \textsc{I} &   2 &    5.31 &    0.01 &  --0.93 &    0.21 &    0.00 \\
-  Mg \textsc{I} &   2 &    6.90 &    0.06 &  --0.70 &    0.44 &    0.05 \\
-  Al \textsc{I} &   4 &    5.65 &    0.08 &  --0.80 &    0.33 &    0.04 \\
-  Si \textsc{I} &   5 &    6.78 &    0.08 &  --0.73 &    0.40 &    0.04 \\
-   K \textsc{I} &   1 &    4.46 &    0.00 &  --0.57 &    0.56 &    0.00 \\
-  Ca \textsc{I} &   4 &    5.56 &    0.04 &  --0.78 &    0.35 &    0.02 \\
- Sc \textsc{II} &   6 &    2.28 &    0.16 &  --0.87 &    0.26 &    0.06 \\
-  Ti \textsc{I} &   4 &    4.13 &    0.03 &  --0.82 &    0.32 &    0.01 \\
- Ti \textsc{II} &   3 &    4.32 &    0.35 &  --0.63 &    0.51 &    0.20 \\
-   V \textsc{I} &   4 &    2.96 &    0.05 &  --0.98 &    0.16 &    0.03 \\
-  Cr \textsc{I} &   3 &    4.13 &    0.12 &  --1.51 &  --0.38 &    0.07 \\
- Cr \textsc{II} &   1 &    4.50 &    0.00 &  --1.14 &  --0.01 &    0.00 \\
-  Mn \textsc{I} &   3 &    4.40 &    0.10 &  --1.03 &    0.10 &    0.06 \\
-  Fe \textsc{I} &  62 &    6.37 &    0.12 &  --1.13 &    0.00 &    0.01 \\
- Fe \textsc{II} &  11 &    6.39 &    0.10 &  --1.11 &    0.02 &    0.03 \\
-  Co \textsc{I} &   5 &    4.14 &    0.14 &  --0.85 &    0.28 &    0.06 \\
-  Ni \textsc{I} &   7 &    5.11 &    0.07 &  --1.11 &    0.02 &    0.03 \\
-  Cu \textsc{I} &   1 &    3.53 &    0.00 &  --0.66 &    0.47 &    0.00 \\
-  Zn \textsc{I} &   2 &    3.48 &    0.15 &  --1.08 &    0.05 &    0.10 \\
-  Sr \textsc{I} &   1 &    0.94 &    0.00 &  --1.93 &  --0.80 &    0.00 \\
- Sr \textsc{II} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
-  Y \textsc{II} &   4 &    1.26 &    0.26 &  --0.95 &    0.18 &    0.13 \\
-  Zr \textsc{I} &   3 &    1.60 &    0.05 &  --0.98 &    0.16 &    0.03 \\
- Zr \textsc{II} &   0 & \nodata & \nodata & \nodata & \nodata & \nodata \\
- Ba \textsc{II} &   2 &    0.99 &    0.04 &  --1.19 &  --0.06 &    0.03 \\
- La \textsc{II} &   2 &  --0.02 &    0.03 &  --1.12 &    0.01 &    0.02 \\
- Ce \textsc{II} &   2 &    0.09 &    0.02 &  --1.49 &  --0.36 &    0.01 \\
- Nd \textsc{II} &   7 &    0.58 &    0.21 &  --0.84 &    0.29 &    0.08 \\
- Eu \textsc{II} &   1 &  --0.32 &    0.00 &  --0.84 &    0.29 &    0.00 \\
- \hline
-\end{longtable*}
-
-\subsubsection{Aluminium}
-\label{sec:aluminium-abundances}
-There are six aluminium transition lines in our optical spectra.
-The strongest of these lines occur at 3944 and {3961\,\AA} and are visible in all of our stars.
-However this is a particularly crowded spectral region: the lines fall between the strong Ca H and K lines, with the {3961\,\AA} transition clearly located in the wing of the Ca H line.
-This makes the continuum determination and subsequent aluminium measurement non-trivial, especially given the metallicity of our stars.
-Additionally, the 3944 and {3961\,{\AA}} lines suffer from appreciable departures from the assumption of local thermal equilibrium (LTE), resulting in under-estimated abundances by up to $\sim$0.60\,dex \citep{baumueller;gehren_1997}.
-Instead, we have measured Al abundances from other available transitions: the {Al\,\textsc{i}} lines at 6696, 6698, 7835 and {7836\,{\AA}}.
-Although these lines are weaker than the bluer {Al\,\textsc{i}} lines, their surrounding regions are uncrowded from strong absorption lines.
-
-Generally the four {Al\,\textsc{i}} lines are in reasonable agreement with one another, yielding random scatter of less than 0.05\,dex.
-However, these lines were not always detected in the data.
-The strength of the lines is noticeably weakened below a 3$\sigma$ detection with decreasing metallicity and increasing temperature.
-For our most metal-poor star, J221821-183424, only a single {Al\,\textsc{i}} line was detectable, and so we have adopted a conservative uncertainty of {$\pm0.10$\,dex}.
-
-\subsubsection{Iron-peak Elements (Sc, V, Cr and Mn)}
-\label{sec:fe-peak-abundances}
-
-As one expects from supernovae, the {Fe-peak} elemental abundances exhibit similar trends (Figure \ref{fig:fe-peak-elements}).
-The noteworthy exception is chromium, where the median abundance is {$\mbox{[Cr/Fe]} = -0.08 \pm 0.12$} and varies little with overall metallicity.
-The number of clean, suitable {Cr\,\textsc{i}} lines available between candidates fluctuated from three to twelve.
-Very little line-to-line scatter is present in both {Cr\,\textsc{i}} and \textsc{ii}: the random scatter is below {0.04\,dex} for most stars, with the isolated example of {J223504-152834} where ${\sigma(\mbox{[Cr\,\textsc{ii}/Fe]}) = 0.29\,{\rm dex}}$, and only three lines were available.
-The {Cr\,\textsc{i}} and \textsc{ii} mean abundances for {J223504-152834} are in good agreement (0.05\,dex), and since none of the measured Gaussian profiles appeared particularly unusual, we chose not to exclude any measurements.
-For all other stars, the ${\langle{\rm Cr}\,\textsc{i} - {\rm Cr}\,\textsc{ii}\rangle}$ abundance differences varied between {0.02\,dex} up to {0.31\,dex}.
-The largest discrepancy occurred in our hottest star, where fewer chromium transitions were measurable.
-Chromium abundances are only available for one of the standard stars, where our {[Cr/Fe] = 0.03}\,dex is in excellent agreement with \citet{fulbright_2000}, where they find {[Cr/Fe] = 0.04}\,dex.
-
-% Iron peak elements
-\begin{figure}[h]
-	\includegraphics[width=\columnwidth]{./figures/aquarius-fe-peak.pdf}
-	\caption{Iron peak element abundances (Sc, V, Cr, and Mn) with respect to iron for all Aquarius stream stars.}
-	\label{fig:fe-peak-elements}
-\end{figure}
-
-All other iron peak elements considered (Sc, V, Mn) all exhibit a slight downward trend in metallicity, with manganese demonstrating the strongest gradient: varying between {$\mbox{[Mn/Fe]} = -0.52$\,dex} to {$+0.31$\,dex} in the most metal-poor and -rich stars respectively.
-The [Sc/Fe] measurements presented in Figure \ref{fig:fe-peak-elements} are calculated from six clean {Sc\,\textsc{ii}} lines, and there is very minimal line-to-line scatter, the largest of which is {0.06\,dex}.
-Three Aquarius stream stars exhibit {[Sc/Fe] $\sim$ +0.20}, while {J221821-183424} and {J223811-104126} have ${\mbox{[Sc/Fe]} = 0.01}$ and {0.05\,dex}, respectively.
-\\
-
-\subsubsection{Nickel}
-Most Aquarius stream stars have seven clean {Ni\,\textsc{i}} transitions available.
-These lines are in excellent agreement, with typical scatter of {0.03\,dex}.
-Nickel abundances have been published for two of our standard stars: HD\,76932 \citep{fulbright_2000} and HD\,141531 \citep{shetrone_1996}.
-In both cases, our [Ni/Fe] abundance ratios are slightly higher by 0.08 and 0.10\,dex respectively.
-The different solar compositions employed by this study accounts for 0.01\,dex.
-While our nickel abundances may be slightly over-estimated, this does not affect our conclusions.
-
-\subsection{Neutron-capture Elements}
-Neutron-capture elements (Sr to Eu; ${38 \leqslant Z \leqslant 63}$) can be forged through multiple nucleosynthetic processes.
-The two primary processes that produce these elements are the rapid ($r$-) process and the slow ($s$-) process.
-While the $r$-process occurs primarily from SN explosions, the $s$-process takes place foremost in AGB stars.
-Measurable neutron-capture elements in our spectra are discussed separately.
-
-\subsubsection{Strontium, Yttrium and Zirconium}
-\label{sec:weak-s-process-elements}
-
-These weak $s$-process elements generally change in lock-step with one another.
-Of Sr, Y and Zr, yttrium has the highest number of clean measurable transitions in our wavelength range.
-The {Sr\,\textsc{ii}} lines at 4077 and {4215\,\AA} were not measurable in any program or standard stars, although {Sr\,\textsc{i}} was detectable at {6645\,\AA}.
-While {[Y\,\textsc{ii}/Fe]} and {[Zr\,\textsc{i}, \textsc{ii}/Fe]} are in good agreement in all candidates, {[Sr\,\textsc{i}/Fe]} is lower and there is significant scatter.
-No obvious telluric contamination was observed in the 6645\,{\AA} line.
-Given that Sr\,\textsc{i} transitions are susceptible to non-LTE effects \citep{hansen;et-al_2013}, we note these Sr abundances should be treated with some caution.
-
-% Sr, Y, Zr in standard stars
-This is the first study to present Sr, Y, and Zr abundances for five of the six standard stars.
-Existing data on neutron-capture abundances were not crucial in selecting standard comparison stars, it was more important to cover a range of stellar parameters.
-
-The Aquarius candidates have yttrium abundances consistent with halo field stars, with the exception of {C222531-145437}.
-With {[Y/Fe] = 0.79}\,dex, {C222531-145437} is significantly overabundant in yttrium for its metallicity \citep[see Figure 4 of][]{travaglio;et-al_2004}.
-The closest star with a similar overabundance in yttrium is the a metal-poor dwarf HD\,23439 with {[Y/Fe] $\sim{}$ 0.60}\,dex.
-{C222531-145437} is consistently over-abundant in Sr and Zr, too.
-All other program and standard stars have $s$-process trends and abundances that are consistent with the chemical evolution of the Milky Way.
-
-\subsubsection{Barium and Lanthanum}
-Barium is primarily produced through the $s$-process, and its measurement requires some careful consideration.
-The strong resonance lines at {4554\,\AA} and {4934\,\AA} have appreciable hyperfine splitting, which can result in over-estimated abundances if unaccounted for.
-There are a few singly ionised lines available in our spectra that do not suffer from strong hyperfine splitting, namely the 5853, 6141 and {6496\,\AA} transitions.
-Depending on the radial velocity of the star, sometimes our {6496\,\AA} line was affected by small amounts of telluric absorption.
-In these cases the line was discarded.
-The abundances tabulated in Table \ref{tab:program-star-abundances} are based on the remaining clean {Ba\,\textsc{ii}} lines at 5853 and {6141\,\AA}, which are generally in good agreement with each other, and the {6496\,\AA} line when it was not affected by Earth's atmospheric absorption.
-
-Our standard stars have [Ba/Fe] abundances very typical of the Milky Way halo.
-Two of the standard stars have published [Ba/Fe] abundance ratios from high-resolution spectra: HD\,44007 and HD\,76932.
-We find HD\,44007 to have ${\mbox{[Ba/Fe]} = -0.05 \pm 0.04}$, which is near the mid-point of existing published measurements from \citet{fulbright_2000} and \citet{burris;et-al_2000} of $-0.27$ and {0.05\,dex}, respectively.
-For HD\,76932 our measurement of {$\mbox{[Ba/Fe]} = 0.03$} is in good agreement with the \citet{fulbright_2000} value of $-0.02$, especially so when differences in adopted solar composition are considered.
-
-With one exception, the Aquarius stream candidates have barium abundances that are quite similar to the stellar halo, ranging between ${\mbox{[Ba/Fe]} = -0.02}$ to {0.15\,dex}.
-The exception -- again -- is {C222531-085103}, which has an anomalously high barium abundance of ${\mbox{[Ba/Fe]} = 0.62\,{\rm dex}}$.
-This is $\sim$0.60\,dex higher than the Milky Way trend at its given metallicity of ${\mbox{[Fe/H]} = -1.26\,{\rm dex}}$.
-Our three {Ba\,\textsc{ii}} lines in {C222531-085103} are in excellent agreement with each other: 0.64, 0.61, and {0.68\,dex}.
-The {6496\,\AA} transition in {C222531-085103} has a negligible telluric contribution and was included for this candidate.
-
-% Iron peak elements
-\begin{figure}[h]
-	\includegraphics[width=\columnwidth,height=22.6cm]{./figures/plot-x-on-fe.pdf}
-	\caption{Element ratios for Aquarius stream candidates.
-In the case of [Zr/Fe], {[Zr\,\textsc{i}/Fe]} is taken where available and {[Zr\,\textsc{ii}/Fe]} if no measurement was available for {Zr\,\textsc{i}}.
-See Table \ref{tab:program-star-abundances} for details.}
-	\label{fig:x-on-fe}
-\end{figure}
-
-%  Lanthanum
-% subject to hyperfine splitting. Needs re-doing. Perhaps remove?
-
-\subsubsection{Cesium, Neodymium and Europium}
-Europium abundances have been determined from the equivalent widths of the 6645\,{\AA} Eu\,\textsc{ii} transition and synthesis of the region surrounding the 6437\,{\AA} Eu\,\textsc{ii} feature.
-As pointed out by \citet{Lawler;et-al_2001}, the 6437\,{\AA} feature is appreciably blended by a silicon line at 6437.71\,{\AA}.
-Measurements of the two lines were consistent with a hidden blend: the 6437\,{\AA} Eu\,\textsc{ii} line abundance from equivalent widths was systematically higher than the 6645\,{\AA} counterpart.
-As with other heavy elements except for europium, candidate C222531-145437 is over-abundant in cesium and neodymium with respect to the rest of the sample.
-We note that in our most metal-poor star the two Eu\,\textsc{ii} lines were wildly discrepant.
-Neither profile seemed ill-fitted, so we kept both and accepted an extremely large uncertainty for this measurement.
-
-% elemental abundances
-
-% comparison to literature for a given star
-
-% chemical synthesis
-
-\subsection{Distances}
-\label{sec:distances}
-
-Many groups have determined distances for stars in the RAVE survey catalog, which includes all known Aquarius members.
+% TODO - Update distances in above table
+
+Many groups have determined distances for stars in the RAVE survey catalog, which includes all Aquarius stream members.
 \citet{williams;et-al_2011} tabulated a range of distances inferred by different techniques.
-Not every measurement approach was applicable to all stream members.
-The reduced proper motion distance technique was the only method to infer distances for all Aquarius candidates.
-The variations between distance measurements for the same star were large.
-In particular the distance for {C222531-146537} ranged from $1.4 \pm 0.1$\,kpc \citep{burnett_binney_2010} to $10.3 \pm 2.4$\,kpc \citep{breddels;et-al_2010}, where both groups claim to have the `most likely' distances.
+Not every measurement technique was applicable to all Aquarius stars.
+The reduced proper motion distance technique was the only method to estimate distances for all Aquarius candidates.
+The variations between distance measurements are large.
+In particular, the distance for {C222531-146537} ranged from $1.4 \pm 0.1$\,kpc \citep{burnett_binney_2010} to $10.3 \pm 2.4$\,kpc \citep{breddels;et-al_2010}, where both groups claim to have the ``most likely'' distances.
 
@@
 Using the stellar parameters tabulated in Table \ref{tab:stellar-parameters}, we have calculated distances by isochrone fitting.
-The \citet{dotter;et-al_2008} alpha-enhanced ([$\alpha$/Fe] = +0.4\,dex) isochrones were employed for these calculations, and an age of 10\,Gyr was assumed for all stars.
-The closest point to the isochrone was found by taking the uncertainties in $T_{\rm eff}$ and $\log{g}$ into account and measuring the distance modulus in $J$ band.
-Given the number of uncertain measurements involved in calculating distances ($T_{\rm eff}$, $\log{g}$, E(B-V), $J$) and resulting asymmetric uncertainties, distances were determined from 10,000 Monte-Carlo realisations.
-For the case of {J223811-104126}, the extinction of ${{\rm E(B-V)} = 0.12^{+0.01}_{-0.02}}$ as from the interstellar Na D1 line has been used.
-Table \ref{tab:monte-carlo-data} shows the parameters and uncertainties adopted for the Monte-Carlo realisations.
-Uncertainties in parameters were assumed to be Gaussian.
-The emergent distances and asymmetric uncertainties are also tabulated.
+The \citet{dotter;et-al_2008} $\alpha$-enhanced isochrones were used for these calculations, and an age of 10\,Gyr was assumed for all stars \citep{williams;et-al_2011,wylie-de-boer;et-al_2012}.
+The closest point to the isochrone was found by taking the uncertainties in $T_{\rm eff}$ and $\log{g}$ (see Section \ref{sec:uncertainties}) into account and measuring the distance modulus in the $J$ band.
+Given the (i) number of uncertain measurements involved in calculating distances ($T_{\rm eff}$, $\log{g}$, $E(B-V)$, $J$) and (ii) the resultant asymmetric uncertainties, distances were determined from 10,000 Monte-Carlo realisations.
+Table \ref{tab:monte-carlo-data} lists the input parameters and uncertainties adopted for the Monte-Carlo realisations, as well as the emergent distances and uncertainties.
+Uncertainties in input parameters were assumed to be normally distributed.
 Of the distance scales collated in \citet{williams;et-al_2011}, our distances are in most agreement with the \citet{zwitter;et-al_2010} system.
 In fact, we find the best agreement with the mean of all the distance scales tabulated in \citet{williams;et-al_2011}.
-The uncertainties in our distance determinations are on the order of twenty percent.
-
-\begin{deluxetable*}{lccccccccc}
-\tablecolumns{2}
-\tabletypesize{\scriptsize}
-\tablecaption{Parameters and Uncertainties Adopted for Monte-Carlo Realisations\label{tab:monte-carlo-data}}
-\tablehead{
-	\colhead{Designation} &
-	\colhead{$T_{\rm eff}$} &
-	\colhead{$\log{g}$} &
-	\colhead{$J$} &
-	\colhead{${\rm E(B-V)}$} &
-	\colhead{$D$} &
-	\colhead{$V_{\rm hel}$} &
-	\colhead{$\mu_\alpha$} &
-	\colhead{$\mu_\delta$}
-	\\
-	& (K) & (dex) & (mag) & (mag) & (kpc) & (km s$^{-1}$) & (mas yr$^{-1}$) & (mas yr$^{-1}$)
-}
-\startdata 
-C222531-145437 & $4365 \pm 150$ & $1.25 \pm 0.30$ & $10.341 \pm 0.022$ & $0.03 \pm 0.01$ & $5.1^{+1.1}_{-0.8}$ & $-156.4 \pm 0.1$ & \phn\phn\,$3.5 \pm 2.1$ & $-14.7 \pm 2.2$ \\
-C230626-085103 & $4225 \pm 150$ & $0.85 \pm 0.30$ & $10.312 \pm 0.025$ & $0.05 \pm 0.01$ & $6.5^{+1.4}_{-1.1}$ & $-221.1 \pm 0.1$ & \phn$-2.5 \pm 2.8$ & $-15.4 \pm 2.7$ \\
-J221821-183424 & $4630 \pm 150$ & $0.88 \pm 0.30$ & $10.340 \pm 0.021$ & $0.03 \pm 0.01$ & $5.6^{+1.3}_{-0.9}$ & $-159.5 \pm 0.1$ & $-10.6 \pm 2.5$ & $-19.3 \pm 2.5$ \\
-J223504-152834 & $4650 \pm 150$ & $2.16 \pm 0.30$ & $10.363 \pm 0.025$ & $0.04 \pm 0.01$ & $1.9^{+0.5}_{-0.4}$ & $-169.7 \pm 0.1$ & \phn\,$15.9 \pm 2.2$ & $-12.8 \pm 2.2$ \\
-J223811-104126 & $5190 \pm 150$ & $2.93 \pm 0.30$ & $10.420 \pm 0.018$ & $0.12^{+0.01}_{-0.02}$\footnote{Extinction measured directly from interstellar Na D1 line} & $1.1^{+0.3}_{-0.2}$ & $-235.7 \pm 0.1$ & $-25.3 \pm 2.1$ & $-99.5 \pm 2.1$
-\enddata
-\end{deluxetable*}
+The uncertainties in our distance determinations are on the order of twenty per cent.
 
@@
 % U, V, W calculations
-Velocity vectors and galactic orbits have been determined in the same Monte-Carlo realisations outlined in Section \ref{sec:distances}.
-Uncertainties in distance, proper motions\footnote{The proper motions in Table 1 of \citet{williams;et-al_2011} are mis-associated to incorrect stars.
+Velocity vectors and galactic orbits have been determined in the same Monte-Carlo realisations outlined in Section \ref{sec:distances}, which includes uncertainties in distances, proper motions\footnote{The proper motions in Table 1 of \citet{williams;et-al_2011} are mis-associated to incorrect stars.
 This error was typographical; it did not affect the transverse velocity calculations (M.E.K.
 Williams, private communication).
-The proper motions listed in our Table \ref{tab:monte-carlo-data} are correct.} and heliocentric velocity have been propagated.
-We assumed zero uncertainty in on-sky projected position $(\alpha, \delta)$.
-Orbital energy calculations have assumed a three-component model (bulge, disc, halo) of the galactic potential that reasonably reproduces the galactic rotation curve.
+The proper motions listed in our Table \ref{tab:monte-carlo-data} are correct.} and heliocentric velocities.
+We assume no uncertainty in on-sky position $(\alpha, \delta)$.
+Orbital energy calculations have assumed a three-component (bulge, disc, halo) model of the Galactic potential that reasonably reproduces the Galactic rotation curve.
 The bulge is represented by a Hernquist potential:
@@
 
-\noindent with $b = 4.5$\,kpc and $c = 0.25$\,kpc and the galactic halo is represented by a Navarro-Frenk-White dark matter halo \citep{navarro;et-al_1997}:
+\noindent with $b = 4.5$\,kpc and $c = 0.25$\,kpc and the Galactic halo is represented by a Navarro-Frenk-White dark matter halo \citep{navarro;et-al_1997}:
 
@@
 
-\noindent{}with the three components scaled such that the disc provides 85\% of the radial force at $R_\odot$, in order to yield a flat circular-speed curve at $R_\odot$.
-The solar motion of \citet{schonrich;et-al_2012} has been assumed where $R_\odot$ = 8.27\,kpc and circular velocity speed of $V_c = 238$\,km s$^{-1}$.
-
-% solar motion
-% galactic potential
-
+\noindent{}with the three components scaled such that the disc provides 85\% of the radial force at $R_{\rm GC}$, in order to yield a flat circular-speed curve at $R_{\rm GC}$.
+The solar motion of \citet{schonrich;et-al_2012} has been adopted, where $R_{\rm GC}$ = 8.27\,kpc and a circular velocity speed $V_c = 238$\,km s$^{-1}$.
+
+The Aquarius stream members have bound orbits, all of which are probably retrograde except for {J223504-152834} (Figure \ref{fig:toombre}).
 Orbital energies and angular momenta from Monte-Carlo simulations are illustrated in Figure \ref{fig:orbits}.
 The 16,686 stars from the Geneva-Cophenhagen Survey sample \citep{nordstrom;et-al_2004} are also shown as a reference, which primarily consists of nearby disc stars.
-The Aquarius stream members have bound orbits, all of which are probably retrograde with the exception of {J223504-152834}.
-The chemically distinct star, {C222531-145437}, has a much lower velocity out of the plane ($\sqrt{U^2 + W^2}$) and has an orbit that is  more tightly bound to the Milky Way than the other Aquarius members.
 
@@
 
+\section{Chemical Abundances}
+\label{sec:chemical-abundances}
+We have scaled our chemical abundances to Solar values using the chemical composition described in \citet{asplund;et-al_2009}.
+The abundances for the standard and program stars are shown in Tables \ref{tab:standard-star-abundances} and \ref{tab:program-star-abundances}, respectively.
+The discussion of comparable elements are grouped accordingly.
+
+\subsection{Carbon}
+Carbon is produced by the triple-$\alpha$ process and ejected through supernovae events, or by mass-loss from asymptotic giant branch (AGB) stars \citep{kobayashi;et-al_2011}.
+The carbon abundance at the stellar surface increases as the star evolves along the AGB \citep[e.g.,][]{herwig_2005} owing to repeated third dredge-up events.
+
+%The enriched envelope is then ejected into the interstellar medium by strong stellar winds.
+
+% In particular, the C/O ratio increases, reaching values above unity owing to repeated third dredge-up events.
+The enriched envelope is then ejected into the interstellar medium through strong stellar winds.
+
+We have measured carbon abundances for all stars from the G-band head near 431.3\,nm and the CH molecular feature at 432.3\,nm, by comparing observed spectra with synthetic spectra for different carbon abundances.
+The synthetic spectra were convolved with a Gaussian kernel where the width was determined from nearby atomic lines with known abundances.
+Carbon was measured separately for both features, and in all stars the two measurements agree within 0.10\,dex.
+An example fit to this spectral region for J223811-104126 is shown in Figure \ref{fig:carbon}.
+
+Carbon abundances in our standard stars agree well with the literature.
+For HD\,136316 we find {${\rm [C/Fe]} = -0.50 \pm 0.15$}, where \citet{gratton;et-al_2000} find {[C/Fe] $= -0.66$}.
+Our ${{\rm [C/Fe]} = -0.48}$ measurement for HD\,141531 agrees with \citet{gratton;et-al_2000} to within 0.06\,dex.
+Most program stars have near-solar carbon abundances, ranging from ${{\rm [C/Fe]} = -0.30}$ for {J221821-183424}, and +0.05 for {J223811-104126}.
+
+\begin{figure}[h!]
+	\includegraphics[width=\columnwidth]{./figures/J223811-C.pdf}
+	\caption{The carbon CH feature near 4313\,{\AA} in program star J223811-104126. The best-fit synthetic spectra is shown, with synthetic spectra for $\pm0.15$\,dex about the best-fitting abundance.}
+	\label{fig:carbon}
+\end{figure}
+
+\subsection{Oxygen}
+\label{sec:oxygen-abundances}
+Oxygen can be a particularly difficult element to measure.
+There are only a handful of lines available in an optical spectrum: the forbidden {[O\,\textsc{i}]} lines at 630\,nm and 636\,nm, and the O\,\textsc{i} triplet lines at 777\,nm.
+The forbidden lines are very weak and become difficult to measure in hot and/or metal-poor stars (${\mbox{[Fe/H]} \lesssim -1.5}$\,dex).
+When they are present, depending on the radial velocity of the star, the {[O\,\textsc{i}]} lines can be significantly affected by telluric absorption.
+Moreover, the 630\,nm line is blended with a Ni\,\textsc{i} absorption line \citep{allende-prieto;et-al_2001}.
+Hence the region requires careful consideration.
+Although the O\,\textsc{i} triplet lines at 777\,nm are stronger than the forbidden lines, they are extremely susceptible to non-LTE effects, surface granulation \citep{asplund;perez_2001}, and are sensitive to changes in microturbulence.
+Forbidden {[O\,\textsc{i}]} abundances in HD\,136316 agree well with \citet{gratton;et-al_2000}, where a difference of $-0.07$\,dex is observed.
+
+The {[O\,\textsc{i}]} lines were measurable in four of our Aquarius stream candidates.
+The 630\,nm line in one of our candidates, {C2306265-085103}, was sufficiently affected by telluric absorption such that we deemed the line unrecoverable.
+Thus, only the 636\,nm transition was used to derive an oxygen abundance for {C2306265-085103}.
+In our hottest star, {J223811-104126}, the forbidden oxygen lines were not detected above a 3$\sigma$ significance.
+After synthesising the region, we deduce a very conservative upper limit of ${\mbox{[O/Fe]} < 0.50}$\,dex from the {[O\,\textsc{i}]} lines.
+This is consistent with the rest of our candidates, with [O/Fe] abundances varying between 0.43 to 0.49\,dex.
+
+In order to derive an oxygen measurement for {J223811-104126}, we were forced to use the triplet lines at 777\,nm.
+We extended these measurements for all Aquarius stars, and a mean abundance for each candidate was found from the synthesis of the permitted triplet lines.
+Oxygen abundances inferred from the triplet lines in all other stars were systematically $+0.27$\,dex higher than abundances calculated from the {[O\,\textsc{i}]} forbidden lines.
+\citet{perez;et-al_2006} found the same result: [O/Fe] values based on the {O\,\textsc{i}} permitted triplet lines are on average ${+0.19 \pm 0.07}$\,dex higher than those found from the forbidden lines, which did not include non-LTE corrections of $+$0.08\,dex.
+Thus, we attribute our $+$0.27\,dex offset between measurements of the {[O\,\textsc{i}]} and {O \textsc{i}} triplet lines to non-LTE and 3D effects.
+\citet{perez;et-al_2006} concluded that the forbidden lines, when not too weak, probably give the most reliable estimate of oxygen abundance.
+From the permitted O\,\textsc{i} triplet in {J223811-104126}, we derive an oxygen abundance of ${\mbox{[O/Fe]} = 0.42 \pm 0.01}$\,dex (random scatter).
+This measurement will be systematically higher than the `true' abundance if it were discernible from the [O\,\textsc{i}] lines, on the order of ${\sim}+0.27$\,dex.
+When we apply this crude offset derived from the rest of our sample, we arrive at a corrected abundance of ${\mbox{[O/Fe]} = 0.15 \pm 0.13}$\,dex (total uncertainty) for {J223811-104126}.
+This is the most oxygen-deficient star in our sample by a factor of two.
+
+\subsection{Sodium and Aluminium}
+\label{sec:sodium-abundances}
+Our line list includes three clean, unblended sodium lines at 568.8\,nm, 615.4\,nm and 616.1\,nm.
+Not all three of these lines were detectable in each star.
+In the hottest and most metal-poor stars, J223811-104126 and J221821-183424 respectively, only the 568.8\,nm line was measurable.
+For stars where multiple sodium lines were available, the line-to-line scatter is usually around 0.04\,dex with a maximum of 0.09\,dex in HD\,41667.
+However, in calculating total abundance uncertainties (see Section \ref{sec:chemical-abundance-uncertainties}) we have conservatively assumed a minimum random scatter of $\pm0.10$\,dex for all stars.
+
+% [Na/Fe] measurements in the standard stars? 
+Our [Na/Fe] abundances appear systematically higher than values found in the literature, on the order of 0.10\,dex.
+For HD\,142948 we find {[Na/Fe] = 0.22}, which is +0.10\,dex higher than that found by \citet{gratton;et-al_2000}, and similarly we find HD\,76932 to be +0.10\,dex higher than reported by \citet{fulbright_2000}.
+\citet{gratton;et-al_2000} also found HD\,136316 to have {[Na/Fe] = $-$0.29}\,dex, where we find {[Na/Fe] = $-0.14$}, yet excellent agreement is found in the stellar parameters in \citet{gratton;et-al_2000} and this study.
+Different solar compositions employed between this study and earlier work can account for $\sim$0.08\,dex of this effect, leaving the residual difference well within the observational uncertainties.
+However, it is important to note that the [Na/Fe] abundance ratios presented in this study may be slightly higher compared to previous studies.
+
+There are six aluminium transitions in our optical spectra.
+The strongest of these lines occur at 394.4\,nm and 396.1\,nm and are visible in all of our stars.
+However this is a particularly crowded spectral region: the lines fall between the strong Ca H and K lines, with the 396.1\,nm transition clearly located in the wing of the Ca H line.
+Additionally, the 394.4 and 3961\,nm lines have appreciable departures from the assumption of LTE, resulting in under-estimated abundances by up to $\sim$0.6\,dex \citep{baumueller;gehren_1997}.
+Instead, we have measured Al abundances from other available transitions: the {Al\,\textsc{i}} lines at 669.6, 669.8, 783.5 and 783.6\,nm.
+Generally the four {Al\,\textsc{i}} lines are in reasonable agreement with one another, yielding random scatter of less than 0.05\,dex.
+
+\subsection{$\alpha$-elements (Mg, Si, Ca and Ti)}
+\label{sec:alpha-elements}
+
+The $\alpha$-elements (Mg, Si, Ca and Ti) are forged through $\alpha$-particle capture during hydrostatic burning of carbon, neon and silicon.
+Material enriched in $\alpha$-elements is eventually dispersed into the interstellar medium following Type II core-collapse supernovae (SN).
+
+Depending on the radial velocity of the star, some magnesium lines were affected by telluric absorption, particularly the 631.8 and 696.5\,nm transitions.
+Atmospheric absorption was most notable for C222531-145437, where three of the four Mg transitions in our line list suffered some degree of telluric absorption, requiring an attentive correction.
+Every amended absorption profile was carefully examined, and lines with suspicious profiles were excluded from the final magnesium abundance.
+All [$\alpha$/Fe] abundance ratios in the standard stars are in excellent agreement with the literature.
+Typically the difference is 0.01\,dex, with the largest discrepancy of {$\Delta$[Ti/Fe] = +0.13\,dex} for HD\,76932 when compared with \citet{fulbright_2000}.
+
+While \citet{wylie-de-boer;et-al_2012} find almost no scatter {($\pm0.02$\,dex)} in [Mg/Fe] for stars common to both studies, we find {C222531-145437} and {J223504-152834} to be almost {$+0.20$\,dex} higher than the rest of the sample.
+The reason for this [Mg/Fe] discrepancy is not obvious, given the stellar parameters between the two studies agree well, with the previously discussed exception in metallicity.
+Of the {Mg\,\textsc{i}} line profiles measured, only two transitions are common to both line lists: 631.8\,nm and 631.9\,nm.
+The oscillator strengths differ between studies; in these two lines the $\log{gf}$ differs by $-0.24$ and {$-0.27$\,dex} respectively (our oscillator strengths are lower).
+This indicates that the difference in oscillator strengths may explain the $\sim{}$0.2\,dex offset in [Mg/Fe] between this study and \citet{wylie-de-boer;et-al_2012}.
+
+% [alpha/Fe]
+\begin{figure}[h]
+	\includegraphics[width=\columnwidth]{./figures/aquarius-alpha-fe.pdf}
+	\caption{$\alpha$-element abundances with respect to iron content.
+The mean [$\alpha$/Fe] abundance from these is shown in the bottom panel.
+The Solar element-to-iron ratio is shown as a dotted line in each panel.}
+	\label{fig:alpha-elements}
+\end{figure}
+
+% calcium measurements + silicon measurements
+Of all the $\alpha$-elements, calcium has the smallest measurement scatter in our stars.
+The mean was formed from four line measurements in each star, with a typical random scatter of 0.01\,dex.
+Nevertheless, the aforementioned conservative minimum of 0.10\,dex for random scatter applies, and uncertainties in stellar parameters will contribute to the total error budget.
+As shown in Figure \ref{fig:alpha-elements}, all Aquarius stream candidates show super-solar [Ca/Fe], ranging between +0.23 to +0.43\,dex, consistent with [(Mg,Si,Ti)/Fe] measurements.
+
+{C222531-145437} has an unusually high silicon abundance (${\mbox{[Si/Fe]} = 0.79}$), well outside the uncertainties of the rest of our sample.
+The 5 silicon line abundances in this star are in relatively good agreement with each another.
+If we exclude the highest measurement, then the mean abundance drops only slightly to ${\mbox{[Si/Fe]} = 0.73 \pm 0.04}$ (random scatter).
+The lowest silicon line abundance for {C222531-145437} is ${\mbox{[Si/Fe]} = 0.61}$, which is still significantly higher than the mean abundance for any other star.
+
+% titanium measurements?
+Titanium abundance ratios for the stream show typical levels of $\alpha$-enhancement.
+Our mean titanium abundances are derived from four to seven clean, unblended lines.
+In our hottest and most metal-poor stars, no suitable Ti\,\textsc{i} transitions were available.
+
+%In other Aquarius members, the mean difference between species is ${\langle{\rm Ti}\,\textsc{i} - {\rm Ti}\,\textsc{ii}\rangle = 0.24\,{\rm dex}}$.
+Although this discrepancy in Ti is non-negligible, it is reassuring to find our mean ${\langle{\rm Cr}\,\textsc{i} - {\rm Cr}\,\textsc{ii}\rangle}$ differences are very small (see Section \ref{sec:fe-peak-abundances}).
+
+\subsection{Iron-peak Elements}
+\label{sec:fe-peak-abundances}
+
+The Fe-peak elements (Sc to Zn) are primarily synthesized by the explosive nucleosynthesis of oxygen, neon, and silicon burning.
+Ignition can occur from Type II SN explosions of massive stars, or once a white dwarf accretes enough material to exceed the Chandrasekhar mass limit and spontaneously ignite carbon, leading to a Type Ia SN.
+
+% The exception here is Cr, where we find a median {$\mbox{[Cr/Fe]} = -0.08 \pm 0.12$} with minimal variation across all [Fe/H], similar to that observed by \citet{reddy;et-al_2006} in the Milky Way.
+Although not all {Fe-peak} elements are created equally, the Fe-peak elements generally exhibit similar trends with overall metallicity.
+All exhibit a positive trend with increasing iron abundance, with varying slope strengths.
+
+The [Sc/Fe] measurements presented in Figure \ref{fig:fe-peak-elements} are averaged from six clean {Sc\,\textsc{ii}} lines, and there is very little line-to-line scatter, the largest of which is {0.06\,dex}.
+The number of clean, suitable {Cr\,\textsc{i}} lines available between members fluctuated from three to twelve.
+Very little line-to-line scatter is present in both {Cr\,\textsc{i}} and Cr\,\textsc{ii}: the random scatter is below {0.04\,dex} for most stars.
+Chromium abundances are only available for one of the standard stars, where our {[Cr/Fe] = 0.03} is in excellent agreement with \citet{fulbright_2000}, where they find {[Cr/Fe] = 0.04}.
+
+% The {Cr\,\textsc{i}} and \textsc{ii} mean abundances for {J223504-152834} are in good agreement (0.05\,dex), and since none of the fitted Gaussian profiles appeared unusual, we chose not to exclude any measurements.
+For all other stars, the ${\langle{\rm Cr}\,\textsc{i} - {\rm Cr}\,\textsc{ii}\rangle}$ abundance differences varied between {0.02\,dex} up to {0.31\,dex}.
+The largest discrepancy occurred in our hottest star, where fewer Cr\,\textsc{i} and Cr\,\textsc{ii} transitions were measurable.
+
+Manganese demonstrates a strong trend with increasing iron abundance (Figure \ref{fig:fe-peak-elements}).
+A significant source of Mn comes from Type Ia SN, and the strong Mn-Fe trend is consistent with chemodynamical simulations \citep{kobayashi;nakasato_2011}, as well as thick disc observations by \citet{reddy;et-al_2006}.
+Although Mn is known to demonstrate significant departures from LTE, we have not applied any non-LTE corrections to our abundances.
+
+Abundances of Co\,\textsc{i} lines were calculated by synthesis, as they demonstrate appreciable broadening due to hyperfine structure.
+Although they are known to suffer significant departures from LTE \citep{bergemann;et-al_2010}, no corrections have been made for these data.
+In general, [Co/H] follows [Fe/H] in our candidates.
+Cu abundances have also been determined by synthesis, and exhibit a strong positive relationship with increasing overall metallicity, consistent with MW trend???
+
+% [TODO] Is Cu/Fe consistent with MW trend?
+
+Most Aquarius stream stars have seven clean {Ni\,\textsc{i}} transitions available.
+These lines are in excellent agreement, with a typical scatter of {0.03\,dex}.
+Nickel abundances have been published for two of our standard stars: HD\,76932 \citep{fulbright_2000} and HD\,141531 \citep{shetrone_1996}.
+In both cases, our [Ni/Fe] abundance ratios are slightly higher by +0.08 and +0.10\,dex respectively.
+The different solar compositions employed by these studies can only accounts for 0.01\,dex of this discrepancy, and the differences in oscillator strengths for common Ni\,\textsc{i} lines are negligible.
+Overall, the [Ni/Fe] abundance ratios in the Aquarius stream stars do not deviate greatly from the Solar ratio.
+
+% Lines commented out in this table are those abundances measured by EWs,
+% before synthesis was done with hyperfine structure and isotopic splitting data.
+\begin{longtable*}[T]{lcccccclccccccc}
+\caption{\\ Standard Star Abundances\label{tab:standard-star-abundances}} \tabularnewline
+\cline{1-13}
+Species & $N$ & $\log\epsilon(X)$ & $\sigma_\epsilon$ & [X/H] & [X/Fe] &&% $\sigma$ && 
+Species & $N$ & $\log\epsilon(X)$ & $\sigma_\epsilon$ & [X/H] & [X/Fe] \tabularnewline %& $\sigma$ \tabularnewline
+\cline{1-13} \tabularnewline
+% This works.
+\endhead
+\hline
+\multicolumn{13}{r}{Continued..}
+\endfoot
+\hline
+\endlastfoot
+
+\\
+\multicolumn{6}{c}{HD\,41667} & \colhead{} & \multicolumn{6}{c}{HD\,44007} \\
+\cline{1-6} \cline{8-13}
+
+   C (CH)       &   2 &    6.95 &    0.20 &  --1.48 &  --0.28 && %    0.20 &&
+   C (CH)       &   2 &    6.66 &    0.20 &  --1.77 &  --0.01 \\ % &    0.20 \\
+   O \textsc{I} &   2 &    7.95 &    0.06 &  --0.74 &    0.46 && %    0.04 &&
+   O \textsc{I} &   1 &    7.41 &    0.00 &  --1.28 &    0.48 \\ % &    0.00 \\
+  Na \textsc{I} &   3 &    4.90 &    0.18 &  --1.34 &  --0.14 && %    0.10 &&
+  Na \textsc{I} &   2 &    4.44 &    0.09 &  --1.80 &  --0.04 \\ % &    0.06 \\
+  Mg \textsc{I} &   4 &    6.72 &    0.10 &  --0.88 &    0.32 && %    0.05 &&
+  Mg \textsc{I} &   2 &    6.30 &    0.06 &  --1.29 &    0.47 \\ % &    0.04 \\
+  Al \textsc{I} &   4 &    5.18 &    0.11 &  --1.27 &  --0.07 && %    0.06 &&
+  Al \textsc{I} &   1 &    4.80 & \nodata &  --1.65 &    0.11 \\ % & \nodata \\
+  Si \textsc{I} &   5 &    6.55 &    0.06 &  --0.96 &    0.24 && %    0.03 &&
+  Si \textsc{I} &   5 &    6.07 &    0.07 &  --1.44 &    0.32 \\ % &    0.03 \\
+   K \textsc{I} &   1 &    4.64 & \nodata &  --0.39 &    0.81 && % \nodata &&
+   K \textsc{I} &   1 &    4.31 & \nodata &  --0.72 &    1.04 \\ % & \nodata \\
+  Ca \textsc{I} &   4 &    5.47 &    0.06 &  --0.87 &    0.33 && %    0.03 &&
+  Ca \textsc{I} &   4 &    4.95 &    0.02 &  --1.39 &    0.37 \\ % &    0.01 \\
+ Sc \textsc{II} &   5 &    2.00 &    0.12 &  --1.15 &    0.05 && %    0.05 &&
+ Sc \textsc{II} &   5 &    1.32 &    0.12 &  --1.85 &  --0.07 \\ % &    0.05 \\
+%Sc \textsc{II} &   6 &    2.13 &    0.13 &  --1.02 &    0.18 && %    0.05 &&
+%Sc \textsc{II} &   6 &    1.39 &    0.10 &  --1.76 &    0.00 \\ % &    0.04 \\
+  Ti \textsc{I} &   4 &    3.96 &    0.04 &  --0.99 &    0.21 && %    0.02 &&
+  Ti \textsc{I} &   1 &    3.48 & \nodata &  --1.47 &    0.29 \\ % & \nodata \\
+ Ti \textsc{II} &   3 &    4.09 &    0.25 &  --0.86 &    0.35 && %    0.14 &&
+ Ti \textsc{II} &   4 &    3.47 &    0.15 &  --1.48 &    0.28 \\ % &    0.07 \\
+   V \textsc{I} &   4 &    2.85 &    0.11 &  --1.08 &    0.12 && %    0.05 &&
+   V \textsc{I} &   1 &    2.22 & \nodata &  --1.72 &    0.05 \\ % & \nodata \\
+%  V \textsc{I} &   6 &    2.87 &    0.13 &  --1.06 &    0.14 && %    0.05 &&
+%  V \textsc{I} &   4 &    2.17 &    0.03 &  --1.77 &  --0.00 \\ % &    0.01 \\
+  Cr \textsc{I} &  10 &    4.22 &    0.08 &  --1.42 &  --0.22 && %    0.03 &&
+  Cr \textsc{I} &  15 &    3.65 &    0.07 &  --1.99 &  --0.22 \\ % &    0.02 \\
+ Cr \textsc{II} &   2 &    4.54 &    0.05 &  --1.09 &    0.11 && %    0.04 &&
+ Cr \textsc{II} &   3 &    4.00 &    0.01 &  --1.64 &    0.12 \\ % &    0.01 \\
+ Mn \textsc{I}  &   3 &    3.87 &    0.04 &  --1.56 &  --0.36 && %    0.03 &&
+ Mn \textsc{I}  &   2 &    3.21 &    0.06 &  --2.22 &  --0.48 \\ % &    0.04 \\
+% Mn \textsc{I} &   3 &    3.96 &    0.01 &  --1.47 &  --0.27 && %    0.01 &&
+% Mn \textsc{I} &   3 &    3.15 &    0.04 &  --2.28 &  --0.52 \\ % &    0.02 \\
+  Fe \textsc{I} &  61 &    6.30 &    0.12 &  --1.20 &    0.00 && %    0.02 &&
+  Fe \textsc{I} &  51 &    5.74 &    0.13 &  --1.76 &    0.00 \\ % &    0.02 \\
+ Fe \textsc{II} &  13 &    6.35 &    0.05 &  --1.15 &    0.05 && %    0.01 &&
+ Fe \textsc{II} &  15 &    5.74 &    0.10 &  --1.76 &  --0.00 \\ % &    0.03 \\
+  Co \textsc{I} &   3 &    3.73 &    0.06 &  --1.26 &  --0.06 && %    0.03 &&
+  Co \textsc{I} &   0 & \nodata & \nodata & \nodata & \nodata \\ % & \nodata \\
+% Co \textsc{I} &   5 &    3.75 &    0.10 &  --1.24 &  --0.04 && %    0.04 &&
+% Co \textsc{I} &   1 &    3.22 &    0.00 &  --1.77 &  --0.01 \\ % &    0.00 \\
+  Ni \textsc{I} &   7 &    4.94 &    0.12 &  --1.28 &  --0.08 && %    0.05 &&
+  Ni \textsc{I} &   4 &    4.47 &    0.05 &  --1.75 &    0.01 \\ % &    0.02 \\
+  Cu \textsc{I} &   1 &    2.29 & \nodata &  --1.90 &  --0.70 && % \nodata &&
+  Cu \textsc{I} &   1 &    1.58 & \nodata &  --2.61 &  --0.85 \\ % & \nodata \\
+% Cu \textsc{I} &   1 &    2.72 &    0.00 &  --1.47 &  --0.27 && %    0.00 &&
+% Cu \textsc{I} &   1 &    1.84 &    0.00 &  --2.35 &  --0.59 \\ % &    0.00 \\
+  Zn \textsc{I} &   2 &    3.36 &    0.08 &  --1.20 &    0.00 && %    0.06 &&
+  Zn \textsc{I} &   2 &    2.83 &    0.05 &  --1.73 &    0.03 \\ % &    0.04 \\
+  Sr \textsc{I} &   1 &    1.31 & \nodata &  --1.56 &  --0.36 && % \nodata &&
+  Sr \textsc{I} &   1 &    0.91 & \nodata &  --1.96 &  --0.20 \\ % & \nodata \\
+  Y \textsc{II} &   5 &    0.97 &    0.19 &  --1.24 &  --0.04 && %    0.09 &&
+  Y \textsc{II} &   6 &    0.28 &    0.11 &  --1.93 &  --0.16 \\ % &    0.05 \\
+  Zr \textsc{I} &   2 &    1.42 &    0.05 &  --1.17 &    0.04 && %    0.04 &&
+  Zr \textsc{I} &   0 & \nodata & \nodata & \nodata & \nodata \\ % & \nodata \\
+ Zr \textsc{II} &   1 &    1.28 & \nodata &  --1.30 &  --0.10 && % \nodata &&
+ Zr \textsc{II} &   1 &    0.59 & \nodata &  --1.99 &  --0.23 \\ % & \nodata \\
+ Ba \textsc{II} &   2 &    0.95 &    0.07 &  --1.23 &  --0.02 && %    0.05 &&
+ Ba \textsc{II} &   2 &    0.31 &    0.06 &  --1.87 &  --0.11 \\ % &    0.04 \\
+%Ba \textsc{II} &   2 &    1.02 &    0.04 &  --1.16 &    0.05 && %    0.02 &&
+%Ba \textsc{II} &   2 &    0.25 &    0.01 &  --1.93 &  --0.17 \\ % &    0.01 \\
+ La \textsc{II} &   1 &    0.17 & \nodata &  --0.93 &     0.27 && % \nodata &&
+ La \textsc{II} &   2 &  --0.57 &    0.05 &  --1.67 &     0.09 \\ % &    0.03 \\
+%La \textsc{II} &   2 &    0.14 &    0.04 &  --0.96 &    0.24 && %    0.03 &&
+%La \textsc{II} &   2 &  --0.52 &    0.02 &  --1.62 &    0.14 \\ % &    0.01 \\
+ Ce \textsc{II} &   4 &    0.35 &    0.18 &  --1.23 &  --0.02 && %    0.09 &&
+ Ce \textsc{II} &   3 &  --0.41 &    0.12 &  --1.99 &  --0.23 \\ % &    0.07 \\
+ Nd \textsc{II} &   9 &    0.54 &    0.10 &  --0.88 &    0.32 && %    0.03 &&
+ Nd \textsc{II} &   9 &  --0.36 &    0.11 &  --1.78 &  --0.01 \\ % &    0.04 \\
+ Eu \textsc{II} &   1 &  --0.13 & \nodata &  --0.65 &    0.55 && % \nodata &&
+ Eu \textsc{II} &   1 &  --1.16 & \nodata &  --1.68 &    0.08 \\ % & \nodata \\
+%Eu \textsc{II} &   1 &  --0.05 &    0.00 &  --0.57 &    0.63 && %    0.00 &&
+%Eu \textsc{II} &   1 &  --0.36 &    0.00 &  --0.88 &    0.88 \\ % &    0.00 \\
+
+\cline{1-6} \cline{8-13} \\ \\
+\multicolumn{6}{c}{HD\,76932} && \multicolumn{6}{c}{HD\,136316} \\
+\cline{1-6} \cline{8-13}
+   C (CH)       &   2 &    7.52 &    0.20 &  --0.91 &    0.14 && %    0.20 &&
+   C (CH)       &   2 &    5.95 &    0.20 &  --2.48 &  --0.50 \\ % &    0.20 \\
+   O \textsc{I} &   0 & \nodata & \nodata & \nodata & \nodata && % \nodata &&
+   O \textsc{I} &   1 &    7.17 & \nodata &  --1.52 &    0.41 \\ % & \nodata \\
+  Na \textsc{I} &   3 &    5.37 &    0.04 &  --0.87 &    0.18 && %    0.02 &&
+  Na \textsc{I} &   2 &    4.17 &    0.04 &  --2.08 &  --0.14 \\ % &    0.02 \\
+  Mg \textsc{I} &   3 &    6.95 &    0.20 &  --0.65 &    0.40 && %    0.11 &&
+  Mg \textsc{I} &   2 &    6.08 &    0.24 &  --1.52 &    0.41 \\ % &    0.17 \\
+  Al \textsc{I} &   4 &    5.45 &    0.07 &  --1.00 &    0.05 && %    0.03 &&
+  Al \textsc{I} &   0 & \nodata & \nodata & \nodata & \nodata \\ % & \nodata \\
+  Si \textsc{I} &   5 &    6.79 &    0.06 &  --0.72 &    0.33 && %    0.03 &&
+  Si \textsc{I} &   4 &    5.89 &    0.05 &  --1.62 &    0.31 \\ % &    0.03 \\
+   K \textsc{I} &   1 &    4.94 & \nodata &  --0.09 &    0.96 && % \nodata &&
+   K \textsc{I} &   1 &    3.91 & \nodata &  --1.12 &    0.81 \\ % & \nodata \\
+  Ca \textsc{I} &   4 &    5.60 &    0.02 &  --0.74 &    0.31 && %    0.01 &&
+  Ca \textsc{I} &   4 &    4.71 &    0.02 &  --1.63 &    0.30 \\ % &    0.01 \\
+ Sc \textsc{II} &   4 &    2.10 &    0.05 &  --1.05 &    0.01 && %    0.03 &&
+ Sc \textsc{II} &   4 &    1.20 &    0.08 &  --1.95 &  --0.02 \\ % &    0.04 \\
+%Sc \textsc{II} &   6 &    2.25 &    0.11 &  --0.90 &    0.16 && %    0.04 &&
+%Sc \textsc{II} &   5 &    1.30 &    0.05 &  --1.85 &    0.08 \\ % &    0.02 \\
+  Ti \textsc{I} &   1 &    4.36 & \nodata &  --0.59 &    0.46 && % \nodata &&
+  Ti \textsc{I} &   3 &    3.19 &    0.03 &  --1.76 &    0.17 \\ % &    0.02 \\
+ Ti \textsc{II} &   3 &    4.33 &    0.04 &  --0.62 &    0.44 && %    0.02 &&
+ Ti \textsc{II} &   3 &    3.44 &    0.10 &  --1.51 &    0.42 \\ % &    0.06 \\
+   V \textsc{I} &   1 &   :3.33 & \nodata &  --0.60 &    0.45 && % \nodata &&
+   V \textsc{I} &   3 &    1.85 &    0.01 &  --2.08 &  --0.15 \\ % &    0.01 \\
+%  V \textsc{I} &   3 &    3.17 &    0.13 &  --0.76 &    0.29 && %    0.08 &&
+%  V \textsc{I} &   5 &    1.87 &    0.07 &  --2.06 &  --0.13 \\ % &    0.03 \\
+  Cr \textsc{I} &  15 &    4.46 &    0.05 &  --1.18 &  --0.13 && %    0.01 &&
+  Cr \textsc{I} &  12 &    3.49 &    0.05 &  --2.15 &  --0.22 \\ % &    0.01 \\
+ Cr \textsc{II} &   3 &    4.76 &    0.02 &  --0.88 &    0.17 && %    0.01 &&
+ Cr \textsc{II} &   2 &    3.90 &    0.02 &  --1.74 &    0.19 \\ % &    0.01 \\
+  Mn \textsc{I} &   3 &    4.09 &    0.06 &  --1.34 &  --0.28 && %    0.04 &&
+  Mn \textsc{I} &   3 &    3.09 &    0.03 &  --2.34 &  --0.41 \\ % &    0.02 \\
+% Mn \textsc{I} &   3 &    4.08 &    0.03 &  --1.35 &  --0.29 && %    0.02 &&
+% Mn \textsc{I} &   3 &    3.08 &    0.02 &  --2.35 &  --0.42 \\ % &    0.01 \\
+  Fe \textsc{I} &  51 &    6.45 &    0.10 &  --1.05 &    0.00 && %    0.01 &&
+  Fe \textsc{I} &  62 &    5.57 &    0.11 &  --1.93 &    0.00 \\ % &    0.01 \\
+ Fe \textsc{II} &  13 &    6.50 &    0.07 &  --1.00 &    0.05 && %    0.02 &&
+ Fe \textsc{II} &  14 &    5.61 &    0.12 &  --1.89 &    0.04 \\ % &    0.03 \\
+  Co \textsc{I} &   1 &    3.94 & \nodata &  --1.05 &    0.00 && % \nodata &&
+  Co \textsc{I} &   2 &    2.95 &    0.11 &  --1.09 &  --0.11 \\ % &    0.08 \\  
+% Co \textsc{I} &   3 &    4.10 &    0.06 &  --0.89 &    0.16 && %    0.03 &&
+% Co \textsc{I} &   6 &    3.11 &    0.07 &  --1.88 &    0.05 \\ % &    0.03 \\
+  Ni \textsc{I} &   5 &    5.29 &    0.02 &  --0.93 &    0.13 && %    0.01 &&
+  Ni \textsc{I} &   5 &    4.22 &    0.11 &  --2.00 &  --0.07 \\ % &    0.05 \\
+  Cu \textsc{I} &   1 &    2.53 & \nodata &  --1.66 &  --0.61 && % \nodata &&
+  Cu \textsc{I} &   1 &    1.36 & \nodata &  --2.09 &  --0.16 \\ % & \nodata \\
+% Cu \textsc{I} &   1 &    2.84 &    0.00 &  --1.35 &  --0.30 && %    0.00 &&
+% Cu \textsc{I} &   1 &    1.73 &    0.00 &  --2.46 &  --0.53 \\ % &    0.00 \\
+  Zn \textsc{I} &   2 &    3.58 &    0.03 &  --0.98 &    0.07 && %    0.02 &&
+  Zn \textsc{I} &   2 &    2.72 &    0.03 &  --1.83 &    0.10 \\ % &    0.02 \\
+  Sr \textsc{I} &   1 &    1.65 & \nodata &  --1.22 &  --0.17 && % \nodata &&
+  Sr \textsc{I} &   1 &    0.53 & \nodata &  --2.34 &  --0.41 \\ % & \nodata \\
+  Y \textsc{II} &   5 &    1.14 &    0.05 &  --1.07 &  --0.02 && %    0.02 &&
+  Y \textsc{II} &   7 &    0.12 &    0.11 &  --2.09 &  --0.16 \\ % &    0.04 \\
+  Zr \textsc{I} &   0 & \nodata & \nodata & \nodata & \nodata && % \nodata &&
+  Zr \textsc{I} &   1 &    0.79 & \nodata &  --1.79 &    0.14 \\ % & \nodata \\
+ Zr \textsc{II} &   0 & \nodata & \nodata & \nodata & \nodata && % \nodata &&
+ Zr \textsc{II} &   1 &    0.68 & \nodata &  --1.90 &    0.03 \\ % & \nodata \\
+ Ba \textsc{II} &   2 &    1.31 &    0.07 &  --0.87 &    0.18 && %    0.05 &&
+ Ba \textsc{II} &   2 &    0.22 &    0.02 &  --1.96 &  --0.03 \\ % &    0.01 \\
+%Ba \textsc{II} &   1 &    1.16 &    0.00 &  --1.02 &    0.03 && %    0.00 &&
+%Ba \textsc{II} &   1 &    0.22 &    0.00 &  --1.96 &  --0.03 \\ % &    0.00 \\
+ La \textsc{II} &   1 &    0.50 & \nodata &  --0.60 &    0.45 && % \nodata &&
+ La \textsc{II} &   1 &  --0.68 & \nodata &  --1.78 &    0.16 \\ % & \nodata \\
+%La \textsc{II} &   1 &    0.61 &    0.00 &  --0.49 &    0.56 && %    0.00 &&
+%La \textsc{II} &   2 &  --0.68 &    0.03 &  --1.78 &    0.16 \\ % &    0.02 \\
+ Ce \textsc{II} &   2 &    0.37 &    0.03 &  --1.21 &  --0.16 && %    0.02 &&
+ Ce \textsc{II} &   5 &  --0.39 &    0.18 &  --1.97 &  --0.04 \\ % &    0.08 \\
+ Nd \textsc{II} &   3 &    0.56 &    0.06 &  --0.86 &    0.19 && %    0.03 &&
+ Nd \textsc{II} &  10 &  --0.36 &    0.04 &  --1.78 &    0.15 \\ % &    0.01 \\
+ Eu \textsc{II} &   1 &  --0.33 & \nodata &  --0.85 &    0.20 && % \nodata &&
+ Eu \textsc{II} &   1 &  --1.06 & \nodata &  --1.58 &    0.33 \\ % & \nodata \\ 
+%Eu \textsc{II} &   1 &  --0.01 &    0.00 &  --0.53 &    0.52 && %    0.00 &&
+%Eu \textsc{II} &   1 &  --1.07 &    0.00 &  --1.59 &    0.34 \\ % &    0.00 \\
+
+\cline{1-6} \cline{8-13} \\ \\
+\multicolumn{6}{c}{HD\,141531} && \multicolumn{6}{c}{HD\,142948} \\
+\cline{1-6} \cline{8-13}
+   C (CH)       &   2 &    6.33 &    0.20 &  --2.10 &  --0.48 && %    0.20 &&
+   C (CH)       &   2 &    7.72 &    0.20 &  --0.71 &    0.03 \\ % &    0.20 \\
+   O \textsc{I} &   2 &    7.33 &    0.01 &  --1.35 &    0.34 && %    0.01 &&
+   O \textsc{I} &   2 &    8.43 &    0.02 &  --0.26 &    0.47 \\ % &    0.02 \\
+  Na \textsc{I} &   2 &    4.28 &    0.05 &  --1.96 &  --0.27 && %    0.04 &&
+  Na \textsc{I} &   3 &    5.73 &    0.13 &  --0.51 &    0.22 \\ % &    0.08 \\
+  Mg \textsc{I} &   2 &    6.30 &    0.15 &  --1.29 &    0.40 && %    0.10 &&
+  Mg \textsc{I} &   3 &    7.24 &    0.12 &  --0.36 &    0.38 \\ % &    0.07 \\
+  Al \textsc{I} &   2 &    4.74 &    0.10 &  --1.71 &  --0.02 && %    0.07 &&
+  Al \textsc{I} &   4 &    5.94 &    0.08 &  --0.51 &    0.23 \\ % &    0.04 \\
+  Si \textsc{I} &   5 &    6.03 &    0.10 &  --1.48 &    0.21 && %    0.04 &&
+  Si \textsc{I} &   5 &    7.07 &    0.05 &  --0.44 &    0.30 \\ % &    0.02 \\
+   K \textsc{I} &   1 &    3.99 & \nodata &  --1.04 &    0.65 && % \nodata &&
+   K \textsc{I} &   1 &    5.04 & \nodata &    0.01 &    0.75 \\ % & \nodata \\
+  Ca \textsc{I} &   4 &    4.90 &    0.03 &  --1.44 &    0.25 && %    0.01 &&
+  Ca \textsc{I} &   4 &    5.78 &    0.01 &  --0.56 &    0.18 \\ % &    0.01 \\
+ Sc \textsc{II} &   5 &    1.40 &    0.11 &  --1.75 &  --0.06 && %    0.05 &&
+ Sc \textsc{II} &   5 &    2.57 &    0.12 &  --0.58 &    0.16 \\ % &    0.05 \\
+%Sc \textsc{II} &   4 &    1.56 &    0.04 &  --1.59 &    0.10 && %    0.02 &&
+%Sc \textsc{II} &   6 &    2.57 &    0.11 &  --0.58 &    0.16 \\ % &    0.05 \\
+  Ti \textsc{I} &   4 &    3.33 &    0.07 &  --1.62 &    0.07 && %    0.03 &&
+  Ti \textsc{I} &   4 &    4.44 &    0.09 &  --0.51 &    0.23 \\ % &    0.04 \\
+ Ti \textsc{II} &   4 &    3.71 &    0.08 &  --1.24 &    0.46 && %    0.04 &&
+ Ti \textsc{II} &   3 &    4.40 &    0.21 &  --0.55 &    0.19 \\ % &    0.12 \\
+   V \textsc{I} &   4 &    2.10 &    0.07 &  --1.83 &  --0.13 && %    0.03 &&
+   V \textsc{I} &   5 &    3.31 &    0.04 &  --0.62 &    0.12 \\ % &    0.02 \\
+%  V \textsc{I} &   5 &    2.12 &    0.07 &  --1.81 &  --0.11 && %    0.03 &&
+%  V \textsc{I} &   5 &    3.31 &    0.11 &  --0.62 &    0.12 \\ % &    0.05 \\
+  Cr \textsc{I} &  12 &    3.68 &    0.06 &  --1.96 &  --0.27 && %    0.02 &&
+  Cr \textsc{I} &  13 &    4.67 &    0.15 &  --0.97 &  --0.23 \\ % &    0.04 \\
+ Cr \textsc{II} &   2 &    4.11 &    0.02 &  --1.53 &    0.16 && %    0.01 &&
+ Cr \textsc{II} &   3 &    4.88 &    0.03 &  --0.76 &  --0.02 \\ % &    0.02 \\
+  Mn \textsc{I} &   3 &    3.29 &    0.04 &  --2.14 &  --0.45 && %    0.02 &&
+  Mn \textsc{I} &   3 &    4.45 &    0.06 &  --0.98 &  --0.24 \\ % &    0.04 \\
+% Mn \textsc{I} &   3 &    3.29 &    0.04 &  --2.14 &  --0.45 && %    0.02 &&
+% Mn \textsc{I} &   3 &    4.54 &    0.03 &  --0.89 &  --0.15 \\ % &    0.02 \\
+  Fe \textsc{I} &  54 &    5.81 &    0.06 &  --1.69 &    0.00 && %    0.01 &&
+  Fe \textsc{I} &  61 &    6.76 &    0.10 &  --0.74 &    0.00 \\ % &    0.01 \\
+ Fe \textsc{II} &  13 &    5.86 &    0.03 &  --1.64 &    0.05 && %    0.01 &&
+ Fe \textsc{II} &  13 &    6.75 &    0.06 &  --0.75 &  --0.02 \\ % &    0.02 \\
+  Co \textsc{I} &   3 &    3.22 &    0.12 &  --1.77 &  --0.08 && %    0.07 &&
+  Co \textsc{I} &   3 &    4.36 &    0.11 &  --0.63 &  --0.13 \\ % &    0.06 \\
+% Co \textsc{I} &   5 &    3.23 &    0.09 &  --1.76 &  --0.07 && %    0.04 &&
+% Co \textsc{I} &   5 &    4.42 &    0.08 &  --0.57 &    0.17 \\ % &    0.03 \\
+  Ni \textsc{I} &   7 &    4.42 &    0.12 &  --1.80 &  --0.11 && %    0.04 &&
+  Ni \textsc{I} &   5 &    5.62 &    0.04 &  --0.60 &    0.13 \\ % &    0.02 \\
+  Cu \textsc{I} &   1 &    1.60 & \nodata &  --2.59 &  --0.90 && % \nodata &&
+  Cu \textsc{I} &   1 &    3.10 & \nodata &  --1.09 &  --0.35 \\ % & \nodata \\
+% Cu \textsc{I} &   1 &    2.03 &    0.00 &  --2.16 &  --0.47 && %    0.00 &&
+% Cu \textsc{I} &   1 &    3.53 &    0.00 &  --0.66 &    0.08 \\ % &    0.00 \\
+  Zn \textsc{I} &   2 &    2.80 &    0.04 &  --1.76 &  --0.07 && %    0.03 &&
+  Zn \textsc{I} &   2 &    3.89 &    0.06 &  --0.67 &    0.07 \\ % &    0.04 \\
+  Sr \textsc{I} &   1 &    0.66 & \nodata &  --2.21 &  --0.52 && % \nodata &&
+  Sr \textsc{I} &   1 &    1.67 & \nodata &  --1.20 &  --0.46 \\ % & \nodata \\
+  Y \textsc{II} &   6 &    0.27 &    0.13 &  --1.94 &  --0.24 && %    0.05 &&
+  Y \textsc{II} &   6 &    1.33 &    0.32 &  --0.88 &  --0.14 \\ % &    0.13 \\
+  Zr \textsc{I} &   0 & \nodata & \nodata & \nodata & \nodata && % \nodata &&
+  Zr \textsc{I} &   0 & \nodata & \nodata & \nodata & \nodata \\ % & \nodata \\
+ Zr \textsc{II} &   1 &    0.75 & \nodata &  --1.83 &  --0.14 && % \nodata &&
+ Zr \textsc{II} &   0 & \nodata & \nodata & \nodata & \nodata \\ % & \nodata \\
+ Ba \textsc{II} &   2 &    0.39 &    0.05 &  --1.79 &  --0.10 && %    0.04 &&
+ Ba \textsc{II} &   2 &    1.17 &    0.01 &  --1.01 &  --0.27 \\ % &    0.01 \\
+%Ba \textsc{II} &   1 &    0.40 &    0.00 &  --1.78 &  --0.09 && %    0.00 &&
+%Ba \textsc{II} &   2 &    1.18 &    0.01 &  --1.00 &  --0.26 \\ % &    0.01 \\
+ La \textsc{II} &   1 &  --0.56 & \nodata &  --1.67 &    0.03 && % \nodata &&
+ La \textsc{II} &   1 &    0.56 & \nodata &  --0.54 &    0.20 \\ % & \nodata \\
+%La \textsc{II} &   2 &  --0.55 &    0.08 &  --1.66 &    0.04 && %    0.05 &&
+%La \textsc{II} &   2 &    0.43 &    0.12 &  --0.67 &    0.07 \\ % &    0.08 \\
+ Ce \textsc{II} &   4 &  --0.31 &    0.12 &  --1.89 &  --0.20 && %    0.06 &&
+ Ce \textsc{II} &   3 &    0.54 &    0.20 &  --1.04 &  --0.30 \\ % &    0.11 \\
+ Nd \textsc{II} &  10 &  --0.20 &    0.08 &  --1.62 &    0.07 && %    0.02 &&
+ Nd \textsc{II} &   6 &    0.79 &    0.10 &  --0.63 &    0.11 \\ % &    0.04 \\
+ Eu \textsc{II} &   1 &  --0.95 & \nodata &  --1.47 &    0.22 && % \nodata &&
+ Eu \textsc{II} &   1 &    0.08 & \nodata &  --1.55 &    0.14 \\ % & \nodata \\
+% Eu \textsc{II} &   1 &  --0.83 &    0.00 &  --1.35 &    0.34 && %    0.00 &&
+% Eu \textsc{II} &   1 &    0.16 &    0.00 &  --0.36 &    0.38 \\ % &    0.00 \\
+\hline
+%\textbf{Note:} Abundances for Co, Cu, Mn, Sc, V, Ba, La, Eu have been determined by spectral synthesis with relevant hyperfine and isotopic splitting data included.
+All other abundances presented in Table \ref{tab:standard-star-abundances} have been measured directly from EWs.
+\end{longtable*}
+
+\begin{longtable*}{lcccccclccccccc}
+\caption{\\ Program Star Abundances\label{tab:program-star-abundances}} \tabularnewline
+\cline{1-13}
+Species & $N$ & $\log\epsilon(X)$ & $\sigma_\epsilon$ & [X/H] & [X/Fe] &&% $\sigma$ && 
+Species & $N$ & $\log\epsilon(X)$ & $\sigma_\epsilon$ & [X/H] & [X/Fe] \tabularnewline %& $\sigma$ \tabularnewline
+\cline{1-15} \tabularnewline
+% This works.
+\endhead
+\hline
+\multicolumn{13}{r}{Continued..}
+\endfoot
+\hline
+\endlastfoot
+
+\\
+\multicolumn{6}{c}{J221821-183424} & \colhead{} & \multicolumn{6}{c}{C222531-145437} \\
+\cline{1-6} \cline{8-13}
+   C (CH)       &   2 &    6.55 &    0.20 &  --1.88 &  --0.30 && %    0.25 &&
+   C (CH)       &   2 &    7.15 &    0.20 &  --1.28 &  --0.05 \\ % &    0.20 \\
+   O \textsc{I} &   2 &    7.55 &    0.04 &  --1.13 &    0.45 && %    0.02 &&
+   O \textsc{I} &   2 &    7.96 & \nodata &  --0.73 &    0.49 \\ % & \nodata \\
+  Na \textsc{I} &   1 &    4.75 & \nodata &  --1.49 &    0.09 && % \nodata &&
+  Na \textsc{I} &   2 &    5.12 &    0.02 &  --1.12 &    0.10 \\ % &    0.01 \\
+  Mg \textsc{I} &   3 &    6.37 &    0.09 &  --1.23 &    0.35 && %    0.05 &&
+  Mg \textsc{I} &   2 &    6.90 &    0.08 &  --0.70 &    0.53 \\ % &    0.06 \\
+  Al \textsc{I} &   1 &    5.08 & \nodata &  --1.37 &    0.21 && % \nodata &&
+  Al \textsc{I} &   4 &    5.94 &    0.10 &  --0.51 &    0.71 \\ % &    0.05 \\
+  Si \textsc{I} &   5 &    6.32 &    0.08 &  --1.19 &    0.39 && %    0.04 &&
+  Si \textsc{I} &   5 &    7.07 &    0.15 &  --0.44 &    0.79 \\ % &    0.07 \\
+   K \textsc{I} &   1 &    4.34 & \nodata &  --0.69 &    0.89 && % \nodata &&
+   K \textsc{I} &   1 &    4.42 & \nodata &  --0.61 &    0.62 \\ % & \nodata \\
+  Ca \textsc{I} &   4 &    5.01 &    0.04 &  --1.33 &    0.25 && %    0.02 &&
+  Ca \textsc{I} &   4 &    5.57 &    0.04 &  --0.77 &    0.45 \\ % &    0.02 \\
+ Sc \textsc{II} &   4 &    1.50 &    0.12 &  --1.65 &  --0.07 && %    0.06 &&
+ Sc \textsc{II} &   4 &    2.08 &    0.13 &  --1.07 &    0.16 \\ % &    0.07 \\
+%Sc \textsc{II} &   6 &    1.53 &    0.08 &  --1.62 &  --0.04 && %    0.03 &&
+%Sc \textsc{II} &   5 &    2.11 &    0.12 &  --1.04 &    0.19 \\ % &    0.06 \\
+  Ti \textsc{I} &   0 & \nodata & \nodata & \nodata & \nodata && % \nodata &&
+  Ti \textsc{I} &   4 &    4.10 &    0.03 &  --0.85 &    0.37 \\ % &    0.01 \\
+ Ti \textsc{II} &   4 &    3.80 &    0.13 &  --1.15 &    0.43 && %    0.06 &&
+ Ti \textsc{II} &   2 &    4.12 &    0.13 &  --0.83 &    0.40 \\ % &    0.09 \\
+   V \textsc{I} &   3 &    2.28 &    0.01 &  --1.65 &  --0.07 && %    0.01 &&
+   V \textsc{I} &   5 &    2.91 &    0.10 &  --1.01 &    0.22 \\ % &    0.05 \\
+%  V \textsc{I} &   6 &    3.02 &    0.16 &  --0.92 &    0.31 \\ % &    0.06 \\
+  Cr \textsc{I} &  11 &    3.80 &    0.06 &  --1.84 &  --0.26 && %    0.02 &&
+  Cr \textsc{I} &   8 &    4.24 &    0.17 &  --1.40 &  --0.17 \\ % &    0.06 \\
+ Cr \textsc{II} &   2 &    4.07 &    0.03 &  --1.57 &    0.01 && %    0.02 &&
+ Cr \textsc{II} &   1 &    4.38 & \nodata &  --1.26 &  --0.03 \\ % & \nodata \\
+  Mn \textsc{I} &   2 &    3.38 &    0.03 &  --2.05 &  --0.46 && %    0.02 &&
+  Mn \textsc{I} &   3 &    3.98 &    0.05 &  --1.45 &  --0.23 \\ % &    0.03 \\
+% Mn \textsc{I} &   3 &    3.35 &    0.03 &  --2.08 &  --0.49 && %    0.02 &&
+% Mn \textsc{I} &   3 &    4.20 &    0.04 &  --1.23 &  --0.01 \\ % &    0.03 \\
+  Fe \textsc{I} &  52 &    5.92 &    0.09 &  --1.58 &    0.00 && %    0.01 &&
+  Fe \textsc{I} &  60 &    6.27 &    0.10 &  --1.23 &    0.00 \\ % &    0.01 \\
+ Fe \textsc{II} &  13 &    5.94 &    0.05 &  --1.56 &    0.02 && %    0.01 &&
+ Fe \textsc{II} &  10 &    6.30 &    0.06 &  --1.20 &    0.03 \\ % &    0.02 \\
+  Co \textsc{I} &   1 &    3.32 & \nodata &  --1.67 &  --0.09 && % \nodata &&
+  Co \textsc{I} &   4 &    3.77 &    0.09 &  --1.22 &    0.00 \\ % &    0.05 \\
+% Co \textsc{I} &   4 &    3.32 &    0.16 &  --1.67 &  --0.09 && %    0.08 &&
+% Co \textsc{I} &   5 &    3.92 &    0.12 &  --1.07 &    0.15 \\ % &    0.05 \\
+  Ni \textsc{I} &   5 &    4.61 &    0.14 &  --1.61 &  --0.03 && %    0.06 &&
+  Ni \textsc{I} &   7 &    5.07 &    0.09 &  --1.15 &    0.08 \\ % &    0.04 \\
+  Cu \textsc{I} &   1 &    1.81 & \nodata &  --2.38 &  --0.80 && % \nodata &&
+  Cu \textsc{I} &   1 &    2.72 & \nodata &  --1.47 &  --0.24 \\ % & \nodata \\
+% Cu \textsc{I} &   1 &    2.18 &    0.00 &  --2.01 &  --0.43 && %    0.00 &&
+% Cu \textsc{I} &   1 &    3.33 &    0.00 &  --0.86 &    0.37 \\ % &    0.00 \\
+  Zn \textsc{I} &   1 &    3.07 & \nodata &  --1.49 &    0.09 && % \nodata &&
+  Zn \textsc{I} &   2 &    3.56 &    0.24 &  --1.00 &    0.23 \\ % &    0.17 \\
+  Sr \textsc{I} &   1 &    0.82 & \nodata &  --2.05 &  --0.47 && % \nodata &&
+  Sr \textsc{I} &   1 &    1.55 & \nodata &  --1.32 &  --0.09 \\ % & \nodata \\
+ Sr \textsc{II} &   0 & \nodata & \nodata & \nodata & \nodata && % \nodata &&
+ Sr \textsc{II} &   0 & \nodata & \nodata & \nodata & \nodata \\ % & \nodata \\
+  Y \textsc{II} &   3 &    0.44 &    0.02 &  --1.77 &  --0.19 && %    0.01 &&
+  Y \textsc{II} &   5 &    1.78 &    0.16 &  --0.43 &    0.79 \\ % &    0.07 \\
+  Zr \textsc{I} &   0 & \nodata & \nodata & \nodata & \nodata && % \nodata &&
+  Zr \textsc{I} &   3 &    2.07 &    0.05 &  --0.51 &    0.72 \\ % &    0.03 \\
+ Zr \textsc{II} &   1 &    0.97 & \nodata &  --1.61 &  --0.03 && % \nodata &&
+ Zr \textsc{II} &   0 & \nodata & \nodata & \nodata & \nodata \\ % & \nodata \\
+ Ba \textsc{II} &   1 &    0.60 & \nodata &  --1.58 &    0.00 && % \nodata &&
+ Ba \textsc{II} &   2 &    1.58 &    0.01 &  --0.60 &    0.62 \\ % &    0.01 \\
+%Ba \textsc{II} &   2 &    0.60 &    0.05 &  --1.58 &    0.00 && %    0.04 &&
+%Ba \textsc{II} &   3 &    1.58 &    0.02 &  --0.60 &    0.62 \\ % &    0.01 \\
+ La \textsc{II} &   1 &  --0.58 & \nodata &  --1.67 &  --0.09 && % \nodata &&
+ La \textsc{II} &   2 &    0.51 &    0.02 &  --0.59 &    0.64 \\ % &    0.02 \\
+%La \textsc{II} &   2 &  --0.47 &    0.00 &  --1.57 &    0.01 && %    0.00 &&
+%La \textsc{II} &   2 &    0.55 &    0.00 &  --0.55 &    0.68 \\ % &    0.00 \\
+ Ce \textsc{II} &   3 &  --0.39 &    0.06 &  --1.97 &  --0.39 && %    0.03 &&
+ Ce \textsc{II} &   5 &    0.73 &    0.15 &  --0.85 &    0.37 \\ % &    0.07 \\
+ Nd \textsc{II} &  10 &  --0.22 &    0.07 &  --1.64 &  --0.06 && %    0.02 &&
+ Nd \textsc{II} &   8 &    0.88 &    0.13 &  --0.54 &    0.69 \\ % &    0.05 \\
+ Eu \textsc{II} &   1 &  --0.86 &  --0.11 &  --1.38 &    0.20 && % \nodata &&
+ Eu \textsc{II} &   1 &  --0.29 & \nodata &  --0.81 &    0.42 \\ % & \nodata \\
+%Eu \textsc{II} &   2 &  --0.10 &    0.65 &  --0.62 &    0.96 && %    0.46 &&
+%Eu \textsc{II} &   1 &  --0.19 &    0.00 &  --0.71 &    0.52 \\ % &    0.00 \\
+
+\cline{1-6} \cline{8-13} \\ \\
+\multicolumn{6}{c}{J223504-152834} && \multicolumn{6}{c}{J223811-104126} \\
+\cline{1-6} \cline{8-13}
+   C (CH)       &   2 &    7.71 &    0.30 &  --0.72 &  --0.10 && %    0.30 &&
+   C (CH)       &   2 &    7.05 &    0.25 &  --1.38 &    0.05 \\ % &    0.25 \\
+   O \textsc{I} &   2 &    8.50 &    0.10 &  --0.19 &    0.43 && %    0.07 &&
+   O \textsc{I} &   1 &    8.27 & \nodata &  --0.42 &    0.15\footnote{Abundance derived from the permitted O \textsc{i} triplet instead of the forbidden [O \textsc{i}] lines, see \S\ref{sec:oxygen-abundances}} \\ % &    0.08 \\
+  Na \textsc{I} &   3 &    5.87 &    0.12 &  --0.37 &    0.26 && %    0.07 &&
+  Na \textsc{I} &   1 &    4.89 & \nodata &  --1.35 &    0.08 \\ % & \nodata \\
+  Mg \textsc{I} &   3 &    7.48 &    0.15 &  --0.12 &    0.51 && %    0.09 &&
+  Mg \textsc{I} &   2 &    6.51 &    0.03 &  --1.09 &    0.34 \\ % &    0.02 \\
+  Al \textsc{I} &   3 &    6.12 &    0.09 &  --0.33 &    0.29 && %    0.05 &&
+  Al \textsc{I} &   2 &    5.13 &    0.13 &  --1.32 &    0.11 \\ % &    0.10 \\
+  Si \textsc{I} &   5 &    7.24 &    0.10 &  --0.27 &    0.35 && %    0.05 &&
+  Si \textsc{I} &   3 &    6.42 &    0.04 &  --1.09 &    0.34 \\ % &    0.02 \\
+   K \textsc{I} &   1 &    5.05 & \nodata &    0.02 &    0.64 && % \nodata &&
+   K \textsc{I} &   1 &    4.50 & \nodata &  --0.53 &    0.90 \\ % & \nodata \\
+  Ca \textsc{I} &   4 &    6.06 &    0.03 &  --0.28 &    0.34 && %    0.01 &&
+  Ca \textsc{I} &   4 &    5.32 &    0.03 &  --1.02 &    0.41 \\ % &    0.02 \\
+ Sc \textsc{II} &   5 &    2.65 &    0.10 &  --0.50 &    0.13 && %    0.04 &&
+ Sc \textsc{II} &   2 &    1.60 &    0.03 &  --1.55 &  --0.12 \\ % &    0.02 \\
+%Sc \textsc{II} &   6 &    2.74 &    0.14 &  --0.41 &    0.22 && %    0.06 &&
+%Sc \textsc{II} &   6 &    1.72 &    0.14 &  --1.43 &  --0.00 \\ % &    0.06 \\
+  Ti \textsc{I} &   4 &    4.65 &    0.02 &  --0.30 &    0.32 && %    0.01 &&
+  Ti \textsc{I} &   0 & \nodata & \nodata & \nodata & \nodata \\ % & \nodata \\
+ Ti \textsc{II} &   1 &    4.67 & \nodata &  --0.28 &    0.34 && % \nodata &&
+ Ti \textsc{II} &   4 &    3.79 &    0.09 &  --1.16 &    0.27 \\ % &    0.04 \\
+   V \textsc{I} &   4 &    3.50 &    0.11 &  --0.43 &    0.19 && %    0.06 &&
+%  V \textsc{I} &   4 &    3.59 &    0.10 &  --0.34 &    0.28 && %    0.05 &&
+   V \textsc{I} &   1 &    2.45 & \nodata &  --1.48 &  --0.05 \\ % & \nodata \\
+  Cr \textsc{I} &   7 &    4.90 &    0.11 &  --0.74 &  --0.11 && %    0.04 &&
+  Cr \textsc{I} &  12 &    4.10 &    0.06 &  --1.54 &  --0.11 \\ % &    0.02 \\
+ Cr \textsc{II} &   2 &    4.84 &    0.04 &  --0.79 &  --0.17 && %    0.03 &&
+ Cr \textsc{II} &   3 &    4.34 &    0.07 &  --1.30 &    0.12 \\ % &    0.04 \\
+  Mn \textsc{I} &   3 &    4.66 &    0.04 &  --0.77 &  --0.15 && %    0.03 &&
+  Mn \textsc{I} &   2 &    3.50 &    0.01 &  --1.93 &  --0.51 \\ % &    0.01 \\
+% Mn \textsc{I} &   3 &    5.06 &    0.10 &  --0.37 &    0.25 && %    0.06 &&
+% Mn \textsc{I} &   3 &    3.58 &    0.04 &  --1.85 &  --0.43 \\ % &    0.02 \\
+  Fe \textsc{I} &  63 &    6.88 &    0.12 &  --0.62 &    0.00 && %    0.02 &&
+  Fe \textsc{I} &  33 &    6.07 &    0.06 &  --1.43 &  --0.00 \\ % &    0.01 \\
+ Fe \textsc{II} &  12 &    6.87 &    0.07 &  --0.63 &  --0.01 && %    0.02 &&
+ Fe \textsc{II} &   9 &    6.04 &    0.07 &  --1.46 &  --0.03 \\ % &    0.02 \\
+  Co \textsc{I} &   3 &    4.39 &    0.09 &  --0.60 &    0.02 && %    0.05 &&
+% Co \textsc{I} &   5 &    4.59 &    0.14 &  --0.40 &    0.22 && %    0.06 &&
+  Co \textsc{I} &   0 & \nodata & \nodata & \nodata & \nodata \\ % & \nodata \\
+  Ni \textsc{I} &   7 &    5.64 &    0.09 &  --0.58 &    0.05 && %    0.03 &&
+  Ni \textsc{I} &   2 &    4.84 &    0.04 &  --1.38 &    0.05 \\ % &    0.03 \\
+  Cu \textsc{I} &   1 &    3.72 & \nodata &  --0.47 &    0.15 && % \nodata &&
+  Cu \textsc{I} &   1 &    1.96 & \nodata &  --2.23 &  --0.80 \\ % & \nodata \\
+% Cu \textsc{I} &   1 &    3.81 &    0.00 &  --0.38 &    0.24 && %    0.00 &&
+% Cu \textsc{I} &   1 &    2.40 & \nodata &  --1.79 &  --0.36 \\ % & \nodata \\
+  Zn \textsc{I} &   2 &    4.21 &    0.03 &  --0.35 &    0.27 && %    0.02 &&
+  Zn \textsc{I} &   2 &    3.15 &    0.05 &  --1.41 &    0.02 \\ % &    0.04 \\
+  Sr \textsc{I} &   1 &    1.83 & \nodata &  --1.04 &  --0.42 && % \nodata &&
+  Sr \textsc{I} &   1 &    1.23 & \nodata &  --1.64 &  --0.21 \\ % & \nodata \\
+ Sr \textsc{II} &   0 & \nodata & \nodata & \nodata & \nodata && % \nodata &&
+ Sr \textsc{II} &   0 & \nodata & \nodata & \nodata & \nodata \\ % & \nodata \\
+  Y \textsc{II} &   3 &    1.80 &    0.03 &  --0.41 &    0.21 && %    0.02 &&
+  Y \textsc{II} &   6 &    0.76 &    0.06 &  --1.45 &  --0.02 \\ % &    0.03 \\
+  Zr \textsc{I} &   3 &    2.26 &    0.05 &  --0.32 &    0.31 && %    0.03 &&
+  Zr \textsc{I} &   0 & \nodata & \nodata & \nodata & \nodata \\ % & \nodata \\
+ Zr \textsc{II} &   0 & \nodata & \nodata & \nodata & \nodata && % \nodata &&
+ Zr \textsc{II} &   0 & \nodata & \nodata & \nodata & \nodata \\ % & \nodata \\
+ Ba \textsc{II} &   2 &    1.65 &    0.02 &  --0.53 &    0.10 && %    0.01 &&
+ Ba \textsc{II} &   2 &    0.78 &    0.07 &  --1.40 &    0.03 \\ % &    0.05 \\
+%Ba \textsc{II} &   2 &    1.65 &    0.02 &  --0.53 &    0.10 && %    0.01 &&
+%Ba \textsc{II} &   2 &    0.70 &    0.03 &  --1.48 &  --0.05 \\ % &    0.02 \\
+ La \textsc{II} &   1 &    0.76 & \nodata &  --0.34 &    0.28 && % \nodata &&
+%La \textsc{II} &   2 &    0.74 &    0.05 &  --0.36 &    0.26 && %    0.04 &&
+ La \textsc{II} &   0 & \nodata & \nodata & \nodata & \nodata \\ % & \nodata \\
+ Ce \textsc{II} &   3 &    0.87 &    0.13 &  --0.71 &  --0.09 && %    0.08 &&
+ Ce \textsc{II} &   2 &  --0.07 &    0.02 &  --1.65 &  --0.22 \\ % &    0.02 \\
+ Nd \textsc{II} &   6 &    1.27 &    0.13 &  --0.15 &    0.47 && %    0.06 &&
+ Nd \textsc{II} &   1 &  --0.25 & \nodata &  --1.67 &  --0.24 \\ % & \nodata \\
+ Eu \textsc{II} &   1 &    0.40 & \nodata &  --0.12 &    0.50 && % \nodata &&
+%Eu \textsc{II} &   1 &    0.52 &    0.00 &    0.00 &    0.62 && %    0.00 &&
+ Eu \textsc{II} &   1 &  --0.55 & \nodata &  --1.07 &    0.36 \\ % & \nodata \\
+
+\cline{1-6} \cline{8-13} \\ \\
+\multicolumn{7}{c}{C2306265-085103} \\
+\cline{1-6}
+   C (CH)       &   2 &    7.20 &    0.20 &  --1.23 &  --0.10 \\ % &    0.20 \\
+   O \textsc{I} &   2 &    8.02 &    0.04 &  --0.67 &    0.46 \\ % &    0.03 \\
+  Na \textsc{I} &   2 &    5.31 &    0.01 &  --0.93 &    0.21 \\ % &    0.01 \\
+  Mg \textsc{I} &   2 &    6.90 &    0.06 &  --0.70 &    0.44 \\ % &    0.05 \\
+  Al \textsc{I} &   4 &    5.65 &    0.08 &  --0.80 &    0.33 \\ % &    0.04 \\
+  Si \textsc{I} &   5 &    6.78 &    0.08 &  --0.73 &    0.40 \\ % &    0.04 \\
+   K \textsc{I} &   1 &    4.46 & \nodata &  --0.57 &    0.56 \\ % & \nodata \\
+  Ca \textsc{I} &   4 &    5.56 &    0.04 &  --0.78 &    0.35 \\ % &    0.02 \\
+ Sc \textsc{II} &   3 &    2.15 &    0.09 &  --1.00 &    0.13 \\ % &    0.05 \\
+%Sc \textsc{II} &   6 &    2.28 &    0.16 &  --0.87 &    0.26 \\ % &    0.06 \\
+  Ti \textsc{I} &   4 &    4.13 &    0.03 &  --0.82 &    0.32 \\ % &    0.01 \\
+ Ti \textsc{II} &   3 &    4.32 &    0.35 &  --0.63 &    0.51 \\ % &    0.20 \\
+   V \textsc{I} &   4 &    2.85 &    0.06 &  --1.09 &    0.05 \\ % &    0.03 \\
+%  V \textsc{I} &   4 &    2.96 &    0.05 &  --0.98 &    0.16 \\ % &    0.03 \\
+  Cr \textsc{I} &   3 &    4.13 &    0.12 &  --1.51 &  --0.38 \\ % &    0.07 \\
+ Cr \textsc{II} &   1 &    4.50 & \nodata &  --1.14 &  --0.01 \\ % & \nodata \\
+  Mn \textsc{I} &   3 &    4.10 &    0.05 &  --1.33 &  --0.20 \\ % &    0.04 \\
+% Mn \textsc{I} &   3 &    4.40 &    0.10 &  --1.03 &    0.10 \\ % &    0.06 \\
+  Fe \textsc{I} &  62 &    6.37 &    0.12 &  --1.13 &    0.00 \\ % &    0.01 \\
+ Fe \textsc{II} &  11 &    6.39 &    0.10 &  --1.11 &    0.02 \\ % &    0.03 \\
+  Co \textsc{I} &   3 &    3.88 &    0.06 &  --1.11 &    0.02 \\ % &    0.04 \\
+% Co \textsc{I} &   5 &    4.14 &    0.14 &  --0.85 &    0.28 \\ % &    0.06 \\
+  Ni \textsc{I} &   7 &    5.11 &    0.07 &  --1.11 &    0.02 \\ % &    0.03 \\
+  Cu \textsc{I} &   1 &    2.96 & \nodata &  --1.23 &  --0.10 \\ % & \nodata \\
+% Cu \textsc{I} &   1 &    3.53 &    0.00 &  --0.66 &    0.47 \\ % &    0.00 \\
+  Zn \textsc{I} &   2 &    3.48 &    0.15 &  --1.08 &    0.05 \\ % &    0.10 \\
+  Sr \textsc{I} &   1 &    0.94 & \nodata &  --1.93 &  --0.80 \\ % & \nodata \\
+ Sr \textsc{II} &   0 & \nodata & \nodata & \nodata & \nodata \\ % & \nodata \\
+  Y \textsc{II} &   4 &    1.26 &    0.26 &  --0.95 &    0.18 \\ % &    0.13 \\
+  Zr \textsc{I} &   3 &    1.60 &    0.05 &  --0.98 &    0.16 \\ % &    0.03 \\
+ Zr \textsc{II} &   0 & \nodata & \nodata & \nodata & \nodata \\ % & \nodata \\
+ Ba \textsc{II} &   2 &    0.95 &    0.10 &  --1.23 &  --0.10 \\ % & \nodata \\
+%Ba \textsc{II} &   2 &    0.99 &    0.04 &  --1.19 &  --0.06 \\ % &    0.03 \\
+ La \textsc{II} &   1 &    0.07 & \nodata &  --1.03 &    0.10 \\ % & \nodata \\
+%La \textsc{II} &   2 &  --0.02 &    0.03 &  --1.12 &    0.01 \\ % &    0.02 \\
+ Ce \textsc{II} &   2 &    0.09 &    0.02 &  --1.49 &  --0.36 \\ % &    0.01 \\
+ Nd \textsc{II} &   7 &    0.58 &    0.21 &  --0.84 &    0.29 \\ % &    0.08 \\
+ Eu \textsc{II} &   1 &  --0.41 & \nodata &  --0.93 &    0.20 \\ % & \nodata \\
+%Eu \textsc{II} &   1 &  --0.32 &    0.00 &  --0.84 &    0.29 \\ % &    0.00 \\
+ \hline
+\end{longtable*}
+
+% Iron peak elements
+\begin{figure}[h]
+	\includegraphics[width=\columnwidth]{./figures/aquarius-fe-peak.pdf}
+	\caption{Iron peak element abundances (Sc, V, Cr, Mn, Co and Cu) with respect to iron for all Aquarius stream stars.
+Ni, an additional Fe-peak element, is discussed in \S\ref{sec:na-ni-relationship} and shown in Figure \ref{fig:na-ni}}
+	\label{fig:fe-peak-elements}
+\end{figure}
+
+\subsection{Neutron-capture Elements}
+Neutron-capture elements (Sr to Eu; ${38 \leqslant Z \leqslant 63}$) can be forged through multiple nucleosynthetic processes.
+The two primary processes that produce these elements are the rapid ($r$-) process and the slow ($s$-) process.
+While the $r$-process is theorised to occur in SN explosions, the $s$-process takes place foremost in AGB stars with a significant contribution from massive stars at higher metallicities \citep[e.g.,]{meyer_1994}, although models of rotating massive stars may change this picture \citep{frischknecht;et-al_2012}.
+
+\subsubsection{Strontium, Yttrium and Zirconium}
+\label{sec:weak-s-process-elements}
+
+These light neutron-capture elements generally increase in lock-step with each another.
+While {[Y\,\textsc{ii}/Fe]} and {[Zr\,\textsc{i}, Zr \textsc{ii}/Fe]} are in good agreement among all candidates, {[Sr\,\textsc{i}/Fe]} ratios are generally lower, with considerable scatter.
+The {Sr\,\textsc{ii}} lines at 407.7\,nm and 421.5\,nm were not detected in any program or standard stars, although {Sr\,\textsc{i}} was measurable at 664.5\,nm and no obvious telluric contamination was observed.
+Given that Sr\,\textsc{i} transitions are susceptible to non-LTE effects \citep{hansen;et-al_2013}, we note these Sr abundances should be treated with some caution.
+
+%This is the first study to present first peak $s$-process elemental abundances for five of the six standard stars.
+Existing data on neutron-capture abundances were not crucial in selecting standard comparison stars: it was more important to cover a range of stellar parameters.
+
+The Aquarius stream candidates have Y abundances consistent with halo field stars, with the exception of {C222531-145437}.
+With {[Y/Fe] = 0.79}, {C222531-145437} is significantly over-abundant in Y for its metallicity \citep[see Figure 4 of][]{travaglio;et-al_2004}.
+{C222531-145437} is consistently over-abundant in Sr and Zr, too.
+All other program and standard stars have light $s$-process abundances and trends that are consistent with the chemical evolution of the Milky Way.
+
+\subsubsection{Barium and Lanthanum}
+
+Barium is primarily produced through the $s$-process, has appreciable hyperfine and isotopic splitting, and its measurement requires some careful consideration.
+Solar Ba isotopic ratios from \citet{citation_needed3} have been adopted.
+Our standard stars have [Ba/Fe] abundances typical of the Milky Way halo.
+Two standard stars have existing [Ba/Fe] measurements from high-resolution spectra: HD\,44007 and HD\,76932.
+We find HD\,44007 to have ${\mbox{[Ba/Fe]} = 0.03}$, which is in good agreement with \citet{burris;et-al_2000}, who find {0.05\,dex}.
+For HD\,76932 our measurement of {$\mbox{[Ba/Fe]} = 0.18$} is in reasonable agreement with the \citet{fulbright_2000} value of $-0.02$\,dex, especially when differences in adopted solar composition are considered.
+
+With one exception, the Aquarius stream candidates have [Ba/Fe] abundance ratios that are indistinguishable from field stars, ranging between ${\mbox{[Ba/Fe]} = -0.10}$ to {0.10\,dex}.
+The exception is {C222531-085103}, which has an anomalously high barium abundance of ${\mbox{[Ba/Fe]} = 0.62}$.
+This is $\sim$+0.60\,dex higher than the Milky Way trend at its given metallicity of ${\mbox{[Fe/H]} = -1.26}$.
+Our two {Ba\,\textsc{ii}} lines in {C222531-085103} are in excellent agreement with each other: [Ba/Fe] = 0.63, and 0.61.
+
+% [TODO] Lanthanum??
+
+% [TODO] Synthesize Lanthanum
+% [TODO] Discuss Lanthanum
+
+\subsubsection{Cerium, Neodymium and Europium}
+
+Europium is primarily produced by the $r$-process, whereas the production of Ce and Nd is split between $s$- and $r$-process.
+Europium abundances have been determined by synthesising the 664.5\,nm Eu\,\textsc{ii} transition with hyperfine splitting data from \citet{citation_needed5}.
+
+We chose not to use the 643.7\,nm line as it is appreciably blended by a nearby Si\,\textsc{i} line \citep{Lawler;et-al_2001}, and our measurements were consistent with a hidden blend: the 643.7\,nm Eu\,\textsc{ii} abundance was systematically higher than the 664.5\,nm counterpart.
+One Aquarius stream candidate, {C222531-145437}, appears enhanced in all [$s$-process/Fe] abundance ratios compared to the program and standard sample.
+However no noteworthy difference in Eu, an $r$-process dominated element, was observed.
+
+% elemental abundances
+\begin{figure}[h]
+	\includegraphics[width=\columnwidth]{./figures/plot-x-on-fe.pdf}
+	\caption{Element ratios for Aquarius stream stars.
+In the case of [Zr/Fe], {[Zr\,\textsc{i}/Fe]} is taken where available and {[Zr\,\textsc{ii}/Fe]} if no measurement was available for {Zr\,\textsc{i}}.
+See Table \ref{tab:program-star-abundances} for details.}
+	\label{fig:x-on-fe}
+\end{figure}
+
+\section{Uncertainties}
+\label{sec:uncertainties}
+
+\subsection{Uncertainties in Stellar Parameters}
+Due to scatter in neutral iron lines measurements, there is a formal uncertainty in our calculated trend line between excitation potential and abundance, as well as between the reduced equivalent width and abundance.
+We have calculated 1-$\sigma$ uncertainties in effective temperature and microturbulence by independently varying each stellar parameter until the relevant slope matches that formal uncertainty.
+This process is repeated for positive and negative offsets in temperature and microturbulence to allow for strong asymmetric uncertaintie.
+The largest absolute offset is taken as the $1\sigma$ uncertainty.
+For surface gravity, the uncertainty has been calculated by varying $\log{g}$ until the difference in mean Fe\,\textsc{i} - Fe\,\textsc{ii} abundance matches the standard error about the mean for Fe\,\textsc{i} and Fe\,\textsc{ii} in quadrature.
+The calculated uncertainties are tabulated in Table \ref{tab:stellar-parameter-uncertainties}.
+
+These uncertainties ignore any correlations between stellar parameters, and therefore are likely to be under-estimated.
+As such, we have assumed the total uncertainty in stellar parameters to be $\sigma(T_{\rm eff}) = \pm125$\,K, $\sigma(\log{g}) = \pm0.30$\,dex, and $\sigma(v_t) = \pm0.20$ km s$^{-1}$.
+These adopted uncertainties are higher than any of the measured the uncorrelated uncertainties, and are \textit{extremely conservative}.
+
+\begin{deluxetable}{lccccccccccc}
+\tablecolumns{1}
+\tabletypesize{\scriptsize}
+\tablecaption{Uncorrelated Uncertainties in Stellar Parameters\label{tab:stellar-parameter-uncertainties}}
+\tablehead{
+    \colhead{Designation} &
+	\colhead{$\sigma(T_{\rm eff})$} &
+	\colhead{$\sigma(v_t)$} &
+	\colhead{$\sigma(\log{g})$} \\
+%	\colhead{$\sigma({\rm [M/H]})$} \\
+ & (K) & (km s$^{-1}$) & (dex) %& (dex)
+ }
+\startdata
+HD\,41667  	&    53   	&   0.09   &   0.13   \\%&   0.12 \\
+HD\,44007 		&    81   	&   0.29   &   0.09   \\%&   0.13 \\
+HD\,76932 		&   107  	&   0.08   &   0.19   \\%&   0.10 \\
+HD\,136316		&    33   	&   0.15   &   0.12   \\%&   0.11 \\
+HD\,141531		&    25   	&   0.05   &   0.13   \\%&   0.06 \\
+HD\,142948		&    47   	&   0.10   &   0.11   \\%&   0.10 \\
+J221821-183424 	&    42   	&   0.11   &   0.09   \\%&   0.09 \\
+C222531-145437  	&    46   	&   0.05   &   0.12   \\%&   0.10 \\
+J223504-152834  	&    61   	&   0.08   &   0.05   \\%&   0.12 \\
+J223811-104126  	&    49   	&   0.16   &   0.08   \\%&   0.06 \\
+C230626-085103  	&    52   	&   0.05   &   0.04   %&   0.12
+\enddata
+\end{deluxetable}
+
+\subsection{Uncertainties in Chemical Abundances}
+
+The uncertainties in chemical abundances are primarily driven by systematic uncertainties in stellar parameters, with a small contribution of random measurement scatter from individual lines.
+In order to calculate the abundance uncertainties due to stellar parameters, we have independently varied the stellar parameters by the adopted uncertainties, and measured the resultant change in chemical abundances.
+For lines requiring synthesis due to hyperfine structure, the difference in chemical abundances has been calculated from EWs.
+However, the effect of wing broadening due to hyperfine or isotopic splitting was generally small, and we can assume these effects are linear.
+
+The abundance offsets from each variation of stellar parameters has been added in quadrature, along with the standard error about the mean for the line measurements.
+In some cases, the standard error about the mean is unrealistically small.
+As discussed earlier in Section \ref{sec:sodium-abundances}, we have conservatively adopted an abundance floor of 0.10\,dex for the standard deviation (i.e.
+$Max(0.10, \sigma(\log_{\epsilon}X)$).
+These resultant changes in abundances and total uncertainties are listed for all stars in Table \ref{tab:chemical-abundance-uncertainties}.
+These total uncertainties have been used in all figures.
+This provides us with an uncertainty for all abundances, in all stars, of [X/H].
+Generally though, we are most interested in the uncertainty in [X/Fe].
+In order to calculate this uncertainty, the correlations in uncertainties due to stellar parameters between (X, Fe) need to be considered.
+We have followed the description in \citet{johnston;et-al_2001} to calculate these correlations, and the overall uncertainties in [X/Fe], which are listed in Table \ref{tab:chemical-abundance-uncertainties} for all program and standard stars.
+
+\begin{deluxetable*}{lcccccc}
+\tablecolumns{1}
+\tabletypesize{\scriptsize}
+\tablecaption{Abundance Uncertainties Due to Stellar Parameters\label{tab:chemical-abundance-uncertainties}}
+\tablehead{
+ & &  & & & \multicolumn{2}{c}{\textbf{Total Uncertainty}} \\
+ \cline{6-7}
+	\colhead{Species} &
+	\colhead{$T_{\rm eff} +125\,{\rm K}$} &
+	\colhead{$\log{g} +0.20\,{\rm dex}$} &
+	\colhead{${v_t} +0.30$\,km s$^{-1}$} &
+	\colhead{$Max(0.10, \sigma)/\sqrt(N)$} & 
+	\colhead{[X/H]} &
+	\colhead{[X/Fe]} \\
+	 & $\Delta$abundance & $\Delta$abundance & $\Delta$abundance & (dex) & (dex) & (dex)
+ }
+\startdata
+\\
+\multicolumn{7}{c}{\textbf{HD 41667}} \\
+\hline
+O I  		& +0.03		& +0.08		&$-$0.01		& 0.07		& 0.11		& 0.12 \\
+Na I  		& +0.13		& +0.00		&$-$0.02		& 0.10		& 0.16		& 0.09 \\
+Mg I  		& +0.08		& +0.01		&$-$0.01		& 0.05		& 0.10		& 0.10 \\
+Al I  		& +0.10		& +0.01		&$-$0.01		& 0.06		& 0.11		& 0.07 \\
+Si I  		& +0.02		& +0.03		&$-$0.02		& 0.04		& 0.06		& 0.13 \\
+K I  		& +0.14		&$-$0.03		&$-$0.17		& 0.10		& 0.24		& 0.15 \\
+Ca I  		& +0.13		&$-$0.01		&$-$0.10		& 0.05		& 0.17		& 0.05 \\
+Sc II  	&$-$0.03		& +0.08		&$-$0.08		& 0.05		& 0.13		& 0.17 \\
+Ti I  		& +0.22		& +0.01		&$-$0.01		& 0.05		& 0.22		& 0.04 \\
+Ti II 		&$-$0.04		& +0.07		&$-$0.15		& 0.14		& 0.23		& 0.25 \\
+V I 		& +0.25		& +0.01		&$-$0.03		& 0.05		& 0.26		& 0.09 \\
+Cr I 		& +0.23		& +0.00		&$-$0.20		& 0.03		& 0.31		& 0.14 \\
+Cr II  	&$-$0.07		& +0.08		&$-$0.06		& 0.07		& 0.14		& 0.22 \\
+Mn I  		& +0.17		& +0.01		&$-$0.07		& 0.06		& 0.19		& 0.05 \\
+Fe I  		& +0.16		& +0.01		&$-$0.07		& 0.02		& 0.17		& \nodata \\
+Fe II  	&$-$0.10		& +0.08		&$-$0.04		& 0.03		& 0.14		& \nodata \\
+Co I  		& +0.18		& +0.03		&$-$0.01		& 0.04		& 0.19		& 0.04 \\
+Ni I  		& +0.12		& +0.03		&$-$0.01		& 0.05		& 0.13		& 0.03 \\
+Cu I  		& +0.19		& +0.03		&$-$0.16		& 0.10		& 0.27		& 0.10 \\
+Zn I  		&$-$0.03		& +0.06		&$-$0.09		& 0.07		& 0.14		& 0.19 \\
+Sr I  		& +0.24		& +0.01		&$-$0.06		& 0.10		& 0.27		& 0.11 \\
+Y II  		& +0.00		& +0.08		&$-$0.09		& 0.09		& 0.15		& 0.15 \\
+Zr I  		& +0.27		& +0.01		& +0.00		& 0.07		& 0.28		& 0.13 \\
+Zr II  	& +0.00		& +0.08		&$-$0.01		& 0.10		& 0.13		& 0.17 \\
+Ba II 		& +0.01		& +0.06		&$-$0.21		& 0.07		& 0.23		& 0.19 \\
+La II 		& +0.01		& +0.07		&$-$0.02		& 0.07		& 0.10		& 0.14 \\
+Ce II 		& +0.04		& +0.08		&$-$0.04		& 0.09		& 0.13		& 0.11 \\
+Nd II 		& +0.02		& +0.06		&$-$0.07		& 0.03		& 0.10		& 0.11 \\
+Eu II 		&$-$0.05		& +0.04		&$-$0.06		& 0.10		& 0.13		& 0.22
+\enddata
+\tablenotetext{}{Table \ref{tab:chemical-abundance-uncertainties} is published for all standard and program stars in the electronic edition.
+A portion is shown here for guidance regarding its form and content.}
+\end{deluxetable*}
+
 \section{Discussion}
@@
 
-We seek to investigate the nature of the Aquarius stream, as well as the specific globular cluster origin claim made by \citet{wylie-de-boer;et-al_2012}.
-The stellar parameters reported in \citet{wylie-de-boer;et-al_2012} differ to those published in Table \ref{tab:stellar-parameters}.
+We seek to investigate the nature of the Aquarius stream.
+Specifically, the globular cluster origin suggested by \citet{wylie-de-boer;et-al_2012}.
+For the four stars common to both samples, the stellar parameters reported in \citet{wylie-de-boer;et-al_2012} differ to our values listed in Table \ref{tab:stellar-parameters}.
 \citet{wylie-de-boer;et-al_2012} deduce their stellar parameters by minimizing the $\chi^2$ difference between the observed spectra and synthetic spectra from the \citet{munari;et-al_2005} spectral library.
-The synthetic library has a slightly lower resolution than the observations.
-The observed spectral range was 4120 to 6920\,{\AA}, and the regions used for $\chi^2$ minimisation were {4900-5200\,\AA} and {5575-5725\,\AA}.
-In general, temperatures between the two studies agree within the uncertainties.
-Given temperature has the principal effect on spectral features, this is perhaps unsurprising.
-The only aberration is {J223811-104126}, where we find an effective temperature of {5190\,K}, {$\sim{}450\,{\rm K}$} cooler than the {5646\,K} found by \citet{wylie-de-boer;et-al_2012}.
+In general, effective temperatures between the two studies agree within the uncertainties.
+The only aberration is {J223811-104126}, where we find an effective temperature of {5190\,K}, $\sim$450\,K cooler than the {5646\,K} found by \citet{wylie-de-boer;et-al_2012}.
 Similarly, \citet{williams;et-al_2011} report a hotter effective temperature of {5502\,K} from low-resolution spectra.
@@
 
-Photometric temperatures only lend marginal weight towards our spectroscopic temperatures.
-If the \citet{schlegel;et-al_1998} dust maps are employed, then the \citet{alonso;et-al_1999} and \citet{casagrande;et-al_2010} relations estimate the effective temperatures to be between {5104\,K} and {5367\,K}.
-Our spectroscopic temperature of {5190\,K} is in excellent agreement with the \citet{alonso;et-al_1999} prediction, but not in strong disagreement with the \citet{casagrande;et-al_2010} relation either.
-If we employ the reddening of $E(B-V) = 0.12$ that we have determined from the interstellar Na D1 line, the photometric temperature increases slightly by {$\sim{}100\,{\rm K}$}, in perfect agreement with the \citet{alonso;et-al_1999} scale.
-We find the surface gravity for {J223811-104126} to be {3.00 $\pm$ 0.50\,dex}, placing this star at the base of the red giant branch.
-Thus, if {J223811-104126} is a giant star, our spectroscopic temperatures should be in slightly better agreement with the \citet{alonso;et-al_1999} scale, rather than the \citet{casagrande;et-al_2010} dwarf/sub-giant scale.
-However, \citet{williams;et-al_2011} and \citet{wylie-de-boer;et-al_2012} find this star to be a sub-giant, with a surface gravity {$\log{g} = 4.16$} and {4.60\,dex} respectively.
-The \citet{williams;et-al_2011} and \citet{wylie-de-boer;et-al_2012} temperatures are 150\,K and 300\,K hotter than the \citet{casagrande;et-al_2010} prediction respectively.
-If our interstellar extinction value is employed -- and the star is a sub-giant -- then the \citet{williams;et-al_2011} and \citet{casagrande;et-al_2010} temperatures are in good agreement, but the \citet{wylie-de-boer;et-al_2012} measurement is still 175\,K cooler.
-
+Photometric temperature relationships support our spectroscopic temperature for J223811-104126.
+The \citet{ramirez;melendez_2005} relationship for giants suggests an effective temperature of 5240\,K, which is 50\,K warmer than our spectroscopically-derived temperature.
+Furthermore, the metallicity-independent $J-K$ colour-$T_{\rm eff}$ relationship for giants by \citet{alonso;et-al_1999} yields an effective temperature of 5215\,K, 25\,K warmer than our spectroscopic temperature.
 As a test, we set the temperature for {J223811-104126} to be 5600\,K -- within the temperature regime reported by \citet{williams;et-al_2011} and \citet{wylie-de-boer;et-al_2012}.
-The slopes in abundance with excitation potential and reduced equivalent width were large (${m_{\rm Fe\,\textsc{i}} = -0.099}$\,dex\,eV$^{-1}$, 0.162\,dex, ${m_{\rm Fe\,\textsc{ii}} = -0.133}$\,dex\,eV$^{-1}$, $-0.033$\,dex respectively), and in doing so we could not find a representative solution for this temperature.
-Thus although photometric temperatures do not completely resolve this discrepancy in spectroscopic temperatures between this study and others, the \citet{alonso;et-al_1999} scale is in good agreement with our spectroscopic temperature if our interstellar extinction value is employed.
-
-In the \citet{wylie-de-boer;et-al_2012} study, the surface gravity was determined during the $\chi^2$ minimisation process.
-Again, with the exception of {J223811-104126}, our surface gravities are largely in agreement.
-The only other noteworthy difference in surface gravity is for {J221821-183424}, where we find a lower gravity of {$\log{g} = 0.88 \pm 0.30$} and \citet{wylie-de-boer;et-al_2012} find {$\log{g} = 1.45 \pm 0.35$\,dex}.
-Given the difference in the $S/N$ ratio between these studies, this difference is not too concerning.
-
-\citet{wylie-de-boer;et-al_2012} calculate microturbulence from empirical relationships derived by \citet{reddy;et-al_2003} for dwarfs and \citet{fulbright_2000} for giants.
+The slopes and offsets in abundance with excitation potential and REW were large: ${m_{\rm Fe\,\textsc{i}} = -0.099}$\,dex\,eV$^{-1}$, 0.162\,dex, ${m_{\rm Fe\,\textsc{ii}} = -0.133}$\,dex\,eV$^{-1}$, $-0.033$\,dex respectively, and in doing so we could not find a representative solution for this temperature.
+
+\citet{williams;et-al_2011} and \citet{wylie-de-boer;et-al_2012} find {J223811-104126} to be a sub-giant/dwarf, with a surface gravity {$\log{g} = 4.16$} and {4.60} respectively.
+We note that the \citet{williams;et-al_2011} and \citet{wylie-de-boer;et-al_2012} effective temperatures for J223811-104126 are 150-300\,K hotter than the \citet{casagrande;et-al_2010} $J-K$ photometric temperature calibration for dwarfs and sub-giants.
+We find the surface gravity for {J223811-104126} to be {$\log{g} = 2.93 \pm 0.30$\,dex}, placing this star at the base of the red giant branch.
+
+With the exception of {J223811-104126}, our surface gravities are largely in agreement with \citet{wylie-de-boer;et-al_2012}.
+The only other noteworthy difference is for {J221821-183424}, where we find a lower gravity of {$\log{g} = 0.88 \pm 0.30$} and \citet{wylie-de-boer;et-al_2012} find {$\log{g} = 1.45 \pm 0.35$\,dex}.
+Given the difference in the $S/N$  between these studies, this difference is not too concerning.
+\citet{wylie-de-boer;et-al_2012} calculate the microturbulence from empirical relationships derived by \citet{reddy;et-al_2003} for dwarfs and \citet{fulbright_2000} for giants.
 These relationships are based on the effective temperature and surface gravity.
@@
 
-Of all the stellar parameters ($T_{\rm eff}$, $\log{g}$, $v_{t}$ and [M/H]), the metallicities between our two studies vary the most.
-Here we discuss the potential causes for these discrepancies.
-In the \citet{wylie-de-boer;et-al_2012} study, after the stellar parameters ($T_{\rm eff}$, $\log{g}$, $v_{t}$, and an initial [M/H] estimate) had been determined through a $\chi^2$ analysis, the authors synthesised individual {Fe\,\textsc{i}} and \textsc{ii} lines using \textsc{moog}.
+Of all the stellar parameters, metallicities exhibit the largest discrepancy between the two studies.
+In the \citet{wylie-de-boer;et-al_2012} study, after the stellar parameters ($T_{\rm eff}$, $\log{g}$, $v_{t}$, and an initial [M/H] estimate) were determined through a $\chi^2$ minimisation, the authors synthesised individual {Fe\,\textsc{i}} and Fe\,\textsc{ii} lines using \textsc{moog}.
 \citet{castelli;kurucz_2003} stellar atmosphere models were employed (K.
 Freeman, private communication, 2013) -- the same ones used in this study -- albeit the interpolation schemes will have subtle differences.
-The median abundance of {Fe\,\textsc{i}} lines was taken as the overall stellar metallicity, scaled using the \citet{grevesse;sauval_1998} solar composition.
+The median abundance of synthesised {Fe\,\textsc{i}} lines was adopted as the overall stellar metallicity, and scaled relative to the Sun using the \citet{grevesse;sauval_1998} Solar composition.
 
 The study of \citet{wylie-de-boer;et-al_2012} is of slightly lower resolution ($\mathcal{R} = 25,000$ compared to $\mathcal{R} = 28,000$ presented here), but with a much lower $S/N$ ratio: ${\sim{}25\,{\rm pixel}^{-1}}$ compared to {$>$100\,pixel$^{-1}$} achieved here.
-Given the slightly lower spectral resolution,  modest $S/N$ and smaller spectral coverage in the \citet{wylie-de-boer;et-al_2012} study, there are fewer unblended absorption lines available.
-In fact, there are very few transitions present in their published line list: a maximum of 14 {Fe\,\textsc{i}} lines and 3 {Fe\,\textsc{ii}} lines were available.
-For contrast, our metallicity determinations are based from 63 {Fe\,\textsc{i}} and 13 {Fe\,\textsc{ii}} clean, unblended lines.
-Given the metallicity of these candidates and the reasonable wavelength coverage of the \citet{wylie-de-boer;et-al_2012} data, it is somewhat surprising that there were not more transitions available for analysis.
-
-The line list employed in the \citet{wylie-de-boer;et-al_2012} utilised different oscillator strengths than those tabulated in Table \ref{tab:equivalent-widths}.
-The oscillator strengths in the \citet{wylie-de-boer;et-al_2012} study are astrophysical; they were derived from a reverse analysis from the \citet{hinkle;et-al_2003} solar atlas.
+The line list employed in the \citet{wylie-de-boer;et-al_2012} utilised astrophysical oscillator derived from a reverse solar analysis on the Solar spectrum.
+However, there are very few transitions listed in their line list: a maximum of 14 {Fe\,\textsc{i}} lines and 3 {Fe\,\textsc{ii}} lines were available.
+For contrast, our analysis is based on 63 {Fe\,\textsc{i}} and 13 {Fe\,\textsc{ii}} clean, unblended lines.
+
+% Removed at David Yong's behest
+%Given the metallicity of these candidates and the reasonable wavelength coverage (4120-6920\,{\AA}) of the \citet{wylie-de-boer;et-al_2012} data, it is somewhat surprising that there were not more transitions available for analysis.
+
 Suspecting the differing line lists may contribute to the metallicity discrepancy, we re-analysed our data using the \citet{wylie-de-boer;et-al_2012} line list and stellar parameters.
 Indeed, in doing so we arrive at reasonably similar metallicities to \citet{wylie-de-boer;et-al_2012}.
-Without using their published stellar parameters a priori, in a `blind' analysis employing just the \citet{wylie-de-boer;et-al_2012} line list, we also arrive at similar stellar parameters.
-However, given the limited number of lines available, extremely subtle changes to the stellar parameters inflicted large variations to both the individual and mean Fe abundances.
-Additionally, we note that one {Fe\,\textsc{i}} transition at {6420.060\,\AA} in the \citet{wylie-de-boer;et-al_2012} line list was either not detected at the {3$\sigma$} level -- even though the $S/N$ at this point exceeds {115\,pixel$^{-1}$} in every observation -- or it was blended with a stronger neighbouring transition.
-Thus, for this comparative analysis a maximum of 13 {Fe\,\textsc{i}} and 3 {Fe\,\textsc{ii}} lines were available.
-
-Given the line list employed in the \citet{wylie-de-boer;et-al_2012} study, the overall data quality and the lack of suitable iron lines available for analysis, it appears the Aquarius stream stars conspired to present a tight metallicity distribution of {$\sigma(\mbox{Fe/H}) = 0.10$\,dex}.
-When viewed in light of enhanced [Ni/Fe], [Na/Fe] abundance ratios, this chemistry might be suggestive of a globular cluster origin.
-Our analysis of high-resolution spectra with high $S/N$ reveals a much broader metallicity distribution for the stream.
-With just five stars we find the stream metallicity varies from {$\mbox{[Fe/H]} = -0.63$} to {$-1.63$\,dex}.
-Although this is a small sample, we find the calculated mean abundance and standard deviation to be {$\mbox{[Fe/H]} = -1.24 \pm 0.36$\,dex}.
-
-\subsection{The Aquarius Stream M.D.F.}
-
-Classical globular clusters typically exhibit very little chemical scatter.
-This is largely because they are primarily -- and somewhat incorrectly -- considered to be a single stellar populations, originating from a lone, largely homogenous proto-stellar cloud.
+Without using their published stellar parameters a priori, in a ``blind'' analysis employing just the \citet{wylie-de-boer;et-al_2012} line list, we find stellar parameters similar to \citet{wylie-de-boer;et-al_2012}.
+However, given the small numbers of lines used, even subtle changes to the stellar parameters can produce large variations to both the individual and mean Fe abundances.
+Additionally, we note that one {Fe\,\textsc{i}} transition at 642\,nm in the \citet{wylie-de-boer;et-al_2012} line list was either not detected at the {3$\sigma$} level -- even though the $S/N$ at this point exceeds {115\,pixel$^{-1}$} in every observation -- or it was blended with a stronger neighbouring transition.
+
+Given the overall data quality and the lack of suitable Fe lines available for analysis, it appears the Aquarius stream stars conspired to present a tight metallicity distribution of {$\sigma(\mbox{[Fe/H]}) = 0.10$\,dex}.
+When viewed in light of enhanced [Ni/Fe] and [Na/Fe] abundance ratios, \citet{wylie-de-boer;et-al_2012} interpreted this chemistry as a signature of a globular cluster origin for the Aquarius stream.
+
+\subsection{The Aquarius Stream Metallicity Distribution}
+
+%This is largely because they are primarily -- and somewhat incorrectly -- considered to be a single stellar populations, originating from a lone, largely homogenous proto-stellar cloud.
 Observations have demonstrated that this is not always the case: many globular clusters clearly host multiple stellar populations.
 The separation between these sub-populations is identifiable through chemical abundances, and often from photometry alone.
-One prominent example is that of $\omega$-Centurai (NGC 5139), which is seen to host many sub-populations with very different metallicity distributions.
-Without the explanation of multiple sub-populations in mind, such a system would be seen to exhibit an unreasonably wide metallicity dispersion for a single stellar population.
-
-Assuming all our candidates are stream members, we find a metallicity dispersion of {$\sigma(\mbox{[Fe/H]}) = 0.36$\,dex}.
-If the stream is the result of a disrupted system, this metallicity dispersion provides little indication on the host.
-If the dispersion were smaller, confirming the observations of \citet{wylie-de-boer;et-al_2012}, a globular cluster scenario may be more likely.
-However, given the multiple stellar populations present in many globular clusters, which can exhibit total cluster dispersions up to X dex (NGC X), Y dex (NGC Y) -- hi Gary :-) --, our dispersion of 0.36\,dex is somewhat inconvenient.
-Since dSph galaxies do not undergo chemical self-enrichment in the same way as globular clusters, they can exhibit significant metallicity dispersions -- well over a dex, depending on the total system luminosity.
-On its own, the metallicity of our stream stars does not provide any indication on the cause of the Aquarius stream, or its enrichment environment.
+
+This study of high-resolution spectra with high $S/N$ reveals a much broader metallicity distribution for the stream.
+With just 5 stars we find the metallicity varies from {$\mbox{[Fe/H]} = -0.63$} to {$-1.58$\,dex}.
+Although this is a small sample, we find the mean abundance and standard deviation to be {$\mbox{[Fe/H]} = -1.20 \pm 0.33$}.
+
+If the metallicity dispersion were smaller, as found by \citet{wylie-de-boer;et-al_2012}, a globular cluster scenario may be plausible.
+Classical globular clusters typically exhibit very little dispersion in metallicity.
+An intrinsic [Fe/H] dispersion of 0.33\,dex -- ignoring error contribution -- is substantially larger than that seen in any globular cluster, with the exception of the unusual system $\omega$-Centauri.
+In that cluster the total abundance range is about $\Delta$[Fe/H] $\sim$ 1.4\,dex: from $-$2 to $-$0.6 \citep[e.g.][]{marino;et-al_2011}, and many sub-populations have been identified \citep[e.g.,][]{johnson_pilachowski_2010}.
+
+Other clusters with established intrinsic [Fe/H] dispersions include M54 -- a nuclear star cluster of the Sagittarius dSph -- where $\sigma_{\rm int}$([Fe/H])$ = 0.19$ \citep{carretta;et-al_2010}, and M22, where the interquartile range in [Fe/H] is $\sim{}$0.24 dex \citep{da_costa;et-al_2009,marino;et-al_2009,marino;et-al_2011}.
+There are a few clusters where the intrinsic dispersion is $\sim$0.10, namely NGC 1851 \citep{carretta;et-al_2011}, NGC 5824 \citep{saviane;et-al_2012}, and NGC 3201 \citep{simmerer;et-al_2013}.
+These globular clusters are outliers, and even in these unusual systems, only one or two system could plausibly match the abundance spread observed in the Aquarius stream \citep[e.g.
+see Figure 4 in][]{simmerer;et-al_2013}.
+In fact, the Aquarius stream metallicity distribution -- on its own -- is large enough to be reconcilable with dSph galaxies like Fornax or Sagittarius, however the $\log(L)-$[Fe/H] relationship would suggest an extremely luminous system on the order of $L_{\rm tot} \sim 10^{7.5}L_\odot$ \citep{kirby;et-al_2011}.
+However, the Aquarius stream stars exhibit [Ba/Y] (e.g.
+heavy/light $s$-process) abundance ratios between $-$0.24 and +0.19, significantly lower than the [Ba/Y] $\geq$ 0.5 level generally observed in the present day dSphs \citep{venn;et-al_2004}.
 
@@
 
-Extensive studies looking at stars in globular clusters have revealed variations in light-element abundances, most notably an anti-correlation in sodium and oxygen content \citep[][and references therein]{norris;da_costa_1995,carretta;et-al_2009a}.
-This chemical pattern has been repeatedly demonstrated in every well-studied globular cluster, although the strength of the anti-correlation varies in each system.
-Between generations of stars within a globular cluster, oxygen is converted into nitrogen, thereby reducing the overall oxygen abundance.
+% From DY:
+%>Just a personal preference, I think you can substantially shorten the text from "Between generations of stars within a globular cluster É" to the end of the subsection.
+
+%>The pertinent points to make are the fact that O depletion and Na synthesis require temperatures that cannot be readily attained in 0.8M_sun giants, i.e., those currently on the RGB.
+Additionally, the temperatures required for O-Na synthesis are *not* attained in main sequence stars, nor is there any plausible mixing mechanism to transport processed material to the atmosphere.
+Thus, the O-Na anticorrelation cannot be due to internal nucleosynthesis and thus an external source/mechanism is demanded.
+
+%>You have already noted the ubiquitous GC O-Na anticorrelation, and can then jump to the final two para's of this subsection.
+
+Extensive studies of stars in globular clusters have revealed variations in light element abundances, most notably an anti-correlation in sodium and oxygen content \citep[see][and references therein]{norris;da_costa_1995,carretta;et-al_2009a}.
+This chemical pattern has been identified in every well-studied globular cluster, although the magnitude and shape of the anti-correlation varies from cluster to cluster.
+
+%Between generations of stars within a globular cluster, oxygen is converted into nitrogen, thereby reducing the overall oxygen abundance.
 Even though oxygen undergoes internal mixing during its evolution along the giant branch, the detection of this chemical pattern in unevolved stars led to the conclusion that observed abundance variations due to mixing are limited to lithium, carbon and nitrogen.
@@
 
-Sodium is primarily produced through through carbon burning in massive stars by the dominant $^{12}\mbox{C}(^{12}\mbox{C}, p)^{23}\mbox{Na}$ process.
+Sodium is primarily produced through carbon burning in massive stars by the dominant $^{12}\mbox{C}(^{12}\mbox{C}, p)^{23}\mbox{Na}$ reaction.
 The final Na abundance is dependent on the neutron excess of the star, which slowly increases during carbon burning due to weak interactions \citep{arnett;truran_1969}.
-Massive stars ($>8 M_\odot$) eventually deliver their manufactured sodium to the interstellar-medium through {Sn\,\textsc{ii}} events.
-Because the eventual {Sn\,\textsc{ii}} explosion is devoid of any significant beta-decay processes, the neutron excess of the exploded material is representative of the pre-explosive abundance.
+Massive stars ($>10 M_\odot$) eventually deliver their synthesized sodium to the interstellar-medium through {SN\,\textsc{ii}} explosions.
+Because the eventual {SN\,\textsc{ii}} explosion is devoid of any significant $\beta$-decay processes, the neutron excess of the ejected material is representative of the pre-explosive abundance.
+The ejected material eventually condenses to form the next generation of stars, which will have a net increase in their neutron excess with respect to their predecessors.
+Since the sodium production rate is correlated with the neutron excess, an overall increase in the total sodium content \textit{and} Na-production rate between stellar generations can be expected.
+The sodium content also becomes important for production of nickel during the {SN\,\textsc{ii}} event (see Section \ref{sec:na-ni-relationship}) because $^{23}$Na is the only stable isotope produced in significant quantities during the C- or O-burning stages.
+
+Oxygen depletion is likely the result of complete CNO burning within the stellar interior.
+The nucleosynthetic pathways that produce the {Na-O} anti-correlation are well understood to be proton-capture nucleosynthesis at high temperatures \citep{prantzos;et-al_2007}.
+However, the temperatures required to produce these patterns are not expected within the interiors of globular cluster stars.
+While the exact mechanism for which these conditions occur remains under investigation, we can describe the abundance variation as an external oxygen depletion (or dilution) model with time.
+Through comparisons with existing globular clusters, we can make inferences on the star-formation history of a system by measuring sodium and oxygen abundances in a sample of its stars.
 
@@
 	\caption{Oxygen and sodium abundances for 14 classical globular clusters from \citet{carretta;et-al_2009a}, demonstrating the clear inverse {Na-O} correlation, ubiquitous to all well-studied globular clusters.
-The [O/Fe] and [Na/Fe] abundances from this study for the five Aquarius stream candidates are also shown (last panel).}
+The [O/Fe] and [Na/Fe] abundances from this study for the 5 Aquarius stream stars (1/3 of the entire stream) are also shown in the last panel.}
 	\label{fig:o-na-clusters}
@@
 
-The explosive material eventually condenses to form the next generation of stars, which will have a net increase in their neutron excess with respect to their predecessors.
-Since the Na-production rate is correlated with the neutron excess, an overall increase in the total sodium content \textit{and} Na-production rate between stellar generations is expected.
-Thus, an increase in the sodium abundance between generations of massive stars is a natural consequence of nucleosynthesis.
-Sodium content also becomes important for production of nickel during the {Sn\,\textsc{ii}} event (see Section \ref{sec:na-ni-relationship}) because $^{23}$Na is the only stable isotope produced in significant quantities during the C- or O-burning stages.
-A small fraction of $^{22}$Na is also forged through proton capture on $^{21}$Ne in the carbon shell, an effect which is enhanced by neutrinos spallating abundant elements like $^{16}$O and $^{20}$Ne, making free protons available for capture \citep{woosley;weaver_1995}.
-
-Oxygen depletion is likely the result of complete CNO burning within the stellar interior.
-The nucleosynthetic pathways that produce the {Na-O} anti-correlation are well known.
-However, the temperatures required to produce these patterns are not expected within the interiors of globular cluster stars.
-While the exact mechanism for which these conditions occur remains under investigation, we can describe the abundance variation as a simple oxygen depletion (or dilution) model with time.
-Through comparisons with existing globular clusters, we can still make inferences on the star-formation history of a system by measuring sodium and oxygen abundances in a sample of its stars.
-
-\citet{carretta;et-al_2009a} defined three components of stars exhibiting an inverse {Na-O} correlation within a population: primordial, intermediate, and extreme components.
+ %Thus, an increase in the sodium abundance between generations of massive stars is a natural consequence of nucleosynthesis.
+
+ %A small fraction of $^{22}$Na is also forged through proton-capture on $^{21}$Ne in the carbon shell, an effect which is enhanced by neutrinos spallating abundant elements like $^{16}$O and $^{20}$Ne, making free protons available for capture \citep{woosley;weaver_1995}.
+
+%\citet{carretta;et-al_2009a} defined three components of stars exhibiting an inverse {Na-O} correlation within a population: primordial, intermediate, and extreme components.
 The [Na/Fe] and [O/Fe] abundances for a given star define which component it belongs to.
-Primordial (first-generation) stars are those with sodium and oxygen abundances which are similar to field stars of the same metallicity.
+An intermediate component -- the second-generation of stars -- will have super-solar sodium abundances and demonstrate a slight depletion in oxygen content.
+Stars with {[O/Na]$ > -0.9$} are classified as belonging to the extreme component, a signature indicating long-lasting star-formation.
+
+%Primordial (first-generation) stars are those with sodium and oxygen abundances which are similar to field stars of the same metallicity.
 An intermediate component -- the second-generation of stars -- will have super-solar sodium abundances and demonstrate a slight depletion in oxygen content.
 The oxygen exhaustion rate is ultimately dependent on the star-formation history of the cluster environment.
-The intermediate population is sub-divided based on how much the sodium and oxygen abundances depart from the primordial population: stars with {[O/Na]$ > -0.9$\,dex} are classified as belonging to an extreme component of this {Na-O} pattern because they differ greatly from the primordial cluster abundance.
-The extreme O-depletion component has only been observed in a few clusters (preferentially more massive clusters with extended horizontal branches), indicating an long-lasting star-formation history in more massive clusters.
-
-It is clear that careful consideration must be given when inferring star-formation histories from observed stellar abundances.
-In addition to the normal care afforded for measuring elemental abundances from high-resolution spectroscopic data, attention must be given to telluric absorption, contamination from nickel transitions, as well as non-LTE and 3D effects when determining oxygen abundances.
-Furthermore, when characterising the oxygen depletion rate -- the strength of the {Na-O} anti-correlation in a given cluster -- it is vital to sample stars belonging to all three components, where possible.
-If only a primordial sample of stars in a globular cluster is observed, their [Na/Fe] and [O/Fe] abundances will be indistinguishable from field stars of a similar metallicity.
-In such a scenario, any inferred anti-correlation could equally be explained by intrinsic chemical scatter or observational uncertainties.
+The extreme O-depletion component has only been observed in a few clusters (preferentially more massive clusters with extended horizontal branches), indicating a long-lasting star-formation history in more massive clusters.
+
+%Careful consideration must be given when inferring star-formation histories from observed stellar abundances.
+Such inferences must be made with careful consideration.
+In addition to the normal care afforded for measuring elemental abundances from high-resolution spectroscopic data, attention must be given to telluric absorption, contamination from Ni\,\textsc{i}, as well as non-LTE and 3D effects when determining oxygen abundances.
+Furthermore, when characterising the oxygen depletion rate -- the strength of the {Na-O} anti-correlation in a globular cluster -- it is vital to sample, where possible, stars belonging to all three components \citep[primordial, intermediate and extreme, see][]{carretta;et-al_2009a}.
+If only a primordial sample of stars is observed, their [Na/Fe] and [O/Fe] abundances will be, by definition, indistinguishable from field stars of a similar metallicity.
+In such a scenario any inferred anti-correlation could equally be explained by small abundance variations or observational uncertainties.
+
+%Finally, one must exclude the possibility that a {Na-O} anti-correlation is being inferred from a composite sample of field stars with a fractional contribution of stars that were born in globular clusters.
+\citet{ramirez;et-al_2012} estimate at least 3\%$\pm$2\% of the local field stars in this metallicity regime were born in globular clusters.
 
 % [O/Fe], [Na/Fe]
-\begin{figure*}[t!]
-	\includegraphics[width=\textwidth]{./figures/aquarius-o-na-halo.pdf}
+\begin{figure}[t!]
+	\includegraphics[width=\columnwidth]{./figures/aquarius-o-na-halo.pdf}
 	\caption{Oxygen and sodium abundances for thick disc ($+$), thin disc ($\times$) and halo ($\circ$) stars from \citet{reddy;et-al_2006}, and globular cluster stars from \citet{carretta;et-al_2009a} (grey symbols).
-The Aquarius candidate abundances are also shown (\textbullet), illustrating how their [O/Fe], [Na/Fe] content is not dissimilar from galactic stars.
+The Aquarius stream stars are also shown (\textbullet), illustrating how their [O/Fe], [Na/Fe] content is not dissimilar from Galactic stars.
 Ambiguous thick disc/thin disc stars in \citet{reddy;et-al_2006} are marked with thick disc symbols ($+$), as are uncertain thick disc/halo stars with halo symbols ($\circ$).}
 	\label{fig:o-na}
-\end{figure*}
+\end{figure}
 
 \citet{wylie-de-boer;et-al_2012} measured sodium and oxygen abundances for four of their six Aquarius stream members.
-This research has four stars in common with the \citet{wylie-de-boer;et-al_2012} study, but sodium and oxygen measurements exist for only three stars intersecting both samples, as the data quality for {J223811-104126} in the \citet{wylie-de-boer;et-al_2012} was such that it prohibited oxygen determination.
-We have sodium and oxygen abundances for all of our stars, including {J223811-104126}, for which we ascertained a conservative upper limit from the {[O\,\textsc{i}]} lines of {${\rm [O/Fe]} < 0.5$\,dex}, and a abundance ratio of {$\mbox{[O/Fe]} = 0.14 \pm 0.08$} from the {O\,\textsc{i}} triplet lines.
-In Figures \ref{fig:o-na-clusters} and \ref{fig:o-na} we have plotted theses abundances, including the corrected value for {J223811-104126} rather than the upper limit.
+These measurements exist for only three stars common to both samples, as the data quality for {J223811-104126} in the \citet{wylie-de-boer;et-al_2012} was too low to permit oxygen measurements.
+We have measured sodium and oxygen abundances for all of our stars, which are plotted in Figures \ref{fig:o-na-clusters} and \ref{fig:o-na}.
+These figures employ the corrected [O/Fe] value for {J223811-104126} rather than a conservative upper limit (see Section \ref{sec:oxygen-abundances}).
 
@@
 
-The \citet{wylie-de-boer;et-al_2012} measurements indicate two stars with solar levels of [Na/Fe] -- identical to field star abundances for their metallicity -- and two stars with enhanced sodium content: {J223504-152834} and {J232619-080808}.
+The \citet{wylie-de-boer;et-al_2012} measurements show two stars with solar levels of [Na/Fe] -- identical to field star abundances for their metallicity -- and two stars with enhanced sodium content: {J223504-152834} and {J232619-080808}.
 We also find {J223504-152834} to be sodium-enhanced, whereas the second star in their study, {J232619-080808}, is not in our sample.
-We find the additional star not present in the \citet{wylie-de-boer;et-al_2012} sample, {C2306265-085103}, to be sodium enhanced to almost the same level of {J223504-152834} with {$\mbox{[Na/Fe]} = 0.26$\,dex}.
+We find the additional star not present in the \citet{wylie-de-boer;et-al_2012} sample, {C2306265-085103}, to be sodium-enhanced to almost the same level of {J223504-152834} with {$\mbox{[Na/Fe]} = 0.26$}.
 The sodium-enhanced stars exhibit no depletion of oxygen; their chemistry does not demonstrate a {Na-O} anti-correlation.
@@
 If the Aquarius stream is the result of a disrupted globular cluster, a large part of the picture must still be missing.
-Almost all of the Aquarius stream stars studied to date (either in this sample or the \citet{wylie-de-boer;et-al_2012} study), would be unambiguously classified as belonging to a `primordial' component, with chemistry indistinguishable from the thick disc or halo.
+Almost all of the Aquarius stream stars studied to date (either in this sample or the \citet{wylie-de-boer;et-al_2012} study), would be unambiguously classified as belonging to a ``primordial'' component, with chemistry indistinguishable from field stars.
 Identifying more Aquarius stream members belonging to the intermediate component with strong oxygen depletion, or perhaps members of an extreme component, would be convincing evidence for a {Na-O} anti-correlation and a globular cluster origin.
-Three stream stars identified to date (including two from this sample) might arguably be classified as members of an intermediate population, with only a slight enhancement in sodium and no oxygen-depletion.
+Three stream stars identified to date (including two from this sample) might tenuously be classified as members of an intermediate population, with only a slight enhancement in sodium and no oxygen-depletion.
 Recall our [Na/Fe] abundance ratios appear systematically higher in our standard stars when compared to the literature.
 Thus, if the strength of any {Na-O} relationship is to be used to vet potential disrupted hosts for the Aquarius stream, many more stream members will need to be identified and observed spectroscopically with high-resolution and high $S/N$.
-Currently, no evidence exists for a {Na-O} anti-correlation in the Aquarius stream.
+In the absence of such data, no evidence exists for a {Na-O} anti-correlation in the Aquarius stream.
 
@@
 
-An inverse relationship between sodium and oxygen is not the only chemical pattern commonly observed in globular clusters.
+%An inverse relationship between sodium and oxygen is not the only chemical pattern commonly observed in globular clusters.
 Although not ubiquitous to every system, many clusters exhibit an anti-correlation between aluminium and magnesium.
 This is perhaps unsurprising, given the nucleosynthetic pathways for these elements.
-In addition to the CNO cycle operating during hydrogen burning, the {Mg-Al} chain can also operate under extreme temperatures \citep[$T_6 \sim 3$\,K;][]{arnould;et-al_1999}.
-In these conditions, aluminium is produced by proton capture of magnesium, beginning with $^{24}$Mg to $^{25}$Al.
-The lifetime of $\beta$-decay to proton capture allows for the production of unstable $^{27}$Si through proton capture.
-Seconds later, the isotope decays to $^{27}$Al, completing the $^{27}$Si path of the Mg-Al cycle.
-The alternative process onwards from $^{25}$Al involves proton capture to $^{26}$Mg, but this process requires much higher temperatures ($T_6 \sim 7$\,K).
-In fact, although the process operates from temperatures above 30 million K, large {Mg-Al} abundance variations are not appreciable unless the temperatures reach $T_6 \sim 6.5$\,K.
-
-The Mg-Al cycle can explain the observed anti-correlation observed in some globular clusters, and most theoretical models predict such a pattern (\#get citations from Amanda).
-However, the locations where these extreme temperatures can be found are under some debate.
-Theoretical models indicate that the interiors of globular cluster stars do not reach sufficient temperatures for the {Mg-Al} cycle to produce the observed variations.
-Thus, although the processes for creating these chemical patterns are understood, the exact site and requisite conditions are lacking a full description.
+In addition to the CNO cycle operating during hydrogen burning, the {Mg-Al} chain can also operate under extreme temperatures \citep[$T \sim 8 \times 10^{6}\,$K;][]{arnould;et-al_1999}.
+In these conditions, aluminium is produced by proton-capture of magnesium, beginning with $^{24}$Mg to $^{25}$Al.
+The relative lifetime of $\beta$-decay to proton-capture allows for the production of unstable $^{27}$Si through proton-capture.
+Seconds later, the isotope decays to $^{27}$Al, completing the $^{27}$Si path of the Mg-Al chain.
+The alternative process onwards from $^{26}$Al involves proton-capture to $^{26}$Mg, but this process requires even higher temperatures ($T \sim 7 \times 10^{6}\,$K).
+
+The Mg-Al cycle can explain the observed anti-correlation observed in some globular clusters, and some AGB models can predict such a pattern (e.g., \citet{ventura;et-al_2011} but see nucleosynthesis yields from \citet{karakas;lattanzio_2007} and \citet{karakas_2010}).
+Thus, while the pathways for creating these chemical patterns are understood, the temperatures required to produce this chain are much higher than expected for stellar interiors, so the exact site and requisite conditions are lacking a full description.
 
 \citet{wylie-de-boer;et-al_2012} published magnesium and aluminium abundances for five stars in their Aquarius sample.
-No inverse correlation is present in their data, and their abundances are not dissimilar from field stars.
-Given that we do not find a {Na-O} anti-correlation, it is not surprising that a {Mg-Al} pattern is also not observed.
-The abundances tabulated in Table \ref{tab:program-star-abundances} vary slightly with those presented in the \citet{wylie-de-boer;et-al_2012} sample, but we also find no {Mg-Al} relationship.
-Two candidates are in good agreement: {J221821-183424} and {J223811-104126}, albeit the data quality in the \citet{wylie-de-boer;et-al_2012} study did not permit measuring aluminium for {J223811-104126}.
+No inverse correlation is present in their data; their abundances are indistinguishable from field stars.
+The [(Mg, Al)/Fe] abundance ratios tabulated in Table \ref{tab:program-star-abundances} are generally in agreement with the \citet{wylie-de-boer;et-al_2012} sample, and we also find no {Mg-Al} anti-correlation.
+Given that we do not find a {Na-O} anti-correlation, it is not surprising that a {Mg-Al} anti-correlation is also not observed.
+
+%Two candidates are in good agreement: {J221821-183424} and {J223811-104126}, albeit the data quality in the \citet{wylie-de-boer;et-al_2012} study did not permit the measurement of aluminium for {J223811-104126}.
 The other two stars common between studies are {C222531-145437} and {J223504-152834}, which we found to be the most abundant in both magnesium and aluminium.
-
-While \citet{wylie-de-boer;et-al_2012} find almost no scatter {($\pm0.02$\,dex)} in [Mg/Fe] for stars common to both studies, we find {C222531-145437} and {J223504-152834} to be almost {$+0.20$\,dex} higher than the rest of the sample.
-C222531-145437 is chemically distinct in other elements, too.
-The reason for this [Mg/Fe] discrepancy is not obvious, given the stellar parameters between the two studies agree well, with the previously discussed exception of metallicity.
-In particular, the stellar parameters agree excellently for {J223504-152834}, but we find {$\mbox{[Fe/H]} = -0.63$} instead of $-0.98$ as found by \citet{wylie-de-boer;et-al_2012}.
-It is worth noting that our measurement is in between that of \citet{williams;et-al_2011} and \citet{wylie-de-boer;et-al_2012}: \citet{williams;et-al_2011} find [M/H]$= -0.33$\,dex.
-Of the {Mg\,\textsc{i}} profiles measured, only two transitions are common to both line lists: {6318\,\AA} and {6319\,\AA}.
-The oscillator strengths differ between studies; in these two lines the $\log{gf}$ differs by $-0.24$ and {$-0.27$\,dex} respectively (our oscillator strengths are lower).
-This indicates that the difference in oscillator strengths may explain the $\sim{}$0.2\,dex offset in [Mg/Fe] between this study and that of \citet{wylie-de-boer;et-al_2012}.
 
@@
 	\includegraphics[width=\columnwidth]{./figures/aquarius-mg-al.pdf}
-	\caption{Magnesium and aluminium abundances for Aquarius stream candidates (\textbullet), and Milky Way halo/disc stars from \citet{reddy;et-al_2003} ($+$) and \citet{fulbright_2000} ($\circ$).
+	\caption{Magnesium and aluminium abundances for Aquarius stream stars (\textbullet), and Milky Way halo/disc stars from \citet{reddy;et-al_2003} ($+$) and \citet{fulbright_2000} ($\circ$).
 The chemically peculiar star, {C222531-145437}, is marked.}
@@
 
-The [Mg/Fe] and [Al/Fe] abundances found for the five Aquarius stars in this sample are illustrated in Figure \ref{fig:mg-al}.
-Our stars exhibit a strong positive relationship, with a best-fitting slope of ${{\rm [Al/Fe]} = 2.08\times\mbox{[Mg/Fe]} - 0.57}$, which is in part driven by {C222531-145437}.
-If we exclude this chemically peculiar star with enhanced [Al/Fe] relative to the rest of the sample, the slope decreases to {${\rm [Al/Fe]} = 0.96\times\mbox{[Mg/Fe]} - 0.16$}, a near 1:1 relationship.
+%The [Mg/Fe] and [Al/Fe] abundances found for the five Aquarius stream stars in this sample are illustrated in Figure \ref{fig:mg-al}.
+However it {\it is} surprising that we find such a strong positive relationship in [Mg/Fe] and [Al/Fe], with a best-fitting slope of ${{\rm [Al/Fe]} = 2.08\times\mbox{[Mg/Fe]} - 0.57}$.
+If we exclude the chemically peculiar star {C222531-145437}, the slope decreases to {${\rm [Al/Fe]} = 0.96\times\mbox{[Mg/Fe]} - 0.16$}, a near 1:1 relationship.
 Even when a {Mg-Al} anti-correlation is not detected in globular clusters, there is generally more scatter in [Al/Fe] at near-constant [Mg/Fe] \citep[e.g.
 see Figure \ref{fig:mg-al} or ][]{carretta;et-al_2009a}.
-To the author's knowledge of the literature no classical globular clusters exhibit a positive correlation, and nor is it expected in globular clusters.
+This is because Mg is much more abundant than Al, requiring only a small amount of Mg atoms to be synthesized to Al before the differences in $\log\epsilon{}$Al become appreciable, whilst the observed Mg abundance could remain within the uncertainties.
 
 % Mg-Al
-\begin{figure*}[t!]
-	\includegraphics[width=\textwidth]{./figures/aquarius-mg-al-cluster.pdf}
-	\caption{[Mg/Fe] and [Al/Fe] abundances for stars in 16 globular clusters from \citet{carretta;et-al_2009a} and for the five Aquarius stream candidates.
+%\begin{figure*}[t!]
+%	\includegraphics[width=\textwidth]{./figures/aquarius-mg-al-cluster.pdf}
+%	\caption{[Mg/Fe] and [Al/Fe] abundances for stars in 16 globular clusters from \citet{carretta;et-al_2009a} and for the five Aquarius stream stars.
 The inverse {Mg-Al} correlation is illustrated, most obviously in {NGC 2808} and {NGC 1904}.
 The strong positive correlation observed in Aquarius is in stark contrast with other classical globular clusters.}
-	\label{fig:mg-al}
-\end{figure*}
-
-A positive relationship between magnesium and aluminium can result from {Sn\,\textsc{ii}} contributions to the local interstellar medium.
-High-resolution observations of disc stars illustrate this correlation, demonstrating efficient {Sn\,\textsc{ii}} mixing.
-Some intermediate-mass ($\sim$4$M_\odot$) AGB models also contribute towards a positive correlation between aluminium and magnesium.
-Under extreme temperatures ($T_6 \sim 300$\,K), substantial $^{25}$Mg and $^{26}$Mg are produced by $\alpha$-capture onto $^{22}$Ne by the $^{22}$Ne($\alpha$,n)$^{25}$Mg and $^{22}$Ne($\alpha$,$\gamma$)$^{26}$Mg reactions respectively.
-Following deep dredge up, significant $^{25}$Mg and $^{26}$Mg is mixed into the photosphere, more so than the quantity of $^{26}$Al produced through the {Mg-Al} cycle.
-This dredge up process replenishes the Mg that is expensed during the {Mg-Al} pathway.
-Therefore, a positive relationship between magnesium and aluminium can occur if there has been significant contributions from intermediate mass AGB stars.
-
-An unrealistically high fraction of intermediate-mass AGB stars would be required to produce the same chemical signature of a single {Sn\,\textsc{ii}} event.
-Given the efficiency of chemical pollution following supernovae, the observed correlation in the thick disc is likely the result of {Sn\,\textsc{ii}} events.
-However, since the chemical enrichment environment of the Aquarius stream is unknown, we cannot exclude either possibility.
+%	\label{fig:mg-al}
+%\end{figure*}
+
+No classical globular clusters exhibit a positive correlation, and nor is such a pattern expected in globular clusters.
+However, a positive relationship between magnesium and aluminium can result from {SN\,\textsc{ii}} contributions to the local interstellar medium.
+Intermediate-mass ($\gtrsim$4$M_\odot$) AGB models can also contribute towards a positive correlation between aluminium and magnesium.
+Under extreme temperatures ($T \gtrsim 300 \times 10^{6}\,$K), substantial $^{25}$Mg and $^{26}$Mg are produced by $\alpha$-capture onto $^{22}$Ne by the $^{22}$Ne($\alpha$,n)$^{25}$Mg and $^{22}$Ne($\alpha$,$\gamma$)$^{26}$Mg reactions respectively \citep[e.g.,][]{karakas;et-al_2006}.
+Depending on uncertain numerical details of the stellar model, the third dredge-up can mix significant quantities of $^{25}$Mg and $^{26}$Mg into the photosphere, even more than the quantity of $^{26}$Al produced through the {Mg-Al} cycle.
+Therefore, a positive relationship between magnesium and aluminium can occur if there has been significant contributions from intermediate-mass AGB stars \citep[][but see results in \citet{ventura;et-al_2011}]{karakas;lattanzio_2003}.
+
+An unrealistically high fraction of intermediate-mass AGB stars would be required to produce the same chemical signature of a single {SN\,\textsc{ii}} event.
+Given the efficiency of chemical mixing following supernovae, the observed positive {Mg-Al} correlation in the thick disc is likely the result of {SN\,\textsc{ii}} events.
 Distinguishing between these processes observationally requires careful measurements of magnesium isotope abundances $^{24}$Mg (indicating supernovae mixing), $^{25}$Mg and $^{26}$Mg (suggesting significant AGB contribution), which is not possible given our $S/N$ or spectral resolution.
+In either scenario, we can summarise that the strong Mg-Al relationship provides additional chemical evidence against a globular cluster scenario for the Aquarius stream, and the chemistry is suggestive of Milky Way disc stars.
 
@@
 
-% need to say about [alpha/fe] and [na/fe] with distance
 Detailed chemical studies of nearby disc stars have noted a correlation with [Na/Fe] and [Ni/Fe] abundance ratios.
@@
 Interestingly, the authors noted that stars at larger galactocentric radii were most deficient in these elements.
-\citet{fulbright_2000} saw a similar signature: stars with low [Na/Fe] were only found at large {($R_\odot > 20$\,kpc)} distances.
+\citet{fulbright_2000} saw a similar signature: stars with low [Na/Fe] were only found at large {($R_{\rm GC} > 20$\,kpc)} distances.
 \citet{nissen;schuster_1997} proposed that since the outer halo is thought to have been largely built up by accretion, then the {Na-Ni} pattern may be a chemical indicator of merger history within the galaxy.
@@
 With additional data from \citet{nissen;schuster_2011}, the {Na-Ni} relationship was found to be slightly steeper than originally proposed.
-The pattern exists only for stars with {$-1.5 < \mbox{[Fe/H]} < -0.5$\,dex}, and is not seen in metal-poor dSph stars, providing a potentially useful indicator for investigating chemical evolution.
-However, it is crucial to note that although there are only a few dSph stars in the $-1.5 < \mbox{[Fe/H]} < -0.5$ metallicity regime with [Na/Fe], [Ni/Fe] measurements, they agree reasonably well with the galactic trend.
-
-The correlation between sodium and nickel content is the nucleosynthetic result of neutron capture in massive stars.
-As previously discussed, the total Na abundance is controlled by the neutron excess, which limits the production of $^{58}$Ni during {Sn\,\textsc{ii}} events.
+The pattern exists only for stars with {$-1.5 < \mbox{[Fe/H]} < -0.5$}, and is not seen in metal-poor dSph stars \citep{venn;et-al_2004}, providing a potentially useful indicator for investigating chemical evolution.
+However, it is crucial to note that although there are only a few dSph stars in the $-1.5 < \mbox{[Fe/H]} < -0.5$ metallicity regime with [Na/Fe] and [Ni/Fe] measurements, they agree reasonably well with the Galactic trend.
+
+The correlation between sodium and nickel content is the nucleosynthetic result of neutron-capture in massive stars.
+As previously discussed, the total Na abundance is controlled by the neutron excess, which limits the production of $^{58}$Ni during {SN\,\textsc{ii}} events.
 When the inevitable supernova begins, the core photodissociates into neutrons and protons, allowing the temporary creation of $^{56}$Ni before it decays to $^{56}$Fe.
@@
 As $^{23}$Na is a relatively plentiful neutron source with respect to other potential sources (like $^{13}$C), the post-supernova $^{58}$Ni abundance is driven by the pre-explosion $^{23}$Na content.
-Recall that the total Na production primarily depends on the neutron excess.
 Thus, through populations of massive stars undergoing C-burning, a positive correlation between sodium and nickel can be expected.
-
-%As \citet{Venn;et-al_2004} point out, this pattern can be altered from contributions by type Ia supernova.
 
@@
 	\includegraphics[width=\columnwidth]{./figures/gc-dsph-na-ni.pdf}
-	\caption{[Na/Fe] and [Ni/Fe] for Aquarius stream candidates and for globular cluster, dSph, and field (halo/disc) stars.
-The \citet{nissen;schuster_2011} plotted sample included halo stars, $\alpha$-low and $\alpha$-high disc members.
+	\caption{[Na/Fe] and [Ni/Fe] for Aquarius stream stars and for globular cluster, dSph, and field (halo/disc) stars.
+Stars from the most representative dSph galaxy, Fornax, are shown as downward triangles ($\blacktriangledown$).
+The \citet{nissen;schuster_2011} plotted sample included halo stars, as well as low- and high-$\alpha$ disc members.
 As noted by \citet{nissen;schuster_1997,nissen;schuster_2011}, a positive Na-Ni relationship exists for field stars, with dSph members exhibiting strong depletion in both elements and globular cluster stars consistently showing an enhancement.
@@
 
-Stars originating in dwarf spheroidal galaxies and globular clusters have very different chemical enrichment environments.
+Stars originating in dSph galaxies and globular clusters have very different chemical enrichment environments.
 Consequently, both types of systems exhibit chemistry that reflects their nucleosynthetic antiquity.
-Dwarf spheroidal stars do not demonstrate enhanced sodium or nickel content with respect to iron, as there has been a relatively small linage of massive stars undergoing supernova.
-In contrast, globular cluster stars do have elevated [Na/Fe], [Ni/Fe] signatures.
-This sharp contrast between dwarf spheroidal and globular cluster star chemistry is illustrated in Figure \ref{fig:na-ni}.
+Stars in dSphs do not demonstrate enhanced sodium or nickel content with respect to iron, as there has been a relatively small lineage of massive stars undergoing supernova.
+In contrast, globular cluster stars do have elevated [Na/Fe] and [Ni/Fe] signatures.
+This sharp contrast between dSph and globular cluster star chemistry is illustrated in Figure \ref{fig:na-ni}.
 Given the extended star formation within the Milky Way disc, globular cluster stars and disc stars are indiscernible in the Na/Ni plane: they both show an extended contribution of massive stars.
-The most that can be inferred from the Na, Ni abundances of Aquarius stream stars is that their enrichment environment is less like a dSph galaxy, and more representative of either a globular cluster, or the disc of the Milky Way.
-
-\subsection{The Distinctiveness of C222531-145437}
-
-% for a high mass AGB
-%Sr/Ba ~ 0.4
-
-C222531-145437 exhibits peculiar chemical abundances compared to the rest of the Aquarius candidates.
-In almost every element with respect to iron, {C222531-145437} is distinct from the other Aquarius candidates.
-It is over-abundant in light refractory elements, weak and heavy $s$-process elements, with a strong barium abundance of {$\mbox{[Ba/Fe]} = 0.68$\,dex}.
+The most that can be inferred from the Na and Ni abundances of Aquarius stream stars is that their enrichment environment is less like a dSph galaxy, and more representative of either a globular cluster, or the Milky Way disc.
+
+\subsection{The Chemically Peculiar Star C222531-145437}
+
+%[TODO] Check this star in context of Verne & Smith for omega en
+% --> Everything matches against D'Orazi (2011), Marino (2011), and Verne & Smith (2000) with the exception of Cu. But, it appears our Cu abundances are higher than the halo, too.
+
+In almost every element with respect to iron, {C222531-145437} is distinct from the other Aquarius stream stars.
+It is over-abundant in light refractory  and neutron-capture elements, with a high barium abundance of {$\mbox{[Ba/Fe]} = 0.68$}.
 This value is well in excess of the halo ({$\mbox{[Ba/Fe]} \sim 0.0$}) -- and our other Aquarius stream stars -- which vary between $-$0.02 to {0.15\,dex}.
 
-Although no radial velocity variations were observed between exposures, it is possible that an unseen AGB star has contributed to the surface abundances of C222531-145437.
-The abundances of heavy elements produced by AGB stars have a high dependence on the overall metallicity and mass of the AGB star.
-Low-mass ($\lesssim{}3M_\odot$) AGB stars produce high fractions of heavy $s$-process elements compared to their weak $s$-process counterparts.
-As such, [Ba/Y] is a useful indicator when considering contributions from a low-mass AGB companion.
-For C222531-145437, ${{\rm [Ba/Y]} = -0.17}$, which is much lower than expected if a low-mass AGB star was the dominant reason for the heavy element enhancements ([Ba/Y] $\sim$ 0.5).
-Intermediate-mass (3-5$M_\odot$) AGB stars also cannot explain the abundances for C222531-145437: using recently computed intermediate-mass AGB yields for 3-5$M_\odot$ for a star of [Fe/H] = $-1.2$ (Fishlock, Karakas et al., forthcoming) we find the expected surface abundances do not match the observations.
-If mass transfer from an AGB companion is ongoing or has occurred very recently, non-negligible amounts of technitium is produced, and remains visible before it decays over $\sim$100\,Myr$^{\rm [citation\phd{}needed]}$.
-We saw no technitium absorption feature at the 4049.11, 4238.19 or 4297.06\,{\AA} wavelengths in the spectrum of C222531-145437.
-Therefore, we find no reason to suspect the heavy element enhancement in C222531-145437 is the result of an AGB companion.
-
-High $s$-process enhancements have been noted for a few disrupted globular clusters that exhibit a wide metallicity range.
-Most notably $\omega$-Centurai \citep{majewski;et-al_2012} and M22 \citep{marino;et-al_2011}.
-Like the Aquarius co-moving group, both clusters are relatively close to the sun: {$R_\odot = 5.2$\,kpc} and {3.2\,kpc}, respectively.
-M22 has a mean metallicity of {$\mbox{[Fe/H]} \sim -1.7$}, varying between {$-2.0 < \mbox{[Fe/H]} < -1.6$\,dex}.
-Since {C222531-145437} has a metallicity of {$\mbox{[Fe/H]} = -1.26$\,dex}, it is unlikely to be associated with M22.
-However, the high barium content and overall metallicity of {C222531-145437} ({$\mbox{[Fe/H]} = -1.26$}) suggests there may be an association with $\omega$-Centurai.
-
-$\omega$-Centurai has a retrograde orbit with low inclination.
+Here we discuss the possibility that an unseen companion has contributed to the surface abundances of C222531-145437.
+Although no radial velocity variations were observed between exposures, we do not have a sufficient baseline to detect such variation.
+The abundances of heavy elements produced by AGB stars have a high dependence on the initial metallicity and mass.
+Low-mass ($\lesssim{}3M_\odot$) AGB stars produce high fractions of heavy $s$-process elements compared to their light $s$-process counterparts.
+As such, [Ba/Y] is a useful indicator for considering contributions from a low-mass AGB companion.
+For C222531-145437, ${{\rm [Ba/Y]} = -0.17}$, which is much lower than expected if a low-mass AGB star was responsible for the heavy element enhancements ([Ba/Y] $\sim$ 0.5 as shown in Figure \ref{fig:ba-y}; see also \citet{cristallo;et-al_2009}).
+If mass transfer from an AGB companion has occurred very recently, non-negligible amounts of technetium are produced, remaining visible before it decays over $\sim$100\,Myr \citep{brown;et-al_1990,van_eck_jorrissen_1999, uttenthaler;et-al_2011}.
+We saw no technetium absorption at the 404.9, 423.8 or 429.7\,nm in the spectrum of C222531-145437.
+Intermediate-mass (3-5$M_\odot$) AGB stars also cannot explain the abundances for C222531-145437: using recently computed intermediate-mass AGB $s$-process yields for 3-5$M_\odot$ for a star of [Fe/H] = $-1.2$ (C.
+Fishlock, in preparation) the resulting surface abundances do not match the observations.
+Therefore, we find no reason to suspect the heavy element enhancement in C222531-145437 is the result of mass transfer from an AGB companion.
+
+Stars in $\omega$-Centauri show large over-abundances of $s$-process elements compared to the Galaxy \citep{norris;da_costa_1995,stanford;et-al_2010}.
+M22 also hosts an $s$-process rich population \citep{marino;et-al_2011}.
+Like the Aquarius co-moving group, both clusters are relatively close to the Sun: {5.2\,kpc} and {3.2\,kpc}, respectively.
+M22 has a mean metallicity of {$\mbox{[Fe/H]} \sim -1.7$} and a range between {$-2.0 < \mbox{[Fe/H]} < -1.6$\,dex}, making an association between {C222531-145437} and M22 unlikely.
+Similarly, {C222531-145437} is unlikely to be associated with the metal-rich Argus association \citep[IC 2391;][]{de_silva;et-al_2013}, which also shows large enhancement in $s$-process abundances.
+Other groups have identified field stars enriched in $s$-process elements, which have generally been associated as tidal debris from $\omega$-Centuari \citep{wylie-de-boer;et-al_2010,majewski;et-al_2012}.
+The high $s$-process abundance ratios and overall metallicity of {C222531-145437} ({$\mbox{[Fe/H]} = -1.22$}) suggests this may be an additional tidal remnant.
+
+% [TODO] How do these abundances match omega Cen core RGB stars?
+
+$\omega$-Centauri has a retrograde orbit with low inclination.
 Many groups simulating this orbit have predicted retrograde tidal debris to occur near the Solar circle \citep{dinescu_2002,tsuchiya_2003,tsuchiya_2004,bekki;freeman_2003}.
-Subsequent searches for $\omega$-Centurai debris in the solar neighbourhood have led to tantalising signatures of debris.
-From over 4,000 stars targeted by \citet{da_costa;coleman_2008}, only six candidate debris members were recovered.
-More recently, \citet{majewski;et-al_2012} presented data from the Grid Giant Star Survey (GGSS), an all-sky search looking for metal-poor giant stars.
-From their data they identified 12 stream candidates.
-Although this scarcity is consistent with tidal stripping occurring long ago, it is perhaps worrying that searches for stripped stars closer to $\omega$-Centurai itself have been even less successful.
-
-In addition to presenting new stream candidates, \citet{majewski;et-al_2012} performed 4,050 simulations in order to predict likely locations for $\omega$-Centurai tidal debris.
+Subsequent searches for $\omega$-Centauri debris in the Solar neighbourhood have led to tantalising signatures of debris.
+From over 4,000 stars targeted by \citet{da_costa;coleman_2008}, only six candidate debris members were recovered, consistent with tidal stripping occurring long ago.
+Using data from the Grid Giant Star Survey (GGSS), an all-sky search looking for metal-poor giant stars, \citet{majewski;et-al_2012} identified 12 stream candidates.
+In addition, \citet{majewski;et-al_2012} performed 4,050 simulations in order to predict likely locations for $\omega$-Centauri tidal debris.
 The results of their simulation are replicated in Figure \ref{fig:omega-cen-tidal-debris}, where the location of {C222531-145437} is also shown.
-Interestingly, the velocity and position of {C222531-145437} line up almost precisely where \citet{majewski;et-al_2012} predict a high probability of tidal debris.
+The velocity and position of {C222531-145437} align almost precisely where \citet{majewski;et-al_2012} predict a high probability of tidal debris.
+More interestingly, the angular momentum and orbital energy for {C222531-145437} (Figure \ref{fig:Lz-E}) matches excellently for $\omega$-Centurai cluster stars as well as its previously identified tidal remnants \citep{wylie-de-boer;et-al_2010}.
+The chemical and phase-space information strongly suggests that {C222531-145437} is associated with the remnant of tidal stripping that occurred as the proto-$\omega$-Centauri fell into the Galaxy \citep{bekki;freeman_2003}.
 
@@
 	\includegraphics[width=\columnwidth]{./figures/omegacen_tidaldebris.pdf}
-	\caption{Panel (a) shows the distribution of giant stars in the GGSS \citep{majewski;et-al_2012} in galactic longitude and $V_{\rm GSR}/cos(b)$ after excluding stars with $|b| > 60\,^\circ$.
-Stars from the GGSS sample believed to be $\omega$Cen tidal debris are shown in green shading.
-Red points are stars from the GGSS sample with abundances that follow the $\omega$Cen [Ba/Fe]--[Fe/H] pattern.
-Blue points are those with echelle spectra that do not follow this trend.
+	\caption{Panel (a) shows the distribution of giant stars in the GGSS \citep{majewski;et-al_2012} in Galactic longitude and $V_{\rm GSR}/cos(b)$ after excluding stars with $|b| > 60^\circ$.
+Stars from the GGSS sample believed to be $\omega$-Centauri tidal debris are shown in green shading.
+Red points are stars from the GGSS sample with abundances that follow the $\omega$-Centauri [Ba/Fe]--[Fe/H] pattern.
+Blue points are those with high-resolution spectra that do not follow this trend.
 Grey shading highlights other potential halo substructures from their study.
-Panel (b) shows the probability distribution of $\omega$Cen tidal debris from 4,050 simulations.
-The $\omega$Cen core is shown as a green cross and the cyan star represents {C222531-145437}, falling almost precisely where a relatively high probability of $\omega$Cen tidal debris is expected.}
+Panel (b) shows the probability distribution of $\omega$-Centauri tidal debris from 4,050 simulations.
+The $\omega$-CenCentauri core is shown as a green cross and the cyan star represents {C222531-145437}, falling almost precisely where a relatively high probability of $\omega$-Centauri tidal debris is expected.}
 	\label{fig:omega-cen-tidal-debris}
@@
 
-Perhaps the most striking evidence for an association between {C222531-145437} and $\omega$-Centurai is in its chemistry.
-Figure \ref{fig:omega-cen-barium} demonstrates the [Ba/Fe] abundance for $\omega$-Centurai stars compared to that of the galactic halo.
-A steep barium enhancement is present, which is unique to the globular clusters $\omega$-Centurai and M22.
-We note that although high $s$-process enrichment is present in other systems \citep[IC 2391, the Argus association;][]{de_silva;et-al_2013}, these systems are have metallicities near solar and are unlikely to be associated with {C222531-145437}.
-Furthermore, \textit{all other elemental abundances} measured here precisely match with those presented by \citet{marino;et-al_2011} for $\omega$-Centurai RGB stars.
+% Check this smith and dorazi paper 
+%Furthermore, \textit{all other elemental abundances} measured here precisely match with those presented by \citet{smith;dorazi_2000} for $\omega$-Centauri RGB stars.
 
@@
 	\includegraphics[width=\columnwidth]{./figures/omegaCen-c222531.pdf}
-	\caption{[Fe/H] and [Ba/Fe] for halo/disc stars (black) from \citet{fulbright_2000,reddy;et-al_2003,reddy;et-al_2006} and $\omega$-Centurai RGB stars (grey) from \citet{francois;et-al_1988,smith;et-al_2000,marino;et-al_2011}.
-Similar trends are observed for other heavy elements in $\omega$-Centurai members.
-The candidate we associate with $\omega$-Centurai tidal debris, C222531-145437, is marked in cyan.}
+	\caption{[Fe/H] and [Ba/Fe] for halo/disc stars (black) from \citet{fulbright_2000,reddy;et-al_2003,reddy;et-al_2006} and $\omega$-Centauri RGB stars (grey) from \citet{francois;et-al_1988,smith;et-al_2000,marino;et-al_2011}.
+Similar trends are observed for other heavy elements in $\omega$-Centauri members.
+The candidate we associate with $\omega$-Centauri tidal debris, C222531-145437, is marked in cyan.}
 	\label{fig:omega-cen-barium}
@@
 
-The chemical peculiarity of {C222531-145437} suggests that it is distinct from the Aquarius co-moving group.
-The high $s$-process enrichment is similar to that observed in $\omega$-Centurai stars, and the overall metallicity {($\mbox{[Fe/H]} = -1.26$)} agrees excellently with the mean metallicity of a known sub-population within $\omega$-Centurai.
-Moreover, the position and velocity for {C222531-145437} precisely coincide with the most likely predictions for tidal debris from $\omega$-Centurai, and the angular momentum and orbital energy precisely matches those found for $\omega$-Centurai by \citet{dinescu;et-al_1999}.
-The chemical and phase-space information indicates that {C222531-145437} is clearly associated with the disrupted globular cluster $\omega$-Centurai.
-
-In their original discovery paper, \citet{williams;et-al_2011} attempted to exclude possible known progenitors for the Aquarius stream.
-On the basis of metallicity, distance, proper motions, transverse velocities and orbital energies, the authors were able to exclude all known Milky Way satellites, with the notable exception of $\omega$-Centurai.
-Although the Aquarius stream metallicity distribution we find is not dissimilar from a known sub-population in $\omega$-Centurai, the individual chemical abundances are quite distinct.
+%The chemical peculiarity of {C222531-145437} suggests that it is distinct from the Aquarius co-moving group.
+The high $s$-process enrichment is similar to that observed in $\omega$-Centauri stars, and the overall metallicity {($\mbox{[Fe/H]} = -1.26$)} agrees excellently with the mean metallicity of a known sub-population within $\omega$-Centauri.
+Moreover, the position and velocity for {C222531-145437} precisely coincide with the most likely predictions for tidal debris from $\omega$-Centauri, and the angular momentum and orbital energy precisely matches those found for $\omega$-Centauri by \citet{dinescu;et-al_1999}.
+The chemical and phase-space information strongly suggests that {C222531-145437} is associated with the remnant of tidal stripping that occurred as the proto-$\omega$-Centauri fell into the Galaxy \citep{bekki;freeman_2003}.
+
+In the Aquarius stream discovery paper, \citet{williams;et-al_2011} attempted to exclude possible known progenitors for the Aquarius stream.
+On the basis of metallicity, distance, proper motions, transverse velocities and orbital energies, the authors were able to exclude all known Milky Way satellites with the notable exception of $\omega$-Centauri.
+Although the Aquarius stream metallicity distribution is not dissimilar from a known sub-population in $\omega$-Centauri, the individual chemical abundances are quite distinct.
 The strong $s$-process enhancement with overall metallicity is not observed in the rest of our sample.
-Thus, with the exception of {C222531-145437}, the Aquarius members do not have chemistry that is synonymous with $\omega$-Centurai tidal debris.
-
-\subsection{Disrupted disc/Halo Stars -- Signature of a Disc-Satellite Interaction?}
-Since the Aquarius stream is kinematically coherent, the default assumption is that the co-moving group has accreted onto the Milky Way from a tidally disrupted satellite.
-The stream candidates presented here are slightly enhanced in sodium and nickel, suggesting that if a satellite parent ever existed then its chemical enrichment environment was more like a globular cluster than a dSph galaxy.
-Based on a lack of $\alpha$-enhancement and increased [Na/Fe], [Ni/Fe] abundance ratios we exclude the possibility that the Aquarius stream has resulted from a disrupted dwarf galaxy.
-If the progenitor is a disrupted globular cluster, and most of our candidates are members, then the parent has a wider metallicity distribution than most globular clusters.
-
-However we find no chemical evidence for a globular cluster origin.
-If the Aquarius co-moving group is a relic of a disrupted globular cluster then high-resolution, high $S/N$ spectra for the entire stream may be required before chemical patterns reminiscent of classical globular clusters becomes apparent.
-As it stands, the Aquarius group appears chemically indistinguishable from thick disc/halo stars.
-
+Thus, with the exception of {C222531-145437}, the Aquarius members do not have a chemistry that is synonymous with $\omega$-Centauri tidal debris.
+It will be most interesting to learn how many other members of the Aquarius stream are tidal remnants of $\omega$-Centauri, given the frequency of these objects is quite low \citep[e.g.
+see][]{da_costa;coleman_2008,majewski;et-al_2012}.
+
+\subsection{Disrupted Disc/Halo Stars -- Signature of a Disc-Satellite Interaction?}
+
+%The stream members presented here are slightly enhanced in sodium and nickel, suggesting that if a satellite parent ever existed then its chemical enrichment environment was more like a globular cluster than a dSph galaxy.
+Stars currently present in existing dSph galaxies with metallicities similar to the Aquarius stream generally lack $\alpha$-enhancement, contrary to what is observed in the Aquarius stream.
+
+% When coupled with the observations of increased [Na/Fe] and [Ni/Fe] abundance ratios, this argues against the possibility that the Aquarius stream has resulted from a disrupted dSph like those that still exist today.
+If the progenitor is a disrupted globular cluster, and most of our candidates are members, then the parent has a wider metallicity distribution than almost every known globular cluster.
+
+Since the Aquarius stream is kinematically coherent, it has been assumed that the co-moving group has been accreted onto the Milky Way from a tidally disrupted satellite.
+The chemical abundances presented in this study do not favour an accretion scenario from a globular cluster or a dSph; there is conflicting evidence for either hypothesis.
+As it stands, the co-moving group  appears chemically indistinguishable from thick disc/halo stars.
 These results force us to consider other scenarios that may replicate the observations.
-In addition to the Aquarius group not being chemically coherent, there is an unusually wide spread in the velocity distribution.
-Generally a stellar stream is considered kinematically `cold' when its velocity dispersion is $\lesssim 8$\,km s$^{-1}$.
-We find the velocity dispersion from five members to near $\sim$30\,km\,s$^{-1}$, consistent with the dispersion of 27\,km s$^{-1}$ reported by \citet{williams;et-al_2011} when all stream members are included.
-Hypotheses to explain the Aquarius co-moving group must reconcile this wide velocity dispersion.
-
-There are other co-moving groups in the Milky Way that were initially considered as tidal tails from disrupted satellites that are now explainable as signatures of galaxy formation that are not specific accretion events.
+
+The Aquarius stream has an unusually wide intrinsic velocity distribution.
+Generally a stellar stream is considered kinematically ``cold'' when its velocity dispersion is $\lesssim 8$\,km s$^{-1}$.
+We find the velocity dispersion from five members to be $\sim$30\,km\,s$^{-1}$, consistent with \citet{williams;et-al_2011}.
+Hypotheses invoked to explain the Aquarius co-moving group must account for the high velocity dispersion.
+
+There are other co-moving groups in the Milky Way that were initially considered as tidal tails from disrupted satellites, that are now explainable as signatures of galaxy formation that are not specific accretion events.
 Like the Aquarius group, the Hercules moving group is significantly offset from the bulk of the observed velocity distribution.
 Members of the Hercules group exhibit a wide range of metallicities and ages \citep{bensby;et-al_2007, bovy;hogg_2010}.
-The observations are well replicated in simulations by stars in the outer disc resonating with the bar in the central region of the Milky Way \citep{dehnen_2000,fux_2001}, and strong predictions are made for disc velocity distributions that would lend further weight to this hypothesis \citep{bovy_2010}.
-The Canis Major stellar over-density was also first considered to be an accretion feature from the Canis Major dwarf spheroidal galaxy \citep{martin;et-al_2004}.
-However, \citet{momany;et-al_2004} demonstrate the star counts, proper-motions, photometry and kinematics of the `accreted feature' can be easily explained by the warp and flare in the outer thick disc.
+Furthermore, Hercules group stars have [X/Fe] abundance ratios at a given [Fe/H] that are {\it not} substantially different from the thin or thick disk.
+The Hercules group kinematics are well replicated in simulations by stars in the outer disc resonating with the bar in the central region of the Milky Way \citep{dehnen_2000,fux_2001}, and strong predictions are made for disc velocity distributions that would lend further weight to this hypothesis \citep{bovy_2010}.
+The Canis Major stellar over-density was also first considered to be an accretion feature from the postulated Canis Majoris dSph galaxy \citep{martin;et-al_2004}.
+However, \citet{momany;et-al_2004} demonstrate that the star counts, proper-motions, photometry and kinematics of the ``accreted feature'' can be easily explained by the warp and flare in the outer thick disc.
 The Monoceros ring \citep{newberg;et-al_2002,juric;et-al_2008} is perhaps another example of such an occurrence, as similar features naturally emerge as a consequence of galaxy-satellite interactions \citep{purcell;et-al_2011}, which has prompted considerable discussion \citep{lopez-corredoira;et-al_2012}.
-It is clear that not all significant deviantly kinematic groups are evidence of accretion or tidal tails: in many scenarios a galactic origin is more likely, and simpler.
+It is clear that not all kinematic groups are attributable to accretion events; in many scenarios a galactic origin is more likely, and simpler.
 
@@
 We hypothesise that the Aquarius group is the result of displaced stars from a perturbation in the thick disc.
-That is, the stars are galactic in origin but have been displaced by a disc-satellite interaction.
+That is, the stars are Galactic in origin but have been displaced by a disc-satellite interaction.
 Minor mergers can significantly disrupt the host galaxy \citep{villalobos;helmi_2008}, producing extended spatial and kinematic structure in the process.
-\citet{minchev;et-al_2009} proposed that such a perturbation would cause a galactic `ringing' effect in the neighbourhood surrounding the merger site, analogous to the resulting interference pattern from a stone falling in water and propagating outwards.
-Stars move closer together in constructive interference nodes, a signature which is observable in the velocities and orbits of nearby stars.
-This signature is most prominent  in the $u$-$v$ velocity plane as concentric circles \citep{gomez;et-al_2012}, and dissolves over time (a few Gyr, depending on the mass of the perturber).
-After the $u$--$v$ velocity signature dissipates, a clear signature in angular momentum and orbital energy ($L_Z$, $E$) persist for long periods following the merger \citep[e.g.
+\citet{minchev;et-al_2009} proposed that such a perturbation would cause a galactic ``ringing'' effect in the neighbourhood surrounding the merger site, analogous to the resulting compression wave propagating outwards from a stone falling in water.
+Stars move closer together in the wave peak, a signature which is observable in the velocities and orbital motions of nearby stars.
+This signature is most prominent in the $U$--$V$ velocity plane as concentric circles \citep{gomez;et-al_2012}, and dissolves over time (a few gigayear, depending on the mass of the perturber).
+After the $U$--$V$ velocity signature dissipates, a clear signature in angular momentum and orbital energy ($L_Z$, $E$) persists for long periods following the merger \citep[e.g.
 see][]{gomez;et-al_2012}.
 
-Through simulations of Milky Way-Sagittarius simulations, \citet{purcell;et-al_2011} found that the disc-satellite interactions can explain ringing perturbations within the disc.
-Additionally, \citet{widrow;et-al_2012} and \citet{gomez;et-al_2012b} independently observed these phenomena -- a `wavelike perturbation', as it was described by Widrow -- in the SDSS and SEGUE catalogues.
+Through Milky Way-Sagittarius simulations, \citet{purcell;et-al_2011} found that these disc-satellite interactions can explain ringing perturbations within the disc.
+Additionally, \citet{widrow;et-al_2012} and \citet{gomez;et-al_2012b} independently observed these phenomena -- a {\it``wavelike perturbation''}, as Widrow described -- in the SDSS and SEGUE catalogues.
 More recently, \citet{gomez;et-al_2013} proposed that these patterns were induced by the Sagittarius dSph interacting with the disc.
 Their simulations reproduce the observed north-south asymmetries and vertical wave-like structure, and show that the amplitude of these oscillations is strongly dependent on galactocentric distance.
-Combined with the oscillating vertical motions with the $u$--$v$ velocity pattern, corrugated waves are observed as a result of the interaction.
+Combined with the oscillating vertical motions with the $U$--$V$ velocity pattern, corrugated waves are observed as a result of the interaction.
 
@@
 Thus, resultant oscillations following a disc-satellite interaction can satisfactorily explain the existence of the Aquarius co-moving group.
-We do not observe a distinct coherence in the $u$--$v$ velocity plane in our data, but the angular momentum and orbital energies for Aquarius members qualitatively reproduces the theoretically predicted pattern by \citet{gomez;et-al_2012}.
-The extent and gradient of this $L_Z$--$E$ signature is dependent on the mass of the perturber, and the time since infall.
-Although our sample size is minute -- and the sample size would still be small even if all Aquarius members had reliable orbits -- the fact that we see no $u$--$v$ velocity coherence is consistent with the observed $L_Z$--$E$ pattern: signatures in the $L_Z$--$E$ plane become more extended (Figure \ref{fig:toombre}) over time as the $u$--$v$ signature dissipates.
-This is consistent with a disc-satellite interaction occurring in the disc approximately a few Gyr ago.
-
-The Aquarius co-moving group resides at a low latitude ($b \approx - 55\,^\circ$) and with a radial distance of up to $\sim$5\,kpc for some stars, the stars are slightly out of the plane.
+We do not observe a distinct coherence in the $U$--$V$ velocity plane in our data, but the angular momentum and orbital energies for Aquarius members qualitatively reproduces the theoretically predicted pattern by \citet{gomez;et-al_2012} in a retrograde direction.
+The extent and gradient of this $L_Z$--$E$ signature is dependent on the mass of the perturber and the time since infall.
+Although our sample size is minute -- and the sample size would still be small even if all Aquarius members had reliable orbits -- the fact that we see no $U$--$V$ velocity coherence (Figure \ref{fig:toombre}) is consistent with the observed $L_Z$--$E$ pattern: signatures in the $L_Z$--$E$ plane (Figure \ref{fig:Lz-E}) become more extended over time as the $U$--$V$ signature dissipates.
+This is consistent with a disc-satellite interaction occurring in the disc approximately a few gigayear ago.
+
+The Aquarius co-moving group resides at a an intermediate latitude ($b \approx -55^\circ$) and with a radial distance of up to $\sim$5\,kpc for some stars, the stars are slightly out of the plane.
 This is not inconsistent with a disc-satellite interaction.
 \citet{gomez;et-al_2013} find that a significant fraction of the total energy goes into vertical perturbations.
-While the mean vertical distance $\langle{}Z\rangle$ in their simulations are near zero, this is an average of disc particles at all plane heights, and the dispersions around $\langle{}Z\rangle$ are very large (F.
+While the mean vertical distance $\langle{}Z\rangle$ in their simulations are near zero, this is an average of disc particles at all plane heights -- positive and negative -- and the dispersions around $\langle{}Z\rangle$ are very large (F.
 G{\'o}mez, private communication, 2013).
@@
 % who is the perturber?
-If the Aquarius group is a feature of a disc-satellite interaction, the perturber must have a mass on the order of a large globular cluster or a dSph to produce the residual pattern in orbital energy and angular momentum.
-The Sagittarius dSph galaxy is an obvious candidate, but $\omega$-Centurai is also a possible perturber.
-We identify {C222531-145437} as tidal debris from $\omega$-Centurai, and its location overlaps with the apocenter of $\omega$-Centurai's orbit.
-In addition, its velocity matches precisely with simulations of tidal debris by \citet{majewski;et-al_2012}.
-Thus, perhaps $\omega$-Centurai disrupted galactic stars as it passed through the plane, adding to any other oscillating modes rippling through the disc, resulting in what we now observe as the Aquarius co-moving group.
+If the Aquarius group is a feature of a disc-satellite interaction, the perturber must have a mass on the order of a large globular cluster or a dSph satellite to produce the residual pattern in orbital energy and angular momenta.
+The Sagittarius dSph galaxy is an obvious candidate, but $\omega$-Centauri is also a possible perturber.
+On the basis on position, velocities, chemical abundances and orbit, we identify {C222531-145437} was highly likely stripped from $\omega$-Centauri in the past.
+Thus, it is plausible that $\omega$-Centauri has disrupted galactic stars as it passed through the plane, adding to any other oscillating modes rippling through the disc, resulting in what we now observe as the Aquarius stream.
 
@@
 \label{sec:conclusions}
-We have presented a detailed chemical and dynamical analysis for five members of the recently discovered Aquarius co-moving group from data taken with the MIKE spectrograph on the Magellan Clay telescope.
-Hereafter we solely refer to the discovery as a co-moving group instead of a stellar stream because we find no evidence that the group is the result of a tidally disrupted globular cluster (or dSph satellite), contrary to the claim by \citet{wylie-de-boer;et-al_2012}.
-These conclusions are drawn from a sample size comprising of a third of all the known Aquarius members.
+We have presented a detailed chemical and dynamical analysis for 5 members of the recently discovered Aquarius stream from data taken with the MIKE spectrograph on the Magellan Clay telescope.
+Hereafter we solely refer to the discovery as a co-moving group instead of a stellar stream, as we find no evidence that the group is a tidal tail of a disrupted satellite.
 The main conclusions are as follows:
@@
 \begin{itemize}
-\item The Aquarius feature is not chemically coherent. A wide spread in metallicities is observed, with [Fe/H] ranging from $-0.63$ to $-1.63$\,dex in just five candidates.
-
-\item The co-moving group shows an alpha enhancement of ${[\alpha/{\rm Fe}] = +0.40}$\,dex (+0.38 if the peculiar star {C222531-145437} is excluded), contrary to that typically observed in stars within dSph galaxies.
+\item The Aquarius stream is not mono-metallic. A wide spread in metallicities is observed, with [Fe/H] ranging from $-0.63$ to $-1.58$\,dex in just 5 members.
+
+\item No Na-O anti-correlation is observed in the Aquarius group.
+Two members have slightly enhanced levels of sodium with respect to iron.
+If the candidates were \textit{known globular cluster members}, they would be classified as belonging to either the primordial component, or at most, tenuous membership could be argued for the lower envelope of the intermediate group.
+
+\item We find a strong positive Mg-Al relationship, reminiscent of Milky Way field stars and contrary to globular cluster observations.
+
+\item We find no evidence that the Aquarius group is the result of a disrupted classical globular cluster.
+The large [Fe/H] variation severely limits the number of possible parent hosts, and both the extreme and intermediate component of the Na-O anti-correlation have not been observed.
+In total, high-resolution spectra exists for more than half of the stream.
+
+\item The co-moving group shows an $\alpha$-enhancement of ${[\alpha/{\rm Fe}] = +0.40}$\,dex, similar to the Milky Way, and distinct to that typically observed in stars in dSph galaxies with comparable metallicities.
 
 \item Aquarius members are enhanced in [Na/Fe] and [Ni/Fe] to levels typically observed in either the thick disc or globular clusters.
-These levels of [Na/Fe], [Ni/Fe] enhancement are not observed in stars from dSph galaxies either.
-Thus, on the basis of sodium, nickel, and $\alpha$-element abundances, it is unlikely the Aquarius co-moving group is the result of a tidally disrupted dSph galaxy.
-
-\item We find no evidence for Aquarius group resulting from a disrupted classical globular cluster.
-No Na-O anti-correlation is observed.
-Two candidates have slightly enhanced levels of sodium with respect to iron.
-However, we reiterate that our [Na/Fe] abundance ratios appear +0.10\,dex systematically higher than measurements made by other groups in both our program or standard stars.
-If the candidates were \textit{known globular cluster members}, they would be classified as belonging to either the primordial component, or at most, the base of the intermediate group.
-
-\item We find a positive Mg-Al relationship, also contrary to observations made in globular cluster stars.
-Given that a Na-O anti-correlation is not evident, it is perhaps unsurprising that no Mg-Al relationship is present since this chemical pattern is less prominent in globular clusters.
-
-\item If the Aquarius co-moving group is the result of a disrupted globular cluster, then the large metallicity variation within the stream severely limits the number of possible parent hosts, and both the extreme and intermediate component of the Na-O anti-correlation have still not been observed.
-
-\item One of our candidates, {C222531-145437}, has chemistry that is clearly distinct from the other Aquarius members.
-It is enhanced in light elements and shows a strong heavy element enhancement, most notably in barium where {[Ba/Fe] = 0.68}\,dex.
-We exclude the possibility that the abundance variations have resulted from an unseen AGB companion through comparisons of expected light and heavy $s$-process yields for AGB stars with a range of stellar masses at the same metallicity as {C222531-145437}.
-The position and velocity of {C222531-145437} coincides precisely where simulations by \citet{majewski;et-al_2012} suggest large amounts of $\omega$-Centurai tidal debris should be found, and its chemistry is precisely consistent with that of RGB stars in the core of $\omega$-Centurai \citep{marino;et-al_2011}.
-The data suggests that {C222531-145437} is a rare tidal debris member of the globular cluster $\omega$-Centurai.
-With a {[Fe/H]$ = -1.22$}\,dex, it matches the mean metallicity of a known sub-population within $\omega$-Centurai, and removing C222531-145437 from the Aquarius sample does not resolve the aforementioned metallicity spread.
-
-\item While no evidence exists for an accreted origin, and the Aquarius members are indistinguishable from thick disc/halo stars, we hypothesise the co-moving group is the result from a disc-satellite interaction.
-We see no coherent pattern in the $u$--$v$ plane from Monte-Carlo simulations, but the orbital energies and angular momenta for Aquarius candidates qualitatively reproduces patterns predicted by \citet{gomez;et-al_2012}.
-This is consistent with a minor merger in the Milky Way occurring perhaps up to a few Gyr ago.
-Given the location and velocity of the Aquarius group, and the identification of {C222531-145437} as a disrupted $\omega$-Centurai star, it is plausible that the Milky Way-$\omega$Cen interaction sufficiently perturbed outer disc/halo stars to produce what we now observe as the Aquarius group.
+These levels of [Na/Fe] and [Ni/Fe] enhancement are not observed in stars from dSph galaxies.
+Low [Ba/Y] abundance ratios are also observed in the Aquarius group, in conflict with chemistry of present day dSph galaxies.
+Thus, on the basis of [(Na, Ni, $\alpha$)/Fe] and [Ba/Y] abundance ratios, it is unlikely the Aquarius co-moving group is the result of a tidally disrupted dSph galaxy.
+
+% [TODO] what about C222531 in other elements with omega-Cen?
+
+\item One of our candidates, {C222531-145437}, has an abundance pattern that is clearly distinct from the other Aquarius members, most notably in barium where {[Ba/Fe] = 0.68}\,dex.
+We exclude the possibility that the abundance variations have resulted from an AGB companion.
+
+\item The position and velocity {C222531-145437} coincides precisely where simulations by \citet{majewski;et-al_2012} predict large amounts of $\omega$-Centauri tidal debris, and the orbital energy and angular momenta are consistent with the $\omega$-Centauri cluster.
+The chemical and phase-space information suggests that {C222531-145437} is a rare tidal debris member of the globular cluster $\omega$-Centauri.
+Removing C222531-145437 from the Aquarius sample does not extinguish or diminish any of the aforementioned conclusions.
+
+\item While no evidence exists for an accreted origin, and the Aquarius group members are indistinguishable from thick disc/halo stars, we hypothesise the co-moving group is the result from a disc-satellite interaction.
+We see no coherent pattern in the $U$--$V$ plane from Monte-Carlo simulations, but the orbital energies and angular momenta for the Aquarius group qualitatively reproduces patterns predicted by \citet{gomez;et-al_2012}.
+This is consistent with a minor merger in the Milky Way thick disc occurring perhaps up to a few gigayear ago.
+Given the location and velocity of the Aquarius group, and the identification of {C222531-145437} as a star tidally stripped from $\omega$-Centauri, it is plausible that the Milky Way-$\omega$Cen interaction sufficiently perturbed outer disc/halo stars to produce what we now observe as the Aquarius group.
 \end{itemize}
 
-It is clear that not all kinematic substructures are tidal tails of disrupted satellites, and that the structure of the Milky Way is indeed complex.
-While we find no chemical evidence that the Aquarius group is a tidal tail from a disrupted satellite, we propose the members are galactic in origin, and the co-moving group is a result of a disc-satellite interaction.
-Thus, while the Aquarius group has not been accreted onto the galaxy, it certainly adds to the rich level of substructure within the Milky Way.
+It is clear that not all co-moving groups are tidal tails of disrupted satellites, and that the structure of the Milky Way is indeed complex.
+While we find no chemical evidence that the Aquarius group is a tidal tail from a disrupted satellite, we propose the members are Galactic in origin, and the co-moving group is a result of a disc-satellite interaction.
+Thus, although the Aquarius group has not been accreted onto the galaxy, it certainly adds to the rich level of kinematic substructure within the Milky Way.
 
 \acknowledgements
-We are indebted to David Nidever and Steven Majewski for kindly replicating a plot from their $\omega$-Centurai simulations (Figure \ref{fig:omega-cen-tidal-debris} in this text) which helped to place {C222531-145437} in context of the cluster's tidal debris.
+We are indebted to David Nidever and Steven Majewski for kindly replicating a plot from their $\omega$-Centauri simulations (Figure \ref{fig:omega-cen-tidal-debris} in this text) which helped to place {C222531-145437} in context of the cluster's tidal debris.
 A.R.C.
-acknowledges the financial support through the Australian Research Council Laureate Fellowship LF0992131, and from the Australian Prime Minister's Endeavour Award Research Fellowship which has facilitated his research at MIT.
+acknowledges the financial support through the Australian Research Council Laureate Fellowship LF0992131, and from the Australian Prime Minister's Endeavour Award Research Fellowship, which facilitated his research at MIT.
 This publication makes use of data products from the Two Micron All Sky Survey, which is a joint project of the University of Massachusetts and the Infrared Processing and Analysis Center/California Institute of Technology, funded by the National Aeronautics and Space Administration and the National Science Foundation.
@@
 
+% [TODO] Stellar parameter uncertainties
+% [TODO] Chemical abundance uncertainties
+
 %\facilities{Magellan:Clay}

### 2013-08-13 2012-aqs/dotter_isochrones/geneva.py

@@ -1,0 +1,103 @@
+import numpy as np
+
+from galpy.potential import HernquistPotential, LogarithmicHaloPotential, MiyamotoNagaiPotential, NFWPotential, MWPotential
+from galpy.potential import plotRotcurve
+from galpy.orbit import Orbit
+
+
+r0 = 8.27   # kpc, Shoenrich 2012
+e_r0 = 0.29 # kpc, Shoenrich 2012
+v0 = 239.   # km/s, Shoenrich 2012
+e_v0 = 9.   # km/s, Shoenrich 2012
+G = 4.302e-3# pc/M (km/s)^2, Universe, The
+z0 = 0.025  # ??, Default in galpy
+e_z0 = 0.0
+
+
+# Miyamoto-Nagai Disc Potential 
+M_disc = 9.3e10 # Solar masses, Helmi et al 2006
+a_d = 6.5       # kpc, Helmi et al 2006
+b_d = 0.26      # kpc, Helmi et al 2006
+
+# Hernquist Bulge Potential
+M_bulge = 3.4e10    # Solar masses, Helmi et al 2006
+c_b = 0.7           # kpc, Helmi et al 2006
+
+# Logarithmic Halo Potential
+v_halo = 134.   # km/s, Helmi et al 2006
+halo_d = 12.    # kpc, Hemli et al 2006
+
+#ra,dec,Dist,UVel,VVel,WVel,RVel,pmRA,pmDE
+
+
+disc_potential  = MiyamotoNagaiPotential(a=a_d/r0, b=b_d/r0)
+halo_potential  = LogarithmicHaloPotential(core=halo_d/r0, normalize=0.27)
+bulge_potential = HernquistPotential(a=c_b/r0)
+
+
+timesteps = np.linspace(0, 100, 1000)
+c_ra, c_dec, c_dist, c_U, c_V, c_W, c_rvel, c_pma, c_pmde = xrange(9)
+
+data = np.loadtxt('geneva-survey-cleaned.csv', delimiter=',')
+
+linblad_data = np.zeros((len(data), 6))
+measured_uvw = np.zeros((len(data), 3))
+
+for i, line in enumerate(data):
+
+    print i
+    ra, dec, distance, U, V, W, velocity, pm_ra, pm_dec = line
+
+    distance /= 1000.
+
[…]

### 2013-08-13 2012-aqs/dotter_isochrones/measure-distances.py

@@ -1,0 +1,537 @@
+import numpy as np
+import random
+from scipy.interpolate import interp1d
+from scipy import ndimage
+
+from galpy.potential import HernquistPotential, LogarithmicHaloPotential, MiyamotoNagaiPotential, NFWPotential, MWPotential
+from galpy.potential import plotRotcurve
+from galpy.orbit import Orbit
+
+
+r0 = 8.27   # kpc, Shoenrich 2012
+e_r0 = 0.29 # kpc, Shoenrich 2012
+v0 = 239.   # km/s, Shoenrich 2012
+e_v0 = 9.   # km/s, Shoenrich 2012
+G = 4.302e-3# pc/M (km/s)^2, Universe, The
+z0 = 0.025  # ??, Default in galpy
+e_z0 = 0.0
+
+
+# Miyamoto-Nagai Disc Potential 
+M_disc = 9.3e10 # Solar masses, Helmi et al 2006
+a_d = 6.5       # kpc, Helmi et al 2006
+b_d = 0.26      # kpc, Helmi et al 2006
+
+# Hernquist Bulge Potential
+M_bulge = 3.4e10    # Solar masses, Helmi et al 2006
+c_b = 0.7           # kpc, Helmi et al 2006
+
+# Logarithmic Halo Potential
+v_halo = 134.   # km/s, Helmi et al 2006
+halo_d = 12.    # kpc, Hemli et al 2006
+
+
+disc_potential  = MiyamotoNagaiPotential(a=a_d/r0, b=b_d/r0)
+halo_potential  = LogarithmicHaloPotential(core=halo_d/r0, normalize=0.27)
+bulge_potential = HernquistPotential(a=c_b/r0)
+
+# Uncertainties
+teff_err = 125
+logg_err = 0.2
+feh_err = 0.1
+
+
+stars = [
+    {
+        'designation':  'J223811-104126',
+        'teff': 5190,
+        'teff_err': teff_err,
+        'logg': 2.93,
+        'logg_err': logg_err,
+        'feh': -1.63,
+        'feh_err': feh_err,
+
+        "v_hel": -235.7, 
+        "e_v_hel": 0.1, 
+        
+        "pmRA": -25.34, 
+        "e_pmRA": 2.1, 
+        
+        "pmDE": -99.53, 
+        "e_pmDE": 2.1,
+
+        "ra": 339.54833, 
+        "dec": -10.6915, 
+        "e_ra": 0.0,
[…]

### 2013-08-13 2012-aqs/figures/plot-alpha-fe.py

@@ -1,6 +1,8 @@
 import matplotlib.pyplot as plt
 import numpy as np
 
+
+aquarius_colors = ['c', 'g', 'm', 'r', 'b']
 # Get Na and O from files:
 data_files = ['c2225316-14437_abundances.data', 'c2306265-085103_abundances.data', 'j221821-183424_abundances.data', 'j223504-152834_abundances.data', 'j223811-104126_abundances.data']
 
@@ -19,6 +21,9 @@ e_Mg_Fe = []
 
 Fe_H = []
 e_Fe_H = []
+
+Ba_Fe = []
+e_Ba_Fe = []
 
 observed_data = {}
 for filename in data_files:
@@ -39,6 +44,11 @@ for filename in data_files:
 	idx = list(data[:,0]).index('Mg')
 	_Mg_Fe, _e_Mg_Fe = data[idx, 2:]
 
+
+
+	idx = list(data[:,0]).index('Ba')
+	_Ba_Fe, _e_Ba_Fe = data[idx, 2:]
+
 	idx = list(data[:, 0]).index('Fe')
 	_Fe_H, _e_Fe_H = data[idx, 1], data[idx, -1]
 
@@ -56,6 +66,9 @@ for filename in data_files:
 
 	Fe_H.append(_Fe_H)
 	e_Fe_H.append(_e_Fe_H)
+
+	Ba_Fe.append(_Ba_Fe)
+	e_Ba_Fe.append(_e_Ba_Fe)
 
 
 
@@ -81,18 +94,20 @@ ylim = np.array([-0.1, 0.7])
 yticks = [0.0, 0.2, 0.4, 0.6]
 
 fig = plt.figure()
-fig.subplots_adjust(left=0.10,bottom=0.10,right=0.95, top=0.95, hspace=0.0)
+fig.subplots_adjust(left=0.10,bottom=0.10,right=0.99, top=0.99, hspace=0.0)
 
 # Magnesium
-ax = fig.add_subplot(411)
-ax.scatter(Fe_H, Mg_Fe, color='k')
-ax.errorbar(Fe_H, Mg_Fe, xerr=e_Fe_H, yerr=e_Mg_Fe, fmt=None, ecolor='k')
+ax = fig.add_subplot(511)
+ax1 = ax
[…]

### 2013-08-13 2012-aqs/figures/plot-fe-peak.py

@@ -1,6 +1,8 @@
 import matplotlib.pyplot as plt
 import numpy as np
 
+aquarius_colors = ['c', 'g', 'm', 'r', 'b']
+
 # Get Na and O from files:
 data_files = ['c2225316-14437_abundances.data', 'c2306265-085103_abundances.data', 'j221821-183424_abundances.data', 'j223504-152834_abundances.data', 'j223811-104126_abundances.data']
 
@@ -16,8 +18,21 @@ e_Cr_Fe = []
 Mn_Fe = []
 e_Mn_Fe = []
 
+
+Co_Fe = []
+e_Co_Fe = []
+
+Ni_Fe = []
+e_Ni_Fe = []
+
+Cu_Fe = []
+e_Cu_Fe = []
+
+
 Fe_H = []
 e_Fe_H = []
+
+
 
 observed_data = {}
 for filename in data_files:
@@ -37,6 +52,15 @@ for filename in data_files:
 	idx = list(data[:,0]).index('Mn')
 	_Mn_Fe, _e_Mn_Fe = data[idx, 2:]
 
+	idx = list(data[:,0]).index('Co')
+	_Co_Fe, _e_Co_Fe = data[idx, 2:]
+
+	idx = list(data[:,0]).index('Ni')
+	_Ni_Fe, _e_Ni_Fe = data[idx, 2:]
+
+	idx = list(data[:,0]).index('Cu')
+	_Cu_Fe, _e_Cu_Fe = data[idx, 2:]
+
 	idx = list(data[:, 0]).index('Fe')
 	_Fe_H, _e_Fe_H = data[idx, 1], data[idx, -1]
 
@@ -52,6 +76,15 @@ for filename in data_files:
 	Mn_Fe.append(_Mn_Fe)
 	e_Mn_Fe.append(_e_Mn_Fe)
 
+	Co_Fe.append(_Co_Fe)
+	e_Co_Fe.append(_e_Co_Fe)
+
+	Ni_Fe.append(_Ni_Fe)
+	e_Ni_Fe.append(_e_Ni_Fe)
+
+	Cu_Fe.append(_Cu_Fe)
+	e_Cu_Fe.append(_e_Cu_Fe)
+
 	Fe_H.append(_Fe_H)
 	e_Fe_H.append(_e_Fe_H)
 
[…]

### 2013-08-13 2012-aqs/figures/plot-j223811-spectra.py

@@ -1,0 +1,62 @@
+import specutils
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib.gridspec as gridspec
+
+fig = plt.figure()
+
+fig.subplots_adjust(left=0.10, bottom=0.1, right=0.95, top=0.95, hspace=0.05)
+
+gs = gridspec.GridSpec(2, 1,
+                       height_ratios=[1,4]
+                       )
+
+diff_ax = plt.subplot(gs[0])
+main_ax = plt.subplot(gs[1])
+
+xlims = np.array([4305, 4316])
+
+observed = specutils.Spectrum1D.load('j223811-obs-C.fits')
+C_690 = specutils.Spectrum1D.load('j223811-6.90-C.fits')
+C_705 = specutils.Spectrum1D.load('j223811-7.05-C.fits')
+C_720 = specutils.Spectrum1D.load('j223811-7.20-C.fits')
+
+colors = 'rkb'
+C_spectra = [C_690, C_705, C_720]
+
+# Plot main
+main_ax.scatter(observed.disp, observed.flux, facecolor='k', s=1)
+
+for color, spectrum in zip(colors, C_spectra):
+    main_ax.plot(spectrum.disp, spectrum.flux, c=color, zorder=1 if color != 'k' else 10)
+
+main_ax.plot([0, 5000], [1, 1], ':k')
+main_ax.set_xlim(xlims)
+main_ax.set_ylim(0, 1.1)
+
+# Plot diff
+diff_ax.plot([0, 5000], [0, 0], ':k')
+
+for color, spectrum in zip(colors, C_spectra):
+
+    diff_flux = spectrum.interpolate(observed.disp).flux - observed.flux
+
+    diff_ax.plot(observed.disp, diff_flux, c=color, zorder=1 if color != 'k' else 10)
+
+diff_ax.xaxis.set_visible(False)
+diff_ax.set_xlim(xlims)
+diff_ax.set_ylim(-0.15, 0.15)
+diff_ax.set_yticks([-0.10, 0.0, 0.1])
+
+main_ax.set_xlabel('Wavelength, $\lambda$ (${\AA}$)')
+main_ax.set_ylabel('Flux, $F_{\lambda}$')
+
+diff_ax.set_ylabel('$\Delta{F_{\lambda}}$')
+
+main_ax.text(4309, 0.15, 'J223811-104126', color='k')
[…]

### 2013-08-13 2012-aqs/figures/plot-mg-al.py

@@ -185,24 +185,36 @@ fig.subplots_adjust(hspace=0.0, wspace=0.0, left=0.10, right=0.95, bottom=0.10, 
 ax = fig.add_subplot(111)
 
 # Draw reddy
-ax.scatter(Reddy_ThickDisk_Mg_Fe, Reddy_ThickDisk_Al_Fe, marker='+', edgecolor='k', facecolor='none', label='Thick disc (Reddy+ 2003)')
-ax.scatter(Reddy_ThinDisk_Mg_Fe, Reddy_ThinDisk_Al_Fe, marker='+', facecolor='none', edgecolor='#666666', label='Thin disc (Reddy+ 2003)')
-ax.scatter(Reddy_Halo_Mg_Fe, Reddy_Halo_Al_Fe, marker='+', facecolor='none', edgecolor='#cccccc', label='Halo (Reddy+ 2003)')
+ax.scatter(Reddy_ThickDisk_Mg_Fe, Reddy_ThickDisk_Al_Fe, s=50, marker='+', edgecolor='k', facecolor='none', label='Thick disc (Reddy et al. 2003)')
+ax.scatter(Reddy_ThinDisk_Mg_Fe, Reddy_ThinDisk_Al_Fe, s=50,  marker='+', facecolor='none', edgecolor='#666666', label='Thin disc (Reddy et al. 2003)')
+ax.scatter(Reddy_Halo_Mg_Fe, Reddy_Halo_Al_Fe, s=50,  marker='x', facecolor='none', edgecolor='#666666', label='Halo (Reddy et al. 2003)')
 
 #ax.scatter(Reddy_ThickThinDisk_Mg_Fe, Reddy_ThickThinDisk_Al_Fe, marker='o', facecolor='none', edgecolor='m')
 #ax.scatter(Reddy_ThickDisk_Halo_Mg_Fe, Reddy_ThickDisk_Halo_Al_Fe, marker='o', facecolor='none', edgecolor='orange')
 
 #ax.scatter(Reddy_2003_Mg_Fe, Reddy_2003_Al_Fe, marker='o', facecolor='none', edgecolor='#666666')
-ax.scatter(Fulbright_2000_Mg_Fe, Fulbright_2000_Al_Fe, marker='o', facecolor='none', edgecolor='#666666', label='Halo & Disc (Fulbright 2000)')
[…]

### 2013-08-13 2012-aqs/figures/plot-na-ni.py

@@ -1,6 +1,8 @@
 import matplotlib.pyplot as plt
 import numpy as np
 
+
+aquarius_colors = ['c', 'g', 'm', 'r', 'b']
 # Get Na and O from files:
 data_files = ['c2225316-14437_abundances.data', 'c2306265-085103_abundances.data', 'j221821-183424_abundances.data', 'j223504-152834_abundances.data', 'j223811-104126_abundances.data']
 
@@ -249,31 +251,37 @@ for a, b, c, d in zip(_fornax_na, _fornax_na_err, _fornax_ni, _fornax_ni_err):
 
 # Draw globular cluster data and dsph
 fig = plt.figure()
+
+fig.subplots_adjust(hspace=0.0, wspace=0.0, left=0.10, right=0.95, bottom=0.10, top=0.95)
+
 ax = fig.add_subplot(111)
 
 # Draw globular clusters
-ax.scatter(ngc_288_na, ngc_288_ni, marker='^', edgecolor='b', facecolor='none', label='NGC 288 (Shetrone & Keane, 2000)')
-ax.scatter(ngc_362_na, ngc_362_ni, marker='o', edgecolor='k', facecolor='none', label='NGC 362 (Shetrone & Keane, 2000)')
-ax.scatter(m3_na, m3_ni, marker='s', edgecolor='r', facecolor='none', label='M3 (Sneden et al. 2004)')
+ax.scatter(ngc_288_na, ngc_288_ni, s=50, marker='^', edgecolor='k', facecolor='none', label='NGC 288 (Shetrone & Keane, 2000)')
+ax.scatter(ngc_362_na, ngc_362_ni, s=50, marker='o', edgecolor='k', facecolor='none', label='NGC 362 (Shetrone & Keane, 2000)')
+ax.scatter(m3_na, m3_ni, marker='s', s=50, edgecolor='k', facecolor='none', label='M3 (Sneden et al. 2004)')
 
 # Draw fornax
-ax.scatter(fornax_na, fornax_ni, marker='v', edgecolor='g', facecolor='none', label='Fornax (Letarte et al. 2010)')
[…]

### 2013-08-13 2012-aqs/figures/plot-na-o-cluster.py

@@ -1,0 +1,295 @@
+import matplotlib.pyplot as plt
+import numpy as np
+
+
+# Caretta et al. 2009 GIRAFFE DATA
+
+Carretta_Cluster, Carretta_Fe_H, Carretta_O_Fe, Carretta_Na_Fe, Carretta_Na_limit = np.loadtxt('Carretta_2009-O-Na.csv', delimiter='|',
+	usecols=(0, 1, 3, 6, 5), dtype=str, unpack=True)
+#Carretta_O_Fe, Carretta_Na_Fe, Carretta_Cluster, Carretta_Fe_H = np.loadtxt('Carretta_2009a.data', delimiter='|', usecols=(-3, -2, 2, -7), dtype=str, unpack=True)
+
+fontsize=8.
+
+delete_rows = []
+for i in xrange(len(Carretta_Cluster)):
+
+	O_Fe = Carretta_O_Fe[i].strip()
+	Na_Fe = Carretta_Na_Fe[i].strip()
+
+	if len(O_Fe) * len(Na_Fe) == 0:
+		delete_rows.append(i)
+
+
+Carretta_Cluster = map(float, np.delete(Carretta_Cluster, delete_rows))
+Carretta_Fe_H = map(float, np.delete(Carretta_Fe_H, delete_rows))
+Carretta_O_Fe = map(float, np.delete(Carretta_O_Fe, delete_rows))
+Carretta_Na_limit = map(lambda x: x.count('<'), np.delete(Carretta_Na_limit, delete_rows)) # 1 = True, 0 = False
+Carretta_Na_Fe = map(float, np.delete(Carretta_Na_Fe, delete_rows))
+
+unique_clusters = np.unique(Carretta_Cluster)
+
+data_files = ['c2225316-14437_abundances.data', 'c2306265-085103_abundances.data', 'j221821-183424_abundances.data', 'j223504-152834_abundances.data', 'j223811-104126_abundances.data']
+
+O_Fe = []
+e_O_Fe = []
+
+Na_Fe = []
+e_Na_Fe = []
+
+observed_data = {}
+for filename in data_files:
+
+	data = np.loadtxt(filename, dtype=str, usecols=(0, -4, -2,))
+	observed_data[filename] = data
+
[…]

### 2013-08-13 2012-aqs/figures/plot-spectra.py

@@ -4,11 +4,11 @@ import numpy as np
 from specutils import Spectrum1D
 
 accompaning_texts = [
-        "C2225316-14437\t\t\t4365 / 1.25 / $-$1.22",
-        "C2306265-085103\t\t\t4225 / 0.85 / $-$1.13",
-        "J221821-183424\t\t\t4630 / 0.88 / $-$1.58",
-        "J223504-152834\t\t\t4650 / 2.16 / $-$0.63",
-        "J223811-104126\t\t\t5190 / 2.93 / $-$1.63"
+        "C2225316-14437\t\t$T_{\\rm eff}$ = 4365 K, $\log{g}$ = 1.25, [Fe/H] = $-$1.22",
+        "C2306265-085103\t\t$T_{\\rm eff}$ = 4225 K, $\log{g}$ = 0.85, [Fe/H] = $-$1.13",
+        "J221821-183424\t\t$T_{\\rm eff}$ = 4630 K, $\log{g}$ = 0.88, [Fe/H] = $-$1.58",
+        "J223504-152834\t\t$T_{\\rm eff}$ = 4650 K, $\log{g}$ = 2.16, [Fe/H] = $-$0.63",
+        "J223811-104126\t\t$T_{\\rm eff}$ = 5190 K, $\log{g}$ = 2.93, [Fe/H] = $-$1.43"
         ]
 
 spectrum_filenames = ['c2225316-14437_rest.fits', 'c2306265-085103_rest.fits', 'j221821-183424_rest.fits', 'j223504-152834_rest.fits', 'j22381-104126_rest.fits']

### 2013-08-13 2012-aqs/figures/plot-x-on-fe.py

@@ -1,0 +1,164 @@
+import matplotlib.pyplot as plt
+import numpy as np
+
+# Get Na and O from files:
+filenames = ['c2225316-14437_abundances.data', 'c2306265-085103_abundances.data', 'j221821-183424_abundances.data', 'j223504-152834_abundances.data', 'j223811-104126_abundances.data']
+
+aquarius_colors = ['c', 'g', 'm', 'r', 'b']
+
+# Make sure 'Fe I' is one of the species
+species_to_plot = ['Sc II', 'V I', 'Cr I', 'Mn I', 'Fe I']
+species_to_plot = ['Na I', 'Al I', 'K I', 'Fe II', 'Co I', 'Cu I', 'Zn I', 'Sr I', 'Y II', 'Zr I|Zr II',
+'Ba II', 'La II', 'Ce II', 'Nd II', 'Eu II', 'Fe I']
+
+species_to_plot = ['Zn I', 'Sr I', 'Y II', 'Zr I|Zr II',
+'Ba II', 'La II', 'Ce II', 'Nd II', 'Eu II', 'Fe I']
+
+
+abundances = np.zeros((len(filenames), len(species_to_plot)))
+uncertainties = np.zeros((len(filenames), len(species_to_plot)))
+
+# Fill with nan's as default
+abundances[:, :] = np.nan
+uncertainties[:, :] = np.nan
+
+Fe_I_index = species_to_plot.index('Fe I')
+
+for i, filename in enumerate(filenames):
+
+    data = np.loadtxt(filename, dtype=str, usecols=(0, 1, -6, -4, -2, ))
+
+    for j, species in enumerate(species_to_plot):
+
+        full_species = [' '.join(row).replace('\\textsc{', '').rstrip('}') for row in data[:, :2]]
+
+        # Is this a mixed species?
+        mixed_species = species.split('|')
+        for mixed_specie in mixed_species:
+            idx = full_species.index(mixed_specie)
+
+            if mixed_specie == 'Fe I':
+                data_slice = [data[idx, 2], data[idx, 4]]
+            else:
+                data_slice = data[idx, 3:5]
+
+            abundance, uncertainty = map(float, [value.replace('$', '').replace('\\', '').replace('nodata', 'nan') for value in data_slice])
+
[…]

### 2013-08-13 2012-aqs/figures/plot_omega_ba_fe.py

@@ -1,0 +1,164 @@
+
+# OMEGA CEN DATA
+# Francois 1988
+fr_feh, fr_e_feh, fr_bah, fr_e_bah = np.loadtxt('omegaCen_francois_1988.data', usecols=(1,2,3,4,), delimiter=',', unpack=True)
+fr_bafe = fr_bah - fr_feh
+fr_e_bafe = pow(pow(fr_e_feh, 2) + pow(fr_e_bah, 2), 0.5)
+
+# Smith 2000
+sm_logfe, sm_e_logfe, sm_logba, sm_e_logba = np.loadtxt('omegaCen_smith_2000.data', usecols=(1,2,3,4,), delimiter=',', unpack=True)
+sm_feh = sm_logfe - 7.5
+sm_bah = sm_logba - 2.18
+sm_bafe = sm_bah - sm_feh
+sm_e_feh = sm_e_logfe # Approx
+sm_e_bafe = pow(pow(sm_e_feh, 2) + pow(sm_e_logba, 2), 0.5)
+
+# Norris & Da Costa
+
+# HALO DATA
+
+# Reddy et al. 2003 + 2005
+rd03_feh, rd03_bafe = np.loadtxt('Reddy_disk_2003.data', usecols=(4, 35,), delimiter='|', dtype=str, comments='#', unpack=True)
+
+idx = np.where(np.array(map(len, [item.strip() for item in rd03_bafe])) > 0)[0]
+rd03_feh = np.array(map(float, rd03_feh[idx]))
+rd03_bafe = np.array(map(float, rd03_bafe[idx]))
+
+
+rd05_feh, rd05_bah = np.loadtxt('Reddy_thick_disk_2005.data', usecols=(18, 36), delimiter='|', dtype=str, comments='#', unpack=True)
+idx = np.where(np.array(map(len, [item.strip() for item in rd05_bah])) > 0)
+rd05_feh = np.array(map(float, rd05_feh[idx]))
+rd05_bah = np.array(map(float, rd05_bah[idx]))
+
+rd05_bafe = rd05_bah - rd05_feh
+
+# Fulbright 2000
+with open('Fulbright_2000.data', 'r') as fp:
+    content = fp.readlines()
+    fb_feh = []
+    fb_bafe = []
+
+    for line in content:
+        if line.startswith('#'): continue
+        try:
+            feh, bah = map(float, [line[8:13], line[87:92]])
+        except:
+            continue
+        else:
[…]
